### 2017-09-17 manuscript/CI_interactions.tex
Partial manuscript

\documentclass[12pt]{article} 
\usepackage{amsmath} 
\usepackage[dvips]{graphicx}
\usepackage{multirow} 
\usepackage{geometry} 
\usepackage{pdflscape}
\usepackage[labelfont=bf]{caption} 
\usepackage{setspace}
\usepackage[running]{lineno} 
% \usepackage[numbers,sort]{natbib}
\usepackage[round]{natbib} 
\usepackage{array}

\newcommand{\methods}{\textit{Materials \& Methods}}
\newcommand{\SI}{\textit{Appendix}~}

\topmargin -1.5cm % 0.0cm 
\oddsidemargin 0.0cm % 0.2cm 
\textwidth 6.5in
\textheight 9.0in % 21cm
\footskip 1.0cm % 1.0cm

\usepackage{authblk}

\title{???A quantitative framework for investigating the reliability of network construction}

\author{Dominique Gravel, D. Carstensen, Timoth\'{e}e Poisot, Daniel B. Stouffer, \& Alyssa R. Cirtwill$^{1}$, others??}
\date{\small$^1$Department of Physics, Chemistry\\ 
and Biology (IFM)\\ 
Link\"{o}ping University\\
Link\"{o}ping, Sweden\\
% \medskip
% $^\dagger$ Corresponding author:\\
% alyssa.cirtwill@gmail.com\\
% +46 723 158464\\
 }

\renewcommand\Authands{ and }

\begin{document} 
\maketitle 
\raggedright
\setlength{\parindent}{15pt}

\section*{Abstract}

% A quantitative framework for investigating the reliability of network construction
% D. Gravel, D. Carstensen, T. Poisot, D. Stouffer, A. Cirtwill

\section*{Introduction}

    % Present Salix data with holes as an example of uncertainty in data. Focus just on the white and grey, ignore uncertainty in the blacks

    Ecological networks-- which include antagonistic food webs and host-parasite networks as well as plant-pollinator and plant-frugivore mutualist networks --are usually considered to be static representations of the communities and interactions they describe. That is, whether the network is assembled based on aggregated data, a single intensive "snapshot" sample, or expert knowledge, interactions are assumed to occur at constant frequencies~\citep{Olesen2011a}. This assumption conflicts with known variation in interactions over time~\citep{Kitching1987,Olesen2011a} and space~\citep{Kitching1987,Baiser2012} and between individuals of a given species~\citep{Pires2011a,Fodrie2015,Novak2015}. Taking the variances in interaction frequencies into account would therefore represent a substantial increase in the realism of ecological networks as representations of ecological communities.

    Efforts to account for variance in interaction frequencies are complicated by the fact that not only interaction frequencies but network structure vary over space and time. Community composition and species abundances vary from site to site~\citep{Baiser2012} and over time within a site~\citep{Olesen2011a}. Moreover, interactions between species may change even if the participating species remain present at a site but do not co-occur temporally or are too rare to detect each other~\citep{Tylianakis2010}, or through changes to individual preferences~\citep{Fodrie2015}. Several researchers have pointed to the importance of sampling intensity for the assessment of network structure (e.g.,~\citealp{}). The acknowledgement that insufficient sampling effort limits our ability to describe variation in ecological networks has not, however, led to a quantitative framework to deal with the uncertainty of ecological interactions and of sampling.

    The main objective of this study is to develop analytical tools that could be used to better represent the uncertainty in the estimation of pairwise interaction probability. We start with the description of a new Bayesian approach to estimate ecological interactions and of a related R package. We first illustrate the framework with simple quantitative examples, followed by an assessment of the quality of an empirically-estimated plant-pollinator network. Next, we use the framework to provide analytical criteria for improving the sampling of rare interations. Finally, we discuss the implications of uncertainty in the estimation of pairwise interactions on the properties of ecological networks. Through these efforts, we demonstrate both the utility of our approach and the importance of acknowledging the uncertainty inherent in ecological networks.

% <!-- ## Background

%   - Ecological interaction networks are usually considered deterministic, but nature is highly variable and interactions should be considered with their variance
%   - There is spatial and temporal variability in network structure and of pairwise interactions
%   - There used to be a debate on the importance of sampling intensity for the assessment of network structure, but it never led to a quantitative framework dealing with uncertainty of ecological interactions and of sampling

% ## Objective:

%   - The main objective of this study is to develop analytical tools that could be used to better represent the uncertainty in the estimation of pairwise interaction probability
%   - We start with the description of a new bayesian approach to estimate ecological interactions and of a related R package. 
%   - We illustre the framework with simple quantitative examples, and then with the assessment of the quality of an empirical estimate of plant-pollinator networks. 
%   - We further use the framework to provide analytical criteria for improving the sampling of rare interations. 
%   - We discuss the implications of the uncertainty in the estimation of pairwise interactions on the properties of ecological networks -->

\section*{Pairwise interactions as a Bernoulli process}

    We consider the occurrence of an ecological interaction as a stochastic process. Provided that the two species could interact, this interaction could happen with a given probability. This probability is likely to be less than one (i.e., the interaction may not occur) because i) the two species may not encounter each other during a given time interval and within a given area, ii) there may be unknown environmental drivers affecting the realization of the interaction or iii) a third species might interfere and prevent the interaction from happenning (Poisot2015).

    We consider that the occurrence of an interaction is a Bernoulli trial. We define $\theta$ as the probability that two species interact with each other. Consequently, the number of success $X = k$ over $n$ trials will follow a binomial distribution:

    \begin{equation}
      X \sim Bin(n,\theta) ,
    \end{equation}

    \noindent and

    \begin{equation}
       P(X = k|\theta,n) = {n \choose k}\theta^k(1-\theta)^{n-k} . 
       \label{likelihood}
    \end{equation}

    \noindent The parameter $\theta$, the probability of observing an interaction over a given time interval
    and area, is the quantity we want to estimate from empirical data. The variance of a 
    Bernoulli experiment is simply n$\theta$(1-$\theta$).

    The maximal likelihood estimate of $\theta$ is straightforward to find given $X=k$ and $n$. It is simply equal to:

    \begin{equation}
      \theta_{MLE} = \frac{k}{n}  .
      \label{theta_MLE}
    \end{equation}

    It is possible to compute the confidence interval for this estimate using any of several methods, including the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull Interval}. Finding this estimate is therefore quite straightforward, but it nonetheless has two drawbacks. First, $\theta$ is a random variable with a given uncertainty and whose distribution is unknown, it is not a single point estimate. Second, the number of trials $n$ might be very low in many instances (and some pairs of species might even not be documented), and consequently the uncertainty in the estimation of $\theta$ might be considerable. We therefore propose a Bayesian approach to solve these two problems.

    % Add section explaining process variation and detection probability here, how that will affect our ability to estimate.

  \section*{Bayesian approach to infer interaction probabilities}

    \subsection*{Posterior distribution of the interaction probability}

  We adopt a bayesian approach to estimate the distribution of the parameter $\theta$. According to Bayes principle, the posterior distribution of $\theta$ is:

  \begin{equation}
    \underbrace{P(\theta|X,n)}_{Posterior} = \frac{\overbrace{P(X|\theta,n)}^{Likelihood}\overbrace{P(\theta)}^{Prior}}{\underbrace{P(X|N)}_{Normalizer}} .
    \label{posterior}
  \end{equation}

  According to the above description, the likelihood is simply the binomial distribution (Eq.~\ref{likelihood}). Since $\theta$ is a probability it is bounded between 0 and 1 and consequently the most appropriate prior distribution is the beta:

    \begin{equation}
      \theta \sim Beta(\alpha,\beta) , \label{prior}
    \end{equation}

  \noindent which has two shape parameters, $\alpha$ and $\beta$.

  It might be complicated in many cases to compute the normalizer, but fortunately there is an analytical solution to the normalizer. The beta-binomial distribution is a conjugate distribution of the binomial distribution. This allows us to analytically compute the posterior distribution of a binomial model with a beta prior distribution. We can re-write the posterior distribution of $\theta$ as:

  \begin{equation}
    P(\theta|k,n) = \frac{\theta^{\alpha+k-1}(1-\theta)^{\beta+n-k-1}}{B(\alpha+k,\beta+n-k)} , \label{posterior}
  \end{equation}

  \noindent where the function $B$ is the beta function:

  \begin{equation}
    Beta(\alpha+k,\beta+n-k) = \frac{\Gamma(\alpha+k)\Gamma(\beta+n-k)}{\Gamma(\alpha+\beta+n)} . \label{betafunction}
  \end{equation}

  The posterior distribution of $\theta$ therefore follows the beta distribution with new parameters $\alpha'= \alpha+k$ and $\beta'=\beta+n-k$. The weight of the prior on the posterior distribution is understood from these definition of the parameters: the difference between the posterior and the prior will increase with $k$ and $n-k$. When plotted, we find the shape of the distribution gets narrower with $k$ and $n$ (see Fig X).

  The posterior distribution of $\theta$ could be computed with R with the following command:

  \vspace{12pt}
  \noindent\emph{dbeta(x = theta, shape1 = alpha+k, shape1 = beta+n-k)}
  \vspace{12pt}

  \subsection*{Moments and other properties}

  The fact that the posterior distribution of $\theta$ follows a beta distribution makes it straightforward to compute moments and other properties.

  The \textbf{average} of $\theta$ is: 
      \begin{equation}
        \bar{\theta} = \frac{\alpha+k}{\alpha+\beta+n} ,
        \label{mean}
      \end{equation}

    and its \textbf{variance} is:  
      \begin{equation}
        Var(\theta|k) = \frac{(\alpha + k)(\beta + n - k)}{(\alpha + \beta + n)^{2}(\alpha + \beta + n +1)}
        \label{variance}
      \end{equation}

    The \textbf{mode} of the distribution (which is not necessarily the maximum likelihood estimate) is:
      \begin{equation}
        \hat{\theta} = \frac{\alpha + k - 1}{\alpha + \beta + n - 2} .
        \label{mode}
      \end{equation}

  \subsection*{The prior distribution}

  Parameters $\alpha$ and $\beta$ determine the shape of the prior distribution, which follows a beta distribution. These are call hyper parameters. We identify at least four ways to formulate the prior distribution of $\theta$.

    \subsubsection*{Uninformative prior}

      In absence of any external information, an uniformative prior is the most conservative 
      hypothesis for the distribution of $\theta$. The beta distribution is uninformative and follows 
      a uniform distribution for $Beta(\alpha=1,\beta=1)$.

    \subsubsection*{Distribution of connectance}

      There is now a great collection of ecological network data for which know the distribution of connectance. Connectance of a network is measured as $C = L/S^2$, where $L$ is the number of links and $S$ is the number of species. It measures the filling of an interaction matrix and also expresses the average probability that any two species interact with each other. If one  knows only the mean $\overline{C}$ and the variance $\sigma_C^2$ of the distribution of $C$, then the beta parameters could be computed as follows using the method of moments:

  \begin{equation}
    \alpha = \overline{C}(\frac{\overline{C}(1-\overline{C})}{\sigma_C^2}-1) ,
  \end{equation}

  \begin{equation}
    \beta = (1-\overline{C})(\frac{\overline{C}(1-\overline{C})}{\sigma_C^2}-1) .
  \end{equation}

  It is also possible to compute maximum likelihood estimates for a sample of the distribution of $C$. The following piece of R code provides an example:

  \vspace{12pt}
  \noindent\emph{
    library(MASS)\\
    pars = fitdistr(x = vecC, "beta", start = list(shape1 = 1, shape2 = 1))\$estimate
  }
  \vspace{12pt}

  Where $vecC$ is a vector of known connectances for a set of networks.

  \subsubsection*{Degree distribution}.

  Connectance is an average property for a given network, it represents the expected degree standardized by the number of species in the network. The standardized degree could therefore be interpreted as an interaction probability. It is consequently possible to use the degree distribution to fuel the prior distribution. The degree distribution could come from several networks, or from the network of interest if interaction probabilities for some species are already documented. The latter approach allows us to apply information from known, abundant species to the rarest species for which interactions are less frequently documented. The procedure for the estimation of the hyper parameters follows exactly the same approach as described above for connectance except that each measurement is at the species level instead of the network level.

  \subsubsection*{Trait-matching function}.

  It is possible to estimate the probability of interaction between a pair of species if there is knowledge of their traits and some functions relating trait matching to interaction probability (Morales-Castilla2015). There are several techniques published to perform this inferrence of interaction probability (REFS). Note that in this case the prior might not be beta distribution and numerical methods might be required to compute the posterior distribution.

\section*{A quantitative example}

The framework is best illustrated with a simple quantiative example. Suppose we have $n = 10$ observations of co-occurrence between speices $i$ and species $j$ in a given time interval and area, and $X = 2$ observations of interactions. The maximum likelihood estimate of the interaction probability is simply $\theta_{MLE} = 2/10 = 0.2$.  Now consider we know that species $i$ is known to interact with 10 other species, which have the following standardized degrees:

\vspace{12pt}
\noindent\emph{
    degree = c(0.66, 0.09, 0.06, 0.08, 0.04, 0.30, 0.06, 0.38, 0.03, 0.19)
    }.
  \vspace{12pt}

Using these standardized degrees to inform our prior expectation of the 
distribution of interaction probabilities and the R code from the 
connectance example, we obtain prior parameters $\alpha$=0.9034876 
and $\beta$=3.6623995. Using these priors in equations~\ref{mean} 
and~\ref{variance} above, we find an average interaction probability of 0.1993348 and a variance of 0.01025322 [[Different from Dom's values]].
% n=number of observed co-occurances.
The average interaction probability is 0.2163971 and the variance is 0.02353319. The hyper parameters are computed according to the following script, using the function \emph{fitdistr} from the R~\citep{R} package MASS~\citep{MASS}, yielding:

\vspace{12pt}
\noindent\emph{    pars = fitdistr(x = degree, "beta", start = list(shape1 = 1, shape2 = 1),lower=c(0,0))\$estimate }.
  \vspace{12pt}

The lower bound of (0,0) for the two parameters of the Beta distribution prevents the function from attempting to fit invalid (negative) parameter estimations.

The average of the distribution is computed as follows:

  \vspace{12pt}
\noindent
\emph{
    \noindent n = 10
    \\\noindent k = 2
    \\\noindent alpha\_prime = alpha + k
    \\\noindent beta\_prime = beta + n - k
    \\\noindent mean\_theta = alpha\_prime/(alpha\_prime+beta\_prime)
},
  \vspace{12pt}

which yields a value $E[\theta]=0.2057651$ [[I get 0.1993348]]. And the variance:

  \vspace{12pt}
\noindent\emph{alpha\_prime$\times$ beta\_prime\/(alpha\_prime+beta\_prime)$^2$\/(alpha\_prime+beta\_prime+1)},
  \vspace{12pt}

which yiealds a value $var[\theta] = 0.009579623$. [[I get 0.01025322]]

The credible interval is not symmetric around the mean since the distribution is bounded between 0 and 1 and is not symmetric. In this case, a 95\% credible interval for the mean of theta is (0.0448479, 0.4308686) and can be computed using the quantile function \emph{qbeta}:

  \vspace{12pt}
\noindent\emph{
    \noindent lowCI = qbeta(p = 0.025, shape1 = alpha\_prime, shape2 = beta\_prime)
    \\\noindent highCI = qbeta(p = 0.975, shape1 = alpha\_prime, shape2 = beta\_prime)}.
  \vspace{12pt}

Now, consider the case where the two species have never been observed interacting across $n$ trials. The question is then "what is the probability these two species do not interact"? Since it will never be possible to prove that the two species could never interact, given the framework above we must fix a threshold below which we consider that there is no interaction. Let this threshold probability be called $\theta*$. We use the cumulative distribution function to estimate $P(\theta<\theta*|X=0,n)$. The following script illustrates this probability for an increasing number of trials and $\theta*$=0.1:

  \vspace{12pt}
\noindent\emph{
    \noindent n = seq(0,100,1)
    \\\noindent X = 0
    \\\noindent theta\_star = 0.1
    \\\noindent cdf = pbeta(theta\_star, shape1 = alpha+X, shape2 = beta+n-X)
    \\\noindent plot(n,cdf, type = "l", xlab = "n", ylab = "Cumulative distribution")
    \\\noindent abline(h = 0.95,lty = 3)}.
  \vspace{12pt}

These trials yield a surprising result: it requires \textgreater30 [[or 23??]] observations of no interactions to be 95\% sure that the interaction probability is smaller than 0.1. Note the special case where there is no observation of the two species co-occurring and failing to interact, $n = 0$. In this situation, the posterior distribution converges to the prior distribution.

\section*{Case study: estimating the uncertainty of a plant-herbivore network}

    \subsection*{Description of the data}

      \emph{Salix}-galler-parasitoid meta-network, here focusing on the smaller \emph{Salix}-galler network. The meta-network consists of interactions between 52? \emph{Salix} species and 222 species of gall-forming insects, sampled from 374 locations in Europe ranging from Sicily to the Arctic. In total, 4295 unique interactions were observed. Each of the 374 locations can be considered as a network in its own right, but here we consider each network as an independent sample from which to build the meta-network.

  \subsection*{Finding the maximum likelihood estimate}

      In a strict Bayesian framework, we wish to use a prior distribution that does not rely on any information from the study at hand. To that end, we use data from another well-described \emph{Salix} galler-parasitoid system (doi: 10.1073/pnas.1513633113). Note that this study used several genotypes of \emph{S. hookeriana} rather than different \emph{Salix} species. We take the degree distributions of four Cecidomyid galler species across \emph{S. hookeriana} genotypes as our prior distribution for the probability of interactions between gallers and \emph{Salix} species. Note that as an interaction frequency depends on the product of the degree of the galler and the degree of the plant involved, we wish to use as our prior the product of the degree distributions of plants and gallers.
      Unfortunately, the product of two beta distributions is not beta-distributed. Instead, we will use the list of interaction probabilities, obtained by multiplying the two degree distributions.

      The degree distribution across \emph{S. hookeriana} genotypes was calculated from data deposited in Dryad using the following R code:

      prior_web=read.csv(path_to_Dryad_file)
      deg_dist_Salix=with(prior_web,tapply(gall_total_rich,Genotype,mean))/4
      gallers=cbind(prior_web$Genotype,prior_web[,27:30])
      aSG_means=with(prior_web,tapply(aSG_abund,Genotype,mean))
      rG_means=with(prior_web,tapply(rG_abund,Genotype,mean))
      vLG_means=with(prior_web,tapply(vLG_abund,Genotype,mean))
      SG_means=with(prior_web,tapply(SG_abund,Genotype,mean))
      deg_dist_galler=c(length(which(aSG_means>0)),length(which(rG_means>0)),length(which(SG_means>0)),length(which(rG_means>0))      )/26
      int_probs=as.numeric(deg_dist_galler\%*\%t(deg_dist_Salix))

      pars=fitdistr(x=int_probs,"beta",start=list(shape1=1,shape2=1))$estimate
      alpha=pars[[1]]
      beta=pars[[2]]
      mu=alpha/(alpha+beta)
      num=alpha*beta
      den=(alpha+beta)**2*(alpha+beta)
      sigma2=num/den

      Using this degree distribution we can obtain prior values for $\alpha$ and $\beta$ using the code above. We obtain
      $\alpha$=2.175656, $\beta$=5.361083.

      For species where no co-occurances were observed, we can calculate the MLE estimates for the mean and variance of $\omega_{ij}$ directly from this prior. These are:
      $\hat{\omega_{ij}}$=0.2886734, var($\omega$)=0.02724535.

      For a pair of species where some co-occurances were observed, we base these estimates on the prior distribution above conditioned by the available data. If we consider only pairs of species which were observed to co-occur but not to interact, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs. Thus $\alpha'$=$\alpha$ and $\beta'$=$\beta + n$. At the most extreme case, for a pair of species which co-occurred at all 374 sites and was never observed to interact, our distribution would become:

      $\hat{\omega_{ij}}$=0.005702349, var($\omega$)=1.486051e-05.

      Realistic values for n when k=0, based on a sample of 20 random sites:
      n=1: 0.25485794 0.02224566
      n=2: 0.22813413 0.01846427
      n=3:
      n=4:

    \subsection*{Computing the posterior distribution}

  \subsection*{Computing the confidence interval around a probability estimate}

    \subsection*{How many samples are required to reach a minimal precision}

\clearpage

    \bibliographystyle{ecollett} 
    \bibliography{manual_abbrev} % Abbreviate journal titles.

\end{document}

### 2017-09-17 manuscript/CI_interactions.tex
Section2 on definitions

@@
     % Add section explaining process variation and detection probability here, how that will affect our ability to estimate.
+
+\section{Why some interactions do not occur ?}
+
+It is getting more and more common to represent interactions as probabilities.
+Some theoretical models of network structure propose to represent interactions with probabilities, for instance the minmum potential model introduces gaps in the feeding niche of predators (Allesina et al.
+2008), while a gaussian probability function is used to represent the niche by Williams et al.
+(2010).
+Eklof et al.
+(2013) introduced variability as well in the computation of network dimensions, allowing the absence of interactions within the n-dimension niche of every species.
+Empirical investigation of trait-matching constraints often consider the occurrence of interactions as binomial process (e.g.
+Rohr et al.
+2016).
+There are also ways to perform analysis of probabilistic networks, with almost all metrics having a probabilistic version (Poisot et al.
+2015).
+But there is not yet consensus on what an interaction probability between a pair of species means, and this is definitely a problem when comes time to estimate the uncertainty of both pairwise interactions and entire networks.
+
+Starting from the problem described in the previous section, we consider that a pair of species have been observed $n$ times co-occurring at one location, and the number of times they interact is $k = 0$.
+We aim to evaluate the uncertainty of this interaction.
+What this is mean exactly ?
+We consider there are three nested level of uncertainty making this phenomenon a stochastic process :
+
+\textit{Interaction uncertainty} First, and most fundamentally, we do not know if these species have the appropriate characteristics to interact or not.
+We define the probability of an interaction $L$ as $P(L)=\lambda$.
+Obviously, because $k=0$, it is very likely they can not interact if provided enough time and there were no environmental constraint for this interaction to happen.
+But it is nonetheless possible the interaction is a rare phenomenon that has never been documented before.
+This source of uncertainty is the one documented by trait-matching models.
+It arises because every model is imperfect and lack information (i.e.
+traits) about the constraints on the interaction.
+In other words, with sufficient sampling and all information accessible, this interaction probability should either tend to 0 or to 1 and the uncertainty vanish.
+
+\textit{Process uncertainty} It could happen that the interaction is feasible, i.e.
+$L=1$, but that it does not occur at a given location or at a moment in time because there are local constraints preventing it to occur.
+We define the realization of the interaction process $X$ given an interaction is feasible as a stochastic process with associated probability $P(X|L)=\chi$.
+This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology about the contingencies of interactions.
+We imagine for instance that an interaction between a gall and a parasitoid is not recorded at a location because it was the wrong time of the year and the gall has not yet formed (phenological constraints), because a late frost killed the larvae (an abiotic environmental constraint) , another parasitoid species competitively excluded the parasitoid species of interst (a biotic environmental constraint) or simply the parasitoid is too rare (an abundance constraint).
+
+\textit{Detection uncertainty} Lastly, measurement errors are always source of uncertainty in the observation of ecological processes.
+We define the detection of an interaction $D$, given an interaction is feasible and occurs in the local conditions, as a stochastic process with associated probability $P(D|X,L)=\delta$.
+Detection failure could happen for several reasons, for instance if the rearing of a parasitoid fails with inappropriate lab conditions or because of species mis-identification.
+Some source of detection error could be minimized with appropriate sampling effort ($\chi$ will converge to one with increasing number of collected galls), but other sources are often difficult to reduce (e.g.
+the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification).
+
+\textit{What is an observation of "no interaction" ?} The combination of these three sources of uncertainty together leads to many potential explanations for the observation of an absence of interaction, but only the situation where $L = 0$ is a true absence therefore is relevant for the investigation of networks.
+While the observation of an interaction is straightforward to interpret, absence of interactions must be decomposed in different quantities.
+It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e.
+the interaction occurred at the location but was not observed, and $D=1 \cup X = 0 \cup L =1$, the interaction would have been detected but did not occur.
+
+It is important to keep in mind that for network analysis, ecologists seek to measure the occurrence of true absences, which is the joint event $L=1\cup X=1 \cup \D=1$), but in reality they measure the marginal probability $P(L) = k/n$.
+This reasonning explains why the above describe MLE estimation of the interaction probability is naive, and could be inappropriate in many instances, in particular when we have no knowledge of the detection and the process uncertainties.
 

### 2017-09-17 manuscript/CI_interactions.tex
changes to the ms outline

@@
 
-\section*{Pairwise interactions as a Bernoulli process}
+\section*{Different uncertainties in computing a network}
 
-    We consider the occurrence of an ecological interaction as a stochastic process.
-Provided that the two species could interact, this interaction could happen with a given probability.
-This probability is likely to be less than one (i.e., the interaction may not occur) because i) the two species may not encounter each other during a given time interval and within a given area, ii) there may be unknown environmental drivers affecting the realization of the interaction or iii) a third species might interfere and prevent the interaction from happenning (Poisot2015).
+THIS SECTIONS BUILDS ON THE SALIX DATA TO ILLUSTRATE THE GAPS THERE ARE IN THE METHOD. DESPITE THE INTENSITY OF THE SAMPLING, THERE ARE SEVERAL HOLES.
 
-    We consider that the occurrence of an interaction is a Bernoulli trial.
-We define $\theta$ as the probability that two species interact with each other.
-Consequently, the number of success $X = k$ over $n$ trials will follow a binomial distribution:
-
-    \begin{equation}
-      X \sim Bin(n,\theta) ,
-    \end{equation}
-
-    \noindent and
-
-    \begin{equation}
-       P(X = k|\theta,n) = {n \choose k}\theta^k(1-\theta)^{n-k} . 
-       \label{likelihood}
-    \end{equation}
-
-    \noindent The parameter $\theta$, the probability of observing an interaction over a given time interval
-    and area, is the quantity we want to estimate from empirical data. The variance of a 
-    Bernoulli experiment is simply n$\theta$(1-$\theta$).
-
-    The maximal likelihood estimate of $\theta$ is straightforward to find given $X=k$ and $n$. It is simply equal to:
-
-    \begin{equation}
-      \theta_{MLE} = \frac{k}{n}  .
-      \label{theta_MLE}
-    \end{equation}
-
-    It is possible to compute the confidence interval for this estimate using any of several methods, including the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull Interval}.
-Finding this estimate is therefore quite straightforward, but it nonetheless has two drawbacks.
-First, $\theta$ is a random variable with a given uncertainty and whose distribution is unknown, it is not a single point estimate.
-Second, the number of trials $n$ might be very low in many instances (and some pairs of species might even not be documented), and consequently the uncertainty in the estimation of $\theta$ might be considerable.
-We therefore propose a Bayesian approach to solve these two problems.
-
-    % Add section explaining process variation and detection probability here, how that will affect our ability to estimate.
-
-\section{Why some interactions do not occur ?}
+\section*{Why some interactions do not occur ?}
 
@@
 This reasonning explains why the above describe MLE estimation of the interaction probability is naive, and could be inappropriate in many instances, in particular when we have no knowledge of the detection and the process uncertainties.
+
+\section*{Pairwise interactions as a Bernoulli process}
+
+    We consider the occurrence of an ecological interaction as a stochastic process.
+Provided that the two species could interact, this interaction could happen with a given probability.
+This probability is likely to be less than one (i.e., the interaction may not occur) because i) the two species may not encounter each other during a given time interval and within a given area, ii) there may be unknown environmental drivers affecting the realization of the interaction or iii) a third species might interfere and prevent the interaction from happenning (Poisot2015).
+
+    We consider that the occurrence of an interaction is a Bernoulli trial.
+We define $\theta$ as the probability that two species interact with each other.
+Consequently, the number of success $X = k$ over $n$ trials will follow a binomial distribution:
+
+    \begin{equation}
+      X \sim Bin(n,\theta) ,
+    \end{equation}
+
+    \noindent and
+
+    \begin{equation}
+       P(X = k|\theta,n) = {n \choose k}\theta^k(1-\theta)^{n-k} . 
+       \label{likelihood}
+    \end{equation}
+
+    \noindent The parameter $\theta$, the probability of observing an interaction over a given time interval
+    and area, is the quantity we want to estimate from empirical data. The variance of a 
+    Bernoulli experiment is simply n$\theta$(1-$\theta$).
+
+    The maximal likelihood estimate of $\theta$ is straightforward to find given $X=k$ and $n$. It is simply equal to:
+
+    \begin{equation}
+      \theta_{MLE} = \frac{k}{n}  .
+      \label{theta_MLE}
+    \end{equation}
+
+    It is possible to compute the confidence interval for this estimate using any of several methods, including the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull Interval}.
+Finding this estimate is therefore quite straightforward, but it nonetheless has two drawbacks.
+First, $\theta$ is a random variable with a given uncertainty and whose distribution is unknown, it is not a single point estimate.
+Second, the number of trials $n$ might be very low in many instances (and some pairs of species might even not be documented), and consequently the uncertainty in the estimation of $\theta$ might be considerable.
+We therefore propose a Bayesian approach to solve these two problems.
+
+    % Add section explaining process variation and detection probability here, how that will affect our ability to estimate.
+
+\section*{Estimating detection and process uncertainty}
 
@@
 
+\section*{Scaling up uncertainty from pairwise interactions to networks}
+
 \section*{Case study: estimating the uncertainty of a plant-herbivore network}

### 2017-09-17 manuscript/CI_interactions.tex
edits to MLE estimation section

@@
 It is important to keep in mind that for network analysis, ecologists seek to measure the occurrence of true absences, which is the joint event $L=1\cup X=1 \cup \D=1$), but in reality they measure the marginal probability $P(L) = k/n$.
-This reasonning explains why the above describe MLE estimation of the interaction probability is naive, and could be inappropriate in many instances, in particular when we have no knowledge of the detection and the process uncertainties.
 
-\section*{Pairwise interactions as a Bernoulli process}
+\section*{Estimating detection and process uncertainty}
 
-    We consider the occurrence of an ecological interaction as a stochastic process.
-Provided that the two species could interact, this interaction could happen with a given probability.
-This probability is likely to be less than one (i.e., the interaction may not occur) because i) the two species may not encounter each other during a given time interval and within a given area, ii) there may be unknown environmental drivers affecting the realization of the interaction or iii) a third species might interfere and prevent the interaction from happenning (Poisot2015).
+\section*{Maximum likelihood estimate and confidence interval of interaction probability}
 
-    We consider that the occurrence of an interaction is a Bernoulli trial.
-We define $\theta$ as the probability that two species interact with each other.
-Consequently, the number of success $X = k$ over $n$ trials will follow a binomial distribution:
+Estimation of the detection and process uncertainties could be tedious, if not infeasible in some instances.
+As a consequence, for now, we will focus on the estimate of the interaction probability $\lambda$, assuming that both the detection and process probabilities, $\delta$ and $\chi$ respectively, are equal to 1.
+The occurrence of an interaction is a Bernoulli trial.
+Consequently, the number of success $k$ over $n$ trials will follow a binomial distribution:
 
     \begin{equation}
-      X \sim Bin(n,\theta) ,
+      X \sim Bin(n,\lambda) ,
     \end{equation}
@@
     \begin{equation}
-       P(X = k|\theta,n) = {n \choose k}\theta^k(1-\theta)^{n-k} . 
+       P(X = k|\lambda,n) = {n \choose k}\lambda^k(1-\lambda)^{n-k} . 
        \label{likelihood}
@@
 
-    \noindent The parameter $\theta$, the probability of observing an interaction over a given time interval
-    and area, is the quantity we want to estimate from empirical data. The variance of a 
-    Bernoulli experiment is simply n$\theta$(1-$\theta$).
+\noindent The parameter $\lambda$, the probability of observing an interaction over an infinite time interval and area, is the quantity we want to estimate from empirical data.
+The variance of a Bernoulli experiment is simply n$\lambda$(1-$\lambda$).
+It is important to remember this variance reports the variability of the number of success $k$ for $n$ trials, it is not the variance associated with the estimation of $\lambda$.
 
-    The maximal likelihood estimate of $\theta$ is straightforward to find given $X=k$ and $n$. It is simply equal to:
+The maximal likelihood estimate of $\lambda$ is straightforward to find given $k$ and $n$. It is simply equal to:
 
@@
 Finding this estimate is therefore quite straightforward, but it nonetheless has two drawbacks.
-First, $\theta$ is a random variable with a given uncertainty and whose distribution is unknown, it is not a single point estimate.
-Second, the number of trials $n$ might be very low in many instances (and some pairs of species might even not be documented), and consequently the uncertainty in the estimation of $\theta$ might be considerable.
-We therefore propose a Bayesian approach to solve these two problems.
+First, $\lambda$ is a random variable with a given uncertainty and whose distribution is unknown, it is not a single point estimate.
+This means that even if $k = 0$ in a given sample, it does not implies necessarily that the two species will never interact.
+It means that no interaction is the most likely situation, but there is nonetheless a significant chance that the two species could interaction.
+In contrast with the situation where $k>0$, where we are sure that an interaction is feasible (in which case, the ratio $k/n$ is smaller than $n$ because of detection and process uncertainty), we are not sure that absence of interactions are caused by $L=0$.
+Second, and most importantly, the number of trials $n$ might be very low in many instances (and some pairs of species might even not be documented), and consequently the uncertainty in the estimation of $\lambda$ might be considerable.
+We illustrated at Fig.
+X how the estimate of $\lambda$ could vary with sampling size using the Clopper-Pearson interval.
+It shows that the 95\% confidence interval requires a signifcant amount of sampling in order to be sure that species are not interacting.
 
-    % Add section explaining process variation and detection probability here, how that will affect our ability to estimate.
-
-\section*{Estimating detection and process uncertainty}
+The situation where $k = 0$ is also problematic because we have very few information to estimate $\lambda$, in particular when $n$ is also small.
+We therefore propose a Bayesian approach to solve this problem, building on two relevant features of such statistics : posterior distribution of parameter estimates and usage of prior information.
 

### 2017-09-17 manuscript/CI_interactions.tex
more changes

--- 2017-09-17 manuscript/CI_interactions.tex
@@
 
-\author{Dominique Gravel, D. Carstensen, Timoth\'{e}e Poisot, Daniel B. Stouffer, \& Alyssa R. Cirtwill$^{1}$, others??}
+\author{Dominique Gravel, \& Alyssa R. Cirtwill$^{1}$, Anna Ekl\"{o}f, Tomas Roslin, Kate Wootton}
 \date{\small$^1$Department of Physics, Chemistry\\ 
@@
 
+      [[Checking this for reasonableness: sum is about 30, so we should have 30 galler-genotype combinations?]]
+
       Using this degree distribution we can obtain prior values for $\alpha$ and $\beta$ using the code above. We obtain
@@
       n=2: 0.22813413 0.01846427
-      n=3:
-      n=4:
+      n=3: 0.20648283 0.01555013
+      n=4: 0.18858498 0.01326377
 
@@
 
+  [[What if we have only one site?
+Can we use the number of observations of a pair of species interacting with any partners as the number of times they co-occur, and the number of interactions within the pair as k?
+This will be sort-of valid for insects but not for plants when researchers camp out by plant individuals...
+]]
+
 \clearpage

### 2017-09-17 manuscript/figure_binomial.R
figure binomial

@@ -1,0 +1,8 @@
+library(binom)
+n <- c(1:30)
+CI <- binom.confint(0, n, method = "exact")
+dev.new(width = 10, height = 8)
+plot(n,CI[,6], xlab = "Number of samples", ylab = "Upper 95% confidence interval", type = "l",cex.axis = 1.5,cex.lab = 1.5,lwd = 2,ylim = c(0,1))
+abline(h = 0.1, lty=3)
+
+

### 2017-09-17 manuscript/figure_binomial.R
edits to legend of figure binomial

@@ -5,4 +5,7 @@ dev.new(width = 10, height = 8)
 plot(n,CI[,6], xlab = "Number of samples", ylab = "Upper 95% confidence interval", type = "l",cex.axis = 1.5,cex.lab = 1.5,lwd = 2,ylim = c(0,1))
 abline(h = 0.1, lty=3)
 
+# CAPTION
+# This figure illustrates the upper confidence interval for the interaction probability $\lamba$ when there is no observation of an interaction ($k = 0$) and $n$ observations of the two species co-occurring at a given location. The confidence interval is based on the Clopper-Pearson derivation from the beta distribution. 
+
 

### 2017-09-17 manuscript/CI_interactions.tex
changes in Bayesian network approach section

--- 2017-09-17 manuscript/CI_interactions.tex
@@
 
-  We adopt a bayesian approach to estimate the distribution of the parameter $\theta$. According to Bayes principle, the posterior distribution of $\theta$ is:
+  We here adopt a Bayesian approach to estimate the distribution of the parameter $\theta$. According to Bayes principle, the posterior distribution of $\theta$ is:
 
@@
 
-  It might be complicated in many cases to compute the normalizer, but fortunately there is an analytical solution to the normalizer.
+ In some cases it can be complicated to compute the normalizer, but fortunately in our case it exists an analytical solution.
 The beta-binomial distribution is a conjugate distribution of the binomial distribution.
@@
 When plotted, we find the shape of the distribution gets narrower with $k$ and $n$ (see Fig X).
-
-  The posterior distribution of $\theta$ could be computed with R with the following command:
-
-  \vspace{12pt}
-  \noindent\emph{dbeta(x = theta, shape1 = alpha+k, shape1 = beta+n-k)}
-  \vspace{12pt}
+%
+%  The posterior distribution of $\theta$ could be computed with R with the following command:
+%
+%
+%  \vspace{12pt}
+%  \noindent\emph{dbeta(x = theta, shape1 = alpha+k, shape1 = beta+n-k)}
+%  \vspace{12pt}
 
@@
 
-    The \textbf{mode} of the distribution (which is not necessarily the maximum likelihood estimate) is:
+    The \textbf{mode} of the distribution is:
       \begin{equation}
@@
   \subsection*{The prior distribution}    
-
   Parameters $\alpha$ and $\beta$ determine the shape of the prior distribution, which follows a beta distribution.
-These are call hyper parameters.
-We identify at least four ways to formulate the prior distribution of $\theta$.
+These are called hyper parameters.
+Below we identify four ways to formulate the prior distribution of $\theta$.
 
@@
       In absence of any external information, an uniformative prior is the most conservative 
-      hypothesis for the distribution of $\theta$. The beta distribution is uninformative and follows 
+      hypothesis for the distribution of $\theta$. The beta distribution is in this case 
       a uniform distribution  for $Beta(\alpha=1,\beta=1)$.
@@
 
-      There is now a great collection of ecological network data for which know the distribution of connectance.
-Connectance of a network is measured as $C = L/S^2$, where $L$ is the number of links and $S$ is the number of species.
-It measures the filling of an interaction matrix and also expresses the average probability that any two species interact with each other.
-If one  knows only the mean $\overline{C}$ and the variance $\sigma_C^2$ of the distribution of $C$, then the beta parameters could be computed as follows using the method of moments:
+      In the literature of ecological networks there is a solid collection of data for which know network connectance, and we can thereby define the connectance distribution.
+Connectance is measured as $C = L/S^2$, where $L$ is the number of interactions and $S$ is the number of species.
+It measures the filling of an interaction matrix and thereby expresses the average probability that any two species interact with each other.
+If we know only the mean $\overline{C}$ and the variance $\sigma_C^2$ of the distribution of $C$, then the beta parameters could be computed as follows using the method of moments:
 
@@
 
-  It is also possible to compute maximum likelihood estimates for a sample of the distribution of $C$. The following piece of R code provides an example:
+%  It is also possible to compute maximum likelihood estimates for a sample of the distribution of $C$.
+%  
+%   The following piece of R code provides an example: 
+%
+%  \vspace{12pt}
+%  \noindent\emph{
+%    library(MASS)\\
+%    pars = fitdistr(x = vecC, "beta", start = list(shape1 = 1, shape2 = 1))\$estimate
+%  }
+%  \vspace{12pt}
+%
+%
+%  Where $vecC$ is a vector of known connectances for a set of networks.
 
-  \vspace{12pt}
-  \noindent\emph{
-    library(MASS)\\
-    pars = fitdistr(x = vecC, "beta", start = list(shape1 = 1, shape2 = 1))\$estimate
-  }
-  \vspace{12pt}
-
-  Where $vecC$ is a vector of known connectances for a set of networks.
-
-  \subsubsection*{Degree distribution}.
-
-  Connectance is an average property for a given network, it represents the expected degree standardized by the number of species in the network.
+  \subsubsection*{Degree distribution for the species in the network}.
+%
+The degree of a node in a network is defined as the number of interactions it has to other nodes.
+The degree distribution of a network is then the probability distribution of these degrees over the whole network.
+Connectance is an average property for a complete given network, and it represents the expected
+degree (expected number of interactions per species) standardized by the number of species in the network.
 The standardized degree could therefore be interpreted as an interaction probability.
-It is consequently possible to use the degree distribution to fuel the prior distribution.
-The degree distribution could come from several networks, or from the network of interest if interaction probabilities for some species are already documented.
-The latter approach allows us to apply information from known, abundant species to the rarest species for which interactions are less frequently documented.
-The procedure for the estimation of the hyper parameters follows exactly the same approach as described above for connectance except that each measurement is at the species level instead of the network level.
+It is consequently possible to
+use the degree distribution to inform the prior distribution. The degree distribution could
+come from several networks, from a similar network (e.g.
+a known network at slightly different location) or from the network of interest if interaction probabilities for some species are already documented.
+The latter approach allows us to apply information from known, abundant species to the rarest species for which interactions are less
+frequently documented. The procedure for the estimation of the hyper parameters follows
+the same approach as described above for connectance except that each
+measurement is at the individual species level instead of the network level.
 
   \subsubsection*{Trait-matching function}. 
-
   It is possible to estimate the probability of interaction between a pair of species if there is knowledge of their traits and some functions relating trait matching to interaction probability (Morales-Castilla2015).
-There are several techniques published to perform this inferrence of interaction probability (REFS).
+There are several techniques available to perform this inferrence of interaction probability (REFS).
 Note that in this case the prior might not be beta distribution and numerical methods might be required to compute the posterior distribution.
@@
 \section*{A quantitative example}
-
-The framework is best illustrated with a simple quantiative example.
+%Perhaps we want to also have a trait matching example in addition to the degree distribution example below?
+The framework can be illustrated with a simple quantiative example.
 Suppose we have $n = 10$ observations of co-occurrence between speices $i$ and species $j$ in a given time interval and area, and $X = 2$ observations of interactions.
 The maximum likelihood estimate of the interaction probability is simply $\theta_{MLE} = 2/10 = 0.2$.
+% We should probabaly have a value  on the interaction probablitity that differs from the average of the degree distrbution
  Now consider we know that species $i$ is known to interact with 10 other species, which have the following standardized degrees:
@@
 Now, consider the case where the two species have never been observed interacting across $n$ trials.
-The question is then "what is the probability these two species do not interact"?
-Since it will never be possible to prove that the two species could never interact, given the framework above we must fix a threshold below which we consider that there is no interaction.
-Let this threshold probability be called $\theta*$.
-We use the cumulative distribution function to estimate $P(\theta<\theta*|X=0,n)$.
+The question is then ``what is the probability these two species do not interact''?
+Since it is not possible to prove that the two species could never interact, given the framework above we must fix a threshold below which we consider that there is no interaction.
+We call this threshold probability $\theta*$.
+We then use the cumulative distribution function to estimate $P(\theta<\theta*|X=0,n)$.
 The following script illustrates this probability for an increasing number of trials and $\theta*$=0.1:
@@
 
-These trials yield a surprising result: it requires \textgreater30 [[or 23??]] observations of no interactions to be 95\% sure that the interaction probability is smaller than 0.1.
+The exercise exemplified above yields a surprising result: it requires \textgreater30 [[or 23??]] observations of no interactions to be 95\% sure that the interaction probability is smaller than 0.1.
 Note the special case where there is no observation of the two species co-occurring and failing to interact, $n = 0$.

### 2017-09-17 manuscript/CI_interactions.tex
added a better code snippet for making the prior web and calculating degree distributions

--- 2017-09-17 manuscript/CI_interactions.tex
@@
 
-      prior_web=read.csv(path_to_Dryad_file)
-      deg_dist_Salix=with(prior_web,tapply(gall_total_rich,Genotype,mean))/4
-      gallers=cbind(prior_web$Genotype,prior_web[,27:30])
-      aSG_means=with(prior_web,tapply(aSG_abund,Genotype,mean))
-      rG_means=with(prior_web,tapply(rG_abund,Genotype,mean))
-      vLG_means=with(prior_web,tapply(vLG_abund,Genotype,mean))
-      SG_means=with(prior_web,tapply(SG_abund,Genotype,mean))
-      deg_dist_galler=c(length(which(aSG_means>0)),length(which(rG_means>0)),length(which(SG_means>0)),length(which(rG_means>0))      )/26
-      int_probs=as.numeric(deg_dist_galler\%*\%t(deg_dist_Salix))
-
-      pars=fitdistr(x=int_probs,"beta",start=list(shape1=1,shape2=1))$estimate
-      alpha=pars[[1]]
-      beta=pars[[2]]
-      mu=alpha/(alpha+beta)
-      num=alpha*beta
-      den=(alpha+beta)**2*(alpha+beta)
-      sigma2=num/den
-
-      [[Checking this for reasonableness: sum is about 30, so we should have 30 galler-genotype combinations?]]
+      prior_web_data=read.csv(path_to_Dryad_file)
+      # Remove extra data on parasitoids, etc.
+      prior_web_data[,31:57]<-NULL
+      prior_web_data[,4:26]<-NULL
+      prior_web_data[,2]<-NULL
+      # Build a web with interactions=1 for any galler observed on any genotype
+      prior_web=matrix(nrow=26,ncol=4)
+      for(r in 1:length(levels(prior_web_data$Genotype))){
+        gen=levels(prior_web_data$Genotype)[r]
+        subset=prior_web_data[which(prior_web_data$Genotype==gen),]
+        for(c in 1:4){
+          if(sum(subset[,2+c])>0){
+            prior_web[r,c]=1
+          } else {
+            prior_web[r,c]=0
+          }
+        }        
+      }
+      # Now get the degree distributions from the web
+      deg_dist_Salix=rowSums(prior_web)/ncol(prior_web)
+      # Remove one genotype that never interacted
+      deg_dist_Salix<-deg_dist_Salix[which(rowSums(prior_web)>0)]
+      deg_dist_galler=colSums(prior_web)/nrow(prior_web)
+      # Interaction probabilities are the product of plant and galler probabilities
+      int_probs=as.numeric(deg_dist_galler%*%t(deg_dist_Salix))
 
       Using this degree distribution we can obtain prior values for $\alpha$ and $\beta$ using the code above. We obtain
-      $\alpha$=2.175656, $\beta$=5.361083.
+      $\alpha$=2.807855, $\beta$=2.342815.
 
       For species where no co-occurances were observed, we can calculate the MLE estimates for the mean and variance of $\omega_{ij}$ directly from this prior. These are:
-      $\hat{\omega_{ij}}$=0.2886734, var($\omega$)=0.02724535.
+      $\hat{\omega_{ij}}$=0.5451437, var($\omega$)=0.0481417.
+      This is consistent with the prior data, where the average interaction probability based on the degree distributions of Salix genotypes and gallers was 0.541.
+It may not be consistent with the degree distributions in our current dataset, however, especially since we are concerned with Salix species rather than genotypes within a species.
+We therefore want to update our distribution using known data from known co-occurances between species.
 
@@
 
-      $\hat{\omega_{ij}}$=0.005702349, var($\omega$)=1.486051e-05.
+      $\hat{\omega_{ij}}$=7.405645e-03, var($\omega$)=1.938755e-05.
 
       Realistic values for n when k=0, based on a sample of 20 random sites:
-      n=1: 0.25485794 0.02224566
-      n=2: 0.22813413 0.01846427
-      n=3: 0.20648283 0.01555013
-      n=4: 0.18858498 0.01326377
+      n=1: 0.4565121 0.0403385
+      n=2: 0.39267022 0.03335076
+      n=3: 0.34449379 0.02770543
+      n=4: 0.30684696 0.02324331
 

### 2017-09-17 manuscript/CI_interactions.tex

--- 2017-09-17 manuscript/CI_interactions.tex
@@
 
-      prior_web=read.csv(path_to_Dryad_file)
-      deg_dist_Salix=with(prior_web,tapply(gall_total_rich,Genotype,mean))/4
-      gallers=cbind(prior_web$Genotype,prior_web[,27:30])
-      aSG_means=with(prior_web,tapply(aSG_abund,Genotype,mean))
-      rG_means=with(prior_web,tapply(rG_abund,Genotype,mean))
-      vLG_means=with(prior_web,tapply(vLG_abund,Genotype,mean))
-      SG_means=with(prior_web,tapply(SG_abund,Genotype,mean))
-      deg_dist_galler=c(length(which(aSG_means>0)),length(which(rG_means>0)),length(which(SG_means>0)),length(which(rG_means>0))      )/26
-      int_probs=as.numeric(deg_dist_galler\%*\%t(deg_dist_Salix))
-
-      pars=fitdistr(x=int_probs,"beta",start=list(shape1=1,shape2=1))$estimate
-      alpha=pars[[1]]
-      beta=pars[[2]]
-      mu=alpha/(alpha+beta)
-      num=alpha*beta
-      den=(alpha+beta)**2*(alpha+beta)
-      sigma2=num/den
+      prior_web_data=read.csv(path_to_Dryad_file)
+      # Remove extra data on parasitoids, etc.
+      prior_web_data[,31:57]<-NULL
+      prior_web_data[,4:26]<-NULL
+      prior_web_data[,2]<-NULL
+      # Build a web with interactions=1 for any galler observed on any genotype
+      prior_web=matrix(nrow=26,ncol=4)
+      for(r in 1:length(levels(prior_web_data$Genotype))){
+        gen=levels(prior_web_data$Genotype)[r]
+        subset=prior_web_data[which(prior_web_data$Genotype==gen),]
+        for(c in 1:4){
+          if(sum(subset[,2+c])>0){
+            prior_web[r,c]=1
+          } else {
+            prior_web[r,c]=0
+          }
+        }        
+      }
+      # Now get the degree distributions from the web
+      deg_dist_Salix=rowSums(prior_web)/ncol(prior_web)
+      # Remove one genotype that never interacted
+      deg_dist_Salix<-deg_dist_Salix[which(rowSums(prior_web)>0)]
+      deg_dist_galler=colSums(prior_web)/nrow(prior_web)
+      # Interaction probabilities are the product of plant and galler probabilities
+      int_probs=as.numeric(deg_dist_galler%*%t(deg_dist_Salix))
 
       Using this degree distribution we can obtain prior values for $\alpha$ and $\beta$ using the code above. We obtain
-      $\alpha$=2.175656, $\beta$=5.361083.
+      $\alpha$=2.807855, $\beta$=2.342815.
 
       For species where no co-occurances were observed, we can calculate the MLE estimates for the mean and variance of $\omega_{ij}$ directly from this prior. These are:
-      $\hat{\omega_{ij}}$=0.2886734, var($\omega$)=0.02724535.
+      $\hat{\omega_{ij}}$=0.5451437, var($\omega$)=0.0481417.
+      This is consistent with the prior data, where the average interaction probability based on the degree distributions of Salix genotypes and gallers was 0.541.
+It may not be consistent with the degree distributions in our current dataset, however, especially since we are concerned with Salix species rather than genotypes within a species.
+We therefore want to update our distribution using known data from known co-occurances between species.
 
@@
 
-      $\hat{\omega_{ij}}$=0.005702349, var($\omega$)=1.486051e-05.
+      $\hat{\omega_{ij}}$=7.405645e-03, var($\omega$)=1.938755e-05.
 
       Realistic values for n when k=0, based on a sample of 20 random sites:
-      n=1: 0.25485794 0.02224566
-      n=2: 0.22813413 0.01846427
-      n=3:
-      n=4:
+      n=1: 0.4565121 0.0403385
+      n=2: 0.39267022 0.03335076
+      n=3: 0.34449379 0.02770543
+      n=4: 0.30684696 0.02324331
 

### 2017-09-17 code/handy_R_functions.R
Code that isn't fancy but beats typing by hand

@@ -1,0 +1,37 @@
+calculate_parameters<-function(priordata,n,k){
+  pars=fitdistr(x=priordata,"beta",start=list(shape1=1,shape2=1),lower=c(0,0))$estimate
+  alpha=pars[[1]]
+  beta=pars[[2]]
+  alpha_prime=alpha+k
+  beta_prime=beta+n-k
+  pars2=c(alpha_prime,beta_prime)
+  return(pars2)
+}
+
+
+calculate_distribution<-function(pars){
+  alpha=pars[[1]]
+  beta=pars[[2]]
+
+  mu_num=alpha
+  mu_den=alpha+beta
+  mu=mu_num/mu_den
+
+  sig_num=alpha*beta
+  den1=alpha+beta
+  den2=den1**2
+  sig_den=den1*den2
+  sigma2=sig_num/sig_den
+
+  return(c(mu,sigma2))
+}
+
+
+credible_interval<-function(pars,p_lower,p_upper){
+  alpha=pars[[1]]
+  beta=pars[[2]]
+  lowCI=qbeta(p=p_lower,shape1=alpha,shape2=beta)
+  highCI=qbeta(p=p_upper,shape1=alpha,shape2=beta)
+  return(c(lowCI,highCI))
+}
+

### 2017-09-17 manuscript/CI_interactions.tex
upscaling uncertainty

--- 2017-09-17 manuscript/CI_interactions.tex
@@
 
-\author{Dominique Gravel, \& Alyssa R. Cirtwill$^{1}$, Anna Ekl\"{o}f, Tomas Roslin, Kate Wootton}
+\author{Dominique Gravel, D. Carstensen, Timoth\'{e}e Poisot, Daniel B. Stouffer, \& Alyssa R. Cirtwill$^{1}$, others??}
 \date{\small$^1$Department of Physics, Chemistry\\ 
@@
 
+It is fairly straigthforward to compute most of network metrics when the different $\lambda$ of the adjacency matrix are known, without variance (Poisot et al.
+2015).
+Several of these metrics derive directly from quantitative indices of network structure.
+It is not as easy however to understand how the uncertainty in these estimates do influence network metrics.
+There are multiple non-linearities in the computation of these metrics and that, because of Jensen's inequality (the principle stating that the average of non-linear function of a stochastic variable differs from the function of the average of that variable), any uncertainty could bias the average estimate of the metric and influence its variance as well.
+For instance, among all of the pairs of species for which only few co-occurrences are observed, many of them are truly interacting.
+If we consider all of these as having no links, then correcting for these false absence would inflate the number of links and therefore influence metrics such as connectance, nestedness and degree distribution.
+Computing network properties from probabilistic networks is one thing, but then computing them with uncertainties in these probabilities is another problem, far more challenging.
+Unfortunately, for now we could only rely on computer simulations to get an answer to this problem.
+In the following section, we will provide an example with the Salix dataset and show how the uncertainty arising from both absences of co-occurrences and false absences of interactions impact these metrics.
+We find uncertainty influences both the average and the variance of network metrics, putting in perspective traditional network comparison studies where these metrics are assumed fixed entities.
+
 \section*{Case study: estimating the uncertainty of a plant-herbivore network}
@@
 
-      prior_web_data=read.csv(path_to_Dryad_file)
-      # Remove extra data on parasitoids, etc.
-      prior_web_data[,31:57]<-NULL
-      prior_web_data[,4:26]<-NULL
-      prior_web_data[,2]<-NULL
-      # Build a web with interactions=1 for any galler observed on any genotype
-      prior_web=matrix(nrow=26,ncol=4)
-      for(r in 1:length(levels(prior_web_data$Genotype))){
-        gen=levels(prior_web_data$Genotype)[r]
-        subset=prior_web_data[which(prior_web_data$Genotype==gen),]
-        for(c in 1:4){
-          if(sum(subset[,2+c])>0){
-            prior_web[r,c]=1
-          } else {
-            prior_web[r,c]=0
-          }
-        }        
-      }
-      # Now get the degree distributions from the web
-      deg_dist_Salix=rowSums(prior_web)/ncol(prior_web)
-      # Remove one genotype that never interacted
-      deg_dist_Salix<-deg_dist_Salix[which(rowSums(prior_web)>0)]
-      deg_dist_galler=colSums(prior_web)/nrow(prior_web)
-      # Interaction probabilities are the product of plant and galler probabilities
-      int_probs=as.numeric(deg_dist_galler%*%t(deg_dist_Salix))
+      prior_web=read.csv(path_to_Dryad_file)
+      deg_dist_Salix=with(prior_web,tapply(gall_total_rich,Genotype,mean))/4
+      gallers=cbind(prior_web$Genotype,prior_web[,27:30])
+      aSG_means=with(prior_web,tapply(aSG_abund,Genotype,mean))
+      rG_means=with(prior_web,tapply(rG_abund,Genotype,mean))
+      vLG_means=with(prior_web,tapply(vLG_abund,Genotype,mean))
+      SG_means=with(prior_web,tapply(SG_abund,Genotype,mean))
+      deg_dist_galler=c(length(which(aSG_means>0)),length(which(rG_means>0)),length(which(SG_means>0)),length(which(rG_means>0))      )/26
+      int_probs=as.numeric(deg_dist_galler\%*\%t(deg_dist_Salix))
+
+      pars=fitdistr(x=int_probs,"beta",start=list(shape1=1,shape2=1))$estimate
+      alpha=pars[[1]]
+      beta=pars[[2]]
+      mu=alpha/(alpha+beta)
+      num=alpha*beta
+      den=(alpha+beta)**2*(alpha+beta)
+      sigma2=num/den
 
       Using this degree distribution we can obtain prior values for $\alpha$ and $\beta$ using the code above. We obtain
-      $\alpha$=2.807855, $\beta$=2.342815.
+      $\alpha$=2.175656, $\beta$=5.361083.
 
       For species where no co-occurances were observed, we can calculate the MLE estimates for the mean and variance of $\omega_{ij}$ directly from this prior. These are:
-      $\hat{\omega_{ij}}$=0.5451437, var($\omega$)=0.0481417.
-      This is consistent with the prior data, where the average interaction probability based on the degree distributions of Salix genotypes and gallers was 0.541.
-It may not be consistent with the degree distributions in our current dataset, however, especially since we are concerned with Salix species rather than genotypes within a species.
-We therefore want to update our distribution using known data from known co-occurances between species.
+      $\hat{\omega_{ij}}$=0.2886734, var($\omega$)=0.02724535.
 
@@
 
-      $\hat{\omega_{ij}}$=7.405645e-03, var($\omega$)=1.938755e-05.
+      $\hat{\omega_{ij}}$=0.005702349, var($\omega$)=1.486051e-05.
 
       Realistic values for n when k=0, based on a sample of 20 random sites:
-      n=1: 0.4565121 0.0403385
-      n=2: 0.39267022 0.03335076
-      n=3: 0.34449379 0.02770543
-      n=4: 0.30684696 0.02324331
+      n=1: 0.25485794 0.02224566
+      n=2: 0.22813413 0.01846427
+      n=3:
+      n=4:
 
@@
 
-  [[What if we have only one site?
-Can we use the number of observations of a pair of species interacting with any partners as the number of times they co-occur, and the number of interactions within the pair as k?
-This will be sort-of valid for insects but not for plants when researchers camp out by plant individuals...
-]]
-
 \clearpage

### 2017-09-17 manuscript/CI_interactions.tex
starting an SI

--- 2017-09-17 manuscript/CI_interactions.tex
@@
 hookeriana} rather than different \emph{Salix} species.
-We take the degree distributions of four Cecidomyid galler species across \emph{S.
-hookeriana} genotypes as our prior distribution for the probability of interactions between gallers and \emph{Salix} species.
-Note that as an interaction frequency depends on the product of the degree of the galler and the degree of the plant involved, we wish to use as our prior the product of the degree distributions of plants and gallers.
-      Unfortunately, the product of two beta distributions is not beta-distributed. Instead, we will use the list of interaction probabilities, obtained by multiplying the two degree distributions.
+We estimated frequencies of  \emph{S.
+hookeriana} genotype-galler and galler-parasitoid interactions [[host-parasitoid still to-do]] based on the normalized degree of each species in each network component (see \emph{Appendix S1} for details and code).
 
-      The degree distribution across \emph{S. hookeriana} genotypes was calculated from data deposited in Dryad using the following R code:
+      Using this prior distribution of galler-\emph{Salix} interaction frequencies, we can obtain parameters for the prior distribution of $\lambda$ in our dataset.
+Specifically, we obtain $\alpha$=2.807855, $\beta$=2.342815.
+We are then able to use these priors to estimate the posterior distriution of interaction probabilities given the additional information in our dataset.
 
-      prior_web_data=read.csv(path_to_Dryad_file)
-      # Remove extra data on parasitoids, etc.
-      prior_web_data[,31:57]<-NULL
-      prior_web_data[,4:26]<-NULL
-      prior_web_data[,2]<-NULL
-      # Build a web with interactions=1 for any galler observed on any genotype
-      prior_web=matrix(nrow=26,ncol=4)
-      for(r in 1:length(levels(prior_web_data$Genotype))){
-        gen=levels(prior_web_data$Genotype)[r]
-        subset=prior_web_data[which(prior_web_data$Genotype==gen),]
-        for(c in 1:4){
-          if(sum(subset[,2+c])>0){
-            prior_web[r,c]=1
-          } else {
-            prior_web[r,c]=0
-          }
-        }        
-      }
-      # Now get the degree distributions from the web
-      deg_dist_Salix=rowSums(prior_web)/ncol(prior_web)
-      # Remove one genotype that never interacted
-      deg_dist_Salix<-deg_dist_Salix[which(rowSums(prior_web)>0)]
-      deg_dist_galler=colSums(prior_web)/nrow(prior_web)
-      # Interaction probabilities are the product of plant and galler probabilities
-      int_probs=as.numeric(deg_dist_galler%*%t(deg_dist_Salix))
+    \subsection*{Computing the posterior distribution}
 
-      Using this degree distribution we can obtain prior values for $\alpha$ and $\beta$ using the code above. We obtain
-      $\alpha$=2.807855, $\beta$=2.342815.
+      [[add references to formulae]]
 
-      For species where no co-occurances were observed, we can calculate the MLE estimates for the mean and variance of $\omega_{ij}$ directly from this prior. These are:
-      $\hat{\omega_{ij}}$=0.5451437, var($\omega$)=0.0481417.
+      For species where no co-occurances were observed, we can calculate the MLE estimates for the mean and variance of $\lambda_{ij}$ directly from this prior. These are:
+      $\hat{\lambda_{ij}}$=0.5451437, var($\lambda$)=0.0481417.
       This is consistent with the prior data, where the average interaction probability based on the degree distributions of Salix genotypes and gallers was 0.541.
-It may not be consistent with the degree distributions in our current dataset, however, especially since we are concerned with Salix species rather than genotypes within a species.
-We therefore want to update our distribution using known data from known co-occurances between species.
+[[What's the connectance of our dataset, of we call greys 0?]] This probability does, however, seem rather high for our dataset.
+This discrepancy may be because~\citep{Balbour2016} were considering genotypes of a single \emph{Salix} species and only four gallers from a single family rather than multiple \emph{Salix} species and galler families as is the case in our dataset.
 
-      For a pair of species where some co-occurances were observed, we base these estimates on the prior distribution above conditioned by the available data.
+      For a pair of species where some co-occurances were observed, we can update the prior distribution with these data.
 If we consider only pairs of species which were observed to co-occur but not to interact, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs.
@@
 
-      $\hat{\omega_{ij}}$=7.405645e-03, var($\omega$)=1.938755e-05.
+      $\hat{\lambda_{ij}}$=7.405645 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=1.938755 $\times$ 10$^{-5}$.
+
+      With species $i$ and $j$ co-occurring at all 374 sites and never being observed to interact, the maximum likelihood expectation for the probability of an interaction $ij$ is very close to 0 and the variance about this estimate is very narrow.
+In most cases, however, species $i$ and $j$ did not co-occur at so many sites and our posterior mean and variance retain some influence of the prior.
 
@@
 
-    \subsection*{Computing the posterior distribution}
+      [[Plot distribution of interaction probabilities at some reasonable values of n]]
 
-  \subsection*{Computing the confidence interval around a probability estimate}
+  \subsection*{Computing the credible interval around a probability estimate}
+
+      As well as obtaining posterior means and variances, it is possible to calculate a 95\% credible interval about the posterior mean.
 
   \subsection*{How many samples are required to reach a minimal precision}
+
+    - Have code for graphing or returning sample size set up.
+    - Plot Increase in sample sizes with decreasing threshold, increasing confidence.
 

### 2017-09-17 manuscript/supplemental.tex
starting an SI

\section*{Appendix S1: Obtaining prior interaction probabilities}

    \subsection*{Creating a binary interaction network}

      Barbour \emph{et al.} sampled 145 branches from \emph{Salix hookeriana} of 26 genotypes. They recorded galls made by four species of Cecidomyid midges on each branch. We transformed these data to a binary genotype-galler network matrix, where an entry $ij$ was 1 if galler $i$ was observed on any branch of genotype $j$ and 0 otherwise. In total, this network contained 75 realized galler-genotype interactions out of a potential 104. The R code used to extract this network follows:

      % prior_web_data=read.csv('tree_level_interaxn_all_plants_traits_size.csv')
      % # Remove extra data on parasitoids, etc.
      % prior_web_data[,31:57]<-NULL
      % prior_web_data[,4:26]<-NULL
      % prior_web_data[,2]<-NULL
      % # Build a web with interactions=1 for any galler observed on any genotype
      % prior_web=matrix(nrow=26,ncol=4)
      % for(r in 1:length(levels(prior_web_data$Genotype))){
      %   gen=levels(prior_web_data$Genotype)[r]
      %   subset=prior_web_data[which(prior_web_data$Genotype==gen),]
      %   for(c in 1:4){
      %     if(sum(subset[,2+c])>0){
      %       prior_web[r,c]=1
      %     } else {
      %       prior_web[r,c]=0
      %     }
      %   }        
      % }

    \subsection*{Degree distributions and interaction probabilities}

      Obtaining degree distributions from the binary interaction network is straightforward. To do this, we simply divide the total number of observed interaction partners for each species (row or column sums) with the number of potential interaction partners (number of column or rows). Degree distributions calculated, we can then calculate the probability of each interaction as the product of the normalized degrees of the two species. For example, the probability of an interaction between two species with normalized degrees of 0.5 (each interacts with half of the available partners) is 0.25. R code used to do this follows:

      %       # Now get the degree distributions from the web
      % deg_dist_Salix=rowSums(prior_web)/ncol(prior_web)
      % # Remove one genotype that never interacted
      % deg_dist_Salix<-deg_dist_Salix[which(rowSums(prior_web)>0)]
      % deg_dist_galler=colSums(prior_web)/nrow(prior_web)
      % # Interaction probabilities are the product of plant and galler probabilities
      % int_probs=as.numeric(deg_dist_galler%*%t(deg_dist_Salix))

\section*{Appendix S2: Calculating posterior distributions and confidence intervals}

  The following simple functions are implemented in the R language. Priordata is the list of interaction frequencies from the prior data, n is the number of sites with observed co-occurrance of species $i$ and $j$, and k is the number of sites with an observed interaction $ij$. When calculating the prior distribution, both n and k are 0. In the main text we assume 100\% confidence in observed interactions and therefore consider only cases where k=0. Only n varies between species pairs.

  To calculate the parameters $\alpha$ and $\beta$ of a prior or posterior distribution:

  \vspace{12pt}
  calculate\_parameters\textless-function(priordata,n,k)\{
  \# Calculate the parameters of the prior distribution
  pars=fitdistr(x=priordata,"beta",start=list(shape1=1,shape2=1),lower=c(0,0))\$estimate
  alpha=pars[[1]]
  beta=pars[[2]]
  \# Update the parameters with data. If n=0 and k=0, no change.
  alpha\_prime=alpha+k
  beta\_prime=beta+n-k
  pars2=c(alpha\_prime,beta\_prime)
  return(pars2)
  }

    % calculate_parameters<-function(priordata,n,k){
    %   pars=fitdistr(x=priordata,"beta",start=list(shape1=1,shape2=1),lower=c(0,0))$estimate
    %   alpha=pars[[1]]
    %   beta=pars[[2]]
    %   alpha_prime=alpha+k
    %   beta_prime=beta+n-k
    %   pars2=c(alpha_prime,beta_prime)
    %   return(pars2)
    % }

    To calculate the maximum likelihood estimates of the mean and variance of the probability of interaction $\lambda_{ij}$:

    \vspace{12pt}
    calculate\_distribution\textless-function(pars){
      \# alpha and beta may be from a prior or posterior distribution
      alpha=pars[[1]]
      beta=pars[[2]]

      \# Calculate the MLE of the mean
      mu\_num=alpha
      mu\_den=alpha+beta
      mu=mu\_num\/mu\_den

      \# Calculate the MLE of the variance
      sig\_num=alpha\*beta
      den1=alpha+beta
      den2=den1\*\*2
      sig\_den=den1\*den2
      sigma2=sig\_num\/sig\_den

      return(c(mu,sigma2))
    }

  % calculate_distribution<-function(pars){
  %       alpha=pars[[1]]
  %       beta=pars[[2]]

  %       mu_num=alpha
  %       mu_den=alpha+beta
  %       mu=mu_num/mu_den

  %       sig_num=alpha*beta
  %       den1=alpha+beta
  %       den2=den1**2
  %       sig_den=den1*den2
  %       sigma2=sig_num/sig_den

  %       return(c(mu,sigma2))
  %     }

  To calculate a credible interval based on the prior or posterior distribution, for given lower and upper bounds:

  \vspace{12pt}

credible_interval<-function(pars,p_lower,p_upper){
  alpha=pars[[1]]
  beta=pars[[2]]
  lowCI=qbeta(p=p_lower,shape1=alpha,shape2=beta)
  highCI=qbeta(p=p_upper,shape1=alpha,shape2=beta)
  return(c(lowCI,highCI))
}

plot_precision<-function(threshold,confidence,pars){
  alpha=pars[[1]]
  beta=pars[[2]]
  n=seq(0,100,1)
  k=0
  cdf=pbeta(threshold,shape1=alpha,shape2=beta+n)
  samples=length(which(cdf<confidence))
  # plot(n,cdf,type="l",xlab="n",ylab="Cumulative distribution")
  # abline(h=0.95,lty=3)
  return(samples)
}

### 2017-09-17 manuscript/There are a wide variety of reasons why two specie.tex

There are a wide variety of reasons why two species might not be observed to interact. One or both species might be rare and so might not be observed or might not encounter the other species. We may not have invested enough sampling effort, sampled at an appropriate time for all interactions (e.g., daytime sampling will miss nocturnal interactions), or our sampling method may be biased towards certain interactions (e.g., some species of caterpillar may be easier to rear than others). The species might interact under ideal conditions, but be prevented due to an unsuitable study site or indirect effects of other species. These different possibilities can be grouped into three hierarchical questions:

1: For a given pair of species considered in isolation, can they interact? I.e., do they have compatible traits and co-occur?
L=stochastic process, 1 if species interact and 0 if not.
P(L)=$\omega$.

Level 2: For a pair of species that can interact, do they interact at this site and time? I.e., is there nothing about the environment, phenology, community, or abundances of the species to prevent an interaction?
P(X|L=1)=$\theta$

Level 3: For a pair of species that can and do interact (if L=1 and X=1), do we detect the interaction? I.e., is there nothing about our sampling approach that prevents detection of the interaction?
P(D|X=1,L=1)=$\phi$

An interaction that is not observed (recorded as "0" in an interaction matrix and referred to as a "zero" hereafter) could be due to a failure at any of these three steps. We often want to know which interactions between species do and do not occur (at any site). Since a "zero" does not necessarily mean that an interaction does not occur, can we put uncertainty on this entry?

More fundamentally, since we cannot have complete confidence in the "zeros" in an interaction matrix, how can we estimate $\omega$, the probability that two species interact? Is it sufficient to use a Maximum Likelihood Estimate (MLE) for $\omega$, such as $k$/$n$ where $k$ is the number of observed interactions and $n$ is the number of observed co-occurances of the two species?

Is it possible to estimate detection probability (D) and process variability (L)?

If we assume perfect detection and no process variability, can we get a distribution of $\omega$? Yes, probably. We can use the posterior P($\omega$|k) to obtain a mean and confidence interval for each observation, including those where we have no data (in which case, the posterior distribution is reduced to the prior).

Finally, what are the consequences of this uncertainty as we scale up from particular interactions to network-level properties? For example, do the average and variance of a property (e.g., connectance) increase with detection and process uncertainty? Can we compute or map the uncertainty?

In the Salix web specifically:
  i) We can fill the holes in the meta-web.
      - condition the prior based on connectance of another web? - could add traits later, but not for this first attempt.
  ii) We can represent the uncertainty in the meta-web (zeros only - assume ones are correct).
  iii) Compile a posterior distribution of network properties to get at the uncertainty at higher levels (do the mean and variances of properties increase with detection and process uncertainty)?

------------------------------------------------------------------------------------------------------------

If $n$ is the number of observed co-occurances and $k$ is the number of observed interacctions, the traditional MLE of omega is k/n. But this is probably incorrect, because both phi and theta add variation. More accurately, k/n is the MLE of P(D,X,L): the probability of detecting an interaction that \emph{can} and \emph{does} occur. To put bounds on our trust in a "zero" observation, we want P(L=0).

P(k=0)= P(D=0,X=1,L=1) % Interaction occurred but is not detected
          + P(D=1,X=0,L=1) % Interaction detectable, but species do not interact at this site
          + P(D=1,X=1,L=0) % Detection method and site suitable, interaction not feasible
          + P(D=0,X=0,L=1) % Interaction not detectable and doesn't happen here
          + P(D=0,X=1,L=0) % Interaction not detectable, not species suitable but site is
          + P(D=1,X=0,L=0) % Detector good, interaction and site not feasible
          + P(D=0,X=0,L=0) % Detector, site, and interaction all bad.

P(D,X,L)=P(D|X,L)P(X|L)P(L)

We can get a prior for P(L) based on e.g., degree distributions (generalists more likely to interact than 2 specialists). Estimating P(D|X,L) seems like a very difficult emprical problem. P(X|L) is more feasible,

Current document assumes P(X|L)=1, P(D|X,L)=1.

P(\omega|k)=\frac{P(k|\omega)P(\omega)}{P(k)}
- can use this when there is no information (such that posterior==prior).
- P(D|X,L) should increase towards an asymptote as $n$ increases.

### 2017-09-18 code/handy_R_functions.R
not sure degree distribution for interactions is right for the quantitative example

@@ -1,5 +1,7 @@
 calculate_parameters<-function(priordata,n,k){
+  library(MASS)
   pars=fitdistr(x=priordata,"beta",start=list(shape1=1,shape2=1),lower=c(0,0))$estimate
+  # The lower=c(0,0) prevents R from fitting invalid (negative) parameters
   alpha=pars[[1]]
   beta=pars[[2]]
   alpha_prime=alpha+k

### 2017-09-18 manuscript/CI_interactions.tex
fixed a merge

@@
 
-\section*{Why some interactions do not occur ?}
+\section*{A naive qunatification of interaction probability and uncertainty}
 
@@
 
-Starting from the problem described in the previous section, we consider that a pair of species have been observed $n$ times co-occurring at one location, and the number of times they interact is $k = 0$.
+As a start, we will consider how we could naively quantify intetraction probability and its associated uncertainty.
+We consider that a pair of species have been observed $n$ times co-occurring at one location, and the number of times they interact is $k = 0$.
 We aim to evaluate the uncertainty of this interaction.
-What this is mean exactly ?
-We consider there are three nested level of uncertainty making this phenomenon a stochastic process :
-
-\textit{Interaction uncertainty} First, and most fundamentally, we do not know if these species have the appropriate characteristics to interact or not.
-We define the probability of an interaction $L$ as $P(L)=\lambda$.
-Obviously, because $k=0$, it is very likely they can not interact if provided enough time and there were no environmental constraint for this interaction to happen.
-But it is nonetheless possible the interaction is a rare phenomenon that has never been documented before.
-This source of uncertainty is the one documented by trait-matching models.
-It arises because every model is imperfect and lack information (i.e.
-traits) about the constraints on the interaction.
-In other words, with sufficient sampling and all information accessible, this interaction probability should either tend to 0 or to 1 and the uncertainty vanish.
-
-\textit{Process uncertainty} It could happen that the interaction is feasible, i.e.
-$L=1$, but that it does not occur at a given location or at a moment in time because there are local constraints preventing it to occur.
-We define the realization of the interaction process $X$ given an interaction is feasible as a stochastic process with associated probability $P(X|L)=\chi$.
-This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology about the contingencies of interactions.
-We imagine for instance that an interaction between a gall and a parasitoid is not recorded at a location because it was the wrong time of the year and the gall has not yet formed (phenological constraints), because a late frost killed the larvae (an abiotic environmental constraint) , another parasitoid species competitively excluded the parasitoid species of interst (a biotic environmental constraint) or simply the parasitoid is too rare (an abundance constraint).
-
-\textit{Detection uncertainty} Lastly, measurement errors are always source of uncertainty in the observation of ecological processes.
-We define the detection of an interaction $D$, given an interaction is feasible and occurs in the local conditions, as a stochastic process with associated probability $P(D|X,L)=\delta$.
-Detection failure could happen for several reasons, for instance if the rearing of a parasitoid fails with inappropriate lab conditions or because of species mis-identification.
-Some source of detection error could be minimized with appropriate sampling effort ($\chi$ will converge to one with increasing number of collected galls), but other sources are often difficult to reduce (e.g.
-the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification).
-
-\textit{What is an observation of "no interaction" ?} The combination of these three sources of uncertainty together leads to many potential explanations for the observation of an absence of interaction, but only the situation where $L = 0$ is a true absence therefore is relevant for the investigation of networks.
-While the observation of an interaction is straightforward to interpret, absence of interactions must be decomposed in different quantities.
-It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e.
-the interaction occurred at the location but was not observed, and $D=1 \cup X = 0 \cup L =1$, the interaction would have been detected but did not occur.
-
-It is important to keep in mind that for network analysis, ecologists seek to measure the occurrence of true absences, which is the joint event $L=1\cup X=1 \cup \D=1$), but in reality they measure the marginal probability $P(L) = k/n$.
-
-\section*{Estimating detection and process uncertainty}
-
-\section*{Maximum likelihood estimate and confidence interval of interaction probability}
-
-Estimation of the detection and process uncertainties could be tedious, if not infeasible in some instances.
-As a consequence, for now, we will focus on the estimate of the interaction probability $\lambda$, assuming that both the detection and process probabilities, $\delta$ and $\chi$ respectively, are equal to 1.
 The occurrence of an interaction is a Bernoulli trial.
@@
 We therefore propose a Bayesian approach to solve this problem, building on two relevant features of such statistics : posterior distribution of parameter estimates and usage of prior information.
+But before moving to this direction, we will first take time to better describe what is exactly meant by an interaction probability and appropriately define sources of uncertainty.
+
+So many sources of interaction pooled into a single entity; hard to estimate.
+
+MLE is zero if no interactions detected, but there may still be a substantial probability of interaction should the two species co-occur.
+[This is particularly important in the context of a changing world, where species not co-occurring today – or species not detected co-occurring today – may well do so tomorrow, forming complex interactions.]
+
+\section*{Why some interactions do not occur ?}
+
+What this is mean exactly ? We consider there are three nested level of uncertainty making this phenomenon a stochastic process :
+
+\textit{Interaction uncertainty} First, and most fundamentally, we do not know if these species have the appropriate characteristics to interact or not.
+We define the probability of an interaction $L$ as $P(L)=\lambda$.
+Obviously, because $k=0$, it is very likely they can not interact if provided enough time and there were no environmental constraint for this interaction to happen.
+But it is nonetheless possible the interaction is a rare phenomenon that has never been documented before.
+This source of uncertainty is the one documented by trait-matching models.
+It arises because every model is imperfect and lack information (i.e.
+traits) about the constraints on the interaction.
+In other words, with sufficient sampling and all information accessible, this interaction probability should either tend to 0 or to 1 and the uncertainty vanish.
+
+\textit{Process uncertainty} It could happen that the interaction is feasible, i.e.
+$L=1$, but that it does not occur at a given location or at a moment in time because there are local constraints preventing it to occur.
+We define the realization of the interaction process $X$ given an interaction is feasible as a stochastic process with associated probability $P(X|L)=\chi$.
+This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology about the contingencies of interactions.
+We imagine for instance that an interaction between a gall and a parasitoid is not recorded at a location because it was the wrong time of the year and the gall has not yet formed (phenological constraints), because a late frost killed the larvae (an abiotic environmental constraint) , another parasitoid species competitively excluded the parasitoid species of interst (a biotic environmental constraint) or simply the parasitoid is too rare (an abundance constraint).
+
+\textit{Detection uncertainty} Lastly, measurement errors are always source of uncertainty in the observation of ecological processes.
+We define the detection of an interaction $D$, given an interaction is feasible and occurs in the local conditions, as a stochastic process with associated probability $P(D|X,L)=\delta$.
+Detection failure could happen for several reasons, for instance if the rearing of a parasitoid fails with inappropriate lab conditions or because of species mis-identification.
+Some source of detection error could be minimized with appropriate sampling effort ($\chi$ will converge to one with increasing number of collected galls), but other sources are often difficult to reduce (e.g.
+the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification).
+
+\textit{What is an observation of "no interaction" ?} The combination of these three sources of uncertainty together leads to many potential explanations for the observation of an absence of interaction, but only the situation where $L = 0$ is a true absence therefore is relevant for the investigation of networks.
+While the observation of an interaction is straightforward to interpret, absence of interactions must be decomposed in different quantities.
+It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e.
+the interaction occurred at the location but was not observed, and $D=1 \cup X = 0 \cup L =1$, the interaction would have been detected but did not occur.
+
+It is important to keep in mind that for network analysis, ecologists seek to measure the occurrence of true absences, which is the joint event $L=1\cup X=1 \cup \D=1$), but in reality they measure the marginal probability $P(L) = k/n$.
+
+\section*{Estimating detection and process uncertainty}
+
+For the ecologist working on collecting network data, and on later interpreting these data, the considerations above raise a major challenge: how may we infer whether unobserved interactions went undetected due to sampling, or whether they truly do not occur.
+How then may we refine our sampling approaches to reduce uncertainties, and to gain insights into the impact of multiple processes on field observations?
+Importantly, some sources can be minimized with appropriate sampling design and efforts, while other sources are difficult or impossible to reduce – since they are generated by chance variation created by the very process in which we are interested.
+
+The basic information that we are collecting consists of interaction matrices of interaction partners.
+If our counts of whether species A is interacting with species B reflects both uncertainty with respect to whether two species interact when co-occurring at a given site, chance variation in whether the interaction is realized, and uncertainty with respect to whether it is detected when realized, then what can we do to pin down any of these different parts?
+
+A simple consideration will illustrate the problem: assuming that we want to infer the probability of an interaction between two species, A and B.
+Now assume that in reality, interaction between A and B is plain impossible (i.e.
+the true (P(L|co-occurrence of A and B = 0).
+Given no added detection error in observing the incidence of the interaction, then a single observation of species co-occurrence will reveal (very) little regarding the probability of the interaction – the confidence limits for one observation essentially spans from 0 to 1 (see following section).
+For 5 observations, this confidence limit will still extends to 0.5.
+Only with thirty observations will it shrink to 0.1.
+Thus, adding (many) more observations is certainly useful in controlling uncertainty due to stochasticity inherent in the process itself.
+
+The pattern of Fig.
+X (binomial CL fig from Dom) should be compared to the frequency of co-occurrence of taxa in the Salix-galler data set.
+Here, most(TO COMPUTE) pairs of species are never found co-occurring, and for species found co-occurring the number of co-occurrences was generally low (Fig from AC and KW).
+Among the species which did sometimes interact when co-occurring, the incidence of interaction was actually low(TO COMPUTE) (freq histogram Fig from AC and KW).
+Thus, even in the most extensive data set that we could think of, limited sampling is clearly a major source of uncertainty.
+
+The obvious rule of thumb derived from the above example will be “sample more”, but we note that there are limits to the utility of this motto.
+Sampling more will clearly reduce uncertainty regarding the upper bound of the probability of interaction, and it will also increase the probability of detecting unlikely interactions (i.e.
+interactions occurring with a low probability).
+Yet, since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences quicker than we will accumulate observations of interactions.
+Thus, the more we sample, the more holes will appear in our interaction matrix, which may seem like a counter-intuitive outcome.
+
+As a solution towards deciding whether unobserved interactions were undetected due to sampling, or whether they truly do not occur, Weinstein et al.
+(2017) used daily repeated sampling rounds to estimate the daily probability of detecting a hummingbird interaction, and to thereby model the observation and process mechanisms (Weinstein, B.
+G., & Graham, C.
+H.
+(2017).
+On comparing traits and abundance for predicting species interactions with imperfect detection.
+Food Webs 11; 17-25: https://doi.org/10.1016/j.fooweb.2017.05.002).
+While conceptually attractive, this approach is unsuitable for interactions occurring over longer time scales (like associations between hosts and parasitoids with a single generation per year), or very rare interactions (since no matter how frequently and extensively we sample, there will still be some rare interactions lurking around).
+What is worse, the problem persists that if a given interaction is not observed on a given day, then it may still be either because it was impossible that day ((P(L|co-occurrence of A and B)=0), because interaction between the two did occur but was not observed, or from any combination of the two.
+Thus, from a conceptual perspective, this approach will fail to satisfactorily separating between all sources of uncertainty.
+An interaction not observed on day t may have gone unobserved either because there were constraints on the process (i.e.
+the probability was really zero), because of chance variation in the realized incidence of an event associated with a finite probability.
+Most importantly, if during a series of days, two species are simply never observed co-occurring, then we still have not learnt a thing about their probability of interacting should they do so.
+In other words, if the two interaction partners do not co-occur, we will still gain no information.
+
+An added complication is that not all sourced of uncertainty are proportional to sample size.
+To score an interaction between A and B, we will need to identify both partners correctly (a non-trivial problem in many food webs; e.g.
+Kaartinen et al.
+2011 Ecol Entomol; Roslin and Majaneva 2016) and be able to resolve all interactions with a similar likelihood.
+For both molecular (ref ref) and rearing techniques, given types of interactions may go unnoticed due to technical challenges.
+
+The bottom line is that separating between different sources of uncertainty is difficult indeed.
+In the best of all possible worlds, we might then use an experimental approach to estimate detection uncertainty: we might create replicate sets of cases where the interaction is really there, then evaluating them and examining the fraction of cases scoring positive.
+Yet, as anyone attempting these experiments will know, most interaction partners are proving notoriously unwilling to collaborate.
+Gallers refuse to lay eggs on their host plants (ref ref), parasitoids to attack their hosts when experimentally introduced (Gariepy 2017; ref ref).
+If we introduce only one of the components (like in the cases where we expose a set of hosts to parasitism; ref ref; Gripenberg et al.
+xxx) then we are already confounding multiple levels of uncertainty in the outcome – that of interaction uncertainty (whether the species will interact once both there), process uncertainty (whether the interaction will occur if and since the probability of interaction is below one), and detection uncertainty (i.e.
+whether we will observed the interaction once realized).
+To perform these experiments in a comprehensive and reliable manner, we will then need to expose a large number of interactions in a comprehensive experiment across space.
+This type of “cafeteria experiments in space” is not only unfeasible, but also undermining our original objective: If the local occurrence of interactions is uninformative regarding the underlying probabilities of occurrence, then we should be doing something else than wasting a monumental effort on collecting local interaction matrices.
+<deep sigh and forget that section?
+>
+
+As a tentative solution to disentangling observation and process mechanisms, we propose that some insights regarding the detectability of interactions between species not found co-occurring may be gained from data on other species, for which it is known that the interaction is feasible.
+If we use this information obtain the joint probability of detection and process (e.g.
+to glean information regarding at how many sites the species are found interacting across the entire dataset), and assuming that most of this pattern is due to variation in detection rate, then insights into the incidence of interactions between species may be gleaned from the accumulation rate of positive interactions at sites were interaction is possible (i.e.
+with at least one observation of a positive interaction) [this reasoning to be further formalized]
 
@@
 %Perhaps we want to also have a trait matching example in addition to the degree distribution example below?
+% Are degree distributions valid priors for interaction probabilities in a unipartite web?
+For the Salix-gall dataset we're using interaction probabilities as priors (since the degree of both Salix and galler matter)...
+maybe we should rephrase this to predict the degree of species $i$ based on the degrees of 10 other species in the network?
 The framework can be illustrated with a simple quantiative example.
-Suppose we have $n = 10$ observations of co-occurrence between speices $i$ and species $j$ in a given time interval and area, and $X = 2$ observations of interactions.
-The maximum likelihood estimate of the interaction probability is simply $\theta_{MLE} = 2/10 = 0.2$.
+Suppose we have $n = 10$ observations of co-occurrence between species $i$ and species $j$ in a given time interval and area, and $X = 3$ observations of interactions.
+The maximum likelihood estimate of the interaction probability is simply $\theta_{MLE} = 3/10 = 0.3$.
 % We should probabaly have a value  on the interaction probablitity that differs from the average of the degree distrbution
@@
 \noindent\emph{
-    degree = c(0.66, 0.09, 0.06, 0.08, 0.04, 0.30, 0.06, 0.38, 0.03, 0.19)
+   degree = c(0.66, 0.09, 0.06, 0.08, 0.04, 0.16, 0.06, 0.38, 0.03, 0.02)
     }.
@@
 
-Using these standardized degrees to inform our prior expectation of the 
-distribution of interaction probabilities and the R code from the 
-connectance example, we obtain prior parameters $\alpha$=0.9034876 
-and $\beta$=3.6623995. Using these priors in equations~\ref{mean} 
-and~\ref{variance} above, we find an average interaction probability of 0.1993348 and a variance of 0.01025322 [[Different from Dom's values]].
-% n=number of observed co-occurances.
-The average interaction probability is 0.2163971 and the variance is 0.02353319.
-The hyper parameters are computed according to the following script, using the function \emph{fitdistr} from the R~\citep{R} package MASS~\citep{MASS}, yielding:
+The mean of these standardized degrees is 0.158, approximately half the $\theta_{MLE}$ obtained from the observed data. We can use these standardized degrees to inform our prior expectation of the 
+distribution of interaction probabilities. With some simple R code (function calculate_parameters, \emph{Appendix S2}), we obtain prior parameters $\alpha$=0.7559544
+and $\beta$=3.6710277. Using these priors in equations~\ref{mean} 
+and~\ref{variance} above (or in the R function calculate_distribution in \emph{Appendix S2}), we find a prior mean interaction probability of 0.1707607 and a prior variance of 0.0319860.
 
-\vspace{12pt}
-\noindent\emph{    pars = fitdistr(x = degree, "beta", start = list(shape1 = 1, shape2 = 1),lower=c(0,0))\$estimate }.
-  \vspace{12pt}
+Adding the observed data (n=10, k=3) and using the same code,
+we obtain posterior hyper parameters $\alpha'$=3.755954 and $\beta'$=10.671028 and a posterior mean 0.2603423 and variance 0.0133475 for the probability of.
+Comparing the posterior distribution to the prior, we see that the posterior is closer to the observed data and that the additional data has reduced the variance.
 
-The lower bound of (0,0) for the two parameters of the Beta distribution prevents the function from attempting to fit invalid (negative) parameter estimations.
-
-The average of the distribution is computed as follows:
-
-  \vspace{12pt}
-\noindent
-\emph{
-    \noindent n = 10
-    \\\noindent k = 2
-    \\\noindent alpha\_prime = alpha + k
-    \\\noindent beta\_prime = beta + n - k
-    \\\noindent mean\_theta = alpha\_prime/(alpha\_prime+beta\_prime)
-},
-  \vspace{12pt}
-
-which yields a value $E[\theta]=0.2057651$ [[I get 0.1993348]]. And the variance:
-
-  \vspace{12pt}
-\noindent\emph{alpha\_prime$\times$ beta\_prime\/(alpha\_prime+beta\_prime)$^2$\/(alpha\_prime+beta\_prime+1)},
-  \vspace{12pt}
-
-which yiealds a value $var[\theta] = 0.009579623$. [[I get 0.01025322]]
-
-The credible interval is not symmetric around the mean since the distribution is bounded between 0 and 1 and is not symmetric.
-In this case, a 95\% credible interval for the mean of theta is (0.0448479, 0.4308686) and can be computed using the quantile function \emph{qbeta}:
-
-  \vspace{12pt}
-\noindent\emph{
-    \noindent lowCI = qbeta(p = 0.025, shape1 = alpha\_prime, shape2 = beta\_prime)
-    \\\noindent highCI = qbeta(p = 0.975, shape1 = alpha\_prime, shape2 = beta\_prime)}.
-  \vspace{12pt}
+We may also wish to calculate a credible interval (analogous to the frequentist confidence interval).
+This is also quite straightforward (see function credible_interval in \emph{Appendix S2}).
+In this case, a 95\% credible interval for the mean of theta is (0.07755119, 0.50557509).
 
@@
 We then use the cumulative distribution function to estimate $P(\theta<\theta*|X=0,n)$.
-The following script illustrates this probability for an increasing number of trials and $\theta*$=0.1:
+The
+function plot_precision in \emph{Appendix S2} calculates distribution function for $\theta*$ with an increasing number of trials. The figure below illustrates this distribution for $\theta*$=0.1.
 
-  \vspace{12pt}
-\noindent\emph{
-    \noindent n = seq(0,100,1)
-    \\\noindent X = 0
-    \\\noindent theta\_star = 0.1
-    \\\noindent cdf = pbeta(theta\_star, shape1 = alpha+X, shape2 = beta+n-X)
-    \\\noindent plot(n,cdf, type = "l", xlab = "n", ylab = "Cumulative distribution")
-    \\\noindent abline(h = 0.95,lty = 3)}.
-  \vspace{12pt}
-
-The exercise exemplified above yields a surprising result: it requires \textgreater30 [[or 23??]] observations of no interactions to be 95\% sure that the interaction probability is smaller than 0.1.
+The exercise exemplified above yields a surprising result: it requires \textgreater21 observations of no interactions to be 95\% sure that the interaction probability is smaller than 0.1.
 Note the special case where there is no observation of the two species co-occurring and failing to interact, $n = 0$.
@@
 \section*{Scaling up uncertainty from pairwise interactions to networks}
+
+It is fairly straigthforward to compute most of network metrics when the different $\lambda$ of the adjacency matrix are known, without variance (Poisot et al.
+2015).
+Several of these metrics derive directly from quantitative indices of network structure.
+It is not as easy however to understand how the uncertainty in these estimates do influence network metrics.
+There are multiple non-linearities in the computation of these metrics and that, because of Jensen's inequality (the principle stating that the average of non-linear function of a stochastic variable differs from the function of the average of that variable), any uncertainty could bias the average estimate of the metric and influence its variance as well.
+For instance, among all of the pairs of species for which only few co-occurrences are observed, many of them are truly interacting.
+If we consider all of these as having no links, then correcting for these false absence would inflate the number of links and therefore influence metrics such as connectance, nestedness and degree distribution.
+Computing network properties from probabilistic networks is one thing, but then computing them with uncertainties in these probabilities is another problem, far more challenging.
+Unfortunately, for now we could only rely on computer simulations to get an answer to this problem.
+In the following section, we will provide an example with the Salix dataset and show how the uncertainty arising from both absences of co-occurrences and false absences of interactions impact these metrics.
+We find uncertainty influences both the average and the variance of network metrics, putting in perspective traditional network comparison studies where these metrics are assumed fixed entities.
 
@@
 
-      [[add references to formulae]]
-
-      For species where no co-occurances were observed, we can calculate the MLE estimates for the mean and variance of $\lambda_{ij}$ directly from this prior. These are:
-      $\hat{\lambda_{ij}}$=0.5451437, var($\lambda$)=0.0481417.
-      This is consistent with the prior data, where the average interaction probability based on the degree distributions of Salix genotypes and gallers was 0.541.
-[[What's the connectance of our dataset, of we call greys 0?]] This probability does, however, seem rather high for our dataset.
-This discrepancy may be because~\citep{Balbour2016} were considering genotypes of a single \emph{Salix} species and only four gallers from a single family rather than multiple \emph{Salix} species and galler families as is the case in our dataset.
+      For species where no co-occurances were observed, we can 
+      calculate the MLE estimates for the mean and variance of 
+      $\lambda_{ij}$ directly from this prior following 
+      equations~\ref{mean} and~\ref{variance} 
+      (see \emph{Appendix S2} for R implementation). The prior 
+      distribution we obtain based on~\citet{Balbour2016} is:
+      $\hat{\lambda_{ij}}$=0.545, var($\lambda$)=0.048.
+      This is consistent with the prior data, where the average 
+      interaction probability based on the degree distributions of Salix genotypes and gallers was 0.541.
+[[What's the connectance of our dataset, if we call greys 0?]] This probability does, however, seem rather high for our dataset.
+This discrepancy may reflect the differences in scale between a network containing different genotypes of a single \emph{Salix} species and four gallers from a single family and a network containing many \emph{Salix} species and gallers from many families as is the case in our dataset.
 

### 2017-09-18 manuscript/CI_interactions.tex
description of posterior distributions, figure, and description of CIs and samples required in Salix data

@@
 In most cases, however, species $i$ and $j$ did not co-occur at so many sites and our posterior mean and variance retain some influence of the prior.
+Nevertheless, as the number of observed co-occurances increases, the posterior mean becomes closer to zero and the posterior variance decreases (Fig.~\ref{Salix_pdfs}).
 
-      Realistic values for n when k=0, based on a sample of 20 random sites:
-      n=1: 0.4565121 0.0403385
-      n=2: 0.39267022 0.03335076
-      n=3: 0.34449379 0.02770543
-      n=4: 0.30684696 0.02324331
-
-      [[Plot distribution of interaction probabilities at some reasonable values of n]]
+      \begin{figure}[ht]
+        \label{Salix_pdfs}
+        \caption{Posterior distributions for the probability of two species observed co-occurring but not interacting narrow and shift towards zero as the number of observed co-occurances increases.
+Here we show a selection of distributions ranging from the prior distribution (with N=0 observed co-occurances) to the distribution when there are 50 observed co-occurances.}
+        \includegraphics*[width=.8\textwidth]{figures/Salix_Galler_pdfs_increasing_N.eps}
+        \end{figure}
 
@@
       As well as obtaining posterior means and variances, it is possible to calculate a 95\% credible interval about the posterior mean.
+This is again straightforward to do in R (see the function "credible interval" in \emph{Appendix S2}).
+Calculating the 95\% credible intervals for species pairs with 0 to 50 observed co-occurrances without any observed interaction (as in Fig.~\ref{Salix_pdfs}), we see that the interval narrows dramatically as the number of observations increases.
+In no case, however, does the confidence interval include 0.
+Even for a pair of species which appeared together in all 374 sites but were never observed interacting, the confidence interval (0.001, 0.018) comes close to, but does not include zero.
+
+      \begin{table}[h]
+        \caption{}
+        \label{interval_table}
+        \begin{tabular}{l | c c}
+        N & Lower bound & Upper bound \\
+        \hline
+        0   & 0.157 & 0.901 \\
+        2   & 0.099 & 0.743 \\
+        4   & 0.072 & 0.621 \\
+        6   & 0.057 & 0.530 \\
+        8   & 0.047 & 0.462 \\
+        10 & 0.040 & 0.408 \\
+        14 & 0.031 & 0.331 \\
+        20 & 0.023 & 0.258 \\
+        30 & 0.016 & 0.188 \\
+        40 & 0.012 & 0.148 \\
+        50 & 0.010 & 0.122 \\
+        \hline
+        374 & 0.001 & 0.018 \\
+        \hline
+        \end{tabular}
+        \end{table}
 
   \subsection*{How many samples are required to reach a minimal precision}
+
+    Rather than calculating confidence intervals for a posterior distribution after collecting data, we may wish to know how many data points are necessary to obtain a given level of confidence that two co-occurring species do not interact.
+The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact.
+If we want to be 95\% confident that the interaction probability for two species in the \emph{Salix}-galler system is below 0.5, 0.1, or 0.01, we would need 6, 54, and 101 observed co-occurrances with no observed interaction (see function samples_required in~\emph{Appendix S2}).
+Given the low levels of replication in most network studies, this implies that we should have fairly low confidence in many "non-interacting" pairs of species.
+Even in the \emph{Salix}-galler dataset, [[how many pairs of species co-occur in >6,54,101 sites?]].
+Discounting potential interactions, then, requires either a stronger prior expectation of no interaction (e.g., we can be highly confident that a palm tree will not predate upon a leopard no matter how many times the two species are observed together) or very extensive sampling.
 

### 2017-09-18 code/figure_generation/pdfs_and_N.py

@@ -1,0 +1,116 @@
+######### R code to generate data files:
+# % Getting distributions:
+# xdata=matrix(ncol=1001,nrow=201)
+# ydata=matrix(ncol=1001,nrow=201)
+# for(n in 0:200){
+#   dist=calculate_distribution(calculate_parameters(int_probs,2*n,0))
+#   x=seq(-10,10,length=1000)*sqrt(dist[[2]])+dist[[1]]
+#   hx=dnorm(x)
+#   xdata[n+1,]=c(2*n,x)
+#   ydata[n+1,]=c(2*n,hx)
+# }
+
+# % Data are along rows for pythonic convenience
+# colnames(xdata)=c("N",seq(1,1000))
+# colnames(ydata)=c("N",seq(1,1000))
+# write.table(xdata,file='../data/Salix_example/Salix_Galler/distfigure_xvals.tsv',sep='\t')
+# write.table(ydata,file='../data/Salix_example/Salix_Galler/distfigure_yvals.tsv',sep='\t')
+
+# Something's funny about these data.
+
+import sys
+import math
+import random
+from decimal import *
+import numpy as np
+
+#Pygrace libraries
+from PyGrace.grace import Grace
+from PyGrace.colors import RandomColorScheme, MarkovChainColorScheme, ColorBrewerScheme
+from PyGrace.dataset import SYMBOLS
+from PyGrace.Extensions.panel import NetworkPanel,Panel,MultiPanelGrace
+from PyGrace.drawing_objects import DrawText, DrawLine, DrawBox
+from PyGrace.axis import LINEAR_SCALE, LOGARITHMIC_SCALE
+from PyGrace.Extensions.network import Network
+
+from PyGrace.Extensions.distribution import CDFGraph, PDFGraph
+from PyGrace.Extensions.latex_string import LatexString, CONVERT
+from PyGrace.Extensions.colorbar import SolidRectangle, ColorBar
+from PyGrace.Styles.el import ElGraph, ElLinColorBar, ElLogColorBar
+
+colors=ColorBrewerScheme('Spectral')  # The blue is very beautiful but maybe harder to see.
+# colors.add_color(120,120,120,'grey')
+
+def read_Rfiles(filename):
+  datadict={}
+
+  f=open(filename,'r')
+  for line in f:
+    if line.split()[0]!='"N"':
+      N=int(line.split()[1])
+      vals=line.split()[2:]
+      datadict[N]=vals
[…]

### 2017-09-18 code/figure_generation/samples_for_thresholds.py
starting on a figure showing how any samples we need

@@ -1,20 +1,25 @@
 ######### R code to generate data files:
-# % Getting distributions:
-# xdata=matrix(ncol=1001,nrow=201)
-# ydata=matrix(ncol=1001,nrow=201)
-# for(n in 0:200){
-#   dist=calculate_distribution(calculate_parameters(int_probs,2*n,0))
-#   x=seq(-10,10,length=1000)*sqrt(dist[[2]])+dist[[1]]
-#   hx=dnorm(x)
-#   xdata[n+1,]=c(2*n,x)
-#   ydata[n+1,]=c(2*n,hx)
+# % Getting cdfs:
+# pars=calculate_parameters(int_probs,0,0)
+# n=seq(0,100,1)
+
+# CDFs=matrix(nrow=9,ncol=104)
+# colnames(CDFs)=c("Threshold","Confidence","Samples",n)
+# r=1
+# for(threshold in c(0.5,0.1,0.01)){
+#   for(confidence in c(0.9,0.95,0.975)){
+#     cdf=pbeta(threshold,shape1=pars[[1]],shape2=pars[[2]]+n)
+#     samples=length(which(cdf<confidence))
+#     CDFs[r,1]=threshold
+#     CDFs[r,2]=confidence
+#     CDFs[r,3]=samples
+#     CDFs[r,4:104]=cdf
+#     print(r)
+#     r=r+1
+#   }
 # }
 
-# % Data are along rows for pythonic convenience
-# colnames(xdata)=c("N",seq(1,1000))
-# colnames(ydata)=c("N",seq(1,1000))
-# write.table(xdata,file='../data/Salix_example/Salix_Galler/distfigure_xvals.tsv',sep='\t')
-# write.table(ydata,file='../data/Salix_example/Salix_Galler/distfigure_yvals.tsv',sep='\t')
+# write.table(CDFs,file='../data/Salix_example/Salix_Galler/samplefigure.tsv',sep='\t')
 
 import sys
 import math
@@ -41,23 +46,31 @@ colors=ColorBrewerScheme('Spectral')  # The blue is very beautiful but maybe har
 
 def read_Rfiles(filename):
   datadict={}
+  sampledict={}
 
   f=open(filename,'r')
   for line in f:
-    if line.split()[0]!='"N"':
-      N=int(line.split()[1])
-      vals=line.split()[2:]
-      datadict[N]=vals
+    if line.split()[0]!='"Threshold"':
+      threshold=float(line.split()[1])
[…]

### 2017-09-19 code/figure_generation/samples_for_thresholds.py
Added the figure to show increasing samples with confidence, threshold.

@@ -1,24 +1,41 @@
-######### R code to generate data files:
-# % Getting cdfs:
+# ######### R code to generate data files:
+# # % Getting cdfs:
 # pars=calculate_parameters(int_probs,0,0)
-# n=seq(0,100,1)
+# n=seq(0,500,1)
 
-# CDFs=matrix(nrow=9,ncol=104)
-# colnames(CDFs)=c("Threshold","Confidence","Samples",n)
+# CDFs=matrix(nrow=4,ncol=502)
+# colnames(CDFs)=c("Threshold",n)
 # r=1
-# for(threshold in c(0.5,0.1,0.01)){
+# for(threshold in c(0.5,0.25,0.1,0.05)){
+#   # for(confidence in c(0.9,0.95,0.975)){
+#     cdf=pbeta(threshold,shape1=pars[[1]],shape2=pars[[2]]+n)
+#     # samples=length(which(cdf<confidence))
+#     CDFs[r,1]=threshold
+#     # CDFs[r,2]=confidence
+#     # CDFs[r,3]=samples
+#     CDFs[r,2:502]=cdf
+#     print(r)
+#     r=r+1
+#   }
+# # }
+
+
+# samples=matrix(nrow=12,ncol=3)
+# colnames(samples)=c("Threshold","Confidence","Samples")
+# r=1
+# for(threshold in c(0.5,0.25,0.1,0.05)){
 #   for(confidence in c(0.9,0.95,0.975)){
 #     cdf=pbeta(threshold,shape1=pars[[1]],shape2=pars[[2]]+n)
-#     samples=length(which(cdf<confidence))
-#     CDFs[r,1]=threshold
-#     CDFs[r,2]=confidence
-#     CDFs[r,3]=samples
-#     CDFs[r,4:104]=cdf
+#     n_obs=length(which(cdf<confidence))
+#     samples[r,1]=threshold
+#     samples[r,2]=confidence
+#     samples[r,3]=n_obs
 #     print(r)
 #     r=r+1
 #   }
 # }
 
+# write.table(samples,file='../data/Salix_example/Salix_Galler/samples_for_threshold.tsv',sep='\t')
 # write.table(CDFs,file='../data/Salix_example/Salix_Galler/samplefigure.tsv',sep='\t')
 
 import sys
@@ -52,24 +69,29 @@ def read_Rfiles(filename):
   for line in f:
     if line.split()[0]!='"Threshold"':
       threshold=float(line.split()[1])
[…]

### 2017-09-19 manuscript/CI_interactions.tex
added the figure to the text

@@
 The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact.
-If we want to be 95\% confident that the interaction probability for two species in the \emph{Salix}-galler system is below 0.5, 0.1, or 0.01, we would need 6, 54, and 101 observed co-occurrances with no observed interaction (see function samples_required in~\emph{Appendix S2}).
+If we want to be 95\% confident that the interaction probability for two species in the \emph{Salix}-galler system is below 0.5, 0.1, or 0.01, we would need 6, 54, and 114 observed co-occurrances with no observed interaction (see function samples_required in~\emph{Appendix S2}).
 Given the low levels of replication in most network studies, this implies that we should have fairly low confidence in many "non-interacting" pairs of species.
-Even in the \emph{Salix}-galler dataset, [[how many pairs of species co-occur in >6,54,101 sites?]].
+Even in the \emph{Salix}-galler dataset, [[how many pairs of species co-occur in >6,54,114 sites?]].
 Discounting potential interactions, then, requires either a stronger prior expectation of no interaction (e.g., we can be highly confident that a palm tree will not predate upon a leopard no matter how many times the two species are observed together) or very extensive sampling.
 
-    - Have code for graphing or returning sample size set up.
-    - Plot Increase in sample sizes with decreasing threshold, increasing confidence.
+    \begin{figure}[ht]
+      \caption{The number of samples required to achieve a given level of confidence that an interaction probability is below a given threshold varies with both parameters.
+With a low threshold, our confidence that $\omega_{ij}$ is below the threshold increases rapidly with repeated observation of co-occurance without interaction.
+Here we show the cumulartive density functions for thresholds probabilities of 0.5 (solid line), 0.25 (dashed line), 0.1 (dash-dot line), and 0.05 (dotted line) as well as the points at which the cdf reaches 0.90 (orange square), 0.95 (red circle), and 0.975 (blue diamond) for each threshold value.
+The large ticks along the x-axis indicate the number of samples associated with each of these points.}
+      \label{Salix_cdfs}
+      \includegraphics[width=.8\textwidth]{figures/Salix_Galler_samples_and_cdfs.eps}
 
-  [[What if we have only one site?
+      \end{figure}
+
+  % [[What if we have only one site?
 Can we use the number of observations of a pair of species interacting with any partners as the number of times they co-occur, and the number of interactions within the pair as k?

### 2017-09-19 code/figure_generation/samples_for_thresholds.py

@@ -100,20 +100,20 @@ def format_graph(graph):
   graph.xaxis.bar.linewidth=1
   graph.frame.linewidth=1
   graph.world.xmin=0
-  graph.world.xmax=200
+  graph.world.xmax=150
   graph.world.ymin=-0
   graph.world.ymax=1
 
-  graph.yaxis.tick.configure(major=.20,onoff='on',minor_ticks=0,major_size=.7,minor_size=.5,place='normal',major_linewidth=1,minor_linewidth=1)
+  graph.yaxis.tick.configure(major=.20,onoff='on',minor_ticks=1,major_size=.5,minor_size=.3,place='normal',major_linewidth=1,minor_linewidth=1)
   graph.yaxis.ticklabel.configure(char_size=.75,format='decimal',prec=1)
 
-  graph.xaxis.tick.configure(major=50,onoff='on',minor_ticks=0,major_size=.5,place='normal',minor_size=.5,major_linewidth=1,minor_linewidth=1)
+  graph.xaxis.tick.configure(major=20,onoff='on',minor_ticks=1,major_size=.5,place='normal',minor_size=.3,major_linewidth=1,minor_linewidth=1)
   graph.xaxis.ticklabel.configure(char_size=.75,format='decimal',prec=0)
 
   graph.xaxis.label.configure(text="Number of samples",char_size=1,just=2,place='normal')
   graph.yaxis.label.configure(text="Cumulative density",char_size=1,just=2)
   graph.legend.configure(box_linestyle=0,fill=0,fill_pattern=0,char_size=.75,
-    loc=(125,.75),loctype='world')
+    loc=(100,.75),loctype='world')
   # graph.add_drawing_object(DrawText,text="Threshold",x=150,y=.9,char_size=.75,just=2,loctype='world')
 
   return graph
@@ -173,7 +173,7 @@ def add_samplelines(graph,sampledict):
   dots.symbol.configure(shape=3,color=11,size=.75,fill_color=11)
   dots.legend="P=0.975"
 
-  print 'sqif'
+  print 'dots added'
   return graph
 
 grace=Grace(colors=colors)

### 2017-09-19 manuscript/CI_interactions.tex
fixed some small compiling errors

@@
 
-It is important to keep in mind that for network analysis, ecologists seek to measure the occurrence of true absences, which is the joint event $L=1\cup X=1 \cup \D=1$), but in reality they measure the marginal probability $P(L) = k/n$.
+It is important to keep in mind that for network analysis, ecologists seek to measure the occurrence of true absences, which is the joint event $L=1\cup X=1 \cup D=1$), but in reality they measure the marginal probability $P(L) = k/n$.
 
@@
 (2017) used daily repeated sampling rounds to estimate the daily probability of detecting a hummingbird interaction, and to thereby model the observation and process mechanisms (Weinstein, B.
-G., & Graham, C.
+G., \& Graham, C.
 H.
@@
 The mean of these standardized degrees is 0.158, approximately half the $\theta_{MLE}$ obtained from the observed data. We can use these standardized degrees to inform our prior expectation of the 
-distribution of interaction probabilities. With some simple R code (function calculate_parameters, \emph{Appendix S2}), we obtain prior parameters $\alpha$=0.7559544
+distribution of interaction probabilities. With some simple R code (function calculate\_parameters, \emph{Appendix S2}), we obtain prior parameters $\alpha$=0.7559544
 and $\beta$=3.6710277. Using these priors in equations~\ref{mean} 
-and~\ref{variance} above (or in the R function calculate_distribution in \emph{Appendix S2}), we find a prior mean interaction probability of 0.1707607 and a prior variance of 0.0319860.
+and~\ref{variance} above (or in the R function calculate\_distribution in \emph{Appendix S2}), we find a prior mean interaction probability of 0.1707607 and a prior variance of 0.0319860.
 
@@
 We may also wish to calculate a credible interval (analogous to the frequentist confidence interval).
-This is also quite straightforward (see function credible_interval in \emph{Appendix S2}).
+This is also quite straightforward (see function credible\_interval in \emph{Appendix S2}).
 In this case, a 95\% credible interval for the mean of theta is (0.07755119, 0.50557509).
@@
 The
-function plot_precision in \emph{Appendix S2} calculates distribution function for $\theta*$ with an increasing number of trials. The figure below illustrates this distribution for $\theta*$=0.1.
+function plot\_precision in \emph{Appendix S2} calculates distribution function for $\theta*$ with an increasing number of trials. The figure below illustrates this distribution for $\theta*$=0.1.
 
@@
 In no case, however, does the confidence interval include 0.
-Even for a pair of species which appeared together in all 374 sites but were never observed interacting, the confidence interval (0.001, 0.018) comes close to, but does not include zero.
+Even for a pair of species which appeared together in all 374 sites but were never observed interacting, the confidence interval (0.001, 0.018) comes close to, but does not include zero (Table~\ref{interval_table}).
 
       \begin{table}[h]
-        \caption{}
+        \caption{95\% credible intervals for the interaction probability of two species that co-occur in $N$ sites but are never observed to interact, obtained using prior information from the \emph{Salix}-galler network in~\citet{Balbour2016}.}
         \label{interval_table}
@@
 The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact.
-If we want to be 95\% confident that the interaction probability for two species in the \emph{Salix}-galler system is below 0.5, 0.1, or 0.01, we would need 6, 54, and 114 observed co-occurrances with no observed interaction (see function samples_required in~\emph{Appendix S2}).
+If we want to be 95\% confident that the interaction probability for two species in the \emph{Salix}-galler system is below 0.5, 0.1, or 0.01, we would need 6, 54, and 114 observed co-occurrances with no observed interaction (Fig.~\ref{Salix_cdfs}; see function samples\_required in~\emph{Appendix S2}).
 Given the low levels of replication in most network studies, this implies that we should have fairly low confidence in many "non-interacting" pairs of species.
-Even in the \emph{Salix}-galler dataset, [[how many pairs of species co-occur in >6,54,114 sites?]].
+Even in the \emph{Salix}-galler dataset, [[how many pairs of species co-occur in \textgreater6,54,114 sites?]].
 Discounting potential interactions, then, requires either a stronger prior expectation of no interaction (e.g., we can be highly confident that a palm tree will not predate upon a leopard no matter how many times the two species are observed together) or very extensive sampling.

### 2017-09-20 manuscript/supplemental.tex
partly formatted R code for nice compiling

@@
+\documentclass[12pt]{article} 
+\usepackage{amsmath} 
+\usepackage[dvips]{graphicx}
+\usepackage{multirow} 
+\usepackage{geometry} 
+\usepackage{pdflscape}
+\usepackage[labelfont=bf]{caption} 
+\usepackage{setspace}
+\usepackage[running]{lineno} 
+% \usepackage[numbers,sort]{natbib}
+\usepackage[round]{natbib} 
+\usepackage{array}
+
+\newcommand{\methods}{\textit{Materials \& Methods}}
+\newcommand{\SI}{\textit{Appendix}~}
+
+\topmargin -1.5cm % 0.0cm 
+\oddsidemargin 0.0cm % 0.2cm 
+\textwidth 6.5in
+\textheight 9.0in % 21cm
+\footskip 1.0cm % 1.0cm
+
+\usepackage{authblk}
+
+\title{Supplemental information}
+
+\author{Authors}
+\date{\small$^1$Department of Physics, Chemistry\\ 
+and Biology (IFM)\\ 
+Link\"{o}ping University\\
+Link\"{o}ping, Sweden\\
+% \medskip
+% $^\dagger$ Corresponding author:\\
+% alyssa.cirtwill@gmail.com\\
+% +46 723 158464\\
+ }
+
+\renewcommand\Authands{ and }
+
+\begin{document} 
+\maketitle 
+\raggedright
+\setlength{\parindent}{15pt} 
+\clearpage
+
 \section*{Appendix S1: Obtaining prior interaction probabilities}
@@
 
-      Barbour \emph{et al.} sampled 145 branches from \emph{Salix hookeriana} of 26 genotypes.
-They recorded galls made by four species of Cecidomyid midges on each branch.
-We transformed these data to a binary genotype-galler network matrix, where an entry $ij$ was 1 if galler $i$ was observed on any branch of genotype $j$ and 0 otherwise.
-In total, this network contained 75 realized galler-genotype interactions out of a potential 104.
-The R code used to extract this network follows:
+      Barbour \emph{et al.} sampled 145 branches from 
+      \emph{Salix hookeriana} of 26 genotypes. They recorded galls 
+      made by four species of Cecidomyid midges on each branch. We 
+      transformed these data to a binary genotype-galler network 
+      matrix, where an entry $ij$ was 1 if galler $i$ was observed 
+      on any branch of genotype $j$ and 0 otherwise. In total, this 
+      network contained 75 realized galler-genotype interactions 
+      out of a potential 104. The R code used to extract this 
+      network follows:
+
+      \vspace{12pt}
+      \emph{
+      \noindent \hspace{-4pt} prior\_web\_data=read.csv(``tree\_level\_interaxn\_all\_plants\_traits\_size.csv")\\
+      \# Remove extra data on parasitoids, etc.\\
+      prior\_web\_data[,31:57]\textless-NULL\\
+      prior\_web\_data[,4:26]\textless-NULL\\
+      prior\_web\_data[,2]\textless-NULL\\
+      \# Build a web with interactions=1 for any galler observed on any genotype\\
+      prior\_web=matrix(nrow=26,ncol=4)\\
+      for(r in 1:length(levels(prior\_web\_data\$Genotype)))\{\\
+      \hspace{4pt}  gen=levels(prior\_web\_data\$Genotype)[r]\\
+      \hspace{4pt}  subset=prior\_web\_data[which(prior\_web\_data\$Genotype==gen),]\\
+      \hspace{4pt}  for(c in 1:4)\{\\
+      \hspace{8pt}    if(sum(subset[,2+c])\textgreater0)\{\\
+      \hspace{12pt}      prior\_web[r,c]=1\\
+      \hspace{8pt}    \} else \{\\
+      \hspace{12pt}      prior\_web[r,c]=0\\
+      \hspace{8pt}    \}\}\}
+      }
 
@@
 
-      Obtaining degree distributions from the binary interaction network is straightforward.
-To do this, we simply divide the total number of observed interaction partners for each species (row or column sums) with the number of potential interaction partners (number of column or rows).
-Degree distributions calculated, we can then calculate the probability of each interaction as the product of the normalized degrees of the two species.
-For example, the probability of an interaction between two species with normalized degrees of 0.5 (each interacts with half of the available partners) is 0.25.
-R code used to do this follows:
+      Obtaining degree distributions from the binary interaction 
+      network is straightforward. To do this, we simply divide the 
+      total number of observed interaction partners for each 
+      species (row or column sums) with the number of potential 
+      interaction partners (number of column or rows). Degree 
+      distributions calculated, we can then calculate the 
+      probability of each interaction as the product of the 
+      normalized degrees of the two species. For example, the 
+      probability of an interaction between two species with 
+      normalized degrees of 0.5 (each interacts with half of the 
+      available partners) is 0.25. R code used to do this follows:
+
+      \vspace{12pt}
+      \emph{
+      \noindent \hspace{-4pt} \# Now get the degree distributions from the web\\
+      deg\_dist\_Salix=rowSums(prior\_web)/ncol(prior\_web)\\
+      \# Remove one genotype that never interacted\\
+      deg\_dist\_Salix\textless-deg\_dist\_Salix[which(rowSums(prior\_web)\textgreater0)]\\
+      deg\_dist\_galler=colSums(prior\_web)/nrow(prior\_web)\\
+      \# Interaction probabilities are the product of plant and galler probabilities\\
+      int\_probs=as.numeric(deg\_dist\_galler\%$*$\%t(deg\_dist\_Salix))\\
+      }
 
@@
 
+\clearpage
+
 \section*{Appendix S2: Calculating posterior distributions and confidence intervals}
@@
   The following simple functions are implemented in the R language. 
-Priordata is the list of interaction frequencies from the prior data, n is the number of sites with observed co-occurrance of species $i$ and $j$, and k is the number of sites with an observed interaction $ij$.
-When calculating the prior distribution, both n and k are 0.
-In the main text we assume 100\% confidence in observed interactions and therefore consider only cases where k=0.
-Only n varies between species pairs.
+  Priordata is the list of interaction frequencies from the prior 
+  data, n is the number of sites with observed co-occurrance of 
+  species $i$ and $j$, and k is the number of sites with an 
+  observed interaction $ij$. When calculating the prior 
+  distribution, both n and k are 0. In the main text we assume 100\%
+  confidence in observed interactions and therefore consider only 
+  cases where k=0. Only n varies between species pairs.
 
-  To calculate the parameters $\alpha$ and $\beta$ of a prior or posterior distribution:
+  To calculate the parameters $\alpha$ and $\beta$ of a prior or 
+  posterior distribution:
 
   \vspace{12pt}
-  calculate\_parameters\textless-function(priordata,n,k)\{
-  \# Calculate the parameters of the prior distribution
-  pars=fitdistr(x=priordata,"beta",start=list(shape1=1,shape2=1),lower=c(0,0))\$estimate
-  alpha=pars[[1]]
-  beta=pars[[2]]
-  \# Update the parameters with data. If n=0 and k=0, no change.
-  alpha\_prime=alpha+k
-  beta\_prime=beta+n-k
-  pars2=c(alpha\_prime,beta\_prime)
-  return(pars2)
+  \emph{
+  \noindent \hspace{-4pt}calculate\_parameters\textless-function(priordata,n,k)\{\\
+  \hspace{4pt} \# Calculate prior parameters\\
+  \hspace{4pt} start=list(shape1=1,shape2=1)
+  \hspace{80pt} pars=fitdistr(x=priordata,`beta',start=start,lower=c(0,0))\$estimate\\
+  \hspace{4pt} alpha=pars[[1]]\\
+  \hspace{4pt} beta=pars[[2]]\\
+  \hspace{4pt} \# Update the parameters with data. If n=0 and k=0, no change.\\
+  \hspace{4pt} alpha\_prime=alpha+k\\
+  \hspace{4pt} beta\_prime=beta+n-k\\
+  \hspace{4pt} pars2=c(alpha\_prime,beta\_prime)\\
+  \hspace{4pt} return(pars2) \}
   }
+  \vspace{12pt}
 
-    % calculate_parameters<-function(priordata,n,k){
-    %   pars=fitdistr(x=priordata,"beta",start=list(shape1=1,shape2=1),lower=c(0,0))$estimate
-    %   alpha=pars[[1]]
-    %   beta=pars[[2]]
-    %   alpha_prime=alpha+k
-    %   beta_prime=beta+n-k
-    %   pars2=c(alpha_prime,beta_prime)
-    %   return(pars2)
-    % }
-
-    To calculate the maximum likelihood estimates of the mean and variance of the probability of interaction $\lambda_{ij}$:
+    To calculate the maximum likelihood estimates of the mean and 
+    variance of the probability of interaction $\lambda_{ij}$:
 
     \vspace{12pt}
-    calculate\_distribution\textless-function(pars){
-      \# alpha and beta may be from a prior or posterior distribution
-      alpha=pars[[1]]
-      beta=pars[[2]]
+    \emph{
+    calculate\_distribution\textless-function(pars)\{\\
+      \# alpha and beta may be from a prior or posterior distribution\\
+      alpha=pars[[1]]\\
+      beta=pars[[2]]\\
 
-      \# Calculate the MLE of the mean
-      mu\_num=alpha
-      mu\_den=alpha+beta
-      mu=mu\_num\/mu\_den
+      \# Calculate the MLE of the mean\\
+      mu\_num=alpha\\
+      mu\_den=alpha+beta\\
+      mu=mu\_num\/mu\_den\\
 
-      \# Calculate the MLE of the variance
-      sig\_num=alpha\*beta
-      den1=alpha+beta
-      den2=den1\*\*2
-      sig\_den=den1\*den2
-      sigma2=sig\_num\/sig\_den
+      \# Calculate the MLE of the variance\\
+      sig\_num=alpha\*beta\\
+      den1=alpha+beta\\
+      den2=den1\*\*2\\
+      sig\_den=den1\*den2\\
+      sigma2=sig\_num\/sig\_den\\
 
-      return(c(mu,sigma2))
+      return(c(mu,sigma2))\}
     }
-
-  % calculate_distribution<-function(pars){
-  %       alpha=pars[[1]]
-  %       beta=pars[[2]]
-
-  %       mu_num=alpha
-  %       mu_den=alpha+beta
-  %       mu=mu_num/mu_den
-
-  %       sig_num=alpha*beta
-  %       den1=alpha+beta
-  %       den2=den1**2
-  %       sig_den=den1*den2
-  %       sigma2=sig_num/sig_den
-
-  %       return(c(mu,sigma2))
-  %     }
+  \vspace{12pt}
 
@@
   \vspace{12pt}
-
-credible_interval<-function(pars,p_lower,p_upper){
-  alpha=pars[[1]]
-  beta=pars[[2]]
-  lowCI=qbeta(p=p_lower,shape1=alpha,shape2=beta)
-  highCI=qbeta(p=p_upper,shape1=alpha,shape2=beta)
-  return(c(lowCI,highCI))
+  \emph{
+  credible\_interval\textless-function(pars,p\_lower,p\_upper)\{\\
+    alpha=pars[[1]]\\
+    beta=pars[[2]]\\
+    lowCI=qbeta(p=p\_lower,shape1=alpha,shape2=beta)\\
+    highCI=qbeta(p=p\_upper,shape1=alpha,shape2=beta)\\
+    return(c(lowCI,highCI))\}
   }
 
-plot_precision<-function(threshold,confidence,pars){
-  alpha=pars[[1]]
-  beta=pars[[2]]
-  n=seq(0,100,1)
-  k=0
-  cdf=pbeta(threshold,shape1=alpha,shape2=beta+n)
-  samples=length(which(cdf<confidence))
-  # plot(n,cdf,type="l",xlab="n",ylab="Cumulative distribution")
-  # abline(h=0.95,lty=3)
-  return(samples)
+  \vspace{12pt}
+  \emph{
+  plot\_precision\textless-function(threshold,confidence,pars)\{\\
+    alpha=pars[[1]]\\
+    beta=pars[[2]]\\
+    n=seq(0,100,1)\\
+    k=0\\
+    cdf=pbeta(threshold,shape1=alpha,shape2=beta+n)\\
+    samples=length(which(cdf<confidence))\\
+    return(samples) \}
   }
+
+\clearpage
+
+    \bibliographystyle{ecollett} 
+    \bibliography{manual_abbrev} % Abbreviate journal titles.
+
+\end{document}

### 2017-09-22 manuscript/CI_interactions.tex
added references and tweaked language in intro, naive quanitification sections

@@
 This assumption conflicts with known variation in interactions over time~\citep{Kitching1987,Olesen2011a} and space~\citep{Kitching1987,Baiser2012} and between individuals of a given species~\citep{Pires2011a,Fodrie2015,Novak2015}.
-Taking the variances in interaction frequencies into account would therefore represent a substantial increase in the realism of ecological networks as representations of ecological communities.
+Taking the variation in interaction frequencies into account would therefore represent a substantial increase in the realism of ecological networks as representations of ecological communities.
 
@@
 Community composition and species abundances vary from site to site~\citep{Baiser2012} and over time within a site~\citep{Olesen2011a}.
-Moreover, interactions between species may change even if the participating species remain present at a site but do not co-occur temporally or are too rare to detect each other~\citep{Tylianakis2010}, or through changes to individual preferences~\citep{Fodrie2015}.
+The removal of a species from a site will obviously also remove its interactions.
+Interactions can also be lost, however, if participating species remain present but do not co-occur temporally or are too rare to detect each other~\citep{Tylianakis2010}, or through changes to individual preferences~\citep{Fodrie2015}.
 Several researchers have pointed to the importance of sampling intensity for the assessment of network structure (e.g.,~\citealp{}).
-The acknowledgement that insufficient sampling effort limits our ability to describe variation in ecological networks has not, however, led to a quantitative framework to deal with the uncertainty of ecological interactions and of sampling.
+Despite this, the acknowledgement that insufficient sampling effort limits our ability to describe variation in ecological networks has not yet led to a quantitative framework to deal with the uncertainty of ecological interactions and of sampling.
 
@@
 We start with the description of a new Bayesian approach to estimate ecological interactions and of a related R package.
-We first illustrate the framework with simple quantitative examples, followed by an assessment of the quality of an empirically-estimated plant-pollinator network.
+[[We first illustrate the framework with a simple quantitative example.
 Next, we use the framework to provide analytical criteria for improving the sampling of rare interations.
-Finally, we discuss the implications of uncertainty in the estimation of pairwise interactions on the properties of ecological networks.
-Through these efforts, we demonstrate both the utility of our approach and the importance of acknowledging the uncertainty inherent in ecological networks.
-
-% <!-- ## Background
-
-%   - Ecological interaction networks are usually considered deterministic, but nature is highly variable and interactions should be considered with their variance
-%   - There is spatial and temporal variability in network structure and of pairwise interactions
-%   - There used to be a debate on the importance of sampling intensity for the assessment of network structure, but it never led to a quantitative framework dealing with uncertainty of ecological interactions and of sampling
-
-% ## Objective:
-
-%   - The main objective of this study is to develop analytical tools that could be used to better represent the uncertainty in the estimation of pairwise interaction probability
-%   - We start with the description of a new bayesian approach to estimate ecological interactions and of a related R package. 
-%   - We illustre the framework with simple quantitative examples, and then with the assessment of the quality of an empirical estimate of plant-pollinator networks. 
-%   - We further use the framework to provide analytical criteria for improving the sampling of rare interations. 
-%   - We discuss the implications of the uncertainty in the estimation of pairwise interactions on the properties of ecological networks -->
+Finally, we discuss the implications of uncertainty in the estimation of pairwise interactions on the properties of ecological networks.]] Through these efforts, we demonstrate both the utility of our approach and the importance of acknowledging the uncertainty inherent in ecological networks.
+    % List of sections may not be accurate any more. Update when paper reaches its final form.
 
@@
 
-It is getting more and more common to represent interactions as probabilities.
-Some theoretical models of network structure propose to represent interactions with probabilities, for instance the minmum potential model introduces gaps in the feeding niche of predators (Allesina et al.
-2008), while a gaussian probability function is used to represent the niche by Williams et al.
-(2010).
-Eklof et al.
-(2013) introduced variability as well in the computation of network dimensions, allowing the absence of interactions within the n-dimension niche of every species.
-Empirical investigation of trait-matching constraints often consider the occurrence of interactions as binomial process (e.g.
-Rohr et al.
-2016).
-There are also ways to perform analysis of probabilistic networks, with almost all metrics having a probabilistic version (Poisot et al.
-2015).
+It is getting more and more common to represent interactions as probabilities in theoretical models of network structure.
+For example, the minimum potential model introduces gaps in the feeding niche of predators by sampling based on the likelihood of each interaction~\citep{Allesina2008}, while a gaussian probability function is used to represent the niche by~\citet{Williams2010}.
+\citet{Eklof2013} also introduced variability  in the computation of network dimensions, allowing the absence of interactions within the n-dimension niche of every species.
+Empirical investigation of trait-matching constraints often consider the occurrence of interactions as binomial process (e.g.,~\citealp{Rohr2016}).
+There are also ways to perform analysis of probabilistic networks, with almost all metrics having a probabilistic version~\citep{Poisot2016}.
 But there is not yet consensus on what an interaction probability between a pair of species means, and this is definitely a problem when comes time to estimate the uncertainty of both pairwise interactions and entire networks.
 
-As a start, we will consider how we could naively quantify intetraction probability and its associated uncertainty.
-We consider that a pair of species have been observed $n$ times co-occurring at one location, and the number of times they interact is $k = 0$.
+As a start, we will consider how we could naively quantify intetraction probability and its associated uncertainty for an interaction that has not yet been observed.
+We consider that a pair of species have been observed $n$ times co-occurring at one location, and the number of times they have been observed interacting is $k = 0$.
 We aim to evaluate the uncertainty of this interaction.
@@
 \noindent The parameter $\lambda$, the probability of observing an interaction over an infinite time interval and area, is the quantity we want to estimate from empirical data. 
-The variance of a Bernoulli experiment is simply n$\lambda$(1-$\lambda$).
-It is important to remember this variance reports the variability of the number of success $k$ for $n$ trials, it is not the variance associated with the estimation of $\lambda$.
-
-The maximal likelihood estimate of $\lambda$ is straightforward to find given $k$ and $n$. It is simply equal to:
+The maximal likelihood estimate (MLE) of $\lambda$ is straightforward to find given $k$ and $n$. It is simply equal to:
 
@@
 
-It is possible to compute the confidence interval for this estimate using any of several methods, including the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull Interval}.
+The variance of a Bernoulli experiment is simply $n\lambda$(1-$\lambda$).
+It is important to remember this variance reports the variability of the number of success $k$ for $n$ trials and is not the variance associated with the estimation of $\lambda$.
+Given this variance, it is possible to compute the confidence interval for the MLE of $\lambda$ using any of several methods, including the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull Interval}.
 Finding this estimate is therefore quite straightforward, but it nonetheless has two drawbacks.
 First, $\lambda$ is a random variable with a given uncertainty and whose distribution is unknown, it is not a single point estimate.
-This means that even if $k = 0$ in a given sample, it does not implies necessarily that the two species will never interact.
-It means that no interaction is the most likely situation, but there is nonetheless a significant chance that the two species could interaction.
-In contrast with the situation where $k>0$, where we are sure that an interaction is feasible (in which case, the ratio $k/n$ is smaller than $n$ because of detection and process uncertainty), we are not sure that absence of interactions are caused by $L=0$.
-Second, and most importantly, the number of trials $n$ might be very low in many instances (and some pairs of species might even not be documented), and consequently the uncertainty in the estimation of $\lambda$ might be considerable.
-We illustrated at Fig.
+This means that even if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact.
+It means that no interaction is the most likely situation but there is nonetheless a significant chance that the two species could interaction.
+In contrast with the situation where $k>0$, when we are sure that an interaction is feasible,
+% (in which case, the ratio $k/n$ is smaller than $n$ because of detection and process uncertainty),  % This parenthetical makes the sentence very long. Is it necessary?
+we are not sure that absence of interactions is caused by $L=0$.
+Second, and most importantly, the number of trials $n$ might be very low in many instances (and some pairs of species might even not be documented once).
+Consequently, the uncertainty in the estimation of $\lambda$ might be considerable.
+We illustrated in Fig.
 X how the estimate of $\lambda$ could vary with sampling size using the Clopper-Pearson interval.
 It shows that the 95\% confidence interval requires a signifcant amount of sampling in order to be sure that species are not interacting.
+% Is the Clopper-Pearson interval the one in Dom's code snippets? If so, this is Fig.~\ref{Salix_cdfs}
 
-The situation where $k = 0$ is also problematic because we have very few information to estimate $\lambda$, in particular when $n$ is also small.
+The situation where $k = 0$ is also problematic because we have very little information with which to estimate $\lambda$, in particular when $n$ is also small.
 We therefore propose a Bayesian approach to solve this problem, building on two relevant features of such statistics : posterior distribution of parameter estimates and usage of prior information.
-But before moving to this direction, we will first take time to better describe what is exactly meant by an interaction probability and appropriately define sources of uncertainty.
+Before moving to this direction, we will first take time to better describe what is exactly meant by an interaction probability and appropriately define sources of uncertainty.
 

### 2017-09-22 manuscript/CI_interactions.tex
added a preliminary bibliography and a couple more refs

@@
 Interactions can also be lost, however, if participating species remain present but do not co-occur temporally or are too rare to detect each other~\citep{Tylianakis2010}, or through changes to individual preferences~\citep{Fodrie2015}.
-Several researchers have pointed to the importance of sampling intensity for the assessment of network structure (e.g.,~\citealp{}).
+Several researchers have pointed to the importance of sampling intensity for the assessment of network structure (e.g.,~\citealp{Martinez1999,Bluthgen2006,XX}).
 Despite this, the acknowledgement that insufficient sampling effort limits our ability to describe variation in ecological networks has not yet led to a quantitative framework to deal with the uncertainty of ecological interactions and of sampling.
@@
       In a strict Bayesian framework, we wish to use a prior distribution that does not rely on any information from the study at hand.
-To that end, we use data from another well-described \emph{Salix} galler-parasitoid system (doi: 10.1073/pnas.1513633113).
+To that end, we use data from another well-described \emph{Salix} galler-parasitoid system~\citep{Barbour2016,Barbour2016Dryad}.
 Note that this study used several genotypes of \emph{S.
@@
       (see \emph{Appendix S2} for R implementation). The prior 
-      distribution we obtain based on~\citet{Balbour2016} is:
+      distribution we obtain based on~\citet{Barbour2016,Barbour2016Dryad} is:
       $\hat{\lambda_{ij}}$=0.545, var($\lambda$)=0.048.
@@
       \begin{table}[h]
-        \caption{95\% credible intervals for the interaction probability of two species that co-occur in $N$ sites but are never observed to interact, obtained using prior information from the \emph{Salix}-galler network in~\citet{Balbour2016}.}
+        \caption{95\% credible intervals for the interaction probability of two species that co-occur in $N$ sites but are never observed to interact, obtained using prior information from the \emph{Salix}-galler network in~\citet{Barbour2016,Barbour2016Dryad}.}
         \label{interval_table}
@@
     \bibliographystyle{ecollett} 
-    \bibliography{manual_abbrev} % Abbreviate journal titles.
+    \bibliography{MyCollection} % Abbreviate journal titles.
 

### 2017-09-22 manuscript/CI_interactions.tex
light formatting and language edits to Why do some interactions not occur section

@@
 
-\section*{Why some interactions do not occur ?}
+\section*{Why do some interactions not occur?}
 
-What this is mean exactly ? We consider there are three nested level of uncertainty making this phenomenon a stochastic process :
+What does this question mean exactly? We consider that there are three nested levels of uncertainty making the occurance of any interaction a stochastic process:
 
-\textit{Interaction uncertainty} First, and most fundamentally, we do not know if these species have the appropriate characteristics to interact or not.
+  \subsection*{Interaction uncertainty}
+
+  First, and most fundamentally, we do not know whether or not a pair of species have the appropriate characteristics to interact.
 We define the probability of an interaction $L$ as $P(L)=\lambda$.
-Obviously, because $k=0$, it is very likely they can not interact if provided enough time and there were no environmental constraint for this interaction to happen.
-But it is nonetheless possible the interaction is a rare phenomenon that has never been documented before.
-This source of uncertainty is the one documented by trait-matching models.
-It arises because every model is imperfect and lack information (i.e.
+Obviously, because $k=0$, it is very likely that they cannot interact even if there were no time or environmental constraints preventing the interaction.
+But it is nonetheless possible that the interaction is a rare phenomenon that has never been documented before.
+This source of uncertainty is the one documented by trait-matching models~\citep{}.
+It arises because every model is imperfect and lacks information (i.e.
 traits) about the constraints on the interaction.
@@
 
-\textit{Process uncertainty} It could happen that the interaction is feasible, i.e.
-$L=1$, but that it does not occur at a given location or at a moment in time because there are local constraints preventing it to occur.
-We define the realization of the interaction process $X$ given an interaction is feasible as a stochastic process with associated probability $P(X|L)=\chi$.
-This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology about the contingencies of interactions.
-We imagine for instance that an interaction between a gall and a parasitoid is not recorded at a location because it was the wrong time of the year and the gall has not yet formed (phenological constraints), because a late frost killed the larvae (an abiotic environmental constraint) , another parasitoid species competitively excluded the parasitoid species of interst (a biotic environmental constraint) or simply the parasitoid is too rare (an abundance constraint).
+  \subsection*{Process uncertainty}
 
-\textit{Detection uncertainty} Lastly, measurement errors are always source of uncertainty in the observation of ecological processes.
+  It could be that the interaction is feasible, i.e.
+$L=1$, but that it does not occur at a given location or moment in time because there are local constraints preventing it from occurring.
+We define the realization of the interaction process $X$ given that the interaction is feasible as a stochastic process with associated probability $P(X|L)=\chi$.
+This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology about the contingencies of interactions~\citep{}.
+We imagine for instance that an interaction between a gall and a parasitoid might not be recorded at a location because it was the wrong time of the year and the gall had not yet formed (phenological constraints), a late frost killed the larvae (an abiotic environmental constraint), another parasitoid species competitively excluded the parasitoid species of interst (a biotic environmental constraint) or simply the parasitoid is too rare to interact with all of its viable hosts (an abundance constraint).
+
+  \subsection*{Detection uncertainty}
+
+  Lastly, measurement errors are always source of uncertainty in the observation of ecological processes.
 We define the detection of an interaction $D$, given an interaction is feasible and occurs in the local conditions, as a stochastic process with associated probability $P(D|X,L)=\delta$.
 Detection failure could happen for several reasons, for instance if the rearing of a parasitoid fails with inappropriate lab conditions or because of species mis-identification.
-Some source of detection error could be minimized with appropriate sampling effort ($\chi$ will converge to one with increasing number of collected galls), but other sources are often difficult to reduce (e.g.
+Some sources of detection error could be minimized with appropriate sampling effort ($\delta$ will converge to one with increasing number of collected galls), but other sources are often difficult to reduce (e.g.
 the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification).
 
-\textit{What is an observation of "no interaction" ?} The combination of these three sources of uncertainty together leads to many potential explanations for the observation of an absence of interaction, but only the situation where $L = 0$ is a true absence therefore is relevant for the investigation of networks.
+  \subsection*{What is an observation of "no interaction"?}
+
+  The combination of these three sources of uncertainty together leads to many potential explanations for the observation of an absence of interaction, but only the situation where $L = 0$ (a true absence) is relevant for the investigation of networks.
 While the observation of an interaction is straightforward to interpret, absence of interactions must be decomposed in different quantities.
 It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e.
-the interaction occurred at the location but was not observed, and $D=1 \cup X = 0 \cup L =1$, the interaction would have been detected but did not occur.
+the interaction occurred at the location but was not observed, and $D=1 \cup X = 0 \cup L =1$, the interaction is feasible and would have been detected but did not occur at the local site.
 
-It is important to keep in mind that for network analysis, ecologists seek to measure the occurrence of true absences, which is the joint event $L=1\cup X=1 \cup D=1$), but in reality they measure the marginal probability $P(L) = k/n$.
+It is important to keep in mind that for network analysis, ecologists seek to measure the occurrence of true absences, which is the joint event $L=0 \cup X=1 \cup D=1$), but in reality they measure the marginal probability $P(L) = k/n$.
+% I'm pretty sure this should be L=0 but X=1 and D=1: interaction not feasible but site and detection perfect.
 

### 2017-09-26 code/figure_generation/upper_CI_after_DG.py
reproduced Dom's binomial figure in Pygrace for consistent visual style

@@ -1,0 +1,85 @@
+# Data generated by manuscript/figure_binomial.R
+
+import sys
+import math
+import random
+from decimal import *
+import numpy as np
+
+#Pygrace libraries
+from PyGrace.grace import Grace
+from PyGrace.colors import RandomColorScheme, MarkovChainColorScheme, ColorBrewerScheme
+from PyGrace.dataset import SYMBOLS
+from PyGrace.Extensions.panel import NetworkPanel,Panel,MultiPanelGrace
+from PyGrace.drawing_objects import DrawText, DrawLine, DrawBox
+from PyGrace.axis import LINEAR_SCALE, LOGARITHMIC_SCALE
+from PyGrace.Extensions.network import Network
+
+from PyGrace.Extensions.distribution import CDFGraph, PDFGraph
+from PyGrace.Extensions.latex_string import LatexString, CONVERT
+from PyGrace.Extensions.colorbar import SolidRectangle, ColorBar
+from PyGrace.Styles.el import ElGraph, ElLinColorBar, ElLogColorBar
+
+colors=ColorBrewerScheme('Spectral')  # The blue is very beautiful but maybe harder to see.
+# colors.add_color(120,120,120,'grey')
+
+def read_Rfiles(filename):
+  dataset=[]
+
+  f=open(filename,'r')
+  for line in f:
+    if line.split()[0]!='"method"':
+      n=int(line.split()[3])
+      upper=float(line.split()[-1])
+      dataset.append((n,upper))
+  f.close()
+
+  return dataset
+
+def format_graph(graph):
+  graph.yaxis.bar.linewidth=1
+  graph.xaxis.bar.linewidth=1
+  graph.frame.linewidth=1
+  graph.world.xmin=0
+  graph.world.xmax=32
+  graph.world.ymin=-0
+  graph.world.ymax=1
+
+  graph.yaxis.tick.configure(major=.20,onoff='on',minor_ticks=1,major_size=.5,minor_size=.3,place='normal',major_linewidth=1,minor_linewidth=1)
+  graph.yaxis.ticklabel.configure(char_size=.75,format='decimal',prec=1)
+
+  graph.xaxis.tick.configure(major=10,onoff='on',minor_ticks=1,major_size=.5,place='normal',minor_size=.3,major_linewidth=1,minor_linewidth=1)
+  graph.xaxis.ticklabel.configure(char_size=.75,format='decimal',prec=0)
+
[…]

### 2017-09-26 manuscript/Ideas_and_perspectives_proposal.tex
First draft of I&P proposal plus supplemental files to compile it

\documentclass[12pt]{letter}

% \usepackage[britdate]{canterbury-letter}
\usepackage[britdate]{LiU-letter}
\usepackage{times}
\usepackage{letterbib}
\usepackage{geometry}
\usepackage[round]{natbib}
\usepackage{graphicx}
\geometry{a4paper}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage[running]{lineno}
\usepackage{amsmath,amsfonts,amssymb}
% \usepackage[margin=10pt,font=small,labelfont=bf]{caption}

%\usepackage{natbib}
% \bibpunct[; ]{(}{)}{;}{a}{,}{;}

\newenvironment{refquote}{\bigskip \begin{it}}{\end{it}\smallskip}

\newenvironment{figure}{}

\position{Postdoctoral fellow}
\department{Department of Physics, Chemistry, and Biology (IFM)}
\location{581 83 Link\"{o}ping, Sweden}
\cityzip{581 83 Link\"{o}ping, Sweden}
\telephone{}
\fax{}
\email{alyssa.cirtwill@liu.se}
\url{http://cirtwill.github.io}
\name{Alyssa R. Cirtwill}

\newcommand{\myjournal}{\emph{Ecology Letters}}

\begin{document}

\begin{letter}{\bf Professor Tim Coulson\\
               Editor-in-Chief, Ecology Letters\\
               Department of Zoology\\
               University of Oxford\\
               Oxford OX1 3PS, UK
                               }

\opening{Dear Prof. Coulson:}

    My co-authors and I cordially invite you to consider the 
    following proposal for an Ideas \& Perspectives article in 
    \myjournal:

Researchers working with ecological networks widely acknowledge that empirical data come with major caveats: the set of observed interactions included in such networks depends on the local conditions and sampling methodology used as well as on the set of interactions that actually occur. An interaction may not be observed because 1) it does not occur, 2) species which could interact are too rare to encounter each other, inclement weather or other conditions prevented the interaction, etc., or 3) detection of interactions was not perfect. From the perspective of an interaction matrix, these sources of non-interaction are indistinguishable. We propose a Bayesian framework with which to quantify the uncertainty around both particular interactions and network-level metrics. We will illustrate this framework using an extraordinarily large and well-replicated set of plant-galler-parasitoid networks. By quantifying the uncertainty around interactions, network ecologists can more rigorously compare networks, identify patterns which should be more robust to variation in sampling, develop better models and predictions, etc.

The authors involved in this study bring varied perspectives to this discussion. Tomas Roslin has extensive expertise in gathering network data and has first-hand experience with each source of variation we describe. Dominique Gravel and Anna Ekl\"{o}f both offer a more theoretical perspective and have extensive experience with probabilistic approaches to network analyses. The two more junior authors, Kate Wootton and Alyssa Cirtwill, are involved with a variety of network analyses using both empirical and simulated networks and have a strong interest in developing more robust methods for network analyses.

We are confident that the applicability of this method to all types of ecological networks and the importance of addressing sources of uncertainty in the data will mean that this article is of interest to a broad readership. We hope that you agree and eagerly await your reply.

\closing{Best regards,}

\end{letter}
\end{document}

### 2017-09-26 manuscript/CI_interactions.tex
more small editsg

@@
 
-The basic information that we are collecting consists of interaction matrices of interaction partners.
-If our counts of whether species A is interacting with species B reflects both uncertainty with respect to whether two species interact when co-occurring at a given site, chance variation in whether the interaction is realized, and uncertainty with respect to whether it is detected when realized, then what can we do to pin down any of these different parts?
+The basic information that we are collecting consists of matrices of interaction partners.
+Our count of interactions between species A and species B reflects uncertainty with respect to whether two species interact when co-occurring at a given site, chance variation in whether the interaction is realized, and uncertainty with respect to whether it is detected when realized.
+In this case, what can we do to pin down any of these different types of variation?
 
-A simple consideration will illustrate the problem: assuming that we want to infer the probability of an interaction between two species, A and B.
-Now assume that in reality, interaction between A and B is plain impossible (i.e.
+A simple example will illustrate the problem: assume that we want to infer the probability of an interaction between two species, A and B.
+Now assume that in reality, interaction between A and B is completely impossible (i.e.
 the true (P(L|co-occurrence of A and B = 0).
@@
 
-The pattern of Fig.
-X (binomial CL fig from Dom) should be compared to the frequency of co-occurrence of taxa in the Salix-galler data set.
+\begin{figure}
+  \caption{This figure illustrates the upper bound (solid black line) of a 95\% confidence interval for the interaction probability $\lamba$ when there is no observation of an interaction ($k = 0$) and $n$ observations of the two species co-occurring at a given location.
+The confidence interval is based on the Clopper-Pearson derivation from the beta distribution.
+A threshold interaction probability of 0.1 is indicated by the dotted red line.}
+  \label{upper_limits}
+  \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
+\end{figure}
+
+The pattern of Fig.~\ref{upper_limits} should be compared to the frequency of co-occurrence of taxa in the Salix-galler data set.
 Here, most(TO COMPUTE) pairs of species are never found co-occurring, and for species found co-occurring the number of co-occurrences was generally low (Fig from AC and KW).

### 2017-09-26 code/figure_generation/observation_interaction_histogram.py
code to make the histogram figure

@@ -1,0 +1,121 @@
+# # ######### R code to generate data files:
+# galldata=read.csv('../../data/Salix_example/cooccur_interact_galler_salix.csv',header=TRUE,rownames=TRUE)
+# n_pairs=nrow(galldata)
+# unobserved=length(which(galldata$cooccur==0))
+# observed=galldata[which(galldata$cooccur>0),]
+# observed$int_freq=observed$interact/observed$cooccur
+# obs_ints=length(which(observed$interact>0))
+
+# observation_histdata=as.data.frame(tapply(observed$cooccur,observed$cooccur,length))
+# interaction_histdata=as.data.frame(tapply(observed$interact,observed$interact,length))
+# colnames(observation_histdata)=c("cooccurances")
+# colnames(interaction_histdata)=c("interactions")
+
+# write.table(observation_histdata,file='../../data/Salix_example/Salix_Galler/nonzero_cooccurances.tsv',sep='\t')
+# write.table(interaction_histdata,file='../../data/Salix_example/Salix_Galler/observed_interactions.tsv',sep='\t')
+
+
+
+import sys
+import math
+import random
+from decimal import *
+import numpy as np
+
+#Pygrace libraries
+from PyGrace.grace import Grace
+from PyGrace.colors import RandomColorScheme, MarkovChainColorScheme, ColorBrewerScheme
+from PyGrace.dataset import SYMBOLS
+from PyGrace.Extensions.panel import NetworkPanel,Panel,MultiPanelGrace
+from PyGrace.drawing_objects import DrawText, DrawLine, DrawBox
+from PyGrace.axis import LINEAR_SCALE, LOGARITHMIC_SCALE
+from PyGrace.Extensions.network import Network
+
+from PyGrace.Extensions.distribution import CDFGraph, PDFGraph
+from PyGrace.Extensions.latex_string import LatexString, CONVERT
+from PyGrace.Extensions.colorbar import SolidRectangle, ColorBar
+from PyGrace.Styles.el import ElGraph, ElLinColorBar, ElLogColorBar
+
+colors=ColorBrewerScheme('Spectral')  # The blue is very beautiful but maybe harder to see.
+# colors.add_color(120,120,120,'grey')
+
+def read_Rfiles(filename):
+  pointlist=[]
+
+  f=open(filename,'r')
+  for line in f:
[…]

### 2017-09-26 code/figure_generation/samples_for_thresholds.py

@@ -73,7 +73,7 @@ def read_Rfiles(filename):
       datadict[threshold]=ys
   f.close()
 
-  g=open('../../data/Salix_example/Salix_Galler/samples_for_threshold.tsv')
+  g=open('../../data/Salix_example/Salix_Galler/samples_for_threshold.tsv','r')
   for line in g:
     if line.split()[0]!='"Threshold"':
       threshold=float(line.split()[1])

### 2017-09-26 manuscript/figure_binomial.R

@@ -4,7 +4,7 @@ CI <- binom.confint(0, n, method = "exact")
 dev.new(width = 10, height = 8)
 plot(n,CI[,6], xlab = "Number of samples", ylab = "Upper 95% confidence interval", type = "l",cex.axis = 1.5,cex.lab = 1.5,lwd = 2,ylim = c(0,1))
 abline(h = 0.1, lty=3)
-
+write.table(CI,file='../data/R/CI_and_samples.tsv',sep='\t')
 # CAPTION
 # This figure illustrates the upper confidence interval for the interaction probability $\lamba$ when there is no observation of an interaction ($k = 0$) and $n$ observations of the two species co-occurring at a given location. The confidence interval is based on the Clopper-Pearson derivation from the beta distribution. 
 

### 2017-09-27 manuscript/CI_interactions.tex
moving on to the Bayesian approach section

@@
 Now assume that in reality, interaction between A and B is completely impossible (i.e.
-the true (P(L|co-occurrence of A and B = 0).
+the true $\lambda$= 0).
 Given no added detection error in observing the incidence of the interaction, then a single observation of species co-occurrence will reveal (very) little regarding the probability of the interaction – the confidence limits for one observation essentially spans from 0 to 1 (see following section).
@@
   The pattern of Fig.~\ref{upper_limits} should be compared to the frequency of co-occurrence of taxa in the Salix-galler data set.
-Here, most(TO COMPUTE) pairs of species are never found co-occurring, and for species found co-occurring the number of co-occurrences was generally low (Fig from AC and KW).
-Among the species which did sometimes interact when co-occurring, the incidence of interaction was actually low(TO COMPUTE) (freq histogram Fig from AC and KW).
+Here, most (3986 out of 4992) pairs of species are never found co-occurring, and for species found co-occurring the number of co-occurrences was generally low (Fig.~\ref{histograms}A).
+Among the species which did sometimes interact when co-occurring, the incidence of interaction was actually low.
+Only 141 pairs of species were observed interacting: of these, 26 were observed interacting only once and 48.2\% were observed interacting five or fewer times (Fig.~\ref{histograms}B).
 Thus, even in the most extensive data set that we could think of, limited sampling is clearly a major source of uncertainty.
 
-The obvious rule of thumb derived from the above example will be “sample more”, but we note that there are limits to the utility of this motto.
+  \begin{figure}
+    \caption{\textbf{A)} Most pairs of \emph{Salix} and galler species were never observed co-occurring despite the high levels of replication in our example dataset.
+For those that were observed together at least once, the number of observed co-occurances was generally small (\textless10).
+Here we show a histogram of the number of pairs of species observed co-occurring at least once.
+3986 pairs of species were never observed co-occurring: this is represented by the upwards triangle at 0.
+\textbf{B)} Most pairs of species that were observed at the same site were never observed interacting.
+Here we show a histogram of the number of observed interactions within pairs of co-occurring species.}
+    \label{histograms}
+    \includegraphics*[width=.8\textwidth]{figures/Salix_Galler_histogram.eps}
+    \end{figure}
+
+  The obvious rule of thumb derived from the above example is “sample more”, but we note that there are limits to the utility of this motto.
 Sampling more will clearly reduce uncertainty regarding the upper bound of the probability of interaction, and it will also increase the probability of detecting unlikely interactions (i.e.
 interactions occurring with a low probability).
-Yet, since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences quicker than we will accumulate observations of interactions.
-Thus, the more we sample, the more holes will appear in our interaction matrix, which may seem like a counter-intuitive outcome.
+Yet, since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions.
+Thus, the more we sample, the more zeros will appear in our interaction matrix, which may seem like a counter-intuitive outcome.
 
-As a solution towards deciding whether unobserved interactions were undetected due to sampling, or whether they truly do not occur, Weinstein et al.
-(2017) used daily repeated sampling rounds to estimate the daily probability of detecting a hummingbird interaction, and to thereby model the observation and process mechanisms (Weinstein, B.
-G., \& Graham, C.
-H.
-(2017).
-On comparing traits and abundance for predicting species interactions with imperfect detection.
-Food Webs 11; 17-25: https://doi.org/10.1016/j.fooweb.2017.05.002).
-While conceptually attractive, this approach is unsuitable for interactions occurring over longer time scales (like associations between hosts and parasitoids with a single generation per year), or very rare interactions (since no matter how frequently and extensively we sample, there will still be some rare interactions lurking around).
-What is worse, the problem persists that if a given interaction is not observed on a given day, then it may still be either because it was impossible that day ((P(L|co-occurrence of A and B)=0), because interaction between the two did occur but was not observed, or from any combination of the two.
-Thus, from a conceptual perspective, this approach will fail to satisfactorily separating between all sources of uncertainty.
-An interaction not observed on day t may have gone unobserved either because there were constraints on the process (i.e.
-the probability was really zero), because of chance variation in the realized incidence of an event associated with a finite probability.
-Most importantly, if during a series of days, two species are simply never observed co-occurring, then we still have not learnt a thing about their probability of interacting should they do so.
-In other words, if the two interaction partners do not co-occur, we will still gain no information.
+  As a solution towards deciding whether unobserved interactions were undetected due to sampling, or whether they truly do not occur,~\citet{Weinstein2017} used daily repeated sampling rounds to estimate the daily probability of detecting a hummingbird interaction, and to thereby model the observation and process mechanisms~\citep{Weinstein2017}.
+While conceptually attractive, this approach is unsuitable for interactions occurring over longer time scales (e.g., associations between hosts and parasitoids with a single generation per year), or very rare interactions (since no matter how frequently and extensively we sample, there will still be some interactions lurking around).
+What is worse, the problem persists that if a given interaction is not observed on a given day, this could be either because it was impossible that day despite being otherwise feasible (P($X|L=1$=0), because interaction between the two did occur but could not be observed (P($D|X$=1,L=1)=0), or from any combination of the two.
+From a conceptual perspective, this approach will thus fail to satisfactorily distinguish between sources of uncertainty.
+An interaction not observed on day $t$ may have gone undetected either because there were constraints on the process (i.e.
+the probability $\lambda$ was really zero) or because of chance variation in the realized incidence of an event associated with a finite probability.
+Most importantly, if two species are never observed co-occurring during several days of sampling then we have learned nothing about their probability of interacting if they should ever co-occur.
+In other words, there is no information without co-occurance.
 
-An added complication is that not all sourced of uncertainty are proportional to sample size.
-To score an interaction between A and B, we will need to identify both partners correctly (a non-trivial problem in many food webs; e.g.
-Kaartinen et al.
-2011 Ecol Entomol; Roslin and Majaneva 2016) and be able to resolve all interactions with a similar likelihood.
-For both molecular (ref ref) and rearing techniques, given types of interactions may go unnoticed due to technical challenges.
+  An added complication is that not all sources of uncertainty are proportional to sample size.
+To record an interaction between A and B, we need to identify both partners correctly (a non-trivial problem in many food webs; e.g.~\citet{Kaartinen2011,Roslin2016}) and be able to resolve all interactions with a similar likelihood.
+For both molecular~\citep{} and rearing~\citep{} techniques, certain types of interactions may go unnoticed due to technical challenges.
+This can bias the set of recorded interactions.
 
-The bottom line is that separating between different sources of uncertainty is difficult indeed.
-In the best of all possible worlds, we might then use an experimental approach to estimate detection uncertainty: we might create replicate sets of cases where the interaction is really there, then evaluating them and examining the fraction of cases scoring positive.
-Yet, as anyone attempting these experiments will know, most interaction partners are proving notoriously unwilling to collaborate.
-Gallers refuse to lay eggs on their host plants (ref ref), parasitoids to attack their hosts when experimentally introduced (Gariepy 2017; ref ref).
-If we introduce only one of the components (like in the cases where we expose a set of hosts to parasitism; ref ref; Gripenberg et al.
-xxx) then we are already confounding multiple levels of uncertainty in the outcome – that of interaction uncertainty (whether the species will interact once both there), process uncertainty (whether the interaction will occur if and since the probability of interaction is below one), and detection uncertainty (i.e.
-whether we will observed the interaction once realized).
-To perform these experiments in a comprehensive and reliable manner, we will then need to expose a large number of interactions in a comprehensive experiment across space.
-This type of “cafeteria experiments in space” is not only unfeasible, but also undermining our original objective: If the local occurrence of interactions is uninformative regarding the underlying probabilities of occurrence, then we should be doing something else than wasting a monumental effort on collecting local interaction matrices.
+  The bottom line is that separating different sources of uncertainty is difficult indeed.
+In the best of all possible worlds, we might use an experimental approach to estimate detection uncertainty by creating replicate cases where the interaction really occurs and then evaluating the fraction of cases where the interaction is detected.
+Yet, as anyone attempting these experiments will know, most interaction partners are notoriously unwilling to collaborate.
+Gallers refuse to lay eggs on their host plants in captivity (ref ref) and parasitoids decline to attack their hosts when experimentally introduced (Gariepy 2017; ref ref).
+If we introduce only one of the components (as in the cases where we expose a set of hosts to parasitism; ref ref; Gripenberg et al.
+xxx) then we are already confounding multiple levels of uncertainty since it is not certain whether the interaction will occur or whether we can detect it.
+To perform these experiments in a comprehensive and reliable manner, we will then need to replicate a large number of interactions in a comprehensive experiment across space.
+This type of “cafeteria experiments in space” is not only unfeasible, but also undermines our original objective: If the local occurrence of interactions is uninformative regarding the underlying probabilities of occurrence, then is not likely to be worthwhile collecting these local interaction matrices in the first place.
 <deep sigh and forget that section?
@@
 
-As a tentative solution to disentangling observation and process mechanisms, we propose that some insights regarding the detectability of interactions between species not found co-occurring may be gained from data on other species, for which it is known that the interaction is feasible.
+  As an alternative to abandoning empirical networks or continuing to ignore the uncertainty inherent in undetected observations, we propose that some insight regarding the detectability of interactions between species not found co-occurring may be gained from data on other species between which interactions are known to be feasible.
 If we use this information obtain the joint probability of detection and process (e.g.

### 2017-09-28 manuscript/CI_interactions.tex
updated quantitative example to be interaction probabilities instead of degrees

@@
 
- In some cases it can be complicated to compute the normalizer, but fortunately in our case it exists an analytical solution.
+     In some cases it can be complicated to compute the normalizer, but fortunately in our case an analytical solution exists.
 The beta-binomial distribution is a conjugate distribution of the binomial distribution.
@@
 The weight of the prior on the posterior distribution is understood from these definition of the parameters: the difference between the posterior and the prior will increase with $k$ and $n-k$.
-When plotted, we find the shape of the distribution gets narrower with $k$ and $n$ (see Fig X).
+When plotted, we find the shape of the distribution gets narrower with $k$ and $n$ (Fig.~\ref{Salix_pdfs}).
       %
@@
       %  \vspace{12pt}
+
+      \begin{figure}[ht]
+        \label{Salix_pdfs}
+        \caption{Using a prior distribution based on the \emph{Salix}-galler network in~\citet{Barbour2016}, we can calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting.
+Here we show posterior distributions for $\lambda$ ranging from the prior distribution (N=0 observed co-occurances) to the distribution obtained when the pair of species has been observed co-occurring 50 times.
+The distribution narrows and approaches zero as the sample size increases, but never includes zero.}
+        \includegraphics*[width=.8\textwidth]{figures/Salix_Galler_pdfs_increasing_N.eps}
+        \end{figure}
 
@@
     \subsection*{The prior distribution}
+
       Parameters $\alpha$ and $\beta$ determine the shape of the prior distribution, which follows a beta distribution.
@@
 
-      In absence of any external information, an uniformative prior is the most conservative 
-      hypothesis for the distribution of $\theta$. The beta distribution is in this case 
-      a uniform distribution  for $Beta(\alpha=1,\beta=1)$.
+          In absence of any external information, an uniformative prior is the most conservative hypothesis for the distribution of $\theta$.
+The beta distribution is in this case a uniform distribution  for $Beta(\alpha=1,\beta=1)$.
 
@@
 
-      In the literature of ecological networks there is a solid collection of data for which know network connectance, and we can thereby define the connectance distribution.
+          In the literature of ecological networks there is a solid collection of data for which know network connectance and from which we can define the connectance distribution.
 Connectance is measured as $C = L/S^2$, where $L$ is the number of interactions and $S$ is the number of species.
@@
 
-  \subsubsection*{Degree distribution for the species in the network}.
-%
+      \subsubsection*{Degree distribution for the species in the network - or - Interaction probabilities in a similar network}.
+
+          [[Should we still have this?
+At the workshop we talked about how interaction probabilities depend on the degrees of both species and so I'm using predicted interaction probabilities (degreeA*degreeB) in the galler example.
+A writeup for that process follows the original text:]]
           The degree of a node in a network is defined as the number of interactions it has to other nodes.
 The degree distribution of a network is then the probability distribution of these degrees over the whole network.
-Connectance is an average property for a complete given network, and it represents the expected
-degree (expected number of interactions per species) standardized by the number of species in the network.
+Connectance is an average property for a complete given network, and it represents the expected degree (expected number of interactions per species) standardized by the number of species in the network.
 The standardized degree could therefore be interpreted as an interaction probability.
-It is consequently possible to
-use the degree distribution to inform the prior distribution. The degree distribution could
-come from several networks, from a similar network (e.g.
+It is consequently possible to use the degree distribution to inform the prior distribution.
+The degree distribution could come from several networks, from a similar network (e.g.
 a known network at slightly different location) or from the network of interest if interaction probabilities for some species are already documented.
-The latter approach allows us to apply information from known, abundant species to the rarest species for which interactions are less
-frequently documented. The procedure for the estimation of the hyper parameters follows
-the same approach as described above for connectance except that each
-measurement is at the individual species level instead of the network level.
+The latter approach allows us to apply information from known, abundant species to the rarest species for which interactions are less frequently documented.
+The procedure for the estimation of the hyper parameters follows the same approach as described above for connectance except that each measurement is at the individual species level instead of the network level.
+
+          If our focal network describes a similar system to that in a known network, we can use the distribution of interaction probabilities in that network to inform our prior.
+The probability of any interaction $L_ij$ depends on the degrees of species $i$ and $j$.
+The degree of a node is defined as the number of interactions it has with other nodes.
+Connectance, as the average number of links per species in the whole network, is thus also the expected degree for any given species normalized by the number of species in the network.
+Using normalized degrees $\Delta_i$ and $\Delta_j$ (i.e., degrees divided by the number of species in the network), we can obtain the probability of interaction $L_ij$=$\Delta_i$\times$\Delta_j$.
+The distribution of these interaction probabilities derived from a similar network or a suite of networks can be used to establish a prior distribution before any data from the focal network are collected.
+We could also use this approach to build a prior distribution using known interaction probabilities for some species in the focal network.
+The latter approach allows us to apply information from known, abundant species to the rarest species for which interactions are less frequently documented.
+The procedure for the estimation of the hyper parameters follows the same approach as described above for connectance except that each measurement is at the individual interaction level instead of the network level.
 
       \subsubsection*{Trait-matching function}.
-  It is possible to estimate the probability of interaction between a pair of species if there is knowledge of their traits and some functions relating trait matching to interaction probability (Morales-Castilla2015).
-There are several techniques available to perform this inferrence of interaction probability (REFS).
+
+          It is possible to estimate the probability of interaction between a pair of species if there is knowledge of their traits and some functions relating trait matching to interaction probability~\citep{Morales-Castilla2015}.
+There are several techniques available to perform this inferrence of interaction probability~\citep{} (REFS).
 Note that in this case the prior might not be beta distribution and numerical methods might be required to compute the posterior distribution.
@@
 \section*{A quantitative example}
+
   %Perhaps we want to also have a trait matching example in addition to the degree distribution example below?
@@
 maybe we should rephrase this to predict the degree of species $i$ based on the degrees of 10 other species in the network?
-The framework can be illustrated with a simple quantiative example.
+  The Bayesian framework can be illustrated with a simple quantiative example.
 Suppose we have $n = 10$ observations of co-occurrence between species $i$ and species $j$ in a given time interval and area, and $X = 3$ observations of interactions.
@@
   % We should probabaly have a value  on the interaction probablitity that differs from the average of the degree distrbution
- Now consider we know that species $i$ is known to interact with 10 other species, which have the following standardized degrees:
+   Now consider we know that species $i$ is known to interact with 10 other species, which have the following normalized degrees:
 
@@
     \noindent\emph{
-   degree = c(0.66, 0.09, 0.06, 0.08, 0.04, 0.16, 0.06, 0.38, 0.03, 0.02)
+       degree = c(0.66, 0.18, 0.12, 0.16, 0.84, 0.32, 0.12, 0.76, 0.06, 0.04)
         }.
@@
 
-The mean of these standardized degrees is 0.158, approximately half the $\theta_{MLE}$ obtained from the observed data. We can use these standardized degrees to inform our prior expectation of the 
-distribution of interaction probabilities. With some simple R code (function calculate\_parameters, \emph{Appendix S2}), we obtain prior parameters $\alpha$=0.7559544
-and $\beta$=3.6710277. Using these priors in equations~\ref{mean} 
-and~\ref{variance} above (or in the R function calculate\_distribution in \emph{Appendix S2}), we find a prior mean interaction probability of 0.1707607 and a prior variance of 0.0319860.
+    If the network has 20 species total, then species $i$ has a normalized degree of 0.5 and
+    we can use this to obtain the following set of interaction probabilities for species $i$ and each of its interaction partners:
+
+    \vspace{12pt}
+    \noindent\emph{
+       int_probs = c(0.33, 0.09, 0.06, 0.08, 0.42, 0.16, 0.06, 0.38, 0.03, 0.02)
+        }.
+      \vspace{12pt}
+
+    The mean of these interaction probabilities is 0.163, approximately half the $\theta_{MLE}$ obtained from the observed data.
+We can use the distribution of these interaction probabilities as our prior distribution and estimate the uncertainty surrounding our $\theta_{MLE}$.
+With some simple R code (function calculate\_parameters, \emph{Appendix S2}), we obtain prior parameters $\alpha$=1.050830
+    and $\beta$=5.365892. Using these priors in equations~\ref{mean} 
+    and~\ref{variance} above (or in the R function calculate\_distribution in \emph{Appendix S2}), we find a prior mean interaction probability of 0.16376436 and a prior variance of 0.02134199.
 
     Adding the observed data (n=10, k=3) and using the same code,
-we obtain posterior hyper parameters $\alpha'$=3.755954 and $\beta'$=10.671028 and a posterior mean 0.2603423 and variance 0.0133475 for the probability of.
+    we obtain posterior hyper parameters $\alpha'$=4.05083 and $\beta'$=12.36589 and a posterior mean 0.247 and variance 0.011 for the probability of.
 Comparing the posterior distribution to the prior, we see that the posterior is closer to the observed data and that the additional data has reduced the variance.
@@
     We may also wish to calculate a credible interval (analogous to the frequentist confidence interval).
-This is also quite straightforward (see function credible\_interval in \emph{Appendix S2}).
-In this case, a 95\% credible interval for the mean of theta is (0.07755119, 0.50557509).
+This is also quite straightforward in R (see function credible\_interval in \emph{Appendix S2}).
+In this case, a 95\% credible interval for the mean of theta is (0.077, 0.474).
 
@@
 We call this threshold probability $\theta*$.
-We then use the cumulative distribution function to estimate $P(\theta<\theta*|X=0,n)$.
+We then use the cumulative distribution function to estimate $P(\theta<\theta*|X=0,n)$ for different $n$.
 The
@@
 
-The exercise exemplified above yields a surprising result: it requires \textgreater21 observations of no interactions to be 95\% sure that the interaction probability is smaller than 0.1.
+    The exercise exemplified above yields a surprising result: it requires \textgreater24 observations of no interactions to be 95\% sure that the interaction probability is smaller than 0.1.
 Note the special case where there is no observation of the two species co-occurring and failing to interact, $n = 0$.
@@
 
-      \begin{figure}[ht]
-        \label{Salix_pdfs}
-        \caption{Posterior distributions for the probability of two species observed co-occurring but not interacting narrow and shift towards zero as the number of observed co-occurances increases.
-Here we show a selection of distributions ranging from the prior distribution (with N=0 observed co-occurances) to the distribution when there are 50 observed co-occurances.}
-        \includegraphics*[width=.8\textwidth]{figures/Salix_Galler_pdfs_increasing_N.eps}
-        \end{figure}
-
   \subsection*{Computing the credible interval around a probability estimate}

### 2017-09-28 manuscript/CI_interactions.tex
finished my first read-through, updated list of completed figures

@@
 
-  It is fairly straigthforward to compute most of network metrics when the different $\lambda$ of the adjacency matrix are known, without variance (Poisot et al.
-2015).
-Several of these metrics derive directly from quantitative indices of network structure.
-It is not as easy however to understand how the uncertainty in these estimates do influence network metrics.
-There are multiple non-linearities in the computation of these metrics and that, because of Jensen's inequality (the principle stating that the average of non-linear function of a stochastic variable differs from the function of the average of that variable), any uncertainty could bias the average estimate of the metric and influence its variance as well.
-For instance, among all of the pairs of species for which only few co-occurrences are observed, many of them are truly interacting.
-If we consider all of these as having no links, then correcting for these false absence would inflate the number of links and therefore influence metrics such as connectance, nestedness and degree distribution.
-Computing network properties from probabilistic networks is one thing, but then computing them with uncertainties in these probabilities is another problem, far more challenging.
-Unfortunately, for now we could only rely on computer simulations to get an answer to this problem.
+    It is fairly straigthforward to compute most of network metrics when the different $\lambda$ of the adjacency matrix are known, without variance~\citep{Poisot2016}.
+Several of these metrics derive directly from quantitative indices of network structure which are equivalent to $\lambda$; the remainder, originally defined for binary networks, can be adjusted to account for interaction probabilities between zero and one.
+It is not as easy, however, to understand how the uncertainty in these estimated interaction probabilities influences network metrics.
+Computation of these metrics involves non-linear functions and therefore, because of Jensen's inequality (which states that the average of non-linear function of a stochastic variable differs from the function of the average of that variable), any uncertainty in $\lambda$s could bias both the mean and variance of a network metric.
+For instance, assume that among all pairs of species with few observed co-occurances there are many pairs which truly interact.
+If we begin with no observed links for these pairs, then correcting for these false absences will inflate the number of links and consequently influence metrics such as connectance, nestedness, and degree distribution.
+While we can, as described above, calculate these network metrics using fixed estimates for $\lambda$ no analytical solution currently exists for uncertain $\lambda$.
+Instead we must rely on computer simulations.
 In the following section, we will provide an example with the Salix dataset and show how the uncertainty arising from both absences of co-occurrences and false absences of interactions impact these metrics.
@@
 
+      [[Kate, can you expand this?]]
       \emph{Salix}-galler-parasitoid meta-network, here focusing on the smaller \emph{Salix}-galler network.
@@
 
+      [[Do we want the host-parasitoid site too, or is the plant-galler enough? This is feeling long already.]]
       In a strict Bayesian framework, we wish to use a prior distribution that does not rely on any information from the study at hand.
@@
 We estimated frequencies of  \emph{S.
-hookeriana} genotype-galler and galler-parasitoid interactions [[host-parasitoid still to-do]] based on the normalized degree of each species in each network component (see \emph{Appendix S1} for details and code).
+hookeriana} genotype-galler interactions based on the normalized degree of each species in each network component (see \emph{Appendix S1} for details and code).
 
@@
 The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact.
-If we want to be 95\% confident that the interaction probability for two species in the \emph{Salix}-galler system is below 0.5, 0.1, or 0.01, we would need 6, 54, and 114 observed co-occurrances with no observed interaction (Fig.~\ref{Salix_cdfs}; see function samples\_required in~\emph{Appendix S2}).
+If we want to be 95\% confident that the interaction probability for two species in the \emph{Salix}-galler system is below 0.5, 0.1, or 0.01, we would need six, 54, and 114 observed co-occurrances with no observed interaction (Fig.~\ref{Salix_cdfs}; see function samples\_required in~\emph{Appendix S2}).
 Given the low levels of replication in most network studies, this implies that we should have fairly low confidence in many "non-interacting" pairs of species.
-Even in the \emph{Salix}-galler dataset, [[how many pairs of species co-occur in \textgreater6,54,114 sites?]].
+Even in the extensively replicated \emph{Salix}-galler dataset very few species pairs were observed co-occurring frequently enough to reach these thresholds (173/4992 pairs were observed at least six times, two pairs were observed at least 54 times, and no pair was observed more than 114 times).
 Discounting potential interactions, then, requires either a stronger prior expectation of no interaction (e.g., we can be highly confident that a palm tree will not predate upon a leopard no matter how many times the two species are observed together) or very extensive sampling.
@@
 
+  \subsection*{Scaling up to network metrics}
+
   % [[What if we have only one site?

### 2017-09-28 manuscript/Ideas_and_perspectives_proposal.tex
added comments from Tomas and Kate

@@
 
+% The instructions are for a single, 300-word paragraph proposal. The large paragraph is now at 299 words, and we can maybe hope that they won't count the preamble and nice closing.
+
 \opening{Dear Prof. Coulson:}
@@
 
-Researchers working with ecological networks widely acknowledge that empirical data come with major caveats: the set of observed interactions included in such networks depends on the local conditions and sampling methodology used as well as on the set of interactions that actually occur.
-An interaction may not be observed because 1) it does not occur, 2) species which could interact are too rare to encounter each other, inclement weather or other conditions prevented the interaction, etc., or 3) detection of interactions was not perfect.
-From the perspective of an interaction matrix, these sources of non-interaction are indistinguishable.
-We propose a Bayesian framework with which to quantify the uncertainty around both particular interactions and network-level metrics.
-We will illustrate this framework using an extraordinarily large and well-replicated set of plant-galler-parasitoid networks.
-By quantifying the uncertainty around interactions, network ecologists can more rigorously compare networks, identify patterns which should be more robust to variation in sampling, develop better models and predictions, etc.
-
-The authors involved in this study bring varied perspectives to this discussion.
-Tomas Roslin has extensive expertise in gathering network data and has first-hand experience with each source of variation we describe.
-Dominique Gravel and Anna Ekl\"{o}f both offer a more theoretical perspective and have extensive experience with probabilistic approaches to network analyses.
-The two more junior authors, Kate Wootton and Alyssa Cirtwill, are involved with a variety of network analyses using both empirical and simulated networks and have a strong interest in developing more robust methods for network analyses.
+    Representing communities as networks of interactions (links) between taxa (nodes) is a central approach in modern community ecology.
+With network data becoming increasingly available, empirical comparisons of network structure along different environmental gradients is emerging as one of the hottest fields of community research.
+Yet, researchers working with ecological networks widely acknowledge that empirical data come with major caveats as the probability of observing different interactions depends on sampling effort/methodology and local conditions as well as the intrinsic probability of any interaction.
+These contingencies mean that there are many reasons one might fail to observe an interaction (e.g., it might occur but not be detectable or be feasible but not occur due to weather conditions during sampling).
+Problematically, these sources of non-interaction are often indistinguishable within an interaction matrix.
+As a potential solution, we propose a Bayesian framework which partitions the uncertainty associated with missing interactions into explicit components.
+This framework can be used to quantify the uncertainty around both particular interactions and network-level metrics.
+We will illustrate this framework using an extraordinarily large and well-replicated set of plant-galler-parasitoid networks recently published as a data paper (Kopelke \emph{et al.}, 2017.
+\textbf{Ecology} 98: 1730).
+Quantifying the uncertainty around interactions will allow more rigorously comparisons between networks and the identification of more robust patterns in network structure.
+The authors involved in this study contribute a range of valuable perspectives.
+Dominique Gravel has developed techniques for novel types of interaction distribution modelling.
+Anna Eklöf contributes extensive experience with probabilistic network analyses.
+Tomas Roslin has vast experience with gathering and using network data and has first-hand experience with each source of variation we describe.
+The two junior authors, Kate Wootton and Alyssa Cirtwill, work with both empirical and simulated networks and have a strong interest in developing more robust methods for network analyses.
 

### 2017-09-28 manuscript/Ideas_and_perspectives_proposal.tex
added a couple comments from Dom

@@
     Representing communities as networks of interactions (links) between taxa (nodes) is a central approach in modern community ecology.
-With network data becoming increasingly available, empirical comparisons of network structure along different environmental gradients is emerging as one of the hottest fields of community research.
-Yet, researchers working with ecological networks widely acknowledge that empirical data come with major caveats as the probability of observing different interactions depends on sampling effort/methodology and local conditions as well as the intrinsic probability of any interaction.
-These contingencies mean that there are many reasons one might fail to observe an interaction (e.g., it might occur but not be detectable or be feasible but not occur due to weather conditions during sampling).
+These networks are usually treated as fixed, deterministic entities.
+Yet, researchers working with ecological networks widely acknowledge that empirical data are in fact samples of a community and come with major caveats.
+The probability of observing different interactions depends on sampling effort/methodology and local conditions as well as the intrinsic probability of any interaction.
+These contingencies mean that there are many reasons one might fail to observe an interaction (e.g., it might occur sometimes but not during sampling due to weather).
 Problematically, these sources of non-interaction are often indistinguishable within an interaction matrix.
-As a potential solution, we propose a Bayesian framework which partitions the uncertainty associated with missing interactions into explicit components.
-This framework can be used to quantify the uncertainty around both particular interactions and network-level metrics.
-We will illustrate this framework using an extraordinarily large and well-replicated set of plant-galler-parasitoid networks recently published as a data paper (Kopelke \emph{et al.}, 2017.
+As a potential solution, we propose a Bayesian framework which partitions the uncertainty associated with missing interactions into explicit components and allows us to place confidence intervals around each estimated interaction probability.
+The Bayesian framework also facilitates the use of prior information (e.g., species traits) to reduce uncertainty around some interactions.
+We will illustrate this framework using an extraordinarily  well-replicated set of plant-galler-parasitoid networks recently published as a data paper (Kopelke \emph{et al.}, 2017.
 \textbf{Ecology} 98: 1730).
-Quantifying the uncertainty around interactions will allow more rigorously comparisons between networks and the identification of more robust patterns in network structure.
+Using this dataset, we will demonstrate how uncertainty surrounding each interaction probability affects network-level metrics.
+Acknowledging this uncertainty is crucial for valid comparison of networks along gradients.
 The authors involved in this study contribute a range of valuable perspectives.
 Dominique Gravel has developed techniques for novel types of interaction distribution modelling.
-Anna Eklöf contributes extensive experience with probabilistic network analyses.
+Anna Ekl\"{o}f contributes extensive experience with probabilistic network analyses.
 Tomas Roslin has vast experience with gathering and using network data and has first-hand experience with each source of variation we describe.

### 2017-09-28 manuscript/CI_interactions.tex
learning to use github
formatting error

@@
   \begin{figure}
-    \caption{This figure illustrates the upper bound (solid black line) of a 95\% confidence interval for the interaction probability $\lamba$ when there is no observation of an interaction ($k = 0$) and $n$ observations of the two species co-occurring at a given location.
+    \caption{This figure illustrates the upper bound (solid black line) of a 95\% confidence interval for the interaction probability $\lambda$ when there is no observation of an interaction ($k = 0$) and $n$ observations of the two species co-occurring at a given location.
 The confidence interval is based on the Clopper-Pearson derivation from the beta distribution.
@@
 Connectance, as the average number of links per species in the whole network, is thus also the expected degree for any given species normalized by the number of species in the network.
-Using normalized degrees $\Delta_i$ and $\Delta_j$ (i.e., degrees divided by the number of species in the network), we can obtain the probability of interaction $L_ij$=$\Delta_i$\times$\Delta_j$.
+Using normalized degrees $\Delta_i$ and $\Delta_j$ (i.e., degrees divided by the number of species in the network), we can obtain the probability of interaction $L_ij$=$\Delta_i\times\Delta_j$.
 The distribution of these interaction probabilities derived from a similar network or a suite of networks can be used to establish a prior distribution before any data from the focal network are collected.
@@
     \noindent\emph{
-       int_probs = c(0.33, 0.09, 0.06, 0.08, 0.42, 0.16, 0.06, 0.38, 0.03, 0.02)
-        }.
+       int\_probs = c(0.33, 0.09, 0.06, 0.08, 0.42, 0.16, 0.06, 0.38, 0.03, 0.02) }.
       \vspace{12pt}

### 2017-10-10 manuscript/CI_interactions.tex
saved with UTF-8 encoding to fix a compiling error
added Kate's dotplot of co-occurances vs interactions to the histogram figure, updated caption in text. Some setup to add galler–parasitoid panels later.

@@
 Here we show a histogram of the number of pairs of species observed co-occurring at least once.
-3986 pairs of species were never observed co-occurring: this is represented by the upwards triangle at 0.
+3986 pairs of species were never observed co-occurring: these pairs are omitted from the histogram.
 \textbf{B)} Most pairs of species that were observed at the same site were never observed interacting.
-Here we show a histogram of the number of observed interactions within pairs of co-occurring species.}
+Here we show a histogram of the number of observed interactions within pairs of co-occurring species.
+\textbf{C)} Here we show, for each species pair, the number of observed interactions plotted against the number of observed co-occurances.
+Most pairs either are never observed interacting or interact almost every time they co-occur.
+The red, dashed line indicates a 1:1 relationship between interactions and co-occurances.}
     \label{histograms}

### 2017-10-10 code/calculate_sim_network_properties.py
made a figure to show underrepresentation of C with a detection filter of 0.5-0.99 percent of links

@@ -1,0 +1,77 @@
+import sys
+import os
+import networkx as nx 
+import numpy as np 
+import scipy as sp 
+
+def web_reader(webdir,proportion,post_number,sample_number): 
+  gallers=set()
+  salixes=set()
+  links=set()
+  if sample_number==0:
+    f=open(webdir+'posterior/P'+str(post_number)+'.web','r')
+  else:
+    f=open(webdir+'detection_filter/'+str(proportion)+'/P'+str(post_number)+'_'+str(sample_number)+'.web','r')
+  for line in f:
+    galler=line.split()[0]
+    salix=line.split()[1]
+    gallers.add(galler)
+    salixes.add(salix)
+    links.add((galler,salix))
+  f.close()
+
+  # G=nx.Graph()
+  # for sp in gallers:
+  #   G.add_node(sp)
+  # for sp in salixes:
+  #   G.add_node(sp)
+  # for (galler,salix) in links:
+  #   G.add_edge(galler,salix)
+
+  return gallers,salixes,links
+
+def calculate_original_properties(gallers,salixes,links):
+  # original_properties['L'][post_number]=len(links)
+  # original_properties['S'][post_number]=len(G.nodes())
+  # original_properties['LS'][post_number]=float(len(G.edges()))/float(len(salixes))
+  # original_properties['LG'][post_number]=float(len(G.edges()))/float(len(gallers))
+  C=float(len(links))/float(len(salixes)*len(gallers))
+
+  return C
+
+def write_summary_file(summary_dict):
+  f=open('../data/randomised_webs/Connectance_table.tsv','w')
+  f.write('Web\tProportion\tObs_C\tSample_mean\tSample_SD\n')
+  for proportion in summary_dict:
+    for post_number in summary_dict[proportion]:
+      f.write(str(post_number)+'\t'+str(proportion)+'\t'+'\t'.join(summary_dict[proportion][post_number])+'\n')
+  f.close()
+
+def main():
+
+  webdir='../data/randomised_webs/'
+
+  # Starting with C
+  summary_dict={0.5:{},0.6:{},0.7:{},0.8:{},0.9:{},0.95:{},0.99:{}}
+
+  for post_number in range(1,101):
+    gallers,salixes,links=web_reader(webdir,0,post_number,0)
+    obs=calculate_original_properties(gallers,salixes,links)
+    for proportion in [0.5,0.6,0.7,0.8,0.9,0.95,0.99]:
+    # for proportion in [0.9,0.95,0.99]:
[…]

### 2017-10-10 code/figure_generation/posterior_property_plot.py

@@ -1,0 +1,100 @@
+import sys
+import math
+import random
+from decimal import *
+import numpy as np
+
+#Pygrace libraries
+from PyGrace.grace import Grace
+from PyGrace.colors import RandomColorScheme, MarkovChainColorScheme, ColorBrewerScheme
+from PyGrace.dataset import SYMBOLS
+from PyGrace.Extensions.panel import NetworkPanel,Panel,MultiPanelGrace
+from PyGrace.drawing_objects import DrawText, DrawLine, DrawBox
+from PyGrace.axis import LINEAR_SCALE, LOGARITHMIC_SCALE
+from PyGrace.Extensions.network import Network
+
+from PyGrace.Extensions.distribution import CDFGraph, PDFGraph
+from PyGrace.Extensions.latex_string import LatexString, CONVERT
+from PyGrace.Extensions.colorbar import SolidRectangle, ColorBar
+from PyGrace.Styles.el import ElGraph, ElLinColorBar, ElLogColorBar
+
+colors=ColorBrewerScheme('Blues')  # The blue is very beautiful but maybe harder to see.
+# colors.add_color(120,120,120,'grey')
+
+def read_summary_file(filename):
+  pointdict={}
+  f=open(filename,'r')
+  for line in f:
+    if line.split()[0]!='Web':
+      proportion=float(line.split()[1]) # Proportion of links observed
+      obs_C=float(line.split()[2]) # C in the full posterior web
+      sample_mean=float(line.split()[3]) # Mean C in the detection filter webs
+      sample_SD=float(line.split()[4])
+      sample_SE=sample_SD/10 # SD/sqrt(100 filter webs)
+      # CI is +- 1.96SE
+      if proportion not in pointdict:
+        pointdict[proportion]=[(obs_C,sample_mean,sample_SD)]
+      else:
+        pointdict[proportion].append((obs_C,sample_mean,sample_SD))
+  f.close()
+  return pointdict
+
+def format_graph(graph):
+  graph.yaxis.bar.linewidth=1
+  graph.xaxis.bar.linewidth=1
+  graph.frame.linewidth=1
+
+  graph.world.xmin=0.5
+  graph.world.ymin=0.2
+  graph.world.xmax=0.545
+  graph.world.ymax=0.55
[…]

### 2017-10-10 code/build_galler_parasit_posterior.R
Calculated number of cooccurrences and interactions for salix-galler and galler-parasitoid for Kopelke dataset. Built a parasitoid-galler web from the Balbour 2016 data. Added all code and a readme for the data

@@ -1,0 +1,36 @@
+setwd("C:/Users/kewo0002/confidence_in_interactions/data/Salix_example") 
+
+###############################################################
+#### Build the galler-parasitoid web from Balbour 2016
+#### to be used as the posterior for Kopelke's data
+###############################################################
+
+# read in the data
+prior_web_data=read.csv('tree_level_interaxn_all_plants_traits_size.csv')
+# just keep what we need
+prior_web_data <- prior_web_data[,8:26]
+
+# Build a web with interactions=1 for any parasitoid on any galler
+prior_web=data.frame()
+
+# each column contains all interactions for a particular parasitoid-galler combination
+for(column in 1:ncol(prior_web_data)){
+  # the column name gives the species which makes the gall, followed by the species emerging from the gall
+  # they need to be separated 
+  galler_emerged=strsplit(colnames(prior_web_data)[column], "_")
+  galler = galler_emerged[[1]][1]
+  emerged = galler_emerged[[1]][2]
+  
+  # the strength of the interaction is the sum of the column (number of galls across all branches sampled)
+  linkstrength = sum(prior_web_data[,column])
+  # put that into a dataframe
+  prior_web[as.character(galler),as.character(emerged)] <- linkstrength
+} 
+
+# Make the naS into 0
+prior_web[is.na(prior_web)] <- 0
+
+# some of the emergers were the gallers, remove those columns if we're only
+# interested in galler-parasitoid interactions
+prior_web_para_only <- prior_web[,c(2:6,8:9,12)]
+write.csv(prior_web_para_only, file="prior_web_para_only.csv", quote=F)

### 2017-10-10 code/calculating_n_and_k.R

@@ -1,0 +1,358 @@
+setwd("//storage.slu.se/Home$/kewo0002/My Documents/Projects/Gallers/data.dataframes/")
+
+#######################################################
+#### Create list of all combinations of galler-salix and 
+#### galler-parasitoid and how often they interact and cooccur
+#######################################################
+
+library("plyr")
+library(igraph)
+
+#### FUNCTIONS ####
+
+# Function to calculate the number of times each galler-salix combination
+# cooccurs and interacts
+calc_cooccurence <- function(galler_salix,dataset){
+  # the first variable in the galler_salix dataframe is the salix
+  salix <- galler_salix[1]
+  # the second is the galler
+  galler <- galler_salix[2]
+  
+  # get only those rows where those two species both appear (and therefore interact)
+  inter_subs <- subset(dataset,Rgaller==galler & Salix == salix)
+  
+  # print(inter_subs)
+  
+  # the number of sites they interact with is the number of unique sites in that list
+  interact <- length(unique(inter_subs$site_ID))
+  
+  if(interact>1){print(head(inter_subs))}
+  
+  # run through each site and calculate co-occurrences
+  cooccurence <- ddply(dataset, .(site_ID), count_cooccur, salix=salix, galler=galler)
+  # if(sum(cooccurence$V1) == 0 ){print("no cooccurence")}
+  
+  # return the salix, galler, number of co-occurrences and number of interactions
+  return(c(salix,galler,sum(cooccurence$V1), interact))
+}
+
+
+# function to count co-occurrences (for galler-salix)
+count_cooccur <- function(site_network, salix, galler){
+  #print(paste(salix,galler))
+  
+  # for each network (passed to the function), if both salix and galler appear
+  # then it's a cooccurrence, return one. Otherwise return 0 (no co-occurrence)
+  if(salix %in% site_network$Salix & galler %in% site_network$Rgaller){  
+    #print(site_network)
+    #print(paste("cooccurrence,", salix, galler, " site_ID = ", site_network[1,"site_ID"]))
+    return(1)
+  }else{return(0)}
+}
+
+
+# calculate cooccurrences for parasitoid-galler (data is in a matrix so it has to be done differently)
+matr_calc_cooccur <- function(paras_galler, dataset){
[…]

### 2017-10-12 code/figure_generation/heatmap.py
code to make pygrace heatmap of interactions vs co-occurrences

@@ -1,0 +1,141 @@
+
+# This example demonstrates how to use a color plot.
+#
+# One important feature of color plots is that drawing objects in
+# XMGrace are plotted above the frame of a graph.  As a result, we use
+# the Grace.clone_graph method to copy the frame of the graph and make
+# things look pretty.
+#
+# Another important feature of color plots is that specifying a
+# particular world coordinate can automatically place drawing objects
+# outside of the domain of the graph.
+# Graph.remove_extraworld_drawing_objects fixes this problem by
+# removing all of the drawing objects that appear in the world
+# coordinates and are out of bounds.
+#
+# It also demonstrates how to use a PyGrace.Style to format figures in
+# a customized format
+
+#import math
+#from PyGrace.Extensions.panel import Panel,MultiPanelGrace
+
+
+
+import random
+import sys
+import os
+
+from PyGrace.grace import Grace as Plot
+from PyGrace.Extensions.colorbar import SolidRectangle, ColorBar
+from PyGrace.colors import ColorBrewerScheme
+from PyGrace.axis import LINEAR_SCALE, LOGARITHMIC_SCALE
+from PyGrace.drawing_objects import DrawBox, DrawText, DrawLine
+
+from PyGrace.Styles.el import ElGraph, ElLogColorBar, ElLinColorBar
+
+
+#------------------------------------------------------------------------------
+# make a nice figure
+#------------------------------------------------------------------------------
+# get the data (as specified in the command line)
+readfile = sys.argv[1]
+filename = readfile+'.csv'
+troph1 = sys.argv[2]
+troph2 = sys.argv[3]
+infile = open(filename)
+header=infile.readline().strip().split(',')
+
+
+# read in the data into something we can manipulate easily
+data = []
+for line in infile:
+	sline = line.strip().split(',')
+	pt = dict(zip(header,[i for i in sline]))
+	data.append(pt)
+infile.close()
+print data[0:7]
+
+ndata = {}
+for d in data:
+	if float(d['interact']) == 0:
+		if float(d['cooccur']) == 0:
+			try:
+				ndata[(d[troph1],d[troph2])].append(0)
+			except KeyError:
+				ndata[(d[troph1],d[troph2])] = 0
+		else:
+			try:
[…]

### 2017-10-12 code/figure_generation/heatmap.py
typo

@@ -138,4 +138,4 @@ graph.remove_extraworld_drawing_objects()
 
 # print out the grace
 outfile=readfile+".jpg"
-grace.write_file(plot1.eps)
+grace.write_file('plot1.eps')

### 2017-10-13 code/calculating_n_and_k.R
attempting to fix bugs in heatmap.py

@@ -1,4 +1,4 @@
-setwd("//storage.slu.se/Home$/kewo0002/My Documents/Projects/Gallers/data.dataframes/")
+setwd("C:/Users/kewo0002/confidence_in_interactions/data/Salix_example")
 
 #######################################################
 #### Create list of all combinations of galler-salix and 
@@ -6,7 +6,7 @@ setwd("//storage.slu.se/Home$/kewo0002/My Documents/Projects/Gallers/data.datafr
 #######################################################
 
 library("plyr")
-library(igraph)
+library("igraph")
 
 #### FUNCTIONS ####
 
@@ -98,7 +98,7 @@ matr_count_cooccur <- function(site,paras_galler,dataset)
 #### GALLER AND SALIX ####
 
 # read in full matrix of all interactions
-interactions <- read.csv("../original.data.from.paper/Salix_webs.csv",stringsAsFactors=FALSE)
+interactions <- read.csv("\\\\storage.slu.se/Home$/kewo0002/My Documents/Projects/Gallers/original.data.from.paper/Salix_webs.csv",stringsAsFactors=FALSE)
 
 # for just the galler-salix interactions, we only need certain columns
 galler_salix <- interactions[,c("X","X.5","X.9","X.14","X.18")]
@@ -148,17 +148,21 @@ toutput$interact <- as.numeric(levels(toutput$interact))[toutput$interact]
 range(toutput$cooccur)
 range(toutput$interact)
 
+# add numeric IDs to make plotting easier
+toutput$salix_ID <- mapvalues(toutput$Salix, from = levels(toutput$Salix), to = 1:length(levels(toutput$Salix)))
+toutput$galler_ID <- mapvalues(toutput$Rgaller, from = levels(toutput$Rgaller), to = 1:length(levels(toutput$Rgaller)))
+
 # get an idea of what the data looks like
 #plot(toutput$cooccur,toutput$interact)
 
-write.csv(toutput,file="../data/Salix_example/cooccur_interact_galler_salix.csv",quote=F)
+write.csv(toutput,file="cooccur_interact_galler_salix.csv",quote=F)
 
 
 
 #### GALLER AND PARASITOID ####
 
 # create a data frame of galler-parasitoid interactions
-int.matrix <- read.csv("df_interaction_matrix.csv",stringsAsFactors=FALSE)
[…]

### 2017-10-13 code/figure_generation/heatmap.py

@@ -41,7 +41,9 @@ from PyGrace.Styles.el import ElGraph, ElLogColorBar, ElLinColorBar
 readfile = sys.argv[1]
 filename = readfile+'.csv'
 troph1 = sys.argv[2]
+tr1id = troph1+'_ID'
 troph2 = sys.argv[3]
+tr2id = troph2+'_ID'
 infile = open(filename)
 header=infile.readline().strip().split(',')
 
@@ -60,25 +62,25 @@ for d in data:
 	if float(d['interact']) == 0:
 		if float(d['cooccur']) == 0:
 			try:
-				ndata[(d[troph1],d[troph2])].append(0)
+				ndata[(float(d[tr1id]),float(d[tr2id]))].append(0)
 			except KeyError:
-				ndata[(d[troph1],d[troph2])] = 0
+				ndata[(float(d[tr1id]),float(d[tr2id]))] = 0
 		else:
 			try:
-				ndata[(d[troph1],d[troph2])].append(-float(d['cooccur']))
+				ndata[(float(d[tr1id]),float(d[tr2id]))].append(-float(d['cooccur']))
 			except KeyError:
-				ndata[(d[troph1],d[troph2])] = -float(d['cooccur'])
+				ndata[(float(d[tr1id]),float(d[tr2id]))] = -float(d['cooccur'])
 	else:
 		try:
-			ndata[(d[troph1],d[troph2])].append(float(d['interact']))
+			ndata[(float(d[tr1id]),float(d[tr2id]))].append(float(d['interact']))
 		except KeyError:
-			ndata[(d[troph1],d[troph2])] = float(d['interact'])
+			ndata[(float(d[tr1id]),float(d[tr2id]))] = float(d['interact'])
 
 
-print ndata[('elaeagnos','Oelaea')]
-print ndata[('appendiculata','Oelaea')]
-print ndata[('myrsinifolia','Oelaea')]
-print ndata[('foetida','Oelaea')]
+print ndata[(63,17)]
+print ndata[(63,5)]
+print ndata[(63,34)]
+print ndata[(63,18)]
 
 
 # instantiate a sweet figgy fig
@@ -103,11 +105,13 @@ colorbar = grace.add_graph(ElLogColorBar,domain=(-zlim,zlim),
 graph = grace.add_graph()
 graph.copy_format(ElGraph)
 
-row = 1
+
 for d in ndata:
[…]

### 2017-10-13 code/figure_generation/heatmap.py
added running instruction

@@ -19,7 +19,8 @@
 #import math
 #from PyGrace.Extensions.panel import Panel,MultiPanelGrace
 
-
+## To run use:
+# python heatmap.py ../../data/Salix_example/cooccur_interact_galler_salix Salix Rgaller
 
 import random
 import sys

### 2017-10-13 code/figure_generation/heatmap.py
updated running instruction

@@ -20,7 +20,7 @@
 #from PyGrace.Extensions.panel import Panel,MultiPanelGrace
 
 ## To run use:
-# python heatmap.py ../../data/Salix_example/cooccur_interact_galler_salix Salix Rgaller
+# python heatmap.py ../../data/Salix_example/cooccur_interact_galler_salix galler salix
 
 import random
 import sys

### 2017-10-13 code/figure_generation/heatmap.py
Still trying to fix bugs

@@ -83,6 +83,7 @@ print ndata[(63,34)]
 print ndata[(63,18)]
 
 
+
 # instantiate a sweet figgy fig
 colors = ColorBrewerScheme("PRGn",n=253) # this is the maximum number of colors
 
@@ -133,8 +134,13 @@ graph.autoscalex()
 graph.autotickx()
 
 # restrict y-axis scale to the same as the x-axis scale
-xmin,ymin,xmax,ymax = graph.get_world()
-graph.set_world(xmin,xmin,xmax,xmax)
+#xmin,ymin,xmax,ymax = graph.get_world()
+xmin = 0
+ymin = 0
+xmax = len(set(d[tr1id] for d in data))
+ymax = len(set(d[tr2id] for d in data))
+
+graph.set_world(xmin,ymin,xmax,ymax)
 graph.autoticky()
 
 # get rid of points that are out of bounds

### 2017-10-13 manuscript/CI_interactions.tex
minor changes
forget what this was
Expanding on description of data section.

@@
 
-      [[Kate, can you expand this?]]
-      \emph{Salix}-galler-parasitoid meta-network, here focusing on the smaller \emph{Salix}-galler network.
-The meta-network consists of interactions between 52?
-\emph{Salix} species and 222 species of gall-forming insects, sampled from 374 locations in Europe ranging from Sicily to the Arctic.
-In total, 4295 unique interactions were observed.
-Each of the 374 locations can be considered as a network in its own right, but here we consider each network as an independent sample from which to build the meta-network.
+      We use an extensively sampled \emph{Salix}-galler-parasitoid meta-network as a case study.
+This dataset consists of a single community type sampled across Europe, including willow (\emph{Salix}) species, willow-galling sawflies (Hymenoptera, Tenthredinidae, Nematinae, Euurina), and their natural enemies (hymenopteran parasitoids and coleopteran, lepidopteran, dipteran, and hymenopteran inquilines).
+The data was collected over 29 years (1982-2010) at 374 unique locations across Europe ranging from Sicily to the Arctic.
+Including repeated visits to a number of sites, the data set contains 641 site-visits, each of which can be considered as a network in its own right, but here we consider each network as an independent sample from which to build the meta-network.
+The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes and 126 natural enemy nodes.
+Interactions were determined by dissecting and rearing gall inhabitants from 165,424 galls.
+Something about how the suitability of this for what we're doing.
+E.g: The high spatiotemporal resolution of this network and the 641 site-visits which can be considered as independent samples of the network make this dataset particularly well suited for testing this method.
 

### 2017-10-13 code/figure_generation/heatmap.py
try setting zeros to white in matrix

@@ -110,7 +110,8 @@ graph.copy_format(ElGraph)
 
 for d in ndata:
 	color = colorbar.z2color(ndata[d])
-
+	if ndata[d] == 0:
+		color = 'white'
 	graph.add_dataset([(d[0]-0.5,d[1]-0.5),(d[0]+0.5,d[1]+0.5)], SolidRectangle, color)
 
 

### 2017-10-13 code/build_n_k_matrix.R
alphabetizing species in matrices to make them comparable to pygrae code

@@ -11,8 +11,8 @@ adj_list <- read.csv("cooccur_interact_galler_salix.csv")
 inter_matrix <- data.frame()
 
 # Run through each salix-galler combination
-for(salix in unique(adj_list$Salix)){
-  for(galler in unique(adj_list$Rgaller)){
+for(salix in sort(unique(adj_list$Salix))){
+  for(galler in sort(unique(adj_list$Rgaller))){
     # if they don't interact, set the matrix value to the negative of the number of times they cooccur
     if(adj_list[which(adj_list$Salix == salix & adj_list$Rgaller == galler),"interact"] == 0){
       inter_matrix[as.character(galler),as.character(salix)] <- -adj_list[which(adj_list$Salix == salix & adj_list$Rgaller == galler),"cooccur"]
@@ -45,8 +45,8 @@ adj_list_g_p <- read.csv("cooccur_interact_galler_parasit.csv")
 
 inter_matrix_g_p <- data.frame()
 
-for(para in unique(adj_list_g_p$Rpara)){
-  for(galler in unique(adj_list_g_p$Rgaller)){
+for(para in sort(unique(adj_list_g_p$Rpara))){
+  for(galler in sort(unique(adj_list_g_p$Rgaller))){
     if(adj_list_g_p[which(adj_list_g_p$Rpara == para & adj_list_g_p$Rgaller == galler),"interact"] == 0){
       inter_matrix_g_p[as.character(galler),as.character(para)] <- -adj_list_g_p[which(adj_list_g_p$Rpara == para & adj_list_g_p$Rgaller == galler),"cooccur"]
     }else{

### 2017-10-17 manuscript/supplemental.tex
added Kate's prior-web code to SI

@@
       % }
+
+      To extract the galler-parsitoid network from the same study above:
+
+      \vspace{12pt}
+      \emph{
+      \noindent \hspace{-4pt} 
+      prior\_web\_data=read.csv('tree\_level\_interaxn\_all\_plants\_traits\_size.csv')\\
+      prior\_web\_data <- prior\_web\_data[,8:26]
+
+      \# Build a web with interactions=1 for any parasitoid on any galler
+      prior\_web=data.frame()
+
+      \# each column contains all interactions for a particular parasitoid-galler combination
+      for(column in 1:ncol(prior\_web\_data)){
+      \hspace{-4pt}   \# the column name gives the species which makes the gall, followed by the species emerging from the gall
+      \hspace{-4pt}   galler\_emerged=strsplit(colnames(prior\_web\_data)[column], "\_")
+      \hspace{-4pt}   galler = galler\_emerged[[1]][1]
+      \hspace{-4pt}   emerged = galler\_emerged[[1]][2]
+
+      \hspace{-4pt}   \# the strength of the interaction is the sum of the column (number of galls across all branches sampled)
+      \hspace{-4pt}   linkstrength = sum(prior\_web_data[,column])
+      \hspace{-4pt}   prior\_web[as.character(galler),as.character(emerged)] <- linkstrength
+      }
+
+      \# Make the naS into 0
+      prior\_web[is.na(prior\_web)] <- 0
+
+      \# remove emerging gallers with no parasitoids
+      prior\_web\_para\_only <- prior\_web[,c(2:6,8:9,12)]
+
+      \# convert interaction strengths to 1
+      prior\_web[which(prior\_web>0)] <- 1
+
+      write.csv(prior\_web\_para\_only, file="prior\_web\_para\_only.csv", quote=F)
+      }
+
+      % # read in the data
+      % prior_web_data=read.csv('../data/Salix_example/tree_level_interaxn_all_plants_traits_size.csv')
+      % # just keep what we need
+      % prior_web_data <- prior_web_data[,8:26]
+
+      % # Build a web with interactions=1 for any parasitoid on any galler
+      % prior_web=data.frame()
+
+      % # each column contains all interactions for a particular parasitoid-galler combination
+      % for(column in 1:ncol(prior_web_data)){
+      %   # the column name gives the species which makes the gall, followed by the species emerging from the gall
+      %   # they need to be separated 
+      %   galler_emerged=strsplit(colnames(prior_web_data)[column], "_")
+      %   galler = galler_emerged[[1]][1]
+      %   emerged = galler_emerged[[1]][2]
+
+      %   # the strength of the interaction is the sum of the column (number of galls across all branches sampled)
+      %   linkstrength = sum(prior_web_data[,column])
+      %   # put that into a dataframe
+      %   prior_web[as.character(galler),as.character(emerged)] <- linkstrength
+      % }
+
+      % # Make the naS into 0
+      % prior_web[is.na(prior_web)] <- 0
+      % # Make the non-zero elements into 1
+      % prior_web[prior_web>0] <- 1
+      % # some of the emergers were the gallers, remove those columns if we're only
+      % # interested in galler-parasitoid interactions
+      % prior_web_para_only <- prior_web[,c(2:6,8:9,12)]
+      % write.csv(prior_web_para_only, file="prior_web_para_only.csv", quote=F)
 

### 2017-10-18 manuscript/CI_interactions.tex
added galler-parasitoid results to text.

@@
 Specifically, we obtain $\alpha$=2.807855, $\beta$=2.342815.
+For the galler-parasitoid component of the network, the corresponding prior parameters are $\alpha$=1.341479, $\beta$=9.487966.
       We are then able to use these priors to estimate the posterior distriution of interaction probabilities given the additional information in our dataset.
@@
       distribution we obtain based on~\citet{Barbour2016,Barbour2016Dryad} is:
-      $\hat{\lambda_{ij}}$=0.545, var($\lambda$)=0.048.
+      $\hat{\lambda_{ij}}$=0.545, var($\lambda$)=0.048 for the \emph{Salix}-galler network and $\hat{\lambda_{ij}}$=0.124, var($\lambda$)=0.010 for the galler-parasitoid network.
       This is consistent with the prior data, where the average 
-      interaction probability based on the degree distributions of Salix genotypes and gallers was 0.541.
+      interaction probability based on the degree distributions of Salix genotypes and gallers was 0.541 and that for gallers and parasitoids was 0.122.
 [[What's the connectance of our dataset, if we call greys 0?]] This probability does, however, seem rather high for our dataset.
@@
 Thus $\alpha'$=$\alpha$ and $\beta'$=$\beta + n$.
-At the most extreme case, for a pair of species which co-occurred at all 374 sites and was never observed to interact, our distribution would become:
+At the most extreme case, for a pair of species which co-occurred at all 374 sites and was never observed to interact, our distributions would become:
 
-      $\hat{\lambda_{ij}}$=7.405645 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=1.938755 $\times$ 10$^{-5}$.
+      $\hat{\lambda_{ij}}$=7.405645 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=1.938755 $\times$ 10$^{-5}$ for the \emph{Salix}-galler network and 
+      $\hat{\lambda_{ij}}$=3.485906 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=9.026737 $\times$ 10$^{-6}$ for the galler-parasitoid network.
 
@@
         \label{interval_table}
-        \begin{tabular}{l | c c}
-        N & Lower bound & Upper bound \\
+        \begin{tabular}{l | c c | c c }
+        \multirow{2}{*}{N} & \multicolumn{2}{c}{\emph{Salix}-galler} & \multicolumn{2}{c}{galler-parasitoid}\\
+         & Lower bound & Upper bound \\
         \hline
-        0   & 0.157 & 0.901 \\
-        2   & 0.099 & 0.743 \\
-        4   & 0.072 & 0.621 \\
-        6   & 0.057 & 0.530 \\
-        8   & 0.047 & 0.462 \\
-        10 & 0.040 & 0.408 \\
-        14 & 0.031 & 0.331 \\
-        20 & 0.023 & 0.258 \\
-        30 & 0.016 & 0.188 \\
-        40 & 0.012 & 0.148 \\
-        50 & 0.010 & 0.122 \\
+        0   & 0.157 & 0.901 & 0.008 & 0.364 \\
+        2   & 0.099 & 0.743 & 0.006 & 0.313 \\
+        4   & 0.072 & 0.621 & 0.006 & 0.274 \\
+        6   & 0.057 & 0.530 & 0.005 & 0.244 \\
+        8   & 0.047 & 0.462 & 0.004 & 0.219 \\
+        10  & 0.040 & 0.408 & 0.004 & 0.200 \\
+        14  & 0.031 & 0.331 & 0.003 & 0.169 \\
+        20  & 0.023 & 0.258 & 0.003 & 0.137 \\
+        30  & 0.016 & 0.188 & 0.002 & 0.104 \\
+        40  & 0.012 & 0.148 & 0.002 & 0.084 \\
+        50  & 0.010 & 0.122 & 0.001 & 0.071 \\
         \hline                  
-        374 & 0.001 & 0.018 \\
+        374 & 0.001 & 0.018 & \textless0.001 & 0.011 \\
         \hline
@@
 The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact.
-If we want to be 95\% confident that the interaction probability for two species in the \emph{Salix}-galler system is below 0.5, 0.1, or 0.01, we would need six, 54, and 114 observed co-occurrances with no observed interaction (Fig.~\ref{Salix_cdfs}; see function samples\_required in~\emph{Appendix S2}).
+If we want to be 95\% confident that the interaction probability for two species in the \emph{Salix}-galler network is below 0.5, 0.1, or 0.01, we would need six, 54, and 114 observed co-occurrances with no observed interaction (Fig.~\ref{Salix_cdfs}; see function samples\_required in~\emph{Appendix S2}).
+      Although the prior distribution of interaction probabilities is narrower and closer to zero for the galler-parasitoid network, the number of samples required to be 95\% confident that the interaction probability is below a threshold still increases quickly; we would need 25 and 101 observed co-occurances with no observed interaction for threshold interaction probabilities of 0.1 and 0.01, respectively.
       Given the low levels of replication in most network studies, this implies that we should have fairly low confidence in many "non-interacting" pairs of species.

### 2017-10-18 manuscript/supplemental.tex
added galler-parasitoid results to text.

@@
       int\_probs=as.numeric(deg\_dist\_galler\%$*$\%t(deg\_dist\_Salix))\\
+
+      \# And for the galler-parasitoid web:\\
+      deg\_dist\_parasitoid=rowSums(prior\_web\_para\_only)/ncol(prior\_web\_para\_only)\\
+      deg\_dist\_parasitized=colSums(prior\_web\_para\_only)/nrow(prior\_web\_para\_only)\\
+      gp\_int\_probs=as.numeric(deg\_dist\_parasitized\%$*$\%t(deg\_dist\_parasitoid))
+
       }
@@
       % int_probs=as.numeric(deg_dist_galler%*%t(deg_dist_Salix))
+
+      % deg_dist_parasitoid=rowSums(prior_web_para_only)/ncol(prior_web_para_only)
+      % deg_dist_parasitized=colSums(prior_web_para_only)/nrow(prior_web_para_only)
+      % gp_int_probs=deg_dist_parasitized%*%t(deg_dist_parasitoid)
 

### 2017-10-18 manuscript/CI_interactions.tex
starting to add parasitoids to the figures

@@
   \begin{figure}
-    \caption{\textbf{A)} Most pairs of \emph{Salix} and galler species were never observed co-occurring despite the high levels of replication in our example dataset.
+    \caption{\textbf{A-B)} Most pairs of \emph{Salix} and galler or galler and parasitoid species were never observed co-occurring despite the high levels of replication in our example dataset.
 For those that were observed together at least once, the number of observed co-occurances was generally small (\textless10).
@@
 3986 pairs of species were never observed co-occurring: these pairs are omitted from the histogram.
-\textbf{B)} Most pairs of species that were observed at the same site were never observed interacting.
+\textbf{C-D)} Most pairs of species that were observed at the same site were never observed interacting.
 Here we show a histogram of the number of observed interactions within pairs of co-occurring species.
-\textbf{C)} Here we show, for each species pair, the number of observed interactions plotted against the number of observed co-occurances.
+\textbf{E-F)} Here we show, for each species pair, the number of observed interactions plotted against the number of observed co-occurances.
 Most pairs either are never observed interacting or interact almost every time they co-occur.

### 2017-10-18 code/figure_generation/observation_interaction_histogram.py

@@ -1,5 +1,5 @@
 # # ######### R code to generate data files:
-# galldata=read.csv('../../data/Salix_example/cooccur_interact_galler_salix.csv',header=TRUE,rownames=TRUE)
+# galldata=read.csv('../../data/Salix_example/cooccur_interact_galler_salix.csv',header=TRUE,row.names=1)
 # n_pairs=nrow(galldata)
 # unobserved=length(which(galldata$cooccur==0))
 # observed=galldata[which(galldata$cooccur>0),]
@@ -14,7 +14,20 @@
 # write.table(observation_histdata,file='../../data/Salix_example/Salix_Galler/nonzero_cooccurances.tsv',sep='\t')
 # write.table(interaction_histdata,file='../../data/Salix_example/Salix_Galler/observed_interactions.tsv',sep='\t')
 
+# pardata=read.csv('../../data/Salix_example/cooccur_interact_galler_parasit.csv',header=TRUE,row.names=1)
+# n_pairs=nrow(pardata)
+# unobserved=length(which(pardata$cooccur==0))
+# observed=pardata[which(pardata$cooccur>0),]
+# observed$int_freq=observed$interact/observed$cooccur
+# obs_ints=length(which(observed$interact>0))
 
+# observation_histdata=as.data.frame(tapply(observed$cooccur,observed$cooccur,length))
+# interaction_histdata=as.data.frame(tapply(observed$interact,observed$interact,length))
+# colnames(observation_histdata)=c("cooccurances")
+# colnames(interaction_histdata)=c("interactions")
+
+# write.table(observation_histdata,file='../../data/Salix_example/Galler_Parasitoid/nonzero_cooccurances.tsv',sep='\t')
+# write.table(interaction_histdata,file='../../data/Salix_example/Galler_Parasitoid/observed_interactions.tsv',sep='\t')
 
 import sys
 import math
@@ -53,19 +66,21 @@ def read_Rfiles(filename):
   return pointlist
 
 def read_csv(filename): # Just using the R input file here.
-  dotlist=[]
+  dotlist=set()
   f=open(filename,'r')
   for line in f:
     newline=line.split('\r')[0].split(',')
+
     if newline[0]!='':
-      cooccurances=int(newline[-2])
-      interactions=int(newline[-1])
[…]

### 2017-10-18 code/figure_generation/samples_for_thresholds.py
sample threshold figure worked at least

@@ -33,10 +33,52 @@
 #     print(r)
 #     r=r+1
 #   }
+# # }
+
+# write.table(samples,file='../../data/Salix_example/Salix_Galler/samples_for_threshold.tsv',sep='\t')
+# write.table(CDFs,file='../../data/Salix_example/Salix_Galler/samplefigure.tsv',sep='\t')
+
+
+# # Galler-parasitoid stuff
+# ######### R code to generate data files:
+# # % Getting cdfs:
+# gp_pars=calculate_parameters(gp_int_probs,0,0)
+# n=seq(0,500,1)
+
+# gp_CDFs=matrix(nrow=4,ncol=502)
+# colnames(gp_CDFs)=c("Threshold",n)
+# r=1
+# for(threshold in c(0.5,0.25,0.1,0.05)){
+#   # for(confidence in c(0.9,0.95,0.975)){
+#     cdf=pbeta(threshold,shape1=gp_pars[[1]],shape2=gp_pars[[2]]+n)
+#     # samples=length(which(cdf<confidence))
+#     gp_CDFs[r,1]=threshold
+#     # CDFs[r,2]=confidence
+#     # CDFs[r,3]=samples
+#     gp_CDFs[r,2:502]=cdf
+#     print(r)
+#     r=r+1
+#   }
+
+
+
+# gp_samples=matrix(nrow=12,ncol=3)
+# colnames(gp_samples)=c("Threshold","Confidence","Samples")
+# r=1
+# for(threshold in c(0.5,0.25,0.1,0.05)){
+#   for(confidence in c(0.9,0.95,0.975)){
+#     cdf=pbeta(threshold,shape1=gp_pars[[1]],shape2=gp_pars[[2]]+n)
+#     n_obs=length(which(cdf<confidence))
+#     gp_samples[r,1]=threshold
+#     gp_samples[r,2]=confidence
+#     gp_samples[r,3]=n_obs
+#     print(r)
+#     r=r+1
+#   }
 # }
 
-# write.table(samples,file='../data/Salix_example/Salix_Galler/samples_for_threshold.tsv',sep='\t')
-# write.table(CDFs,file='../data/Salix_example/Salix_Galler/samplefigure.tsv',sep='\t')
+# write.table(gp_samples,file='../../data/Salix_example/Galler_Parasitoid/samples_for_threshold.tsv',sep='\t')
[…]

### 2017-10-19 code/figure_generation/pdfs_and_N.py
prepping to add gp

@@ -1,20 +1,22 @@
-######### R code to generate data files:
-# % Getting distributions:
-# xdata=matrix(ncol=1001,nrow=201)
-# ydata=matrix(ncol=1001,nrow=201)
-# for(n in 0:200){
-#   dist=calculate_distribution(calculate_parameters(int_probs,2*n,0))
-#   x=seq(-10,10,length=1000)*sqrt(dist[[2]])+dist[[1]]
-#   hx=dnorm(x)
-#   xdata[n+1,]=c(2*n,x)
-#   ydata[n+1,]=c(2*n,hx)
-# }
+######## R code to generate data files:
+# Getting distributions:
+xdata=matrix(ncol=1001,nrow=26)
+ydata=matrix(ncol=1001,nrow=26)
+for(n in 0:25){
+  dist=calculate_distribution(calculate_parameters(sg_int_probs,2*n,0))
+  x=seq(-10,10,length=1000)*sqrt(dist[[2]])+dist[[1]]
+  hx=dnorm(x)
+  xdata[n+1,]=c(2*n,x)
+  ydata[n+1,]=c(2*n,hx)
+}
 
-# % Data are along rows for pythonic convenience
-# colnames(xdata)=c("N",seq(1,1000))
-# colnames(ydata)=c("N",seq(1,1000))
-# write.table(xdata,file='../data/Salix_example/Salix_Galler/distfigure_xvals.tsv',sep='\t')
-# write.table(ydata,file='../data/Salix_example/Salix_Galler/distfigure_yvals.tsv',sep='\t')
+# Data are along rows for pythonic convenience
+colnames(xdata)=c("N",seq(1,1000))
+colnames(ydata)=c("N",seq(1,1000))
+
+
+write.table(xdata,file='../data/Salix_example/Salix_Galler/distfigure_xvals.tsv',sep='\t')
+write.table(ydata,file='../data/Salix_example/Salix_Galler/distfigure_yvals.tsv',sep='\t')
 
 import sys
 import math

### 2017-10-19 manuscript/CI_interactions.tex
Added galler-parasitoids to text and figures, starting to add LS and percent specialists to posterior sampling

@@
         \label{Salix_pdfs}
-        \caption{Using a prior distribution based on the \emph{Salix}-galler network in~\citet{Barbour2016}, we can calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting.
-Here we show posterior distributions for $\lambda$ ranging from the prior distribution (N=0 observed co-occurances) to the distribution obtained when the pair of species has been observed co-occurring 50 times.
-The distribution narrows and approaches zero as the sample size increases, but never includes zero.}
+        \caption{Using prior distribution based on the \emph{Salix}-galler and galler-parasitoid networks in~\citet{Barbour2016}, we can calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting.
+Here we show posterior distributions for each $\lambda$ in each network ranging from the prior distribution (N=0 observed co-occurances) to the distribution obtained when the pair of species has been observed co-occurring 100 times.
+The distribution narrows and approaches zero as the sample size increases.
+\textbf{A)} The posterior distributions for the \emph{Salix}-galler component are always wider and farther from zero than those for \textbf{B)} the galler-parasitoid component.}
         \includegraphics*[width=.8\textwidth]{figures/Salix_Galler_pdfs_increasing_N.eps}
         \end{figure}
+        [[Maybe I was using the int_probs from the other example?]]
 
@@
 
-      [[Do we want the host-parasitoid site too, or is the plant-galler enough? This is feeling long already.]]
       In a strict Bayesian framework, we wish to use a prior distribution that does not rely on any information from the study at hand.
@@
       Using this prior distribution of galler-\emph{Salix} interaction frequencies, we can obtain parameters for the prior distribution of $\lambda$ in our dataset.
-Specifically, we obtain $\alpha$=2.807855, $\beta$=2.342815.
+Specifically, we obtain $\alpha$=2.507217, $\beta$=1.888079.
 For the galler-parasitoid component of the network, the corresponding prior parameters are $\alpha$=1.341479, $\beta$=9.487966.
@@
       distribution we obtain based on~\citet{Barbour2016,Barbour2016Dryad} is:
-      $\hat{\lambda_{ij}}$=0.545, var($\lambda$)=0.048 for the \emph{Salix}-galler network and $\hat{\lambda_{ij}}$=0.124, var($\lambda$)=0.010 for the galler-parasitoid network.
+      $\hat{\lambda_{ij}}$=0.570, var($\lambda$)=0.056 for the \emph{Salix}-galler network and $\hat{\lambda_{ij}}$=0.124, var($\lambda$)=0.010 for the galler-parasitoid network.
       This is consistent with the prior data, where the average 
-      interaction probability based on the degree distributions of Salix genotypes and gallers was 0.541 and that for gallers and parasitoids was 0.122.
+      interaction probability based on the degree distributions of Salix genotypes and gallers was 0.562 and that for gallers and parasitoids was 0.122.
 [[What's the connectance of our dataset, if we call greys 0?]] This probability does, however, seem rather high for our dataset.
@@
 
-      $\hat{\lambda_{ij}}$=7.405645 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=1.938755 $\times$ 10$^{-5}$ for the \emph{Salix}-galler network and 
+      $\hat{\lambda_{ij}}$=6.625921 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=1.739456 $\times$ 10$^{-5}$ for the \emph{Salix}-galler network and 
       $\hat{\lambda_{ij}}$=3.485906 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=9.026737 $\times$ 10$^{-6}$ for the galler-parasitoid network.
@@
 
+      % # R code to make the table:
+      % output=matrix(nrow=length(ns),ncol=5)
+      % ns=c(0,1,2,5,10,15,20,25,50,100,150,200,374)
+      % output[,1]=ns
+      % for(r in 1:nrow(output)){
+      %   interval1=credible_interval(calculate_parameters(sg_int_probs,ns[r],0),0.025,0.975)    
+      %   interval2=credible_interval(calculate_parameters(gp_int_probs,ns[r],0),0.025,0.975)    
+      %   output[r,2:3]=interval1
+      %   output[r,4:5]=interval2
+      % }
+
       \begin{table}[h]
@@
         \hline
-        0   & 0.157 & 0.901 & 0.008 & 0.364 \\
-        2   & 0.099 & 0.743 & 0.006 & 0.313 \\
-        4   & 0.072 & 0.621 & 0.006 & 0.274 \\
-        6   & 0.057 & 0.530 & 0.005 & 0.244 \\
-        8   & 0.047 & 0.462 & 0.004 & 0.219 \\
-        10  & 0.040 & 0.408 & 0.004 & 0.200 \\
-        14  & 0.031 & 0.331 & 0.003 & 0.169 \\
-        20  & 0.023 & 0.258 & 0.003 & 0.137 \\
-        30  & 0.016 & 0.188 & 0.002 & 0.104 \\
-        40  & 0.012 & 0.148 & 0.002 & 0.084 \\
-        50  & 0.010 & 0.122 & 0.001 & 0.071 \\
+        0   & 0.152 & 0.931 & 0.008 & 0.364 \\
+        1   & 0.110 & 0.843 & 0.007 & 0.337 \\
+        2   & 0.087 & 0.760 & 0.006 & 0.313 \\
+        5   & 0.053 & 0.573 & 0.005 & 0.258 \\
+        10  & 0.033 & 0.400 & 0.004 & 0.200 \\
+        15  & 0.023 & 0.306 & 0.003 & 0.163 \\
+        20  & 0.018 & 0.247 & 0.003 & 0.137 \\
+        25  & 0.015 & 0.208 & 0.002 & 0.119 \\
+        50  & 0.008 & 0.115 & 0.001 & 0.071 \\
+        100 & 0.004 & 0.061 & 0.001 & 0.039 \\
+        150 & 0.003 & 0.041 & \textless0.001 & 0.027 \\
+        200 & 0.002 & 0.031 & \textless0.001 & 0.021 \\
         \hline
-        374 & 0.001 & 0.018 & \textless0.001 & 0.011 \\
+        374 & 0.001 & 0.017 & \textless0.001 & 0.011 \\
         \hline
@@
 The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact.
-If we want to be 95\% confident that the interaction probability for two species in the \emph{Salix}-galler network is below 0.5, 0.1, or 0.01, we would need six, 54, and 114 observed co-occurrances with no observed interaction (Fig.~\ref{Salix_cdfs}; see function samples\_required in~\emph{Appendix S2}).
+If we want to be 95\% confident that the interaction probability for two species in the \emph{Salix}-galler network is below 0.5, 0.1, or 0.01, we would need six, 51, and 101 observed co-occurrances with no observed interaction (Fig.~\ref{Salix_cdfs}; see function samples\_required in~\emph{Appendix S2}).
       Although the prior distribution of interaction probabilities is narrower and closer to zero for the galler-parasitoid network, the number of samples required to be 95\% confident that the interaction probability is below a threshold still increases quickly; we would need 25 and 101 observed co-occurances with no observed interaction for threshold interaction probabilities of 0.1 and 0.01, respectively.
       Given the low levels of replication in most network studies, this implies that we should have fairly low confidence in many "non-interacting" pairs of species.
-Even in the extensively replicated \emph{Salix}-galler dataset very few species pairs were observed co-occurring frequently enough to reach these thresholds (173/4992 pairs were observed at least six times, two pairs were observed at least 54 times, and no pair was observed more than 114 times).
+Even in the extensively replicated \emph{Salix}-galler-parasitoid dataset very few species pairs were observed co-occurring frequently enough to reach these thresholds (only three \emph{Salix}-galler pairs and 31 galler-parasitoid pairs were observed co-occurring frequently enough to reach the threshold for an interaction probability of 0.1, and no pairs were observed co-occurring frequently enough to reach the threshold for an interaction probability of 0.01).
 Discounting potential interactions, then, requires either a stronger prior expectation of no interaction (e.g., we can be highly confident that a palm tree will not predate upon a leopard no matter how many times the two species are observed together) or very extensive sampling.
@@
 Here we show the cumulartive density functions for thresholds probabilities of 0.5 (solid line), 0.25 (dashed line), 0.1 (dash-dot line), and 0.05 (dotted line) as well as the points at which the cdf reaches 0.90 (orange square), 0.95 (red circle), and 0.975 (blue diamond) for each threshold value.
-The large ticks along the x-axis indicate the number of samples associated with each of these points.}
+The large ticks along the x-axis indicate the number of samples associated with each of these points.
+Note that the number of samples required to reach any given threshold is smaller for \textbf{A)} the \emph{Salix}-galler network than for \textbf{B)} the galler-parasitoid network.}
         \label{Salix_cdfs}

### 2017-10-19 manuscript/supplemental.tex
starting to add parasitoids to the figures
Added galler-parasitoids to text and figures, starting to add LS and percent specialists to posterior sampling

@@
 
-      % prior_web_data=read.csv('tree_level_interaxn_all_plants_traits_size.csv')
+      % prior_web_data=read.csv('../../data/Salix_example/tree_level_interaxn_all_plants_traits_size.csv')
       % # Remove extra data on parasitoids, etc.
@@
       % }
+      % write.csv(prior_web,file='binary_prior_web_SG.csv',quote=F)
 
@@
 
-      % # read in the data
-      % prior_web_data=read.csv('../data/Salix_example/tree_level_interaxn_all_plants_traits_size.csv')
+      % % # read in the data
+      % prior_web_data=read.csv('../../data/Salix_example/tree_level_interaxn_all_plants_traits_size.csv')
       % # just keep what we need
@@
       % prior_web_para_only <- prior_web[,c(2:6,8:9,12)]
-      % write.csv(prior_web_para_only, file="prior_web_para_only.csv", quote=F)
+      % write.csv(prior_web_para_only, file="binary_prior_web_para_only.csv", quote=F)
 
@@
 
-      %       # Now get the degree distributions from the web
-      % deg_dist_Salix=rowSums(prior_web)/ncol(prior_web)
-      % # Remove one genotype that never interacted
-      % deg_dist_Salix<-deg_dist_Salix[which(rowSums(prior_web)>0)]
-      % deg_dist_galler=colSums(prior_web)/nrow(prior_web)
-      % # Interaction probabilities are the product of plant and galler probabilities
-      % int_probs=as.numeric(deg_dist_galler%*%t(deg_dist_Salix))
+            # Now get the degree distributions from the web
+      deg_dist_Salix=rowSums(prior_web)/ncol(prior_web)
+      # Remove one genotype that never interacted
+      deg_dist_Salix<-deg_dist_Salix[which(rowSums(prior_web)>0)]
+      deg_dist_galler=colSums(prior_web)/nrow(prior_web)
+      # Interaction probabilities are the product of plant and galler probabilities
+      int_probs=as.numeric(deg_dist_galler%*%t(deg_dist_Salix))
 
-      % deg_dist_parasitoid=rowSums(prior_web_para_only)/ncol(prior_web_para_only)
-      % deg_dist_parasitized=colSums(prior_web_para_only)/nrow(prior_web_para_only)
-      % gp_int_probs=deg_dist_parasitized%*%t(deg_dist_parasitoid)
+      deg_dist_parasitoid=rowSums(prior_web_para_only)/ncol(prior_web_para_only)
+      deg_dist_parasitized=colSums(prior_web_para_only)/nrow(prior_web_para_only)
+      gp_int_probs=as.numeric(deg_dist_parasitized%*%t(deg_dist_parasitoid))
 

### 2017-10-19 code/calculate_sim_network_properties.py

@@ -20,54 +20,90 @@ def web_reader(webdir,proportion,post_number,sample_number):
     links.add((galler,salix))
   f.close()
 
-  # G=nx.Graph()
-  # for sp in gallers:
-  #   G.add_node(sp)
-  # for sp in salixes:
-  #   G.add_node(sp)
-  # for (galler,salix) in links:
-  #   G.add_edge(galler,salix)
+  G=nx.Graph()
+  for sp in gallers:
+    G.add_node(sp)
+  for sp in salixes:
+    G.add_node(sp)
+  for (galler,salix) in links:
+    G.add_edge(galler,salix)
 
-  return gallers,salixes,links
+  return gallers,salixes,links,G
 
-def calculate_original_properties(gallers,salixes,links):
+def calculate_original_properties(gallers,salixes,links,G):
   # original_properties['L'][post_number]=len(links)
   # original_properties['S'][post_number]=len(G.nodes())
   # original_properties['LS'][post_number]=float(len(G.edges()))/float(len(salixes))
   # original_properties['LG'][post_number]=float(len(G.edges()))/float(len(gallers))
   C=float(len(links))/float(len(salixes)*len(gallers))
+  LS=[]
+  specialists=[]
+  for node in G.nodes():
+    links=len(G.neighbors(node))
+    LS.append(links)
+    if links==1:
+      specialists.append(node)
+  meanLS=np.mean(LS)
+  Spec=float(len(specialists))/float(len(G.nodes()))
 
-  return C
+  return C,meanLS,Spec
 
 def write_summary_file(summary_dict):
   f=open('../data/randomised_webs/Connectance_table.tsv','w')
   f.write('Web\tProportion\tObs_C\tSample_mean\tSample_SD\n')
-  for proportion in summary_dict:
-    for post_number in summary_dict[proportion]:
-      f.write(str(post_number)+'\t'+str(proportion)+'\t'+'\t'.join(summary_dict[proportion][post_number])+'\n')
+  for proportion in summary_dict['C']:
+    for post_number in summary_dict['C'][proportion]:
+      f.write(str(post_number)+'\t'+str(proportion)+'\t'+'\t'.join(summary_dict['C'][proportion][post_number])+'\n')
   f.close()
+
+  g=open('../data/randomised_webs/LS_table.tsv','w')
[…]

### 2017-10-19 code/figure_generation/pdfs_and_N.py

@@ -1,22 +1,45 @@
-######## R code to generate data files:
-# Getting distributions:
-xdata=matrix(ncol=1001,nrow=26)
-ydata=matrix(ncol=1001,nrow=26)
-for(n in 0:25){
-  dist=calculate_distribution(calculate_parameters(sg_int_probs,2*n,0))
-  x=seq(-10,10,length=1000)*sqrt(dist[[2]])+dist[[1]]
-  hx=dnorm(x)
-  xdata[n+1,]=c(2*n,x)
-  ydata[n+1,]=c(2*n,hx)
-}
+# ####### R code to generate data files:
+# # Getting distributions:
+# xdata=matrix(ncol=1001,nrow=12)
+# ydata=matrix(ncol=1001,nrow=12)
+# ns=as.vector(c(0,5,10,15,20,25,50,100,150,200,300,374))
+# for(i in 1:length(ns)){
+#   n=ns[i]
+#   dist=calculate_distribution(calculate_parameters(sg_int_probs,n,0))
+#   x=seq(-5,5,length=1000)*sqrt(dist[[2]])+dist[[1]]
+#   hx=dnorm(x,dist[[1]],sqrt(dist[[2]]))
+#   xdata[i,]=c(n,x)
+#   ydata[i,]=c(n,hx)
+# }
 
-# Data are along rows for pythonic convenience
-colnames(xdata)=c("N",seq(1,1000))
-colnames(ydata)=c("N",seq(1,1000))
+# # Data are along rows for pythonic convenience
+# colnames(xdata)=c("N",seq(1,1000))
+# colnames(ydata)=c("N",seq(1,1000))
 
 
-write.table(xdata,file='../data/Salix_example/Salix_Galler/distfigure_xvals.tsv',sep='\t')
-write.table(ydata,file='../data/Salix_example/Salix_Galler/distfigure_yvals.tsv',sep='\t')
+# write.table(xdata,file='../../data/Salix_example/Salix_Galler/distfigure_xvals.tsv',sep='\t')
+# write.table(ydata,file='../../data/Salix_example/Salix_Galler/distfigure_yvals.tsv',sep='\t')
+
+# xdata=matrix(ncol=1001,nrow=12)
+# ydata=matrix(ncol=1001,nrow=12)
+# ns=as.vector(c(0,5,10,15,20,25,50,100,150,200,300,374))
+# for(i in 1:length(ns)){
+#   n=ns[i]
[…]

### 2017-10-20 code/calculate_sim_network_properties.py
making randomized webs for galler-parasitoids too

@@ -4,6 +4,10 @@ import networkx as nx
 import numpy as np 
 import scipy as sp 
 
+# To build posterior interaction probabilities:
+
+
+
 def web_reader(webdir,proportion,post_number,sample_number): 
   gallers=set()
   salixes=set()
@@ -20,33 +24,38 @@ def web_reader(webdir,proportion,post_number,sample_number):
     links.add((galler,salix))
   f.close()
 
-  G=nx.Graph()
-  for sp in gallers:
-    G.add_node(sp)
-  for sp in salixes:
-    G.add_node(sp)
-  for (galler,salix) in links:
-    G.add_edge(galler,salix)
+  # G=nx.Graph()
+  # for sp in gallers:
+  #   G.add_node(sp)
+  # for sp in salixes:
+  #   G.add_node(sp)
+  # for (galler,salix) in links:
+  #   G.add_edge(galler,salix)
 
-  return gallers,salixes,links,G
+  return gallers,salixes,links
 
-def calculate_original_properties(gallers,salixes,links,G):
+def calculate_original_properties(gallers,salixes,links):
   # original_properties['L'][post_number]=len(links)
   # original_properties['S'][post_number]=len(G.nodes())
   # original_properties['LS'][post_number]=float(len(G.edges()))/float(len(salixes))
   # original_properties['LG'][post_number]=float(len(G.edges()))/float(len(gallers))
   C=float(len(links))/float(len(salixes)*len(gallers))
-  LS=[]
-  specialists=[]
-  for node in G.nodes():
-    links=len(G.neighbors(node))
-    LS.append(links)
-    if links==1:
-      specialists.append(node)
-  meanLS=np.mean(LS)
-  Spec=float(len(specialists))/float(len(G.nodes()))
+  LperSalix=[] # Ranges between 18 and 37 in the posterior predicted webs
+  LperGaller=[] # Ranges between 40 and 68
+  for salix in salixes:
+    slist=[]
+    for (g,s) in links:
+      if s==salix:
+        slist.append(g)
+    LperSalix.append(len(slist))
+  for galler in gallers:
+    glist=[]
+    for (g,s) in links:
+      if g==galler:
+        glist.append(s)
+    LperGaller.append(len(glist))
 
-  return C,meanLS,Spec
[…]

### 2017-10-20 code/create_posterior_GP_webs.py

@@ -1,0 +1,109 @@
+import os
+import sys
+import math
+import random
+from decimal import *
+import numpy as np
+import scipy as sp
+
+#   numpy.random.binomial(n,p,size) draws [size] samples from a binomial distribution
+#   % Each observation is a Bernoulli, or a binomial with n=1. Use p=mean(posterior).
+
+def read_in_data(datafile):
+  pdict={}
+  f=open(datafile,'r')
+  for line in f:
+    if line.split()[0]!='"Salix"':
+      if len(line.split())==7:
+        plant=line.split()[1][1:-1]
+        galler=line.split()[2][1:-1]
+        occurs=int(line.split()[3])
+        interacts=int(line.split()[4])
+        postmean=float(line.split()[5])
+        postSD=float(line.split()[6])
+        sppair=(plant,galler)
+        pdict[sppair]=((postmean,postSD))
+      elif len(line.split())==10:
+        plant='.'.join([line.split()[1][1:],line.split()[2],line.split()[3],'?']) # 4 is always '?'
+        galler=line.split()[5][1:-1]
+        occurs=int(line.split()[6])
+        interacts=int(line.split()[7])
+        postmean=float(line.split()[8])
+        postSD=float(line.split()[9])
+        sppair=(plant,galler)
+        pdict[sppair]=((postmean,postSD))
+      elif len(line.split())==9:
+        plant='.'.join([line.split()[1][1:],line.split()[2],line.split()[3][:-1]]) 
+        galler=line.split()[4][1:-1]
+        occurs=int(line.split()[5])
+        interacts=int(line.split()[6])
+        postmean=float(line.split()[7])
+        postSD=float(line.split()[8])
+        sppair=(plant,galler)
+        pdict[sppair]=((postmean,postSD))
+      elif len(line.split())==8:
+        plant='.'.join([line.split()[1][1:],line.split()[2][:-1]]) 
+        galler=line.split()[3][1:-1]
+        occurs=int(line.split()[4])
+        interacts=int(line.split()[5])
+        postmean=float(line.split()[6])
+        postSD=float(line.split()[7])
+        sppair=(plant,galler)
+        pdict[sppair]=((postmean,postSD))        
+      else:
+        print len(line.split())
+  f.close()
+
+  return pdict
+
+
+def posterior_sampling(pdict):
+  random_ints={}
+  for pair in pdict:
+    samples=np.random.binomial(1,pdict[pair][0],10)
[…]

### 2017-10-20 code/create_posterior_webs.py

@@ -6,6 +6,42 @@ from decimal import *
 import numpy as np
 import scipy as sp
 
+# # To create the data file:
+# SG_dataset=read.csv('../data/Salix_example/cooccur_interact_galler_salix.csv',row.names=1)
+# SG_web=read.csv('figure_generation/binary_prior_web_SG.csv',row.names=1)
+# deg_dist_Salix=rowSums(SG_web)/ncol(SG_web)
+# deg_dist_galler=colSums(SG_web)/nrow(SG_web)
+# # Interaction probabilities are the product of plant and galler probabilities
+# sg_int_probs=as.numeric(deg_dist_galler%*%t(deg_dist_Salix))
+# SG_dataset$post.mean<-1
+# SG_dataset$post.sd<-0
+# for(r in 1:nrow(SG_dataset)){
+#   if(SG_dataset$interact[r]==0){
+#     pars=calculate_parameters(sg_int_probs,SG_dataset$cooccur[r],0)
+#     dist=calculate_distribution(pars)
+#     SG_dataset[r,7:8]=dist
+#   }
+# }
+# write.table(SG_dataset,file='../data/Salix_example/Salix_Galler/posterior_probabilities.tsv')
+
+# GP_dataset=read.csv('../data/Salix_example/cooccur_interact_galler_parasit.csv',row.names=1)
+# GP_web=read.csv('figure_generation/binary_prior_web_para_only.csv',row.names=1)
+# deg_dist_galler=rowSums(GP_web)/ncol(GP_web)
+# deg_dist_paras=colSums(GP_web)/nrow(GP_web)
+# # Interaction probabilities are the product of plant and galler probabilities
+# gp_int_probs=as.numeric(deg_dist_paras%*%t(deg_dist_galler))
+# GP_dataset$post.mean<-1
+# GP_dataset$post.sd<-0
+# for(r in 1:nrow(GP_dataset)){
+#   if(GP_dataset$interact[r]==0){
+#     pars=calculate_parameters(gp_int_probs,GP_dataset$cooccur[r],0)
+#     dist=calculate_distribution(pars)
+#     GP_dataset[r,7:8]=dist
+#   }
+# }
+# write.table(GP_dataset,file='../data/Salix_example/Galler_Parasitoid/posterior_probabilities.tsv')
+
+
 #   numpy.random.binomial(n,p,size) draws [size] samples from a binomial distribution
[…]

### 2017-10-20 manuscript/supplemental.tex
galler-parasitoid posterior webs

@@
       network contained 75 realized galler-genotype interactions 
-      out of a potential 104. The R code used to extract this 
+      out of a potential 104. One \emph{S. hookeriana} genotype did
+      not interact with any galles and was removed from the network.
+      The R code used to extract this 
       network follows:
@@
       \hspace{8pt}    \}\}\}
+      \# Remove non-interactive genotype
+      prior\_web<-prior\_web[which(rowSums(prior\_web)\textgreater0),]
       }
@@
       % }
+      % prior_web<-prior_web[which(rowSums(prior_web)>0),]
       % write.csv(prior_web,file='binary_prior_web_SG.csv',quote=F)
@@
 
-            # Now get the degree distributions from the web
-      deg_dist_Salix=rowSums(prior_web)/ncol(prior_web)
-      # Remove one genotype that never interacted
-      deg_dist_Salix<-deg_dist_Salix[which(rowSums(prior_web)>0)]
-      deg_dist_galler=colSums(prior_web)/nrow(prior_web)
-      # Interaction probabilities are the product of plant and galler probabilities
-      int_probs=as.numeric(deg_dist_galler%*%t(deg_dist_Salix))
+      % SG_web=read.csv('binary_prior_web_SG.csv',row.names=1)
+      % GP_web=read.csv('binary_prior_web_para_only.csv',row.names=1)
 
-      deg_dist_parasitoid=rowSums(prior_web_para_only)/ncol(prior_web_para_only)
-      deg_dist_parasitized=colSums(prior_web_para_only)/nrow(prior_web_para_only)
-      gp_int_probs=as.numeric(deg_dist_parasitized%*%t(deg_dist_parasitoid))
+      %       # Now get the degree distributions from the web
+      % deg_dist_Salix=rowSums(SG_web)/ncol(SG_web)
+      % deg_dist_galler=colSums(SG_web)/nrow(SG_web)
+      % # Interaction probabilities are the product of plant and galler probabilities
+      % sg_int_probs=as.numeric(deg_dist_galler%*%t(deg_dist_Salix))
+
+      % deg_dist_parasitoid=rowSums(GP_web)/ncol(GP_web)
+      % deg_dist_parasitized=colSums(GP_web)/nrow(GP_web)
+      % gp_int_probs=as.numeric(deg_dist_parasitized%*%t(deg_dist_parasitoid))
 

### 2017-10-20 code/create_posterior_GP_webs.py

@@ -1,109 +1,0 @@
-import os
-import sys
-import math
-import random
-from decimal import *
-import numpy as np
-import scipy as sp
-
-#   numpy.random.binomial(n,p,size) draws [size] samples from a binomial distribution
-#   % Each observation is a Bernoulli, or a binomial with n=1. Use p=mean(posterior).
-
-def read_in_data(datafile):
-  pdict={}
-  f=open(datafile,'r')
-  for line in f:
-    if line.split()[0]!='"Salix"':
-      if len(line.split())==7:
-        plant=line.split()[1][1:-1]
-        galler=line.split()[2][1:-1]
-        occurs=int(line.split()[3])
-        interacts=int(line.split()[4])
-        postmean=float(line.split()[5])
-        postSD=float(line.split()[6])
-        sppair=(plant,galler)
-        pdict[sppair]=((postmean,postSD))
-      elif len(line.split())==10:
-        plant='.'.join([line.split()[1][1:],line.split()[2],line.split()[3],'?']) # 4 is always '?'
-        galler=line.split()[5][1:-1]
-        occurs=int(line.split()[6])
-        interacts=int(line.split()[7])
-        postmean=float(line.split()[8])
-        postSD=float(line.split()[9])
-        sppair=(plant,galler)
-        pdict[sppair]=((postmean,postSD))
-      elif len(line.split())==9:
-        plant='.'.join([line.split()[1][1:],line.split()[2],line.split()[3][:-1]]) 
-        galler=line.split()[4][1:-1]
-        occurs=int(line.split()[5])
-        interacts=int(line.split()[6])
-        postmean=float(line.split()[7])
-        postSD=float(line.split()[8])
-        sppair=(plant,galler)
-        pdict[sppair]=((postmean,postSD))
-      elif len(line.split())==8:
-        plant='.'.join([line.split()[1][1:],line.split()[2][:-1]]) 
-        galler=line.split()[3][1:-1]
-        occurs=int(line.split()[4])
-        interacts=int(line.split()[5])
-        postmean=float(line.split()[6])
-        postSD=float(line.split()[7])
-        sppair=(plant,galler)
-        pdict[sppair]=((postmean,postSD))        
-      else:
-        print len(line.split())
-  f.close()
-
-  return pdict
-
-
-def posterior_sampling(pdict):
-  random_ints={}
-  for pair in pdict:
-    samples=np.random.binomial(1,pdict[pair][0],10)
[…]

### 2017-10-20 code/figure_generation/posterior_property_plot.py

@@ -39,61 +39,96 @@ def read_summary_file(filename):
   f.close()
   return pointdict
 
-def format_graph(graph):
+def format_graph(graph,prop):
   graph.yaxis.bar.linewidth=1
   graph.xaxis.bar.linewidth=1
   graph.frame.linewidth=1
 
-  graph.world.xmin=0.5
-  graph.world.ymin=0.2
-  graph.world.xmax=0.545
-  graph.world.ymax=0.55
-  graph.yaxis.tick.configure(major=0.1,onoff='on',minor_ticks=1,major_size=.5,place='normal',minor_size=.3,major_linewidth=1,minor_linewidth=1)
-  graph.xaxis.tick.configure(major=0.02,onoff='on',minor_ticks=1,major_size=.5,place='normal',minor_size=.3,major_linewidth=1,minor_linewidth=1)
+  if prop=='C':
+    graph.world.xmin=0.5
+    graph.world.ymin=0.45
+    graph.world.xmax=0.55
+    graph.world.ymax=0.55
+    graph.yaxis.tick.configure(major=0.01,onoff='on',minor_ticks=1,major_size=.5,place='normal',minor_size=.3,major_linewidth=1,minor_linewidth=1)
+    graph.xaxis.tick.configure(major=0.01,onoff='on',minor_ticks=1,major_size=.5,place='normal',minor_size=.3,major_linewidth=1,minor_linewidth=1)
+    xtext="Posterior connectance"
+    ytext="Detected connectance"
+    graph.xaxis.ticklabel.configure(char_size=.75,format='decimal',prec=2)
+    graph.yaxis.ticklabel.configure(char_size=.75,format='decimal',prec=2)
+  elif prop=='LS':
+    graph.world.xmin=33
+    graph.world.ymin=30
+    graph.world.xmax=39
+    graph.world.ymax=36.5
+    graph.yaxis.tick.configure(major=2,onoff='on',minor_ticks=1,major_size=.5,place='normal',minor_size=.3,major_linewidth=1,minor_linewidth=1)
+    graph.xaxis.tick.configure(major=1,onoff='on',minor_ticks=1,major_size=.5,place='normal',minor_size=.3,major_linewidth=1,minor_linewidth=1)
+    xtext="Posterior L/S"
+    ytext="Detected L/S"
+    graph.xaxis.ticklabel.configure(char_size=.75,format='decimal',prec=0)
+    graph.yaxis.ticklabel.configure(char_size=.75,format='decimal',prec=0)
+  else:
[…]

### 2017-10-27 manuscript/CI_interactions.tex
trying to talk about posterior webs

@@
       As well as obtaining posterior means and variances, it is possible to calculate a 95\% credible interval about the posterior mean.
-This is again straightforward to do in R (see the function "credible interval" in \emph{Appendix S2}).
+This is again straightforward to do in R (see the function ``credible interval" in \emph{Appendix S2}).
 Calculating the 95\% credible intervals for species pairs with 0 to 50 observed co-occurrances without any observed interaction (as in Fig.~\ref{Salix_pdfs}), we see that the interval narrows dramatically as the number of observations increases.
@@
       Although the prior distribution of interaction probabilities is narrower and closer to zero for the galler-parasitoid network, the number of samples required to be 95\% confident that the interaction probability is below a threshold still increases quickly; we would need 25 and 101 observed co-occurances with no observed interaction for threshold interaction probabilities of 0.1 and 0.01, respectively.
-      Given the low levels of replication in most network studies, this implies that we should have fairly low confidence in many "non-interacting" pairs of species.
+      Given the low levels of replication in most network studies, this implies that we should have fairly low confidence in many ``non-interacting" pairs of species.
 Even in the extensively replicated \emph{Salix}-galler-parasitoid dataset very few species pairs were observed co-occurring frequently enough to reach these thresholds (only three \emph{Salix}-galler pairs and 31 galler-parasitoid pairs were observed co-occurring frequently enough to reach the threshold for an interaction probability of 0.1, and no pairs were observed co-occurring frequently enough to reach the threshold for an interaction probability of 0.01).
@@
 
+    Using the prior distributions and procedures described above, we calculated posterior probability descriptions for each pair of \emph{Salix} and galler or galler and parasitoid species that were not observed interacting, with each posterior distribution reflecting the number of times the pair of species had been observed co-occurring.
+Using these posterior distributions and assuming probabilities of 1 for pairs of species that were observed interacting, we created a suite of 100 webs of each network type by randomly sampling from each posterior distribution.
+These networks always included the interactions observed in the original network, as well as other interactions which may occur but have not been observed.
+
+    After obtaining these posterior networks, we calculated the connectance of each web, as well as the number of links per resource (\emph{Salix} in the \emph{Salix}-galler networks or galler in the galler-parasitoid networks) and links per consumer.
+To demonstrate how these network metrics will be affected by detection uncertainty, we then created a suite of filtered networks for each posterior network.
+Networks were filtered by randomly sampling 99\%, 95\%, 90\%, 80\%, 70\&, 60\%, and 50\% of the interactions included in each posterior network.
+For level of detection accuracy, we created 100 randomly-sampled network per posterior-probability network.
+We then calculated the same network properties as described above.
+
   % [[What if we have only one site?

### 2017-10-27 manuscript/CI_interactions.tex
spellcheck, all sections now included?

@@
 [[We first illustrate the framework with a simple quantitative example.
-Next, we use the framework to provide analytical criteria for improving the sampling of rare interations.
-Finally, we discuss the implications of uncertainty in the estimation of pairwise interactions on the properties of ecological networks.]] Through these efforts, we demonstrate both the utility of our approach and the importance of acknowledging the uncertainty inherent in ecological networks.
+Next, we use the framework to provide analytical criteria for improving the sampling of rare interactions.
+Finally, we discuss the implications of uncertainty in the estimation of pairwise interactions on the properties of ecological networks.]][[Order has probably changed.]] Through these efforts, we demonstrate both the utility of our approach and the importance of acknowledging the uncertainty inherent in ecological networks.
     % List of sections may not be accurate any more. Update when paper reaches its final form.
@@
 
-THIS SECTIONS BUILDS ON THE SALIX DATA TO ILLUSTRATE THE GAPS THERE ARE IN THE METHOD. DESPITE THE INTENSITY OF THE SAMPLING, THERE ARE SEVERAL HOLES.
+THIS SECTIONS BUILDS ON THE SALIX DATA TO ILLUSTRATE THE GAPS THERE ARE IN THE METHOD.
+DESPITE THE INTENSITY OF THE SAMPLING, THERE ARE SEVERAL HOLES.[[Still necessary?
+If so, we should flesh this out into a paragraph.]]
 
-\section*{A naive qunatification of interaction probability and uncertainty}
+\section*{A naive quantification of interaction probability and uncertainty}
 
@@
 
-  As a start, we will consider how we could naively quantify intetraction probability and its associated uncertainty for an interaction that has not yet been observed.
+  As a start, we will consider how we could naively quantify interaction probability and its associated uncertainty for an interaction that has not yet been observed.
 We consider that a pair of species have been observed $n$ times co-occurring at one location, and the number of times they have been observed interacting is $k = 0$.
@@
 X how the estimate of $\lambda$ could vary with sampling size using the Clopper-Pearson interval.
-It shows that the 95\% confidence interval requires a signifcant amount of sampling in order to be sure that species are not interacting.
+It shows that the 95\% confidence interval requires a significant amount of sampling in order to be sure that species are not interacting.
   % Is the Clopper-Pearson interval the one in Dom's code snippets? If so, this is Fig.~\ref{Salix_cdfs}
@@
 
-  What does this question mean exactly? We consider that there are three nested levels of uncertainty making the occurance of any interaction a stochastic process:
+  What does this question mean exactly? We consider that there are three nested levels of uncertainty making the occurrence of any interaction a stochastic process:
 
@@
 $L=1$, but that it does not occur at a given location or moment in time because there are local constraints preventing it from occurring.
-We define the realization of the interaction process $X$ given that the interaction is feasible as a stochastic process with associated probability $P(X|L)=\chi$.
+We define the realisation of the interaction process $X$ given that the interaction is feasible as a stochastic process with associated probability $P(X|L)=\chi$.
 This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology about the contingencies of interactions~\citep{}.
-We imagine for instance that an interaction between a gall and a parasitoid might not be recorded at a location because it was the wrong time of the year and the gall had not yet formed (phenological constraints), a late frost killed the larvae (an abiotic environmental constraint), another parasitoid species competitively excluded the parasitoid species of interst (a biotic environmental constraint) or simply the parasitoid is too rare to interact with all of its viable hosts (an abundance constraint).
+We imagine for instance that an interaction between a gall and a parasitoid might not be recorded at a location because it was the wrong time of the year and the gall had not yet formed (phenological constraints), a late frost killed the larvae (an abiotic environmental constraint), another parasitoid species competitively excluded the parasitoid species of interest (a biotic environmental constraint) or simply the parasitoid is too rare to interact with all of its viable hosts (an abundance constraint).
 
@@
 Detection failure could happen for several reasons, for instance if the rearing of a parasitoid fails with inappropriate lab conditions or because of species mis-identification.
-Some sources of detection error could be minimized with appropriate sampling effort ($\delta$ will converge to one with increasing number of collected galls), but other sources are often difficult to reduce (e.g.
+Some sources of detection error could be minimised with appropriate sampling effort ($\delta$ will converge to one with increasing number of collected galls), but other sources are often difficult to reduce (e.g.
 the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification).
@@
 How then may we refine our sampling approaches to reduce uncertainties, and to gain insights into the impact of multiple processes on field observations?
-Importantly, some sources can be minimized with appropriate sampling design and efforts, while other sources are difficult or impossible to reduce – since they are generated by chance variation created by the very process in which we are interested.
+Importantly, some sources can be minimised with appropriate sampling design and efforts, while other sources are difficult or impossible to reduce – since they are generated by chance variation created by the very process in which we are interested.
 
   The basic information that we are collecting consists of matrices of interaction partners.
-Our count of interactions between species A and species B reflects uncertainty with respect to whether two species interact when co-occurring at a given site, chance variation in whether the interaction is realized, and uncertainty with respect to whether it is detected when realized.
+Our count of interactions between species A and species B reflects uncertainty with respect to whether two species interact when co-occurring at a given site, chance variation in whether the interaction is realised, and uncertainty with respect to whether it is detected when realised.
 In this case, what can we do to pin down any of these different types of variation?
@@
     \caption{\textbf{A-B)} Most pairs of \emph{Salix} and galler or galler and parasitoid species were never observed co-occurring despite the high levels of replication in our example dataset.
-For those that were observed together at least once, the number of observed co-occurances was generally small (\textless10).
+For those that were observed together at least once, the number of observed co-occurrences was generally small (\textless10).
 Here we show a histogram of the number of pairs of species observed co-occurring at least once.
@@
 Here we show a histogram of the number of observed interactions within pairs of co-occurring species.
-\textbf{E-F)} Here we show, for each species pair, the number of observed interactions plotted against the number of observed co-occurances.
+\textbf{E-F)} Here we show, for each species pair, the number of observed interactions plotted against the number of observed co-occurrences.
 Most pairs either are never observed interacting or interact almost every time they co-occur.
-The red, dashed line indicates a 1:1 relationship between interactions and co-occurances.}
+The red, dashed line indicates a 1:1 relationship between interactions and co-occurrences.}
     \label{histograms}
@@
 An interaction not observed on day $t$ may have gone undetected either because there were constraints on the process (i.e.
-the probability $\lambda$ was really zero) or because of chance variation in the realized incidence of an event associated with a finite probability.
+the probability $\lambda$ was really zero) or because of chance variation in the realised incidence of an event associated with a finite probability.
 Most importantly, if two species are never observed co-occurring during several days of sampling then we have learned nothing about their probability of interacting if they should ever co-occur.
-In other words, there is no information without co-occurance.
+In other words, there is no information without co-occurrence.
 
@@
 to glean information regarding at how many sites the species are found interacting across the entire dataset), and assuming that most of this pattern is due to variation in detection rate, then insights into the incidence of interactions between species may be gleaned from the accumulation rate of positive interactions at sites were interaction is possible (i.e.
-with at least one observation of a positive interaction) [this reasoning to be further formalized]
+with at least one observation of a positive interaction) [this reasoning to be further formalised]
 
@@
       \begin{equation}
-        \underbrace{P(\theta|X,n)}_{Posterior} = \frac{\overbrace{P(X|\theta,n)}^{Likelihood}\overbrace{P(\theta)}^{Prior}}{\underbrace{P(X|N)}_{Normalizer}} .
+        \underbrace{P(\theta|X,n)}_{Posterior} = \frac{\overbrace{P(X|\theta,n)}^{Likelihood}\overbrace{P(\theta)}^{Prior}}{\underbrace{P(X|N)}_{Normaliser}} .
         \label{posterior}
@@
 
-     In some cases it can be complicated to compute the normalizer, but fortunately in our case an analytical solution exists.
+     In some cases it can be complicated to compute the normaliser, but fortunately in our case an analytical solution exists.
 The beta-binomial distribution is a conjugate distribution of the binomial distribution.
@@
         \caption{Using prior distribution based on the \emph{Salix}-galler and galler-parasitoid networks in~\citet{Barbour2016}, we can calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting.
-Here we show posterior distributions for each $\lambda$ in each network ranging from the prior distribution (N=0 observed co-occurances) to the distribution obtained when the pair of species has been observed co-occurring 100 times.
+Here we show posterior distributions for each $\lambda$ in each network ranging from the prior distribution (N=0 observed co-occurrence) to the distribution obtained when the pair of species has been observed co-occurring 100 times.
 The distribution narrows and approaches zero as the sample size increases.
@@
         \end{figure}
-        [[Maybe I was using the int_probs from the other example?]]
 
@@
 
-          In absence of any external information, an uniformative prior is the most conservative hypothesis for the distribution of $\theta$.
+          In absence of any external information, an uninformative prior is the most conservative hypothesis for the distribution of $\theta$.
 The beta distribution is in this case a uniform distribution  for $Beta(\alpha=1,\beta=1)$.
@@
 The degree distribution of a network is then the probability distribution of these degrees over the whole network.
-Connectance is an average property for a complete given network, and it represents the expected degree (expected number of interactions per species) standardized by the number of species in the network.
-The standardized degree could therefore be interpreted as an interaction probability.
+Connectance is an average property for a complete given network, and it represents the expected degree (expected number of interactions per species) standardised by the number of species in the network.
+The standardised degree could therefore be interpreted as an interaction probability.
 It is consequently possible to use the degree distribution to inform the prior distribution.
@@
 The degree of a node is defined as the number of interactions it has with other nodes.
-Connectance, as the average number of links per species in the whole network, is thus also the expected degree for any given species normalized by the number of species in the network.
-Using normalized degrees $\Delta_i$ and $\Delta_j$ (i.e., degrees divided by the number of species in the network), we can obtain the probability of interaction $L_ij$=$\Delta_i\times\Delta_j$.
+Connectance, as the average number of links per species in the whole network, is thus also the expected degree for any given species normalised by the number of species in the network.
+Using normalised degrees $\Delta_i$ and $\Delta_j$ (i.e., degrees divided by the number of species in the network), we can obtain the probability of interaction $L_ij$=$\Delta_i\times\Delta_j$.
 The distribution of these interaction probabilities derived from a similar network or a suite of networks can be used to establish a prior distribution before any data from the focal network are collected.
@@
           It is possible to estimate the probability of interaction between a pair of species if there is knowledge of their traits and some functions relating trait matching to interaction probability~\citep{Morales-Castilla2015}.
-There are several techniques available to perform this inferrence of interaction probability~\citep{} (REFS).
+There are several techniques available to perform this inference of interaction probability~\citep{} (REFS).
 Note that in this case the prior might not be beta distribution and numerical methods might be required to compute the posterior distribution.
@@
 maybe we should rephrase this to predict the degree of species $i$ based on the degrees of 10 other species in the network?
-  The Bayesian framework can be illustrated with a simple quantiative example.
+  The Bayesian framework can be illustrated with a simple quantitative example.
 Suppose we have $n = 10$ observations of co-occurrence between species $i$ and species $j$ in a given time interval and area, and $X = 3$ observations of interactions.
@@
   % We should probabaly have a value  on the interaction probablitity that differs from the average of the degree distrbution
-   Now consider we know that species $i$ is known to interact with 10 other species, which have the following normalized degrees:
+   Now consider we know that species $i$ is known to interact with 10 other species, which have the following normalised degrees:
 
@@
 
-    If the network has 20 species total, then species $i$ has a normalized degree of 0.5 and
+    If the network has 20 species total, then species $i$ has a normalised degree of 0.5 and
     we can use this to obtain the following set of interaction probabilities for species $i$ and each of its interaction partners:
@@
 
-    It is fairly straigthforward to compute most of network metrics when the different $\lambda$ of the adjacency matrix are known, without variance~\citep{Poisot2016}.
+    It is fairly straightforward to compute most of network metrics when the different $\lambda$ of the adjacency matrix are known, without variance~\citep{Poisot2016}.
 Several of these metrics derive directly from quantitative indices of network structure which are equivalent to $\lambda$; the remainder, originally defined for binary networks, can be adjusted to account for interaction probabilities between zero and one.
@@
 Computation of these metrics involves non-linear functions and therefore, because of Jensen's inequality (which states that the average of non-linear function of a stochastic variable differs from the function of the average of that variable), any uncertainty in $\lambda$s could bias both the mean and variance of a network metric.
-For instance, assume that among all pairs of species with few observed co-occurances there are many pairs which truly interact.
+For instance, assume that among all pairs of species with few observed co-occurrence there are many pairs which truly interact.
 If we begin with no observed links for these pairs, then correcting for these false absences will inflate the number of links and consequently influence metrics such as connectance, nestedness, and degree distribution.
@@
 We estimated frequencies of  \emph{S.
-hookeriana} genotype-galler interactions based on the normalized degree of each species in each network component (see \emph{Appendix S1} for details and code).
+hookeriana} genotype-galler interactions based on the normalised degree of each species in each network component (see \emph{Appendix S1} for details and code).
 
@@
 For the galler-parasitoid component of the network, the corresponding prior parameters are $\alpha$=1.341479, $\beta$=9.487966.
-      We are then able to use these priors to estimate the posterior distriution of interaction probabilities given the additional information in our dataset.
+      We are then able to use these priors to estimate the posterior distribution of interaction probabilities given the additional information in our dataset.
 
@@
 
-      For species where no co-occurances were observed, we can 
+      For species where no co-occurrence were observed, we can 
       calculate the MLE estimates for the mean and variance of 
@@
       interaction probability based on the degree distributions of Salix genotypes and gallers was 0.562 and that for gallers and parasitoids was 0.122.
-[[What's the connectance of our dataset, if we call greys 0?]] This probability does, however, seem rather high for our dataset.
+These probabilities are much higher than those in our dataset (0.028 and 0.078 for the \emph{Salix}-galler and galler-parasitoid networks, respectively).
 This discrepancy may reflect the differences in scale between a network containing different genotypes of a single \emph{Salix} species and four gallers from a single family and a network containing many \emph{Salix} species and gallers from many families as is the case in our dataset.
 
-      For a pair of species where some co-occurances were observed, we can update the prior distribution with these data.
+      For a pair of species where some co-occurrence were observed, we can update the prior distribution with these data.
 If we consider only pairs of species which were observed to co-occur but not to interact, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs.
@@
 In most cases, however, species $i$ and $j$ did not co-occur at so many sites and our posterior mean and variance retain some influence of the prior.
-Nevertheless, as the number of observed co-occurances increases, the posterior mean becomes closer to zero and the posterior variance decreases (Fig.~\ref{Salix_pdfs}).
+Nevertheless, as the number of observed co-occurrence increases, the posterior mean becomes closer to zero and the posterior variance decreases (Fig.~\ref{Salix_pdfs}).
 
@@
 This is again straightforward to do in R (see the function ``credible interval" in \emph{Appendix S2}).
-Calculating the 95\% credible intervals for species pairs with 0 to 50 observed co-occurrances without any observed interaction (as in Fig.~\ref{Salix_pdfs}), we see that the interval narrows dramatically as the number of observations increases.
+Calculating the 95\% credible intervals for species pairs with 0 to 50 observed co-occurrences without any observed interaction (as in Fig.~\ref{Salix_pdfs}), we see that the interval narrows dramatically as the number of observations increases.
 In no case, however, does the confidence interval include 0.
@@
 The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact.
-If we want to be 95\% confident that the interaction probability for two species in the \emph{Salix}-galler network is below 0.5, 0.1, or 0.01, we would need six, 51, and 101 observed co-occurrances with no observed interaction (Fig.~\ref{Salix_cdfs}; see function samples\_required in~\emph{Appendix S2}).
-      Although the prior distribution of interaction probabilities is narrower and closer to zero for the galler-parasitoid network, the number of samples required to be 95\% confident that the interaction probability is below a threshold still increases quickly; we would need 25 and 101 observed co-occurances with no observed interaction for threshold interaction probabilities of 0.1 and 0.01, respectively.
+If we want to be 95\% confident that the interaction probability for two species in the \emph{Salix}-galler network is below 0.5, 0.1, or 0.01, we would need six, 51, and 101 observed co-occurrences with no observed interaction (Fig.~\ref{Salix_cdfs}; see function samples\_required in~\emph{Appendix S2}).
+      Although the prior distribution of interaction probabilities is narrower and closer to zero for the galler-parasitoid network, the number of samples required to be 95\% confident that the interaction probability is below a threshold still increases quickly; we would need 25 and 101 observed co-occurrence with no observed interaction for threshold interaction probabilities of 0.1 and 0.01, respectively.
       Given the low levels of replication in most network studies, this implies that we should have fairly low confidence in many ``non-interacting" pairs of species.
@@
         \caption{The number of samples required to achieve a given level of confidence that an interaction probability is below a given threshold varies with both parameters.
-With a low threshold, our confidence that $\omega_{ij}$ is below the threshold increases rapidly with repeated observation of co-occurance without interaction.
-Here we show the cumulartive density functions for thresholds probabilities of 0.5 (solid line), 0.25 (dashed line), 0.1 (dash-dot line), and 0.05 (dotted line) as well as the points at which the cdf reaches 0.90 (orange square), 0.95 (red circle), and 0.975 (blue diamond) for each threshold value.
+With a low threshold, our confidence that $\omega_{ij}$ is below the threshold increases rapidly with repeated observation of co-occurrence without interaction.
+Here we show the cumulative density functions for thresholds probabilities of 0.5 (solid line), 0.25 (dashed line), 0.1 (dash-dot line), and 0.05 (dotted line) as well as the points at which the cdf reaches 0.90 (orange square), 0.95 (red circle), and 0.975 (blue diamond) for each threshold value.
 The large ticks along the x-axis indicate the number of samples associated with each of these points.
@@
 
+    Note that the posterior webs for the Salix-galler network all had much higher connectance than the original, observed web (C=0.028 for the observed web, Fig.~\ref{posterior_webs}).
+Likewise, the number of links per \emph{Salix} and galler species in the observed web (2.71 and 1.47, respectively) were much lower than those predicted in the posterior webs, even when filtering with a detection probability of only 50\%.
+There are two possible explanations for this discrepancy: either the~\citet{Barbour2016} data do no give an appropriate prior for our dataset, or the true detection probability for links between \emph{Salix} and galler species is much less than 50\%.
+As the scale of the two datasets is quite different (genotypes of a single \emph{Salix} species in~\citet{Barbour2016}, various \emph{Salix} species in our dataset), we suspect the former is more likely.
+
+    Considering the galler-parasitoid networks, the connectance, mean links per galler, and mean links per parasitoid (0.078, 9.99, and 7.45, respectively) are similar to those in the posterior webs with a detection filter of 50\% (Fig.~\ref{posterior_webs}).
+The~\citet{Barbour2016} network likely provides a better prior here than for the \emph{Salix}-galler networks, as both networks included different galler and parasitoid species.
+Although the two networks differ vastly in scale, and the inclusion of multiple \emph{Salix} species likely causes structural differences from~\citet{Barbour2016} despite the similar resolution of gallers and parasitoids, this result nevertheless suggests that even such a large and well-replicated network is missing a large proportion of interactions.
+This should be a strong warning to researchers comparing structural characteristics between networks - small structural differences are very likely to be completely masked by structural changes that would result if missing interactions were included.
+
+    \begin{figure}[h]
+    \label{posterior_webs}
+    \caption{Here we show the mean connectance, links per resource (\emph{Salix} in the \emph{Salix}-galler networks and gallers in the galler-parasitoid networks), and links per consumer (gallers in the \emph{Salix}-galler networks and parasitoids in the galler-parasitoid networks) for networks assembled using posterior distributions based on~\citet{Barbour2016,Barbour2016Dryad}.
+We created 100 "posterior-sampling" networks and then, for each of these, created 100 "detection-filter" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network.
+This simulates imperfect detection of interactions in the field.
+Each point represents the mean network property (e.g., connectance) obtained from a set of 100 detection-filter networks, plotted against the value of the network property in the posterior-sampling network used to create the detection-filter networks.
+For each property and both network types, the posterior-sampling networks cover a relatively small range of network properties and the value of each property decreases with the proportion of links included in the detection-filter networks.}
+    \includegraphics*{}
+
   % [[What if we have only one site?

### 2017-10-27 manuscript/supplemental.tex
spellcheck, all sections now included?

@@
       on any branch of genotype $j$ and 0 otherwise. In total, this 
-      network contained 75 realized galler-genotype interactions 
+      network contained 75 realised galler-genotype interactions 
       out of a potential 104. One \emph{S. hookeriana} genotype did
-      not interact with any galles and was removed from the network.
+      not interact with any gallers and was removed from the network.
       The R code used to extract this 
@@
       probability of each interaction as the product of the 
-      normalized degrees of the two species. For example, the 
+      normalised degrees of the two species. For example, the 
       probability of an interaction between two species with 
-      normalized degrees of 0.5 (each interacts with half of the 
+      normalised degrees of 0.5 (each interacts with half of the 
       available partners) is 0.25. R code used to do this follows:

### 2017-10-27 code/figure_generation/posterior_property_plot.py

@@ -19,6 +19,7 @@ from PyGrace.Extensions.colorbar import SolidRectangle, ColorBar
 from PyGrace.Styles.el import ElGraph, ElLinColorBar, ElLogColorBar
 
 colors=ColorBrewerScheme('Blues')  # The blue is very beautiful but maybe harder to see.
+colors.add_color(130,20,20,'red')
 # colors.add_color(120,120,120,'grey')
 
 def read_summary_file(filename):
@@ -49,31 +50,33 @@ def format_graph(graph,prop,nettype):
       graph.world.xmin=0.52
       graph.world.ymin=0.20
       graph.world.xmax=0.575
-      graph.world.ymax=0.60
+      graph.world.ymax=0.600000000001
+      graph.yaxis.tick.configure(major=0.1,onoff='on',minor_ticks=1,major_size=.5,place='normal',minor_size=.3,major_linewidth=1,minor_linewidth=1)
+      graph.yaxis.ticklabel.configure(char_size=.75,format='decimal',prec=1)
     else:
       graph.world.xmin=0.18
       graph.world.ymin=0.075
       graph.world.xmax=0.20
       graph.world.ymax=0.20
-    graph.yaxis.tick.configure(major=0.05,onoff='on',minor_ticks=1,major_size=.5,place='normal',minor_size=.3,major_linewidth=1,minor_linewidth=1)
+      graph.yaxis.tick.configure(major=0.05,onoff='on',minor_ticks=1,major_size=.5,place='normal',minor_size=.3,major_linewidth=1,minor_linewidth=1)
+      graph.yaxis.ticklabel.configure(char_size=.75,format='decimal',prec=2)
     graph.xaxis.tick.configure(major=0.01,onoff='on',minor_ticks=1,major_size=.5,place='normal',minor_size=.3,major_linewidth=1,minor_linewidth=1)
     xtext="Posterior Connectance (C)"
     ytext="Detected C"
     graph.xaxis.ticklabel.configure(char_size=.75,format='decimal',prec=2)
-    graph.yaxis.ticklabel.configure(char_size=.75,format='decimal',prec=2)
   elif prop=='LS':
     if nettype=='SG':
       graph.world.xmin=27
       graph.world.ymin=12
       graph.world.xmax=30
-      graph.world.ymax=31
+      graph.world.ymax=32
[…]

### 2017-10-27 manuscript/supplemental.tex
fixed some compiling errors, supplemental still isn't perfect

@@
 
-      \vspace{12pt}
+      \vspace{6pt}
       \emph{
@@
       \# Remove non-interactive genotype
-      prior\_web<-prior\_web[which(rowSums(prior\_web)\textgreater0),]
+      prior\_web\textless-prior\_web[which(rowSums(prior\_web)\textgreater0),]
       }
@@
 
+      \vspace{6pt}
+
       To extract the galler-parsitoid network from the same study above:
 
-      \vspace{12pt}
-      \emph{
-      \noindent \hspace{-4pt} 
-      prior\_web\_data=read.csv('tree\_level\_interaxn\_all\_plants\_traits\_size.csv')\\
-      prior\_web\_data <- prior\_web\_data[,8:26]
+      \vspace{6pt}
+      \noindent \emph{
+      \hspace{-4pt} prior\_web\_data=read.csv(``tree\_level\_interaxn\_all\_plants\_traits\_size.csv")\\
+      prior\_web\_data \textless- prior\_web\_data[,8:26]\\
 
-      \# Build a web with interactions=1 for any parasitoid on any galler
-      prior\_web=data.frame()
+      \# Build a web with interactions=1 for any parasitoid on any galler\\
+      prior\_web=data.frame()\\
 
-      \# each column contains all interactions for a particular parasitoid-galler combination
-      for(column in 1:ncol(prior\_web\_data)){
-      \hspace{-4pt}   \# the column name gives the species which makes the gall, followed by the species emerging from the gall
-      \hspace{-4pt}   galler\_emerged=strsplit(colnames(prior\_web\_data)[column], "\_")
-      \hspace{-4pt}   galler = galler\_emerged[[1]][1]
-      \hspace{-4pt}   emerged = galler\_emerged[[1]][2]
+      \# each column contains all interactions for a particular parasitoid-galler combination\\
+      for(column in 1:ncol(prior\_web\_data))\{\\
+      \hspace{-4pt}   \# the column name gives the species which makes the gall, followed by the species emerging from the gall\\
+      \hspace{-4pt}   galler\_emerged=strsplit(colnames(prior\_web\_data)[column], "\_")\\
+      \hspace{-4pt}   galler = galler\_emerged[[1]][1]\\
+      \hspace{-4pt}   emerged = galler\_emerged[[1]][2]\\
 
-      \hspace{-4pt}   \# the strength of the interaction is the sum of the column (number of galls across all branches sampled)
-      \hspace{-4pt}   linkstrength = sum(prior\_web_data[,column])
-      \hspace{-4pt}   prior\_web[as.character(galler),as.character(emerged)] <- linkstrength
-      }
-
-      \# Make the naS into 0
-      prior\_web[is.na(prior\_web)] <- 0
-
-      \# remove emerging gallers with no parasitoids
-      prior\_web\_para\_only <- prior\_web[,c(2:6,8:9,12)]
-
-      \# convert interaction strengths to 1
-      prior\_web[which(prior\_web>0)] <- 1
-
-      write.csv(prior\_web\_para\_only, file="prior\_web\_para\_only.csv", quote=F)
-      }
+      \hspace{-4pt}   \# the strength of the interaction is the sum of the column (number of galls across all branches sampled)\\
+      \hspace{-4pt}   linkstrength = sum(prior\_web\_data[,column])\\
+      \hspace{-4pt}   prior\_web[as.character(galler),as.character(emerged)] \textless- linkstrength\\
+      \} 
+      \# Make the NAs into 0\\
+      prior\_web[is.na(prior\_web)] \textless- 0\\
+      \# remove emerging gallers with no parasitoids\\
+      prior\_web\_para\_only \textless- prior\_web[,c(2:6,8:9,12)]\\
+      \# convert interaction strengths to 1\\
+      prior\_web[which(prior\_web\textgreater0)] \textless- 1\\
+      write.csv(prior\_web\_para\_only, file=``prior\_web\_para\_only.csv", quote=F)
+      }\par
 

### 2017-11-15 manuscript/CI_interactions.tex
fixed some compiling errors, supplemental still isn't perfect
added Tomas' comments

@@
     % Present Salix data with holes as an example of uncertainty in data. Focus just on the white and grey, ignore uncertainty in the blacks
+    In modern community ecology, species assemblages are increasingly described and analyzed as networks~\citep{Thompson2012,RecentReviews}.
+Such representations offer convenient summaries of how communities are constructed since they simultaneously account for species composition and their interactions.
+Species are represented as nodes, hence a tabulation of the nodes present and of their relative abundances form the basis for traditional metrics of community composition.
+On top of this information, interactions are represented by links, so that networks provide additional, higher-order information on community structure.
+Metrics of how networks are structured at the level of links emerging from individual species (such as link density, vulnerability and degree distribution), and of network-level structure (such as nestedness, connectance and modularity), then offer key descriptors of how species interactions are structured across the globe~\citep{Schleuning2012,Morris2014,XX}, valuable proxies of community dynamics~\citep{Thebault2010,XX} and [many other nice things].
+Thus, deriving robust descriptors of network properties is a key objective for modern community ecology.
 
-    Ecological networks-- which include antagonistic food webs and host-parasite networks as well as plant-pollinator and plant-frugivore mutualist networks --are usually considered to be static representations of the communities and interactions they describe.
-That is, whether the network is assembled based on aggregated data, a single intensive "snapshot" sample, or expert knowledge, interactions are assumed to occur at constant frequencies~\citep{Olesen2011a}.
+    Importantly, empirical descriptions of ecological networks are usually considered to be static representations of the communities and interactions they describe.
+That is, whether the network is assembled based on aggregated data, a single intensive "snapshot" sample, or expert knowledge, interactions are assumed to occur at the same frequencies wherever and whenever the network is observed~\citep{Olesen2011a}.
 This assumption conflicts with known variation in interactions over time~\citep{Kitching1987,Olesen2011a} and space~\citep{Kitching1987,Baiser2012} and between individuals of a given species~\citep{Pires2011a,Fodrie2015,Novak2015}.
@@
 Interactions can also be lost, however, if participating species remain present but do not co-occur temporally or are too rare to detect each other~\citep{Tylianakis2010}, or through changes to individual preferences~\citep{Fodrie2015}.
-Several researchers have pointed to the importance of sampling intensity for the assessment of network structure (e.g.,~\citealp{Martinez1999,Bluthgen2006,XX}).
-Despite this, the acknowledgement that insufficient sampling effort limits our ability to describe variation in ecological networks has not yet led to a quantitative framework to deal with the uncertainty of ecological interactions and of sampling.
 
-    The main objective of this study is to develop analytical tools that could be used to better represent the uncertainty in the estimation of pairwise interaction probability.
-We start with the description of a new Bayesian approach to estimate ecological interactions and of a related R package.
-[[We first illustrate the framework with a simple quantitative example.
+    Beyond "true" variation in network structure, several researchers have pointed to the importance of sampling intensity for the assessment of network structure (e.g.,~\citealp{Martinez1999,Bluthgen2006,XX}).
+Despite this, the acknowledgement that insufficient sampling effort limits our ability to describe variation in ecological networks has not yet led to a quantitative framework to deal with the uncertainty generated by spatiotemporal variation in ecological interactions and by sampling.
+
+    In this study, we develop analytical tools to capture the uncertainty in the estimation of pairwise interaction probability.
+To define the problem, we first discuss the pervasive implications of uncertainty in the estimation of pairwise interactions on the properties of ecological networks.
+We then define a framework which identifies and dissects the different contributions to uncertainty of interaction.
+We illustrate this framework with a simple quantitative example.
 Next, we use the framework to provide analytical criteria for improving the sampling of rare interactions.
-Finally, we discuss the implications of uncertainty in the estimation of pairwise interactions on the properties of ecological networks.]][[Order has probably changed.]] Through these efforts, we demonstrate both the utility of our approach and the importance of acknowledging the uncertainty inherent in ecological networks.
+Finally, we offer tangible recommendations for improved descriptors of ecological interactions.
+Through these efforts, we demonstrate both the utility of our approach and the importance of acknowledging the uncertainty inherent in ecological networks.
     % List of sections may not be accurate any more. Update when paper reaches its final form.
 
-\section*{Different uncertainties in computing a network}
+\section*{Why do some interactions \emph{not} occur?}
 
-THIS SECTIONS BUILDS ON THE SALIX DATA TO ILLUSTRATE THE GAPS THERE ARE IN THE METHOD.
-DESPITE THE INTENSITY OF THE SAMPLING, THERE ARE SEVERAL HOLES.[[Still necessary?
-If so, we should flesh this out into a paragraph.]]
-
-\section*{A naive quantification of interaction probability and uncertainty}
-
-  It is getting more and more common to represent interactions as probabilities in theoretical models of network structure.
-For example, the minimum potential model introduces gaps in the feeding niche of predators by sampling based on the likelihood of each interaction~\citep{Allesina2008}, while a gaussian probability function is used to represent the niche by~\citet{Williams2010}.
-\citet{Eklof2013} also introduced variability  in the computation of network dimensions, allowing the absence of interactions within the n-dimension niche of every species.
-Empirical investigation of trait-matching constraints often consider the occurrence of interactions as binomial process (e.g.,~\citealp{Rohr2016}).
-There are also ways to perform analysis of probabilistic networks, with almost all metrics having a probabilistic version~\citep{Poisot2016}.
-But there is not yet consensus on what an interaction probability between a pair of species means, and this is definitely a problem when comes time to estimate the uncertainty of both pairwise interactions and entire networks.
-
-  As a start, we will consider how we could naively quantify interaction probability and its associated uncertainty for an interaction that has not yet been observed.
-We consider that a pair of species have been observed $n$ times co-occurring at one location, and the number of times they have been observed interacting is $k = 0$.
-We aim to evaluate the uncertainty of this interaction.
-The occurrence of an interaction is a Bernoulli trial.
-Consequently, the number of success $k$ over $n$ trials will follow a binomial distribution:
-
-      \begin{equation}
-        X \sim Bin(n,\lambda) ,
-      \end{equation}
-
-      \noindent and
-
-      \begin{equation}
-         P(X = k|\lambda,n) = {n \choose k}\lambda^k(1-\lambda)^{n-k} . 
-         \label{likelihood}
-      \end{equation}
-
-  \noindent The parameter $\lambda$, the probability of observing an interaction over an infinite time interval and area, is the quantity we want to estimate from empirical data. 
-  The maximal likelihood estimate (MLE) of $\lambda$ is straightforward to find given $k$ and $n$. It is simply equal to:
-
-      \begin{equation}
-        \theta_{MLE} = \frac{k}{n}  .
-        \label{theta_MLE}
-      \end{equation}
-
-  The variance of a Bernoulli experiment is simply $n\lambda$(1-$\lambda$).
-It is important to remember this variance reports the variability of the number of success $k$ for $n$ trials and is not the variance associated with the estimation of $\lambda$.
-  Given this variance, it is possible to compute the confidence interval for the MLE of $\lambda$ using any of several methods, including the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull Interval}.
-Finding this estimate is therefore quite straightforward, but it nonetheless has two drawbacks.
-First, $\lambda$ is a random variable with a given uncertainty and whose distribution is unknown, it is not a single point estimate.
-This means that even if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact.
-It means that no interaction is the most likely situation but there is nonetheless a significant chance that the two species could interaction.
-In contrast with the situation where $k>0$, when we are sure that an interaction is feasible,
-  % (in which case, the ratio $k/n$ is smaller than $n$ because of detection and process uncertainty),  % This parenthetical makes the sentence very long. Is it necessary?
-  we are not sure that absence of interactions is caused by $L=0$.
-Second, and most importantly, the number of trials $n$ might be very low in many instances (and some pairs of species might even not be documented once).
-Consequently, the uncertainty in the estimation of $\lambda$ might be considerable.
-We illustrated in Fig.
-X how the estimate of $\lambda$ could vary with sampling size using the Clopper-Pearson interval.
-It shows that the 95\% confidence interval requires a significant amount of sampling in order to be sure that species are not interacting.
-  % Is the Clopper-Pearson interval the one in Dom's code snippets? If so, this is Fig.~\ref{Salix_cdfs}
-
-  The situation where $k = 0$ is also problematic because we have very little information with which to estimate $\lambda$, in particular when $n$ is also small.
-We therefore propose a Bayesian approach to solve this problem, building on two relevant features of such statistics : posterior distribution of parameter estimates and usage of prior information.
-Before moving to this direction, we will first take time to better describe what is exactly meant by an interaction probability and appropriately define sources of uncertainty.
-
-  So many sources of interaction pooled into a single entity; hard to estimate.
-
-  MLE is zero if no interactions detected, but there may still be a substantial probability of interaction should the two species co-occur.
-[This is particularly important in the context of a changing world, where species not co-occurring today – or species not detected co-occurring today – may well do so tomorrow, forming complex interactions.]
-
-\section*{Why do some interactions not occur?}
-
-  What does this question mean exactly? We consider that there are three nested levels of uncertainty making the occurrence of any interaction a stochastic process:
+  To define the problem associated with describing ecological interaction networks, we will start from the perspective of an empirical community ecologist faced with the task of describing an interaction networks.
+This ecologist will be interested in generating a description of the blocks present, and the links between them (Roslin and Majaneva 2017).
+In other words, he or she seeks to fill in a matrix of species by species interactions.
+Importantly, the information sought is as much in the presence of given links as in the absence of others.
+An observed link will always remain an observed link, but to why given links are not observed, there may be multiple contributions.
+Thus, we will set off by contemplating what factors may contribute to links missing from the matrix.
+We consider that there are three nested levels of uncertainty making the occurrence of any interaction a stochastic process:
 
@@
 traits) about the constraints on the interaction.
-In other words, with sufficient sampling and all information accessible, this interaction probability should either tend to 0 or to 1 and the uncertainty vanish.
+In other words, with sufficient sampling and all information accessible, this interaction probability should either tend to 0 or to 1 and the uncertainty vanishes.
 
@@
 This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology about the contingencies of interactions~\citep{}.
-We imagine for instance that an interaction between a gall and a parasitoid might not be recorded at a location because it was the wrong time of the year and the gall had not yet formed (phenological constraints), a late frost killed the larvae (an abiotic environmental constraint), another parasitoid species competitively excluded the parasitoid species of interest (a biotic environmental constraint) or simply the parasitoid is too rare to interact with all of its viable hosts (an abundance constraint).
+    % We imagine for instance that an interaction between a gall and a parasitoid might not be recorded at a location because it was the wrong time of the year and the gall had not yet formed (phenological constraints), a late frost killed the larvae (an abiotic environmental constraint), another parasitoid species competitively excluded the parasitoid species of interest (a biotic environmental constraint) or simply the parasitoid is too rare to interact with all of its viable hosts (an abundance constraint).
 
@@
 
-    \subsection*{What is an observation of "no interaction"?}
+    % \subsection*{What is an observation of "no interaction"?}
 
@@
 the true $\lambda$= 0).
-Given no added detection error in observing the incidence of the interaction, then a single observation of species co-occurrence will reveal (very) little regarding the probability of the interaction – the confidence limits for one observation essentially spans from 0 to 1 (see following section).
+Given no added detection error in observing the incidence of the interaction, then a single observation of species co-occurrence will reveal (very) little regarding the probability of the interaction – the confidence limits for one observation essentially spans from 0 to 1 (Fig.~\ref{upper_limits}).
 For 5 observations, this confidence limit will still extends to 0.5.
@@
     \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
-  \end{figure}
-
-  The pattern of Fig.~\ref{upper_limits} should be compared to the frequency of co-occurrence of taxa in the Salix-galler data set.
-Here, most (3986 out of 4992) pairs of species are never found co-occurring, and for species found co-occurring the number of co-occurrences was generally low (Fig.~\ref{histograms}A).
-Among the species which did sometimes interact when co-occurring, the incidence of interaction was actually low.
-Only 141 pairs of species were observed interacting: of these, 26 were observed interacting only once and 48.2\% were observed interacting five or fewer times (Fig.~\ref{histograms}B).
-Thus, even in the most extensive data set that we could think of, limited sampling is clearly a major source of uncertainty.
-
-  \begin{figure}
-    \caption{\textbf{A-B)} Most pairs of \emph{Salix} and galler or galler and parasitoid species were never observed co-occurring despite the high levels of replication in our example dataset.
-For those that were observed together at least once, the number of observed co-occurrences was generally small (\textless10).
-Here we show a histogram of the number of pairs of species observed co-occurring at least once.
-3986 pairs of species were never observed co-occurring: these pairs are omitted from the histogram.
-\textbf{C-D)} Most pairs of species that were observed at the same site were never observed interacting.
-Here we show a histogram of the number of observed interactions within pairs of co-occurring species.
-\textbf{E-F)} Here we show, for each species pair, the number of observed interactions plotted against the number of observed co-occurrences.
-Most pairs either are never observed interacting or interact almost every time they co-occur.
-The red, dashed line indicates a 1:1 relationship between interactions and co-occurrences.}
-    \label{histograms}
-    \includegraphics*[width=.8\textwidth]{figures/Salix_Galler_histogram.eps}
   \end{figure}
@@
 
-  The bottom line is that separating different sources of uncertainty is difficult indeed.
+  % The bottom line is that separating different sources of uncertainty is difficult indeed.
 In the best of all possible worlds, we might use an experimental approach to estimate detection uncertainty by creating replicate cases where the interaction really occurs and then evaluating the fraction of cases where the interaction is detected.
@@
 
-  As an alternative to abandoning empirical networks or continuing to ignore the uncertainty inherent in undetected observations, we propose that some insight regarding the detectability of interactions between species not found co-occurring may be gained from data on other species between which interactions are known to be feasible.
+  % As an alternative to abandoning empirical networks or continuing to ignore the uncertainty inherent in undetected observations, we propose that some insight regarding the detectability of interactions between species not found co-occurring may be gained from data on other species between which interactions are known to be feasible.
 If we use this information obtain the joint probability of detection and process (e.g.
@@
 with at least one observation of a positive interaction) [this reasoning to be further formalised]
+
+\section*{A naive quantification of interaction probability and uncertainty}
+
+  % It is getting more and more common to represent interactions as probabilities in theoretical models of network structure.
+For example, the minimum potential model introduces gaps in the feeding niche of predators by sampling based on the likelihood of each interaction~\citep{Allesina2008}, while a gaussian probability function is used to represent the niche by~\citet{Williams2010}.
+\citet{Eklof2013} also introduced variability  in the computation of network dimensions, allowing the absence of interactions within the n-dimension niche of every species.
+Empirical investigation of trait-matching constraints often consider the occurrence of interactions as binomial process (e.g.,~\citealp{Rohr2016}).
+There are also ways to perform analysis of probabilistic networks, with almost all metrics having a probabilistic version~\citep{Poisot2016}.
+But there is not yet consensus on what an interaction probability between a pair of species means, and this is definitely a problem when comes time to estimate the uncertainty of both pairwise interactions and entire networks.
+
+  To progressively dissect the different contributions to uncertainty, we will start by considering how we could naively quantify interaction probability and its associated uncertainty \emph{for an interaction that has not yet been observed}.
+We consider that a pair of species have been observed $n$ times co-occurring at one location, and the number of times they have been observed interacting is $k = 0$.
+We now aim to evaluate the uncertainty of this interaction.
+The occurrence of an interaction is a Bernoulli trial.
+Consequently, the number of success $k$ over $n$ trials will follow a binomial distribution:
+
+      \begin{equation}
+        X \sim Bin(n,\lambda) ,
+      \end{equation}
+
+      \noindent and
+
+      \begin{equation}
+         P(X = k|\lambda,n) = {n \choose k}\lambda^k(1-\lambda)^{n-k} . 
+         \label{likelihood}
+      \end{equation}
+
+  \noindent The parameter $\lambda$, the probability of observing an interaction over an infinite time interval and area, is the quantity we want to estimate from empirical data. 
+  The maximal likelihood estimate (MLE) of $\lambda$ is straightforward to find given $k$ and $n$:
+
+      \begin{equation}
+        \theta_{MLE} = \frac{k}{n}  .
+        \label{theta_MLE}
+      \end{equation}
+
+  The variance of a Bernoulli experiment is $n\lambda$(1-$\lambda$).
+It is important to remember that this variance describes the variability of the number of success $k$ for $n$ trials and is not the variance associated with the estimation of $\lambda$.
+  Given this variance, it is possible to compute the confidence interval for the MLE of $\lambda$ using any of several methods, including the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull Interval} (for details, see [\citealp{}]).
+Finding this estimate is therefore quite straightforward, but it nonetheless has two drawbacks.
+First, $\lambda$ is not a single point estimate but rather a random variable with a given uncertainty, the distribution of which is unknown.
+This means that even if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact.
+What it implies is that no interaction is the most likely situation but there is nonetheless a significant chance that the two species \emph{could} interact.
+In contrast with the situation where $k>0$, when we are sure that an interaction is feasible,
+  % (in which case, the ratio $k/n$ is smaller than $n$ because of detection and process uncertainty),  % This parenthetical makes the sentence very long. Is it necessary?
+  we are not sure that absence of interactions is caused by $L=0$.
+Second, and most importantly, the number of trials $n$ might be very low in many instances (and some pairs of species might not have been documented as co-occuring in even one case).
+Consequently, the uncertainty in the estimation of $\lambda$ might be considerable.
+In Fig.~\ref{upper_limits}, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda$ varies with sample size.
+At a small sample size, the 95\% confidence interval spans all values of $\lambda$.
+To establish that species are not interacting with any acceptable certainty requires tens of observations of the two species co-occurring but not interacting.
+  % Is the Clopper-Pearson interval the one in Dom's code snippets? If so, this is Fig.~\ref{Salix_cdfs}
+
+  The situation where $k = 0$ is also problematic because we have very little information with which to estimate $\lambda$, in particular when $n$ is also small.
+We therefore propose a Bayesian approach to solve this problem, building on two relevant features of such statistics: the posterior distribution of parameter estimates and usage of prior information.
+Before moving to this direction, we will first take time to better describe what is exactly meant by an interaction probability and appropriately define sources of uncertainty.
+
+  So many sources of interaction pooled into a single entity; hard to estimate.
+
+  MLE is zero if no interactions detected, but there may still be a substantial probability of interaction should the two species co-occur.
+[This is particularly important in the context of a changing world, where species not co-occurring today – or species not detected co-occurring today – may well do so tomorrow, forming complex interactions.]
 
@@
 
-      We here adopt a Bayesian approach to estimate the distribution of the parameter $\theta$. According to Bayes principle, the posterior distribution of $\theta$ is:
+      We here adopt a Bayesian approach to estimate the distribution of the parameter $\theta$, the maximum likelihood estimate of the interaction probability.
+According to Bayes principle, the posterior distribution of $\theta$ is:
 
@@
 The distribution narrows and approaches zero as the sample size increases.
-\textbf{A)} The posterior distributions for the \emph{Salix}-galler component are always wider and farther from zero than those for \textbf{B)} the galler-parasitoid component.}
+\textbf{A)} The posterior distributions for the \emph{Salix}-galler component are always wider and farther from zero than those for \textbf{B)} the galler-parasitoid component.
+This is likely because the prior distribution for the galler-parasitoid component of the network was both narrower and had a mean closer to that in the~\citet{Kopelke2017} data than the \emph{Salix}-galler component.}
         \includegraphics*[width=.8\textwidth]{figures/Salix_Galler_pdfs_increasing_N.eps}
@@
 
+          [Tomas adds: This is a bit of a stump]
           It is possible to estimate the probability of interaction between a pair of species if there is knowledge of their traits and some functions relating trait matching to interaction probability~\citep{Morales-Castilla2015}.
 There are several techniques available to perform this inference of interaction probability~\citep{} (REFS).
-Note that in this case the prior might not be beta distribution and numerical methods might be required to compute the posterior distribution.
+Note that in this case the prior might not be beta distributed and numerical methods might be required to compute the posterior distribution.
 
@@
 
-    The exercise exemplified above yields a surprising result: it requires \textgreater24 observations of no interactions to be 95\% sure that the interaction probability is smaller than 0.1.
+    The exercise exemplified above yields a surprising result: it requires \textgreater24 observations of no interactions to be 95\% sure that the interaction probability is smaller than 0.1 (recall Fig.~\ref{upper_limits}).
 Note the special case where there is no observation of the two species co-occurring and failing to interact, $n = 0$.
-In this situation, the posterior distribution converges to the prior distribution.
+In this situation, the posterior distribution converges to the prior distribution since the data include no information on the probability with which species might interact should the co-occur; see above).
 
@@
 Instead we must rely on computer simulations.
-In the following section, we will provide an example with the Salix dataset and show how the uncertainty arising from both absences of co-occurrences and false absences of interactions impact these metrics.
+In the following section, we will provide an empirical example, based on the data set published by~\citet{Kopelke2017}.
+We will show how the uncertainty arising from both absences of co-occurrences and false absences of interactions impact these metrics.
 We find uncertainty influences both the average and the variance of network metrics, putting in perspective traditional network comparison studies where these metrics are assumed fixed entities.
@@
 The data was collected over 29 years (1982-2010) at 374 unique locations across Europe ranging from Sicily to the Arctic.
-Including repeated visits to a number of sites, the data set contains 641 site-visits, each of which can be considered as a network in its own right, but here we consider each network as an independent sample from which to build the meta-network.
+Including repeated visits to a number of sites, the data set contains 641 site-visits, each of which can be considered as a network in its own right.
+Here we consider each network as an independent sample from which to build the meta-network.
 The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes and 126 natural enemy nodes.
 Interactions were determined by dissecting and rearing gall inhabitants from 165,424 galls.
-Something about how the suitability of this for what we're doing.
-E.g: The high spatiotemporal resolution of this network and the 641 site-visits which can be considered as independent samples of the network make this dataset particularly well suited for testing this method.
+The high spatiotemporal resolution of this network and the unusually high sampling effor implemented at the site level (641 site-visits, which can be considered as repeated samples of the network) makes this dataset particularly well suited for testing this method.
+
+      Importantly, while large, this network will illustrate the very real constraints on the sampling of ecological networks.
+As a baseline pattern, we may compare the frequency of co-occurrence of taxa in the example data set to the pattern of Fig.~\citep{upper_limits}.
+In the example data, most (3986 out of 4992) pairs of species are never found co-occurring, and for species found co-occurring the number of co-occurrences was generally low (Fig.~\ref{histograms}A).
+Among the species which did sometimes interact when co-occurring, the incidence of interaction was actually low.
+Only 141 pairs of species were observed interacting: of these, 26 were observed interacting only once and 48.2\% were observed interacting five or fewer times (Fig.~\ref{histograms}B).
+Thus, even in the most extensive data set that we could think of, limited sampling is clearly a major source of uncertainty.
+
+    \begin{figure}
+      \caption{\textbf{A-B)} Most pairs of \emph{Salix} and galler or galler and parasitoid species were never observed co-occurring despite the high levels of replication in our example dataset.
+For those that were observed together at least once, the number of observed co-occurrences was generally small (\textless10).
+Here we show a histogram of the number of pairs of species observed co-occurring at least once.
+3986 pairs of species were never observed co-occurring: these pairs are omitted from the histogram.
+\textbf{C-D)} Most pairs of species that were observed at the same site were never observed interacting.
+Here we show a histogram of the number of observed interactions within pairs of co-occurring species.
+\textbf{E-F)} Here we show, for each species pair, the number of observed interactions plotted against the number of observed co-occurrences.
+Most pairs either are never observed interacting or interact almost every time they co-occur.
+The red, dashed line indicates a 1:1 relationship between interactions and co-occurrences.}
+      \label{histograms}
+      \includegraphics*[width=.8\textwidth]{figures/Salix_Galler_histogram.eps}
+      \end{figure}
 
@@
       With species $i$ and $j$ co-occurring at all 374 sites and never being observed to interact, the maximum likelihood expectation for the probability of an interaction $ij$ is very close to 0 and the variance about this estimate is very narrow.
-In most cases, however, species $i$ and $j$ did not co-occur at so many sites and our posterior mean and variance retain some influence of the prior.
+In other words, we could establish with high certainty that the species will never interact.
+However, for most pairs of species $i$ and $j$, the species did not co-occur at so many sites and our posterior mean and variance retain some influence of the prior.
 Nevertheless, as the number of observed co-occurrence increases, the posterior mean becomes closer to zero and the posterior variance decreases (Fig.~\ref{Salix_pdfs}).
@@
 Even for a pair of species which appeared together in all 374 sites but were never observed interacting, the confidence interval (0.001, 0.018) comes close to, but does not include zero (Table~\ref{interval_table}).
+In other words, even with a very large data set, we will have problems in establishing that a given species pair can never interact.
 
@@
       \begin{table}[h]
-        \caption{95\% credible intervals for the interaction probability of two species that co-occur in $N$ sites but are never observed to interact, obtained using prior information from the \emph{Salix}-galler network in~\citet{Barbour2016,Barbour2016Dryad}.}
+        \caption{95\% credible intervals for the interaction probability of two species that co-occur in $N$ sites but are never observed to interact, obtained using prior information from the \emph{Salix}-galler network in~\citet{Barbour2016,Barbour2016Dryad}.
+[Tomas notes that this is conceptually very similar to Fig.~\ref{Salix_pdfs}]}
         \label{interval_table}
@@
 
-    \begin{figure}[h]
-    \label{posterior_webs}
+    \begin{figure}[ht]
     \caption{Here we show the mean connectance, links per resource (\emph{Salix} in the \emph{Salix}-galler networks and gallers in the galler-parasitoid networks), and links per consumer (gallers in the \emph{Salix}-galler networks and parasitoids in the galler-parasitoid networks) for networks assembled using posterior distributions based on~\citet{Barbour2016,Barbour2016Dryad}.
@@
 For each property and both network types, the posterior-sampling networks cover a relatively small range of network properties and the value of each property decreases with the proportion of links included in the detection-filter networks.}
-    \includegraphics*{}
+    \label{posterior_webs}    
+    \includegraphics[width=.8\textwidth]{Figures/Salix_Galler_posterior_properties.eps}
+    \end{figure}
 
@@
 ]]
+
+\section*{Conclusions/recommendations}
+
+  [Here we need to be very hands-on and remember the invitation letter form Ecol Letters:
+  As a contribution primarily to methodology, the manuscript will not be considered for "Ideas \& Perspectives".
+(Please recall my message concerning your past presubmission inquiry.) However, Ecology Letters is entertaining the idea of a new section for "Novel Methods".
+As we have not advertised this, I would ask you to keep that information in confidence.
+If acceptable to an Associate Editor and reviewers, your paper could be the first, or one of the first, contributions to this new section.
+Accordingly, the work would be subject to considerable scrutiny and I would urge you to make the paper as strong as you can.
+This would include demonstrating the need for this new method (i.e.
+outlining how this is different than other approaches currently in use and how they fail at some important task), documenting the robustness and accuracy of the approach, performing case study, and making robust high-quality code freely available.]
 

### 2017-11-16 manuscript/CI_interactions.tex
Kate's edits to the manuscript. Comments enclosed in square brackets

@@
 
-    Efforts to account for variance in interaction frequencies are complicated by the fact that not only interaction frequencies but network structure vary over space and time.
+    Efforts to account for variance in interaction frequencies are complicated by the fact that not only interaction frequencies but also network structure vary over space and time.
 Community composition and species abundances vary from site to site~\citep{Baiser2012} and over time within a site~\citep{Olesen2011a}.
@@
     Beyond "true" variation in network structure, several researchers have pointed to the importance of sampling intensity for the assessment of network structure (e.g.,~\citealp{Martinez1999,Bluthgen2006,XX}).
-Despite this, the acknowledgement that insufficient sampling effort limits our ability to describe variation in ecological networks has not yet led to a quantitative framework to deal with the uncertainty generated by spatiotemporal variation in ecological interactions and by sampling.
+Despite this, the acknowledgment that insufficient sampling effort limits our ability to describe variation in ecological networks has not yet led to a quantitative framework to deal with the uncertainty generated by spatiotemporal variation in ecological interactions and by sampling.
 
@@
 
-  To define the problem associated with describing ecological interaction networks, we will start from the perspective of an empirical community ecologist faced with the task of describing an interaction networks.
+  To define the problem associated with describing ecological interaction networks, we will start from the perspective of an empirical community ecologist faced with the task of describing an interaction network.
 This ecologist will be interested in generating a description of the blocks present, and the links between them (Roslin and Majaneva 2017).
 In other words, he or she seeks to fill in a matrix of species by species interactions.
-Importantly, the information sought is as much in the presence of given links as in the absence of others.
-An observed link will always remain an observed link, but to why given links are not observed, there may be multiple contributions.
+Importantly, the information sought is as much [in] the presence of given links as [in] the absence of others.
+An observed link will always remain an observed link, but as to why given links are not observed, there may be multiple contributions.
 Thus, we will set off by contemplating what factors may contribute to links missing from the matrix.
@@
 We define the probability of an interaction $L$ as $P(L)=\lambda$.
-Obviously, because $k=0$, it is very likely that they cannot interact even if there were no time or environmental constraints preventing the interaction.
-But it is nonetheless possible that the interaction is a rare phenomenon that has never been documented before.
+Obviously, because $k=0$ [[k hasn't been defined up to this point]], it is very likely that they cannot interact even if there were no time or environmental constraints preventing the interaction.
+[[The previous sentence doesn't follow, k hasn't been defined and we don't know that it's zero.
+Also, are we assuming that these interactions have been observed over a large area/time like the Kopelke data?
+Otherwise couldn't something about that particular site prevent species interacting even if they otherwise could?]] But it is nonetheless possible that the interaction is a rare phenomenon that has never been documented before.
 This source of uncertainty is the one documented by trait-matching models~\citep{}.
@@
 In other words, with sufficient sampling and all information accessible, this interaction probability should either tend to 0 or to 1 and the uncertainty vanishes.
+[[For species which actually co occur (?)]]
 
@@
     It could be that the interaction is feasible, i.e.
-$L=1$, but that it does not occur at a given location or moment in time because there are local constraints preventing it from occurring.
-We define the realisation of the interaction process $X$ given that the interaction is feasible as a stochastic process with associated probability $P(X|L)=\chi$.
+$L=1$, but that it does not occur at a given location or moment in time because there are local constraints [[such as...]] preventing it from occurring.
+We define the realisation of the interaction process $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L)=\chi$.
 This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology about the contingencies of interactions~\citep{}.
@@
 
-    Lastly, measurement errors are always source of uncertainty in the observation of ecological processes.
+    Lastly, measurement errors are always a source of uncertainty in the observation of ecological processes.
 We define the detection of an interaction $D$, given an interaction is feasible and occurs in the local conditions, as a stochastic process with associated probability $P(D|X,L)=\delta$.
-Detection failure could happen for several reasons, for instance if the rearing of a parasitoid fails with inappropriate lab conditions or because of species mis-identification.
+Detection failure could happen for several reasons, for instance if the rearing of a parasitoid fails with inappropriate lab conditions or because of species mis-identification [[or because the interaction is rare enough that we just miss it?
+Or we're just looking in the wrong place at the wrong time?]].
 Some sources of detection error could be minimised with appropriate sampling effort ($\delta$ will converge to one with increasing number of collected galls), but other sources are often difficult to reduce (e.g.
@@
     The combination of these three sources of uncertainty together leads to many potential explanations for the observation of an absence of interaction, but only the situation where $L = 0$ (a true absence) is relevant for the investigation of networks.
-While the observation of an interaction is straightforward to interpret, absence of interactions must be decomposed in different quantities.
+While the observation of an interaction is straightforward to interpret, absence of interactions must be decomposed into different quantities.
 It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e.
@@
   It is important to keep in mind that for network analysis, ecologists seek to measure the occurrence of true absences, which is the joint event $L=0 \cup X=1 \cup D=1$), but in reality they measure the marginal probability $P(L) = k/n$.
-% I'm pretty sure this should be L=0 but X=1 and D=1: interaction not feasible but site and detection perfect.
+[[k and n still haven't been defined]]% I'm pretty sure this should be L=0 but X=1 and D=1: interaction not feasible but site and detection perfect.
 
@@
 How then may we refine our sampling approaches to reduce uncertainties, and to gain insights into the impact of multiple processes on field observations?
-Importantly, some sources can be minimised with appropriate sampling design and efforts, while other sources are difficult or impossible to reduce – since they are generated by chance variation created by the very process in which we are interested.
+Importantly, some sources [[of uncertainty]] can be minimised with appropriate sampling design and efforts, while other sources are difficult or impossible to reduce – since they are generated by chance variation created by the very process in which we are interested.
 
   The basic information that we are collecting consists of matrices of interaction partners.
-Our count of interactions between species A and species B reflects uncertainty with respect to whether two species interact when co-occurring at a given site, chance variation in whether the interaction is realised, and uncertainty with respect to whether it is detected when realised.
+Our count of interactions between species A and species B reflects uncertainty with respect to whether two species interact when co-occurring at a given site, chance variation in whether the interaction is realised, [[the previous two things sound like the same thing.
+Maybe ``whether two species are capable of interacting when co-occuring at a given site, chance variation as to whether the interaction is realized...'']] and uncertainty with respect to whether it is detected when realised.
 In this case, what can we do to pin down any of these different types of variation?
@@
 Given no added detection error in observing the incidence of the interaction, then a single observation of species co-occurrence will reveal (very) little regarding the probability of the interaction – the confidence limits for one observation essentially spans from 0 to 1 (Fig.~\ref{upper_limits}).
-For 5 observations, this confidence limit will still extends to 0.5.
+For 5 observations, this confidence limit still extends to 0.5.
 Only with thirty observations will it shrink to 0.1.
@@
 Thus, the more we sample, the more zeros will appear in our interaction matrix, which may seem like a counter-intuitive outcome.
+[[Furthermore, depending on the spatial and temporal extent of our sampling, more sampling may not help us detect feasible interactions which are prevented from being realized by local processes at the sites/times we are sampling.]]
 
@@
 This can bias the set of recorded interactions.
+
+  [[How do we define samples?
+For the Kopelke set we use sampling occasion, but what about sampling twice as many trees on the same day and same place?
+Does that count?
+Does it have to be spatially and/or temporally separated?
+Is it relevant??]]
 
@@
 The occurrence of an interaction is a Bernoulli trial.
-Consequently, the number of success $k$ over $n$ trials will follow a binomial distribution:
+Consequently, the number of success[es] $k$ over $n$ trials will follow a binomial distribution:
 
@@
   The variance of a Bernoulli experiment is $n\lambda$(1-$\lambda$).
-It is important to remember that this variance describes the variability of the number of success $k$ for $n$ trials and is not the variance associated with the estimation of $\lambda$.
+It is important to remember that this variance describes the variability of the number of success[es] $k$ for $n$ trials and is not the variance associated with the estimation of $\lambda$.
   Given this variance, it is possible to compute the confidence interval for the MLE of $\lambda$ using any of several methods, including the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull Interval} (for details, see [\citealp{}]).
@@
 
-  MLE is zero if no interactions detected, but there may still be a substantial probability of interaction should the two species co-occur.
+  MLE is zero if no interaction is detected, but there may still be a substantial probability of interaction should the two species co-occur.
 [This is particularly important in the context of a changing world, where species not co-occurring today – or species not detected co-occurring today – may well do so tomorrow, forming complex interactions.]
@@
 
-          In the literature of ecological networks there is a solid collection of data for which know network connectance and from which we can define the connectance distribution.
+          In the literature of ecological networks there is a solid collection of data for which we know network connectance and from which we can define the connectance distribution.
 Connectance is measured as $C = L/S^2$, where $L$ is the number of interactions and $S$ is the number of species.
 It measures the filling of an interaction matrix and thereby expresses the average probability that any two species interact with each other.
-If we know only the mean $\overline{C}$ and the variance $\sigma_C^2$ of the distribution of $C$, then the beta parameters could be computed as follows using the method of moments:
+If we know only the mean $\overline{C}$ and the variance $\sigma_C^2$ of the distribution of $C$,[[from the literature or from our network?]] then the beta parameters could be computed as follows using the method of moments:
 
@@
   The Bayesian framework can be illustrated with a simple quantitative example.
-Suppose we have $n = 10$ observations of co-occurrence between species $i$ and species $j$ in a given time interval and area, and $X = 3$ observations of interactions.
+Suppose we have $n = 10$ observations of co-occurrence between species $i$ and species $j$ in a given time interval and area, and $X = 3$[ = k?] observations of interactions.
 The maximum likelihood estimate of the interaction probability is simply $\theta_{MLE} = 3/10 = 0.3$.
@@
     Adding the observed data (n=10, k=3) and using the same code,
-    we obtain posterior hyper parameters $\alpha'$=4.05083 and $\beta'$=12.36589 and a posterior mean 0.247 and variance 0.011 for the probability of.
+    we obtain posterior hyper parameters $\alpha'$=4.05083 and $\beta'$=12.36589 and a posterior mean 0.247 and variance 0.011 for the probability of [[...?]].
 Comparing the posterior distribution to the prior, we see that the posterior is closer to the observed data and that the additional data has reduced the variance.
@@
     The exercise exemplified above yields a surprising result: it requires \textgreater24 observations of no interactions to be 95\% sure that the interaction probability is smaller than 0.1 (recall Fig.~\ref{upper_limits}).
-Note the special case where there is no observation of the two species co-occurring and failing to interact, $n = 0$.
-In this situation, the posterior distribution converges to the prior distribution since the data include no information on the probability with which species might interact should the co-occur; see above).
+Note the special case where there is no observation of the two species co-occurring and failing to interact, $n = 0$ [[shouldn't it just be ``no observation of the two species co-occuring, $n=0$.'' I.e.
+nothing about failing to interact?
+Wouldn't that be $n = k$ and then you're pretty certain that an interaction does indeed exist?]] In this situation, the posterior distribution converges to the prior distribution since the data include no information on the probability with which species might interact should they co-occur; see above).
 
@@
 Computation of these metrics involves non-linear functions and therefore, because of Jensen's inequality (which states that the average of non-linear function of a stochastic variable differs from the function of the average of that variable), any uncertainty in $\lambda$s could bias both the mean and variance of a network metric.
-For instance, assume that among all pairs of species with few observed co-occurrence there are many pairs which truly interact.
+For instance, assume that among all pairs of species with few observed co-occurrences there are many pairs which truly interact.
 If we begin with no observed links for these pairs, then correcting for these false absences will inflate the number of links and consequently influence metrics such as connectance, nestedness, and degree distribution.
@@
 We will show how the uncertainty arising from both absences of co-occurrences and false absences of interactions impact these metrics.
-We find uncertainty influences both the average and the variance of network metrics, putting in perspective traditional network comparison studies where these metrics are assumed fixed entities.
+We find uncertainty influences both the average and the variance of network metrics, putting in perspective traditional network comparison studies where these metrics are assumed [[to be]] fixed entities.
 
@@
       We use an extensively sampled \emph{Salix}-galler-parasitoid meta-network as a case study.
-This dataset consists of a single community type sampled across Europe, including willow (\emph{Salix}) species, willow-galling sawflies (Hymenoptera, Tenthredinidae, Nematinae, Euurina), and their natural enemies (hymenopteran parasitoids and coleopteran, lepidopteran, dipteran, and hymenopteran inquilines).
-The data was collected over 29 years (1982-2010) at 374 unique locations across Europe ranging from Sicily to the Arctic.
+This dataset consists of a single community type sampled across Europe; willow (\emph{Salix}) species, willow-galling sawflies (Hymenoptera, Tenthredinidae, Nematinae, Euurina), and their natural enemies (hymenopteran parasitoids and coleopteran, lepidopteran, dipteran, and hymenopteran inquilines).
+The data were collected over 29 years (1982-2010) at 374 unique locations across Europe ranging from Sicily to the Arctic.
 Including repeated visits to a number of sites, the data set contains 641 site-visits, each of which can be considered as a network in its own right.
@@
 Only 141 pairs of species were observed interacting: of these, 26 were observed interacting only once and 48.2\% were observed interacting five or fewer times (Fig.~\ref{histograms}B).
-Thus, even in the most extensive data set that we could think of, limited sampling is clearly a major source of uncertainty.
+Thus, even in the most extensive data set that we could find, limited sampling is clearly a major source of uncertainty.
 
@@
 
-      For species where no co-occurrence were observed, we can 
+      For species where no co-occurrences were observed, we can 
       calculate the MLE estimates for the mean and variance of 
@@
 
-      For a pair of species where some co-occurrence were observed, we can update the prior distribution with these data.
+      For a pair of species where some co-occurrences were observed, we can update the prior distribution with these data.
 If we consider only pairs of species which were observed to co-occur but not to interact, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs.
@@
 In other words, we could establish with high certainty that the species will never interact.
-However, for most pairs of species $i$ and $j$, the species did not co-occur at so many sites and our posterior mean and variance retain some influence of the prior.
+However, for most [[all??]] pairs of species $i$ and $j$, the species did not co-occur at so many sites and our posterior mean and variance retain some influence of the prior.
 Nevertheless, as the number of observed co-occurrence increases, the posterior mean becomes closer to zero and the posterior variance decreases (Fig.~\ref{Salix_pdfs}).
@@
 This is again straightforward to do in R (see the function ``credible interval" in \emph{Appendix S2}).
-Calculating the 95\% credible intervals for species pairs with 0 to 50 observed co-occurrences without any observed interaction (as in Fig.~\ref{Salix_pdfs}), we see that the interval narrows dramatically as the number of observations increases.
+Calculating the 95\% credible intervals for species pairs with 0 to 50 observed co-occurrences without any observed interaction [[ were there any species with 50 co-occurrences and no interaction?]] (as in Fig.~\ref{Salix_pdfs}), we see that the interval narrows dramatically as the number of observations increases.
 In no case, however, does the confidence interval include 0.
@@
       Given the low levels of replication in most network studies, this implies that we should have fairly low confidence in many ``non-interacting" pairs of species.
-Even in the extensively replicated \emph{Salix}-galler-parasitoid dataset very few species pairs were observed co-occurring frequently enough to reach these thresholds (only three \emph{Salix}-galler pairs and 31 galler-parasitoid pairs were observed co-occurring frequently enough to reach the threshold for an interaction probability of 0.1, and no pairs were observed co-occurring frequently enough to reach the threshold for an interaction probability of 0.01).
+Even in the extensively replicated \emph{Salix}-galler-parasitoid dataset very few species pairs were observed co-occurring frequently enough to reach these thresholds (only three \emph{Salix}-galler pairs and 31 galler-parasitoid pairs were observed co-occurring frequently enough to reach the threshold for an interaction probability of 0.1 [[were there any pairs that interacted 51 times (or 25 for galler-parasitoid) and didn't interact at all?]], and no pairs were observed co-occurring frequently enough to reach the threshold for an interaction probability of 0.01).
 Discounting potential interactions, then, requires either a stronger prior expectation of no interaction (e.g., we can be highly confident that a palm tree will not predate upon a leopard no matter how many times the two species are observed together) or very extensive sampling.
@@
 Networks were filtered by randomly sampling 99\%, 95\%, 90\%, 80\%, 70\&, 60\%, and 50\% of the interactions included in each posterior network.
-For level of detection accuracy, we created 100 randomly-sampled network per posterior-probability network.
+For each level of detection accuracy, we created 100 randomly-sampled networks per posterior-probability network.
 We then calculated the same network properties as described above.
@@
 Likewise, the number of links per \emph{Salix} and galler species in the observed web (2.71 and 1.47, respectively) were much lower than those predicted in the posterior webs, even when filtering with a detection probability of only 50\%.
-There are two possible explanations for this discrepancy: either the~\citet{Barbour2016} data do no give an appropriate prior for our dataset, or the true detection probability for links between \emph{Salix} and galler species is much less than 50\%.
+There are two possible explanations for this discrepancy: either the~\citet{Barbour2016} data do not give an appropriate prior for our dataset, or the true detection probability for links between \emph{Salix} and galler species is much less than 50\%.
 As the scale of the two datasets is quite different (genotypes of a single \emph{Salix} species in~\citet{Barbour2016}, various \emph{Salix} species in our dataset), we suspect the former is more likely.

### 2017-11-16 manuscript/CI_interactions.tex
addressed Kate's comments quickly

@@
     Importantly, empirical descriptions of ecological networks are usually considered to be static representations of the communities and interactions they describe.
-That is, whether the network is assembled based on aggregated data, a single intensive "snapshot" sample, or expert knowledge, interactions are assumed to occur at the same frequencies wherever and whenever the network is observed~\citep{Olesen2011a}.
+That is, whether the network is assembled based on aggregated data, a single intensive ``snapshot" sample, or expert knowledge, interactions are assumed to occur at the same frequencies wherever and whenever the network is observed~\citep{Olesen2011a}.
 This assumption conflicts with known variation in interactions over time~\citep{Kitching1987,Olesen2011a} and space~\citep{Kitching1987,Baiser2012} and between individuals of a given species~\citep{Pires2011a,Fodrie2015,Novak2015}.
@@
 
-    Beyond "true" variation in network structure, several researchers have pointed to the importance of sampling intensity for the assessment of network structure (e.g.,~\citealp{Martinez1999,Bluthgen2006,XX}).
+    Beyond ``true" variation in network structure, several researchers have pointed to the importance of sampling intensity for the assessment of network structure (e.g.,~\citealp{Martinez1999,Bluthgen2006,XX}).
 Despite this, the acknowledgment that insufficient sampling effort limits our ability to describe variation in ecological networks has not yet led to a quantitative framework to deal with the uncertainty generated by spatiotemporal variation in ecological interactions and by sampling.
@@
 Through these efforts, we demonstrate both the utility of our approach and the importance of acknowledging the uncertainty inherent in ecological networks.
-    % List of sections may not be accurate any more. Update when paper reaches its final form.
 
@@
 In other words, he or she seeks to fill in a matrix of species by species interactions.
-Importantly, the information sought is as much [in] the presence of given links as [in] the absence of others.
+Importantly, the information sought is conveyed by both the presence and \emph{absence} of links.
 An observed link will always remain an observed link, but as to why given links are not observed, there may be multiple contributions.
@@
 We define the probability of an interaction $L$ as $P(L)=\lambda$.
-Obviously, because $k=0$ [[k hasn't been defined up to this point]], it is very likely that they cannot interact even if there were no time or environmental constraints preventing the interaction.
-[[The previous sentence doesn't follow, k hasn't been defined and we don't know that it's zero.
+Obviously, because $k$ (the number of observed interactions) is 0, it is possible that the two species cannot interact even if there were no time or environmental constraints preventing the interaction.
+    % [[The previous sentence doesn't follow, k hasn't been defined and we don't know that it's zero.
 Also, are we assuming that these interactions have been observed over a large area/time like the Kopelke data?
-Otherwise couldn't something about that particular site prevent species interacting even if they otherwise could?]] But it is nonetheless possible that the interaction is a rare phenomenon that has never been documented before.
+Otherwise couldn't something about that particular site prevent species interacting even if they otherwise could?]]
+    % [[With defining k I think this is fine...
+site uncertainty will come in later, and it's not necessary to assume anything about the sampling design to get from not observing two species to interact to suspecting that they don't (degree of confidence depending on the species involved).
+I've toned down "very likely" to "possible" though - does that help?]]
+    But it is nonetheless possible that the interaction is a rare phenomenon that has never been documented before.
 This source of uncertainty is the one documented by trait-matching models~\citep{}.
@@
 In other words, with sufficient sampling and all information accessible, this interaction probability should either tend to 0 or to 1 and the uncertainty vanishes.
-[[For species which actually co occur (?)]]
+    % [[For species which actually co occur (?)]]
+    % [[I think that gets covered under "sufficient sampling"]]
 
@@
     It could be that the interaction is feasible, i.e.
-$L=1$, but that it does not occur at a given location or moment in time because there are local constraints [[such as...]] preventing it from occurring.
+$L=1$, but that it does not occur at a given location or moment in time because there are local constraints, such as inclement weather or lack of suitable habitat, that prevent the interaction from occurring.
 We define the realisation of the interaction process $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L)=\chi$.
@@
 We define the detection of an interaction $D$, given an interaction is feasible and occurs in the local conditions, as a stochastic process with associated probability $P(D|X,L)=\delta$.
-Detection failure could happen for several reasons, for instance if the rearing of a parasitoid fails with inappropriate lab conditions or because of species mis-identification [[or because the interaction is rare enough that we just miss it?
-Or we're just looking in the wrong place at the wrong time?]].
-Some sources of detection error could be minimised with appropriate sampling effort ($\delta$ will converge to one with increasing number of collected galls), but other sources are often difficult to reduce (e.g.
+Detection failure could happen for several reasons, for instance if the rearing of a parasitoid fails with inappropriate lab conditions, because of species mis-identification, or because the interaction is very rare.
+Some sources of detection error could be minimised with appropriate sampling effort ($\delta$ will converge to one with increasing number of samples), but other sources are often difficult to reduce (e.g.
 the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification).
@@
 
-  It is important to keep in mind that for network analysis, ecologists seek to measure the occurrence of true absences, which is the joint event $L=0 \cup X=1 \cup D=1$), but in reality they measure the marginal probability $P(L) = k/n$.
-[[k and n still haven't been defined]]% I'm pretty sure this should be L=0 but X=1 and D=1: interaction not feasible but site and detection perfect.
+  It is important to keep in mind that for network analysis, ecologists seek to measure the occurrence of true absences, which is the joint event $L=0 \cup X=1 \cup D=1$), but in reality they measure the marginal probability $P(L) = k/n$ where $k$ is again the number of observed interactions and $n$ the number of observed co-occurances.
+% I'm pretty sure this should be L=0 but X=1 and D=1: interaction not feasible but site and detection perfect.
 
@@
 How then may we refine our sampling approaches to reduce uncertainties, and to gain insights into the impact of multiple processes on field observations?
-Importantly, some sources [[of uncertainty]] can be minimised with appropriate sampling design and efforts, while other sources are difficult or impossible to reduce – since they are generated by chance variation created by the very process in which we are interested.
+Importantly, some sources of uncertainty can be minimised with appropriate sampling design and efforts, while other sources are difficult or impossible to reduce – since they are generated by chance variation created by the very process in which we are interested.
 
   The basic information that we are collecting consists of matrices of interaction partners.
-Our count of interactions between species A and species B reflects uncertainty with respect to whether two species interact when co-occurring at a given site, chance variation in whether the interaction is realised, [[the previous two things sound like the same thing.
-Maybe ``whether two species are capable of interacting when co-occuring at a given site, chance variation as to whether the interaction is realized...'']] and uncertainty with respect to whether it is detected when realised.
+Our count of interactions between species A and species B reflects uncertainty with respect to whether two species are capable of interacting when co-occurring at a given site, chance variation in whether the interaction is realised,  and uncertainty with respect to whether it is detected when realised.
 In this case, what can we do to pin down any of these different types of variation?
@@
 
-  The obvious rule of thumb derived from the above example is “sample more”, but we note that there are limits to the utility of this motto.
+  The obvious rule of thumb derived from the above example is ``sample more", but we note that there are limits to the utility of this motto.
 Sampling more will clearly reduce uncertainty regarding the upper bound of the probability of interaction, and it will also increase the probability of detecting unlikely interactions (i.e.
@@
 Thus, the more we sample, the more zeros will appear in our interaction matrix, which may seem like a counter-intuitive outcome.
-[[Furthermore, depending on the spatial and temporal extent of our sampling, more sampling may not help us detect feasible interactions which are prevented from being realized by local processes at the sites/times we are sampling.]]
 
@@
 
-  [[How do we define samples?
+  % [[How do we define samples?
 For the Kopelke set we use sampling occasion, but what about sampling twice as many trees on the same day and same place?
@@
 Is it relevant??]]
+  % [[Pretty sure this will always depend on the study - also seems like a pretty large digression.]]
 
@@
 It measures the filling of an interaction matrix and thereby expresses the average probability that any two species interact with each other.
-If we know only the mean $\overline{C}$ and the variance $\sigma_C^2$ of the distribution of $C$,[[from the literature or from our network?]] then the beta parameters could be computed as follows using the method of moments:
+If we know only the mean $\overline{C}$ and the variance $\sigma_C^2$ of the distribution of $C$,
+          % [[from the literature or from our network? Has to be from the literature - if it was our network we'd know way more than just C]] 
+          then the beta parameters could be computed as follows using the method of moments:
 
@@
   The Bayesian framework can be illustrated with a simple quantitative example.
-Suppose we have $n = 10$ observations of co-occurrence between species $i$ and species $j$ in a given time interval and area, and $X = 3$[ = k?] observations of interactions.
+Suppose we have $n = 10$ observations of co-occurrence between species $i$ and species $j$ in a given time interval and area, and $k = 3$ observations of interactions.
 The maximum likelihood estimate of the interaction probability is simply $\theta_{MLE} = 3/10 = 0.3$.
@@
     Adding the observed data (n=10, k=3) and using the same code,
-    we obtain posterior hyper parameters $\alpha'$=4.05083 and $\beta'$=12.36589 and a posterior mean 0.247 and variance 0.011 for the probability of [[...?]].
+    we obtain posterior hyper parameters $\alpha'$=4.05083 and $\beta'$=12.36589 and a posterior mean 0.247 and variance 0.011 for the probability of interaction.
 Comparing the posterior distribution to the prior, we see that the posterior is closer to the observed data and that the additional data has reduced the variance.
@@
     The exercise exemplified above yields a surprising result: it requires \textgreater24 observations of no interactions to be 95\% sure that the interaction probability is smaller than 0.1 (recall Fig.~\ref{upper_limits}).
-Note the special case where there is no observation of the two species co-occurring and failing to interact, $n = 0$ [[shouldn't it just be ``no observation of the two species co-occuring, $n=0$.'' I.e.
-nothing about failing to interact?
-Wouldn't that be $n = k$ and then you're pretty certain that an interaction does indeed exist?]] In this situation, the posterior distribution converges to the prior distribution since the data include no information on the probability with which species might interact should they co-occur; see above).
+Note the special case where there is no observation of the two species co-occurring, $n = 0$  In this situation, the posterior distribution converges to the prior distribution since the data include no information on the probability with which species might interact should they co-occur; see above).
 
@@
 We will show how the uncertainty arising from both absences of co-occurrences and false absences of interactions impact these metrics.
-We find uncertainty influences both the average and the variance of network metrics, putting in perspective traditional network comparison studies where these metrics are assumed [[to be]] fixed entities.
+We find uncertainty influences both the average and the variance of network metrics, putting in perspective traditional network comparison studies where these metrics are assumed to be fixed entities.
 
@@
 In other words, we could establish with high certainty that the species will never interact.
-However, for most [[all??]] pairs of species $i$ and $j$, the species did not co-occur at so many sites and our posterior mean and variance retain some influence of the prior.
+However, for most pairs of species $i$ and $j$, the species did not co-occur at many sites and our posterior mean and variance retain some of the influence of the prior.
 Nevertheless, as the number of observed co-occurrence increases, the posterior mean becomes closer to zero and the posterior variance decreases (Fig.~\ref{Salix_pdfs}).
@@
 This is again straightforward to do in R (see the function ``credible interval" in \emph{Appendix S2}).
-Calculating the 95\% credible intervals for species pairs with 0 to 50 observed co-occurrences without any observed interaction [[ were there any species with 50 co-occurrences and no interaction?]] (as in Fig.~\ref{Salix_pdfs}), we see that the interval narrows dramatically as the number of observations increases.
+Calculating the 95\% credible intervals for species pairs with 0 to 50 observed co-occurrences without any observed interaction (as in Fig.~\ref{Salix_pdfs}), we see that the interval narrows dramatically as the number of observations increases.
 In no case, however, does the confidence interval include 0.
@@
       Given the low levels of replication in most network studies, this implies that we should have fairly low confidence in many ``non-interacting" pairs of species.
-Even in the extensively replicated \emph{Salix}-galler-parasitoid dataset very few species pairs were observed co-occurring frequently enough to reach these thresholds (only three \emph{Salix}-galler pairs and 31 galler-parasitoid pairs were observed co-occurring frequently enough to reach the threshold for an interaction probability of 0.1 [[were there any pairs that interacted 51 times (or 25 for galler-parasitoid) and didn't interact at all?]], and no pairs were observed co-occurring frequently enough to reach the threshold for an interaction probability of 0.01).
+Even in the extensively replicated \emph{Salix}-galler-parasitoid dataset very few species pairs were observed co-occurring frequently enough to reach these thresholds (only three \emph{Salix}-galler pairs and 31 galler-parasitoid pairs were observed co-occurring frequently enough to reach the threshold for an interaction probability of 0.1, and no pairs were observed co-occurring frequently enough to reach the threshold for an interaction probability of 0.01 [[Do we need the other thresholds?
+Seems like it'll get redundant]]).
 Discounting potential interactions, then, requires either a stronger prior expectation of no interaction (e.g., we can be highly confident that a palm tree will not predate upon a leopard no matter how many times the two species are observed together) or very extensive sampling.
@@
     \caption{Here we show the mean connectance, links per resource (\emph{Salix} in the \emph{Salix}-galler networks and gallers in the galler-parasitoid networks), and links per consumer (gallers in the \emph{Salix}-galler networks and parasitoids in the galler-parasitoid networks) for networks assembled using posterior distributions based on~\citet{Barbour2016,Barbour2016Dryad}.
-We created 100 "posterior-sampling" networks and then, for each of these, created 100 "detection-filter" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network.
+We created 100 ``posterior-sampling" networks and then, for each of these, created 100 ``detection-filter" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network.
 This simulates imperfect detection of interactions in the field.
@@
   [Here we need to be very hands-on and remember the invitation letter form Ecol Letters:
-  As a contribution primarily to methodology, the manuscript will not be considered for "Ideas \& Perspectives".
-(Please recall my message concerning your past presubmission inquiry.) However, Ecology Letters is entertaining the idea of a new section for "Novel Methods".
+  As a contribution primarily to methodology, the manuscript will not be considered for ``Ideas \& Perspectives".
+(Please recall my message concerning your past presubmission inquiry.) However, Ecology Letters is entertaining the idea of a new section for ``Novel Methods".
 As we have not advertised this, I would ask you to keep that information in confidence.

### 2017-11-18 manuscript/CI_interactions.tex
Gravel first read

@@
     % Present Salix data with holes as an example of uncertainty in data. Focus just on the white and grey, ignore uncertainty in the blacks
-    In modern community ecology, species assemblages are increasingly described and analyzed as networks~\citep{Thompson2012,RecentReviews}.
-Such representations offer convenient summaries of how communities are constructed since they simultaneously account for species composition and their interactions.
-Species are represented as nodes, hence a tabulation of the nodes present and of their relative abundances form the basis for traditional metrics of community composition.
+
+  %DG : I cut down significantly the first paragraph, as I think we could assume readers know about networks and don't need to be convinced of their usage. 
+   Representation of species assemblages as a network offers a convenient summary of how communities are constructed, as it simultaneously account for species composition and their interactions.
+A tabulation of the nodes and of their relative abundances form the basis for traditional metrics of community composition.
 On top of this information, interactions are represented by links, so that networks provide additional, higher-order information on community structure.
-Metrics of how networks are structured at the level of links emerging from individual species (such as link density, vulnerability and degree distribution), and of network-level structure (such as nestedness, connectance and modularity), then offer key descriptors of how species interactions are structured across the globe~\citep{Schleuning2012,Morris2014,XX}, valuable proxies of community dynamics~\citep{Thebault2010,XX} and [many other nice things].
-Thus, deriving robust descriptors of network properties is a key objective for modern community ecology.
+Empirical descriptions of ecological networks are however usually considered to be static representations of the communities and interactions they describe.
+This approach contrasts significantly with the widely recognized stochasticity of ecological communities \citep{Gotelli2000}.
+That is, whether the network is assembled based on aggregated data, a single intensive ``snapshot" sample, or expert knowledge, interactions are assumed to occur deterministically wherever and whenever the community is observed~\citep{Olesen2011a}.
+This assumption conflicts with known variation in interactions over time~\citep{Kitching1987,Olesen2011a} and space~\citep{Kitching1987,Baiser2012} and between individuals of a given species~\citep{Pires2011a,Fodrie2015,Novak2015}.
 
-    Importantly, empirical descriptions of ecological networks are usually considered to be static representations of the communities and interactions they describe.
-That is, whether the network is assembled based on aggregated data, a single intensive ``snapshot" sample, or expert knowledge, interactions are assumed to occur at the same frequencies wherever and whenever the network is observed~\citep{Olesen2011a}.
-This assumption conflicts with known variation in interactions over time~\citep{Kitching1987,Olesen2011a} and space~\citep{Kitching1987,Baiser2012} and between individuals of a given species~\citep{Pires2011a,Fodrie2015,Novak2015}.
-Taking the variation in interaction frequencies into account would therefore represent a substantial increase in the realism of ecological networks as representations of ecological communities.
-
-    Efforts to account for variance in interaction frequencies are complicated by the fact that not only interaction frequencies but also network structure vary over space and time.
+    Efforts to account for the variability in interaction occurrence and frequency are complicated by the fact that not only species but also interactions vary over space and time.
 Community composition and species abundances vary from site to site~\citep{Baiser2012} and over time within a site~\citep{Olesen2011a}.
-The removal of a species from a site will obviously also remove its interactions.
-Interactions can also be lost, however, if participating species remain present but do not co-occur temporally or are too rare to detect each other~\citep{Tylianakis2010}, or through changes to individual preferences~\citep{Fodrie2015}.
+The removal of a species from a site will obviously also remove its interactions, but the co-occurrence of potentially interacting species do not guarantee they will.
+Interactions can be lost, or not detected, if participating species remain present but do not co-occur temporally, are too rare to detect each other~\citep{Tylianakis2010}, because of environmental contingencies \citep{Poisot2015a} or through changes to individual preferences~\citep{Fodrie2015}.
 
     Beyond ``true" variation in network structure, several researchers have pointed to the importance of sampling intensity for the assessment of network structure (e.g.,~\citealp{Martinez1999,Bluthgen2006,XX}).
-Despite this, the acknowledgment that insufficient sampling effort limits our ability to describe variation in ecological networks has not yet led to a quantitative framework to deal with the uncertainty generated by spatiotemporal variation in ecological interactions and by sampling.
+Accumulation of interactions with increasing sampling effort suggests that it is even more challenging to document them than species richness \citep{Poisot2012}.
+As a result, it was proposed that interactions should be described probabilistically and network metrics computed accordingly \citep{Poisot2015b}.
+Despite this, the acknowledgment that insufficient sampling effort limits our ability to describe variation in ecological networks has not yet led to a quantitative methodology to deal with the uncertainty generated by spatiotemporal variation in ecological interactions and by sampling.
 
-    In this study, we develop analytical tools to capture the uncertainty in the estimation of pairwise interaction probability.
+% DG : I wonder if a paragraph summarizing the extent of the problem with the salix data should not be provided here.
+Either within the text, or a box.
+But we need to convingly show how large is this problem even for such an extensive dataset
+
+    In this study, we develop analytical tools to capture the uncertainty in the estimation of pairwise interactions.
+We focus on binary interactions as a first step, but the framework could be expanded to deal with interaction frequencies and strength.
 To define the problem, we first discuss the pervasive implications of uncertainty in the estimation of pairwise interactions on the properties of ecological networks.
 We then define a framework which identifies and dissects the different contributions to uncertainty of interaction.
-We illustrate this framework with a simple quantitative example.
+We illustrate this framework with a simple quantitative example using the most extensively sample network to date.
 Next, we use the framework to provide analytical criteria for improving the sampling of rare interactions.
 Finally, we offer tangible recommendations for improved descriptors of ecological interactions.
-Through these efforts, we demonstrate both the utility of our approach and the importance of acknowledging the uncertainty inherent in ecological networks.
+Through these efforts, we demonstrate both the utility of our approach and the importance of acknowledging the uncertainty inherent in network studies.
 
@@
 This ecologist will be interested in generating a description of the blocks present, and the links between them (Roslin and Majaneva 2017).
-In other words, he or she seeks to fill in a matrix of species by species interactions.
 Importantly, the information sought is conveyed by both the presence and \emph{absence} of links.
@@
 
-    First, and most fundamentally, we do not know whether or not a pair of species have the appropriate characteristics to interact.
-We define the probability of an interaction $L$ as $P(L)=\lambda$.
-Obviously, because $k$ (the number of observed interactions) is 0, it is possible that the two species cannot interact even if there were no time or environmental constraints preventing the interaction.
+    First, and most fundamentally, we do not know whether or not a pair of species have the appropriate characteristics (or traits) to interact.
+We define the probability of an interaction $L$ given those characteristics $\mathbf{T}$ as $P(L | \mathbf{T})=\lambda$.
+Obviously, if $k$ (the number of observed interactions) is 0, it is possible that the two species cannot interact even if there were no time or environmental constraints preventing it to occur.
+In such case, $\lambda$ would take a value of 0.
     % [[The previous sentence doesn't follow, k hasn't been defined and we don't know that it's zero.
@@
 I've toned down "very likely" to "possible" though - does that help?]]
-    But it is nonetheless possible that the interaction is a rare phenomenon that has never been documented before.
-This source of uncertainty is the one documented by trait-matching models~\citep{}.
+    But it is nonetheless possible that the interaction is a rare phenomenon that has never been documented before, with $\lambda>0$.
+This source of uncertainty is the one documented by trait-matching models~\citep{Bartomeus2016}.
 It arises because every model is imperfect and lacks information (i.e.
 traits) about the constraints on the interaction.
-In other words, with sufficient sampling and all information accessible, this interaction probability should either tend to 0 or to 1 and the uncertainty vanishes.
+In other words, with sufficient sampling and all information accessible, this interaction probability $\lambda$ should either tend to 0 or to 1 and the uncertainty vanishes.
     % [[For species which actually co occur (?)]]
@@
 
-    It could be that the interaction is feasible, i.e.
+    It could be that we know an interaction is feasible, i.e.
 $L=1$, but that it does not occur at a given location or moment in time because there are local constraints, such as inclement weather or lack of suitable habitat, that prevent the interaction from occurring.
-We define the realisation of the interaction process $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L)=\chi$.
+We define the realisation of the interaction process with the variable $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L)=\chi$.
 This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology about the contingencies of interactions~\citep{}.
@@
     Lastly, measurement errors are always a source of uncertainty in the observation of ecological processes.
-We define the detection of an interaction $D$, given an interaction is feasible and occurs in the local conditions, as a stochastic process with associated probability $P(D|X,L)=\delta$.
+We define the detection of an interaction with the variable $D$, given an interaction is feasible and occurs in the local conditions, as a stochastic process with associated probability $P(D|X,L)=\delta$.
 Detection failure could happen for several reasons, for instance if the rearing of a parasitoid fails with inappropriate lab conditions, because of species mis-identification, or because the interaction is very rare.
@@
 the interaction occurred at the location but was not observed, and $D=1 \cup X = 0 \cup L =1$, the interaction is feasible and would have been detected but did not occur at the local site.
-
-  It is important to keep in mind that for network analysis, ecologists seek to measure the occurrence of true absences, which is the joint event $L=0 \cup X=1 \cup D=1$), but in reality they measure the marginal probability $P(L) = k/n$ where $k$ is again the number of observed interactions and $n$ the number of observed co-occurances.
+Ecologists seek to measure the occurrence of true absences, which is the joint event $L=0 \cup X=1 \cup D=1$), but in reality they measure the marginal probability $P(L) = k/n$ where $k$ is again the number of observed interactions and $n$ the number of observed co-occurrences.
 % I'm pretty sure this should be L=0 but X=1 and D=1: interaction not feasible but site and detection perfect.
+    %DG: YES
 
@@
   The basic information that we are collecting consists of matrices of interaction partners.
-Our count of interactions between species A and species B reflects uncertainty with respect to whether two species are capable of interacting when co-occurring at a given site, chance variation in whether the interaction is realised,  and uncertainty with respect to whether it is detected when realised.
+Our count of interactions between two species reflects uncertainty with respect to whether two species are capable of interacting when co-occurring at a given site ($\lambda$), chance variation in whether the interaction is realised ($\chi$),  and uncertainty with respect to whether it is detected when realised ($\delta$).
 In this case, what can we do to pin down any of these different types of variation?
 
-  A simple example will illustrate the problem: assume that we want to infer the probability of an interaction between two species, A and B.
+% DG: it's bizarre to present here the outcome of the naive binomial formulation, while the reasoning is provided later.
+My solution is to move the following section on the binomial model along with the figure within a box.
+It's not central, but formalizes the problem.
+It would respect the order of appearance and better emphasize the bayes section.
+
+  A simple example will illustrate the problem (the full reasoning is provided below): assume that we want to infer the probability of an interaction between two species, A and B.
 Now assume that in reality, interaction between A and B is completely impossible (i.e.
-the true $\lambda$= 0).
-Given no added detection error in observing the incidence of the interaction, then a single observation of species co-occurrence will reveal (very) little regarding the probability of the interaction – the confidence limits for one observation essentially spans from 0 to 1 (Fig.~\ref{upper_limits}).
+the true $\lambda=0$), but the observer does not know it and seeks to estimate this interaction probability.
+The record of the number of observed interactions will follow a binomial distribution, with number of trials $k$ and number of observations $n$, for which we can compute the confidence interval of the estimated probability $\lambda$.
+Given no added detection error in observing the incidence of the interaction, then a single observation of species co-occurrence will reveal (very) little regarding the probability of the interaction – the confidence limits for one observation essentially spans from 0 to 1 (Fig.~\ref{upper_limits} - using Clopper-Pearson's true confidence interval).
 For 5 observations, this confidence limit still extends to 0.5.
 Only with thirty observations will it shrink to 0.1.
-Thus, adding (many) more observations is certainly useful in controlling uncertainty due to stochasticity inherent in the process itself.
+Thus, adding (many) more observations is certainly useful in controlling uncertainty due to stochasticity inherent in the process itself, but the number of observations nonetheless needs to be very high.
 
@@
 
-  As a solution towards deciding whether unobserved interactions were undetected due to sampling, or whether they truly do not occur,~\citet{Weinstein2017} used daily repeated sampling rounds to estimate the daily probability of detecting a hummingbird interaction, and to thereby model the observation and process mechanisms~\citep{Weinstein2017}.
+  As a solution towards deciding whether unobserved interactions were undetected due to sampling, or whether they truly do not occur,~\citet{Weinstein2017} used repeated sampling rounds to estimate the daily probability of detecting a hummingbird interaction, and to thereby model the observation and process mechanisms.
 While conceptually attractive, this approach is unsuitable for interactions occurring over longer time scales (e.g., associations between hosts and parasitoids with a single generation per year), or very rare interactions (since no matter how frequently and extensively we sample, there will still be some interactions lurking around).
-What is worse, the problem persists that if a given interaction is not observed on a given day, this could be either because it was impossible that day despite being otherwise feasible (P($X|L=1$=0), because interaction between the two did occur but could not be observed (P($D|X$=1,L=1)=0), or from any combination of the two.
+What is worse, the problem persists that if a given interaction is not observed on a given day, this could be either because it was impossible that day despite being otherwise feasible (P($X|D=1,L=1$=0), because interaction between the two did occur but could not be observed (P($D|X$=1,L=1)=0), or from any combination of the two.
 From a conceptual perspective, this approach will thus fail to satisfactorily distinguish between sources of uncertainty.
@@
 This can bias the set of recorded interactions.
+
+% DG : I propose to maintain part of this paragraph that was commented out, just to keep the transition. 
+The bottom line is that separating different sources of uncertainty is difficult indeed.
+As an alternative to abandoning empirical networks or continuing to ignore the uncertainty inherent in undetected observations, we propose that some insight regarding the detectability of interactions between species not found co-occurring may be gained from data on other species between which interactions are known to be feasible.
 
@@
 The occurrence of an interaction is a Bernoulli trial.
-Consequently, the number of success[es] $k$ over $n$ trials will follow a binomial distribution:
+Consequently, the number of successes $k$ over $n$ trials will follow a binomial distribution:
 
@@
 
-  The situation where $k = 0$ is also problematic because we have very little information with which to estimate $\lambda$, in particular when $n$ is also small.
+% DG: The following should be removed to avoid repetitions
+%  The situation where $k = 0$ is also problematic because we have very little information with which to estimate $\lambda$, in particular when $n$ is also small.
 We therefore propose a Bayesian approach to solve this problem, building on two relevant features of such statistics: the posterior distribution of parameter estimates and usage of prior information.
@@
 
-  So many sources of interaction pooled into a single entity; hard to estimate.
+%  So many sources of interaction pooled into a single entity; hard to estimate.
 
-  MLE is zero if no interaction is detected, but there may still be a substantial probability of interaction should the two species co-occur.
+% MLE is zero if no interaction is detected, but there may still be a substantial probability of interaction should the two species co-occur.
 [This is particularly important in the context of a changing world, where species not co-occurring today – or species not detected co-occurring today – may well do so tomorrow, forming complex interactions.]
@@
 
-      We here adopt a Bayesian approach to estimate the distribution of the parameter $\theta$, the maximum likelihood estimate of the interaction probability.
-According to Bayes principle, the posterior distribution of $\theta$ is:
+    %DG: note that I replaced theta by lambda to follow the above definitions. Need to make sure it's done throughout
+    %DG: I realize there is an X in here that should be removed as well to avoid confusion with the above nomenclature
+
+      We here adopt a Bayesian approach to estimate the distribution of the parameter $\lambda$. According to Bayes principle, the posterior distribution of $\lambda$ is:
 
       \begin{equation}
-        \underbrace{P(\theta|X,n)}_{Posterior} = \frac{\overbrace{P(X|\theta,n)}^{Likelihood}\overbrace{P(\theta)}^{Prior}}{\underbrace{P(X|N)}_{Normaliser}} .
+        \underbrace{P(\lambda|X,n)}_{Posterior} = \frac{\overbrace{P(X|\lambda,n)}^{Likelihood}\overbrace{P(\lambda)}^{Prior}}{\underbrace{P(X|N)}_{Normaliser}} .
         \label{posterior}
@@
       According to the above description, the likelihood is simply the binomial distribution (Eq.~\ref{likelihood}).
-Since $\theta$ is a probability it is bounded between 0 and 1 and consequently the most appropriate prior distribution is the beta:
+Since $\lambda$ is a probability it is bounded between 0 and 1 and consequently the most appropriate prior distribution is the beta:
 
       \begin{equation}
-        \theta \sim Beta(\alpha,\beta) , \label{prior}
+        \lambda \sim Beta(\alpha,\beta) , \label{prior}
       \end{equation}
@@
 This allows us to analytically compute the posterior distribution of a binomial model with a beta prior distribution.
-We can re-write the posterior distribution of $\theta$ as:
+We can re-write the posterior distribution of $\lambda$ as:
 
       \begin{equation}
-        P(\theta|k,n) = \frac{\theta^{\alpha+k-1}(1-\theta)^{\beta+n-k-1}}{B(\alpha+k,\beta+n-k)} , \label{posterior}
+        P(\lambda|k,n) = \frac{\lambda^{\alpha+k-1}(1-\lambda)^{\beta+n-k-1}}{B(\alpha+k,\beta+n-k)} , \label{posterior}
       \end{equation}
 
-      \noindent where the function $B$ is the beta function:
+%      \begin{equation}
+%        Beta(\alpha+k,\beta+n-k) = \frac{\Gamma(\alpha+k)\Gamma(\beta+n-k)}{\Gamma(\alpha+\beta+n)} . \label{betafunction}
+%      \end{equation}
 
-      \begin{equation}
-        Beta(\alpha+k,\beta+n-k) = \frac{\Gamma(\alpha+k)\Gamma(\beta+n-k)}{\Gamma(\alpha+\beta+n)} . \label{betafunction}
-      \end{equation}
-
-      The posterior distribution of $\theta$ therefore follows the beta distribution with new parameters $\alpha'= \alpha+k$ and $\beta'=\beta+n-k$.
-The weight of the prior on the posterior distribution is understood from these definition of the parameters: the difference between the posterior and the prior will increase with $k$ and $n-k$.
+      \noindent where the function $B$ is the beta function.
+The posterior distribution of $\lambda$ therefore follows the beta distribution with new parameters $\alpha'= \alpha+k$ and $\beta'=\beta+n-k$.
+The weigth of the prior on the posterior distribution is understood from these definition of the parameters: the difference between the posterior and the prior will increase with $k$ and $n-k$.
 When plotted, we find the shape of the distribution gets narrower with $k$ and $n$ (Fig.~\ref{Salix_pdfs}).
+We also find an important difference between the salix-gallers and gallers-parasitoids because of the differences in the prior distributions.
       %
@@
 
+%DG :  I think we should add the MLE estimate along with the binomial confidence interval on the figure in order to better illustrate the impact of the prior (obviously only for one N).
+You may draw it with a line to contrast with polygons.
+
+%DG: otherwise the difference between the two interaction types is very interesting and useful to show the effect of the priors. Bravo ! 
       \begin{figure}[ht]
@@
 
-      The fact that the posterior distribution of $\theta$ follows a beta distribution makes it straightforward to compute moments and other properties.
+      The fact that the posterior distribution of $\lambda$ follows a beta distribution makes it straightforward to compute moments and other properties.
 
-      The \textbf{average} of $\theta$ is: 
+      The \textbf{average} of $\lambda$ is: 
           \begin{equation}
-            \bar{\theta} = \frac{\alpha+k}{\alpha+\beta+n} ,
+            \bar{\lambda} = \frac{\alpha+k}{\alpha+\beta+n} ,
             \label{mean}
@@
           \begin{equation}
-            Var(\theta|k) = \frac{(\alpha + k)(\beta + n - k)}{(\alpha + \beta + n)^{2}(\alpha + \beta + n +1)}
+            Var(\lambda|k) = \frac{(\alpha + k)(\beta + n - k)}{(\alpha + \beta + n)^{2}(\alpha + \beta + n +1)}
             \label{variance}
@@
           \begin{equation}
-            \hat{\theta} = \frac{\alpha + k - 1}{\alpha + \beta + n - 2} .
+            \hat{\lambda} = \frac{\alpha + k - 1}{\alpha + \beta + n - 2} .
             \label{mode}
@@
 These are called hyper parameters.
-Below we identify four ways to formulate the prior distribution of $\theta$.
+Below we identify four ways to formulate the prior distribution of $\lambda$.
 
@@
 
-          In absence of any external information, an uninformative prior is the most conservative hypothesis for the distribution of $\theta$.
-The beta distribution is in this case a uniform distribution  for $Beta(\alpha=1,\beta=1)$.
+          In absence of any external information, an uninformative prior is the most conservative hypothesis for the distribution of $\lambda$.
+The beta distribution is in this case a uniform distribution, specified with hyper parameters $\alpha=1$ and $\beta=1$.
 
@@
 A writeup for that process follows the original text:]]
+
+%DG: I think so, it is a very useful proposition in the paper to increasingly improve the quality of the prior. I just tried to cut it down in order to follow the above layout. 
+%DG: actually, once I got down to the following section, I realized that the example is based on the degree distribution, so there is not much choice to keep it
+
           The degree of a node in a network is defined as the number of interactions it has to other nodes.
-The degree distribution of a network is then the probability distribution of these degrees over the whole network.
-Connectance is an average property for a complete given network, and it represents the expected degree (expected number of interactions per species) standardised by the number of species in the network.
-The standardised degree could therefore be interpreted as an interaction probability.
+The degree distribution of a network is then the probability distribution of these degrees over the whole network and the standardised degree could therefore be interpreted as an interaction probability.
 It is consequently possible to use the degree distribution to inform the prior distribution.
@@
 The probability of any interaction $L_ij$ depends on the degrees of species $i$ and $j$.
-The degree of a node is defined as the number of interactions it has with other nodes.
-Connectance, as the average number of links per species in the whole network, is thus also the expected degree for any given species normalised by the number of species in the network.
 Using normalised degrees $\Delta_i$ and $\Delta_j$ (i.e., degrees divided by the number of species in the network), we can obtain the probability of interaction $L_ij$=$\Delta_i\times\Delta_j$.
@@
           [Tomas adds: This is a bit of a stump]
-          It is possible to estimate the probability of interaction between a pair of species if there is knowledge of their traits and some functions relating trait matching to interaction probability~\citep{Morales-Castilla2015}.
-There are several techniques available to perform this inference of interaction probability~\citep{} (REFS).
+%DG: I tried to expand just a little, but I don't want to get lost in this paragraph as it would be a distraction. We should basically mention it as a possibility.
+
+          The last approach we envision to document the prior distribution of $\lambda$ is to use the outcome of a trait-matching model, provided such a model has been documented using external data and relevant traits are available.
+          In such as case, the prior distribution would follow the function $P(\lambda|\mathbf{T})=f(\mathbf{T})$ based on a set of traits for both species $\mathbf{T}$.
+There are several techniques available to perform this inference of interaction probability, some of which are bayesian, and we refer to ~\citep{Bartomeus2016} and \citep{Weinstein2017} for recent reviews about this topic.
 Note that in this case the prior might not be beta distributed and numerical methods might be required to compute the posterior distribution.
+
+%DG: I want to be sure that the following example is clear and understandable for everyone. Tomas, Kate, both of you can follow the entire logic ? Would you be able to reproduce it using the R code ?
 
@@
   %Perhaps we want to also have a trait matching example in addition to the degree distribution example below?
+%DG: that would be great, but I think it will be simply too much and too mathy.
+
   % Are degree distributions valid priors for interaction probabilities in a unipartite web?
@@
 Suppose we have $n = 10$ observations of co-occurrence between species $i$ and species $j$ in a given time interval and area, and $k = 3$ observations of interactions.
-The maximum likelihood estimate of the interaction probability is simply $\theta_{MLE} = 3/10 = 0.3$.
+The maximum likelihood estimate of the interaction probability (Box 1) is simply $\lambda_{MLE} = 3/10 = 0.3$.
   % We should probabaly have a value  on the interaction probablitity that differs from the average of the degree distrbution
-   Now consider we know that species $i$ is known to interact with 10 other species, which have the following normalised degrees:
+
+%DG: the following example should provide first the real degree, and below the normalized degree. We need to help the reader translating degrees into interaction probabilities
+
+  Now consider we know that species $i$ is known to interact with 10 species (other than species $j$), which have the following normalised degrees:
 
@@
 
-    The mean of these interaction probabilities is 0.163, approximately half the $\theta_{MLE}$ obtained from the observed data.
-We can use the distribution of these interaction probabilities as our prior distribution and estimate the uncertainty surrounding our $\theta_{MLE}$.
-With some simple R code (function calculate\_parameters, \emph{Appendix S2}), we obtain prior parameters $\alpha$=1.050830
-    and $\beta$=5.365892. Using these priors in equations~\ref{mean} 
-    and~\ref{variance} above (or in the R function calculate\_distribution in \emph{Appendix S2}), we find a prior mean interaction probability of 0.16376436 and a prior variance of 0.02134199.
-
-    Adding the observed data (n=10, k=3) and using the same code,
-    we obtain posterior hyper parameters $\alpha'$=4.05083 and $\beta'$=12.36589 and a posterior mean 0.247 and variance 0.011 for the probability of interaction.
+    The mean of these interaction probabilities is 0.163, approximately half the $\lambda_{MLE}$ obtained from the observed data.
+We can use the distribution of these interaction probabilities as our prior distribution and estimate the uncertainty surrounding our $\lambda_{MLE}$.
+With some simple R code (function calculate\_parameters, \emph{Appendix S2}), we obtain prior parameters $\alpha$=1.050830 and $\beta$=5.365892.
+Using these priors in equations~\ref{mean} and~\ref{variance} above (or in the R function calculate\_distribution in \emph{Appendix S2}), we find a prior mean interaction probability of 0.16376436 and a prior variance of 0.02134199.
+Adding the observed data ($n=10$, $k=3$) and using the same code, we obtain posterior parameters $\alpha'$=4.05083 and $\beta'$=12.36589 and a posterior distribution of $\lambda$ with mean 0.247 and variance 0.011.
 Comparing the posterior distribution to the prior, we see that the posterior is closer to the observed data and that the additional data has reduced the variance.
-
 We may also wish to calculate a credible interval (analogous to the frequentist confidence interval).
@@
 
-    Now, consider the case where the two species have never been observed interacting across $n$ trials.
-The question is then ``what is the probability these two species do not interact''?
-Since it is not possible to prove that the two species could never interact, given the framework above we must fix a threshold below which we consider that there is no interaction.
-We call this threshold probability $\theta*$.
-We then use the cumulative distribution function to estimate $P(\theta<\theta*|X=0,n)$ for different $n$.
+    Now, consider the case where the two species have never been observed interacting across $n$ trials, i-e.
+$k=0$.
+The question is then ``what is the probability these two species do not interact''$?
+Since it is not possible to prove that the two species could never interact (strickly speaking, in such an approach $\lambda=0$ is impossible), given the framework above we must fix a threshold below which we consider that there is no interaction ($\lambda~0$).
+We call this threshold probability $\lambda*$.
+We then use the cumulative distribution function to estimate $P(\lambda<\lambda*|L=0,n)$ for different $n$.
 The
-    function plot\_precision in \emph{Appendix S2} calculates distribution function for $\theta*$ with an increasing number of trials. The figure below illustrates this distribution for $\theta*$=0.1.
-
-    The exercise exemplified above yields a surprising result: it requires \textgreater24 observations of no interactions to be 95\% sure that the interaction probability is smaller than 0.1 (recall Fig.~\ref{upper_limits}).
+    function plot\_precision in \emph{Appendix S2} calculates distribution function for $\lambda*$ with an increasing number of trials.
+The figure below illustrates this distribution for $\lambda*$=0.1.
+This yields a surprising result: it requires \textgreater24 observations of no interactions to be 95\% sure that the interaction probability is smaller than 0.1 (recall Fig.~\ref{upper_limits}).
 Note the special case where there is no observation of the two species co-occurring, $n = 0$  In this situation, the posterior distribution converges to the prior distribution since the data include no information on the probability with which species might interact should they co-occur; see above).
@@
 If we begin with no observed links for these pairs, then correcting for these false absences will inflate the number of links and consequently influence metrics such as connectance, nestedness, and degree distribution.
-While we can, as described above, calculate these network metrics using fixed estimates for $\lambda$ no analytical solution currently exists for uncertain $\lambda$.
+While we can, as described above, calculate these network metrics using fixed estimates for $\lambda$, no analytical solution currently exists for uncertain $\lambda$.
 Instead we must rely on computer simulations.
@@
 We will show how the uncertainty arising from both absences of co-occurrences and false absences of interactions impact these metrics.
-We find uncertainty influences both the average and the variance of network metrics, putting in perspective traditional network comparison studies where these metrics are assumed to be fixed entities.
+%We find uncertainty influences both the average and the variance of network metrics, putting in perspective traditional network comparison studies where these metrics are assumed to be fixed entities.
 
-\section*{Case study: estimating the uncertainty of a plant-herbivore network}
+%\section*{Case study: estimating the uncertainty of a plant-herbivore network}
 
@@
 
-      Importantly, while large, this network will illustrate the very real constraints on the sampling of ecological networks.
-As a baseline pattern, we may compare the frequency of co-occurrence of taxa in the example data set to the pattern of Fig.~\citep{upper_limits}.
+      Importantly, while large, this network illustrates the very real constraints on the sampling of ecological networks.
+As a baseline, we may compare the frequency of co-occurrence of taxa to reveal the challenge of having sufficiently large $n_{ij}$ (Fig.~\citep{upper_limits}).
 In the example data, most (3986 out of 4992) pairs of species are never found co-occurring, and for species found co-occurring the number of co-occurrences was generally low (Fig.~\ref{histograms}A).
+%DG: can you provide mean and variance in the text?
       Among the species which did sometimes interact when co-occurring, the incidence of interaction was actually low. 
+%DG: in the following, would be useful to present both absolute and relative numbers, or just relative
       Only 141 pairs of species were observed interacting: of these, 26 were observed interacting only once and 48.2\% were observed interacting five or fewer times (Fig.~\ref{histograms}B).
@@
 
+%DG: be careful : occurrence, not occurance on the figures
     \begin{figure}
       \caption{\textbf{A-B)} Most pairs of \emph{Salix} and galler or galler and parasitoid species were never observed co-occurring despite the high levels of replication in our example dataset.
-For those that were observed together at least once, the number of observed co-occurrences was generally small (\textless10).
+For those pairs that were observed together at least once ($n_{ij}>0$), the number of observed co-occurrences was generally small (\textless10).
 Here we show a histogram of the number of pairs of species observed co-occurring at least once.
@@
       \end{figure}
+%DG: I really appreciate this figure, it makes the point so clear.
 
-    \subsection*{Finding the maximum likelihood estimate}
+%    \subsection*{Finding the maximum likelihood estimate}
+
+  \subsection*{Computing the posterior distribution}
 
@@
 hookeriana} genotype-galler interactions based on the normalised degree of each species in each network component (see \emph{Appendix S1} for details and code).
-
-      Using this prior distribution of galler-\emph{Salix} interaction frequencies, we can obtain parameters for the prior distribution of $\lambda$ in our dataset.
-Specifically, we obtain $\alpha$=2.507217, $\beta$=1.888079.
+Specifically, we obtain prior parameters $\alpha$=2.507217 and $\beta$=1.888079.
 For the galler-parasitoid component of the network, the corresponding prior parameters are $\alpha$=1.341479, $\beta$=9.487966.
@@
 
-    \subsection*{Computing the posterior distribution}
-
       For species where no co-occurrences were observed, we can 
-      calculate the MLE estimates for the mean and variance of 
+      calculate the estimates for the mean and variance of 
       $\lambda_{ij}$ directly from this prior following 
@@
 Nevertheless, as the number of observed co-occurrence increases, the posterior mean becomes closer to zero and the posterior variance decreases (Fig.~\ref{Salix_pdfs}).
+
+%DG: the following subsection could be moved to the appendix if we need to cut down
 
@@
 
-    Using the prior distributions and procedures described above, we calculated posterior probability descriptions for each pair of \emph{Salix} and galler or galler and parasitoid species that were not observed interacting, with each posterior distribution reflecting the number of times the pair of species had been observed co-occurring.
+    Using the prior distributions and procedures described above, we calculated posterior probability distributions for each pair of \emph{Salix} and galler or galler and parasitoid species that were not observed interacting.
 Using these posterior distributions and assuming probabilities of 1 for pairs of species that were observed interacting, we created a suite of 100 webs of each network type by randomly sampling from each posterior distribution.
-These networks always included the interactions observed in the original network, as well as other interactions which may occur but have not been observed.
-
 After obtaining these posterior networks, we calculated the connectance of each web, as well as the number of links per resource (\emph{Salix} in the \emph{Salix}-galler networks or galler in the galler-parasitoid networks) and links per consumer.
-To demonstrate how these network metrics will be affected by detection uncertainty, we then created a suite of filtered networks for each posterior network.
+To demonstrate how these network metrics will be affected by detection uncertainty ($\delta$), we then created a suite of filtered networks for each posterior network.
 Networks were filtered by randomly sampling 99\%, 95\%, 90\%, 80\%, 70\&, 60\%, and 50\% of the interactions included in each posterior network.
+This gradient is akin to a gradient of sampling effort.
 For each level of detection accuracy, we created 100 randomly-sampled networks per posterior-probability network.
@@
 
-    Note that the posterior webs for the Salix-galler network all had much higher connectance than the original, observed web (C=0.028 for the observed web, Fig.~\ref{posterior_webs}).
+%DG: the different posterior connectance are the results of different samples of the posterior distribution, righ ?
+
+    We find, not surprisingly, that the posterior webs for the Salix-galler network all had much higher connectance than the original, observed web (C=0.028 for the observed web, Fig.~\ref{posterior_webs}).
 Likewise, the number of links per \emph{Salix} and galler species in the observed web (2.71 and 1.47, respectively) were much lower than those predicted in the posterior webs, even when filtering with a detection probability of only 50\%.

### 2017-11-20 manuscript/CI_interactions.tex
fixed a compilation error

@@
 $k=0$.
-The question is then ``what is the probability these two species do not interact''$?
-Since it is not possible to prove that the two species could never interact (strickly speaking, in such an approach $\lambda=0$ is impossible), given the framework above we must fix a threshold below which we consider that there is no interaction ($\lambda~0$).
+The question is then ``what is the probability these two species do not interact''?
+Since it is not possible to prove that the two species could never interact (strickly speaking, in such an approach $\lambda=0$ is impossible), given the framework above we must fix a threshold below which we consider that there is no interaction ($\lambda \sim 0$).
 We call this threshold probability $\lambda*$.
@@
       Importantly, while large, this network illustrates the very real constraints on the sampling of ecological networks.
-As a baseline, we may compare the frequency of co-occurrence of taxa to reveal the challenge of having sufficiently large $n_{ij}$ (Fig.~\citep{upper_limits}).
+As a baseline, we may compare the frequency of co-occurrence of taxa to reveal the challenge of having sufficiently large $n_{ij}$ (Fig.~\ref{upper_limits}).
 In the example data, most (3986 out of 4992) pairs of species are never found co-occurring, and for species found co-occurring the number of co-occurrences was generally low (Fig.~\ref{histograms}A).

### 2017-11-21 manuscript/CI_interactions.tex
added a shell for a box about the Salix data, Dom's comments to intro.

@@
 \usepackage{array}
+\usepackage{hyperref}
+\usepackage{float}
+\makeatletter
+
+% this creates a custom and simpler ruled box style
+\newcommand\floatc@simplerule[2]{{\@fs@cfont #1 #2}\par}
+\newcommand\fs@simplerule{\def\@fs@cfont{\bfseries}\let\@fs@capt\floatc@simplerule
+  \def\@fs@pre{\hrule height.8pt depth0pt \kern4pt}%
+  \def\@fs@post{\kern4pt\hrule height.8pt depth0pt \kern4pt \relax}%
+  \def\@fs@mid{\kern8pt}%
+  \let\@fs@iftopcapt\iftrue}
+
+% this code block defines the new and custom floatbox float environment
+\floatstyle{simplerule}
+\newfloat{floatbox}{thp}{lob}
+\floatname{floatbox}{Box}
 
@@
 
-\author{Dominique Gravel, \& Alyssa R. Cirtwill$^{1}$, Anna Ekl\"{o}f, Tomas Roslin, Kate Wootton}
+\author{Alyssa R. Cirtwill$^{1}$, Dominique Gravel, \&  Anna Ekl\"{o}f$^{1}$, Tomas Roslin$^{x,y}$, Kate Wootton$^{x}$}
 \date{\small$^1$Department of Physics, Chemistry\\ 
@@
 Link\"{o}ping, Sweden\\
+\medskip $^x$ Department of Ecology\\ P.O. Box 7044, Swedish University of Agricultural Sciences \\ SE-750 07 Uppsala, Sweden \\
+\medskip $^y$ Spatial Foodweb Ecology Group\\ Department of Agricultural Sciences \\ PO Box 27 (Latokartanonkaari 5)\\ FI-00014 University of Helsinki, Finland \\
 % \medskip
@@
 
-% A quantitative framework for investigating the reliability of network construction
-% D. Gravel, D. Carstensen, T. Poisot, D. Stouffer, A. Cirtwill
-
 \section*{Introduction}
 
-    % Present Salix data with holes as an example of uncertainty in data. Focus just on the white and grey, ignore uncertainty in the blacks
-
-  %DG : I cut down significantly the first paragraph, as I think we could assume readers know about networks and don't need to be convinced of their usage. 
-   Representation of species assemblages as a network offers a convenient summary of how communities are constructed, as it simultaneously account for species composition and their interactions.
-A tabulation of the nodes and of their relative abundances form the basis for traditional metrics of community composition.
-On top of this information, interactions are represented by links, so that networks provide additional, higher-order information on community structure.
-Empirical descriptions of ecological networks are however usually considered to be static representations of the communities and interactions they describe.
+    Representation of a species assemblage as a network offers a convenient summary of how the community is constructed as it simultaneously accounts for species composition and their interactions.
+A tabulation of the nodes (species) and of their relative abundances forms the basis for traditional metrics of community composition.
+On top of this information, interactions are represented by links between nodes so that networks provide additional, higher-order information on community structure.
+Empirical descriptions of ecological networks are, however, usually considered to be static representations of the communities and interactions they describe.
 This approach contrasts significantly with the widely recognized stochasticity of ecological communities \citep{Gotelli2000}.
 That is, whether the network is assembled based on aggregated data, a single intensive ``snapshot" sample, or expert knowledge, interactions are assumed to occur deterministically wherever and whenever the community is observed~\citep{Olesen2011a}.
-This assumption conflicts with known variation in interactions over time~\citep{Kitching1987,Olesen2011a} and space~\citep{Kitching1987,Baiser2012} and between individuals of a given species~\citep{Pires2011a,Fodrie2015,Novak2015}.
 
-    Efforts to account for the variability in interaction occurrence and frequency are complicated by the fact that not only species but also interactions vary over space and time.
+    The assumption of static communities conflicts with known variation in both  the nodes and links included in a network.
 Community composition and species abundances vary from site to site~\citep{Baiser2012} and over time within a site~\citep{Olesen2011a}.
-The removal of a species from a site will obviously also remove its interactions, but the co-occurrence of potentially interacting species do not guarantee they will.
-Interactions can be lost, or not detected, if participating species remain present but do not co-occur temporally, are too rare to detect each other~\citep{Tylianakis2010}, because of environmental contingencies \citep{Poisot2015a} or through changes to individual preferences~\citep{Fodrie2015}.
+Likewise, interactions over space~\citep{Kitching1987,Baiser2012}, time~\citep{Kitching1987,Olesen2011a}, and between individuals of a given species~\citep{Pires2011a,Fodrie2015,Novak2015}.
+Moreover, variability in community composition and interactions may or may not be closely related.
+The removal of a species from a site will obviously also remove its interactions, but the co-occurrence of potentially interacting species do not guarantee they will interact at a given place and time.
+Interactions can be lost, or not detected, if participating species remain present but do not co-occur temporally, are too rare to detect each other~\citep{Tylianakis2010}, because of environmental contingencies \citep{Poisot2015a}, or through changes to individual preferences~\citep{Fodrie2015}.
 
     Beyond ``true" variation in network structure, several researchers have pointed to the importance of sampling intensity for the assessment of network structure (e.g.,~\citealp{Martinez1999,Bluthgen2006,XX}).
-Accumulation of interactions with increasing sampling effort suggests that it is even more challenging to document them than species richness \citep{Poisot2012}.
+Accumulation of interactions with increasing sampling effort suggests that it is even more challenging to document interactions than species richness \citep{Poisot2012}.
 As a result, it was proposed that interactions should be described probabilistically and network metrics computed accordingly \citep{Poisot2015b}.
 Despite this, the acknowledgment that insufficient sampling effort limits our ability to describe variation in ecological networks has not yet led to a quantitative methodology to deal with the uncertainty generated by spatiotemporal variation in ecological interactions and by sampling.
+Moreover, even in extremely well-sampled networks uneven sampling across species (or pairs of species) can lead to the assumption that some species do not interact because they co-occur rarely or have not yet been observed co-occuring (see Box 1).
+It is therefore likely that nearly all network studies are missing some interactions and could benefit from an approach that acknowledges this uncertainty.
 
+\begin{floatbox}{}
+
+  We have lots and lots of data, but still not enough for almost all pairs of species.   
 % DG : I wonder if a paragraph summarizing the extent of the problem with the salix data should not be provided here.
@@
 But we need to convingly show how large is this problem even for such an extensive dataset
+% AC : I like the box idea. Since we refer to the Salix data throughout the manuscript it makes sense to make it stand out.
+
+  \caption{\emph{Salix} dataset}
+  \label{box1}
+\end{floatbox}
 
@@
 We then define a framework which identifies and dissects the different contributions to uncertainty of interaction.
-We illustrate this framework with a simple quantitative example using the most extensively sample network to date.
+We illustrate this framework with a simple quantitative example using the most extensively sampled network to date (see Box 1).
 Next, we use the framework to provide analytical criteria for improving the sampling of rare interactions.

### 2017-11-22 manuscript/CI_interactions.tex
finished the box maybe

@@
 
+    As a case study, we use an extensively sampled \emph{Salix}-galler-parasitoid meta-network.
+This dataset consists of a single community type sampled across Europe; willow (\emph{Salix}) species, willow-galling sawflies, and their natural enemies.
+The data were collected over 29 years at 374 unique locations across Europe, with a total of 641 site visits.
+Each site visit can be considered as a network in its own right and an independent sample from which to build the meta-network.
+The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes.
+The high spatiotemporal resolution of this network and the unusually high sampling effort implemented at the site level makes this dataset particularly well suited for illustrating the difficulties in completely sampling a network and testing Bayesian approaches to overcome these difficulties.
+
+    We may begin by comparing the frequency of of co-occurence of taxa to reveal the challenge of having sufficient sampling to be confident that an interaction does not occur (Fig.~\ref{upper_limits}).
+Most pairs of species (3986/4992 \emph{Salix}-galler pairs and  9794/12096 galler-natural enemy pairs) are never found co-occurring, and for species that did occur the number of co-occurrences was generally low (mean=4.24, var=36.3 for \emph{Salix}-galler pairs; mean=3.87, var=28.8 for galler-natural enemy pairs; Fig.~\ref{histograms}A-B).
+For those species which interacted when co-occurring, the incidence of interaction was also low (mean=12.0, var=155 for \emph{Salix}-galler pairs; mean=4.04, var=29.3 for galler-natural enemy pairs; Fig.~\ref{histograms}C-D).
+Only 2.82\% of \emph{Salix}-galler pairs and 7.76\% of galler-natural enemy pairs were observed interacting at all.
+Thus, even in the most extensive data set that we could find, limited sampling is clearly a major source of uncertainty.
+
   \caption{\emph{Salix} dataset}
@@
 \end{floatbox}
+
+%DG: be careful : occurrence, not occurance on the figures
+    \begin{figure}
+      \caption{\textbf{A-B)} Most pairs of \emph{Salix} and galler or galler and parasitoid species were never observed co-occurring despite the high levels of replication in our example dataset.
+For those pairs that were observed together at least once ($n_{ij}>0$), the number of observed co-occurrences was generally small (\textless10).
+Here we show a histogram of the number of pairs of species observed co-occurring at least once.
+3986 pairs of species were never observed co-occurring: these pairs are omitted from the histogram.
+\textbf{C-D)} Most pairs of species that were observed at the same site were never observed interacting.
+Here we show a histogram of the number of observed interactions within pairs of co-occurring species.
+\textbf{E-F)} Here we show, for each species pair, the number of observed interactions plotted against the number of observed co-occurrences.
+Most pairs either are never observed interacting or interact almost every time they co-occur.
+The red, dashed line indicates a 1:1 relationship between interactions and co-occurrences.}
+      \label{histograms}
+      \includegraphics*[width=.8\textwidth]{figures/Salix_Galler_histogram.eps}
+      \end{figure}
+
+%DG: I really appreciate this figure, it makes the point so clear.
 
@@
       \end{figure}
+
 %DG: I really appreciate this figure, it makes the point so clear. 
-
 %    \subsection*{Finding the maximum likelihood estimate}

### 2017-11-22 code/figure_generation/observation_interaction_histogram.py
corrected histogram labels

@@ -108,7 +108,7 @@ def format_graph(graph,graphtype,nettype):
   if graphtype=='interacts':
     xtext="Observed interactions"
   else:
-    xtext="Observed co-occurances"
+    xtext="Observed co-occurences"
   if graphtype=='dotplot':
     ytext="Observed interactions"
   else:
@@ -177,9 +177,9 @@ grace.multi(rows=3,cols=2,vgap=.08,hgap=.04)
 grace.hide_redundant_labels()
 
 # Just add row labels and you're done.
-grace.set_row_xaxislabel(colspan=(None,None),row=0,label="Observed co-occurances",just=2,char_size=1,perpendicular_offset=0.05)
+grace.set_row_xaxislabel(colspan=(None,None),row=0,label="Observed co-occurences",just=2,char_size=1,perpendicular_offset=0.05)
 grace.set_row_xaxislabel(colspan=(None,None),row=1,label="Observed interactions",just=2,char_size=1,perpendicular_offset=0.05)
-grace.set_row_xaxislabel(colspan=(None,None),row=2,label="Observed co-occurances",just=2,char_size=1,perpendicular_offset=0.05)
+grace.set_row_xaxislabel(colspan=(None,None),row=2,label="Observed co-occurences",just=2,char_size=1,perpendicular_offset=0.05)
 
 # grace.set_col_yaxislabel(rowspan=(None,None),col=0,label="Species pairs",just=2,char_size=1)
 # grace.graphs[0].set_view(0.15,0.73,0.55,0.95)

### 2017-11-22 manuscript/CI_interactions.tex
added a few more refs

@@
 The removal of a species from a site will obviously also remove its interactions, but the co-occurrence of potentially interacting species do not guarantee they will interact at a given place and time.
-Interactions can be lost, or not detected, if participating species remain present but do not co-occur temporally, are too rare to detect each other~\citep{Tylianakis2010}, because of environmental contingencies \citep{Poisot2015a}, or through changes to individual preferences~\citep{Fodrie2015}.
+Interactions can be lost, or not detected, if participating species remain present but do not co-occur temporally, are too rare to detect each other~\citep{Tylianakis2010}, because of environmental contingencies \citep{Poisot2015}, or through changes to individual preferences~\citep{Fodrie2015}.
 
@@
 Accumulation of interactions with increasing sampling effort suggests that it is even more challenging to document interactions than species richness \citep{Poisot2012}.
-As a result, it was proposed that interactions should be described probabilistically and network metrics computed accordingly \citep{Poisot2015b}.
+As a result, it was proposed that interactions should be described probabilistically and network metrics computed accordingly \citep{Poisot2016}.
 Despite this, the acknowledgment that insufficient sampling effort limits our ability to describe variation in ecological networks has not yet led to a quantitative methodology to deal with the uncertainty generated by spatiotemporal variation in ecological interactions and by sampling.
@@
 
-  We have lots and lots of data, but still not enough for almost all pairs of species.   
 % DG : I wonder if a paragraph summarizing the extent of the problem with the salix data should not be provided here.
@@
 
-    As a case study, we use an extensively sampled \emph{Salix}-galler-parasitoid meta-network.
+    \indent As a case study, we use an extensively sampled \emph{Salix}-galler-parasitoid meta-network.
 This dataset consists of a single community type sampled across Europe; willow (\emph{Salix}) species, willow-galling sawflies, and their natural enemies.
@@
 
-    We may begin by comparing the frequency of of co-occurence of taxa to reveal the challenge of having sufficient sampling to be confident that an interaction does not occur (Fig.~\ref{upper_limits}).
+    \indent We may begin by comparing the frequency of of co-occurence of taxa to reveal the challenge of having sufficient sampling to be confident that an interaction does not occur (Fig.~\ref{upper_limits}).
 Most pairs of species (3986/4992 \emph{Salix}-galler pairs and  9794/12096 galler-natural enemy pairs) are never found co-occurring, and for species that did occur the number of co-occurrences was generally low (mean=4.24, var=36.3 for \emph{Salix}-galler pairs; mean=3.87, var=28.8 for galler-natural enemy pairs; Fig.~\ref{histograms}A-B).
@@
 Ecologists seek to measure the occurrence of true absences, which is the joint event $L=0 \cup X=1 \cup D=1$), but in reality they measure the marginal probability $P(L) = k/n$ where $k$ is again the number of observed interactions and $n$ the number of observed co-occurrences.
-% I'm pretty sure this should be L=0 but X=1 and D=1: interaction not feasible but site and detection perfect.
-    %DG: YES
 
@@
 This can bias the set of recorded interactions.
-
   % DG : I propose to maintain part of this paragraph that was commented out, just to keep the transition. 
@@
 
-          [[Should we still have this?
+          % [[Should we still have this?
 At the workshop we talked about how interaction probabilities depend on the degrees of both species and so I'm using predicted interaction probabilities (degreeA*degreeB) in the galler example.
@@
 
-          [Tomas adds: This is a bit of a stump]
+          % [Tomas adds: This is a bit of a stump]
 %DG: I tried to expand just a little, but I don't want to get lost in this paragraph as it would be a distraction. We should basically mention it as a possibility.
@@
 Instead we must rely on computer simulations.
-In the following section, we will provide an empirical example, based on the data set published by~\citet{Kopelke2017}.
+In the following section, we will provide an empirical example, based on the data set published by~\citet{Kopelke2017} (see Box~\ref{box1}).
 We will show how the uncertainty arising from both absences of co-occurrences and false absences of interactions impact these metrics.
 %We find uncertainty influences both the average and the variance of network metrics, putting in perspective traditional network comparison studies where these metrics are assumed to be fixed entities.
-
-%\section*{Case study: estimating the uncertainty of a plant-herbivore network}
-
-    \subsection*{Description of the data}
-
-      We use an extensively sampled \emph{Salix}-galler-parasitoid meta-network as a case study.
-This dataset consists of a single community type sampled across Europe; willow (\emph{Salix}) species, willow-galling sawflies (Hymenoptera, Tenthredinidae, Nematinae, Euurina), and their natural enemies (hymenopteran parasitoids and coleopteran, lepidopteran, dipteran, and hymenopteran inquilines).
-The data were collected over 29 years (1982-2010) at 374 unique locations across Europe ranging from Sicily to the Arctic.
-Including repeated visits to a number of sites, the data set contains 641 site-visits, each of which can be considered as a network in its own right.
-Here we consider each network as an independent sample from which to build the meta-network.
-The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes and 126 natural enemy nodes.
-Interactions were determined by dissecting and rearing gall inhabitants from 165,424 galls.
-The high spatiotemporal resolution of this network and the unusually high sampling effor implemented at the site level (641 site-visits, which can be considered as repeated samples of the network) makes this dataset particularly well suited for testing this method.
-
-      Importantly, while large, this network illustrates the very real constraints on the sampling of ecological networks.
-As a baseline, we may compare the frequency of co-occurrence of taxa to reveal the challenge of having sufficiently large $n_{ij}$ (Fig.~\ref{upper_limits}).
-In the example data, most (3986 out of 4992) pairs of species are never found co-occurring, and for species found co-occurring the number of co-occurrences was generally low (Fig.~\ref{histograms}A).
-%DG: can you provide mean and variance in the text?
-      Among the species which did sometimes interact when co-occurring, the incidence of interaction was actually low. 
-%DG: in the following, would be useful to present both absolute and relative numbers, or just relative
-      Only 141 pairs of species were observed interacting: of these, 26 were observed interacting only once and 48.2\% were observed interacting five or fewer times (Fig.~\ref{histograms}B).
-Thus, even in the most extensive data set that we could find, limited sampling is clearly a major source of uncertainty.
-
-%DG: be careful : occurrence, not occurance on the figures
-    \begin{figure}
-      \caption{\textbf{A-B)} Most pairs of \emph{Salix} and galler or galler and parasitoid species were never observed co-occurring despite the high levels of replication in our example dataset.
-For those pairs that were observed together at least once ($n_{ij}>0$), the number of observed co-occurrences was generally small (\textless10).
-Here we show a histogram of the number of pairs of species observed co-occurring at least once.
-3986 pairs of species were never observed co-occurring: these pairs are omitted from the histogram.
-\textbf{C-D)} Most pairs of species that were observed at the same site were never observed interacting.
-Here we show a histogram of the number of observed interactions within pairs of co-occurring species.
-\textbf{E-F)} Here we show, for each species pair, the number of observed interactions plotted against the number of observed co-occurrences.
-Most pairs either are never observed interacting or interact almost every time they co-occur.
-The red, dashed line indicates a 1:1 relationship between interactions and co-occurrences.}
-      \label{histograms}
-      \includegraphics*[width=.8\textwidth]{figures/Salix_Galler_histogram.eps}
-      \end{figure}
-
-%DG: I really appreciate this figure, it makes the point so clear. 
-%    \subsection*{Finding the maximum likelihood estimate}
 
@@
 %DG: the different posterior connectance are the results of different samples of the posterior distribution, righ ? 
+%Yes
 

### 2017-11-23 manuscript/CI_interactions.tex
adding corrections

@@
 
-\title{???A quantitative framework for investigating the reliability of network construction}
+\title{A quantitative framework for investigating the reliability of network construction}
 
@@
 Community composition and species abundances vary from site to site~\citep{Baiser2012} and over time within a site~\citep{Olesen2011a}.
-Likewise, interactions over space~\citep{Kitching1987,Baiser2012}, time~\citep{Kitching1987,Olesen2011a}, and between individuals of a given species~\citep{Pires2011a,Fodrie2015,Novak2015}.
+Likewise, interactions vary over space~\citep{Kitching1987,Baiser2012}, time~\citep{Kitching1987,Olesen2011a}, and between individuals of a given species~\citep{Pires2011a,Fodrie2015,Novak2015}.
 Moreover, variability in community composition and interactions may or may not be closely related.
@@
 
-    Beyond ``true" variation in network structure, several researchers have pointed to the importance of sampling intensity for the assessment of network structure (e.g.,~\citealp{Martinez1999,Bluthgen2006,XX}).
+    Beyond ``true" variation in network structure, several researchers have pointed to the importance of sampling intensity for the assessment of network structure (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007}).
 Accumulation of interactions with increasing sampling effort suggests that it is even more challenging to document interactions than species richness \citep{Poisot2012}.
-As a result, it was proposed that interactions should be described probabilistically and network metrics computed accordingly \citep{Poisot2016}.
-Despite this, the acknowledgment that insufficient sampling effort limits our ability to describe variation in ecological networks has not yet led to a quantitative methodology to deal with the uncertainty generated by spatiotemporal variation in ecological interactions and by sampling.
-Moreover, even in extremely well-sampled networks uneven sampling across species (or pairs of species) can lead to the assumption that some species do not interact because they co-occur rarely or have not yet been observed co-occuring (see Box 1).
+As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly \citep{Poisot2016}.
+Despite this possibility, the acknowledgment that insufficient sampling effort limits our ability to describe variation in ecological networks has not yet led to a quantitative methodology to deal with the uncertainty generated by spatiotemporal variation in ecological interactions and by sampling.
+Moreover, even in extremely well-sampled networks uneven sampling across species (or pairs of species) can lead to the assumption that some species do not interact because they co-occur rarely or have not yet been observed co-occuring (see Box 1 for an example).
 It is therefore likely that nearly all network studies are missing some interactions and could benefit from an approach that acknowledges this uncertainty.
@@
 
-    \indent We may begin by comparing the frequency of of co-occurence of taxa to reveal the challenge of having sufficient sampling to be confident that an interaction does not occur (Fig.~\ref{upper_limits}).
+    \indent We may begin by comparing the frequency of of co-occurence of taxa to reveal the challenge of having sufficient sampling to be confident that an interaction does not occur.
 Most pairs of species (3986/4992 \emph{Salix}-galler pairs and  9794/12096 galler-natural enemy pairs) are never found co-occurring, and for species that did occur the number of co-occurrences was generally low (mean=4.24, var=36.3 for \emph{Salix}-galler pairs; mean=3.87, var=28.8 for galler-natural enemy pairs; Fig.~\ref{histograms}A-B).
@@
 Thus, even in the most extensive data set that we could find, limited sampling is clearly a major source of uncertainty.
+This dataset also illustrates the potential for increased sampling to not necessarily reveal more interactions as a pair of species that interacts in some cases may not be observed interacting in all cases (Fig.~\ref{histograms}E-F).
 
@@
     \begin{figure}
-      \caption{\textbf{A-B)} Most pairs of \emph{Salix} and galler or galler and parasitoid species were never observed co-occurring despite the high levels of replication in our example dataset.
+      \caption{\textbf{A-B)} Most pairs of \emph{Salix} and gallers or gallers and natural enemies were never observed co-occurring despite the high levels of replication in our example dataset.
 For those pairs that were observed together at least once ($n_{ij}>0$), the number of observed co-occurrences was generally small (\textless10).
 Here we show a histogram of the number of pairs of species observed co-occurring at least once.
-3986 pairs of species were never observed co-occurring: these pairs are omitted from the histogram.
+3986 \emph{Salix}-galler and 9794 galler-enemy pairs were never observed co-occurring: these pairs are omitted from the histogram.
 \textbf{C-D)} Most pairs of species that were observed at the same site were never observed interacting.
@@
 \textbf{E-F)} Here we show, for each species pair, the number of observed interactions plotted against the number of observed co-occurrences.
-Most pairs either are never observed interacting or interact almost every time they co-occur.
-The red, dashed line indicates a 1:1 relationship between interactions and co-occurrences.}
+Most \emph{Salix}-galler pairs either are never observed interacting or interact almost every time they co-occur, while galler-enemy pairs had more variable frequencies of interaction.
+In panels E and F the red, dashed line indicates a 1:1 relationship between interactions and co-occurrences.}
       \label{histograms}
@@
 We then define a framework which identifies and dissects the different contributions to uncertainty of interaction.
-We illustrate this framework with a simple quantitative example using the most extensively sampled network to date (see Box 1).
+We illustrate this framework with a simple quantitative example using the most extensively sampled network to date (Box 1).
 Next, we use the framework to provide analytical criteria for improving the sampling of rare interactions.
@@
   To define the problem associated with describing ecological interaction networks, we will start from the perspective of an empirical community ecologist faced with the task of describing an interaction network.
-This ecologist will be interested in generating a description of the blocks present, and the links between them (Roslin and Majaneva 2017).
+This ecologist will be interested in generating a description of the species/nodes present, and the links between them~\citep{Roslin2016}.
 Importantly, the information sought is conveyed by both the presence and \emph{absence} of links.
-An observed link will always remain an observed link, but as to why given links are not observed, there may be multiple contributions.
-Thus, we will set off by contemplating what factors may contribute to links missing from the matrix.
-We consider that there are three nested levels of uncertainty making the occurrence of any interaction a stochastic process:
+The two types of information are not, however, equally certain.
+An observed link will always remain an observed link, but there are multiple reasons why a given link may not be observed.
+Thus, the detection of any interaction is a stochastic process.
+We consider that there are three nested levels of uncertainty contributing to this stochasticity:
 
@@
 We define the probability of an interaction $L$ given those characteristics $\mathbf{T}$ as $P(L | \mathbf{T})=\lambda$.
-Obviously, if $k$ (the number of observed interactions) is 0, it is possible that the two species cannot interact even if there were no time or environmental constraints preventing it to occur.
-In such case, $\lambda$ would take a value of 0.
+Obviously, if $k$ (the number of observed interactions) is 0, it is possible that the two species cannot interact even if there were no time or environmental constraints preventing it from occurring.
+In such cases, $\lambda$ would take a value of 0.
     % [[The previous sentence doesn't follow, k hasn't been defined and we don't know that it's zero.
@@
 It arises because every model is imperfect and lacks information (i.e.
-traits) about the constraints on the interaction.
+about traits) defining the constraints on the interaction.
 In other words, with sufficient sampling and all information accessible, this interaction probability $\lambda$ should either tend to 0 or to 1 and the uncertainty vanishes.
@@
     It could be that we know an interaction is feasible, i.e.
-$L=1$, but that it does not occur at a given location or moment in time because there are local constraints, such as inclement weather or lack of suitable habitat, that prevent the interaction from occurring.
+$L=1$, but that it does not occur at a given location or moment in time because of local constraints such as inclement weather or lack of suitable habitat.
 We define the realisation of the interaction process with the variable $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L)=\chi$.
-This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology about the contingencies of interactions~\citep{}.
+This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology about the contingencies of interactions.
+Phenological matching~\citep{MillerRushing2010,Gezon2016}, species preferences~\citep{Pires2011,Novak2015,Coux2016}, and fear effects of other species~\citep{} are just some of the factors contributing to variation in the frequency of interactions between a given pair of species.
     % We imagine for instance that an interaction between a gall and a parasitoid might not be recorded at a location because it was the wrong time of the year and the gall had not yet formed (phenological constraints), a late frost killed the larvae (an abiotic environmental constraint), another parasitoid species competitively excluded the parasitoid species of interest (a biotic environmental constraint) or simply the parasitoid is too rare to interact with all of its viable hosts (an abundance constraint).
@@
 We define the detection of an interaction with the variable $D$, given an interaction is feasible and occurs in the local conditions, as a stochastic process with associated probability $P(D|X,L)=\delta$.
-Detection failure could happen for several reasons, for instance if the rearing of a parasitoid fails with inappropriate lab conditions, because of species mis-identification, or because the interaction is very rare.
+Detection failure could happen for several reasons, for instance if the rearing of a parasitoid fails with inappropriate lab conditions, because of species mis-identification, or because the interaction is very rare (see~\citet{Wirta2014,FrostXX} for examples of some of these difficulties and partial solutions to them).
 Some sources of detection error could be minimised with appropriate sampling effort ($\delta$ will converge to one with increasing number of samples), but other sources are often difficult to reduce (e.g.
-the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification).
+the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification as in~\citet{Wirta2014,FrostXX}).
 
@@
 
-    The combination of these three sources of uncertainty together leads to many potential explanations for the observation of an absence of interaction, but only the situation where $L = 0$ (a true absence) is relevant for the investigation of networks.
+    The combination of these three sources of uncertainty together leads to many potential explanations for the observation of an absence of interaction ($D$, $X$, and/or $L = 0$), but only the situation where $L = 0$ (a true absence) is relevant for the investigation of networks.
 While the observation of an interaction is straightforward to interpret, absence of interactions must be decomposed into different quantities.
@@
 
-  For the ecologist working on collecting network data, and on later interpreting these data, the considerations above raise a major challenge: how may we infer whether unobserved interactions went undetected due to sampling, or whether they truly do not occur.
+  For the ecologist collecting or interpreting network data, the considerations above raise a major challenge: how may we infer whether unobserved interactions went undetected due to sampling, or whether they truly do not occur.
 How then may we refine our sampling approaches to reduce uncertainties, and to gain insights into the impact of multiple processes on field observations?
-Importantly, some sources of uncertainty can be minimised with appropriate sampling design and efforts, while other sources are difficult or impossible to reduce – since they are generated by chance variation created by the very process in which we are interested.
+Importantly, some sources of uncertainty can be minimised with appropriate sampling design and efforts while other sources are difficult or impossible to reduce since they are generated by chance variation created by the very process in which we are interested.
 
@@
 Now assume that in reality, interaction between A and B is completely impossible (i.e.
-the true $\lambda=0$), but the observer does not know it and seeks to estimate this interaction probability.
+the true $\lambda=0$), but the observer does not know this and seeks to estimate this interaction probability ($\lambda$).
 The record of the number of observed interactions will follow a binomial distribution, with number of trials $k$ and number of observations $n$, for which we can compute the confidence interval of the estimated probability $\lambda$.
-Given no added detection error in observing the incidence of the interaction, then a single observation of species co-occurrence will reveal (very) little regarding the probability of the interaction – the confidence limits for one observation essentially spans from 0 to 1 (Fig.~\ref{upper_limits} - using Clopper-Pearson's true confidence interval).
+Given no added detection error in observing the incidence of the interaction, then a single observation of species co-occurrence will reveal very little regarding the probability of the interaction – the confidence limits for one observation essentially spans from 0 to 1 (Fig.~\ref{upper_limits} - using Clopper-Pearson's true confidence interval).
 For 5 observations, this confidence limit still extends to 0.5.
 Only with thirty observations will it shrink to 0.1.
-Thus, adding (many) more observations is certainly useful in controlling uncertainty due to stochasticity inherent in the process itself, but the number of observations nonetheless needs to be very high.
+Thus, adding m ore observations is certainly useful in controlling uncertainty due to stochasticity inherent in the process itself, but the number of observations nonetheless needs to be very high.
 
@@
 interactions occurring with a low probability).
-Yet, since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions.
+Yet, since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present; see Fig.~\ref{histograms}E-F), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions.
 Thus, the more we sample, the more zeros will appear in our interaction matrix, which may seem like a counter-intuitive outcome.
@@
   As a solution towards deciding whether unobserved interactions were undetected due to sampling, or whether they truly do not occur,~\citet{Weinstein2017} used repeated sampling rounds to estimate the daily probability of detecting a hummingbird interaction, and to thereby model the observation and process mechanisms.
-While conceptually attractive, this approach is unsuitable for interactions occurring over longer time scales (e.g., associations between hosts and parasitoids with a single generation per year), or very rare interactions (since no matter how frequently and extensively we sample, there will still be some interactions lurking around).
-What is worse, the problem persists that if a given interaction is not observed on a given day, this could be either because it was impossible that day despite being otherwise feasible (P($X|D=1,L=1$=0), because interaction between the two did occur but could not be observed (P($D|X$=1,L=1)=0), or from any combination of the two.
+While conceptually attractive, this approach is unsuitable for interactions occurring over longer time scales (e.g., associations between hosts and parasitoids with a single generation per year), or very rare interactions which might not occur on any of the sampling days or might involve individuals of a species that are not under observation.
+What is worse, the problem persists that if a given interaction is not observed on a given day, this could be either because it was impossible that day despite being otherwise feasible [$P(X|D=1,L=1)=0$], because interaction between the two did occur but could not be observed [$P(D|X=1,L=1)=0$], or from any combination of the two.
 From a conceptual perspective, this approach will thus fail to satisfactorily distinguish between sources of uncertainty.
-An interaction not observed on day $t$ may have gone undetected either because there were constraints on the process (i.e.
-the probability $\lambda$ was really zero) or because of chance variation in the realised incidence of an event associated with a finite probability.
 Most importantly, if two species are never observed co-occurring during several days of sampling then we have learned nothing about their probability of interacting if they should ever co-occur.
-In other words, there is no information without co-occurrence.
+In other words, there is no information about interactions without co-occurrence.
 

### 2017-11-23 manuscript/CI_interactions.tex
almost finished my corrections

@@
 \begin{floatbox}{}
-
 % DG : I wonder if a paragraph summarizing the extent of the problem with the salix data should not be provided here.
@@
 % AC : I like the box idea. Since we refer to the Salix data throughout the manuscript it makes sense to make it stand out. 
-
     \indent As a case study, we use an extensively sampled \emph{Salix}-galler-parasitoid meta-network.
@@
 The high spatiotemporal resolution of this network and the unusually high sampling effort implemented at the site level makes this dataset particularly well suited for illustrating the difficulties in completely sampling a network and testing Bayesian approaches to overcome these difficulties.
-
     \indent We may begin by comparing the frequency of of co-occurence of taxa to reveal the challenge of having sufficient sampling to be confident that an interaction does not occur.
@@
 This dataset also illustrates the potential for increased sampling to not necessarily reveal more interactions as a pair of species that interacts in some cases may not be observed interacting in all cases (Fig.~\ref{histograms}E-F).
-
   \caption{\emph{Salix} dataset}
@@
   An added complication is that not all sources of uncertainty are proportional to sample size.
-To record an interaction between A and B, we need to identify both partners correctly (a non-trivial problem in many food webs; e.g.~\citet{Kaartinen2011,Roslin2016}) and be able to resolve all interactions with a similar likelihood.
-For both molecular~\citep{} and rearing~\citep{} techniques, certain types of interactions may go unnoticed due to technical challenges.
+To record an interaction between A and B, we need to identify both partners correctly (a non-trivial problem in many food webs; e.g.~\citealp{Kaartinen2011,Roslin2016}) and be able to resolve all interactions with a similar likelihood.
+For both molecular and rearing techniques, certain types of interactions may go unnoticed due to technical challenges~\citep{Wirta2016}.
 This can bias the set of recorded interactions.
-  % DG : I propose to maintain part of this paragraph that was commented out, just to keep the transition. 
 The bottom line is that separating different sources of uncertainty is difficult indeed.
@@
   % [[Pretty sure this will always depend on the study - also seems like a pretty large digression.]]
-
-  % The bottom line is that separating different sources of uncertainty is difficult indeed.
-In the best of all possible worlds, we might use an experimental approach to estimate detection uncertainty by creating replicate cases where the interaction really occurs and then evaluating the fraction of cases where the interaction is detected.
-Yet, as anyone attempting these experiments will know, most interaction partners are notoriously unwilling to collaborate.
-Gallers refuse to lay eggs on their host plants in captivity (ref ref) and parasitoids decline to attack their hosts when experimentally introduced (Gariepy 2017; ref ref).
-If we introduce only one of the components (as in the cases where we expose a set of hosts to parasitism; ref ref; Gripenberg et al.
-xxx) then we are already confounding multiple levels of uncertainty since it is not certain whether the interaction will occur or whether we can detect it.
-To perform these experiments in a comprehensive and reliable manner, we will then need to replicate a large number of interactions in a comprehensive experiment across space.
-This type of “cafeteria experiments in space” is not only unfeasible, but also undermines our original objective: If the local occurrence of interactions is uninformative regarding the underlying probabilities of occurrence, then is not likely to be worthwhile collecting these local interaction matrices in the first place.
-<deep sigh and forget that section?
->
-
-  % As an alternative to abandoning empirical networks or continuing to ignore the uncertainty inherent in undetected observations, we propose that some insight regarding the detectability of interactions between species not found co-occurring may be gained from data on other species between which interactions are known to be feasible.
-If we use this information obtain the joint probability of detection and process (e.g.
-to glean information regarding at how many sites the species are found interacting across the entire dataset), and assuming that most of this pattern is due to variation in detection rate, then insights into the incidence of interactions between species may be gleaned from the accumulation rate of positive interactions at sites were interaction is possible (i.e.
-with at least one observation of a positive interaction) [this reasoning to be further formalised]
 
@@
       \begin{equation}
-        \theta_{MLE} = \frac{k}{n}  .
+        \lambda_{MLE} = \frac{k}{n}  .
         \label{theta_MLE}
@@
   The variance of a Bernoulli experiment is $n\lambda$(1-$\lambda$).
-It is important to remember that this variance describes the variability of the number of success[es] $k$ for $n$ trials and is not the variance associated with the estimation of $\lambda$.
+It is important to remember that this variance describes the variability of the number of successes $k$ for $n$ trials and is not the variance associated with the estimation of $\lambda$.
 Given this variance, it is possible to compute the confidence interval for the MLE of $\lambda$ using any of several methods, including the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull Interval} (for details, see [\citealp{}]).
@@
 This means that even if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact.
-What it implies is that no interaction is the most likely situation but there is nonetheless a significant chance that the two species \emph{could} interact.
-In contrast with the situation where $k>0$, when we are sure that an interaction is feasible,
-  % (in which case, the ratio $k/n$ is smaller than $n$ because of detection and process uncertainty),  % This parenthetical makes the sentence very long. Is it necessary?
-  we are not sure that absence of interactions is caused by $L=0$.
-Second, and most importantly, the number of trials $n$ might be very low in many instances (and some pairs of species might not have been documented as co-occuring in even one case).
+What it implies is that no interaction is the most likely situation but there is nonetheless a substantial chance that the two species \emph{could} interact.
+In contrast with the situation where $k>0$, when we are sure that an interaction is feasible, we are not sure that absence of interactions is caused by $L=0$.
+Second, and most importantly, the number of trials $n$ might be very low in many instances (and some pairs of species might not have been documented as co-occuring even once).
 Consequently, the uncertainty in the estimation of $\lambda$ might be considerable.
@@
 To establish that species are not interacting with any acceptable certainty requires tens of observations of the two species co-occurring but not interacting.
-  % Is the Clopper-Pearson interval the one in Dom's code snippets? If so, this is Fig.~\ref{Salix_cdfs}
-
-% DG: The following should be removed to avoid repetitions
-%  The situation where $k = 0$ is also problematic because we have very little information with which to estimate $\lambda$, in particular when $n$ is also small.
-We therefore propose a Bayesian approach to solve this problem, building on two relevant features of such statistics: the posterior distribution of parameter estimates and usage of prior information.
-Before moving to this direction, we will first take time to better describe what is exactly meant by an interaction probability and appropriately define sources of uncertainty.
-
-%  So many sources of interaction pooled into a single entity; hard to estimate.
-
-% MLE is zero if no interaction is detected, but there may still be a substantial probability of interaction should the two species co-occur.
-[This is particularly important in the context of a changing world, where species not co-occurring today – or species not detected co-occurring today – may well do so tomorrow, forming complex interactions.]
+As most data sets will not have such extensive sampling across all observations, we can use a Bayesian approach to supplement what data we do have with other sources of information.
 
@@
       \begin{equation}
-        \underbrace{P(\lambda|X,n)}_{Posterior} = \frac{\overbrace{P(X|\lambda,n)}^{Likelihood}\overbrace{P(\lambda)}^{Prior}}{\underbrace{P(X|N)}_{Normaliser}} .
+        \underbrace{P(\lambda|k,n)}_{Posterior} = \frac{\overbrace{P(k|\lambda,n)}^{Likelihood}\overbrace{P(\lambda)}^{Prior}}{\underbrace{P(k|N)}_{Normaliser}} .
         \label{posterior}
@@
       According to the above description, the likelihood is simply the binomial distribution (Eq.~\ref{likelihood}).
-Since $\lambda$ is a probability it is bounded between 0 and 1 and consequently the most appropriate prior distribution is the beta:
+Since $\lambda$ is a probability, it is bounded between 0 and 1 and the most appropriate prior distribution is the beta:
 
@@
 
-%      \begin{equation}
-%        Beta(\alpha+k,\beta+n-k) = \frac{\Gamma(\alpha+k)\Gamma(\beta+n-k)}{\Gamma(\alpha+\beta+n)} . \label{betafunction}
-%      \end{equation}
-
       \noindent where the function $B$ is the beta function.
 The posterior distribution of $\lambda$ therefore follows the beta distribution with new parameters $\alpha'= \alpha+k$ and $\beta'=\beta+n-k$.
-The weigth of the prior on the posterior distribution is understood from these definition of the parameters: the difference between the posterior and the prior will increase with $k$ and $n-k$.
+The weight of the prior on the posterior distribution can be understood from these parameter definitions: the difference between the posterior and the prior will increase with $k$ and $n-k$.
+In other words, the distribution of $\lambda$ for better-sampled pairs of species will rely less on the information used to build the prior distribution and depend more on the observed data.
       When plotted, we find the shape of the distribution gets narrower with $k$ and $n$ (Fig.~\ref{Salix_pdfs}).
-We also find an important difference between the salix-gallers and gallers-parasitoids because of the differences in the prior distributions.
-      %
+
       %  The posterior distribution of $\theta$ could be computed with R with the following command:
@@
       \begin{figure}[ht]
-        \label{Salix_pdfs}
         \caption{Using prior distribution based on the \emph{Salix}-galler and galler-parasitoid networks in~\citet{Barbour2016}, we can calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting.
-Here we show posterior distributions for each $\lambda$ in each network ranging from the prior distribution (N=0 observed co-occurrence) to the distribution obtained when the pair of species has been observed co-occurring 100 times.
+Here we show posterior distributions for each $\lambda$ in each network ranging from the prior distribution ($n=0$ observed co-occurrence) to the distribution obtained when the pair of species has been observed co-occurring 100 times.
 The distribution narrows and approaches zero as the sample size increases.
 \textbf{A)} The posterior distributions for the \emph{Salix}-galler component are always wider and farther from zero than those for \textbf{B)} the galler-parasitoid component.
-This is likely because the prior distribution for the galler-parasitoid component of the network was both narrower and had a mean closer to that in the~\citet{Kopelke2017} data than the \emph{Salix}-galler component.}
+This is likely because the prior distribution for the galler-parasitoid component of the network was both narrower and had a mean closer to that in the~\citet{Kopelke2017} data than did the \emph{Salix}-galler component.}
+        \label{Salix_pdfs}
         \includegraphics*[width=.8\textwidth]{figures/Salix_Galler_pdfs_increasing_N.eps}
@@
       The fact that the posterior distribution of $\lambda$ follows a beta distribution makes it straightforward to compute moments and other properties.
+These moments may then be used when calculating higher-order network properties.
 
@@
 
-      \subsubsection*{Degree distribution for the species in the network - or - Interaction probabilities in a similar network}.
+      \subsubsection*{Degree distribution or interaction probabilities}
 
@@
 The latter approach allows us to apply information from known, abundant species to the rarest species for which interactions are less frequently documented.
-The procedure for the estimation of the hyper parameters follows the same approach as described above for connectance except that each measurement is at the individual species level instead of the network level.
 
@@
 Using normalised degrees $\Delta_i$ and $\Delta_j$ (i.e., degrees divided by the number of species in the network), we can obtain the probability of interaction $L_ij$=$\Delta_i\times\Delta_j$.
-The distribution of these interaction probabilities derived from a similar network or a suite of networks can be used to establish a prior distribution before any data from the focal network are collected.
-We could also use this approach to build a prior distribution using known interaction probabilities for some species in the focal network.
-The latter approach allows us to apply information from known, abundant species to the rarest species for which interactions are less frequently documented.
-The procedure for the estimation of the hyper parameters follows the same approach as described above for connectance except that each measurement is at the individual interaction level instead of the network level.
+Similar to the procedure for degree distribution, the distribution of these interaction probabilities derived from a similar network or a suite of networks can be used to establish a prior distribution before any data from the focal network are collected.
+For distributions of either degrees or interaction probabilities, the procedure for the estimation of the hyper parameters follows the same approach as described above for connectance except that each measurement is at the individual interaction level instead of the network level.
 
@@
           In such as case, the prior distribution would follow the function $P(\lambda|\mathbf{T})=f(\mathbf{T})$ based on a set of traits for both species $\mathbf{T}$.
-There are several techniques available to perform this inference of interaction probability, some of which are bayesian, and we refer to ~\citep{Bartomeus2016} and \citep{Weinstein2017} for recent reviews about this topic.
+There are several techniques available to perform this inference of interaction probability, some of which are Bayesian, and we refer to ~\citep{Bartomeus2016} and \citep{Weinstein2017} for recent reviews about this topic.
 Note that in this case the prior might not be beta distributed and numerical methods might be required to compute the posterior distribution.
@@
 The maximum likelihood estimate of the interaction probability (Box 1) is simply $\lambda_{MLE} = 3/10 = 0.3$.
-  % We should probabaly have a value  on the interaction probablitity that differs from the average of the degree distrbution
 
@@
 
-  Now consider we know that species $i$ is known to interact with 10 species (other than species $j$), which have the following normalised degrees:
+  Now consider we know that species $i$ is known to interact with 10 species (other than species $j$), which have the following degrees:
 
@@
     \noindent\emph{
-       degree = c(0.66, 0.18, 0.12, 0.16, 0.84, 0.32, 0.12, 0.76, 0.06, 0.04)
+      degree=c(14, 4, 2, 3, 17, 6, 2, 15, 1, 1)
         }.
@@
 
-    If the network has 20 species total, then species $i$ has a normalised degree of 0.5 and
+    If the network has 20 species total, this gives the normalised degrees:
+
+    \vspace{12pt}
+    \noindent\emph{
+      norm\_degree=c(0.65, 0.20, 0.10, 0.15, 0.85, 0.30, 0.10, 0.75, 0.05, 0.05)}.
+      \vspace{12pt}
+
+    then species $i$ has a normalised degree of 0.55 (it interacts with species $j$ and 10 other species) and
     we can use this to obtain the following set of interaction probabilities for species $i$ and each of its interaction partners:
@@
     \noindent\emph{
-       int\_probs = c(0.33, 0.09, 0.06, 0.08, 0.42, 0.16, 0.06, 0.38, 0.03, 0.02) }.
+       int\_probs = c(0.358, 0.110, 0.055, 0.082, 0.468, 0.165, 0.055, 0.412, 0.028, 0.028) }.
       \vspace{12pt}
 
-    The mean of these interaction probabilities is 0.163, approximately half the $\lambda_{MLE}$ obtained from the observed data.
+    The mean of these interaction probabilities is 0.176, approximately two-thirds the $\lambda_{MLE}$ obtained from the observed data.
 We can use the distribution of these interaction probabilities as our prior distribution and estimate the uncertainty surrounding our $\lambda_{MLE}$.
-With some simple R code (function calculate\_parameters, \emph{Appendix S2}), we obtain prior parameters $\alpha$=1.050830 and $\beta$=5.365892.
-Using these priors in equations~\ref{mean} and~\ref{variance} above (or in the R function calculate\_distribution in \emph{Appendix S2}), we find a prior mean interaction probability of 0.16376436 and a prior variance of 0.02134199.
-Adding the observed data ($n=10$, $k=3$) and using the same code, we obtain posterior parameters $\alpha'$=4.05083 and $\beta'$=12.36589 and a posterior distribution of $\lambda$ with mean 0.247 and variance 0.011.
+With some simple R code (function ``calculate\_parameters", \emph{Appendix S2}), we obtain prior parameters $\alpha$=0.998 and $\beta$=4.63.
+Using these priors in equations~\ref{mean} and~\ref{variance} above (or in the R function ``calculate\_distribution" in \emph{Appendix S2}), we find a prior $\bar\lambda$=0.177 and var($\lambda$)=0.026.
+Adding the observed data ($n=10$, $k=3$) and using the same code, we obtain posterior parameters $\alpha'$=4.00 and $\beta'$=11.6 and a posterior $\bar\lambda$=0.256 and var($\lambda$)=0.012.
 Comparing the posterior distribution to the prior, we see that the posterior is closer to the observed data and that the additional data has reduced the variance.
 We may also wish to calculate a credible interval (analogous to the frequentist confidence interval).
-This is also quite straightforward in R (see function credible\_interval in \emph{Appendix S2}).
-In this case, a 95\% credible interval for the mean of theta is (0.077, 0.474).
+This is also quite straightforward in R (see function ``credible\_interval" in \emph{Appendix S2}).
+In this case, a 95\% credible interval for $\bar\lambda$ is (0.080, 0.491).
 
@@
 The question is then ``what is the probability these two species do not interact''?
-Since it is not possible to prove that the two species could never interact (strickly speaking, in such an approach $\lambda=0$ is impossible), given the framework above we must fix a threshold below which we consider that there is no interaction ($\lambda \sim 0$).
+Since it is not possible to prove that the two species could never interact (strickly speaking, in this approach $\lambda=0$ is impossible), given the framework above we must fix a threshold below which we consider that there is no interaction ($\lambda \sim 0$).
 We call this threshold probability $\lambda*$.
 We then use the cumulative distribution function to estimate $P(\lambda<\lambda*|L=0,n)$ for different $n$.
-The
-    function plot\_precision in \emph{Appendix S2} calculates distribution function for $\lambda*$ with an increasing number of trials.
-The figure below illustrates this distribution for $\lambda*$=0.1.
-This yields a surprising result: it requires \textgreater24 observations of no interactions to be 95\% sure that the interaction probability is smaller than 0.1 (recall Fig.~\ref{upper_limits}).
-Note the special case where there is no observation of the two species co-occurring, $n = 0$  In this situation, the posterior distribution converges to the prior distribution since the data include no information on the probability with which species might interact should they co-occur; see above).
+The function ``plot\_precision" in \emph{Appendix S2} calculates distribution function for $\lambda*$ with an increasing number of trials.
+This yields a surprising result: it requires \textgreater24 observations of no interactions to be 95\% sure that the interaction probability is smaller than $\lambda*$=0.1 (recall Fig.~\ref{upper_limits}).
+Note the special case where there is no observation of the two species co-occurring, $n = 0$.
+In this situation, the posterior distribution converges to the prior distribution since the data include no information on the probability with which species might interact should they co-occur).
 
@@
     It is fairly straightforward to compute most of network metrics when the different $\lambda$ of the adjacency matrix are known, without variance~\citep{Poisot2016}.
-Several of these metrics derive directly from quantitative indices of network structure which are equivalent to $\lambda$; the remainder, originally defined for binary networks, can be adjusted to account for interaction probabilities between zero and one.
+Several of these metrics derive directly from quantitative indices of network structure which are equivalent to $\lambda$.
+The remainder, originally defined for binary networks, can be adjusted to account for interaction probabilities between zero and one.
 It is not as easy, however, to understand how the uncertainty in these estimated interaction probabilities influences network metrics.
-Computation of these metrics involves non-linear functions and therefore, because of Jensen's inequality (which states that the average of non-linear function of a stochastic variable differs from the function of the average of that variable), any uncertainty in $\lambda$s could bias both the mean and variance of a network metric.
-For instance, assume that among all pairs of species with few observed co-occurrences there are many pairs which truly interact.
+Computation of these metrics involves non-linear functions and therefore, because of Jensen's inequality (which states that the average of a non-linear function of a stochastic variable differs from the function of the average of that variable), any uncertainty in $\lambda$s could bias both the mean and variance of a network metric.
+For instance, assume that among the pairs of species with few observed co-occurrences there are many pairs which truly interact.
 If we begin with no observed links for these pairs, then correcting for these false absences will inflate the number of links and consequently influence metrics such as connectance, nestedness, and degree distribution.
@@
 Instead we must rely on computer simulations.
-In the following section, we will provide an empirical example, based on the data set published by~\citet{Kopelke2017} (see Box~\ref{box1}).
+In the following section, we will provide an empirical example based on an extremely well-sampled \emph{Salix}-galler-natural enemy system (see Box~\ref{box1};~\citealp{Kopelke2017}).
 We will show how the uncertainty arising from both absences of co-occurrences and false absences of interactions impact these metrics.

### 2017-11-23 manuscript/CI_interactions.tex
nearly done my read-through

@@
 % AC : I like the box idea. Since we refer to the Salix data throughout the manuscript it makes sense to make it stand out. 
-    \indent As a case study, we use an extensively sampled \emph{Salix}-galler-parasitoid meta-network.
+    \indent As a case study, we use an extensively sampled \emph{Salix}-galler-natural enemy meta-network.
 This dataset consists of a single community type sampled across Europe; willow (\emph{Salix}) species, willow-galling sawflies, and their natural enemies.
@@
       \begin{figure}[ht]
-        \caption{Using prior distribution based on the \emph{Salix}-galler and galler-parasitoid networks in~\citet{Barbour2016}, we can calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting.
+        \caption{Using prior distribution based on the \emph{Salix}-galler and galler-natural enemy networks in~\citet{Barbour2016}, we can calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting.
 Here we show posterior distributions for each $\lambda$ in each network ranging from the prior distribution ($n=0$ observed co-occurrence) to the distribution obtained when the pair of species has been observed co-occurring 100 times.
 The distribution narrows and approaches zero as the sample size increases.
-\textbf{A)} The posterior distributions for the \emph{Salix}-galler component are always wider and farther from zero than those for \textbf{B)} the galler-parasitoid component.
-This is likely because the prior distribution for the galler-parasitoid component of the network was both narrower and had a mean closer to that in the~\citet{Kopelke2017} data than did the \emph{Salix}-galler component.}
+\textbf{A)} The posterior distributions for the \emph{Salix}-galler component are always wider and farther from zero than those for \textbf{B)} the galler-natural enemy component.
+This is likely because the prior distribution for the galler-natural enemy component of the network was both narrower and had a mean closer to that in the~\citet{Kopelke2017} data than did the \emph{Salix}-galler component.}
         \label{Salix_pdfs}
@@
 Instead we must rely on computer simulations.
-In the following section, we will provide an empirical example based on an extremely well-sampled \emph{Salix}-galler-natural enemy system (see Box~\ref{box1};~\citealp{Kopelke2017}).
+In the following section, we will provide an empirical example based on an extremely well-sampled \emph{Salix}-galler-natural enemy system (\citealp{Kopelke2017}; see Box~\ref{box1} for a description).
 We will show how the uncertainty arising from both absences of co-occurrences and false absences of interactions impact these metrics.
@@
       In a strict Bayesian framework, we wish to use a prior distribution that does not rely on any information from the study at hand.
-To that end, we use data from another well-described \emph{Salix} galler-parasitoid system~\citep{Barbour2016,Barbour2016Dryad}.
-Note that this study used several genotypes of \emph{S.
-hookeriana} rather than different \emph{Salix} species.
+To that end, we use data from another well-described \emph{Salix} galler-natural enemy system~\citep{Barbour2016,Barbour2016Dryad}.
+Note that this study used several genotypes of \emph{Salix hookeriana} rather than different \emph{Salix} species.
 We estimated frequencies of  \emph{S.
 hookeriana} genotype-galler interactions based on the normalised degree of each species in each network component (see \emph{Appendix S1} for details and code).
-Specifically, we obtain prior parameters $\alpha$=2.507217 and $\beta$=1.888079.
-For the galler-parasitoid component of the network, the corresponding prior parameters are $\alpha$=1.341479, $\beta$=9.487966.
-We are then able to use these priors to estimate the posterior distribution of interaction probabilities given the additional information in our dataset.
+Specifically, we obtain prior parameters $\alpha$=2.51 and $\beta$=1.89.
+For the galler-natural enemy component of the network, the corresponding prior parameters are $\alpha$=1.34, $\beta$=9.49.
+We are then able to use these prior parameters to estimate the posterior distribution of interaction probabilities given the additional information in our dataset.
 
-      For species where no co-occurrences were observed, we can 
-      calculate the estimates for the mean and variance of 
-      $\lambda_{ij}$ directly from this prior following 
-      equations~\ref{mean} and~\ref{variance} 
-      (see \emph{Appendix S2} for R implementation). The prior 
-      distribution we obtain based on~\citet{Barbour2016,Barbour2016Dryad} is:
-      $\hat{\lambda_{ij}}$=0.570, var($\lambda$)=0.056 for the \emph{Salix}-galler network and $\hat{\lambda_{ij}}$=0.124, var($\lambda$)=0.010 for the galler-parasitoid network.
-This is consistent with the prior data, where the average
-      interaction probability based on the degree distributions of Salix genotypes and gallers was 0.562 and that for gallers and parasitoids was 0.122.
-These probabilities are much higher than those in our dataset (0.028 and 0.078 for the \emph{Salix}-galler and galler-parasitoid networks, respectively).
-This discrepancy may reflect the differences in scale between a network containing different genotypes of a single \emph{Salix} species and four gallers from a single family and a network containing many \emph{Salix} species and gallers from many families as is the case in our dataset.
+      For species where no co-occurrences were observed, we can calculate the estimates for the mean and variance of $\lambda_{ij}$ directly from the prior parameters following equations~\ref{mean} and~\ref{variance} (see \emph{Appendix S2} for R implementation).
+For the \emph{Salix}-galler network, the prior distribution we obtained was: $\bar\lambda$=0.570, var($\lambda$)=0.056.
+The prior distribution for the galler-natural enemy network was $\bar\lambda$=0.124, var($\lambda$)=0.010.
+This is consistent with the prior data, where the average interaction probability based on the degree distributions of \emph{Salix} genotypes and gallers was 0.562 and that for gallers and natural enemies was 0.122.
+These probabilities are much higher than those in our dataset (0.028 and 0.078 for the \emph{Salix}-galler and galler-natural enemy networks, respectively).
+This discrepancy may reflect the differences in scale between a network containing different genotypes of a single \emph{Salix} species and four gallers from a single family in~\citet{Barbour2016} and a network containing many \emph{Salix} species and gallers from many families as is the case in~\citet{Kopelke2017}.
 
@@
 Thus $\alpha'$=$\alpha$ and $\beta'$=$\beta + n$.
-At the most extreme case, for a pair of species which co-occurred at all 374 sites and was never observed to interact, our distributions would become:
-
-      $\hat{\lambda_{ij}}$=6.625921 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=1.739456 $\times$ 10$^{-5}$ for the \emph{Salix}-galler network and 
-      $\hat{\lambda_{ij}}$=3.485906 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=9.026737 $\times$ 10$^{-6}$ for the galler-parasitoid network.
+At the most extreme case, for a pair of species which co-occurred at all 374 sites and was never observed to interact, our distributions would become
+      $\bar\lambda_{ij}$=6.63 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=1.74 $\times$ 10$^{-5}$ for the \emph{Salix}-galler network and 
+      $\bar\lambda_{ij}$=3.49 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=9.03 $\times$ 10$^{-6}$ for the galler-natural enemy network.
 
@@
         \begin{tabular}{l | c c | c c }
-        \multirow{2}{*}{N} & \multicolumn{2}{c}{\emph{Salix}-galler} & \multicolumn{2}{c}{galler-parasitoid}\\
+        \multirow{2}{*}{N} & \multicolumn{2}{c}{\emph{Salix}-galler} & \multicolumn{2}{c}{galler-natural enemy}\\
          & Lower bound & Upper bound \\
@@
 If we want to be 95\% confident that the interaction probability for two species in the \emph{Salix}-galler network is below 0.5, 0.1, or 0.01, we would need six, 51, and 101 observed co-occurrences with no observed interaction (Fig.~\ref{Salix_cdfs}; see function samples\_required in~\emph{Appendix S2}).
-Although the prior distribution of interaction probabilities is narrower and closer to zero for the galler-parasitoid network, the number of samples required to be 95\% confident that the interaction probability is below a threshold still increases quickly; we would need 25 and 101 observed co-occurrence with no observed interaction for threshold interaction probabilities of 0.1 and 0.01, respectively.
+Although the prior distribution of interaction probabilities is narrower and closer to zero for the galler-natural enemy network, the number of samples required to be 95\% confident that the interaction probability is below a threshold still increases quickly; we would need 25 and 101 observed co-occurrence with no observed interaction for threshold interaction probabilities of 0.1 and 0.01, respectively.
 Given the low levels of replication in most network studies, this implies that we should have fairly low confidence in many ``non-interacting" pairs of species.
-Even in the extensively replicated \emph{Salix}-galler-parasitoid dataset very few species pairs were observed co-occurring frequently enough to reach these thresholds (only three \emph{Salix}-galler pairs and 31 galler-parasitoid pairs were observed co-occurring frequently enough to reach the threshold for an interaction probability of 0.1, and no pairs were observed co-occurring frequently enough to reach the threshold for an interaction probability of 0.01 [[Do we need the other thresholds?
+Even in the extensively replicated \emph{Salix}-galler-natural enemy dataset very few species pairs were observed co-occurring frequently enough to reach these thresholds (only three \emph{Salix}-galler pairs and 31 galler-natural enemy pairs were observed co-occurring frequently enough to reach the threshold for an interaction probability of 0.1, and no pairs were observed co-occurring frequently enough to reach the threshold for an interaction probability of 0.01 [[Do we need the other thresholds?
 Seems like it'll get redundant]]).
@@
 The large ticks along the x-axis indicate the number of samples associated with each of these points.
-Note that the number of samples required to reach any given threshold is smaller for \textbf{A)} the \emph{Salix}-galler network than for \textbf{B)} the galler-parasitoid network.}
+Note that the number of samples required to reach any given threshold is smaller for \textbf{A)} the \emph{Salix}-galler network than for \textbf{B)} the galler-natural enemy network.}
         \label{Salix_cdfs}
@@
 
-    Using the prior distributions and procedures described above, we calculated posterior probability distributions for each pair of \emph{Salix} and galler or galler and parasitoid species that were not observed interacting.
+    Using the prior distributions and procedures described above, we calculated posterior probability distributions for \emph{Salix}-galler or galler-natural ememy pair that was not observed interacting.
 Using these posterior distributions and assuming probabilities of 1 for pairs of species that were observed interacting, we created a suite of 100 webs of each network type by randomly sampling from each posterior distribution.
-After obtaining these posterior networks, we calculated the connectance of each web, as well as the number of links per resource (\emph{Salix} in the \emph{Salix}-galler networks or galler in the galler-parasitoid networks) and links per consumer.
+After obtaining these posterior networks, we calculated the connectance of each web, as well as the number of links per resource (\emph{Salix} in the \emph{Salix}-galler networks or galler in the galler-natural enemy networks) and links per consumer.
 To demonstrate how these network metrics will be affected by detection uncertainty ($\delta$), we then created a suite of filtered networks for each posterior network.
@@
 
-    Considering the galler-parasitoid networks, the connectance, mean links per galler, and mean links per parasitoid (0.078, 9.99, and 7.45, respectively) are similar to those in the posterior webs with a detection filter of 50\% (Fig.~\ref{posterior_webs}).
-The~\citet{Barbour2016} network likely provides a better prior here than for the \emph{Salix}-galler networks, as both networks included different galler and parasitoid species.
-Although the two networks differ vastly in scale, and the inclusion of multiple \emph{Salix} species likely causes structural differences from~\citet{Barbour2016} despite the similar resolution of gallers and parasitoids, this result nevertheless suggests that even such a large and well-replicated network is missing a large proportion of interactions.
+    Considering the galler-natural enemy networks, the connectance, mean links per galler, and mean links per natural enemy (0.078, 9.99, and 7.45, respectively) are similar to those in the posterior webs with a detection filter of 50\% (Fig.~\ref{posterior_webs}).
+The~\citet{Barbour2016} network likely provides a better prior here than for the \emph{Salix}-galler networks, as both networks included different galler and natural enemy species.
+Although the two networks differ vastly in scale, and the inclusion of multiple \emph{Salix} species likely causes structural differences from~\citet{Barbour2016} despite the similar resolution of gallers and natural enemies, this result nevertheless suggests that even such a large and well-replicated network is missing a large proportion of interactions.
 This should be a strong warning to researchers comparing structural characteristics between networks - small structural differences are very likely to be completely masked by structural changes that would result if missing interactions were included.
@@
     \begin{figure}[ht]
-    \caption{Here we show the mean connectance, links per resource (\emph{Salix} in the \emph{Salix}-galler networks and gallers in the galler-parasitoid networks), and links per consumer (gallers in the \emph{Salix}-galler networks and parasitoids in the galler-parasitoid networks) for networks assembled using posterior distributions based on~\citet{Barbour2016,Barbour2016Dryad}.
+    \caption{Here we show the mean connectance, links per resource (\emph{Salix} in the \emph{Salix}-galler networks and gallers in the galler-natural enemy networks), and links per consumer (gallers in the \emph{Salix}-galler networks and natural enemies in the galler-natural enemy networks) for networks assembled using posterior distributions based on~\citet{Barbour2016,Barbour2016Dryad}.
 We created 100 ``posterior-sampling" networks and then, for each of these, created 100 ``detection-filter" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network.

### 2017-11-23 manuscript/CI_interactions.tex
just need to update network metrics section, two figures

@@
 % AC : I like the box idea. Since we refer to the Salix data throughout the manuscript it makes sense to make it stand out. 
+[[I had understood that each of the 374 sites was a sample - should we switch to 641 as the maximum sites?]]
     \indent As a case study, we use an extensively sampled \emph{Salix}-galler-natural enemy meta-network.
@@
 Nevertheless, as the number of observed co-occurrence increases, the posterior mean becomes closer to zero and the posterior variance decreases (Fig.~\ref{Salix_pdfs}).
+The 95\% credible interval around the estimate of $\lambda$ also shrinks with increasing sample sizes, from (0.152,0.931) and (0.008, 0.364) for \emph{Salix}-galler and galler-natural enemy pairs that were never observed co-occurring to (0.001, 0.017) and (\textless0.001, 0.11) for hypothetical \emph{Salix}-galler and galler-natural enemy pairs that might be observed co-occurring at all 374 sites without any observed interaction.
 
-%DG: the following subsection could be moved to the appendix if we need to cut down
+% %DG: the following subsection could be moved to the appendix if we need to cut down
+% Add to appendix.
 
-  \subsection*{Computing the credible interval around a probability estimate}
+%   \subsection*{Computing the credible interval around a probability estimate}
 
-      As well as obtaining posterior means and variances, it is possible to calculate a 95\% credible interval about the posterior mean.
-This is again straightforward to do in R (see the function ``credible interval" in \emph{Appendix S2}).
+%       As well as obtaining posterior means and variances, it is possible to calculate a 95\% credible interval about the posterior mean.
+This is again straightforward to do in R (see the function ``credible\_interval" in \emph{Appendix S2}).
 Calculating the 95\% credible intervals for species pairs with 0 to 50 observed co-occurrences without any observed interaction (as in Fig.~\ref{Salix_pdfs}), we see that the interval narrows dramatically as the number of observations increases.
@@
 
-      % # R code to make the table:
-      % output=matrix(nrow=length(ns),ncol=5)
-      % ns=c(0,1,2,5,10,15,20,25,50,100,150,200,374)
-      % output[,1]=ns
-      % for(r in 1:nrow(output)){
-      %   interval1=credible_interval(calculate_parameters(sg_int_probs,ns[r],0),0.025,0.975)    
-      %   interval2=credible_interval(calculate_parameters(gp_int_probs,ns[r],0),0.025,0.975)    
-      %   output[r,2:3]=interval1
-      %   output[r,4:5]=interval2
-      % }
+%       % # R code to make the table:
+%       % output=matrix(nrow=length(ns),ncol=5)
+%       % ns=c(0,1,2,5,10,15,20,25,50,100,150,200,374)
+%       % output[,1]=ns
+%       % for(r in 1:nrow(output)){
+%       %   interval1=credible_interval(calculate_parameters(sg_int_probs,ns[r],0),0.025,0.975)    
+%       %   interval2=credible_interval(calculate_parameters(gp_int_probs,ns[r],0),0.025,0.975)    
+%       %   output[r,2:3]=interval1
+%       %   output[r,4:5]=interval2
+%       % }
 
-      \begin{table}[h]
-        \caption{95\% credible intervals for the interaction probability of two species that co-occur in $N$ sites but are never observed to interact, obtained using prior information from the \emph{Salix}-galler network in~\citet{Barbour2016,Barbour2016Dryad}.
+%       \begin{table}[h]
+%         \caption{95\% credible intervals for the interaction probability of two species that co-occur in $N$ sites but are never observed to interact, obtained using prior information from the \emph{Salix}-galler network in~\citet{Barbour2016,Barbour2016Dryad}.
 [Tomas notes that this is conceptually very similar to Fig.~\ref{Salix_pdfs}]}
-        \label{interval_table}
-        \begin{tabular}{l | c c | c c }
-        \multirow{2}{*}{N} & \multicolumn{2}{c}{\emph{Salix}-galler} & \multicolumn{2}{c}{galler-natural enemy}\\
-         & Lower bound & Upper bound \\
-        \hline
-        0   & 0.152 & 0.931 & 0.008 & 0.364 \\
-        1   & 0.110 & 0.843 & 0.007 & 0.337 \\
-        2   & 0.087 & 0.760 & 0.006 & 0.313 \\
-        5   & 0.053 & 0.573 & 0.005 & 0.258 \\
-        10  & 0.033 & 0.400 & 0.004 & 0.200 \\
-        15  & 0.023 & 0.306 & 0.003 & 0.163 \\
-        20  & 0.018 & 0.247 & 0.003 & 0.137 \\
-        25  & 0.015 & 0.208 & 0.002 & 0.119 \\
-        50  & 0.008 & 0.115 & 0.001 & 0.071 \\
-        100 & 0.004 & 0.061 & 0.001 & 0.039 \\
-        150 & 0.003 & 0.041 & \textless0.001 & 0.027 \\
-        200 & 0.002 & 0.031 & \textless0.001 & 0.021 \\
-        \hline
-        374 & 0.001 & 0.017 & \textless0.001 & 0.011 \\
-        \hline
-        \end{tabular}
-        \end{table}
+%         \label{interval_table}
+%         \begin{tabular}{l | c c | c c }
+%         \multirow{2}{*}{N} & \multicolumn{2}{c}{\emph{Salix}-galler} & \multicolumn{2}{c}{galler-natural enemy}\\
+%          & Lower bound & Upper bound \\
+%         \hline
+%         0   & 0.152 & 0.931 & 0.008 & 0.364 \\
+%         1   & 0.110 & 0.843 & 0.007 & 0.337 \\
+%         2   & 0.087 & 0.760 & 0.006 & 0.313 \\
+%         5   & 0.053 & 0.573 & 0.005 & 0.258 \\
+%         10  & 0.033 & 0.400 & 0.004 & 0.200 \\
+%         15  & 0.023 & 0.306 & 0.003 & 0.163 \\
+%         20  & 0.018 & 0.247 & 0.003 & 0.137 \\
+%         25  & 0.015 & 0.208 & 0.002 & 0.119 \\
+%         50  & 0.008 & 0.115 & 0.001 & 0.071 \\
+%         100 & 0.004 & 0.061 & 0.001 & 0.039 \\
+%         150 & 0.003 & 0.041 & \textless0.001 & 0.027 \\
+%         200 & 0.002 & 0.031 & \textless0.001 & 0.021 \\
+%         \hline
+%         374 & 0.001 & 0.017 & \textless0.001 & 0.011 \\
+%         \hline
+%         \end{tabular}
+%         \end{table}
 
@@
 The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact.
-If we want to be 95\% confident that the interaction probability for two species in the \emph{Salix}-galler network is below 0.5, 0.1, or 0.01, we would need six, 51, and 101 observed co-occurrences with no observed interaction (Fig.~\ref{Salix_cdfs}; see function samples\_required in~\emph{Appendix S2}).
-Although the prior distribution of interaction probabilities is narrower and closer to zero for the galler-natural enemy network, the number of samples required to be 95\% confident that the interaction probability is below a threshold still increases quickly; we would need 25 and 101 observed co-occurrence with no observed interaction for threshold interaction probabilities of 0.1 and 0.01, respectively.
+If we want to be 95\% confident that the interaction probability for two species in the \emph{Salix}-galler network is below 0.1, 0.05, or 0.01, we would need 51, 106, and 550 observed co-occurrences with no observed interaction (Fig.~\ref{Salix_cdfs}; see function plot\_precision in~\emph{Appendix S2}).
+Although the prior distribution of interaction probabilities is narrower and closer to zero for the galler-natural enemy network, the number of samples required to be 95\% confident that the interaction probability is below a threshold still increases quickly; we would need 25, 62, and 352 observed co-occurrence with no observed interaction for threshold interaction probabilities of 0.1, 0.05, and 0.01, respectively.
 Given the low levels of replication in most network studies, this implies that we should have fairly low confidence in many ``non-interacting" pairs of species.
-Even in the extensively replicated \emph{Salix}-galler-natural enemy dataset very few species pairs were observed co-occurring frequently enough to reach these thresholds (only three \emph{Salix}-galler pairs and 31 galler-natural enemy pairs were observed co-occurring frequently enough to reach the threshold for an interaction probability of 0.1, and no pairs were observed co-occurring frequently enough to reach the threshold for an interaction probability of 0.01 [[Do we need the other thresholds?
-Seems like it'll get redundant]]).
+Even in the extensively replicated \emph{Salix}-galler-natural enemy dataset very few species pairs were observed co-occurring frequently enough to reach these thresholds (only three \emph{Salix}-galler pairs and 31 galler-natural enemy pairs were observed co-occurring frequently enough to reach the threshold for an interaction probability of 0.1, and no pairs were observed co-occurring frequently enough to reach the threshold for an interaction probability of 0.01).
 Discounting potential interactions, then, requires either a stronger prior expectation of no interaction (e.g., we can be highly confident that a palm tree will not predate upon a leopard no matter how many times the two species are observed together) or very extensive sampling.

### 2017-11-23 manuscript/supplemental.tex
just need to update network metrics section, two figures

@@
 \clearpage
+
+\section*{Appendix S1: Details of \emph{Salix} data collection}
+
+      The \emph{Salix}-galler-parasitoid meta-network dataset consists of a single community type sampled across Europe; willow (\emph{Salix}) species, willow-galling sawflies (Hymenoptera, Tenthredinidae, Nematinae, Euurina), and their natural enemies (hymenopteran parasitoids and coleopteran, lepidopteran, dipteran, and hymenopteran inquilines).
+The data were collected over 29 years (1982-2010) at 374 unique locations across Europe ranging from Sicily to the Arctic.
+Including repeated visits to a number of sites, the data set contains 641 site-visits, each of which can be considered as a network in its own right and an independent sample from which to build the meta-network.
+The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 parasitoid nodes.
+Interactions were determined by dissecting and rearing gall inhabitants from 165,424 galls.
+The high spatiotemporal resolution of this network and the unusually high sampling effor implemented at the site level (641 site-visits, which can be considered as repeated samples of the network) makes this dataset particularly well suited for testing this method.
 
@@
 
-      % SG_web=read.csv('binary_prior_web_SG.csv',row.names=1)
-      % GP_web=read.csv('binary_prior_web_para_only.csv',row.names=1)
+      SG_web=read.csv('binary_prior_web_SG.csv',row.names=1)
+      GP_web=read.csv('binary_prior_web_para_only.csv',row.names=1)
 
-      %       # Now get the degree distributions from the web
-      % deg_dist_Salix=rowSums(SG_web)/ncol(SG_web)
-      % deg_dist_galler=colSums(SG_web)/nrow(SG_web)
-      % # Interaction probabilities are the product of plant and galler probabilities
-      % sg_int_probs=as.numeric(deg_dist_galler%*%t(deg_dist_Salix))
+            # Now get the degree distributions from the web
+      deg_dist_Salix=rowSums(SG_web)/ncol(SG_web)
+      deg_dist_galler=colSums(SG_web)/nrow(SG_web)
+      # Interaction probabilities are the product of plant and galler probabilities
+      sg_int_probs=as.numeric(deg_dist_galler%*%t(deg_dist_Salix))
 
-      % deg_dist_parasitoid=rowSums(GP_web)/ncol(GP_web)
-      % deg_dist_parasitized=colSums(GP_web)/nrow(GP_web)
-      % gp_int_probs=as.numeric(deg_dist_parasitized%*%t(deg_dist_parasitoid))
+      deg_dist_parasitoid=rowSums(GP_web)/ncol(GP_web)
+      deg_dist_parasitized=colSums(GP_web)/nrow(GP_web)
+      gp_int_probs=as.numeric(deg_dist_parasitized%*%t(deg_dist_parasitoid))
 

### 2017-11-23 code/handy_R_functions.R

@@ -40,7 +40,7 @@ credible_interval<-function(pars,p_lower,p_upper){
 plot_precision<-function(threshold,confidence,pars){
   alpha=pars[[1]]
   beta=pars[[2]]
-  n=seq(0,100,1)
+  n=seq(0,1000,1)
   k=0
   cdf=pbeta(threshold,shape1=alpha,shape2=beta+n)
   samples=length(which(cdf<confidence))

### 2017-11-24 manuscript/CI_interactions.tex
addressed all but one of Dom's comments

@@
 \begin{floatbox}{}
-% DG : I wonder if a paragraph summarizing the extent of the problem with the salix data should not be provided here.
-Either within the text, or a box.
-But we need to convingly show how large is this problem even for such an extensive dataset
-% AC : I like the box idea. Since we refer to the Salix data throughout the manuscript it makes sense to make it stand out. 
+
 [[I had understood that each of the 374 sites was a sample - should we switch to 641 as the maximum sites?]]
@@
 It would respect the order of appearance and better emphasize the bayes section.
+% AC: I couldn't figure out how to put a figure inside a text box, so instead (following an e-mail suggestion) I moved the naive binomial outcome to the figure caption.
 
-  A simple example will illustrate the problem (the full reasoning is provided below): assume that we want to infer the probability of an interaction between two species, A and B.
+  \begin{figure}[h!]
+    \caption{A simple example will illustrate the problem of imperfect detection of interactions (the full reasoning is provided below).
+Assume that we want to infer the probability of an interaction between two species, A and B.
 Now assume that in reality, interaction between A and B is completely impossible (i.e.
 the true $\lambda=0$), but the observer does not know this and seeks to estimate this interaction probability ($\lambda$).
-The record of the number of observed interactions will follow a binomial distribution, with number of trials $k$ and number of observations $n$, for which we can compute the confidence interval of the estimated probability $\lambda$.
-Given no added detection error in observing the incidence of the interaction, then a single observation of species co-occurrence will reveal very little regarding the probability of the interaction – the confidence limits for one observation essentially spans from 0 to 1 (Fig.~\ref{upper_limits} - using Clopper-Pearson's true confidence interval).
-For 5 observations, this confidence limit still extends to 0.5.
+The record of the number of observed interactions will follow a binomial distribution, with number of interactions $k$ and number of observations $n$, for which we can compute the confidence interval of the estimated probability $\lambda$.
+Given no added detection error in observing the incidence of the interaction, then a single observation of species co-occurrence will reveal very little regarding the probability of the interaction – the confidence limits for one observation essentially spans from 0 to 1.
 Only with thirty observations will it shrink to 0.1.
-Thus, adding m ore observations is certainly useful in controlling uncertainty due to stochasticity inherent in the process itself, but the number of observations nonetheless needs to be very high.
-
-  \begin{figure}
-    \caption{This figure illustrates the upper bound (solid black line) of a 95\% confidence interval for the interaction probability $\lambda$ when there is no observation of an interaction ($k = 0$) and $n$ observations of the two species co-occurring at a given location.
-The confidence interval is based on the Clopper-Pearson derivation from the beta distribution.
-A threshold interaction probability of 0.1 is indicated by the dotted red line.}
+Thus, adding more observations is certainly useful in controlling uncertainty due to stochasticity inherent in the process itself, but the number of observations nonetheless needs to be very high.
+Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true confidence interval for $\lambda$ when $k=0$ (A and B have not been observed interacting) for a variety of $n$ (observed co-occurences of A and B).
+A threshold interaction probability of 0.1 is indicated by the dotted red line.
+}
     \label{upper_limits}
@@
 
-  The obvious rule of thumb derived from the above example is ``sample more", but we note that there are limits to the utility of this motto.
+  The obvious rule of thumb is to ``sample more" (see Fig.~\ref{upper_limits} for a demonstration of the power of increasing sample size), but we note that there are limits to the utility of this motto.
 Sampling more will clearly reduce uncertainty regarding the upper bound of the probability of interaction, and it will also increase the probability of detecting unlikely interactions (i.e.
@@
 To record an interaction between A and B, we need to identify both partners correctly (a non-trivial problem in many food webs; e.g.~\citealp{Kaartinen2011,Roslin2016}) and be able to resolve all interactions with a similar likelihood.
-For both molecular and rearing techniques, certain types of interactions may go unnoticed due to technical challenges~\citep{Wirta2016}.
+For both molecular and rearing techniques, certain types of interactions may go unnoticed due to technical challenges~\citep{Wirta2014}.
 This can bias the set of recorded interactions.
@@
 Consequently, the uncertainty in the estimation of $\lambda$ might be considerable.
-In Fig.~\ref{upper_limits}, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda$ varies with sample size.
+In Fig.~\ref{upper_limits} and Box~\ref{box2}, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda$ varies with sample size.
 At a small sample size, the 95\% confidence interval spans all values of $\lambda$.
@@
     \subsection*{Posterior distribution of the interaction probability}
-
-    %DG: note that I replaced theta by lambda to follow the above definitions. Need to make sure it's done throughout
-    %DG: I realize there is an X in here that should be removed as well to avoid confusion with the above nomenclature
 
@@
 
-          % [[Should we still have this?
-At the workshop we talked about how interaction probabilities depend on the degrees of both species and so I'm using predicted interaction probabilities (degreeA*degreeB) in the galler example.
-A writeup for that process follows the original text:]]
-
-%DG: I think so, it is a very useful proposition in the paper to increasingly improve the quality of the prior. I just tried to cut it down in order to follow the above layout. 
-%DG: actually, once I got down to the following section, I realized that the example is based on the degree distribution, so there is not much choice to keep it
-
           The degree of a node in a network is defined as the number of interactions it has to other nodes.
@@
 
-  %Perhaps we want to also have a trait matching example in addition to the degree distribution example below?
-%DG: that would be great, but I think it will be simply too much and too mathy.
-
-  % Are degree distributions valid priors for interaction probabilities in a unipartite web?
-For the Salix-gall dataset we're using interaction probabilities as priors (since the degree of both Salix and galler matter)...
-maybe we should rephrase this to predict the degree of species $i$ based on the degrees of 10 other species in the network?
   The Bayesian framework can be illustrated with a simple quantitative example.
@@
 The maximum likelihood estimate of the interaction probability (Box 1) is simply $\lambda_{MLE} = 3/10 = 0.3$.
-
-%DG: the following example should provide first the real degree, and below the normalized degree. We need to help the reader translating degrees into interaction probabilities
 
@@
 The function ``plot\_precision" in \emph{Appendix S2} calculates distribution function for $\lambda*$ with an increasing number of trials.
-This yields a surprising result: it requires \textgreater24 observations of no interactions to be 95\% sure that the interaction probability is smaller than $\lambda*$=0.1 (recall Fig.~\ref{upper_limits}).
+This yields a surprising result: it requires \textgreater24 observations of no interactions to be 95\% sure that the interaction probability is smaller than $\lambda*$=0.1 (recall Fig.~\ref{upper_limits}, Box~\ref{box2}).
 Note the special case where there is no observation of the two species co-occurring, $n = 0$.
@@
 After obtaining these posterior networks, we calculated the connectance of each web, as well as the number of links per resource (\emph{Salix} in the \emph{Salix}-galler networks or galler in the galler-natural enemy networks) and links per consumer.
-To demonstrate how these network metrics will be affected by detection uncertainty ($\delta$), we then created a suite of filtered networks for each posterior network.
-Networks were filtered by randomly sampling 99\%, 95\%, 90\%, 80\%, 70\&, 60\%, and 50\% of the interactions included in each posterior network.
+To demonstrate how these network metrics will be affected by detection uncertainty, we then created a suite of filtered networks for each posterior network.
+Networks were filtered by randomly sampling 99\%, 95\%, 90\%, 80\%, 70\%, 60\%, and 50\% of the interactions included in each posterior network.
 This gradient is akin to a gradient of sampling effort.
-For each level of detection accuracy, we created 100 randomly-sampled networks per posterior-probability network.
+For each level of detection accuracy, we created 100 randomly-sampled networks per posterior-probability network (giving 100 posterior networks and 1000 detection-filtered networks each for the \emph{Salix}-galler and galler-natural enemy networks).
 We then calculated the same network properties as described above.
@@
 
-    We find, not surprisingly, that the posterior webs for the Salix-galler network all had much higher connectance than the original, observed web (C=0.028 for the observed web, Fig.~\ref{posterior_webs}).
-Likewise, the number of links per \emph{Salix} and galler species in the observed web (2.71 and 1.47, respectively) were much lower than those predicted in the posterior webs, even when filtering with a detection probability of only 50\%.
+    We find, not surprisingly, that the posterior webs for the Salix-galler network all had much higher connectance than the original, observed web (C=0.028 for the observed web and 0.528$\leq$C$\leq$0.568 for the posterior webs; Fig.~\ref{posterior_webs}A).
+Likewise, the number of links per \emph{Salix} and galler species in the observed web ($L_{\emph{Salix}}$=2.71 and $L_{galler}$=1.47, respectively) were much lower than those predicted in the posterior webs (27.4$\leq L_{\emph{Salix}} \leq$29.5 and 50.6$\leq L_{galler} \leq $54.5, respectively; Fig.~\ref{posterior_webs}C,E), even when filtering with a detection probability of only 50\%.
 There are two possible explanations for this discrepancy: either the~\citet{Barbour2016} data do not give an appropriate prior for our dataset, or the true detection probability for links between \emph{Salix} and galler species is much less than 50\%.
@@
 
-    Considering the galler-natural enemy networks, the connectance, mean links per galler, and mean links per natural enemy (0.078, 9.99, and 7.45, respectively) are similar to those in the posterior webs with a detection filter of 50\% (Fig.~\ref{posterior_webs}).
+    Considering the galler-natural enemy networks, the connectance, mean links per galler, and mean links per natural enemy were also much lower in the observed web (C=0.078, $L_{galler}$=9.99, and $L_{natural enemy}$=7.45, respectively) than in the posterior webs (0.183$\leq$ C $\leq$ 0.196, 17.5 $\leq L_{galler} \leq$ 18.9, and 23.0 $\leq L_{natural enemy} \leq$ 24.8).
+When the detection probability was relatively low (i.e., 50\%), however, the properties of randomised networks became similar to those in the observed webs (Fig.~\ref{posterior_webs}B,D,F).
 The~\citet{Barbour2016} network likely provides a better prior here than for the \emph{Salix}-galler networks, as both networks included different galler and natural enemy species.
-Although the two networks differ vastly in scale, and the inclusion of multiple \emph{Salix} species likely causes structural differences from~\citet{Barbour2016} despite the similar resolution of gallers and natural enemies, this result nevertheless suggests that even such a large and well-replicated network is missing a large proportion of interactions.
+Although the two networks differ vastly in scale, and the inclusion of multiple \emph{Salix} species likely causes structural differences from~\citet{Barbour2016} despite the similar resolution of gallers and natural enemies, this result nevertheless suggests that even such a large and well-replicated network as that in~\citet{Kopelke2017} is missing many interactions.
 This should be a strong warning to researchers comparing structural characteristics between networks - small structural differences are very likely to be completely masked by structural changes that would result if missing interactions were included.

### 2017-11-24 manuscript/CI_interactions.tex
moved figs to end
fixed the Frost ref

@@
 
-\begin{floatbox}{}
-
-[[I had understood that each of the 374 sites was a sample - should we switch to 641 as the maximum sites?]]
-    \indent As a case study, we use an extensively sampled \emph{Salix}-galler-natural enemy meta-network.
-This dataset consists of a single community type sampled across Europe; willow (\emph{Salix}) species, willow-galling sawflies, and their natural enemies.
-The data were collected over 29 years at 374 unique locations across Europe, with a total of 641 site visits.
-Each site visit can be considered as a network in its own right and an independent sample from which to build the meta-network.
-The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes.
-The high spatiotemporal resolution of this network and the unusually high sampling effort implemented at the site level makes this dataset particularly well suited for illustrating the difficulties in completely sampling a network and testing Bayesian approaches to overcome these difficulties.
-    \indent We may begin by comparing the frequency of of co-occurence of taxa to reveal the challenge of having sufficient sampling to be confident that an interaction does not occur.
-Most pairs of species (3986/4992 \emph{Salix}-galler pairs and  9794/12096 galler-natural enemy pairs) are never found co-occurring, and for species that did occur the number of co-occurrences was generally low (mean=4.24, var=36.3 for \emph{Salix}-galler pairs; mean=3.87, var=28.8 for galler-natural enemy pairs; Fig.~\ref{histograms}A-B).
-For those species which interacted when co-occurring, the incidence of interaction was also low (mean=12.0, var=155 for \emph{Salix}-galler pairs; mean=4.04, var=29.3 for galler-natural enemy pairs; Fig.~\ref{histograms}C-D).
-Only 2.82\% of \emph{Salix}-galler pairs and 7.76\% of galler-natural enemy pairs were observed interacting at all.
-Thus, even in the most extensive data set that we could find, limited sampling is clearly a major source of uncertainty.
-This dataset also illustrates the potential for increased sampling to not necessarily reveal more interactions as a pair of species that interacts in some cases may not be observed interacting in all cases (Fig.~\ref{histograms}E-F).
-  \caption{\emph{Salix} dataset}
-  \label{box1}
-\end{floatbox}
-
-%DG: be careful : occurrence, not occurance on the figures
-    \begin{figure}
-      \caption{\textbf{A-B)} Most pairs of \emph{Salix} and gallers or gallers and natural enemies were never observed co-occurring despite the high levels of replication in our example dataset.
-For those pairs that were observed together at least once ($n_{ij}>0$), the number of observed co-occurrences was generally small (\textless10).
-Here we show a histogram of the number of pairs of species observed co-occurring at least once.
-3986 \emph{Salix}-galler and 9794 galler-enemy pairs were never observed co-occurring: these pairs are omitted from the histogram.
-\textbf{C-D)} Most pairs of species that were observed at the same site were never observed interacting.
-Here we show a histogram of the number of observed interactions within pairs of co-occurring species.
-\textbf{E-F)} Here we show, for each species pair, the number of observed interactions plotted against the number of observed co-occurrences.
-Most \emph{Salix}-galler pairs either are never observed interacting or interact almost every time they co-occur, while galler-enemy pairs had more variable frequencies of interaction.
-In panels E and F the red, dashed line indicates a 1:1 relationship between interactions and co-occurrences.}
-      \label{histograms}
-      \includegraphics*[width=.8\textwidth]{figures/Salix_Galler_histogram.eps}
-      \end{figure}
-
-%DG: I really appreciate this figure, it makes the point so clear.
-
     In this study, we develop analytical tools to capture the uncertainty in the estimation of pairwise interactions.
@@
 We define the detection of an interaction with the variable $D$, given an interaction is feasible and occurs in the local conditions, as a stochastic process with associated probability $P(D|X,L)=\delta$.
-Detection failure could happen for several reasons, for instance if the rearing of a parasitoid fails with inappropriate lab conditions, because of species mis-identification, or because the interaction is very rare (see~\citet{Wirta2014,FrostXX} for examples of some of these difficulties and partial solutions to them).
+Detection failure could happen for several reasons, for instance if the rearing of a parasitoid fails with inappropriate lab conditions, because of species mis-identification, or because the interaction is very rare (see~\citet{Wirta2014} for examples of some of these difficulties and partial solutions to them).
 Some sources of detection error could be minimised with appropriate sampling effort ($\delta$ will converge to one with increasing number of samples), but other sources are often difficult to reduce (e.g.
-the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification as in~\citet{Wirta2014,FrostXX}).
+the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification as in~\citet{Wirta2014,Frost2016}).
 
@@
 In this case, what can we do to pin down any of these different types of variation?
-
-% DG: it's bizarre to present here the outcome of the naive binomial formulation, while the reasoning is provided later.
-My solution is to move the following section on the binomial model along with the figure within a box.
-It's not central, but formalizes the problem.
-It would respect the order of appearance and better emphasize the bayes section.
-% AC: I couldn't figure out how to put a figure inside a text box, so instead (following an e-mail suggestion) I moved the naive binomial outcome to the figure caption.
-
-  \begin{figure}[h!]
-    \caption{A simple example will illustrate the problem of imperfect detection of interactions (the full reasoning is provided below).
-Assume that we want to infer the probability of an interaction between two species, A and B.
-Now assume that in reality, interaction between A and B is completely impossible (i.e.
-the true $\lambda=0$), but the observer does not know this and seeks to estimate this interaction probability ($\lambda$).
-The record of the number of observed interactions will follow a binomial distribution, with number of interactions $k$ and number of observations $n$, for which we can compute the confidence interval of the estimated probability $\lambda$.
-Given no added detection error in observing the incidence of the interaction, then a single observation of species co-occurrence will reveal very little regarding the probability of the interaction – the confidence limits for one observation essentially spans from 0 to 1.
-Only with thirty observations will it shrink to 0.1.
-Thus, adding more observations is certainly useful in controlling uncertainty due to stochasticity inherent in the process itself, but the number of observations nonetheless needs to be very high.
-Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true confidence interval for $\lambda$ when $k=0$ (A and B have not been observed interacting) for a variety of $n$ (observed co-occurences of A and B).
-A threshold interaction probability of 0.1 is indicated by the dotted red line.
-}
-    \label{upper_limits}
-    \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
-  \end{figure}
 
@@
       %  \vspace{12pt}
-
-%DG :  I think we should add the MLE estimate along with the binomial confidence interval on the figure in order to better illustrate the impact of the prior (obviously only for one N).
-You may draw it with a line to contrast with polygons.
-
-%DG: otherwise the difference between the two interaction types is very interesting and useful to show the effect of the priors. Bravo ! 
-      \begin{figure}[ht]
-        \caption{Using prior distribution based on the \emph{Salix}-galler and galler-natural enemy networks in~\citet{Barbour2016}, we can calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting.
-Here we show posterior distributions for each $\lambda$ in each network ranging from the prior distribution ($n=0$ observed co-occurrence) to the distribution obtained when the pair of species has been observed co-occurring 100 times.
-The distribution narrows and approaches zero as the sample size increases.
-\textbf{A)} The posterior distributions for the \emph{Salix}-galler component are always wider and farther from zero than those for \textbf{B)} the galler-natural enemy component.
-This is likely because the prior distribution for the galler-natural enemy component of the network was both narrower and had a mean closer to that in the~\citet{Kopelke2017} data than did the \emph{Salix}-galler component.}
-        \label{Salix_pdfs}
-        \includegraphics*[width=.8\textwidth]{figures/Salix_Galler_pdfs_increasing_N.eps}
-        \end{figure}
 
@@
 
-      \begin{figure}[ht]
-        \caption{The number of samples required to achieve a given level of confidence that an interaction probability is below a given threshold varies with both parameters.
-With a low threshold, our confidence that $\omega_{ij}$ is below the threshold increases rapidly with repeated observation of co-occurrence without interaction.
-Here we show the cumulative density functions for thresholds probabilities of 0.5 (solid line), 0.25 (dashed line), 0.1 (dash-dot line), and 0.05 (dotted line) as well as the points at which the cdf reaches 0.90 (orange square), 0.95 (red circle), and 0.975 (blue diamond) for each threshold value.
-The large ticks along the x-axis indicate the number of samples associated with each of these points.
-Note that the number of samples required to reach any given threshold is smaller for \textbf{A)} the \emph{Salix}-galler network than for \textbf{B)} the galler-natural enemy network.}
-        \label{Salix_cdfs}
-        \includegraphics[width=.8\textwidth]{figures/Salix_Galler_samples_and_cdfs.eps}
-
-        \end{figure}
-
   \subsection*{Scaling up to network metrics}
@@
 
+\section*{Conclusions/recommendations}
+
+  [Here we need to be very hands-on and remember the invitation letter form Ecol Letters:
+  As a contribution primarily to methodology, the manuscript will not be considered for ``Ideas \& Perspectives".
+(Please recall my message concerning your past presubmission inquiry.) However, Ecology Letters is entertaining the idea of a new section for ``Novel Methods".
+As we have not advertised this, I would ask you to keep that information in confidence.
+If acceptable to an Associate Editor and reviewers, your paper could be the first, or one of the first, contributions to this new section.
+Accordingly, the work would be subject to considerable scrutiny and I would urge you to make the paper as strong as you can.
+This would include demonstrating the need for this new method (i.e.
+outlining how this is different than other approaches currently in use and how they fail at some important task), documenting the robustness and accuracy of the approach, performing case study, and making robust high-quality code freely available.]
+
+\section*{Boxes and figures}
+
+\begin{floatbox}{}
+
+[[I had understood that each of the 374 sites was a sample - should we switch to 641 as the maximum sites?]]
+    \indent As a case study, we use an extensively sampled \emph{Salix}-galler-natural enemy meta-network.
+This dataset consists of a single community type sampled across Europe; willow (\emph{Salix}) species, willow-galling sawflies, and their natural enemies.
+The data were collected over 29 years at 374 unique locations across Europe, with a total of 641 site visits.
+Each site visit can be considered as a network in its own right and an independent sample from which to build the meta-network.
+The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes.
+The high spatiotemporal resolution of this network and the unusually high sampling effort implemented at the site level makes this dataset particularly well suited for illustrating the difficulties in completely sampling a network and testing Bayesian approaches to overcome these difficulties.
+    \indent We may begin by comparing the frequency of of co-occurence of taxa to reveal the challenge of having sufficient sampling to be confident that an interaction does not occur.
+Most pairs of species (3986/4992 \emph{Salix}-galler pairs and  9794/12096 galler-natural enemy pairs) are never found co-occurring, and for species that did occur the number of co-occurrences was generally low (mean=4.24, var=36.3 for \emph{Salix}-galler pairs; mean=3.87, var=28.8 for galler-natural enemy pairs; Fig.~\ref{histograms}A-B).
+For those species which interacted when co-occurring, the incidence of interaction was also low (mean=12.0, var=155 for \emph{Salix}-galler pairs; mean=4.04, var=29.3 for galler-natural enemy pairs; Fig.~\ref{histograms}C-D).
+Only 2.82\% of \emph{Salix}-galler pairs and 7.76\% of galler-natural enemy pairs were observed interacting at all.
+Thus, even in the most extensive data set that we could find, limited sampling is clearly a major source of uncertainty.
+This dataset also illustrates the potential for increased sampling to not necessarily reveal more interactions as a pair of species that interacts in some cases may not be observed interacting in all cases (Fig.~\ref{histograms}E-F).
+  \caption{\emph{Salix} dataset}
+  \label{box1}
+\end{floatbox}
+
+%DG: be careful : occurrence, not occurance on the figures
+    \begin{figure}
+      \caption{\textbf{A-B)} Most pairs of \emph{Salix} and gallers or gallers and natural enemies were never observed co-occurring despite the high levels of replication in our example dataset.
+For those pairs that were observed together at least once ($n_{ij}>0$), the number of observed co-occurrences was generally small (\textless10).
+Here we show a histogram of the number of pairs of species observed co-occurring at least once.
+3986 \emph{Salix}-galler and 9794 galler-enemy pairs were never observed co-occurring: these pairs are omitted from the histogram.
+\textbf{C-D)} Most pairs of species that were observed at the same site were never observed interacting.
+Here we show a histogram of the number of observed interactions within pairs of co-occurring species.
+\textbf{E-F)} Here we show, for each species pair, the number of observed interactions plotted against the number of observed co-occurrences.
+Most \emph{Salix}-galler pairs either are never observed interacting or interact almost every time they co-occur, while galler-enemy pairs had more variable frequencies of interaction.
+In panels E and F the red, dashed line indicates a 1:1 relationship between interactions and co-occurrences.}
+      \label{histograms}
+      \includegraphics*[width=.8\textwidth]{figures/Salix_Galler_histogram.eps}
+      \end{figure}
+
+%DG: I really appreciate this figure, it makes the point so clear.
+
+% DG: it's bizarre to present here the outcome of the naive binomial formulation, while the reasoning is provided later.
+My solution is to move the following section on the binomial model along with the figure within a box.
+It's not central, but formalizes the problem.
+It would respect the order of appearance and better emphasize the bayes section.
+% AC: I couldn't figure out how to put a figure inside a text box, so instead (following an e-mail suggestion) I moved the naive binomial outcome to the figure caption.
+
+  \begin{figure}[h!]
+    \caption{A simple example will illustrate the problem of imperfect detection of interactions (the full reasoning is provided below).
+Assume that we want to infer the probability of an interaction between two species, A and B.
+Now assume that in reality, interaction between A and B is completely impossible (i.e.
+the true $\lambda=0$), but the observer does not know this and seeks to estimate this interaction probability ($\lambda$).
+The record of the number of observed interactions will follow a binomial distribution, with number of interactions $k$ and number of observations $n$, for which we can compute the confidence interval of the estimated probability $\lambda$.
+Given no added detection error in observing the incidence of the interaction, then a single observation of species co-occurrence will reveal very little regarding the probability of the interaction – the confidence limits for one observation essentially spans from 0 to 1.
+Only with thirty observations will it shrink to 0.1.
+Thus, adding more observations is certainly useful in controlling uncertainty due to stochasticity inherent in the process itself, but the number of observations nonetheless needs to be very high.
+Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true confidence interval for $\lambda$ when $k=0$ (A and B have not been observed interacting) for a variety of $n$ (observed co-occurences of A and B).
+A threshold interaction probability of 0.1 is indicated by the dotted red line.
+}
+    \label{upper_limits}
+    \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
+  \end{figure}
+
+%DG :  I think we should add the MLE estimate along with the binomial confidence interval on the figure in order to better illustrate the impact of the prior (obviously only for one N).
+You may draw it with a line to contrast with polygons.
+
+%DG: otherwise the difference between the two interaction types is very interesting and useful to show the effect of the priors. Bravo ! 
+      \begin{figure}[ht]
+        \caption{Using prior distribution based on the \emph{Salix}-galler and galler-natural enemy networks in~\citet{Barbour2016}, we can calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting.
+Here we show posterior distributions for each $\lambda$ in each network ranging from the prior distribution ($n=0$ observed co-occurrence) to the distribution obtained when the pair of species has been observed co-occurring 100 times.
+The distribution narrows and approaches zero as the sample size increases.
+\textbf{A)} The posterior distributions for the \emph{Salix}-galler component are always wider and farther from zero than those for \textbf{B)} the galler-natural enemy component.
+This is likely because the prior distribution for the galler-natural enemy component of the network was both narrower and had a mean closer to that in the~\citet{Kopelke2017} data than did the \emph{Salix}-galler component.}
+        \label{Salix_pdfs}
+        \includegraphics*[width=.8\textwidth]{figures/Salix_Galler_pdfs_increasing_N.eps}
+        \end{figure}
+
+      \begin{figure}[ht]
+        \caption{The number of samples required to achieve a given level of confidence that an interaction probability is below a given threshold varies with both parameters.
+With a low threshold, our confidence that $\omega_{ij}$ is below the threshold increases rapidly with repeated observation of co-occurrence without interaction.
+Here we show the cumulative density functions for thresholds probabilities of 0.5 (solid line), 0.25 (dashed line), 0.1 (dash-dot line), and 0.05 (dotted line) as well as the points at which the cdf reaches 0.90 (orange square), 0.95 (red circle), and 0.975 (blue diamond) for each threshold value.
+The large ticks along the x-axis indicate the number of samples associated with each of these points.
+Note that the number of samples required to reach any given threshold is smaller for \textbf{A)} the \emph{Salix}-galler network than for \textbf{B)} the galler-natural enemy network.}
+        \label{Salix_cdfs}
+        \includegraphics[width=.8\textwidth]{figures/Salix_Galler_samples_and_cdfs.eps}
+
+        \end{figure}
+
     \begin{figure}[ht]
@@
 
-\section*{Conclusions/recommendations}
-
-  [Here we need to be very hands-on and remember the invitation letter form Ecol Letters:
-  As a contribution primarily to methodology, the manuscript will not be considered for ``Ideas \& Perspectives".
-(Please recall my message concerning your past presubmission inquiry.) However, Ecology Letters is entertaining the idea of a new section for ``Novel Methods".
-As we have not advertised this, I would ask you to keep that information in confidence.
-If acceptable to an Associate Editor and reviewers, your paper could be the first, or one of the first, contributions to this new section.
-Accordingly, the work would be subject to considerable scrutiny and I would urge you to make the paper as strong as you can.
-This would include demonstrating the need for this new method (i.e.
-outlining how this is different than other approaches currently in use and how they fail at some important task), documenting the robustness and accuracy of the approach, performing case study, and making robust high-quality code freely available.]
-
 \clearpage

### 2017-11-24 code/figure_generation/pdfs_and_N.py
prepping to add MLE and CI to fig. 3.

@@ -92,7 +92,7 @@ def format_graph(graph,nettype):
   graph.world.xmin=0
   graph.world.xmax=.6
   graph.world.ymin=-0
-  graph.world.ymax=40
+  graph.world.ymax=45
 
   graph.yaxis.tick.configure(major=50,onoff='off',minor_ticks=0,major_size=.7,minor_size=.5,place='both',major_linewidth=1,minor_linewidth=1)
   graph.yaxis.ticklabel.configure(char_size=0,format='decimal',prec=0)
@@ -103,10 +103,10 @@ def format_graph(graph,nettype):
   graph.xaxis.label.configure(text="Probability of interaction",char_size=1,just=2,place='normal')
   graph.yaxis.label.configure(text="Probability density",char_size=1,just=2)
   graph.legend.configure(box_linestyle=0,fill=0,fill_pattern=0,char_size=.75,
-    loc=(0.475,37),loctype='world')
+    loc=(0.475,25),loctype='world')
   if nettype=='SG':
-    graph.add_drawing_object(DrawText,text="N",x=0.545,y=37.5,char_size=.75,just=2,loctype='world')
-  graph.panel_label.configure(placement='iul',char_size=.75,dx=.02,dy=.01)
+    graph.add_drawing_object(DrawText,text="N",x=0.545,y=25.5,char_size=.75,just=2,loctype='world')
+  graph.panel_label.configure(placement='iur',char_size=.75,dx=.02,dy=.01)
 
 
   return graph

### 2017-11-27 code/figure_generation/pdfs_and_N.py
added MLEs and CIs to Fig. 3

@@ -1,7 +1,8 @@
-# ####### R code to generate data files:
-# # Getting distributions:
+####### R code to generate data files:
+# Getting distributions:
 # xdata=matrix(ncol=1001,nrow=12)
 # ydata=matrix(ncol=1001,nrow=12)
+# MLEs=matrix(ncol=4,nrow=12)
 # ns=as.vector(c(0,5,10,15,20,25,50,100,150,200,300,374))
 # for(i in 1:length(ns)){
 #   n=ns[i]
@@ -10,18 +11,25 @@
 #   hx=dnorm(x,dist[[1]],sqrt(dist[[2]]))
 #   xdata[i,]=c(n,x)
 #   ydata[i,]=c(n,hx)
+
+#   MLE=calculate_mean_MLE(sg_int_probs,n,0)
+#   interval=credible_interval(calculate_parameters(sg_int_probs,n,0),0.025,0.975)
+#   MLEs[i,]=c(n,MLE,interval)
+
 # }
 
 # # Data are along rows for pythonic convenience
 # colnames(xdata)=c("N",seq(1,1000))
 # colnames(ydata)=c("N",seq(1,1000))
-
+# colnames(MLEs)=c("N","MLE","lower","upper")
 
 # write.table(xdata,file='../../data/Salix_example/Salix_Galler/distfigure_xvals.tsv',sep='\t')
 # write.table(ydata,file='../../data/Salix_example/Salix_Galler/distfigure_yvals.tsv',sep='\t')
+# write.table(MLEs,file='../../data/Salix_example/Salix_Galler/distfigure_MLEs.tsv',sep='\t')
 
 # xdata=matrix(ncol=1001,nrow=12)
 # ydata=matrix(ncol=1001,nrow=12)
+# MLEs=matrix(ncol=4,nrow=12)
 # ns=as.vector(c(0,5,10,15,20,25,50,100,150,200,300,374))
 # for(i in 1:length(ns)){
 #   n=ns[i]
@@ -30,15 +38,21 @@
 #   hx=dnorm(x,dist[[1]],sqrt(dist[[2]]))
 #   xdata[i,]=c(n,x)
 #   ydata[i,]=c(n,hx)
+
+#   MLE=calculate_mean_MLE(gp_int_probs,n,0)
+#   interval=credible_interval(calculate_parameters(gp_int_probs,n,0),0.025,0.975)
+#   MLEs[i,]=c(n,MLE,interval)
+
 # }
 
[…]

### 2017-11-27 code/handy_R_functions.R

@@ -11,6 +11,19 @@ calculate_parameters<-function(priordata,n,k){
 }
 
 
+calculate_mean_MLE<-function(priordata,n,k){
+  library(MASS)
+  pars=fitdistr(x=priordata,"beta",start=list(shape1=1,shape2=1),lower=c(0,0))$estimate
+  # The lower=c(0,0) prevents R from fitting invalid (negative) parameters
+  alpha=pars[[1]]
+  beta=pars[[2]]
+
+  numerator=alpha+k
+  denominator=alpha+beta+n
+  MLE=numerator/denominator
+  return(MLE)
+}
+
 calculate_distribution<-function(pars){
   alpha=pars[[1]]
   beta=pars[[2]]

### 2017-11-27 code/figure_generation/pdfs_and_N.py
updated fig. caption, put xaxis ticks on top too

@@ -124,7 +124,7 @@ def format_graph(graph,nettype):
   graph.yaxis.tick.configure(major=50,onoff='off',minor_ticks=0,major_size=.7,minor_size=.5,place='both',major_linewidth=1,minor_linewidth=1)
   graph.yaxis.ticklabel.configure(char_size=0,format='decimal',prec=0)
 
-  graph.xaxis.tick.configure(major=.1,onoff='on',minor_ticks=0,major_size=.5,place='normal',minor_size=.5,major_linewidth=1,minor_linewidth=1)
+  graph.xaxis.tick.configure(major=.1,onoff='on',minor_ticks=0,major_size=.5,place='both',minor_size=.5,major_linewidth=1,minor_linewidth=1)
   graph.xaxis.ticklabel.configure(char_size=.75,format='decimal',prec=1)
 
   graph.xaxis.label.configure(text="Probability of interaction",char_size=1,just=2,place='normal')

### 2018-01-16 manuscript/CI_interactions.tex
updated fig. caption, put xaxis ticks on top too
older changes
added Tomes' comments, abstract and first draft of conclusiong

@@
 
+% Main text can be up to 7500 words, 10 fig., tables, boxes
+
 \section*{Abstract}
+
+  Current descriptions of ecological networks will typically assume that specific interactions occur wherever and whenever the community is observed.
+This runs in stark contrast with the widely recognized stochastic nature of ecological communities.
+When accurately resolved, community composition, species abundances and link structure have typically been found to vary in space and time.
+On top of this, finite sampling will generate variation in what links are observed and what not.
+Despite these challenges, we still lack the quantitative methodology to deal with the uncertainty generated by “true” spatiotemporal variation in ecological interactions and by sampling.
+In this study, we develop analytical tools to capture the uncertainty in the estimation of pairwise interactions.
+To define the problem, we first discuss the pervasive implications of uncertainty in the estimation of pairwise interactions on the properties of ecological networks.
+We then define a framework which identifies and dissects the different contributions to uncertainty of interaction.
+We illustrate this framework with a simple quantitative example using the most extensively sampled network to date.
+Next, we use the framework to provide analytical criteria for improving the sampling of rare interactions.
+Finally, we offer tangible recommendations for improved descriptors of ecological interactions.
+Through these efforts, we demonstrate both the utility of our approach and the importance of acknowledging the uncertainty inherent in network studies.
+
+  % Can be up to 200 words
 
@@
 Empirical descriptions of ecological networks are, however, usually considered to be static representations of the communities and interactions they describe.
-This approach contrasts significantly with the widely recognized stochasticity of ecological communities \citep{Gotelli2000}.
 That is, whether the network is assembled based on aggregated data, a single intensive ``snapshot" sample, or expert knowledge, interactions are assumed to occur deterministically wherever and whenever the community is observed~\citep{Olesen2011a}.
 
-    The assumption of static communities conflicts with known variation in both  the nodes and links included in a network.
+    The assumption of static communities contrasts significantly with the widely recognized stochasticity of ecological communities \citep{Gotelli2000}.
 Community composition and species abundances vary from site to site~\citep{Baiser2012} and over time within a site~\citep{Olesen2011a}.
@@
 Moreover, variability in community composition and interactions may or may not be closely related.
-The removal of a species from a site will obviously also remove its interactions, but the co-occurrence of potentially interacting species do not guarantee they will interact at a given place and time.
-Interactions can be lost, or not detected, if participating species remain present but do not co-occur temporally, are too rare to detect each other~\citep{Tylianakis2010}, because of environmental contingencies \citep{Poisot2015}, or through changes to individual preferences~\citep{Fodrie2015}.
+The removal of a species from a site will obviously also remove its interactions, but conversely, the co-occurrence of potentially interacting species does not in itself guarantee that they will interact at a given place and time.
+Interactions can be lost if the interaction partners remain present but are separated in time or are too rare to detect each other~\citep{Tylianakis2010}.
+Interactions can also fail to occur because of environmental contingencies \citep{Poisot2015}, or through changes to individual preferences~\citep{Fodrie2015}.
 
     Beyond ``true" variation in network structure, several researchers have pointed to the importance of sampling intensity for the assessment of network structure (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007}).
-Accumulation of interactions with increasing sampling effort suggests that it is even more challenging to document interactions than species richness \citep{Poisot2012}.
+An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to document interactions than species richness \citep{Poisot2012}.
 As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly \citep{Poisot2016}.
-Despite this possibility, the acknowledgment that insufficient sampling effort limits our ability to describe variation in ecological networks has not yet led to a quantitative methodology to deal with the uncertainty generated by spatiotemporal variation in ecological interactions and by sampling.
-Moreover, even in extremely well-sampled networks uneven sampling across species (or pairs of species) can lead to the assumption that some species do not interact because they co-occur rarely or have not yet been observed co-occuring (see Box 1 for an example).
-It is therefore likely that nearly all network studies are missing some interactions and could benefit from an approach that acknowledges this uncertainty.
+Yet, to dat, we lack the quantitative methodology to deal with the uncertainty generated by spatiotemporal variation in ecological interactions and by sampling.
+Moreover, even in extremely well-sampled networks uneven sampling across species (or pairs of species) can lead to the erroneous inference that some species do not interact because they co-occur rarely or have not yet been observed together - even if they do interact when they do co-occur (see Box 1 for an example).
+Nearly all network studies will thus neglect some interactions, necessitating an approach that acknowledges this uncertainty.
 
@@
 
-  To define the problem associated with describing ecological interaction networks, we will start from the perspective of an empirical community ecologist faced with the task of describing an interaction network.
+  To define the problem associated with quantifying ecological interaction networks, we will start from the perspective of an empirical community ecologist faced with the task of describing a previously unknown interaction network.
 This ecologist will be interested in generating a description of the species/nodes present, and the links between them~\citep{Roslin2016}.
@@
 Thus, the detection of any interaction is a stochastic process.
-We consider that there are three nested levels of uncertainty contributing to this stochasticity:
+We define three nested levels of uncertainty contributing to this stochasticity:
 
@@
 We define the probability of an interaction $L$ given those characteristics $\mathbf{T}$ as $P(L | \mathbf{T})=\lambda$.
-Obviously, if $k$ (the number of observed interactions) is 0, it is possible that the two species cannot interact even if there were no time or environmental constraints preventing it from occurring.
+Obviously, if $k$ (the number of observed interactions) is 0, it is possible that the two species could not interact even if there were no external constraints (e.g., temporal or environmental separation) preventing the interaction from occurring.
+As a simple example, a prey species may be too large to be consumed by a particular predator.
 In such cases, $\lambda$ would take a value of 0.
@@
 I've toned down "very likely" to "possible" though - does that help?]]
-    But it is nonetheless possible that the interaction is a rare phenomenon that has never been documented before, with $\lambda>0$.
+    Nevertheless, it is also possible that the interaction is a rare phenomenon with $\lambda>0$ that has not yet been documented.
 This source of uncertainty is the one documented by trait-matching models~\citep{Bartomeus2016}.
@@
 
-    It could be that we know an interaction is feasible, i.e.
-$L=1$, but that it does not occur at a given location or moment in time because of local constraints such as inclement weather or lack of suitable habitat.
+    Even when an interaction is feasible, i.e.
+$L=1$, it may not occur at a given location or moment in time because of local constraints such as inclement weather or the lack of suitable habitat.
 We define the realisation of the interaction process with the variable $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L)=\chi$.
@@
 
-    Lastly, measurement errors are always a source of uncertainty in the observation of ecological processes.
-We define the detection of an interaction with the variable $D$, given an interaction is feasible and occurs in the local conditions, as a stochastic process with associated probability $P(D|X,L)=\delta$.
+    Lastly, measurement errors are a pervasive source of uncertainty in the observation of ecological processes.
+Given that an interaction with the variable $D$, given an interaction is feasible and occurs under the local conditions, we may define the detection of an interaction, $D$, as a stochastic process with the associated probability $P(D|X,L)=\delta$.
 Detection failure could happen for several reasons, for instance if the rearing of a parasitoid fails with inappropriate lab conditions, because of species mis-identification, or because the interaction is very rare (see~\citet{Wirta2014} for examples of some of these difficulties and partial solutions to them).
@@
 
-    % \subsection*{What is an observation of "no interaction"?}
-
-    The combination of these three sources of uncertainty together leads to many potential explanations for the observation of an absence of interaction ($D$, $X$, and/or $L = 0$), but only the situation where $L = 0$ (a true absence) is relevant for the investigation of networks.
-While the observation of an interaction is straightforward to interpret, absence of interactions must be decomposed into different quantities.
-It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e.
-the interaction occurred at the location but was not observed, and $D=1 \cup X = 0 \cup L =1$, the interaction is feasible and would have been detected but did not occur at the local site.
-Ecologists seek to measure the occurrence of true absences, which is the joint event $L=0 \cup X=1 \cup D=1$), but in reality they measure the marginal probability $P(L) = k/n$ where $k$ is again the number of observed interactions and $n$ the number of observed co-occurrences.
-
 \section*{Estimating detection and process uncertainty}
 
-  For the ecologist collecting or interpreting network data, the considerations above raise a major challenge: how may we infer whether unobserved interactions went undetected due to sampling, or whether they truly do not occur.
+    Together, the combination of these three sources of uncertainty --interaction uncertainty, process uncertainty, and detection uncertainty-- results in a range of potential explanations for the observation of an absence of interaction ($D$, $X$, and/or $L = 0$).
+The ecologist wanting to describe the network, however, is specifically interested in the situation where $L = 0$ (i.e., in true absences).
+Thus, while she or he will have no difficulty interpreting the observation of an interaction, the observation of an absence of an interaction offers more of a challence since it must be decomposed into different quantities.
+It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e.
+where the interaction occurred at the location but was not observed, and $D=1 \cup X = 0 \cup L =1$, when the interaction is feasible and would have been detected but did not occur at the local site.
+The occurrence of a true absence, our quantity of interest, corresponds to the joint event $L=0 \cup X=1 \cup D=1$), but in reality an empirical ecologist will measure the marginal probability $P(L) = k/n$ where $k$ is again the number of observed interactions and $n$ the number of observed co-occurrences.
+
+    The considerations above raise a major challenge: when faced with empirical data, how may we infer whether unobserved interactions went undetected due to sampling, or whether they truly do not occur.
 How then may we refine our sampling approaches to reduce uncertainties, and to gain insights into the impact of multiple processes on field observations?
@@
 
-  The basic information that we are collecting consists of matrices of interaction partners.
+  % [[Tomas suggests removing the following because it slows down procedings:]]
+  % The basic information that we are collecting consists of matrices of interaction partners.
 Our count of interactions between two species reflects uncertainty with respect to whether two species are capable of interacting when co-occurring at a given site ($\lambda$), chance variation in whether the interaction is realised ($\chi$),  and uncertainty with respect to whether it is detected when realised ($\delta$).
@@
 
-  The obvious rule of thumb is to ``sample more" (see Fig.~\ref{upper_limits} for a demonstration of the power of increasing sample size), but we note that there are limits to the utility of this motto.
+  % The obvious rule of thumb is to ``sample more" (see Fig.~\ref{upper_limits} for a demonstration of the power of increasing sample size), but we note that there are limits to the utility of this motto.
 Sampling more will clearly reduce uncertainty regarding the upper bound of the probability of interaction, and it will also increase the probability of detecting unlikely interactions (i.e.
@@
 
-  As a solution towards deciding whether unobserved interactions were undetected due to sampling, or whether they truly do not occur,~\citet{Weinstein2017} used repeated sampling rounds to estimate the daily probability of detecting a hummingbird interaction, and to thereby model the observation and process mechanisms.
+  % As a solution towards deciding whether unobserved interactions were undetected due to sampling, or whether they truly do not occur,~\citet{Weinstein2017} used repeated sampling rounds to estimate the daily probability of detecting a hummingbird interaction, and to thereby model the observation and process mechanisms.
 While conceptually attractive, this approach is unsuitable for interactions occurring over longer time scales (e.g., associations between hosts and parasitoids with a single generation per year), or very rare interactions which might not occur on any of the sampling days or might involve individuals of a species that are not under observation.
@@
 
-  An added complication is that not all sources of uncertainty are proportional to sample size.
+  % An added complication is that not all sources of uncertainty are proportional to sample size.
 To record an interaction between A and B, we need to identify both partners correctly (a non-trivial problem in many food webs; e.g.~\citealp{Kaartinen2011,Roslin2016}) and be able to resolve all interactions with a similar likelihood.
@@
   To progressively dissect the different contributions to uncertainty, we will start by considering how we could naively quantify interaction probability and its associated uncertainty \emph{for an interaction that has not yet been observed}.
-We consider that a pair of species have been observed $n$ times co-occurring at one location, and the number of times they have been observed interacting is $k = 0$.
+We consider the case where a pair of species have been observed co-occurring $n$ times, of which they have been observed to interact in $k = 0$ cases.
 We now aim to evaluate the uncertainty of this interaction.
@@
 This means that even if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact.
-What it implies is that no interaction is the most likely situation but there is nonetheless a substantial chance that the two species \emph{could} interact.
-In contrast with the situation where $k>0$, when we are sure that an interaction is feasible, we are not sure that absence of interactions is caused by $L=0$.
-Second, and most importantly, the number of trials $n$ might be very low in many instances (and some pairs of species might not have been documented as co-occuring even once).
+What it implies is that 'no interaction' is the most likely ø¨†come when the species do co-occur, but there is nonetheless a substantial chance that the two species \emph{could} interact.
+In contrast, in the situation where $k>0$, i.e., when we are sure that an interaction is feasible, we still cannot be sure that absence of interactions is caused by $L=0$.
+Second, and most importantly, the number of trials $n$ might be very low in many instances (and some pairs of species may never have been documented as co-occuring).
 Consequently, the uncertainty in the estimation of $\lambda$ might be considerable.
@@
 To establish that species are not interacting with any acceptable certainty requires tens of observations of the two species co-occurring but not interacting.
-As most data sets will not have such extensive sampling across all observations, we can use a Bayesian approach to supplement what data we do have with other sources of information.
+As most data sets will lack such extensive sampling across all observations, we can use a Bayesian approach to supplement what data we do have with other sources of information.
 
@@
 
-      We here adopt a Bayesian approach to estimate the distribution of the parameter $\lambda$. According to Bayes principle, the posterior distribution of $\lambda$ is:
+      Here we adopt a Bayesian approach to estimate the distribution of the parameter $\lambda$. According to Bayes principle, the posterior distribution of $\lambda$ is:
 
@@
 
-     In some cases it can be complicated to compute the normaliser, but fortunately in our case an analytical solution exists.
+     In some cases it can be complicated to compute the normaliser, but fortunately an analytical solution already exists in our case.
 The beta-binomial distribution is a conjugate distribution of the binomial distribution.
@@
 
-          In the literature of ecological networks there is a solid collection of data for which we know network connectance and from which we can define the connectance distribution.
+          In the literature of ecological networks there is a solid collection of networks for which connectance has been calculated and for which we can thus define the connectance distribution.
 Connectance is measured as $C = L/S^2$, where $L$ is the number of interactions and $S$ is the number of species.
@@
 
-          The degree of a node in a network is defined as the number of interactions it has to other nodes.
+          The degree of a node in a network is defined as its number of connections to other nodes.
 The degree distribution of a network is then the probability distribution of these degrees over the whole network and the standardised degree could therefore be interpreted as an interaction probability.
@@
 
-          If our focal network describes a similar system to that in a known network, we can use the distribution of interaction probabilities in that network to inform our prior.
+          If our focal network describes a system similar to that in a known network, we can use the distribution of interaction probabilities in that network to inform our prior.
 The probability of any interaction $L_ij$ depends on the degrees of species $i$ and $j$.
@@
 
-          The last approach we envision to document the prior distribution of $\lambda$ is to use the outcome of a trait-matching model, provided such a model has been documented using external data and relevant traits are available.
+          As a fourth and final approach to obtain the prior distribution of $\lambda$, we envisage using the outcome of a trait-matching model, provided such a model has been documented using external data and relevant traits are available.
           In such as case, the prior distribution would follow the function $P(\lambda|\mathbf{T})=f(\mathbf{T})$ based on a set of traits for both species $\mathbf{T}$.
@@
 Suppose we have $n = 10$ observations of co-occurrence between species $i$ and species $j$ in a given time interval and area, and $k = 3$ observations of interactions.
-The maximum likelihood estimate of the interaction probability (Box 1) is simply $\lambda_{MLE} = 3/10 = 0.3$.
+Then, the maximum likelihood estimate of the interaction probability (Box 1) is simply $\lambda_{MLE} = 3/10 = 0.3$.
 
@@
 $k=0$.
-The question is then ``what is the probability these two species do not interact''?
-Since it is not possible to prove that the two species could never interact (strickly speaking, in this approach $\lambda=0$ is impossible), given the framework above we must fix a threshold below which we consider that there is no interaction ($\lambda \sim 0$).
+The question is then ``what is the probability that these two species do not interact''?
+Since it is not possible to prove that the two species could never interact (strictly speaking, in this approach $\lambda=0$ is impossible), we must fix a threshold below which we consider that there is no interaction ($\lambda \sim 0$).
 We call this threshold probability $\lambda*$.
@@
 Note the special case where there is no observation of the two species co-occurring, $n = 0$.
-In this situation, the posterior distribution converges to the prior distribution since the data include no information on the probability with which species might interact should they co-occur).
+In this situation, the posterior distribution converges to the prior distribution since the data include no information on the probability with which species might interact should they co-occur.
 
@@
 It is not as easy, however, to understand how the uncertainty in these estimated interaction probabilities influences network metrics.
-Computation of these metrics involves non-linear functions and therefore, because of Jensen's inequality (which states that the average of a non-linear function of a stochastic variable differs from the function of the average of that variable), any uncertainty in $\lambda$s could bias both the mean and variance of a network metric.
+Computation of these metrics involves non-linear functions.
+Since Jensen's inequality states that the average of a non-linear function of a stochastic variable differs from the function of the average of that variable, any uncertainty in the values of $\lambda$ could bias both the mean and variance of a network metric.
 For instance, assume that among the pairs of species with few observed co-occurrences there are many pairs which truly interact.
@@
 Instead we must rely on computer simulations.
-In the following section, we will provide an empirical example based on an extremely well-sampled \emph{Salix}-galler-natural enemy system (\citealp{Kopelke2017}; see Box~\ref{box1} for a description).
+In the following section, we will provide an empirical example based on the well-sampled system of \emph{Salix}  plants, herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}; see Box~\ref{box1} for a description).
+This tripartite network can be examined as two bipartite networks, namely \emph{Salix}-galler and galler-natural enemy networks.
 We will show how the uncertainty arising from both absences of co-occurrences and false absences of interactions impact these metrics.
@@
       In a strict Bayesian framework, we wish to use a prior distribution that does not rely on any information from the study at hand.
-To that end, we use data from another well-described \emph{Salix} galler-natural enemy system~\citep{Barbour2016,Barbour2016Dryad}.
-Note that this study used several genotypes of \emph{Salix hookeriana} rather than different \emph{Salix} species.
-We estimated frequencies of  \emph{S.
+To that end, we use data from another well-described system of \emph{Salix}, gallers, and natural enemies~\citep{Barbour2016,Barbour2016Dryad}.
+We note that this study used several genotypes of \emph{Salix hookeriana} rather than different \emph{Salix} species, but stress that this difference is unlikely to be critical for our purposes.
+Our interest in specifically in what information can be gained from the extensive sampling of \emph{Salix}, gallers, and natural enemies across Europe and what even such thorough sampling does not reveal; the similar but much smaller system in the United States is merely a starting point from which to obtain somewhat reasonable priors.
+To do this, we estimated frequencies of  \emph{S.
 hookeriana} genotype-galler interactions based on the normalised degree of each species in each network component (see \emph{Appendix S1} for details and code).
@@
 This is consistent with the prior data, where the average interaction probability based on the degree distributions of \emph{Salix} genotypes and gallers was 0.562 and that for gallers and natural enemies was 0.122.
-These probabilities are much higher than those in our dataset (0.028 and 0.078 for the \emph{Salix}-galler and galler-natural enemy networks, respectively).
-This discrepancy may reflect the differences in scale between a network containing different genotypes of a single \emph{Salix} species and four gallers from a single family in~\citet{Barbour2016} and a network containing many \emph{Salix} species and gallers from many families as is the case in~\citet{Kopelke2017}.
+These probabilities are much higher than those in our dataset (0.028 and 0.078 for the \emph{Salix}-galler and galler-natural enemy networks, respectively) - a discrepancy which may reflect the differences in scale between the network containing different genotypes of a single \emph{Salix} species and four gallers from a single family in~\citet{Barbour2016} and the extensive network of~\citet{Kopelke2017} which contains tens of \emph{Salix}, galler, and natural enemy species, with the insects representing many different families.
 
       For a pair of species where some co-occurrences were observed, we can update the prior distribution with these data.
-If we consider only pairs of species which were observed to co-occur but not to interact, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs.
-Thus $\alpha'$=$\alpha$ and $\beta'$=$\beta + n$.
-At the most extreme case, for a pair of species which co-occurred at all 374 sites and was never observed to interact, our distributions would become
+If we consider only pairs of species which were observed to co-occur but not to interact, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs; thus $\alpha'$=$\alpha$ and $\beta'$=$\beta + n$.
+As the most extreme case, for a pair of species which co-occurred at all 374 sites and was never observed to interact, our distributions would become
       $\bar\lambda_{ij}$=6.63 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=1.74 $\times$ 10$^{-5}$ for the \emph{Salix}-galler network and 
       $\bar\lambda_{ij}$=3.49 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=9.03 $\times$ 10$^{-6}$ for the galler-natural enemy network.
-
-      With species $i$ and $j$ co-occurring at all 374 sites and never being observed to interact, the maximum likelihood expectation for the probability of an interaction $ij$ is very close to 0 and the variance about this estimate is very narrow.
+Thus, for species $i$ and $j$ co-occurring at all 374 sites and never being observed to interact, the maximum likelihood expectation for the probability of an interaction $ij$ is very close to 0 and the variance about this estimate is very narrow.
 In other words, we could establish with high certainty that the species will never interact.
@@
 Given the low levels of replication in most network studies, this implies that we should have fairly low confidence in many ``non-interacting" pairs of species.
-Even in the extensively replicated \emph{Salix}-galler-natural enemy dataset very few species pairs were observed co-occurring frequently enough to reach these thresholds (only three \emph{Salix}-galler pairs and 31 galler-natural enemy pairs were observed co-occurring frequently enough to reach the threshold for an interaction probability of 0.1, and no pairs were observed co-occurring frequently enough to reach the threshold for an interaction probability of 0.01).
+Even in the extensively replicated \emph{Salix}-galler-natural enemy dataset very few species pairs were observed co-occurring frequently enough to reach these thresholds.
+In fact, only three \emph{Salix}-galler pairs and 31 pairs of gallers and their natural enemies were observed co-occurring frequently enough to reach the threshold for an interaction probability of 0.1.
+No pairs were observed to co-occur frequently enough to reach the threshold for an interaction probability of 0.01.
 Discounting potential interactions, then, requires either a stronger prior expectation of no interaction (e.g., we can be highly confident that a palm tree will not predate upon a leopard no matter how many times the two species are observed together) or very extensive sampling.
+For all we know, most links absent from current descriptions of network structure may be so not because the species do not interact, but because we have not sampled deeply enough to detect them.
 
@@
 
-    Using the prior distributions and procedures described above, we calculated posterior probability distributions for \emph{Salix}-galler or galler-natural ememy pair that was not observed interacting.
+    Using the prior distributions and procedures described above, we calculated posterior probability distributions for \emph{Salix}-galler or galler-natural enemy pairs that were not observed interacting.
 Using these posterior distributions and assuming probabilities of 1 for pairs of species that were observed interacting, we created a suite of 100 webs of each network type by randomly sampling from each posterior distribution.
@@
 
-    We find, not surprisingly, that the posterior webs for the Salix-galler network all had much higher connectance than the original, observed web (C=0.028 for the observed web and 0.528$\leq$C$\leq$0.568 for the posterior webs; Fig.~\ref{posterior_webs}A).
+    We find, perhaps not surprisingly, that the posterior webs for the Salix-galler network all had much higher connectance than the original, observed web (C=0.028 for the observed web and 0.528$\leq$C$\leq$0.568 for the posterior webs; Fig.~\ref{posterior_webs}A).
 Likewise, the number of links per \emph{Salix} and galler species in the observed web ($L_{\emph{Salix}}$=2.71 and $L_{galler}$=1.47, respectively) were much lower than those predicted in the posterior webs (27.4$\leq L_{\emph{Salix}} \leq$29.5 and 50.6$\leq L_{galler} \leq $54.5, respectively; Fig.~\ref{posterior_webs}C,E), even when filtering with a detection probability of only 50\%.
-There are two possible explanations for this discrepancy: either the~\citet{Barbour2016} data do not give an appropriate prior for our dataset, or the true detection probability for links between \emph{Salix} and galler species is much less than 50\%.
+There are two possible explanations for this discrepancy: either the data of~\citet{Barbour2016} is simply too different from that of~\citet{Kopelke2017} to offer an appropriate prior for our dataset, or the true detection probability for links between \emph{Salix} and galler species is much less than 50\%.
 As the scale of the two datasets is quite different (genotypes of a single \emph{Salix} species in~\citet{Barbour2016}, various \emph{Salix} species in our dataset), we suspect the former is more likely.
+    [[This is a little boring. Tomas has ideas for people with potentially better priors - may require another co-author. Also maybe could use one site as a prior like "training data"?]]
 
@@
 Although the two networks differ vastly in scale, and the inclusion of multiple \emph{Salix} species likely causes structural differences from~\citet{Barbour2016} despite the similar resolution of gallers and natural enemies, this result nevertheless suggests that even such a large and well-replicated network as that in~\citet{Kopelke2017} is missing many interactions.
-This should be a strong warning to researchers comparing structural characteristics between networks - small structural differences are very likely to be completely masked by structural changes that would result if missing interactions were included.
+This should be a strong warning to researchers comparing structural characteristics between networks - small structural differences are likely to be masked by substantial noise resulting from sampling uncertainty.
 
@@
 
-  [Here we need to be very hands-on and remember the invitation letter form Ecol Letters:
-  As a contribution primarily to methodology, the manuscript will not be considered for ``Ideas \& Perspectives".
+  Real interaction networks vary~\citep{}, and to capture this variation we must turn from static descriptions of network structure to probabilistic descriptions.
+In this study, we have developed the analytical tools to capture the uncertainty in the estimation of pairwise interactions, and to partition it into its individual components: interaction uncertainty, process uncertainty and detection uncertainty.
+The patters unveiled offer tangible recommendations for improved descriptors of ecological interactions.
+First, our analyses point to detection uncertainty as a major contributor to overall uncertainty of is establishing the absence of interaction.
+To counter these establish the true absence of interactions will then require comparatively large sample size – on the order of xxx.
+Second, xxxx.
+Third, xxxx.
+Through these efforts, we demonstrate both the utility of our approach and the importance of acknowledging the uncertainty inherent in network studies.
+All code used in the paper is made available in the companion supplementary material.
+
+  % [Here we need to be very hands-on and remember the invitation letter form Ecol Letters:
+  % As a contribution primarily to methodology, the manuscript will not be considered for ``Ideas \& Perspectives".
 (Please recall my message concerning your past presubmission inquiry.) However, Ecology Letters is entertaining the idea of a new section for ``Novel Methods".
@@
 
-[[I had understood that each of the 374 sites was a sample - should we switch to 641 as the maximum sites?]]
     \indent As a case study, we use an extensively sampled \emph{Salix}-galler-natural enemy meta-network.
@@
 You may draw it with a line to contrast with polygons.
+% Done, think it works for all N
 
@@
 The distribution narrows and approaches zero as the sample size increases.
+Likewise, the maximum likelihood estimator for the mean probability of interaction (diamonds) approaches zero and the 95\% credible interval (lines) narrows as sample size increases.
 \textbf{A)} The posterior distributions for the \emph{Salix}-galler component are always wider and farther from zero than those for \textbf{B)} the galler-natural enemy component.

### 2018-01-17 manuscript/CI_interactions.tex
some small updates

@@
 
-  Current descriptions of ecological networks will typically assume that specific interactions occur wherever and whenever the community is observed.
-This runs in stark contrast with the widely recognized stochastic nature of ecological communities.
-When accurately resolved, community composition, species abundances and link structure have typically been found to vary in space and time.
-On top of this, finite sampling will generate variation in what links are observed and what not.
-Despite these challenges, we still lack the quantitative methodology to deal with the uncertainty generated by “true” spatiotemporal variation in ecological interactions and by sampling.
-In this study, we develop analytical tools to capture the uncertainty in the estimation of pairwise interactions.
-To define the problem, we first discuss the pervasive implications of uncertainty in the estimation of pairwise interactions on the properties of ecological networks.
-We then define a framework which identifies and dissects the different contributions to uncertainty of interaction.
-We illustrate this framework with a simple quantitative example using the most extensively sampled network to date.
-Next, we use the framework to provide analytical criteria for improving the sampling of rare interactions.
-Finally, we offer tangible recommendations for improved descriptors of ecological interactions.
+  Descriptions of ecological networks typically assume that the same interspecific interactions occur wherever and whenever a community is observed.
+This contrasts with the known stochasticity of ecological communities: community composition, species abundances, and link structure all vary in space and time.
+On top of this, finite sampling will generate variation in the set of interactions that are actually observed.
+Despite recognising these challenges, we lack the quantitative methodology to deal with the uncertainty generated by “true” spatiotemporal variation in ecological interactions or by incomplete sampling.
+Here we develop analytical tools to capture the uncertainty in the estimation of pairwise interactions.
+To define the problem, we identify the different contributions to the uncertainty of an interaction and discuss the implications of this uncertainty in the estimation of network properties.
+We then develop a framework to explicitly quantify the uncertainty around each interaction.
+We illustrate this framework using the most extensively sampled network to date, demonstrating the universal uncertainty in network studies.
+Finally, we offer tangible recommendations for improving descriptions of ecological networks and for better sampling of rare interactions.
 Through these efforts, we demonstrate both the utility of our approach and the importance of acknowledging the uncertainty inherent in network studies.
 
-  % Can be up to 200 words
+  % Can be up to 200 words. This is 200 exactly.
+  % Word count can be up to 7500, we're at about 5700 without the boxes. Should be grand.
 
@@
 
-    Representation of a species assemblage as a network offers a convenient summary of how the community is constructed as it simultaneously accounts for species composition and their interactions.
-A tabulation of the nodes (species) and of their relative abundances forms the basis for traditional metrics of community composition.
-On top of this information, interactions are represented by links between nodes so that networks provide additional, higher-order information on community structure.
-Empirical descriptions of ecological networks are, however, usually considered to be static representations of the communities and interactions they describe.
+    Representating an assemblage of species as a network offers a convenient summary of how the community is constructed as it simultaneously accounts for species composition and interactions between species.
+A tabulation of the nodes (species) and their relative abundances forms the basis for traditional metrics of community composition.
+To move from these simpler metrics to a network framework, the tabulation of nodes is combined with interactions (links between nodes) so that networks provide additional, higher-order information on community structure.
+While this additional information is useful (as, for example, interactions can affect changes in species abundances over time), empirical descriptions of ecological networks are still limited because they are usually considered to be static representations of the communities and interactions they describe.
 That is, whether the network is assembled based on aggregated data, a single intensive ``snapshot" sample, or expert knowledge, interactions are assumed to occur deterministically wherever and whenever the community is observed~\citep{Olesen2011a}.
 
-    The assumption of static communities contrasts significantly with the widely recognized stochasticity of ecological communities \citep{Gotelli2000}.
+    The assumption of static communities contrasts significantly with the widely recognized stochasticity of ecological communities~\citep{Gotelli2000}.
 Community composition and species abundances vary from site to site~\citep{Baiser2012} and over time within a site~\citep{Olesen2011a}.
@@
 Moreover, variability in community composition and interactions may or may not be closely related.
-The removal of a species from a site will obviously also remove its interactions, but conversely, the co-occurrence of potentially interacting species does not in itself guarantee that they will interact at a given place and time.
+The removal of a species from a site will obviously also remove its interactions but, conversely, the co-occurrence of potentially interacting species does not in itself guarantee that they will interact at a given place and time.
 Interactions can be lost if the interaction partners remain present but are separated in time or are too rare to detect each other~\citep{Tylianakis2010}.
-Interactions can also fail to occur because of environmental contingencies \citep{Poisot2015}, or through changes to individual preferences~\citep{Fodrie2015}.
+Interactions can also fail to occur because of environmental contingencies~\citep{Poisot2015}, or through changes to individual preferences~\citep{Fodrie2015}.
 
     Beyond ``true" variation in network structure, several researchers have pointed to the importance of sampling intensity for the assessment of network structure (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007}).
-An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to document interactions than species richness \citep{Poisot2012}.
-As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly \citep{Poisot2016}.
-Yet, to dat, we lack the quantitative methodology to deal with the uncertainty generated by spatiotemporal variation in ecological interactions and by sampling.
-Moreover, even in extremely well-sampled networks uneven sampling across species (or pairs of species) can lead to the erroneous inference that some species do not interact because they co-occur rarely or have not yet been observed together - even if they do interact when they do co-occur (see Box 1 for an example).
+An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to document interactions than species~\citep{Poisot2012}.
+As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Poisot2016}.
+Yet, to date, we lack the quantitative methodology to deal with the uncertainty generated by spatiotemporal variation in ecological interactions and by sampling.
+Even in extremely well-sampled networks, uneven sampling across species (or pairs of species) can lead to the erroneous inference that some species do not interact because they co-occur rarely or have not yet been observed together - even if they do interact when they do co-occur (see Box 1 for an example).
 Nearly all network studies will thus neglect some interactions, necessitating an approach that acknowledges this uncertainty.
@@
 We focus on binary interactions as a first step, but the framework could be expanded to deal with interaction frequencies and strength.
-To define the problem, we first discuss the pervasive implications of uncertainty in the estimation of pairwise interactions on the properties of ecological networks.
-We then define a framework which identifies and dissects the different contributions to uncertainty of interaction.
-We illustrate this framework with a simple quantitative example using the most extensively sampled network to date (Box 1).
-Next, we use the framework to provide analytical criteria for improving the sampling of rare interactions.
-Finally, we offer tangible recommendations for improved descriptors of ecological interactions.
+To define the problem, we first identify the different contributions to the uncertainty of an interaction and discuss the implications of each source of uncertainty for the properties of ecological networks.
+Next, we develop an analystical framework to quantify the uncertainty around interactions in an empirical web.
+We illustrate this framework using the most extensively sampled network to date (Box 1).
+Finally, we offer tangible recommendations for improved descriptors of ecological interactions [[double-check that we do this]].
 Through these efforts, we demonstrate both the utility of our approach and the importance of acknowledging the uncertainty inherent in network studies.
@@
 
-  To define the problem associated with quantifying ecological interaction networks, we will start from the perspective of an empirical community ecologist faced with the task of describing a previously unknown interaction network.
+  To define the problems associated with quantifying ecological interaction networks, we will start from the perspective of an empirical community ecologist faced with the task of describing a previously unknown interaction network.
 This ecologist will be interested in generating a description of the species/nodes present, and the links between them~\citep{Roslin2016}.
@@
 It arises because every model is imperfect and lacks information (i.e.
-about traits) defining the constraints on the interaction.
-In other words, with sufficient sampling and all information accessible, this interaction probability $\lambda$ should either tend to 0 or to 1 and the uncertainty vanishes.
+about traits) that could be used to define constraints on the interaction.
+In other words, with sufficient sampling and all information accessible, this interaction probability $\lambda$ should either tend to 0 or to 1 and the uncertainty should vanish.
     % [[For species which actually co occur (?)]]
@@
 This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology about the contingencies of interactions.
-Phenological matching~\citep{MillerRushing2010,Gezon2016}, species preferences~\citep{Pires2011,Novak2015,Coux2016}, and fear effects of other species~\citep{} are just some of the factors contributing to variation in the frequency of interactions between a given pair of species.
+Phenological matching~\citep{MillerRushing2010,Gezon2016}, species preferences~\citep{Pires2011,Novak2015,Coux2016}, and fear effects of other species~\citep{Luttbeg2005,Wirsing2007} are just some of the factors contributing to variation in the frequency of interactions between a given pair of species.
     % We imagine for instance that an interaction between a gall and a parasitoid might not be recorded at a location because it was the wrong time of the year and the gall had not yet formed (phenological constraints), a late frost killed the larvae (an abiotic environmental constraint), another parasitoid species competitively excluded the parasitoid species of interest (a biotic environmental constraint) or simply the parasitoid is too rare to interact with all of its viable hosts (an abundance constraint).
@@
 Detection failure could happen for several reasons, for instance if the rearing of a parasitoid fails with inappropriate lab conditions, because of species mis-identification, or because the interaction is very rare (see~\citet{Wirta2014} for examples of some of these difficulties and partial solutions to them).
-Some sources of detection error could be minimised with appropriate sampling effort ($\delta$ will converge to one with increasing number of samples), but other sources are often difficult to reduce (e.g.
-the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification as in~\citet{Wirta2014,Frost2016}).
+Some sources of detection error can be minimised with appropriate sampling effort ($\delta$ will converge to one with increasing number of samples), but other sources are often difficult to reduce (e.g.
+the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification as in~\citealt{Wirta2014,Frost2016}).
 
@@
 
-    The considerations above raise a major challenge: when faced with empirical data, how may we infer whether unobserved interactions went undetected due to sampling, or whether they truly do not occur.
-How then may we refine our sampling approaches to reduce uncertainties, and to gain insights into the impact of multiple processes on field observations?
+    The considerations above raise a major challenge: when faced with empirical data, how may we infer whether unobserved interactions went undetected due to sampling or whether they truly do not occur?
+How then may we refine our sampling approaches to reduce uncertainties, and do we gain insights into the impact of multiple processes on field observations?
 Importantly, some sources of uncertainty can be minimised with appropriate sampling design and efforts while other sources are difficult or impossible to reduce since they are generated by chance variation created by the very process in which we are interested.
@@
           In such as case, the prior distribution would follow the function $P(\lambda|\mathbf{T})=f(\mathbf{T})$ based on a set of traits for both species $\mathbf{T}$.
-There are several techniques available to perform this inference of interaction probability, some of which are Bayesian, and we refer to ~\citep{Bartomeus2016} and \citep{Weinstein2017} for recent reviews about this topic.
+There are several techniques available to perform this inference of interaction probability, some of which are Bayesian, and we refer to ~\citep{Bartomeus2016} and~\citep{Weinstein2017} for recent reviews about this topic.
 Note that in this case the prior might not be beta distributed and numerical methods might be required to compute the posterior distribution.

### 2018-01-18 manuscript/CI_interactions.tex
my read-through edits. Need to make Box 2

@@
 This means that even if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact.
-What it implies is that 'no interaction' is the most likely ø¨†come when the species do co-occur, but there is nonetheless a substantial chance that the two species \emph{could} interact.
-In contrast, in the situation where $k>0$, i.e., when we are sure that an interaction is feasible, we still cannot be sure that absence of interactions is caused by $L=0$.
-Second, and most importantly, the number of trials $n$ might be very low in many instances (and some pairs of species may never have been documented as co-occuring).
-Consequently, the uncertainty in the estimation of $\lambda$ might be considerable.
+Rather, $k = 0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless a substantial chance that the two species \emph{could} interact.
+In the situation where $k>0$, in contrast, we are sure that the interaction is feasible ($L = 1$) but still cannot be sure of the cause if the interaction is not observed at some sites/times (i.e., we cannot say why $k<n$).
+There may be local constraints ($X=0$) or we might simply not observe the interaction in every sample ($D<1$).
+
+  Second, where the number of samples $n$ is very low (some pairs of species may never have been documenting as co-occurring), there will be considerable uncertainty around our estimate of $\lambda$.
 In Fig.~\ref{upper_limits} and Box~\ref{box2}, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda$ varies with sample size.
@@
 To establish that species are not interacting with any acceptable certainty requires tens of observations of the two species co-occurring but not interacting.
-As most data sets will lack such extensive sampling across all observations, we can use a Bayesian approach to supplement what data we do have with other sources of information.
+As most data sets will lack such extensive sampling across all species pairs, we can use a Bayesian approach to supplement what data we do have with other sources of information.
 
@@
 
-          In absence of any external information, an uninformative prior is the most conservative hypothesis for the distribution of $\lambda$.
+          In the absence of any external information, an uninformative prior is the most conservative hypothesis for the distribution of $\lambda$.
 The beta distribution is in this case a uniform distribution, specified with hyper parameters $\alpha=1$ and $\beta=1$.
@@
 
-          In the literature of ecological networks there is a solid collection of networks for which connectance has been calculated and for which we can thus define the connectance distribution.
+          The ecological network literature boasts a solid collection of networks for which connectance has been calculated and for which we can thus define the connectance distribution.
 Connectance is measured as $C = L/S^2$, where $L$ is the number of interactions and $S$ is the number of species.
@@
 
-      \subsubsection*{Trait-matching function}.
+      \subsubsection*{Trait-matching function}
 
@@
           In such as case, the prior distribution would follow the function $P(\lambda|\mathbf{T})=f(\mathbf{T})$ based on a set of traits for both species $\mathbf{T}$.
-There are several techniques available to perform this inference of interaction probability, some of which are Bayesian, and we refer to ~\citep{Bartomeus2016} and~\citep{Weinstein2017} for recent reviews about this topic.
-Note that in this case the prior might not be beta distributed and numerical methods might be required to compute the posterior distribution.
+There are several techniques available to perform this inference of interaction probability, some of which are Bayesian, and we refer to~\citet{Bartomeus2016} and~\citet{Weinstein2017} for recent reviews about this topic.
+Note that in this case the prior might not be beta-distributed and numerical methods might be required to compute the posterior distribution.
 
@@
 Suppose we have $n = 10$ observations of co-occurrence between species $i$ and species $j$ in a given time interval and area, and $k = 3$ observations of interactions.
-Then, the maximum likelihood estimate of the interaction probability (Box 1) is simply $\lambda_{MLE} = 3/10 = 0.3$.
+The maximum likelihood estimate of the interaction probability (Box~\ref{Box2}) is simply $\lambda_{MLE} = 3/10 = 0.3$.
 
@@
 
-    then species $i$ has a normalised degree of 0.55 (it interacts with species $j$ and 10 other species) and
-    we can use this to obtain the following set of interaction probabilities for species $i$ and each of its interaction partners:
+    Species $i$ has a normalised degree of 0.55 (it interacts with species $j$ and 10 other species).
+We can combine the normalised degree of $i$ with the normalised degrees of its interaction partners to obtain the following set of interaction probabilities for species $i$ and each of its interaction partners:
 
@@
 Adding the observed data ($n=10$, $k=3$) and using the same code, we obtain posterior parameters $\alpha'$=4.00 and $\beta'$=11.6 and a posterior $\bar\lambda$=0.256 and var($\lambda$)=0.012.
-Comparing the posterior distribution to the prior, we see that the posterior is closer to the observed data and that the additional data has reduced the variance.
+Comparing the posterior distribution to the prior, we see that the posterior is closer to the observed data and that the additional data about interactions between species $i$ and $j$ has reduced the variance.
 We may also wish to calculate a credible interval (analogous to the frequentist confidence interval).
@@
 The question is then ``what is the probability that these two species do not interact''?
-Since it is not possible to prove that the two species could never interact (strictly speaking, in this approach $\lambda=0$ is impossible), we must fix a threshold below which we consider that there is no interaction ($\lambda \sim 0$).
+Since it is not possible to prove that the two species could never interact (strictly speaking, in a Bayesian approach $\lambda=0$ is impossible), we must fix a threshold below which we consider that there is no interaction ($\lambda \sim 0$).
 We call this threshold probability $\lambda*$.
@@
 We note that this study used several genotypes of \emph{Salix hookeriana} rather than different \emph{Salix} species, but stress that this difference is unlikely to be critical for our purposes.
-Our interest in specifically in what information can be gained from the extensive sampling of \emph{Salix}, gallers, and natural enemies across Europe and what even such thorough sampling does not reveal; the similar but much smaller system in the United States is merely a starting point from which to obtain somewhat reasonable priors.
-To do this, we estimated frequencies of  \emph{S.
+Our interest is specifically in what information can be gained from the extensive sampling of \emph{Salix}, gallers, and natural enemies across Europe; the similar but much smaller system in the United States is merely a starting point from which to obtain somewhat reasonable priors.
+To obtain these priors, we estimated frequencies of  \emph{S.
 hookeriana} genotype-galler interactions based on the normalised degree of each species in each network component (see \emph{Appendix S1} for details and code).
@@
 
-      For species where no co-occurrences were observed, we can calculate the estimates for the mean and variance of $\lambda_{ij}$ directly from the prior parameters following equations~\ref{mean} and~\ref{variance} (see \emph{Appendix S2} for R implementation).
+      For species where no co-occurrences were observed ($n=0$), we can calculate the estimates for the mean and variance of $\lambda_{ij}$ directly from the prior parameters following equations~\ref{mean} and~\ref{variance} (see \emph{Appendix S2} for R implementation).
 For the \emph{Salix}-galler network, the prior distribution we obtained was: $\bar\lambda$=0.570, var($\lambda$)=0.056.
@@
 
-      For a pair of species where some co-occurrences were observed, we can update the prior distribution with these data.
-If we consider only pairs of species which were observed to co-occur but not to interact, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs; thus $\alpha'$=$\alpha$ and $\beta'$=$\beta + n$.
+      For a pair of species with some observed co-occurrences ($n>0$), we can update the prior distribution with these data.
+If we consider only pairs of species which were observed to co-occur but not to interact, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs, giving $\alpha'$=$\alpha$ and $\beta'$=$\beta + n$.
 As the most extreme case, for a pair of species which co-occurred at all 374 sites and was never observed to interact, our distributions would become
@@
       $\bar\lambda_{ij}$=3.49 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=9.03 $\times$ 10$^{-6}$ for the galler-natural enemy network.
-Thus, for species $i$ and $j$ co-occurring at all 374 sites and never being observed to interact, the maximum likelihood expectation for the probability of an interaction $ij$ is very close to 0 and the variance about this estimate is very narrow.
-In other words, we could establish with high certainty that the species will never interact.
-However, for most pairs of species $i$ and $j$, the species did not co-occur at many sites and our posterior mean and variance retain some of the influence of the prior.
-Nevertheless, as the number of observed co-occurrence increases, the posterior mean becomes closer to zero and the posterior variance decreases (Fig.~\ref{Salix_pdfs}).
-The 95\% credible interval around the estimate of $\lambda$ also shrinks with increasing sample sizes, from (0.152,0.931) and (0.008, 0.364) for \emph{Salix}-galler and galler-natural enemy pairs that were never observed co-occurring to (0.001, 0.017) and (\textless0.001, 0.11) for hypothetical \emph{Salix}-galler and galler-natural enemy pairs that might be observed co-occurring at all 374 sites without any observed interaction.
+Both distributions are very close to 0 with small variance about our estimate of $\lambda$; species $i$ and $j$ are extremely unlikely to interact at sites or times not included in our sample.
+
+      For most pairs of species $i$ and $j$, however, $n$ was much less than 374 and our posterior mean and variance therefore retain more of the influence of the prior.
+We can see this in the increasing means and variances as we decrease $n$ (Fig.~\ref{Salix_pdfs}).
+The 95\% credible interval around the estimate of $\lambda$ also widens as $n$ decreases, from (0.001, 0.017) and (\textless0.001, 0.11) for hypothetical \emph{Salix}-galler and galler-natural enemy pairs that might be observed co-occurring at all 374 sites without any observed interaction to (0.152,0.931) and (0.008, 0.364) for \emph{Salix}-galler and galler-natural enemy pairs that were never observed co-occurring.
 
@@
 
-      Rather than calculating confidence intervals for a posterior distribution after collecting data, we may wish to know how many data points are necessary to obtain a given level of confidence that two co-occurring species do not interact.
+      Rather than calculating credible intervals for a posterior distribution after collecting data, we may wish to know how many data points are necessary to obtain a given level of confidence that two co-occurring species do not interact.
 The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact.
@@
 As the scale of the two datasets is quite different (genotypes of a single \emph{Salix} species in~\citet{Barbour2016}, various \emph{Salix} species in our dataset), we suspect the former is more likely.
-    [[This is a little boring. Tomas has ideas for people with potentially better priors - may require another co-author. Also maybe could use one site as a prior like "training data"?]]
+    [[This is a little boring. Tomas has ideas for people with potentially better priors - may require another co-author. Also maybe could use one site as a prior like ``training data"?]]
 
@@
 First, our analyses point to detection uncertainty as a major contributor to overall uncertainty of is establishing the absence of interaction.
-To counter these establish the true absence of interactions will then require comparatively large sample size – on the order of xxx.
-Second, xxxx.
-Third, xxxx.
-Through these efforts, we demonstrate both the utility of our approach and the importance of acknowledging the uncertainty inherent in network studies.
-All code used in the paper is made available in the companion supplementary material.
+To counter these establish the true absence of interactions will then require comparatively large sample size – on the order of 30-50 observations per species pair.
+Second, where such extensive sampling is not feasible, researchers should still acknowledge the varying levels of confidence surrounding the presence or absence of interactions between different pairs of species.
+Including the $n$ and $k$ values for each interaction will clearly indicate which unobserved interactions are most likely to be observed with further sampling and which estimates are more reliable.
+Third, the uncertainty around interactions (especially interactions that were not observed) should be incorporated in calculations of network properties like connectance or nestedness.
+Re-sampling networks based on a probabilistic understanding of networks is straightforward and gives distributions for network properties rather than point estimates.
+This not only acknowledges the fact that interactions vary over time and space and with different sampling effort and methodology but will also facilitate comparisons between networks.
+With confidence intervals around network metrics, we can not only say that one network is more connected than another but also whether the networks are more different than we would expect based on imperfect sampling of interactions.
+To facilitate these recommendations, we provide all code used in this paper in the supplementary material.
 
@@
 The data were collected over 29 years at 374 unique locations across Europe, with a total of 641 site visits.
-Each site visit can be considered as a network in its own right and an independent sample from which to build the meta-network.
+Each site visit can be considered as a network in its own right or as an independent sample from which to build the meta-network.
 The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes.
-The high spatiotemporal resolution of this network and the unusually high sampling effort implemented at the site level makes this dataset particularly well suited for illustrating the difficulties in completely sampling a network and testing Bayesian approaches to overcome these difficulties.
-    \indent We may begin by comparing the frequency of of co-occurence of taxa to reveal the challenge of having sufficient sampling to be confident that an interaction does not occur.
-Most pairs of species (3986/4992 \emph{Salix}-galler pairs and  9794/12096 galler-natural enemy pairs) are never found co-occurring, and for species that did occur the number of co-occurrences was generally low (mean=4.24, var=36.3 for \emph{Salix}-galler pairs; mean=3.87, var=28.8 for galler-natural enemy pairs; Fig.~\ref{histograms}A-B).
-For those species which interacted when co-occurring, the incidence of interaction was also low (mean=12.0, var=155 for \emph{Salix}-galler pairs; mean=4.04, var=29.3 for galler-natural enemy pairs; Fig.~\ref{histograms}C-D).
-Only 2.82\% of \emph{Salix}-galler pairs and 7.76\% of galler-natural enemy pairs were observed interacting at all.
-Thus, even in the most extensive data set that we could find, limited sampling is clearly a major source of uncertainty.
+The high spatiotemporal resolution of this network and the unusually high sampling effort implemented at the site level makes this dataset particularly well suited for illustrating the difficulties in completely sampling a network and testing Bayesian approaches to overcome these difficulties.\\
+    \indent We may begin by comparing the frequency of co-occurences for pairs of species in each part of the network to reveal the challenge of having sufficient sampling to be confident that an interaction does not occur.
+Most pairs of species (3986/4992 \emph{Salix}-galler pairs and  9794/12096 galler-natural enemy pairs) are never found co-occurring and, even for species that did occur, the total number of co-occurrences was generally low (mean=4.24, variance=36.3 for \emph{Salix}-galler pairs; mean=3.87, variance=28.8 for galler-natural enemy pairs; Fig.~\ref{histograms}A-B).
+The bulk of these co-occurring species pairs were never observed to interact: only 2.82\% of \emph{Salix}-galler pairs and 7.76\% of galler-natural enemy pairs were observed interacting at one or more sites.
+Of those pairs that did interact, the incidence of interaction was also low (mean=12.0, variance=155 for \emph{Salix}-galler pairs; mean=4.04, variance=29.3 for galler-natural enemy pairs; Fig.~\ref{histograms}C-D).
+Thus, even in the most extensive data set that we could find, there was very little empirical data for each species pair.
+This suggests that limited sampling is a major source of uncertainty.
 This dataset also illustrates the potential for increased sampling to not necessarily reveal more interactions as a pair of species that interacts in some cases may not be observed interacting in all cases (Fig.~\ref{histograms}E-F).
@@
   \label{box1}
+\end{floatbox}
+
+\begin{floatbox}{}
+
+  This yields a surprising result: it requires \textgreater24 observations of no interactions to be 95\% sure that the interaction probability is smaller than $\lambda*$=0.1 (recall Fig.~\ref{upper_limits}, Box~\ref{box2}).
+   In Fig.~\ref{upper_limits} and Box~\ref{box2}, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda$ varies with sample size.
+At a small sample size, the 95\% credibleinterval spans all values of $\lambda$.
+  \caption{Here we derive the Clopper-Pearson credible interval for the estimated probability of interaction $\lambda$ of a pair of species observed co-occurring $n$ times and interacting $k$ times.
+As we are most interested in the probability of interaction between species pairs that have never been observed co-occurring, we consider only the case where $k=0$ over a variety of $n$.}
+  \label{box2}
 \end{floatbox}
@@
 \textbf{E-F)} Here we show, for each species pair, the number of observed interactions plotted against the number of observed co-occurrences.
-Most \emph{Salix}-galler pairs either are never observed interacting or interact almost every time they co-occur, while galler-enemy pairs had more variable frequencies of interaction.
+\emph{Salix}-galler pairs either are never observed interacting or interact almost every time they co-occur, while galler-enemy pairs had more variable frequencies of interaction.
 In panels E and F the red, dashed line indicates a 1:1 relationship between interactions and co-occurrences.}
@@
     \caption{A simple example will illustrate the problem of imperfect detection of interactions (the full reasoning is provided below).
-Assume that we want to infer the probability of an interaction between two species, A and B.
-Now assume that in reality, interaction between A and B is completely impossible (i.e.
+Assume that we want to infer the probability of an interaction between two species, $i$ and $j$.
+Now assume that in reality, interaction between $i$ and $j$ is completely impossible (i.e.
 the true $\lambda=0$), but the observer does not know this and seeks to estimate this interaction probability ($\lambda$).
-The record of the number of observed interactions will follow a binomial distribution, with number of interactions $k$ and number of observations $n$, for which we can compute the confidence interval of the estimated probability $\lambda$.
-Given no added detection error in observing the incidence of the interaction, then a single observation of species co-occurrence will reveal very little regarding the probability of the interaction – the confidence limits for one observation essentially spans from 0 to 1.
-Only with thirty observations will it shrink to 0.1.
-Thus, adding more observations is certainly useful in controlling uncertainty due to stochasticity inherent in the process itself, but the number of observations nonetheless needs to be very high.
-Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true confidence interval for $\lambda$ when $k=0$ (A and B have not been observed interacting) for a variety of $n$ (observed co-occurences of A and B).
+The number of observed interactions will follow a binomial distribution, with number of interactions $k$ and number of observations $n$.
+Using this distribution, we can compute the credible interval of the estimated probability $\lambda$.
+Assuming no added detection error in observing the incidence of the interaction, a single observation of species co-occurrence will reveal very little regarding the probability of the interaction as the credible interval for a pair of species with one observation essentially spans from 0 to 1.
+Only with thirty observations will the uppoer limit of the credible interval be lowered to 0.1.
+Thus, adding more observations is certainly useful in controlling uncertainty, but the number of observations nonetheless needs to be very high.
+Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true credible interval for $\lambda$ when $k=0$ ($i$ and $j$ have not been observed interacting) for a variety of $n$ (observed co-occurences of $i$ and $j$).
 A threshold interaction probability of 0.1 is indicated by the dotted red line.
@@
 The distribution narrows and approaches zero as the sample size increases.
-Likewise, the maximum likelihood estimator for the mean probability of interaction (diamonds) approaches zero and the 95\% credible interval (lines) narrows as sample size increases.
+Likewise, the maximum likelihood estimator for the mean probability of interaction (diamonds at top of each panel) approaches zero and the 95\% credible interval (lines at top of each panel) narrows as sample size increases.
 \textbf{A)} The posterior distributions for the \emph{Salix}-galler component are always wider and farther from zero than those for \textbf{B)} the galler-natural enemy component.
@@
       \begin{figure}[ht]
-        \caption{The number of samples required to achieve a given level of confidence that an interaction probability is below a given threshold varies with both parameters.
-With a low threshold, our confidence that $\omega_{ij}$ is below the threshold increases rapidly with repeated observation of co-occurrence without interaction.
-Here we show the cumulative density functions for thresholds probabilities of 0.5 (solid line), 0.25 (dashed line), 0.1 (dash-dot line), and 0.05 (dotted line) as well as the points at which the cdf reaches 0.90 (orange square), 0.95 (red circle), and 0.975 (blue diamond) for each threshold value.
+        \caption{The number of samples required to achieve a given level of confidence that an interaction probability $\lambda_{ij}$ is below a given threshold varies with both parameters.
+With a low threshold, our confidence that $\lambda_{ij}$ is below the threshold increases rapidly with repeated observation of co-occurrence without interaction.
+Here we show the cumulative density functions for threshold probabilities of 0.5 (solid line), 0.25 (dashed line), 0.1 (dash-dot line), and 0.05 (dotted line) as well as the points at which the cdf reaches 0.90 (orange square), 0.95 (red circle), and 0.975 (blue diamond) for each threshold value.
 The large ticks along the x-axis indicate the number of samples associated with each of these points.
-Note that the number of samples required to reach any given threshold is smaller for \textbf{A)} the \emph{Salix}-galler network than for \textbf{B)} the galler-natural enemy network.}
+Note that the number of samples required to reach any given threshold is larger for \textbf{A)} the \emph{Salix}-galler network than for \textbf{B)} the galler-natural enemy network.
+In the galler-natural enemy network, the credible interval for a pair of species with no observed co-occurrances was 0.364.
+All pairs of species therefore have $\lambda$\textless0.5.}
         \label{Salix_cdfs}
@@
     \begin{figure}[ht]
-    \caption{Here we show the mean connectance, links per resource (\emph{Salix} in the \emph{Salix}-galler networks and gallers in the galler-natural enemy networks), and links per consumer (gallers in the \emph{Salix}-galler networks and natural enemies in the galler-natural enemy networks) for networks assembled using posterior distributions based on~\citet{Barbour2016,Barbour2016Dryad}.
+    \caption{Here we show the mean connectance, links per resource (\emph{Salix} in the \emph{Salix}-galler networks and gallers in the galler-natural enemy networks), and links per consumer for networks assembled using posterior distributions based on a smaller, North American \emph{Salix}-galler-natural enemy system~\citep{Barbour2016,Barbour2016Dryad}.
 We created 100 ``posterior-sampling" networks and then, for each of these, created 100 ``detection-filter" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network.
@@
 Each point represents the mean network property (e.g., connectance) obtained from a set of 100 detection-filter networks, plotted against the value of the network property in the posterior-sampling network used to create the detection-filter networks.
-For each property and both network types, the posterior-sampling networks cover a relatively small range of network properties and the value of each property decreases with the proportion of links included in the detection-filter networks.}
+For each property and both network types, the posterior-sampling networks cover a relatively small range of network properties than the range covered by networks with varying detection probabilities.
+The value of each property decreases with the proportion of links included in the detection-filter networks.}
     \label{posterior_webs}    

### 2018-01-19 code/figure_generation/samples_for_thresholds.py
improved a fig

@@ -204,7 +204,13 @@ def add_samplelines(graph,sampledict,nettype):
     for threshold in sampledict[confidence]:
       liner=graph.add_dataset([(sampledict[confidence][threshold],0.1),(sampledict[confidence][threshold],0)])
       liner.symbol.shape=0
-      liner.line.configure(linewidth=.75,linestyle=1,color=1)
+      if confidence==0.9:
+        col=5
+      elif confidence==0.95:
+        col=2
+      else:
+        col=11
+      liner.line.configure(linewidth=2.75,linestyle=1,color=col)
 
   for threshold in sampledict[0.9]:
     dots90.append((sampledict[0.9][threshold],0.9)) 

### 2018-01-19 manuscript/CI_interactions.tex
added some comments and made pretty

@@
 We can use the distribution of these interaction probabilities as our prior distribution and estimate the uncertainty surrounding our $\lambda_{MLE}$.
-With some simple R code (function ``calculate\_parameters", \emph{Appendix S2}), we obtain prior parameters $\alpha$=0.998 and $\beta$=4.63.
-Using these priors in equations~\ref{mean} and~\ref{variance} above (or in the R function ``calculate\_distribution" in \emph{Appendix S2}), we find a prior $\bar\lambda$=0.177 and var($\lambda$)=0.026.
+With some simple R code (function ``calculate\_parameters", \emph{Appendix S1}), we obtain prior parameters $\alpha$=0.998 and $\beta$=4.63.
+Using these priors in equations~\ref{mean} and~\ref{variance} above (or in the R function ``calculate\_distribution" in \emph{Appendix S1}), we find a prior $\bar\lambda$=0.177 and var($\lambda$)=0.026.
 Adding the observed data ($n=10$, $k=3$) and using the same code, we obtain posterior parameters $\alpha'$=4.00 and $\beta'$=11.6 and a posterior $\bar\lambda$=0.256 and var($\lambda$)=0.012.
@@
 We may also wish to calculate a credible interval (analogous to the frequentist confidence interval).
-This is also quite straightforward in R (see function ``credible\_interval" in \emph{Appendix S2}).
+This is also quite straightforward in R (see function ``credible\_interval" in \emph{Appendix S1}).
 In this case, a 95\% credible interval for $\bar\lambda$ is (0.080, 0.491).
@@
 We then use the cumulative distribution function to estimate $P(\lambda<\lambda*|L=0,n)$ for different $n$.
-The function ``plot\_precision" in \emph{Appendix S2} calculates distribution function for $\lambda*$ with an increasing number of trials.
+The function ``samples\_for\_threshold" in \emph{Appendix S1} calculates distribution function for $\lambda*$ with an increasing number of trials.
 This yields a surprising result: it requires \textgreater24 observations of no interactions to be 95\% sure that the interaction probability is smaller than $\lambda*$=0.1 (recall Fig.~\ref{upper_limits}, Box~\ref{box2}).
@@
 Instead we must rely on computer simulations.
-In the following section, we will provide an empirical example based on the well-sampled system of \emph{Salix}  plants, herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}; see Box~\ref{box1} for a description).
+In the following section, we will provide an empirical example based on the well-sampled system of \emph{Salix}  plants, herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}; see Box~\ref{box1} or \emph{Appendix S2} for a description).
 This tripartite network can be examined as two bipartite networks, namely \emph{Salix}-galler and galler-natural enemy networks.
@@
 To obtain these priors, we estimated frequencies of  \emph{S.
-hookeriana} genotype-galler interactions based on the normalised degree of each species in each network component (see \emph{Appendix S1} for details and code).
+hookeriana} genotype-galler interactions based on the normalised degree of each species in each network component (see \emph{Appendix S3} for details and code).
 Specifically, we obtain prior parameters $\alpha$=2.51 and $\beta$=1.89.
@@
 
-      For species where no co-occurrences were observed ($n=0$), we can calculate the estimates for the mean and variance of $\lambda_{ij}$ directly from the prior parameters following equations~\ref{mean} and~\ref{variance} (see \emph{Appendix S2} for R implementation).
+      For species where no co-occurrences were observed ($n=0$), we can calculate the estimates for the mean and variance of $\lambda_{ij}$ directly from the prior parameters following equations~\ref{mean} and~\ref{variance} (see \emph{Appendix S1} for R implementation).
 For the \emph{Salix}-galler network, the prior distribution we obtained was: $\bar\lambda$=0.570, var($\lambda$)=0.056.
@@
 The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact.
-If we want to be 95\% confident that the interaction probability for two species in the \emph{Salix}-galler network is below 0.1, 0.05, or 0.01, we would need 51, 106, and 550 observed co-occurrences with no observed interaction (Fig.~\ref{Salix_cdfs}; see function plot\_precision in~\emph{Appendix S2}).
+If we want to be 95\% confident that the interaction probability for two species in the \emph{Salix}-galler network is below 0.1, 0.05, or 0.01, we would need 51, 106, and 550 observed co-occurrences with no observed interaction (Fig.~\ref{Salix_cdfs}; see function samples\_for\_threshold in~\emph{Appendix S1}).
 Although the prior distribution of interaction probabilities is narrower and closer to zero for the galler-natural enemy network, the number of samples required to be 95\% confident that the interaction probability is below a threshold still increases quickly; we would need 25, 62, and 352 observed co-occurrence with no observed interaction for threshold interaction probabilities of 0.1, 0.05, and 0.01, respectively.
@@
     \indent As a case study, we use an extensively sampled \emph{Salix}-galler-natural enemy meta-network.
-This dataset consists of a single community type sampled across Europe; willow (\emph{Salix}) species, willow-galling sawflies, and their natural enemies.
+This dataset consists of a single community type sampled across Europe: willow (\emph{Salix}) species, willow-galling sawflies, and their natural enemies.
 The data were collected over 29 years at 374 unique locations across Europe, with a total of 641 site visits.
@@
 
-  This yields a surprising result: it requires \textgreater24 observations of no interactions to be 95\% sure that the interaction probability is smaller than $\lambda*$=0.1 (recall Fig.~\ref{upper_limits}, Box~\ref{box2}).
-   In Fig.~\ref{upper_limits} and Box~\ref{box2}, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda$ varies with sample size.
-At a small sample size, the 95\% credibleinterval spans all values of $\lambda$.
-  \caption{Here we derive the Clopper-Pearson credible interval for the estimated probability of interaction $\lambda$ of a pair of species observed co-occurring $n$ times and interacting $k$ times.
-As we are most interested in the probability of interaction between species pairs that have never been observed co-occurring, we consider only the case where $k=0$ over a variety of $n$.}
+  Here we describe the derivation of the Clopper-Pearson credible interval for the estimated probability of interaction $\lambda$ of a pair of species observed co-occurring $n$ times and interacting $k$ times.
+As we are most interested in the probability of interaction between species pairs that have never been observed co-occurring, we consider only the case where $k=0$ over a variety of $n$.
+This is straightforward to do in R (see the function ``credible\_interval" in \emph{Appendix S1}).
+
+  First, we must obtain the $\alpha$ and $\beta$ parameters for the prior distribution.
+In this study we obtained these parameters using the R~\citep{R} function fitdispr from the package MASS~\citep{MASS}.
+Once $\alpha$ and $\beta$ are known, we can update them using our observed data.
+Specifically, we are interested in $\alpha'=\alpha+k$ and $\beta'=\beta+n-k$.
+These parameters can then be used to calculate a credible interval using the R~\citep{R} function qbeta.
+In the table below, we present the 95\% credible intervals for \emph{Salix}-galler and galler-natural enemy paris with different numbers of observed co-occurrences ($n$) and no observed interactions ($k=0$).
+Both sets of intervals rely on prior information from the network in~\citet{Barbour2016,Barbour2016Dryad}.
+
+      % # R code to make the table:
+      % output=matrix(nrow=length(ns),ncol=5)
+      % ns=c(0,1,2,5,10,15,20,25,50,100,150,200,374)
+      % output[,1]=ns
+      % for(r in 1:nrow(output)){
+      %   interval1=credible_interval(calculate_parameters(sg_int_probs,ns[r],0),0.025,0.975)    
+      %   interval2=credible_interval(calculate_parameters(gp_int_probs,ns[r],0),0.025,0.975)    
+      %   output[r,2:3]=interval1
+      %   output[r,4:5]=interval2
+      % }
+
+        \begin{tabular}{l  c c  c c }
+        \multirow{2}{*}{$n$} & \multicolumn{2}{c}{\emph{Salix}-galler} & \multicolumn{2}{c}{galler-natural enemy}\\
+         & Lower bound & Upper bound \\
+        \hline
+        0   & 0.152 & 0.931 & 0.008 & 0.364 \\
+        1   & 0.110 & 0.843 & 0.007 & 0.337 \\
+        2   & 0.087 & 0.760 & 0.006 & 0.313 \\
+        5   & 0.053 & 0.573 & 0.005 & 0.258 \\
+        10  & 0.033 & 0.400 & 0.004 & 0.200 \\
+        15  & 0.023 & 0.306 & 0.003 & 0.163 \\
+        20  & 0.018 & 0.247 & 0.003 & 0.137 \\
+        25  & 0.015 & 0.208 & 0.002 & 0.119 \\
+        50  & 0.008 & 0.115 & 0.001 & 0.071 \\
+        100 & 0.004 & 0.061 & 0.001 & 0.039 \\
+        150 & 0.003 & 0.041 & \textless0.001 & 0.027 \\
+        200 & 0.002 & 0.031 & \textless0.001 & 0.021 \\
+        \hline
+        374 & 0.001 & 0.017 & \textless0.001 & 0.011 \\
+        \hline
+        \end{tabular}
+
+  \caption{Calculating the credible interval around a probability estimate}
   \label{box2}

### 2018-01-19 manuscript/supplemental.tex
added some comments and made pretty

--- 2017-10-27 manuscript/supplemental.tex
@@
 
-\section*{Appendix S1: Obtaining prior interaction probabilities}
+\section*{Appendix S1: Calculating posterior distributions and confidence intervals}
+
+  The following simple functions are implemented in the R language. They are 
+  also provided as R code in a separate file.
+  Priordata is the list of interaction frequencies from the prior 
+  data, n is the number of sites with observed co-occurrance of 
+  species $i$ and $j$, and k is the number of sites with an 
+  observed interaction $ij$. When calculating the prior 
+  distribution, both n and k are 0. In the main text we assume 100\%
+  confidence in observed interactions and therefore consider only 
+  cases where k=0. Only n varies between species pairs.
+
+  To calculate the parameters $\alpha$ and $\beta$ of a prior or 
+  posterior distribution:
+
+  \vspace{12pt}
+  \begin{em}
+  \noindent \hspace{2pt}calculate\_parameters\textless-function(priordata,n,k)\{\\
+  \vspace{4pt}
+    \# Calculate prior parameters\\
+    start=list(shape1=1,shape2=1)\\
+    pars=fitdistr(x=priordata,`beta',start=start,lower=c(0,0))\$estimate\\
+    alpha=pars[[1]]\\
+    beta=pars[[2]]\\
+  \vspace{4pt}
+    \# Update the parameters with data. If n=0 and k=0, no change.\\
+    alpha\_prime=alpha+k\\
+    beta\_prime=beta+n-k\\
+    pars2=c(alpha\_prime,beta\_prime)\\
+    return(pars2) \}
+  \end{em}
+  \vspace{12pt}
+
+    All of the following functions use the parameters returned by 
+    ``calculate\_parameters". To calculate the maximum likelihood estimates of 
+    the mean and variance of the probability of interaction $\lambda_{ij}$:
+
+    \vspace{12pt}
+    \begin{em}
+    \noindent \hspace{2pt}calculate\_distribution\textless-function(pars)\{\\
+     \vspace{4pt}
+     \# alpha and beta may be from a prior or posterior distribution\\
+      alpha=pars[[1]]\\
+      beta=pars[[2]]\\
+      \vspace{4pt}
+      \# Calculate the MLE of the mean\\
+      mu\_numerator=alpha\\
+      mu\_denominator=alpha+beta\\
+      mu=mu\_numerator/mu\_denomenator\\
+      \vspace{4pt}
+      \# Calculate the MLE of the variance\\
+      sig\_numerator=alpha\*beta\\
+      den1=alpha+beta\\
+      den2=den1$**$2\\
+      sig\_denomenator=den1$*$den2\\
+      sigma2=sig\_numerator/sig\_denomenator\\
+      return(c(mu,sigma2))\}
+    \end{em}
+  \vspace{12pt}
+
+  \clearpage
+
+  To calculate a credible interval based on the prior or posterior distribution, for given lower and upper bounds:
+
+  \vspace{12pt}
+  \begin{em}
+  \noindent \hspace{2pt}credible\_interval\textless-function(pars,p\_lower,p\_upper)\{\\
+    \vspace{4pt}
+    alpha=pars[[1]]\\
+    beta=pars[[2]]\\
+    lowCI=qbeta(p=p\_lower,shape1=alpha,shape2=beta)\\
+    highCI=qbeta(p=p\_upper,shape1=alpha,shape2=beta)\\
+    return(c(lowCI,highCI))\}
+  \end{em}
+  \vspace{12pt}
+
+  To calculate the number of samples required to reach a given level of confidence that the probability of interaction between two species ($\lambda_{ij}$) that have not been observed co-occurring is below a threshold value:
+
+  \vspace{12pt}
+  \begin{em}
+  \noindent \hspace{2pt}samples\_for\_threshold\textless-function(threshold,confidence,pars)\{\\
+    \vspace{4pt}
+    alpha=pars[[1]]\\
+    beta=pars[[2]]\\
+    n=seq(0,100,1)\\
+    k=0\\ 
+    cdf=pbeta(threshold,shape1=alpha,shape2=beta+n)\\
+    samples=length(which(cdf\textless confidence))\\
+    return(samples) \}
+  \end{em}
+
+\clearpage
+
+\section*{Appendix S2: Details of \emph{Salix} data collection}
+
+      The \emph{Salix}-galler-parasitoid meta-network dataset collected 
+      by~\citet{Kopelke2017} consists of a single community type sampled across 
+      Europe: willow (\emph{Salix}) species, willow-galling sawflies (
+      Hymenoptera, Tenthredinidae, Nematinae, Euurina), and their natural 
+      enemies (hymenopteran parasitoids and coleopteran, lepidopteran, dipteran, 
+      and hymenopteran inquilines). The data were collected over 29 years 
+      (1982-2010) at 374 unique locations across Europe ranging from Sicily to 
+      the Arctic. Including repeated visits to a number of sites, the data set 
+      contains 641 site-visits, each of which can be considered as a network in 
+      its own right and an independent sample from which to build the 
+      meta-network. The meta-network consists of 1,173 different interactions 
+      between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 parasitoid 
+      nodes. Interactions were determined by dissecting and rearing gall 
+      inhabitants from 165,424 galls. Some sites were visited repeatedly, for a 
+      total of 641 site-visits. We consider these to be repeated samples and 
+      take the 374 unique sites as our sample size. The high spatiotemporal 
+      resolution of this network and the unusually high sampling effort together 
+      make this dataset particularly well suited for testing Bayesian approaches 
+      to network structure.
+
+\clearpage
+
+\section*{Appendix S3: Obtaining prior interaction probabilities}
 
@@
 
-      Barbour \emph{et al.} sampled 145 branches from 
+      \citet{Barbour2016,Barbour2016Dryad} sampled 145 branches from 
       \emph{Salix hookeriana} of 26 genotypes. They recorded galls 
@@
       \vspace{12pt}
-      \emph{
-      \noindent \hspace{-4pt} prior\_web\_data=read.csv(``tree\_level\_interaxn\_all\_plants\_traits\_size.csv")\\
-      \# Remove extra data on parasitoids, etc.\\
-      prior\_web\_data[,31:57]\textless-NULL\\
-      prior\_web\_data[,4:26]\textless-NULL\\
-      prior\_web\_data[,2]\textless-NULL\\
-      \# Build a web with interactions=1 for any galler observed on any genotype\\
-      prior\_web=matrix(nrow=26,ncol=4)\\
-      for(r in 1:length(levels(prior\_web\_data\$Genotype)))\{\\
-      \hspace{4pt}  gen=levels(prior\_web\_data\$Genotype)[r]\\
-      \hspace{4pt}  subset=prior\_web\_data[which(prior\_web\_data\$Genotype==gen),]\\
-      \hspace{4pt}  for(c in 1:4)\{\\
-      \hspace{8pt}    if(sum(subset[,2+c])\textgreater0)\{\\
-      \hspace{12pt}      prior\_web[r,c]=1\\
-      \hspace{8pt}    \} else \{\\
-      \hspace{12pt}      prior\_web[r,c]=0\\
-      \hspace{8pt}    \}\}\}
-      \# Remove non-interactive genotype
-      prior\_web<-prior\_web[which(rowSums(prior\_web)\textgreater0),]
-      }
+      \begin{em}
+      \noindent \hspace{2pt}prior\_web\_data=read.csv(``tree\_level\_interaxn\_all\_plants\_traits\_size.csv")\\
+      \vspace{4pt}
+      \noindent \hspace{2pt}\# Remove extra data on parasitoids, etc.\\
+      \noindent \hspace{2pt}prior\_web\_data[,31:57]\textless-NULL\\
+      \noindent \hspace{2pt}prior\_web\_data[,4:26]\textless-NULL\\
+      \noindent \hspace{2pt}prior\_web\_data[,2]\textless-NULL\\
+      \vspace{4pt}
+      \noindent \hspace{2pt}\# Build a web with interactions=1 for any galler observed on any genotype\\
+      \noindent \hspace{2pt}prior\_web=matrix(nrow=26,ncol=4)\\
+      \noindent \hspace{2pt}for(r in 1:length(levels(prior\_web\_data\$Genotype)))\{\\
+      \hspace{4pt}gen=levels(prior\_web\_data\$Genotype)[r]\\
+      \hspace{4pt}subset=prior\_web\_data[which(prior\_web\_data\$Genotype==gen),]\\
+      \hspace{4pt}for(c in 1:4)\{\\
+      \hspace{8pt}if(sum(subset[,2+c])\textgreater0)\{\\
+      \hspace{12pt}prior\_web[r,c]=1\\
+      \hspace{8pt}\} else \{\\
+      \hspace{12pt}prior\_web[r,c]=0\\
+      \hspace{8pt}\}\}\}\\
+      \vspace{4pt}
+      \noindent \hspace{2pt}\# Remove non-interactive genotype to obtain the final web\\
+      \noindent \hspace{2pt}prior\_web\textless-prior\_web[which(rowSums(prior\_web)\textgreater0),]
+      \end{em}
 
@@
 
+      \vspace{12pt}
+      \clearpage
+
       To extract the galler-parsitoid network from the same study above:
@@
       \vspace{12pt}
-      \emph{
-      \noindent \hspace{-4pt} 
-      prior\_web\_data=read.csv('tree\_level\_interaxn\_all\_plants\_traits\_size.csv')\\
-      prior\_web\_data <- prior\_web\_data[,8:26]
-
-      \# Build a web with interactions=1 for any parasitoid on any galler
-      prior\_web=data.frame()
-
-      \# each column contains all interactions for a particular parasitoid-galler combination
-      for(column in 1:ncol(prior\_web\_data)){
-      \hspace{-4pt}   \# the column name gives the species which makes the gall, followed by the species emerging from the gall
-      \hspace{-4pt}   galler\_emerged=strsplit(colnames(prior\_web\_data)[column], "\_")
-      \hspace{-4pt}   galler = galler\_emerged[[1]][1]
-      \hspace{-4pt}   emerged = galler\_emerged[[1]][2]
-
-      \hspace{-4pt}   \# the strength of the interaction is the sum of the column (number of galls across all branches sampled)
-      \hspace{-4pt}   linkstrength = sum(prior\_web_data[,column])
-      \hspace{-4pt}   prior\_web[as.character(galler),as.character(emerged)] <- linkstrength
-      }
-
-      \# Make the naS into 0
-      prior\_web[is.na(prior\_web)] <- 0
-
-      \# remove emerging gallers with no parasitoids
-      prior\_web\_para\_only <- prior\_web[,c(2:6,8:9,12)]
-
-      \# convert interaction strengths to 1
-      prior\_web[which(prior\_web>0)] <- 1
-
-      write.csv(prior\_web\_para\_only, file="prior\_web\_para\_only.csv", quote=F)
-      }
+      \begin{em}
+      \noindent \hspace{2pt}prior\_web\_data=read.csv(``tree\_level\_interaxn\_all\_plants\_traits\_size.csv")\\
+      \noindent \hspace{2pt}prior\_web\_data \textless- prior\_web\_data[,8:26]\\
+      \vspace{4pt}
+      \noindent \hspace{2pt}\# Build a web with interactions=1 for any parasitoid on any galler\\
+      \noindent \hspace{2pt}prior\_web=data.frame()\\
+      \vspace{4pt}
+      \noindent \hspace{2pt}\# each column contains all interactions for a \noindent \hspace{2pt}particular parasitoid-galler combination\\
+      \noindent \hspace{2pt}for(column in 1:ncol(prior\_web\_data))\{\\
+      \hspace{4pt}\# the column name gives the species which makes the gall,\\
+      \hspace{4pt}\#followed by the species emerging from the gall\\
+      \hspace{4pt}galler\_emerged=strsplit(colnames(prior\_web\_data)[column], "\_")\\
+      \hspace{4pt}galler = galler\_emerged[[1]][1]\\
+      \hspace{4pt}emerged = galler\_emerged[[1]][2]\\
+      \vspace{4pt}
+      \hspace{4pt}\# the strength of the interaction is the sum of the column\\
+      \hspace{4pt}(number of galls across all branches sampled)\\
+      \hspace{4pt}linkstrength = sum(prior\_web\_data[,column])\\
+      \hspace{4pt}prior\_web[as.character(galler),as.character(emerged)] \textless- linkstrength\\
+      \}\\
+      \vspace{4pt}
+      \noindent \hspace{2pt}\# Make the NAs into 0\\
+      \noindent \hspace{2pt}prior\_web[is.na(prior\_web)] \textless- 0\\
+      \vspace{4pt}
+      \noindent \hspace{2pt}\# remove emerging gallers with no parasitoids\\
+      \noindent \hspace{2pt}prior\_web\_para\_only \textless- prior\_web[,c(2:6,8:9,12)]\\
+      \vspace{4pt}
+      \noindent \hspace{2pt}\# convert interaction strengths to 1\\
+      \noindent \hspace{2pt}prior\_web[which(prior\_web\textgreater0)] \textless- 1\\
+      \noindent \hspace{2pt}write.csv(prior\_web\_para\_only, file=``prior\_web\_para\_only.csv", quote=F)\\
+      \end{em}
 
@@
 
+      \clearpage
+
     \subsection*{Degree distributions and interaction probabilities}
@@
       \vspace{12pt}
-      \emph{
-      \noindent \hspace{-4pt} \# Now get the degree distributions from the web\\
-      deg\_dist\_Salix=rowSums(prior\_web)/ncol(prior\_web)\\
-      \# Remove one genotype that never interacted\\
-      deg\_dist\_Salix\textless-deg\_dist\_Salix[which(rowSums(prior\_web)\textgreater0)]\\
-      deg\_dist\_galler=colSums(prior\_web)/nrow(prior\_web)\\
-      \# Interaction probabilities are the product of plant and galler probabilities\\
-      int\_probs=as.numeric(deg\_dist\_galler\%$*$\%t(deg\_dist\_Salix))\\
-
-      \# And for the galler-parasitoid web:\\
-      deg\_dist\_parasitoid=rowSums(prior\_web\_para\_only)/ncol(prior\_web\_para\_only)\\
-      deg\_dist\_parasitized=colSums(prior\_web\_para\_only)/nrow(prior\_web\_para\_only)\\
-      gp\_int\_probs=as.numeric(deg\_dist\_parasitized\%$*$\%t(deg\_dist\_parasitoid))
-
-      }
+      \begin{em}
+      \noindent \hspace{2pt}\# Now get the degree distributions from the web\\
+      \noindent \hspace{2pt}deg\_dist\_Salix=rowSums(prior\_web)/ncol(prior\_web)\\
+      \vspace{4pt}
+      \noindent \hspace{2pt}\# Remove one genotype that never interacted\\
+      \noindent \hspace{2pt}deg\_dist\_Salix\textless-deg\_dist\_Salix[which(rowSums(prior\_web)\textgreater0)]\\
+      \noindent \hspace{2pt}deg\_dist\_galler=colSums(prior\_web)/nrow(prior\_web)\\
+      \vspace{4pt}
+      \noindent \hspace{2pt}\# Interaction probabilities are the product of plant and galler probabilities\\
+      \noindent \hspace{2pt}int\_probs=as.numeric(deg\_dist\_galler\%$*$\%t(deg\_dist\_Salix))\\
+      \vspace{4pt}
+      \noindent \hspace{2pt}\# And for the galler-parasitoid web:\\
+      \noindent \hspace{2pt}deg\_dist\_parasitoid=rowSums(prior\_web\_para\_only)/ncol(prior\_web\_para\_only)\\
+      \noindent \hspace{2pt}deg\_dist\_parasitized=colSums(prior\_web\_para\_only)/nrow(prior\_web\_para\_only)\\
+      \noindent \hspace{2pt}gp\_int\_probs=as.numeric(deg\_dist\_parasitized\%$*$\%t(deg\_dist\_parasitoid))\\
+      \end{em}
 
@@
 
-\section*{Appendix S2: Calculating posterior distributions and confidence intervals}
-
-  The following simple functions are implemented in the R language. 
-  Priordata is the list of interaction frequencies from the prior 
-  data, n is the number of sites with observed co-occurrance of 
-  species $i$ and $j$, and k is the number of sites with an 
-  observed interaction $ij$. When calculating the prior 
-  distribution, both n and k are 0. In the main text we assume 100\%
-  confidence in observed interactions and therefore consider only 
-  cases where k=0. Only n varies between species pairs.
-
-  To calculate the parameters $\alpha$ and $\beta$ of a prior or 
-  posterior distribution:
-
-  \vspace{12pt}
-  \emph{
-  \noindent \hspace{-4pt}calculate\_parameters\textless-function(priordata,n,k)\{\\
-  \hspace{4pt} \# Calculate prior parameters\\
-  \hspace{4pt} start=list(shape1=1,shape2=1)
-  \hspace{80pt} pars=fitdistr(x=priordata,`beta',start=start,lower=c(0,0))\$estimate\\
-  \hspace{4pt} alpha=pars[[1]]\\
-  \hspace{4pt} beta=pars[[2]]\\
-  \hspace{4pt} \# Update the parameters with data. If n=0 and k=0, no change.\\
-  \hspace{4pt} alpha\_prime=alpha+k\\
-  \hspace{4pt} beta\_prime=beta+n-k\\
-  \hspace{4pt} pars2=c(alpha\_prime,beta\_prime)\\
-  \hspace{4pt} return(pars2) \}
-  }
-  \vspace{12pt}
-
-    To calculate the maximum likelihood estimates of the mean and 
-    variance of the probability of interaction $\lambda_{ij}$:
-
-    \vspace{12pt}
-    \emph{
-    calculate\_distribution\textless-function(pars)\{\\
-      \# alpha and beta may be from a prior or posterior distribution\\
-      alpha=pars[[1]]\\
-      beta=pars[[2]]\\
-
-      \# Calculate the MLE of the mean\\
-      mu\_num=alpha\\
-      mu\_den=alpha+beta\\
-      mu=mu\_num\/mu\_den\\
-
-      \# Calculate the MLE of the variance\\
-      sig\_num=alpha\*beta\\
-      den1=alpha+beta\\
-      den2=den1\*\*2\\
-      sig\_den=den1\*den2\\
-      sigma2=sig\_num\/sig\_den\\
-
-      return(c(mu,sigma2))\}
-    }
-  \vspace{12pt}
-
-  To calculate a credible interval based on the prior or posterior distribution, for given lower and upper bounds:
-
-  \vspace{12pt}
-  \emph{
-  credible\_interval\textless-function(pars,p\_lower,p\_upper)\{\\
-    alpha=pars[[1]]\\
-    beta=pars[[2]]\\
-    lowCI=qbeta(p=p\_lower,shape1=alpha,shape2=beta)\\
-    highCI=qbeta(p=p\_upper,shape1=alpha,shape2=beta)\\
-    return(c(lowCI,highCI))\}
-  }
-
-  \vspace{12pt}
-  \emph{
-  plot\_precision\textless-function(threshold,confidence,pars)\{\\
-    alpha=pars[[1]]\\
-    beta=pars[[2]]\\
-    n=seq(0,100,1)\\
-    k=0\\
-    cdf=pbeta(threshold,shape1=alpha,shape2=beta+n)\\
-    samples=length(which(cdf<confidence))\\
-    return(samples) \}
-  }
-
-\clearpage
-
     \bibliographystyle{ecollett} 
-    \bibliography{manual_abbrev} % Abbreviate journal titles.
+    \bibliography{MyCollection}
 

### 2018-01-19 manuscript/CI_interactions.tex
added a couple refs

@@
 
+\linenumbers
+\begin{spacing}{2.0}
 \section*{Introduction}
@@
 This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology about the contingencies of interactions.
-Phenological matching~\citep{MillerRushing2010,Gezon2016}, species preferences~\citep{Pires2011,Novak2015,Coux2016}, and fear effects of other species~\citep{Luttbeg2005,Wirsing2007} are just some of the factors contributing to variation in the frequency of interactions between a given pair of species.
+Phenological matching~\citep{MillerRushing2010,Gezon2016}, species preferences~\citep{Pires2011,Novak2015,Coux2016}, and fear effects of other species~\citep{Luttbeg2005,Wirsing2008} are just some of the factors contributing to variation in the frequency of interactions between a given pair of species.
     % We imagine for instance that an interaction between a gall and a parasitoid might not be recorded at a location because it was the wrong time of the year and the gall had not yet formed (phenological constraints), a late frost killed the larvae (an abiotic environmental constraint), another parasitoid species competitively excluded the parasitoid species of interest (a biotic environmental constraint) or simply the parasitoid is too rare to interact with all of its viable hosts (an abundance constraint).
@@
 It is important to remember that this variance describes the variability of the number of successes $k$ for $n$ trials and is not the variance associated with the estimation of $\lambda$.
-Given this variance, it is possible to compute the confidence interval for the MLE of $\lambda$ using any of several methods, including the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull Interval} (for details, see [\citealp{}]).
+Given this variance, it is possible to compute the confidence interval for the MLE of $\lambda$ using any of several methods, including the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]).
 Finding this estimate is therefore quite straightforward, but it nonetheless has two drawbacks.
@@
 
-  Real interaction networks vary~\citep{}, and to capture this variation we must turn from static descriptions of network structure to probabilistic descriptions.
+  Real interaction networks vary~\citep{Kitching1987,Olesen2011a,Pires2011a,Baiser2012,Fodrie2015,Novak2015}, and to capture this variation we must turn from static descriptions of network structure to probabilistic descriptions.
 In this study, we have developed the analytical tools to capture the uncertainty in the estimation of pairwise interactions, and to partition it into its individual components: interaction uncertainty, process uncertainty and detection uncertainty.
@@
 outlining how this is different than other approaches currently in use and how they fail at some important task), documenting the robustness and accuracy of the approach, performing case study, and making robust high-quality code freely available.]
+\end{spacing}
 

### 2018-01-29 manuscript/CI_interactions.tex
Fixed a few minor spelling mistakes

@@
 To define the problem, we first identify the different contributions to the uncertainty of an interaction and discuss the implications of each source of uncertainty for the properties of ecological networks.
-Next, we develop an analystical framework to quantify the uncertainty around interactions in an empirical web.
+Next, we develop an analytical framework to quantify the uncertainty around interactions in an empirical web.
 We illustrate this framework using the most extensively sampled network to date (Box 1).
@@
 
-  Second, where the number of samples $n$ is very low (some pairs of species may never have been documenting as co-occurring), there will be considerable uncertainty around our estimate of $\lambda$.
+  Second, where the number of samples $n$ is very low (some pairs of species may never have been documented as co-occurring), there will be considerable uncertainty around our estimate of $\lambda$.
 In Fig.~\ref{upper_limits} and Box~\ref{box2}, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda$ varies with sample size.
@@
           If our focal network describes a system similar to that in a known network, we can use the distribution of interaction probabilities in that network to inform our prior.
-The probability of any interaction $L_ij$ depends on the degrees of species $i$ and $j$.
-Using normalised degrees $\Delta_i$ and $\Delta_j$ (i.e., degrees divided by the number of species in the network), we can obtain the probability of interaction $L_ij$=$\Delta_i\times\Delta_j$.
+The probability of any interaction $L_{ij}$ depends on the degrees of species $i$ and $j$.
+Using normalised degrees $\Delta_i$ and $\Delta_j$ (i.e., degrees divided by the number of species in the network), we can obtain the probability of interaction $L_{ij}$=$\Delta_i\times\Delta_j$.
 Similar to the procedure for degree distribution, the distribution of these interaction probabilities derived from a similar network or a suite of networks can be used to establish a prior distribution before any data from the focal network are collected.
@@
 Assuming no added detection error in observing the incidence of the interaction, a single observation of species co-occurrence will reveal very little regarding the probability of the interaction as the credible interval for a pair of species with one observation essentially spans from 0 to 1.
-Only with thirty observations will the uppoer limit of the credible interval be lowered to 0.1.
+Only with thirty observations will the upper limit of the credible interval be lowered to 0.1.
 Thus, adding more observations is certainly useful in controlling uncertainty, but the number of observations nonetheless needs to be very high.

### 2018-01-30 manuscript/CI_interactions.tex
Minor edits

@@
 
-\author{Alyssa R. Cirtwill$^{1}$, Dominique Gravel, \&  Anna Ekl\"{o}f$^{1}$, Tomas Roslin$^{x,y}$, Kate Wootton$^{x}$}
+% DG : if ok with all of you, I would appreciate being last author
+
+\author{Alyssa R. Cirtwill$^{1}$, Dominique Gravel$^{2}$, \&  Anna Ekl\"{o}f$^{1}$, Tomas Roslin$^{x,y}$, Kate Wootton$^{x}$}
 \date{\small$^1$Department of Physics, Chemistry\\ 
@@
 Link\"{o}ping, Sweden\\
+
+\small$^2$ Département de biologie\\ 
+Université de Sherbrooke\\ 
+Sherbrooke, Canada\\
+
 \medskip $^x$ Department of Ecology\\ P.O. Box 7044, Swedish University of Agricultural Sciences \\ SE-750 07 Uppsala, Sweden \\
@@
   % Word count can be up to 7500, we're at about 5700 without the boxes. Should be grand.
+
+%DG: Eco Lett proposed the new format for methods papers, but I think they are nonetheless looking for conceptual contributions.
+We might have to tweak just a little bit the abstract to show that our proposition also help formalizing the idea that interactions should be described probabilistically.
+This is not only technical, it is fundamental as well.
 
@@
 As a simple example, a prey species may be too large to be consumed by a particular predator.
-In such cases, $\lambda$ would take a value of 0.
+In such cases, $\lambda$ would take a value of 0 and there would be no uncertainty.
     % [[The previous sentence doesn't follow, k hasn't been defined and we don't know that it's zero.
@@
 $L=1$, it may not occur at a given location or moment in time because of local constraints such as inclement weather or the lack of suitable habitat.
-We define the realisation of the interaction process with the variable $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L)=\chi$.
+We define the realisation of the interaction process with the variable $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L=1)=\chi$.
 This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology about the contingencies of interactions.
@@
     Lastly, measurement errors are a pervasive source of uncertainty in the observation of ecological processes.
-Given that an interaction with the variable $D$, given an interaction is feasible and occurs under the local conditions, we may define the detection of an interaction, $D$, as a stochastic process with the associated probability $P(D|X,L)=\delta$.
+Given that an interaction with the variable $D$, given an interaction is feasible and occurs under the local conditions, we may define the detection of an interaction, $D$, as a stochastic process with the associated probability $P(D|X=1,L=1)=\delta$.
 Detection failure could happen for several reasons, for instance if the rearing of a parasitoid fails with inappropriate lab conditions, because of species mis-identification, or because the interaction is very rare (see~\citet{Wirta2014} for examples of some of these difficulties and partial solutions to them).
@@
 The ecologist wanting to describe the network, however, is specifically interested in the situation where $L = 0$ (i.e., in true absences).
-Thus, while she or he will have no difficulty interpreting the observation of an interaction, the observation of an absence of an interaction offers more of a challence since it must be decomposed into different quantities.
+Thus, while there is have no difficulty interpreting the observation of an interaction, the observation of an absence of an interaction offers more of a challence since it must be decomposed into different quantities.
 It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e.
 where the interaction occurred at the location but was not observed, and $D=1 \cup X = 0 \cup L =1$, when the interaction is feasible and would have been detected but did not occur at the local site.
-The occurrence of a true absence, our quantity of interest, corresponds to the joint event $L=0 \cup X=1 \cup D=1$), but in reality an empirical ecologist will measure the marginal probability $P(L) = k/n$ where $k$ is again the number of observed interactions and $n$ the number of observed co-occurrences.
+The occurrence of a true absence, our quantity of interest, corresponds to the joint event $L=0 \cup X=1 \cup D=1$, but in reality an empirical ecologist will measure the marginal probability $P(L) = k/n$ where $k$ is again the number of observed interactions and $n$ the number of observed co-occurrences.
 
@@
 Importantly, some sources of uncertainty can be minimised with appropriate sampling design and efforts while other sources are difficult or impossible to reduce since they are generated by chance variation created by the very process in which we are interested.
+
+%DG: I do understand Tomas' point about the following, but I really appreciate it !
+Keep in mind the suggestion to drop the following paragraph was made when there was much more material above.
+Perhaps we should revisit this suggestion, given the actual material that will follow.
+To me this is fairly important for the non-technical people.
+There are some important things, such as the "the more sample the more zeros will appear in the interaction matrix"
 
@@
 We now aim to evaluate the uncertainty of this interaction.
-The occurrence of an interaction is a Bernoulli trial.
+We consider the occurrence of an interaction as a Bernoulli trial.
 Consequently, the number of successes $k$ over $n$ trials will follow a binomial distribution:
@@
 
-      Here we adopt a Bayesian approach to estimate the distribution of the parameter $\lambda$. According to Bayes principle, the posterior distribution of $\lambda$ is:
+      Here we adopt a Bayesian approach to estimate the posterior distribution of the parameter $\lambda$ :
 
@@
 
-     In some cases it can be complicated to compute the normaliser, but fortunately an analytical solution already exists in our case.
      The beta-binomial distribution is a conjugate distribution of the binomial distribution.
@@
 a known network at slightly different location) or from the network of interest if interaction probabilities for some species are already documented.
-The latter approach allows us to apply information from known, abundant species to the rarest species for which interactions are less frequently documented.
+The latter approach allows to apply information from known, abundant species to the rarest species for which interactions are less frequently documented.
 
@@
 
-    It is fairly straightforward to compute most of network metrics when the different $\lambda$ of the adjacency matrix are known, without variance~\citep{Poisot2016}.
+    %It is fairly straightforward to compute most of network metrics when the different $\lambda$ of the adjacency matrix are known, without variance~\citep{Poisot2016}.
 Several of these metrics derive directly from quantitative indices of network structure which are equivalent to $\lambda$.
@@
 For instance, assume that among the pairs of species with few observed co-occurrences there are many pairs which truly interact.
-If we begin with no observed links for these pairs, then correcting for these false absences will inflate the number of links and consequently influence metrics such as connectance, nestedness, and degree distribution.
+If we %begin with no observed links for these pairs, then correcting for these false absences will inflate the number of links and consequently influence metrics such as connectance, nestedness, and degree distribution.
 While we can, as described above, calculate these network metrics using fixed estimates for $\lambda$, no analytical solution currently exists for uncertain $\lambda$.
@@
     In the following section, we will provide an empirical example based on the well-sampled system of \emph{Salix}  plants, herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}; see Box~\ref{box1} or \emph{Appendix S2} for a description).
-This tripartite network can be examined as two bipartite networks, namely \emph{Salix}-galler and galler-natural enemy networks.
+    %This tripartite network can be examined as two bipartite networks, namely \emph{Salix}-galler and galler-natural enemy networks. 
     We will show how the uncertainty arising from both absences of co-occurrences and false absences of interactions impact these metrics.
 %We find uncertainty influences both the average and the variance of network metrics, putting in perspective traditional network comparison studies where these metrics are assumed to be fixed entities.
+
+%DG: I dropped pieces of the above paragraph because it was bizarre to get back at the posterior distribution, and then to the computer simulations.
+This section is first and foremost an empirical example.
+But then, an introduction about the scaling up was missing, so I moved part of the paragraph below
 
@@
       For a pair of species with some observed co-occurrences ($n>0$), we can update the prior distribution with these data.
-If we consider only pairs of species which were observed to co-occur but not to interact, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs, giving $\alpha'$=$\alpha$ and $\beta'$=$\beta + n$.
+If we consider only pairs of species which were observed to co-occur but not to interact, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs, giving $\alpha'$=$\alpha$ and $\beta'$=$\beta + n_{ij}$.
 As the most extreme case, for a pair of species which co-occurred at all 374 sites and was never observed to interact, our distributions would become
@@
 
-      For most pairs of species $i$ and $j$, however, $n$ was much less than 374 and our posterior mean and variance therefore retain more of the influence of the prior.
-We can see this in the increasing means and variances as we decrease $n$ (Fig.~\ref{Salix_pdfs}).
-The 95\% credible interval around the estimate of $\lambda$ also widens as $n$ decreases, from (0.001, 0.017) and (\textless0.001, 0.11) for hypothetical \emph{Salix}-galler and galler-natural enemy pairs that might be observed co-occurring at all 374 sites without any observed interaction to (0.152,0.931) and (0.008, 0.364) for \emph{Salix}-galler and galler-natural enemy pairs that were never observed co-occurring.
+      For most pairs of species $i$ and $j$, however, $n_{ij}$ was much less than 374 and our posterior mean and variance therefore retain more of the influence of the prior.
+We can see this in the increasing means and variances as we decrease $n_{ij}$ (Fig.~\ref{Salix_pdfs}).
+The 95\% credible interval around the estimate of $\lambda$ also widens as $n_{ij}$ decreases, from (0.001, 0.017) and (\textless0.001, 0.11) for hypothetical \emph{Salix}-galler and galler-natural enemy pairs that might be observed co-occurring at all 374 sites without any observed interaction to (0.152,0.931) and (0.008, 0.364) for \emph{Salix}-galler and galler-natural enemy pairs that were never observed co-occurring.
 
@@
 The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact.
-If we want to be 95\% confident that the interaction probability for two species in the \emph{Salix}-galler network is below 0.1, 0.05, or 0.01, we would need 51, 106, and 550 observed co-occurrences with no observed interaction (Fig.~\ref{Salix_cdfs}; see function samples\_for\_threshold in~\emph{Appendix S1}).
+If we want to be 95\% confident that the interaction probability for two species in the \emph{Salix}-galler network is below 0.1, 0.05, or 0.01, we would need 51, 106, and 550 observed co-occurrences with no observed interaction, respectively (Fig.~\ref{Salix_cdfs}; see function samples\_for\_threshold in~\emph{Appendix S1}).
 Although the prior distribution of interaction probabilities is narrower and closer to zero for the galler-natural enemy network, the number of samples required to be 95\% confident that the interaction probability is below a threshold still increases quickly; we would need 25, 62, and 352 observed co-occurrence with no observed interaction for threshold interaction probabilities of 0.1, 0.05, and 0.01, respectively.
@@
 No pairs were observed to co-occur frequently enough to reach the threshold for an interaction probability of 0.01.
-Discounting potential interactions, then, requires either a stronger prior expectation of no interaction (e.g., we can be highly confident that a palm tree will not predate upon a leopard no matter how many times the two species are observed together) or very extensive sampling.
+Discounting potential interactions, then, requires either a stronger prior expectation of no interaction (e.g.
+for forbidden interactions) or very extensive sampling.
 For all we know, most links absent from current descriptions of network structure may be so not because the species do not interact, but because we have not sampled deeply enough to detect them.
@@
   \subsection*{Scaling up to network metrics}
+
+  %DG: here is where I moved material from aboce
+
+    It is fairly straightforward to compute most of network metrics when the different $\lambda$ of the adjacency matrix are known, without variance~\citep{Poisot2016}.
+Several of these metrics derive directly from quantitative indices of network structure which are equivalent to $\lambda$.
+The remainder, originally defined for binary networks, can be adjusted to account for interaction probabilities between zero and one.
+It is not as easy, however, to understand how the uncertainty in these estimated interaction probabilities influences network metrics.
+Computation of these metrics involves non-linear functions.
+Since Jensen's inequality states that the average of a non-linear function of a stochastic variable differs from the function of the average of that variable, any uncertainty in the values of $\lambda$ could bias both the mean and variance of a network metric.
 
@@
 As the scale of the two datasets is quite different (genotypes of a single \emph{Salix} species in~\citet{Barbour2016}, various \emph{Salix} species in our dataset), we suspect the former is more likely.
-    [[This is a little boring. Tomas has ideas for people with potentially better priors - may require another co-author. Also maybe could use one site as a prior like ``training data"?]]
+%    [[This is a little boring. Tomas has ideas for people with potentially better priors - may require another co-author. Also maybe could use one site as a prior like ``training data"?]]
+% DG: not so sure, I find it very useful because it simply illustrates the point. Nestedness will be a nice complement with lest trivial results
 
@@
 Re-sampling networks based on a probabilistic understanding of networks is straightforward and gives distributions for network properties rather than point estimates.
-This not only acknowledges the fact that interactions vary over time and space and with different sampling effort and methodology but will also facilitate comparisons between networks.
+This not only acknowledges the fact that interactions vary over time and space but will also facilitate comparisons between networks.
 With confidence intervals around network metrics, we can not only say that one network is more connected than another but also whether the networks are more different than we would expect based on imperfect sampling of interactions.

### 2018-01-31 manuscript/CI_interactions.tex
Minor edits, some comments

@@
 
+%AE: I agree with Dom here, as I think the paragraphs below are good for getting a bit deeper into the width of the problem we are addressing. Could possibly be shortened if needed?
+
   % [[Tomas suggests removing the following because it slows down procedings:]]
@@
 \section*{A naive quantification of interaction probability and uncertainty}
+
+%%AE: I think the section that is commented  below not should be placed here, but when reading the pdf without this part in it I really thoght that this was missing.
+One option is to move this part to the Introduction, where it would fit better.
 
@@
 
-      The fact that the posterior distribution of $\lambda$ follows a beta distribution makes it straightforward to compute moments and other properties.
-These moments may then be used when calculating higher-order network properties.
+      It is common to preform analyses that require calculating higher-order network properties in interaction networks.
+The fact that the posterior distribution of $\lambda$ follows a beta distribution makes it straightforward to compute moments and other properties neede for this.
+%%AE: Should we give examples of these higher-order properties?
 
@@
 % DG: not so sure, I find it very useful because it simply illustrates the point. Nestedness will be a nice complement with lest trivial results
+%%AE: If we are doing a complement here (I agree it is a bit boring) I think option c) from Alyssas mail is the most straight forward option.
 
@@
 
-  Real interaction networks vary~\citep{Kitching1987,Olesen2011a,Pires2011a,Baiser2012,Fodrie2015,Novak2015}, and to capture this variation we must turn from static descriptions of network structure to probabilistic descriptions.
+  Real interaction networks vary over several dimensions~\citep{Kitching1987,Olesen2011a,Pires2011a,Baiser2012,Fodrie2015,Novak2015}, and to capture this variation we must turn from static descriptions of network structure to probabilistic descriptions.
 In this study, we have developed the analytical tools to capture the uncertainty in the estimation of pairwise interactions, and to partition it into its individual components: interaction uncertainty, process uncertainty and detection uncertainty.
@@
 
+%%AE: I think Box 2 is nice to have in as a hands-on example.
 \begin{floatbox}{}

### 2018-02-07 manuscript/CI_interactions.tex
fixed the and between equations

@@
 
-\author{Alyssa R. Cirtwill$^{1}$, Dominique Gravel$^{2}$, \&  Anna Ekl\"{o}f$^{1}$, Tomas Roslin$^{x,y}$, Kate Wootton$^{x}$}
+\author{Alyssa R. Cirtwill$^{1}$, Dominique Gravel$^{2}$, \&  Anna Ekl\"{o}f$^{1}$, Tomas Roslin$^{3,4}$, Kate Wootton$^{3}$}
 \date{\small$^1$Department of Physics, Chemistry\\ 
@@
 Link\"{o}ping, Sweden\\
-
-\small$^2$ Département de biologie\\ 
+\medskip$^2$ Département de biologie\\ 
 Université de Sherbrooke\\ 
 Sherbrooke, Canada\\ 
-
-\medskip $^x$ Department of Ecology\\ P.O. Box 7044, Swedish University of Agricultural Sciences \\ SE-750 07 Uppsala, Sweden \\
-\medskip $^y$ Spatial Foodweb Ecology Group\\ Department of Agricultural Sciences \\ PO Box 27 (Latokartanonkaari 5)\\ FI-00014 University of Helsinki, Finland \\
+\medskip $^3$ Department of Ecology\\ P.O. Box 7044, Swedish University of Agricultural Sciences \\ SE-750 07 Uppsala, Sweden \\
+\medskip $^4$ Spatial Foodweb Ecology Group\\ Department of Agricultural Sciences \\ PO Box 27 (Latokartanonkaari 5)\\ FI-00014 University of Helsinki, Finland \\
 % \medskip
@@
       \end{equation}
-
-      \noindent and
 

### 2018-02-09 code/calculate_sim_network_properties.py
making notes to add NODF

@@ -4,6 +4,14 @@ import networkx as nx
 import numpy as np 
 import scipy as sp 
 
+# Think I will have to do NODF in R. vegan function nestednodf(web,order=TRUE,weighted=FALSE) should get it done
+# vegan takes community data as a matrix. This may be a problem. 
+# Something like the following should convert interaction list to matrix:
+# library(igraph);
+# edge_list <- read.delim("data_file.txt", header = TRUE, sep = "\t");
+# G <- graph.data.frame(edge_list,directed=FALSE);
+# A <- as_adjacency_matrix(G,type="both",names=TRUE,sparse=FALSE,attr="weight");
+
 def web_reader(webdir,proportion,post_number,sample_number,nettype): 
   gallers=set()
   salixes=set()

### 2018-02-14 manuscript/CI_interactions.tex
probably replicated changes to addresses
new priors based on a couple of sample subwebs

@@
 Link\"{o}ping, Sweden\\
-\medskip$^2$ Département de biologie\\ 
-Université de Sherbrooke\\ 
+\medskip$^2$ D\'{e}partement de biologie\\ 
+Universit\'{e} de Sherbrooke\\ 
 Sherbrooke, Canada\\ 
@@
   First, we must obtain the $\alpha$ and $\beta$ parameters for the prior distribution.
-In this study we obtained these parameters using the R~\citep{R} function fitdispr from the package MASS~\citep{MASS}.
+In this study we obtained these parameters using the R~\citep{R} function fitdist from the package fitdistrplus~\citep{fitdistrplus}.
 Once $\alpha$ and $\beta$ are known, we can update them using our observed data.

### 2018-02-14 code/Zillis_prior/calculating_prior_distributions.R

@@ -1,0 +1,42 @@
+source('../handy_R_functions.R')
+# This prior isn't working with fitdistr, somehow. :(
+
+# To create the data file:
+for(subweb in  c('Zillis','Zillertal')){
+  SG_dataset=read.csv('../../data/Salix_example/cooccur_interact_galler_salix.csv',row.names=1)
+  SG_web=read.csv(paste0('../../data/Salix_example/Zillis/',subweb,'_SG_prior.csv',sep=''),row.names=1)
+  deg_dist_Salix=rowSums(SG_web)/ncol(SG_web)
+  deg_dist_galler=colSums(SG_web)/nrow(SG_web)
+  # Interaction probabilities are the product of plant and galler probabilities
+  sg_int_probs=as.numeric(deg_dist_galler%*%t(deg_dist_Salix))
+  SG_dataset$post.mean<-1
+  SG_dataset$post.sd<-0
+  for(r in 1:nrow(SG_dataset)){
+    if(SG_dataset$interact[r]==0){
+      pars=calculate_parameters(sg_int_probs,SG_dataset$cooccur[r],0)
+      dist=calculate_distribution(pars)
+      SG_dataset[r,7:8]=dist
+    }
+  }
+  write.table(SG_dataset,file=paste0('../../data/Salix_example/Zillis/Salix_Galler/posterior_probabilities_',subweb,'.tsv',sep=''))
+  print(subweb)
+
+  GP_dataset=read.csv('../../data/Salix_example/cooccur_interact_galler_parasit.csv',row.names=1)
+  GP_web=read.csv(paste0('../../data/Salix_example/Zillis/',subweb,'_GP_prior.csv',sep=''),row.names=1)
+  deg_dist_galler=rowSums(GP_web)/ncol(GP_web)
+  deg_dist_paras=colSums(GP_web)/nrow(GP_web)
+  # Interaction probabilities are the product of plant and galler probabilities
+  gp_int_probs=as.numeric(deg_dist_paras%*%t(deg_dist_galler))
+  GP_dataset$post.mean<-1
+  GP_dataset$post.sd<-0
+  for(r in 1:nrow(GP_dataset)){
+    if(GP_dataset$interact[r]==0){
+      pars=calculate_parameters(gp_int_probs,GP_dataset$cooccur[r],0)
+      dist=calculate_distribution(pars)
+      GP_dataset[r,7:8]=dist
+    }
+  }
[…]

### 2018-02-14 code/Zillis_prior/create_Zillis_priors.py

@@ -45,7 +45,7 @@ import scipy as sp
 #   numpy.random.binomial(n,p,size) draws [size] samples from a binomial distribution
 #   % Each observation is a Bernoulli, or a binomial with n=1. Use p=mean(posterior).
 
-def read_data(datafile):
+def read_data(datafile,site):
   ints={'SG':set(),'GP':set()}
   Salix_sp=set()
   galler_sp=set()
@@ -53,12 +53,22 @@ def read_data(datafile):
   f=open(datafile,'r')
   for line in f:
     newline=line.split('\r')[0]
-    if newline.split(',')[1]!='REARING_NUMBER':
-      Salix=newline.split(',')[10]
-      galler=newline.split(',')[11]
-      para=newline.split(',')[12] 
-      n_galls=int(newline.split(',')[13])
-      n_galls_parasit=int(newline.split(',')[14])
+    if site=='Zillertal':
+      if newline.split(',')[0]!='REARING_NUMBER':
+        Salix_ID=newline.split(',')[10]
+        galler=newline.split(',')[11]
+        para=newline.split(',')[12] 
+        n_galls=int(newline.split(',')[13])
+        n_galls_parasit=int(newline.split(',')[14])
+        Salix=newline.split(',')[15]
+    else:
+      if newline.split(',')[1]!='REARING_NUMBER':
+        Salix=newline.split(',')[10]
+        galler=newline.split(',')[11]
+        para=newline.split(',')[12] 
+        n_galls=int(newline.split(',')[13])
+        n_galls_parasit=int(newline.split(',')[14])
+    if newline.split(',')[0]!='REARING_NUMBER' and newline.split(',')[1]!='REARING_NUMBER':
       Salix_sp.add(Salix)
       galler_sp.add(galler)
       ints['SG'].add((Salix,galler))
@@ -69,11 +79,11 @@ def read_data(datafile):
   f.close()
   return ints, Salix_sp, galler_sp, para_sp
 
-def write_prior_web(ints,resources,consumers,flavour):
+def write_prior_web(ints,resources,consumers,flavour,site):
   if flavour=='SG':
-    f=open('../../data/Salix_example/Zillis/Zillis_SG_prior.csv','w')
+    f=open('../../data/Salix_example/Zillis/'+site+'_SG_prior.csv','w')
   else:
[…]

### 2018-02-14 code/handy_R_functions.R

@@ -1,9 +1,9 @@
 # Returns prior distribution when n=0 and k=0. 
 # Otherwise, returns posterior distribution
 calculate_parameters<-function(priordata,n,k){
-  library(MASS)
+  library(fitdistrplus)
   # Calculate prior parameters
-  pars=fitdistr(x=priordata,"beta",start=list(shape1=1,shape2=1),lower=c(0,0))$estimate
+  pars=fitdist(priordata,distr="beta",method="mle",start=list(shape1=10,shape2=10),lower=c(0,0))$estimate
   # The lower=c(0,0) prevents R from fitting invalid (negative) parameters
   alpha=pars[[1]]
   beta=pars[[2]]

### 2018-03-05 manuscript/CI_interactions.tex
adding the first rounds of results for the other priors

@@
 Our interest is specifically in what information can be gained from the extensive sampling of \emph{Salix}, gallers, and natural enemies across Europe; the similar but much smaller system in the United States is merely a starting point from which to obtain somewhat reasonable priors.
-To obtain these priors, we estimated frequencies of  \emph{S.
-hookeriana} genotype-galler interactions based on the normalised degree of each species in each network component (see \emph{Appendix S3} for details and code).
-Specifically, we obtain prior parameters $\alpha$=2.51 and $\beta$=1.89.
-For the galler-natural enemy component of the network, the corresponding prior parameters are $\alpha$=1.34, $\beta$=9.49.
-We are then able to use these prior parameters to estimate the posterior distribution of interaction probabilities given the additional information in our dataset.
+As the \emph{Salix}-galler component of~\citet{Barbour2016}'s study is quite different from that in~\citet{Kopelke2017}, we repeated our analyses using two subnetworks from the middle of the geographical distribution of the~\citet{Kopelke2017} dataset (Zillis and Zillertal sites) as priors.
+This is analogous to using the first sample as ``training data" with which to guide future sampling.
+To obtain the priors based on~\citet{Barbour2016}, we estimated frequencies of  \emph{S.
+hookeriana} genotype-galler interactions based on the normalised degree of each node (species or genotype) in each network component (see \emph{Appendix S3} for details and code).
+Specifically, we obtained prior parameters $\alpha$=2.51 and $\beta$=1.89.
+For the galler-natural enemy component of the network, the corresponding prior parameters were $\alpha$=1.34, $\beta$=9.49.
+We followed the same procedure to obtain priors based on~\citet{Kopelke2017} except that we used the normalised degree of each species in each network component.
+For the \emph{Salix}-galler component of the network, we obtained prior parameters of $\alpha$=8.72, $\beta$=305 and $\alpha$=6.73, $\beta$=101 for the Zillis and Zillertal subwebs, respectively.
+For the galler-natural enemy component, we obtained prior parameters of $\alpha$=0.700, $\beta$=8.49 and $\alpha$=1.64, $\beta$=11.2 for the Zillis and Zillertal subwebs, respectively.
+Note that the priors obtained for the \emph{Salix}-galler component of the network differ greatly depending on whether data from~\citet{Barbour2016} or~\citet{Kopelke2017} were used while priors for the galler-natural enemy component were relatively similar.
+After calculating these prior parameters, we were then able to estimate the posterior distribution of interaction probabilities given the additional information in our dataset.
 
       For species where no co-occurrences were observed ($n=0$), we can calculate the estimates for the mean and variance of $\lambda_{ij}$ directly from the prior parameters following equations~\ref{mean} and~\ref{variance} (see \emph{Appendix S1} for R implementation).
-For the \emph{Salix}-galler network, the prior distribution we obtained was: $\bar\lambda$=0.570, var($\lambda$)=0.056.
-The prior distribution for the galler-natural enemy network was $\bar\lambda$=0.124, var($\lambda$)=0.010.
-This is consistent with the prior data, where the average interaction probability based on the degree distributions of \emph{Salix} genotypes and gallers was 0.562 and that for gallers and natural enemies was 0.122.
-These probabilities are much higher than those in our dataset (0.028 and 0.078 for the \emph{Salix}-galler and galler-natural enemy networks, respectively) - a discrepancy which may reflect the differences in scale between the network containing different genotypes of a single \emph{Salix} species and four gallers from a single family in~\citet{Barbour2016} and the extensive network of~\citet{Kopelke2017} which contains tens of \emph{Salix}, galler, and natural enemy species, with the insects representing many different families.
+For the \emph{Salix}-galler network, the prior distribution we obtained based on~\citet{Barbour2016} was: $\bar\lambda$=0.570, var($\lambda$)=0.056.
+The prior distributions based on~\citet{Kopelke2017} were $\bar\lambda$=0.028, var($\lambda$)=8.60$\times$10$^{-5}$ and $\bar\lambda$=0.062, var($\lambda$)=5.43$\times$10$^{-4}$ for the Zillis and Zillertal subwebs, respectively.
+The prior distribution for the galler-natural enemy network based on~\citet{Barbour2016} was $\bar\lambda$=0.124, var($\lambda$)=0.010.
+Prior distributions based on~\citet{Kopelke2017} were $\bar\lambda$=0.076, var($\lambda$)=0.008 and $\bar\lambda$=0.127, var($\lambda$)=0.009 for the Zillis and Zillertal subwebs, respectively.
+The posterior interaction probabilities obtained based on~\citet{Barbour206} are much higher than those obtained based on~\citet{Kopelke2017}, especially for the \emph{Salix}-galler component of the network.
+This likely reflects the differences in scale between the network containing different genotypes of a single \emph{Salix} species and four gallers from a single family in~\citet{Barbour2016} and the more extensive networks in~\citet{Kopelke2017}.
+The prior distributions calculated from subwebs in~\citet{Kopelke2017} are more likely to reflect the sparsely-connected meta-network than is a distribution calculated from the smaller and denser network in~\citet{Barbour2016}.
+This emphasises the importance of using an appropriate study system when constructing a prior.
 
@@
 If we consider only pairs of species which were observed to co-occur but not to interact, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs, giving $\alpha'$=$\alpha$ and $\beta'$=$\beta + n_{ij}$.
-As the most extreme case, for a pair of species which co-occurred at all 374 sites and was never observed to interact, our distributions would become
+As the most extreme case, consider a pair of species which co-occurred at all 374 sites and was never observed to interact.
+Using the prior derived from~\citet{Barbour2016}, our distributions would become
       $\bar\lambda_{ij}$=6.63 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=1.74 $\times$ 10$^{-5}$ for the \emph{Salix}-galler network and 
       $\bar\lambda_{ij}$=3.49 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=9.03 $\times$ 10$^{-6}$ for the galler-natural enemy network.
-Both distributions are very close to 0 with small variance about our estimate of $\lambda$; species $i$ and $j$ are extremely unlikely to interact at sites or times not included in our sample.
+Using the priors derived from~\citet{Kopelke2017}, our distributions for the \emph{Salix}-galler network would become $\bar\lambda_{ij}$=1.27 $\times$ 10$^{-2}$, var($\lambda_{ij}$)=1.82 $\times$ 10$^{-5}$ and $\bar\lambda_{ij}$=1.40 $\times$ 10$^{-2}$, var($\lambda_{ij}$)=2.86 $\times$ 10$^{-5}$ for the Zillis and Zillertal subwebs, respectively.
+Our distributions for the galler-natural enemy network would become $\bar\lambda_{ij}$=1.83 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=4.76 $\times$ 10$^{-6}$ and $\bar\lambda_{ij}$=4.23 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=1.09 $\times$ 10$^{-5}$ for the Zillis and Zillertal subwebs.
+Distributions for both network components were very close to 0 with small variance about our estimate of $\lambda$; species $i$ and $j$ are extremely unlikely to interact at sites or times not included in our sample.
 
@@
 We can see this in the increasing means and variances as we decrease $n_{ij}$ (Fig.~\ref{Salix_pdfs}).
-The 95\% credible interval around the estimate of $\lambda$ also widens as $n_{ij}$ decreases, from (0.001, 0.017) and (\textless0.001, 0.11) for hypothetical \emph{Salix}-galler and galler-natural enemy pairs that might be observed co-occurring at all 374 sites without any observed interaction to (0.152,0.931) and (0.008, 0.364) for \emph{Salix}-galler and galler-natural enemy pairs that were never observed co-occurring.
+Using the priors derived from~\citet{Barbour2016}, the 95\% credible interval around the estimate of $\lambda$ also widens as $n_{ij}$ decreases from (0.001, 0.017) and (\textless0.001, 0.11) for hypothetical \emph{Salix}-galler and galler-natural enemy pairs that might be observed co-occurring at all 374 sites without any observed interaction to (0.152,0.931) and (0.008, 0.364) for \emph{Salix}-galler and galler-natural enemy pairs that were never observed co-occurring.
+The priors derived from~\citet{Kopelke} gave intervals that were closer to 0, widening from (0.006, 0.022) and (0.006, 0.026) to (0.013, 0.049) and (0.025, 0.115) for the \emph{Salix}-galler network and widening from (0.00001, 0.008) and (0.0004, 0.013) to (0.0005, 0.304) and (0.012, 0.348) for the galler-natural enemy network.
 

### 2018-03-06 manuscript/CI_interactions.tex
moving Barbour to SI

--- 2018-02-14 manuscript/CI_interactions.tex
@@
 % DG : if ok with all of you, I would appreciate being last author
+% AC : Makes sense to me since Dom was the originator of this ms and laid a lot of the groundwork.
 
-\author{Alyssa R. Cirtwill$^{1}$, Dominique Gravel$^{2}$, \&  Anna Ekl\"{o}f$^{1}$, Tomas Roslin$^{3,4}$, Kate Wootton$^{3}$}
+% AC : Assuming I'm going to be corresponding author on this but happy to let anyone else step in if you're eager
+
+\author{Alyssa R. Cirtwill$^{1\dagger}$, \&  Anna Ekl\"{o}f$^{1}$, Tomas Roslin$^{2,3}$, Kate Wootton$^{2}$, Dominique Gravel$^{4}$}
 \date{\small$^1$Department of Physics, Chemistry\\ 
@@
 Link\"{o}ping, Sweden\\
-\medskip$^2$ D\'{e}partement de biologie\\ 
+\medskip $^2$ Department of Ecology\\ P.O. Box 7044, Swedish University of Agricultural Sciences \\ SE-750 07 Uppsala, Sweden \\
+\medskip $^3$ Spatial Foodweb Ecology Group\\ Department of Agricultural Sciences \\ PO Box 27 (Latokartanonkaari 5)\\ FI-00014 University of Helsinki, Finland \\
+\medskip$^4$ D\'{e}partement de biologie\\ 
 Universit\'{e} de Sherbrooke\\ 
 Sherbrooke, Canada\\ 
-\medskip $^3$ Department of Ecology\\ P.O. Box 7044, Swedish University of Agricultural Sciences \\ SE-750 07 Uppsala, Sweden \\
-\medskip $^4$ Spatial Foodweb Ecology Group\\ Department of Agricultural Sciences \\ PO Box 27 (Latokartanonkaari 5)\\ FI-00014 University of Helsinki, Finland \\
-% \medskip
-% $^\dagger$ Corresponding author:\\
-% alyssa.cirtwill@gmail.com\\
-% +46 723 158464\\
+\medskip
+$^\dagger$ Corresponding author:\\
+alyssa.cirtwill@gmail.com\\
++46 723 158464\\
 }
@@
 In such cases, $\lambda$ would take a value of 0 and there would be no uncertainty.
-    % [[The previous sentence doesn't follow, k hasn't been defined and we don't know that it's zero.
-Also, are we assuming that these interactions have been observed over a large area/time like the Kopelke data?
-Otherwise couldn't something about that particular site prevent species interacting even if they otherwise could?]]
-    % [[With defining k I think this is fine...
-site uncertainty will come in later, and it's not necessary to assume anything about the sampling design to get from not observing two species to interact to suspecting that they don't (degree of confidence depending on the species involved).
-I've toned down "very likely" to "possible" though - does that help?]]
     Nevertheless, it is also possible that the interaction is a rare phenomenon with $\lambda>0$ that has not yet been documented.
@@
 In other words, with sufficient sampling and all information accessible, this interaction probability $\lambda$ should either tend to 0 or to 1 and the uncertainty should vanish.
-    % [[For species which actually co occur (?)]]
-    % [[I think that gets covered under "sufficient sampling"]]
 
@@
 
-  % [[Tomas suggests removing the following because it slows down procedings:]]
-  % The basic information that we are collecting consists of matrices of interaction partners.
+  [[Tomas suggests removing the following because it slows down procedings, Anna and Dom want it back. Shortening sounds like a good middle ground:]]
+  The basic information that we are collecting consists of matrices of interaction partners.
 Our count of interactions between two species reflects uncertainty with respect to whether two species are capable of interacting when co-occurring at a given site ($\lambda$), chance variation in whether the interaction is realised ($\chi$),  and uncertainty with respect to whether it is detected when realised ($\delta$).
@@
 
-  % The obvious rule of thumb is to ``sample more" (see Fig.~\ref{upper_limits} for a demonstration of the power of increasing sample size), but we note that there are limits to the utility of this motto.
+  The obvious rule of thumb is to ``sample more" (see Fig.~\ref{upper_limits} for a demonstration of the power of increasing sample size), but we note that there are limits to the utility of this motto.
 Sampling more will clearly reduce uncertainty regarding the upper bound of the probability of interaction, and it will also increase the probability of detecting unlikely interactions (i.e.
@@
 
-  % As a solution towards deciding whether unobserved interactions were undetected due to sampling, or whether they truly do not occur,~\citet{Weinstein2017} used repeated sampling rounds to estimate the daily probability of detecting a hummingbird interaction, and to thereby model the observation and process mechanisms.
+  As a solution towards deciding whether unobserved interactions were undetected due to sampling, or whether they truly do not occur,~\citet{Weinstein2017} used repeated sampling rounds to estimate the daily probability of detecting a hummingbird interaction, and to thereby model the observation and process mechanisms.
 While conceptually attractive, this approach is unsuitable for interactions occurring over longer time scales (e.g., associations between hosts and parasitoids with a single generation per year), or very rare interactions which might not occur on any of the sampling days or might involve individuals of a species that are not under observation.
@@
 
-  % An added complication is that not all sources of uncertainty are proportional to sample size.
+  An added complication is that not all sources of uncertainty are proportional to sample size.
 To record an interaction between A and B, we need to identify both partners correctly (a non-trivial problem in many food webs; e.g.~\citealp{Kaartinen2011,Roslin2016}) and be able to resolve all interactions with a similar likelihood.
@@
 
-  % [[How do we define samples?
-For the Kopelke set we use sampling occasion, but what about sampling twice as many trees on the same day and same place?
-Does that count?
-Does it have to be spatially and/or temporally separated?
-Is it relevant??]]
-  % [[Pretty sure this will always depend on the study - also seems like a pretty large digression.]]
-
 \section*{A naive quantification of interaction probability and uncertainty}
@@
 
-  % It is getting more and more common to represent interactions as probabilities in theoretical models of network structure.
+   [[Move this paragraph to intro?]] It is getting more and more common to represent interactions as probabilities in theoretical models of network structure.
 For example, the minimum potential model introduces gaps in the feeding niche of predators by sampling based on the likelihood of each interaction~\citep{Allesina2008}, while a gaussian probability function is used to represent the niche by~\citet{Williams2010}.
@@
       It is common to preform analyses that require calculating higher-order network properties in interaction networks.
-The fact that the posterior distribution of $\lambda$ follows a beta distribution makes it straightforward to compute moments and other properties neede for this.
+The fact that the posterior distribution of $\lambda$ follows a beta distribution makes it straightforward to compute moments and other properties needed for this.
 %%AE: Should we give examples of these higher-order properties?    
+% AC: How do you mean? Examples of averages/variances/modes or of "other properties" ?
 
@@
 
-          % [Tomas adds: This is a bit of a stump]
-%DG: I tried to expand just a little, but I don't want to get lost in this paragraph as it would be a distraction. We should basically mention it as a possibility.
-
           As a fourth and final approach to obtain the prior distribution of $\lambda$, we envisage using the outcome of a trait-matching model, provided such a model has been documented using external data and relevant traits are available.
@@
 Note that in this case the prior might not be beta-distributed and numerical methods might be required to compute the posterior distribution.
-
-%DG: I want to be sure that the following example is clear and understandable for everyone. Tomas, Kate, both of you can follow the entire logic ? Would you be able to reproduce it using the R code ?
 
@@
 
+% AC : Maybe we should change the section title to highlight that this is an empirical example and covers the effect of uncertainty on network-level properties
+
   \subsection*{Computing the posterior distribution}
@@
       In a strict Bayesian framework, we wish to use a prior distribution that does not rely on any information from the study at hand.
-To that end, we use data from another well-described system of \emph{Salix}, gallers, and natural enemies~\citep{Barbour2016,Barbour2016Dryad}.
-We note that this study used several genotypes of \emph{Salix hookeriana} rather than different \emph{Salix} species, but stress that this difference is unlikely to be critical for our purposes.
-Our interest is specifically in what information can be gained from the extensive sampling of \emph{Salix}, gallers, and natural enemies across Europe; the similar but much smaller system in the United States is merely a starting point from which to obtain somewhat reasonable priors.
-To obtain these priors, we estimated frequencies of  \emph{S.
-hookeriana} genotype-galler interactions based on the normalised degree of each species in each network component (see \emph{Appendix S3} for details and code).
-Specifically, we obtain prior parameters $\alpha$=2.51 and $\beta$=1.89.
-For the galler-natural enemy component of the network, the corresponding prior parameters are $\alpha$=1.34, $\beta$=9.49.
-We are then able to use these prior parameters to estimate the posterior distribution of interaction probabilities given the additional information in our dataset.
+Network data for a similar study system may, however, not be available.
+In that case, one might use the first subnetwork collected as ``training data" to guide future sampling.
+To simulate this situation, we created priors using a single subnetwork from the middle of the geographical distribution of the~\citep{Kopelke2017} dataset (Zillis subweb).
+To demonstrate how the use of a data from a different system can affect the prior distribution and conclusions based on it, we repeated our analyses using priors derived from a much smaller \emph{Salix}-galler-natural enemy system~\citep{Barbour2016,Barbour2016Dryad}.
+This smaller system was much more densely-connected than that described in~\citet{Kopelke2017} and provided unreasonable distributions for interaction probabilities (\emph{Appendix SX}).
+
+      To obtain the priors based on the Zillis subweb, we estimated frequencies of \emph{Salix}-galler interactions based on the normalised degree of each species in each network component (see \emph{Appendix S3} for details and code).
+Specifically, we obtained prior parameters of $\alpha$=8.72, $\beta$=305 for the \emph{Salix}-galler component and $\alpha$=0.700, $\beta$=8.49 for the galler-natural enemy components of the network.
+After calculating these prior parameters, we were then able to estimate the posterior distribution of interaction probabilities given the additional information in our dataset.
 
       For species where no co-occurrences were observed ($n=0$), we can calculate the estimates for the mean and variance of $\lambda_{ij}$ directly from the prior parameters following equations~\ref{mean} and~\ref{variance} (see \emph{Appendix S1} for R implementation).
-For the \emph{Salix}-galler network, the prior distribution we obtained was: $\bar\lambda$=0.570, var($\lambda$)=0.056.
-The prior distribution for the galler-natural enemy network was $\bar\lambda$=0.124, var($\lambda$)=0.010.
-This is consistent with the prior data, where the average interaction probability based on the degree distributions of \emph{Salix} genotypes and gallers was 0.562 and that for gallers and natural enemies was 0.122.
-These probabilities are much higher than those in our dataset (0.028 and 0.078 for the \emph{Salix}-galler and galler-natural enemy networks, respectively) - a discrepancy which may reflect the differences in scale between the network containing different genotypes of a single \emph{Salix} species and four gallers from a single family in~\citet{Barbour2016} and the extensive network of~\citet{Kopelke2017} which contains tens of \emph{Salix}, galler, and natural enemy species, with the insects representing many different families.
+For the \emph{Salix}-galler network, the prior distribution  was: $\bar\lambda$=0.028, var($\lambda$)=8.60$\times$10$^{-5}$.
+The prior distribution for the galler-natural enemy network was: $\bar\lambda$=0.076, var($\lambda$)=0.008.
+The posterior interaction probabilities obtained based on the Zillis subweb were much lower than those obtained based on~\citet{Barbour2016}; this emphasises the importance of using an appropriate study system when constructing a prior (\emph{Appendix SX}).
 
@@
 If we consider only pairs of species which were observed to co-occur but not to interact, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs, giving $\alpha'$=$\alpha$ and $\beta'$=$\beta + n_{ij}$.
-As the most extreme case, for a pair of species which co-occurred at all 374 sites and was never observed to interact, our distributions would become
-      $\bar\lambda_{ij}$=6.63 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=1.74 $\times$ 10$^{-5}$ for the \emph{Salix}-galler network and 
-      $\bar\lambda_{ij}$=3.49 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=9.03 $\times$ 10$^{-6}$ for the galler-natural enemy network.
-Both distributions are very close to 0 with small variance about our estimate of $\lambda$; species $i$ and $j$ are extremely unlikely to interact at sites or times not included in our sample.
+As the most extreme case, consider a pair of species which co-occurred at all 374 sites and was never observed to interact.
+Using the priors described above, our distribution for the \emph{Salix}-galler network would become $\bar\lambda_{ij}$=1.27 $\times$ 10$^{-2}$, var($\lambda_{ij}$)=1.82 $\times$ 10$^{-5}$ while our distribution for the galler-natural enemy network would become $\bar\lambda_{ij}$=1.83 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=4.76.
+Distributions for both network components were very close to 0 with small variance about our estimate of $\lambda$; species $i$ and $j$ are extremely unlikely to interact at sites or times not included in our sample.
 
@@
 We can see this in the increasing means and variances as we decrease $n_{ij}$ (Fig.~\ref{Salix_pdfs}).
-The 95\% credible interval around the estimate of $\lambda$ also widens as $n_{ij}$ decreases, from (0.001, 0.017) and (\textless0.001, 0.11) for hypothetical \emph{Salix}-galler and galler-natural enemy pairs that might be observed co-occurring at all 374 sites without any observed interaction to (0.152,0.931) and (0.008, 0.364) for \emph{Salix}-galler and galler-natural enemy pairs that were never observed co-occurring.
+The change in distribution as $n_{ij}$ decreases can also be shown  by calculating 95\% credible intervals for $\lambda$ (see the function ``credible\_interval" in \emph{Appendix S2}).
+The 95\% credible interval around the estimate of $\lambda$ also widens as $n_{ij}$ decreases from (0.001, 0.017) and (\textless0.001, 0.11) for hypothetical \emph{Salix}-galler and galler-natural enemy pairs that might be observed co-occurring at all 374 sites without any observed interaction to (0.152,0.931) and (0.008, 0.364) for \emph{Salix}-galler and galler-natural enemy pairs that were never observed co-occurring.
+The 95\% credible interval for hypothetical \emph{Salix}-galler pairs widened from (0.006, 0.022) if the pair co-occurred at all sites to (0.013, 0.049) if they co-occurred at none.
+The 95\% credible interval for hypothetical galler-natural enemy pairs, meanwhile, widened from (0.00001, 0.008) to (0.0005, 0.304).
 
@@
       Rather than calculating credible intervals for a posterior distribution after collecting data, we may wish to know how many data points are necessary to obtain a given level of confidence that two co-occurring species do not interact.
-The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact.
-If we want to be 95\% confident that the interaction probability for two species in the \emph{Salix}-galler network is below 0.1, 0.05, or 0.01, we would need 51, 106, and 550 observed co-occurrences with no observed interaction, respectively (Fig.~\ref{Salix_cdfs}; see function samples\_for\_threshold in~\emph{Appendix S1}).
-Although the prior distribution of interaction probabilities is narrower and closer to zero for the galler-natural enemy network, the number of samples required to be 95\% confident that the interaction probability is below a threshold still increases quickly; we would need 25, 62, and 352 observed co-occurrence with no observed interaction for threshold interaction probabilities of 0.1, 0.05, and 0.01, respectively.
+The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact (Fig.~\ref{Salix_cdfs}; see function samples\_for\_threshold in~\emph{Appendix S1}).
+In our dataset, the entire 95\% credible interval was (0.013, 0.049).
+We may therefore be 95\% confident that the interaction probability for \emph{Salix} and galler species that have not been observed cooccurring is below 0.05.
+To be 95\% confident that the interaction probability for these species is below 0.01 would require 139 observed co-occurrences with no interaction.
+
+      The number of samples required to be 95\% confident that the interaction probability between galler and natural enemy species is below a threshold also increases quickly as the threshold decreasesy.
+The 95\% credible interval is (0.0005, 0.303) for the probability of interaction between two species observed to co-occur but never interact.
+To be 95\% confident that the probability of interaction is below 0.1, 0.05, or 0.001 would require 15, 39, and 229 observed co-occurrances, respectively.
+
       Given the low levels of replication in most network studies, this implies that we should have fairly low confidence in many ``non-interacting" pairs of species.
 Even in the extensively replicated \emph{Salix}-galler-natural enemy dataset very few species pairs were observed co-occurring frequently enough to reach these thresholds.
-In fact, only three \emph{Salix}-galler pairs and 31 pairs of gallers and their natural enemies were observed co-occurring frequently enough to reach the threshold for an interaction probability of 0.1.
-No pairs were observed to co-occur frequently enough to reach the threshold for an interaction probability of 0.01.
+Regardless of our choice of prior, no species pairs were observed to co-occur frequently enough to reach the threshold for an interaction probability of 0.01.
 Discounting potential interactions, then, requires either a stronger prior expectation of no interaction (e.g.
@@
   \subsection*{Scaling up to network metrics}
+  [[Haven't added NODF or checked this yet.]]
 
@@
 
+    \begin{figure}[ht]
+    \caption{Here we show the mean connectance, links per resource (\emph{Salix} in the \emph{Salix}-galler networks and gallers in the galler-natural enemy networks), and links per consumer for networks assembled using posterior distributions based on a single subweb in the~\citet{Kopelke2017} dataset (Zillis).
+We created 100 ``posterior-sampling" networks and then, for each of these, created 100 ``detection-filter" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network.
+This simulates imperfect detection of interactions in the field.
+Each point represents the mean network property (e.g., connectance) obtained from a set of 100 detection-filter networks, plotted against the value of the network property in the posterior-sampling network used to create the detection-filter networks.
+For each property and both network types, the posterior-sampling networks cover a relatively small range of network properties than the range covered by networks with varying detection probabilities.
+The value of each property decreases with the proportion of links included in the detection-filter networks.}
+    \label{posterior_webs}    
+    \includegraphics[width=.8\textwidth]{Figures/Salix_Galler_posterior_properties_Zillis.eps}
+    \end{figure}
+
   % [[What if we have only one site?

### 2018-03-06 manuscript/supplemental.tex
moving Barbour to SI

@@
 
+    \subsection*{Degree distributions and interaction probabilities}
+
+      Obtaining degree distributions from the binary interaction 
+      network is straightforward. To do this, we simply divide the 
+      total number of observed interaction partners for each 
+      species (row or column sums) with the number of potential 
+      interaction partners (number of column or rows). Degree 
+      distributions calculated, we can then calculate the 
+      probability of each interaction as the product of the 
+      normalised degrees of the two species. For example, the 
+      probability of an interaction between two species with 
+      normalised degrees of 0.5 (each interacts with half of the 
+      available partners) is 0.25. R code used to do this follows:
+
+      \vspace{12pt}
+      \begin{em}
+      \noindent \hspace{2pt}\# Now get the degree distributions from the web\\
+      \noindent \hspace{2pt}deg\_dist\_Salix=rowSums(prior\_web)/ncol(prior\_web)\\
+      \vspace{4pt}
+      \noindent \hspace{2pt}\# Remove one genotype that never interacted\\
+      \noindent \hspace{2pt}deg\_dist\_Salix\textless-deg\_dist\_Salix[which(rowSums(prior\_web)\textgreater0)]\\
+      \noindent \hspace{2pt}deg\_dist\_galler=colSums(prior\_web)/nrow(prior\_web)\\
+      \vspace{4pt}
+      \noindent \hspace{2pt}\# Interaction probabilities are the product of plant and galler probabilities\\
+      \noindent \hspace{2pt}int\_probs=as.numeric(deg\_dist\_galler\%$*$\%t(deg\_dist\_Salix))\\
+      \vspace{4pt}
+      \noindent \hspace{2pt}\# And for the galler-parasitoid web:\\
+      \noindent \hspace{2pt}deg\_dist\_parasitoid=rowSums(prior\_web\_para\_only)/ncol(prior\_web\_para\_only)\\
+      \noindent \hspace{2pt}deg\_dist\_parasitized=colSums(prior\_web\_para\_only)/nrow(prior\_web\_para\_only)\\
+      \noindent \hspace{2pt}gp\_int\_probs=as.numeric(deg\_dist\_parasitized\%$*$\%t(deg\_dist\_parasitoid))\\
+      \end{em}
+
+      % SG_web=read.csv('binary_prior_web_SG.csv',row.names=1)
+      % GP_web=read.csv('binary_prior_web_para_only.csv',row.names=1)
+
+      %       # Now get the degree distributions from the web
+      % deg_dist_Salix=rowSums(SG_web)/ncol(SG_web)
+      % deg_dist_galler=colSums(SG_web)/nrow(SG_web)
+      % # Interaction probabilities are the product of plant and galler probabilities
+      % sg_int_probs=as.numeric(deg_dist_galler%*%t(deg_dist_Salix))
+
+      % deg_dist_parasitoid=rowSums(GP_web)/ncol(GP_web)
+      % deg_dist_parasitized=colSums(GP_web)/nrow(GP_web)
+      % gp_int_probs=as.numeric(deg_dist_parasitized%*%t(deg_dist_parasitoid))
+
+\clearpage
+
+\section*{Appendix S4: Analyses using alternative prior}
+
+  We repeated our analyses using an alternative prior derived from a study of a similar \emph{Salix}-galler-natural enemy system in North America~\citep{Barbour2016,Barbour2016Dryad}.
+We note that this study used several genotypes of \emph{Salix hookeriana} rather than different \emph{Salix} species and so did not produce networks of similar size and connectedness to those in~\citep{Kopelke2016}.
+To obtain the priors based on~\citet{Barbour2016}, we estimated frequencies of  \emph{S.
+hookeriana} genotype-galler interactions based on the normalised degree of each node (species or genotype) in each network component.
+
     \subsection*{Creating a binary interaction network}
@@
 
-    \subsection*{Degree distributions and interaction probabilities}
+    \subsection*{Prior and posterior distributions}
 
-      Obtaining degree distributions from the binary interaction 
-      network is straightforward. To do this, we simply divide the 
-      total number of observed interaction partners for each 
-      species (row or column sums) with the number of potential 
-      interaction partners (number of column or rows). Degree 
-      distributions calculated, we can then calculate the 
-      probability of each interaction as the product of the 
-      normalised degrees of the two species. For example, the 
-      probability of an interaction between two species with 
-      normalised degrees of 0.5 (each interacts with half of the 
-      available partners) is 0.25. R code used to do this follows:
+      Using the binary networks described above, we obtained prior parameters $\alpha$=2.51 and $\beta$=1.89 for the \emph{Salix}-galler component and $\alpha$=1.34, $\beta$=9.49 for the galler-natural enemy component of the network.
+After calculating these prior parameters, we were then able to estimate the posterior distribution of interaction probabilities given the additional information in our dataset.
+      For species where no co-occurrences were observed ($n=0$), we can calculate the estimates for the mean and variance of $\lambda_{ij}$ directly from the prior parameters following equations~\ref{mean} and~\ref{variance} (see \emph{Appendix S1} for R implementation).
+For the \emph{Salix}-galler network, the prior distribution was: $\bar\lambda$=0.570, var($\lambda$)=0.056.
+The prior distribution for the galler-natural enemy network was: $\bar\lambda$=0.124, var($\lambda$)=0.010.
 
-      \vspace{12pt}
-      \begin{em}
-      \noindent \hspace{2pt}\# Now get the degree distributions from the web\\
-      \noindent \hspace{2pt}deg\_dist\_Salix=rowSums(prior\_web)/ncol(prior\_web)\\
-      \vspace{4pt}
-      \noindent \hspace{2pt}\# Remove one genotype that never interacted\\
-      \noindent \hspace{2pt}deg\_dist\_Salix\textless-deg\_dist\_Salix[which(rowSums(prior\_web)\textgreater0)]\\
-      \noindent \hspace{2pt}deg\_dist\_galler=colSums(prior\_web)/nrow(prior\_web)\\
-      \vspace{4pt}
-      \noindent \hspace{2pt}\# Interaction probabilities are the product of plant and galler probabilities\\
-      \noindent \hspace{2pt}int\_probs=as.numeric(deg\_dist\_galler\%$*$\%t(deg\_dist\_Salix))\\
-      \vspace{4pt}
-      \noindent \hspace{2pt}\# And for the galler-parasitoid web:\\
-      \noindent \hspace{2pt}deg\_dist\_parasitoid=rowSums(prior\_web\_para\_only)/ncol(prior\_web\_para\_only)\\
-      \noindent \hspace{2pt}deg\_dist\_parasitized=colSums(prior\_web\_para\_only)/nrow(prior\_web\_para\_only)\\
-      \noindent \hspace{2pt}gp\_int\_probs=as.numeric(deg\_dist\_parasitized\%$*$\%t(deg\_dist\_parasitoid))\\
-      \end{em}
+      For a pair of species with some observed co-occurrences ($n>0$), we can update the prior distribution with these data.
+If we consider only pairs of species which were observed to co-occur but not to interact, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs, giving $\alpha'$=$\alpha$ and $\beta'$=$\beta + n_{ij}$.
+As the most extreme case, consider a pair of species which co-occurred at all 374 sites and was never observed to interact.
+Using the priors described above, our distributions would become
+      $\bar\lambda_{ij}$=6.63 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=1.74 $\times$ 10$^{-5}$ for the \emph{Salix}-galler network and 
+      $\bar\lambda_{ij}$=3.49 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=9.03 $\times$ 10$^{-6}$ for the galler-natural enemy network.
+Distributions for both network components were close to 0 with small variance about our estimate of $\lambda$; species $i$ and $j$ are unlikely to interact at sites or times not included in our sample.
 
-      % SG_web=read.csv('binary_prior_web_SG.csv',row.names=1)
-      % GP_web=read.csv('binary_prior_web_para_only.csv',row.names=1)
+    \subsection*{Credible intervals and sampling requirements}
 
-      %       # Now get the degree distributions from the web
-      % deg_dist_Salix=rowSums(SG_web)/ncol(SG_web)
-      % deg_dist_galler=colSums(SG_web)/nrow(SG_web)
-      % # Interaction probabilities are the product of plant and galler probabilities
-      % sg_int_probs=as.numeric(deg_dist_galler%*%t(deg_dist_Salix))
+      For most pairs of species $i$ and $j$, however, $n_{ij}$ was much less than 374 and our posterior mean and variance therefore retain more of the influence of the prior.
+We can see this in the increasing means and variances as we decrease $n_{ij}$ (Fig.~\ref{Salix_pdfs}).
+The 95\% credible interval around the estimate of $\lambda$ also widens as $n_{ij}$ decreases, from (0.001, 0.017) and (\textless0.001, 0.11) for hypothetical \emph{Salix}-galler and galler-natural enemy pairs that might be observed co-occurring at all 374 sites without any observed interaction to (0.152,0.931) and (0.008, 0.364) for \emph{Salix}-galler and galler-natural enemy pairs that were never observed co-occurring.
 
-      % deg_dist_parasitoid=rowSums(GP_web)/ncol(GP_web)
-      % deg_dist_parasitized=colSums(GP_web)/nrow(GP_web)
-      % gp_int_probs=as.numeric(deg_dist_parasitized%*%t(deg_dist_parasitoid))
+      If we want to be 95\% confident that the interaction probability for two species in the \emph{Salix}-galler network is below 0.1, 0.05, or 0.01, we would need 51, 106, and 550 observed co-occurrences with no observed interaction, respectively (Fig.~\ref{Salix_cdfs}; see function samples\_for\_threshold in~\emph{Appendix S1}).
+The number of samples required to be 95\% confident that the interaction probability between galler and natural enemy species is below a threshold also increases quickly as the threshold decreases; we would need 25, 62, and 352 observed co-occurrence with no observed interaction for threshold interaction probabilities of 0.1, 0.05, and 0.01, respectively.
 
-\clearpage
+    \subsection*{Scaling up to network metrics}
 

### 2018-03-06 manuscript/CI_interactions.tex
going well with the updating

@@
 
+    [[check that all the figs are with Zillis]]
+
     %It is fairly straightforward to compute most of network metrics when the different $\lambda$ of the adjacency matrix are known, without variance~\citep{Poisot2016}.
@@
 %DG: otherwise the difference between the two interaction types is very interesting and useful to show the effect of the priors. Bravo ! 
+[[Update these two figs with Zillis data.]]
       \begin{figure}[ht]
@@
 
-    \begin{figure}[ht]
-    \caption{Here we show the mean connectance, links per resource (\emph{Salix} in the \emph{Salix}-galler networks and gallers in the galler-natural enemy networks), and links per consumer for networks assembled using posterior distributions based on a smaller, North American \emph{Salix}-galler-natural enemy system~\citep{Barbour2016,Barbour2016Dryad}.
+    % \begin{figure}[ht]
+    % \caption{Here we show the mean connectance, links per resource (\emph{Salix} in the \emph{Salix}-galler networks and gallers in the galler-natural enemy networks), and links per consumer for networks assembled using posterior distributions based on a smaller, North American \emph{Salix}-galler-natural enemy system~\citep{Barbour2016,Barbour2016Dryad}.
 We created 100 ``posterior-sampling" networks and then, for each of these, created 100 ``detection-filter" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network.
@@
 The value of each property decreases with the proportion of links included in the detection-filter networks.}
-    \label{posterior_webs}    
-    \includegraphics[width=.8\textwidth]{Figures/Salix_Galler_posterior_properties.eps}
-    \end{figure}
+    % \label{posterior_webs}    
+    % \includegraphics[width=.8\textwidth]{Figures/Salix_Galler_posterior_properties.eps}
+    % \end{figure}
 

### 2018-03-06 code/Zillis_prior/create_Zillis_posterior_webs.py

@@ -99,7 +99,8 @@ def filter_posterior_webs(postdir,proportion,altdir,site):
 
 def main():
 
-  for site in ['Zillis','Zillertal']:
+  for site in ['Zillis']:
+  # for site in ['Zillis','Zillertal']:
     for nettype in ['SG','GP']:
       if nettype=='SG':
         datafile='../../data/Salix_example/Zillis/Salix_Galler/posterior_probabilities_'+site+'.tsv'

### 2018-03-06 code/figure_generation/Zillis_posterior_plots.py

@@ -90,26 +90,24 @@ def obs_breaker(obsdict):
   return maxdots,meandots,mindots
 
 def Zillis_yaxes(prop,graph):
+  graph.world.ymin=0.0
   if prop=='C':
-    graph.world.ymin=0.0
-    graph.world.ymax=0.12
-    graph.yaxis.tick.configure(major=0.03,onoff='on',minor_ticks=1,major_size=.5,place='normal',minor_size=.3,major_linewidth=1,minor_linewidth=1)
+    graph.world.ymax=0.07
+    graph.yaxis.tick.configure(major=0.02,onoff='on',minor_ticks=1,major_size=.5,place='normal',minor_size=.3,major_linewidth=1,minor_linewidth=1)
     graph.yaxis.ticklabel.configure(char_size=.75,format='decimal',prec=2)
     ytext="Connectance"
   elif prop=='LS':
-    graph.world.ymin=0
-    graph.world.ymax=6
-    graph.yaxis.tick.configure(major=2,onoff='on',minor_ticks=1,major_size=.5,place='normal',minor_size=.3,major_linewidth=1,minor_linewidth=1)
+    graph.world.ymax=4
+    graph.yaxis.tick.configure(major=1,onoff='on',minor_ticks=1,major_size=.5,place='normal',minor_size=.3,major_linewidth=1,minor_linewidth=1)
     ytext="Links/resource"
   elif prop=='LG':
-    graph.world.ymin=0
-    graph.world.ymax=11
+    graph.world.ymax=7
     graph.yaxis.tick.configure(major=2,onoff='on',minor_ticks=1,major_size=.5,place='normal',minor_size=.3,major_linewidth=1,minor_linewidth=1)
     ytext="Links/consumer"
   else:
-    graph.world.ymin=0
-    graph.world.ymax=4
-    graph.yaxis.tick.configure(major=1,onoff='on',minor_ticks=1,major_size=.5,place='normal',minor_size=.3,major_linewidth=1,minor_linewidth=1)
+    graph.world.ymax=2.25
+    graph.yaxis.tick.configure(major=.5,onoff='on',minor_ticks=1,major_size=.5,place='normal',minor_size=.3,major_linewidth=1,minor_linewidth=1)
+    graph.yaxis.ticklabel.configure(char_size=.75,format='decimal',prec=1)
     ytext='NODF'
   graph.yaxis.label.configure(text=ytext,char_size=1,just=2)
 
[…]

### 2018-03-06 code/figure_generation/pdfs_and_N.py
prepped to re-run other 2 figure

@@ -23,9 +23,9 @@
 # colnames(ydata)=c("N",seq(1,1000))
 # colnames(MLEs)=c("N","MLE","lower","upper")
 
-# write.table(xdata,file='../../data/Salix_example/Salix_Galler/distfigure_xvals.tsv',sep='\t')
-# write.table(ydata,file='../../data/Salix_example/Salix_Galler/distfigure_yvals.tsv',sep='\t')
-# write.table(MLEs,file='../../data/Salix_example/Salix_Galler/distfigure_MLEs.tsv',sep='\t')
+# write.table(xdata,file='../../data/Salix_example/Zillis/Salix_Galler/distfigure_xvals.tsv',sep='\t')
+# write.table(ydata,file='../../data/Salix_example/Zillis/Salix_Galler/distfigure_yvals.tsv',sep='\t')
+# write.table(MLEs,file='../../data/Salix_example/Zillis/Salix_Galler/distfigure_MLEs.tsv',sep='\t')
 
 # xdata=matrix(ncol=1001,nrow=12)
 # ydata=matrix(ncol=1001,nrow=12)
@@ -50,9 +50,9 @@
 # colnames(ydata)=c("N",seq(1,1000))
 # colnames(MLEs)=c("N","MLE","lower","upper")
 
-# write.table(xdata,file='../../data/Salix_example/Galler_Parasitoid/distfigure_xvals.tsv',sep='\t')
-# write.table(ydata,file='../../data/Salix_example/Galler_Parasitoid/distfigure_yvals.tsv',sep='\t')
-# write.table(MLEs,file='../../data/Salix_example/Galler_Parasitoid/distfigure_MLEs.tsv',sep='\t')
+# write.table(xdata,file='../../data/Salix_example/Zillis/Galler_Parasitoid/distfigure_xvals.tsv',sep='\t')
+# write.table(ydata,file='../../data/Salix_example/Zillis/Galler_Parasitoid/distfigure_yvals.tsv',sep='\t')
+# write.table(MLEs,file='../../data/Salix_example/Zillis/Galler_Parasitoid/distfigure_MLEs.tsv',sep='\t')
 
 
 import sys
@@ -173,13 +173,19 @@ grace.set_label_scheme('dummy')
 
 for nettype in ['SG','GP']:
   if nettype=='SG':
-    xdata=read_Rfiles('../../data/Salix_example/Salix_Galler/distfigure_xvals.tsv')
[…]

### 2018-03-06 code/figure_generation/samples_for_thresholds.py

@@ -35,8 +35,8 @@
 #   }
 # # }
 
-# write.table(samples,file='../../data/Salix_example/Salix_Galler/samples_for_threshold.tsv',sep='\t')
-# write.table(CDFs,file='../../data/Salix_example/Salix_Galler/samplefigure.tsv',sep='\t')
+# write.table(samples,file='../../data/Salix_example/Zillis/Salix_Galler/samples_for_threshold.tsv',sep='\t')
+# write.table(CDFs,file='../../data/Salix_example/Zillis/Salix_Galler/samplefigure.tsv',sep='\t')
 
 
 # # Galler-parasitoid stuff
@@ -77,8 +77,8 @@
 #   }
 # }
 
-# write.table(gp_samples,file='../../data/Salix_example/Galler_Parasitoid/samples_for_threshold.tsv',sep='\t')
-# write.table(gp_CDFs,file='../../data/Salix_example/Galler_Parasitoid/samplefigure.tsv',sep='\t')
+# write.table(gp_samples,file='../../data/Salix_example/Zillis/Galler_Parasitoid/samples_for_threshold.tsv',sep='\t')
+# write.table(gp_CDFs,file='../../data/Salix_example/Zillis/Galler_Parasitoid/samplefigure.tsv',sep='\t')
 
 import sys
 import math
@@ -244,9 +244,11 @@ grace=MultiPanelGrace(colors=colors)
 
 for nettype in ['SG','GP']:
   if nettype=='SG':
-    datadict,sampledict=read_Rfiles('../../data/Salix_example/Salix_Galler/samplefigure.tsv',nettype)
+    # datadict,sampledict=read_Rfiles('../../data/Salix_example/Salix_Galler/samplefigure.tsv',nettype)
+    datadict,sampledict=read_Rfiles('../../data/Salix_example/Zillis/Salix_Galler/samplefigure.tsv',nettype)
   else:
-    datadict,sampledict=read_Rfiles('../../data/Salix_example/Galler_Parasitoid/samplefigure.tsv',nettype)    
+    # datadict,sampledict=read_Rfiles('../../data/Salix_example/Galler_Parasitoid/samplefigure.tsv',nettype)    
+    datadict,sampledict=read_Rfiles('../../data/Salix_example/Zillis/Galler_Parasitoid/samplefigure.tsv',nettype)    
 
   datasets=combiner(datadict)
 
[…]

### 2018-03-07 code/figure_generation/pdfs_and_N.py
updated pdf figure

@@ -1,4 +1,4 @@
-####### R code to generate data files:
+# ###### R code to generate data files:
 # Getting distributions:
 # xdata=matrix(ncol=1001,nrow=12)
 # ydata=matrix(ncol=1001,nrow=12)
@@ -6,6 +6,7 @@
 # ns=as.vector(c(0,5,10,15,20,25,50,100,150,200,300,374))
 # for(i in 1:length(ns)){
 #   n=ns[i]
+#   print(n)
 #   dist=calculate_distribution(calculate_parameters(sg_int_probs,n,0))
 #   x=seq(-5,5,length=1000)*sqrt(dist[[2]])+dist[[1]]
 #   hx=dnorm(x,dist[[1]],sqrt(dist[[2]]))
@@ -117,23 +118,29 @@ def format_graph(graph,nettype):
   graph.xaxis.bar.linewidth=1
   graph.frame.linewidth=1
   graph.world.xmin=0
-  graph.world.xmax=.6
+  if nettype=='SG':
+    graph.world.xmax=.1
+    major=.02
+  else:
+    graph.world.xmax=.3000001
+    major=.05
   graph.world.ymin=-0
-  graph.world.ymax=46
+  graph.world.ymax=72
 
   graph.yaxis.tick.configure(major=50,onoff='off',minor_ticks=0,major_size=.7,minor_size=.5,place='both',major_linewidth=1,minor_linewidth=1)
   graph.yaxis.ticklabel.configure(char_size=0,format='decimal',prec=0)
 
-  graph.xaxis.tick.configure(major=.1,onoff='on',minor_ticks=0,major_size=.5,place='both',minor_size=.5,major_linewidth=1,minor_linewidth=1)
-  graph.xaxis.ticklabel.configure(char_size=.75,format='decimal',prec=1)
+
+  graph.xaxis.tick.configure(major=major,onoff='on',minor_ticks=0,major_size=.5,place='both',minor_size=.5,major_linewidth=1,minor_linewidth=1)
+  graph.xaxis.ticklabel.configure(char_size=.75,format='decimal',prec=2)
 
   graph.xaxis.label.configure(text="Probability of interaction",char_size=1,just=2,place='normal')
   graph.yaxis.label.configure(text="Probability density",char_size=1,just=2)
   graph.legend.configure(box_linestyle=0,fill=0,fill_pattern=0,char_size=.75,
[…]

### 2018-03-07 manuscript/CI_interactions.tex
There, now just need to add posterior property results

@@
 We may therefore be 95\% confident that the interaction probability for \emph{Salix} and galler species that have not been observed cooccurring is below 0.05.
-To be 95\% confident that the interaction probability for these species is below 0.01 would require 139 observed co-occurrences with no interaction.
+As the peak of the prior distribution for the probability of interaction between \emph{Salix} and galler probabilities is around 0.02 (Fig.~\ref{salix_pdfs}), to be 95\% confident that the interaction probability for these species is below 0.01 would require 1029 observed co-occurrences with no interaction - far more than the number of sites in the~\citep{Kopelke2017} dataset.
 
@@
 The 95\% credible interval is (0.0005, 0.303) for the probability of interaction between two species observed to co-occur but never interact.
-To be 95\% confident that the probability of interaction is below 0.1, 0.05, or 0.001 would require 15, 39, and 229 observed co-occurrances, respectively.
+To be 95\% confident that the probability of interaction is below 0.1, 0.05, or 0.01 would require 15, 39, and 229 observed co-occurrances, respectively.
 
@@
         \label{Salix_pdfs}
-        \includegraphics*[width=.8\textwidth]{figures/Salix_Galler_pdfs_increasing_N.eps}
+        \includegraphics*[width=.8\textwidth]{figures/Salix_Galler_pdfs_increasing_N_Zillis.eps}
         \end{figure}
@@
         \label{Salix_cdfs}
-        \includegraphics[width=.8\textwidth]{figures/Salix_Galler_samples_and_cdfs.eps}
+        \includegraphics[width=.8\textwidth]{figures/Salix_Galler_samples_and_cdfs_Zillis.eps}
 

### 2018-03-07 code/Zillis_prior/calculating_prior_distributions.R

@@ -1,7 +1,8 @@
 source('../handy_R_functions.R')
 
 # To create the data file:
-for(subweb in  c('Zillis','Zillertal')){
+subweb="Zillis"
+# for(subweb in  c('Zillis','Zillertal')){
   SG_dataset=read.csv('../../data/Salix_example/cooccur_interact_galler_salix.csv',row.names=1)
   SG_web=read.csv(paste0('../../data/Salix_example/Zillis/',subweb,'_SG_prior.csv',sep=''),row.names=1)
   deg_dist_Salix=rowSums(SG_web)/ncol(SG_web)
@@ -37,5 +38,5 @@ for(subweb in  c('Zillis','Zillertal')){
   }
   write.table(GP_dataset,file=paste0('../../data/Salix_example/Zillis/Galler_Parasitoid/posterior_probabilities_',subweb,'.tsv',sep=''))
 
-}
+# }
 

### 2018-03-07 code/figure_generation/pdfs_and_N.py

@@ -146,10 +146,12 @@ def format_graph(graph,nettype):
   return graph
 
 def populate_graph(graph,pointdict,MLEdict,nettype):
-  cols=[2,3,5,9,10,11]
+  # cols=[2,3,5,9,10,11]
+  cols=[11,9,7,5,3,2]
   x=0
   y=0
-  for N in [0,5,10,20,50,100]:
+  # for N in [0,5,10,20,50,100]:
+  for N in [100,50,20,10,5,0]:
     data=graph.add_dataset(pointdict[N])
     data.symbol.shape=0
     data.line.configure(linewidth=1,linestyle=1,color=cols[x])
@@ -161,11 +163,11 @@ def populate_graph(graph,pointdict,MLEdict,nettype):
     lower=MLEdict[N][1]
     upper=MLEdict[N][2]
 
-    MLEline=graph.add_dataset([(lower,graph.world.ymax-14+y),(upper,graph.world.ymax-14+y)])
+    MLEline=graph.add_dataset([(lower,graph.world.ymax-4-y),(upper,graph.world.ymax-4-y)])
     MLEline.symbol.shape=0
     MLEline.line.configure(linestyle=1,color=cols[x],linewidth=3)
 
-    MLEdot=graph.add_dataset([(MLE,graph.world.ymax-14+y)])
+    MLEdot=graph.add_dataset([(MLE,graph.world.ymax-4-y)])
     MLEdot.line.linestyle=0
     MLEdot.symbol.configure(shape=3,color=1,fill_color=cols[x],size=.75)
 

### 2018-03-07 code/figure_generation/samples_for_thresholds.py

@@ -1,39 +1,33 @@
-# ######### R code to generate data files:
-# # % Getting cdfs:
-# pars=calculate_parameters(int_probs,0,0)
-# n=seq(0,500,1)
+# ######## R code to generate data files:
+# % Getting cdfs:
+# pars=calculate_parameters(sg_int_probs,0,0)
+# n=seq(0,2000,1)
 
-# CDFs=matrix(nrow=4,ncol=502)
+# CDFs=matrix(nrow=3,ncol=2002)
 # colnames(CDFs)=c("Threshold",n)
 # r=1
-# for(threshold in c(0.5,0.25,0.1,0.05)){
-#   # for(confidence in c(0.9,0.95,0.975)){
+# for(threshold in c(0.1,0.05,0.01)){
 #     cdf=pbeta(threshold,shape1=pars[[1]],shape2=pars[[2]]+n)
-#     # samples=length(which(cdf<confidence))
 #     CDFs[r,1]=threshold
-#     # CDFs[r,2]=confidence
-#     # CDFs[r,3]=samples
-#     CDFs[r,2:502]=cdf
+#     CDFs[r,2:2002]=cdf
 #     print(r)
 #     r=r+1
-#   }
-# # }
+# }
 
 
-# samples=matrix(nrow=12,ncol=3)
+# samples=matrix(nrow=9,ncol=3)
 # colnames(samples)=c("Threshold","Confidence","Samples")
 # r=1
-# for(threshold in c(0.5,0.25,0.1,0.05)){
+# for(threshold in c(0.1,0.05,0.01)){
 #   for(confidence in c(0.9,0.95,0.975)){
-#     cdf=pbeta(threshold,shape1=pars[[1]],shape2=pars[[2]]+n)
-#     n_obs=length(which(cdf<confidence))
+#     n_obs=samples_for_threshold(threshold,confidence,pars)
 #     samples[r,1]=threshold
 #     samples[r,2]=confidence
 #     samples[r,3]=n_obs
 #     print(r)
 #     r=r+1
 #   }
-# # }
+# }
 
 # write.table(samples,file='../../data/Salix_example/Zillis/Salix_Galler/samples_for_threshold.tsv',sep='\t')
 # write.table(CDFs,file='../../data/Salix_example/Zillis/Salix_Galler/samplefigure.tsv',sep='\t')
@@ -45,16 +39,12 @@
[…]

### 2018-03-07 code/handy_R_functions.R

@@ -18,8 +18,8 @@ calculate_parameters<-function(priordata,n,k){
 # Returns maximum likelihood estimator for interaction probability
 # Based on parameters returned by calculate_parameters
 calculate_mean_MLE<-function(priordata,n,k){
-  library(MASS)
-  pars=fitdistr(x=priordata,"beta",start=list(shape1=1,shape2=1),lower=c(0,0))$estimate
+  library(fitdistrplus)
+  pars=fitdist(priordata,distr="beta",method="mle",start=list(shape1=10,shape2=10),lower=c(0,0))$estimate
   # The lower=c(0,0) prevents R from fitting invalid (negative) parameters
   alpha=pars[[1]]
   beta=pars[[2]]
@@ -69,7 +69,7 @@ credible_interval<-function(pars,p_lower,p_upper){
 samples_for_threshold<-function(threshold,confidence,pars){
   alpha=pars[[1]]
   beta=pars[[2]]
-  n=seq(0,1000,1)
+  n=seq(0,4000,1)
   k=0
   cdf=pbeta(threshold,shape1=alpha,shape2=beta+n)
   samples=length(which(cdf<confidence))

### 2018-03-08 manuscript/CI_interactions.tex
think everything is in the SI now, may need to shorten

@@
   \subsection*{Scaling up to network metrics}
-  [[Haven't added NODF or checked this yet.]]
 
@@
 
-    We find, perhaps not surprisingly, that the posterior webs for the Salix-galler network all had much higher connectance than the original, observed web (C=0.028 for the observed web and 0.528$\leq$C$\leq$0.568 for the posterior webs; Fig.~\ref{posterior_webs}A).
-Likewise, the number of links per \emph{Salix} and galler species in the observed web ($L_{\emph{Salix}}$=2.71 and $L_{galler}$=1.47, respectively) were much lower than those predicted in the posterior webs (27.4$\leq L_{\emph{Salix}} \leq$29.5 and 50.6$\leq L_{galler} \leq $54.5, respectively; Fig.~\ref{posterior_webs}C,E), even when filtering with a detection probability of only 50\%.
-There are two possible explanations for this discrepancy: either the data of~\citet{Barbour2016} is simply too different from that of~\citet{Kopelke2017} to offer an appropriate prior for our dataset, or the true detection probability for links between \emph{Salix} and galler species is much less than 50\%.
-As the scale of the two datasets is quite different (genotypes of a single \emph{Salix} species in~\citet{Barbour2016}, various \emph{Salix} species in our dataset), we suspect the former is more likely.
+    We find, perhaps not surprisingly, that the posterior webs for the Salix-galler network  had higher connectances than the original, observed web (C=0.028 for the observed web and 0.082$\leq$C$\leq$0.096 for the posterior webs; Fig.~\ref{posterior_webs}A).
+The number of links per \emph{Salix} species in the observed web ($L_{\emph{Salix}}$=2.71 was similar to those in the posterior webs (2.53$\leq L_{\emph{Salix}} \leq$3.19; Fig~\ref{posterior_webs}C).
+The number of links per galler, however, was lower in the observed web ($L_{galler}$=1.47) than in the posterior webs, accounting for the increased connectance (4.67$\leq L_{galler} \leq $5.88; Fig.~\ref{posterior_webs}E).
+There was a more substantial difference in the nestedness of the observed and posterior webs: the observed network had NODF=0.560 while the posterior networks were more nested (1.39 $\leq NODF \leq$1.94).
+Even the networks sampled with a detection filter of 50\% had non-zero nestedness (Fig.~\ref{posterior_webs}G).
+This last result highlights the potential for the possibility for network structure to vary when considering the possibility that unobserved species pairs may interact.
+
 %    [[This is a little boring. Tomas has ideas for people with potentially better priors - may require another co-author. Also maybe could use one site as a prior like ``training data"?]]
@@
 %%AE: If we are doing a complement here (I agree it is a bit boring) I think option c) from Alyssas mail is the most straight forward option. 
+% AC: Added nestedness and replaced the Barbour data with training data from one site. Couldn't find any good published data.
 
-    Considering the galler-natural enemy networks, the connectance, mean links per galler, and mean links per natural enemy were also much lower in the observed web (C=0.078, $L_{galler}$=9.99, and $L_{natural enemy}$=7.45, respectively) than in the posterior webs (0.183$\leq$ C $\leq$ 0.196, 17.5 $\leq L_{galler} \leq$ 18.9, and 23.0 $\leq L_{natural enemy} \leq$ 24.8).
+    Considering the galler-natural enemy networks, the connectance, mean links per galler, and mean links per natural enemy were also much lower in the observed web (C=0.078, $L_{galler}$=9.99, and $L_{natural enemy}$=7.45, respectively) than in the posterior webs (0.186$\leq$ C $\leq$ 0.198, 13.4 $\leq L_{galler} \leq$ 14.6, and 23.4 $\leq L_{natural enemy} \leq$ 25.0).
 When the detection probability was relatively low (i.e., 50\%), however, the properties of randomised networks became similar to those in the observed webs (Fig.~\ref{posterior_webs}B,D,F).
-The~\citet{Barbour2016} network likely provides a better prior here than for the \emph{Salix}-galler networks, as both networks included different galler and natural enemy species.
-Although the two networks differ vastly in scale, and the inclusion of multiple \emph{Salix} species likely causes structural differences from~\citet{Barbour2016} despite the similar resolution of gallers and natural enemies, this result nevertheless suggests that even such a large and well-replicated network as that in~\citet{Kopelke2017} is missing many interactions.
-This should be a strong warning to researchers comparing structural characteristics between networks - small structural differences are likely to be masked by substantial noise resulting from sampling uncertainty.
+Nestedness was higher in the observed network (NODF=6.85) than in the posterior webs (6.31 $\leq NODF \leq$ 6.82; Fig.~\ref{posterior_webs}H); in this case, the stronger the detection filter the farther apart were the observed and posterior webs.
 

### 2018-03-08 manuscript/supplemental.tex
think everything is in the SI now, may need to shorten

@@
 
+      We find, perhaps not surprisingly, that the posterior webs for the Salix-galler network all had much higher connectance than the original, observed web (C=0.028 for the observed web and 0.528$\leq$C$\leq$0.568 for the posterior webs; Fig.~\ref{posterior_webs}A).
+Likewise, the number of links per \emph{Salix} and galler species in the observed web ($L_{\emph{Salix}}$=2.71 and $L_{galler}$=1.47, respectively) were much lower than those predicted in the posterior webs (27.4$\leq L_{\emph{Salix}} \leq$29.5 and 50.6$\leq L_{galler} \leq $54.5, respectively; Fig.~\ref{posterior_webs}C,E), even when filtering with a detection probability of only 50\%.
+Nestedness was also much higher in the posterior networks (14.2 $\leq NODF \leq$ 15.4; Fig.~\ref{posterior_webs}G) than in the observed network (NODF=0.560).
+There are two possible explanations for these discrepancies: either the data of~\citet{Barbour2016} is simply too different from that of~\citet{Kopelke2017} to offer an appropriate prior for our dataset, or the true detection probability for links between \emph{Salix} and galler species is much less than 50\%.
+As the scale of the two datasets is quite different (genotypes of a single \emph{Salix} species in~\citet{Barbour2016}, various \emph{Salix} species in our dataset), we suspect the former is more likely.
+
+      Considering the galler-natural enemy networks, the connectance, mean links per galler, and mean links per natural enemy were also much lower in the observed web (C=0.078, $L_{galler}$=9.99, and $L_{natural enemy}$=7.45, respectively) than in the posterior webs (0.183$\leq$ C $\leq$ 0.196, 17.5 $\leq L_{galler} \leq$ 18.9, and 23.0 $\leq L_{natural enemy} \leq$ 24.8).
+When the detection probability was relatively low (i.e., 50\%), however, the properties of randomised networks became similar to those in the observed webs (Fig.~\ref{posterior_webs}B,D,F).
+Nestedness was higher in the observed network (NODF=6.85) than in the posterior networks (6.30 $\leq NODF \leq$ 6.74; Fig.~\ref{posterior_webs}H), but network structure was much more similar in the observed and posterior galler-natural enemy networks than in the \emph{Salix}-galler networks.
+The~\citet{Barbour2016} network likely provides a better prior here than for the \emph{Salix}-galler networks, as both networks included different galler and natural enemy species.
+Although the two networks differ vastly in scale, and the inclusion of multiple \emph{Salix} species likely causes structural differences from~\citet{Barbour2016} despite the similar resolution of gallers and natural enemies, this result nevertheless suggests that even such a large and well-replicated network as that in~\citet{Kopelke2017} is missing many interactions.
+This should be a strong warning to researchers comparing structural characteristics between networks - small structural differences are likely to be masked by substantial noise resulting from sampling uncertainty.
+
+      \begin{figure}[ht]
+        \caption{Using prior distribution based on the \emph{Salix}-galler and galler-natural enemy networks in~\citet{Barbour2016}, we can calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting.
+Here we show posterior distributions for each $\lambda$ in each network ranging from the prior distribution ($n=0$ observed co-occurrence) to the distribution obtained when the pair of species has been observed co-occurring 100 times.
+The distribution narrows and approaches zero as the sample size increases.
+Likewise, the maximum likelihood estimator for the mean probability of interaction (diamonds at top of each panel) approaches zero and the 95\% credible interval (lines at top of each panel) narrows as sample size increases.
+\textbf{A)} The posterior distributions for the \emph{Salix}-galler component are always wider and farther from zero than those for \textbf{B)} the galler-natural enemy component.
+This is likely because the prior distribution for the galler-natural enemy component of the network was both narrower and had a mean closer to that in the~\citet{Kopelke2017} data than did the \emph{Salix}-galler component.}
+        \label{Salix_pdfs}
+        \includegraphics*[width=.8\textwidth]{figures/Salix_Galler_pdfs_increasing_N.eps}
+        \end{figure}
+
+      \begin{figure}[ht]
+        \caption{The number of samples required to achieve a given level of confidence that an interaction probability $\lambda_{ij}$ is below a given threshold varies with both parameters.
+With a low threshold, our confidence that $\lambda_{ij}$ is below the threshold increases rapidly with repeated observation of co-occurrence without interaction.
+Here we show the cumulative density functions for threshold probabilities of 0.5 (solid line), 0.25 (dashed line), 0.1 (dash-dot line), and 0.05 (dotted line) as well as the points at which the cdf reaches 0.90 (orange square), 0.95 (red circle), and 0.975 (blue diamond) for each threshold value.
+The large ticks along the x-axis indicate the number of samples associated with each of these points.
+Note that the number of samples required to reach any given threshold is larger for \textbf{A)} the \emph{Salix}-galler network than for \textbf{B)} the galler-natural enemy network.
+In the galler-natural enemy network, the credible interval for a pair of species with no observed co-occurrances was 0.364.
+All pairs of species therefore have $\lambda$\textless0.5.}
+        \label{Salix_cdfs}
+        \includegraphics[width=.8\textwidth]{figures/Salix_Galler_samples_and_cdfs.eps}
+
+        \end{figure}
+
+      \begin{figure}[ht]
+      \caption{Here we show the mean connectance, links per resource (\emph{Salix} in the \emph{Salix}-galler networks and gallers in the galler-natural enemy networks), and links per consumer for networks assembled using posterior distributions based on a smaller, North American \emph{Salix}-galler-natural enemy system~\citep{Barbour2016,Barbour2016Dryad}.
+We created 100 ``posterior-sampling" networks and then, for each of these, created 100 ``detection-filter" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network.
+This simulates imperfect detection of interactions in the field.
+Each point represents the mean network property (e.g., connectance) obtained from a set of 100 detection-filter networks, plotted against the value of the network property in the posterior-sampling network used to create the detection-filter networks.
+For each property and both network types, the posterior-sampling networks cover a relatively small range of network properties than the range covered by networks with varying detection probabilities.
+The value of each property decreases with the proportion of links included in the detection-filter networks.}
+      \label{posterior_webs}    
+      \includegraphics[width=.8\textwidth]{Figures/Salix_Galler_posterior_properties.eps}
+      \end{figure}
+
     \bibliographystyle{ecollett} 

### 2018-03-08 code/figure_generation/Zillis_posterior_plots.py

@@ -22,6 +22,9 @@ colors=ColorBrewerScheme('Blues')  # The blue is very beautiful but maybe harder
 colors.add_color(130,20,20,'red')
 # colors.add_color(120,120,120,'grey')
 
+obsvals={'SG':{'C':0.028,'LS':2.71,'LG':1.47,'NODF':0.5600535},
+'GP':{'C':0.078,'LS':9.99,'LG':7.45,'NODF':6.853653}}
+
 def read_summary_file(filename):
   whiskers={0.5:[],0.6:[],0.7:[],0.8:[],0.9:[],0.95:[],0.99:[]}
   obs={0.5:[],0.6:[],0.7:[],0.8:[],0.9:[],0.95:[],0.99:[]}
@@ -65,7 +68,6 @@ def read_NODF_file(filename):
       whiskers[proportion].append(sample_mean)
   f.close()
   return whiskers, obs
-
 
 def mean_calculator(listdict):
   dots=[]
@@ -138,6 +140,7 @@ def Zillertal_yaxes(prop,graph):
   graph.yaxis.label.configure(text=ytext,char_size=1,just=2)
 
   return graph
+
 def format_graph(graph,prop,nettype,site):
   graph.yaxis.bar.linewidth=1
   graph.xaxis.bar.linewidth=1
@@ -173,7 +176,7 @@ def format_graph(graph,prop,nettype,site):
       ytext="NODF"
     graph.yaxis.label.configure(text=ytext,char_size=1,just=2)
   graph.legend.configure(box_linestyle=0,fill=0,fill_pattern=0,char_size=.5,
-    loc=(0.625,3),loctype='world')
+    loc=(0.635,3.8),loctype='world')
   graph.panel_label.configure(placement='iul',char_size=.75,dx=.02,dy=.01)
   if prop=='C' and nettype=='SG':
     graph.xaxis.label.configure(text='Salix-Galler',place='opposite',char_size=1.25,just=2,loctype='world')
@@ -183,6 +186,11 @@ def format_graph(graph,prop,nettype,site):
   return graph
 
 def populate_graph(graph,prop,nettype,obs,whiskers):
+  obsval=obsvals[nettype][prop]
+  obsline=graph.add_dataset([(-1,obsval),(1,obsval)])
+  obsline.symbol.shape=0
+  obsline.line.configure(linestyle=2,linewidth=2,color='red')
+
   maxdots,meandots,mindots=obs_breaker(obs)
[…]

### 2018-03-08 code/figure_generation/posterior_property_dotplot.py

@@ -22,6 +22,10 @@ colors=ColorBrewerScheme('Blues')  # The blue is very beautiful but maybe harder
 colors.add_color(130,20,20,'red')
 # colors.add_color(120,120,120,'grey')
 
+obsvals={'SG':{'C':0.028,'LS':2.71,'LG':1.47,'NODF':0.5600535},
+'GP':{'C':0.078,'LS':9.99,'LG':7.45,'NODF':6.853653}}
+
+
 def read_summary_file(filename):
   whiskers={0.5:[],0.6:[],0.7:[],0.8:[],0.9:[],0.95:[],0.99:[]}
   obs={0.5:[],0.6:[],0.7:[],0.8:[],0.9:[],0.95:[],0.99:[]}
@@ -66,7 +70,6 @@ def read_NODF_file(filename):
   f.close()
   return whiskers, obs
 
-
 def mean_calculator(listdict):
   dots=[]
   for prop in listdict:
@@ -103,34 +106,34 @@ def format_graph(graph,prop,nettype):
   if prop=='C':
     if nettype=='SG':
       graph.world.ymin=0.20
-      graph.world.ymax=0.6500000000001
-      graph.yaxis.tick.configure(major=0.1,onoff='on',minor_ticks=1,major_size=.5,place='normal',minor_size=.3,major_linewidth=1,minor_linewidth=1)
+      graph.world.ymax=0.700000000001
+      graph.yaxis.tick.configure(major=0.2,onoff='on',minor_ticks=1,major_size=.5,place='normal',minor_size=.3,major_linewidth=1,minor_linewidth=1)
       graph.yaxis.ticklabel.configure(char_size=.75,format='decimal',prec=1)
     else:
       graph.world.ymin=0.075
-      graph.world.ymax=0.225
-      graph.yaxis.tick.configure(major=0.05,onoff='on',minor_ticks=1,major_size=.5,place='normal',minor_size=.3,major_linewidth=1,minor_linewidth=1)
-      graph.yaxis.ticklabel.configure(char_size=.75,format='decimal',prec=2)
+      graph.world.ymax=0.25
+      graph.yaxis.tick.configure(major=0.1,onoff='on',minor_ticks=1,major_size=.5,place='normal',minor_size=.3,major_linewidth=1,minor_linewidth=1)
+      graph.yaxis.ticklabel.configure(char_size=.75,format='decimal',prec=1)
     ytext="Connectance"
   elif prop=='LS':
     if nettype=='SG':
       graph.world.ymin=12
[…]

### 2018-03-08 manuscript/CI_interactions.tex
figure tweaking still

@@
 Suppose we have $n = 10$ observations of co-occurrence between species $i$ and species $j$ in a given time interval and area, and $k = 3$ observations of interactions.
-The maximum likelihood estimate of the interaction probability (Box~\ref{Box2}) is simply $\lambda_{MLE} = 3/10 = 0.3$.
+The maximum likelihood estimate of the interaction probability (Box~\ref{box2}) is simply $\lambda_{MLE} = 3/10 = 0.3$.
 
@@
 We may therefore be 95\% confident that the interaction probability for \emph{Salix} and galler species that have not been observed cooccurring is below 0.05.
-As the peak of the prior distribution for the probability of interaction between \emph{Salix} and galler probabilities is around 0.02 (Fig.~\ref{salix_pdfs}), to be 95\% confident that the interaction probability for these species is below 0.01 would require 1029 observed co-occurrences with no interaction - far more than the number of sites in the~\citep{Kopelke2017} dataset.
+As the peak of the prior distribution for the probability of interaction between \emph{Salix} and galler probabilities is around 0.02 (Fig.~\ref{Salix_pdfs}), to be 95\% confident that the interaction probability for these species is below 0.01 would require 1029 observed co-occurrences with no interaction - far more than the number of sites in the~\citep{Kopelke2017} dataset.
 
@@
     \indent We may begin by comparing the frequency of co-occurences for pairs of species in each part of the network to reveal the challenge of having sufficient sampling to be confident that an interaction does not occur.
-Most pairs of species (3986/4992 \emph{Salix}-galler pairs and  9794/12096 galler-natural enemy pairs) are never found co-occurring and, even for species that did occur, the total number of co-occurrences was generally low (mean=4.24, variance=36.3 for \emph{Salix}-galler pairs; mean=3.87, variance=28.8 for galler-natural enemy pairs; Fig.~\ref{histograms}A-B).
+Most pairs of species (3,986/4,992 \emph{Salix}-galler pairs and  9,794/12,096 galler-natural enemy pairs) are never found co-occurring and, for species that did occur together, the total number of co-occurrences was generally low (mean=4.24, variance=36.3 for \emph{Salix}-galler pairs; mean=3.87, variance=28.8 for galler-natural enemy pairs; Fig.~\ref{histograms}A-B).
 The bulk of these co-occurring species pairs were never observed to interact: only 2.82\% of \emph{Salix}-galler pairs and 7.76\% of galler-natural enemy pairs were observed interacting at one or more sites.
@@
 Thus, even in the most extensive data set that we could find, there was very little empirical data for each species pair.
-This suggests that limited sampling is a major source of uncertainty.
-This dataset also illustrates the potential for increased sampling to not necessarily reveal more interactions as a pair of species that interacts in some cases may not be observed interacting in all cases (Fig.~\ref{histograms}E-F).
+This suggests that limited sampling is a major source of uncertainty in all empirical networks.
+This dataset also illustrates the potential for increased sampling to not necessarily reveal more interactions as a pair of species that is able to interact may not be observed interacting in all samples where the pair co-occurrs (Fig.~\ref{histograms}E-F).
   \caption{\emph{Salix} dataset}
@@
 In the table below, we present the 95\% credible intervals for \emph{Salix}-galler and galler-natural enemy paris with different numbers of observed co-occurrences ($n$) and no observed interactions ($k=0$).
-Both sets of intervals rely on prior information from the network in~\citet{Barbour2016,Barbour2016Dryad}.
+Both sets of intervals rely on prior information derived from the Zillis subweb~\citep{Kopelke2017}.
 
-      % # R code to make the table:
+      % % # R code to make the table:
+      % ns=c(0,1,2,5,10,15,20,25,50,100,150,200,374)
       % output=matrix(nrow=length(ns),ncol=5)
-      % ns=c(0,1,2,5,10,15,20,25,50,100,150,200,374)
       % output[,1]=ns
@@
         \multirow{2}{*}{$n$} & \multicolumn{2}{c}{\emph{Salix}-galler} & \multicolumn{2}{c}{galler-natural enemy}\\
-         & Lower bound & Upper bound \\
+         & Lower bound & Upper bound & Lower bound & Upper bound \\
         \hline
-        0   & 0.152 & 0.931 & 0.008 & 0.364 \\
-        1   & 0.110 & 0.843 & 0.007 & 0.337 \\
-        2   & 0.087 & 0.760 & 0.006 & 0.313 \\
-        5   & 0.053 & 0.573 & 0.005 & 0.258 \\
-        10  & 0.033 & 0.400 & 0.004 & 0.200 \\
-        15  & 0.023 & 0.306 & 0.003 & 0.163 \\
-        20  & 0.018 & 0.247 & 0.003 & 0.137 \\
-        25  & 0.015 & 0.208 & 0.002 & 0.119 \\
-        50  & 0.008 & 0.115 & 0.001 & 0.071 \\
-        100 & 0.004 & 0.061 & 0.001 & 0.039 \\
-        150 & 0.003 & 0.041 & \textless0.001 & 0.027 \\
-        200 & 0.002 & 0.031 & \textless0.001 & 0.021 \\
+        0   & 0.013 & 0.049 & 5.39 $\times10^{-4}$ & 0.304 \\
+        1   & 0.013 & 0.048 & 4.82 $\times10^{-4}$ & 0.276 \\
+        2   & 0.013 & 0.048 & 4.35 $\times10^{-4}$ & 0.253 \\
+        5   & 0.012 & 0.048 & 3.37 $\times10^{-4}$ & 0.203 \\
+        10  & 0.012 & 0.047 & 2.45 $\times10^{-4}$ & 0.152 \\
+        15  & 0.012 & 0.046 & 1.93 $\times10^{-4}$ & 0.121 \\
+        20  & 0.012 & 0.046 & 1.59 $\times10^{-4}$ & 0.101 \\
+        25  & 0.012 & 0.045 & 1.35 $\times10^{-4}$ & 0.087 \\
+        50  & 0.011 & 0.042 & 7.72 $\times10^{-5}$ & 0.050 \\
+        100 & 0.010 & 0.037 & 4.16 $\times10^{-5}$ & 0.027 \\
+        150 & 0.009 & 0.033 & 2.84 $\times10^{-5}$ & 0.019 \\
+        200 & 0.008 & 0.030 & 2.16 $\times10^{-5}$ & 0.014 \\
         \hline
-        374 & 0.001 & 0.017 & \textless0.001 & 0.011 \\
+        374 & 0.006 & 0.022 & 1.18 $\times10^{-5}$ & 0.008 \\
         \hline
@@
 Here we show a histogram of the number of observed interactions within pairs of co-occurring species.
+Species which co-occurred but never interacted are included in these histograms.
 \textbf{E-F)} Here we show, for each species pair, the number of observed interactions plotted against the number of observed co-occurrences.
@@
   \begin{figure}[h!]
-    \caption{A simple example will illustrate the problem of imperfect detection of interactions (the full reasoning is provided below).
+    \caption{A simple example will illustrate the problem of imperfect detection of interactions.
 Assume that we want to infer the probability of an interaction between two species, $i$ and $j$.
 Now assume that in reality, interaction between $i$ and $j$ is completely impossible (i.e.
-the true $\lambda=0$), but the observer does not know this and seeks to estimate this interaction probability ($\lambda$).
-The number of observed interactions will follow a binomial distribution, with number of interactions $k$ and number of observations $n$.
+the true $\lambda=0$) but the observer does not know this and seeks to estimate this interaction probability ($\lambda$).
+The number of observed interactions will follow a binomial distribution with number of interactions $k$ and number of observations $n$.
 Using this distribution, we can compute the credible interval of the estimated probability $\lambda$.
-Assuming no added detection error in observing the incidence of the interaction, a single observation of species co-occurrence will reveal very little regarding the probability of the interaction as the credible interval for a pair of species with one observation essentially spans from 0 to 1.
-Only with thirty observations will the upper limit of the credible interval be lowered to 0.1.
-Thus, adding more observations is certainly useful in controlling uncertainty, but the number of observations nonetheless needs to be very high.
+Even assuming no added detection error in observing the incidence of the interaction, a single observation of species co-occurrence reveals very little regarding the probability of the interaction as the credible interval for a pair of species with one observation essentially spans from 0 to 1.
+Only with about 35 observations will the upper limit of the credible interval be lowered to 0.1.
+Thus, adding more observations is certainly useful in controlling uncertainty, but the number of observations added needs to be very high.
 Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true credible interval for $\lambda$ when $k=0$ ($i$ and $j$ have not been observed interacting) for a variety of $n$ (observed co-occurences of $i$ and $j$).
-A threshold interaction probability of 0.1 is indicated by the dotted red line.
+A threshold interaction probability of 0.1 is indicated by the dashed red line.
 }
@@
 %DG: otherwise the difference between the two interaction types is very interesting and useful to show the effect of the priors. Bravo !
-[[Update these two figs with Zillis data.]]
+
       \begin{figure}[ht]
-        \caption{Using prior distribution based on the \emph{Salix}-galler and galler-natural enemy networks in~\citet{Barbour2016}, we can calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting.
-Here we show posterior distributions for each $\lambda$ in each network ranging from the prior distribution ($n=0$ observed co-occurrence) to the distribution obtained when the pair of species has been observed co-occurring 100 times.
+        \caption{Using prior distribution based on the \emph{Salix}-galler and galler-natural enemy networks sampled at a single site in~\citet{Kopelke2017}, we can calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting.
+Here we show posterior distributions for $\lambda$ in each network component ranging from the prior distribution ($n=0$ observed co-occurrence) to the distribution obtained when the pair of species has been observed co-occurring 100 times.
 The distribution narrows and approaches zero as the sample size increases.
 Likewise, the maximum likelihood estimator for the mean probability of interaction (diamonds at top of each panel) approaches zero and the 95\% credible interval (lines at top of each panel) narrows as sample size increases.
-\textbf{A)} The posterior distributions for the \emph{Salix}-galler component are always wider and farther from zero than those for \textbf{B)} the galler-natural enemy component.
-This is likely because the prior distribution for the galler-natural enemy component of the network was both narrower and had a mean closer to that in the~\citet{Kopelke2017} data than did the \emph{Salix}-galler component.}
+\textbf{A)} The posterior distributions for $\lambda$ in the \emph{Salix}-galler component are narrower at low $n$ but shrink less with increased sampling than those for \textbf{B)} the distributions of $\lambda$ in the galler-natural enemy component.}
         \label{Salix_pdfs}
@@
         \end{figure}
-
-    % \begin{figure}[ht]
-    % \caption{Here we show the mean connectance, links per resource (\emph{Salix} in the \emph{Salix}-galler networks and gallers in the galler-natural enemy networks), and links per consumer for networks assembled using posterior distributions based on a smaller, North American \emph{Salix}-galler-natural enemy system~\citep{Barbour2016,Barbour2016Dryad}.
-We created 100 ``posterior-sampling" networks and then, for each of these, created 100 ``detection-filter" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network.
-This simulates imperfect detection of interactions in the field.
-Each point represents the mean network property (e.g., connectance) obtained from a set of 100 detection-filter networks, plotted against the value of the network property in the posterior-sampling network used to create the detection-filter networks.
-For each property and both network types, the posterior-sampling networks cover a relatively small range of network properties than the range covered by networks with varying detection probabilities.
-The value of each property decreases with the proportion of links included in the detection-filter networks.}
-    % \label{posterior_webs}    
-    % \includegraphics[width=.8\textwidth]{Figures/Salix_Galler_posterior_properties.eps}
-    % \end{figure}
 

### 2018-03-08 code/Zillis_prior/calculate_NODF.R

@@ -1,7 +1,8 @@
 library(vegan)
 library(igraph)
 
-for(site in c("Zillis","Zillertal")){
+site="Zillis"
+# for(site in c("Zillis","Zillertal")){
 # for(site in c("Zillertal")){
   for(webtype in c("SG","GP")){
     if(webtype=="SG"){
@@ -46,4 +47,4 @@ for(site in c("Zillis","Zillertal")){
     }
     write.table(nesttable,file=paste0('../../data/Zillis_webs/',webtype,'_NODF_table_',site,'.tsv',sep=''))
   }
-}
+# }

### 2018-03-08 code/figure_generation/upper_CI_after_DG.py

@@ -33,7 +33,6 @@ def read_Rfiles(filename):
       upper=float(line.split()[-1])
       dataset.append((n,upper))
   f.close()
-
   return dataset
 
 def format_graph(graph):
@@ -41,7 +40,7 @@ def format_graph(graph):
   graph.xaxis.bar.linewidth=1
   graph.frame.linewidth=1
   graph.world.xmin=0
-  graph.world.xmax=32
+  graph.world.xmax=40
   graph.world.ymin=-0
   graph.world.ymax=1
 
@@ -67,7 +66,7 @@ def populate_graph(graph,dataset):
 
   bar95=graph.add_dataset([(0,0.1),(1000,.1)])
   bar95.symbol.shape=0
-  bar95.line.configure(linewidth=2,linestyle=2,color=2)
+  bar95.line.configure(linewidth=2,linestyle=3,color=2)
 
   return graph
 

### 2018-03-08 manuscript/figure_binomial.R

@@ -1,5 +1,5 @@
 library(binom)
-n <- c(1:30)
+n <- c(1:40)
 CI <- binom.confint(0, n, method = "exact")
 dev.new(width = 10, height = 8)
 plot(n,CI[,6], xlab = "Number of samples", ylab = "Upper 95% confidence interval", type = "l",cex.axis = 1.5,cex.lab = 1.5,lwd = 2,ylim = c(0,1))

### 2018-03-08 manuscript/CI_interactions.tex
spellchecked

@@
 
-    Representating an assemblage of species as a network offers a convenient summary of how the community is constructed as it simultaneously accounts for species composition and interactions between species.
+    Representing an assemblage of species as a network offers a convenient summary of how the community is constructed as it simultaneously accounts for species composition and interactions between species.
 A tabulation of the nodes (species) and their relative abundances forms the basis for traditional metrics of community composition.
@@
 
-    The assumption of static communities contrasts significantly with the widely recognized stochasticity of ecological communities~\citep{Gotelli2000}.
+    The assumption of static communities contrasts significantly with the widely recognised stochasticity of ecological communities~\citep{Gotelli2000}.
 Community composition and species abundances vary from site to site~\citep{Baiser2012} and over time within a site~\citep{Olesen2011a}.
@@
 The ecologist wanting to describe the network, however, is specifically interested in the situation where $L = 0$ (i.e., in true absences).
-Thus, while there is have no difficulty interpreting the observation of an interaction, the observation of an absence of an interaction offers more of a challence since it must be decomposed into different quantities.
+Thus, while there is have no difficulty interpreting the observation of an interaction, the observation of an absence of an interaction offers more of a challenge since it must be decomposed into different quantities.
 It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e.
@@
 
-  [[Tomas suggests removing the following because it slows down procedings, Anna and Dom want it back. Shortening sounds like a good middle ground:]]
+  [[Tomas suggests removing the following because it slows down proceedings, Anna and Dom want it back. Shortening sounds like a good middle ground:]]
   The basic information that we are collecting consists of matrices of interaction partners.
@@
    [[Move this paragraph to intro?]] It is getting more and more common to represent interactions as probabilities in theoretical models of network structure.
-For example, the minimum potential model introduces gaps in the feeding niche of predators by sampling based on the likelihood of each interaction~\citep{Allesina2008}, while a gaussian probability function is used to represent the niche by~\citet{Williams2010}.
+For example, the minimum potential model introduces gaps in the feeding niche of predators by sampling based on the likelihood of each interaction~\citep{Allesina2008}, while a Gaussian probability function is used to represent the niche by~\citet{Williams2010}.
 \citet{Eklof2013} also introduced variability  in the computation of network dimensions, allowing the absence of interactions within the n-dimension niche of every species.
@@
 Network data for a similar study system may, however, not be available.
-In that case, one might use the first subnetwork collected as ``training data" to guide future sampling.
-To simulate this situation, we created priors using a single subnetwork from the middle of the geographical distribution of the~\citep{Kopelke2017} dataset (Zillis subweb).
+In that case, one might use the first sub-network collected as ``training data" to guide future sampling.
+To simulate this situation, we created priors using a single sub-network from the middle of the geographical distribution of the~\citep{Kopelke2017} dataset (Zillis sub-network).
 To demonstrate how the use of a data from a different system can affect the prior distribution and conclusions based on it, we repeated our analyses using priors derived from a much smaller \emph{Salix}-galler-natural enemy system~\citep{Barbour2016,Barbour2016Dryad}.
@@
 
-      To obtain the priors based on the Zillis subweb, we estimated frequencies of \emph{Salix}-galler interactions based on the normalised degree of each species in each network component (see \emph{Appendix S3} for details and code).
+      To obtain the priors based on the Zillis sub-network, we estimated frequencies of \emph{Salix}-galler interactions based on the normalised degree of each species in each network component (see \emph{Appendix S3} for details and code).
 Specifically, we obtained prior parameters of $\alpha$=8.72, $\beta$=305 for the \emph{Salix}-galler component and $\alpha$=0.700, $\beta$=8.49 for the galler-natural enemy components of the network.
@@
 The prior distribution for the galler-natural enemy network was: $\bar\lambda$=0.076, var($\lambda$)=0.008.
-The posterior interaction probabilities obtained based on the Zillis subweb were much lower than those obtained based on~\citet{Barbour2016}; this emphasises the importance of using an appropriate study system when constructing a prior (\emph{Appendix SX}).
+The posterior interaction probabilities obtained based on the Zillis sub-network were much lower than those obtained based on~\citet{Barbour2016}; this emphasises the importance of using an appropriate study system when constructing a prior (\emph{Appendix SX}).
 
@@
 In our dataset, the entire 95\% credible interval was (0.013, 0.049).
-We may therefore be 95\% confident that the interaction probability for \emph{Salix} and galler species that have not been observed cooccurring is below 0.05.
+We may therefore be 95\% confident that the interaction probability for \emph{Salix} and galler species that have not been observed co-occurring is below 0.05.
 As the peak of the prior distribution for the probability of interaction between \emph{Salix} and galler probabilities is around 0.02 (Fig.~\ref{Salix_pdfs}), to be 95\% confident that the interaction probability for these species is below 0.01 would require 1029 observed co-occurrences with no interaction - far more than the number of sites in the~\citep{Kopelke2017} dataset.
 
-      The number of samples required to be 95\% confident that the interaction probability between galler and natural enemy species is below a threshold also increases quickly as the threshold decreasesy.
+      The number of samples required to be 95\% confident that the interaction probability between galler and natural enemy species is below a threshold also increases quickly as the threshold decreases.
 The 95\% credible interval is (0.0005, 0.303) for the probability of interaction between two species observed to co-occur but never interact.
-To be 95\% confident that the probability of interaction is below 0.1, 0.05, or 0.01 would require 15, 39, and 229 observed co-occurrances, respectively.
+To be 95\% confident that the probability of interaction is below 0.1, 0.05, or 0.01 would require 15, 39, and 229 observed co-occurrences, respectively.
 
@@
 This dataset consists of a single community type sampled across Europe: willow (\emph{Salix}) species, willow-galling sawflies, and their natural enemies.
-The data were collected over 29 years at 374 unique locations across Europe, with a total of 641 site visits.
-Each site visit can be considered as a network in its own right or as an independent sample from which to build the meta-network.
+The data were collected over 29 years at 374 unique locations across Europe with a total of 641 site visits.
+Each site visit or each unique site can be considered as a network in its own right or as an independent sample from which to build the meta-network.
+Here we take the more conservative approach and pool visits to the same site for a sample size of 374 sub-networks.
 The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes.
 The high spatiotemporal resolution of this network and the unusually high sampling effort implemented at the site level makes this dataset particularly well suited for illustrating the difficulties in completely sampling a network and testing Bayesian approaches to overcome these difficulties.\\
-    \indent We may begin by comparing the frequency of co-occurences for pairs of species in each part of the network to reveal the challenge of having sufficient sampling to be confident that an interaction does not occur.
+    \indent We may begin by comparing the frequency of co-occurrences for pairs of species in each part of the network to reveal the challenge of having sufficient sampling to be confident that an interaction does not occur.
 Most pairs of species (3,986/4,992 \emph{Salix}-galler pairs and  9,794/12,096 galler-natural enemy pairs) are never found co-occurring and, for species that did occur together, the total number of co-occurrences was generally low (mean=4.24, variance=36.3 for \emph{Salix}-galler pairs; mean=3.87, variance=28.8 for galler-natural enemy pairs; Fig.~\ref{histograms}A-B).
@@
 This suggests that limited sampling is a major source of uncertainty in all empirical networks.
-This dataset also illustrates the potential for increased sampling to not necessarily reveal more interactions as a pair of species that is able to interact may not be observed interacting in all samples where the pair co-occurrs (Fig.~\ref{histograms}E-F).
+This dataset also illustrates the potential for increased sampling to not necessarily reveal more interactions as a pair of species that is able to interact may not be observed interacting in all samples where the pair co-occurs (Fig.~\ref{histograms}E-F).
   \caption{\emph{Salix} dataset}
@@
 These parameters can then be used to calculate a credible interval using the R~\citep{R} function qbeta.
-In the table below, we present the 95\% credible intervals for \emph{Salix}-galler and galler-natural enemy paris with different numbers of observed co-occurrences ($n$) and no observed interactions ($k=0$).
-Both sets of intervals rely on prior information derived from the Zillis subweb~\citep{Kopelke2017}.
+In the table below, we present the 95\% credible intervals for \emph{Salix}-galler and galler-natural enemy pairs with different numbers of observed co-occurrences ($n$) and no observed interactions ($k=0$).
+Both sets of intervals rely on prior information derived from the Zillis sub-network~\citep{Kopelke2017}.
 
@@
 Even assuming no added detection error in observing the incidence of the interaction, a single observation of species co-occurrence reveals very little regarding the probability of the interaction as the credible interval for a pair of species with one observation essentially spans from 0 to 1.
-Only with about 35 observations will the upper limit of the credible interval be lowered to 0.1.
+Only with 35 observations will the upper limit of the credible interval be lowered to 0.1.
 Thus, adding more observations is certainly useful in controlling uncertainty, but the number of observations added needs to be very high.
-Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true credible interval for $\lambda$ when $k=0$ ($i$ and $j$ have not been observed interacting) for a variety of $n$ (observed co-occurences of $i$ and $j$).
+Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true credible interval for $\lambda$ when $k=0$ ($i$ and $j$ have not been observed interacting) for a variety of $n$ (observed co-occurrences of $i$ and $j$).
 A threshold interaction probability of 0.1 is indicated by the dashed red line.
@@
       \begin{figure}[ht]
-        \caption{Using prior distribution based on the \emph{Salix}-galler and galler-natural enemy networks sampled at a single site in~\citet{Kopelke2017}, we can calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting.
+        \caption{Using prior distributions based on the \emph{Salix}-galler and galler-natural enemy networks sampled at a single site in~\citet{Kopelke2017}, we can calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting.
 Here we show posterior distributions for $\lambda$ in each network component ranging from the prior distribution ($n=0$ observed co-occurrence) to the distribution obtained when the pair of species has been observed co-occurring 100 times.
@@
 The large ticks along the x-axis indicate the number of samples associated with each of these points.
-Note that the number of samples required to reach any given threshold is larger for \textbf{A)} the \emph{Salix}-galler network than for \textbf{B)} the galler-natural enemy network.
-In the galler-natural enemy network, the credible interval for a pair of species with no observed co-occurrances was 0.364.
-All pairs of species therefore have $\lambda$\textless0.5.}
+\textbf{A)} In the \emph{Salix}-galler network component, the 95\% credible interval for $\lambda$ when $n$=0 was (0.013, 0.049).
+We can therefore be at least 95\% confident that $\lambda$ is below thresholds of 0.1 or 0.05 without any observed co-occurrence.
+To be confident that $\lambda$ is less than 0.01, however, would require more observed co-occurrences than there are sites in our dataset.
+\textbf{B)} In the galler-parasitoid network component, the 95\% credible interval for $\lambda$ was substantially broader and many observed co-occurrences (\approx 15-35) are required to be 95\% confident that $\lambda$ is below thresholds of 0.1 or 0.05.}
         \label{Salix_cdfs}
@@
     \begin{figure}[ht]
-    \caption{Here we show the mean connectance, links per resource (\emph{Salix} in the \emph{Salix}-galler networks and gallers in the galler-natural enemy networks), and links per consumer for networks assembled using posterior distributions based on a single subweb in the~\citet{Kopelke2017} dataset (Zillis).
+    \caption{Here we show the mean connectance, links per resource (\emph{Salix} in the \emph{Salix}-galler networks and gallers in the galler-natural enemy networks), links per consumer, and nestedness (NODF) for networks assembled using posterior distributions based on a single sub-network in the~\citet{Kopelke2017} dataset (Zillis).
 We created 100 ``posterior-sampling" networks and then, for each of these, created 100 ``detection-filter" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network.

### 2018-03-08 manuscript/supplemental.tex
spellchecked SI

@@
   Priordata is the list of interaction frequencies from the prior 
-  data, n is the number of sites with observed co-occurrance of 
+  data, n is the number of sites with observed co-occurrence of 
   species $i$ and $j$, and k is the number of sites with an 
@@
       mu\_denominator=alpha+beta\\
-      mu=mu\_numerator/mu\_denomenator\\
+      mu=mu\_numerator/mu\_denominator\\
       \vspace{4pt}
@@
       den2=den1$**$2\\
-      sig\_denomenator=den1$*$den2\\
-      sigma2=sig\_numerator/sig\_denomenator\\
+      sig\_denominator=den1$*$den2\\
+      sigma2=sig\_numerator/sig\_denominator\\
       return(c(mu,sigma2))\}
@@
 
-      To extract the galler-parsitoid network from the same study above:
+      To extract the galler-parasitoid network from the same study above:
 
@@
 Note that the number of samples required to reach any given threshold is larger for \textbf{A)} the \emph{Salix}-galler network than for \textbf{B)} the galler-natural enemy network.
-In the galler-natural enemy network, the credible interval for a pair of species with no observed co-occurrances was 0.364.
+In the galler-natural enemy network, the credible interval for a pair of species with no observed co-occurrences was 0.364.
 All pairs of species therefore have $\lambda$\textless0.5.}
@@
       \begin{figure}[ht]
-      \caption{Here we show the mean connectance, links per resource (\emph{Salix} in the \emph{Salix}-galler networks and gallers in the galler-natural enemy networks), and links per consumer for networks assembled using posterior distributions based on a smaller, North American \emph{Salix}-galler-natural enemy system~\citep{Barbour2016,Barbour2016Dryad}.
+      \caption{Here we show the mean connectance, links per resource (\emph{Salix} in the \emph{Salix}-galler networks and gallers in the galler-natural enemy networks), links per consumer, and nestedness (NODF) for networks assembled using posterior distributions based on a smaller, North American \emph{Salix}-galler-natural enemy system~\citep{Barbour2016,Barbour2016Dryad}.
 We created 100 ``posterior-sampling" networks and then, for each of these, created 100 ``detection-filter" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network.

### 2018-03-08 manuscript/CI_interactions.tex
spellchecked SI
intro looks good to me

@@
 
-    Representing an assemblage of species as a network offers a convenient summary of how the community is constructed as it simultaneously accounts for species composition and interactions between species.
+    Representing an assemblage of species as a network offers a convenient summary of how the community is constructed as a network simultaneously describes species composition and interactions between species.
 A tabulation of the nodes (species) and their relative abundances forms the basis for traditional metrics of community composition.
@@
 Likewise, interactions vary over space~\citep{Kitching1987,Baiser2012}, time~\citep{Kitching1987,Olesen2011a}, and between individuals of a given species~\citep{Pires2011a,Fodrie2015,Novak2015}.
-Moreover, variability in community composition and interactions may or may not be closely related.
+We emphasise that variability in community composition and interactions may or may not be closely related.
 The removal of a species from a site will obviously also remove its interactions but, conversely, the co-occurrence of potentially interacting species does not in itself guarantee that they will interact at a given place and time.
@@
 
-    In this study, we develop analytical tools to capture the uncertainty in the estimation of pairwise interactions.
+    In this study, we formalize the description of interactions between species as probabilities and develop analytical tools to capture the uncertainty in the estimation of pairwise interactions.
 We focus on binary interactions as a first step, but the framework could be expanded to deal with interaction frequencies and strength.
@@
 
-    [[check that all the figs are with Zillis]]
-
     %It is fairly straightforward to compute most of network metrics when the different $\lambda$ of the adjacency matrix are known, without variance~\citep{Poisot2016}.
@@
 To demonstrate how the use of a data from a different system can affect the prior distribution and conclusions based on it, we repeated our analyses using priors derived from a much smaller \emph{Salix}-galler-natural enemy system~\citep{Barbour2016,Barbour2016Dryad}.
-This smaller system was much more densely-connected than that described in~\citet{Kopelke2017} and provided unreasonable distributions for interaction probabilities (\emph{Appendix SX}).
+This smaller system was much more densely-connected than that described in~\citet{Kopelke2017} and provided unreasonable distributions for interaction probabilities (\emph{Appendix S4}).
 
@@
 The prior distribution for the galler-natural enemy network was: $\bar\lambda$=0.076, var($\lambda$)=0.008.
-The posterior interaction probabilities obtained based on the Zillis sub-network were much lower than those obtained based on~\citet{Barbour2016}; this emphasises the importance of using an appropriate study system when constructing a prior (\emph{Appendix SX}).
+The posterior interaction probabilities obtained based on the Zillis sub-network were much lower than those obtained based on~\citet{Barbour2016}; this emphasises the importance of using an appropriate study system when constructing a prior (\emph{Appendix S4}).
 
@@
 The large ticks along the x-axis indicate the number of samples associated with each of these points.
-\textbf{A)} In the \emph{Salix}-galler network component, the 95\% credible interval for $\lambda$ when $n$=0 was (0.013, 0.049).
-We can therefore be at least 95\% confident that $\lambda$ is below thresholds of 0.1 or 0.05 without any observed co-occurrence.
-To be confident that $\lambda$ is less than 0.01, however, would require more observed co-occurrences than there are sites in our dataset.
-\textbf{B)} In the galler-parasitoid network component, the 95\% credible interval for $\lambda$ was substantially broader and many observed co-occurrences (\approx 15-35) are required to be 95\% confident that $\lambda$ is below thresholds of 0.1 or 0.05.}
+\textbf{A)} In the \emph{Salix}-galler network component, the 95\% credible interval for $\lambda_{ij}$ when $n$=0 was (0.013, 0.049).
+We can therefore be at least 95\% confident that $\lambda_{ij}$ is below thresholds of 0.1 or 0.05 without any observed co-occurrence of species $i$ and $j$.
+To be confident that $\lambda_{ij}$ is less than 0.01, however, would require more observed co-occurrences than there are sites in our dataset.
+\textbf{B)} In the galler-parasitoid network component, the 95\% credible interval for $\lambda_{ij}$ was substantially broader and many observed co-occurrences ($\approx$ 15-35) are required to be 95\% confident that $\lambda_{ij}$ is below thresholds of 0.1 or 0.05.}
         \label{Salix_cdfs}

### 2018-03-08 manuscript/CI_interactions.tex
finished read-through of main text

@@
 
+\clearpage
 % Main text can be up to 7500 words, 10 fig., tables, boxes
@@
   % Can be up to 200 words. This is 200 exactly.
-  % Word count can be up to 7500, we're at about 5700 without the boxes. Should be grand.
+  % Word count can be up to 7500, we're at about 6506 without the boxes, intro, references.
 
@@
 
+% AC: Good idea - I've also changed the "In this study, we ..." paragraph to make it sound less like we just built some software and hopefully emphasise the conceptual side more.
+
 \linenumbers
+\clearpage
+
 \begin{spacing}{2.0}
@@
 As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Poisot2016}.
-Yet, to date, we lack the quantitative methodology to deal with the uncertainty generated by spatiotemporal variation in ecological interactions and by sampling.
+Early work in this vein includes food-web models using likelihood-based approaches~\citep{Allesina2008} or Gaussian~\citep{Williams2010} or binomial~\citep{Rohr2016} probability functions for each possible interaction.
+These models may include information about species' traits~\citep{Rohr2016} or may attempt to reproduce empirical network structures using a set of simple rules~\citep{Allesina2008,Williams2010}.
+    % \citet{Eklof2013} also introduced variability  in the computation of network dimensions, allowing the absence of interactions within the n-dimension niche of every species.
+% AC: Does this really fit in now that this is in the introduction?
+
+    Despite these preliminary efforts, to date we lack the quantitative methodology to deal with the uncertainty generated by spatiotemporal variation in ecological interactions and by sampling.
 Even in extremely well-sampled networks, uneven sampling across species (or pairs of species) can lead to the erroneous inference that some species do not interact because they co-occur rarely or have not yet been observed together - even if they do interact when they do co-occur (see Box 1 for an example).
@@
 
-    In this study, we formalize the description of interactions between species as probabilities and develop analytical tools to capture the uncertainty in the estimation of pairwise interactions.
+   % [[Move this paragraph to intro?]] It is getting more and more common to represent interactions as probabilities in theoretical models of network structure.
+For example, the minimum potential model introduces gaps in the feeding niche of predators by sampling based on the likelihood of each interaction~\citep{Allesina2008}, while a Gaussian probability function is used to represent the niche by~\citet{Williams2010}.
+\citet{Eklof2013} also introduced variability  in the computation of network dimensions, allowing the absence of interactions within the n-dimension niche of every species.
+Empirical investigation of trait-matching constraints often consider the occurrence of interactions as binomial process (e.g.,~\citealp{Rohr2016}).
+There are also ways to perform analysis of probabilistic networks, with almost all metrics having a probabilistic version~\citep{Poisot2016}.
+But there is not yet consensus on what an interaction probability between a pair of species means, and this is definitely a problem when comes time to estimate the uncertainty of both pairwise interactions and entire networks.
+
+    In this study, we formalize the description of interactions between species as probabilities and develop analytical tools to capture the uncertainty in the estimation of these interactions.
 We focus on binary interactions as a first step, but the framework could be expanded to deal with interaction frequencies and strength.
@@
   To define the problems associated with quantifying ecological interaction networks, we will start from the perspective of an empirical community ecologist faced with the task of describing a previously unknown interaction network.
-This ecologist will be interested in generating a description of the species/nodes present, and the links between them~\citep{Roslin2016}.
+This ecologist will be interested in generating a description of the species/nodes present and the links between them~\citep{Roslin2016}.
 Importantly, the information sought is conveyed by both the presence and \emph{absence} of links.
-The two types of information are not, however, equally certain.
+Presences and absences are not, however, equally certain.
 An observed link will always remain an observed link, but there are multiple reasons why a given link may not be observed.
 Thus, the detection of any interaction is a stochastic process.
-We define three nested levels of uncertainty contributing to this stochasticity:
+We define three nested levels of uncertainty contributing to this stochasticity: interaction uncertainty, process uncertainty, and detection uncertainty.
 
@@
 We define the probability of an interaction $L$ given those characteristics $\mathbf{T}$ as $P(L | \mathbf{T})=\lambda$.
-Obviously, if $k$ (the number of observed interactions) is 0, it is possible that the two species could not interact even if there were no external constraints (e.g., temporal or environmental separation) preventing the interaction from occurring.
+Obviously, if $k$ (the number of observed interactions) is 0, it is possible that the two species would not interact even if there were no external constraints (e.g., temporal or environmental separation) preventing the interaction from co-occurring.
 As a simple example, a prey species may be too large to be consumed by a particular predator.
 In such cases, $\lambda$ would take a value of 0 and there would be no uncertainty.
+
       Nevertheless, it is also possible that the interaction is a rare phenomenon with $\lambda>0$ that has not yet been documented.
@@
 It arises because every model is imperfect and lacks information (i.e.
-about traits) that could be used to define constraints on the interaction.
-In other words, with sufficient sampling and all information accessible, this interaction probability $\lambda$ should either tend to 0 or to 1 and the uncertainty should vanish.
+about traits) that could be used to define constraints on the interaction~\citep{Dormann2017}.
+Further study may, however, eventually reveal the traits of interest and allow us to reduce interaction uncertainty.
+In other words, with sufficient sampling and all information accessible, this interaction probability $\lambda$ should either tend to 0 or to 1.
 
@@
 Phenological matching~\citep{MillerRushing2010,Gezon2016}, species preferences~\citep{Pires2011,Novak2015,Coux2016}, and fear effects of other species~\citep{Luttbeg2005,Wirsing2008} are just some of the factors contributing to variation in the frequency of interactions between a given pair of species.
+Although some of the factors leading to process uncertainty can be addressed in mesocosm studies of networks (e.g., environmental conditions can be held stable), process uncertainty is likely inevitable in the field.
       % We imagine for instance that an interaction between a gall and a parasitoid might not be recorded at a location because it was the wrong time of the year and the gall had not yet formed (phenological constraints), a late frost killed the larvae (an abiotic environmental constraint), another parasitoid species competitively excluded the parasitoid species of interest (a biotic environmental constraint) or simply the parasitoid is too rare to interact with all of its viable hosts (an abundance constraint).
@@
       Lastly, measurement errors are a pervasive source of uncertainty in the observation of ecological processes.
-Given that an interaction with the variable $D$, given an interaction is feasible and occurs under the local conditions, we may define the detection of an interaction, $D$, as a stochastic process with the associated probability $P(D|X=1,L=1)=\delta$.
-Detection failure could happen for several reasons, for instance if the rearing of a parasitoid fails with inappropriate lab conditions, because of species mis-identification, or because the interaction is very rare (see~\citet{Wirta2014} for examples of some of these difficulties and partial solutions to them).
+Given that an interaction is feasible and occurs under the local conditions ($L$=1 and $X$=1), we may define the detection of an interaction, $D$, as a stochastic process with the associated probability $P(D|X=1,L=1)=\delta$.
+Detection failure could happen for several reasons including failure to rear a parasitoid, species mis-identification, or because the interaction is very rare (see~\citet{Wirta2014} for examples of some of these difficulties and partial solutions to them).
 Some sources of detection error can be minimised with appropriate sampling effort ($\delta$ will converge to one with increasing number of samples), but other sources are often difficult to reduce (e.g.
@@
 The ecologist wanting to describe the network, however, is specifically interested in the situation where $L = 0$ (i.e., in true absences).
-Thus, while there is have no difficulty interpreting the observation of an interaction, the observation of an absence of an interaction offers more of a challenge since it must be decomposed into different quantities.
+Thus while there is no difficulty interpreting the observation of an interaction, the observation of an absence of an interaction offers more of a challenge since it must be decomposed into different quantities.
 It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e.
-where the interaction occurred at the location but was not observed, and $D=1 \cup X = 0 \cup L =1$, when the interaction is feasible and would have been detected but did not occur at the local site.
-The occurrence of a true absence, our quantity of interest, corresponds to the joint event $L=0 \cup X=1 \cup D=1$, but in reality an empirical ecologist will measure the marginal probability $P(L) = k/n$ where $k$ is again the number of observed interactions and $n$ the number of observed co-occurrences.
+where the interaction occurred at the location but was not observed, and $D=1 \cup X = 0 \cup L =1$, i.e., where the interaction is feasible and would have been detected but did not occur at the local site.
+The occurrence of a true absence, our quantity of interest, corresponds to the joint event $L=0 \cup X=1 \cup D=1$ but in reality an empirical ecologist will measure the marginal probability $P(L) = k/n$ where $k$ is again the number of observed interactions and $n$ the number of observed co-occurrences.
 
@@
 Importantly, some sources of uncertainty can be minimised with appropriate sampling design and efforts while other sources are difficult or impossible to reduce since they are generated by chance variation created by the very process in which we are interested.
+Given this multifaceted problem of uncertainty, what can we do to separate the different types of variation and reduce those that can be reduced?
 
@@
 
-  [[Tomas suggests removing the following because it slows down proceedings, Anna and Dom want it back. Shortening sounds like a good middle ground:]]
-  The basic information that we are collecting consists of matrices of interaction partners.
+    %AC: I've added this section back in but shortened it slightly (mostly the first paragraph). We're ok on word-count with this included.
+
+    % The basic information that we are collecting consists of matrices of interaction partners.
 Our count of interactions between two species reflects uncertainty with respect to whether two species are capable of interacting when co-occurring at a given site ($\lambda$), chance variation in whether the interaction is realised ($\chi$),  and uncertainty with respect to whether it is detected when realised ($\delta$).
@@
 
-  The obvious rule of thumb is to ``sample more" (see Fig.~\ref{upper_limits} for a demonstration of the power of increasing sample size), but we note that there are limits to the utility of this motto.
-Sampling more will clearly reduce uncertainty regarding the upper bound of the probability of interaction, and it will also increase the probability of detecting unlikely interactions (i.e.
-interactions occurring with a low probability).
-Yet, since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present; see Fig.~\ref{histograms}E-F), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions.
-Thus, the more we sample, the more zeros will appear in our interaction matrix, which may seem like a counter-intuitive outcome.
+    The obvious rule of thumb is to ``sample more" (see Fig.~\ref{upper_limits} for a demonstration of the power of increasing sample size).
+Sampling more will clearly reduce uncertainty regarding the upper bound of the probability of interaction and it will also increase the probability of detecting unlikely interactions (e.g.,.
+interactions where $L$=1 but process uncertainty is high).
+    Despite these benefits, we note that there are limits to the utility of increased sampling.
+Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present; see Fig.~\ref{histograms}E-F), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions.
+Thus, the more we sample, the more zeros will appear in our interaction matrix.
 
-  As a solution towards deciding whether unobserved interactions were undetected due to sampling, or whether they truly do not occur,~\citet{Weinstein2017} used repeated sampling rounds to estimate the daily probability of detecting a hummingbird interaction, and to thereby model the observation and process mechanisms.
-While conceptually attractive, this approach is unsuitable for interactions occurring over longer time scales (e.g., associations between hosts and parasitoids with a single generation per year), or very rare interactions which might not occur on any of the sampling days or might involve individuals of a species that are not under observation.
-What is worse, the problem persists that if a given interaction is not observed on a given day, this could be either because it was impossible that day despite being otherwise feasible [$P(X|D=1,L=1)=0$], because interaction between the two did occur but could not be observed [$P(D|X=1,L=1)=0$], or from any combination of the two.
-From a conceptual perspective, this approach will thus fail to satisfactorily distinguish between sources of uncertainty.
+    As a solution towards deciding whether unobserved interactions were undetected due to sampling, or whether they truly do not occur,~\citet{Weinstein2017} used repeated sampling rounds to estimate the daily probability of detecting a hummingbird interaction, and to thereby model detection and process uncertainty.
+While conceptually attractive, this approach is unsuitable for interactions occurring over longer time scales (e.g., associations between hosts and parasitoids with a single generation per year), or very rare interactions which might not occur on any of the sampling days or might involve individuals of a species that is not under observation.
+What is worse, the problem persists that the absence of an interaction of a given day could  either be because it was impossible on that day despite being otherwise feasible [$P(X|D=1,L=1)=0$], because interaction did occur but could not be observed [$P(D|X=1,L=1)=0$], or any combination of the two.
+From a conceptual perspective, this approach therefore fails to satisfactorily distinguish between sources of uncertainty.
 Most importantly, if two species are never observed co-occurring during several days of sampling then we have learned nothing about their probability of interacting if they should ever co-occur.
@@
 The bottom line is that separating different sources of uncertainty is difficult indeed.
-As an alternative to abandoning empirical networks or continuing to ignore the uncertainty inherent in undetected observations, we propose that some insight regarding the detectability of interactions between species not found co-occurring may be gained from data on other species between which interactions are known to be feasible.
+As an alternative to abandoning empirical networks or continuing to ignore the uncertainty inherent in undetected observations, we propose that some insight regarding the detectability of interactions between species not found co-occurring in a focal system may be gained from data on other species pairs in the same or a similar system.
 
-\section*{A naive quantification of interaction probability and uncertainty}
+\section*{A naive quantification of uncertainty}
+  %AC: This section header was too long and running beyond a line... is the shortened version ok?
+  % \section*{A naive quantification of interaction probability and uncertainty}
 
@@
 
-   [[Move this paragraph to intro?]] It is getting more and more common to represent interactions as probabilities in theoretical models of network structure.
+   % [[Move this paragraph to intro?]] It is getting more and more common to represent interactions as probabilities in theoretical models of network structure.
 For example, the minimum potential model introduces gaps in the feeding niche of predators by sampling based on the likelihood of each interaction~\citep{Allesina2008}, while a Gaussian probability function is used to represent the niche by~\citet{Williams2010}.
@@
 Finding this estimate is therefore quite straightforward, but it nonetheless has two drawbacks.
-First, $\lambda$ is not a single point estimate but rather a random variable with a given uncertainty, the distribution of which is unknown.
-This means that even if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact.
+First, $\lambda$ is not a single point estimate but rather a random variable with an unknown distribution.
+This means that if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact.
 Rather, $k = 0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless a substantial chance that the two species \emph{could} interact.
@@
 
-          The ecological network literature boasts a solid collection of networks for which connectance has been calculated and for which we can thus define the connectance distribution.
+          The ecological network literature boasts a collection of networks for which connectance has been calculated and for which we can thus define the connectance distribution.
 Connectance is measured as $C = L/S^2$, where $L$ is the number of interactions and $S$ is the number of species.
@@
 a known network at slightly different location) or from the network of interest if interaction probabilities for some species are already documented.
-The latter approach allows to apply information from known, abundant species to the rarest species for which interactions are less frequently documented.
+The latter approach allows researchers to apply information from known, abundant species to the rarest species for which interactions are less frequently documented.
 
@@
 Using normalised degrees $\Delta_i$ and $\Delta_j$ (i.e., degrees divided by the number of species in the network), we can obtain the probability of interaction $L_{ij}$=$\Delta_i\times\Delta_j$.
-Similar to the procedure for degree distribution, the distribution of these interaction probabilities derived from a similar network or a suite of networks can be used to establish a prior distribution before any data from the focal network are collected.
+Similar to the procedure for degree distribution, the distribution of these interaction probabilities can be used to establish a prior distribution before any data from the focal network are collected.
 For distributions of either degrees or interaction probabilities, the procedure for the estimation of the hyper parameters follows the same approach as described above for connectance except that each measurement is at the individual interaction level instead of the network level.
@@
 
-          As a fourth and final approach to obtain the prior distribution of $\lambda$, we envisage using the outcome of a trait-matching model, provided such a model has been documented using external data and relevant traits are available.
-In such as case, the prior distribution would follow the function $P(\lambda|\mathbf{T})=f(\mathbf{T})$ based on a set of traits for both species $\mathbf{T}$.
+          As a fourth and final approach, it may be possible to obtain the prior distribution of $\lambda$ using the outcome of a trait-matching model, provided such a model has been parameterised using external data and relevant traits are available.
+In such a case, the prior distribution would follow the function $P(\lambda|\mathbf{T})=f(\mathbf{T})$ based on a set of traits for both species $\mathbf{T}$.
 There are several techniques available to perform this inference of interaction probability, some of which are Bayesian, and we refer to~\citet{Bartomeus2016} and~\citet{Weinstein2017} for recent reviews about this topic.
@@
 Suppose we have $n = 10$ observations of co-occurrence between species $i$ and species $j$ in a given time interval and area, and $k = 3$ observations of interactions.
-The maximum likelihood estimate of the interaction probability (Box~\ref{box2}) is simply $\lambda_{MLE} = 3/10 = 0.3$.
+The maximum likelihood estimate of the interaction probability is simply $\lambda_{MLE} = 3/10 = 0.3$.
 
@@
 
-\section*{Scaling up uncertainty from pairwise interactions to networks}
+\section*{Scaling up to networks - an empirical example}
 
@@
     In the following section, we will provide an empirical example based on the well-sampled system of \emph{Salix}  plants, herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}; see Box~\ref{box1} or \emph{Appendix S2} for a description).
-    %This tripartite network can be examined as two bipartite networks, namely \emph{Salix}-galler and galler-natural enemy networks. 
-    We will show how the uncertainty arising from both absences of co-occurrences and false absences of interactions impact these metrics.
+Using this dataset, we will demonstrate the derivation of prior distributions for the \emph{Salix}-galler and galler-natural enemy components of these networks and the differences between these priors and posterior distributions which include all information available in this dataset~\citep{Kopelke2017}.
+Finally, we will calculate network properties using a suite of networks sampled from these posterior distributions and show how the uncertainty around interactions that have not been observed impact these metrics.
 %We find uncertainty influences both the average and the variance of network metrics, putting in perspective traditional network comparison studies where these metrics are assumed to be fixed entities.
@@
 In that case, one might use the first sub-network collected as ``training data" to guide future sampling.
-To simulate this situation, we created priors using a single sub-network from the middle of the geographical distribution of the~\citep{Kopelke2017} dataset (Zillis sub-network).
-To demonstrate how the use of a data from a different system can affect the prior distribution and conclusions based on it, we repeated our analyses using priors derived from a much smaller \emph{Salix}-galler-natural enemy system~\citep{Barbour2016,Barbour2016Dryad}.
+To simulate this situation, we created priors using a single sub-network from the middle of the geographical distribution of the~\citet{Kopelke2017} dataset.
+To demonstrate how the use of data from a different system can affect the prior distribution and conclusions based on it, we repeated our analyses using priors derived from a much smaller \emph{Salix}-galler-natural enemy system~\citep{Barbour2016,Barbour2016Dryad}.
 This smaller system was much more densely-connected than that described in~\citet{Kopelke2017} and provided unreasonable distributions for interaction probabilities (\emph{Appendix S4}).
@@
 The prior distribution for the galler-natural enemy network was: $\bar\lambda$=0.076, var($\lambda$)=0.008.
-The posterior interaction probabilities obtained based on the Zillis sub-network were much lower than those obtained based on~\citet{Barbour2016}; this emphasises the importance of using an appropriate study system when constructing a prior (\emph{Appendix S4}).
+The posterior interaction probabilities obtained based on the Zillis sub-network were much lower than those obtained based on~\citet{Barbour2016}; this emphasizes the importance of using an appropriate study system when constructing a prior (\emph{Appendix S4}).
 
@@
 The change in distribution as $n_{ij}$ decreases can also be shown  by calculating 95\% credible intervals for $\lambda$ (see the function ``credible\_interval" in \emph{Appendix S2}).
-The 95\% credible interval around the estimate of $\lambda$ also widens as $n_{ij}$ decreases from (0.001, 0.017) and (\textless0.001, 0.11) for hypothetical \emph{Salix}-galler and galler-natural enemy pairs that might be observed co-occurring at all 374 sites without any observed interaction to (0.152,0.931) and (0.008, 0.364) for \emph{Salix}-galler and galler-natural enemy pairs that were never observed co-occurring.
+The 95\% credible interval around the estimate of $\lambda$ also widens as $n_{ij}$ decreases from (0.001, 0.017) and (\textless0.001, 0.11) for hypothetical \emph{Salix}-galler and galler-natural enemy pairs that might be observed co-occurring at all 374 sites without any observed interaction to (0.152, 0.931) and (0.008, 0.364) for \emph{Salix}-galler and galler-natural enemy pairs that were never observed co-occurring.
 The 95\% credible interval for hypothetical \emph{Salix}-galler pairs widened from (0.006, 0.022) if the pair co-occurred at all sites to (0.013, 0.049) if they co-occurred at none.
@@
 
-  \subsection*{How many samples are required to reach a minimal precision}
+  \subsection*{How many samples are required to reach a minimal precision?}
 
@@
       The number of samples required to be 95\% confident that the interaction probability between galler and natural enemy species is below a threshold also increases quickly as the threshold decreases.
-The 95\% credible interval is (0.0005, 0.303) for the probability of interaction between two species observed to co-occur but never interact.
+The 95\% credible interval is (\textless0.001, 0.303) for the probability of interaction between two species observed to co-occur but never interact.
 To be 95\% confident that the probability of interaction is below 0.1, 0.05, or 0.01 would require 15, 39, and 229 observed co-occurrences, respectively.
@@
       Given the low levels of replication in most network studies, this implies that we should have fairly low confidence in many ``non-interacting" pairs of species.
-Even in the extensively replicated \emph{Salix}-galler-natural enemy dataset very few species pairs were observed co-occurring frequently enough to reach these thresholds.
+Even in the extensively replicated \emph{Salix}-galler-natural enemy dataset, very few species pairs were observed co-occurring frequently enough to reach these thresholds.
 Regardless of our choice of prior, no species pairs were observed to co-occur frequently enough to reach the threshold for an interaction probability of 0.01.
@@
 
-    It is fairly straightforward to compute most of network metrics when the different $\lambda$ of the adjacency matrix are known, without variance~\citep{Poisot2016}.
+    It is fairly straightforward to compute most network metrics when the different $\lambda$ of the adjacency matrix are known and assumed not to vary without variance~\citep{Poisot2016}.
 Several of these metrics derive directly from quantitative indices of network structure which are equivalent to $\lambda$.
@@
 Since Jensen's inequality states that the average of a non-linear function of a stochastic variable differs from the function of the average of that variable, any uncertainty in the values of $\lambda$ could bias both the mean and variance of a network metric.
+One way to avoid potentially biased analytical calculation of network properties is to calculate the properties of a suite of simulated networks.
 
@@
     We find, perhaps not surprisingly, that the posterior webs for the Salix-galler network  had higher connectances than the original, observed web (C=0.028 for the observed web and 0.082$\leq$C$\leq$0.096 for the posterior webs; Fig.~\ref{posterior_webs}A).
-The number of links per \emph{Salix} species in the observed web ($L_{\emph{Salix}}$=2.71 was similar to those in the posterior webs (2.53$\leq L_{\emph{Salix}} \leq$3.19; Fig~\ref{posterior_webs}C).
+The number of links per \emph{Salix} species in the observed web ($L_{\emph{Salix}}$=2.71) was similar to those in the posterior webs (2.53$\leq L_{\emph{Salix}} \leq$3.19; Fig~\ref{posterior_webs}C).
 The number of links per galler, however, was lower in the observed web ($L_{galler}$=1.47) than in the posterior webs, accounting for the increased connectance (4.67$\leq L_{galler} \leq $5.88; Fig.~\ref{posterior_webs}E).
@@
 
-  Real interaction networks vary over several dimensions~\citep{Kitching1987,Olesen2011a,Pires2011a,Baiser2012,Fodrie2015,Novak2015}, and to capture this variation we must turn from static descriptions of network structure to probabilistic descriptions.
-In this study, we have developed the analytical tools to capture the uncertainty in the estimation of pairwise interactions, and to partition it into its individual components: interaction uncertainty, process uncertainty and detection uncertainty.
-The patters unveiled offer tangible recommendations for improved descriptors of ecological interactions.
+  Real interaction networks vary over several dimensions~\citep{Kitching1987,Olesen2011a,Pires2011a,Baiser2012,Fodrie2015,Novak2015} and to capture this variation we must turn from static descriptions of network structure to probabilistic descriptions.
+In this study, we have developed the analytical tools to capture the uncertainty in the estimation of pairwise interactions and a conceptual framework for its individual components: interaction uncertainty, process uncertainty, and detection uncertainty.
+Using this framework leads us to offer tangible recommendations for improved descriptors of ecological interactions.
 First, our analyses point to detection uncertainty as a major contributor to overall uncertainty of is establishing the absence of interaction.
-To counter these establish the true absence of interactions will then require comparatively large sample size – on the order of 30-50 observations per species pair.
+To counter this and establish true absences of interactions requires comparatively large sample size – on the order of 30-50 observations per species pair.
 Second, where such extensive sampling is not feasible, researchers should still acknowledge the varying levels of confidence surrounding the presence or absence of interactions between different pairs of species.
@@
 Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true credible interval for $\lambda$ when $k=0$ ($i$ and $j$ have not been observed interacting) for a variety of $n$ (observed co-occurrences of $i$ and $j$).
+Using a Bayesian approach with an informative prior can reduce the confidence interval about $\lambda$ for a given sample size.
 A threshold interaction probability of 0.1 is indicated by the dashed red line.

### 2018-03-08 manuscript/CI_interactions.tex
made figures match in SI

@@
 
-    We find, perhaps not surprisingly, that the posterior webs for the Salix-galler network  had higher connectances than the original, observed web (C=0.028 for the observed web and 0.082$\leq$C$\leq$0.096 for the posterior webs; Fig.~\ref{posterior_webs}A).
-The number of links per \emph{Salix} species in the observed web ($L_{\emph{Salix}}$=2.71) was similar to those in the posterior webs (2.53$\leq L_{\emph{Salix}} \leq$3.19; Fig~\ref{posterior_webs}C).
-The number of links per galler, however, was lower in the observed web ($L_{galler}$=1.47) than in the posterior webs, accounting for the increased connectance (4.67$\leq L_{galler} \leq $5.88; Fig.~\ref{posterior_webs}E).
-There was a more substantial difference in the nestedness of the observed and posterior webs: the observed network had NODF=0.560 while the posterior networks were more nested (1.39 $\leq NODF \leq$1.94).
+    We find, perhaps not surprisingly, that the posterior webs for the Salix-galler network  had higher connectances than the original, observed web (C=0.028 for the observed web and 0.082 $\leq$ C $\leq$ 0.096 for the posterior webs; Fig.~\ref{posterior_webs}A).
+The number of links per \emph{Salix} species in the observed web ($L_{\emph{Salix}}$=2.71) was similar to those in the posterior webs (2.53 $\leq L_{\emph{Salix}} \leq$ 3.19; Fig~\ref{posterior_webs}C).
+The number of links per galler, however, was lower in the observed web ($L_{galler}$=1.47) than in the posterior webs, accounting for the increased connectance (4.67 $\leq L_{galler} \leq$ 5.88; Fig.~\ref{posterior_webs}E).
+There was a more substantial difference in the nestedness of the observed and posterior webs: the observed network had NODF=0.560 while the posterior networks were more nested (1.39 $\leq NODF \leq$ 1.94).
 Even the networks sampled with a detection filter of 50\% had non-zero nestedness (Fig.~\ref{posterior_webs}G).
@@
 
-    Considering the galler-natural enemy networks, the connectance, mean links per galler, and mean links per natural enemy were also much lower in the observed web (C=0.078, $L_{galler}$=9.99, and $L_{natural enemy}$=7.45, respectively) than in the posterior webs (0.186$\leq$ C $\leq$ 0.198, 13.4 $\leq L_{galler} \leq$ 14.6, and 23.4 $\leq L_{natural enemy} \leq$ 25.0).
+    Considering the galler-natural enemy networks, the connectance, mean links per galler, and mean links per natural enemy were also much lower in the observed web (C=0.078, $L_{galler}$=9.99, and $L_{natural enemy}$=7.45, respectively) than in the posterior webs (0.186 $\leq$ C $\leq$ 0.198, 13.4 $\leq L_{galler} \leq$ 14.6, and 23.4 $\leq L_{natural enemy} \leq$ 25.0).
 When the detection probability was relatively low (i.e., 50\%), however, the properties of randomised networks became similar to those in the observed webs (Fig.~\ref{posterior_webs}B,D,F).

### 2018-03-08 manuscript/supplemental.tex
made figures match in SI

@@
 \newcommand{\SI}{\textit{Appendix}~}
+\renewcommand{\thefigure}{S\arabic{figure}}
+\renewcommand{\thetable}{S\arabic{table}}
 
@@
 
-\title{Supplemental information}
+\title{A quantitative framework for investigating the reliability of network construction: supplemental information}
 
-\author{Authors}
+\author{Alyssa R. Cirtwill$^{1\dagger}$, \&  Anna Ekl\"{o}f$^{1}$, Tomas Roslin$^{2,3}$, Kate Wootton$^{2}$, Dominique Gravel$^{4}$}
 \date{\small$^1$Department of Physics, Chemistry\\ 
@@
 Link\"{o}ping, Sweden\\
-% \medskip
-% $^\dagger$ Corresponding author:\\
-% alyssa.cirtwill@gmail.com\\
-% +46 723 158464\\
+\medskip $^2$ Department of Ecology\\ P.O. Box 7044, Swedish University of Agricultural Sciences \\ SE-750 07 Uppsala, Sweden \\
+\medskip $^3$ Spatial Foodweb Ecology Group\\ Department of Agricultural Sciences \\ PO Box 27 (Latokartanonkaari 5)\\ FI-00014 University of Helsinki, Finland \\
+\medskip$^4$ D\'{e}partement de biologie\\ 
+Universit\'{e} de Sherbrooke\\ 
+Sherbrooke, Canada\\ 
+\medskip
+$^\dagger$ Corresponding author:\\
+alyssa.cirtwill@gmail.com\\
++46 723 158464\\
 }
-
 \renewcommand\Authands{ and }
@@
   Priordata is the list of interaction frequencies from the prior 
-  data, n is the number of sites with observed co-occurrence of 
-  species $i$ and $j$, and k is the number of sites with an 
+  data, $n$ is the number of sites with observed co-occurrence of 
+  species $i$ and $j$, and $k$ is the number of sites with an 
   observed interaction $ij$. When calculating the prior 
-  distribution, both n and k are 0. In the main text we assume 100\%
+  distribution, both $n$ and $k$ are 0. In the main text we assume 100\%
   confidence in observed interactions and therefore consider only 
-  cases where k=0. Only n varies between species pairs.
+  cases where $k$=0. Only $n$ varies between species pairs.
 
@@
       by~\citet{Kopelke2017} consists of a single community type sampled across 
-      Europe: willow (\emph{Salix}) species, willow-galling sawflies (
-      Hymenoptera, Tenthredinidae, Nematinae, Euurina), and their natural 
+      Europe: willow (\emph{Salix}) species, willow-galling sawflies (Hymenoptera, Tenthredinidae, Nematinae, Euurina), and their natural 
       enemies (hymenopteran parasitoids and coleopteran, lepidopteran, dipteran, 
@@
       the Arctic. Including repeated visits to a number of sites, the data set 
-      contains 641 site-visits, each of which can be considered as a network in 
-      its own right and an independent sample from which to build the 
-      meta-network. The meta-network consists of 1,173 different interactions 
+      contains 641 site-visits. The meta-network consists of 1,173 different interactions 
       between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 parasitoid 
@@
       total of 641 site-visits. We consider these to be repeated samples and 
-      take the 374 unique sites as our sample size. The high spatiotemporal 
-      resolution of this network and the unusually high sampling effort together 
-      make this dataset particularly well suited for testing Bayesian approaches 
-      to network structure.
+      take the 374 unique sites as our sample size.
 
@@
   We repeated our analyses using an alternative prior derived from a study of a similar \emph{Salix}-galler-natural enemy system in North America~\citep{Barbour2016,Barbour2016Dryad}.
-We note that this study used several genotypes of \emph{Salix hookeriana} rather than different \emph{Salix} species and so did not produce networks of similar size and connectedness to those in~\citep{Kopelke2016}.
+We note that this study used several genotypes of \emph{Salix hookeriana} rather than different \emph{Salix} species and so did not produce networks of similar size and connectedness to those in~\citep{Kopelke2017}.
 To obtain the priors based on~\citet{Barbour2016}, we estimated frequencies of  \emph{S.
@@
       Using the binary networks described above, we obtained prior parameters $\alpha$=2.51 and $\beta$=1.89 for the \emph{Salix}-galler component and $\alpha$=1.34, $\beta$=9.49 for the galler-natural enemy component of the network.
-After calculating these prior parameters, we were then able to estimate the posterior distribution of interaction probabilities given the additional information in our dataset.
-      For species where no co-occurrences were observed ($n=0$), we can calculate the estimates for the mean and variance of $\lambda_{ij}$ directly from the prior parameters following equations~\ref{mean} and~\ref{variance} (see \emph{Appendix S1} for R implementation).
+We then calculated prior distributions using these parameters.
 For the \emph{Salix}-galler network, the prior distribution was: $\bar\lambda$=0.570, var($\lambda$)=0.056.
 The prior distribution for the galler-natural enemy network was: $\bar\lambda$=0.124, var($\lambda$)=0.010.
-
-      For a pair of species with some observed co-occurrences ($n>0$), we can update the prior distribution with these data.
-If we consider only pairs of species which were observed to co-occur but not to interact, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs, giving $\alpha'$=$\alpha$ and $\beta'$=$\beta + n_{ij}$.
-As the most extreme case, consider a pair of species which co-occurred at all 374 sites and was never observed to interact.
-Using the priors described above, our distributions would become
+As with the results in the main text, we can update this prior distribution using observed co-occurrences.
+In the most extreme case where a pair of species co-occurred at all 374 sites and was never observed interacting, our distributions would become
       $\bar\lambda_{ij}$=6.63 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=1.74 $\times$ 10$^{-5}$ for the \emph{Salix}-galler network and 
       $\bar\lambda_{ij}$=3.49 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=9.03 $\times$ 10$^{-6}$ for the galler-natural enemy network.
-Distributions for both network components were close to 0 with small variance about our estimate of $\lambda$; species $i$ and $j$ are unlikely to interact at sites or times not included in our sample.
 
@@
 
-      For most pairs of species $i$ and $j$, however, $n_{ij}$ was much less than 374 and our posterior mean and variance therefore retain more of the influence of the prior.
-We can see this in the increasing means and variances as we decrease $n_{ij}$ (Fig.~\ref{Salix_pdfs}).
-The 95\% credible interval around the estimate of $\lambda$ also widens as $n_{ij}$ decreases, from (0.001, 0.017) and (\textless0.001, 0.11) for hypothetical \emph{Salix}-galler and galler-natural enemy pairs that might be observed co-occurring at all 374 sites without any observed interaction to (0.152,0.931) and (0.008, 0.364) for \emph{Salix}-galler and galler-natural enemy pairs that were never observed co-occurring.
+      The 95\% credible intervals calculated using the priors derived from~\citet{Barbour2016} were much wider than those reported in the main text (Fig.~\ref{Salix_pdfs}).
+For hypothetical \emph{Salix}-galler and galler-natural enemy pairs these intervals widened from (0.001, 0.017) and (\textless0.001, 0.11) for pairs observed co-occurring at all 374 sites without any observed interaction to (0.152,0.931) and (0.008, 0.364) for \emph{Salix}-galler and galler-natural enemy pairs that were never observed co-occurring.
 
-      If we want to be 95\% confident that the interaction probability for two species in the \emph{Salix}-galler network is below 0.1, 0.05, or 0.01, we would need 51, 106, and 550 observed co-occurrences with no observed interaction, respectively (Fig.~\ref{Salix_cdfs}; see function samples\_for\_threshold in~\emph{Appendix S1}).
-The number of samples required to be 95\% confident that the interaction probability between galler and natural enemy species is below a threshold also increases quickly as the threshold decreases; we would need 25, 62, and 352 observed co-occurrence with no observed interaction for threshold interaction probabilities of 0.1, 0.05, and 0.01, respectively.
-
-    \subsection*{Scaling up to network metrics}
-
-      We find, perhaps not surprisingly, that the posterior webs for the Salix-galler network all had much higher connectance than the original, observed web (C=0.028 for the observed web and 0.528$\leq$C$\leq$0.568 for the posterior webs; Fig.~\ref{posterior_webs}A).
-Likewise, the number of links per \emph{Salix} and galler species in the observed web ($L_{\emph{Salix}}$=2.71 and $L_{galler}$=1.47, respectively) were much lower than those predicted in the posterior webs (27.4$\leq L_{\emph{Salix}} \leq$29.5 and 50.6$\leq L_{galler} \leq $54.5, respectively; Fig.~\ref{posterior_webs}C,E), even when filtering with a detection probability of only 50\%.
-Nestedness was also much higher in the posterior networks (14.2 $\leq NODF \leq$ 15.4; Fig.~\ref{posterior_webs}G) than in the observed network (NODF=0.560).
-There are two possible explanations for these discrepancies: either the data of~\citet{Barbour2016} is simply too different from that of~\citet{Kopelke2017} to offer an appropriate prior for our dataset, or the true detection probability for links between \emph{Salix} and galler species is much less than 50\%.
-As the scale of the two datasets is quite different (genotypes of a single \emph{Salix} species in~\citet{Barbour2016}, various \emph{Salix} species in our dataset), we suspect the former is more likely.
-
-      Considering the galler-natural enemy networks, the connectance, mean links per galler, and mean links per natural enemy were also much lower in the observed web (C=0.078, $L_{galler}$=9.99, and $L_{natural enemy}$=7.45, respectively) than in the posterior webs (0.183$\leq$ C $\leq$ 0.196, 17.5 $\leq L_{galler} \leq$ 18.9, and 23.0 $\leq L_{natural enemy} \leq$ 24.8).
-When the detection probability was relatively low (i.e., 50\%), however, the properties of randomised networks became similar to those in the observed webs (Fig.~\ref{posterior_webs}B,D,F).
-Nestedness was higher in the observed network (NODF=6.85) than in the posterior networks (6.30 $\leq NODF \leq$ 6.74; Fig.~\ref{posterior_webs}H), but network structure was much more similar in the observed and posterior galler-natural enemy networks than in the \emph{Salix}-galler networks.
-The~\citet{Barbour2016} network likely provides a better prior here than for the \emph{Salix}-galler networks, as both networks included different galler and natural enemy species.
-Although the two networks differ vastly in scale, and the inclusion of multiple \emph{Salix} species likely causes structural differences from~\citet{Barbour2016} despite the similar resolution of gallers and natural enemies, this result nevertheless suggests that even such a large and well-replicated network as that in~\citet{Kopelke2017} is missing many interactions.
-This should be a strong warning to researchers comparing structural characteristics between networks - small structural differences are likely to be masked by substantial noise resulting from sampling uncertainty.
-
-      \begin{figure}[ht]
+      \begin{figure}[h!]
         \caption{Using prior distribution based on the \emph{Salix}-galler and galler-natural enemy networks in~\citet{Barbour2016}, we can calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting.
@@
         \label{Salix_pdfs}
-        \includegraphics*[width=.8\textwidth]{figures/Salix_Galler_pdfs_increasing_N.eps}
+        \begin{center}
+        \includegraphics*[width=.6\textwidth]{figures/Salix_Galler_pdfs_increasing_N.eps}
+        \end{center}
         \end{figure}
 
-      \begin{figure}[ht]
+      If we want to be 95\% confident that the interaction probability for two species in the \emph{Salix}-galler network is below 0.1, 0.05, or 0.01, we would need 51, 106, and 550 observed co-occurrences with no observed interaction, respectively (Fig.~\ref{Salix_cdfs}).
+The number of samples required to be 95\% confident that the interaction probability between galler and natural enemy species is below a threshold also increases quickly as the threshold decreases; we would need 25, 62, and 352 observed co-occurrence with no observed interaction for threshold interaction probabilities of 0.1, 0.05, and 0.01, respectively.
+
+      \begin{figure}[h!]
         \caption{The number of samples required to achieve a given level of confidence that an interaction probability $\lambda_{ij}$ is below a given threshold varies with both parameters.
@@
         \label{Salix_cdfs}
-        \includegraphics[width=.8\textwidth]{figures/Salix_Galler_samples_and_cdfs.eps}
+        \begin{center}
+        \includegraphics[width=.6\textwidth]{figures/Salix_Galler_samples_and_cdfs.eps}
+        \end{center}
+        \end{figure}
 
-        \end{figure}
+    \subsection*{Scaling up to network metrics}
+
+      We find, perhaps not surprisingly, that the posterior webs for the Salix-galler network all had much higher connectance than the original, observed web (C=0.028 for the observed web and 0.528 $\leq$ C $\leq$ 0.568 for the posterior webs; Fig.~\ref{posterior_webs}A).
+Likewise, the number of links per \emph{Salix} and galler species in the observed web ($L_{\emph{Salix}}$=2.71 and $L_{galler}$=1.47, respectively) were much lower than those predicted in the posterior webs (27.4 $\leq L_{\emph{Salix}} \leq$ 29.5 and 50.6 $\leq L_{galler} \leq $54.5, respectively; Fig.~\ref{posterior_webs}C,E), even when filtering with a detection probability of only 50\%.
+Nestedness was also much higher in the posterior networks (14.2 $\leq NODF \leq$ 15.4; Fig.~\ref{posterior_webs}G) than in the observed network (NODF=0.560).
+There are two possible explanations for these discrepancies: either the data of~\citet{Barbour2016} is simply too different from that of~\citet{Kopelke2017} to offer an appropriate prior for our dataset, or the true detection probability for links between \emph{Salix} and galler species is much less than 50\%.
+As the scale of the two datasets is quite different (genotypes of a single \emph{Salix} species in~\citet{Barbour2016}, various \emph{Salix} species in our dataset), we suspect the former is more likely.
+
+      Considering the galler-natural enemy networks, the connectance, mean links per galler, and mean links per natural enemy were also much lower in the observed web (C=0.078, $L_{galler}$=9.99, and $L_{natural enemy}$=7.45, respectively) than in the posterior webs (0.183 $\leq$ C $\leq$ 0.196, 17.5 $\leq L_{galler} \leq$ 18.9, and 23.0 $\leq L_{natural enemy} \leq$ 24.8).
+When the detection probability was relatively low (i.e., 50\%), however, the properties of randomised networks became similar to those in the observed webs (Fig.~\ref{posterior_webs}B,D,F).
+Nestedness was higher in the observed network (NODF=6.85) than in the posterior networks (6.30 $\leq NODF \leq$ 6.74; Fig.~\ref{posterior_webs}H), but network structure was much more similar in the observed and posterior galler-natural enemy networks than in the \emph{Salix}-galler networks.
+The~\citet{Barbour2016} network likely provides a better prior here than for the \emph{Salix}-galler networks, as both networks included different galler and natural enemy species.
+Although the two networks differ vastly in scale, and the inclusion of multiple \emph{Salix} species likely causes structural differences from~\citet{Barbour2016} despite the similar resolution of gallers and natural enemies, this result nevertheless suggests that even such a large and well-replicated network as that in~\citet{Kopelke2017} is missing many interactions.
+This should be a strong warning to researchers comparing structural characteristics between networks - small structural differences are likely to be masked by substantial noise resulting from sampling uncertainty.
 
@@
       \label{posterior_webs}    
-      \includegraphics[width=.8\textwidth]{Figures/Salix_Galler_posterior_properties.eps}
+      \begin{center}
+      \includegraphics[width=.6\textwidth]{Figures/Salix_Galler_posterior_properties.eps}
+      \end{center}
       \end{figure}
+
+  \clearpage
 

### 2018-03-08 code/figure_generation/pdfs_and_N.py

@@ -120,12 +120,15 @@ def format_graph(graph,nettype):
   graph.world.xmin=0
   if nettype=='SG':
     graph.world.xmax=.1
+    # graph.world.xmax=.8
     major=.02
+    # major=.2
   else:
     graph.world.xmax=.3000001
     major=.05
   graph.world.ymin=-0
   graph.world.ymax=72
+  # graph.world.ymax=55
 
   graph.yaxis.tick.configure(major=50,onoff='off',minor_ticks=0,major_size=.7,minor_size=.5,place='both',major_linewidth=1,minor_linewidth=1)
   graph.yaxis.ticklabel.configure(char_size=0,format='decimal',prec=0)
@@ -138,7 +141,9 @@ def format_graph(graph,nettype):
   graph.yaxis.label.configure(text="Probability density",char_size=1,just=2)
   graph.legend.configure(box_linestyle=0,fill=0,fill_pattern=0,char_size=.75,
     loc=(0.08,35),loctype='world',size=2)
+    # loc=(0.625,35),loctype='world',size=2)
   if nettype=='SG':
+    # graph.add_drawing_object(DrawText,text="N",x=0.665,y=35.5,char_size=.75,just=2,loctype='world')
     graph.add_drawing_object(DrawText,text="N",x=0.085,y=35.5,char_size=.75,just=2,loctype='world')
   graph.panel_label.configure(placement='iur',char_size=.75,dx=.02,dy=.02)
 
@@ -211,3 +216,4 @@ grace.hide_redundant_labels()
 grace.set_col_yaxislabel(rowspan=(None,None),col=0,label="Probability density",just=2,char_size=1,perpendicular_offset=.04)
 
 grace.write_file('../../manuscript/figures/Salix_Galler_pdfs_increasing_N_Zillis.eps')
+# grace.write_file('../../manuscript/figures/Salix_Galler_pdfs_increasing_N.eps')

### 2018-03-08 code/figure_generation/samples_for_thresholds.py

@@ -31,6 +31,8 @@
 
 # write.table(samples,file='../../data/Salix_example/Zillis/Salix_Galler/samples_for_threshold.tsv',sep='\t')
 # write.table(CDFs,file='../../data/Salix_example/Zillis/Salix_Galler/samplefigure.tsv',sep='\t')
+# # write.table(samples,file='../data/Salix_example/Salix_Galler/samples_for_threshold.tsv',sep='\t')
+# # write.table(CDFs,file='../data/Salix_example/Salix_Galler/samplefigure.tsv',sep='\t')
 
 
 # # Galler-parasitoid stuff
@@ -68,6 +70,8 @@
 
 # write.table(gp_samples,file='../../data/Salix_example/Zillis/Galler_Parasitoid/samples_for_threshold.tsv',sep='\t')
 # write.table(gp_CDFs,file='../../data/Salix_example/Zillis/Galler_Parasitoid/samplefigure.tsv',sep='\t')
+# # write.table(gp_samples,file='../data/Salix_example/Galler_Parasitoid/samples_for_threshold.tsv',sep='\t')
+# # write.table(gp_CDFs,file='../data/Salix_example/Galler_Parasitoid/samplefigure.tsv',sep='\t')
 
 import sys
 import math
@@ -106,8 +110,10 @@ def read_Rfiles(filename,nettype):
 
   if nettype=='SG':
     g=open('../../data/Salix_example/Zillis/Salix_Galler/samples_for_threshold.tsv','r')
+    # g=open('../../data/Salix_example/Salix_Galler/samples_for_threshold.tsv','r')
   else:
     g=open('../../data/Salix_example/Zillis/Galler_Parasitoid/samples_for_threshold.tsv','r')    
+    # g=open('../../data/Salix_example/Galler_Parasitoid/samples_for_threshold.tsv','r')    
   for line in g:
     if line.split()[0]!='"Threshold"':
       threshold=float(line.split()[1])
@@ -142,6 +148,8 @@ def format_graph(graph,nettype):
     major=50
   graph.world.ymin=-0
   graph.world.ymax=1
+  # graph.world.xmax=750
+  # major=250
 
   graph.yaxis.tick.configure(major=.20,onoff='on',minor_ticks=1,major_size=.5,minor_size=.3,place='normal',major_linewidth=1,minor_linewidth=1)
   graph.yaxis.ticklabel.configure(char_size=.75,format='decimal',prec=1)
[…]

### 2018-03-09 manuscript/CI_interactions.tex
old changes

--- 2018-03-08 manuscript/CI_interactions.tex
@@
 
-    Representing an assemblage of species as a network offers a convenient summary of how the community is constructed as a network simultaneously describes species composition and interactions between species.
+    Representating an assemblage of species as a network offers a convenient summary of how the community is constructed as it simultaneously accounts for species composition and interactions between species.
 A tabulation of the nodes (species) and their relative abundances forms the basis for traditional metrics of community composition.
@@
 
-    The assumption of static communities contrasts significantly with the widely recognised stochasticity of ecological communities~\citep{Gotelli2000}.
+    The assumption of static communities contrasts significantly with the widely recognized stochasticity of ecological communities~\citep{Gotelli2000}.
 Community composition and species abundances vary from site to site~\citep{Baiser2012} and over time within a site~\citep{Olesen2011a}.
 Likewise, interactions vary over space~\citep{Kitching1987,Baiser2012}, time~\citep{Kitching1987,Olesen2011a}, and between individuals of a given species~\citep{Pires2011a,Fodrie2015,Novak2015}.
-We emphasise that variability in community composition and interactions may or may not be closely related.
+Moreover, variability in community composition and interactions may or may not be closely related.
 The removal of a species from a site will obviously also remove its interactions but, conversely, the co-occurrence of potentially interacting species does not in itself guarantee that they will interact at a given place and time.
@@
 
-    In this study, we formalize the description of interactions between species as probabilities and develop analytical tools to capture the uncertainty in the estimation of pairwise interactions.
+    In this study, we develop analytical tools to capture the uncertainty in the estimation of pairwise interactions.
 We focus on binary interactions as a first step, but the framework could be expanded to deal with interaction frequencies and strength.
@@
 The ecologist wanting to describe the network, however, is specifically interested in the situation where $L = 0$ (i.e., in true absences).
-Thus, while there is have no difficulty interpreting the observation of an interaction, the observation of an absence of an interaction offers more of a challenge since it must be decomposed into different quantities.
+Thus, while there is have no difficulty interpreting the observation of an interaction, the observation of an absence of an interaction offers more of a challence since it must be decomposed into different quantities.
 It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e.
@@
 
-  [[Tomas suggests removing the following because it slows down proceedings, Anna and Dom want it back. Shortening sounds like a good middle ground:]]
+  [[Tomas suggests removing the following because it slows down procedings, Anna and Dom want it back. Shortening sounds like a good middle ground:]]
   The basic information that we are collecting consists of matrices of interaction partners.
@@
    [[Move this paragraph to intro?]] It is getting more and more common to represent interactions as probabilities in theoretical models of network structure.
-For example, the minimum potential model introduces gaps in the feeding niche of predators by sampling based on the likelihood of each interaction~\citep{Allesina2008}, while a Gaussian probability function is used to represent the niche by~\citet{Williams2010}.
+For example, the minimum potential model introduces gaps in the feeding niche of predators by sampling based on the likelihood of each interaction~\citep{Allesina2008}, while a gaussian probability function is used to represent the niche by~\citet{Williams2010}.
 \citet{Eklof2013} also introduced variability  in the computation of network dimensions, allowing the absence of interactions within the n-dimension niche of every species.
@@
 Suppose we have $n = 10$ observations of co-occurrence between species $i$ and species $j$ in a given time interval and area, and $k = 3$ observations of interactions.
-The maximum likelihood estimate of the interaction probability (Box~\ref{box2}) is simply $\lambda_{MLE} = 3/10 = 0.3$.
+The maximum likelihood estimate of the interaction probability (Box~\ref{Box2}) is simply $\lambda_{MLE} = 3/10 = 0.3$.
 
@@
 Network data for a similar study system may, however, not be available.
-In that case, one might use the first sub-network collected as ``training data" to guide future sampling.
-To simulate this situation, we created priors using a single sub-network from the middle of the geographical distribution of the~\citep{Kopelke2017} dataset (Zillis sub-network).
+In that case, one might use the first subnetwork collected as ``training data" to guide future sampling.
+To simulate this situation, we created priors using a single subnetwork from the middle of the geographical distribution of the~\citep{Kopelke2017} dataset (Zillis subweb).
 To demonstrate how the use of a data from a different system can affect the prior distribution and conclusions based on it, we repeated our analyses using priors derived from a much smaller \emph{Salix}-galler-natural enemy system~\citep{Barbour2016,Barbour2016Dryad}.
-This smaller system was much more densely-connected than that described in~\citet{Kopelke2017} and provided unreasonable distributions for interaction probabilities (\emph{Appendix S4}).
+This smaller system was much more densely-connected than that described in~\citet{Kopelke2017} and provided unreasonable distributions for interaction probabilities (\emph{Appendix SX}).
 
-      To obtain the priors based on the Zillis sub-network, we estimated frequencies of \emph{Salix}-galler interactions based on the normalised degree of each species in each network component (see \emph{Appendix S3} for details and code).
+      To obtain the priors based on the Zillis subweb, we estimated frequencies of \emph{Salix}-galler interactions based on the normalised degree of each species in each network component (see \emph{Appendix S3} for details and code).
 Specifically, we obtained prior parameters of $\alpha$=8.72, $\beta$=305 for the \emph{Salix}-galler component and $\alpha$=0.700, $\beta$=8.49 for the galler-natural enemy components of the network.
@@
 The prior distribution for the galler-natural enemy network was: $\bar\lambda$=0.076, var($\lambda$)=0.008.
-The posterior interaction probabilities obtained based on the Zillis sub-network were much lower than those obtained based on~\citet{Barbour2016}; this emphasises the importance of using an appropriate study system when constructing a prior (\emph{Appendix S4}).
+The posterior interaction probabilities obtained based on the Zillis subweb were much lower than those obtained based on~\citet{Barbour2016}; this emphasises the importance of using an appropriate study system when constructing a prior (\emph{Appendix SX}).
 
@@
 
-% %DG: the following subsection could be moved to the appendix if we need to cut down
-% Add to appendix.
-
-%   \subsection*{Computing the credible interval around a probability estimate}
-
-%       As well as obtaining posterior means and variances, it is possible to calculate a 95\% credible interval about the posterior mean.
-This is again straightforward to do in R (see the function ``credible\_interval" in \emph{Appendix S2}).
-Calculating the 95\% credible intervals for species pairs with 0 to 50 observed co-occurrences without any observed interaction (as in Fig.~\ref{Salix_pdfs}), we see that the interval narrows dramatically as the number of observations increases.
-In no case, however, does the confidence interval include 0.
-Even for a pair of species which appeared together in all 374 sites but were never observed interacting, the confidence interval (0.001, 0.018) comes close to, but does not include zero (Table~\ref{interval_table}).
-In other words, even with a very large data set, we will have problems in establishing that a given species pair can never interact.
-
-%       % # R code to make the table:
-%       % output=matrix(nrow=length(ns),ncol=5)
-%       % ns=c(0,1,2,5,10,15,20,25,50,100,150,200,374)
-%       % output[,1]=ns
-%       % for(r in 1:nrow(output)){
-%       %   interval1=credible_interval(calculate_parameters(sg_int_probs,ns[r],0),0.025,0.975)    
-%       %   interval2=credible_interval(calculate_parameters(gp_int_probs,ns[r],0),0.025,0.975)    
-%       %   output[r,2:3]=interval1
-%       %   output[r,4:5]=interval2
-%       % }
-
-%       \begin{table}[h]
-%         \caption{95\% credible intervals for the interaction probability of two species that co-occur in $N$ sites but are never observed to interact, obtained using prior information from the \emph{Salix}-galler network in~\citet{Barbour2016,Barbour2016Dryad}.
-[Tomas notes that this is conceptually very similar to Fig.~\ref{Salix_pdfs}]}
-%         \label{interval_table}
-%         \begin{tabular}{l | c c | c c }
-%         \multirow{2}{*}{N} & \multicolumn{2}{c}{\emph{Salix}-galler} & \multicolumn{2}{c}{galler-natural enemy}\\
-%          & Lower bound & Upper bound \\
-%         \hline
-%         0   & 0.152 & 0.931 & 0.008 & 0.364 \\
-%         1   & 0.110 & 0.843 & 0.007 & 0.337 \\
-%         2   & 0.087 & 0.760 & 0.006 & 0.313 \\
-%         5   & 0.053 & 0.573 & 0.005 & 0.258 \\
-%         10  & 0.033 & 0.400 & 0.004 & 0.200 \\
-%         15  & 0.023 & 0.306 & 0.003 & 0.163 \\
-%         20  & 0.018 & 0.247 & 0.003 & 0.137 \\
-%         25  & 0.015 & 0.208 & 0.002 & 0.119 \\
-%         50  & 0.008 & 0.115 & 0.001 & 0.071 \\
-%         100 & 0.004 & 0.061 & 0.001 & 0.039 \\
-%         150 & 0.003 & 0.041 & \textless0.001 & 0.027 \\
-%         200 & 0.002 & 0.031 & \textless0.001 & 0.021 \\
-%         \hline
-%         374 & 0.001 & 0.017 & \textless0.001 & 0.011 \\
-%         \hline
-%         \end{tabular}
-%         \end{table}
-
   \subsection*{How many samples are required to reach a minimal precision}
@@
 In our dataset, the entire 95\% credible interval was (0.013, 0.049).
-We may therefore be 95\% confident that the interaction probability for \emph{Salix} and galler species that have not been observed co-occurring is below 0.05.
-As the peak of the prior distribution for the probability of interaction between \emph{Salix} and galler probabilities is around 0.02 (Fig.~\ref{Salix_pdfs}), to be 95\% confident that the interaction probability for these species is below 0.01 would require 1029 observed co-occurrences with no interaction - far more than the number of sites in the~\citep{Kopelke2017} dataset.
+We may therefore be 95\% confident that the interaction probability for \emph{Salix} and galler species that have not been observed cooccurring is below 0.05.
+To be 95\% confident that the interaction probability for these species is below 0.01 would require 139 observed co-occurrences with no interaction.
 
-      The number of samples required to be 95\% confident that the interaction probability between galler and natural enemy species is below a threshold also increases quickly as the threshold decreases.
+      The number of samples required to be 95\% confident that the interaction probability between galler and natural enemy species is below a threshold also increases quickly as the threshold decreasesy.
 The 95\% credible interval is (0.0005, 0.303) for the probability of interaction between two species observed to co-occur but never interact.
-To be 95\% confident that the probability of interaction is below 0.1, 0.05, or 0.01 would require 15, 39, and 229 observed co-occurrences, respectively.
+To be 95\% confident that the probability of interaction is below 0.1, 0.05, or 0.001 would require 15, 39, and 229 observed co-occurrances, respectively.
 
@@
 
-    We find, perhaps not surprisingly, that the posterior webs for the Salix-galler network  had higher connectances than the original, observed web (C=0.028 for the observed web and 0.082$\leq$C$\leq$0.096 for the posterior webs; Fig.~\ref{posterior_webs}A).
-The number of links per \emph{Salix} species in the observed web ($L_{\emph{Salix}}$=2.71 was similar to those in the posterior webs (2.53$\leq L_{\emph{Salix}} \leq$3.19; Fig~\ref{posterior_webs}C).
-The number of links per galler, however, was lower in the observed web ($L_{galler}$=1.47) than in the posterior webs, accounting for the increased connectance (4.67$\leq L_{galler} \leq $5.88; Fig.~\ref{posterior_webs}E).
-There was a more substantial difference in the nestedness of the observed and posterior webs: the observed network had NODF=0.560 while the posterior networks were more nested (1.39 $\leq NODF \leq$1.94).
-Even the networks sampled with a detection filter of 50\% had non-zero nestedness (Fig.~\ref{posterior_webs}G).
-This last result highlights the potential for the possibility for network structure to vary when considering the possibility that unobserved species pairs may interact.
-
+    We find, perhaps not surprisingly, that the posterior webs for the Salix-galler network all had much higher connectance than the original, observed web (C=0.028 for the observed web and 0.528$\leq$C$\leq$0.568 for the posterior webs; Fig.~\ref{posterior_webs}A).
+Likewise, the number of links per \emph{Salix} and galler species in the observed web ($L_{\emph{Salix}}$=2.71 and $L_{galler}$=1.47, respectively) were much lower than those predicted in the posterior webs (27.4$\leq L_{\emph{Salix}} \leq$29.5 and 50.6$\leq L_{galler} \leq $54.5, respectively; Fig.~\ref{posterior_webs}C,E), even when filtering with a detection probability of only 50\%.
+There are two possible explanations for this discrepancy: either the data of~\citet{Barbour2016} is simply too different from that of~\citet{Kopelke2017} to offer an appropriate prior for our dataset, or the true detection probability for links between \emph{Salix} and galler species is much less than 50\%.
+As the scale of the two datasets is quite different (genotypes of a single \emph{Salix} species in~\citet{Barbour2016}, various \emph{Salix} species in our dataset), we suspect the former is more likely.
 %    [[This is a little boring. Tomas has ideas for people with potentially better priors - may require another co-author. Also maybe could use one site as a prior like ``training data"?]]
@@
 %%AE: If we are doing a complement here (I agree it is a bit boring) I think option c) from Alyssas mail is the most straight forward option.
-% AC: Added nestedness and replaced the Barbour data with training data from one site. Couldn't find any good published data.
 
-    Considering the galler-natural enemy networks, the connectance, mean links per galler, and mean links per natural enemy were also much lower in the observed web (C=0.078, $L_{galler}$=9.99, and $L_{natural enemy}$=7.45, respectively) than in the posterior webs (0.186$\leq$ C $\leq$ 0.198, 13.4 $\leq L_{galler} \leq$ 14.6, and 23.4 $\leq L_{natural enemy} \leq$ 25.0).
+    Considering the galler-natural enemy networks, the connectance, mean links per galler, and mean links per natural enemy were also much lower in the observed web (C=0.078, $L_{galler}$=9.99, and $L_{natural enemy}$=7.45, respectively) than in the posterior webs (0.183$\leq$ C $\leq$ 0.196, 17.5 $\leq L_{galler} \leq$ 18.9, and 23.0 $\leq L_{natural enemy} \leq$ 24.8).
 When the detection probability was relatively low (i.e., 50\%), however, the properties of randomised networks became similar to those in the observed webs (Fig.~\ref{posterior_webs}B,D,F).
-Nestedness was higher in the observed network (NODF=6.85) than in the posterior webs (6.31 $\leq NODF \leq$ 6.82; Fig.~\ref{posterior_webs}H); in this case, the stronger the detection filter the farther apart were the observed and posterior webs.
+The~\citet{Barbour2016} network likely provides a better prior here than for the \emph{Salix}-galler networks, as both networks included different galler and natural enemy species.
+Although the two networks differ vastly in scale, and the inclusion of multiple \emph{Salix} species likely causes structural differences from~\citet{Barbour2016} despite the similar resolution of gallers and natural enemies, this result nevertheless suggests that even such a large and well-replicated network as that in~\citet{Kopelke2017} is missing many interactions.
+This should be a strong warning to researchers comparing structural characteristics between networks - small structural differences are likely to be masked by substantial noise resulting from sampling uncertainty.
 
@@
 This dataset consists of a single community type sampled across Europe: willow (\emph{Salix}) species, willow-galling sawflies, and their natural enemies.
-The data were collected over 29 years at 374 unique locations across Europe with a total of 641 site visits.
-Each site visit or each unique site can be considered as a network in its own right or as an independent sample from which to build the meta-network.
-Here we take the more conservative approach and pool visits to the same site for a sample size of 374 sub-networks.
+The data were collected over 29 years at 374 unique locations across Europe, with a total of 641 site visits.
+Each site visit can be considered as a network in its own right or as an independent sample from which to build the meta-network.
 The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes.
 The high spatiotemporal resolution of this network and the unusually high sampling effort implemented at the site level makes this dataset particularly well suited for illustrating the difficulties in completely sampling a network and testing Bayesian approaches to overcome these difficulties.\\
-    \indent We may begin by comparing the frequency of co-occurrences for pairs of species in each part of the network to reveal the challenge of having sufficient sampling to be confident that an interaction does not occur.
-Most pairs of species (3,986/4,992 \emph{Salix}-galler pairs and  9,794/12,096 galler-natural enemy pairs) are never found co-occurring and, for species that did occur together, the total number of co-occurrences was generally low (mean=4.24, variance=36.3 for \emph{Salix}-galler pairs; mean=3.87, variance=28.8 for galler-natural enemy pairs; Fig.~\ref{histograms}A-B).
+    \indent We may begin by comparing the frequency of co-occurences for pairs of species in each part of the network to reveal the challenge of having sufficient sampling to be confident that an interaction does not occur.
+Most pairs of species (3986/4992 \emph{Salix}-galler pairs and  9794/12096 galler-natural enemy pairs) are never found co-occurring and, even for species that did occur, the total number of co-occurrences was generally low (mean=4.24, variance=36.3 for \emph{Salix}-galler pairs; mean=3.87, variance=28.8 for galler-natural enemy pairs; Fig.~\ref{histograms}A-B).
 The bulk of these co-occurring species pairs were never observed to interact: only 2.82\% of \emph{Salix}-galler pairs and 7.76\% of galler-natural enemy pairs were observed interacting at one or more sites.
@@
 Thus, even in the most extensive data set that we could find, there was very little empirical data for each species pair.
-This suggests that limited sampling is a major source of uncertainty in all empirical networks.
-This dataset also illustrates the potential for increased sampling to not necessarily reveal more interactions as a pair of species that is able to interact may not be observed interacting in all samples where the pair co-occurs (Fig.~\ref{histograms}E-F).
+This suggests that limited sampling is a major source of uncertainty.
+This dataset also illustrates the potential for increased sampling to not necessarily reveal more interactions as a pair of species that interacts in some cases may not be observed interacting in all cases (Fig.~\ref{histograms}E-F).
   \caption{\emph{Salix} dataset}
@@
 These parameters can then be used to calculate a credible interval using the R~\citep{R} function qbeta.
-In the table below, we present the 95\% credible intervals for \emph{Salix}-galler and galler-natural enemy pairs with different numbers of observed co-occurrences ($n$) and no observed interactions ($k=0$).
-Both sets of intervals rely on prior information derived from the Zillis sub-network~\citep{Kopelke2017}.
+In the table below, we present the 95\% credible intervals for \emph{Salix}-galler and galler-natural enemy paris with different numbers of observed co-occurrences ($n$) and no observed interactions ($k=0$).
+Both sets of intervals rely on prior information from the network in~\citet{Barbour2016,Barbour2016Dryad}.
 
-      % % # R code to make the table:
+      % # R code to make the table:
+      % output=matrix(nrow=length(ns),ncol=5)
       % ns=c(0,1,2,5,10,15,20,25,50,100,150,200,374)
-      % output=matrix(nrow=length(ns),ncol=5)
       % output[,1]=ns
@@
         \multirow{2}{*}{$n$} & \multicolumn{2}{c}{\emph{Salix}-galler} & \multicolumn{2}{c}{galler-natural enemy}\\
-         & Lower bound & Upper bound & Lower bound & Upper bound \\
+         & Lower bound & Upper bound \\
         \hline
-        0   & 0.013 & 0.049 & 5.39 $\times10^{-4}$ & 0.304 \\
-        1   & 0.013 & 0.048 & 4.82 $\times10^{-4}$ & 0.276 \\
-        2   & 0.013 & 0.048 & 4.35 $\times10^{-4}$ & 0.253 \\
-        5   & 0.012 & 0.048 & 3.37 $\times10^{-4}$ & 0.203 \\
-        10  & 0.012 & 0.047 & 2.45 $\times10^{-4}$ & 0.152 \\
-        15  & 0.012 & 0.046 & 1.93 $\times10^{-4}$ & 0.121 \\
-        20  & 0.012 & 0.046 & 1.59 $\times10^{-4}$ & 0.101 \\
-        25  & 0.012 & 0.045 & 1.35 $\times10^{-4}$ & 0.087 \\
-        50  & 0.011 & 0.042 & 7.72 $\times10^{-5}$ & 0.050 \\
-        100 & 0.010 & 0.037 & 4.16 $\times10^{-5}$ & 0.027 \\
-        150 & 0.009 & 0.033 & 2.84 $\times10^{-5}$ & 0.019 \\
-        200 & 0.008 & 0.030 & 2.16 $\times10^{-5}$ & 0.014 \\
+        0   & 0.152 & 0.931 & 0.008 & 0.364 \\
+        1   & 0.110 & 0.843 & 0.007 & 0.337 \\
+        2   & 0.087 & 0.760 & 0.006 & 0.313 \\
+        5   & 0.053 & 0.573 & 0.005 & 0.258 \\
+        10  & 0.033 & 0.400 & 0.004 & 0.200 \\
+        15  & 0.023 & 0.306 & 0.003 & 0.163 \\
+        20  & 0.018 & 0.247 & 0.003 & 0.137 \\
+        25  & 0.015 & 0.208 & 0.002 & 0.119 \\
+        50  & 0.008 & 0.115 & 0.001 & 0.071 \\
+        100 & 0.004 & 0.061 & 0.001 & 0.039 \\
+        150 & 0.003 & 0.041 & \textless0.001 & 0.027 \\
+        200 & 0.002 & 0.031 & \textless0.001 & 0.021 \\
         \hline
-        374 & 0.006 & 0.022 & 1.18 $\times10^{-5}$ & 0.008 \\
+        374 & 0.001 & 0.017 & \textless0.001 & 0.011 \\
         \hline
@@
 Here we show a histogram of the number of observed interactions within pairs of co-occurring species.
-Species which co-occurred but never interacted are included in these histograms.
 \textbf{E-F)} Here we show, for each species pair, the number of observed interactions plotted against the number of observed co-occurrences.
@@
   \begin{figure}[h!]
-    \caption{A simple example will illustrate the problem of imperfect detection of interactions.
+    \caption{A simple example will illustrate the problem of imperfect detection of interactions (the full reasoning is provided below).
 Assume that we want to infer the probability of an interaction between two species, $i$ and $j$.
 Now assume that in reality, interaction between $i$ and $j$ is completely impossible (i.e.
-the true $\lambda=0$) but the observer does not know this and seeks to estimate this interaction probability ($\lambda$).
-The number of observed interactions will follow a binomial distribution with number of interactions $k$ and number of observations $n$.
+the true $\lambda=0$), but the observer does not know this and seeks to estimate this interaction probability ($\lambda$).
+The number of observed interactions will follow a binomial distribution, with number of interactions $k$ and number of observations $n$.
 Using this distribution, we can compute the credible interval of the estimated probability $\lambda$.
-Even assuming no added detection error in observing the incidence of the interaction, a single observation of species co-occurrence reveals very little regarding the probability of the interaction as the credible interval for a pair of species with one observation essentially spans from 0 to 1.
-Only with 35 observations will the upper limit of the credible interval be lowered to 0.1.
-Thus, adding more observations is certainly useful in controlling uncertainty, but the number of observations added needs to be very high.
-Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true credible interval for $\lambda$ when $k=0$ ($i$ and $j$ have not been observed interacting) for a variety of $n$ (observed co-occurrences of $i$ and $j$).
-A threshold interaction probability of 0.1 is indicated by the dashed red line.
+Assuming no added detection error in observing the incidence of the interaction, a single observation of species co-occurrence will reveal very little regarding the probability of the interaction as the credible interval for a pair of species with one observation essentially spans from 0 to 1.
+Only with thirty observations will the upper limit of the credible interval be lowered to 0.1.
+Thus, adding more observations is certainly useful in controlling uncertainty, but the number of observations nonetheless needs to be very high.
+Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true credible interval for $\lambda$ when $k=0$ ($i$ and $j$ have not been observed interacting) for a variety of $n$ (observed co-occurences of $i$ and $j$).
+A threshold interaction probability of 0.1 is indicated by the dotted red line.
 }
@@
 %DG: otherwise the difference between the two interaction types is very interesting and useful to show the effect of the priors. Bravo ! 
-
+[[Update these two figs with Zillis data.]]
       \begin{figure}[ht]
-        \caption{Using prior distributions based on the \emph{Salix}-galler and galler-natural enemy networks sampled at a single site in~\citet{Kopelke2017}, we can calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting.
-Here we show posterior distributions for $\lambda$ in each network component ranging from the prior distribution ($n=0$ observed co-occurrence) to the distribution obtained when the pair of species has been observed co-occurring 100 times.
+        \caption{Using prior distribution based on the \emph{Salix}-galler and galler-natural enemy networks in~\citet{Barbour2016}, we can calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting.
+Here we show posterior distributions for each $\lambda$ in each network ranging from the prior distribution ($n=0$ observed co-occurrence) to the distribution obtained when the pair of species has been observed co-occurring 100 times.
 The distribution narrows and approaches zero as the sample size increases.
 Likewise, the maximum likelihood estimator for the mean probability of interaction (diamonds at top of each panel) approaches zero and the 95\% credible interval (lines at top of each panel) narrows as sample size increases.
-\textbf{A)} The posterior distributions for $\lambda$ in the \emph{Salix}-galler component are narrower at low $n$ but shrink less with increased sampling than those for \textbf{B)} the distributions of $\lambda$ in the galler-natural enemy component.}
+\textbf{A)} The posterior distributions for the \emph{Salix}-galler component are always wider and farther from zero than those for \textbf{B)} the galler-natural enemy component.
+This is likely because the prior distribution for the galler-natural enemy component of the network was both narrower and had a mean closer to that in the~\citet{Kopelke2017} data than did the \emph{Salix}-galler component.}
         \label{Salix_pdfs}
@@
 The large ticks along the x-axis indicate the number of samples associated with each of these points.
-\textbf{A)} In the \emph{Salix}-galler network component, the 95\% credible interval for $\lambda_{ij}$ when $n$=0 was (0.013, 0.049).
-We can therefore be at least 95\% confident that $\lambda_{ij}$ is below thresholds of 0.1 or 0.05 without any observed co-occurrence of species $i$ and $j$.
-To be confident that $\lambda_{ij}$ is less than 0.01, however, would require more observed co-occurrences than there are sites in our dataset.
-\textbf{B)} In the galler-parasitoid network component, the 95\% credible interval for $\lambda_{ij}$ was substantially broader and many observed co-occurrences ($\approx$ 15-35) are required to be 95\% confident that $\lambda_{ij}$ is below thresholds of 0.1 or 0.05.}
+Note that the number of samples required to reach any given threshold is larger for \textbf{A)} the \emph{Salix}-galler network than for \textbf{B)} the galler-natural enemy network.
+In the galler-natural enemy network, the credible interval for a pair of species with no observed co-occurrances was 0.364.
+All pairs of species therefore have $\lambda$\textless0.5.}
         \label{Salix_cdfs}
@@
 
+    % \begin{figure}[ht]
+    % \caption{Here we show the mean connectance, links per resource (\emph{Salix} in the \emph{Salix}-galler networks and gallers in the galler-natural enemy networks), and links per consumer for networks assembled using posterior distributions based on a smaller, North American \emph{Salix}-galler-natural enemy system~\citep{Barbour2016,Barbour2016Dryad}.
+We created 100 ``posterior-sampling" networks and then, for each of these, created 100 ``detection-filter" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network.
+This simulates imperfect detection of interactions in the field.
+Each point represents the mean network property (e.g., connectance) obtained from a set of 100 detection-filter networks, plotted against the value of the network property in the posterior-sampling network used to create the detection-filter networks.
+For each property and both network types, the posterior-sampling networks cover a relatively small range of network properties than the range covered by networks with varying detection probabilities.
+The value of each property decreases with the proportion of links included in the detection-filter networks.}
+    % \label{posterior_webs}    
+    % \includegraphics[width=.8\textwidth]{Figures/Salix_Galler_posterior_properties.eps}
+    % \end{figure}
+
     \begin{figure}[ht]
-    \caption{Here we show the mean connectance, links per resource (\emph{Salix} in the \emph{Salix}-galler networks and gallers in the galler-natural enemy networks), links per consumer, and nestedness (NODF) for networks assembled using posterior distributions based on a single sub-network in the~\citet{Kopelke2017} dataset (Zillis).
+    \caption{Here we show the mean connectance, links per resource (\emph{Salix} in the \emph{Salix}-galler networks and gallers in the galler-natural enemy networks), and links per consumer for networks assembled using posterior distributions based on a single subweb in the~\citet{Kopelke2017} dataset (Zillis).
 We created 100 ``posterior-sampling" networks and then, for each of these, created 100 ``detection-filter" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network.

### 2018-03-19 manuscript/CI_interactions.tex
converted bib to Ecol Lett style

--- 2018-03-08 manuscript/CI_interactions.tex
@@
 This contrasts with the known stochasticity of ecological communities: community composition, species abundances, and link structure all vary in space and time.
-On top of this, finite sampling will generate variation in the set of interactions that are actually observed.
-Despite recognising these challenges, we lack the quantitative methodology to deal with the uncertainty generated by “true” spatiotemporal variation in ecological interactions or by incomplete sampling.
-Here we develop analytical tools to capture the uncertainty in the estimation of pairwise interactions.
-To define the problem, we identify the different contributions to the uncertainty of an interaction and discuss the implications of this uncertainty in the estimation of network properties.
-We then develop a framework to explicitly quantify the uncertainty around each interaction.
-We illustrate this framework using the most extensively sampled network to date, demonstrating the universal uncertainty in network studies.
-Finally, we offer tangible recommendations for improving descriptions of ecological networks and for better sampling of rare interactions.
-Through these efforts, we demonstrate both the utility of our approach and the importance of acknowledging the uncertainty inherent in network studies.
+Moreover, finite sampling generates variation in the set of interactions actually observed.
+Here we develop the conceptual and analytical tools needed to capture uncertainty in the estimation of pairwise interactions.
+To define the problem, we identify the different contributions to the uncertainty of an interaction and its implications for the estimation of network properties.
+We then outline a framework to quantify the uncertainty around each interaction.
+We illustrate this framework using the most extensively sampled network to date.
+Finally, we offer both code and tangible recommendations for improving descriptions of ecological networks and sampling of rare interactions.
+Through these efforts, we demonstrate the utility of our approach and the importance of acknowledging the uncertainty inherent in network studies.
+Most importantly, we stress that networks are best thought of as systems constructed from random variables, the stochastic nature of which must be acknowledged for an accurate representation.
+Doing so will fundamentally change networks analyses, but should lead to greater realism.
 
@@
 We illustrate this framework using the most extensively sampled network to date (Box 1).
-Finally, we offer tangible recommendations for improved descriptors of ecological interactions [[double-check that we do this]].
+Finally, we offer tangible recommendations for improved descriptors of ecological interactions.
 Through these efforts, we demonstrate both the utility of our approach and the importance of acknowledging the uncertainty inherent in network studies.
@@
 
-      % %DG: the following subsection could be moved to the appendix if we need to cut down
-      % Add to appendix.
-
-      %   \subsection*{Computing the credible interval around a probability estimate}
-
-      %       As well as obtaining posterior means and variances, it is possible to calculate a 95\% credible interval about the posterior mean.
-This is again straightforward to do in R (see the function ``credible\_interval" in \emph{Appendix S2}).
-Calculating the 95\% credible intervals for species pairs with 0 to 50 observed co-occurrences without any observed interaction (as in Fig.~\ref{Salix_pdfs}), we see that the interval narrows dramatically as the number of observations increases.
-In no case, however, does the confidence interval include 0.
-Even for a pair of species which appeared together in all 374 sites but were never observed interacting, the confidence interval (0.001, 0.018) comes close to, but does not include zero (Table~\ref{interval_table}).
-In other words, even with a very large data set, we will have problems in establishing that a given species pair can never interact.
-
-      %       % # R code to make the table:
-      %       % output=matrix(nrow=length(ns),ncol=5)
-      %       % ns=c(0,1,2,5,10,15,20,25,50,100,150,200,374)
-      %       % output[,1]=ns
-      %       % for(r in 1:nrow(output)){
-      %       %   interval1=credible_interval(calculate_parameters(sg_int_probs,ns[r],0),0.025,0.975)    
-      %       %   interval2=credible_interval(calculate_parameters(gp_int_probs,ns[r],0),0.025,0.975)    
-      %       %   output[r,2:3]=interval1
-      %       %   output[r,4:5]=interval2
-      %       % }
-
-      %       \begin{table}[h]
-      %         \caption{95\% credible intervals for the interaction probability of two species that co-occur in $N$ sites but are never observed to interact, obtained using prior information from the \emph{Salix}-galler network in~\citet{Barbour2016,Barbour2016Dryad}.
-[Tomas notes that this is conceptually very similar to Fig.~\ref{Salix_pdfs}]}
-      %         \label{interval_table}
-      %         \begin{tabular}{l | c c | c c }
-      %         \multirow{2}{*}{N} & \multicolumn{2}{c}{\emph{Salix}-galler} & \multicolumn{2}{c}{galler-natural enemy}\\
-      %          & Lower bound & Upper bound \\
-      %         \hline
-      %         0   & 0.152 & 0.931 & 0.008 & 0.364 \\
-      %         1   & 0.110 & 0.843 & 0.007 & 0.337 \\
-      %         2   & 0.087 & 0.760 & 0.006 & 0.313 \\
-      %         5   & 0.053 & 0.573 & 0.005 & 0.258 \\
-      %         10  & 0.033 & 0.400 & 0.004 & 0.200 \\
-      %         15  & 0.023 & 0.306 & 0.003 & 0.163 \\
-      %         20  & 0.018 & 0.247 & 0.003 & 0.137 \\
-      %         25  & 0.015 & 0.208 & 0.002 & 0.119 \\
-      %         50  & 0.008 & 0.115 & 0.001 & 0.071 \\
-      %         100 & 0.004 & 0.061 & 0.001 & 0.039 \\
-      %         150 & 0.003 & 0.041 & \textless0.001 & 0.027 \\
-      %         200 & 0.002 & 0.031 & \textless0.001 & 0.021 \\
-      %         \hline
-      %         374 & 0.001 & 0.017 & \textless0.001 & 0.011 \\
-      %         \hline
-      %         \end{tabular}
-      %         \end{table}
-
-  \subsection*{How many samples are required to reach a minimal precision?}
+  \subsection*{How many samples are required to reach a minimal precision}
 
@@
 
-    \bibliographystyle{ecollett} 
-    \bibliography{MyCollection} % Abbreviate journal titles.
+    \bibliographystyle{ecol_let} 
+    \bibliography{manual_abbrev} % Abbreviate journal titles.
 

### 2018-03-19 manuscript/CI_interactions.tex

@@
 \usepackage{array}
-\usepackage{hyperref}
+\usepackage{hyperref,url}
 \usepackage{float}
@@
 To simulate this situation, we created priors using a single sub-network from the middle of the geographical distribution of the~\citet{Kopelke2017} dataset.
-To demonstrate how the use of data from a different system can affect the prior distribution and conclusions based on it, we repeated our analyses using priors derived from a much smaller \emph{Salix}-galler-natural enemy system~\citep{Barbour2016,Barbour2016Dryad}.
+To demonstrate how the use of data from a different system can affect the prior distribution and conclusions based on it, we repeated our analyses using priors derived from a much smaller \emph{Salix}-galler-natural enemy system~\citep[Data available from the Dryad Digital Repository: https://doi.org/10.5061/dryad.g7805]{Barbour2016}\nocite{Barbour2016Dryad}.
 This smaller system was much more densely-connected than that described in~\citet{Kopelke2017} and provided unreasonable distributions for interaction probabilities (\emph{Appendix S4}).
@@
 The prior distribution for the galler-natural enemy network was: $\bar\lambda$=0.076, var($\lambda$)=0.008.
-The posterior interaction probabilities obtained based on the Zillis sub-network were much lower than those obtained based on~\citet{Barbour2016}; this emphasizes the importance of using an appropriate study system when constructing a prior (\emph{Appendix S4}).
+The posterior interaction probabilities obtained based on the Zillis sub-network were much lower than those obtained based on~\citet[Data available from the Dryad Digital Repository: https://doi.org/10.5061/dryad.g7805]{Barbour2016}; this emphasizes the importance of using an appropriate study system when constructing a prior (\emph{Appendix S4}).
 

### 2018-03-20 manuscript/CI_interactions.tex
formatting mostly done, need to finalize author statement and add acknowledgements

@@
 
-\author{Alyssa R. Cirtwill$^{1\dagger}$, \&  Anna Ekl\"{o}f$^{1}$, Tomas Roslin$^{2,3}$, Kate Wootton$^{2}$, Dominique Gravel$^{4}$}
-\date{\small$^1$Department of Physics, Chemistry\\ 
-and Biology (IFM)\\ 
+\author{Alyssa R. Cirtwill$^{1\dagger}$, \&  Anna Ekl\"{o}f$^{1\ddagger}$, Tomas Roslin$^{2,3\star}$, Kate Wootton$^{2\diamond}$, Dominique Gravel$^{4\triangleright}$}
+\date{\begin{minipage}[h]{0.45\textwidth}
+\small$^1$ Department of Physics,\\
+Chemistry and Biology (IFM)\\ 
 Link\"{o}ping University\\
 Link\"{o}ping, Sweden\\
-\medskip $^2$ Department of Ecology\\ P.O. Box 7044, Swedish University of Agricultural Sciences \\ SE-750 07 Uppsala, Sweden \\
-\medskip $^3$ Spatial Foodweb Ecology Group\\ Department of Agricultural Sciences \\ PO Box 27 (Latokartanonkaari 5)\\ FI-00014 University of Helsinki, Finland \\
-\medskip$^4$ D\'{e}partement de biologie\\ 
+$^2$ Department of Ecology\\ 
+P.O. Box 7044\\ 
+Swedish University of Agricultural Sciences \\ 
+SE-750 07 Uppsala, Sweden 
+\end{minipage}\hspace{.05\textwidth}\begin{minipage}[h]{0.45\textwidth}
+\small$^3$ Spatial Foodweb Ecology Group\\ 
+Department of Agricultural Sciences \\ 
+PO Box 27 (Latokartanonkaari 5)\\ 
+FI-00014 University of Helsinki, Finland\\
+$^4$ D\'{e}partement de biologie\\ 
 Universit\'{e} de Sherbrooke\\ 
-Sherbrooke, Canada\\ 
-\medskip
-$^\dagger$ Corresponding author:\\
-alyssa.cirtwill@gmail.com\\
-+46 723 158464\\
+Sherbrooke, Canada
+\end{minipage}
 }
@@
 
-\clearpage
+\vspace{-.25in}
+\begin{minipage}[h]{0.25\textwidth}
+\small$^\dagger$ Corresponding author:\\
+alyssa.cirtwill@gmail.com\\
+tel: +46 723 158464
+\end{minipage}\hspace{.05\textwidth}\begin{minipage}[h]{0.22\textwidth}
+\small$^\ddagger$ anna.eklof@liu.se\\
+$^\star$ tomas.roslin@slu.se
+\end{minipage}\hspace{.05\textwidth}\begin{minipage}[h]{0.38\textwidth}
+\small$^\diamond$ kate.wootton@slu.se\\
+$^\triangleright$ dominique.gravel@usherbrooke.ca
+\end{minipage}
+
+{\small
+\section*{\small Statement of authorship}
+
+AC and DG wrote the code. AC performed statistical analyses. All authors contributed to writing and revising the manuscript. TR contributed dat. [[Anything missing?]]
+
+\section*{\small Data accessibility}
+
+All data used in this study have been independently published and are accessible following the references provided in text.
+
+\section*{\small Keywords}
+
+ecological networks; probabilistic interactions; Bayesian networks; sampling error; spatial variability; temporal variability
+
+\section*{\small Details}
+
+\begin{minipage}[h]{0.6\textwidth}
+\begin{itemize}
+\item Running title: Quantitative network construction
+\item Article type: Ideas and Perspectives
+\item Number of references: 36
+\item Number of figs, tables, \& text boxes: 8 % Limit is 10
+\end{itemize}
+\end{minipage}\begin{minipage}[h]{0.4\textwidth}
+\begin{itemize}
+\item Text box 1 word count: 381
+\item Text box 2 word count: 210
+\item Abstract word count: 200
+\item Main text word count: 6482 % Including 18 page numbers. % No abstract, acknowledgements, references, table or figure legends. Limit is 7500
+\end{itemize}
+\end{minipage}
+}
+
+\newpage
 % Main text can be up to 7500 words, 10 fig., tables, boxes
+\begin{spacing}{2.0}
 
@@
 
-\linenumbers
+% \linenumbers
 \clearpage
 
-\begin{spacing}{2.0}
 \section*{Introduction}
@@
       \begin{equation}
-        P(\lambda|k,n) = \frac{\lambda^{\alpha+k-1}(1-\lambda)^{\beta+n-k-1}}{B(\alpha+k,\beta+n-k)} , \label{posterior}
+        P(\lambda|k,n) = \frac{\lambda^{\alpha+k-1}(1-\lambda)^{\beta+n-k-1}}{B(\alpha+k,\beta+n-k)} , \label{posterior2}
       \end{equation}
@@
 outlining how this is different than other approaches currently in use and how they fail at some important task), documenting the robustness and accuracy of the approach, performing case study, and making robust high-quality code freely available.]
+
+\section*{Acknowledgements}
+
+  [[Anything to add here?]
+
 \end{spacing}
+\clearpage
 
@@
       % }
-
+      \medskip
+        \textbf{Table 1:} Here we give the lower and upper bounds of 95\% credible intervals for the probability of interaction $\lambda$ between \emph{Salix}-galler or galler-natural enemy pairs that have been observed co-occurring $n$ times but have never been observed interacting.
         \begin{tabular}{l  c c  c c }

### 2018-03-20 manuscript/coverletter.tex
coverletter drafted

--- 2017-09-28 manuscript/Ideas_and_perspectives_proposal.tex
@@
 
-% The instructions are for a single, 300-word paragraph proposal. The large paragraph is now at 299 words, and we can maybe hope that they won't count the preamble and nice closing.
+% Borrowing heavily from the proposal
 
@@
 
-    My co-authors and I cordially invite you to consider the 
-    following proposal for an Ideas \& Perspectives article in 
-    \myjournal:
+    My co-authors and I are pleased to submit the attached manuscript \emph{A quantitative framework for investigating the reliability of network construction} for consideration as a Novel Methods paper in \emph{Ecology Letters} as per our previous correspondence with Senior Editor John Drake.
+As instructed, we have submitted the manuscript under the Ideas \& Perspectives mechanism (and following the associated formatting guidelines).
 
-    Representing communities as networks of interactions (links) between taxa (nodes) is a central approach in modern community ecology.
-These networks are usually treated as fixed, deterministic entities.
-Yet, researchers working with ecological networks widely acknowledge that empirical data are in fact samples of a community and come with major caveats.
-The probability of observing different interactions depends on sampling effort/methodology and local conditions as well as the intrinsic probability of any interaction.
-These contingencies mean that there are many reasons one might fail to observe an interaction (e.g., it might occur sometimes but not during sampling due to weather).
-Problematically, these sources of non-interaction are often indistinguishable within an interaction matrix.
+    We begin the manuscript by reviewing the many sources of variation inherent in ecological networks.
+Some sources of variation can be reduced through improved sampling, but others are intrinsic properties of ecological communities.
+This uncertainty limits the accuracy of network studies which consider communities as static, invariant entities and demonstrates the need for descriptions of network structure that acknowledge and address the uncertainty surrounding estimates of interspecific interactions.
+
     As a potential solution, we propose a Bayesian framework which partitions the uncertainty associated with missing interactions into explicit components and allows us to place confidence intervals around each estimated interaction probability.
 The Bayesian framework also facilitates the use of prior information (e.g., species traits) to reduce uncertainty around some interactions.
-We will illustrate this framework using an extraordinarily  well-replicated set of plant-galler-parasitoid networks recently published as a data paper (Kopelke \emph{et al.}, 2017.
+We illustrate this framework using an extraordinarily  well-replicated set of plant-galler-parasitoid networks recently published as a data paper (Kopelke \emph{et al.}, 2017.
 \textbf{Ecology} 98: 1730).
-Using this dataset, we will demonstrate how uncertainty surrounding each interaction probability affects network-level metrics.
-Acknowledging this uncertainty is crucial for valid comparison of networks along gradients.
-The authors involved in this study contribute a range of valuable perspectives.
-Dominique Gravel has developed techniques for novel types of interaction distribution modelling.
-Anna Ekl\"{o}f contributes extensive experience with probabilistic network analyses.
-Tomas Roslin has vast experience with gathering and using network data and has first-hand experience with each source of variation we describe.
-The two junior authors, Kate Wootton and Alyssa Cirtwill, work with both empirical and simulated networks and have a strong interest in developing more robust methods for network analyses.
+Using this dataset, we demonstrate how uncertainty surrounding each interaction probability affects network-level metrics.
+Our derivation of the Bayesian framework and quantitative examples are constructed so as to be accessible to readers with little or no prior experience with Bayesian statistics.
+We hope that this gentle introduction will help the broadest possible set of readers apply the framework we propose.
 
-    We are confident that the applicability of this method to all types of ecological networks and the importance of addressing sources of uncertainty in the data will mean that this article is of interest to a broad readership.
+    The present work is outstandingly novel relative to the recent work by one of the authors (Tomas Roslin) cited in this manuscript.
+Kopelke \emph{et al.} (2017) is the data paper describing the \emph{Salix}-galler-parasitoid system used for the quantitative analyses in the present work.
+Kopelke \emph{et al.} (2017) does not contain any analyses and so does not affect the novelty of the present work in any way.
+
+    We appreciate the chance to submit one of the first Novel Methods papers at \emph{Ecology Letters}.
+We are confident that the fundamental conceptual shift implied by our approach, accompanied by clear examples and easy-to-use scripts, can achieve the high standard you are looking for.
 We hope that you agree and eagerly await your reply.
@@
 \end{document}
+
+% Suggested reviewers:

### 2018-03-21 manuscript/CI_interactions.tex
removed comments from main text prior to upload

@@
 
-AC and DG wrote the code. AC performed statistical analyses. All authors contributed to writing and revising the manuscript. TR contributed dat. [[Anything missing?]]
+DG designed the analytical approach. AC and DG wrote the code. AC performed statistical analyses. All authors contributed to writing and revising the manuscript.
 
@@
 
-ecological networks; probabilistic interactions; Bayesian networks; sampling error; spatial variability; temporal variability
+ecological networks; probabilistic interactions; Bayesian networks; sampling error; spatial variability; temporal variability; uncertainty
 
@@
 \newpage
-% Main text can be up to 7500 words, 10 fig., tables, boxes
+
 \begin{spacing}{2.0}
@@
 
-  Descriptions of ecological networks typically assume that the same interspecific interactions occur wherever and whenever a community is observed.
+  Descriptions of ecological networks typically assume that the same interspecific interactions occur each time a community is observed.
 This contrasts with the known stochasticity of ecological communities: community composition, species abundances, and link structure all vary in space and time.
@@
 We illustrate this framework using the most extensively sampled network to date.
-Finally, we offer both code and tangible recommendations for improving descriptions of ecological networks and sampling of rare interactions.
+We found significant uncertainty in estimates for the probability of most pairwise interactions which we could, however, limit with informative priors.
 Through these efforts, we demonstrate the utility of our approach and the importance of acknowledging the uncertainty inherent in network studies.
 Most importantly, we stress that networks are best thought of as systems constructed from random variables, the stochastic nature of which must be acknowledged for an accurate representation.
-Doing so will fundamentally change networks analyses, but should lead to greater realism.
+Doing so will fundamentally change networks analyses but should yield greater realism.
+  % Can be up to 200 words. This is 200 exactly.
 
-  % Can be up to 200 words. This is 200 exactly.
-  % Word count can be up to 7500, we're at about 6506 without the boxes, intro, references.
-
-%DG: Eco Lett proposed the new format for methods papers, but I think they are nonetheless looking for conceptual contributions.
-We might have to tweak just a little bit the abstract to show that our proposition also help formalizing the idea that interactions should be described probabilistically.
-This is not only technical, it is fundamental as well.
-
-% AC: Good idea - I've also changed the "In this study, we ..." paragraph to make it sound less like we just built some software and hopefully emphasise the conceptual side more.
-
-% \linenumbers
+\linenumbers
 \clearpage
@@
 These models may include information about species' traits~\citep{Rohr2016} or may attempt to reproduce empirical network structures using a set of simple rules~\citep{Allesina2008,Williams2010}.
-    % \citet{Eklof2013} also introduced variability  in the computation of network dimensions, allowing the absence of interactions within the n-dimension niche of every species.
-% AC: Does this really fit in now that this is in the introduction?
 
@@
 
-   % [[Move this paragraph to intro?]] It is getting more and more common to represent interactions as probabilities in theoretical models of network structure.
-For example, the minimum potential model introduces gaps in the feeding niche of predators by sampling based on the likelihood of each interaction~\citep{Allesina2008}, while a Gaussian probability function is used to represent the niche by~\citet{Williams2010}.
-\citet{Eklof2013} also introduced variability  in the computation of network dimensions, allowing the absence of interactions within the n-dimension niche of every species.
-Empirical investigation of trait-matching constraints often consider the occurrence of interactions as binomial process (e.g.,~\citealp{Rohr2016}).
-There are also ways to perform analysis of probabilistic networks, with almost all metrics having a probabilistic version~\citep{Poisot2016}.
-But there is not yet consensus on what an interaction probability between a pair of species means, and this is definitely a problem when comes time to estimate the uncertainty of both pairwise interactions and entire networks.
-
-    In this study, we formalize the description of interactions between species as probabilities and develop analytical tools to capture the uncertainty in the estimation of these interactions.
+    In this study, we formalise the description of interactions between species as probabilities and develop analytical tools to capture the uncertainty in the estimation of these interactions.
 We focus on binary interactions as a first step, but the framework could be expanded to deal with interaction frequencies and strength.
@@
 Although some of the factors leading to process uncertainty can be addressed in mesocosm studies of networks (e.g., environmental conditions can be held stable), process uncertainty is likely inevitable in the field.
-      % We imagine for instance that an interaction between a gall and a parasitoid might not be recorded at a location because it was the wrong time of the year and the gall had not yet formed (phenological constraints), a late frost killed the larvae (an abiotic environmental constraint), another parasitoid species competitively excluded the parasitoid species of interest (a biotic environmental constraint) or simply the parasitoid is too rare to interact with all of its viable hosts (an abundance constraint).
 
@@
 
-    %DG: I do understand Tomas' point about the following, but I really appreciate it !
-Keep in mind the suggestion to drop the following paragraph was made when there was much more material above.
-Perhaps we should revisit this suggestion, given the actual material that will follow.
-To me this is fairly important for the non-technical people.
-There are some important things, such as the "the more sample the more zeros will appear in the interaction matrix"
-
-    %AE: I agree with Dom here, as I think the paragraphs below are good for getting a bit deeper into the width of the problem we are addressing. Could possibly be shortened if needed?
-
-    %AC: I've added this section back in but shortened it slightly (mostly the first paragraph). We're ok on word-count with this included.
-
-    % The basic information that we are collecting consists of matrices of interaction partners.
-Our count of interactions between two species reflects uncertainty with respect to whether two species are capable of interacting when co-occurring at a given site ($\lambda$), chance variation in whether the interaction is realised ($\chi$),  and uncertainty with respect to whether it is detected when realised ($\delta$).
-In this case, what can we do to pin down any of these different types of variation?
-
     The obvious rule of thumb is to ``sample more" (see Fig.~\ref{upper_limits} for a demonstration of the power of increasing sample size).
@@
 \section*{A naive quantification of uncertainty}
-  %AC: This section header was too long and running beyond a line... is the shortened version ok?
-  % \section*{A naive quantification of interaction probability and uncertainty}
-
-  %%AE: I think the section that is commented  below not should be placed here, but when reading the pdf without this part in it I really thoght that this was missing.
-One option is to move this part to the Introduction, where it would fit better.
-
-   % [[Move this paragraph to intro?]] It is getting more and more common to represent interactions as probabilities in theoretical models of network structure.
-For example, the minimum potential model introduces gaps in the feeding niche of predators by sampling based on the likelihood of each interaction~\citep{Allesina2008}, while a Gaussian probability function is used to represent the niche by~\citet{Williams2010}.
-\citet{Eklof2013} also introduced variability  in the computation of network dimensions, allowing the absence of interactions within the n-dimension niche of every species.
-Empirical investigation of trait-matching constraints often consider the occurrence of interactions as binomial process (e.g.,~\citealp{Rohr2016}).
-There are also ways to perform analysis of probabilistic networks, with almost all metrics having a probabilistic version~\citep{Poisot2016}.
-But there is not yet consensus on what an interaction probability between a pair of species means, and this is definitely a problem when comes time to estimate the uncertainty of both pairwise interactions and entire networks.
 
@@
 
-      %  The posterior distribution of $\theta$ could be computed with R with the following command:
-      %
-      %
-      %  \vspace{12pt}
-      %  \noindent\emph{dbeta(x = theta, shape1 = alpha+k, shape1 = beta+n-k)}
-      %  \vspace{12pt}
-
     \subsection*{Moments and other properties}
@@
 The fact that the posterior distribution of $\lambda$ follows a beta distribution makes it straightforward to compute moments and other properties needed for this.
-    %%AE: Should we give examples of these higher-order properties?    
-    % AC: How do you mean? Examples of averages/variances/modes or of "other properties" ?
 
@@
 It measures the filling of an interaction matrix and thereby expresses the average probability that any two species interact with each other.
-If we know only the mean $\overline{C}$ and the variance $\sigma_C^2$ of the distribution of $C$,
-          % [[from the literature or from our network? Has to be from the literature - if it was our network we'd know way more than just C]] 
-          then the beta parameters could be computed as follows using the method of moments:
+If we know only the mean $\overline{C}$ and the variance $\sigma_C^2$ of the distribution of $C$,          then the beta parameters could be computed as follows using the method of moments:
 
@@
           \end{equation}
-
-          %  It is also possible to compute maximum likelihood estimates for a sample of the distribution of $C$.
-          %  
-          %   The following piece of R code provides an example: 
-          %
-          %  \vspace{12pt}
-          %  \noindent\emph{
-          %    library(MASS)\\
-          %    pars = fitdistr(x = vecC, "beta", start = list(shape1 = 1, shape2 = 1))\$estimate
-          %  }
-          %  \vspace{12pt}
-          %
-          %
-          %  Where $vecC$ is a vector of known connectances for a set of networks.
 
@@
 
-    %It is fairly straightforward to compute most of network metrics when the different $\lambda$ of the adjacency matrix are known, without variance~\citep{Poisot2016}.
-Several of these metrics derive directly from quantitative indices of network structure which are equivalent to $\lambda$.
-The remainder, originally defined for binary networks, can be adjusted to account for interaction probabilities between zero and one.
-It is not as easy, however, to understand how the uncertainty in these estimated interaction probabilities influences network metrics.
-Computation of these metrics involves non-linear functions.
-Since Jensen's inequality states that the average of a non-linear function of a stochastic variable differs from the function of the average of that variable, any uncertainty in the values of $\lambda$ could bias both the mean and variance of a network metric.
-For instance, assume that among the pairs of species with few observed co-occurrences there are many pairs which truly interact.
-If we %begin with no observed links for these pairs, then correcting for these false absences will inflate the number of links and consequently influence metrics such as connectance, nestedness, and degree distribution.
-While we can, as described above, calculate these network metrics using fixed estimates for $\lambda$, no analytical solution currently exists for uncertain $\lambda$.
-Instead we must rely on computer simulations.
     In the following section, we will provide an empirical example based on the well-sampled system of \emph{Salix}  plants, herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}; see Box~\ref{box1} or \emph{Appendix S2} for a description).
@@
 Finally, we will calculate network properties using a suite of networks sampled from these posterior distributions and show how the uncertainty around interactions that have not been observed impact these metrics.
-%We find uncertainty influences both the average and the variance of network metrics, putting in perspective traditional network comparison studies where these metrics are assumed to be fixed entities.
-
-    %DG: I dropped pieces of the above paragraph because it was bizarre to get back at the posterior distribution, and then to the computer simulations.
-This section is first and foremost an empirical example.
-But then, an introduction about the scaling up was missing, so I moved part of the paragraph below
-
-    % AC : Maybe we should change the section title to highlight that this is an empirical example and covers the effect of uncertainty on network-level properties
 
@@
 The prior distribution for the galler-natural enemy network was: $\bar\lambda$=0.076, var($\lambda$)=0.008.
-The posterior interaction probabilities obtained based on the Zillis sub-network were much lower than those obtained based on~\citet[Data available from the Dryad Digital Repository: https://doi.org/10.5061/dryad.g7805]{Barbour2016}; this emphasizes the importance of using an appropriate study system when constructing a prior (\emph{Appendix S4}).
+The posterior interaction probabilities obtained based on the Zillis sub-network were much lower than those obtained based on~\citet[Data available from the Dryad Digital Repository: https://doi.org/10.5061/dryad.g7805]{Barbour2016}; this emphasises the importance of using an appropriate study system when constructing a prior (\emph{Appendix S4}).
 
@@
 
-    %DG: here is where I moved material from aboce
-
     It is fairly straightforward to compute most network metrics when the different $\lambda$ of the adjacency matrix are known and assumed not to vary without variance~\citep{Poisot2016}.
@@
 
-    %DG: the different posterior connectance are the results of different samples of the posterior distribution, righ ? 
-    %Yes
-
     We find, perhaps not surprisingly, that the posterior webs for the Salix-galler network  had higher connectances than the original, observed web (C=0.028 for the observed web and 0.082 $\leq$ C $\leq$ 0.096 for the posterior webs; Fig.~\ref{posterior_webs}A).
@@
 This last result highlights the potential for the possibility for network structure to vary when considering the possibility that unobserved species pairs may interact.
-
-    %    [[This is a little boring. Tomas has ideas for people with potentially better priors - may require another co-author. Also maybe could use one site as a prior like ``training data"?]]
-    % DG: not so sure, I find it very useful because it simply illustrates the point. Nestedness will be a nice complement with lest trivial results
-    %%AE: If we are doing a complement here (I agree it is a bit boring) I think option c) from Alyssas mail is the most straight forward option. 
-    % AC: Added nestedness and replaced the Barbour data with training data from one site. Couldn't find any good published data.
 
@@
 
-  % [Here we need to be very hands-on and remember the invitation letter form Ecol Letters:
-  % As a contribution primarily to methodology, the manuscript will not be considered for ``Ideas \& Perspectives".
-(Please recall my message concerning your past presubmission inquiry.) However, Ecology Letters is entertaining the idea of a new section for ``Novel Methods".
-As we have not advertised this, I would ask you to keep that information in confidence.
-If acceptable to an Associate Editor and reviewers, your paper could be the first, or one of the first, contributions to this new section.
-Accordingly, the work would be subject to considerable scrutiny and I would urge you to make the paper as strong as you can.
-This would include demonstrating the need for this new method (i.e.
-outlining how this is different than other approaches currently in use and how they fail at some important task), documenting the robustness and accuracy of the approach, performing case study, and making robust high-quality code freely available.]
-
 \section*{Acknowledgements}
 
-  [[Anything to add here?]
+  The authors thank Daniel Cartensen for fruitful discussion of the ideas in this manuscript. We also thank K\'{e}vin Cazalles for providing feedback on the manuscript.
 
@@
 
-%%AE: I think Box 2 is nice to have in as a hands-on example.
 \begin{floatbox}{}
@@
 
-%DG: be careful : occurrence, not occurance on the figures
     \begin{figure}
@@
       \label{histograms}
-      \includegraphics*[width=.8\textwidth]{figures/Salix_Galler_histogram.eps}
+      % \includegraphics*[width=.8\textwidth]{Salix_Galler_histogram.eps}
       \end{figure}
-
-%DG: I really appreciate this figure, it makes the point so clear.
-
-% DG: it's bizarre to present here the outcome of the naive binomial formulation, while the reasoning is provided later.
-My solution is to move the following section on the binomial model along with the figure within a box.
-It's not central, but formalizes the problem.
-It would respect the order of appearance and better emphasize the bayes section.
-% AC: I couldn't figure out how to put a figure inside a text box, so instead (following an e-mail suggestion) I moved the naive binomial outcome to the figure caption.
 
@@
     \label{upper_limits}
-    \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
+    % \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
   \end{figure}
-
-%DG :  I think we should add the MLE estimate along with the binomial confidence interval on the figure in order to better illustrate the impact of the prior (obviously only for one N).
-You may draw it with a line to contrast with polygons.
-% Done, think it works for all N
-
-%DG: otherwise the difference between the two interaction types is very interesting and useful to show the effect of the priors. Bravo !
 
@@
         \label{Salix_pdfs}
-        \includegraphics*[width=.8\textwidth]{figures/Salix_Galler_pdfs_increasing_N_Zillis.eps}
+        % \includegraphics*[width=.8\textwidth]{figures/Salix_Galler_pdfs_increasing_N_Zillis.eps}
         \end{figure}
@@
         \label{Salix_cdfs}
-        \includegraphics[width=.8\textwidth]{figures/Salix_Galler_samples_and_cdfs_Zillis.eps}
+        % \includegraphics[width=.8\textwidth]{figures/Salix_Galler_samples_and_cdfs_Zillis.eps}
 
@@
     \label{posterior_webs}    
-    \includegraphics[width=.8\textwidth]{Figures/Salix_Galler_posterior_properties_Zillis.eps}
+    % \includegraphics[width=.8\textwidth]{Figures/Salix_Galler_posterior_properties_Zillis.eps}
     \end{figure}
-
-  % [[What if we have only one site?
-Can we use the number of observations of a pair of species interacting with any partners as the number of times they co-occur, and the number of interactions within the pair as k?
-This will be sort-of valid for insects but not for plants when researchers camp out by plant individuals...
-]]
 

### 2018-03-21 manuscript/coverletter.tex
removed comments from main text prior to upload

@@
 \url{http://cirtwill.github.io}
-\name{Alyssa R. Cirtwill}
+\name{Dr. Alyssa R. Cirtwill}
 
@@
 
-    My co-authors and I are pleased to submit the attached manuscript \emph{A quantitative framework for investigating the reliability of network construction} for consideration as a Novel Methods paper in \emph{Ecology Letters} as per our previous correspondence with Senior Editor John Drake.
+    My co-authors and I are pleased to submit the attached manuscript \emph{A quantitative framework for investigating the reliability of network construction} for consideration as a Novel Methods paper in \textbf{Ecology Letters} as per our previous correspondence with Senior Editor John Drake.
 As instructed, we have submitted the manuscript under the Ideas \& Perspectives mechanism (and following the associated formatting guidelines).
@@
 
-    We appreciate the chance to submit one of the first Novel Methods papers at \emph{Ecology Letters}.
+    We appreciate the chance to submit one of the first Novel Methods papers at \textbf{Ecology Letters}.
 We are confident that the fundamental conceptual shift implied by our approach, accompanied by clear examples and easy-to-use scripts, can achieve the high standard you are looking for.
@@
 % Suggested reviewers:
+
+% Pedro Jordano pedroj@me.com Estacion Biologica de Donana CSIC
+% Phillip Staniczenko pstaniczenko@sesync.org National Socio-Environmental Synthesis Center (SESYNC)

### 2018-03-21 manuscript/supplemental.tex
removed comments from main text prior to upload

@@
       \noindent \hspace{2pt}deg\_dist\_parasitoid=rowSums(prior\_web\_para\_only)/ncol(prior\_web\_para\_only)\\
-      \noindent \hspace{2pt}deg\_dist\_parasitized=colSums(prior\_web\_para\_only)/nrow(prior\_web\_para\_only)\\
-      \noindent \hspace{2pt}gp\_int\_probs=as.numeric(deg\_dist\_parasitized\%$*$\%t(deg\_dist\_parasitoid))\\
+      \noindent \hspace{2pt}deg\_dist\_parasitised=colSums(prior\_web\_para\_only)/nrow(prior\_web\_para\_only)\\
+      \noindent \hspace{2pt}gp\_int\_probs=as.numeric(deg\_dist\_parasitised\%$*$\%t(deg\_dist\_parasitoid))\\
       \end{em}
@@
       % deg_dist_parasitoid=rowSums(GP_web)/ncol(GP_web)
-      % deg_dist_parasitized=colSums(GP_web)/nrow(GP_web)
-      % gp_int_probs=as.numeric(deg_dist_parasitized%*%t(deg_dist_parasitoid))
+      % deg_dist_parasitised=colSums(GP_web)/nrow(GP_web)
+      % gp_int_probs=as.numeric(deg_dist_parasitised%*%t(deg_dist_parasitoid))
 

### 2018-03-21 manuscript/CI_interactions.tex
all uploaded pending Anna and Tomas final oks

@@
 \usepackage{float}
+\usepackage{mdframed}
 \makeatletter
@@
 
-% this code block defines the new and custom floatbox float environment
-\floatstyle{simplerule}
-\newfloat{floatbox}{thp}{lob}
-\floatname{floatbox}{Box}
+% this code block defines the new and custom mdframed environment
+\newmdenv[rightline=true,bottomline=true,topline=true,leftline=true,linewidth=2pt]{fullbox}
 
@@
 \title{A quantitative framework for investigating the reliability of network construction}
-
-% DG : if ok with all of you, I would appreciate being last author
-% AC : Makes sense to me since Dom was the originator of this ms and laid a lot of the groundwork.
-
-% AC : Assuming I'm going to be corresponding author on this but happy to let anyone else step in if you're eager
 
@@
   Second, where the number of samples $n$ is very low (some pairs of species may never have been documented as co-occurring), there will be considerable uncertainty around our estimate of $\lambda$.
-In Fig.~\ref{upper_limits} and Box~\ref{box2}, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda$ varies with sample size.
+In Fig.~\ref{upper_limits} and Box 2, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda$ varies with sample size.
 At a small sample size, the 95\% confidence interval spans all values of $\lambda$.
@@
 The function ``samples\_for\_threshold" in \emph{Appendix S1} calculates distribution function for $\lambda*$ with an increasing number of trials.
-This yields a surprising result: it requires \textgreater24 observations of no interactions to be 95\% sure that the interaction probability is smaller than $\lambda*$=0.1 (recall Fig.~\ref{upper_limits}, Box~\ref{box2}).
+This yields a surprising result: it requires \textgreater24 observations of no interactions to be 95\% sure that the interaction probability is smaller than $\lambda*$=0.1 (recall Fig.~\ref{upper_limits}, Box 2).
 Note the special case where there is no observation of the two species co-occurring, $n = 0$.
@@
 
-    In the following section, we will provide an empirical example based on the well-sampled system of \emph{Salix}  plants, herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}; see Box~\ref{box1} or \emph{Appendix S2} for a description).
+    In the following section, we will provide an empirical example based on the well-sampled system of \emph{Salix}  plants, herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}; see Box 1 or \emph{Appendix S2} for a description).
 Using this dataset, we will demonstrate the derivation of prior distributions for the \emph{Salix}-galler and galler-natural enemy components of these networks and the differences between these priors and posterior distributions which include all information available in this dataset~\citep{Kopelke2017}.
@@
 
+\captionsetup{singlelinecheck=false, font={stretch=2}}
+
 \section*{Boxes and figures}
 
-\begin{floatbox}{}
-
+\begin{fullbox}{}
+  \begin{spacing}{2.0}
+    \textbf{Box 1: }\emph{Salix}-galler-natural enemy dataset.\\
     \indent As a case study, we use an extensively sampled \emph{Salix}-galler-natural enemy meta-network.
@@
 This dataset also illustrates the potential for increased sampling to not necessarily reveal more interactions as a pair of species that is able to interact may not be observed interacting in all samples where the pair co-occurs (Fig.~\ref{histograms}E-F).
-  \caption{\emph{Salix} dataset}
-  \label{box1}
-\end{floatbox}
+  \end{spacing}
+\end{fullbox}
 
-\begin{floatbox}{}
+\clearpage
 
-  Here we describe the derivation of the Clopper-Pearson credible interval for the estimated probability of interaction $\lambda$ of a pair of species observed co-occurring $n$ times and interacting $k$ times.
+\begin{fullbox}{}
+    \begin{spacing}{2.0}
+    \textbf{Box 2: }Calculating the credible interval around a probability estimate\\
+  \indent Here we describe the derivation of the Clopper-Pearson credible interval for the estimated probability of interaction $\lambda$ of a pair of species observed co-occurring $n$ times and interacting $k$ times.
 As we are most interested in the probability of interaction between species pairs that have never been observed co-occurring, we consider only the case where $k=0$ over a variety of $n$.
@@
 These parameters can then be used to calculate a credible interval using the R~\citep{R} function qbeta.
-In the table below, we present the 95\% credible intervals for \emph{Salix}-galler and galler-natural enemy pairs with different numbers of observed co-occurrences ($n$) and no observed interactions ($k=0$).
-Both sets of intervals rely on prior information derived from the Zillis sub-network~\citep{Kopelke2017}.
+In the table below, we present the 95\% credible intervals for \emph{Salix}-galler and galler-natural enemy pairs with different numbers of observed co-occurrences ($n$) and no observed interactions ($k=0$), calculated using prior information derived from the Zillis sub-network~\citep{Kopelke2017}.
 
@@
       \medskip
-        \textbf{Table 1:} Here we give the lower and upper bounds of 95\% credible intervals for the probability of interaction $\lambda$ between \emph{Salix}-galler or galler-natural enemy pairs that have been observed co-occurring $n$ times but have never been observed interacting.
+        \textbf{Table 1:} Here we give the lower and upper bounds of 95\% credible intervals for the probability of interaction $\lambda$ between \emph{Salix}-galler or galler-natural enemy pairs that have been observed co-occurring $n$ times but have never been observed interacting.\\
         \begin{tabular}{l  c c  c c }
@@
         \end{tabular}
+    \end{spacing}
+\end{fullbox}
 
-  \caption{Calculating the credible interval around a probability estimate}
-  \label{box2}
-\end{floatbox}
+\clearpage
 
-    \begin{figure}
+  \begin{figure}[h!]
       \caption{\textbf{A-B)} Most pairs of \emph{Salix} and gallers or gallers and natural enemies were never observed co-occurring despite the high levels of replication in our example dataset.
@@
     \label{upper_limits}
-    % \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
+    % \includegraphics*[width=.8\textwidth]{upper_limit_DG.eps}
     \end{figure}
 
-      \begin{figure}[ht]
+  \begin{figure}[h!]
     \caption{Using prior distributions based on the \emph{Salix}-galler and galler-natural enemy networks sampled at a single site in~\citet{Kopelke2017}, we can calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting.
@@
     \label{Salix_pdfs}
-        % \includegraphics*[width=.8\textwidth]{figures/Salix_Galler_pdfs_increasing_N_Zillis.eps}
+    % \includegraphics*[width=.8\textwidth]{Salix_Galler_pdfs_increasing_N_Zillis.eps}
     \end{figure}
 
-      \begin{figure}[ht]
+  \begin{figure}[h!]
     \caption{The number of samples required to achieve a given level of confidence that an interaction probability $\lambda_{ij}$ is below a given threshold varies with both parameters.
@@
     \label{Salix_cdfs}
-        % \includegraphics[width=.8\textwidth]{figures/Salix_Galler_samples_and_cdfs_Zillis.eps}
+    % \includegraphics[width=.8\textwidth]{Salix_Galler_samples_and_cdfs_Zillis.eps}
 
@@
 
-    \begin{figure}[ht]
+  \begin{figure}[h!]
     \caption{Here we show the mean connectance, links per resource (\emph{Salix} in the \emph{Salix}-galler networks and gallers in the galler-natural enemy networks), links per consumer, and nestedness (NODF) for networks assembled using posterior distributions based on a single sub-network in the~\citet{Kopelke2017} dataset (Zillis).
@@
     \label{posterior_webs}    
-    % \includegraphics[width=.8\textwidth]{Figures/Salix_Galler_posterior_properties_Zillis.eps}
+    % \includegraphics[width=.8\textwidth]{Salix_Galler_posterior_properties_Zillis.eps}
     \end{figure}

### 2018-03-21 manuscript/CI_interactions.tex
more reviewers, funding, affiliation change

@@
 
-\author{Alyssa R. Cirtwill$^{1\dagger}$, \&  Anna Ekl\"{o}f$^{1\ddagger}$, Tomas Roslin$^{2,3\star}$, Kate Wootton$^{2\diamond}$, Dominique Gravel$^{4\triangleright}$}
+\author{Alyssa R. Cirtwill$^{1\dagger}$, \&  Anna Ekl\"{o}f$^{1\ddagger}$, Tomas Roslin$^{2\star}$, Kate Wootton$^{2\diamond}$, Dominique Gravel$^{3\triangleright}$}
 \date{\begin{minipage}[h]{0.45\textwidth}
@@
 Swedish University of Agricultural Sciences \\ 
-SE-750 07 Uppsala, Sweden 
-\end{minipage}\hspace{.05\textwidth}\begin{minipage}[h]{0.45\textwidth}
-\small$^3$ Spatial Foodweb Ecology Group\\ 
-Department of Agricultural Sciences \\ 
-PO Box 27 (Latokartanonkaari 5)\\ 
-FI-00014 University of Helsinki, Finland\\
-$^4$ D\'{e}partement de biologie\\ 
+SE-750 07 Uppsala, Sweden\\
+$^3$ D\'{e}partement de biologie\\ 
 Universit\'{e} de Sherbrooke\\ 
 Sherbrooke, Canada
+\end{minipage}\hspace{.05\textwidth}\begin{minipage}[h]{0.45\textwidth}
+\small$^\dagger$ Corresponding author:\\
+alyssa.cirtwill@gmail.com\\
+tel: +46 723 158464\\
+$^\ddagger$ anna.eklof@liu.se\\
+$^\star$ tomas.roslin@slu.se\\
+$^\diamond$ kate.wootton@slu.se\\
+$^\triangleright$ dominique.gravel@usherbrooke.ca
 \end{minipage}
@@
 
-\vspace{-.25in}
-\begin{minipage}[h]{0.25\textwidth}
-\small$^\dagger$ Corresponding author:\\
-alyssa.cirtwill@gmail.com\\
-tel: +46 723 158464
-\end{minipage}\hspace{.05\textwidth}\begin{minipage}[h]{0.22\textwidth}
-\small$^\ddagger$ anna.eklof@liu.se\\
-$^\star$ tomas.roslin@slu.se
-\end{minipage}\hspace{.05\textwidth}\begin{minipage}[h]{0.38\textwidth}
-\small$^\diamond$ kate.wootton@slu.se\\
-$^\triangleright$ dominique.gravel@usherbrooke.ca
-\end{minipage}
+\vspace{-.4in}
 
@@
 
-  The authors thank Daniel Cartensen for fruitful discussion of the ideas in this manuscript. We also thank K\'{e}vin Cazalles for providing feedback on the manuscript.
+  The authors thank Daniel Cartensen for fruitful discussion of the ideas in this manuscript.
+We also thank K\'{e}vin Cazalles for providing feedback on the manuscript.
+The authors also appreciate support from the Swedish Research Council (VR) for grant \#2016-06872 (to TR).
+Additional funding was provided by a Formas grant (\#942-2015-1262) to AE.
 

### 2018-03-21 manuscript/coverletter.tex
more reviewers, funding, affiliation change

@@
 
-    The present work is outstandingly novel relative to the recent work by one of the authors (Tomas Roslin) cited in this manuscript.
-Kopelke \emph{et al.} (2017) is the data paper describing the \emph{Salix}-galler-parasitoid system used for the quantitative analyses in the present work.
-Kopelke \emph{et al.} (2017) does not contain any analyses and so does not affect the novelty of the present work in any way.
+    The present work uses empirical material published as a data paper by one of the authors (Tomas Roslin).
+The cited paper, Kopelke \emph{et al.} (2017), presents the extremely high-quality dataset used in the present work but does not contain any analyses.
+As such, the present work is an entirely novel use of these data, which are also available to the full ecological community.
 
@@
 % Phillip Staniczenko pstaniczenko@sesync.org National Socio-Environmental Synthesis Center (SESYNC) 
+% Louis-Félix Bersier louis-felix.bersier@unifr.ch Université de Fribourg
+
+% Extra suggestion
+% Jacopo Grilli jgrilli@santafe.edu Santa Fe Institute
+% Eve McDonald-Madden e.mcdonaldmadden@uq.edu.au University of Queensland
+
+% Ben Weinstein Oregon State University weinsteb@oregonstate.edu
+% Jean-Philippe Lessard Concordia University jp.lessard@concordia.ca
+% Catherine Graham catherine.graham@wsl.ch Swiss Federal Research Institute WSL 
+% Anne Chao chao@stat.nthu.edu.tw National Tsing Hua University
+% Robert Colwell robertkcolwell@gmail.com Museum of Natural History, University of Colorado Boulder

### 2018-03-21 manuscript/supplemental.tex
more reviewers, funding, affiliation change

@@
 
-\author{Alyssa R. Cirtwill$^{1\dagger}$, \&  Anna Ekl\"{o}f$^{1}$, Tomas Roslin$^{2,3}$, Kate Wootton$^{2}$, Dominique Gravel$^{4}$}
+\author{Alyssa R. Cirtwill$^{1\dagger}$, \&  Anna Ekl\"{o}f$^{1}$, Tomas Roslin$^{2}$, Kate Wootton$^{2}$, Dominique Gravel$^{3}$}
 \date{\small$^1$Department of Physics, Chemistry\\ 
@@
 \medskip $^2$ Department of Ecology\\ P.O. Box 7044, Swedish University of Agricultural Sciences \\ SE-750 07 Uppsala, Sweden \\
-\medskip $^3$ Spatial Foodweb Ecology Group\\ Department of Agricultural Sciences \\ PO Box 27 (Latokartanonkaari 5)\\ FI-00014 University of Helsinki, Finland \\
-\medskip$^4$ D\'{e}partement de biologie\\ 
+\medskip$^3$ D\'{e}partement de biologie\\ 
 Universit\'{e} de Sherbrooke\\ 
@@
 
-    \bibliographystyle{ecollett} 
-    \bibliography{MyCollection}
+    \bibliographystyle{ecol_let} 
+    \bibliography{manual_abbrev}
 

### 2018-03-22 manuscript/CI_interactions.tex
few final tweaks

@@
 \author{Alyssa R. Cirtwill$^{1\dagger}$, \&  Anna Ekl\"{o}f$^{1\ddagger}$, Tomas Roslin$^{2\star}$, Kate Wootton$^{2\diamond}$, Dominique Gravel$^{3\triangleright}$}
-\date{\begin{minipage}[h]{0.45\textwidth}
+\date{\begin{minipage}[h]{0.6\textwidth}
 \small$^1$ Department of Physics,\\
@@
 Sherbrooke, Canada
-\end{minipage}\hspace{.05\textwidth}\begin{minipage}[h]{0.45\textwidth}
+\end{minipage}\begin{minipage}[h]{0.4\textwidth}
 \small$^\dagger$ Corresponding author:\\
@@
 \item Text box 2 word count: 210
-\item Abstract word count: 200
+\item Abstract word count: 199
 \item Main text word count: 6482 % Including 18 page numbers. % No abstract, acknowledgements, references, table or figure legends. Limit is 7500
@@
 Most importantly, we stress that networks are best thought of as systems constructed from random variables, the stochastic nature of which must be acknowledged for an accurate representation.
-Doing so will fundamentally change networks analyses but should yield greater realism.
+Doing so will fundamentally change networks analyses and yield greater realism.
   % Can be up to 200 words. This is 200 exactly.
@@
 
-    Representing an assemblage of species as a network offers a convenient summary of how the community is constructed as a network simultaneously describes species composition and interactions between species.
-A tabulation of the nodes (species) and their relative abundances forms the basis for traditional metrics of community composition.
+    Representing an assemblage of species as a network offers a convenient summary of how the community is constructed as networks simultaneously describe species composition and interactions between species.
+A tabulation of the nodes (species) and their relative abundances forms the basis for traditional metrics of community composition such as alpha diversity.
 To move from these simpler metrics to a network framework, the tabulation of nodes is combined with interactions (links between nodes) so that networks provide additional, higher-order information on community structure.

### 2018-03-22 manuscript/CI_interactions.tex
few final tweaks

@@
 Presences and absences are not, however, equally certain.
-An observed link will always remain an observed link, but there are multiple reasons why a given link may not be observed.
+An observed link will always remain an observed link but there are multiple reasons why a given link may not be observed.
 Thus, the detection of any interaction is a stochastic process.
@@
 The ecologist wanting to describe the network, however, is specifically interested in the situation where $L = 0$ (i.e., in true absences).
-Thus while there is no difficulty interpreting the observation of an interaction, the observation of an absence of an interaction offers more of a challenge since it must be decomposed into different quantities.
+Thus, while there is no difficulty interpreting the observation of an interaction, the observation of an absence of an interaction offers more of a challenge since it must be decomposed into different quantities.
 It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e.
@@
 
-    As a solution towards deciding whether unobserved interactions were undetected due to sampling, or whether they truly do not occur,~\citet{Weinstein2017} used repeated sampling rounds to estimate the daily probability of detecting a hummingbird interaction, and to thereby model detection and process uncertainty.
+    In one endeavour to determine whether unobserved interactions were undetected due to sampling, or whether they truly do not occur,~\citet{Weinstein2017} used repeated sampling rounds to estimate the daily probability of detecting a hummingbird interaction, and to thereby model detection and process uncertainty.
 While conceptually attractive, this approach is unsuitable for interactions occurring over longer time scales (e.g., associations between hosts and parasitoids with a single generation per year), or very rare interactions which might not occur on any of the sampling days or might involve individuals of a species that is not under observation.

### 2018-05-28 manuscript/CI_interactions.tex
updated fig sizes for nice compiling

@@
 
-\captionsetup{singlelinecheck=false, font={stretch=2}}
+\captionsetup{singlelinecheck=false, font={stretch=1}}
 
@@
 \begin{fullbox}{}
-  \begin{spacing}{2.0}
+  \begin{spacing}{1.0}
     \textbf{Box 1: }\emph{Salix}-galler-natural enemy dataset.\\
@@
 \begin{fullbox}{}
-    \begin{spacing}{2.0}
+    \begin{spacing}{1.0}
     \textbf{Box 2: }Calculating the credible interval around a probability estimate\\
@@
       \label{histograms}
-      % \includegraphics*[width=.8\textwidth]{Salix_Galler_histogram.eps}
+      \begin{center}
+      \includegraphics*[width=.8\textwidth]{figures/Salix_Galler_histogram.eps}
+      \end{center}
       \end{figure}
@@
     \label{upper_limits}
-    % \includegraphics*[width=.8\textwidth]{upper_limit_DG.eps}
+    \begin{center}
+    \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
+    \end{center}
     \end{figure}
@@
     \label{Salix_pdfs}
-    % \includegraphics*[width=.8\textwidth]{Salix_Galler_pdfs_increasing_N_Zillis.eps}
+    \begin{center}
+    \includegraphics*[width=.7\textwidth]{figures/Salix_Galler_pdfs_increasing_N_Zillis.eps}
+    \end{center}
     \end{figure}
@@
     \label{Salix_cdfs}
-    % \includegraphics[width=.8\textwidth]{Salix_Galler_samples_and_cdfs_Zillis.eps}
+    \begin{center}
+    \includegraphics[width=.5\textwidth]{figures/Salix_Galler_samples_and_cdfs_Zillis.eps}
+    \end{center}
 
@@
     \label{posterior_webs}    
-    % \includegraphics[width=.8\textwidth]{Salix_Galler_posterior_properties_Zillis.eps}
+    \begin{center}
+    \includegraphics[width=.7\textwidth]{figures/Salix_Galler_posterior_properties_Zillis.eps}
+    \end{center}
     \end{figure}

### 2018-06-04 manuscript/CI_interactions.tex
9636 words

@@
 
-\author{Alyssa R. Cirtwill$^{1\dagger}$, \&  Anna Ekl\"{o}f$^{1\ddagger}$, Tomas Roslin$^{2\star}$, Kate Wootton$^{2\diamond}$, Dominique Gravel$^{3\triangleright}$}
-\date{\begin{minipage}[h]{0.6\textwidth}
+\author{Alyssa R. Cirtwill$^{1\dagger}$, \&  Anna Ekl\"{o}f$^{1}$, Tomas Roslin$^{2}$, Kate Wootton$^{2}$, Dominique Gravel$^{3}$}
+\date{
+% \begin{minipage}[h]{0.6\textwidth}
 \small$^1$ Department of Physics,\\
@@
 Link\"{o}ping, Sweden\\
-$^2$ Department of Ecology\\ 
+\medskip
+\small$^2$ Department of Ecology\\ 
 P.O. Box 7044\\ 
@@
 SE-750 07 Uppsala, Sweden\\
-$^3$ D\'{e}partement de biologie\\ 
+\medskip
+\small$^3$ D\'{e}partement de biologie\\ 
 Universit\'{e} de Sherbrooke\\ 
 Sherbrooke, Canada
-\end{minipage}\begin{minipage}[h]{0.4\textwidth}
+\medskip
 \small$^\dagger$ Corresponding author:\\
 alyssa.cirtwill@gmail.com\\
-tel: +46 723 158464\\
-$^\ddagger$ anna.eklof@liu.se\\
-$^\star$ tomas.roslin@slu.se\\
-$^\diamond$ kate.wootton@slu.se\\
-$^\triangleright$ dominique.gravel@usherbrooke.ca
-\end{minipage}
+\medskip
+\medskip
+\normalsize Running head: Constructing quantitative interaction networks
+% tel: +46 723 158464\\
+% $^\ddagger$ anna.eklof@liu.se\\
+% $^\star$ tomas.roslin@slu.se\\
+% $^\diamond$ kate.wootton@slu.se\\
+% $^\triangleright$ dominique.gravel@usherbrooke.ca
 }
@@
 
-{\small
-\section*{\small Statement of authorship}
+% {\small
 
-DG designed the analytical approach. AC and DG wrote the code. AC performed statistical analyses. All authors contributed to writing and revising the manuscript.
+% \section*{\small Details}
 
-\section*{\small Data accessibility}
-
-All data used in this study have been independently published and are accessible following the references provided in text.
-
-\section*{\small Keywords}
-
-ecological networks; probabilistic interactions; Bayesian networks; sampling error; spatial variability; temporal variability; uncertainty
-
-\section*{\small Details}
-
-\begin{minipage}[h]{0.6\textwidth}
-\begin{itemize}
-\item Running title: Quantitative network construction
-\item Article type: Ideas and Perspectives
-\item Number of references: 36
-\item Number of figs, tables, \& text boxes: 8 % Limit is 10
-\end{itemize}
-\end{minipage}\begin{minipage}[h]{0.4\textwidth}
-\begin{itemize}
-\item Text box 1 word count: 381
-\item Text box 2 word count: 210
-\item Abstract word count: 199
-\item Main text word count: 6482 % Including 18 page numbers. % No abstract, acknowledgements, references, table or figure legends. Limit is 7500
-\end{itemize}
-\end{minipage}
-}
+% \begin{minipage}[h]{0.6\textwidth}
+% \begin{itemize}
+% \item Running title: Quantitative network construction
+% \item Article type: Ideas and Perspectives
+% \item Number of references: 36
+% \item Number of figs, tables, \& text boxes: 8 % Limit is 10
+% \end{itemize}
+% \end{minipage}\begin{minipage}[h]{0.4\textwidth}
+% \begin{itemize}
+% \item Text box 1 word count: 381
+% \item Text box 2 word count: 210
+% \item Abstract word count: 199
+% \item Main text word count: 6482 % Including 18 page numbers.
+% No abstract, acknowledgements, references, table or figure legends.
+Limit is 6000-7000 including figs, tables, references.
+approx.
+10K all in :/
+% \end{itemize}
+% \end{minipage}
+% }
 
@@
 
-  Descriptions of ecological networks typically assume that the same interspecific interactions occur each time a community is observed.
+  \begin{enumerate}
+
+    \item  Descriptions of ecological networks typically assume that the same interspecific interactions occur each time a community is observed.
 This contrasts with the known stochasticity of ecological communities: community composition, species abundances, and link structure all vary in space and time.
 Moreover, finite sampling generates variation in the set of interactions actually observed.
-Here we develop the conceptual and analytical tools needed to capture uncertainty in the estimation of pairwise interactions.
+    \item Here we develop the conceptual and analytical tools needed to capture uncertainty in the estimation of pairwise interactions.
 To define the problem, we identify the different contributions to the uncertainty of an interaction and its implications for the estimation of network properties.
@@
 We illustrate this framework using the most extensively sampled network to date.
-We found significant uncertainty in estimates for the probability of most pairwise interactions which we could, however, limit with informative priors.
-Through these efforts, we demonstrate the utility of our approach and the importance of acknowledging the uncertainty inherent in network studies.
+    \item We found significant uncertainty in estimates for the probability of most pairwise interactions which we could, however, limit with informative priors.
+This uncertainty scaled up to summary measures of network structure such as connectance or nestedness.
+Even with informative priors, our results suggest that the relatively well-sampled network we use as a test case is missing many interactions that may occur rarely or under different local conditions.
+    \item Through these efforts, we demonstrate the utility of our approach and the importance of acknowledging the uncertainty inherent in network studies.
 Most importantly, we stress that networks are best thought of as systems constructed from random variables, the stochastic nature of which must be acknowledged for an accurate representation.
 Doing so will fundamentally change networks analyses and yield greater realism.
-  % Can be up to 200 words. This is 200 exactly.
+  % Can be up to 350 words for MEE. This is 200 exactly.
+\end{enumerate}
 
-\linenumbers
+\section*{\small Keywords}
+
+ecological networks; probabilistic interactions; Bayesian networks; sampling error; spatial variability; temporal variability; uncertainty
+
+% \linenumbers
 \clearpage
@@
 To move from these simpler metrics to a network framework, the tabulation of nodes is combined with interactions (links between nodes) so that networks provide additional, higher-order information on community structure.
-While this additional information is useful (as, for example, interactions can affect changes in species abundances over time), empirical descriptions of ecological networks are still limited because they are usually considered to be static representations of the communities and interactions they describe.
+Despite this additional information, empirical descriptions of ecological networks are still limited because they are usually considered to be static representations of the communities and interactions they describe.
 That is, whether the network is assembled based on aggregated data, a single intensive ``snapshot" sample, or expert knowledge, interactions are assumed to occur deterministically wherever and whenever the community is observed~\citep{Olesen2011a}.
 
-    The assumption of static communities contrasts significantly with the widely recognised stochasticity of ecological communities~\citep{Gotelli2000}.
-Community composition and species abundances vary from site to site~\citep{Baiser2012} and over time within a site~\citep{Olesen2011a}.
-Likewise, interactions vary over space~\citep{Kitching1987,Baiser2012}, time~\citep{Kitching1987,Olesen2011a}, and between individuals of a given species~\citep{Pires2011a,Fodrie2015,Novak2015}.
-We emphasise that variability in community composition and interactions may or may not be closely related.
-The removal of a species from a site will obviously also remove its interactions but, conversely, the co-occurrence of potentially interacting species does not in itself guarantee that they will interact at a given place and time.
+    The assumption of static communities contrasts significantly with the known stochasticity of ecological communities~\citep{Gotelli2000}.
+Community composition and species abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a} while interactions vary over space~\citep{Kitching1987,Baiser2012}, time~\citep{Kitching1987,Olesen2011a}, and between individuals~\citep{Pires2011a,Fodrie2015,Novak2015}.
+Moreover, variability in community composition and interactions may or may not be closely related.
+The removal of a species from a site will obviously also remove its interactions but, conversely, the co-occurrence of potentially interacting species does not guarantee that the species will interact at a given place and time.
 Interactions can be lost if the interaction partners remain present but are separated in time or are too rare to detect each other~\citep{Tylianakis2010}.
@@
 
-    Beyond ``true" variation in network structure, several researchers have pointed to the importance of sampling intensity for the assessment of network structure (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007}).
+    Beyond ``true" variation in network structure, several researchers have pointed to the effects of sampling intensity on network structure (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007}).
 An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to document interactions than species~\citep{Poisot2012}.
@@
 Presences and absences are not, however, equally certain.
-An observed link will always remain an observed link but there are multiple reasons why a given link may not be observed.
-Thus, the detection of any interaction is a stochastic process.
+An observed link definitely occurred, but there are multiple reasons why a given link may not be observed whether or not the interaction truly occurred.
+The detection of any interaction is a stochastic process.
 We define three nested levels of uncertainty contributing to this stochasticity: interaction uncertainty, process uncertainty, and detection uncertainty.
@@
       First, and most fundamentally, we do not know whether or not a pair of species have the appropriate characteristics (or traits) to interact.
-We define the probability of an interaction $L$ given those characteristics $\mathbf{T}$ as $P(L | \mathbf{T})=\lambda$.
-Obviously, if $k$ (the number of observed interactions) is 0, it is possible that the two species would not interact even if there were no external constraints (e.g., temporal or environmental separation) preventing the interaction from co-occurring.
+We define the probability of an interaction $L$ given characteristics $\mathbf{T}$ as $P(L | \mathbf{T})=\lambda$.
+If two species have incompatible traits, they may not interact even if there are no other constraints (e.g., temporal separation of species, inability to detect cryptic species) preventing the interaction from being observed.
 As a simple example, a prey species may be too large to be consumed by a particular predator.
@@
 
-      Nevertheless, it is also possible that the interaction is a rare phenomenon with $\lambda>0$ that has not yet been documented.
-This source of uncertainty is the one documented by trait-matching models~\citep{Bartomeus2016}.
-It arises because every model is imperfect and lacks information (i.e.
-about traits) that could be used to define constraints on the interaction~\citep{Dormann2017}.
-Further study may, however, eventually reveal the traits of interest and allow us to reduce interaction uncertainty.
-In other words, with sufficient sampling and all information accessible, this interaction probability $\lambda$ should either tend to 0 or to 1.
+      Based on an observed network, however, it is often unclear whether an unobserved interaction is impossible due to incompatible traits or a rare phenomenon with $\lambda>0$.
+This uncertainty is partly addressed by trait-matching models~\citep{Bartomeus2016}.
+Nevertheless, every model is imperfect and lacks information (i.e.
+about traits) that could be used to define constraints on interactions~\citep{Dormann2017}.
+Some interaction uncertainty therefore remains in current trait-matching models.
+As more information about the influence of traits on interactions is uncovered, this uncertainty is likely to be reduced and $\lambda$ should either tend to 0 or to 1.
 
@@
      Even when an interaction is feasible, i.e.
-$L=1$, it may not occur at a given location or moment in time because of local constraints such as inclement weather or the lack of suitable habitat.
-We define the realisation of the interaction process with the variable $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L=1)=\chi$.
+$L=1$, it may still not occur at a given location or moment in time because of local constraints such as inclement weather or the lack of suitable habitat.
+We define the local realisation of an interaction with the variable $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L=1)=\chi$.
 This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology about the contingencies of interactions.
 Phenological matching~\citep{MillerRushing2010,Gezon2016}, species preferences~\citep{Pires2011,Novak2015,Coux2016}, and fear effects of other species~\citep{Luttbeg2005,Wirsing2008} are just some of the factors contributing to variation in the frequency of interactions between a given pair of species.
-Although some of the factors leading to process uncertainty can be addressed in mesocosm studies of networks (e.g., environmental conditions can be held stable), process uncertainty is likely inevitable in the field.
+Some of the factors leading to process uncertainty can be addressed in mesocosm studies of networks (e.g., environmental conditions can be held stable) or could be included in models along the line of trait-matching models (e.g., phenological matching).
+In the field, however, process uncertainty is likely inevitable.
 
@@
 Given that an interaction is feasible and occurs under the local conditions ($L$=1 and $X$=1), we may define the detection of an interaction, $D$, as a stochastic process with the associated probability $P(D|X=1,L=1)=\delta$.
-Detection failure could happen for several reasons including failure to rear a parasitoid, species mis-identification, or because the interaction is very rare (see~\citet{Wirta2014} for examples of some of these difficulties and partial solutions to them).
+Detection failure could happen for many reasons (see~\citet{Wirta2014} for examples of some of these difficulties and partial solutions to them).
 Some sources of detection error can be minimised with appropriate sampling effort ($\delta$ will converge to one with increasing number of samples), but other sources are often difficult to reduce (e.g.
@@
 
-    Together, the combination of these three sources of uncertainty --interaction uncertainty, process uncertainty, and detection uncertainty-- results in a range of potential explanations for the observation of an absence of interaction ($D$, $X$, and/or $L = 0$).
-The ecologist wanting to describe the network, however, is specifically interested in the situation where $L = 0$ (i.e., in true absences).
-Thus, while there is no difficulty interpreting the observation of an interaction, the observation of an absence of an interaction offers more of a challenge since it must be decomposed into different quantities.
+    An observed interaction indicates that an interaction was feasible, occurred at the study site during sampling, and was detectable.
+That is, $L = 1$, $X = 1$, and $D = 1$.
+An unobserved interaction could be due to any of the three sources of uncertainty ($D$, $X$, and/or $L = 0$).
+Only the case where $L = 0$ is a true absence of interaction --the usual interpretation of a $0$ value in an interaction matrix.
 It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e.
-where the interaction occurred at the location but was not observed, and $D=1 \cup X = 0 \cup L =1$, i.e., where the interaction is feasible and would have been detected but did not occur at the local site.
-The occurrence of a true absence, our quantity of interest, corresponds to the joint event $L=0 \cup X=1 \cup D=1$ but in reality an empirical ecologist will measure the marginal probability $P(L) = k/n$ where $k$ is again the number of observed interactions and $n$ the number of observed co-occurrences.
+where the interaction occurred at the location but was not observed, and $X = 0 \cup L =1$, i.e., where the interaction is feasible but did not occur at the local site.
+    % The occurrence of a true absence, our quantity of interest, corresponds to the joint event $L=0 \cup X=1 \cup D=1$ but %% AC: Doesn't a true absence just mean $L=0$ regardless of our ability to detect/local conditions?
+    Using empirical data, however, it is impossible to distinguish between sources of variation.
+An empirical ecologist will measure the marginal probability $P(L) = k/n$, where $k$ is the number of observed interactions and $n$ the number of observed co-occurrences.
+This probability does not contain any information about $D$ or $X$.
 
-    The considerations above raise a major challenge: when faced with empirical data, how may we infer whether unobserved interactions went undetected due to sampling or whether they truly do not occur?
-How then may we refine our sampling approaches to reduce uncertainties, and do we gain insights into the impact of multiple processes on field observations?
-Importantly, some sources of uncertainty can be minimised with appropriate sampling design and efforts while other sources are difficult or impossible to reduce since they are generated by chance variation created by the very process in which we are interested.
+    The considerations above raise major challenges: when faced with empirical data, how may we infer whether unobserved interactions truly do not occur?
+How may we refine our sampling approaches to reduce uncertainties gain insights into the impact of multiple processes on field observations?
+Importantly, some sources of uncertainty within these three broad groupings can be minimised with appropriate sampling (e.g., sampling in a variety of weather conditions, combining different methods of detection) while other sources are difficult or impossible to reduce since they are generated by the process in which we are interested (e.g., variation in individual preferences or traits).
 Given this multifaceted problem of uncertainty, what can we do to separate the different types of variation and reduce those that can be reduced?
 
-    The obvious rule of thumb is to ``sample more" (see Fig.~\ref{upper_limits} for a demonstration of the power of increasing sample size).
-Sampling more will clearly reduce uncertainty regarding the upper bound of the probability of interaction and it will also increase the probability of detecting unlikely interactions (e.g.,.
-interactions where $L$=1 but process uncertainty is high).
+    The obvious rule of thumb is to ``sample more" (Fig.~\ref{upper_limits}).
+Sampling more will reduce uncertainty about the upper bound of the interaction probability and will also increase the probability of detecting unlikely or cryptic interactions (e.g., interactions where $L$=1 but process or detection uncertainty is high).
 Despite these benefits, we note that there are limits to the utility of increased sampling.
-Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present; see Fig.~\ref{histograms}E-F), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions.
+Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig.~\ref{histograms}E-F).
 Thus, the more we sample, the more zeros will appear in our interaction matrix.
 
-    In one endeavour to determine whether unobserved interactions were undetected due to sampling, or whether they truly do not occur,~\citet{Weinstein2017} used repeated sampling rounds to estimate the daily probability of detecting a hummingbird interaction, and to thereby model detection and process uncertainty.
-While conceptually attractive, this approach is unsuitable for interactions occurring over longer time scales (e.g., associations between hosts and parasitoids with a single generation per year), or very rare interactions which might not occur on any of the sampling days or might involve individuals of a species that is not under observation.
-What is worse, the problem persists that the absence of an interaction of a given day could  either be because it was impossible on that day despite being otherwise feasible [$P(X|D=1,L=1)=0$], because interaction did occur but could not be observed [$P(D|X=1,L=1)=0$], or any combination of the two.
-From a conceptual perspective, this approach therefore fails to satisfactorily distinguish between sources of uncertainty.
-Most importantly, if two species are never observed co-occurring during several days of sampling then we have learned nothing about their probability of interacting if they should ever co-occur.
-In other words, there is no information about interactions without co-occurrence.
-
-    An added complication is that not all sources of uncertainty are proportional to sample size.
+    An added complication is that increased sampling will not reduce uncertainty evenly across interactions.
 To record an interaction between A and B, we need to identify both partners correctly (a non-trivial problem in many food webs; e.g.~\citealp{Kaartinen2011,Roslin2016}) and be able to resolve all interactions with a similar likelihood.
 For both molecular and rearing techniques, certain types of interactions may go unnoticed due to technical challenges~\citep{Wirta2014}.
-This can bias the set of recorded interactions.
+This can bias the set of recorded interactions towards those that are easier to observe.
+
+    A slight variation on the theme of ``sample more" is to sample repeatedly.
+In one endeavour to uncover the cause of unobserved interactions,~\citet{Weinstein2017} used repeated sampling rounds to estimate the daily probability of detecting an interaction and thereby model detection and process uncertainty.
+While conceptually attractive, this approach is unsuitable for interactions occurring over longer time scales (e.g., associations between hosts and parasitoids with a single generation per year), or very rare interactions which might not occur on any of the sampling days.
+Worse, the problem persists that the absence of an interaction on a given day could be because it was impossible on that day despite being otherwise feasible [$P(X|L=1)=0$], because interaction did occur but could not be observed [$P(D|X=1,L=1)=0$].
+From a conceptual perspective, this approach therefore fails to satisfactorily distinguish between sources of uncertainty.
+
+    Most importantly, if two species are never observed co-occurring during several days of sampling then repeated sampling reveals nothing about their probability of interacting if they should ever co-occur.
 The bottom line is that separating different sources of uncertainty is difficult indeed.
-As an alternative to abandoning empirical networks or continuing to ignore the uncertainty inherent in undetected observations, we propose that some insight regarding the detectability of interactions between species not found co-occurring in a focal system may be gained from data on other species pairs in the same or a similar system.
+Nevertheless, we propose that information on the probability of detecting interactions in a focal system can be obtained by combining repeated sampling with prior information from the same or a similar system.
 
@@
 
+\section*{Statement of authorship}
+
+DG designed the analytical approach. AC and DG wrote the code. AC performed statistical analyses. All authors contributed to writing and revising the manuscript.
+
+\section*{Data accessibility}
+
+All data used in this study have been independently published and are accessible following the references provided in text.
+
 \end{spacing}

### 2018-06-05 manuscript/CI_interactions.tex
less than 200 words too many now

@@
 
-  To progressively dissect the different contributions to uncertainty, we will start by considering how we could naively quantify interaction probability and its associated uncertainty \emph{for an interaction that has not yet been observed}.
-We consider the case where a pair of species have been observed co-occurring $n$ times, of which they have been observed to interact in $k = 0$ cases.
-We now aim to evaluate the uncertainty of this interaction.
-We consider the occurrence of an interaction as a Bernoulli trial.
-Consequently, the number of successes $k$ over $n$ trials will follow a binomial distribution:
+  We will start by considering how we could naively quantify interaction probability and its associated uncertainty \emph{for an interaction that has not yet been observed}.
+Consider the case where a pair of species have been observed co-occurring $n$ times, of which they have been observed to interact in $k = 0$ cases.
+To evaluate the uncertainty of this interaction, consider the occurrence of an interaction as a Bernoulli trial.
+In this framework, the number of successes $k$ over $n$ trials will follow a binomial distribution:
 
@@
 Given this variance, it is possible to compute the confidence interval for the MLE of $\lambda$ using any of several methods, including the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]).
-Finding this estimate is therefore quite straightforward, but it nonetheless has two drawbacks.
-First, $\lambda$ is not a single point estimate but rather a random variable with an unknown distribution.
+Finding this estimate is therefore quite straightforward.
+Importantly, $\lambda$ is not a single point estimate but rather a random variable with an unknown distribution.
 This means that if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact.
-Rather, $k = 0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless a substantial chance that the two species \emph{could} interact.
-In the situation where $k>0$, in contrast, we are sure that the interaction is feasible ($L = 1$) but still cannot be sure of the cause if the interaction is not observed at some sites/times (i.e., we cannot say why $k<n$).
-There may be local constraints ($X=0$) or we might simply not observe the interaction in every sample ($D<1$).
+Rather, $k = 0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless some chance that the two species \emph{could} interact.
+In the situation where $k>0$, in contrast, we are sure that the interaction is feasible ($L = 1$).
+If $n>k>0$, the interaction is feasible but there may be local constraints ($X=0$) or detection errors ($D<1$) causing the interaction not to be observed in some samples.
+% The non-point nature of lambda seems like a feature, not a bug.
 
-  Second, where the number of samples $n$ is very low (some pairs of species may never have been documented as co-occurring), there will be considerable uncertainty around our estimate of $\lambda$.
-In Fig.~\ref{upper_limits} and Box 2, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda$ varies with sample size.
+  Treating $\lambda$ as a distribution does, however, have an important drawback.
+Where the number of samples $n$ is very low, as for rare species, there will be considerable uncertainty around our estimate of $\lambda$.
+In Fig.~\ref{upper_limits}, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda$ varies with sample size.
 At a small sample size, the 95\% confidence interval spans all values of $\lambda$.
 To establish that species are not interacting with any acceptable certainty requires tens of observations of the two species co-occurring but not interacting.
-As most data sets will lack such extensive sampling across all species pairs, we can use a Bayesian approach to supplement what data we do have with other sources of information.
+As most data sets will lack such extensive sampling across all species pairs, we can use a Bayesian approach to supplement the data we have with other sources of information.
 
@@
 In other words, the distribution of $\lambda$ for better-sampled pairs of species will rely less on the information used to build the prior distribution and depend more on the observed data.
-      When plotted, we find the shape of the distribution gets narrower with $k$ and $n$ (Fig.~\ref{Salix_pdfs}).
+      When plotted, we find the shape of the distribution gets narrower with $k$ and $n$ (Fig.~\ref{Salix_pdfs_cdfs}).
 
@@
 
-      Parameters $\alpha$ and $\beta$ determine the shape of the prior distribution, which follows a beta distribution.
+      Parameters $\alpha$ and $\beta$ determine the shape of the prior distribution of $\lambda$, which follows a beta distribution.
 These are called hyper parameters.
-Below we identify four ways to formulate the prior distribution of $\lambda$.
-
-      \subsubsection*{Uninformative prior}
-
-          In the absence of any external information, an uninformative prior is the most conservative hypothesis for the distribution of $\lambda$.
-The beta distribution is in this case a uniform distribution, specified with hyper parameters $\alpha=1$ and $\beta=1$.
-
-      \subsubsection*{Distribution of connectance}
-
-          The ecological network literature boasts a collection of networks for which connectance has been calculated and for which we can thus define the connectance distribution.
-Connectance is measured as $C = L/S^2$, where $L$ is the number of interactions and $S$ is the number of species.
-It measures the filling of an interaction matrix and thereby expresses the average probability that any two species interact with each other.
-If we know only the mean $\overline{C}$ and the variance $\sigma_C^2$ of the distribution of $C$,          then the beta parameters could be computed as follows using the method of moments:
-
-          \begin{equation}
-          \alpha = \overline{C}(\frac{\overline{C}(1-\overline{C})}{\sigma_C^2}-1) ,
-          \end{equation}
-
-          \begin{equation}
-          \beta = (1-\overline{C})(\frac{\overline{C}(1-\overline{C})}{\sigma_C^2}-1) .
-          \end{equation}
-
-      \subsubsection*{Degree distribution or interaction probabilities}
-
-          The degree of a node in a network is defined as its number of connections to other nodes.
-The degree distribution of a network is then the probability distribution of these degrees over the whole network and the standardised degree could therefore be interpreted as an interaction probability.
-It is consequently possible to use the degree distribution to inform the prior distribution.
-The degree distribution could come from several networks, from a similar network (e.g.
-a known network at slightly different location) or from the network of interest if interaction probabilities for some species are already documented.
-The latter approach allows researchers to apply information from known, abundant species to the rarest species for which interactions are less frequently documented.
-
-          If our focal network describes a system similar to that in a known network, we can use the distribution of interaction probabilities in that network to inform our prior.
-The probability of any interaction $L_{ij}$ depends on the degrees of species $i$ and $j$.
-Using normalised degrees $\Delta_i$ and $\Delta_j$ (i.e., degrees divided by the number of species in the network), we can obtain the probability of interaction $L_{ij}$=$\Delta_i\times\Delta_j$.
-Similar to the procedure for degree distribution, the distribution of these interaction probabilities can be used to establish a prior distribution before any data from the focal network are collected.
-For distributions of either degrees or interaction probabilities, the procedure for the estimation of the hyper parameters follows the same approach as described above for connectance except that each measurement is at the individual interaction level instead of the network level.
-
-      \subsubsection*{Trait-matching function}
-
-          As a fourth and final approach, it may be possible to obtain the prior distribution of $\lambda$ using the outcome of a trait-matching model, provided such a model has been parameterised using external data and relevant traits are available.
-In such a case, the prior distribution would follow the function $P(\lambda|\mathbf{T})=f(\mathbf{T})$ based on a set of traits for both species $\mathbf{T}$.
-There are several techniques available to perform this inference of interaction probability, some of which are Bayesian, and we refer to~\citet{Bartomeus2016} and~\citet{Weinstein2017} for recent reviews about this topic.
-Note that in this case the prior might not be beta-distributed and numerical methods might be required to compute the posterior distribution.
-
-\section*{A quantitative example}
-
-  The Bayesian framework can be illustrated with a simple quantitative example.
-Suppose we have $n = 10$ observations of co-occurrence between species $i$ and species $j$ in a given time interval and area, and $k = 3$ observations of interactions.
-The maximum likelihood estimate of the interaction probability is simply $\lambda_{MLE} = 3/10 = 0.3$.
-
-  Now consider we know that species $i$ is known to interact with 10 species (other than species $j$), which have the following degrees:
-
-    \vspace{12pt}
-    \noindent\emph{
-      degree=c(14, 4, 2, 3, 17, 6, 2, 15, 1, 1)
-        }.
-      \vspace{12pt}
-
-    If the network has 20 species total, this gives the normalised degrees:
-
-    \vspace{12pt}
-    \noindent\emph{
-      norm\_degree=c(0.65, 0.20, 0.10, 0.15, 0.85, 0.30, 0.10, 0.75, 0.05, 0.05)}.
-      \vspace{12pt}
-
-    Species $i$ has a normalised degree of 0.55 (it interacts with species $j$ and 10 other species).
-We can combine the normalised degree of $i$ with the normalised degrees of its interaction partners to obtain the following set of interaction probabilities for species $i$ and each of its interaction partners:
-
-    \vspace{12pt}
-    \noindent\emph{
-       int\_probs = c(0.358, 0.110, 0.055, 0.082, 0.468, 0.165, 0.055, 0.412, 0.028, 0.028) }.
-      \vspace{12pt}
-
-    The mean of these interaction probabilities is 0.176, approximately two-thirds the $\lambda_{MLE}$ obtained from the observed data.
-We can use the distribution of these interaction probabilities as our prior distribution and estimate the uncertainty surrounding our $\lambda_{MLE}$.
-With some simple R code (function ``calculate\_parameters", \emph{Appendix S1}), we obtain prior parameters $\alpha$=0.998 and $\beta$=4.63.
-Using these priors in equations~\ref{mean} and~\ref{variance} above (or in the R function ``calculate\_distribution" in \emph{Appendix S1}), we find a prior $\bar\lambda$=0.177 and var($\lambda$)=0.026.
-Adding the observed data ($n=10$, $k=3$) and using the same code, we obtain posterior parameters $\alpha'$=4.00 and $\beta'$=11.6 and a posterior $\bar\lambda$=0.256 and var($\lambda$)=0.012.
-Comparing the posterior distribution to the prior, we see that the posterior is closer to the observed data and that the additional data about interactions between species $i$ and $j$ has reduced the variance.
-We may also wish to calculate a credible interval (analogous to the frequentist confidence interval).
-This is also quite straightforward in R (see function ``credible\_interval" in \emph{Appendix S1}).
-In this case, a 95\% credible interval for $\bar\lambda$ is (0.080, 0.491).
-
-    Now, consider the case where the two species have never been observed interacting across $n$ trials, i-e.
-$k=0$.
-The question is then ``what is the probability that these two species do not interact''?
-Since it is not possible to prove that the two species could never interact (strictly speaking, in a Bayesian approach $\lambda=0$ is impossible), we must fix a threshold below which we consider that there is no interaction ($\lambda \sim 0$).
-We call this threshold probability $\lambda*$.
-We then use the cumulative distribution function to estimate $P(\lambda<\lambda*|L=0,n)$ for different $n$.
-The function ``samples\_for\_threshold" in \emph{Appendix S1} calculates distribution function for $\lambda*$ with an increasing number of trials.
-This yields a surprising result: it requires \textgreater24 observations of no interactions to be 95\% sure that the interaction probability is smaller than $\lambda*$=0.1 (recall Fig.~\ref{upper_limits}, Box 2).
-Note the special case where there is no observation of the two species co-occurring, $n = 0$.
-In this situation, the posterior distribution converges to the prior distribution since the data include no information on the probability with which species might interact should they co-occur.
+The prior may be chosen to be uninformative, if no external information is available, or may draw on information such as distributions of connectance across webs, degree within webs, or a trait-matching function (see \emph{Appendix S1} for details and a simple quantitative example).
 
@@
     In the following section, we will provide an empirical example based on the well-sampled system of \emph{Salix} plants, herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}; see Box 1 or \emph{Appendix S2} for a description).
-Using this dataset, we will demonstrate the derivation of prior distributions for the \emph{Salix}-galler and galler-natural enemy components of these networks and the differences between these priors and posterior distributions which include all information available in this dataset~\citep{Kopelke2017}.
+Using this dataset, we will demonstrate the derivation of prior distributions for the galler-natural enemy component of these networks (see \emph{Appendix S3} for the \emph{Salix}-galler component) and the differences between these priors and posterior distributions which include all information available in this dataset~\citep{Kopelke2017}.
 Finally, we will calculate network properties using a suite of networks sampled from these posterior distributions and show how the uncertainty around interactions that have not been observed impact these metrics.
 
-  \subsection*{Computing the posterior distribution}
+  \subsection*{Computing the prior and posterior distributions}
 
@@
 
-      To obtain the priors based on the Zillis sub-network, we estimated frequencies of \emph{Salix}-galler interactions based on the normalised degree of each species in each network component (see \emph{Appendix S3} for details and code).
-Specifically, we obtained prior parameters of $\alpha$=8.72, $\beta$=305 for the \emph{Salix}-galler component and $\alpha$=0.700, $\beta$=8.49 for the galler-natural enemy components of the network.
+      To obtain the priors based on the Zillis sub-network, we estimated frequencies of interactions based on the normalised degree of each species in each network component
+      (see \emph{Appendix S6} for details and code).
+Specifically, we obtained prior parameters of $\alpha$=0.700, $\beta$=8.49.
 After calculating these prior parameters, we were then able to estimate the posterior distribution of interaction probabilities given the additional information in our dataset.
 
-      For species where no co-occurrences were observed ($n=0$), we can calculate the estimates for the mean and variance of $\lambda_{ij}$ directly from the prior parameters following equations~\ref{mean} and~\ref{variance} (see \emph{Appendix S1} for R implementation).
-For the \emph{Salix}-galler network, the prior distribution  was: $\bar\lambda$=0.028, var($\lambda$)=8.60$\times$10$^{-5}$.
-The prior distribution for the galler-natural enemy network was: $\bar\lambda$=0.076, var($\lambda$)=0.008.
+      For species where no co-occurrences were observed ($n=0$), we can calculate the estimates for the mean and variance of $\lambda_{ij}$ directly from the prior parameters following equations~\ref{mean} and~\ref{variance} (see \emph{Appendix S7} for R implementation).
+For these interactions, we obtain $\bar\lambda$=0.076, var($\lambda$)=0.008.
 The posterior interaction probabilities obtained based on the Zillis sub-network were much lower than those obtained based on~\citet[Data available from the Dryad Digital Repository: https://doi.org/10.5061/dryad.g7805]{Barbour2016}; this emphasises the importance of using an appropriate study system when constructing a prior (\emph{Appendix S4}).
 
-      For a pair of species with some observed co-occurrences ($n>0$), we can update the prior distribution with these data.
-If we consider only pairs of species which were observed to co-occur but not to interact, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs, giving $\alpha'$=$\alpha$ and $\beta'$=$\beta + n_{ij}$.
+      For a pair of species with some observed co-occurrences ($n>0$), we can update the prior distribution with data.
+If we consider only pairs of species which were observed to co-occur but not to interact, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs.
+This gives $\alpha'$=$\alpha$ and $\beta'$=$\beta + n_{ij}$.
 As the most extreme case, consider a pair of species which co-occurred at all 374 sites and was never observed to interact.
-Using the priors described above, our distribution for the \emph{Salix}-galler network would become $\bar\lambda_{ij}$=1.27 $\times$ 10$^{-2}$, var($\lambda_{ij}$)=1.82 $\times$ 10$^{-5}$ while our distribution for the galler-natural enemy network would become $\bar\lambda_{ij}$=1.83 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=4.76.
-Distributions for both network components were very close to 0 with small variance about our estimate of $\lambda$; species $i$ and $j$ are extremely unlikely to interact at sites or times not included in our sample.
+Using the priors described above, our distribution would become $\bar\lambda_{ij}$=1.83 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=4.76.
+This distributions is very close to 0 with small variance about $\lambda$; species $i$ and $j$ are extremely unlikely to interact at sites or times not included in our sample.
 
       For most pairs of species $i$ and $j$, however, $n_{ij}$ was much less than 374 and our posterior mean and variance therefore retain more of the influence of the prior.
-We can see this in the increasing means and variances as we decrease $n_{ij}$ (Fig.~\ref{Salix_pdfs}).
+We can see this in the increasing means and variances as we decrease $n_{ij}$ (Fig.~\ref{Salix_pdfs_cdfs}).
 The change in distribution as $n_{ij}$ decreases can also be shown  by calculating 95\% credible intervals for $\lambda$ (see the function ``credible\_interval" in \emph{Appendix S2}).
-The 95\% credible interval around the estimate of $\lambda$ also widens as $n_{ij}$ decreases from (0.001, 0.017) and (\textless0.001, 0.11) for hypothetical \emph{Salix}-galler and galler-natural enemy pairs that might be observed co-occurring at all 374 sites without any observed interaction to (0.152, 0.931) and (0.008, 0.364) for \emph{Salix}-galler and galler-natural enemy pairs that were never observed co-occurring.
-The 95\% credible interval for hypothetical \emph{Salix}-galler pairs widened from (0.006, 0.022) if the pair co-occurred at all sites to (0.013, 0.049) if they co-occurred at none.
 The 95\% credible interval for hypothetical galler-natural enemy pairs, meanwhile, widened from (0.00001, 0.008) to (0.0005, 0.304).
@@
       Rather than calculating credible intervals for a posterior distribution after collecting data, we may wish to know how many data points are necessary to obtain a given level of confidence that two co-occurring species do not interact.
-The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact (Fig.~\ref{Salix_cdfs}; see function samples\_for\_threshold in~\emph{Appendix S1}).
-In our dataset, the entire 95\% credible interval was (0.013, 0.049).
-We may therefore be 95\% confident that the interaction probability for \emph{Salix} and galler species that have not been observed co-occurring is below 0.05.
-As the peak of the prior distribution for the probability of interaction between \emph{Salix} and galler probabilities is around 0.02 (Fig.~\ref{Salix_pdfs}), to be 95\% confident that the interaction probability for these species is below 0.01 would require 1029 observed co-occurrences with no interaction - far more than the number of sites in the~\citep{Kopelke2017} dataset.
-
-      The number of samples required to be 95\% confident that the interaction probability between galler and natural enemy species is below a threshold also increases quickly as the threshold decreases.
+The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact (Fig.~\ref{Salix_pdfs_cdfs}; see function samples\_for\_threshold in~\emph{Appendix S3}).
+The number of samples required to be 95\% confident that the interaction probability between galler and natural enemy species is below a threshold increases quickly as the threshold decreases (\emph{Appendix S5}).
 The 95\% credible interval is (\textless0.001, 0.303) for the probability of interaction between two species observed to co-occur but never interact.
@@
 
-    It is fairly straightforward to compute most network metrics when the different $\lambda$ of the adjacency matrix are known and assumed not to vary without variance~\citep{Poisot2016}.
-Several of these metrics derive directly from quantitative indices of network structure which are equivalent to $\lambda$.
-The remainder, originally defined for binary networks, can be adjusted to account for interaction probabilities between zero and one.
-It is not as easy, however, to understand how the uncertainty in these estimated interaction probabilities influences network metrics.
-Computation of these metrics involves non-linear functions.
-Since Jensen's inequality states that the average of a non-linear function of a stochastic variable differs from the function of the average of that variable, any uncertainty in the values of $\lambda$ could bias both the mean and variance of a network metric.
+    It is straightforward to compute most network metrics when the different $\lambda$ of the adjacency matrix are known and assumed not to vary~\citep{Poisot2016}.
+Incorporating variance in $\lambda$ into these calculations, however, is not so easy.
+Computation of these metrics involves non-linear functions, and Jensen's inequality states that the average of a non-linear function of a stochastic variable differs from the function of the average of that variable.
+Any uncertainty in the values of $\lambda$ could therefore bias both the mean and variance of a network metric.
 One way to avoid potentially biased analytical calculation of network properties is to calculate the properties of a suite of simulated networks.
 
-    Using the prior distributions and procedures described above, we calculated posterior probability distributions for \emph{Salix}-galler or galler-natural enemy pairs that were not observed interacting.
-Using these posterior distributions and assuming probabilities of 1 for pairs of species that were observed interacting, we created a suite of 100 webs of each network type by randomly sampling from each posterior distribution.
-After obtaining these posterior networks, we calculated the connectance of each web, as well as the number of links per resource (\emph{Salix} in the \emph{Salix}-galler networks or galler in the galler-natural enemy networks) and links per consumer.
+    Using the prior distributions and procedures described above, we calculated posterior probability distributions for species pairs that were not observed interacting.
+Using these posterior distributions and assuming probabilities of 1 for pairs of species that were observed interacting, we created a suite of 100 webs by randomly sampling from each posterior distribution.
+After obtaining these posterior networks, we calculated the connectance of each web, as well as the mean number of links per galler and per natural enemy, and the nestedness (NODF) of the network.
 To demonstrate how these network metrics will be affected by detection uncertainty, we then created a suite of filtered networks for each posterior network.
@@
 This gradient is akin to a gradient of sampling effort.
-For each level of detection accuracy, we created 100 randomly-sampled networks per posterior-probability network (giving 100 posterior networks and 1000 detection-filtered networks each for the \emph{Salix}-galler and galler-natural enemy networks).
-We then calculated the same network properties as described above.
+For each level of detection accuracy, we created 100 randomly-sampled networks per posterior-probability network (giving 100 posterior networks and 1000 detection-filtered networks).
+We calculated the same network properties as described above for all posterior and detection-filtered networks.
 
-    We find, perhaps not surprisingly, that the posterior webs for the Salix-galler network  had higher connectances than the original, observed web (C=0.028 for the observed web and 0.082 $\leq$ C $\leq$ 0.096 for the posterior webs; Fig.~\ref{posterior_webs}A).
-The number of links per \emph{Salix} species in the observed web ($L_{\emph{Salix}}$=2.71) was similar to those in the posterior webs (2.53 $\leq L_{\emph{Salix}} \leq$ 3.19; Fig~\ref{posterior_webs}C).
-The number of links per galler, however, was lower in the observed web ($L_{galler}$=1.47) than in the posterior webs, accounting for the increased connectance (4.67 $\leq L_{galler} \leq$ 5.88; Fig.~\ref{posterior_webs}E).
-There was a more substantial difference in the nestedness of the observed and posterior webs: the observed network had NODF=0.560 while the posterior networks were more nested (1.39 $\leq NODF \leq$ 1.94).
-Even the networks sampled with a detection filter of 50\% had non-zero nestedness (Fig.~\ref{posterior_webs}G).
-This last result highlights the potential for the possibility for network structure to vary when considering the possibility that unobserved species pairs may interact.
-
-    Considering the galler-natural enemy networks, the connectance, mean links per galler, and mean links per natural enemy were also much lower in the observed web (C=0.078, $L_{galler}$=9.99, and $L_{natural enemy}$=7.45, respectively) than in the posterior webs (0.186 $\leq$ C $\leq$ 0.198, 13.4 $\leq L_{galler} \leq$ 14.6, and 23.4 $\leq L_{natural enemy} \leq$ 25.0).
-When the detection probability was relatively low (i.e., 50\%), however, the properties of randomised networks became similar to those in the observed webs (Fig.~\ref{posterior_webs}B,D,F).
-Nestedness was higher in the observed network (NODF=6.85) than in the posterior webs (6.31 $\leq NODF \leq$ 6.82; Fig.~\ref{posterior_webs}H); in this case, the stronger the detection filter the farther apart were the observed and posterior webs.
+    We found that the connectance, mean links per galler, and mean links per natural enemy were much lower in the observed web (C=0.078, $L_{galler}$=9.99, and $L_{natural enemy}$=7.45, respectively) than in the posterior webs (0.186 $\leq$ C $\leq$ 0.198, 13.4 $\leq L_{galler} \leq$ 14.6, and 23.4 $\leq L_{natural enemy} \leq$ 25.0).
+When the detection probability was relatively low (i.e., 50\%), however, the properties of randomised networks became similar to those in the observed webs (Fig.~\ref{posterior_webs}A,B,D).
+Nestedness was higher in the observed network (NODF=6.85) than in the posterior webs (6.31 $\leq NODF \leq$ 6.82; Fig.~\ref{posterior_webs}C); in this case, the stronger the detection filter the farther apart were the observed and posterior webs.
 
@@
 This dataset consists of a single community type sampled across Europe: willow (\emph{Salix}) species, willow-galling sawflies, and their natural enemies.
-The data were collected over 29 years at 374 unique locations across Europe with a total of 641 site visits.
-Each site visit or each unique site can be considered as a network in its own right or as an independent sample from which to build the meta-network.
-Here we take the more conservative approach and pool visits to the same site for a sample size of 374 sub-networks.
+The data were collected over 29 years at 374 unique locations across Europe.
 The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes.
 The high spatiotemporal resolution of this network and the unusually high sampling effort implemented at the site level makes this dataset particularly well suited for illustrating the difficulties in completely sampling a network and testing Bayesian approaches to overcome these difficulties.\\
-    \indent We may begin by comparing the frequency of co-occurrences for pairs of species in each part of the network to reveal the challenge of having sufficient sampling to be confident that an interaction does not occur.
-Most pairs of species (3,986/4,992 \emph{Salix}-galler pairs and  9,794/12,096 galler-natural enemy pairs) are never found co-occurring and, for species that did occur together, the total number of co-occurrences was generally low (mean=4.24, variance=36.3 for \emph{Salix}-galler pairs; mean=3.87, variance=28.8 for galler-natural enemy pairs; Fig.~\ref{histograms}A-B).
-The bulk of these co-occurring species pairs were never observed to interact: only 2.82\% of \emph{Salix}-galler pairs and 7.76\% of galler-natural enemy pairs were observed interacting at one or more sites.
-Of those pairs that did interact, the incidence of interaction was also low (mean=12.0, variance=155 for \emph{Salix}-galler pairs; mean=4.04, variance=29.3 for galler-natural enemy pairs; Fig.~\ref{histograms}C-D).
+    \indent We may begin by comparing the frequencies of co-occurrences and interactions to reveal the challenge of having sufficient sampling to be confident that an interaction does not occur.
+Most pairs of species (9,794/12,096 galler-natural enemy pairs) are never found co-occurring and, for species that did occur together, the total number of co-occurrences was generally low (mean=3.87, variance=28.8; Fig.~\ref{histograms}A).
+The bulk of these co-occurring species pairs were never observed to interact: only 7.76\% of galler-natural enemy pairs were observed interacting.
+Of those pairs that did interact, the incidence of interaction was also low (mean=4.04, variance=29.3; Fig.~\ref{histograms}B).
 Thus, even in the most extensive data set that we could find, there was very little empirical data for each species pair.
 This suggests that limited sampling is a major source of uncertainty in all empirical networks.
-This dataset also illustrates the potential for increased sampling to not necessarily reveal more interactions as a pair of species that is able to interact may not be observed interacting in all samples where the pair co-occurs (Fig.~\ref{histograms}E-F).
-  \end{spacing}
-\end{fullbox}
-
-\clearpage
-
-\begin{fullbox}{}
-    \begin{spacing}{1.0}
-    \textbf{Box 2: }Calculating the credible interval around a probability estimate\\
-  \indent Here we describe the derivation of the Clopper-Pearson credible interval for the estimated probability of interaction $\lambda$ of a pair of species observed co-occurring $n$ times and interacting $k$ times.
-As we are most interested in the probability of interaction between species pairs that have never been observed co-occurring, we consider only the case where $k=0$ over a variety of $n$.
-This is straightforward to do in R (see the function ``credible\_interval" in \emph{Appendix S1}).
-
-  First, we must obtain the $\alpha$ and $\beta$ parameters for the prior distribution.
-In this study we obtained these parameters using the R~\citep{R} function fitdist from the package fitdistrplus~\citep{fitdistrplus}.
-Once $\alpha$ and $\beta$ are known, we can update them using our observed data.
-Specifically, we are interested in $\alpha'=\alpha+k$ and $\beta'=\beta+n-k$.
-These parameters can then be used to calculate a credible interval using the R~\citep{R} function qbeta.
-In the table below, we present the 95\% credible intervals for \emph{Salix}-galler and galler-natural enemy pairs with different numbers of observed co-occurrences ($n$) and no observed interactions ($k=0$), calculated using prior information derived from the Zillis sub-network~\citep{Kopelke2017}.
-
-      % % # R code to make the table:
-      % ns=c(0,1,2,5,10,15,20,25,50,100,150,200,374)
-      % output=matrix(nrow=length(ns),ncol=5)
-      % output[,1]=ns
-      % for(r in 1:nrow(output)){
-      %   interval1=credible_interval(calculate_parameters(sg_int_probs,ns[r],0),0.025,0.975)    
-      %   interval2=credible_interval(calculate_parameters(gp_int_probs,ns[r],0),0.025,0.975)    
-      %   output[r,2:3]=interval1
-      %   output[r,4:5]=interval2
-      % }
-      \medskip
-        \textbf{Table 1:} Here we give the lower and upper bounds of 95\% credible intervals for the probability of interaction $\lambda$ between \emph{Salix}-galler or galler-natural enemy pairs that have been observed co-occurring $n$ times but have never been observed interacting.\\
-        \begin{tabular}{l  c c  c c }
-        \multirow{2}{*}{$n$} & \multicolumn{2}{c}{\emph{Salix}-galler} & \multicolumn{2}{c}{galler-natural enemy}\\
-         & Lower bound & Upper bound & Lower bound & Upper bound \\
-        \hline
-        0   & 0.013 & 0.049 & 5.39 $\times10^{-4}$ & 0.304 \\
-        1   & 0.013 & 0.048 & 4.82 $\times10^{-4}$ & 0.276 \\
-        2   & 0.013 & 0.048 & 4.35 $\times10^{-4}$ & 0.253 \\
-        5   & 0.012 & 0.048 & 3.37 $\times10^{-4}$ & 0.203 \\
-        10  & 0.012 & 0.047 & 2.45 $\times10^{-4}$ & 0.152 \\
-        15  & 0.012 & 0.046 & 1.93 $\times10^{-4}$ & 0.121 \\
-        20  & 0.012 & 0.046 & 1.59 $\times10^{-4}$ & 0.101 \\
-        25  & 0.012 & 0.045 & 1.35 $\times10^{-4}$ & 0.087 \\
-        50  & 0.011 & 0.042 & 7.72 $\times10^{-5}$ & 0.050 \\
-        100 & 0.010 & 0.037 & 4.16 $\times10^{-5}$ & 0.027 \\
-        150 & 0.009 & 0.033 & 2.84 $\times10^{-5}$ & 0.019 \\
-        200 & 0.008 & 0.030 & 2.16 $\times10^{-5}$ & 0.014 \\
-        \hline
-        374 & 0.006 & 0.022 & 1.18 $\times10^{-5}$ & 0.008 \\
-        \hline
-        \end{tabular}
+This dataset also illustrates the potential for increased sampling to not necessarily reveal more interactions as a pair of species that is able to interact may not be observed interacting in all samples where the pair co-occurs (Fig.~\ref{histograms}C).
   \end{spacing}
@@
   \begin{figure}[h!]
-      \caption{\textbf{A-B)} Most pairs of \emph{Salix} and gallers or gallers and natural enemies were never observed co-occurring despite the high levels of replication in our example dataset.
-For those pairs that were observed together at least once ($n_{ij}>0$), the number of observed co-occurrences was generally small (\textless10).
-Here we show a histogram of the number of pairs of species observed co-occurring at least once.
-3986 \emph{Salix}-galler and 9794 galler-enemy pairs were never observed co-occurring: these pairs are omitted from the histogram.
-\textbf{C-D)} Most pairs of species that were observed at the same site were never observed interacting.
-Here we show a histogram of the number of observed interactions within pairs of co-occurring species.
-Species which co-occurred but never interacted are included in these histograms.
-\textbf{E-F)} Here we show, for each species pair, the number of observed interactions plotted against the number of observed co-occurrences.
-\emph{Salix}-galler pairs either are never observed interacting or interact almost every time they co-occur, while galler-enemy pairs had more variable frequencies of interaction.
-In panels E and F the red, dashed line indicates a 1:1 relationship between interactions and co-occurrences.}
+      \caption{Despite the high levels of replicaiton in our example dataset, most galler-natural enemy pairs were never observed co-occurring, and those that did co-occur were rarely observed interacting.
+\textbf{A)} Here we show a histogram of the number of pairs of species observed co-occurring at least once; the 9794 galler-enemy pairs that were never observed co-occurring are omitted.
+      \textbf{B)} Here we show a histogram of the number of observed interactions within pairs of co-occurring species. Species which co-occurred but never interacted are included. 
+      \textbf{C)} Here we show, for each species pair, the number of observed interactions plotted against the number of observed co-occurrences.
+The red, dashed line indicates a 1:1 relationship between interactions and co-occurrences.}
       \label{histograms}
       \begin{center}
-      \includegraphics*[width=.8\textwidth]{figures/Salix_Galler_histogram.eps}
+      \includegraphics*[height=.6\textheight]{figures/GP_histogram.eps}
       \end{center}
@@
   \begin{figure}[h!]
-    \caption{A simple example will illustrate the problem of imperfect detection of interactions.
-Assume that we want to infer the probability of an interaction between two species, $i$ and $j$.
-Now assume that in reality, interaction between $i$ and $j$ is completely impossible (i.e.
-the true $\lambda=0$) but the observer does not know this and seeks to estimate this interaction probability ($\lambda$).
-The number of observed interactions will follow a binomial distribution with number of interactions $k$ and number of observations $n$.
+    \caption{Imperfect detection of interactions has a strong effect on the number of samples required to be confident that an interaction does not occur.
+Assume that we want to infer the probability of an interaction between two species, $i$ and $j$ and that this interaction is completely impossible (i.e.
+the true $\lambda=0$).
+When estimating $\lambda$, the number of observed interactions will follow a binomial distribution with number of interactions $k$ and number of observations $n$.
 Using this distribution, we can compute the credible interval of the estimated probability $\lambda$.
-Even assuming no added detection error in observing the incidence of the interaction, a single observation of species co-occurrence reveals very little regarding the probability of the interaction as the credible interval for a pair of species with one observation essentially spans from 0 to 1.
-Only with 35 observations will the upper limit of the credible interval be lowered to 0.1.
-Thus, adding more observations is certainly useful in controlling uncertainty, but the number of observations added needs to be very high.
-Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true credible interval for $\lambda$ when $k=0$ ($i$ and $j$ have not been observed interacting) for a variety of $n$ (observed co-occurrences of $i$ and $j$).
-Using a Bayesian approach with an informative prior can reduce the confidence interval about $\lambda$ for a given sample size.
+A single observation of species co-occurrence reveals very little regarding the probability of the interaction as the credible interval for a pair of species with one observation essentially spans from 0 to 1.
+Only with 35 observations will the upper limit of the credible interval be lowered to 0.1 (dashed, red line).
+Thus, adding more observations is useful in controlling uncertainty, but the number of observations added needs to be very high.
+Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true credible interval for $\lambda$ when $k=0$ ($i$ and $j$ have not been observed interacting) for a variety of $n$.
 A threshold interaction probability of 0.1 is indicated by the dashed red line.
@@
   \begin{figure}[h!]
-    \caption{Using prior distributions based on the \emph{Salix}-galler and galler-natural enemy networks sampled at a single site in~\citet{Kopelke2017}, we can calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting.
-Here we show posterior distributions for $\lambda$ in each network component ranging from the prior distribution ($n=0$ observed co-occurrence) to the distribution obtained when the pair of species has been observed co-occurring 100 times.
-The distribution narrows and approaches zero as the sample size increases.
+    \caption{Using prior distributions based on the galler-natural enemy network sampled at a single site in~\citet{Kopelke2017}, we calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting ($k = 0$).
+    Posterior distributions for $\lambda$ narrow and approach zero as the number of observed co-occurrences ($n$) increases.
 Likewise, the maximum likelihood estimator for the mean probability of interaction (diamonds at top of each panel) approaches zero and the 95\% credible interval (lines at top of each panel) narrows as sample size increases.
-\textbf{A)} The posterior distributions for $\lambda$ in the \emph{Salix}-galler component are narrower at low $n$ but shrink less with increased sampling than those for \textbf{B)} the distributions of $\lambda$ in the galler-natural enemy component.}
-    \label{Salix_pdfs}
+    Dashed lines indicate threshold probabilities of 0.01, 0.05, and 0.1.
+The number of samples required to obtain a 95\% credible interval below each threshold increases rapidly.
+It takes just over 20 observed co-occurrences to be 95\% confident that $\lambda<0.10$, approximately 50 co-occurrences to be 95\% confident that $\lambda<0.05$, and over 100 co-occurrences to be 95\% confident that $\lambda<0.01$.
+Increasing the desired confidence level will also increase the number of samples required.
+    }
+    \label{Salix_pdfs_cdfs}
     \begin{center}
-    \includegraphics*[width=.7\textwidth]{figures/Salix_Galler_pdfs_increasing_N_Zillis.eps}
+    \includegraphics*[width=.8\textwidth]{figures/GP_pdfs_increasing_N_Zillis.eps}
     \end{center}
@@
 
-  \begin{figure}[h!]
-    \caption{The number of samples required to achieve a given level of confidence that an interaction probability $\lambda_{ij}$ is below a given threshold varies with both parameters.
+  % \begin{figure}[h!]
+  %   \caption{The number of samples required to achieve a given level of confidence that an interaction probability $\lambda_{ij}$ is below a given threshold varies with both parameters.
 With a low threshold, our confidence that $\lambda_{ij}$ is below the threshold increases rapidly with repeated observation of co-occurrence without interaction.
@@
 \textbf{B)} In the galler-parasitoid network component, the 95\% credible interval for $\lambda_{ij}$ was substantially broader and many observed co-occurrences ($\approx$ 15-35) are required to be 95\% confident that $\lambda_{ij}$ is below thresholds of 0.1 or 0.05.}
-    \label{Salix_cdfs}
-    \begin{center}
-    \includegraphics[width=.5\textwidth]{figures/Salix_Galler_samples_and_cdfs_Zillis.eps}
-    \end{center}
+  %   \label{Salix_cdfs}
+  %   \begin{center}
+  %   \includegraphics[width=.5\textwidth]{figures/Salix_Galler_samples_and_cdfs_Zillis.eps}
+  %   \end{center}
 
-    \end{figure}
+  %   \end{figure}
 
   \begin{figure}[h!]
-    \caption{Here we show the mean connectance, links per resource (\emph{Salix} in the \emph{Salix}-galler networks and gallers in the galler-natural enemy networks), links per consumer, and nestedness (NODF) for networks assembled using posterior distributions based on a single sub-network in the~\citet{Kopelke2017} dataset (Zillis).
+    \caption{Here we show the mean connectance, links per galler, nestedness (NODF), and links per natural enemy for networks assembled using posterior distributions based on a single sub-network in the~\citet{Kopelke2017} dataset (Zillis).
 We created 100 ``posterior-sampling" networks and then, for each of these, created 100 ``detection-filter" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network.
@@
     \begin{center}
-    \includegraphics[width=.7\textwidth]{figures/Salix_Galler_posterior_properties_Zillis.eps}
+    \includegraphics[width=.8\textwidth]{figures/GP_posterior_properties_Zillis.eps}
     \end{center}

### 2018-06-05 manuscript/supplemental.tex
less than 200 words too many now

@@
 
-\section*{Appendix S1: Calculating posterior distributions and confidence intervals}
+% Definite first
+\section*{Appendix S1: Calculating uninformative and informative priors}
 
-  The following simple functions are implemented in the R language. They are 
-  also provided as R code in a separate file.
-  Priordata is the list of interaction frequencies from the prior 
-  data, $n$ is the number of sites with observed co-occurrence of 
-  species $i$ and $j$, and $k$ is the number of sites with an 
-  observed interaction $ij$. When calculating the prior 
-  distribution, both $n$ and $k$ are 0. In the main text we assume 100\%
-  confidence in observed interactions and therefore consider only 
-  cases where $k$=0. Only $n$ varies between species pairs.
+    \subsection*{Uninformative prior}
 
-  To calculate the parameters $\alpha$ and $\beta$ of a prior or 
-  posterior distribution:
+        In the absence of any external information, an uninformative prior is the most conservative hypothesis for the distribution of $\lambda$.
+The beta distribution is in this case a uniform distribution, specified with hyper parameters $\alpha=1$ and $\beta=1$.
+
+    \subsection*{Distribution of connectance}
+
+        The ecological network literature boasts a collection of networks for which connectance has been calculated and for which we can thus define the connectance distribution.
+Connectance is measured as $C = L/S^2$, where $L$ is the number of interactions and $S$ is the number of species.
+It measures the filling of an interaction matrix and thereby expresses the average probability that any two species interact with each other.
+If we know only the mean $\overline{C}$ and the variance $\sigma_C^2$ of the distribution of $C$, then the beta parameters could be computed as follows using the method of moments:
+
+        \begin{equation}
+        \alpha = \overline{C}(\frac{\overline{C}(1-\overline{C})}{\sigma_C^2}-1) ,
+        \end{equation}
+
+        \begin{equation}
+        \beta = (1-\overline{C})(\frac{\overline{C}(1-\overline{C})}{\sigma_C^2}-1) .
+        \end{equation}
+
+    \subsection*{Degree distribution or interaction probabilities}
+
+        The degree of a node in a network is defined as its number of connections to other nodes.
+The degree distribution of a network is then the probability distribution of these degrees over the whole network and the normalised degree (i.e., degree divided by the number of potential interaction partners) could therefore be interpreted as an interaction probability.
+It is consequently possible to use the degree distribution to inform the prior distribution.
+The degree distribution could come from several networks, from a similar network (e.g.
+a known network at slightly different location) or from the network of interest if interaction probabilities for some species are already documented.
+The latter approach allows researchers to apply information from known, abundant species to the rarest species for which interactions are less frequently documented.
+That is, we can use detection probabilities for interactions between abundant species to set bounds on detection probabilities for interactions involving rare species.
+
+        If our focal network describes a system similar to that in a known network, we can use the distribution of interaction probabilities in that network to inform our prior.
+The probability of any interaction $L_{ij}$ depends on the degrees of species $i$ and $j$.
+Using normalised degrees $\Delta_i$ and $\Delta_j$, we can obtain the probability of interaction $L_{ij}$=$\Delta_i\times\Delta_j$.
+Similar to the procedure for degree distribution, the distribution of these interaction probabilities can be used to establish a prior distribution before any data from the focal network are collected.
+For distributions of either degrees or interaction probabilities, the procedure for the estimation of the hyper parameters follows the same approach as described above for connectance except that each measurement is at the individual interaction level instead of the network level.
+
+    \subsection*{Trait-matching function}
+
+        As a fourth and final approach, it may be possible to obtain the prior distribution of $\lambda$ using the outcome of a trait-matching model, provided such a model has been parameterised using external data and relevant traits are available.
+In such a case, the prior distribution would follow the function $P(\lambda|\mathbf{T})=f(\mathbf{T})$ based on a set of traits for both species $\mathbf{T}$.
+There are several techniques available to perform this inference of interaction probability, some of which are Bayesian, and we refer interested readers to~\citet{Bartomeus2016} and~\citet{Weinstein2017} for recent reviews about this topic.
+Note that in this case the prior might not be beta-distributed and numerical methods might be required to compute the posterior distribution.
+
+        Trait-matching functions reduce uncertainty around the feasibility of interactions.
+Interactions between species with extremely mis-matched traits are very unlikely, and we can therefore be more confident that an unobserved interaction does not occur.
+This approach could be extended to models including environmental or phenological constraints, allowing researchers to reduce process uncertainty as well.
+Such models are, however, likely to be large and therefore may pose a risk of over-fitting.
+
+    \subsection*{A quantitative example}
+
+      The Bayesian framework can be illustrated with a simple quantitative example.
+Suppose we have $n = 10$ observations of co-occurrence between species $i$ and species $j$ in a given time interval and area, and $k = 3$ observations of interactions.
+The maximum likelihood estimate of the interaction probability is simply $\lambda_{MLE} = 3/10 = 0.3$.
+
+      Now consider we know that species $i$ is known to interact with 10 species (other than species $j$), which have the following degrees:
 
         \vspace{12pt}
-  \begin{em}
-  \noindent \hspace{2pt}calculate\_parameters\textless-function(priordata,n,k)\{\\
-  \vspace{4pt}
-    \# Calculate prior parameters\\
-    start=list(shape1=1,shape2=1)\\
-    pars=fitdistr(x=priordata,`beta',start=start,lower=c(0,0))\$estimate\\
-    alpha=pars[[1]]\\
-    beta=pars[[2]]\\
-  \vspace{4pt}
-    \# Update the parameters with data. If n=0 and k=0, no change.\\
-    alpha\_prime=alpha+k\\
-    beta\_prime=beta+n-k\\
-    pars2=c(alpha\_prime,beta\_prime)\\
-    return(pars2) \}
-  \end{em}
+        \noindent\emph{
+          degree=c(14, 4, 2, 3, 17, 6, 2, 15, 1, 1)
+            }.
           \vspace{12pt}
 
-    All of the following functions use the parameters returned by 
-    ``calculate\_parameters". To calculate the maximum likelihood estimates of 
-    the mean and variance of the probability of interaction $\lambda_{ij}$:
+        If the network has 20 species total, this gives the normalised degrees:
 
         \vspace{12pt}
-    \begin{em}
-    \noindent \hspace{2pt}calculate\_distribution\textless-function(pars)\{\\
-     \vspace{4pt}
-     \# alpha and beta may be from a prior or posterior distribution\\
-      alpha=pars[[1]]\\
-      beta=pars[[2]]\\
-      \vspace{4pt}
-      \# Calculate the MLE of the mean\\
-      mu\_numerator=alpha\\
-      mu\_denominator=alpha+beta\\
-      mu=mu\_numerator/mu\_denominator\\
-      \vspace{4pt}
-      \# Calculate the MLE of the variance\\
-      sig\_numerator=alpha\*beta\\
-      den1=alpha+beta\\
-      den2=den1$**$2\\
-      sig\_denominator=den1$*$den2\\
-      sigma2=sig\_numerator/sig\_denominator\\
-      return(c(mu,sigma2))\}
-    \end{em}
+        \noindent\emph{
+          norm\_degree=c(0.65, 0.20, 0.10, 0.15, 0.85, 0.30, 0.10, 0.75, 0.05, 0.05)}.
           \vspace{12pt}
+
+        Species $i$ has a normalised degree of 0.55 (it interacts with species $j$ and 10 other species).
+We can combine the normalised degree of $i$ with the normalised degrees of its interaction partners to obtain the following set of interaction probabilities for species $i$ and each of its interaction partners:
+
+        \vspace{12pt}
+        \noindent\emph{
+           int\_probs = c(0.358, 0.110, 0.055, 0.082, 0.468, 0.165, 0.055, 0.412, 0.028, 0.028) }.
+          \vspace{12pt}
+
+        The mean of these interaction probabilities is 0.176, approximately two-thirds the $\lambda_{MLE}$ obtained from the observed data.
+We can use the distribution of these interaction probabilities as our prior distribution and estimate the uncertainty surrounding our $\lambda_{MLE}$.
+With some simple R code (function ``calculate\_parameters", \emph{Appendix S3}), we obtain prior parameters $\alpha$=0.998 and $\beta$=4.63.
+Using these priors in equations~\ref{mean} and~\ref{variance} above (or in the R function ``calculate\_distribution" in \emph{Appendix S3}), we find a prior $\bar\lambda$=0.177 and var($\lambda$)=0.026.
+Adding the observed data ($n=10$, $k=3$) and using the same code, we obtain posterior parameters $\alpha'$=4.00 and $\beta'$=11.6 and a posterior $\bar\lambda$=0.256 and var($\lambda$)=0.012.
+Comparing the posterior distribution to the prior, we see that the posterior is closer to the observed data and that the additional data about interactions between species $i$ and $j$ has reduced the variance.
+We may also wish to calculate a credible interval (analogous to the frequentist confidence interval).
+This is also quite straightforward in R (see function ``credible\_interval" in \emph{Appendix S3}).
+In this case, a 95\% credible interval for $\bar\lambda$ is (0.080, 0.491).
+
+        Now, consider the case where the two species have never been observed interacting across $n$ trials, i-e.
+$k=0$.
+The question is then ``what is the probability that these two species do not interact''?
+Since it is not possible to prove that the two species could never interact (strictly speaking, in a Bayesian approach $\lambda=0$ is impossible), we must fix a threshold below which we consider that there is no interaction ($\lambda \sim 0$).
+We call this threshold probability $\lambda*$.
+We then use the cumulative distribution function to estimate $P(\lambda<\lambda*|L=0,n)$ for different $n$.
+The function ``samples\_for\_threshold" in \emph{Appendix S3} calculates distribution function for $\lambda*$ with an increasing number of trials.
+This yields a surprising result: it requires \textgreater24 observations of no interactions to be 95\% sure that the interaction probability is smaller than $\lambda*$=0.1 (recall Fig.~\ref{upper_limits}, Box 2).
+Note the special case where there is no observation of the two species co-occurring, $n = 0$.
+In this situation, the posterior distribution converges to the prior distribution since the data include no information on the probability with which species might interact should they co-occur.
 
@@
 
-  To calculate a credible interval based on the prior or posterior distribution, for given lower and upper bounds:
-
-  \vspace{12pt}
-  \begin{em}
-  \noindent \hspace{2pt}credible\_interval\textless-function(pars,p\_lower,p\_upper)\{\\
-    \vspace{4pt}
-    alpha=pars[[1]]\\
-    beta=pars[[2]]\\
-    lowCI=qbeta(p=p\_lower,shape1=alpha,shape2=beta)\\
-    highCI=qbeta(p=p\_upper,shape1=alpha,shape2=beta)\\
-    return(c(lowCI,highCI))\}
-  \end{em}
-  \vspace{12pt}
-
-  To calculate the number of samples required to reach a given level of confidence that the probability of interaction between two species ($\lambda_{ij}$) that have not been observed co-occurring is below a threshold value:
-
-  \vspace{12pt}
-  \begin{em}
-  \noindent \hspace{2pt}samples\_for\_threshold\textless-function(threshold,confidence,pars)\{\\
-    \vspace{4pt}
-    alpha=pars[[1]]\\
-    beta=pars[[2]]\\
-    n=seq(0,100,1)\\
-    k=0\\ 
-    cdf=pbeta(threshold,shape1=alpha,shape2=beta+n)\\
-    samples=length(which(cdf\textless confidence))\\
-    return(samples) \}
-  \end{em}
-
-\clearpage
-
+% Definite second
 \section*{Appendix S2: Details of \emph{Salix} data collection}
@@
       the Arctic. Including repeated visits to a number of sites, the data set 
-      contains 641 site-visits. The meta-network consists of 1,173 different interactions 
+      contains 641 site-visits. Here we take the more conservative approach and pool visits to the same site for a sample size of 374 sub-networks.
+
+      The meta-network consists of 1,173 different interactions 
       between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 parasitoid 
@@
 
-\section*{Appendix S3: Obtaining prior interaction probabilities}
+% Definite third
+\section*{Appendix S3: Results for \emph{Salix}-galler component}
 
-    \subsection*{Degree distributions and interaction probabilities}
+    \subsection*{Computing the prior and posterior distributions}
 
-      Obtaining degree distributions from the binary interaction 
-      network is straightforward. To do this, we simply divide the 
-      total number of observed interaction partners for each 
-      species (row or column sums) with the number of potential 
-      interaction partners (number of column or rows). Degree 
-      distributions calculated, we can then calculate the 
-      probability of each interaction as the product of the 
-      normalised degrees of the two species. For example, the 
-      probability of an interaction between two species with 
-      normalised degrees of 0.5 (each interacts with half of the 
-      available partners) is 0.25. R code used to do this follows:
+      As with the galler-natural enemy component, we estimated frequencies of \emph{Salix}-galler interactions based on the normalised degree of each species (\emph{Appendix S5}).
+We obtained prior parameters of $\alpha$=8.72, $\beta$=305 for the \emph{Salix}-galler component.
+These prior parameters were then used to estimate the posterior distribution.
 
-      \vspace{12pt}
-      \begin{em}
-      \noindent \hspace{2pt}\# Now get the degree distributions from the web\\
-      \noindent \hspace{2pt}deg\_dist\_Salix=rowSums(prior\_web)/ncol(prior\_web)\\
-      \vspace{4pt}
-      \noindent \hspace{2pt}\# Remove one genotype that never interacted\\
-      \noindent \hspace{2pt}deg\_dist\_Salix\textless-deg\_dist\_Salix[which(rowSums(prior\_web)\textgreater0)]\\
-      \noindent \hspace{2pt}deg\_dist\_galler=colSums(prior\_web)/nrow(prior\_web)\\
-      \vspace{4pt}
-      \noindent \hspace{2pt}\# Interaction probabilities are the product of plant and galler probabilities\\
-      \noindent \hspace{2pt}int\_probs=as.numeric(deg\_dist\_galler\%$*$\%t(deg\_dist\_Salix))\\
-      \vspace{4pt}
-      \noindent \hspace{2pt}\# And for the galler-parasitoid web:\\
-      \noindent \hspace{2pt}deg\_dist\_parasitoid=rowSums(prior\_web\_para\_only)/ncol(prior\_web\_para\_only)\\
-      \noindent \hspace{2pt}deg\_dist\_parasitised=colSums(prior\_web\_para\_only)/nrow(prior\_web\_para\_only)\\
-      \noindent \hspace{2pt}gp\_int\_probs=as.numeric(deg\_dist\_parasitised\%$*$\%t(deg\_dist\_parasitoid))\\
-      \end{em}
+      For species where $n=0$ (3,986/4,992 \emph{Salix}-galler pairs in our dataset), estimates for the mean and variance of $\lambda_{ij}$ can be calculated directly from the prior distribution (\emph{Appendix S6}).
+For the \emph{Salix}-galler network, these parameters were: $\bar\lambda$=0.028, var($\lambda$)=8.60$\times$10$^{-5}$; note that this mean is much lower than that obtained using a prior based on~\citet[Data available from the Dryad Digital Repository: https://doi.org/10.5061/dryad.g7805]{Barbour2016}.
+Note that, despite the intensive sampling in the~\ref{Kopelke2017} dataset, most \emph{Salix}-galler pairs were never observed co-occurring (3,986/4,992; Fig.~\ref{histograms}).
 
-      % SG_web=read.csv('binary_prior_web_SG.csv',row.names=1)
-      % GP_web=read.csv('binary_prior_web_para_only.csv',row.names=1)
+      \begin{figure}[h!]
+          \caption{\textbf{A)} Most pairs of \emph{Salix} and gallers were never observed co-occurring despite the high levels of replication in our example dataset.
+For those pairs that were observed together at least once ($n_{ij}>0$), the number of observed co-occurrences was generally small (\textless10).
+Here we show a histogram of the number of pairs of species observed co-occurring at least once.
+The 3986 \emph{Salix}-galler pairs never observed co-occurring are omitted from the histogram.
+\textbf{B)} Most pairs of species that were observed at the same site were never observed interacting.
+Here we show a histogram of the number of observed interactions within pairs of co-occurring species.
+Species which co-occurred but never interacted are included.
+\textbf{C)} Here we show, for each species pair, the number of observed interactions plotted against the number of observed co-occurrences.
+\emph{Salix}-galler pairs either are never observed interacting or interact almost every time they co-occur.
+IThe red, dashed line indicates a 1:1 relationship between interactions and co-occurrences.}
+          \label{histograms}
+          \begin{center}
+          \includegraphics*[width=.8\textwidth]{figures/SG_histogram.eps}
+          \end{center}
+          \end{figure}
 
-      %       # Now get the degree distributions from the web
-      % deg_dist_Salix=rowSums(SG_web)/ncol(SG_web)
-      % deg_dist_galler=colSums(SG_web)/nrow(SG_web)
-      % # Interaction probabilities are the product of plant and galler probabilities
-      % sg_int_probs=as.numeric(deg_dist_galler%*%t(deg_dist_Salix))
+      For species with $n>0$, the posterior distribution will depend on the values of $n$ and $k$.
+Here we are interested only in cases where $k = 0$.
+This gives $\alpha'$=$\alpha$ and $\beta'$=$\beta + n_{ij}$.
+For a pair of species which co-occurred at all 374 sites and was never observed to interact, the distribution for the \emph{Salix}-galler network would become $\bar\lambda_{ij}$=1.27 $\times$ 10$^{-2}$, var($\lambda_{ij}$)=1.82 $\times$ 10$^{-5}$.
+As $n$ decreases, the distribution widens and moves away from the origin (Fig.~\ref{Salix_pdfs}).
+The 95\% credible interval for hypothetical \emph{Salix}-galler pairs widened from (0.006, 0.022) if the pair co-occurred at all sites to (0.013, 0.049) if they co-occurred at none (Table~\ref{credints}).
 
-      % deg_dist_parasitoid=rowSums(GP_web)/ncol(GP_web)
-      % deg_dist_parasitised=colSums(GP_web)/nrow(GP_web)
-      % gp_int_probs=as.numeric(deg_dist_parasitised%*%t(deg_dist_parasitoid))
+      \begin{figure}[h!]
+        \caption{Using prior distributions based on the \emph{Salix}-galler network sampled at a single site in~\citet{Kopelke2017}, we can calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting.
+Here we show posterior distributions for $\lambda$ ranging from the prior distribution ($n=0$ observed co-occurrence) to the distribution obtained when the pair of species has been observed co-occurring 100 times.
+The distribution narrows and approaches zero as the sample size increases.
+Likewise, the maximum likelihood estimator for the mean probability of interaction (diamonds at top of each panel) approaches zero and the 95\% credible interval (lines at top of each panel) narrows as sample size increases.
+Dashed lines indicate threshold probabilities of 0.1, 0.05, and 0.01.}
+        \label{Salix_pdfs}
+        \begin{center}
+        \includegraphics*[width=.7\textwidth]{figures/SG_pdfs_increasing_N_Zillis.eps}
+        \end{center}
+        \end{figure}
+
+    \subsection*{How many samples are required to reach a minimal precision}
+
+        In our dataset, the entire 95\% credible interval for the probability of an interaction between a \emph{Salix}-galler pair was (0.013, 0.049).
+We may therefore be 95\% confident that the interaction probability for \emph{Salix} and galler species that have not been observed co-occurring is below 0.05.
+As the peak of the prior distribution for the probability of interaction between \emph{Salix} and galler probabilities is around 0.02 (Fig.~\ref{Salix_pdfs}), to be 95\% confident that the interaction probability for these species is below 0.01 would require 1029 observed co-occurrences with no interaction - far more than the number of sites in the~\citep{Kopelke2017} dataset.
+
+    \subsection*{Scaling up to network metrics}
+
+      As with the galler-natural enemy component, we calculated posterior probability distributions for \emph{Salix}-galler pairs that were not observed interacting.
+For each posterior web, we calculated the connectance of each web, as well the mean links per \emph{Salix}, mean links per galler, and nestedness (NODF).
+Likewise, we created a suite of detection-filtered networks by randomly sampling 99\%, 95\%, 90\%, 80\%, 70\%, 60\%, and 50\% of the interactions included in each posterior network.
+We then calculated the same network properties as described above.
+
+      We find, perhaps not surprisingly, that the posterior webs for the Salix-galler network  had higher connectances than the original, observed web (C=0.028 for the observed web and 0.082 $\leq$ C $\leq$ 0.096 for the posterior webs; Fig.~\ref{posterior_webs}A).
+The number of links per \emph{Salix} species in the observed web ($L_{\emph{Salix}}$=2.71) was similar to those in the posterior webs (2.53 $\leq L_{\emph{Salix}} \leq$ 3.19; Fig~\ref{posterior_webs}B).
+The number of links per galler, however, was lower in the observed web ($L_{galler}$=1.47) than in the posterior webs, accounting for the increased connectance (4.67 $\leq L_{galler} \leq$ 5.88; Fig.~\ref{posterior_webs}D).
+There was a more substantial difference in the nestedness of the observed and posterior webs: the observed network had NODF=0.560 while the posterior networks were more nested (1.39 $\leq NODF \leq$ 1.94).
+Even the networks sampled with a detection filter of 50\% had non-zero nestedness (Fig.~\ref{posterior_webs}C).
+This last result highlights the potential for the possibility for network structure to vary when considering the possibility that unobserved species pairs may interact.
+
+  \begin{figure}[h!]
+    \caption{Here we show the mean connectance, links per resource (\emph{Salix} in the \emph{Salix}-galler networks and gallers in the galler-natural enemy networks), links per consumer, and nestedness (NODF) for networks assembled using posterior distributions based on a single sub-network in the~\citet{Kopelke2017} dataset (Zillis).
+We created 100 ``posterior-sampling" networks and then, for each of these, created 100 ``detection-filter" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network.
+This simulates imperfect detection of interactions in the field.
+Each point represents the mean network property (e.g., connectance) obtained from a set of 100 detection-filter networks, plotted against the value of the network property in the posterior-sampling network used to create the detection-filter networks.
+For each property and both network types, the posterior-sampling networks cover a relatively small range of network properties than the range covered by networks with varying detection probabilities.
+The value of each property decreases with the proportion of links included in the detection-filter networks.}
+    \label{posterior_webs}    
+    \begin{center}
+    \includegraphics[width=.7\textwidth]{figures/SG_posterior_properties_Zillis.eps}
+    \end{center}
+    \end{figure}
 
@@
 
+% Definite fourth
 \section*{Appendix S4: Analyses using alternative prior}
@@
 
+\section*{Appendix S5: Calculating the credible interval around a probability estimate}
+
+  Here we describe the derivation of the Clopper-Pearson credible interval for the estimated probability of interaction $\lambda$ of a pair of species observed co-occurring $n$ times and interacting $k$ times.
+As we are most interested in the probability of interaction between species pairs that have never been observed co-occurring, we consider only the case where $k=0$ over a variety of $n$.
+This is straightforward to do in R (see the function ``credible\_interval" in \emph{Appendix S2}).
+
+  First, we must obtain the $\alpha$ and $\beta$ parameters for the prior distribution.
+In this study we obtained these parameters using the R~\citep{R} function fitdist from the package fitdistrplus~\citep{fitdistrplus}.
+Once $\alpha$ and $\beta$ are known, we can update them using our observed data.
+Specifically, we are interested in $\alpha'=\alpha+k$ and $\beta'=\beta+n-k$.
+These parameters can then be used to calculate a credible interval using the R~\citep{R} function qbeta.
+In the table below, we present the 95\% credible intervals for \emph{Salix}-galler and galler-natural enemy pairs with different numbers of observed co-occurrences ($n$) and no observed interactions ($k=0$), calculated using prior information derived from the Zillis sub-network~\citep{Kopelke2017}.
+
+      % % # R code to make the table:
+      % ns=c(0,1,2,5,10,15,20,25,50,100,150,200,374)
+      % output=matrix(nrow=length(ns),ncol=5)
+      % output[,1]=ns
+      % for(r in 1:nrow(output)){
+      %   interval1=credible_interval(calculate_parameters(sg_int_probs,ns[r],0),0.025,0.975)    
+      %   interval2=credible_interval(calculate_parameters(gp_int_probs,ns[r],0),0.025,0.975)    
+      %   output[r,2:3]=interval1
+      %   output[r,4:5]=interval2
+      % }
+      \medskip
+      \begin{table}
+        \label{credints}
+        \caption{Here we give the lower and upper bounds of 95\% credible intervals for the probability of interaction $\lambda$ between \emph{Salix}-galler or galler-natural enemy pairs that have been observed co-occurring $n$ times but have never been observed interacting.}
+        \begin{tabular}{l  c c  c c }
+        \multirow{2}{*}{$n$} & \multicolumn{2}{c}{\emph{Salix}-galler} & \multicolumn{2}{c}{galler-natural enemy}\\
+         & Lower bound & Upper bound & Lower bound & Upper bound \\
+        \hline
+        0   & 0.013 & 0.049 & 5.39 $\times10^{-4}$ & 0.304 \\
+        1   & 0.013 & 0.048 & 4.82 $\times10^{-4}$ & 0.276 \\
+        2   & 0.013 & 0.048 & 4.35 $\times10^{-4}$ & 0.253 \\
+        5   & 0.012 & 0.048 & 3.37 $\times10^{-4}$ & 0.203 \\
+        10  & 0.012 & 0.047 & 2.45 $\times10^{-4}$ & 0.152 \\
+        15  & 0.012 & 0.046 & 1.93 $\times10^{-4}$ & 0.121 \\
+        20  & 0.012 & 0.046 & 1.59 $\times10^{-4}$ & 0.101 \\
+        25  & 0.012 & 0.045 & 1.35 $\times10^{-4}$ & 0.087 \\
+        50  & 0.011 & 0.042 & 7.72 $\times10^{-5}$ & 0.050 \\
+        100 & 0.010 & 0.037 & 4.16 $\times10^{-5}$ & 0.027 \\
+        150 & 0.009 & 0.033 & 2.84 $\times10^{-5}$ & 0.019 \\
+        200 & 0.008 & 0.030 & 2.16 $\times10^{-5}$ & 0.014 \\
+        \hline
+        374 & 0.006 & 0.022 & 1.18 $\times10^{-5}$ & 0.008 \\
+        \hline
+        \end{tabular}
+      \end{table}
+
+\clearpage
+
+\section*{Appendix S6: Obtaining prior interaction probabilities}
+
+    \subsection*{Degree distributions and interaction probabilities}
+
+      Obtaining degree distributions from the binary interaction 
+      network is straightforward. To do this, we simply divide the 
+      total number of observed interaction partners for each 
+      species (row or column sums) with the number of potential 
+      interaction partners (number of column or rows). Degree 
+      distributions calculated, we can then calculate the 
+      probability of each interaction as the product of the 
+      normalised degrees of the two species. For example, the 
+      probability of an interaction between two species with 
+      normalised degrees of 0.5 (each interacts with half of the 
+      available partners) is 0.25. R code used to do this follows:
+
+      \vspace{12pt}
+      \begin{em}
+      \noindent \hspace{2pt}\# Now get the degree distributions from the web\\
+      \noindent \hspace{2pt}deg\_dist\_Salix=rowSums(prior\_web)/ncol(prior\_web)\\
+      \vspace{4pt}
+      \noindent \hspace{2pt}\# Remove one genotype that never interacted\\
+      \noindent \hspace{2pt}deg\_dist\_Salix\textless-deg\_dist\_Salix[which(rowSums(prior\_web)\textgreater0)]\\
+      \noindent \hspace{2pt}deg\_dist\_galler=colSums(prior\_web)/nrow(prior\_web)\\
+      \vspace{4pt}
+      \noindent \hspace{2pt}\# Interaction probabilities are the product of plant and galler probabilities\\
+      \noindent \hspace{2pt}int\_probs=as.numeric(deg\_dist\_galler\%$*$\%t(deg\_dist\_Salix))\\
+      \vspace{4pt}
+      \noindent \hspace{2pt}\# And for the galler-parasitoid web:\\
+      \noindent \hspace{2pt}deg\_dist\_parasitoid=rowSums(prior\_web\_para\_only)/ncol(prior\_web\_para\_only)\\
+      \noindent \hspace{2pt}deg\_dist\_parasitised=colSums(prior\_web\_para\_only)/nrow(prior\_web\_para\_only)\\
+      \noindent \hspace{2pt}gp\_int\_probs=as.numeric(deg\_dist\_parasitised\%$*$\%t(deg\_dist\_parasitoid))\\
+      \end{em}
+
+      % SG_web=read.csv('binary_prior_web_SG.csv',row.names=1)
+      % GP_web=read.csv('binary_prior_web_para_only.csv',row.names=1)
+
+      %       # Now get the degree distributions from the web
+      % deg_dist_Salix=rowSums(SG_web)/ncol(SG_web)
+      % deg_dist_galler=colSums(SG_web)/nrow(SG_web)
+      % # Interaction probabilities are the product of plant and galler probabilities
+      % sg_int_probs=as.numeric(deg_dist_galler%*%t(deg_dist_Salix))
+
+      % deg_dist_parasitoid=rowSums(GP_web)/ncol(GP_web)
+      % deg_dist_parasitised=colSums(GP_web)/nrow(GP_web)
+      % gp_int_probs=as.numeric(deg_dist_parasitised%*%t(deg_dist_parasitoid))
+
+\clearpage
+
+\section*{Appendix S7: Calculating posterior distributions and confidence intervals}
+
+  The following simple functions are implemented in the R language. They are 
+  also provided as R code in a separate file.
+  Priordata is the list of interaction frequencies from the prior 
+  data, $n$ is the number of sites with observed co-occurrence of 
+  species $i$ and $j$, and $k$ is the number of sites with an 
+  observed interaction $ij$. When calculating the prior 
+  distribution, both $n$ and $k$ are 0. In the main text we assume 100\%
+  confidence in observed interactions and therefore consider only 
+  cases where $k$=0. Only $n$ varies between species pairs.
+
+  To calculate the parameters $\alpha$ and $\beta$ of a prior or 
+  posterior distribution:
+
+  \vspace{12pt}
+  \begin{em}
+  \noindent \hspace{2pt}calculate\_parameters\textless-function(priordata,n,k)\{\\
+  \vspace{4pt}
+    \# Calculate prior parameters\\
+    start=list(shape1=1,shape2=1)\\
+    pars=fitdistr(x=priordata,`beta',start=start,lower=c(0,0))\$estimate\\
+    alpha=pars[[1]]\\
+    beta=pars[[2]]\\
+  \vspace{4pt}
+    \# Update the parameters with data. If n=0 and k=0, no change.\\
+    alpha\_prime=alpha+k\\
+    beta\_prime=beta+n-k\\
+    pars2=c(alpha\_prime,beta\_prime)\\
+    return(pars2) \}
+  \end{em}
+  \vspace{12pt}
+
+    All of the following functions use the parameters returned by 
+    ``calculate\_parameters". To calculate the maximum likelihood estimates of 
+    the mean and variance of the probability of interaction $\lambda_{ij}$:
+
+    \vspace{12pt}
+    \begin{em}
+    \noindent \hspace{2pt}calculate\_distribution\textless-function(pars)\{\\
+     \vspace{4pt}
+     \# alpha and beta may be from a prior or posterior distribution\\
+      alpha=pars[[1]]\\
+      beta=pars[[2]]\\
+      \vspace{4pt}
+      \# Calculate the MLE of the mean\\
+      mu\_numerator=alpha\\
+      mu\_denominator=alpha+beta\\
+      mu=mu\_numerator/mu\_denominator\\
+      \vspace{4pt}
+      \# Calculate the MLE of the variance\\
+      sig\_numerator=alpha\*beta\\
+      den1=alpha+beta\\
+      den2=den1$**$2\\
+      sig\_denominator=den1$*$den2\\
+      sigma2=sig\_numerator/sig\_denominator\\
+      return(c(mu,sigma2))\}
+    \end{em}
+  \vspace{12pt}
+
+  \clearpage
+
+  To calculate a credible interval based on the prior or posterior distribution, for given lower and upper bounds:
+
+  \vspace{12pt}
+  \begin{em}
+  \noindent \hspace{2pt}credible\_interval\textless-function(pars,p\_lower,p\_upper)\{\\
+    \vspace{4pt}
+    alpha=pars[[1]]\\
+    beta=pars[[2]]\\
+    lowCI=qbeta(p=p\_lower,shape1=alpha,shape2=beta)\\
+    highCI=qbeta(p=p\_upper,shape1=alpha,shape2=beta)\\
+    return(c(lowCI,highCI))\}
+  \end{em}
+  \vspace{12pt}
+
+  To calculate the number of samples required to reach a given level of confidence that the probability of interaction between two species ($\lambda_{ij}$) that have not been observed co-occurring is below a threshold value:
+
+  \vspace{12pt}
+  \begin{em}
+  \noindent \hspace{2pt}samples\_for\_threshold\textless-function(threshold,confidence,pars)\{\\
+    \vspace{4pt}
+    alpha=pars[[1]]\\
+    beta=pars[[2]]\\
+    n=seq(0,100,1)\\
+    k=0\\ 
+    cdf=pbeta(threshold,shape1=alpha,shape2=beta+n)\\
+    samples=length(which(cdf\textless confidence))\\
+    return(samples) \}
+  \end{em}
+
+\clearpage
+
   \bibliographystyle{ecol_let} 

### 2018-06-05 code/figure_generation/Zillis_posterior_plots.py
updated figures to split SG and GP components

@@ -101,11 +101,11 @@ def Zillis_yaxes(prop,graph):
   elif prop=='LS':
     graph.world.ymax=4
     graph.yaxis.tick.configure(major=1,onoff='on',minor_ticks=1,major_size=.5,place='normal',minor_size=.3,major_linewidth=1,minor_linewidth=1)
-    ytext="Links/resource"
+    ytext="Links per Salix"
   elif prop=='LG':
     graph.world.ymax=7
     graph.yaxis.tick.configure(major=2,onoff='on',minor_ticks=1,major_size=.5,place='normal',minor_size=.3,major_linewidth=1,minor_linewidth=1)
-    ytext="Links/consumer"
+    ytext="Links per galler"
   else:
     graph.world.ymax=2.25
     graph.yaxis.tick.configure(major=.5,onoff='on',minor_ticks=1,major_size=.5,place='normal',minor_size=.3,major_linewidth=1,minor_linewidth=1)
@@ -126,12 +126,12 @@ def Zillertal_yaxes(prop,graph):
     graph.world.ymin=0
     graph.world.ymax=6
     graph.yaxis.tick.configure(major=2,onoff='on',minor_ticks=1,major_size=.5,place='normal',minor_size=.3,major_linewidth=1,minor_linewidth=1)
-    ytext="Links/resource"
+    ytext="Links per Salix"
   elif prop=='LG':
     graph.world.ymin=0
     graph.world.ymax=11
     graph.yaxis.tick.configure(major=2,onoff='on',minor_ticks=1,major_size=.5,place='normal',minor_size=.3,major_linewidth=1,minor_linewidth=1)
-    ytext="Links/consumer"
+    ytext="Links per galler"
   else:
     graph.world.ymin=0
     graph.world.ymax=4
@@ -165,11 +165,11 @@ def format_graph(graph,prop,nettype,site):
     elif prop=='LS':
       graph.world.ymax=18
       graph.yaxis.tick.configure(major=4,onoff='on',minor_ticks=1,major_size=.5,place='normal',minor_size=.3,major_linewidth=1,minor_linewidth=1)
-      ytext="Links/resource"
+      ytext="Links per galler"
     elif prop=='LG':
       graph.world.ymax=23    
       graph.yaxis.tick.configure(major=5,onoff='on',minor_ticks=1,major_size=.5,place='normal',minor_size=.3,major_linewidth=1,minor_linewidth=1)
-      ytext="Links/consumer"
[…]

### 2018-06-05 code/figure_generation/observation_interaction_histogram.py

@@ -119,10 +119,10 @@ def format_graph(graph,graphtype,nettype):
     loc=(100,.75),loctype='world')
   # graph.add_drawing_object(DrawText,text="Threshold",x=150,y=.9,char_size=.75,just=2,loctype='world')
 
-  if graphtype=='occurs' and nettype=='SG':
-    graph.add_drawing_object(DrawText,text="Salix-Galler",x=35,y=2500,char_size=1.25,just=2,loctype='world')
-  elif graphtype=='occurs' and nettype=='GP':
-    graph.add_drawing_object(DrawText,text="Galler-Parasitoid",x=35,y=2500,char_size=1.25,just=2,loctype='world')
+  # if graphtype=='occurs' and nettype=='SG':
+  #   graph.add_drawing_object(DrawText,text="Salix-Galler",x=35,y=2500,char_size=1.25,just=2,loctype='world')
+  # elif graphtype=='occurs' and nettype=='GP':
+  #   graph.add_drawing_object(DrawText,text="Galler-Parasitoid",x=35,y=2500,char_size=1.25,just=2,loctype='world')
 
   graph.panel_label.configure(placement='iul',char_size=.75,dx=.02,dy=.01)
 
@@ -148,10 +148,9 @@ def populate_graph(graph,occurs,graphtype):
 
   return graph
 
-grace=MultiPanelGrace(colors=colors)
-
-for graphtype in ['occurs','interacts','dotplot']:
-  for nettype in ['SG','GP']:
+for nettype in ['SG','GP']:
+  grace=MultiPanelGrace(colors=colors)
+  for graphtype in ['occurs','interacts','dotplot']:
     if nettype=='SG':
       occurs=read_Rfiles('../../data/Salix_example/Salix_Galler/nonzero_cooccurances.tsv')
       interacts=read_Rfiles('../../data/Salix_example/Salix_Galler/observed_interactions.tsv')
@@ -170,21 +169,21 @@ for graphtype in ['occurs','interacts','dotplot']:
     graph=grace.add_graph(Panel)
     graph=format_graph(graph,graphtype,nettype)
     graph=populate_graph(graph,dataset,graphtype)
-# graph.set_view(0.15,0.15,0.95,0.65)
+  # graph.set_view(0.15,0.15,0.95,0.65)
 
-grace.multi(rows=3,cols=2,vgap=.08,hgap=.04)
-# graph.set_view(0.15,0.15,0.95,0.65)
[…]

### 2018-06-05 code/figure_generation/pdf_and_cdf_combined.py

@@ -61,6 +61,7 @@ import math
 import random
 from decimal import *
 import numpy as np
+import samples_for_thresholds as cdf
 
 #Pygrace libraries
 from PyGrace.grace import Grace
@@ -147,22 +148,15 @@ def format_graph(graph,nettype):
     graph.add_drawing_object(DrawText,text="N",x=0.085,y=35.5,char_size=.75,just=2,loctype='world')
   elif nettype=='GP':
     graph.legend.configure(box_linestyle=0,fill=0,fill_pattern=0,char_size=.75,
-      loc=(0.25,35),loctype='world',size=2)
+      loc=(0.22,35),loctype='world',size=2)
     # graph.add_drawing_object(DrawText,text="N",x=0.665,y=35.5,char_size=.75,just=2,loctype='world')
-    graph.add_drawing_object(DrawText,text="N",x=0.265,y=35.5,char_size=.75,just=2,loctype='world')
+    graph.add_drawing_object(DrawText,text="N",x=0.235,y=35.5,char_size=.75,just=2,loctype='world')
   graph.panel_label.configure(placement='iur',char_size=.75,dx=.02,dy=.02)
 
 
   return graph
 
 def populate_graph(graph,pointdict,MLEdict,nettype):
-
-  if nettype=='GP':
-    for x in [0.01,0.05,0.10]:
-      vertline=graph.add_dataset([(x,0),(x,1000)])
-      vertline.symbol.shape=0
-      vertline.line.linestyle=3
-
   # cols=[2,3,5,9,10,11]
   cols=[11,9,7,5,3,2]
   x=0
@@ -176,13 +170,6 @@ def populate_graph(graph,pointdict,MLEdict,nettype):
     # if nettype=='SG': 
     data.legend=str(N)
 
-    y+=2
-    x+=1
-
-
-  x=0
-  y=0
-  for N in [100,50,20,10,5,0]:
     MLE=MLEdict[N][0]
     lower=MLEdict[N][1]
     upper=MLEdict[N][2]
@@ -198,6 +185,7 @@ def populate_graph(graph,pointdict,MLEdict,nettype):
     y+=2
     x+=1
 
+
   return graph
 
 # grace=MultiPanelGrace(colors=colors)
@@ -205,9 +193,10 @@ def populate_graph(graph,pointdict,MLEdict,nettype):
 # grace.set_label_scheme('dummy')
 
 for nettype in ['SG','GP']:
[…]

### 2018-06-05 code/figure_generation/samples_for_thresholds.py

@@ -143,9 +143,13 @@ def format_graph(graph,nettype):
   if nettype=='SG':
     graph.world.xmax=1300
     major=250
+    graph.legend.configure(box_linestyle=0,fill=0,fill_pattern=0,char_size=.75,
+      loc=(750,.65),loctype='world')
   else:
     graph.world.xmax=300
     major=50
+    graph.legend.configure(box_linestyle=0,fill=0,fill_pattern=0,char_size=.75,
+      loc=(155,.65),loctype='world')
   graph.world.ymin=-0
   graph.world.ymax=1
   # graph.world.xmax=750
@@ -159,11 +163,9 @@ def format_graph(graph,nettype):
 
   graph.xaxis.label.configure(text="Number of samples",char_size=1,just=2,place='normal')
   graph.yaxis.label.configure(text="Cumulative density",char_size=1,just=2)
-  graph.legend.configure(box_linestyle=0,fill=0,fill_pattern=0,char_size=.75,
-    loc=(750,.65),loctype='world')
     # loc=(400,.65),loctype='world')
   # graph.add_drawing_object(DrawText,text="Threshold",x=150,y=.9,char_size=.75,just=2,loctype='world')
-  graph.panel_label.configure(placement='iur',char_size=.75,dx=.02,dy=.03)
+  # graph.panel_label.configure(placement='iur',char_size=.75,dx=.02,dy=.03)
 
   return graph
 
@@ -181,18 +183,18 @@ def populate_graph(graph,pointdict,nettype):
     data=graph.add_dataset(pointdict[threshold])
     data.symbol.shape=0
     data.line.configure(linewidth=2,linestyle=x)
-    if nettype=='SG':
-      data.legend="Threshold="+str(threshold)
+    # if nettype=='SG':
+    data.legend="Threshold="+str(threshold)
 
   bar95=graph.add_dataset([(0,0.95),(2000,.95)])
   bar95.symbol.shape=0
   bar95.line.configure(linewidth=1,linestyle=1,color=2)
 
-  if nettype=="SG":
-    graph.add_drawing_object(DrawText,text="Salix-Galler",char_size=1,just=0,x=0,y=1.05,loctype='world')
-  else:
+  # if nettype=="SG":
+    # graph.add_drawing_object(DrawText,text="Salix-Galler",char_size=1,just=0,x=0,y=1.05,loctype='world')
+  # else:
[…]

### 2018-06-06 manuscript/CI_interactions.tex
trimmed figure captions a bit more

@@
 
-  The authors thank Daniel Cartensen for fruitful discussion of the ideas in this manuscript.
-We also thank K\'{e}vin Cazalles for providing feedback on the manuscript.
-The authors also appreciate support from the Swedish Research Council (VR) for grant \#2016-06872 (to TR).
-Additional funding was provided by a Formas grant (\#942-2015-1262) to AE.
+  The authors thank Daniel Cartensen for fruitful discussion of the ideas in this manuscript and K\'{e}vin Cazalles for providing feedback.
+The authors appreciate support from the Swedish Research Council (VR) for grant \#2016-06872 (to TR) from Formas for grant \#942-2015-1262 (to AE).
 
-\section*{Statement of authorship}
+\section*{Authors' contributions}
 
@@
   \begin{figure}[h!]
-    \caption{Imperfect detection of interactions has a strong effect on the number of samples required to be confident that an interaction does not occur.
-Assume that we want to infer the probability of an interaction between two species, $i$ and $j$ and that this interaction is completely impossible (i.e.
+    \caption{Imperfect detection of interactions increases the number of samples required to be confident that an interaction does not occur.
+Assume that we want to infer the probability of an interaction between two species, $i$ and $j$, and that this interaction is completely impossible (i.e.
 the true $\lambda=0$).
@@
 The number of samples required to obtain a 95\% credible interval below each threshold increases rapidly.
-It takes just over 20 observed co-occurrences to be 95\% confident that $\lambda<0.10$, approximately 50 co-occurrences to be 95\% confident that $\lambda<0.05$, and over 100 co-occurrences to be 95\% confident that $\lambda<0.01$.
-Increasing the desired confidence level will also increase the number of samples required.
-    }
+It takes just over 20 observed co-occurrences to be 95\% confident that $\lambda<0.10$, approximately 50 co-occurrences to be 95\% confident that $\lambda<0.05$, and over 100 co-occurrences to be 95\% confident that $\lambda<0.01$.}
     \label{Salix_pdfs_cdfs}
@@
   \begin{figure}[h!]
-    \caption{Here we show the mean connectance, links per galler, nestedness (NODF), and links per natural enemy for networks assembled using posterior distributions based on a single sub-network in the~\citet{Kopelke2017} dataset (Zillis).
+    \caption{Mean connectance, links per galler, nestedness (NODF), and links per natural enemy for networks assembled using posterior distributions based on a single sub-network in the~\citet{Kopelke2017} dataset (Zillis) occupied a narrow range.
 We created 100 ``posterior-sampling" networks and then, for each of these, created 100 ``detection-filter" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network.
 This simulates imperfect detection of interactions in the field.
-Each point represents the mean network property (e.g., connectance) obtained from a set of 100 detection-filter networks, plotted against the value of the network property in the posterior-sampling network used to create the detection-filter networks.
-For each property and both network types, the posterior-sampling networks cover a relatively small range of network properties than the range covered by networks with varying detection probabilities.
-The value of each property decreases with the proportion of links included in the detection-filter networks.}
+Each point represents the mean (+/- SD) network property (e.g., connectance) obtained from a set of 100 detection-filter networks.
+For each property and both network types, the detection-filter networks cover a broader range of network properties than the posterior-sampling networks.
+The value of each property decreases with the proportion of links included in the detection-filter networks; values in the original web are indicated by dashed lines.}
     \label{posterior_webs}    

### 2018-06-07 manuscript/CI_interactions.tex
re-ordering is tough

@@
 To move from these simpler metrics to a network framework, the tabulation of nodes is combined with interactions (links between nodes) so that networks provide additional, higher-order information on community structure.
-Despite this additional information, empirical descriptions of ecological networks are still limited because they are usually considered to be static representations of the communities and interactions they describe.
+Despite this additional information, empirical descriptions of ecological networks are still limited because they are usually considered static representations of the communities they describe.
 That is, whether the network is assembled based on aggregated data, a single intensive ``snapshot" sample, or expert knowledge, interactions are assumed to occur deterministically wherever and whenever the community is observed~\citep{Olesen2011a}.
@@
 
-    Beyond ``true" variation in network structure, several researchers have pointed to the effects of sampling intensity on network structure (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007}).
+    Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity on network structure (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007}).
 An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to document interactions than species~\citep{Poisot2012}.
@@
 
-    Despite these preliminary efforts, to date we lack the quantitative methodology to deal with the uncertainty generated by spatiotemporal variation in ecological interactions and by sampling.
-Even in extremely well-sampled networks, uneven sampling across species (or pairs of species) can lead to the erroneous inference that some species do not interact because they co-occur rarely or have not yet been observed together - even if they do interact when they do co-occur (see Box 1 for an example).
+    Despite these preliminary efforts, we currently lack the quantitative methodology to deal with the uncertainty generated by spatiotemporal variation in ecological interactions and by sampling.
+Even in extremely well-sampled networks, uneven sampling across species (or pairs of species) can lead to the erroneous inference that some species do not interact because they co-occur rarely or have not yet been observed together - even if they do interact when they do co-occur (see Fig.~\ref{histograms} for an example).
 Nearly all network studies will thus neglect some interactions, necessitating an approach that acknowledges this uncertainty.
@@
 We focus on binary interactions as a first step, but the framework could be expanded to deal with interaction frequencies and strength.
-To define the problem, we first identify the different contributions to the uncertainty of an interaction and discuss the implications of each source of uncertainty for the properties of ecological networks.
-Next, we develop an analytical framework to quantify the uncertainty around interactions in an empirical web.
-We illustrate this framework using the most extensively sampled network to date (Box 1).
+To define the problem, we will first identify the different contributions to the uncertainty of an interaction and discuss the implications of each source of uncertainty for the properties of ecological networks.
+    % Next, we develop an analytical framework to quantify the uncertainty around interactions in an empirical web and, finally, illustrate this framework using an extensively sampled empirical network.
+    % We illustrate this framework using the most extensively sampled network to date (Box 1).
 Finally, we offer tangible recommendations for improved descriptors of ecological interactions.
@@
 
-\section*{Why do some interactions \emph{not} occur?}
+    \subsection*{Why do some interactions \emph{not} occur?}
 
@@
 Presences and absences are not, however, equally certain.
-An observed link definitely occurred, but there are multiple reasons why a given link may not be observed whether or not the interaction truly occurred.
+An observed link definitely occurred, but there are multiple reasons why a given link may not be observed \emph{whether or not the interaction truly occurred}.
 The detection of any interaction is a stochastic process.
@@
 
-    \subsection*{Interaction uncertainty}
+        \subsubsection*{Interaction uncertainty}
 
@@
 If two species have incompatible traits, they may not interact even if there are no other constraints (e.g., temporal separation of species, inability to detect cryptic species) preventing the interaction from being observed.
-As a simple example, a prey species may be too large to be consumed by a particular predator.
+As a simple example, a prey species may be too large to be consumed by a predator.
 In such cases, $\lambda$ would take a value of 0 and there would be no uncertainty.
 
-      Based on an observed network, however, it is often unclear whether an unobserved interaction is impossible due to incompatible traits or a rare phenomenon with $\lambda>0$.
+          Based on an observed network, however, it is often unclear whether an unobserved interaction is impossible due to incompatible traits or simply a rare phenomenon with $\lambda>0$.
 This uncertainty is partly addressed by trait-matching models~\citep{Bartomeus2016}.
-Nevertheless, every model is imperfect and lacks information (i.e.
-about traits) that could be used to define constraints on interactions~\citep{Dormann2017}.
+Nevertheless, every model is imperfect and lacks information that could be used to define constraints on interactions~\citep{Dormann2017}.
 Some interaction uncertainty therefore remains in current trait-matching models.
@@
 
-    \subsection*{Process uncertainty}
+        \subsubsection*{Process uncertainty}
 
@@
 $L=1$, it may still not occur at a given location or moment in time because of local constraints such as inclement weather or the lack of suitable habitat.
-We define the local realisation of an interaction with the variable $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L=1)=\chi$.
-This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology about the contingencies of interactions.
+We define the local realisation of an interaction, $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L=1)=\chi$.
+This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology describing the contingencies of interactions.
 Phenological matching~\citep{MillerRushing2010,Gezon2016}, species preferences~\citep{Pires2011,Novak2015,Coux2016}, and fear effects of other species~\citep{Luttbeg2005,Wirsing2008} are just some of the factors contributing to variation in the frequency of interactions between a given pair of species.
@@
 
-    \subsection*{Detection uncertainty}
+        \subsubsection*{Detection uncertainty}
 
@@
 Given that an interaction is feasible and occurs under the local conditions ($L$=1 and $X$=1), we may define the detection of an interaction, $D$, as a stochastic process with the associated probability $P(D|X=1,L=1)=\delta$.
-Detection failure could happen for many reasons (see~\citet{Wirta2014} for examples of some of these difficulties and partial solutions to them).
+Detection failure could happen for many reasons (see~\citet{Wirta2014} for examples of these difficulties and partial solutions to them).
 Some sources of detection error can be minimised with appropriate sampling effort ($\delta$ will converge to one with increasing number of samples), but other sources are often difficult to reduce (e.g.
@@
 
-\section*{Estimating detection and process uncertainty}
+    \subsection*{Estimating detection and process uncertainty}
 
@@
         The considerations above raise major challenges: when faced with empirical data, how may we infer whether unobserved interactions truly do not occur?
-How may we refine our sampling approaches to reduce uncertainties gain insights into the impact of multiple processes on field observations?
+How may we refine our sampling approaches to reduce uncertainties and gain insights into the impact of multiple processes on field observations?
 Importantly, some sources of uncertainty within these three broad groupings can be minimised with appropriate sampling (e.g., sampling in a variety of weather conditions, combining different methods of detection) while other sources are difficult or impossible to reduce since they are generated by the process in which we are interested (e.g., variation in individual preferences or traits).
@@
 
-    The obvious rule of thumb is to ``sample more" (Fig.~\ref{upper_limits}).
-Sampling more will reduce uncertainty about the upper bound of the interaction probability and will also increase the probability of detecting unlikely or cryptic interactions (e.g., interactions where $L$=1 but process or detection uncertainty is high).
+        When attempting to reduce uncertainty, the obvious rule of thumb is to ``sample more" (Fig.~\ref{upper_limits}).
+Increasing sample sizes will reduce uncertainty about the upper bound of the interaction probability and will also increase the probability of detecting unlikely or cryptic interactions (e.g., interactions where $L$=1 but process or detection uncertainty is high).
 Despite these benefits, we note that there are limits to the utility of increased sampling.
-Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig.~\ref{histograms}E-F).
+Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig.~\ref{histograms}C).
 Thus, the more we sample, the more zeros will appear in our interaction matrix.
@@
 Nevertheless, we propose that information on the probability of detecting interactions in a focal system can be obtained by combining repeated sampling with prior information from the same or a similar system.
+Here, we first outline the statistical framework for a Bayesian approach to probabilistic interactions and then illustrate this approach with an intensively and repeatedly sampled empirical dataset.
 
-\section*{A naive quantification of uncertainty}
+\section*{Materials and methods}
 
-  We will start by considering how we could naively quantify interaction probability and its associated uncertainty \emph{for an interaction that has not yet been observed}.
+  \subsection*{A naive quantification of uncertainty}
+
+    We start by considering how to naively quantify an interaction probability and its associated uncertainty \emph{for an interaction that has not yet been observed}.
 Consider the case where a pair of species have been observed co-occurring $n$ times, of which they have been observed to interact in $k = 0$ cases.
@@
         \begin{equation}
-        X \sim Bin(n,\lambda) ,
+          L \sim Bin(n,\lambda) ,
         \end{equation}
@@
         \begin{equation}
-         P(X = k|\lambda,n) = {n \choose k}\lambda^k(1-\lambda)^{n-k} . 
+           P(L = k|\lambda,n) = {n \choose k}\lambda^k(1-\lambda)^{n-k} . 
            \label{likelihood}
@@
 
-  The variance of a Bernoulli experiment is $n\lambda$(1-$\lambda$).
-It is important to remember that this variance describes the variability of the number of successes $k$ for $n$ trials and is not the variance associated with the estimation of $\lambda$.
-Given this variance, it is possible to compute the confidence interval for the MLE of $\lambda$ using any of several methods, including the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]).
-Finding this estimate is therefore quite straightforward.
-Importantly, $\lambda$ is not a single point estimate but rather a random variable with an unknown distribution.
+    Note that $\lambda$ is not a single point estimate but rather a random variable with an unknown distribution.
 This means that if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact.
@@
 In the situation where $k>0$, in contrast, we are sure that the interaction is feasible ($L = 1$).
-If $n>k>0$, the interaction is feasible but there may be local constraints ($X=0$) or detection errors ($D<1$) causing the interaction not to be observed in some samples.
+If $n>k>0$, the interaction is feasible but there may be local constraints ($X = 0$) or detection errors ($D<1$) causing the interaction not to be observed in some samples.
+
+    To properly interpret $\lambda$, we need to estimate the variance as well as the MLE.
+The variance of a Bernoulli experiment is $n\lambda$(1-$\lambda$) and, importantly, describes the variability of the number of successes $k$ for $n$ trials rather than the variance associated with the estimation of $\lambda$.
+It is, however, straightforward to compute the confidence interval for the MLE of $\lambda$ using any of several methods, including the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]).
 % The non-point nature of lambda seems like a feature, not a bug.
 
-  Treating $\lambda$ as a distribution does, however, have an important drawback.
-Where the number of samples $n$ is very low, as for rare species, there will be considerable uncertainty around our estimate of $\lambda$.
+    All of the above methods for estimating the variance of $\lambda$ include the number of samples $n$.
+This means that where the number of samples $n$ is very low, as for rare species, there will be considerable uncertainty around our estimate of $\lambda$.
 In Fig.~\ref{upper_limits}, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda$ varies with sample size.
@@
 
-\section*{Bayesian approach to infer interaction probabilities}
+  \subsection*{Inferring interaction probabilities}
 
-    \subsection*{Posterior distribution of the interaction probability}
+      \subsubsection*{Posterior distribution of the interaction probability}
 
@@
 
-    \subsection*{Moments and other properties}
+      \subsubsection*{Moments and other properties}
 
@@
 
-    \subsection*{The prior distribution}
+      \subsubsection*{The prior distribution}
 
@@
 
-\section*{Scaling up to networks - an empirical example}
+\subsection*{Scaling up to networks - an empirical example}
 
-    In the following section, we will provide an empirical example based on the well-sampled system of \emph{Salix} plants, herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}; see Box 1 or \emph{Appendix S2} for a description).
-Using this dataset, we will demonstrate the derivation of prior distributions for the galler-natural enemy component of these networks (see \emph{Appendix S3} for the \emph{Salix}-galler component) and the differences between these priors and posterior distributions which include all information available in this dataset~\citep{Kopelke2017}.
-Finally, we will calculate network properties using a suite of networks sampled from these posterior distributions and show how the uncertainty around interactions that have not been observed impact these metrics.
+    In the following section, we will provide an empirical example based on the well-sampled system of willow (\emph{Salix}) species, herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}.
+This dataset consists of a single community type sampled across Europe over 29 years and at 374 unique locations.
+The data were collected over 29 years at 374 unique locations across Europe.
+The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (see \emph{Appendix S2} for details).
+
+    The high spatiotemporal resolution of this network and the unusually high sampling effort implemented at the site level makes this dataset particularly well suited for illustrating the difficulties in completely sampling a network and testing Bayesian approaches to overcome these difficulties.
+To do this, we first compared the frequencies of observed co-occurrences and interactions.
+We analysed both the \emph{Salix}-galler and galler-natural enemy components of the network but, for the sake of brevity, present only the latter here.
+For the \emph{Salix}-galler component see \emph{Appendix S3}.
 
@@
       To obtain the priors based on the Zillis sub-network, we estimated frequencies of interactions based on the normalised degree of each species in each network component
-      (see \emph{Appendix S6} for details and code).
-Specifically, we obtained prior parameters of $\alpha$=0.700, $\beta$=8.49.
-After calculating these prior parameters, we were then able to estimate the posterior distribution of interaction probabilities given the additional information in our dataset.
-
-      For species where no co-occurrences were observed ($n=0$), we can calculate the estimates for the mean and variance of $\lambda_{ij}$ directly from the prior parameters following equations~\ref{mean} and~\ref{variance} (see \emph{Appendix S7} for R implementation).
-For these interactions, we obtain $\bar\lambda$=0.076, var($\lambda$)=0.008.
-The posterior interaction probabilities obtained based on the Zillis sub-network were much lower than those obtained based on~\citet[Data available from the Dryad Digital Repository: https://doi.org/10.5061/dryad.g7805]{Barbour2016}; this emphasises the importance of using an appropriate study system when constructing a prior (\emph{Appendix S4}).
-
-      For a pair of species with some observed co-occurrences ($n>0$), we can update the prior distribution with data.
+      (see \emph{Appendix S5} for details and code).
+Using these prior parameters, we then estimated the posterior distributions of interaction probabilities $\lambda$.
+For species without observed interactions ($n = 0$), the posterior distribution is identical to the prior distribution.
+For species where $n>0$, we can update the prior distribution with data.
 If we consider only pairs of species which were observed to co-occur but not to interact, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs.
 This gives $\alpha'$=$\alpha$ and $\beta'$=$\beta + n_{ij}$.
-As the most extreme case, consider a pair of species which co-occurred at all 374 sites and was never observed to interact.
-Using the priors described above, our distribution would become $\bar\lambda_{ij}$=1.83 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=4.76.
-This distributions is very close to 0 with small variance about $\lambda$; species $i$ and $j$ are extremely unlikely to interact at sites or times not included in our sample.
-
-      For most pairs of species $i$ and $j$, however, $n_{ij}$ was much less than 374 and our posterior mean and variance therefore retain more of the influence of the prior.
-We can see this in the increasing means and variances as we decrease $n_{ij}$ (Fig.~\ref{Salix_pdfs_cdfs}).
-The change in distribution as $n_{ij}$ decreases can also be shown  by calculating 95\% credible intervals for $\lambda$ (see the function ``credible\_interval" in \emph{Appendix S2}).
-The 95\% credible interval for hypothetical galler-natural enemy pairs, meanwhile, widened from (0.00001, 0.008) to (0.0005, 0.304).
+We calculated posterior distributions and 95\% credible intervals (see function ``credible\_interval" in \emph{Appendix S6}) for species with $n$ ranging between 0 and 374, the total number of sites in our dataset.
 
@@
       Rather than calculating credible intervals for a posterior distribution after collecting data, we may wish to know how many data points are necessary to obtain a given level of confidence that two co-occurring species do not interact.
-The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact (Fig.~\ref{Salix_pdfs_cdfs}; see function samples\_for\_threshold in~\emph{Appendix S3}).
-The number of samples required to be 95\% confident that the interaction probability between galler and natural enemy species is below a threshold increases quickly as the threshold decreases (\emph{Appendix S5}).
+The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact (Fig.~\ref{Salix_pdfs_cdfs}; see function samples\_for\_threshold in~\emph{Appendix S6}).
+The number of samples required to be 95\% confident that the interaction probability between galler and natural enemy species is below a threshold increases quickly as the threshold decreases (\emph{Appendix S7}).
 The 95\% credible interval is (\textless0.001, 0.303) for the probability of interaction between two species observed to co-occur but never interact.
@@
 
-\section*{Conclusions/recommendations}
+\section*{Results}
+
+  Most pairs of species (9,794/12,096 galler-natural enemy pairs) are never found co-occurring and, for species that did occur together, the total number of co-occurrences was generally low (mean=3.87, variance=28.8; Fig.~\ref{histograms}A).
+The bulk of these co-occurring species pairs were never observed to interact: only 7.76\% of galler-natural enemy pairs were observed interacting.
+Of those pairs that did interact, the incidence of interaction was also low (mean=4.04, variance=29.3; Fig.~\ref{histograms}B).
+Moreover, even when a pair of species was observed to interact, the number of interactions was often lower than the number of co-occurrences (Fig.~\ref{histograms}C).
+
+  \subsection*{Computing the prior and posterior distributions}
+
+      We obtained prior parameters of $\alpha$=0.700, $\beta$=8.49.
+Where $n = 0$, these parameters gave a posterior distribution with $\bar\lambda$=0.076, var($\lambda$)=0.008.
+The posterior interaction probabilities obtained based on the Zillis sub-network were much lower than those obtained based on~\citet[Data available from the Dryad Digital Repository: https://doi.org/10.5061/dryad.g7805]{Barbour2016}; this emphasises the importance of using an appropriate study system when constructing a prior (\emph{Appendix S4}).
+When $n = 374$, we obtained a posterior distribution with $\bar\lambda_{ij}$=1.83 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=4.76.
+This distributions is very close to 0 with small variance about $\lambda$; species $i$ and $j$ are extremely unlikely to interact at sites or times not included in our sample.
+
+      For most pairs of species $i$ and $j$, however, $n_{ij}$ was much less than 374 and our posterior mean and variance therefore retain more of the influence of the prior.
+We can see this in the increasing means and variances as we decrease $n_{ij}$ (Fig.~\ref{Salix_pdfs_cdfs}).
+The change in distribution as $n_{ij}$ decreases can also be shown  by calculating 95\% credible intervals for $\lambda$ (see the function ``credible\_interval" in \emph{Appendix S6}).
+The 95\% credible interval for hypothetical galler-natural enemy pairs, meanwhile, widened from (0.00001, 0.008) to (0.0005, 0.304).
+
+  \subsection*{How many samples are required to reach a minimal precision}
+
+  \subsection*{Scaling up to network metrics}
+
+\section*{Discussion}
+
+  Even in the most extensive data set that we could find, there was very little empirical data for each species pair.
+Most pairs of species were not observed co-occurring even once, and less than 10\% of species pairs were observed interacting.
+This suggests that limited sampling is a major source of uncertainty in all empirical networks.
+This dataset also illustrates the problem of process uncertainty - pairs of species which were observed to interact did not interact in all of the samples in which they co-occurred.
+The number of observed co-occurrences strongly affected the posterior distribution of $\lambda$, meaning that our level of confidence that an interaction probability is below some threshold depends strongly on the amount of information available for each pair of species.
+
+  [[Recap results]]
 
@@
 
-\begin{fullbox}{}
-  \begin{spacing}{1.0}
-    \textbf{Box 1: }\emph{Salix}-galler-natural enemy dataset.\\
-    \indent As a case study, we use an extensively sampled \emph{Salix}-galler-natural enemy meta-network.
+% \begin{fullbox}{}
+%   \begin{spacing}{1.0}
+%     \textbf{Box 1: }\emph{Salix}-galler-natural enemy dataset.\\
+%     \indent As a case study, we use an extensively sampled \emph{Salix}-galler-natural enemy meta-network.
 This dataset consists of a single community type sampled across Europe: willow (\emph{Salix}) species, willow-galling sawflies, and their natural enemies.
@@
 The high spatiotemporal resolution of this network and the unusually high sampling effort implemented at the site level makes this dataset particularly well suited for illustrating the difficulties in completely sampling a network and testing Bayesian approaches to overcome these difficulties.\\
-    \indent We may begin by comparing the frequencies of co-occurrences and interactions to reveal the challenge of having sufficient sampling to be confident that an interaction does not occur.
+%     \indent We may begin by comparing the frequencies of co-occurrences and interactions to reveal the challenge of having sufficient sampling to be confident that an interaction does not occur.
 Most pairs of species (9,794/12,096 galler-natural enemy pairs) are never found co-occurring and, for species that did occur together, the total number of co-occurrences was generally low (mean=3.87, variance=28.8; Fig.~\ref{histograms}A).
@@
 This dataset also illustrates the potential for increased sampling to not necessarily reveal more interactions as a pair of species that is able to interact may not be observed interacting in all samples where the pair co-occurs (Fig.~\ref{histograms}C).
-  \end{spacing}
-\end{fullbox}
+%   \end{spacing}
+% \end{fullbox}
 

### 2018-06-07 manuscript/CI_interactions.tex
81 words too many

@@
 Moreover, finite sampling generates variation in the set of interactions actually observed.
+For interactions that have not been observed, most data sets will not contain enough information to be confident that unobserved interactions truly did not occur.
     \item Here we develop the conceptual and analytical tools needed to capture uncertainty in the estimation of pairwise interactions.
-To define the problem, we identify the different contributions to the uncertainty of an interaction and its implications for the estimation of network properties.
-We then outline a framework to quantify the uncertainty around each interaction.
+To define the problem, we identify the different contributions to the uncertainty of an interaction.
+We then outline a framework to quantify the uncertainty around each interaction by combining data on observed co-occurrences with prior knowledge.
 We illustrate this framework using the most extensively sampled network to date.
@@
 This uncertainty scaled up to summary measures of network structure such as connectance or nestedness.
-Even with informative priors, our results suggest that the relatively well-sampled network we use as a test case is missing many interactions that may occur rarely or under different local conditions.
+Even with informative priors, our results suggest that the extremely well-sampled network we use as a test case is missing many interactions that may occur rarely or under different local conditions.
     \item Through these efforts, we demonstrate the utility of our approach and the importance of acknowledging the uncertainty inherent in network studies.
@@
 Doing so will fundamentally change networks analyses and yield greater realism.
-  % Can be up to 350 words for MEE. This is 200 exactly.
+  % Can be up to 350 words for MEE. This is 270 exactly.
 \end{enumerate}
@@
 
-          First, and most fundamentally, we do not know whether or not a pair of species have the appropriate characteristics (or traits) to interact.
+          First, and most fundamentally, we may not know whether or not a pair of species have the appropriate characteristics (or traits) to interact.
 We define the probability of an interaction $L$ given characteristics $\mathbf{T}$ as $P(L | \mathbf{T})=\lambda$.
-If two species have incompatible traits, they may not interact even if there are no other constraints (e.g., temporal separation of species, inability to detect cryptic species) preventing the interaction from being observed.
-As a simple example, a prey species may be too large to be consumed by a predator.
-In such cases, $\lambda$ would take a value of 0 and there would be no uncertainty.
+Some species pairs, such as a salmon and a saguaro cactus, have incompatible traits and would never interact even if they should co-occur.
+In such cases, $\lambda = 0$ and there is no uncertainty.
 
-          Based on an observed network, however, it is often unclear whether an unobserved interaction is impossible due to incompatible traits or simply a rare phenomenon with $\lambda>0$.
-This uncertainty is partly addressed by trait-matching models~\citep{Bartomeus2016}.
+          Most species pairs, however, do not have traits that absolutely prevent an interaction.
+This means that it is generally unclear whether an unobserved interaction is impossible or simply a rare phenomenon with $\lambda>0$.
+This uncertainty is partly addressed by trait-matching models in which species with better-matched traits are more likely to interact~\citep{Bartomeus2016}.
+As these models improve and include better information about the influence of traits on interactions, the uncertainty will be reduced and $\lambda$ should either tend to 0 or to 1.
 Nevertheless, every model is imperfect and lacks information that could be used to define constraints on interactions~\citep{Dormann2017}.
-Some interaction uncertainty therefore remains in current trait-matching models.
-As more information about the influence of traits on interactions is uncovered, this uncertainty is likely to be reduced and $\lambda$ should either tend to 0 or to 1.
+Some interaction uncertainty will remain even using a very good trait-matching model.
 
@@
 
+         One proposed solution to the problem of process uncertainty is to use repeated sampling of networks.
+For example,~\citet{Weinstein2017} used repeated sampling rounds to estimate the daily probability of detecting an interaction and thereby model detection and process uncertainty.
+While conceptually attractive, this approach is unsuitable for interactions occurring over longer time scales (e.g., associations between hosts and parasitoids with a single generation per year), or very rare interactions which might not occur on any of the sampling days.
+Moreover, the faster accumulation of species than interactions means that repeated sampling will tend to introduce more unobserved interactions than observed interactions unless the number of samples is very high~\citep{Poisot2012}.
+
         \subsubsection*{Detection uncertainty}
@@
           Lastly, measurement errors are a pervasive source of uncertainty in the observation of ecological processes.
-Given that an interaction is feasible and occurs under the local conditions ($L$=1 and $X$=1), we may define the detection of an interaction, $D$, as a stochastic process with the associated probability $P(D|X=1,L=1)=\delta$.
-Detection failure could happen for many reasons (see~\citet{Wirta2014} for examples of these difficulties and partial solutions to them).
-Some sources of detection error can be minimised with appropriate sampling effort ($\delta$ will converge to one with increasing number of samples), but other sources are often difficult to reduce (e.g.
+That is, even if an interaction is feasible and occurs during sampling ($L = 1$ and $X = 1$), we may fail to detect it.
+We may define the probability of detecting of an interaction, $D$, as a stochastic process with the associated probability $P(D|X=1,L=1)=\delta$.
+Detection failure could happen for many reasons (see~\citet{Wirta2014} for examples and partial solutions to them).
+Some sources of detection error can be minimised with appropriate sampling effort ($\delta$ will approach one with increasing number of samples), but other sources are often difficult to reduce (e.g.
 the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification as in~\citealt{Wirta2014,Frost2016}).
+The impossibility of eliminating detection uncertainty also limits the usefulness of repeated sampling; the absence of an interaction on a given day could either be because it was not feasible [$P(L) = 0$], was feasible but did not occur because of local conditions during sampling ($P(X|L=1) = 0$], or was feasible and occurred during sampling but could not be observed [$P(D|X=1,L=1)=0$].
+From a conceptual perspective, repeated sampling therefore fails to satisfactorily address the uncertainty inherent in empirical networks.
 
@@
 It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e.
-where the interaction occurred at the location but was not observed, and $X = 0 \cup L =1$, i.e., where the interaction is feasible but did not occur at the local site.
+where the interaction occurred at the location but was not observed, and $X = 0 \cup L =1$, i.e., where the interaction is feasible but did not occur at the local site (Fig.~\ref{concept_fig}).
         % The occurrence of a true absence, our quantity of interest, corresponds to the joint event $L=0 \cup X=1 \cup D=1$ but %% AC: Doesn't a true absence just mean $L=0$ regardless of our ability to detect/local conditions?
@@
 This probability does not contain any information about $D$ or $X$.
+The major question then becomes: how can we reduce the uncertainty around our estimated interaction probability?
 
-        The considerations above raise major challenges: when faced with empirical data, how may we infer whether unobserved interactions truly do not occur?
+        % The considerations above raise major challenges: when faced with empirical data, how may we infer whether unobserved interactions truly do not occur?
 How may we refine our sampling approaches to reduce uncertainties and gain insights into the impact of multiple processes on field observations?
@@
 
-        When attempting to reduce uncertainty, the obvious rule of thumb is to ``sample more" (Fig.~\ref{upper_limits}).
+        When attempting to reduce uncertainty, the obvious rule of thumb is to ``sample more".
 Increasing sample sizes will reduce uncertainty about the upper bound of the interaction probability and will also increase the probability of detecting unlikely or cryptic interactions (e.g., interactions where $L$=1 but process or detection uncertainty is high).
@@
 
-        A slight variation on the theme of ``sample more" is to sample repeatedly.
-In one endeavour to uncover the cause of unobserved interactions,~\citet{Weinstein2017} used repeated sampling rounds to estimate the daily probability of detecting an interaction and thereby model detection and process uncertainty.
-While conceptually attractive, this approach is unsuitable for interactions occurring over longer time scales (e.g., associations between hosts and parasitoids with a single generation per year), or very rare interactions which might not occur on any of the sampling days.
-Worse, the problem persists that the absence of an interaction on a given day could be because it was impossible on that day despite being otherwise feasible [$P(X|L=1)=0$], because interaction did occur but could not be observed [$P(D|X=1,L=1)=0$].
-From a conceptual perspective, this approach therefore fails to satisfactorily distinguish between sources of uncertainty.
-
         Most importantly, if two species are never observed co-occurring during several days of sampling then repeated sampling reveals nothing about their probability of interacting if they should ever co-occur.
-The bottom line is that separating different sources of uncertainty is difficult indeed.
-Nevertheless, we propose that information on the probability of detecting interactions in a focal system can be obtained by combining repeated sampling with prior information from the same or a similar system.
-Here, we first outline the statistical framework for a Bayesian approach to probabilistic interactions and then illustrate this approach with an intensively and repeatedly sampled empirical dataset.
+Intensive sampling is, therefore, an important step towards reducing uncertainty in ecological networks but is unlikely to be enough in most cases.
+To supplement repeated and intensive sampling efforts and further reduce uncertainty around unobserved interactions, we suggest researchers use prior information drawn from the same or a similar system.
+Here, we first outline the statistical framework for a Bayesian approach to probabilistic interactions and then demonstrate how to construct such a probabilistic network using an intensively and repeatedly sampled empirical dataset.
+Finally, we show how a probabilistic understanding of a network allows us to establish confidence intervals around measures of network structure.
 
@@
 
-  \subsection*{A naive quantification of uncertainty}
+  \subsection*{A Bayesian framework for interaction probabilities}
 
-    We start by considering how to naively quantify an interaction probability and its associated uncertainty \emph{for an interaction that has not yet been observed}.
-Consider the case where a pair of species have been observed co-occurring $n$ times, of which they have been observed to interact in $k = 0$ cases.
-To evaluate the uncertainty of this interaction, consider the occurrence of an interaction as a Bernoulli trial.
-In this framework, the number of successes $k$ over $n$ trials will follow a binomial distribution:
-
-        \begin{equation}
-          L \sim Bin(n,\lambda) ,
-        \end{equation}
-
-        \begin{equation}
-           P(L = k|\lambda,n) = {n \choose k}\lambda^k(1-\lambda)^{n-k} . 
-           \label{likelihood}
-        \end{equation}
-
-    \noindent The parameter $\lambda$, the probability of observing an interaction over an infinite time interval and area, is the quantity we want to estimate from empirical data. 
-    The maximal likelihood estimate (MLE) of $\lambda$ is straightforward to find given $k$ and $n$:
+    We are most interested in how to quantify an interaction probability, and its associated uncertainty, for an interaction that has not yet been observed.
+Say a pair of species has been observed co-occurring $n$ times and observed interacting in $k = 0$ cases.
+We want to know the probability $\lambda$ that the species would be observed interacting if not constrained by local conditions, timing, imperfect detection, etc.
+We can consider the occurrence of an interaction as a Bernoulli trail where the number of successes ($k$) over $n$ trials will follow a binomial distribution (see~\emph{Appendix S1} for a full description of the mathematical framework).
+In this framework, the maximum likelihood estimate (MLE) for $\lambda$ is:
 
@@
 This means that where the number of samples $n$ is very low, as for rare species, there will be considerable uncertainty around our estimate of $\lambda$.
-In Fig.~\ref{upper_limits}, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda$ varies with sample size.
-At a small sample size, the 95\% confidence interval spans all values of $\lambda$.
+In Fig.~\ref{upper_limits}, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda$ (for true $\lambda = 0$) varies with sample size.
+At a small sample size, the 95\% confidence interval is nearly (0, 1).
 To establish that species are not interacting with any acceptable certainty requires tens of observations of the two species co-occurring but not interacting.
-As most data sets will lack such extensive sampling across all species pairs, we can use a Bayesian approach to supplement the data we have with other sources of information.
+Most data sets will lack such extensive sampling across all species pairs, but we can still use a Bayesian approach to supplement the available data with other sources of information.
 
-  \subsection*{Inferring interaction probabilities}
-
-      \subsubsection*{Posterior distribution of the interaction probability}
-
-        Here we adopt a Bayesian approach to estimate the posterior distribution of the parameter $\lambda$ :
-
-        \begin{equation}
-          \underbrace{P(\lambda|k,n)}_{Posterior} = \frac{\overbrace{P(k|\lambda,n)}^{Likelihood}\overbrace{P(\lambda)}^{Prior}}{\underbrace{P(k|N)}_{Normaliser}} .
-          \label{posterior}
-        \end{equation}
-
-        According to the above description, the likelihood is simply the binomial distribution (Eq.~\ref{likelihood}).
-Since $\lambda$ is a probability, it is bounded between 0 and 1 and the most appropriate prior distribution is the beta:
+    The Bayesian approach combines the MLE of $\lambda$ described above with a prior distribution and a normaliser to give a posterior distribution.
+For species pairs with a great deal of observed data (high $n$), the posterior distribution will mostly be based on the MLE of $\lambda$.
+Where there is little or no observed data (low $n$), the posterior distribution will reflect our prior knowledge.
+Since $\lambda$ is a probability and bounded between 0 and 1, the most appropriate prior distribution is the beta:
 
@@
 
-       The beta-binomial distribution is a conjugate distribution of the binomial distribution.
-This allows us to analytically compute the posterior distribution of a binomial model with a beta prior distribution.
-We can re-write the posterior distribution of $\lambda$ as:
-
-        \begin{equation}
-          P(\lambda|k,n) = \frac{\lambda^{\alpha+k-1}(1-\lambda)^{\beta+n-k-1}}{B(\alpha+k,\beta+n-k)} , \label{posterior2}
-        \end{equation}
-
-        \noindent where the function $B$ is the beta function.
-The posterior distribution of $\lambda$ therefore follows the beta distribution with new parameters $\alpha'= \alpha+k$ and $\beta'=\beta+n-k$.
+    Combining the beta-distributed prior with the binomial-distributed MLE of $\lambda$ is straightforward (see~\emph{Appendix S1}).
+By doing so, we obtain a posterior distribution that follows a beta distribution with new parameters $\alpha'= \alpha+k$ and $\beta'=\beta+n-k$.
 The weight of the prior on the posterior distribution can be understood from these parameter definitions: the difference between the posterior and the prior will increase with $k$ and $n-k$.
@@
 
-      \subsubsection*{The prior distribution}
+    \subsubsection*{Choosing a prior distribution}
 
@@
 These are called hyper parameters.
-The prior may be chosen to be uninformative, if no external information is available, or may draw on information such as distributions of connectance across webs, degree within webs, or a trait-matching function (see \emph{Appendix S1} for details and a simple quantitative example).
+The prior may be chosen to be uninformative, if no external information is available, or may draw on information such as distributions of connectance across webs, degree within webs, or a trait-matching function (see \emph{Appendix S2} for details and a simple quantitative example).
 
-\subsection*{Scaling up to networks - an empirical example}
+      When using an informative prior, it is important to ensure that the prior accurately reflects the focal  system.
+For example, if the focal system is a large network containing many plant species and insects from different families, it is inappropriate to use a prior distribution drawn from a small network describing interactions between different genotypes of a single plant species wtih a set of closely-related insects.
+The similarity of traits for genotypes within a species means that an insect which interacts with one genotype is likely to interact with many others.
+Trait differences between species means that a species-species network will likely contain fewer interactions than a genotype-species network.
+Similarly, highly-aggregated networks containing nodes which represent whole classes or families are likely to have very different structures than networks where most nodes represent single species.
 
-    In the following section, we will provide an empirical example based on the well-sampled system of willow (\emph{Salix}) species, herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}.
+      The choice of prior will depend on the information available.
+In general, it is best to use a prior taken from a similar system.
+If such data are not available, a prior based on many networks systems with a similar level of resolution could be useful, as could a prior based on a preliminary round of sampling (analogous to ``training data").
+If there is no suitable informative prior, it is best to use an explicitly uninformative prior.
+While an uninformative prior will not greatly reduce variance about $\lambda$, it does clearly state our lack of prior knowledge and will not bias our conclusions.
+
+  \subsection*{An empirical example}
+
+      We illustrate the process of constructing a Bayesian network using the well-sampled system of willow (\emph{Salix}) species, herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}.
 This dataset consists of a single community type sampled across Europe over 29 years and at 374 unique locations.
 The data were collected over 29 years at 374 unique locations across Europe.
-The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (see \emph{Appendix S2} for details).
+The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (see \emph{Appendix S3} for details).
 
-    The high spatiotemporal resolution of this network and the unusually high sampling effort implemented at the site level makes this dataset particularly well suited for illustrating the difficulties in completely sampling a network and testing Bayesian approaches to overcome these difficulties.
+      The high spatiotemporal resolution and unusally high sampling effort of this dataset make this it particularly well suited for illustrating the difficulties in completely sampling a network.
 To do this, we first compared the frequencies of observed co-occurrences and interactions.
-We analysed both the \emph{Salix}-galler and galler-natural enemy components of the network but, for the sake of brevity, present only the latter here.
-For the \emph{Salix}-galler component see \emph{Appendix S3}.
+We analysed both the \emph{Salix}-galler and galler-natural enemy components of the network but present only the latter here (see~\emph{Appendix S4} for \emph{Salix}-galler results).
 
-  \subsection*{Computing the prior and posterior distributions}
+    \subsubsection*{Computing the prior and posterior distributions}
 
-      In a strict Bayesian framework, we wish to use a prior distribution that does not rely on any information from the study at hand.
-Network data for a similar study system may, however, not be available.
-In that case, one might use the first sub-network collected as ``training data" to guide future sampling.
+        A strict Bayesian framework requires a prior distribution that does not rely on any information from the study at hand.
+If such data are not available, one might instead use the first sub-network collected as ``training data" to guide future sampling.
 To simulate this situation, we created priors using a single sub-network from the middle of the geographical distribution of the~\citet{Kopelke2017} dataset.
-To demonstrate how the use of data from a different system can affect the prior distribution and conclusions based on it, we repeated our analyses using priors derived from a much smaller \emph{Salix}-galler-natural enemy system~\citep[Data available from the Dryad Digital Repository: https://doi.org/10.5061/dryad.g7805]{Barbour2016}\nocite{Barbour2016Dryad}.
-This smaller system was much more densely-connected than that described in~\citet{Kopelke2017} and provided unreasonable distributions for interaction probabilities (\emph{Appendix S4}).
+To demonstrate how the use of data from a different system can affect the prior distribution and conclusions based on it, we repeated our analyses using priors derived from a much smaller \emph{Salix}-galler-natural enemy system based around genotypes of a single \emph{Salix} species~\citep[Data available from the Dryad Digital Repository: https://doi.org/10.5061/dryad.g7805]{Barbour2016}\nocite{Barbour2016Dryad}.
+This smaller system was much more densely-connected than that described in~\citet{Kopelke2017} and provided unreasonable distributions for interaction probabilities (\emph{Appendix S5}).
 
         To obtain the priors based on the Zillis sub-network, we estimated frequencies of interactions based on the normalised degree of each species in each network component
-      (see \emph{Appendix S5} for details and code).
+        (see \emph{Appendix S6} for details and code).
 Using these prior parameters, we then estimated the posterior distributions of interaction probabilities $\lambda$.
@@
 This gives $\alpha'$=$\alpha$ and $\beta'$=$\beta + n_{ij}$.
-We calculated posterior distributions and 95\% credible intervals (see function ``credible\_interval" in \emph{Appendix S6}) for species with $n$ ranging between 0 and 374, the total number of sites in our dataset.
-
-  \subsection*{How many samples are required to reach a minimal precision}
+We calculated posterior distributions and 95\% credible intervals (see function ``credible\_interval";~\emph{Appendix S7}) for species with $n$ ranging between 0 and 374, the total number of sites in our dataset.
 
         Rather than calculating credible intervals for a posterior distribution after collecting data, we may wish to know how many data points are necessary to obtain a given level of confidence that two co-occurring species do not interact.
-The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact (Fig.~\ref{Salix_pdfs_cdfs}; see function samples\_for\_threshold in~\emph{Appendix S6}).
-The number of samples required to be 95\% confident that the interaction probability between galler and natural enemy species is below a threshold increases quickly as the threshold decreases (\emph{Appendix S7}).
-The 95\% credible interval is (\textless0.001, 0.303) for the probability of interaction between two species observed to co-occur but never interact.
-To be 95\% confident that the probability of interaction is below 0.1, 0.05, or 0.01 would require 15, 39, and 229 observed co-occurrences, respectively.
+The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact.
+We calculated the number of samples required to reach 95\% confidence that $\lambda$ was below thresholds of 0.1, 0.05, and 0.01 as examples (see function ``samples\_for\_threshold";~\emph{Appendix S7}).
 
-      Given the low levels of replication in most network studies, this implies that we should have fairly low confidence in many ``non-interacting" pairs of species.
-Even in the extensively replicated \emph{Salix}-galler-natural enemy dataset, very few species pairs were observed co-occurring frequently enough to reach these thresholds.
-Regardless of our choice of prior, no species pairs were observed to co-occur frequently enough to reach the threshold for an interaction probability of 0.01.
-Discounting potential interactions, then, requires either a stronger prior expectation of no interaction (e.g.
-for forbidden interactions) or very extensive sampling.
-For all we know, most links absent from current descriptions of network structure may be so not because the species do not interact, but because we have not sampled deeply enough to detect them.
-
-  \subsection*{Scaling up to network metrics}
+    \subsubsection*{Scaling up to network metrics}
 
@@
 
-    We found that the connectance, mean links per galler, and mean links per natural enemy were much lower in the observed web (C=0.078, $L_{galler}$=9.99, and $L_{natural enemy}$=7.45, respectively) than in the posterior webs (0.186 $\leq$ C $\leq$ 0.198, 13.4 $\leq L_{galler} \leq$ 14.6, and 23.4 $\leq L_{natural enemy} \leq$ 25.0).
-When the detection probability was relatively low (i.e., 50\%), however, the properties of randomised networks became similar to those in the observed webs (Fig.~\ref{posterior_webs}A,B,D).
-Nestedness was higher in the observed network (NODF=6.85) than in the posterior webs (6.31 $\leq NODF \leq$ 6.82; Fig.~\ref{posterior_webs}C); in this case, the stronger the detection filter the farther apart were the observed and posterior webs.
-
 \section*{Results}
@@
 
-  \subsection*{Computing the prior and posterior distributions}
-
   We obtained prior parameters of $\alpha$=0.700, $\beta$=8.49.
 Where $n = 0$, these parameters gave a posterior distribution with $\bar\lambda$=0.076, var($\lambda$)=0.008.
-The posterior interaction probabilities obtained based on the Zillis sub-network were much lower than those obtained based on~\citet[Data available from the Dryad Digital Repository: https://doi.org/10.5061/dryad.g7805]{Barbour2016}; this emphasises the importance of using an appropriate study system when constructing a prior (\emph{Appendix S4}).
 When $n = 374$, we obtained a posterior distribution with $\bar\lambda_{ij}$=1.83 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=4.76.
@@
   For most pairs of species $i$ and $j$, however, $n_{ij}$ was much less than 374 and our posterior mean and variance therefore retain more of the influence of the prior.
-We can see this in the increasing means and variances as we decrease $n_{ij}$ (Fig.~\ref{Salix_pdfs_cdfs}).
-The change in distribution as $n_{ij}$ decreases can also be shown  by calculating 95\% credible intervals for $\lambda$ (see the function ``credible\_interval" in \emph{Appendix S6}).
-The 95\% credible interval for hypothetical galler-natural enemy pairs, meanwhile, widened from (0.00001, 0.008) to (0.0005, 0.304).
+We can see this in the increasing means and variances as we decrease $n_{ij}$ (Fig.~\ref{Salix_pdfs_cdfs};~\emph{Appendix S8}).
+The number of samples required to be 95\% confident that the interaction probability between galler and natural enemy species is below a threshold increases quickly as the threshold decreases (Fig.~\ref{Salix_pdfs_cdfs};~\emph{Appendix S8}).
+To be 95\% confident that the probability of interaction is below 0.1, 0.05, or 0.01 would require 15, 39, and 229 observed co-occurrences, respectively.
 
-  \subsection*{How many samples are required to reach a minimal precision}
-
-  \subsection*{Scaling up to network metrics}
+  We found that the connectance, mean links per galler, and mean links per natural enemy were much lower in the observed web (C=0.078, $L_{galler}$=9.99, and $L_{natural enemy}$=7.45, respectively) than in the posterior webs (0.186 $\leq$ C $\leq$ 0.198, 13.4 $\leq L_{galler} \leq$ 14.6, and 23.4 $\leq L_{natural enemy} \leq$ 25.0).
+When the detection probability was relatively low (i.e., 50\%), however, the properties of randomised networks became similar to those in the observed webs (Fig.~\ref{posterior_webs}A,B,D).
+Nestedness was higher in the observed network (NODF=6.85) than in the posterior webs (6.31 $\leq NODF \leq$ 6.82; Fig.~\ref{posterior_webs}C); in this case, the stronger the detection filter the farther apart were the observed and posterior webs.
 
@@
 
+  Real interaction networks vary over several dimensions~\citep{Kitching1987,Olesen2011a,Pires2011a,Baiser2012,Fodrie2015,Novak2015}, leading to pervasive under-estimation of interactions in published networks.
 Even in the most extensive data set that we could find, there was very little empirical data for each species pair.
-Most pairs of species were not observed co-occurring even once, and less than 10\% of species pairs were observed interacting.
-This suggests that limited sampling is a major source of uncertainty in all empirical networks.
+Most pairs of species were not observed co-occurring even once, and less than 10\% of species pairs were observed interacting and no pairs were observed to co-occur frequently enough to reach the threshold for an interaction probability of 0.01.
+This suggests that limited sampling is a major source of uncertainty in empirical networks.
 This dataset also illustrates the problem of process uncertainty - pairs of species which were observed to interact did not interact in all of the samples in which they co-occurred.
-The number of observed co-occurrences strongly affected the posterior distribution of $\lambda$, meaning that our level of confidence that an interaction probability is below some threshold depends strongly on the amount of information available for each pair of species.
+This emphasizes the importance of accounting for imperfect detection when analysing empirical networks.
 
-  [[Recap results]]
+  Using prior knowledge to build a Bayesian distribution for each interaction probability allows us to treat unobserved interactions as less likely to occur while setting appropriate bounds on interaction probabilities between pairs of species which were never observed co-occurring.
+The number of observations required to conclude that an interaction is unfeasible is quite high (tens of observations per species pair); some species pairs are likely to fall short of this even in the highest-quality networks.
+In such cases, an informative prior distribution gives us more reasonable estimates of interaciton probabilities than assuming all unobserved interactions never occur.
+Moreover, interactions involving species entering new ranges due to climate change or introductions are important for a variety of conservation questions.
+A Bayesian approach using a trait-matching model or data from species' current ranges could be useful in anticipating how species will integrate into new communities.
 
-  Real interaction networks vary over several dimensions~\citep{Kitching1987,Olesen2011a,Pires2011a,Baiser2012,Fodrie2015,Novak2015} and to capture this variation we must turn from static descriptions of network structure to probabilistic descriptions.
-In this study, we have developed the analytical tools to capture the uncertainty in the estimation of pairwise interactions and a conceptual framework for its individual components: interaction uncertainty, process uncertainty, and detection uncertainty.
+  Our results also demonstrate how incomplete detection of interactions scales up to affect network structure.
+The structure of our well-sampled, replicated observed network is most similar to the structure of networks including only 50\% of the interactions suggested by the posterior distribution of interaction probabilities.
+Acknowledging the uncertainty inherent in a description of a system that is missing up to half of the feasible interactions is vital if we are to compare structures across systems, link structure to stability, etc.
+
   Using this framework leads us to offer tangible recommendations for improved descriptors of ecological interactions.
-First, our analyses point to detection uncertainty as a major contributor to overall uncertainty of is establishing the absence of interaction.
-To counter this and establish true absences of interactions requires comparatively large sample size – on the order of 30-50 observations per species pair.
-Second, where such extensive sampling is not feasible, researchers should still acknowledge the varying levels of confidence surrounding the presence or absence of interactions between different pairs of species.
+First, sample sizes should be as large as possible in order to reduce detection uncertainty.
+Second, where sampling on the order of 30-50 observations per species pair is not possible (likely the bulk of studies), researchers should acknowledge the varying levels of confidence surrounding interactions between different species pairs.
 Including the $n$ and $k$ values for each interaction will clearly indicate which unobserved interactions are most likely to be observed with further sampling and which estimates are more reliable.
-Third, the uncertainty around interactions (especially interactions that were not observed) should be incorporated in calculations of network properties like connectance or nestedness.
+Third, the uncertainty around interactions should be incorporated in calculations of network properties.
 Re-sampling networks based on a probabilistic understanding of networks is straightforward and gives distributions for network properties rather than point estimates.
-This not only acknowledges the fact that interactions vary over time and space but will also facilitate comparisons between networks.
-With confidence intervals around network metrics, we can not only say that one network is more connected than another but also whether the networks are more different than we would expect based on imperfect sampling of interactions.
+This not only acknowledges the fact that interactions vary over time and space but will also facilitate comparisons between networks by adding confidence intervals to estimates of network properties.
+This will allow us to say whether networks have different structures \emph{and} whether those differences are greater than we would expect given the inherent variability of interactions.
 To facilitate these recommendations, we provide all code used in this paper in the supplementary material.

### 2018-06-07 manuscript/supplemental.tex
mostly re-ordered

@@
 
-% Definite first
-\section*{Appendix S1: Calculating uninformative and informative priors}
+\section*{Appendix S1: Detailed description of mathematical framework}
+
+  \subsection*{A naive quantification of uncertainty}
+
+    We start by considering how to naively quantify an interaction probability and its associated uncertainty \emph{for an interaction that has not yet been observed}.
+Consider the case where a pair of species have been observed co-occurring $n$ times, of which they have been observed to interact in $k = 0$ cases.
+To evaluate the uncertainty of this interaction, consider the occurrence of an interaction as a Bernoulli trial.
+In this framework, the number of successes $k$ over $n$ trials will follow a binomial distribution:
+
+        \begin{equation}
+          L \sim Bin(n,\lambda) ,
+        \end{equation}
+
+        \begin{equation}
+           P(L = k|\lambda,n) = {n \choose k}\lambda^k(1-\lambda)^{n-k} . 
+           \label{likelihood}
+        \end{equation}
+
+    \noindent The parameter $\lambda$, the probability of observing an interaction over an infinite time interval and area, is the quantity we want to estimate from empirical data. 
+    The maximal likelihood estimate (MLE) of $\lambda$ is straightforward to find given $k$ and $n$:
+
+        \begin{equation}
+          \lambda_{MLE} = \frac{k}{n}  .
+          \label{theta_MLE}
+        \end{equation}
+
+  \subsection*{Posterior distribution of the interaction probability}
+
+    Here we adopt a Bayesian approach to estimate the posterior distribution of the parameter $\lambda$ :
+
+    \begin{equation}
+      \underbrace{P(\lambda|k,n)}_{Posterior} = \frac{\overbrace{P(k|\lambda,n)}^{Likelihood}\overbrace{P(\lambda)}^{Prior}}{\underbrace{P(k|N)}_{Normaliser}} .
+      \label{posterior}
+    \end{equation}
+
+    According to the above description, the likelihood is simply the binomial distribution (Eq.~\ref{likelihood}).
+Since $\lambda$ is a probability, it is bounded between 0 and 1 and the most appropriate prior distribution is the beta:
+
+    \begin{equation}
+      \lambda \sim Beta(\alpha,\beta) , \label{prior}
+    \end{equation}
+
+    \noindent which has two shape parameters, $\alpha$ and $\beta$.
+
+   The beta-binomial distribution is a conjugate distribution of the binomial distribution.
+This allows us to analytically compute the posterior distribution of a binomial model with a beta prior distribution.
+We can re-write the posterior distribution of $\lambda$ as:
+
+    \begin{equation}
+      P(\lambda|k,n) = \frac{\lambda^{\alpha+k-1}(1-\lambda)^{\beta+n-k-1}}{B(\alpha+k,\beta+n-k)} , \label{posterior2}
+    \end{equation}
+
+    \noindent where the function $B$ is the beta function.
+The posterior distribution of $\lambda$ therefore follows the beta distribution with new parameters $\alpha'= \alpha+k$ and $\beta'=\beta+n-k$.
+
+\clearpage
+
+\section*{Appendix S2: Calculating uninformative and informative priors}
 
@@
 We can use the distribution of these interaction probabilities as our prior distribution and estimate the uncertainty surrounding our $\lambda_{MLE}$.
-With some simple R code (function ``calculate\_parameters", \emph{Appendix S3}), we obtain prior parameters $\alpha$=0.998 and $\beta$=4.63.
-Using these priors in equations~\ref{mean} and~\ref{variance} above (or in the R function ``calculate\_distribution" in \emph{Appendix S3}), we find a prior $\bar\lambda$=0.177 and var($\lambda$)=0.026.
+With some simple R code (function ``calculate\_parameters", \emph{Appendix S7}), we obtain prior parameters $\alpha$=0.998 and $\beta$=4.63.
+Using these priors in equations~\ref{mean} and~\ref{variance} above (or in the R function ``calculate\_distribution" in \emph{Appendix S7}), we find a prior $\bar\lambda$=0.177 and var($\lambda$)=0.026.
 Adding the observed data ($n=10$, $k=3$) and using the same code, we obtain posterior parameters $\alpha'$=4.00 and $\beta'$=11.6 and a posterior $\bar\lambda$=0.256 and var($\lambda$)=0.012.
@@
 We may also wish to calculate a credible interval (analogous to the frequentist confidence interval).
-This is also quite straightforward in R (see function ``credible\_interval" in \emph{Appendix S3}).
+This is also quite straightforward in R (see function ``credible\_interval" in \emph{Appendix S7}).
 In this case, a 95\% credible interval for $\bar\lambda$ is (0.080, 0.491).
@@
 We then use the cumulative distribution function to estimate $P(\lambda<\lambda*|L=0,n)$ for different $n$.
-The function ``samples\_for\_threshold" in \emph{Appendix S3} calculates distribution function for $\lambda*$ with an increasing number of trials.
+The function ``samples\_for\_threshold" in \emph{Appendix S7} calculates distribution function for $\lambda*$ with an increasing number of trials.
 This yields a surprising result: it requires \textgreater24 observations of no interactions to be 95\% sure that the interaction probability is smaller than $\lambda*$=0.1 (recall Fig.~\ref{upper_limits}, Box 2).
@@
 
-% Definite second
-\section*{Appendix S2: Details of \emph{Salix} data collection}
+\section*{Appendix S3: Details of \emph{Salix} data collection}
 
@@
 
-% Definite third
-\section*{Appendix S3: Results for \emph{Salix}-galler component}
+\section*{Appendix S4: Results for \emph{Salix}-galler component}
 
@@
 
-      As with the galler-natural enemy component, we estimated frequencies of \emph{Salix}-galler interactions based on the normalised degree of each species (\emph{Appendix S5}).
+      As with the galler-natural enemy component, we estimated frequencies of \emph{Salix}-galler interactions based on the normalised degree of each species (\emph{Appendix S6}).
 We obtained prior parameters of $\alpha$=8.72, $\beta$=305 for the \emph{Salix}-galler component.
@@
 
-% Definite fourth
-\section*{Appendix S4: Analyses using alternative prior}
+\section*{Appendix S5: Analyses using alternative prior}
 
@@
 
-\section*{Appendix S5: Calculating the credible interval around a probability estimate}
-
-  Here we describe the derivation of the Clopper-Pearson credible interval for the estimated probability of interaction $\lambda$ of a pair of species observed co-occurring $n$ times and interacting $k$ times.
-As we are most interested in the probability of interaction between species pairs that have never been observed co-occurring, we consider only the case where $k=0$ over a variety of $n$.
-This is straightforward to do in R (see the function ``credible\_interval" in \emph{Appendix S2}).
-
-  First, we must obtain the $\alpha$ and $\beta$ parameters for the prior distribution.
-In this study we obtained these parameters using the R~\citep{R} function fitdist from the package fitdistrplus~\citep{fitdistrplus}.
-Once $\alpha$ and $\beta$ are known, we can update them using our observed data.
-Specifically, we are interested in $\alpha'=\alpha+k$ and $\beta'=\beta+n-k$.
-These parameters can then be used to calculate a credible interval using the R~\citep{R} function qbeta.
-In the table below, we present the 95\% credible intervals for \emph{Salix}-galler and galler-natural enemy pairs with different numbers of observed co-occurrences ($n$) and no observed interactions ($k=0$), calculated using prior information derived from the Zillis sub-network~\citep{Kopelke2017}.
-
-      % % # R code to make the table:
-      % ns=c(0,1,2,5,10,15,20,25,50,100,150,200,374)
-      % output=matrix(nrow=length(ns),ncol=5)
-      % output[,1]=ns
-      % for(r in 1:nrow(output)){
-      %   interval1=credible_interval(calculate_parameters(sg_int_probs,ns[r],0),0.025,0.975)    
-      %   interval2=credible_interval(calculate_parameters(gp_int_probs,ns[r],0),0.025,0.975)    
-      %   output[r,2:3]=interval1
-      %   output[r,4:5]=interval2
-      % }
-      \medskip
-      \begin{table}
-        \label{credints}
-        \caption{Here we give the lower and upper bounds of 95\% credible intervals for the probability of interaction $\lambda$ between \emph{Salix}-galler or galler-natural enemy pairs that have been observed co-occurring $n$ times but have never been observed interacting.}
-        \begin{tabular}{l  c c  c c }
-        \multirow{2}{*}{$n$} & \multicolumn{2}{c}{\emph{Salix}-galler} & \multicolumn{2}{c}{galler-natural enemy}\\
-         & Lower bound & Upper bound & Lower bound & Upper bound \\
-        \hline
-        0   & 0.013 & 0.049 & 5.39 $\times10^{-4}$ & 0.304 \\
-        1   & 0.013 & 0.048 & 4.82 $\times10^{-4}$ & 0.276 \\
-        2   & 0.013 & 0.048 & 4.35 $\times10^{-4}$ & 0.253 \\
-        5   & 0.012 & 0.048 & 3.37 $\times10^{-4}$ & 0.203 \\
-        10  & 0.012 & 0.047 & 2.45 $\times10^{-4}$ & 0.152 \\
-        15  & 0.012 & 0.046 & 1.93 $\times10^{-4}$ & 0.121 \\
-        20  & 0.012 & 0.046 & 1.59 $\times10^{-4}$ & 0.101 \\
-        25  & 0.012 & 0.045 & 1.35 $\times10^{-4}$ & 0.087 \\
-        50  & 0.011 & 0.042 & 7.72 $\times10^{-5}$ & 0.050 \\
-        100 & 0.010 & 0.037 & 4.16 $\times10^{-5}$ & 0.027 \\
-        150 & 0.009 & 0.033 & 2.84 $\times10^{-5}$ & 0.019 \\
-        200 & 0.008 & 0.030 & 2.16 $\times10^{-5}$ & 0.014 \\
-        \hline
-        374 & 0.006 & 0.022 & 1.18 $\times10^{-5}$ & 0.008 \\
-        \hline
-        \end{tabular}
-      \end{table}
-
-\clearpage
-
 \section*{Appendix S6: Obtaining prior interaction probabilities}
@@
 
-\section*{Appendix S7: Calculating posterior distributions and confidence intervals}
+\section*{Appendix S7: R code for calculating posterior distributions and confidence intervals}
 
@@
 
+\section*{Appendix S8: Calculating the credible interval around a probability estimate}
+
+  Here we describe the derivation of the Clopper-Pearson credible interval for the estimated probability of interaction $\lambda$ of a pair of species observed co-occurring $n$ times and interacting $k$ times.
+As we are most interested in the probability of interaction between species pairs that have never been observed co-occurring, we consider only the case where $k=0$ over a variety of $n$.
+This is straightforward to do in R (see the function ``credible\_interval" in \emph{Appendix S7}).
+
+  First, we must obtain the $\alpha$ and $\beta$ parameters for the prior distribution.
+In this study we obtained these parameters using the R~\citep{R} function fitdist from the package fitdistrplus~\citep{fitdistrplus}.
+Once $\alpha$ and $\beta$ are known, we can update them using our observed data.
+Specifically, we are interested in $\alpha'=\alpha+k$ and $\beta'=\beta+n-k$.
+These parameters can then be used to calculate a credible interval using the R~\citep{R} function qbeta.
+In the table below, we present the 95\% credible intervals for \emph{Salix}-galler and galler-natural enemy pairs with different numbers of observed co-occurrences ($n$) and no observed interactions ($k=0$), calculated using prior information derived from the Zillis sub-network~\citep{Kopelke2017}.
+
+      % % # R code to make the table:
+      % ns=c(0,1,2,5,10,15,20,25,50,100,150,200,374)
+      % output=matrix(nrow=length(ns),ncol=5)
+      % output[,1]=ns
+      % for(r in 1:nrow(output)){
+      %   interval1=credible_interval(calculate_parameters(sg_int_probs,ns[r],0),0.025,0.975)    
+      %   interval2=credible_interval(calculate_parameters(gp_int_probs,ns[r],0),0.025,0.975)    
+      %   output[r,2:3]=interval1
+      %   output[r,4:5]=interval2
+      % }
+      \medskip
+      \begin{table}
+        \label{credints}
+        \caption{Here we give the lower and upper bounds of 95\% credible intervals for the probability of interaction $\lambda$ between \emph{Salix}-galler or galler-natural enemy pairs that have been observed co-occurring $n$ times but have never been observed interacting.}
+        \begin{tabular}{l  c c  c c }
+        \multirow{2}{*}{$n$} & \multicolumn{2}{c}{\emph{Salix}-galler} & \multicolumn{2}{c}{galler-natural enemy}\\
+         & Lower bound & Upper bound & Lower bound & Upper bound \\
+        \hline
+        0   & 0.013 & 0.049 & 5.39 $\times10^{-4}$ & 0.304 \\
+        1   & 0.013 & 0.048 & 4.82 $\times10^{-4}$ & 0.276 \\
+        2   & 0.013 & 0.048 & 4.35 $\times10^{-4}$ & 0.253 \\
+        5   & 0.012 & 0.048 & 3.37 $\times10^{-4}$ & 0.203 \\
+        10  & 0.012 & 0.047 & 2.45 $\times10^{-4}$ & 0.152 \\
+        15  & 0.012 & 0.046 & 1.93 $\times10^{-4}$ & 0.121 \\
+        20  & 0.012 & 0.046 & 1.59 $\times10^{-4}$ & 0.101 \\
+        25  & 0.012 & 0.045 & 1.35 $\times10^{-4}$ & 0.087 \\
+        50  & 0.011 & 0.042 & 7.72 $\times10^{-5}$ & 0.050 \\
+        100 & 0.010 & 0.037 & 4.16 $\times10^{-5}$ & 0.027 \\
+        150 & 0.009 & 0.033 & 2.84 $\times10^{-5}$ & 0.019 \\
+        200 & 0.008 & 0.030 & 2.16 $\times10^{-5}$ & 0.014 \\
+        \hline
+        374 & 0.006 & 0.022 & 1.18 $\times10^{-5}$ & 0.008 \\
+        \hline
+        \end{tabular}
+      \end{table}
+
+\clearpage
+
   \bibliographystyle{ecol_let} 

### 2018-06-08 manuscript/CI_interactions.tex
Have 30 words to spare now

@@
 
-    Representing an assemblage of species as a network offers a convenient summary of how the community is constructed as networks simultaneously describe species composition and interactions between species.
+    Representing an ecological community as a network offers a convenient summary of how the community is constructed as networks simultaneously describe species composition and interactions between species.
 A tabulation of the nodes (species) and their relative abundances forms the basis for traditional metrics of community composition such as alpha diversity.
-To move from these simpler metrics to a network framework, the tabulation of nodes is combined with interactions (links between nodes) so that networks provide additional, higher-order information on community structure.
+A network framework combines this tabulation of nodes with a list of interactions (links between nodes) so that networks provide additional, higher-order information on community structure.
 Despite this additional information, empirical descriptions of ecological networks are still limited because they are usually considered static representations of the communities they describe.
@@
 
-    The assumption of static communities contrasts significantly with the known stochasticity of ecological communities~\citep{Gotelli2000}.
+    The assumption of static communities contrasts with the known stochasticity of ecological communities~\citep{Gotelli2000}.
 Community composition and species abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a} while interactions vary over space~\citep{Kitching1987,Baiser2012}, time~\citep{Kitching1987,Olesen2011a}, and between individuals~\citep{Pires2011a,Fodrie2015,Novak2015}.
@@
 Early work in this vein includes food-web models using likelihood-based approaches~\citep{Allesina2008} or Gaussian~\citep{Williams2010} or binomial~\citep{Rohr2016} probability functions for each possible interaction.
-These models may include information about species' traits~\citep{Rohr2016} or may attempt to reproduce empirical network structures using a set of simple rules~\citep{Allesina2008,Williams2010}.
+These models may include information about species' traits~\citep{Rohr2016} or attempt to reproduce empirical network structures using a set of simple rules~\citep{Allesina2008,Williams2010}.
 
     Despite these preliminary efforts, we currently lack the quantitative methodology to deal with the uncertainty generated by spatiotemporal variation in ecological interactions and by sampling.
-Even in extremely well-sampled networks, uneven sampling across species (or pairs of species) can lead to the erroneous inference that some species do not interact because they co-occur rarely or have not yet been observed together - even if they do interact when they do co-occur (see Fig.~\ref{histograms} for an example).
+Even in extremely well-sampled networks, uneven sampling across species can lead to the erroneous inference that some species do not interact because they co-occur rarely or have not yet been observed together - even if they do interact when they do co-occur (see Fig.~\ref{histograms} for an example).
 Nearly all network studies will thus neglect some interactions, necessitating an approach that acknowledges this uncertainty.
@@
 
-      To define the problems associated with quantifying ecological interaction networks, we will start from the perspective of an empirical community ecologist faced with the task of describing a previously unknown interaction network.
+      We will start from the perspective of an empirical community ecologist faced with the task of describing a previously unknown interaction network.
 This ecologist will be interested in generating a description of the species/nodes present and the links between them~\citep{Roslin2016}.
@@
 The detection of any interaction is a stochastic process.
-We define three nested levels of uncertainty contributing to this stochasticity: interaction uncertainty, process uncertainty, and detection uncertainty.
+We define three nested levels of uncertainty contributing to this stochasticity: interaction uncertainty, process uncertainty, and detection uncertainty (Fig.~\ref{concept_fig}).
 
@@
 
-          First, and most fundamentally, we may not know whether or not a pair of species have the appropriate characteristics (or traits) to interact.
+          First, and most fundamentally, a pair of species may or may not have the appropriate characteristics (or traits) to interact.
 We define the probability of an interaction $L$ given characteristics $\mathbf{T}$ as $P(L | \mathbf{T})=\lambda$.
@@
          Even when an interaction is feasible, i.e.
-$L=1$, it may still not occur at a given location or moment in time because of local constraints such as inclement weather or the lack of suitable habitat.
+$L=1$, it may still not occur at a given location or moment in time because of local constraints such as inclement weather or unsuitable habitat.
 We define the local realisation of an interaction, $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L=1)=\chi$.
@@
 
-        An observed interaction indicates that an interaction was feasible, occurred at the study site during sampling, and was detectable.
+        An observed interaction indicates that an interaction was feasible, occurred during sampling, and was detectable.
 That is, $L = 1$, $X = 1$, and $D = 1$.
@@
 It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e.
-where the interaction occurred at the location but was not observed, and $X = 0 \cup L =1$, i.e., where the interaction is feasible but did not occur at the local site (Fig.~\ref{concept_fig}).
+where the interaction occurred at the location but was not observed, and $X = 0 \cup L =1$, i.e., where the interaction is feasible but did not occur at the local site (Fig.~\ref{conceptual_fig}).
         % The occurrence of a true absence, our quantity of interest, corresponds to the joint event $L=0 \cup X=1 \cup D=1$ but %% AC: Doesn't a true absence just mean $L=0$ regardless of our ability to detect/local conditions?
-        Using empirical data, however, it is impossible to distinguish between sources of variation.
+        Using empirical data, however, it is impossible to identify the cause of an unobserved interaction.
 An empirical ecologist will measure the marginal probability $P(L) = k/n$, where $k$ is the number of observed interactions and $n$ the number of observed co-occurrences.
-This probability does not contain any information about $D$ or $X$.
-The major question then becomes: how can we reduce the uncertainty around our estimated interaction probability?
+Given this information, the question becomes: how can we reduce the uncertainty around our estimated interaction probability?
 
@@
 
-        When attempting to reduce uncertainty, the obvious rule of thumb is to ``sample more".
+        When attempting to reduce uncertainty, the obvious rule of thumb is ``sample more".
 Increasing sample sizes will reduce uncertainty about the upper bound of the interaction probability and will also increase the probability of detecting unlikely or cryptic interactions (e.g., interactions where $L$=1 but process or detection uncertainty is high).
@@
         An added complication is that increased sampling will not reduce uncertainty evenly across interactions.
-To record an interaction between A and B, we need to identify both partners correctly (a non-trivial problem in many food webs; e.g.~\citealp{Kaartinen2011,Roslin2016}) and be able to resolve all interactions with a similar likelihood.
+To record an interaction between A and B, we need to identify both partners correctly (a non-trivial problem in many food webs; e.g.~\citealp{Kaartinen2011,Roslin2016}).
 For both molecular and rearing techniques, certain types of interactions may go unnoticed due to technical challenges~\citep{Wirta2014}.
@@
 Intensive sampling is, therefore, an important step towards reducing uncertainty in ecological networks but is unlikely to be enough in most cases.
-To supplement repeated and intensive sampling efforts and further reduce uncertainty around unobserved interactions, we suggest researchers use prior information drawn from the same or a similar system.
-Here, we first outline the statistical framework for a Bayesian approach to probabilistic interactions and then demonstrate how to construct such a probabilistic network using an intensively and repeatedly sampled empirical dataset.
+To supplement repeated and intensive sampling efforts and reduce uncertainty around unobserved interactions, we suggest researchers use prior knowledge of the same or similar systems.
+Here, we outline a Bayesian approach to combining repeated sampling and prior knowledge to obtain probabilistic networks.
+We then demonstrate how to construct such a probabilistic network using an intensively and repeatedly sampled empirical dataset.
 Finally, we show how a probabilistic understanding of a network allows us to establish confidence intervals around measures of network structure.
@@
 
-    We are most interested in how to quantify an interaction probability, and its associated uncertainty, for an interaction that has not yet been observed.
-Say a pair of species has been observed co-occurring $n$ times and observed interacting in $k = 0$ cases.
-We want to know the probability $\lambda$ that the species would be observed interacting if not constrained by local conditions, timing, imperfect detection, etc.
+    We are most interested in how to quantify an interaction probability, and its associated uncertainty, for interactions that have not been observed.
+Say a pair of species has been observed co-occurring $n$ times and interacting in $k = 0$ cases.
+We want to know the probability $\lambda$ that the species would be observed interacting if not constrained by local conditions, imperfect detection, etc.
 We can consider the occurrence of an interaction as a Bernoulli trail where the number of successes ($k$) over $n$ trials will follow a binomial distribution (see~\emph{Appendix S1} for a full description of the mathematical framework).
@@
 It is, however, straightforward to compute the confidence interval for the MLE of $\lambda$ using any of several methods, including the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]).
-% The non-point nature of lambda seems like a feature, not a bug.
 
     All of the above methods for estimating the variance of $\lambda$ include the number of samples $n$.
-This means that where the number of samples $n$ is very low, as for rare species, there will be considerable uncertainty around our estimate of $\lambda$.
+This means that where the number of samples $n$ is very low (e.g., for rare species), there will be considerable uncertainty around our estimate of $\lambda$.
 In Fig.~\ref{upper_limits}, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda$ (for true $\lambda = 0$) varies with sample size.
@@
     The Bayesian approach combines the MLE of $\lambda$ described above with a prior distribution and a normaliser to give a posterior distribution.
-For species pairs with a great deal of observed data (high $n$), the posterior distribution will mostly be based on the MLE of $\lambda$.
-Where there is little or no observed data (low $n$), the posterior distribution will reflect our prior knowledge.
 Since $\lambda$ is a probability and bounded between 0 and 1, the most appropriate prior distribution is the beta:
@@
 
-      It is common to preform analyses that require calculating higher-order network properties in interaction networks.
-The fact that the posterior distribution of $\lambda$ follows a beta distribution makes it straightforward to compute moments and other properties needed for this.
+      It is common to perform analyses that require calculating higher-order network properties in interaction networks.
+The fact that the posterior distribution of $\lambda$ follows a beta distribution makes it straightforward to compute moments and other properties needed for these analyses.
 
@@
 These are called hyper parameters.
-The prior may be chosen to be uninformative, if no external information is available, or may draw on information such as distributions of connectance across webs, degree within webs, or a trait-matching function (see \emph{Appendix S2} for details and a simple quantitative example).
+The prior may be chosen to be uninformative, if no external information is available, or may draw on information such as distributions of connectance across webs, degree distributions, or trait-matching functions (see \emph{Appendix S2} for details and a simple quantitative example).
 
@@
 For example, if the focal system is a large network containing many plant species and insects from different families, it is inappropriate to use a prior distribution drawn from a small network describing interactions between different genotypes of a single plant species wtih a set of closely-related insects.
-The similarity of traits for genotypes within a species means that an insect which interacts with one genotype is likely to interact with many others.
-Trait differences between species means that a species-species network will likely contain fewer interactions than a genotype-species network.
-Similarly, highly-aggregated networks containing nodes which represent whole classes or families are likely to have very different structures than networks where most nodes represent single species.
+The similarity of traits across genotypes within a species means that an insect which interacts with one genotype is likely to interact with many others.
+Trait differences between species mean that a species-species network will likely contain fewer interactions than a genotype-species network.
+Similarly, highly-aggregated networks containing nodes which represent whole classes or families are likely to have very different structures than networks where most nodes represent single species as aggregated nodes are likely to have more interaction partners than single species.
 
@@
       The high spatiotemporal resolution and unusally high sampling effort of this dataset make this it particularly well suited for illustrating the difficulties in completely sampling a network.
-To do this, we first compared the frequencies of observed co-occurrences and interactions.
+To show the gaps in sampling, we compared the frequencies of observed co-occurrences and interactions.
 We analysed both the \emph{Salix}-galler and galler-natural enemy components of the network but present only the latter here (see~\emph{Appendix S4} for \emph{Salix}-galler results).
@@
 
-        To obtain the priors based on the Zillis sub-network, we estimated frequencies of interactions based on the normalised degree of each species in each network component
-        (see \emph{Appendix S6} for details and code).
+        To obtain the priors based on the Zillis sub-network, we estimated frequencies of interactions based on the normalised degree of each species in each network component (see \emph{Appendix S6} for details and code).
 Using these prior parameters, we then estimated the posterior distributions of interaction probabilities $\lambda$.
@@
 
-      It is straightforward to compute most network metrics when the different $\lambda$ of the adjacency matrix are known and assumed not to vary~\citep{Poisot2016}.
+      Researchers usually use interaction matrices as a tool to calculate measures of network structure.
+Computing most network metrics is straightforward when the different $\lambda$ of the adjacency matrix are known and assumed not to vary~\citep{Poisot2016}.
 Incorporating variance in $\lambda$ into these calculations, however, is not so easy.
-Computation of these metrics involves non-linear functions, and Jensen's inequality states that the average of a non-linear function of a stochastic variable differs from the function of the average of that variable.
-Any uncertainty in the values of $\lambda$ could therefore bias both the mean and variance of a network metric.
-One way to avoid potentially biased analytical calculation of network properties is to calculate the properties of a suite of simulated networks.
+Computation of these metrics involves non-linear functions.
+By Jensen's inequality, this means that the average of a network metric (a function of stochastic interactions) is not the same as the network metric calculated based on the average interaction probability.
+Any uncertainty in the values of $\lambda$ could bias both the mean and variance of network metrics, giving misleading results.
+One way to avoid this situation is to calculate the properties of a suite of simulated networks.
 
@@
 
-  Most pairs of species (9,794/12,096 galler-natural enemy pairs) are never found co-occurring and, for species that did occur together, the total number of co-occurrences was generally low (mean=3.87, variance=28.8; Fig.~\ref{histograms}A).
+  Most pairs of species (9,794/12,096 galler-natural enemy pairs) were never found co-occurring and, for species that did occur together, the total number of co-occurrences was generally low (mean=3.87; Fig.~\ref{histograms}A).
 The bulk of these co-occurring species pairs were never observed to interact: only 7.76\% of galler-natural enemy pairs were observed interacting.
-Of those pairs that did interact, the incidence of interaction was also low (mean=4.04, variance=29.3; Fig.~\ref{histograms}B).
-Moreover, even when a pair of species was observed to interact, the number of interactions was often lower than the number of co-occurrences (Fig.~\ref{histograms}C).
+Of those pairs that did interact, the incidence of interaction was also low (mean=4.04; Fig.~\ref{histograms}B) and tended to be lower than the number of observed co-occurrences (Fig.~\ref{histograms}C).
 
@@
 Even in the most extensive data set that we could find, there was very little empirical data for each species pair.
-Most pairs of species were not observed co-occurring even once, and less than 10\% of species pairs were observed interacting and no pairs were observed to co-occur frequently enough to reach the threshold for an interaction probability of 0.01.
+Most pairs of species were not observed co-occurring even once, less than 10\% of species pairs were observed interacting, and no pairs were observed to co-occur frequently enough to reach the threshold for an interaction probability of 0.01.
 This suggests that limited sampling is a major source of uncertainty in empirical networks.
 This dataset also illustrates the problem of process uncertainty - pairs of species which were observed to interact did not interact in all of the samples in which they co-occurred.
-This emphasizes the importance of accounting for imperfect detection when analysing empirical networks.
+As such, increasing sampling is likely to add more zeros than ones to an interaction network.
 
-  Using prior knowledge to build a Bayesian distribution for each interaction probability allows us to treat unobserved interactions as less likely to occur while setting appropriate bounds on interaction probabilities between pairs of species which were never observed co-occurring.
-The number of observations required to conclude that an interaction is unfeasible is quite high (tens of observations per species pair); some species pairs are likely to fall short of this even in the highest-quality networks.
-In such cases, an informative prior distribution gives us more reasonable estimates of interaciton probabilities than assuming all unobserved interactions never occur.
-Moreover, interactions involving species entering new ranges due to climate change or introductions are important for a variety of conservation questions.
-A Bayesian approach using a trait-matching model or data from species' current ranges could be useful in anticipating how species will integrate into new communities.
+  Using prior knowledge to build a Bayesian distribution for each interaction probability allows us to set appropriate bounds on interaction probabilities for species which were rarely or never observed co-occurring.
+In such cases, an informative prior distribution gives us more reasonable estimates of interaciton probabilities than assuming all unobserved interactions cannot occur.
+This approach will also be useful when considering interactions involving species entering new ranges due to climate change or introductions.
+Understanding these species' interactions is important for a variety of conservation questions, and a Bayesian approach using a trait-matching model or data from species' current ranges could help us to anticipate how species will integrate into new communities.
 
@@
 
-  Using this framework leads us to offer tangible recommendations for improved descriptors of ecological interactions.
+  Based on the framework described above, we offer some recommendations for improved descriptions of ecological interactions.
 First, sample sizes should be as large as possible in order to reduce detection uncertainty.
-Second, where sampling on the order of 30-50 observations per species pair is not possible (likely the bulk of studies), researchers should acknowledge the varying levels of confidence surrounding interactions between different species pairs.
+Second, where sampling on the order of 30-50 observations per species pair is not possible (i.e., in most cases), researchers should acknowledge the varying levels of confidence surrounding interactions between different species pairs.
 Including the $n$ and $k$ values for each interaction will clearly indicate which unobserved interactions are most likely to be observed with further sampling and which estimates are more reliable.
@@
   \begin{figure}[h!]
+    \caption{Three nested levels of uncertainty mean that the zeros (unobserved interactions) and ones (observed interactions) in an interaction matrix are not equally certain.
+A one indicates an interaction that definitely occurred, while a zero could indicate an interaction that never occurs, an interaction that occurs sometimes but did not occur during sampling, or an interaction that occurred but was not detected.
+If the large rectangle represents the probability space for an interaction, only the shaded areas represent accurate records of the interaction probability.}
+    \label{conceptual_fig}
+    \begin{center}
+    \end{center}
+    \end{figure}
+
+  \begin{figure}[h!]
       \caption{Despite the high levels of replicaiton in our example dataset, most galler-natural enemy pairs were never observed co-occurring, and those that did co-occur were rarely observed interacting.
@@
     \caption{Imperfect detection of interactions increases the number of samples required to be confident that an interaction does not occur.
-Assume that we want to infer the probability of an interaction between two species, $i$ and $j$, and that this interaction is completely impossible (i.e.
-the true $\lambda=0$).
-When estimating $\lambda$, the number of observed interactions will follow a binomial distribution with number of interactions $k$ and number of observations $n$.
-Using this distribution, we can compute the credible interval of the estimated probability $\lambda$.
-A single observation of species co-occurrence reveals very little regarding the probability of the interaction as the credible interval for a pair of species with one observation essentially spans from 0 to 1.
+Assume that two species cannot interact (i.e., $\lambda=0$) and that the number of observed interactions follows a binomial distribution.
+Here we show the upper bound (solid black line) of a 95\% Cloper-Pearson true credible interval for the interaction probability $\lambda$ for a pair of species that has been observed co-occurring $n$ times but never observed interacting ($k = 0$).
 Only with 35 observations will the upper limit of the credible interval be lowered to 0.1 (dashed, red line).
 Thus, adding more observations is useful in controlling uncertainty, but the number of observations added needs to be very high.
-Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true credible interval for $\lambda$ when $k=0$ ($i$ and $j$ have not been observed interacting) for a variety of $n$.
-A threshold interaction probability of 0.1 is indicated by the dashed red line.
 }

### 2018-06-26 manuscript/CI_interactions.tex
adding Tomas comments to main text

@@
 
-\title{A quantitative framework for investigating the reliability of network construction}
+\title{A quantitative framework for investigating the reliability of empirical network construction}
 
@@
 Moreover, finite sampling generates variation in the set of interactions actually observed.
-For interactions that have not been observed, most data sets will not contain enough information to be confident that unobserved interactions truly did not occur.
+For interactions that have not been observed, most data sets will not contain enough information for the ecologist to be confident that unobserved interactions truly did not occur.
     \item Here we develop the conceptual and analytical tools needed to capture uncertainty in the estimation of pairwise interactions.
@@
 We illustrate this framework using the most extensively sampled network to date.
-    \item We found significant uncertainty in estimates for the probability of most pairwise interactions which we could, however, limit with informative priors.
+    \item We found significant uncertainty in estimates for the probability of most pairwise interactions.
+This uncertainty can, however, be constrained with informative priors.
 This uncertainty scaled up to summary measures of network structure such as connectance or nestedness.
-Even with informative priors, our results suggest that the extremely well-sampled network we use as a test case is missing many interactions that may occur rarely or under different local conditions.
-    \item Through these efforts, we demonstrate the utility of our approach and the importance of acknowledging the uncertainty inherent in network studies.
+By using an extremely well-sampled network as a test case, we find that even with informative priors we are likely to miss many interactions that may occur rarely or under different local conditions.
+    \item Overall, we demonstrate the utility of our approach and the importance of acknowledging the uncertainty inherent in network studies and the utility of treating interactions as probabilities in pinpointing areas where more study is needed.
 Most importantly, we stress that networks are best thought of as systems constructed from random variables, the stochastic nature of which must be acknowledged for an accurate representation.
 Doing so will fundamentally change networks analyses and yield greater realism.
-  % Can be up to 350 words for MEE. This is 270 exactly.
+  % Can be up to 350 words for MEE. This is 290 exactly.
 \end{enumerate}
@@
 
-    Representing an ecological community as a network offers a convenient summary of how the community is constructed as networks simultaneously describe species composition and interactions between species.
+    Representing an ecological community as a network offers a convenient summary of how it is constructed since networks simultaneously describe species composition and interactions between species.
 A tabulation of the nodes (species) and their relative abundances forms the basis for traditional metrics of community composition such as alpha diversity.
@@
     The assumption of static communities contrasts with the known stochasticity of ecological communities~\citep{Gotelli2000}.
-Community composition and species abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a} while interactions vary over space~\citep{Kitching1987,Baiser2012}, time~\citep{Kitching1987,Olesen2011a}, and between individuals~\citep{Pires2011a,Fodrie2015,Novak2015}.
+Community composition and species abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}.
+Moreover, interactions vary over space~\citep{Kitching1987,Baiser2012}, time~\citep{Kitching1987,Olesen2011a}, and between individuals~\citep{Pires2011a,Fodrie2015,Novak2015}.
 Moreover, variability in community composition and interactions may or may not be closely related.
@@
     In this study, we formalise the description of interactions between species as probabilities and develop analytical tools to capture the uncertainty in the estimation of these interactions.
-We focus on binary interactions as a first step, but the framework could be expanded to deal with interaction frequencies and strength.
+We focus on binary interactions as a first step, but the framework could later be expanded to deal with interaction frequencies and strength.
 To define the problem, we will first identify the different contributions to the uncertainty of an interaction and discuss the implications of each source of uncertainty for the properties of ecological networks.
@@
     We are most interested in how to quantify an interaction probability, and its associated uncertainty, for interactions that have not been observed.
-Say a pair of species has been observed co-occurring $n$ times and interacting in $k = 0$ cases.
+Assume that a pair of species has been observed co-occurring $n$ times and interacting in $k = 0$ cases.
 We want to know the probability $\lambda$ that the species would be observed interacting if not constrained by local conditions, imperfect detection, etc.
@@
 
-      When using an informative prior, it is important to ensure that the prior accurately reflects the focal  system.
-For example, if the focal system is a large network containing many plant species and insects from different families, it is inappropriate to use a prior distribution drawn from a small network describing interactions between different genotypes of a single plant species wtih a set of closely-related insects.
+      When using an informative prior, it is important to ensure that this prior accurately reflects the focal  system.
+For example, if the focal system is a large network containing many plant species and insects from different families, it is inappropriate to use a prior distribution drawn from a small network describing interactions between different genotypes of a single plant species with a set of closely-related insects.
 The similarity of traits across genotypes within a species means that an insect which interacts with one genotype is likely to interact with many others.
@@
       The choice of prior will depend on the information available.
-In general, it is best to use a prior taken from a similar system.
+In general, it is best to use a prior taken from a similar system as emphasized above.
 If such data are not available, a prior based on many networks systems with a similar level of resolution could be useful, as could a prior based on a preliminary round of sampling (analogous to ``training data").
@@
 
-      We illustrate the process of constructing a Bayesian network using the well-sampled system of willow (\emph{Salix}) species, herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}.
+      To illustrate the process of constructing a Bayesian network, we use the well-sampled system of willow (\emph{Salix}) species, herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}.
 This dataset consists of a single community type sampled across Europe over 29 years and at 374 unique locations.
@@
 
-      The high spatiotemporal resolution and unusally high sampling effort of this dataset make this it particularly well suited for illustrating the difficulties in completely sampling a network.
+      The high spatiotemporal resolution and unusally high sampling effort of this dataset make it particularly well suited for illustrating the difficulties in completely sampling a network.
 To show the gaps in sampling, we compared the frequencies of observed co-occurrences and interactions.
-We analysed both the \emph{Salix}-galler and galler-natural enemy components of the network but present only the latter here (see~\emph{Appendix S4} for \emph{Salix}-galler results).
+We analysed both the \emph{Salix}-galler and galler-natural enemy components of the network but, for brevity, present only the latter here (see~\emph{Appendix S4} for \emph{Salix}-galler results).
 
@@
 
+        To treat each interaction as a Bayesian probability, we will combine the observed data with a distribution based on prior information.
 A strict Bayesian framework requires a prior distribution that does not rely on any information from the study at hand.
@@
 
-        To obtain the priors based on the Zillis sub-network, we estimated frequencies of interactions based on the normalised degree of each species in each network component (see \emph{Appendix S6} for details and code).
+        To obtain priors based on a single sub-network --Zillis in Graub\"{u}nchen, Switzerland-- we estimated frequencies of interactions based on the normalised degree of each species in each network component (see \emph{Appendix S6} for details and code).
 Using these prior parameters, we then estimated the posterior distributions of interaction probabilities $\lambda$.
@@
 Computation of these metrics involves non-linear functions.
-By Jensen's inequality, this means that the average of a network metric (a function of stochastic interactions) is not the same as the network metric calculated based on the average interaction probability.
+By Jensen's inequality~\citep{Jensen1906}, this means that the average of a network metric (a function of stochastic interactions) is not the same as the network metric calculated based on the average interaction probability.
 Any uncertainty in the values of $\lambda$ could bias both the mean and variance of network metrics, giving misleading results.
@@
 When $n = 374$, we obtained a posterior distribution with $\bar\lambda_{ij}$=1.83 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=4.76.
-This distributions is very close to 0 with small variance about $\lambda$; species $i$ and $j$ are extremely unlikely to interact at sites or times not included in our sample.
+This distributions is very close to 0 with small variance about $\lambda$; if species $i$ and $j$ co-occurred 374 times without interacting, they   are extremely unlikely to do so at other sites or times.
 
@@
 To be 95\% confident that the probability of interaction is below 0.1, 0.05, or 0.01 would require 15, 39, and 229 observed co-occurrences, respectively.
+Note that these are relatively large sample sizes compared to currently-available empirical networks~\citep{Morris2014}.
 
-  We found that the connectance, mean links per galler, and mean links per natural enemy were much lower in the observed web (C=0.078, $L_{galler}$=9.99, and $L_{natural enemy}$=7.45, respectively) than in the posterior webs (0.186 $\leq$ C $\leq$ 0.198, 13.4 $\leq L_{galler} \leq$ 14.6, and 23.4 $\leq L_{natural enemy} \leq$ 25.0).
+  Scaling up to network structure, we found that the connectance, mean links per galler, and mean links per natural enemy were much lower in the observed web (C=0.078, $L_{galler}$=9.99, and $L_{natural enemy}$=7.45, respectively) than in the posterior webs (0.186 $\leq$ C $\leq$ 0.198, 13.4 $\leq L_{galler} \leq$ 14.6, and 23.4 $\leq L_{natural enemy} \leq$ 25.0).
 When the detection probability was relatively low (i.e., 50\%), however, the properties of randomised networks became similar to those in the observed webs (Fig.~\ref{posterior_webs}A,B,D).
-Nestedness was higher in the observed network (NODF=6.85) than in the posterior webs (6.31 $\leq NODF \leq$ 6.82; Fig.~\ref{posterior_webs}C); in this case, the stronger the detection filter the farther apart were the observed and posterior webs.
+Nestedness was higher in the observed network (NODF=6.85) than in the posterior webs (6.31 $\leq NODF \leq$ 6.82; Fig.~\ref{posterior_webs}C); in this case, the stronger the detection filter, the farther apart were the observed and posterior webs.
+In general, the observed network is most similar to simulated networks where only half of the plausible links are detected.
 
@@
   Using prior knowledge to build a Bayesian distribution for each interaction probability allows us to set appropriate bounds on interaction probabilities for species which were rarely or never observed co-occurring.
-In such cases, an informative prior distribution gives us more reasonable estimates of interaciton probabilities than assuming all unobserved interactions cannot occur.
+In such cases, an informative prior distribution gives us more reasonable estimates of interacition probabilities than assuming that no unobserved interactions can ever occur.
 This approach will also be useful when considering interactions involving species entering new ranges due to climate change or introductions.
@@
   Our results also demonstrate how incomplete detection of interactions scales up to affect network structure.
-The structure of our well-sampled, replicated observed network is most similar to the structure of networks including only 50\% of the interactions suggested by the posterior distribution of interaction probabilities.
-Acknowledging the uncertainty inherent in a description of a system that is missing up to half of the feasible interactions is vital if we are to compare structures across systems, link structure to stability, etc.
+The structure of the well-sampled network used in our case study is most similar to the structure of simulated networks including only 50\% of the interactions suggested by the posterior distribution of interaction probabilities.
+If our descriptions of empirical systems are missing up to half of the feasible interactions, then it is vital to acknowledge this inherent uncertainty before comparing structures across systems or relating structure to stability.
 
-  Based on the framework described above, we offer some recommendations for improved descriptions of ecological interactions.
+  Based on the framework described above, we can now offer some recommendations for improved descriptions of ecological interactions.
 First, sample sizes should be as large as possible in order to reduce detection uncertainty.
@@
 This will allow us to say whether networks have different structures \emph{and} whether those differences are greater than we would expect given the inherent variability of interactions.
-To facilitate these recommendations, we provide all code used in this paper in the supplementary material.
+To facilitate the practical application of these recommendations, we provide all code used in this paper in the supplementary material.
 
@@
   \begin{figure}[h!]
-      \caption{Despite the high levels of replicaiton in our example dataset, most galler-natural enemy pairs were never observed co-occurring, and those that did co-occur were rarely observed interacting.
+      \caption{Despite the high levels of replication in our empirical dataset, most galler-natural enemy pairs were never observed co-occurring, and those that did co-occur were rarely observed interacting.
 \textbf{A)} Here we show a histogram of the number of pairs of species observed co-occurring at least once; the 9794 galler-enemy pairs that were never observed co-occurring are omitted.

### 2018-06-26 code/figure_generation/simulation_summary_fig.py

@@ -49,41 +49,45 @@ def read_property_lists(propfile):
 def configure_yaxes(prop,graph):
   graph.yaxis.tick.configure(onoff='on',minor_ticks=1,major_size=.5,place='normal',minor_size=.3,major_linewidth=1,minor_linewidth=1)
   if prop=='N_plants':
-    graph.world.ymax=15
+    graph.world.ymax=16
     graph.yaxis.tick.configure(major=3)
     graph.yaxis.label.configure(text="N(plants)",char_size=1,just=2,place='normal')
   elif prop=='N_gallers':
-    graph.world.ymax=20
+    graph.world.ymax=21
     graph.yaxis.tick.configure(major=4)
     graph.yaxis.label.configure(text="N(gallers)",char_size=1,just=2,place='normal')
   elif prop=='C':
-    graph.world.ymax=0.5
-    graph.yaxis.tick.configure(major=0.1)
-    graph.yaxis.ticklabel.configure(prec=1)
+    graph.world.ymax=0.35
+    graph.world.ymin=0.0
+    graph.yaxis.tick.configure(major=0.02)
+    graph.yaxis.ticklabel.configure(prec=2)
     graph.yaxis.label.configure(text="Connectance",char_size=1,just=2,place='normal')
   elif prop=='L_per_plant':
-    graph.world.ymax=20
-    graph.yaxis.tick.configure(major=4)
+    graph.world.ymax=12
+    graph.world.ymin=0
+    graph.yaxis.tick.configure(major=1)
     graph.yaxis.label.configure(text="Links per plant",char_size=1,just=2,place='normal')
   elif prop=='L_per_galler':
-    graph.world.ymax=15
+    graph.world.ymax=9
+    graph.world.ymin=0
     graph.yaxis.tick.configure(major=3)
     graph.yaxis.label.configure(text="Links per galler",char_size=1,just=2,place='normal')
   else:
-    graph.world.ymax=40
-    graph.yaxis.tick.configure(major=10)
+    graph.world.ymax=70
+    graph.world.ymin=0
+    graph.yaxis.tick.configure(major=5)
     graph.yaxis.label.configure(text='NODF',char_size=1,just=2,place='normal')
 
   return graph
 
-def format_graph(graph,prop,nettype,site):
+def format_graph(graph,prop):
   graph.yaxis.bar.linewidth=1
   graph.xaxis.bar.linewidth=1
   graph.frame.linewidth=1
 
[…]

### 2018-06-26 code/nested_variance_example.R

@@ -1,0 +1,60 @@
+
+connectance=.5
+n_plants=15
+n_gallers=20
+links=c(rep(1,connectance*n_plants*n_gallers),rep(0,(1-connectance)*n_plants*n_gallers))
+
+# Some matrices to store 
+A_props=matrix(nrow=100,ncol=3)
+colnames(A_props)=c("L_per_plant","L_per_galler","NODF")
+B_props=matrix(nrow=10000,ncol=6)
+colnames(B_props)=c("N_plants","N_gallers","C","L_per_plant","L_per_galler","NODF")
+C_props=matrix(nrow=1000000,ncol=6)
+colnames(C_props)=c("N_plants","N_gallers","C","L_per_plant","L_per_galler","NODF")
+
+
+# Create a matrix with links randomly assigned to give our desired connectance
+A=matrix(nrow=n_plants,ncol=n_gallers,data=sample(links,replace=FALSE))
+
+# Assume that we have 100 sampling days.
+# The occurrence of each interaction during sampling depends on the process uncertainty of the interaction
+# Assume that process uncertainties are uniformly distributed.
+# The occurrance of an interaction during any sampling day is drawn from 
+# a binomial distribution with n=100, size=
+
+
+
+# Assume that each interaction has a process certainty of 0.8 and we have 100 sampling occasions
+# I.e., the interaction truly occurs during 80% of sampling occasions.
+# Occurrence of the interaction during any sampling day is a binom
+process=0.5
+B=matrix(nrow=n_plants,ncol=n_gallers)
+for(plant in 1:nrow(A)){
+	for(galler in 1:ncol(A)){
+		B[plant,galler]=A[plant,galler]*rbinom(1,1,process)
+	}
+}
+
+
+# Assume that all interactions are detectable in 60% of the samples in which they occur
+# Assume that each pair is observed co-occurring a random number of times between 0 and 100
+# The number of detected interactions is a Bernoulli process depending on the number of 
+# observed co-occurrences
+detection=0.5
+C=matrix(nrow=n_plants,ncol=n_gallers)
+for(plant in 1:nrow(B)){
+	for(galler in 1:ncol(B)){
+		cooccurrences=round(runif(n=1,min=0,max=1))
+		detections_if_occurring=rbinom(1,cooccurrences,detection)
+		if(B[plant,galler]==1 & detections_if_occurring>0){
+			C[plant,galler]=1
+		} else {
[…]

### 2018-06-26 manuscript/CI_interactions.tex

@@
 % \item Abstract word count: 199
-% \item Main text word count: 6482 % Including 18 page numbers.
-% No abstract, acknowledgements, references, table or figure legends.
-Limit is 6000-7000 including figs, tables, references.
-approx.
-10K all in :/
+% \item Main text word count: 7078 % Including 31 page numbers. Limit is 6000-7000 including figs, tables, references. 
 % \end{itemize}
@@
   \begin{figure}[h!]
-    \caption{Using prior distributions based on the galler-natural enemy network sampled at a single site in~\citet{Kopelke2017}, we calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting ($k = 0$).
+    \caption{Using prior distributions based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017}, we calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting ($k = 0$).
     Posterior distributions for $\lambda$ narrow and approach zero as the number of observed co-occurrences ($n$) increases.
@@
   \begin{figure}[h!]
-    \caption{Mean connectance, links per galler, nestedness (NODF), and links per natural enemy for networks assembled using posterior distributions based on a single sub-network in the~\citet{Kopelke2017} dataset (Zillis) occupied a narrow range.
+    \caption{Mean connectance, links per galler, nestedness (NODF), and links per natural enemy for networks assembled using posterior distributions based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017} occupied a narrow range.
 We created 100 ``posterior-sampling" networks and then, for each of these, created 100 ``detection-filter" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network.
@@
 Each point represents the mean (+/- SD) network property (e.g., connectance) obtained from a set of 100 detection-filter networks.
-For each property and both network types, the detection-filter networks cover a broader range of network properties than the posterior-sampling networks.
-The value of each property decreases with the proportion of links included in the detection-filter networks; values in the original web are indicated by dashed lines.}
+The detection-filter networks cover a broader range of network properties than the posterior-sampling networks but the value of each property decreases as the strength of the detection filter increases.
+Values in the original web are indicated by dashed lines.}
     \label{posterior_webs}    

### 2018-06-26 manuscript/supplemental.tex

@@
 
-\title{A quantitative framework for investigating the reliability of network construction: supplemental information}
+\title{A quantitative framework for investigating the reliability of empirical network construction: supplemental information}
 
@@
 
-\section*{Appendix S1: Detailed description of mathematical framework}
+\section*{Appendix S1: Mathematical framework}
 

### 2018-06-26 manuscript/CI_interactions.tex
About 30 words to be removed, got the figure to work

@@
 
-    Representing an ecological community as a network offers a convenient summary of how it is constructed since networks simultaneously describe species composition and interactions between species.
+    Representing an ecological community as a network summarizes both species composition and interactions between species.
 A tabulation of the nodes (species) and their relative abundances forms the basis for traditional metrics of community composition such as alpha diversity.
 A network framework combines this tabulation of nodes with a list of interactions (links between nodes) so that networks provide additional, higher-order information on community structure.
-Despite this additional information, empirical descriptions of ecological networks are still limited because they are usually considered static representations of the communities they describe.
+Despite this additional information, empirical descriptions of ecological networks are usually limited to static representations of the communities they describe.
 That is, whether the network is assembled based on aggregated data, a single intensive ``snapshot" sample, or expert knowledge, interactions are assumed to occur deterministically wherever and whenever the community is observed~\citep{Olesen2011a}.
@@
     The assumption of static communities contrasts with the known stochasticity of ecological communities~\citep{Gotelli2000}.
-Community composition and species abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}.
+Community composition and abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}.
 Moreover, interactions vary over space~\citep{Kitching1987,Baiser2012}, time~\citep{Kitching1987,Olesen2011a}, and between individuals~\citep{Pires2011a,Fodrie2015,Novak2015}.
-Moreover, variability in community composition and interactions may or may not be closely related.
+Worse, variability in community composition and interactions may not be closely related.
 The removal of a species from a site will obviously also remove its interactions but, conversely, the co-occurrence of potentially interacting species does not guarantee that the species will interact at a given place and time.
 Interactions can be lost if the interaction partners remain present but are separated in time or are too rare to detect each other~\citep{Tylianakis2010}.
-Interactions can also fail to occur because of environmental contingencies~\citep{Poisot2015}, or through changes to individual preferences~\citep{Fodrie2015}.
+Interactions can also fail to occur because of environmental contingencies~\citep{Poisot2015}, or because of individual preferences~\citep{Fodrie2015}.
 
-    Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity on network structure (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007}).
+    Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007}).
 An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to document interactions than species~\citep{Poisot2012}.
@@
 
-    Despite these preliminary efforts, we currently lack the quantitative methodology to deal with the uncertainty generated by spatiotemporal variation in ecological interactions and by sampling.
-Even in extremely well-sampled networks, uneven sampling across species can lead to the erroneous inference that some species do not interact because they co-occur rarely or have not yet been observed together - even if they do interact when they do co-occur (see Fig.~\ref{histograms} for an example).
+    Despite these efforts, we currently lack the quantitative methodology to deal with uncertainty generated by spatiotemporal variation in ecological interactions and by limited sampling.
+Even in extremely well-sampled networks, uneven sampling across species can lead to the inference that some species do not interact because they co-occur rarely or have not yet been observed together - even if they do interact when they do co-occur (see Fig.~\ref{histograms}).
 Nearly all network studies will thus neglect some interactions, necessitating an approach that acknowledges this uncertainty.
@@
     In this study, we formalise the description of interactions between species as probabilities and develop analytical tools to capture the uncertainty in the estimation of these interactions.
-We focus on binary interactions as a first step, but the framework could later be expanded to deal with interaction frequencies and strength.
-To define the problem, we will first identify the different contributions to the uncertainty of an interaction and discuss the implications of each source of uncertainty for the properties of ecological networks.
+We focus on binary interactions as a first step, but the framework could be expanded to deal with interaction frequencies or strengths.
+To define the problem, we first identify different contributions to the uncertainty of an interaction and discuss the implications of each source of uncertainty for the properties of ecological networks.
     % Next, we develop an analytical framework to quantify the uncertainty around interactions in an empirical web and, finally, illustrate this framework using an extensively sampled empirical network.
@@
 
-      We will start from the perspective of an empirical community ecologist faced with the task of describing a previously unknown interaction network.
+      We start from the perspective of a community ecologist faced with the task of describing a previously unknown interaction network.
 This ecologist will be interested in generating a description of the species/nodes present and the links between them~\citep{Roslin2016}.
@@
 Nevertheless, every model is imperfect and lacks information that could be used to define constraints on interactions~\citep{Dormann2017}.
-Some interaction uncertainty will remain even using a very good trait-matching model.
+Some interaction uncertainty is therefore inevitable.
 
@@
 
-         Even when an interaction is feasible, i.e.
-$L=1$, it may still not occur at a given location or moment in time because of local constraints such as inclement weather or unsuitable habitat.
+         Even a feasible interaction, i.e.
+$L=1$, still may not occur at a given location or moment in time because of local constraints such as inclement weather or unsuitable habitat.
 We define the local realisation of an interaction, $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L=1)=\chi$.
-This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology describing the contingencies of interactions.
-Phenological matching~\citep{MillerRushing2010,Gezon2016}, species preferences~\citep{Pires2011,Novak2015,Coux2016}, and fear effects of other species~\citep{Luttbeg2005,Wirsing2008} are just some of the factors contributing to variation in the frequency of interactions between a given pair of species.
-Some of the factors leading to process uncertainty can be addressed in mesocosm studies of networks (e.g., environmental conditions can be held stable) or could be included in models along the line of trait-matching models (e.g., phenological matching).
+This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology  on the topic.
+Phenological matching~\citep{MillerRushing2010,Gezon2016}, species preferences~\citep{Pires2011,Novak2015,Coux2016}, and fear effects~\citep{Luttbeg2005,Wirsing2008} are just some of the factors contributing to variation in the frequency of interactions between a given pair of species.
+Some of these factors can be addressed in mesocosm studies of networks (e.g., environmental conditions can be held stable) or could be included in models along the line of trait-matching models (e.g., phenological matching).
 In the field, however, process uncertainty is likely inevitable.
@@
          One proposed solution to the problem of process uncertainty is to use repeated sampling of networks.
-For example,~\citet{Weinstein2017} used repeated sampling rounds to estimate the daily probability of detecting an interaction and thereby model detection and process uncertainty.
+For example,~\citet{Weinstein2017} used repeated sampling to estimate the daily probability of detecting an interaction and thereby model detection and process uncertainty.
 While conceptually attractive, this approach is unsuitable for interactions occurring over longer time scales (e.g., associations between hosts and parasitoids with a single generation per year), or very rare interactions which might not occur on any of the sampling days.
@@
           Lastly, measurement errors are a pervasive source of uncertainty in the observation of ecological processes.
-That is, even if an interaction is feasible and occurs during sampling ($L = 1$ and $X = 1$), we may fail to detect it.
-We may define the probability of detecting of an interaction, $D$, as a stochastic process with the associated probability $P(D|X=1,L=1)=\delta$.
+Even if an interaction is feasible and occurs during sampling ($L = 1$ and $X = 1$), we may still fail to detect it.
+We may define the probability of detecting of an interaction, $D$, given the interaction is feasible and occurs, as a stochastic process with the associated probability $P(D|X=1,L=1)=\delta$.
 Detection failure could happen for many reasons (see~\citet{Wirta2014} for examples and partial solutions to them).
@@
 the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification as in~\citealt{Wirta2014,Frost2016}).
-The impossibility of eliminating detection uncertainty also limits the usefulness of repeated sampling; the absence of an interaction on a given day could either be because it was not feasible [$P(L) = 0$], was feasible but did not occur because of local conditions during sampling ($P(X|L=1) = 0$], or was feasible and occurred during sampling but could not be observed [$P(D|X=1,L=1)=0$].
-From a conceptual perspective, repeated sampling therefore fails to satisfactorily address the uncertainty inherent in empirical networks.
+The absence of an interaction on a given day could therefore be because it was not feasible [$P(L) = 0$], was feasible but did not occur because of local conditions during sampling ($P(X|L=1) = 0$], or was feasible and occurred during sampling but could not be observed [$P(D|X=1,L=1)=0$].
+Because we cannot separate these possibilities, repeated sampling fails to satisfactorily address the uncertainty inherent in empirical networks.
 
@@
 
-        An observed interaction indicates that an interaction was feasible, occurred during sampling, and was detectable.
-That is, $L = 1$, $X = 1$, and $D = 1$.
+        An observed interaction indicates that an interaction was feasible, occurred during sampling, and was detectable ($L = 1$, $X = 1$, and $D = 1$).
 An unobserved interaction could be due to any of the three sources of uncertainty ($D$, $X$, and/or $L = 0$).
-Only the case where $L = 0$ is a true absence of interaction --the usual interpretation of a $0$ value in an interaction matrix.
+Only the case where $L = 0$ is an interaction that never occurs --the usual interpretation of a $0$ value in an interaction matrix.
 It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e.
@@
         % The occurrence of a true absence, our quantity of interest, corresponds to the joint event $L=0 \cup X=1 \cup D=1$ but %% AC: Doesn't a true absence just mean $L=0$ regardless of our ability to detect/local conditions?
-        Using empirical data, however, it is impossible to identify the cause of an unobserved interaction.
-An empirical ecologist will measure the marginal probability $P(L) = k/n$, where $k$ is the number of observed interactions and $n$ the number of observed co-occurrences.
+        This is not possible, however, using empirical data.
+An empirical ecologist will instead measure the marginal probability $P(L) = k/n$, where $k$ is the number of observed interactions and $n$ the number of observed co-occurrences.
 Given this information, the question becomes: how can we reduce the uncertainty around our estimated interaction probability?
@@
 
-        When attempting to reduce uncertainty, the obvious rule of thumb is ``sample more".
+        The obvious rule of thumb to reduce uncertainty is ``sample more".
 Increasing sample sizes will reduce uncertainty about the upper bound of the interaction probability and will also increase the probability of detecting unlikely or cryptic interactions (e.g., interactions where $L$=1 but process or detection uncertainty is high).
@@
 Intensive sampling is, therefore, an important step towards reducing uncertainty in ecological networks but is unlikely to be enough in most cases.
-To supplement repeated and intensive sampling efforts and reduce uncertainty around unobserved interactions, we suggest researchers use prior knowledge of the same or similar systems.
-Here, we outline a Bayesian approach to combining repeated sampling and prior knowledge to obtain probabilistic networks.
+To supplement repeated sampling efforts and reduce uncertainty around unobserved interactions, we suggest researchers use prior knowledge of the same or similar systems.
+Here, we outline a Bayesian approach to combining repeated sampling and prior knowledge in probabilistic networks.
 We then demonstrate how to construct such a probabilistic network using an intensively and repeatedly sampled empirical dataset.
@@
 
-\section*{Boxes and figures}
+\section*{Figures}
 
@@
 
-\clearpage
+% \clearpage
 
   \begin{figure}[h!]
-    \caption{Three nested levels of uncertainty mean that the zeros (unobserved interactions) and ones (observed interactions) in an interaction matrix are not equally certain.
-A one indicates an interaction that definitely occurred, while a zero could indicate an interaction that never occurs, an interaction that occurs sometimes but did not occur during sampling, or an interaction that occurred but was not detected.
-If the large rectangle represents the probability space for an interaction, only the shaded areas represent accurate records of the interaction probability.}
+    \caption{Three nested levels of uncertainty mean that an observed interaction matrix is unlikely to capture all of the interactions that can really occur at a site.
+Beginning with a true interaction matrix (top left) of zeros (interactions that cannot occur, white) and ones (interactions that do occur, black), each level of uncertainty adds more zeros.
+Interaction uncertainty refers to the fact that some interactions are more likely than others based on species' traits.
+For example, lions are less likely to predate upon elephants than zebras.
+If our trait model is incomplete (e.g., if we neglect group hunting in lions), we might assume that elephants are too large to ever be prey for lions.
+Process uncertainty further reduces the probability of observing an interaction as not every interaction occurs during each sampling period.
+We show six example interaction matrices representing interactions observed over two days at three sites.
+The probability of observing an interaction now reflects the rarity of each interaction occurring during a given sampling day.
+Detection uncertainty reflects the fact that not all interactions are equally detectable.
+For example, rare species may be hard to find and follow in the field.
+After applying these three layers of uncertainty, some of the interactions which truly occur are very unlikely to be observed.
+An observed matrix sampled based on this matrix (lower left) is likely to contain far fewer interactions than the original, true matrix.}
     \label{conceptual_fig}
     \begin{center}
+    \includegraphics*[height=.6\textheight]{figures/conceptual_fig.eps}
     \end{center}
@@
   \begin{figure}[h!]
-      \caption{Despite the high levels of replication in our empirical dataset, most galler-natural enemy pairs were never observed co-occurring, and those that did co-occur were rarely observed interacting.
-\textbf{A)} Here we show a histogram of the number of pairs of species observed co-occurring at least once; the 9794 galler-enemy pairs that were never observed co-occurring are omitted.
+      \caption{Despite the replication in our empirical dataset, most galler-natural enemy pairs were never observed co-occurring and those that did co-occur rarely interacted.
+\textbf{A)} Here we show a histogram of the number of pairs of species observed co-occurring at least once.
+9794 galler-enemy pairs were never observed co-occurring (not shown).
       \textbf{B)} Here we show a histogram of the number of observed interactions within pairs of co-occurring species. Species which co-occurred but never interacted are included. 
@@
 Assume that two species cannot interact (i.e., $\lambda=0$) and that the number of observed interactions follows a binomial distribution.
-Here we show the upper bound (solid black line) of a 95\% Cloper-Pearson true credible interval for the interaction probability $\lambda$ for a pair of species that has been observed co-occurring $n$ times but never observed interacting ($k = 0$).
-Only with 35 observations will the upper limit of the credible interval be lowered to 0.1 (dashed, red line).
-Thus, adding more observations is useful in controlling uncertainty, but the number of observations added needs to be very high.
+Here we show the upper bound (solid black line) of a 95\% Cloper-Pearson true credible interval for the interaction probability $\lambda$ for a pair of species that has been observed co-occurring $n$ times but never interacting ($k = 0$).
+The upper limit of the credible interval only reaches 0.1 (dashed, red line) with 35 observations.
+Thus, adding more observations is useful in controlling uncertainty, but the number of observations added must be very high.
 }
@@
     \caption{Using prior distributions based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017}, we calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting ($k = 0$).
-    Posterior distributions for $\lambda$ narrow and approach zero as the number of observed co-occurrences ($n$) increases.
-Likewise, the maximum likelihood estimator for the mean probability of interaction (diamonds at top of each panel) approaches zero and the 95\% credible interval (lines at top of each panel) narrows as sample size increases.
+    Posterior distributions (curves) and 95\% credible intervals (lines at top of panell) for $\lambda$ narrow and approach zero as the number of observed co-occurrences ($n$) increases.
+Diamonds indicate the maximum likelihood estimator for the mean probability of interaction.
     Dashed lines indicate threshold probabilities of 0.01, 0.05, and 0.1.
@@
     \caption{Mean connectance, links per galler, nestedness (NODF), and links per natural enemy for networks assembled using posterior distributions based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017} occupied a narrow range.
-We created 100 ``posterior-sampling" networks and then, for each of these, created 100 ``detection-filter" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network.
+To obtain distributions of network properties, we created 100 ``posterior-sampling" networks and then, for each of these, created 100 ``detection-filter" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network.
 This simulates imperfect detection of interactions in the field.

### 2018-06-27 manuscript/supplemental.tex
Tomas comments to supplemental

@@
 
+    To create Bayesian distributions for the probability of interactions, we must begin with a prior distribution.
+This distribution reflects our prior knowledge (or lack thereof) about the likelihood of a given interaction.
+Priors may be selected to be uninformative, so as not to bias the posterior distribution in any particular direction, or may be informative and based on some prior knowledge about the system.
+
     \subsection*{Uninformative prior}
@@
       (1982-2010) at 374 unique locations across Europe ranging from Sicily to 
-      the Arctic. Including repeated visits to a number of sites, the data set 
+      the Arctic. Since the dataset includes repeated visits to a number of sites, the data set 
       contains 641 site-visits. Here we take the more conservative approach and pool visits to the same site for a sample size of 374 sub-networks.
@@
 
-      As with the galler-natural enemy component, we estimated frequencies of \emph{Salix}-galler interactions based on the normalised degree of each species (\emph{Appendix S6}).
+      As with the galler-natural enemy component (presented in the main text), we estimated frequencies of \emph{Salix}-galler interactions based on the normalised degree of each species (\emph{Appendix S6}).
 We obtained prior parameters of $\alpha$=8.72, $\beta$=305 for the \emph{Salix}-galler component.
@@
 The distribution narrows and approaches zero as the sample size increases.
-Likewise, the maximum likelihood estimator for the mean probability of interaction (diamonds at top of each panel) approaches zero and the 95\% credible interval (lines at top of each panel) narrows as sample size increases.
+Likewise, the maximum likelihood estimator for the mean probability of interaction (diamonds at top) approaches zero and the 95\% credible interval (lines at top) narrows as sample size increases.
 Dashed lines indicate threshold probabilities of 0.1, 0.05, and 0.01.}

### 2018-06-27 manuscript/CI_interactions.tex
Think I just need to fine-tune that figureg

@@
 
-    Note that $\lambda$ is not a single point estimate but rather a random variable with an unknown distribution.
+    Note that $\lambda$ is not a point estimate but rather a random variable with an unknown distribution.
 This means that if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact.
@@
 
-      When using an informative prior, it is important to ensure that this prior accurately reflects the focal  system.
-For example, if the focal system is a large network containing many plant species and insects from different families, it is inappropriate to use a prior distribution drawn from a small network describing interactions between different genotypes of a single plant species with a set of closely-related insects.
+      It is important to ensure that an informative prior accurately reflects the focal  system.
+For example, if the system is a large network containing many plant species and insects from different families, it is inappropriate to use a prior distribution drawn from a small network describing interactions between different genotypes of a single plant species and a set of closely-related insects.
 The similarity of traits across genotypes within a species means that an insect which interacts with one genotype is likely to interact with many others.
@@
 In general, it is best to use a prior taken from a similar system as emphasized above.
-If such data are not available, a prior based on many networks systems with a similar level of resolution could be useful, as could a prior based on a preliminary round of sampling (analogous to ``training data").
+If such data are not available, a prior based on many networks with a similar level of resolution could be useful, as could a prior based on a preliminary round of sampling (analogous to ``training data").
 If there is no suitable informative prior, it is best to use an explicitly uninformative prior.
@@
 
-      To illustrate the process of constructing a Bayesian network, we use the well-sampled system of willow (\emph{Salix}) species, herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}.
+      To illustrate the process of constructing a Bayesian network, we use the well-sampled system of willows (\emph{Salix}), herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}.
 This dataset consists of a single community type sampled across Europe over 29 years and at 374 unique locations.
@@
 
-      The high spatiotemporal resolution and unusally high sampling effort of this dataset make it particularly well suited for illustrating the difficulties in completely sampling a network.
+      The high spatiotemporal resolution and unusally high sampling effort of this dataset make it well suited for illustrating the difficulties in completely sampling a network.
 To show the gaps in sampling, we compared the frequencies of observed co-occurrences and interactions.
@@
 For species where $n>0$, we can update the prior distribution with data.
-If we consider only pairs of species which were observed to co-occur but not to interact, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs.
+If we consider only pairs of species which were observed co-occurring but not interacting, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs.
 This gives $\alpha'$=$\alpha$ and $\beta'$=$\beta + n_{ij}$.
@@
 By Jensen's inequality~\citep{Jensen1906}, this means that the average of a network metric (a function of stochastic interactions) is not the same as the network metric calculated based on the average interaction probability.
-Any uncertainty in the values of $\lambda$ could bias both the mean and variance of network metrics, giving misleading results.
+Any uncertainty in the values of $\lambda$ could bias both the mean and variance of network metrics, giving misleading results (simulated in \emph{Appendix S8}).
 One way to avoid this situation is to calculate the properties of a suite of simulated networks.
@@
 
-  Most pairs of species (9,794/12,096 galler-natural enemy pairs) were never found co-occurring and, for species that did occur together, the total number of co-occurrences was generally low (mean=3.87; Fig.~\ref{histograms}A).
-The bulk of these co-occurring species pairs were never observed to interact: only 7.76\% of galler-natural enemy pairs were observed interacting.
-Of those pairs that did interact, the incidence of interaction was also low (mean=4.04; Fig.~\ref{histograms}B) and tended to be lower than the number of observed co-occurrences (Fig.~\ref{histograms}C).
+  Most pairs of species (9,794/12,096) never co-occurred and, for species that did occur together, the total number of co-occurrences was generally low (mean=3.87; Fig.~\ref{histograms}A).
+The bulk (92.24\%) of these co-occurring species pairs were never observed interacting.
+Of those pairs that did interact, the incidence of interaction was also low (mean=4.04; Fig.~\ref{histograms}B) and was lower than the number of observed co-occurrences (Fig.~\ref{histograms}C).
 
@@
 
-  For most pairs of species $i$ and $j$, however, $n_{ij}$ was much less than 374 and our posterior mean and variance therefore retain more of the influence of the prior.
-We can see this in the increasing means and variances as we decrease $n_{ij}$ (Fig.~\ref{Salix_pdfs_cdfs};~\emph{Appendix S8}).
-The number of samples required to be 95\% confident that the interaction probability between galler and natural enemy species is below a threshold increases quickly as the threshold decreases (Fig.~\ref{Salix_pdfs_cdfs};~\emph{Appendix S8}).
+  For most pairs of species $i$ and $j$, $n_{ij}$ was much less than 374 and our posterior mean and variance therefore retain more of the influence of the prior.
+We can see this in the increasing means and variances as we decrease $n_{ij}$ (Fig.~\ref{Salix_pdfs_cdfs};~\emph{Appendix S9}).
 To be 95\% confident that the probability of interaction is below 0.1, 0.05, or 0.01 would require 15, 39, and 229 observed co-occurrences, respectively.
@@
 
-  Scaling up to network structure, we found that the connectance, mean links per galler, and mean links per natural enemy were much lower in the observed web (C=0.078, $L_{galler}$=9.99, and $L_{natural enemy}$=7.45, respectively) than in the posterior webs (0.186 $\leq$ C $\leq$ 0.198, 13.4 $\leq L_{galler} \leq$ 14.6, and 23.4 $\leq L_{natural enemy} \leq$ 25.0).
+  Scaling up to network structure, we found that the connectance and mean links per galler and natural enemy were much lower in the observed web (C=0.078, $L_{galler}$=9.99, and $L_{natural enemy}$=7.45, respectively) than in the posterior webs (0.186 $\leq$ C $\leq$ 0.198, 13.4 $\leq L_{galler} \leq$ 14.6, and 23.4 $\leq L_{natural enemy} \leq$ 25.0).
 When the detection probability was relatively low (i.e., 50\%), however, the properties of randomised networks became similar to those in the observed webs (Fig.~\ref{posterior_webs}A,B,D).
@@
 Even in the most extensive data set that we could find, there was very little empirical data for each species pair.
-Most pairs of species were not observed co-occurring even once, less than 10\% of species pairs were observed interacting, and no pairs were observed to co-occur frequently enough to reach the threshold for an interaction probability of 0.01.
+Most pairs of species were not observed co-occurring even once, less than 10\% of species pairs were observed interacting, and no pairs were observed to co-occur frequently enough to conclude that their probability of interacting was below 0.01.
 This suggests that limited sampling is a major source of uncertainty in empirical networks.
-This dataset also illustrates the problem of process uncertainty - pairs of species which were observed to interact did not interact in all of the samples in which they co-occurred.
-As such, increasing sampling is likely to add more zeros than ones to an interaction network.
+This dataset also illustrates the problem of process uncertainty - pairs of species which were observed interacting did not interact in all of the samples in which they co-occurred.
+Increasing sampling is therefore likely to add more zeros than ones to an interaction network.
 
   Using prior knowledge to build a Bayesian distribution for each interaction probability allows us to set appropriate bounds on interaction probabilities for species which were rarely or never observed co-occurring.
-In such cases, an informative prior distribution gives us more reasonable estimates of interacition probabilities than assuming that no unobserved interactions can ever occur.
-This approach will also be useful when considering interactions involving species entering new ranges due to climate change or introductions.
+In such cases, an informative prior distribution gives us more reasonable estimates of interaction probabilities than assuming that $p$=0 for unobserved interactions.
+This approach is particularly useful when considering interactions involving species entering new ranges due to climate change or introductions.
 Understanding these species' interactions is important for a variety of conservation questions, and a Bayesian approach using a trait-matching model or data from species' current ranges could help us to anticipate how species will integrate into new communities.
@@
 Re-sampling networks based on a probabilistic understanding of networks is straightforward and gives distributions for network properties rather than point estimates.
-This not only acknowledges the fact that interactions vary over time and space but will also facilitate comparisons between networks by adding confidence intervals to estimates of network properties.
+This not only acknowledges the fact that interactions vary over time and space but will also facilitate comparisons between networks by adding confidence intervals to ezostimates of network properties.
 This will allow us to say whether networks have different structures \emph{and} whether those differences are greater than we would expect given the inherent variability of interactions.
@@
     \caption{Three nested levels of uncertainty mean that an observed interaction matrix is unlikely to capture all of the interactions that can really occur at a site.
-Beginning with a true interaction matrix (top left) of zeros (interactions that cannot occur, white) and ones (interactions that do occur, black), each level of uncertainty adds more zeros.
-Interaction uncertainty refers to the fact that some interactions are more likely than others based on species' traits.
+Interaction uncertainty means that some inteactions that truly occur (black squares in True matrix) are less likely than others (grey squares) based on species traits.
 For example, lions are less likely to predate upon elephants than zebras.
-If our trait model is incomplete (e.g., if we neglect group hunting in lions), we might assume that elephants are too large to ever be prey for lions.
-Process uncertainty further reduces the probability of observing an interaction as not every interaction occurs during each sampling period.
-We show six example interaction matrices representing interactions observed over two days at three sites.
-The probability of observing an interaction now reflects the rarity of each interaction occurring during a given sampling day.
-Detection uncertainty reflects the fact that not all interactions are equally detectable.
-For example, rare species may be hard to find and follow in the field.
-After applying these three layers of uncertainty, some of the interactions which truly occur are very unlikely to be observed.
-An observed matrix sampled based on this matrix (lower left) is likely to contain far fewer interactions than the original, true matrix.}
+If our trait model is incomplete (e.g., if we neglect group hunting in lions), we might assume that elephants are too large to ever be prey for lions and assign this interaction a probability of 0.\\
+    Process uncertainty describes the fact that interactions occur with different probabilities during any given sample.
+We show six example networks representing interactions observed over two days at three sites.
+Interactions which occur during fewer sampling days are less likely to be observed.\\
+    Detection uncertainty reflects the fact that not all interactions are equally detectable. For example, interactions involving cryptic species are less likely to be seen.\\
+    After applying these three layers of uncertainty, some interactions which truly occur are very unlikely to be observed.
+An observed matrix sampled based on this matrix (lower left) is thus likely to contain far fewer interactions than the original, true matrix.}
     \label{conceptual_fig}
     \begin{center}
-    \includegraphics*[height=.6\textheight]{figures/conceptual_fig.eps}
+    % \includegraphics*[height=.5\textheight]{figures/conceptual_fig.eps}
     \end{center}
@@
       \begin{center}
-      \includegraphics*[height=.6\textheight]{figures/GP_histogram.eps}
+      % \includegraphics*[height=.6\textheight]{figures/GP_histogram.eps}
       \end{center}
@@
   \begin{figure}[h!]
-    \caption{Imperfect detection of interactions increases the number of samples required to be confident that an interaction does not occur.
+    \caption{Imperfect detection of interactions increases the number of samples required to be confident that an interaction never occurs.
 Assume that two species cannot interact (i.e., $\lambda=0$) and that the number of observed interactions follows a binomial distribution.
@@
     \begin{center}
-    \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
+    % \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
     \end{center}
@@
     \begin{center}
-    \includegraphics*[width=.8\textwidth]{figures/GP_pdfs_increasing_N_Zillis.eps}
+    % \includegraphics*[width=.8\textwidth]{figures/GP_pdfs_increasing_N_Zillis.eps}
     \end{center}
@@
     \begin{center}
-    \includegraphics[width=.8\textwidth]{figures/GP_posterior_properties_Zillis.eps}
+    % \includegraphics[width=.8\textwidth]{figures/GP_posterior_properties_Zillis.eps}
     \end{center}

### 2018-06-27 manuscript/supplemental.tex
Think I just need to fine-tune that figureg

@@
 
-\section*{Appendix S8: Calculating the credible interval around a probability estimate}
+\section*{Appendix S8: Simulating the effects of uncertainty on network structure}
+
+  To demonstrate the effects of nested interaction, process, and detection uncertainty on network structure, we can observe how the structure of randomly-generated networks changes as we add layers of uncertainty.
+We began by constructing 100 "true" networks with 50 plant species, 50 galler species, and a connectance of 0.1.
+We ensured that each network had at least one link per plant and per galler.
+For each network, we calculated the mean number of links per plant, mean number of links per galler, and nestedness (NODF) as described in the main text.
+For simplicity, we assume that there is no interaction uncertainty in this system (i.e., all interactions are either 100\% feasible or 100\% infeasible based on species' traits).
+
+  Taking each "true" network as a starting point, we then applied process uncertainty.
+The probability $p$ of the occurrance of each interaction on a given sampling day was assigned a random probability drawn from the uniform distribution.
+As the probability that an interaction will occur during sampling also depends on the probability of the two species co-occurring, we also assigned a random number of sampling days on which each species co-occurred.
+The number of co-occurrances, $n$, was drawn from a uniform distribution and could be any integer between 0 and 30 (our simulated number of sampling days), inclusive.
+The number of occurrances, $k$, of each interaction was then drawn from a binomial distribution based on $n$ and $p$.
+If the number of occurrances during sampling was greater than 0 and the interaction occurred in the true network, we included the interaction in the "process-filtered" network.
+As the inclusion of interactions in the process matrices is random, we created 100 process-filtered networks for each true network.
+For each network, we calculated the number of plants and gallers (after removing any species with no interactions), mean links per plant and per galler, connectance, and NODF.
+
+  Next, we applied a layer of detection uncertainty to create "detection-filtered" networks.
+As with the process-filtered networks, we randomly selected the number of times each species co-occurred, $n$, from a uniform distribution.
+We also randomly selected the probability, $p$, of detecting each interaction.
+To reflect the fact that some interactions are easy to observe but many will be more difficult (because one or both interaction partners are rare, cryptic, or difficult to rear in the lab), we drew $p$ from a beta distribution with shape parameters 2 and 10.
+We created 100 detection-filtered networks for each process-filtered network (10000 per true network).
+For each network, we calculated the number of plants and gallers (after removing any species with no interactions), mean links per plant and per galler, connectance, and NODF.
+Code used in this simulation example is contained in the file \emph{simulation_example.R}, uploaded separately.
+
+  With each additional layer of uncertainty, the number of plants and gallers included in the web decreased (state means here).
+The connectance and number of links per plant and per galler decreased significantly at each level (Fig.~\ref{sim_props}A,B,D).
+The effects of uncertainty on nestedness were less predictable.
+The process-filtered networks were significantly less nested than the original networks, but the variation in the detection-filtered webs was so great that there were no significant differences between the original and detection-filtered networks (Fig.~\ref{sim_props}C).
+This simulation demonstrates the fact that process and detection uncertainty mean that we are very unlikely to observe all of the interactions that can truly occur in a system, as well as the sometimes unpredictable effects this uncertainty can have on higher-order structures such as nestedness.
+
+  Note that this simulation uses several simplifying assumptions.
+For instance, we treat interactions as independent and ignore the possibility for, for example, competition between gallers.
+A thorough exploration of the effects of interaction contingency, different distributions of co-occurrences, etc.
+would be an interesting topic for future work but is beyond the scope of the current study.
+We also neglect interaction uncertainty in this example.
+Interaction uncertainty could be included by, for example, modelling interactions between individuals of each species.
+In this framework, individuals could vary in some trait (e.g., body size) that affects the interactions in which they participate.
+Very small or very large individuals might not participate in some interactions that are feasbile for most members of the species.
+
+  \begin{figure}
+  \label{sim_props}
+  \caption{We created 100 random networks containing 50 plants and 50 gallers, with a connectance of 0.1.
+For each of these "original" networks, we created 100 process-filtered ("process") networks incorporating uncertainty around the occurrance of each interaction during sampling.
+For each "process" network, we further created 100 detection-filtered ("detection") networks incorporating uncertainty around the detection of each interaction.
+For each network, we show the mean (+/- SD) connectance, links per plant, nestedness (NODF), and links per galler.}
+  \begin{center}
+  \includegraphics*[width=\textwidth]{figures/simulation_example.eps}
+  \end{center}
+  \end{figure}
+
+\clearpage
+
+\section*{Appendix S9: Calculating the credible interval around a probability estimate}
 

### 2018-06-27 code/figure_generation/simulation_summary_fig.py

@@ -32,9 +32,9 @@ def read_property_lists(propfile):
         prop_dict["N_gallers"].append(float(line.split()[2]))
         prop_dict["C"].append((float(line.split()[3])))
       else:
-        prop_dict["N_plants"].append(15)
-        prop_dict["N_gallers"].append(20)
-        prop_dict["C"].append(0.5)
+        prop_dict["N_plants"].append(50)
+        prop_dict["N_gallers"].append(50)
+        prop_dict["C"].append(0.1)
       prop_dict["L_per_plant"].append(float(line.split()[-3]))
       prop_dict["L_per_galler"].append(float(line.split()[-2]))
       prop_dict["NODF"].append(float(line.split()[-1]))
@@ -57,25 +57,25 @@ def configure_yaxes(prop,graph):
     graph.yaxis.tick.configure(major=4)
     graph.yaxis.label.configure(text="N(gallers)",char_size=1,just=2,place='normal')
   elif prop=='C':
-    graph.world.ymax=0.35
-    graph.world.ymin=0.0
-    graph.yaxis.tick.configure(major=0.02)
+    graph.world.ymax=0.105
+    graph.world.ymin=0.06
+    graph.yaxis.tick.configure(major=0.01)
     graph.yaxis.ticklabel.configure(prec=2)
     graph.yaxis.label.configure(text="Connectance",char_size=1,just=2,place='normal')
   elif prop=='L_per_plant':
-    graph.world.ymax=12
-    graph.world.ymin=0
+    graph.world.ymax=6
+    graph.world.ymin=2
     graph.yaxis.tick.configure(major=1)
     graph.yaxis.label.configure(text="Links per plant",char_size=1,just=2,place='normal')
   elif prop=='L_per_galler':
-    graph.world.ymax=9
-    graph.world.ymin=0
-    graph.yaxis.tick.configure(major=3)
+    graph.world.ymax=6
+    graph.world.ymin=2
+    graph.yaxis.tick.configure(major=1)
     graph.yaxis.label.configure(text="Links per galler",char_size=1,just=2,place='normal')
   else:
-    graph.world.ymax=70
+    graph.world.ymax=40
     graph.world.ymin=0
-    graph.yaxis.tick.configure(major=5)
+    graph.yaxis.tick.configure(major=10)
     graph.yaxis.label.configure(text='NODF',char_size=1,just=2,place='normal')
 
   return graph
[…]

### 2018-06-27 manuscript/coverletter.tex
draft coverletter

@@
 
-\begin{letter}{\bf Professor Tim Coulson\\
-               Editor-in-Chief, Ecology Letters\\
-               Department of Zoology\\
-               University of Oxford\\
-               Oxford OX1 3PS, UK
+\begin{letter}{\bf Professor Rob Freckleton\\
+               Executive Editor, Methods in Ecology and Evolution\\
+               Department of Animal and Plant Sciences\\
+               University of Sheffield\\
+               Sheffield S10 2TN, UK
                                }
@@
 
-\opening{Dear Prof. Coulson:}
+\opening{Dear Prof. Freckleton:}
 
-    My co-authors and I are pleased to submit the attached manuscript \emph{A quantitative framework for investigating the reliability of network construction} for consideration as a Novel Methods paper in \textbf{Ecology Letters} as per our previous correspondence with Senior Editor John Drake.
-As instructed, we have submitted the manuscript under the Ideas \& Perspectives mechanism (and following the associated formatting guidelines).
+    My co-authors and I are pleased to submit the attached manuscript \emph{A quantitative framework for investigating the reliability of emprical network construction} for consideration as a research article in \textbf{Methods in Ecology and Evolution}.
+The goals of this manuscript are A) to illustrate the extreme difficulty in fully sampling the set of interactions occurring within a community, B) to demonstrate the construction of networks treating each interaction probabilistically (based on prior information as well as available data), and C) to offer concrete recommendations that will facilitate the use of this framework in future work.
 
-    We begin the manuscript by reviewing the many sources of variation inherent in ecological networks.
-Some sources of variation can be reduced through improved sampling, but others are intrinsic properties of ecological communities.
-This uncertainty limits the accuracy of network studies which consider communities as static, invariant entities and demonstrates the need for descriptions of network structure that acknowledge and address the uncertainty surrounding estimates of interspecific interactions.
+    We argue that, because of multiple levels of uncertainty surrounding interactions between species, the set of observed interactions will almost certainly be a subset of the interactions that can occur in a community.
+Some interactions may be rare because of species traits (e.g., prey that are only consumed by the largest individuals of a predator species), others may be difficult to detect because they occur under conditions not conducive to sampling (e.g., during inclement weather or at night), and yet other interactions may be common but very difficult to detect (e.g., interactions involving species that are highly cryptic).
+We emphasize that some of these sources of uncertainty can be reduced with increased sampling but that, because it is easier to observe species than interactions between species, increased sampling will tend to add more unobserved than observed interactions to a matrix.
+We illustrate the problem using an extensively-sampled, spatially-replicated \emph{Salix}-galler-natural enemy system (Kopelke \emph{et al.}, 2017.
+\textbf{Ecology} 98: 1730).
 
-    As a potential solution, we propose a Bayesian framework which partitions the uncertainty associated with missing interactions into explicit components and allows us to place confidence intervals around each estimated interaction probability.
-The Bayesian framework also facilitates the use of prior information (e.g., species traits) to reduce uncertainty around some interactions.
-We illustrate this framework using an extraordinarily  well-replicated set of plant-galler-parasitoid networks recently published as a data paper (Kopelke \emph{et al.}, 2017.
-\textbf{Ecology} 98: 1730).
-Using this dataset, we demonstrate how uncertainty surrounding each interaction probability affects network-level metrics.
-Our derivation of the Bayesian framework and quantitative examples are constructed so as to be accessible to readers with little or no prior experience with Bayesian statistics.
-We hope that this gentle introduction will help the broadest possible set of readers apply the framework we propose.
+    With extensive sampling being time- and resource-intensive and not a complete solution to the problems posed by interaction uncertainty, we suggest that researchers instead treat interactions probabilistically and incorporate prior information to set bounds on the probability of interaction between species that were not observed interacting.
+As mentioned above, a lack of observed interaction could have several causes and does not necessarily imply that the interaction truly does not occur.
+We demonstrate a simple Bayesian framework, including the selection of a prior distribution, and use it to predict the likely set of feasible interactions in our example \emph{Salix} system.
+Based on this framework, we close with a set of recommendations for both empiricists and theoreticians that should improve our ability to deal with the uncertainty inherent in ecological networks and compare networks across systems.
 
-    The present work uses empirical material published as a data paper by one of the authors (Tomas Roslin).
-The cited paper, Kopelke \emph{et al.} (2017), presents the extremely high-quality dataset used in the present work but does not contain any analyses.
-As such, the present work is an entirely novel use of these data, which are also available to the full ecological community.
+    We are aware that there are several studies already using various forms of Bayesian networks to treat interactions as probabilities.
+These efforts have, however, so far remained confined to fairly theoretical work.
+We believe that empirical ecologists will also find Bayesian networks a useful tool when planning field sampling and when describing and analysing their focal communities.
+Our goal with this manuscript is, therefore, to introduce a Bayesian line of thought in as approachable and broadly-applicable terms as possible.
+To that end, we provide simple R code that illustrates each step of our approach.
 
-    We appreciate the chance to submit one of the first Novel Methods papers at \textbf{Ecology Letters}.
-We are confident that the fundamental conceptual shift implied by our approach, accompanied by clear examples and easy-to-use scripts, can achieve the high standard you are looking for.
+    We hope that the general nature of uncertainty around interactions, as well as the broadly-applicable solution we offer, will be of interest to the readership of \textbf{Methods in Ecology and Evolution}.
+We are confident that our worked example and easy-to-use scripts will provide a useful template for empiricists and theoreticians alike.
 We hope that you agree and eagerly await your reply.
@@
 % Louis-Félix Bersier louis-felix.bersier@unifr.ch Université de Fribourg
+% Paolo Guimaraes
+% Jason Tylianakis
+% ask Tomas for empiricists
+% Owen Petchey
 

### 2018-06-27 manuscript/CI_interactions.tex
figure fine-tuned

@@
     \caption{Three nested levels of uncertainty mean that an observed interaction matrix is unlikely to capture all of the interactions that can really occur at a site.
-Interaction uncertainty means that some inteactions that truly occur (black squares in True matrix) are less likely than others (grey squares) based on species traits.
+Interaction uncertainty means that some inteactions that truly occur (black squares in True matrix) are less likely than others (grey squares; lighter grey is less likely) based on species traits.
 For example, lions are less likely to predate upon elephants than zebras.
@@
     After applying these three layers of uncertainty, some interactions which truly occur are very unlikely to be observed.
-An observed matrix sampled based on this matrix (lower left) is thus likely to contain far fewer interactions than the original, true matrix.}
+An observed matrix sampled based on this matrix (lower right) is thus likely to contain far fewer interactions than the original, true matrix.}
     \label{conceptual_fig}
     \begin{center}
-    % \includegraphics*[height=.5\textheight]{figures/conceptual_fig.eps}
+    \includegraphics*[height=.5\textheight]{figures/conceptual_fig.eps}
     \end{center}

### 2018-06-27 manuscript/CI_interactions.tex
updated conceptual caption

@@
     After applying these three layers of uncertainty, some interactions which truly occur are very unlikely to be observed.
-An observed matrix sampled based on this matrix (lower right) is thus likely to contain far fewer interactions than the original, true matrix.}
+The observed matrix (lower right) is a subsample of the true matrix, with the probability of observing each interaction depending on the interaction, process, and detection uncertainty associated with it.
+Note that some low-probability interactions (e.g., lion predation on zebra) are included while others (e.g., lion predation on elephants) are not.}
     \label{conceptual_fig}
@@
       \begin{center}
-      % \includegraphics*[height=.6\textheight]{figures/GP_histogram.eps}
+      \includegraphics*[height=.6\textheight]{figures/GP_histogram.eps}
       \end{center}
@@
     \begin{center}
-    % \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
+    \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
     \end{center}
@@
     \begin{center}
-    % \includegraphics*[width=.8\textwidth]{figures/GP_pdfs_increasing_N_Zillis.eps}
+    \includegraphics*[width=.8\textwidth]{figures/GP_pdfs_increasing_N_Zillis.eps}
     \end{center}
@@
     \begin{center}
-    % \includegraphics[width=.8\textwidth]{figures/GP_posterior_properties_Zillis.eps}
+    \includegraphics[width=.8\textwidth]{figures/GP_posterior_properties_Zillis.eps}
     \end{center}

### 2018-06-27 manuscript/supplemental.tex
updated conceptual caption

@@
   To demonstrate the effects of nested interaction, process, and detection uncertainty on network structure, we can observe how the structure of randomly-generated networks changes as we add layers of uncertainty.
-We began by constructing 100 "true" networks with 50 plant species, 50 galler species, and a connectance of 0.1.
+We began by constructing 100 ``true" networks with 50 plant species, 50 galler species, and a connectance of 0.1.
 We ensured that each network had at least one link per plant and per galler.
@@
 
-  Taking each "true" network as a starting point, we then applied process uncertainty.
+  Taking each ``true" network as a starting point, we then applied process uncertainty.
 The probability $p$ of the occurrance of each interaction on a given sampling day was assigned a random probability drawn from the uniform distribution.
@@
 The number of occurrances, $k$, of each interaction was then drawn from a binomial distribution based on $n$ and $p$.
-If the number of occurrances during sampling was greater than 0 and the interaction occurred in the true network, we included the interaction in the "process-filtered" network.
+If the number of occurrances during sampling was greater than 0 and the interaction occurred in the true network, we included the interaction in the ``process-filtered" network.
 As the inclusion of interactions in the process matrices is random, we created 100 process-filtered networks for each true network.
@@
 
-  Next, we applied a layer of detection uncertainty to create "detection-filtered" networks.
+  Next, we applied a layer of detection uncertainty to create ``detection-filtered" networks.
 As with the process-filtered networks, we randomly selected the number of times each species co-occurred, $n$, from a uniform distribution.
@@
 For each network, we calculated the number of plants and gallers (after removing any species with no interactions), mean links per plant and per galler, connectance, and NODF.
-Code used in this simulation example is contained in the file \emph{simulation_example.R}, uploaded separately.
+Code used in this simulation example is contained in the file \emph{simulation\_example.R}, uploaded separately.
 
@@
   \caption{We created 100 random networks containing 50 plants and 50 gallers, with a connectance of 0.1.
-For each of these "original" networks, we created 100 process-filtered ("process") networks incorporating uncertainty around the occurrance of each interaction during sampling.
-For each "process" network, we further created 100 detection-filtered ("detection") networks incorporating uncertainty around the detection of each interaction.
+For each of these ``original" networks, we created 100 process-filtered ("process") networks incorporating uncertainty around the occurrance of each interaction during sampling.
+For each ``process" network, we further created 100 detection-filtered ("detection") networks incorporating uncertainty around the detection of each interaction.
 For each network, we show the mean (+/- SD) connectance, links per plant, nestedness (NODF), and links per galler.}

### 2018-06-27 manuscript/CI_interactions.tex
spellchecked

@@
 
-    Representing an ecological community as a network summarizes both species composition and interactions between species.
+    Representing an ecological community as a network summarises both species composition and interactions between species.
 A tabulation of the nodes (species) and their relative abundances forms the basis for traditional metrics of community composition such as alpha diversity.
@@
       The choice of prior will depend on the information available.
-In general, it is best to use a prior taken from a similar system as emphasized above.
+In general, it is best to use a prior taken from a similar system as emphasised above.
 If such data are not available, a prior based on many networks with a similar level of resolution could be useful, as could a prior based on a preliminary round of sampling (analogous to ``training data").
@@
 
-      The high spatiotemporal resolution and unusally high sampling effort of this dataset make it well suited for illustrating the difficulties in completely sampling a network.
+      The high spatiotemporal resolution and unusually high sampling effort of this dataset make it well suited for illustrating the difficulties in completely sampling a network.
 To show the gaps in sampling, we compared the frequencies of observed co-occurrences and interactions.
@@
 Re-sampling networks based on a probabilistic understanding of networks is straightforward and gives distributions for network properties rather than point estimates.
-This not only acknowledges the fact that interactions vary over time and space but will also facilitate comparisons between networks by adding confidence intervals to ezostimates of network properties.
+This not only acknowledges the fact that interactions vary over time and space but will also facilitate comparisons between networks by adding confidence intervals to estimates of network properties.
 This will allow us to say whether networks have different structures \emph{and} whether those differences are greater than we would expect given the inherent variability of interactions.
@@
     \caption{Three nested levels of uncertainty mean that an observed interaction matrix is unlikely to capture all of the interactions that can really occur at a site.
-Interaction uncertainty means that some inteactions that truly occur (black squares in True matrix) are less likely than others (grey squares; lighter grey is less likely) based on species traits.
+Interaction uncertainty means that some interactions that truly occur (black squares in True matrix) are less likely than others (grey squares; lighter grey is less likely) based on species traits.
 For example, lions are less likely to predate upon elephants than zebras.
@@
 Assume that two species cannot interact (i.e., $\lambda=0$) and that the number of observed interactions follows a binomial distribution.
-Here we show the upper bound (solid black line) of a 95\% Cloper-Pearson true credible interval for the interaction probability $\lambda$ for a pair of species that has been observed co-occurring $n$ times but never interacting ($k = 0$).
+Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true credible interval for the interaction probability $\lambda$ for a pair of species that has been observed co-occurring $n$ times but never interacting ($k = 0$).
 The upper limit of the credible interval only reaches 0.1 (dashed, red line) with 35 observations.
@@
     \caption{Using prior distributions based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017}, we calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting ($k = 0$).
-    Posterior distributions (curves) and 95\% credible intervals (lines at top of panell) for $\lambda$ narrow and approach zero as the number of observed co-occurrences ($n$) increases.
+    Posterior distributions (curves) and 95\% credible intervals (lines at top of panel) for $\lambda$ narrow and approach zero as the number of observed co-occurrences ($n$) increases.
 Diamonds indicate the maximum likelihood estimator for the mean probability of interaction.

### 2018-06-27 manuscript/supplemental.tex
spellchecked

@@
 For each network, we calculated the mean number of links per plant, mean number of links per galler, and nestedness (NODF) as described in the main text.
-For simplicity, we assume that there is no interaction uncertainty in this system (i.e., all interactions are either 100\% feasible or 100\% infeasible based on species' traits).
+For simplicity, we assume that there is no interaction uncertainty in this system (i.e., all interactions are either 100\% feasible or 100\% unfeasible based on species' traits).
 
   Taking each ``true" network as a starting point, we then applied process uncertainty.
-The probability $p$ of the occurrance of each interaction on a given sampling day was assigned a random probability drawn from the uniform distribution.
+The probability $p$ of the occurrence of each interaction on a given sampling day was assigned a random probability drawn from the uniform distribution.
 As the probability that an interaction will occur during sampling also depends on the probability of the two species co-occurring, we also assigned a random number of sampling days on which each species co-occurred.
-The number of co-occurrances, $n$, was drawn from a uniform distribution and could be any integer between 0 and 30 (our simulated number of sampling days), inclusive.
-The number of occurrances, $k$, of each interaction was then drawn from a binomial distribution based on $n$ and $p$.
-If the number of occurrances during sampling was greater than 0 and the interaction occurred in the true network, we included the interaction in the ``process-filtered" network.
+The number of co-occurrences, $n$, was drawn from a uniform distribution and could be any integer between 0 and 30 (our simulated number of sampling days), inclusive.
+The number of occurrences, $k$, of each interaction was then drawn from a binomial distribution based on $n$ and $p$.
+If the number of occurrences during sampling was greater than 0 and the interaction occurred in the true network, we included the interaction in the ``process-filtered" network.
 As the inclusion of interactions in the process matrices is random, we created 100 process-filtered networks for each true network.
@@
 
-  With each additional layer of uncertainty, the number of plants and gallers included in the web decreased (state means here).
+  With each additional layer of uncertainty, the number of plants and gallers included in the web decreased ([[state means here]]).
 The connectance and number of links per plant and per galler decreased significantly at each level (Fig.~\ref{sim_props}A,B,D).
@@
 In this framework, individuals could vary in some trait (e.g., body size) that affects the interactions in which they participate.
-Very small or very large individuals might not participate in some interactions that are feasbile for most members of the species.
+Very small or very large individuals might not participate in some interactions that are feasible for most members of the species.
 
@@
   \caption{We created 100 random networks containing 50 plants and 50 gallers, with a connectance of 0.1.
-For each of these ``original" networks, we created 100 process-filtered ("process") networks incorporating uncertainty around the occurrance of each interaction during sampling.
+For each of these ``original" networks, we created 100 process-filtered ("process") networks incorporating uncertainty around the occurrence of each interaction during sampling.
 For each ``process" network, we further created 100 detection-filtered ("detection") networks incorporating uncertainty around the detection of each interaction.

### 2018-06-27 manuscript/coverletter.tex
spellchecked

@@
 
-    My co-authors and I are pleased to submit the attached manuscript \emph{A quantitative framework for investigating the reliability of emprical network construction} for consideration as a research article in \textbf{Methods in Ecology and Evolution}.
+    My co-authors and I are pleased to submit the attached manuscript \emph{A quantitative framework for investigating the reliability of empirical network construction} for consideration as a research article in \textbf{Methods in Ecology and Evolution}.
 The goals of this manuscript are A) to illustrate the extreme difficulty in fully sampling the set of interactions occurring within a community, B) to demonstrate the construction of networks treating each interaction probabilistically (based on prior information as well as available data), and C) to offer concrete recommendations that will facilitate the use of this framework in future work.
@@
 Some interactions may be rare because of species traits (e.g., prey that are only consumed by the largest individuals of a predator species), others may be difficult to detect because they occur under conditions not conducive to sampling (e.g., during inclement weather or at night), and yet other interactions may be common but very difficult to detect (e.g., interactions involving species that are highly cryptic).
-We emphasize that some of these sources of uncertainty can be reduced with increased sampling but that, because it is easier to observe species than interactions between species, increased sampling will tend to add more unobserved than observed interactions to a matrix.
+We emphasise that some of these sources of uncertainty can be reduced with increased sampling but that, because it is easier to observe species than interactions between species, increased sampling will tend to add more unobserved than observed interactions to a matrix.
 We illustrate the problem using an extensively-sampled, spatially-replicated \emph{Salix}-galler-natural enemy system (Kopelke \emph{et al.}, 2017.

### 2018-06-29 manuscript/CI_interactions.tex
added t-tests from simulation to supplemental. Just waiting for Tomas comments, then ready to submit

@@
 % \item Running title: Quantitative network construction
-% \item Article type: Ideas and Perspectives
-% \item Number of references: 36
-% \item Number of figs, tables, \& text boxes: 8 % Limit is 10
+% \item Number of references: 37
+% \item Number of figs, tables, \& text boxes: 6 % Limit is 10
 % \end{itemize}
@@
 % \begin{itemize}
-% \item Text box 1 word count: 381
-% \item Text box 2 word count: 210
-% \item Abstract word count: 199
-% \item Main text word count: 7078 % Including 31 page numbers. Limit is 6000-7000 including figs, tables, references. 
+% \item Abstract word count: 290
+% \item Main text word count: 6872 % Limit is 6000-7000 including figs, tables, references. 
 % \end{itemize}
@@
 
-% \linenumbers
+\linenumbers
 \clearpage
@@
 To define the problem, we first identify different contributions to the uncertainty of an interaction and discuss the implications of each source of uncertainty for the properties of ecological networks.
-    % Next, we develop an analytical framework to quantify the uncertainty around interactions in an empirical web and, finally, illustrate this framework using an extensively sampled empirical network.
-    % We illustrate this framework using the most extensively sampled network to date (Box 1).
-Finally, we offer tangible recommendations for improved descriptors of ecological interactions.
-Through these efforts, we demonstrate both the utility of our approach and the importance of acknowledging the uncertainty inherent in network studies.
 
@@
 where the interaction occurred at the location but was not observed, and $X = 0 \cup L =1$, i.e., where the interaction is feasible but did not occur at the local site (Fig.~\ref{conceptual_fig}).
-        % The occurrence of a true absence, our quantity of interest, corresponds to the joint event $L=0 \cup X=1 \cup D=1$ but %% AC: Doesn't a true absence just mean $L=0$ regardless of our ability to detect/local conditions?
         This is not possible, however, using empirical data.
@@
 Given this information, the question becomes: how can we reduce the uncertainty around our estimated interaction probability?
-
-        % The considerations above raise major challenges: when faced with empirical data, how may we infer whether unobserved interactions truly do not occur?
-How may we refine our sampling approaches to reduce uncertainties and gain insights into the impact of multiple processes on field observations?
-Importantly, some sources of uncertainty within these three broad groupings can be minimised with appropriate sampling (e.g., sampling in a variety of weather conditions, combining different methods of detection) while other sources are difficult or impossible to reduce since they are generated by the process in which we are interested (e.g., variation in individual preferences or traits).
-Given this multifaceted problem of uncertainty, what can we do to separate the different types of variation and reduce those that can be reduced?
 
@@
   The authors thank Daniel Cartensen for fruitful discussion of the ideas in this manuscript and K\'{e}vin Cazalles for providing feedback.
-The authors appreciate support from the Swedish Research Council (VR) for grant \#2016-06872 (to TR) from Formas for grant \#942-2015-1262 (to AE).
+The authors appreciate support from the Swedish Research Council (VR) for grant \#2016-06872 (to TR) and from Formas for grant \#942-2015-1262 (to AE).
 
@@
 
-\captionsetup{singlelinecheck=false, font={stretch=1}}
+\captionsetup{singlelinecheck=false, font={stretch=2}}
 
 \section*{Figures}
-
-% \begin{fullbox}{}
-%   \begin{spacing}{1.0}
-%     \textbf{Box 1: }\emph{Salix}-galler-natural enemy dataset.\\
-%     \indent As a case study, we use an extensively sampled \emph{Salix}-galler-natural enemy meta-network.
-This dataset consists of a single community type sampled across Europe: willow (\emph{Salix}) species, willow-galling sawflies, and their natural enemies.
-The data were collected over 29 years at 374 unique locations across Europe.
-The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes.
-The high spatiotemporal resolution of this network and the unusually high sampling effort implemented at the site level makes this dataset particularly well suited for illustrating the difficulties in completely sampling a network and testing Bayesian approaches to overcome these difficulties.\\
-%     \indent We may begin by comparing the frequencies of co-occurrences and interactions to reveal the challenge of having sufficient sampling to be confident that an interaction does not occur.
-Most pairs of species (9,794/12,096 galler-natural enemy pairs) are never found co-occurring and, for species that did occur together, the total number of co-occurrences was generally low (mean=3.87, variance=28.8; Fig.~\ref{histograms}A).
-The bulk of these co-occurring species pairs were never observed to interact: only 7.76\% of galler-natural enemy pairs were observed interacting.
-Of those pairs that did interact, the incidence of interaction was also low (mean=4.04, variance=29.3; Fig.~\ref{histograms}B).
-Thus, even in the most extensive data set that we could find, there was very little empirical data for each species pair.
-This suggests that limited sampling is a major source of uncertainty in all empirical networks.
-This dataset also illustrates the potential for increased sampling to not necessarily reveal more interactions as a pair of species that is able to interact may not be observed interacting in all samples where the pair co-occurs (Fig.~\ref{histograms}C).
-%   \end{spacing}
-% \end{fullbox}
-
-% \clearpage
 
@@
     \begin{center}
-    \includegraphics*[height=.5\textheight]{figures/conceptual_fig.eps}
+    % \includegraphics*[height=.5\textheight]{figures/conceptual_fig.eps}
     \end{center}
@@
     \begin{center}
-    \includegraphics*[width=.8\textwidth]{figures/GP_pdfs_increasing_N_Zillis.eps}
+    % \includegraphics*[width=.8\textwidth]{figures/GP_pdfs_increasing_N_Zillis.eps}
     \end{center}
     \end{figure}
-
-  % \begin{figure}[h!]
-  %   \caption{The number of samples required to achieve a given level of confidence that an interaction probability $\lambda_{ij}$ is below a given threshold varies with both parameters.
-With a low threshold, our confidence that $\lambda_{ij}$ is below the threshold increases rapidly with repeated observation of co-occurrence without interaction.
-Here we show the cumulative density functions for threshold probabilities of 0.5 (solid line), 0.25 (dashed line), 0.1 (dash-dot line), and 0.05 (dotted line) as well as the points at which the cdf reaches 0.90 (orange square), 0.95 (red circle), and 0.975 (blue diamond) for each threshold value.
-The large ticks along the x-axis indicate the number of samples associated with each of these points.
-\textbf{A)} In the \emph{Salix}-galler network component, the 95\% credible interval for $\lambda_{ij}$ when $n$=0 was (0.013, 0.049).
-We can therefore be at least 95\% confident that $\lambda_{ij}$ is below thresholds of 0.1 or 0.05 without any observed co-occurrence of species $i$ and $j$.
-To be confident that $\lambda_{ij}$ is less than 0.01, however, would require more observed co-occurrences than there are sites in our dataset.
-\textbf{B)} In the galler-parasitoid network component, the 95\% credible interval for $\lambda_{ij}$ was substantially broader and many observed co-occurrences ($\approx$ 15-35) are required to be 95\% confident that $\lambda_{ij}$ is below thresholds of 0.1 or 0.05.}
-  %   \label{Salix_cdfs}
-  %   \begin{center}
-  %   \includegraphics[width=.5\textwidth]{figures/Salix_Galler_samples_and_cdfs_Zillis.eps}
-  %   \end{center}
-
-  %   \end{figure}
 

### 2018-06-29 manuscript/coverletter.tex
added t-tests from simulation to supplemental. Just waiting for Tomas comments, then ready to submit

@@
     My co-authors and I are pleased to submit the attached manuscript \emph{A quantitative framework for investigating the reliability of empirical network construction} for consideration as a research article in \textbf{Methods in Ecology and Evolution}.
-The goals of this manuscript are A) to illustrate the extreme difficulty in fully sampling the set of interactions occurring within a community, B) to demonstrate the construction of networks treating each interaction probabilistically (based on prior information as well as available data), and C) to offer concrete recommendations that will facilitate the use of this framework in future work.
+The goals of this manuscript are to demonstrate the extreme difficulty of observing all interactions that occur within a community and, given this difficulty, to illustrate a framework for combining prior knowledge about the system with observed data in order to gauge the probability of interactions which were not observed.
+We close by offering concrete recommendations that will facilitate researchers' efforts to acknowledge and set bounds on the uncertainty inherent in ecological data.
 
     We argue that, because of multiple levels of uncertainty surrounding interactions between species, the set of observed interactions will almost certainly be a subset of the interactions that can occur in a community.
-Some interactions may be rare because of species traits (e.g., prey that are only consumed by the largest individuals of a predator species), others may be difficult to detect because they occur under conditions not conducive to sampling (e.g., during inclement weather or at night), and yet other interactions may be common but very difficult to detect (e.g., interactions involving species that are highly cryptic).
+Interactions may not be observed because a species is rare and does not encounter its partner during sampling, because environmental constraints prohibit the interaction during sampling, because one or both species is difficult to observe in the field, or because the interaction truly does not occur.
 We emphasise that some of these sources of uncertainty can be reduced with increased sampling but that, because it is easier to observe species than interactions between species, increased sampling will tend to add more unobserved than observed interactions to a matrix.
@@
 
-    With extensive sampling being time- and resource-intensive and not a complete solution to the problems posed by interaction uncertainty, we suggest that researchers instead treat interactions probabilistically and incorporate prior information to set bounds on the probability of interaction between species that were not observed interacting.
-As mentioned above, a lack of observed interaction could have several causes and does not necessarily imply that the interaction truly does not occur.
-We demonstrate a simple Bayesian framework, including the selection of a prior distribution, and use it to predict the likely set of feasible interactions in our example \emph{Salix} system.
+    In many cases, it will not be feasible to sample all species pairs intensively enough (tens of observations per pair) to be confident that the pair does not interact.
+Given the time and resource constraints that often restrict fieldwork, we suggest that researchers supplement observed data with prior information about the system.
+Thus, they can set bounds on the probability of interaction between species that were not observed interacting.
+We demonstrate this simple Bayesian framework, including the selection of a prior distribution, and use it to predict the likely set of feasible interactions in our example \emph{Salix} system.
 Based on this framework, we close with a set of recommendations for both empiricists and theoreticians that should improve our ability to deal with the uncertainty inherent in ecological networks and compare networks across systems.
@@
     We are aware that there are several studies already using various forms of Bayesian networks to treat interactions as probabilities.
-These efforts have, however, so far remained confined to fairly theoretical work.
-We believe that empirical ecologists will also find Bayesian networks a useful tool when planning field sampling and when describing and analysing their focal communities.
+These efforts are, however, generally confined to fairly theoretical work.
+We believe that empirical ecologists will find Bayesian interaction probabilities to be a useful tool when planning field sampling and when describing and analysing their focal communities.
 Our goal with this manuscript is, therefore, to introduce a Bayesian line of thought in as approachable and broadly-applicable terms as possible.
@@
 % Paolo Guimaraes 
-% Jason Tylianakis
+% Jason Tylianakis jason.tylianakis@canterbury.ac.nz :)
 % ask Tomas for empiricists
-% Owen Petchey
+% Owen Petchey University of Zurich owen.petchey@ieu.uzh.ch
 

### 2018-06-29 manuscript/supplemental.tex
added t-tests from simulation to supplemental. Just waiting for Tomas comments, then ready to submit

@@
 \clearpage
+
+\linenumbers
 
@@
 \emph{Salix}-galler pairs either are never observed interacting or interact almost every time they co-occur.
-IThe red, dashed line indicates a 1:1 relationship between interactions and co-occurrences.}
+The red, dashed line indicates a 1:1 relationship between interactions and co-occurrences.}
           \label{histograms}
           \begin{center}
-          \includegraphics*[width=.8\textwidth]{figures/SG_histogram.eps}
+          \includegraphics*[height=.7\textheight]{figures/SG_histogram.eps}
           \end{center}
@@
         \begin{center}
-        \includegraphics*[width=.7\textwidth]{figures/SG_pdfs_increasing_N_Zillis.eps}
+        \includegraphics*[width=.9\textwidth]{figures/SG_pdfs_increasing_N_Zillis.eps}
         \end{center}
@@
       \begin{center}
-      \includegraphics[width=.7\textwidth]{figures/SG_posterior_properties_Zillis.eps}
+      \includegraphics[width=.9\textwidth]{figures/SG_posterior_properties_Zillis.eps}
       \end{center}
@@
         \begin{center}
-        \includegraphics*[width=.6\textwidth]{figures/Salix_Galler_pdfs_increasing_N.eps}
+        \includegraphics*[width=.65\textwidth]{figures/Salix_Galler_pdfs_increasing_N.eps}
         \end{center}
@@
         \begin{center}
-        \includegraphics[width=.6\textwidth]{figures/Salix_Galler_samples_and_cdfs.eps}
+        \includegraphics[width=.65\textwidth]{figures/Salix_Galler_samples_and_cdfs.eps}
         \end{center}
@@
       \begin{center}
-      \includegraphics[width=.6\textwidth]{Figures/Salix_Galler_posterior_properties.eps}
+      \includegraphics[width=.65\textwidth]{Figures/Salix_Galler_posterior_properties.eps}
       \end{center}
@@
 
-  With each additional layer of uncertainty, the number of plants and gallers included in the web decreased ([[state means here]]).
-The connectance and number of links per plant and per galler decreased significantly at each level (Fig.~\ref{sim_props}A,B,D).
-The effects of uncertainty on nestedness were less predictable.
-The process-filtered networks were significantly less nested than the original networks, but the variation in the detection-filtered webs was so great that there were no significant differences between the original and detection-filtered networks (Fig.~\ref{sim_props}C).
+  With each additional layer of uncertainty, the number of plants and gallers included in the web decreased (mean 49.8 of each species type in detection-filter webs and mean 48.6 of each type in process-filtered webs).
+The connectance and number of links per plant and per galler decreased significantly at each level (Fig.~\ref{sim_props}A,B,D; $p$\textless0.001 in all cases based on one-tailed Student's t tests).
+The effects of uncertainty on nestedness were less predictable, particularly in the detection-filtered webs where variability was much higher than in other web types.
+Nevertheless, mean nestedness was lower in detection-filtered webs than in the original webs ($t$=19.9, $p$\textless0.001) and lower in the process-filtered webs than the original and detection-filtered webs (Fig.~\ref{sim_props}C; $t$=32.8, $p$\textless0.001 and $t$=93.7, $p$\textless0.001).
+We note that these tests may reflect the large number of detection-filtered webs generated by our simulation.
+A single observed network drawn from these detection-filtered webs might well have a higher nestedness than the ``true" network.
 This simulation demonstrates the fact that process and detection uncertainty mean that we are very unlikely to observe all of the interactions that can truly occur in a system, as well as the sometimes unpredictable effects this uncertainty can have on higher-order structures such as nestedness.
@@
   \caption{We created 100 random networks containing 50 plants and 50 gallers, with a connectance of 0.1.
-For each of these ``original" networks, we created 100 process-filtered ("process") networks incorporating uncertainty around the occurrence of each interaction during sampling.
-For each ``process" network, we further created 100 detection-filtered ("detection") networks incorporating uncertainty around the detection of each interaction.
+For each of these ``original" networks, we created 100 process-filtered (``process") networks incorporating uncertainty around the occurrence of each interaction during sampling.
+For each ``process" network, we further created 100 detection-filtered (``detection") networks incorporating uncertainty around the detection of each interaction.
 For each network, we show the mean (+/- SD) connectance, links per plant, nestedness (NODF), and links per galler.}
   \begin{center}
-  \includegraphics*[width=\textwidth]{figures/simulation_example.eps}
+  \includegraphics*[width=.9\textwidth]{figures/simulation_example.eps}
   \end{center}

### 2018-07-02 manuscript/CI_interactions.tex
some more Tomas comments

@@
 We then outline a framework to quantify the uncertainty around each interaction by combining data on observed co-occurrences with prior knowledge.
-We illustrate this framework using the most extensively sampled network to date.
+We illustrate this framework using perhaps the most extensively sampled network to date.
     \item We found significant uncertainty in estimates for the probability of most pairwise interactions.
@@
 This uncertainty scaled up to summary measures of network structure such as connectance or nestedness.
-By using an extremely well-sampled network as a test case, we find that even with informative priors we are likely to miss many interactions that may occur rarely or under different local conditions.
-    \item Overall, we demonstrate the utility of our approach and the importance of acknowledging the uncertainty inherent in network studies and the utility of treating interactions as probabilities in pinpointing areas where more study is needed.
+By using a comprehensively sampled network as a test case, we find that even with informative priors we are likely to miss many interactions that may occur rarely or under different local conditions.
+    \item Overall, we demonstrate the utility of our approach, given the importance of acknowledging the uncertainty inherent in network studies, and the utility of treating interactions as probabilities in pinpointing areas where more study is needed.
 Most importantly, we stress that networks are best thought of as systems constructed from random variables, the stochastic nature of which must be acknowledged for an accurate representation.
@@
     Despite these efforts, we currently lack the quantitative methodology to deal with uncertainty generated by spatiotemporal variation in ecological interactions and by limited sampling.
-Even in extremely well-sampled networks, uneven sampling across species can lead to the inference that some species do not interact because they co-occur rarely or have not yet been observed together - even if they do interact when they do co-occur (see Fig.~\ref{histograms}).
+Even in well-sampled networks, uneven sampling across species can lead to the inference that some species do not interact because they co-occur rarely or have not yet been observed together - even if they do interact when they do co-occur (see Fig.~\ref{histograms}).
 Nearly all network studies will thus neglect some interactions, necessitating an approach that acknowledges this uncertainty.
@@
 
-        Most importantly, if two species are never observed co-occurring during several days of sampling then repeated sampling reveals nothing about their probability of interacting if they should ever co-occur.
+        Most importantly, if two species are never observed co-occurring during several days of sampling then repeated sampling reveals nothing about their probability of interacting should they ever co-occur.
 Intensive sampling is, therefore, an important step towards reducing uncertainty in ecological networks but is unlikely to be enough in most cases.
@@
 We want to know the probability $\lambda$ that the species would be observed interacting if not constrained by local conditions, imperfect detection, etc.
-We can consider the occurrence of an interaction as a Bernoulli trail where the number of successes ($k$) over $n$ trials will follow a binomial distribution (see~\emph{Appendix S1} for a full description of the mathematical framework).
+We can consider the occurrence of an interaction as a Bernoulli trail where the number of successes ($k$) over $n$ trials will follow a binomial distribution (see~\emph{Appendix S2} for a full description of the mathematical framework).
 In this framework, the maximum likelihood estimate (MLE) for $\lambda$ is:
@@
 
-    Combining the beta-distributed prior with the binomial-distributed MLE of $\lambda$ is straightforward (see~\emph{Appendix S1}).
+    Combining the beta-distributed prior with the binomial-distributed MLE of $\lambda$ is straightforward (see~\emph{Appendix S2}).
 By doing so, we obtain a posterior distribution that follows a beta distribution with new parameters $\alpha'= \alpha+k$ and $\beta'=\beta+n-k$.
@@
 These are called hyper parameters.
-The prior may be chosen to be uninformative, if no external information is available, or may draw on information such as distributions of connectance across webs, degree distributions, or trait-matching functions (see \emph{Appendix S2} for details and a simple quantitative example).
+The prior may be chosen to be uninformative, if no external information is available, or may draw on information such as distributions of connectance across webs, degree distributions, or trait-matching functions (see \emph{Appendix S3} for details and a simple quantitative example).
 
@@
 
-      To illustrate the process of constructing a Bayesian network, we use the well-sampled system of willows (\emph{Salix}), herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}.
+      To illustrate the process of constructing a Bayesian network, we use the comprehensively-sampled system of willows (\emph{Salix}), herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}.
 This dataset consists of a single community type sampled across Europe over 29 years and at 374 unique locations.
 The data were collected over 29 years at 374 unique locations across Europe.
-The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (see \emph{Appendix S3} for details).
+The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (see \emph{Appendix S4} for details).
 
@@
 To show the gaps in sampling, we compared the frequencies of observed co-occurrences and interactions.
-We analysed both the \emph{Salix}-galler and galler-natural enemy components of the network but, for brevity, present only the latter here (see~\emph{Appendix S4} for \emph{Salix}-galler results).
+We analysed both the \emph{Salix}-galler and galler-natural enemy components of the network but, for brevity, present only the latter here (see~\emph{Appendix S5} for \emph{Salix}-galler results).
 
@@
 To demonstrate how the use of data from a different system can affect the prior distribution and conclusions based on it, we repeated our analyses using priors derived from a much smaller \emph{Salix}-galler-natural enemy system based around genotypes of a single \emph{Salix} species~\citep[Data available from the Dryad Digital Repository: https://doi.org/10.5061/dryad.g7805]{Barbour2016}\nocite{Barbour2016Dryad}.
-This smaller system was much more densely-connected than that described in~\citet{Kopelke2017} and provided unreasonable distributions for interaction probabilities (\emph{Appendix S5}).
+This smaller system was much more densely-connected than that described in~\citet{Kopelke2017} and provided unreasonable distributions for interaction probabilities (\emph{Appendix S6}).
 
-        To obtain priors based on a single sub-network --Zillis in Graub\"{u}nchen, Switzerland-- we estimated frequencies of interactions based on the normalised degree of each species in each network component (see \emph{Appendix S6} for details and code).
+        To obtain priors based on a single sub-network --Zillis in Graub\"{u}nchen, Switzerland-- we estimated frequencies of interactions based on the normalised degree of each species in each network component (see \emph{Appendix S7} for details and code).
 Using these prior parameters, we then estimated the posterior distributions of interaction probabilities $\lambda$.
@@
 This gives $\alpha'$=$\alpha$ and $\beta'$=$\beta + n_{ij}$.
-We calculated posterior distributions and 95\% credible intervals (see function ``credible\_interval";~\emph{Appendix S7}) for species with $n$ ranging between 0 and 374, the total number of sites in our dataset.
+We calculated posterior distributions and 95\% credible intervals (see function ``credible\_interval";~\emph{Appendix S8}) for species with $n$ ranging between 0 and 374, the total number of sites in our dataset.
 
@@
 The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact.
-We calculated the number of samples required to reach 95\% confidence that $\lambda$ was below thresholds of 0.1, 0.05, and 0.01 as examples (see function ``samples\_for\_threshold";~\emph{Appendix S7}).
+We calculated the number of samples required to reach 95\% confidence that $\lambda$ was below thresholds of 0.1, 0.05, and 0.01 as examples (see function ``samples\_for\_threshold";~\emph{Appendix S8}).
 
@@
 By Jensen's inequality~\citep{Jensen1906}, this means that the average of a network metric (a function of stochastic interactions) is not the same as the network metric calculated based on the average interaction probability.
-Any uncertainty in the values of $\lambda$ could bias both the mean and variance of network metrics, giving misleading results (simulated in \emph{Appendix S8}).
+Any uncertainty in the values of $\lambda$ could bias both the mean and variance of network metrics, giving misleading results (simulated in \emph{Appendix S1}).
 One way to avoid this situation is to calculate the properties of a suite of simulated networks.
@@
 
-  Most pairs of species (9,794/12,096) never co-occurred and, for species that did occur together, the total number of co-occurrences was generally low (mean=3.87; Fig.~\ref{histograms}A).
+  In the \emph{Salix}-based food webs sampled by~\citet{Kopelke2017}, most pairs of gallers and natural enemies (9,794/12,096) never co-occurred and, for species that did occur together, the total number of co-occurrences was generally low (mean=3.87; Fig.~\ref{histograms}A).
 The bulk (92.24\%) of these co-occurring species pairs were never observed interacting.
@@
 To be 95\% confident that the probability of interaction is below 0.1, 0.05, or 0.01 would require 15, 39, and 229 observed co-occurrences, respectively.
-Note that these are relatively large sample sizes compared to currently-available empirical networks~\citep{Morris2014}.
+Note that these are relatively large sample sizes compared to currently-available empirical networks (e.g.,~\citealp{Morris2014}).
 
@@
 If our trait model is incomplete (e.g., if we neglect group hunting in lions), we might assume that elephants are too large to ever be prey for lions and assign this interaction a probability of 0.\\
-    Process uncertainty describes the fact that interactions occur with different probabilities during any given sample.
+    \indent Process uncertainty describes the fact that interactions occur with different probabilities in any given sample.
 We show six example networks representing interactions observed over two days at three sites.
 Interactions which occur during fewer sampling days are less likely to be observed.\\
-    Detection uncertainty reflects the fact that not all interactions are equally detectable. For example, interactions involving cryptic species are less likely to be seen.\\
-    After applying these three layers of uncertainty, some interactions which truly occur are very unlikely to be observed.
+    \indent Detection uncertainty reflects the fact that not all interactions are equally detectable. For example, interactions involving cryptic species are less likely to be seen.\\
+    \indent After applying these three layers of uncertainty, some interactions which truly occur are very unlikely to be observed.
 The observed matrix (lower right) is a subsample of the true matrix, with the probability of observing each interaction depending on the interaction, process, and detection uncertainty associated with it.
-Note that some low-probability interactions (e.g., lion predation on zebra) are included while others (e.g., lion predation on elephants) are not.}
+Note that some low-probability interactions (e.g., lion predation on zebra) are included while others (e.g., lion predation on elephants) are not.
+For an illustration of the way in which these levels of uncertainty combine in simulated data, and the effects of uncertainty on network structure, see \emph{Appendix S1}.}
     \label{conceptual_fig}

### 2018-07-02 manuscript/supplemental.tex
some more Tomas comments

@@
 
-\section*{Appendix S1: Mathematical framework}
+\section*{Appendix S1: Simulating the effects of uncertainty on network structure}
+
+  To demonstrate the effects of nested interaction, process, and detection uncertainty on network structure, we can observe how the structure of randomly-generated networks changes as we add layers of uncertainty.
+We began by constructing 100 ``true" networks with 50 consumer species, 50 resource species, and a connectance of 0.1.
+We ensured that each network had at least one link per consumer and per resource.
+For each network, we calculated the mean number of links per consumer, mean number of links per resource, and nestedness (NODF) as described in the main text.
+For simplicity, we assume that there is no interaction uncertainty in this system (i.e., all interactions are either 100\% feasible or 100\% unfeasible based on species' traits).
+
+  Taking each ``true" network as a starting point, we then applied process uncertainty.
+The probability $p$ of the occurrence of each interaction on a given sampling day was assigned a random probability drawn from the uniform distribution.
+As the probability that an interaction will occur during sampling also depends on the probability of the two species co-occurring, we also assigned a random number of sampling days on which each species co-occurred.
+The number of co-occurrences, $n$, was drawn from a uniform distribution and could be any integer between 0 and 30 (our simulated number of sampling days), inclusive.
+The number of occurrences, $k$, of each interaction was then drawn from a binomial distribution based on $n$ and $p$.
+If the number of occurrences during sampling was greater than 0 and the interaction occurred in the true network, we included the interaction in the ``process-filtered" network.
+As the inclusion of interactions in the process matrices is random, we created 100 process-filtered networks for each true network.
+For each network, we calculated the number of consumers and resources (after removing any species with no interactions), mean links per consumer and per resource, connectance, and NODF.
+
+  Next, we applied a layer of detection uncertainty to create ``detection-filtered" networks.
+As with the process-filtered networks, we randomly selected the number of times each species co-occurred, $n$, from a uniform distribution.
+We also randomly selected the probability, $p$, of detecting each interaction.
+To reflect the fact that some interactions are easy to observe but many will be more difficult (because one or both interaction partners are rare, cryptic, or difficult to rear in the lab), we drew $p$ from a beta distribution with shape parameters 2 and 10.
+We created 100 detection-filtered networks for each process-filtered network (10000 per true network).
+For each network, we calculated the number of consumers and resources (after removing any species with no interactions), mean links per consumer and per resource, connectance, and NODF.
+Code used in this simulation example is contained in the file \emph{simulation\_example.R}, uploaded separately.
+
+  With each additional layer of uncertainty, the number of consumers and resources included in the web decreased (mean 49.8 of each species type in detection-filter webs and mean 48.6 of each type in process-filtered webs).
+The connectance and number of links per consumer and per resource decreased significantly at each level (Fig.~\ref{sim_props}A,B,D; $p$\textless0.001 in all cases based on one-tailed Student's t tests).
+The effects of uncertainty on nestedness were less predictable, particularly in the detection-filtered webs where variability was much higher than in other web types.
+Nevertheless, mean nestedness was lower in detection-filtered webs than in the original webs ($t$=19.9, $p$\textless0.001) and lower in the process-filtered webs than the original and detection-filtered webs (Fig.~\ref{sim_props}C; $t$=32.8, $p$\textless0.001 and $t$=93.7, $p$\textless0.001).
+We note that these tests may reflect the large number of detection-filtered webs generated by our simulation.
+A single observed network drawn from these detection-filtered webs might well have a higher nestedness than the ``true" network.
+This simulation demonstrates the fact that process and detection uncertainty mean that we are very unlikely to observe all of the interactions that can truly occur in a system, as well as the sometimes unpredictable effects this uncertainty can have on higher-order structures such as nestedness.
+
+  Note that this simulation uses several simplifying assumptions.
+For instance, we treat interactions as independent and ignore the possibility for, for example, competition between resources.
+A thorough exploration of the effects of interaction contingency, different distributions of co-occurrences, etc.
+would be an interesting topic for future work but is beyond the scope of the current study.
+We also neglect interaction uncertainty in this example.
+Interaction uncertainty could be included by, for example, modelling interactions between individuals of each species.
+In this framework, individuals could vary in some trait (e.g., body size) that affects the interactions in which they participate.
+Very small or very large individuals might not participate in some interactions that are feasible for most members of the species.
+
+  \begin{figure}
+  \label{sim_props}
+  \caption{We created 100 random networks containing 50 consumers and 50 resources, with a connectance of 0.1.
+For each of these ``original" networks, we created 100 process-filtered (``process") networks incorporating uncertainty around the occurrence of each interaction during sampling.
+For each ``process" network, we further created 100 detection-filtered (``detection") networks incorporating uncertainty around the detection of each interaction.
+For each network, we show the mean (+/- SD) connectance, links per consumer, nestedness (NODF), and links per resource.}
+  \begin{center}
+  \includegraphics*[width=.9\textwidth]{figures/simulation_example.eps}
+  \end{center}
+  \end{figure}
+
+\clearpage
+
+\section*{Appendix S2: Mathematical framework}
 
@@
 
-\section*{Appendix S2: Calculating uninformative and informative priors}
+\section*{Appendix S3: Calculating uninformative and informative priors}
 
@@
 
-\section*{Appendix S3: Details of \emph{Salix} data collection}
+\section*{Appendix S4: Details of \emph{Salix} data collection}
 
@@
 
-\section*{Appendix S4: Results for \emph{Salix}-galler component}
+\section*{Appendix S5: Results for \emph{Salix}-galler component}
 
@@
 
-\section*{Appendix S5: Analyses using alternative prior}
+\section*{Appendix S6: Analyses using alternative prior}
 
@@
 
-\section*{Appendix S6: Obtaining prior interaction probabilities}
+\section*{Appendix S7: Obtaining prior interaction probabilities}
 
@@
 
-\section*{Appendix S7: R code for calculating posterior distributions and confidence intervals}
+\section*{Appendix S8: R code for calculating posterior distributions and confidence intervals}
 
@@
 
-\section*{Appendix S8: Simulating the effects of uncertainty on network structure}
-
-  To demonstrate the effects of nested interaction, process, and detection uncertainty on network structure, we can observe how the structure of randomly-generated networks changes as we add layers of uncertainty.
-We began by constructing 100 ``true" networks with 50 plant species, 50 galler species, and a connectance of 0.1.
-We ensured that each network had at least one link per plant and per galler.
-For each network, we calculated the mean number of links per plant, mean number of links per galler, and nestedness (NODF) as described in the main text.
-For simplicity, we assume that there is no interaction uncertainty in this system (i.e., all interactions are either 100\% feasible or 100\% unfeasible based on species' traits).
-
-  Taking each ``true" network as a starting point, we then applied process uncertainty.
-The probability $p$ of the occurrence of each interaction on a given sampling day was assigned a random probability drawn from the uniform distribution.
-As the probability that an interaction will occur during sampling also depends on the probability of the two species co-occurring, we also assigned a random number of sampling days on which each species co-occurred.
-The number of co-occurrences, $n$, was drawn from a uniform distribution and could be any integer between 0 and 30 (our simulated number of sampling days), inclusive.
-The number of occurrences, $k$, of each interaction was then drawn from a binomial distribution based on $n$ and $p$.
-If the number of occurrences during sampling was greater than 0 and the interaction occurred in the true network, we included the interaction in the ``process-filtered" network.
-As the inclusion of interactions in the process matrices is random, we created 100 process-filtered networks for each true network.
-For each network, we calculated the number of plants and gallers (after removing any species with no interactions), mean links per plant and per galler, connectance, and NODF.
-
-  Next, we applied a layer of detection uncertainty to create ``detection-filtered" networks.
-As with the process-filtered networks, we randomly selected the number of times each species co-occurred, $n$, from a uniform distribution.
-We also randomly selected the probability, $p$, of detecting each interaction.
-To reflect the fact that some interactions are easy to observe but many will be more difficult (because one or both interaction partners are rare, cryptic, or difficult to rear in the lab), we drew $p$ from a beta distribution with shape parameters 2 and 10.
-We created 100 detection-filtered networks for each process-filtered network (10000 per true network).
-For each network, we calculated the number of plants and gallers (after removing any species with no interactions), mean links per plant and per galler, connectance, and NODF.
-Code used in this simulation example is contained in the file \emph{simulation\_example.R}, uploaded separately.
-
-  With each additional layer of uncertainty, the number of plants and gallers included in the web decreased (mean 49.8 of each species type in detection-filter webs and mean 48.6 of each type in process-filtered webs).
-The connectance and number of links per plant and per galler decreased significantly at each level (Fig.~\ref{sim_props}A,B,D; $p$\textless0.001 in all cases based on one-tailed Student's t tests).
-The effects of uncertainty on nestedness were less predictable, particularly in the detection-filtered webs where variability was much higher than in other web types.
-Nevertheless, mean nestedness was lower in detection-filtered webs than in the original webs ($t$=19.9, $p$\textless0.001) and lower in the process-filtered webs than the original and detection-filtered webs (Fig.~\ref{sim_props}C; $t$=32.8, $p$\textless0.001 and $t$=93.7, $p$\textless0.001).
-We note that these tests may reflect the large number of detection-filtered webs generated by our simulation.
-A single observed network drawn from these detection-filtered webs might well have a higher nestedness than the ``true" network.
-This simulation demonstrates the fact that process and detection uncertainty mean that we are very unlikely to observe all of the interactions that can truly occur in a system, as well as the sometimes unpredictable effects this uncertainty can have on higher-order structures such as nestedness.
-
-  Note that this simulation uses several simplifying assumptions.
-For instance, we treat interactions as independent and ignore the possibility for, for example, competition between gallers.
-A thorough exploration of the effects of interaction contingency, different distributions of co-occurrences, etc.
-would be an interesting topic for future work but is beyond the scope of the current study.
-We also neglect interaction uncertainty in this example.
-Interaction uncertainty could be included by, for example, modelling interactions between individuals of each species.
-In this framework, individuals could vary in some trait (e.g., body size) that affects the interactions in which they participate.
-Very small or very large individuals might not participate in some interactions that are feasible for most members of the species.
-
-  \begin{figure}
-  \label{sim_props}
-  \caption{We created 100 random networks containing 50 plants and 50 gallers, with a connectance of 0.1.
-For each of these ``original" networks, we created 100 process-filtered (``process") networks incorporating uncertainty around the occurrence of each interaction during sampling.
-For each ``process" network, we further created 100 detection-filtered (``detection") networks incorporating uncertainty around the detection of each interaction.
-For each network, we show the mean (+/- SD) connectance, links per plant, nestedness (NODF), and links per galler.}
-  \begin{center}
-  \includegraphics*[width=.9\textwidth]{figures/simulation_example.eps}
-  \end{center}
-  \end{figure}
-
-\clearpage
-
 \section*{Appendix S9: Calculating the credible interval around a probability estimate}

### 2018-07-02 code/figure_generation/simulation_summary_fig.py
changed SI axes labels

@@ -51,11 +51,11 @@ def configure_yaxes(prop,graph):
   if prop=='N_plants':
     graph.world.ymax=16
     graph.yaxis.tick.configure(major=3)
-    graph.yaxis.label.configure(text="N(plants)",char_size=1,just=2,place='normal')
+    graph.yaxis.label.configure(text="N(consumers)",char_size=1,just=2,place='normal')
   elif prop=='N_gallers':
     graph.world.ymax=21
     graph.yaxis.tick.configure(major=4)
-    graph.yaxis.label.configure(text="N(gallers)",char_size=1,just=2,place='normal')
+    graph.yaxis.label.configure(text="N(resources)",char_size=1,just=2,place='normal')
   elif prop=='C':
     graph.world.ymax=0.105
     graph.world.ymin=0.06
@@ -66,12 +66,12 @@ def configure_yaxes(prop,graph):
     graph.world.ymax=6
     graph.world.ymin=2
     graph.yaxis.tick.configure(major=1)
-    graph.yaxis.label.configure(text="Links per plant",char_size=1,just=2,place='normal')
+    graph.yaxis.label.configure(text="Links per consumer",char_size=1,just=2,place='normal')
   elif prop=='L_per_galler':
     graph.world.ymax=6
     graph.world.ymin=2
     graph.yaxis.tick.configure(major=1)
-    graph.yaxis.label.configure(text="Links per galler",char_size=1,just=2,place='normal')
+    graph.yaxis.label.configure(text="Links per resource",char_size=1,just=2,place='normal')
   else:
     graph.world.ymax=40
     graph.world.ymin=0

### 2018-07-02 manuscript/CI_interactions.tex
changed SI axes labels
fixed a figure ref

@@
 The detection of any interaction is a stochastic process.
-We define three nested levels of uncertainty contributing to this stochasticity: interaction uncertainty, process uncertainty, and detection uncertainty (Fig.~\ref{concept_fig}).
+We define three nested levels of uncertainty contributing to this stochasticity: interaction uncertainty, process uncertainty, and detection uncertainty (Fig.~\ref{conceptual_fig}).
 

### 2018-07-02 manuscript/coverletter.tex
fixed a figure ref

@@
     My co-authors and I are pleased to submit the attached manuscript \emph{A quantitative framework for investigating the reliability of empirical network construction} for consideration as a research article in \textbf{Methods in Ecology and Evolution}.
-The goals of this manuscript are to demonstrate the extreme difficulty of observing all interactions that occur within a community and, given this difficulty, to illustrate a framework for combining prior knowledge about the system with observed data in order to gauge the probability of interactions which were not observed.
+This manuscript is aimed squarely at the audiencce of \textbf{Methods in Ecology and Evolution}: ecologists in need of new tools for addressing topical questions in ecology and for recognizing key limitations and caveats in their research.
+Thus, the goals of this manuscript are to demonstrate the extreme difficulty of observing all interactions that occur within a community and, given this difficulty, to provide a way forward: a framework for combining prior knowledge about the system with observed data in order to gauge the probability of interactions which were not observed.
 We close by offering concrete recommendations that will facilitate researchers' efforts to acknowledge and set bounds on the uncertainty inherent in ecological data.
 
-    We argue that, because of multiple levels of uncertainty surrounding interactions between species, the set of observed interactions will almost certainly be a subset of the interactions that can occur in a community.
+    % We argue that, because of multiple levels of uncertainty surrounding interactions between species, the set of observed interactions will almost certainly be a subset of the interactions that can occur in a community.
 Interactions may not be observed because a species is rare and does not encounter its partner during sampling, because environmental constraints prohibit the interaction during sampling, because one or both species is difficult to observe in the field, or because the interaction truly does not occur.
@@
 
-    In many cases, it will not be feasible to sample all species pairs intensively enough (tens of observations per pair) to be confident that the pair does not interact.
+    % In many cases, it will not be feasible to sample all species pairs intensively enough (tens of observations per pair) to be confident that the pair does not interact.
 Given the time and resource constraints that often restrict fieldwork, we suggest that researchers supplement observed data with prior information about the system.
@@
 
+    As our central approach to this topic, we use a simple Bayesian framework.
 We are aware that there are several studies already using various forms of Bayesian networks to treat interactions as probabilities.
@@
 % Pedro Jordano pedroj@me.com Estacion Biologica de Donana CSIC
+
 % Phillip Staniczenko pstaniczenko@sesync.org National Socio-Environmental Synthesis Center (SESYNC)
-% Louis-Félix Bersier louis-felix.bersier@unifr.ch Université de Fribourg
-% Paolo Guimaraes 
-% Jason Tylianakis jason.tylianakis@canterbury.ac.nz :)
-% ask Tomas for empiricists
+
+% Louis-Félix Bersier louis-felix.bersier@unifr.ch Université de Fribourg - co-author with DG in 2016
+
+% Paulo Guimaraes prguima@gmail.com Universidade de Sao Paola
+
+% Jason Tylianakis jason.tylianakis@canterbury.ac.nz :) - co-author with DG in 2016
+
 % Owen Petchey University of Zurich owen.petchey@ieu.uzh.ch
 
-% Extra suggestion
-% Jacopo Grilli jgrilli@santafe.edu Santa Fe Institute
 % Eve McDonald-Madden e.mcdonaldmadden@uq.edu.au University of Queensland
 
+% Laura Burkle laura.burkle@montana.edu Montana State University Dept. of Ecology - co-author with DG in 2017
+
+% Jane Memmott jane.memmott@bristol.ac.uk University of Briston, School of Biological Sciences
+
+% Sonia Kefi sonia.kefi@umontpellier.fr Institut des Sciences de l'Evolution de Montpellier co-author with DG in 2017, 2016; co-author with AE in 2017
+
+% Charles Godfray charles.godfray@zoo.ok.ac.uk Oxford, Dept. of Zoology
+
+% Catherine Graham catherine.graham@wsl.ch Swiss Federal Research Institute (WSL) - co-ahtour with DG in 2018, TR in 2018
+
+% Extra suggestions
+% Jacopo Grilli jgrilli@santafe.edu Santa Fe Institute
 % Ben Weinstein Oregon State University weinsteb@oregonstate.edu
@@
 % Robert Colwell robertkcolwell@gmail.com Museum of Natural History, University of Colorado Boulder
+% Mari Moora mari.moora@ut.ee (as working on fungal interaction networks, but being well on the map)
+% (Anna Traveset atraveset@uib.es )
+% Ignasi Bartomeus nacho.bartomeus@gmail.com 
+% Owen Lewis owen.lewis@zoo.ox.ac.uk

### 2018-07-02 code/figure_generation/Zillis_posterior_plots.py
fixed scaling

@@ -176,7 +176,7 @@ def format_graph(graph,prop,nettype,site):
       ytext="NODF"
     graph.yaxis.label.configure(text=ytext,char_size=1,just=2)
   graph.legend.configure(box_linestyle=0,fill=0,fill_pattern=0,char_size=.5,
-    loc=(0.635,3.8),loctype='world')
+    loc=(0.725,3),loctype='world')
   graph.panel_label.configure(placement='iul',char_size=.75,dx=.02,dy=.01)
   # if prop=='C' and nettype=='SG':
   #   graph.xaxis.label.configure(text='Salix-Galler',place='opposite',char_size=1.25,just=2,loctype='world')
@@ -244,8 +244,15 @@ def main():
 
       grace.multi(rows=2,cols=2,vgap=.04,hgap=.1)
       grace.hide_redundant_labels()
-      grace.set_row_xaxislabel(colspan=(None,None),row=1,label="Percent of links detected",just=2,char_size=1.5,perpendicular_offset=0.05)
 
+      for graph in grace.graphs:
+        print graph.get_view()
+
+      grace.graphs[0].set_view(0.15, 0.7020588235294118, 0.4970588235294118, 0.95)
+      grace.graphs[1].set_view(0.5970588235294119, 0.7020588235294118, 0.95, 0.95)
+      grace.graphs[2].set_view(0.15, 0.4141176470588234, 0.4970588235294118, 0.6620588235294117)
+      grace.graphs[3].set_view(0.5970588235294119, 0.4141176470588234, 0.95, 0.6620588235294117)
+      grace.set_row_xaxislabel(colspan=(None,None),row=1,label="Percent of links detected",just=2,char_size=1.5,perpendicular_offset=0.075)
 
       grace.write_file('../../manuscript/figures/'+nettype+'_posterior_properties_'+site+'.eps')
 

### 2018-07-02 code/figure_generation/posterior_property_dotplot.py

@@ -213,7 +213,11 @@ def main():
       graph=populate_graph(graph,prop,nettype,obs,whiskers)
 
 
+
   grace.multi(rows=4,cols=2,vgap=.04,hgap=.07)
+  for graph in grace.graphs:
+    print graph.get_view()
+  grace.graphs[0].set_view(0.15,0.15,0.95,0.85)
   grace.hide_redundant_labels()
   grace.set_row_xaxislabel(colspan=(None,None),row=3,label="Percent of links detected",just=2,char_size=1,perpendicular_offset=0.05)
 

### 2018-07-02 code/simulation_example.R
final updates

@@ -52,7 +52,7 @@ Make_B<-function(A,n_samples){
 # Detection probability might therefore follow a beta distribution with parameters 2 and 10
 
 # Assume that the number of co-occurrences for each species pair is uniformly distributed
-# Assume that the probability of detecting an interaction, for a given number of co-occurrences, is uniformly distributed
+# Assume that the probability of detecting an interaction, for a given number of co-occurrences, is beta distributed
 # The overall detection uncertainty is a binomial process depending on the number of co-occurrences and detection probability for each interaction
 
 Make_C<-function(B,n_samples){
@@ -87,7 +87,6 @@ test_network<-function(net){
 	NODF=nestedness(trimmed,null.models=FALSE)$temperature
 
 	properties=c(n_plants,n_gallers,C,mean_L_per_p,mean_L_per_g,NODF)
-	# properties=c(n_plants,n_gallers,C,mean_L_per_p,mean_L_per_g)
 	return(properties)
 }
 
@@ -98,27 +97,28 @@ test_network<-function(net){
 # colnames(B_props)=c("N_plants","N_gallers","C","L_per_plant","L_per_galler")
 # C_props=matrix(nrow=1000,ncol=5)
 # colnames(C_props)=c("N_plants","N_gallers","C","L_per_plant","L_per_galler")
-A_props=matrix(nrow=10,ncol=3)
+A_props=matrix(nrow=100,ncol=3)
 colnames(A_props)=c("L_per_plant","L_per_galler","NODF")
-B_props=matrix(nrow=100,ncol=6)
+B_props=matrix(nrow=10000,ncol=6)
 colnames(B_props)=c("N_plants","N_gallers","C","L_per_plant","L_per_galler","NODF")
-C_props=matrix(nrow=1000,ncol=6)
+C_props=matrix(nrow=1000000,ncol=6)
 colnames(C_props)=c("N_plants","N_gallers","C","L_per_plant","L_per_galler","NODF")
-for(a in 1:10){
+for(a in 1:100){
 	print(a)
 	A=Make_A(n_plants,n_gallers,connectance)
 	properties=test_network(A)
 	A_props[a,]=properties[4:6]
 	# A_props[a,]=properties[4:5]
-	for(b in 1:10){
+	for(b in 1:100){
 		B=Make_B(A,n_samples)
 		properties=test_network(B)
-		rownum=b+(a-1)*10
[…]

### 2018-07-03 manuscript/CI_preprint.tex
removing the details from Ecol Letts

\documentclass[12pt]{article}
\usepackage{amsmath} 
\usepackage[dvips]{graphicx}
\usepackage{multirow} 
\usepackage{geometry} 
\usepackage{pdflscape}
\usepackage[labelfont=bf]{caption} 
\usepackage{setspace}
\usepackage[running]{lineno} 
% \usepackage[numbers,sort]{natbib}
\usepackage[round]{natbib} 
\usepackage{array}
\usepackage{hyperref,url}
\usepackage{float}
\usepackage{mdframed}
\makeatletter

% this creates a custom and simpler ruled box style
\newcommand\floatc@simplerule[2]{{\@fs@cfont #1 #2}\par}
\newcommand\fs@simplerule{\def\@fs@cfont{\bfseries}\let\@fs@capt\floatc@simplerule
  \def\@fs@pre{\hrule height.8pt depth0pt \kern4pt}%
  \def\@fs@post{\kern4pt\hrule height.8pt depth0pt \kern4pt \relax}%
  \def\@fs@mid{\kern8pt}%
  \let\@fs@iftopcapt\iftrue}

% this code block defines the new and custom mdframed environment
\newmdenv[rightline=true,bottomline=true,topline=true,leftline=true,linewidth=2pt]{fullbox}

\newcommand{\methods}{\textit{Materials \& Methods}}
\newcommand{\SI}{\textit{Appendix}~}

\topmargin -1.5cm % 0.0cm 
\oddsidemargin 0.0cm % 0.2cm 
\textwidth 6.5in
\textheight 9.0in % 21cm
\footskip 1.0cm % 1.0cm

\usepackage{authblk}

\title{A quantitative framework for investigating the reliability of network construction}

\author{Alyssa R. Cirtwill$^{1\dagger}$, \&  Anna Ekl\"{o}f$^{1\ddagger}$, Tomas Roslin$^{2\star}$, Kate Wootton$^{2\diamond}$, Dominique Gravel$^{3\triangleright}$}
\date{\begin{minipage}[h]{0.6\textwidth}
\small$^1$ Department of Physics,\\
Chemistry and Biology (IFM)\\ 
Link\"{o}ping University\\
Link\"{o}ping, Sweden\\
$^2$ Department of Ecology\\ 
P.O. Box 7044\\ 
Swedish University of Agricultural Sciences \\ 
SE-750 07 Uppsala, Sweden\\
$^3$ D\'{e}partement de biologie\\ 
Universit\'{e} de Sherbrooke\\ 
Sherbrooke, Canada
\end{minipage}\begin{minipage}[h]{0.4\textwidth}
\small$^\dagger$ Corresponding author:\\
alyssa.cirtwill@gmail.com\\
tel: +46 723 158464\\
$^\ddagger$ anna.eklof@liu.se\\
$^\star$ tomas.roslin@slu.se\\
$^\diamond$ kate.wootton@slu.se\\
$^\triangleright$ dominique.gravel@usherbrooke.ca
\end{minipage}
}

\renewcommand\Authands{ and }

\begin{document} 
\maketitle 
\raggedright
\setlength{\parindent}{15pt}

\vspace{-.4in}

{\small
\section*{\small Statement of authorship}

DG designed the analytical approach. AC and DG wrote the code. AC performed statistical analyses. All authors contributed to writing and revising the manuscript.

\section*{\small Data accessibility}

All data used in this study have been independently published and are accessible following the references provided in text.

\section*{\small Keywords}

ecological networks; probabilistic interactions; Bayesian networks; sampling error; spatial variability; temporal variability; uncertainty

% \section*{\small Details}

% \begin{minipage}[h]{0.6\textwidth}
% \begin{itemize}
% \item Running title: Quantitative network construction
% \item Article type: Ideas and Perspectives
% \item Number of references: 36
% \item Number of figs, tables, \& text boxes: 8 % Limit is 10
% \end{itemize}
% \end{minipage}\begin{minipage}[h]{0.4\textwidth}
% \begin{itemize}
% \item Text box 1 word count: 381
% \item Text box 2 word count: 210
% \item Abstract word count: 199
% \item Main text word count: 6482 % Including 18 page numbers. % No abstract, acknowledgements, references, table or figure legends. Limit is 7500
% \end{itemize}
% \end{minipage}
% }

\newpage

\begin{spacing}{1.0}

\section*{Abstract}

  Descriptions of ecological networks typically assume that the same interspecific interactions occur each time a community is observed. This contrasts with the known stochasticity of ecological communities: community composition, species abundances, and link structure all vary in space and time. Moreover, finite sampling generates variation in the set of interactions actually observed. Here we develop the conceptual and analytical tools needed to capture uncertainty in the estimation of pairwise interactions. To define the problem, we identify the different contributions to the uncertainty of an interaction and its implications for the estimation of network properties. We then outline a framework to quantify the uncertainty around each interaction. We illustrate this framework using the most extensively sampled network to date. We found significant uncertainty in estimates for the probability of most pairwise interactions which we could, however, limit with informative priors. Through these efforts, we demonstrate the utility of our approach and the importance of acknowledging the uncertainty inherent in network studies. Most importantly, we stress that networks are best thought of as systems constructed from random variables, the stochastic nature of which must be acknowledged for an accurate representation. Doing so will fundamentally change networks analyses and yield greater realism.
  % Can be up to 200 words. This is 200 exactly.

% \linenumbers
\clearpage

\section*{Introduction}

    Representing an assemblage of species as a network offers a convenient summary of how the community is constructed as networks simultaneously describe species composition and interactions between species. A tabulation of the nodes (species) and their relative abundances forms the basis for traditional metrics of community composition such as alpha diversity. To move from these simpler metrics to a network framework, the tabulation of nodes is combined with interactions (links between nodes) so that networks provide additional, higher-order information on community structure. While this additional information is useful (as, for example, interactions can affect changes in species abundances over time), empirical descriptions of ecological networks are still limited because they are usually considered to be static representations of the communities and interactions they describe. That is, whether the network is assembled based on aggregated data, a single intensive ``snapshot" sample, or expert knowledge, interactions are assumed to occur deterministically wherever and whenever the community is observed~\citep{Olesen2011a}.

    The assumption of static communities contrasts significantly with the widely recognised stochasticity of ecological communities~\citep{Gotelli2000}. Community composition and species abundances vary from site to site~\citep{Baiser2012} and over time within a site~\citep{Olesen2011a}. Likewise, interactions vary over space~\citep{Kitching1987,Baiser2012}, time~\citep{Kitching1987,Olesen2011a}, and between individuals of a given species~\citep{Pires2011a,Fodrie2015,Novak2015}. We emphasise that variability in community composition and interactions may or may not be closely related. The removal of a species from a site will obviously also remove its interactions but, conversely, the co-occurrence of potentially interacting species does not in itself guarantee that they will interact at a given place and time. Interactions can be lost if the interaction partners remain present but are separated in time or are too rare to detect each other~\citep{Tylianakis2010}. Interactions can also fail to occur because of environmental contingencies~\citep{Poisot2015}, or through changes to individual preferences~\citep{Fodrie2015}.

    Beyond ``true" variation in network structure, several researchers have pointed to the importance of sampling intensity for the assessment of network structure (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007}). An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to document interactions than species~\citep{Poisot2012}. As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Poisot2016}. Early work in this vein includes food-web models using likelihood-based approaches~\citep{Allesina2008} or Gaussian~\citep{Williams2010} or binomial~\citep{Rohr2016} probability functions for each possible interaction. These models may include information about species' traits~\citep{Rohr2016} or may attempt to reproduce empirical network structures using a set of simple rules~\citep{Allesina2008,Williams2010}.

    Despite these preliminary efforts, to date we lack the quantitative methodology to deal with the uncertainty generated by spatiotemporal variation in ecological interactions and by sampling. Even in extremely well-sampled networks, uneven sampling across species (or pairs of species) can lead to the erroneous inference that some species do not interact because they co-occur rarely or have not yet been observed together - even if they do interact when they do co-occur (see Box 1 for an example). Nearly all network studies will thus neglect some interactions, necessitating an approach that acknowledges this uncertainty.

    In this study, we formalise the description of interactions between species as probabilities and develop analytical tools to capture the uncertainty in the estimation of these interactions. We focus on binary interactions as a first step, but the framework could be expanded to deal with interaction frequencies and strength. To define the problem, we first identify the different contributions to the uncertainty of an interaction and discuss the implications of each source of uncertainty for the properties of ecological networks. Next, we develop an analytical framework to quantify the uncertainty around interactions in an empirical web. We illustrate this framework using the most extensively sampled network to date (Box 1).  Finally, we offer tangible recommendations for improved descriptors of ecological interactions. Through these efforts, we demonstrate both the utility of our approach and the importance of acknowledging the uncertainty inherent in network studies.

\section*{Why do some interactions \emph{not} occur?}

  To define the problems associated with quantifying ecological interaction networks, we will start from the perspective of an empirical community ecologist faced with the task of describing a previously unknown interaction network. This ecologist will be interested in generating a description of the species/nodes present and the links between them~\citep{Roslin2016}.  Importantly, the information sought is conveyed by both the presence and \emph{absence} of links. Presences and absences are not, however, equally certain. An observed link will always remain an observed link but there are multiple reasons why a given link may not be observed. Thus, the detection of any interaction is a stochastic process. We define three nested levels of uncertainty contributing to this stochasticity: interaction uncertainty, process uncertainty, and detection uncertainty.

    \subsection*{Interaction uncertainty}

      First, and most fundamentally, we do not know whether or not a pair of species have the appropriate characteristics (or traits) to interact. We define the probability of an interaction $L$ given those characteristics $\mathbf{T}$ as $P(L | \mathbf{T})=\lambda$. Obviously, if $k$ (the number of observed interactions) is 0, it is possible that the two species would not interact even if there were no external constraints (e.g., temporal or environmental separation) preventing the interaction from co-occurring. As a simple example, a prey species may be too large to be consumed by a particular predator. In such cases, $\lambda$ would take a value of 0 and there would be no uncertainty.

      Nevertheless, it is also possible that the interaction is a rare phenomenon with $\lambda>0$ that has not yet been documented. This source of uncertainty is the one documented by trait-matching models~\citep{Bartomeus2016}. It arises because every model is imperfect and lacks information (i.e. about traits) that could be used to define constraints on the interaction~\citep{Dormann2017}. Further study may, however, eventually reveal the traits of interest and allow us to reduce interaction uncertainty. In other words, with sufficient sampling and all information accessible, this interaction probability $\lambda$ should either tend to 0 or to 1.

    \subsection*{Process uncertainty}

     Even when an interaction is feasible, i.e. $L=1$, it may not occur at a given location or moment in time because of local constraints such as inclement weather or the lack of suitable habitat. We define the realisation of the interaction process with the variable $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L=1)=\chi$. This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology about the contingencies of interactions. Phenological matching~\citep{MillerRushing2010,Gezon2016}, species preferences~\citep{Pires2011,Novak2015,Coux2016}, and fear effects of other species~\citep{Luttbeg2005,Wirsing2008} are just some of the factors contributing to variation in the frequency of interactions between a given pair of species. Although some of the factors leading to process uncertainty can be addressed in mesocosm studies of networks (e.g., environmental conditions can be held stable), process uncertainty is likely inevitable in the field.

    \subsection*{Detection uncertainty}

      Lastly, measurement errors are a pervasive source of uncertainty in the observation of ecological processes. Given that an interaction is feasible and occurs under the local conditions ($L$=1 and $X$=1), we may define the detection of an interaction, $D$, as a stochastic process with the associated probability $P(D|X=1,L=1)=\delta$. Detection failure could happen for several reasons including failure to rear a parasitoid, species mis-identification, or because the interaction is very rare (see~\citet{Wirta2014} for examples of some of these difficulties and partial solutions to them). Some sources of detection error can be minimised with appropriate sampling effort ($\delta$ will converge to one with increasing number of samples), but other sources are often difficult to reduce (e.g. the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification as in~\citealt{Wirta2014,Frost2016}).

\section*{Estimating detection and process uncertainty}

    Together, the combination of these three sources of uncertainty --interaction uncertainty, process uncertainty, and detection uncertainty-- results in a range of potential explanations for the observation of an absence of interaction ($D$, $X$, and/or $L = 0$). The ecologist wanting to describe the network, however, is specifically interested in the situation where $L = 0$ (i.e., in true absences). Thus, while there is no difficulty interpreting the observation of an interaction, the observation of an absence of an interaction offers more of a challenge since it must be decomposed into different quantities. It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e. where the interaction occurred at the location but was not observed, and $D=1 \cup X = 0 \cup L =1$, i.e., where the interaction is feasible and would have been detected but did not occur at the local site. The occurrence of a true absence, our quantity of interest, corresponds to the joint event $L=0 \cup X=1 \cup D=1$ but in reality an empirical ecologist will measure the marginal probability $P(L) = k/n$ where $k$ is again the number of observed interactions and $n$ the number of observed co-occurrences.

    The considerations above raise a major challenge: when faced with empirical data, how may we infer whether unobserved interactions went undetected due to sampling or whether they truly do not occur? How then may we refine our sampling approaches to reduce uncertainties, and do we gain insights into the impact of multiple processes on field observations? Importantly, some sources of uncertainty can be minimised with appropriate sampling design and efforts while other sources are difficult or impossible to reduce since they are generated by chance variation created by the very process in which we are interested. Given this multifaceted problem of uncertainty, what can we do to separate the different types of variation and reduce those that can be reduced?

    The obvious rule of thumb is to ``sample more" (see Fig.~\ref{upper_limits} for a demonstration of the power of increasing sample size). Sampling more will clearly reduce uncertainty regarding the upper bound of the probability of interaction and it will also increase the probability of detecting unlikely interactions (e.g.,. interactions where $L$=1 but process uncertainty is high).
    Despite these benefits, we note that there are limits to the utility of increased sampling. Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present; see Fig.~\ref{histograms}E-F), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions. Thus, the more we sample, the more zeros will appear in our interaction matrix.

    In one endeavour to determine whether unobserved interactions were undetected due to sampling, or whether they truly do not occur,~\citet{Weinstein2017} used repeated sampling rounds to estimate the daily probability of detecting a hummingbird interaction, and to thereby model detection and process uncertainty. While conceptually attractive, this approach is unsuitable for interactions occurring over longer time scales (e.g., associations between hosts and parasitoids with a single generation per year), or very rare interactions which might not occur on any of the sampling days or might involve individuals of a species that is not under observation. What is worse, the problem persists that the absence of an interaction of a given day could  either be because it was impossible on that day despite being otherwise feasible [$P(X|D=1,L=1)=0$], because interaction did occur but could not be observed [$P(D|X=1,L=1)=0$], or any combination of the two. From a conceptual perspective, this approach therefore fails to satisfactorily distinguish between sources of uncertainty. Most importantly, if two species are never observed co-occurring during several days of sampling then we have learned nothing about their probability of interacting if they should ever co-occur. In other words, there is no information about interactions without co-occurrence.

    An added complication is that not all sources of uncertainty are proportional to sample size. To record an interaction between A and B, we need to identify both partners correctly (a non-trivial problem in many food webs; e.g.~\citealp{Kaartinen2011,Roslin2016}) and be able to resolve all interactions with a similar likelihood. For both molecular and rearing techniques, certain types of interactions may go unnoticed due to technical challenges~\citep{Wirta2014}. This can bias the set of recorded interactions. The bottom line is that separating different sources of uncertainty is difficult indeed. As an alternative to abandoning empirical networks or continuing to ignore the uncertainty inherent in undetected observations, we propose that some insight regarding the detectability of interactions between species not found co-occurring in a focal system may be gained from data on other species pairs in the same or a similar system.

\section*{A naive quantification of uncertainty}

  To progressively dissect the different contributions to uncertainty, we will start by considering how we could naively quantify interaction probability and its associated uncertainty \emph{for an interaction that has not yet been observed}. We consider the case where a pair of species have been observed co-occurring $n$ times, of which they have been observed to interact in $k = 0$ cases. We now aim to evaluate the uncertainty of this interaction. We consider the occurrence of an interaction as a Bernoulli trial. Consequently, the number of successes $k$ over $n$ trials will follow a binomial distribution:

      \begin{equation}
        X \sim Bin(n,\lambda) ,
      \end{equation}

      \begin{equation}
         P(X = k|\lambda,n) = {n \choose k}\lambda^k(1-\lambda)^{n-k} . 
         \label{likelihood}
      \end{equation}

  \noindent The parameter $\lambda$, the probability of observing an interaction over an infinite time interval and area, is the quantity we want to estimate from empirical data. 
  The maximal likelihood estimate (MLE) of $\lambda$ is straightforward to find given $k$ and $n$:

      \begin{equation}
        \lambda_{MLE} = \frac{k}{n}  .
        \label{theta_MLE}
      \end{equation}

  The variance of a Bernoulli experiment is $n\lambda$(1-$\lambda$). It is important to remember that this variance describes the variability of the number of successes $k$ for $n$ trials and is not the variance associated with the estimation of $\lambda$. Given this variance, it is possible to compute the confidence interval for the MLE of $\lambda$ using any of several methods, including the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]). Finding this estimate is therefore quite straightforward, but it nonetheless has two drawbacks. First, $\lambda$ is not a single point estimate but rather a random variable with an unknown distribution. This means that if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact. Rather, $k = 0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless a substantial chance that the two species \emph{could} interact. In the situation where $k>0$, in contrast, we are sure that the interaction is feasible ($L = 1$) but still cannot be sure of the cause if the interaction is not observed at some sites/times (i.e., we cannot say why $k<n$). There may be local constraints ($X=0$) or we might simply not observe the interaction in every sample ($D<1$).

  Second, where the number of samples $n$ is very low (some pairs of species may never have been documented as co-occurring), there will be considerable uncertainty around our estimate of $\lambda$. In Fig.~\ref{upper_limits} and Box 2, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda$ varies with sample size. At a small sample size, the 95\% confidence interval spans all values of $\lambda$. To establish that species are not interacting with any acceptable certainty requires tens of observations of the two species co-occurring but not interacting. As most data sets will lack such extensive sampling across all species pairs, we can use a Bayesian approach to supplement what data we do have with other sources of information.

\section*{Bayesian approach to infer interaction probabilities}

    \subsection*{Posterior distribution of the interaction probability}

      Here we adopt a Bayesian approach to estimate the posterior distribution of the parameter $\lambda$ :

      \begin{equation}
        \underbrace{P(\lambda|k,n)}_{Posterior} = \frac{\overbrace{P(k|\lambda,n)}^{Likelihood}\overbrace{P(\lambda)}^{Prior}}{\underbrace{P(k|N)}_{Normaliser}} .
        \label{posterior}
      \end{equation}

      According to the above description, the likelihood is simply the binomial distribution (Eq.~\ref{likelihood}). Since $\lambda$ is a probability, it is bounded between 0 and 1 and the most appropriate prior distribution is the beta:

      \begin{equation}
        \lambda \sim Beta(\alpha,\beta) , \label{prior}
      \end{equation}

      \noindent which has two shape parameters, $\alpha$ and $\beta$.

     The beta-binomial distribution is a conjugate distribution of the binomial distribution. This allows us to analytically compute the posterior distribution of a binomial model with a beta prior distribution. We can re-write the posterior distribution of $\lambda$ as:

      \begin{equation}
        P(\lambda|k,n) = \frac{\lambda^{\alpha+k-1}(1-\lambda)^{\beta+n-k-1}}{B(\alpha+k,\beta+n-k)} , \label{posterior2}
      \end{equation}

      \noindent where the function $B$ is the beta function. The posterior distribution of $\lambda$ therefore follows the beta distribution with new parameters $\alpha'= \alpha+k$ and $\beta'=\beta+n-k$. The weight of the prior on the posterior distribution can be understood from these parameter definitions: the difference between the posterior and the prior will increase with $k$ and $n-k$. In other words, the distribution of $\lambda$ for better-sampled pairs of species will rely less on the information used to build the prior distribution and depend more on the observed data.
      When plotted, we find the shape of the distribution gets narrower with $k$ and $n$ (Fig.~\ref{Salix_pdfs}).

    \subsection*{Moments and other properties}

      It is common to preform analyses that require calculating higher-order network properties in interaction networks. The fact that the posterior distribution of $\lambda$ follows a beta distribution makes it straightforward to compute moments and other properties needed for this.

      The \textbf{average} of $\lambda$ is: 
          \begin{equation}
            \bar{\lambda} = \frac{\alpha+k}{\alpha+\beta+n} ,
            \label{mean}
          \end{equation}

        and its \textbf{variance} is:  
          \begin{equation}
            Var(\lambda|k) = \frac{(\alpha + k)(\beta + n - k)}{(\alpha + \beta + n)^{2}(\alpha + \beta + n +1)}
            \label{variance}
          \end{equation}

        The \textbf{mode} of the distribution is:
          \begin{equation}
            \hat{\lambda} = \frac{\alpha + k - 1}{\alpha + \beta + n - 2} .
            \label{mode}
          \end{equation}

    \subsection*{The prior distribution}

      Parameters $\alpha$ and $\beta$ determine the shape of the prior distribution, which follows a beta distribution. These are called hyper parameters. Below we identify four ways to formulate the prior distribution of $\lambda$.

      \subsubsection*{Uninformative prior}

          In the absence of any external information, an uninformative prior is the most conservative hypothesis for the distribution of $\lambda$. The beta distribution is in this case a uniform distribution, specified with hyper parameters $\alpha=1$ and $\beta=1$.

      \subsubsection*{Distribution of connectance}

          The ecological network literature boasts a collection of networks for which connectance has been calculated and for which we can thus define the connectance distribution. Connectance is measured as $C = L/S^2$, where $L$ is the number of interactions and $S$ is the number of species. It measures the filling of an interaction matrix and thereby expresses the average probability that any two species interact with each other. If we know only the mean $\overline{C}$ and the variance $\sigma_C^2$ of the distribution of $C$,          then the beta parameters could be computed as follows using the method of moments:

          \begin{equation}
          \alpha = \overline{C}(\frac{\overline{C}(1-\overline{C})}{\sigma_C^2}-1) ,
          \end{equation}

          \begin{equation}
          \beta = (1-\overline{C})(\frac{\overline{C}(1-\overline{C})}{\sigma_C^2}-1) .
          \end{equation}

      \subsubsection*{Degree distribution or interaction probabilities}

          The degree of a node in a network is defined as its number of connections to other nodes. The degree distribution of a network is then the probability distribution of these degrees over the whole network and the standardised degree could therefore be interpreted as an interaction probability. It is consequently possible to use the degree distribution to inform the prior distribution. The degree distribution could come from several networks, from a similar network (e.g. a known network at slightly different location) or from the network of interest if interaction probabilities for some species are already documented. The latter approach allows researchers to apply information from known, abundant species to the rarest species for which interactions are less frequently documented.

          If our focal network describes a system similar to that in a known network, we can use the distribution of interaction probabilities in that network to inform our prior. The probability of any interaction $L_{ij}$ depends on the degrees of species $i$ and $j$. Using normalised degrees $\Delta_i$ and $\Delta_j$ (i.e., degrees divided by the number of species in the network), we can obtain the probability of interaction $L_{ij}$=$\Delta_i\times\Delta_j$. Similar to the procedure for degree distribution, the distribution of these interaction probabilities can be used to establish a prior distribution before any data from the focal network are collected. For distributions of either degrees or interaction probabilities, the procedure for the estimation of the hyper parameters follows the same approach as described above for connectance except that each measurement is at the individual interaction level instead of the network level.

      \subsubsection*{Trait-matching function}

          As a fourth and final approach, it may be possible to obtain the prior distribution of $\lambda$ using the outcome of a trait-matching model, provided such a model has been parameterised using external data and relevant traits are available. In such a case, the prior distribution would follow the function $P(\lambda|\mathbf{T})=f(\mathbf{T})$ based on a set of traits for both species $\mathbf{T}$. There are several techniques available to perform this inference of interaction probability, some of which are Bayesian, and we refer to~\citet{Bartomeus2016} and~\citet{Weinstein2017} for recent reviews about this topic. Note that in this case the prior might not be beta-distributed and numerical methods might be required to compute the posterior distribution.

\section*{A quantitative example}

  The Bayesian framework can be illustrated with a simple quantitative example. Suppose we have $n = 10$ observations of co-occurrence between species $i$ and species $j$ in a given time interval and area, and $k = 3$ observations of interactions. The maximum likelihood estimate of the interaction probability is simply $\lambda_{MLE} = 3/10 = 0.3$.

  Now consider we know that species $i$ is known to interact with 10 species (other than species $j$), which have the following degrees:

    \vspace{12pt}
    \noindent\emph{
      degree=c(14, 4, 2, 3, 17, 6, 2, 15, 1, 1)
        }.
      \vspace{12pt}

    If the network has 20 species total, this gives the normalised degrees:

    \vspace{12pt}
    \noindent\emph{
      norm\_degree=c(0.65, 0.20, 0.10, 0.15, 0.85, 0.30, 0.10, 0.75, 0.05, 0.05)}.
      \vspace{12pt}

    Species $i$ has a normalised degree of 0.55 (it interacts with species $j$ and 10 other species). We can combine the normalised degree of $i$ with the normalised degrees of its interaction partners to obtain the following set of interaction probabilities for species $i$ and each of its interaction partners:

    \vspace{12pt}
    \noindent\emph{
       int\_probs = c(0.358, 0.110, 0.055, 0.082, 0.468, 0.165, 0.055, 0.412, 0.028, 0.028) }.
      \vspace{12pt}

    The mean of these interaction probabilities is 0.176, approximately two-thirds the $\lambda_{MLE}$ obtained from the observed data. We can use the distribution of these interaction probabilities as our prior distribution and estimate the uncertainty surrounding our $\lambda_{MLE}$. With some simple R code (function ``calculate\_parameters", \emph{Appendix S1}), we obtain prior parameters $\alpha$=0.998 and $\beta$=4.63. Using these priors in equations~\ref{mean} and~\ref{variance} above (or in the R function ``calculate\_distribution" in \emph{Appendix S1}), we find a prior $\bar\lambda$=0.177 and var($\lambda$)=0.026. Adding the observed data ($n=10$, $k=3$) and using the same code, we obtain posterior parameters $\alpha'$=4.00 and $\beta'$=11.6 and a posterior $\bar\lambda$=0.256 and var($\lambda$)=0.012. Comparing the posterior distribution to the prior, we see that the posterior is closer to the observed data and that the additional data about interactions between species $i$ and $j$ has reduced the variance. We may also wish to calculate a credible interval (analogous to the frequentist confidence interval). This is also quite straightforward in R (see function ``credible\_interval" in \emph{Appendix S1}). In this case, a 95\% credible interval for $\bar\lambda$ is (0.080, 0.491).

    Now, consider the case where the two species have never been observed interacting across $n$ trials, i-e. $k=0$. The question is then ``what is the probability that these two species do not interact''? Since it is not possible to prove that the two species could never interact (strictly speaking, in a Bayesian approach $\lambda=0$ is impossible), we must fix a threshold below which we consider that there is no interaction ($\lambda \sim 0$). We call this threshold probability $\lambda*$. We then use the cumulative distribution function to estimate $P(\lambda<\lambda*|L=0,n)$ for different $n$. The function ``samples\_for\_threshold" in \emph{Appendix S1} calculates distribution function for $\lambda*$ with an increasing number of trials. This yields a surprising result: it requires \textgreater24 observations of no interactions to be 95\% sure that the interaction probability is smaller than $\lambda*$=0.1 (recall Fig.~\ref{upper_limits}, Box 2). Note the special case where there is no observation of the two species co-occurring, $n = 0$.  In this situation, the posterior distribution converges to the prior distribution since the data include no information on the probability with which species might interact should they co-occur.

\section*{Scaling up to networks - an empirical example}

    In the following section, we will provide an empirical example based on the well-sampled system of \emph{Salix}  plants, herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}; see Box 1 or \emph{Appendix S2} for a description). Using this dataset, we will demonstrate the derivation of prior distributions for the \emph{Salix}-galler and galler-natural enemy components of these networks and the differences between these priors and posterior distributions which include all information available in this dataset~\citep{Kopelke2017}. Finally, we will calculate network properties using a suite of networks sampled from these posterior distributions and show how the uncertainty around interactions that have not been observed impact these metrics.

  \subsection*{Computing the posterior distribution}

      In a strict Bayesian framework, we wish to use a prior distribution that does not rely on any information from the study at hand. Network data for a similar study system may, however, not be available. In that case, one might use the first sub-network collected as ``training data" to guide future sampling. To simulate this situation, we created priors using a single sub-network from the middle of the geographical distribution of the~\citet{Kopelke2017} dataset. To demonstrate how the use of data from a different system can affect the prior distribution and conclusions based on it, we repeated our analyses using priors derived from a much smaller \emph{Salix}-galler-natural enemy system~\citep[Data available from the Dryad Digital Repository: https://doi.org/10.5061/dryad.g7805]{Barbour2016}\nocite{Barbour2016Dryad}. This smaller system was much more densely-connected than that described in~\citet{Kopelke2017} and provided unreasonable distributions for interaction probabilities (\emph{Appendix S4}).

      To obtain the priors based on the Zillis sub-network, we estimated frequencies of \emph{Salix}-galler interactions based on the normalised degree of each species in each network component (see \emph{Appendix S3} for details and code). Specifically, we obtained prior parameters of $\alpha$=8.72, $\beta$=305 for the \emph{Salix}-galler component and $\alpha$=0.700, $\beta$=8.49 for the galler-natural enemy components of the network. After calculating these prior parameters, we were then able to estimate the posterior distribution of interaction probabilities given the additional information in our dataset.

      For species where no co-occurrences were observed ($n=0$), we can calculate the estimates for the mean and variance of $\lambda_{ij}$ directly from the prior parameters following equations~\ref{mean} and~\ref{variance} (see \emph{Appendix S1} for R implementation). For the \emph{Salix}-galler network, the prior distribution  was: $\bar\lambda$=0.028, var($\lambda$)=8.60$\times$10$^{-5}$. The prior distribution for the galler-natural enemy network was: $\bar\lambda$=0.076, var($\lambda$)=0.008. The posterior interaction probabilities obtained based on the Zillis sub-network were much lower than those obtained based on~\citet[Data available from the Dryad Digital Repository: https://doi.org/10.5061/dryad.g7805]{Barbour2016}; this emphasises the importance of using an appropriate study system when constructing a prior (\emph{Appendix S4}).

      For a pair of species with some observed co-occurrences ($n>0$), we can update the prior distribution with these data. If we consider only pairs of species which were observed to co-occur but not to interact, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs, giving $\alpha'$=$\alpha$ and $\beta'$=$\beta + n_{ij}$. As the most extreme case, consider a pair of species which co-occurred at all 374 sites and was never observed to interact. Using the priors described above, our distribution for the \emph{Salix}-galler network would become $\bar\lambda_{ij}$=1.27 $\times$ 10$^{-2}$, var($\lambda_{ij}$)=1.82 $\times$ 10$^{-5}$ while our distribution for the galler-natural enemy network would become $\bar\lambda_{ij}$=1.83 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=4.76. Distributions for both network components were very close to 0 with small variance about our estimate of $\lambda$; species $i$ and $j$ are extremely unlikely to interact at sites or times not included in our sample.

      For most pairs of species $i$ and $j$, however, $n_{ij}$ was much less than 374 and our posterior mean and variance therefore retain more of the influence of the prior. We can see this in the increasing means and variances as we decrease $n_{ij}$ (Fig.~\ref{Salix_pdfs}). The change in distribution as $n_{ij}$ decreases can also be shown  by calculating 95\% credible intervals for $\lambda$ (see the function ``credible\_interval" in \emph{Appendix S2}). The 95\% credible interval around the estimate of $\lambda$ also widens as $n_{ij}$ decreases from (0.001, 0.017) and (\textless0.001, 0.11) for hypothetical \emph{Salix}-galler and galler-natural enemy pairs that might be observed co-occurring at all 374 sites without any observed interaction to (0.152, 0.931) and (0.008, 0.364) for \emph{Salix}-galler and galler-natural enemy pairs that were never observed co-occurring. The 95\% credible interval for hypothetical \emph{Salix}-galler pairs widened from (0.006, 0.022) if the pair co-occurred at all sites to (0.013, 0.049) if they co-occurred at none. The 95\% credible interval for hypothetical galler-natural enemy pairs, meanwhile, widened from (0.00001, 0.008) to (0.0005, 0.304).

  \subsection*{How many samples are required to reach a minimal precision}

      Rather than calculating credible intervals for a posterior distribution after collecting data, we may wish to know how many data points are necessary to obtain a given level of confidence that two co-occurring species do not interact. The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact (Fig.~\ref{Salix_cdfs}; see function samples\_for\_threshold in~\emph{Appendix S1}). In our dataset, the entire 95\% credible interval was (0.013, 0.049). We may therefore be 95\% confident that the interaction probability for \emph{Salix} and galler species that have not been observed co-occurring is below 0.05. As the peak of the prior distribution for the probability of interaction between \emph{Salix} and galler probabilities is around 0.02 (Fig.~\ref{Salix_pdfs}), to be 95\% confident that the interaction probability for these species is below 0.01 would require 1029 observed co-occurrences with no interaction - far more than the number of sites in the~\citep{Kopelke2017} dataset.

      The number of samples required to be 95\% confident that the interaction probability between galler and natural enemy species is below a threshold also increases quickly as the threshold decreases. The 95\% credible interval is (\textless0.001, 0.303) for the probability of interaction between two species observed to co-occur but never interact. To be 95\% confident that the probability of interaction is below 0.1, 0.05, or 0.01 would require 15, 39, and 229 observed co-occurrences, respectively.

      Given the low levels of replication in most network studies, this implies that we should have fairly low confidence in many ``non-interacting" pairs of species. Even in the extensively replicated \emph{Salix}-galler-natural enemy dataset, very few species pairs were observed co-occurring frequently enough to reach these thresholds.  Regardless of our choice of prior, no species pairs were observed to co-occur frequently enough to reach the threshold for an interaction probability of 0.01. Discounting potential interactions, then, requires either a stronger prior expectation of no interaction (e.g. for forbidden interactions) or very extensive sampling. For all we know, most links absent from current descriptions of network structure may be so not because the species do not interact, but because we have not sampled deeply enough to detect them.

  \subsection*{Scaling up to network metrics}

    It is fairly straightforward to compute most network metrics when the different $\lambda$ of the adjacency matrix are known and assumed not to vary without variance~\citep{Poisot2016}. Several of these metrics derive directly from quantitative indices of network structure which are equivalent to $\lambda$. The remainder, originally defined for binary networks, can be adjusted to account for interaction probabilities between zero and one. It is not as easy, however, to understand how the uncertainty in these estimated interaction probabilities influences network metrics. Computation of these metrics involves non-linear functions. Since Jensen's inequality states that the average of a non-linear function of a stochastic variable differs from the function of the average of that variable, any uncertainty in the values of $\lambda$ could bias both the mean and variance of a network metric. One way to avoid potentially biased analytical calculation of network properties is to calculate the properties of a suite of simulated networks.

    Using the prior distributions and procedures described above, we calculated posterior probability distributions for \emph{Salix}-galler or galler-natural enemy pairs that were not observed interacting. Using these posterior distributions and assuming probabilities of 1 for pairs of species that were observed interacting, we created a suite of 100 webs of each network type by randomly sampling from each posterior distribution. After obtaining these posterior networks, we calculated the connectance of each web, as well as the number of links per resource (\emph{Salix} in the \emph{Salix}-galler networks or galler in the galler-natural enemy networks) and links per consumer. To demonstrate how these network metrics will be affected by detection uncertainty, we then created a suite of filtered networks for each posterior network. Networks were filtered by randomly sampling 99\%, 95\%, 90\%, 80\%, 70\%, 60\%, and 50\% of the interactions included in each posterior network. This gradient is akin to a gradient of sampling effort. For each level of detection accuracy, we created 100 randomly-sampled networks per posterior-probability network (giving 100 posterior networks and 1000 detection-filtered networks each for the \emph{Salix}-galler and galler-natural enemy networks). We then calculated the same network properties as described above.

    We find, perhaps not surprisingly, that the posterior webs for the Salix-galler network  had higher connectances than the original, observed web (C=0.028 for the observed web and 0.082 $\leq$ C $\leq$ 0.096 for the posterior webs; Fig.~\ref{posterior_webs}A). The number of links per \emph{Salix} species in the observed web ($L_{\emph{Salix}}$=2.71) was similar to those in the posterior webs (2.53 $\leq L_{\emph{Salix}} \leq$ 3.19; Fig~\ref{posterior_webs}C). The number of links per galler, however, was lower in the observed web ($L_{galler}$=1.47) than in the posterior webs, accounting for the increased connectance (4.67 $\leq L_{galler} \leq$ 5.88; Fig.~\ref{posterior_webs}E). There was a more substantial difference in the nestedness of the observed and posterior webs: the observed network had NODF=0.560 while the posterior networks were more nested (1.39 $\leq NODF \leq$ 1.94). Even the networks sampled with a detection filter of 50\% had non-zero nestedness (Fig.~\ref{posterior_webs}G). This last result highlights the potential for the possibility for network structure to vary when considering the possibility that unobserved species pairs may interact.

    Considering the galler-natural enemy networks, the connectance, mean links per galler, and mean links per natural enemy were also much lower in the observed web (C=0.078, $L_{galler}$=9.99, and $L_{natural enemy}$=7.45, respectively) than in the posterior webs (0.186 $\leq$ C $\leq$ 0.198, 13.4 $\leq L_{galler} \leq$ 14.6, and 23.4 $\leq L_{natural enemy} \leq$ 25.0). When the detection probability was relatively low (i.e., 50\%), however, the properties of randomised networks became similar to those in the observed webs (Fig.~\ref{posterior_webs}B,D,F). Nestedness was higher in the observed network (NODF=6.85) than in the posterior webs (6.31 $\leq NODF \leq$ 6.82; Fig.~\ref{posterior_webs}H); in this case, the stronger the detection filter the farther apart were the observed and posterior webs.

\section*{Conclusions/recommendations}

  Real interaction networks vary over several dimensions~\citep{Kitching1987,Olesen2011a,Pires2011a,Baiser2012,Fodrie2015,Novak2015} and to capture this variation we must turn from static descriptions of network structure to probabilistic descriptions. In this study, we have developed the analytical tools to capture the uncertainty in the estimation of pairwise interactions and a conceptual framework for its individual components: interaction uncertainty, process uncertainty, and detection uncertainty. Using this framework leads us to offer tangible recommendations for improved descriptors of ecological interactions. First, our analyses point to detection uncertainty as a major contributor to overall uncertainty of is establishing the absence of interaction. To counter this and establish true absences of interactions requires comparatively large sample size – on the order of 30-50 observations per species pair. Second, where such extensive sampling is not feasible, researchers should still acknowledge the varying levels of confidence surrounding the presence or absence of interactions between different pairs of species. Including the $n$ and $k$ values for each interaction will clearly indicate which unobserved interactions are most likely to be observed with further sampling and which estimates are more reliable. Third, the uncertainty around interactions (especially interactions that were not observed) should be incorporated in calculations of network properties like connectance or nestedness. Re-sampling networks based on a probabilistic understanding of networks is straightforward and gives distributions for network properties rather than point estimates. This not only acknowledges the fact that interactions vary over time and space but will also facilitate comparisons between networks. With confidence intervals around network metrics, we can not only say that one network is more connected than another but also whether the networks are more different than we would expect based on imperfect sampling of interactions. To facilitate these recommendations, we provide all code used in this paper in the supplementary material.

\section*{Acknowledgements}

  The authors thank Daniel Cartensen for fruitful discussion of the ideas in this manuscript. We also thank K\'{e}vin Cazalles for providing feedback on the manuscript. The authors also appreciate support from the Swedish Research Council (VR) for grant \#2016-06872 (to TR). Additional funding was provided by a Formas grant (\#942-2015-1262) to AE.

\end{spacing}
\clearpage

\captionsetup{singlelinecheck=false, font={stretch=1}}

\section*{Boxes and figures}

\begin{fullbox}{}
  \begin{spacing}{1.0}
    \textbf{Box 1: }\emph{Salix}-galler-natural enemy dataset.\\
    \indent As a case study, we use an extensively sampled \emph{Salix}-galler-natural enemy meta-network. This dataset consists of a single community type sampled across Europe: willow (\emph{Salix}) species, willow-galling sawflies, and their natural enemies. The data were collected over 29 years at 374 unique locations across Europe with a total of 641 site visits. Each site visit or each unique site can be considered as a network in its own right or as an independent sample from which to build the meta-network. Here we take the more conservative approach and pool visits to the same site for a sample size of 374 sub-networks. The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes. The high spatiotemporal resolution of this network and the unusually high sampling effort implemented at the site level makes this dataset particularly well suited for illustrating the difficulties in completely sampling a network and testing Bayesian approaches to overcome these difficulties.\\
    \indent We may begin by comparing the frequency of co-occurrences for pairs of species in each part of the network to reveal the challenge of having sufficient sampling to be confident that an interaction does not occur. Most pairs of species (3,986/4,992 \emph{Salix}-galler pairs and  9,794/12,096 galler-natural enemy pairs) are never found co-occurring and, for species that did occur together, the total number of co-occurrences was generally low (mean=4.24, variance=36.3 for \emph{Salix}-galler pairs; mean=3.87, variance=28.8 for galler-natural enemy pairs; Fig.~\ref{histograms}A-B). The bulk of these co-occurring species pairs were never observed to interact: only 2.82\% of \emph{Salix}-galler pairs and 7.76\% of galler-natural enemy pairs were observed interacting at one or more sites. Of those pairs that did interact, the incidence of interaction was also low (mean=12.0, variance=155 for \emph{Salix}-galler pairs; mean=4.04, variance=29.3 for galler-natural enemy pairs; Fig.~\ref{histograms}C-D). Thus, even in the most extensive data set that we could find, there was very little empirical data for each species pair. This suggests that limited sampling is a major source of uncertainty in all empirical networks. This dataset also illustrates the potential for increased sampling to not necessarily reveal more interactions as a pair of species that is able to interact may not be observed interacting in all samples where the pair co-occurs (Fig.~\ref{histograms}E-F).
  \end{spacing}
\end{fullbox}

\clearpage

\begin{fullbox}{}
    \begin{spacing}{1.0}
    \textbf{Box 2: }Calculating the credible interval around a probability estimate\\
  \indent Here we describe the derivation of the Clopper-Pearson credible interval for the estimated probability of interaction $\lambda$ of a pair of species observed co-occurring $n$ times and interacting $k$ times. As we are most interested in the probability of interaction between species pairs that have never been observed co-occurring, we consider only the case where $k=0$ over a variety of $n$. This is straightforward to do in R (see the function ``credible\_interval" in \emph{Appendix S1}).

  First, we must obtain the $\alpha$ and $\beta$ parameters for the prior distribution. In this study we obtained these parameters using the R~\citep{R} function fitdist from the package fitdistrplus~\citep{fitdistrplus}. Once $\alpha$ and $\beta$ are known, we can update them using our observed data. Specifically, we are interested in $\alpha'=\alpha+k$ and $\beta'=\beta+n-k$. These parameters can then be used to calculate a credible interval using the R~\citep{R} function qbeta. In the table below, we present the 95\% credible intervals for \emph{Salix}-galler and galler-natural enemy pairs with different numbers of observed co-occurrences ($n$) and no observed interactions ($k=0$), calculated using prior information derived from the Zillis sub-network~\citep{Kopelke2017}.

      % % # R code to make the table:
      % ns=c(0,1,2,5,10,15,20,25,50,100,150,200,374)
      % output=matrix(nrow=length(ns),ncol=5)
      % output[,1]=ns
      % for(r in 1:nrow(output)){
      %   interval1=credible_interval(calculate_parameters(sg_int_probs,ns[r],0),0.025,0.975)    
      %   interval2=credible_interval(calculate_parameters(gp_int_probs,ns[r],0),0.025,0.975)    
      %   output[r,2:3]=interval1
      %   output[r,4:5]=interval2
      % }
      \medskip
        \textbf{Table 1:} Here we give the lower and upper bounds of 95\% credible intervals for the probability of interaction $\lambda$ between \emph{Salix}-galler or galler-natural enemy pairs that have been observed co-occurring $n$ times but have never been observed interacting.\\
        \begin{tabular}{l  c c  c c }
        \multirow{2}{*}{$n$} & \multicolumn{2}{c}{\emph{Salix}-galler} & \multicolumn{2}{c}{galler-natural enemy}\\
         & Lower bound & Upper bound & Lower bound & Upper bound \\
        \hline
        0   & 0.013 & 0.049 & 5.39 $\times10^{-4}$ & 0.304 \\
        1   & 0.013 & 0.048 & 4.82 $\times10^{-4}$ & 0.276 \\
        2   & 0.013 & 0.048 & 4.35 $\times10^{-4}$ & 0.253 \\
        5   & 0.012 & 0.048 & 3.37 $\times10^{-4}$ & 0.203 \\
        10  & 0.012 & 0.047 & 2.45 $\times10^{-4}$ & 0.152 \\
        15  & 0.012 & 0.046 & 1.93 $\times10^{-4}$ & 0.121 \\
        20  & 0.012 & 0.046 & 1.59 $\times10^{-4}$ & 0.101 \\
        25  & 0.012 & 0.045 & 1.35 $\times10^{-4}$ & 0.087 \\
        50  & 0.011 & 0.042 & 7.72 $\times10^{-5}$ & 0.050 \\
        100 & 0.010 & 0.037 & 4.16 $\times10^{-5}$ & 0.027 \\
        150 & 0.009 & 0.033 & 2.84 $\times10^{-5}$ & 0.019 \\
        200 & 0.008 & 0.030 & 2.16 $\times10^{-5}$ & 0.014 \\
        \hline
        374 & 0.006 & 0.022 & 1.18 $\times10^{-5}$ & 0.008 \\
        \hline
        \end{tabular}
    \end{spacing}
\end{fullbox}

\clearpage

  \begin{figure}[h!]
      \caption{\textbf{A-B)} Most pairs of \emph{Salix} and gallers or gallers and natural enemies were never observed co-occurring despite the high levels of replication in our example dataset. For those pairs that were observed together at least once ($n_{ij}>0$), the number of observed co-occurrences was generally small (\textless10). Here we show a histogram of the number of pairs of species observed co-occurring at least once. 3986 \emph{Salix}-galler and 9794 galler-enemy pairs were never observed co-occurring: these pairs are omitted from the histogram. \textbf{C-D)} Most pairs of species that were observed at the same site were never observed interacting. Here we show a histogram of the number of observed interactions within pairs of co-occurring species. Species which co-occurred but never interacted are included in these histograms. \textbf{E-F)} Here we show, for each species pair, the number of observed interactions plotted against the number of observed co-occurrences. \emph{Salix}-galler pairs either are never observed interacting or interact almost every time they co-occur, while galler-enemy pairs had more variable frequencies of interaction. In panels E and F the red, dashed line indicates a 1:1 relationship between interactions and co-occurrences.}
      \label{histograms}
      \begin{center}
      \includegraphics*[width=.7\textwidth]{figures/Salix_Galler_histogram.eps}
      \end{center}
      \end{figure}

  \begin{figure}[h!]
    \caption{A simple example will illustrate the problem of imperfect detection of interactions. Assume that we want to infer the probability of an interaction between two species, $i$ and $j$. Now assume that in reality, interaction between $i$ and $j$ is completely impossible (i.e. the true $\lambda=0$) but the observer does not know this and seeks to estimate this interaction probability ($\lambda$). The number of observed interactions will follow a binomial distribution with number of interactions $k$ and number of observations $n$. Using this distribution, we can compute the credible interval of the estimated probability $\lambda$. Even assuming no added detection error in observing the incidence of the interaction, a single observation of species co-occurrence reveals very little regarding the probability of the interaction as the credible interval for a pair of species with one observation essentially spans from 0 to 1. Only with 35 observations will the upper limit of the credible interval be lowered to 0.1. Thus, adding more observations is certainly useful in controlling uncertainty, but the number of observations added needs to be very high. Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true credible interval for $\lambda$ when $k=0$ ($i$ and $j$ have not been observed interacting) for a variety of $n$ (observed co-occurrences of $i$ and $j$). Using a Bayesian approach with an informative prior can reduce the confidence interval about $\lambda$ for a given sample size. A threshold interaction probability of 0.1 is indicated by the dashed red line. }
    \label{upper_limits}
    \begin{center}
    \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
    \end{center}
    \end{figure}

  \begin{figure}[h!]
    \caption{Using prior distributions based on the \emph{Salix}-galler and galler-natural enemy networks sampled at a single site in~\citet{Kopelke2017}, we can calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting. Here we show posterior distributions for $\lambda$ in each network component ranging from the prior distribution ($n=0$ observed co-occurrence) to the distribution obtained when the pair of species has been observed co-occurring 100 times. The distribution narrows and approaches zero as the sample size increases. Likewise, the maximum likelihood estimator for the mean probability of interaction (diamonds at top of each panel) approaches zero and the 95\% credible interval (lines at top of each panel) narrows as sample size increases. \textbf{A)} The posterior distributions for $\lambda$ in the \emph{Salix}-galler component are narrower at low $n$ but shrink less with increased sampling than those for \textbf{B)} the distributions of $\lambda$ in the galler-natural enemy component.}
    \label{Salix_pdfs}
    \begin{center}
    \includegraphics*[width=.7\textwidth]{figures/Salix_Galler_pdfs_increasing_N_Zillis.eps}
    \end{center}
    \end{figure}

  \begin{figure}[h!]
    \caption{The number of samples required to achieve a given level of confidence that an interaction probability $\lambda_{ij}$ is below a given threshold varies with both parameters. With a low threshold, our confidence that $\lambda_{ij}$ is below the threshold increases rapidly with repeated observation of co-occurrence without interaction. Here we show the cumulative density functions for threshold probabilities of 0.5 (solid line), 0.25 (dashed line), 0.1 (dash-dot line), and 0.05 (dotted line) as well as the points at which the cdf reaches 0.90 (orange square), 0.95 (red circle), and 0.975 (blue diamond) for each threshold value. The large ticks along the x-axis indicate the number of samples associated with each of these points. \textbf{A)} In the \emph{Salix}-galler network component, the 95\% credible interval for $\lambda_{ij}$ when $n$=0 was (0.013, 0.049). We can therefore be at least 95\% confident that $\lambda_{ij}$ is below thresholds of 0.1 or 0.05 without any observed co-occurrence of species $i$ and $j$. To be confident that $\lambda_{ij}$ is less than 0.01, however, would require more observed co-occurrences than there are sites in our dataset. \textbf{B)} In the galler-parasitoid network component, the 95\% credible interval for $\lambda_{ij}$ was substantially broader and many observed co-occurrences ($\approx$ 15-35) are required to be 95\% confident that $\lambda_{ij}$ is below thresholds of 0.1 or 0.05.}
    \label{Salix_cdfs}
    \begin{center}
    \includegraphics[width=.5\textwidth]{figures/Salix_Galler_samples_and_cdfs_Zillis.eps}
    \end{center}
    \end{figure}

  \begin{figure}[h!]
    \caption{Here we show the mean connectance, links per resource (\emph{Salix} in the \emph{Salix}-galler networks and gallers in the galler-natural enemy networks), links per consumer, and nestedness (NODF) for networks assembled using posterior distributions based on a single sub-network in the~\citet{Kopelke2017} dataset (Zillis). We created 100 ``posterior-sampling" networks and then, for each of these, created 100 ``detection-filter" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network. This simulates imperfect detection of interactions in the field. Each point represents the mean network property (e.g., connectance) obtained from a set of 100 detection-filter networks, plotted against the value of the network property in the posterior-sampling network used to create the detection-filter networks. For each property and both network types, the posterior-sampling networks cover a relatively small range of network properties than the range covered by networks with varying detection probabilities. The value of each property decreases with the proportion of links included in the detection-filter networks.}
    \label{posterior_webs}   
    \begin{center} 
    \includegraphics[width=.7\textwidth]{figures/Salix_Galler_posterior_properties_Zillis.eps}
    \end{center}
    \end{figure}

\clearpage

    \bibliographystyle{ecol_let} 
    \bibliography{manual_abbrev} % Abbreviate journal titles.

\end{document}

### 2018-07-04 manuscript/CI_interactions.tex
final updates
shrank Figure 1 to compile on manuscript central. Added table of PhyloPic image attributions

@@
 Doing so will fundamentally change networks analyses and yield greater realism.
-  % Can be up to 350 words for MEE. This is 290 exactly.
+  % Can be up to 350 words for MEE.
 \end{enumerate}
@@
 Note that some low-probability interactions (e.g., lion predation on zebra) are included while others (e.g., lion predation on elephants) are not.
-For an illustration of the way in which these levels of uncertainty combine in simulated data, and the effects of uncertainty on network structure, see \emph{Appendix S1}.}
+For an illustration of the way in which these levels of uncertainty combine in simulated data, and the effects of uncertainty on network structure, see \emph{Appendix S1}.
+Attributions for PhyloPic silhouette images are given in \emph{Appendix S1-A}.}
     \label{conceptual_fig}
@@
     % \includegraphics*[height=.5\textheight]{figures/conceptual_fig.eps}
+    % \includegraphics*[height=.5\textheight]{Figure_1.eps}
     \end{center}
@@
       % \includegraphics*[height=.6\textheight]{figures/GP_histogram.eps}
+      % \includegraphics*[height=.6\textheight]{Figure_2.eps}
       \end{center}
@@
     % \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
+    % \includegraphics*[width=.8\textwidth]{Figure_3.eps}
     \end{center}
@@
     % \includegraphics*[width=.8\textwidth]{figures/GP_pdfs_increasing_N_Zillis.eps}
+    % \includegraphics*[width=.8\textwidth]{Figure_4.eps}
     \end{center}
@@
     % \includegraphics[width=.8\textwidth]{figures/GP_posterior_properties_Zillis.eps}
+    % \includegraphics[width=.8\textwidth]{Figure_5.eps}
     \end{center}

### 2018-07-04 manuscript/supplemental.tex
shrank Figure 1 to compile on manuscript central. Added table of PhyloPic image attributions

@@
   \end{figure}
+
+\clearpage
+
+\section*{Appendix S1-A: Attributions for PhyloPic images used in Figure 1 (main text)}
+
+  \begin{table}
+  \caption{Attributions for silhouette images taken from PhyloPic.org and used in Figure 1 (\emph{main text}).
+Terms for the CC BY-NC-SA 3.0 license can be found at \emph{https://creativecommons.org/licenses/by-nc-sa/3.0/}.
+Terms for the CC BY 3.0 license can be found at \emph{https://creativecommons.org/licenses/by/3.0/}.}
+  \begin{tabular}{l|ll}
+  Image & PhyloPic taxon & Attribution \\
+  \hline
+  Lion & Panthera leo & Public domain (uncredited) \\
+  Leopard & Panthera pardus & Lukasiniho (CC BY-NC-SA 3.0; image not changed) \\
+  Jackal & Canidae & Brian Gratwicke (photo) and T. Michael Keesey (vectorization). (CC BY 3.0; image not changed) \\
+  Elephant & Loxodonta africana & Jan A. Venter, Herbert H. T. Prins, David A. Balfour & Rob Slotow (vectorized by T. Michael Keesey) (CC BY 3.0; image not changed) \\
+  Zebra & Equus quagga & Cathy (CC BY-NC-SA 3.0; image not changed) \\
+  Impala & Aepyceros melampus & Public domain (unknown author) \\
+  Hare & Leporidae & Sarah Werning (CC A 3.0; image not changed) \\
+  Acacia & Acacia tree & Mattia Menchetti (public domain) \\
+  Grass & \multicolumn{2}{c}{Not sourced from PhyloPic. Public domain.} \\
+  \hline
+  \end{tabular}
+  \end{table}
 

### 2018-07-04 manuscript/supplemental.tex
fine-tuned attribution table

@@
 Terms for the CC BY 3.0 license can be found at \emph{https://creativecommons.org/licenses/by/3.0/}.}
-  \begin{tabular}{l|ll}
+  \begin{tabular}{l|l m{10cm}}
   Image & PhyloPic taxon & Attribution \\
@@
   Jackal & Canidae & Brian Gratwicke (photo) and T. Michael Keesey (vectorization). (CC BY 3.0; image not changed) \\
-  Elephant & Loxodonta africana & Jan A. Venter, Herbert H. T. Prins, David A. Balfour & Rob Slotow (vectorized by T. Michael Keesey) (CC BY 3.0; image not changed) \\
+  Elephant & Loxodonta africana & Jan A. Venter, Herbert H. T. Prins, David A. Balfour \& Rob Slotow (vectorized by T. Michael Keesey) (CC BY 3.0; image not changed) \\
   Zebra & Equus quagga & Cathy (CC BY-NC-SA 3.0; image not changed) \\
@@
   Hare & Leporidae & Sarah Werning (CC A 3.0; image not changed) \\
-  Acacia & Acacia tree & Mattia Menchetti (public domain) \\
-  Grass & \multicolumn{2}{c}{Not sourced from PhyloPic. Public domain.} \\
+  Acacia & Acacia & Mattia Menchetti (public domain) \\
+  Grass & & Not sourced from PhyloPic. Public domain. \\
   \hline

### 2018-10-29 manuscript/reply_to_reviewers.tex
starting reply file

\section*{Associate Editor}

\begin{refquote}
Your manuscript has been assessed by four different referees who agree that you touch upon a very important problem. However, they all feel your manuscript needs substantial improvements. They provide excellent advise on how to revise your manuscript and you should carefully consider all their comments. Overall, you do not acknowledge important past contributions and do not clearly explain the importance of the methodological issues you cover in your study. Importantly, referee 1 feels the real novelty of your study is the consideration of the importance and complexity of choosing prior information in constructing networks. Obviously, this is an issue in the context of Bayesian approaches, which are not necessarily well understood by empiricists, precisely the audience your manuscript should address. Please, follow very closely the suggestions of the referees when revising your manuscript.

\end{refquote}

\textbf{R:} We appreciate the thoughtful feedback by the four referees. We take particular note of the comments regarding the structure and grounding of our introduction and have worked to address this. Reviewer 2's comments take a different view of the purpose and scope of the manuscript than the other reviewers; we respect their ideas but feel that some are beyond the scope of the present manuscript. We therefore prioritise comments by the other three Reviewers and hope that, by addressing these, the purpose of our manuscript becomes clearer and our changes will at least partially satisfy Reviewer 2.

\section*{Reviewer 1}

Below I offer my thoughts on this well-written manuscript. Normally I condense my review into a few key points, but I found myself uncharacteristically divided with the paper as presented. At first, the introduction covers ground very well-trod by prior works and doesn’t really address its contribution. I was mostly frustrated by the rehashing of topics made by many previous papers, include many by the authors themselves. But then the paper seems to morph and pick up steam on L248. Rather than reaching towards an amorphous and grandiose “quantitative framework”, the authors briefly zoom into a very concise, and hugely important, question of choosing prior distributions for harnessing information among networks. This has been completely unexplored and merits attention. In ecology more broadly, priors are treated with timidity, as if we couldn’t dare to leverage past work on our current understanding. Personally, I have always felt limited by this standard. I applaud the authors for taking on this challenge, and I would like to see an introduction that merits and debates this question in much more detail. When should we use prior information? How do we go about constructing informed priors for networks? When can we use priors from the data in question? This is sometimes called approximate bayes (http://andrewgelman.com/2016/03/25/28321/), or empirical bayes, perhaps alluded to in the title, but not fully explained in the introduction. Should empirical priors be drawn from hyperpriors or fixed for each interaction? Can we combine qualitative information and quantitative information? This is all exciting ground that will open up new avenues for networks. Walking the reader through flat priors, informed priors and empirical priors is crucial for the importance of analysis to be understood by the reader. The use of empirical priors can be quite controversial, and should be atleast touched on in the discussion.
I’ve left my comments below on the introduction, but in my opinion, it should be almost wholly rewritten in favor of a more targeted question constructing networks using priors, which is the key novelty of the work and is mostly hidden by the current introduction. I’m not convinced any new analysis needs to be done, which speaks to the conflict between the current introduction and the actual data presented. I see the makings of a really nice paper here, and I’m confident the authors will be able to achieve this text revision.

Comments
The introduction flows well and is thoughtfully laid out. Given the enormous amount of literature in the field, it is not possible to provide a full set of citations. However, it seems remiss to not consider Jordano (2016) in the sampling section.

It’s a bit confusing to lead the reader towards a Bayesian analysis, and then immediately start with the MLE estimate. Why is this needed at all? (L162-186). Just start at 187?
I think a bit of space is wasted on defining the moments of the beta distribution. This is very googleable, and almost too thorough. I think the space is better utilized aligning the ecological challenge and the quantitative method.
I’m wrestling with the novelty of the work as presented and whether it reaches the standard for publication at MEE. Certainly, much of this logic is laid out in other works. The authors are well aware of this and have made significant contributions to this topic in the last few years. In particular, the authors should try to be much more explicit about the contribution they hope to offer that hasn’t been covered. I could list atleast two dozen papers here, but some key ones might include:
All have the theme of detection, occurrence and interaction as a central challenge in constructing
reliable networks. Several prior papers have offered Bayesian approaches, starting with the individual model by
While it is true that none of the above papers do the exact same thing as this manuscript, they all
orbit the same topic. L89 for example, seems to conflict with the two paragraphs immediately following it?
At the same time, the paper is clear and very readable. I wholly support the method and I think it is something critical that needs to be adopted by the community.

Having read the paper several times, I think that the authors are trying to cast their net too widely, even starting from the title. From that perspective, they don’t meet the expectation of new insight. However!! I was extremely interested in the brief discussion on using prior knowledge, especially the delicacy of trying to transfer information among networks (L248). My recommendation is to drastically reduce the grandiose attempt at a “quantitative framework for networks” (L1 – L246) and really zoom in on the contribution of transferring information among networks through informed priors.
Again L278, this is very well covered in concept by recent papers in MEE that include the authors of this work, as well as several by Weinstein, Bartomeus and others.

	Literature suggestions:

Jordano, P. (2016). Sampling networks of ecological interactions. Functional Ecology, 30(12), 1883–1893. doi:10.1111/1365-2435.12763

Bartomeus, I. (2013). Understanding Linkage Rules in Plant-Pollinator Networks by Using Hierarchical Models That Incorporate Pollinator Detectability and Plant Traits. PLoS ONE, 8(7), 1–9. doi:10.1371/journal.pone.0069200
Poisot, T., Cirtwill, A. R., Cazelles, K., Gravel, D., Fortin, M.-J., & Stouffer, D. B. (2016). The structure of probabilistic networks. Methods in Ecology and Evolution, 7(3), 303–312. doi:10.1111/2041-210X.12468
Poisot, T., Stouffer, D. B., & Gravel, D. (2015). Beyond species: why ecological interaction networks vary through space and time. Oikos, 124(3), 243–251. doi:10.1111/oik.01719
Graham, C. H., & Weinstein, B. G. (2018). Towards a predictive model of species interaction beta diversity. Ecology Letters. doi:10.1111/ele.13084
Gravel, D., Poisot, T., Albouy, C., Velez, L., & Mouillot, D. (2013). Inferring food web structure from predator-prey body size relationships. Methods in Ecology and Evolution, 4(11), 1083–1090. doi:10.1111/2041-210X.12103
Wells, K., & O’Hara, R. B. (2013). Species interactions: Estimating per-individual interaction strength and covariates before simplifying data into per-species ecological networks. Methods in Ecology and Evolution, 4(1), 1–8. doi:10.1111/j.2041-210x.2012.00249.x

\section*{Reviewer 2}

I do not know what to do with this.

The paper by A.Cirtwill and colleagues tackles a very interesting problem, quantifying the uncertainity of interactions, using three levels of nested uncertainity. The authors proposed a bayesian framework to obtain estimate of the parameters of the model and show the results of their approach on a recent dataset. The question of disentangling the true presence/absence of an interaction given a series of observations (replicates) is of primary interest and, seen in this light, the paper is tackling one of the hottest topics in the field.

The introduction is particularly pleasant to read and the problematic is well stated. However, the paper has also a number of weaknesses that I enumerate in the following :

1/ lack of references: the fundamental question about predicting interactions given some incertainity has been and is debated in many papers (see the seminal paper by Roger Guimerà and Marta Sales-Pardo, PNAS, 2009). Even if the proposed framework is probably not stated in its exact terms in the literature, bridges between existing approaches (beyond Ecology) and the one in the paper would be very welcomed. An appropriate discussion between points of convergence and difference would help the reader to appreciate the significance and the impact of the proposed methodology.

2/ network oversight: the approach considers that the interactions are independent, which is not the case in real data. Indeed, the paper is supposed to be “network-oriented“ but the methodology deals with independent interactions (e.g. the variables L,T,X and D introduced lines 62,77,101 are for instance not indexed by ij which could have suggested that the interactions were seen as a whole). Consequently, the mathematical framework remains quite simple and may not reflect nor model the processes governing the actual detection of interactions. Despite of this drawback, the proposed method is interesting but at least the authors should add some discussion on the limits of dealing with independent interactions,

3/ identifiability: the reader would appreciate that the authors discuss and prove the identifiability of the model. Indeed, the three levels of uncertainity are nested but one could wonder whether different parameters at the three levels can fit the same data with the same quality (i.e. no identifiability).  I would suggest this point to be addressed in a specific section.

4/ absence of simulations: the authors proposed an original approach based on a bayesian framework. Beyond the identifiability question (see above), the reader can question the power of the method. Usually, a methodological proposal comes with a complete simulation study that is supposed to show  the proposed model is adapted/suitable to the question and efficient to solve it. In the paper in its present form, the authors assume that the reader will be convinced by the results obtained on a single real dataset… In my opinion, the reader can’t be fairly convinced: how powerfull is the method? what can we say about the priors? how much data (n, k) is necessary to expect good results? An so on… Only a well-conducted simulation study can answer these questions.

5/ results&discussion too short: the reader is surprised to read 27 lines of raw results only… Given the amount of new methodology that is proposed, one can expect a complete description of its pros and cons. Obvisouly, a simulation study (see above) would enrich the results part. Forgetting about the length of these parts, it is still difficult to catch the key messages from the text, and it is not obvious to relate discussion and the obtained results (for instance,from l.343 to l.351).

6/ lack of rigorous notations: it is possible to understand the approach with the present notations but some improvements can help the reader because there are a series of inconsistencies. Here are some suggestions. The authors chose upper case letters L,T ,X,D for single entities whereas the mathematician is used to expect matrices or constants in upper case. Traditionaly, given species i and j, we would consider interaction L_ij, feasibility X_ij, detectionability D_ij...
Still, what is T?? not defined, never reused: is it a characteristics on i, on j, on both?
How can be D<1 on l.169? D=0 or 1 since it says if an interaction is detectable or not...
Moreover, L is reused later but is the number of interactions (l.100 supp.mat)…
What is “N” in Figure 4? is it “n”? What is n_ij and k_ij l.266? Never defined, never reused.
In the beginning of the paper, \lambda is a probability (l.62) but it becomes a random variable (l.164): it would be more consistent to introduce before the notion of hyperparameters  (l.209-213) and to explain we consider that \lambda is drawn into its distribution.

Minor points:

-l.62: define formally T
-l.244: this is weird to mention that the analysis has been done on another dataset but that the results will not be discussed… What is the interest for the reader?
-l.149: since the authors consider the interactions are independent, there is morally no network in the approach (except the result)
-l.252: not clear. Why this choice?
-l.259: not clear
-l.278: the authors investigate the consequence of uncertainity on network metrics. This question is of peculiar interest, but here it is restricted to the connectance and nestedness. Why these two metrics? Why not others? What is the impact of integrating incertainity into the metrics computation? (we guess the answers but we could expect the authors develop these points).
l.291: explain better the simulation procedure
l.306: given the shape of the distribution (exponential), the mean is not an appropriate indicator.
l.327: what does it mean? How is it possible?

\section*{Reviewer 3}

Reviewer: 3

Comments to the Corresponding Author
Overall, I think this is a very good paper and makes an important contribution.  I think there are three main ways it can be improved:

1.      The simplest – do a better job of acknowledging what else has been done in the field – much of which has actually been done by the authors and their collaborators.  Given that they know there work I won’t point that out (but they are under-siting this literature a bit) but they could consider Graham and Weinstein on-line early 2018 (I realize that this was just out when the author’s submitted but it has some very similar messages) and the empirical example of Weinstein and Graham in Ecology letters 2017.  I don’t think this would in any way diminish the importance of the current paper because I think the challenge in network ecology is to get people to use better quantitative methods.
2.      Provide more clarity in descriptions making sure to consider how terms and ideas have been used previously.  Two things come to mind – the use of terms and distinction between interaction and process uncertainty; and the somewhat contradictory sounding statements about if sampling more is actually good.
3.      The set up (introduction) to the case study is quite odd and somehow seems off topic – or at least not logical based on what the reader has read up to that point.

Below I provide specific comments

Line 7.  It is certainly true that most networks are snapshots in time but there is a growing realization – including some nice examples (including those by the authors) that address this issue.  Maybe what you want to say is that we know that networks should not be considered static but we lack the tools – or ability to collect data – or whatever you think is the cause – to correct this situation.

Line 23.  Delete the “because” (you have one in the sentence already).

Line 30.  There are several conceptual and empirical attempts to consider detection probability – why aren’t these cited (work by Bartomeus comes to mind).

Line 36.  I certainly see value in the approach and the general ideas of these authors in particular but they should acknowledge the work that has been done by themselves and others!

Line 86.  So, similar factors (i.e., trait matching) can be used to detect different kinds of uncertainty.  Should this be stated?  You might also consider a different word that process as “observation models” and “process models” are commonly used terms in Bayesian stats and in this case “process” often considers what you call “interaction”.  There are some interesting to attempts to model co-evolution that consider similar ideas (i.e., a barrier to interaction and then trait-matching; but maybe outside of the scope of this MS). While I appreciate that your naming has merit, I think if your hope is that more ecologists use these methods then the terminology should be consistent across papers/approaches to the greatest extent possible.

Line 73, 87.  Maybe the idea that some uncertainty is “inevitable” should not be repeated in multiple sections.  Either find a different way of saying it – or state it in your introductory paragraph and then don’t keep repeating.

Line 89.  In Weinstein and Graham (Ecology Letters) the processes modeled were trait matching (which you place in interaction uncertainty) and abundance (which is perhaps your process uncertainty??).  I find myself quite confused based on how you describe things in this MS (See text above) and how you cite the literature.

Line 94.  I find this a very odd argument against sampling multiple times.  So, if you sample more you might see more then understand the system less?  The logic does not make sense to me.

Line 107.  There is a lot of literature in wildlife ecology emphasizing the importance of repeat sampling for estimating detection probability.  Is this just wrong?  If so this does need more explanation in the context of this literature.

Line 130.  The ideas here are largely a repeat from those above.  Further, while it may be true that we can sample too much – I think it is dangerous to suggest we should sample less – do the authors think that sampling across most network studies is sufficient (the opposite is stated in the discussion)?  I wonder if the argument is a bit more statistical than biological.

Line 142.  But shouldn’t you model the probability of two species co-occurring?  The authors have a paper doing this…. Is that not a good idea?

Line 144.  I am much more comfortable with this statement than how sampling effort should be considered and I would suggest moving this up and then explaining how even if we sample well we need to consider uncertainty for the reasons you mention in the previous section.  Please note that you make the same point in your discussion on line 338.

Line 148.  Please note that a paper with a very similar aim was recently published (Graham and Weinstein).  This does not to diminish the value of this study in any way, as multiple perspectives on quantitative solutions in network ecology are urgently needed….. but the other work should be considered. More generally, the introduction does not really do justice to what has been done already – even the authors own work.  The problem in my view is that the community using better statistics – of which the authors are very important members – has not managed to communicate to most people studying networks and better methods are simply not being adopted.  The current paper is a very nice attempt to show the broader community that the Bayesian approach is not so complex and has many advantages.  I think this is a very important message and is what makes this paper an important contribution.  Further, the approach to parse out different types of uncertainty and suggestions for how to come-up with informative priors – is very useful.  The theory/method is well developed overall and provides an example – which is great.

Line 121.  I think one of the reason non-Bayesians’ are not comfortable with the approach is that if you put in prior information on something like trait matching and test for trait matching and then discover trait matching is important – what does it mean?  Maybe this is too obvious (I realize there are tons of papers on how to choose priors) but I wonder if it is worth explaining (would a box or something be worthwhile?  I leave it up to the authors/editor)?  Maybe the issue could be acknowledged and an appropriate paper cited?

Line 235.  Correct redundancy.

Line 240.  I found the justification for the system a bit odd.  Is the goal to show the gaps in sampling or to apply the model described thus far to consider the 3 different types of uncertainty outlined?  At this point the reader is confused about the goal…

Line 249.  The statement about training data is redundant with what is stated above – adjust writing.

Line 288.  I am pretty sure this idea is in the literature several times and should be cited.  Isn’t this the same as drawing a probability of interaction from a distribution where the distribution of each interaction is an output of the Bayesian method?

Line 295 to 302.  I would think that this second step (i.e., filtered networks) is to explore sampling not to determine how networks will be influenced by uncertainty?  Do you need the filtering step to evaluate uncertainty (as written it seems that this is the case)?

Line 319.  It is clear that these are large samples but if interaction among co-occurring species was greater than you need lower samples – correct?  Should this be made clear?  Otherwise, we maybe can just never get enough data!

Line 338 to 342.  Throughout I am confused if the authors suggest more sampling is good or bad…  At the end of the paragraph it seems it isn’t so great to sample more because you end up with these annoying “0” values…??????

Line 352 – 358.  Citations are needed in this section as this has been suggested before.

Line 361.  I find the statement that 30-50 individuals need to be evaluated a bit strong.  This statement is based on this study – are all systems like the gall system?  If species are specialized or bound to interact for some other reason (i.e., co-occurring when there are few other resources) wouldn’t you need to observe fewer individuals?  The point of the method is that you can estimate how many individuals are needed…. This is great!  But given that this can be estimated from any given system why give a value from one system and state that is what is required?  It defeats the point of the very nice method proposed…??

I hope this review is helpful.

\section*{Reviewer 4}

Comments to the Corresponding Author
I have been surprised how little that sampling effects have been formally considered in the analysis of networks, so I welcome this contribution that provides a theoretical framework. Overall, I felt that this contribution was really helpful, and that it provides both a theoretical framework and a practical example.

However, I felt that the structuring of the paper made it a challenge to understand and apply. It felt like the paper itself had been written in different sections (by different authors?) with not enough links between the sections. I also felt that there was a strong theoretical component, which is important, but there needed to be a stronger link with the issues around empirical ecology, as explained below.

Introduction – T. Poisot and colleagues have done a lot of relevant work in this area, but I felt there was undue reference to their work in comparison with other relevant work. There were some obvious papers (e.g. sampling by Jordano, forbidden links by various others) that were not cited. A broader perspective on the literature would, I think, help the authors appreciate the value of their paper and the need to ensure that it is fully understandable and of practical use.

L36ff The authors should note the value of weighted metrics in taking account of sampling biases.

L45 It is a shame not to give some idea of how the method could be extended (or is this the intention of the authors?). For empirical analysis of networks it is rare to use binary networks given the value of weighted networks for taking account of sampling biases. Indeed, I am much less concerned about whether an interaction never occurs, and much more concerned with the frequency of occurrence.

L50 This is a nice and clearly explained description of the problem that many network ecologists ignore, or are unaware of.

Section from L50. This section is valuable, but had very weak links with the empirical analysis later in the paper. For instance in the example of the gall-formers, there was not formal discussion about the different sources of uncertainty.

L76ff ‘Process uncertainty’ is not defined. The simplistic example of interaction uncertainty (fish eating a cactus) does not help the reader understand the detail of what is meant by ‘interaction uncertainty’. The two examples of ‘local constraints’ (weather and habitat) are operating on completely different temporal scales (note – it is defined differently in L109). I would regard the issue of weather as much closer to detection uncertainty (e.g. for a pollinator, it would be likely to be interacting if the weather was better), whereas the issue of habitat is closer to the authors’ ‘interaction uncertainty’ (the species don’t interact because they are not, or never, co-occurring in a habitat). Also if the species occur in different habitats then with an appropriate spatial scale of sampling then they do not co-occur – so the issue seems redundant. I suspect that the authors are thinking of a meta- or master network in much of their study, but this is not clear (or I have misunderstood and it needs to be explained better), i.e. the predicted presence of an interaction is not the presence of an interaction at the local site (taking detection and process uncertainty into account) but the ability to assess ‘interaction uncertainty’.

L76ff Different interactions occur at different temporal scales, so it is important to consider where the role of this study lies. For instance, a pollinator-flower interaction is quick (and even the evidence of it, e.g. pollen on the insect, is not long-lasting) whereas an active gall-former interaction could be present for a couple of months and could be detected for even longer (on senescing leaves).

I was struggling to really understand what the authors were really trying to model (partly because of the lack of a link between the theoretical and empirical parts of the paper). Are the authors trying to estimate L (the probability that an interaction is feasible or not – I would describe this as a ‘master’ or meta- network), or is it that they are trying to estimate X|L (the probability that the interaction locally occurs)? I would be interested in both, but the second aspect seemed to be ignored in the gall-former example.

L136 This is a completely different issue, that you do not address in the paper.

L147 Your Bayesian approach seems important, especially the prior information, and I would have appreciated it being explained more simply.

L155ff I think it would be helpful for this section to be integrated with the previous section. It relies on the reader putting quite a lot of work in to understand the link between the two.

L209ff This seems a really important set of ideas, but they are exemplified very briefly and very simplistically in the paper (L262, L310). I would have appreciated a much clearer explanation and example.

L241 I wonder if you could phrase this more positively as ‘solutions’ rather than just ‘difficulties’?

L283 This seems a very important point and should be explained/expanded more clearly.

L291 I have wondered about this – does assuming a probability of 1 for observed interactions create a bias? The observed interactions are a stochastic set of the possible interactions, so by treating observed interactions as 1 and other (equally likely?) unobserved interactions as <1 will surely bias the network metrics. I’m not sure of the solution and would welcome thoughts on this in the paper.

L298 These seem arbitrary. It is not clear what is filtered, or its justification – is it the unique interactions, unique interaction per site or samples? How do these compare to typical sampling effort?

L321 This is a really important and interesting set of results that are worthy of greater discussion. The issue of metrics from sampled networks is important, but gets lost in the paper. Please expand upon this.

Overall, I fear that this review is rather meandering, but I think that reflects some of the challenges I have with the paper. Currently I do not think the paper would be used by empirical network ecologists because they either would not understand its relevance or would not be able to apply it practically. This would be a great shame. I hope that the comments are clear enough to allow the authors to improve the paper – the paper has the potential to be important and very useful.

### 2018-10-29 manuscript/linewise_changes.tex
starting reply file

1-278: reduce?
7.  It is certainly true that most networks are snapshots in time but there is a growing realization – including some nice examples (including those by the authors) that address this issue.  Maybe what you want to say is that we know that networks should not be considered static but we lack the tools – or ability to collect data – or whatever you think is the cause – to correct this situation. 
23.  Delete the “because” (you have one in the sentence already).
30.  There are several conceptual and empirical attempts to consider detection probability – why aren’t these cited (work by Bartomeus comes to mind).
36.  I certainly see value in the approach and the general ideas of these authors in particular but they should acknowledge the work that has been done by themselves and others!
36ff The authors should note the value of weighted metrics in taking account of sampling biases.
45 It is a shame not to give some idea of how the method could be extended (or is this the intention of the authors?). For empirical analysis of networks it is rare to use binary networks given the value of weighted networks for taking account of sampling biases. Indeed, I am much less concerned about whether an interaction never occurs, and much more concerned with the frequency of occurrence.
50 This is a nice and clearly explained description of the problem that many network ecologists ignore, or are unaware of.
62: define formally T
73, 87.  Maybe the idea that some uncertainty is “inevitable” should not be repeated in multiple sections.  Either find a different way of saying it – or state it in your introductory paragraph and then don’t keep repeating.
76ff Different interactions occur at different temporal scales, so it is important to consider where the role of this study lies. For instance, a pollinator-flower interaction is quick (and even the evidence of it, e.g. pollen on the insect, is not long-lasting) whereas an active gall-former interaction could be present for a couple of months and could be detected for even longer (on senescing leaves).
76ff ‘Process uncertainty’ is not defined. The simplistic example of interaction uncertainty (fish eating a cactus) does not help the reader understand the detail of what is meant by ‘interaction uncertainty’. The two examples of ‘local constraints’ (weather and habitat) are operating on completely different temporal scales (note – it is defined differently in L109). I would regard the issue of weather as much closer to detection uncertainty (e.g. for a pollinator, it would be likely to be interacting if the weather was better), whereas the issue of habitat is closer to the authors’ ‘interaction uncertainty’ (the species don’t interact because they are not, or never, co-occurring in a habitat). Also if the species occur in different habitats then with an appropriate spatial scale of sampling then they do not co-occur – so the issue seems redundant. I suspect that the authors are thinking of a meta- or master network in much of their study, but this is not clear (or I have misunderstood and it needs to be explained better), i.e. the predicted presence of an interaction is not the presence of an interaction at the local site (taking detection and process uncertainty into account) but the ability to assess ‘interaction uncertainty’.
86.  So, similar factors (i.e., trait matching) can be used to detect different kinds of uncertainty.  Should this be stated?  You might also consider a different word that process as “observation models” and “process models” are commonly used terms in Bayesian stats and in this case “process” often considers what you call “interaction”.  There are some interesting to attempts to model co-evolution that consider similar ideas (i.e., a barrier to interaction and then trait-matching; but maybe outside of the scope of this MS). While I appreciate that your naming has merit, I think if your hope is that more ecologists use these methods then the terminology should be consistent across papers/approaches to the greatest extent possible.
89.  In Weinstein and Graham (Ecology Letters) the processes modeled were trait matching (which you place in interaction uncertainty) and abundance (which is perhaps your process uncertainty??).  I find myself quite confused based on how you describe things in this MS (See text above) and how you cite the literature.
89: Seems to contradict two preceding paragraphs
94.  I find this a very odd argument against sampling multiple times.  So, if you sample more you might see more then understand the system less?  The logic does not make sense to me.

107.  There is a lot of literature in wildlife ecology emphasizing the importance of repeat sampling for estimating detection probability.  Is this just wrong?  If so this does need more explanation in the context of this literature.
121.  I think one of the reason non-Bayesians’ are not comfortable with the approach is that if you put in prior information on something like trait matching and test for trait matching and then discover trait matching is important – what does it mean?  Maybe this is too obvious (I realize there are tons of papers on how to choose priors) but I wonder if it is worth explaining (would a box or something be worthwhile?  I leave it up to the authors/editor)?  Maybe the issue could be acknowledged and an appropriate paper cited?
130.  The ideas here are largely a repeat from those above.  Further, while it may be true that we can sample too much – I think it is dangerous to suggest we should sample less – do the authors think that sampling across most network studies is sufficient (the opposite is stated in the discussion)?  I wonder if the argument is a bit more statistical than biological.
136 This is a completely different issue, that you do not address in the paper.
142.  But shouldn’t you model the probability of two species co-occurring?  The authors have a paper doing this…. Is that not a good idea?
144.  I am much more comfortable with this statement than how sampling effort should be considered and I would suggest moving this up and then explaining how even if we sample well we need to consider uncertainty for the reasons you mention in the previous section.  Please note that you make the same point in your discussion on line 338.
147 Your Bayesian approach seems important, especially the prior information, and I would have appreciated it being explained more simply.
148.  Please note that a paper with a very similar aim was recently published (Graham and Weinstein).  This does not to diminish the value of this study in any way, as multiple perspectives on quantitative solutions in network ecology are urgently needed….. but the other work should be considered. More generally, the introduction does not really do justice to what has been done already – even the authors own work.  The problem in my view is that the community using better statistics – of which the authors are very important members – has not managed to communicate to most people studying networks and better methods are simply not being adopted.  The current paper is a very nice attempt to show the broader community that the Bayesian approach is not so complex and has many advantages.  I think this is a very important message and is what makes this paper an important contribution.  Further, the approach to parse out different types of uncertainty and suggestions for how to come-up with informative priors – is very useful.  The theory/method is well developed overall and provides an example – which is great.
149: since the authors consider the interactions are independent, there is morally no network in the approach (except the result)
155ff I think it would be helpful for this section to be integrated with the previous section. It relies on the reader putting quite a lot of work in to understand the link between the two.
209ff This seems a really important set of ideas, but they are exemplified very briefly and very simplistically in the paper (L262, L310). I would have appreciated a much clearer explanation and example.
235.  Correct redundancy.
240.  I found the justification for the system a bit odd.  Is the goal to show the gaps in sampling or to apply the model described thus far to consider the 3 different types of uncertainty outlined?  At this point the reader is confused about the goal…
241 I wonder if you could phrase this more positively as ‘solutions’ rather than just ‘difficulties’?
244: this is weird to mention that the analysis has been done on another dataset but that the results will not be discussed… What is the interest for the reader?
249.  The statement about training data is redundant with what is stated above – adjust writing.
252: not clear. Why this choice?
259: not clear
278: Add citations
278: the authors investigate the consequence of uncertainity on network metrics. This question is of peculiar interest, but here it is restricted to the connectance and nestedness. Why these two metrics? Why not others? What is the impact of integrating incertainity into the metrics computation? (we guess the answers but we could expect the authors develop these points).
283 This seems a very important point and should be explained/expanded more clearly.
288.  I am pretty sure this idea is in the literature several times and should be cited.  Isn’t this the same as drawing a probability of interaction from a distribution where the distribution of each interaction is an output of the Bayesian method?
291 I have wondered about this – does assuming a probability of 1 for observed interactions create a bias? The observed interactions are a stochastic set of the possible interactions, so by treating observed interactions as 1 and other (equally likely?) unobserved interactions as <1 will surely bias the network metrics. I’m not sure of the solution and would welcome thoughts on this in the paper.
291: explain better the simulation procedure
295 to 302.  I would think that this second step (i.e., filtered networks) is to explore sampling not to determine how networks will be influenced by uncertainty?  Do you need the filtering step to evaluate uncertainty (as written it seems that this is the case)?
298 These seem arbitrary. It is not clear what is filtered, or its justification – is it the unique interactions, unique interaction per site or samples? How do these compare to typical sampling effort?
306: given the shape of the distribution (exponential), the mean is not an appropriate indicator.
319.  It is clear that these are large samples but if interaction among co-occurring species was greater than you need lower samples – correct?  Should this be made clear?  Otherwise, we maybe can just never get enough data!
321 This is a really important and interesting set of results that are worthy of greater discussion. The issue of metrics from sampled networks is important, but gets lost in the paper. Please expand upon this.
327: what does it mean? How is it possible?
338 to 342.  Throughout I am confused if the authors suggest more sampling is good or bad…  At the end of the paragraph it seems it isn’t so great to sample more because you end up with these annoying “0” values…??????
343-351: difficult to relate results to discussion
352 – 358.  Citations are needed in this section as this has been suggested before.
361.  I find the statement that 30-50 individuals need to be evaluated a bit strong.  This statement is based on this study – are all systems like the gall system?  If species are specialized or bound to interact for some other reason (i.e., co-occurring when there are few other resources) wouldn’t you need to observe fewer individuals?  The point of the method is that you can estimate how many individuals are needed…. This is great!  But given that this can be estimated from any given system why give a value from one system and state that is what is required?  It defeats the point of the very nice method proposed…??

### 2018-10-29 manuscript/CI_interactions.tex
roughing out a box all about sampling

@@
 
+\section*{Boxes}
+
+Can't we just sample more?
+
+The obvious solution to the problem of uncertainty in the occurrence and detection of interactions is to increase sampling effort.
+A high sampling effort will increase the number of observed species and interactions and provide estimates of the interaction probabilities of species which are observed many times.
+Indeed, an infinitely high sampling effort would reveal the true probabilities of interactions that are detectable using the sampling methodology.
+Increasing sampling effort does not address the problem of interactions which may be undetectable because one or both species involved is cryptic (as with many parasitoids, which can only be identified using molecular methods~\citep{Carol,Wirta}) or because the interaction occurs at a spatial or temporal scale not considered (can use R's point about brevity of pollination here); unless the increase in sampling effort includes adding detection methods as well as adding sampling periods~\citep{Tomas}.
+
+Such infinite sampling is, of course, impossible.
+The sampling effort used in a given study is more likely to be constrained by the time and resources available than to be increased until all interactions that ever occur in a system are observed.
+Given the reality of limited resources for field studies, there are several reasons that sampling alone cannot solve ecology's problem with uncertainty.
+Note that this is not to say that we should sample \emph{less}.
+To reduce sampling effort voluntarily would be foolish in the extreme as a lower sampling effort reduces the number of interactions (and non-interactions) that are observed and increases the chance that species will be missed entirely.
+Rather we assume that researchers are sampling with the maximum effort feasible given constraints on their time, resources, and study systems (e.g., destructive sampling of endangered species may not be permitted even if resources would otherwise allow for such sampling).
+Under these conditions, some uncertainty will always remain.
+
+First, there is the problem of trade-offs between sampling one site intensively and sampling many sites less thoroughly.
+Species at a single site are not likely to interact continually (although some interactions, such as parasitism, can be long-term), so a brief sampling window will mean that some interactions do not occur during sampling.
+Even long-term interactions may not be detected during a brief sampling window if interacting individuals are not among those observed.
+Sampling a single site intensively, on the other hand, means that interactions which do not occur at the site due to lack of co-occurrance or other factors (e.g., some predator-prey interactions may not occur if the presence of a third species suppresses predator activity).
+The best way to manage this trade-off will vary with study systems, but in any case finite sampling effort means that some interactions will not be observed due to process or detection uncertainty.
+
+Second, even if we can increase sampling effort, this increased effort will not apply to all species equally.
+Some species are more common, interact more frequently, or are easier to observe.
+Given this, increasing sampling effort will give us more information about previously-observed interactions more often than it will reveal previously-unobserved interactions.
+It is still useful to understand the frequencies of common interactions, but this does not help us to remove "false zeros" from an interaction matrix.
+
+Third, there is the problem that species are added to the network "faster" (relatively speaking) than interactions.
+If sampling is not sufficient to ensure that all species present have been included (which seems likely except in fairly species-poor systems), the observation of a rare species interacting with some partner will add a single observed interaction (a "one") and many unobserved interactions ("zeros").
+Note that the zeros may be true reflections of interactions which do not occur, or they may be "false zeros" reflecting the lack of observations for interactions which do occur.
+As we accumulate more rare/cryptic/infrequently interacting species in a network, we discover more about what we do not know (i.e., which zeros are "true zeros" and which are not).
+However, by adding rare species and the disproportionate numbers of unobserved interactions associated with them, increased sampling can \emph{increase} uncertainty around the interaction network.
+Again, increased sampling, where possible, is not a bad thing because of the increased knowledge about rare species, the interactions we do observe, and the revealing of knowledge gaps.
+It does not, however, eliminate the problems of uncertainty we focus on here.
+
 \section*{Figures}

### 2018-10-30 manuscript/reply_to_reviewers.tex
corrections

@@
-\section*{Associate Editor}
+\documentclass[12pt]{letter}
+
+\usepackage[britdate]{LiU-letter}
+\usepackage{times}
+\usepackage{letterbib}
+\usepackage{geometry}
+\usepackage[round]{natbib}
+\usepackage{graphicx}
+\geometry{a4paper}
+\usepackage[T1]{fontenc}
+\usepackage[utf8]{inputenc}
+\usepackage{authblk}
+\usepackage[running]{lineno}
+\usepackage{amsmath,amsfonts,amssymb}
+\usepackage[margin=10pt,font=small,labelfont=bf]{caption}
+
+%\usepackage{natbib}
+% \bibpunct[; ]{(}{)}{;}{a}{,}{;}
+
+\newenvironment{refquote}{\bigskip \begin{it}}{\end{it}\smallskip}
+
+\newenvironment{figure}{}
+
+\begin{document}
+
+\newpage
+
+\setcounter{page}{1}
+
+% -----------------------------------------------------------------------------
+% -----------------------------------------------------------------------------
+{\Large \bf Reply to Associate Editor}
+% ---------------------------------------
 
@@
 
-\section*{Reviewer 1}
+% -----------------------------------------------------------------------------
+% -----------------------------------------------------------------------------
+{\Large \bf Reply to Reviewer \#1}
+% ---------------------------------------
 
@@
 
-\section*{Reviewer 2}
+% -----------------------------------------------------------------------------
+% -----------------------------------------------------------------------------
+{\Large \bf Reply to Referee \#2}
+% ---------------------------------------
 
@@
 
+	\begin{refquote}
 	The paper by A.Cirtwill and colleagues tackles a very interesting problem, quantifying the uncertainity of interactions, using three levels of nested uncertainity.
@@
 
+	\end{refquote}
+
 	Minor points:
@@
 
+4. Misunderstanding of our point about sampling effort
+
+	\textbf{R:} We believe that the Reviewer has badly misunderstood the point of our comments on sampling effort.
+We (like other sane people) would never suggest that researchers intensively sample less intensively.
+We assumed that field researchers already sample to the maximum extent possible given their time and resource constraints and so a call to "sample more" would have no effect.
+We now state these assumptions explicitly.
+Moreover, we believe that increased sampling effort will not reduce all sources of sampling uncertainty.
+For example, interactions that are not detectable using a particular sampling methodology will not be included by sampling more intensively using that method.
+Our comments about sampling were intended to draw attention to this and other issues, not to say that sampling is bad.
+Indeed, we point out that a high degree of sampling is necessary to detect rare species and to gain confidence that any two co-occurring species do not interact.
+Sampling is a valuable tool that happens not to solve the problems we are most interested here.
+To be absolutely clear about this to future readers we have added a box (Box 1) where we discuss why sampling alone will not solve problems about uncertainty.
+We hope that this box will make our (pro-sampling) stance clearer to the Reviewer and to future readers.
+
+	Line 94.  I find this a very odd argument against sampling multiple times.  So, if you sample more you might see more then understand the system less?  The logic does not make sense to me.
+
+	\textbf{R:} Of course sampling more does not lead to less understanding.
+It can, however, reveal knowledge gaps (as when a rare species is detected, revealing our ignorance of its interactions).
+This is not an argument against multiple sampling but a statement that increased sampling is likely to lead to the addition of more "false zeros" as species about which we know little are added to the network.
+
+	Line 107.
+There is a lot of literature in wildlife ecology emphasizing the importance of repeat sampling for estimating detection probability.
+Is this just wrong?
+If so this does need more explanation in the context of this literature.
+
+	\textbf{R:} I do not know how the Reviewer assumes that we are against repeat sampling when this is, in fact, one of the core parts of our approach.
+Our point here is that some species (e.g., cryptic or difficult-to-identify species) and interactions (e.g., brief visits of pollinators to plants) are difficult to detect and may be missed even with multiple sampling.
+If a rare species is only detected in one sampling round, then the repeated sampling necessarily tells us little about its interactions.
+For species which are frequently detected, we absolutely learn about the detection probability of their interactions with repeated sampling.
+
+	Line 130.
+The ideas here are largely a repeat from those above.
+Further, while it may be true that we can sample too much – I think it is dangerous to suggest we should sample less – do the authors think that sampling across most network studies is sufficient (the opposite is stated in the discussion)?
+I wonder if the argument is a bit more statistical than biological.
+
+	\textbf{R:} We agree that it is dangerous to suggest that anyone sample less, that is why we have not done so.
+We argue only that the amount of sampling required to be confident that co-occurring species do not interact is large -- likely beyond what is feasible for speciose systems given the limited resources available to many researchers.
+Sampling across most network studies is almost certainly not sufficient, but data which would allow readers to judge this (i.e., number of times each species is observed, independent of numbers of observed interactions) is not generally provided.
+We chose to be more charitable than the Reviewer and assume that those compiling empirical networks are sampling as much as possible given the constraints of their system and available resources.
+Infite sampling would, of course, be the best option but it is unlikely that researchers will be able to perpetually increase sampling.
+
+	Line 144.
+I am much more comfortable with this statement than how sampling effort should be considered and I would suggest moving this up and then explaining how even if we sample well we need to consider uncertainty for the reasons you mention in the previous section.
+Please note that you make the same point in your discussion on line 338.
+
+	Line 319.
+It is clear that these are large samples but if interaction among co-occurring species was greater than you need lower samples – correct?
+Should this be made clear?
+Otherwise, we maybe can just never get enough data!
+
+	Line 338 to 342.
+Throughout I am confused if the authors suggest more sampling is good or bad…  At the end of the paragraph it seems it isn’t so great to sample more because you end up with these annoying “0” values…??????
+
 Below I provide specific comments
@@
 
+	\textbf{R:} We have softened this statement to say that empirical networks are "often limited" and hope that this rephrasing will not offend those who are working to include variation in their descriptions.
+
+		\begin{quotation}
+			Despite this additional information, empirical descriptions of ecological networks are still often limited by a lack of data or tools to adequately incorporate variation in interactions into networks.
+		\end{quotation}
+
 	Line 23.  Delete the “because” (you have one in the sentence already).
+
+	\textbf{R:} Done.
 
@@
 
+	\textbf{R:} We have rephrased the paragraph about detection uncertainty. The last line now reads:
+
+		\begin{quotation}
+
+			Until these gaps are filled, some interaction uncertainty will remain.
+
+		\end{quotation}
+
 Line 89.
@@
 
-Line 94.  I find this a very odd argument against sampling multiple times.  So, if you sample more you might see more then understand the system less?  The logic does not make sense to me.
-
-Line 107.
-There is a lot of literature in wildlife ecology emphasizing the importance of repeat sampling for estimating detection probability.
-Is this just wrong?
-If so this does need more explanation in the context of this literature.
-
-Line 130.
-The ideas here are largely a repeat from those above.
-Further, while it may be true that we can sample too much – I think it is dangerous to suggest we should sample less – do the authors think that sampling across most network studies is sufficient (the opposite is stated in the discussion)?
-I wonder if the argument is a bit more statistical than biological.
-
 Line 142.  But shouldn’t you model the probability of two species co-occurring?  The authors have a paper doing this…. Is that not a good idea?
-
-Line 144.
-I am much more comfortable with this statement than how sampling effort should be considered and I would suggest moving this up and then explaining how even if we sample well we need to consider uncertainty for the reasons you mention in the previous section.
-Please note that you make the same point in your discussion on line 338.
 
@@
 Do you need the filtering step to evaluate uncertainty (as written it seems that this is the case)?
-
-Line 319.
-It is clear that these are large samples but if interaction among co-occurring species was greater than you need lower samples – correct?
-Should this be made clear?
-Otherwise, we maybe can just never get enough data!
-
-Line 338 to 342.
-Throughout I am confused if the authors suggest more sampling is good or bad…  At the end of the paragraph it seems it isn’t so great to sample more because you end up with these annoying “0” values…??????
 
@@
 
+\textbf{R:} Unfortunately, the use of binary networks is not as rare as the Reviewer thinks, particularly in food webs where it is often difficult to quantify interaction strengths or frequencies in the field.
+We absolutely agree that weighted networks are much more valuable when they are available but did not wish to exclude those without such data.
+[[Do we want to add a bit of non-binary stuff or just make it clearer that we are talking about feasibility and that probabilities of occurrance could be layered on later?]]
+
 L50 This is a nice and clearly explained description of the problem that many network ecologists ignore, or are unaware of.
@@
 For instance in the example of the gall-formers, there was not formal discussion about the different sources of uncertainty.
+[[So we need to state more clearly that we cannot distinguish these after the fact.]]
 
@@
 Also if the species occur in different habitats then with an appropriate spatial scale of sampling then they do not co-occur – so the issue seems redundant.
-I suspect that the authors are thinking of a meta- or master network in much of their study, but this is not clear (or I have misunderstood and it needs to be explained better), i.e.
-the predicted presence of an interaction is not the presence of an interaction at the local site (taking detection and process uncertainty into account) but the ability to assess ‘interaction uncertainty’.
+[[I suspect that the authors are thinking of a meta- or master network in much of their study, but this is not clear (or I have misunderstood and it needs to be explained better), i.e.
+the predicted presence of an interaction is not the presence of an interaction at the local site (taking detection and process uncertainty into account) but the ability to assess ‘interaction uncertainty’.]][[This is a bit separate from their issue]]
+
+\textbf{R:} It seems our descriptions of interaction uncertainty and process uncertainty were both unclear, as the Reviewer has badly mixed them up.
+We have expanded the paragraph introducing the different levels of uncertainty to include plain-language questions addressed by each level of uncertainty; hopefully this will help to avoid confusion at the outset.
+
+	\begin{quotation}
+
+		As a conceptual guide to the factors affecting this process, we describe three nested levels of uncertainty: interaction uncertainty, process uncertainty, and detection uncertainty (Fig.~\ref{conceptual_fig}).
+These levels roughly address the questions: "Could species $i$ and $j$ interact?", "Do they interact at this site/time?" and "Do we observe the interaction?".
+
+	\end{quotation}
+
+We have also added a paragraph to explain the interaction uncertainty explicitly \emph{does not} depend on co-occurrence; only on species traits.
+The Reviewer is not correct that habitat belongs in interaction uncertainty as species which do not currently share a habitat might still interact if one is introduced into the other's habitat (for example).
+We now state this explicitly.
+
+	\begin{quotation}
+
+		Note that interaction uncertainty does not depend upon whether species $i$ and $j$ actually co-occur.
+Ecologists are often interested in predicting which species are likely to interact following an introduction~\citep{} or range shift~\citep{}.
+In such cases, models based on trait matching can give some information about $\lambda$ while past co-occurance will, of course, not yield much insight.
+
+	\end{quotation}
+
+Process uncertainty covers factors which prevent an interaction which \emph{can occur} from actually occurring at particular places/times.
+This includes factors which mean that two potentially interactive species do not co-occur (e.g., habitat requirements) as well as factors which reduce interaction probability between co-occurring species (weather, abundances, etc.).
+We have rephrased the first line of this section to make this explicit.
+
+	\begin{quotation}
+
+		Assuming that an interaction is feasible (i.e., $L=1$; species traits do not prohibit an interaction if they should co-occur), an interaction still not occur at a particular place or time.
+
+	\end{quotation}
+
+Weather likely affects both process uncertainty and detection uncertainty.
+For pollination, pollinators are much less likely to interact in the rain (process uncertainty) and the lower visibility may mean that some interactions which do occur are missed (detection uncertainty).
+We have added a paragraph in the section describing detection uncertainty to make it clear that some external factors can affect multiple types of uncertainty.
+
+	\begin{quotation}
+
+		Note that some exteral factors can affect both process and detection uncertainty.
+For example, rare species are less likely to interact at a given site due to neutral processes (process uncertainty)~\citep{}.
+Interactions involving rare species are also less likely to be detected (detection uncertainty), unless more sampling effort is focused on rare than common species~\citep{}.
+Similarly, bad weather can make interactions such as pollination less likely by reducing pollinator activity~\citep{}.
+For those pollinators which do venture forth in poor conditions, bad weather might also reduce visibility and therefore increase detection uncertainty.
+
+	\end{quotation}
+
+The Reviewer is correct that increasing sampling effort to include more interaction-promoting weather, sites, etc.
+will reduce process uncertainty.
+It would also be possible to gerrymander the spatial scale of sampling such that non-interacting species do not co-occur, but we would not advocate selecting a study site to avoid particular species.
+The appropriate spatial and temporal scale of sampling is an important question, but it is not the question we are addressing here.
+Instead, we have added a line to include the Reviewer's point that expanded sampling can help to address process uncertainty and left it at that.
+
+	\begin{quotation}
+
+	Expanding sampling to cover a broader spatial or temporal range (e.g., sampling in a variety of microhabitats or during a variety of weather conditions) will also help to reduce process uncertainty if resource constraints permit.
+
+	\end{quotation}
 
@@
 pollen on the insect, is not long-lasting) whereas an active gall-former interaction could be present for a couple of months and could be detected for even longer (on senescing leaves).
+
+\textbf{R:} Long-term interactions may be easier to detect, but we do not see how this affects process uncertainty.
+Spatial variation in interaction probabilities will affect all interaction types, as does variation in abundances between years, so we cannot conceive of any interactions that are exempt from this issue.
+The timescale of an interaction (and the evidence it leaves) does affect detection uncertainty, so we have added a note in that section.
+Long-term interactions may fail to be detected, however, and we now add an example to make it clear that detection uncertainty applies to even long-term interacitons such as gall-forming.
+
+	\begin{quotation}
+
+		Some types of interactions will have higher detection uncertainty than others (e.g., pollination or predation often take place very quickly while parasitism can last for months or years).
+Even long-term interactions, however, can be missed, especially if species are difficult to identify or if not all individuals of a species share the interaction.
+Parasites, for example, are often concentrated in only a few individuals~\citep{Lagrue2017}.
+If these infected individuals do not happen to be included in a sample, their interactoins will be missed.
+
+	\end{quotation}
 

### 2018-10-30 manuscript/CI_interactions.tex
corrections

@@
 A network framework combines this tabulation of nodes with a list of interactions (links between nodes) so that networks provide additional, higher-order information on community structure.
-Despite this additional information, empirical descriptions of ecological networks are usually limited to static representations of the communities they describe.
+Despite this additional information, empirical descriptions of ecological networks are still often limited by a lack of data or tools to adequately incorporate variation in interactions into networks.
 That is, whether the network is assembled based on aggregated data, a single intensive ``snapshot" sample, or expert knowledge, interactions are assumed to occur deterministically wherever and whenever the community is observed~\citep{Olesen2011a}.
@@
 Interactions can be lost if the interaction partners remain present but are separated in time or are too rare to detect each other~\citep{Tylianakis2010}.
-Interactions can also fail to occur because of environmental contingencies~\citep{Poisot2015}, or because of individual preferences~\citep{Fodrie2015}.
+Interactions can also fail to occur because of environmental contingencies~\citep{Poisot2015} or individual preferences~\citep{Fodrie2015}.
 
     Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007}).
-An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to document interactions than species~\citep{Poisot2012}.
+An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to document interactions than species~\citep{Poisot2012,Bartomeus,others}.
 As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Poisot2016}.
@@
     Despite these efforts, we currently lack the quantitative methodology to deal with uncertainty generated by spatiotemporal variation in ecological interactions and by limited sampling.
-Even in well-sampled networks, uneven sampling across species can lead to the inference that some species do not interact because they co-occur rarely or have not yet been observed together - even if they do interact when they do co-occur (see Fig.~\ref{histograms}).
+[[cite previous attempts]] Even in well-sampled networks, uneven sampling across species can lead to the inference that some species do not interact because they co-occur rarely or have not yet been observed together - even if they do interact when they do co-occur (see Fig.~\ref{histograms}).
 Nearly all network studies will thus neglect some interactions, necessitating an approach that acknowledges this uncertainty.
@@
 An observed link definitely occurred, but there are multiple reasons why a given link may not be observed \emph{whether or not the interaction truly occurred}.
+In terms of the ones and zeros in a binary interaction matrix, we know that the ones are true but we cannot be sure that the zeros reflect interactions which actually do not occur.
 The detection of any interaction is a stochastic process.
-We define three nested levels of uncertainty contributing to this stochasticity: interaction uncertainty, process uncertainty, and detection uncertainty (Fig.~\ref{conceptual_fig}).
+As a conceptual guide to the factors affecting this process, we describe three nested levels of uncertainty: interaction uncertainty, process uncertainty, and detection uncertainty (Fig.~\ref{conceptual_fig}).
+These levels roughly address the questions: "Could species $i$ and $j$ interact?", "Do they interact at this site/time?" and "Do we observe the interaction?".
 
@@
 
-          First, and most fundamentally, a pair of species may or may not have the appropriate characteristics (or traits) to interact.
-We define the probability of an interaction $L$ given characteristics $\mathbf{T}$ as $P(L | \mathbf{T})=\lambda$.
-Some species pairs, such as a salmon and a saguaro cactus, have incompatible traits and would never interact even if they should co-occur.
-In such cases, $\lambda = 0$ and there is no uncertainty.
+          First, and most fundamentally, some interactions are feasible if a pair of species should co-occur while others are not.
+Assuming that the feasibility of interactions depends on the traits of species involved, we can define the probability of an interaction $L$ given some description of trait-matching $\mathbf{T}$ as $P(L | \mathbf{T})=\lambda$~\citep{Dom?}.
+In some cases the traits prohibiting an interaction are known.
+A potential prey may be too large, small, or well-armoured for a predator to attack, or it might be toxic or non-nutritious (e.g., large carnivores do not consume plants because they cannot digest them and typically do not consume small insects because of the large handling cost relative to the energy gained from tiny prey).
+Where the critical traits are known and mean that an interaction is unfeasbile, $\lambda = 0$ and there is no uncertainty about associated zeros in an interaction matrix.
 
-          Most species pairs, however, do not have traits that absolutely prevent an interaction.
-This means that it is generally unclear whether an unobserved interaction is impossible or simply a rare phenomenon with $\lambda>0$.
+          In most cases, however, it is not known what traits might prohibit an interaction~\citep{Dormann2017}.
+Pollinators may visit plants outside of those predicted based on "pollination syndromes"~\citep{} and herbivores may consume animal prey when it becomes accessible~\citep{}.
+These examples show that we often cannot say that an interaction absolutely does not occur.
+Instead, an unobserved interaction may be a rare phenomenon with $\lambda>0$ and an associated zero in an interaction matrix might be false.
 This uncertainty is partly addressed by trait-matching models in which species with better-matched traits are more likely to interact~\citep{Bartomeus2016}.
 As these models improve and include better information about the influence of traits on interactions, the uncertainty will be reduced and $\lambda$ should either tend to 0 or to 1.
-Nevertheless, every model is imperfect and lacks information that could be used to define constraints on interactions~\citep{Dormann2017}.
-Some interaction uncertainty is therefore inevitable.
+Nevertheless, every model is imperfect and lacks information that could be used to define constraints on at least some interactions~\citep{Dormann2017}.
+Until these gaps are filled, some interaction uncertainty will remain.
 
-        \subsubsection*{Process uncertainty}
+          Note that interaction uncertainty does not depend upon whether species $i$ and $j$ actually co-occur.
+Ecologists are often interested in predicting which species are likely to interact following an introduction~\citep{} or range shift~\citep{}.
+In such cases, models based on trait matching can give some information about $\lambda$ while past co-occurance will, of course, not yield much insight.
 
-         Even a feasible interaction, i.e.
-$L=1$, still may not occur at a given location or moment in time because of local constraints such as inclement weather or unsuitable habitat.
-We define the local realisation of an interaction, $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L=1)=\chi$.
+        \subsubsection*{Process uncertainty} [[Maybe need to rename]]
+
+          Assuming that an interaction is feasible (i.e., $L=1$; species traits do not prohibit an interaction if they should co-occur), an interaction still not occur at a particular place or time.
+This could be because the two species do not co-occur or, if they did occur, because constraints such as inclement weather or low abundance prevented the interaction.
+For example, a pollination interaction may not occur on a rainy day or a rare galler may not parasitize a rare plant because they do not encounter each other.
+          We can define the local realisation of an interaction, $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L=1)=\chi$.
+It is unlikely that $\chi$=1 except in the case of obligate specialists who always interact whenever they co-occur and always co-occur.
+When $\chi<1$ we cannot be sure whether an unobserved interaction did not occur and when it occurred but was not observed.
+
           This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology  on the topic.
@@
 Some of these factors can be addressed in mesocosm studies of networks (e.g., environmental conditions can be held stable) or could be included in models along the line of trait-matching models (e.g., phenological matching).
-In the field, however, process uncertainty is likely inevitable.
+Expanding sampling to cover a broader spatial or temporal range (e.g., sampling in a variety of microhabitats or during a variety of weather conditions) will also help to reduce process uncertainty if resource constraints permit.
+In the field, however, process uncertainty is likely inevitable as long as local conditions are not constant during sampling.
 
-         One proposed solution to the problem of process uncertainty is to use repeated sampling of networks.
-For example,~\citet{Weinstein2017} used repeated sampling to estimate the daily probability of detecting an interaction and thereby model detection and process uncertainty.
-While conceptually attractive, this approach is unsuitable for interactions occurring over longer time scales (e.g., associations between hosts and parasitoids with a single generation per year), or very rare interactions which might not occur on any of the sampling days.
+         % One proposed solution to the problem of process uncertainty is to use repeated sampling of networks.
+For example,~\citet{Weinstein2017-wrong one?} used repeated sampling to estimate the daily probability of detecting an interaction and thereby model detection and process uncertainty.[[This apparently confused R3]] While conceptually attractive, this approach is unsuitable for interactions occurring over longer time scales (e.g., associations between hosts and parasitoids with a single generation per year), or very rare interactions which might not occur on any of the sampling days.
 Moreover, the faster accumulation of species than interactions means that repeated sampling will tend to introduce more unobserved interactions than observed interactions unless the number of samples is very high~\citep{Poisot2012}.
@@
 the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification as in~\citealt{Wirta2014,Frost2016}).
-The absence of an interaction on a given day could therefore be because it was not feasible [$P(L) = 0$], was feasible but did not occur because of local conditions during sampling ($P(X|L=1) = 0$], or was feasible and occurred during sampling but could not be observed [$P(D|X=1,L=1)=0$].
-Because we cannot separate these possibilities, repeated sampling fails to satisfactorily address the uncertainty inherent in empirical networks.
+Some types of interactions will have higher detection uncertainty than others (e.g., pollination or predation often take place very quickly while parasitism can last for months or years).
+Even long-term interactions, however, can be missed, especially if species are difficult to identify or if not all individuals of a species share the interaction.
+Parasites, for example, are often concentrated in only a few individuals~\citep{Lagrue2017}.
+If these infected individuals do not happen to be included in a sample, their interactoins will be missed.
+
+          To sum up, the absence of an interaction on a given day could therefore be because it was not feasible [$P(L) = 0$], was feasible but did not occur because of local conditions during sampling ($P(X|L=1) = 0$], or was feasible and occurred during sampling but could not be observed [$P(D|X=1,L=1)=0$].
+Note that some exteral factors can affect both process and detection uncertainty.
+For example, rare species are less likely to interact at a given site due to neutral processes (process uncertainty)~\citep{}.
+Interactions involving rare species are also less likely to be detected (detection uncertainty), unless more sampling effort is focused on rare than common species~\citep{}.
+Similarly, bad weather can make interactions such as pollination less likely by reducing pollinator activity~\citep{}.
+For those pollinators which do venture forth in poor conditions, bad weather might also reduce visibility and therefore increase detection uncertainty.
 

### 2018-11-06 manuscript/CI_interactions.tex
mostly updating reply to R1

@@
 
-    Representing an ecological community as a network summarises both species composition and interactions between species.
+    Representing an ecological community as a network allows ecologists to address both community composition and the interactions between species~\citep{Roslin2016}.
+Identifying these interactions is a crucial step towards understanding (and predicting) the effects that species have on each other and the response of the community as a whole to external perturbations~\citep{Bartomeus2016,Giron2018}.
+Importantly, information is conveyed both by the presence and \emph{absence} of links between species.
+Presences and absences are not, however, equally certain.
+An observed link definitely occurred, but there are multiple reasons why a given link may not be observed.
+
+    First and foremost, ecological communities are known to be stochastic~\citep{Gotelli2000}.
+Community composition and abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}, leading to variation in encounter probabilites and hence in interactions~\citep{Vazquez2005,Poisot2015,Graham2018}.
+Species must co-occur in order to be observed interacting, so any variation in co-occurrence will create variation in the set of observed interactions~\citep{Gravel2013}.
+Even assuming constant co-occurrence within a given study system, changing abundances can affect interactions if species which would otherwise interact become too rare to detect each other~\citep{Tylianakis2010}.
+Moreover, interactions vary over space~\citep{Kitching1987,Baiser2012,Emer2018}, time~\citep{Kitching1987,Olesen2011a,Lopez2017}, between individuals~\citep{Pires2011a,Fodrie2015,Novak2015}, throughout life cycles~\citep{Preston2014,Clegg2018}, and with environmental conditions~\citep{Poisot2015}.
+
+    Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007}).
+An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to correctly document interactions than species~\citep{Poisot2012,Bartomeus2013,Jordano2016,Giron2018,Graham2018}.
+As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Bartomeeus2013,Poisot2016}.
+Efforts in this vein usually take the form of creating model food webs that approximate observed empirical networks~\citep{Allesina2008,Williams2010,Rohr2016}.
+These models may be based on species traits and/or abundances~\citep{Rohr2016,Graham2018,more} or on simple abstract rules~\citep{Allesina2008,Williams2010}.
+Such networks provide an important ''reality check'' by allowing us to compare the observed network to what would be expected under a particular set of assumptions~\citep{Bartomeus2013,Weinstein??}.
+They allow us to estimate the numbers of interactions which have not been observed and predict which unobserved interactions are most likely~\citep{Bartomeus2013}.
+
+    [[Trying to give a more precise summary of our goal here.]]
+    While predictive networks acknowledge the variability of interaction networks, they do not quantify the different degrees of uncertainty about different interactions.
+In fact, many assume that all interactions which actually occur have been observed and that there are no false positives~\citep{Bartomeus2016,others?}.
+This amounts of assuming that, while the strengths or frequencies of interactions may vary, we can be certain about the structure of the binary presence or absence of interactions.
+Other models assume that the probability of interaction is constant during the sampling period~\citep{Bartomeus2013}.
+Here we show that both assumptions are unlikely due to the many layers of uncertainty affecting the observation of interactions~\citep{Jordano2016}.
+Increased or improved sampling could reduce many of these sources uncertainty, but we suspect that most research groups limit sampling due to time or budget constraints.
+Given that increased sampling is not likely to be a viable solution to the problem of uncertainty about unobserved interactions (see Box 1), we offer a Bayesian framework to capture the uncertainty surrounding interactions which were not observed.
+This framework can be applied to any network type and does not require strong assumptions or pre-existing data about the study system, but can include such information if it is available.
+
+    % Development of molecular sampling methods such as DNA barcoding hold great potential for uncovering interactions missed by other sampling methods (such as visit surveys)~\citep{Giron2018}, but these novel methods are also somewhat error-prone at present~\citep{}.
+
+    % Accounting for differences in feasible (binary) interactions across life stages changes network structure~\citep{Clegg2018}.
+
+    % Representing an ecological community as a network summarises both species composition and interactions between species.
 A tabulation of the nodes (species) and their relative abundances forms the basis for traditional metrics of community composition such as alpha diversity.
@@
 
-    The assumption of static communities contrasts with the known stochasticity of ecological communities~\citep{Gotelli2000}.
+    % The assumption of static communities contrasts with the known stochasticity of ecological communities~\citep{Gotelli2000}.
 Community composition and abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}.
@@
 
-    Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007}).
+    % Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007}).
 An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to document interactions than species~\citep{Poisot2012,Bartomeus,others}.
@@
 
-    Despite these efforts, we currently lack the quantitative methodology to deal with uncertainty generated by spatiotemporal variation in ecological interactions and by limited sampling.
+    % Despite these efforts, we currently lack the quantitative methodology to deal with uncertainty generated by spatiotemporal variation in ecological interactions and by limited sampling.
 [[cite previous attempts]] Even in well-sampled networks, uneven sampling across species can lead to the inference that some species do not interact because they co-occur rarely or have not yet been observed together - even if they do interact when they do co-occur (see Fig.~\ref{histograms}).
@@
 
-    In this study, we formalise the description of interactions between species as probabilities and develop analytical tools to capture the uncertainty in the estimation of these interactions.
+    % In this study, we formalise the description of interactions between species as probabilities and develop analytical tools to capture the uncertainty in the estimation of these interactions.
 We focus on binary interactions as a first step, but the framework could be expanded to deal with interaction frequencies or strengths.
@@
 Parasites, for example, are often concentrated in only a few individuals~\citep{Lagrue2017}.
-If these infected individuals do not happen to be included in a sample, their interactoins will be missed.
+If these infected individuals do not happen to be included in a sample, their interactions will be missed.
 
@@
 
-    We are most interested in how to quantify an interaction probability, and its associated uncertainty, for interactions that have not been observed.
-Assume that a pair of species has been observed co-occurring $n$ times and interacting in $k = 0$ cases.
+    % Maybe we can move much of this to the Box and satisfy reviewer 1
+
+    % We are most interested in how to quantify an interaction probability, and its associated uncertainty, for interactions that have not been observed.
+For interactions which have been observed, methods already exist to quantify the probability of the interaction.
+
+    % Assume that a pair of species has been observed co-occurring $n$ times and interacting in $k = 0$ cases.
 We want to know the probability $\lambda$ that the species would be observed interacting if not constrained by local conditions, imperfect detection, etc.
@@
 
-        \begin{equation}
-          \lambda_{MLE} = \frac{k}{n}  .
-          \label{theta_MLE}
-        \end{equation}
+    %     \begin{equation}
+    %       \lambda_{MLE} = \frac{k}{n}  .
+    %       \label{theta_MLE}
+    %     \end{equation}
 
-    Note that $\lambda$ is not a point estimate but rather a random variable with an unknown distribution.
+    % Note that $\lambda$ is not a point estimate but rather a random variable with an unknown distribution.
 This means that if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact.
@@
 
-    To properly interpret $\lambda$, we need to estimate the variance as well as the MLE.
+    % To properly interpret $\lambda$, we need to estimate the variance as well as the MLE.
 The variance of a Bernoulli experiment is $n\lambda$(1-$\lambda$) and, importantly, describes the variability of the number of successes $k$ for $n$ trials rather than the variance associated with the estimation of $\lambda$.
@@
 
-    All of the above methods for estimating the variance of $\lambda$ include the number of samples $n$.
+    % All of the above methods for estimating the variance of $\lambda$ include the number of samples $n$.
 This means that where the number of samples $n$ is very low (e.g., for rare species), there will be considerable uncertainty around our estimate of $\lambda$.
@@
 
-    The Bayesian approach combines the MLE of $\lambda$ described above with a prior distribution and a normaliser to give a posterior distribution.
-Since $\lambda$ is a probability and bounded between 0 and 1, the most appropriate prior distribution is the beta:
+    We can create a simple Bayesian approach to modelling the probability of an interaction occurring ($\lambda$) by combining a maximum likelihood estimate of $\lambda$ with a prior distribution (described in the next section) and a normalising function.
+The MLE of $\lambda$, based on the number of observed interactions $k$ and observed co-occurrances $n$ is $\lambda = \frac{k}{n}$.
+The most appropriate prior distribution for a probability such as $\lambda$ is the beta distribution:
 
@@
 
-    Combining the beta-distributed prior with the binomial-distributed MLE of $\lambda$ is straightforward (see~\emph{Appendix S2}).
-By doing so, we obtain a posterior distribution that follows a beta distribution with new parameters $\alpha'= \alpha+k$ and $\beta'=\beta+n-k$.
+    Combining this prior distribution with the MLE of $\lambda$ derived from observed data, we obtain a posterior distribution that also follows a beta distribution with new parameters $\alpha'= \alpha+k$ and $\beta'=\beta+n-k$ (see~\emph{Appendix S2} for details).
 The weight of the prior on the posterior distribution can be understood from these parameter definitions: the difference between the posterior and the prior will increase with $k$ and $n-k$.
-In other words, the distribution of $\lambda$ for better-sampled pairs of species will rely less on the information used to build the prior distribution and depend more on the observed data.
-When plotted, we find the shape of the distribution gets narrower with $k$ and $n$ (Fig.~\ref{Salix_pdfs_cdfs}).
+In other words, the distribution of $\lambda$ for better-sampled pairs of species will rely less on the information used to build the prior distribution and depend more on the observed data and uncertainty about the probability of the pair interacting will decrease (Fig.~\ref{Salix_pdfs_cdfs}).
 
-    \subsubsection*{Moments and other properties}
+    % R1 suggests removing this - could be in the SI I guess?
+    % \subsubsection*{Moments and other properties}
 
-      It is common to perform analyses that require calculating higher-order network properties in interaction networks.
+    %   It is common to perform analyses that require calculating higher-order network properties in interaction networks.
 The fact that the posterior distribution of $\lambda$ follows a beta distribution makes it straightforward to compute moments and other properties needed for these analyses.
 
-      The \textbf{average} of $\lambda$ is: 
-          \begin{equation}
-            \bar{\lambda} = \frac{\alpha+k}{\alpha+\beta+n} ,
-            \label{mean}
-          \end{equation}
+    %   The \textbf{average} of $\lambda$ is: 
+    %       \begin{equation}
+    %         \bar{\lambda} = \frac{\alpha+k}{\alpha+\beta+n} ,
+    %         \label{mean}
+    %       \end{equation}
 
-        and its \textbf{variance} is:  
-          \begin{equation}
-            Var(\lambda|k) = \frac{(\alpha + k)(\beta + n - k)}{(\alpha + \beta + n)^{2}(\alpha + \beta + n +1)}
-            \label{variance}
-          \end{equation}
+    %     and its \textbf{variance} is:  
+    %       \begin{equation}
+    %         Var(\lambda|k) = \frac{(\alpha + k)(\beta + n - k)}{(\alpha + \beta + n)^{2}(\alpha + \beta + n +1)}
+    %         \label{variance}
+    %       \end{equation}
 
-        The \textbf{mode} of the distribution is:
-          \begin{equation}
-            \hat{\lambda} = \frac{\alpha + k - 1}{\alpha + \beta + n - 2} .
-            \label{mode}
-          \end{equation}
+    %     The \textbf{mode} of the distribution is:
+    %       \begin{equation}
+    %         \hat{\lambda} = \frac{\alpha + k - 1}{\alpha + \beta + n - 2} .
+    %         \label{mode}
+    %       \end{equation}
 
@@
 
-Can't we just sample more?
+\begin{figure}[h!]
+\caption{\textbf{Why isn't sampling the solution?}
+While sufficient sampling is a vital part of any scientific study, we do not think that an exhortation to "sample more" is the appropriate solution to analysing uncertain interactions.
+There are four main reasons for this: \\
+\textbf{1)} First, and most importantly, we assume that the majority of researchers are aware that insufficient sampling leads to shoddy data and are sampling as intensively and extensively as their time and budget allow.
+The development and decreasing price of novel methods such as DNA barcoding and remote sensing can help field researchers to do more with less, but it remains to be seen whether these improvements will be enough to fully-describe large study systems.
+\\
+\textbf{2)} High sampling effort with a constant methodology will reliably describe some interactions but not others.
+For example, many insect species are difficult to distinguish except by molecular methods.
+Non-descructive sampling (e.g., by observing insect flower-visitors) will not allow researchers to separate these cryptic species~\citep{}.
+Increasing the number of person-hours spent in the field will not change this situation, although of course it will allow more accurate estimations of interaction probabilities for species which \emph{can} be distinguished.
+Adding another type of sampling (e.g., molecular methods) would reduce the set of interactions which cannot be detected/distinguished, but it will also increase the time, resources, and expertise required to complete the study.
+\\
+\textbf{3)} High sampling effort in a narrow spatiotemporal window will reliably describe some interactions but not others.
+Species abundances vary between sites and over time, and some interactions may not occur if one or both partners is rare.
+In addition, some interactions only occur in brief temporal windows (e.g., flowers of Arctic plants may only open for a few days~\citep{}) or when mediated by other species (e.g., consumption of some shellfish by fish only occurs when the shellfish are heavily parasitised and cannot burrow~\citep{}).
+Expanding sampling to cover broader ranges of space and time will expand the set of interactions that are observed, but again will increase the time and resources needed.
+\\
+\textbf{4)}{} Observations of rare species add disproportionately more "zeros" than ones to an interaction matrix.
+Rare species may appear to be specialists purely because of their rarity~\citep{}.
+If increasing sampling effort adds many rare species to a network, but each species is observed only one or a few times, it is likely that only a fraction of the rare species' interactions will be included.
+Note that we should not avoid sampling rare species!
+It is better to identify species about which we know little as targets for future study than to ignore these species.
+Nevertheless, sampling which is sufficiently high to identify most species at a site but not most interactions for rare species will underestimate the number of interactions and skew the distribution of interactions to rare species.
+Targeted sampling of rare species would reduce this problem, but again either increase the cost of a study or take away resources from sampling more abundant species.
+\\
+Increased or targeted sampling could improve (and, given enough resources, perhaps solve) any one of the above problems.
+As each places demands on the same limited resource pool, however, it is extremely unlikely that researchers will be able to sample their way out of uncertainty about interactions.
+To illustrate the scale of sampling needed, we can consider the observation of an interaction as a Bernoulli trial.
+The number of successes ($k$ observed interaction) over ($n$ observed co-occurrances) trials will follow a binomial distribution (see~\emph{Appendix S2} for a full description of the mathematical framework).
+In this framework, the maximum likelihood estimate (MLE) for $\lambda$ is:
 
-The obvious solution to the problem of uncertainty in the occurrence and detection of interactions is to increase sampling effort.
-A high sampling effort will increase the number of observed species and interactions and provide estimates of the interaction probabilities of species which are observed many times.
-Indeed, an infinitely high sampling effort would reveal the true probabilities of interactions that are detectable using the sampling methodology.
-Increasing sampling effort does not address the problem of interactions which may be undetectable because one or both species involved is cryptic (as with many parasitoids, which can only be identified using molecular methods~\citep{Carol,Wirta}) or because the interaction occurs at a spatial or temporal scale not considered (can use R's point about brevity of pollination here); unless the increase in sampling effort includes adding detection methods as well as adding sampling periods~\citep{Tomas}.
+        \begin{equation}
+          \lambda_{MLE} = \frac{k}{n}  .
+          \label{theta_MLE}
+        \end{equation}
 
-Such infinite sampling is, of course, impossible.
-The sampling effort used in a given study is more likely to be constrained by the time and resources available than to be increased until all interactions that ever occur in a system are observed.
-Given the reality of limited resources for field studies, there are several reasons that sampling alone cannot solve ecology's problem with uncertainty.
-Note that this is not to say that we should sample \emph{less}.
-To reduce sampling effort voluntarily would be foolish in the extreme as a lower sampling effort reduces the number of interactions (and non-interactions) that are observed and increases the chance that species will be missed entirely.
-Rather we assume that researchers are sampling with the maximum effort feasible given constraints on their time, resources, and study systems (e.g., destructive sampling of endangered species may not be permitted even if resources would otherwise allow for such sampling).
-Under these conditions, some uncertainty will always remain.
+    Note that $\lambda$ is not a point estimate but rather a random variable with an unknown distribution.
+This means that if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact.
+Rather, $k = 0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless some chance that the two species \emph{could} interact.
+In the situation where $k>0$, in contrast, we are sure that the interaction is feasible.
+$k$ may not equal $n$ if local constraints or detection errors prevent the interaction from being observed in each sample, but we nevertheless know that the interaction does occur.
 
-First, there is the problem of trade-offs between sampling one site intensively and sampling many sites less thoroughly.
-Species at a single site are not likely to interact continually (although some interactions, such as parasitism, can be long-term), so a brief sampling window will mean that some interactions do not occur during sampling.
-Even long-term interactions may not be detected during a brief sampling window if interacting individuals are not among those observed.
-Sampling a single site intensively, on the other hand, means that interactions which do not occur at the site due to lack of co-occurrance or other factors (e.g., some predator-prey interactions may not occur if the presence of a third species suppresses predator activity).
-The best way to manage this trade-off will vary with study systems, but in any case finite sampling effort means that some interactions will not be observed due to process or detection uncertainty.
-
-Second, even if we can increase sampling effort, this increased effort will not apply to all species equally.
-Some species are more common, interact more frequently, or are easier to observe.
-Given this, increasing sampling effort will give us more information about previously-observed interactions more often than it will reveal previously-unobserved interactions.
-It is still useful to understand the frequencies of common interactions, but this does not help us to remove "false zeros" from an interaction matrix.
-
-Third, there is the problem that species are added to the network "faster" (relatively speaking) than interactions.
-If sampling is not sufficient to ensure that all species present have been included (which seems likely except in fairly species-poor systems), the observation of a rare species interacting with some partner will add a single observed interaction (a "one") and many unobserved interactions ("zeros").
-Note that the zeros may be true reflections of interactions which do not occur, or they may be "false zeros" reflecting the lack of observations for interactions which do occur.
-As we accumulate more rare/cryptic/infrequently interacting species in a network, we discover more about what we do not know (i.e., which zeros are "true zeros" and which are not).
-However, by adding rare species and the disproportionate numbers of unobserved interactions associated with them, increased sampling can \emph{increase} uncertainty around the interaction network.
-Again, increased sampling, where possible, is not a bad thing because of the increased knowledge about rare species, the interactions we do observe, and the revealing of knowledge gaps.
-It does not, however, eliminate the problems of uncertainty we focus on here.
+    Importantly, we can estimate the variance of $\lambda$ as well as the MLE; available methods include the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]).
+Examining the changing variance about $\lambda$ with increasing sample size (Fig.~\ref{upper_limits}), we see that tens of observations are required to establish that two co-occurring species do not interact.
+Most datasets lack such extensive sampling for some species pairs, especially rare species which may be of particular conservation interest~\citep{Bartomeus2013}.
+The main advantage of the Bayesian approach we suggest here is that it can reduce uncertainty about interactions involving species with limited numbers of observations.}
+\label{Box1}
+\end{figure}
 

### 2018-11-08 manuscript/reply_to_reviewers.tex
making a bit more progress on the rreview

@@
 Reviewer 2's comments take a different view of the purpose and scope of the manuscript than the other reviewers; we respect their ideas but feel that some are beyond the scope of the present manuscript.
-We therefore prioritise comments by the other three Reviewers and hope that, by addressing these, the purpose of our manuscript becomes clearer and our changes will at least partially satisfy Reviewer 2.
+In particular, we do not feel that a full simulation study is necessary given the simplicity of our framework.
+We emphasize that we are not introducing a software package (although we do provide simple code to aid those who are new to the field), nor are we introducing an entirely new framework (as the other Reviewers point out, many components of our approach have been touched on by previous work).
+The novelty and impact of our work lies in connecting a Bayesian statistical approach to the problem of limited and uneven sampling (driven by difference in species abundances, detectabilities, constrained time and budgets, etc.) and, we hope, in making this method more accessable to those without extensive statistical or modelling experience.
+Because of the difference between Reviewer 2 and the other Reviewers, we have opted to prioritise the majority view and focused first on comments by Reviewers 1, 3, and 4.
+We hope that, in the course of these revisions, we have at least partially adressed Reviewer 2's concertns as well.
+
+\newpage
 
@@
 
+	1. Suggestion to refocus on prior selection
+
+	\begin{refquote}
 	Below I offer my thoughts on this well-written manuscript.
@@
 The use of empirical priors can be quite controversial, and should be atleast touched on in the discussion.
+\\
 	I’ve left my comments below on the introduction, but in my opinion, it should be almost wholly rewritten in favor of a more targeted question constructing networks using priors, which is the key novelty of the work and is mostly hidden by the current introduction.
@@
 I see the makings of a really nice paper here, and I’m confident the authors will be able to achieve this text revision.
+	\end{refquote}
 
-	Comments
+	\textbf{R:} [[Definitely should expand this, but do we want to really focus on those?]][[not quite done]]
+
+	2. Suggestion to add more literature
+
+	\begin{refquote}
 	The introduction flows well and is thoughtfully laid out.
@@
 However, it seems remiss to not consider Jordano (2016) in the sampling section.
+	\end{refquote}
 
+	\textbf{R:} We thank the Reviewer for their compliments to our introduction and for the recommendation of Jordano 2016.
+We have incorporated this reference as suggested.
+Following comments from other reviewers, we have refined and slightly restructured our introduction in the hope of more clearly establishing the goal of our manuscript ('narrowing our net'.
+We hope that this revised introduction will also meet with the Reviewer's approval.
+[[done]]
+
+	3. Suggestion to de-emphasize MLE estimate and get straight to Bayes
+
+	\begin{refquote}
 	It’s a bit confusing to lead the reader towards a Bayesian analysis, and then immediately start with the MLE estimate. Why is this needed at all? (L162-186). Just start at 187?
+	\end{refquote}
+
+	\textbf{R:} The section on the MLE estimate was designed to illustrate the large sample sizes needed in the absence of a Bayesian framework.
+Upon reflection, we see have moved this demonstration to a box dealing specifically with sampling.
+We now begin with the Bayesian beta distribution as suggested.
+[[I think done?]]
+
+	4. Suggestion to remove moments of the beta distribution
+
+	\begin{refquote}
 	I think a bit of space is wasted on defining the moments of the beta distribution.
@@
 I think the space is better utilized aligning the ecological challenge and the quantitative method.
+	\end{refquote}
+
+	\textbf{R:} While we feel that a short introduction to the beta distribution is important to bring researchers new to Bayesian statistics up to speed (and give them some keywords to Google), we accept the Reviewer's suggestion to reduce the amount of space given to the beta.
+We have therefore moved the description of basic properties to Appendix S2.
+The remaining paragraph introducing the beta distribution now leads directly into the section describing prior selection.
+
+	5. Novelty of the study not clear in current framing
+
+	\begin{refquote}
 	I’m wrestling with the novelty of the work as presented and whether it reaches the standard for publication at MEE.
@@
 In particular, the authors should try to be much more explicit about the contribution they hope to offer that hasn’t been covered.
-I could list atleast two dozen papers here, but some key ones might include:
-	All have the theme of detection, occurrence and interaction as a central challenge in constructing
-	reliable networks. Several prior papers have offered Bayesian approaches, starting with the individual model by
-	While it is true that none of the above papers do the exact same thing as this manuscript, they all
-	orbit the same topic. L89 for example, seems to conflict with the two paragraphs immediately following it?
-	At the same time, the paper is clear and very readable. I wholly support the method and I think it is something critical that needs to be adopted by the community.
+I could list atleast two dozen papers here, but some key ones might include ...	All have the theme of detection, occurrence and interaction as a central challenge in constructing reliable networks.
+Several prior papers have offered Bayesian approaches, starting with the individual model by ...
+	While it is true that none of the above papers do the exact same thing as this manuscript, they all	orbit the same topic. 
+	\end{refquote}
 
+	\textbf{R:} We thank the Reviewer for the literature suggestions and now include them in our introduction and/or discussion.
+We emphasize the board applicability of our appraoch across network types and where species traits affecting interaction probability may not be known.
+[[Make sure this comes through]] We hope that the contribution our manuscript makes is now clearer.
+
+	6. Potential contradiction
+
+	\begin{refquote}
+	L89 for example, seems to conflict with the two paragraphs immediately following it?
+	\end{refquote}
+
+	\textbf{R:} [[]]
+
+	7. Final comment on framing the study
+
+	\begin{refquote}
+	At the same time, the paper is clear and very readable. I wholly support the method and I think it is something critical that needs to be adopted by the community. \\
 	Having read the paper several times, I think that the authors are trying to cast their net too widely, even starting from the title.
@@
 I was extremely interested in the brief discussion on using prior knowledge, especially the delicacy of trying to transfer information among networks (L248).
-My recommendation is to drastically reduce the grandiose attempt at a “quantitative framework for networks” (L1 – L246) and really zoom in on the contribution of transferring information among networks through informed priors.
-	Again L278, this is very well covered in concept by recent papers in MEE that include the authors of this work, as well as several by Weinstein, Bartomeus and others.
+My recommendation is to drastically reduce the grandiose attempt at a “quantitative framework for networks” (L1 – L246) and really zoom in on the contribution of transferring information among networks through informed priors.	Again L278, this is very well covered in concept by recent papers in MEE that include the authors of this work, as well as several by Weinstein, Bartomeus and others.
+	\end{refquote}
 
-		Literature suggestions:
+	\textbf{R:} We thank the Reviewer for their compliments and accept their suggestion that we are somewhat overexcited about our approach.
+We have refined the introduction to be more specific about the problem we are attempting to solve.
+We have also expanded our treatment of prior selection and hope that our paper now reads as achieving its goal.
 
-	Jordano, P. (2016). Sampling networks of ecological interactions. Functional Ecology, 30(12), 1883–1893. doi:10.1111/1365-2435.12763
-
-	Bartomeus, I.
+	% 	Literature suggestions:
+	% Jordano, P. (2016). Sampling networks of ecological interactions. Functional Ecology, 30(12), 1883–1893. doi:10.1111/1365-2435.12763
+	% Bartomeus, I.
 (2013).
@@
 doi:10.1371/journal.pone.0069200
-	Poisot, T., Cirtwill, A.
+	% Poisot, T., Cirtwill, A.
 R., Cazelles, K., Gravel, D., Fortin, M.-J., & Stouffer, D.
@@
 doi:10.1111/2041-210X.12468
-	Poisot, T., Stouffer, D. B., & Gravel, D. (2015). Beyond species: why ecological interaction networks vary through space and time. Oikos, 124(3), 243–251. doi:10.1111/oik.01719
-	Graham, C. H., & Weinstein, B. G. (2018). Towards a predictive model of species interaction beta diversity. Ecology Letters. doi:10.1111/ele.13084
-	Gravel, D., Poisot, T., Albouy, C., Velez, L., & Mouillot, D.
+	% Poisot, T., Stouffer, D. B., & Gravel, D. (2015). Beyond species: why ecological interaction networks vary through space and time. Oikos, 124(3), 243–251. doi:10.1111/oik.01719
+	% Graham, C. H., & Weinstein, B. G. (2018). Towards a predictive model of species interaction beta diversity. Ecology Letters. doi:10.1111/ele.13084
+	% Gravel, D., Poisot, T., Albouy, C., Velez, L., & Mouillot, D.
 (2013).
@@
 doi:10.1111/2041-210X.12103
-	Wells, K., & O’Hara, R.
+	% Wells, K., & O’Hara, R.
 B.
@@
 
-\section*{Reviewer 3}
+% -----------------------------------------------------------------------------
+% -----------------------------------------------------------------------------
+{\Large \bf Reply to Referee \#3}
+% ---------------------------------------
 
-Reviewer: 3
-
+	\begin{refquote}
 	Comments to the Corresponding Author
 	Overall, I think this is a very good paper and makes an important contribution.  I think there are three main ways it can be improved:
+	\end{refquote}
 
+	\textbf{R:} [[Move the end bit up here?]]
+
+	1. Add more references to the literature
+
+	\begin{refquote}
 	1.
@@
 I don’t think this would in any way diminish the importance of the current paper because I think the challenge in network ecology is to get people to use better quantitative methods.
+	\end{refquote}
+
+	\textbf{R:} We had not intended to write a review paper and did not wish to over-cite ourselves, but we take the Reviewer's point and have expanded our references to the literature.
+We have taken particular care to add references to Graham/Weinsten papers as two of the reviewers suggested work by these authors.
+We hope that we now adequately acknowledge previous work.
+
+	2. Confusing terminology
+
+	\begin{refquote}
 	2.
@@
 Two things come to mind – the use of terms and distinction between interaction and process uncertainty; and the somewhat contradictory sounding statements about if sampling more is actually good.
+	\end{refquote}
+
+	\textbf{R:} [[interaction and process uncertainty...]] We respond to the Reviewer's comments about sampling below.
+
+	3. Introduction of the case study seems off-topic and illogical.
+
+	\begin{refquote}
 	3.      The set up (introduction) to the case study is quite odd and somehow seems off topic – or at least not logical based on what the reader has read up to that point.
+	\end{refquote}
+
+	\textbf{R:}
 
@@
 		\textbf{R:} We believe that the Reviewer has badly misunderstood the point of our comments on sampling effort.
-We (like other sane people) would never suggest that researchers intensively sample less intensively.
-We assumed that field researchers already sample to the maximum extent possible given their time and resource constraints and so a call to "sample more" would have no effect.
-We now state these assumptions explicitly.
-Moreover, we believe that increased sampling effort will not reduce all sources of sampling uncertainty.
-For example, interactions that are not detectable using a particular sampling methodology will not be included by sampling more intensively using that method.
-Our comments about sampling were intended to draw attention to this and other issues, not to say that sampling is bad.
-Indeed, we point out that a high degree of sampling is necessary to detect rare species and to gain confidence that any two co-occurring species do not interact.
-Sampling is a valuable tool that happens not to solve the problems we are most interested here.
-To be absolutely clear about this to future readers we have added a box (Box 1) where we discuss why sampling alone will not solve problems about uncertainty.
-We hope that this box will make our (pro-sampling) stance clearer to the Reviewer and to future readers.
+Several of their comments suggest that we are advocating for reducing sampling effort.
+This is emphatically not the case.
+Rather, we assumed that field researchers already sample to the maximum extent possible given their time and resource constraints and so a call to "sample more" would not be helpful.
+We now address this assumption explicitly in a box dedicated to the potential for sampling effort to reduce uncertainty about interactions.
+Below, we address the Reviewer's sampling-related comments one by one.
 
+		\begin{refquote}
 		Line 94.  I find this a very odd argument against sampling multiple times.  So, if you sample more you might see more then understand the system less?  The logic does not make sense to me. 
+		\end{refquote}
 
@@
 
+		\begin{refquote}
 		Line 107.
@@
 If so this does need more explanation in the context of this literature.
+		\end{refquote}
 
@@
 
+		\begin{refquote}
 		Line 130.
@@
 I wonder if the argument is a bit more statistical than biological.
+		\end{refquote}
 
@@
 
+		\begin{refquote}
 		Line 144.
@@
 Please note that you make the same point in your discussion on line 338.
+		\end{refquote}
 
+		\begin{refquote}
 		Line 319.
@@
 Otherwise, we maybe can just never get enough data!
+		\end{refquote}
 
+		\begin{refquote}
 		Line 338 to 342.
 Throughout I am confused if the authors suggest more sampling is good or bad…  At the end of the paragraph it seems it isn’t so great to sample more because you end up with these annoying “0” values…??????
+		\end{refquote}
 
@@
 
+		5. Rephrase to acknowledge prior work
+
+		\begin{refquote}
 		Line 7.
@@
 Maybe what you want to say is that we know that networks should not be considered static but we lack the tools – or ability to collect data – or whatever you think is the cause – to correct this situation.
+		\end{refquote}
 
@@
 
+		6. Redundancy
+
 		Line 23.  Delete the “because” (you have one in the sentence already).
@@
 
-Line 30.  There are several conceptual and empirical attempts to consider detection probability – why aren’t these cited (work by Bartomeus comes to mind).
-
-Line 36.  I certainly see value in the approach and the general ideas of these authors in particular but they should acknowledge the work that has been done by themselves and others!
-
-Line 86.
-So, similar factors (i.e., trait matching) can be used to detect different kinds of uncertainty.
-Should this be stated?
-You might also consider a different word that process as “observation models” and “process models” are commonly used terms in Bayesian stats and in this case “process” often considers what you call “interaction”.
-There are some interesting to attempts to model co-evolution that consider similar ideas (i.e., a barrier to interaction and then trait-matching; but maybe outside of the scope of this MS).
-While I appreciate that your naming has merit, I think if your hope is that more ecologists use these methods then the terminology should be consistent across papers/approaches to the greatest extent possible.
-
-	Line 73, 87.
-Maybe the idea that some uncertainty is “inevitable” should not be repeated in multiple sections.
-Either find a different way of saying it – or state it in your introductory paragraph and then don’t keep repeating.
-
-	\textbf{R:} We have rephrased the paragraph about detection uncertainty. The last line now reads:
+		7. Increase references to prior work
 
 		\begin{quotation}
+		Line 30.  There are several conceptual and empirical attempts to consider detection probability – why aren’t these cited (work by Bartomeus comes to mind).\\
 
-			Until these gaps are filled, some interaction uncertainty will remain.
-
-		\end{quotation}
+		Line 36.  I certainly see value in the approach and the general ideas of these authors in particular but they should acknowledge the work that has been done by themselves and others!\\
 
@@
 In Weinstein and Graham (Ecology Letters) the processes modeled were trait matching (which you place in interaction uncertainty) and abundance (which is perhaps your process uncertainty??).
-I find myself quite confused based on how you describe things in this MS (See text above) and how you cite the literature.
-
-Line 142.  But shouldn’t you model the probability of two species co-occurring?  The authors have a paper doing this…. Is that not a good idea?
+I find myself quite confused based on how you describe things in this MS (See text above) and how you cite the literature.\\
 
@@
 Further, the approach to parse out different types of uncertainty and suggestions for how to come-up with informative priors – is very useful.
-The theory/method is well developed overall and provides an example – which is great.
+The theory/method is well developed overall and provides an example – which is great.\\
+		Line 288.
+I am pretty sure this idea is in the literature several times and should be cited.
+Isn’t this the same as drawing a probability of interaction from a distribution where the distribution of each interaction is an output of the Bayesian method?\\
+		Line 352 – 358.  Citations are needed in this section as this has been suggested before.
+		\end{refquote}
 
+		\textbf{R:}
+
+		8. Potential for confusion about "process" nomenclature
+
+		\begin{refquote}
+		Line 86.
+So, similar factors (i.e., trait matching) can be used to detect different kinds of uncertainty.
+Should this be stated?
+You might also consider a different word that process as “observation models” and “process models” are commonly used terms in Bayesian stats and in this case “process” often considers what you call “interaction”.
+There are some interesting to attempts to model co-evolution that consider similar ideas (i.e., a barrier to interaction and then trait-matching; but maybe outside of the scope of this MS).
+While I appreciate that your naming has merit, I think if your hope is that more ecologists use these methods then the terminology should be consistent across papers/approaches to the greatest extent possible.
+		\end{refquote}
+
+		\textbf{R:} Interesting... [[not done, do we want to?]]
+
+		9. Reduce repetition of inevitable uncertainty
+
+		\begin{refquote}
+		Line 73, 87.
+Maybe the idea that some uncertainty is “inevitable” should not be repeated in multiple sections.
+Either find a different way of saying it – or state it in your introductory paragraph and then don’t keep repeating.
+		\end{refquote}
+
+		\textbf{R:} We have rephrased the paragraph about detection uncertainty. The last line now reads:
+
+			\begin{quotation}
+
+				Until these gaps are filled, some interaction uncertainty will remain.
+
+			\end{quotation}
+
+		10. Why not always model probabilities of co-occurrance?
+
+		\begin{refquote}
+		Line 142.  But shouldn’t you model the probability of two species co-occurring?  The authors have a paper doing this…. Is that not a good idea?
+		\end{refquote}
+
+		\textbf{R:} Sure, this is an option in some cases, but we may not always have the information to do this. Co-occurrance modelling shouldn't be the only tool in the box.
+
+		11. Issue of testing hypotheses based on inputs into models
+
+		\begin{refquote}
 		Line 121.
@@
 Maybe the issue could be acknowledged and an appropriate paper cited?
+		\end{refquote}
 
-Line 235.  Correct redundancy.
+		\textbf{R:} This question seems dumb. Do people actually do this?
 
+		12. Redundancy in line 235
+
+		\textbf{R:}
+
+		13. System justification/description is odd.
+
+		\begin{refquote}
 		Line 240.
@@
 Is the goal to show the gaps in sampling or to apply the model described thus far to consider the 3 different types of uncertainty outlined?
-At this point the reader is confused about the goal…
+At this point the reader is confused about the goal… \\
+		Line 249.  The statement about training data is redundant with what is stated above – adjust writing.
+		\end{refquote}
 
-Line 249.  The statement about training data is redundant with what is stated above – adjust writing.
+		\textbf{R:}
 
-Line 288.
-I am pretty sure this idea is in the literature several times and should be cited.
-Isn’t this the same as drawing a probability of interaction from a distribution where the distribution of each interaction is an output of the Bayesian method?
+		14. Unsure about the point of filtering networks
 
+		\begin{refquote}
 		Line 295 to 302.
@@
 Do you need the filtering step to evaluate uncertainty (as written it seems that this is the case)?
+		\end{refquote}
 
-Line 352 – 358.  Citations are needed in this section as this has been suggested before.
+		15. Skepticism about sampling requirements to be sure interactions do not occur
 
+		\begin{refquote}
 		Line 361.
@@
 It defeats the point of the very nice method proposed…??
+		\end{refquote}
 
+		\textbf{R:} Of course, if you have extremely strong priors then you need less sampling.
+With a strong enough prior assumption that two species never interact, a researcher may feel justified not sampling at all (e.g., webs constructed based on "expert knowledge").
+But if species shifting ranges are interesting/may be specialised because rare/information is not so available....
+
+		\begin{refquote}
 		I hope this review is helpful.  
+		\end{refquote}
 
-\section*{Reviewer 4}
+		\textbf{R:} We than the Reviewer for their literature suggestions and for demonstrating that our desire not to criticise hard-working empiricists could be misinterpreted as suggesting reduced sampling effort.
+We had not realised that anyone would consider such a possibility and have revised our manuscript to make it clearer that our approach is a complement to extensive sampling, not an excuse for poor sampling.
 
+\newpage
+
+% -----------------------------------------------------------------------------
+% -----------------------------------------------------------------------------
+{\Large \bf Reply to Referee \#4}
+% ---------------------------------------
+
+	\begin{refquote}
 	Comments to the Corresponding Author
@@
 Overall, I felt that this contribution was really helpful, and that it provides both a theoretical framework and a practical example.
+	\end{refquote}
 
+	\textbf{R:} [[Add end bit to this?]]
+
+	1. Paper is poorly structured
+
+	\begin{refquote}
 	However, I felt that the structuring of the paper made it a challenge to understand and apply.
@@
 I also felt that there was a strong theoretical component, which is important, but there needed to be a stronger link with the issues around empirical ecology, as explained below.
+	\end{refquote}
 
+	\textbf{R:}
+
+	2. Add more citations
+
+	\begin{refquote}
 	Introduction – T.
@@
 A broader perspective on the literature would, I think, help the authors appreciate the value of their paper and the need to ensure that it is fully understandable and of practical use.
+	\end{refquote}
 
+	\textbf{R:} [[copy reply to R2]]
+
+	3. Demand for praise of weighted metrics
+
+	\begin{refquote}
 	L36ff The authors should note the value of weighted metrics in taking account of sampling biases.
+	\end{refquote}
 
+	\textbf{R:} This is slightly confusing.
+How do weighted metrics account for sampling biases, exactly?
+Especially if species abundances are not assessed independently from interactions, it seems like weighted metrics would be more succeptable to sampling bias than unweighted metrics (as the weights will also be affected by differences in detectability).
+[[Is this acutally useful?]]
+
+	4. Demand for extension to weigthed networks
+
+	\begin{refquote}
 	L45 It is a shame not to give some idea of how the method could be extended (or is this the intention of the authors?).
@@
 Indeed, I am much less concerned about whether an interaction never occurs, and much more concerned with the frequency of occurrence.
+	\end{refquote}
 
@@
 
+	5. The one valuable section is poorly-integrated with the rest of the paper.
+
+	\begin{refquote}
 	L50 This is a nice and clearly explained description of the problem that many network ecologists ignore, or are unaware of.
-
 	Section from L50.
@@
 [[So we need to state more clearly that we cannot distinguish these after the fact.]]
+	\end{refquote}
 
+	\textbf{R:}
+
+	6. Process uncertainty poorly defined, many quibbles about sampling
+
+	\begin{refquote}
 	L76ff ‘Process uncertainty’ is not defined.
@@
 the predicted presence of an interaction is not the presence of an interaction at the local site (taking detection and process uncertainty into account) but the ability to assess ‘interaction uncertainty’.]][[This is a bit separate from their issue]]
+	\end{refquote}
 
@@
 
+	7. Point about temporal scales of interaction
+
+	\begin{refquote}
 	L76ff Different interactions occur at different temporal scales, so it is important to consider where the role of this study lies.
@@
 pollen on the insect, is not long-lasting) whereas an active gall-former interaction could be present for a couple of months and could be detected for even longer (on senescing leaves).
+	\end{refquote}
 
@@
 
+	8. Confusion about goal of modelling
+
+	\begin{refquote}
 	I was struggling to really understand what the authors were really trying to model (partly because of the lack of a link between the theoretical and empirical parts of the paper).
@@
 I would be interested in both, but the second aspect seemed to be ignored in the gall-former example.
+	\end{refquote}
 
+	\textbf{R:}
+
+	9. ??
+
+	\begin{refquote}
 	L136 This is a completely different issue, that you do not address in the paper.
+	\end{refquote}
 
+	\textbf{R:}
+
+	10. Explain Bayesian approach more simply
+
+	\begin{refquote}
 	L147 Your Bayesian approach seems important, especially the prior information, and I would have appreciated it being explained more simply.
+	\end{refquote}
 
+	\textbf{R:} This comment conflicts with Reviewer 1's request that we remove much of our early description of the Bayesian framework on the grounds that it is easy to Google.
+As one way to address both comments, we have revised the manuscript to more clearly position our analysis of the willow-galler network as a worked example.
+We hope that the Reviewer will find it easier to understand our framework by following along with an example than would be the case if we expanded our abstract discussion.
+
+	11. Integrate L155ff with previous section
+
+	\begin{refquote}
 	L155ff I think it would be helpful for this section to be integrated with the previous section. It relies on the reader putting quite a lot of work in to understand the link between the two.
+	\end{refquote}
 
+	\textbf{R:}
+
+	12. Ideas presented in L209, L262, L310 are important but explained too briefly
+
+	\begin{refquote}
 	L209ff This seems a really important set of ideas, but they are exemplified very briefly and very simplistically in the paper (L262, L310).
 I would have appreciated a much clearer explanation and example.
+	\end{refquote}
 
+	\textbf{R:}
+
+	13. Reframe line 241 in terms of solutions rather than difficulties
+
+	\begin{refquote}
 	L241 I wonder if you could phrase this more positively as ‘solutions’ rather than just ‘difficulties’?
+	\end{refquote}
+
+	\textbf{R:}
+
+	14. Line 283 is unclear
 
@@
 
+	\textbf{R:}
+
+	15. Line 291: does assuming probability of 1 for observed interactions introduce bias?
+
+	\begin{refquote}
 	L291 I have wondered about this – does assuming a probability of 1 for observed interactions create a bias?
@@
 I’m not sure of the solution and would welcome thoughts on this in the paper.
+	\end{refquote}
 
+	16. Filtering seems arbitrary
+
+	\begin{refquote}
 	L298 These seem arbitrary.
@@
 How do these compare to typical sampling effort?
+	\end{refquote}
 
+	\textbf{R:} The filtering threshold were arbitrary and intended solely to demonstrate how decreasing detection probability might shape the network actually collected in the field.
+We had believed that our example network was extremely well-sampled and therefore clustered filtering thesholds closer to p(detection)=1; as it appears that even this very intesively sampled network did not detect many interactions we have changed to a broader and more even set of filtering thresholds.
+We have also revised this section to make it clear what is being filtered [[to do]].\\
+	Unfortunately, we do cannot compare our filtered networks to many published networks as detection probabilities are not often estimated or reported.
+We do note, however, that Bascompte (2013) also reports quite low proportions of detected interactions ([[exact #]]).
+This suggests that the low detection probabilities we infer are not unique to our study.
+We have added a note comparing our results with Bascompte's [[to do]] and an explicit call for future researchers to report estimates of their detection probabilities [[to do]].
+
+	17. Expand discussion of results on line 321
+
+	\begin{refquote}
 	L321 This is a really important and interesting set of results that are worthy of greater discussion.
@@
 Please expand upon this.
+	\end{refquote}
 
+	\textbf{R:}
+
+	18. As a review, the manuscript is disappointing.
+
+	\begin{refquote}
 	Overall, I fear that this review is rather meandering, but I think that reflects some of the challenges I have with the paper.
@@
 I hope that the comments are clear enough to allow the authors to improve the paper – the paper has the potential to be important and very useful.
+	\end{refquote}
+
+	\textbf{R:} As we did not intend to write a review, we understand the Reviewer's complaint.
+This shows that we did not clearly establish the purpose of our manuscript, and we hope that our revision corrects this.
+In particular, we hope that we have established the relevance of our method and offered enough of an explanation that empiricists will be able to apply it.
+Our goal is to increase access to a statistical technique which we see as complementary to high-quality field work, and we believe that the Reviewer's comments will help us to achieve this.
+
+\clearpage
+
+\end{document}

### 2018-11-22 manuscript/reply_to_reviewers.tex
more revisions

@@
 
-% -----------------------------------------------------------------------------
-% -----------------------------------------------------------------------------
+% ----------------------------------------------------------------------
+% ----------------------------------------------------------------------
 {\Large \bf Reply to Reviewer \#1}
@@
 
-	1. Suggestion to refocus on prior selection
+	1. Suggestion to refocus on prior selection [[not done]]
 
@@
 
-	\textbf{R:} [[Definitely should expand this, but do we want to really focus on those?]][[not quite done]]
+		\textbf{R:} We thank the Reviewer for the suggestion to expand our discussion of prior selection, particularly with regard to approxmimate/empirical bayes.
+[[Expand refs to this]] We now walk through flat, informed, and empirical priors as suggested (lines XX-XX) and refer to the controversy surrounding empirical priors in our discussion (lines XX-XX).\\
+		We also appreciate the Reviewer's comments on our introduction.
+We feel that understanding the problem of uncertain detection of interactions is important motivation for a reader not already familiar with Bayesian procedures to wade through a larger discussion on priors.
+Therefore we have revised and, hopefully, streamlined our discussion but do not jump straight in to priors.
+We have, however, taken care to introduce our analysis as a worked example (lines XX-XX) and hope that this helps to reduce the conflict between the introduction and our data.
+[[Add something else about different priors?
+Add different priors to our analyses?]]
+		[[Definitely should expand this, but do we want to really focus on those?]][[not quite done]]
 
-	2. Suggestion to add more literature
+	2. Suggestion to add more literature [[in progress]]
 
@@
 We have incorporated this reference as suggested.
-Following comments from other reviewers, we have refined and slightly restructured our introduction in the hope of more clearly establishing the goal of our manuscript ('narrowing our net'.
+Following comments from other reviewers, we have refined and slightly restructured our introduction in the hope of more clearly establishing the goal of our manuscript ('narrowing our net').
 We hope that this revised introduction will also meet with the Reviewer's approval.
@@
 
-	3. Suggestion to de-emphasize MLE estimate and get straight to Bayes
+	3. Suggestion to de-emphasize MLE estimate and get straight to Bayes [[done]]
 
@@
 
-	4. Suggestion to remove moments of the beta distribution
+	4. Suggestion to remove moments of the beta distribution [[done]]
 
@@
 
-	5. Novelty of the study not clear in current framing
+	5. Novelty of the study not clear in current framing [[not done? Done? Clearer?]]
 
@@
 In particular, the authors should try to be much more explicit about the contribution they hope to offer that hasn’t been covered.
-I could list atleast two dozen papers here, but some key ones might include ...	All have the theme of detection, occurrence and interaction as a central challenge in constructing reliable networks.
-Several prior papers have offered Bayesian approaches, starting with the individual model by ...
-	While it is true that none of the above papers do the exact same thing as this manuscript, they all	orbit the same topic. 
+...
+		While it is true that none of the [suggested] papers do the exact same thing as this manuscript, they all	orbit the same topic. 
 		\end{refquote}
@@
 
-	6. Potential contradiction
+	6. Potential contradiction [[done]]
 
@@
 
-	\textbf{R:} [[]]
+		\textbf{R:} We have now address questions relating to sampling in a dedicated box.
+We hope that the revisions make our stance on repeated sampling clearer and that there are no longer apparent contradictions.
 
-	7. Final comment on framing the study
+	7. Final comment on framing the study [[I think done?]]
 
@@
 
-% -----------------------------------------------------------------------------
-% -----------------------------------------------------------------------------
+% ----------------------------------------------------------------------
+% ---------------------------------------------------------------------
 {\Large \bf Reply to Referee \#2}
@@
 
-% -----------------------------------------------------------------------------
-% -----------------------------------------------------------------------------
+% ----------------------------------------------------------------------
+% ----------------------------------------------------------------------
 {\Large \bf Reply to Referee \#3}
@@
 		Comments to the Corresponding Author
-	Overall, I think this is a very good paper and makes an important contribution.  I think there are three main ways it can be improved:
+		Overall, I think this is a very good paper and makes an important contribution.
+I think there are three main ways it can be improved: 1.
+The simplest – do a better job of acknowledging what else has been done in the field – much of which has actually been done by the authors and their collaborators.
+...
+2.
+Provide more clarity in descriptions making sure to consider how terms and ideas have been used previously.
+...
+3.
+The set up (introduction) to the case study is quite odd and somehow seems off topic – or at least not logical based on what the reader has read up to that point.
+		I hope this review is helpful.  
 		\end{refquote}
 
-	\textbf{R:} [[Move the end bit up here?]]
+		\textbf{R:} We than the Reviewer for their literature suggestions and for demonstrating that our desire not to criticise hard-working empiricists could be misinterpreted as suggesting reduced sampling effort.
+We had not realised that anyone would consider such a possibility and have revised our manuscript to make it clearer that our approach is a complement to extensive sampling, not an excuse for poor sampling.
 
-	1. Add more references to the literature
+	1. Add more references to the literature [[in progress]]
 
@@
 
-	2. Confusing terminology
+		\begin{refquote}
+		Line 7.
+It is certainly true that most networks are snapshots in time but there is a growing realization – including some nice examples (including those by the authors) that address this issue.
+Maybe what you want to say is that we know that networks should not be considered static but we lack the tools – or ability to collect data – or whatever you think is the cause – to correct this situation.
+		\end{refquote}
+
+		\textbf{R:} We have softened this statement to say that empirical networks are "often limited" and hope that this rephrasing will not offend those who are working to include variation in their descriptions.
+
+			\begin{quotation}
+				Despite this additional information, empirical descriptions of ecological networks are still often limited by a lack of data or tools to adequately incorporate variation in interactions into networks.
+			\end{quotation}
+
+		\begin{quotation}
+		Line 30.  There are several conceptual and empirical attempts to consider detection probability – why aren’t these cited (work by Bartomeus comes to mind).\\
+
+		Line 36.  I certainly see value in the approach and the general ideas of these authors in particular but they should acknowledge the work that has been done by themselves and others!\\
+
+		Line 89.
+In Weinstein and Graham (Ecology Letters) the processes modeled were trait matching (which you place in interaction uncertainty) and abundance (which is perhaps your process uncertainty??).
+I find myself quite confused based on how you describe things in this MS (See text above) and how you cite the literature.\\
+
+		Line 148.
+Please note that a paper with a very similar aim was recently published (Graham and Weinstein).
+This does not to diminish the value of this study in any way, as multiple perspectives on quantitative solutions in network ecology are urgently needed…..
+but the other work should be considered.
+More generally, the introduction does not really do justice to what has been done already – even the authors own work.
+The problem in my view is that the community using better statistics – of which the authors are very important members – has not managed to communicate to most people studying networks and better methods are simply not being adopted.
+The current paper is a very nice attempt to show the broader community that the Bayesian approach is not so complex and has many advantages.
+I think this is a very important message and is what makes this paper an important contribution.
+Further, the approach to parse out different types of uncertainty and suggestions for how to come-up with informative priors – is very useful.
+The theory/method is well developed overall and provides an example – which is great.\\
+		Line 288.
+I am pretty sure this idea is in the literature several times and should be cited.
+Isn’t this the same as drawing a probability of interaction from a distribution where the distribution of each interaction is an output of the Bayesian method?\\
+		Line 352 – 358.  Citations are needed in this section as this has been suggested before.
+		\end{refquote}
+
+		\textbf{R:}
+
+	2. Confusing terminology [[not done]]
 
@@
 Two things come to mind – the use of terms and distinction between interaction and process uncertainty; and the somewhat contradictory sounding statements about if sampling more is actually good.
+		\medskip
+		Line 86.
+So, similar factors (i.e., trait matching) can be used to detect different kinds of uncertainty.
+Should this be stated?
+You might also consider a different word that process as “observation models” and “process models” are commonly used terms in Bayesian stats and in this case “process” often considers what you call “interaction”.
+There are some interesting to attempts to model co-evolution that consider similar ideas (i.e., a barrier to interaction and then trait-matching; but maybe outside of the scope of this MS).
+While I appreciate that your naming has merit, I think if your hope is that more ecologists use these methods then the terminology should be consistent across papers/approaches to the greatest extent possible.
 		\end{refquote}
@@
 
-	3. Introduction of the case study seems off-topic and illogical.
+	3. Introduction of the case study seems off-topic and illogical. [[not done - R1 also points out that this is a weak point]]
 
@@
 
-	4. Misunderstanding of our point about sampling effort
+		\begin{refquote}
+		Line 240.
+I found the justification for the system a bit odd.
+Is the goal to show the gaps in sampling or to apply the model described thus far to consider the 3 different types of uncertainty outlined?
+At this point the reader is confused about the goal… \\
+		Line 249.  The statement about training data is redundant with what is stated above – adjust writing.
+		\end{refquote}
+
+		\textbf{R:}
+
+	4. Misunderstanding of our point about sampling effort [[maybe done? in progress]]
 
@@
 
-	Below I provide specific comments
-
-		5. Rephrase to acknowledge prior work
-
-		\begin{refquote}
-		Line 7.
-It is certainly true that most networks are snapshots in time but there is a growing realization – including some nice examples (including those by the authors) that address this issue.
-Maybe what you want to say is that we know that networks should not be considered static but we lack the tools – or ability to collect data – or whatever you think is the cause – to correct this situation.
-		\end{refquote}
-
-		\textbf{R:} We have softened this statement to say that empirical networks are "often limited" and hope that this rephrasing will not offend those who are working to include variation in their descriptions.
-
-			\begin{quotation}
-				Despite this additional information, empirical descriptions of ecological networks are still often limited by a lack of data or tools to adequately incorporate variation in interactions into networks.
-			\end{quotation}
-
-		6. Redundancy
-
-		Line 23.  Delete the “because” (you have one in the sentence already).
+	5. Eliminate redundant "because" on line 23 [[done]]
 
@@
 
-		7. Increase references to prior work
-
-		\begin{quotation}
-		Line 30.  There are several conceptual and empirical attempts to consider detection probability – why aren’t these cited (work by Bartomeus comes to mind).\\
-
-		Line 36.  I certainly see value in the approach and the general ideas of these authors in particular but they should acknowledge the work that has been done by themselves and others!\\
-
-		Line 89.
-In Weinstein and Graham (Ecology Letters) the processes modeled were trait matching (which you place in interaction uncertainty) and abundance (which is perhaps your process uncertainty??).
-I find myself quite confused based on how you describe things in this MS (See text above) and how you cite the literature.\\
-
-		Line 148.
-Please note that a paper with a very similar aim was recently published (Graham and Weinstein).
-This does not to diminish the value of this study in any way, as multiple perspectives on quantitative solutions in network ecology are urgently needed…..
-but the other work should be considered.
-More generally, the introduction does not really do justice to what has been done already – even the authors own work.
-The problem in my view is that the community using better statistics – of which the authors are very important members – has not managed to communicate to most people studying networks and better methods are simply not being adopted.
-The current paper is a very nice attempt to show the broader community that the Bayesian approach is not so complex and has many advantages.
-I think this is a very important message and is what makes this paper an important contribution.
-Further, the approach to parse out different types of uncertainty and suggestions for how to come-up with informative priors – is very useful.
-The theory/method is well developed overall and provides an example – which is great.\\
-		Line 288.
-I am pretty sure this idea is in the literature several times and should be cited.
-Isn’t this the same as drawing a probability of interaction from a distribution where the distribution of each interaction is an output of the Bayesian method?\\
-		Line 352 – 358.  Citations are needed in this section as this has been suggested before.
-		\end{refquote}
-
-		\textbf{R:}
-
-		8. Potential for confusion about "process" nomenclature
-
-		\begin{refquote}
-		Line 86.
-So, similar factors (i.e., trait matching) can be used to detect different kinds of uncertainty.
-Should this be stated?
-You might also consider a different word that process as “observation models” and “process models” are commonly used terms in Bayesian stats and in this case “process” often considers what you call “interaction”.
-There are some interesting to attempts to model co-evolution that consider similar ideas (i.e., a barrier to interaction and then trait-matching; but maybe outside of the scope of this MS).
-While I appreciate that your naming has merit, I think if your hope is that more ecologists use these methods then the terminology should be consistent across papers/approaches to the greatest extent possible.
-		\end{refquote}
-
-		\textbf{R:} Interesting... [[not done, do we want to?]]
-
-		9. Reduce repetition of inevitable uncertainty
+	6. Reduce repetition of inevitable uncertainty [[done]]
 
@@
 
-		10. Why not always model probabilities of co-occurrance?
+	7. Why not always model probabilities of co-occurrance? [[done]]
 
@@
 
-		\textbf{R:} Sure, this is an option in some cases, but we may not always have the information to do this. Co-occurrance modelling shouldn't be the only tool in the box.
+		\textbf{R:} Of course modelling the probability of co-occurrence is an option for many systems (e.g., aquatic food webs where ranges of fish species are fairly well-known, as in~\citet{Gravel2013}).
+In some systems, however, the factors affecting probabilities of co-occurrence may not be known.
+We therefore cannot suggest modelling co-occurrence as a panacea.
+Instead, we now emphasize that co-occurrence probabilities are one thing that could be included in a prior (lines XX-XX - section Informative priors).
+		\smallskip
+		The fact remains that a lack of observed interactions between species which do not co-occur tells us nothing about whether these species \emph{could} interact if they should begin to co-occur (e.g., following a range shift).
+Following the Revewier's suggestion, we have revised our manuscript to clarify our technology.
+In particular, we have taken care to specify which level of uncertainty we are addressing at different points in the manuscript.
+We hope that this will remove some of the confusion about whether or not modelling different components of uncertainty/sampling more is a good idea.
 
-		11. Issue of testing hypotheses based on inputs into models
+	8. Issue of testing hypotheses based on inputs into models [[done]]
 
@@
 
-		\textbf{R:} This question seems dumb. Do people actually do this?
+		\textbf{R:} Following suggestions by this Reviewer and another, we have substantially expanded our discussion of different options for priors (including the trait-based and co-occurrence models the Reviewer points out).
+It seems fairly obvious that discovering that trait-matching is important in a model framework which relies of trait-matching as a starting assumption does not mean very much...
+but we also recognize that researchers unfamiliar with Bayesian approaches might prioritize reducing uncertainty and therefore include all available information even when it conflicts with the study question.
+We have therefore added an explicit statement that researchers wishing to test the influence of a particular trait (for example) should \emph{not} include that trait in their prior (lines XX-XX).
+We hope that this statement, and the expanded discussion of different types of priors more generally, allay the Reviewer's concerns.
 
-		12. Redundancy in line 235
+		\begin{quotation}
+			Similarly, if detailed information is available but refers to the question at hand, it is best to use a less informative prior so as not to force a particular result.
+For example, if researchers are interested in testing whether body-size ratios affect probabilities of interaction they should not use a prior which predicts interactions based on body sizes.
+		\end{quotation}
 
-		\textbf{R:}
+	9. Redundancy in line 235 [[done]]
 
-		13. System justification/description is odd.
+		\textbf{R:} The redundant line has been removed. Thank you for pointing this out.
 
-		\begin{refquote}
-		Line 240.
-I found the justification for the system a bit odd.
-Is the goal to show the gaps in sampling or to apply the model described thus far to consider the 3 different types of uncertainty outlined?
-At this point the reader is confused about the goal… \\
-		Line 249.  The statement about training data is redundant with what is stated above – adjust writing.
-		\end{refquote}
-
-		\textbf{R:}
-
-		14. Unsure about the point of filtering networks
+	10. Unsure about the point of filtering networks [[not done]]
 
@@
 
-		15. Skepticism about sampling requirements to be sure interactions do not occur
+		\textbf{R:}
+
+	11. Skepticism about sampling requirements to be sure interactions do not occur [[done]]
 
@@
 
-		\textbf{R:} Of course, if you have extremely strong priors then you need less sampling.
-With a strong enough prior assumption that two species never interact, a researcher may feel justified not sampling at all (e.g., webs constructed based on "expert knowledge").
-But if species shifting ranges are interesting/may be specialised because rare/information is not so available....
+		\textbf{R:} The point of our method is not actually to quantify the amount of sampling needed.
+Although the ideal sampling effort \emph{can} be calculated using the framework we put forward (as we demonstrate), the real point is to quantify how uncertain we are that an interaction we do not observe really does not occur.
+Given this, we do not think that recommending uncertainty be explicitly stated undermines our point at all.
+		\smallskip
+		The Reviewer's suggestion that we might need fewer samples for species that are "specialized or bound to interact for some other reason" reflects a very strong prior.
+In this case, yes we would need fewer samples for the species concerned.
+With sufficiently strong priors, it is not necessary to sample at all!
+For example, in most food webs it is assumed that basal resources will never consume prey even if a given resource and a given animal are never observed co-occurring and it is generally accepted that there is very low uncertainty about these zeros.
+In many cases, the assumptions involved in excluding interactions are less clear-cut and different researchers may disagree about which species are "bound to interact" (or not to interact).
+The concept of pollination syndromes is one example - many flower visitors are less rigidly specialized on particular flower types than initially thought~\citep{}.
+To address such "forbidden links", we now suggest that researchers explicitly state both the uncertainty about data-based zeros and the assumptions by which they create structural zeros.
+This will allow future researchers to evaluate the uncertainty about all interactions in a network as the state of expert knowledge changes.
+We hope that this expanded recommendation (lines XX-XX) is clearer.
 
-		\begin{refquote}
-		I hope this review is helpful.  
-		\end{refquote}
+		\begin{quotation}
 
-		\textbf{R:} We than the Reviewer for their literature suggestions and for demonstrating that our desire not to criticise hard-working empiricists could be misinterpreted as suggesting reduced sampling effort.
-We had not realised that anyone would consider such a possibility and have revised our manuscript to make it clearer that our approach is a complement to extensive sampling, not an excuse for poor sampling.
+			Second, researchers should acknowledge the varying levels of confidence surrounding interactions between species pairs.
+In the absence of strong prior information a very high level of sampling (i.e., 30-50 observations in our example) is needed \emph{for each species pair}.
+This is not likely to be possible for most studies.
+including the $n$ and $k$ values for each interaction will clearly indicate which unobserved interactions are most likely to be observed with further sampling and which estimates are more reliable.
+Where there are strong prior expectations about pairs of species that will not interact, these should be explicitly stated so that readers know which zeros in an interaction matrix are based on observed data and which are based primarily upon expert knowledge.
+
+		\end{quotation}
 
@@
 
-% -----------------------------------------------------------------------------
-% -----------------------------------------------------------------------------
+% ----------------------------------------------------------------------
+% ----------------------------------------------------------------------
 {\Large \bf Reply to Referee \#4}
@@
 Overall, I felt that this contribution was really helpful, and that it provides both a theoretical framework and a practical example.
+
+		Overall, I fear that this review is rather meandering, but I think that reflects some of the challenges I have with the paper.
+Currently I do not think the paper would be used by empirical network ecologists because they either would not understand its relevance or would not be able to apply it practically.
+This would be a great shame.
+I hope that the comments are clear enough to allow the authors to improve the paper – the paper has the potential to be important and very useful.
 		\end{refquote}
 
-	\textbf{R:} [[Add end bit to this?]]
+		\textbf{R:} As we did not intend to write a review, we understand the Reviewer's complaint.
+This shows that we did not clearly establish the purpose of our manuscript, and we hope that our revision corrects this.
+In particular, we hope that we have established the relevance of our method and offered enough of an explanation that empiricists will be able to apply it.
+Our goal is to increase access to a statistical technique which we see as complementary to high-quality field work, and we believe that the Reviewer's comments will help us to achieve this.
 
-	1. Paper is poorly structured
+	1. Paper is poorly structured [[not done]]
 
@@
 
-	2. Add more citations
+	2. Add more citations [[done]]
 
@@
 
-	\textbf{R:} [[copy reply to R2]]
+		\textbf{R:} We have cited addition literature as recommended by Reviewer 1, including a paper by Jordano.
+If the Reviewer has any suggestions of specific papers that they feel are missing, we would be happy to consider them as well.
+Note, however, that we do not intend our manuscript to be a complete review of the literature surrounding interaction probabilities.
+We hope that the citations we have added appear more balanced to the Reviewer.
 
-	3. Demand for praise of weighted metrics
+	3. Demand for praise of weighted metrics [[not done]]
 
@@
 
-	4. Demand for extension to weigthed networks
+	4. Demand for extension to weighted networks [[not done]]
 
@@
 
-	5. The one valuable section is poorly-integrated with the rest of the paper.
+	5. The one valuable section is poorly-integrated with the rest of the paper. [[not done]]
 
@@
 
-	6. Process uncertainty poorly defined, many quibbles about sampling
+	6. Process uncertainty poorly defined, many quibbles about sampling [[done?]]
 
@@
 
-	7. Point about temporal scales of interaction
+	7. Point about temporal scales of interaction [[done?]]
 
@@
 
-	8. Confusion about goal of modelling
+	8. Confusion about goal of modelling [[not done]]
 
@@
 
-	9. ??
+	9. ?? [[not done]]
 
@@
 
-	10. Explain Bayesian approach more simply
+	10. Explain Bayesian approach more simply [[done?]]
 
@@
 
-	11. Integrate L155ff with previous section
+	11. Integrate L155ff with previous section [[not done]]
 
@@
 
-	12. Ideas presented in L209, L262, L310 are important but explained too briefly
+	12. Ideas presented in L209, L262, L310 are important but explained too briefly [[not done]]
 
@@
 
-	13. Reframe line 241 in terms of solutions rather than difficulties
+	13. Reframe line 241 in terms of solutions rather than difficulties [[not done]]
 
@@
 
-	14. Line 283 is unclear
-
-	L283 This seems a very important point and should be explained/expanded more clearly.
+	14. Line 283 seems to be a very important point and should be explained more clearly [[not done]]
 
@@
 
-	15. Line 291: does assuming probability of 1 for observed interactions introduce bias?
+	15. Line 291: does assuming probability of 1 for observed interactions introduce bias? [[not done]]
 
@@
 
-	16. Filtering seems arbitrary
+		\textbf{R:}
+
+	16. Filtering seems arbitrary [[not done]]
 
@@
 
-	17. Expand discussion of results on line 321
+	17. Expand discussion of results on line 321 [[not done]]
 
@@
 
-	18. As a review, the manuscript is disappointing.
-
-	\begin{refquote}
-	Overall, I fear that this review is rather meandering, but I think that reflects some of the challenges I have with the paper.
-Currently I do not think the paper would be used by empirical network ecologists because they either would not understand its relevance or would not be able to apply it practically.
-This would be a great shame.
-I hope that the comments are clear enough to allow the authors to improve the paper – the paper has the potential to be important and very useful.
-	\end{refquote}
-
-	\textbf{R:} As we did not intend to write a review, we understand the Reviewer's complaint.
-This shows that we did not clearly establish the purpose of our manuscript, and we hope that our revision corrects this.
-In particular, we hope that we have established the relevance of our method and offered enough of an explanation that empiricists will be able to apply it.
-Our goal is to increase access to a statistical technique which we see as complementary to high-quality field work, and we believe that the Reviewer's comments will help us to achieve this.
-
 \clearpage

### 2018-11-22 manuscript/CI_interactions.tex
more revisions

@@
 \section*{Abstract}
-
+  [[was fine? Maybe lightly edit to make clear we're not doing a review]]
   \begin{enumerate}
@@
 Presences and absences are not, however, equally certain.
-An observed link definitely occurred, but there are multiple reasons why a given link may not be observed.
+An observed link definitely occurred, but there are multiple reasons why a given link may not be observed~\citep{Jordano2016}.
 
@@
 Species must co-occur in order to be observed interacting, so any variation in co-occurrence will create variation in the set of observed interactions~\citep{Gravel2013}.
-Even assuming constant co-occurrence within a given study system, changing abundances can affect interactions if species which would otherwise interact become too rare to detect each other~\citep{Tylianakis2010}.
+Even assuming constant co-occurrence within a given study system, changing abundances can affect interactions if species which would otherwise interact become too rare to detect each other~\citep{Tylianakis2010,Jordano2016}.
 Moreover, interactions vary over space~\citep{Kitching1987,Baiser2012,Emer2018}, time~\citep{Kitching1987,Olesen2011a,Lopez2017}, between individuals~\citep{Pires2011a,Fodrie2015,Novak2015}, throughout life cycles~\citep{Preston2014,Clegg2018}, and with environmental conditions~\citep{Poisot2015}.
 
-    Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007}).
+    Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007,Jordano2016}).
 An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to correctly document interactions than species~\citep{Poisot2012,Bartomeus2013,Jordano2016,Giron2018,Graham2018}.
@@
 They allow us to estimate the numbers of interactions which have not been observed and predict which unobserved interactions are most likely~\citep{Bartomeus2013}.
+Alternatively, it is possible to estimate the number of unobserved interactions which likely occurred~\citep{Jordano2016}.
+This...
 
@@
 
-    We can create a simple Bayesian approach to modelling the probability of an interaction occurring ($\lambda$) by combining a maximum likelihood estimate of $\lambda$ with a prior distribution (described in the next section) and a normalising function.
-The MLE of $\lambda$, based on the number of observed interactions $k$ and observed co-occurrances $n$ is $\lambda = \frac{k}{n}$.
+    We can create a simple Bayesian approach to modelling the probability of observing an interaction ($\lambda$) by combining a maximum likelihood estimate (MLE) of $\lambda$ with a prior distribution (described in the next section) and a normalising function.
+The MLE of $\lambda$ can be modelled as a Bernoulli trial based on the number of observed interactions $k$ and observed co-occurrances $n$: $\lambda = \frac{k}{n}$.
 The most appropriate prior distribution for a probability such as $\lambda$ is the beta distribution:
@@
 
-    \subsubsection*{Choosing a prior distribution}
+    \subsubsection*{Choosing a prior distribution}  [[expand]]
+      [[expand]]
 
@@
 
-      The choice of prior will depend on the information available.
+      The choice of prior will depend on the information available and the question of interest.
 In general, it is best to use a prior taken from a similar system as emphasised above.
@@
 While an uninformative prior will not greatly reduce variance about $\lambda$, it does clearly state our lack of prior knowledge and will not bias our conclusions.
+Similarly, if detailed information is available but refers to the question at hand, it is best to use a less informative prior so as not to force a particular result.
+For example, if researchers are interested in testing whether body-size ratios affect probabilities of interaction they should not use a prior which predicts interactions based on body sizes.
+
+      \textbf{Uninformative priors}
+
+        An uninformative prior is chosen so as not to bias the posterior distribution in any particular direction.
+That is, all of the information will come from the observed data.
+For pairs of species with little or no observed data, an uninformative prior will leave large variance about $\lambda$ and reflect our lack of knowledge about the pair.
+Since we model $\lambda$ as a Bernoulli trial, the appropriate uninformative prior is Jeffreys prios: a beta distribution with $\alpha$=$\beta$=0.5.
+The sum of $\alpha$ and $\beta$ is roughly equivalent to the weight of the prior, so Jeffreys prior has equal weight to a single observation.
+An uninformative prior is most appropriate when considering a novel system or a system where the only prior knowledge available directly relates to the question we wish to analyse.
+
+      \textbf{Informed priors}
+
+        In most cases, researchers will be able to draw upon prior knowledge for at least some interactions.
+One very simple example is the assumption that, in a food web, plants will not consume any prey.
+There is very little uncertainty around the lack of a observed predation of any plant upon any animal in the system, regardless of how often the plant and animal are observed together.
+
+        [[addressing different types of uncertainty]]
+        [[drawing upon system-specific or broader knowledge]]
+
+        If we are interested only in interactions which occur in the focal system under current environmental conditions, we might use a prior which includes probabilities of co-occurrence.
+That is, we could limit the set of potential interactions to pairs of species which currently co-occur~\citep{Gravel2013}, condition probabilities of interaction on probabilities of co-occurrence based on abundance~\citep{}, etc.
+Note that such models lump together interaction uncertainty and process uncertainty and are only concerned with measuring detection uncertainty.
+Whether or not this is appropriate will depend upon the question of interest.
+
+        If traits governing interactions are known (e.g., body size in food webs~\citep{Gravel2013} or corolla depth in pollination networks~\citep{Graham,Weinstein}), then trait-based models may be used as a prior.
+Such models address interaction uncertainty directly (i.e., they estimate whether a pair of species \emph{can} interact, regardless of whether they are likely to encounter each other).
+To address both interaction and process uncertainty, a researcher might combine trait-based and co-occurrence models into a single prior.
+Such a model would reduce the uncertainty about unobserved interactions, but at the cost of adding more assumptions about the study system.
+This type of very detailed prior is therefore most appropriate in very well-understood systems where a great deal of expert knowledge can be applied.
+
+      \textbf{Empirical priors} [[using data from the data in question]][[contentious]][[should these be drawn from hyperpriors or fixed for each interaction]]
 
   \subsection*{An empirical example}
-
+    [[Make the point of this clearer]]
       To illustrate the process of constructing a Bayesian network, we use the comprehensively-sampled system of willows (\emph{Salix}), herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}.
 This dataset consists of a single community type sampled across Europe over 29 years and at 374 unique locations.
-The data were collected over 29 years at 374 unique locations across Europe.
 The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (see \emph{Appendix S4} for details).
@@
 First, sample sizes should be as large as possible in order to reduce detection uncertainty.
-Second, where sampling on the order of 30-50 observations per species pair is not possible (i.e., in most cases), researchers should acknowledge the varying levels of confidence surrounding interactions between different species pairs.
-Including the $n$ and $k$ values for each interaction will clearly indicate which unobserved interactions are most likely to be observed with further sampling and which estimates are more reliable.
+Second, researchers should acknowledge the varying levels of confidence surrounding interactions between species pairs.
+In the absence of strong prior information a very high level of sampling (i.e., 30-50 observations in our example) is needed \emph{for each species pair}.
+This is not likely to be possible for most studies.
+including the $n$ and $k$ values for each interaction will clearly indicate which unobserved interactions are most likely to be observed with further sampling and which estimates are more reliable.
+Where there are strong prior expectations about pairs of species that will not interact, these should be explicitly stated so that readers know which zeros in an interaction matrix are based on observed data and which are based primarily upon expert knowledge.
 Third, the uncertainty around interactions should be incorporated in calculations of network properties.

### 2018-11-23 manuscript/CI_interactions.tex
adding refs

@@
 Community composition and abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}, leading to variation in encounter probabilites and hence in interactions~\citep{Vazquez2005,Poisot2015,Graham2018}.
-Species must co-occur in order to be observed interacting, so any variation in co-occurrence will create variation in the set of observed interactions~\citep{Gravel2013}.
+Species must co-occur in order to be observed interacting, so any variation in co-occurrence will create variation in the set of observed interactions~\citep{Gravel2013,Graham2018}.
 Even assuming constant co-occurrence within a given study system, changing abundances can affect interactions if species which would otherwise interact become too rare to detect each other~\citep{Tylianakis2010,Jordano2016}.
@@
     Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007,Jordano2016}).
-An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to correctly document interactions than species~\citep{Poisot2012,Bartomeus2013,Jordano2016,Giron2018,Graham2018}.
+An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to correctly document interactions than species~\citep{Guimera2009,Poisot2012,Bartomeus2013,Jordano2016,Giron2018,Graham2018}.
 As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Bartomeeus2013,Poisot2016}.
-Efforts in this vein usually take the form of creating model food webs that approximate observed empirical networks~\citep{Allesina2008,Williams2010,Rohr2016}.
-These models may be based on species traits and/or abundances~\citep{Rohr2016,Graham2018,more} or on simple abstract rules~\citep{Allesina2008,Williams2010}.
+Efforts in this vein usually take the form of creating model food webs that approximate observed empirical networks~\citep{Allesina2008,Guimera2009,Williams2010,Rohr2016}.
+These models may be based on species traits and/or abundances~\citep{Rohr2016,Weinstein2017,Graham2018} or on simple abstract rules~\citep{Allesina2008,Guimera2009,Williams2010}.
 Such networks provide an important ''reality check'' by allowing us to compare the observed network to what would be expected under a particular set of assumptions~\citep{Bartomeus2013,Weinstein??}.
-They allow us to estimate the numbers of interactions which have not been observed and predict which unobserved interactions are most likely~\citep{Bartomeus2013}.
-Alternatively, it is possible to estimate the number of unobserved interactions which likely occurred~\citep{Jordano2016}.
-This...
+They allow us to estimate the numbers of interactions which have not been observed~\citep{Jordano2016,Weinstein2017} and predict which unobserved interactions are most likely~\citep{Guimera2009,Bartomeus2013}.
 
@@
 The detection of any interaction is a stochastic process.
-As a conceptual guide to the factors affecting this process, we describe three nested levels of uncertainty: interaction uncertainty, process uncertainty, and detection uncertainty (Fig.~\ref{conceptual_fig}).
-These levels roughly address the questions: "Could species $i$ and $j$ interact?", "Do they interact at this site/time?" and "Do we observe the interaction?".
+As a conceptual guide to the factors affecting this process, we describe three nested levels of uncertainty that roughly address the questions: "Could species $i$ and $j$ interact?", "Do they interact?" and "Do we observe the interaction?" (Fig.~\ref{conceptual_fig}).
 
-        \subsubsection*{Interaction uncertainty}
+        \subsubsection*{Could the species interact under ideal conditions?}
 
           First, and most fundamentally, some interactions are feasible if a pair of species should co-occur while others are not.
-Assuming that the feasibility of interactions depends on the traits of species involved, we can define the probability of an interaction $L$ given some description of trait-matching $\mathbf{T}$ as $P(L | \mathbf{T})=\lambda$~\citep{Dom?}.
-In some cases the traits prohibiting an interaction are known.
-A potential prey may be too large, small, or well-armoured for a predator to attack, or it might be toxic or non-nutritious (e.g., large carnivores do not consume plants because they cannot digest them and typically do not consume small insects because of the large handling cost relative to the energy gained from tiny prey).
-Where the critical traits are known and mean that an interaction is unfeasbile, $\lambda = 0$ and there is no uncertainty about associated zeros in an interaction matrix.
+Assuming that the feasibility of interactions depends on the traits of species involved, we can define the probability of an interaction $L$ given some description of trait-matching $\mathbf{T}$ as $P(L|\mathbf{T}) = \lambda$~\citep{Gravel2013,others}.
+          In some cases the traits prohibiting an interaction are known, and there will be little uncertainty about $\lambda$.
+          In most cases, however, it is not known what traits might prohibit an interaction~\citep{Dormann2017}.
+Pollinators may visit plants outside of those predicted based on "pollination syndromes"~\citep{Weinstein2017} and herbivores may consume animal prey when it becomes accessible~\citep{}.
+These examples show that we often cannot say that an interaction absolutely does not occur.
+Instead, an unobserved interaction may be a rare phenomenon with $\lambda>0$ and the associated zero in an interaction matrix might be false.
+This uncertainty is partly addressed by trait-matching models in which species with better-matched traits are more likely to interact~\citep{Bartomeus2016,Jordano2016}.
+As these models improve and include better information about the influence of traits on interactions, the uncertainty will be reduced~\citep{Jordano2016} and $\lambda$ should either tend to 0 or to 1.
+Nevertheless, every model is imperfect and lacks information that could be used to define constraints on at least some interactions~\citep{Dormann2017}.
+Until these gaps are filled, some uncertainty will remain about whether some species pairs could interact.
 
-          In most cases, however, it is not known what traits might prohibit an interaction~\citep{Dormann2017}.
-Pollinators may visit plants outside of those predicted based on "pollination syndromes"~\citep{} and herbivores may consume animal prey when it becomes accessible~\citep{}.
-These examples show that we often cannot say that an interaction absolutely does not occur.
-Instead, an unobserved interaction may be a rare phenomenon with $\lambda>0$ and an associated zero in an interaction matrix might be false.
-This uncertainty is partly addressed by trait-matching models in which species with better-matched traits are more likely to interact~\citep{Bartomeus2016}.
-As these models improve and include better information about the influence of traits on interactions, the uncertainty will be reduced and $\lambda$ should either tend to 0 or to 1.
-Nevertheless, every model is imperfect and lacks information that could be used to define constraints on at least some interactions~\citep{Dormann2017}.
-Until these gaps are filled, some interaction uncertainty will remain.
+        \subsubsection*{Did the species interact during sampling?}
 
-          Note that interaction uncertainty does not depend upon whether species $i$ and $j$ actually co-occur.
-Ecologists are often interested in predicting which species are likely to interact following an introduction~\citep{} or range shift~\citep{}.
-In such cases, models based on trait matching can give some information about $\lambda$ while past co-occurance will, of course, not yield much insight.
-
-        \subsubsection*{Process uncertainty} [[Maybe need to rename]]
-
-          Assuming that an interaction is feasible (i.e., $L=1$; species traits do not prohibit an interaction if they should co-occur), an interaction still not occur at a particular place or time.
-This could be because the two species do not co-occur or, if they did occur, because constraints such as inclement weather or low abundance prevented the interaction.
-For example, a pollination interaction may not occur on a rainy day or a rare galler may not parasitize a rare plant because they do not encounter each other.
+          Assuming that an interaction is feasible (i.e., $L=1$;), an interaction may still not occur at a particular place or time~\citep{Graham2018}.
+This could be because the two species do not co-occur or, if they did occur, because constraints such as inclement weather or low abundance prevented the interaction~\citep{Jordano2016,Graham2018} or because a more preferred interaction partnre was available~\citep{Weinstein2017}.
+For example, a rare galler may not parasitize a rare plant because they do not encounter each other.
           We can define the local realisation of an interaction, $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L=1)=\chi$.
-It is unlikely that $\chi$=1 except in the case of obligate specialists who always interact whenever they co-occur and always co-occur.
+It is unlikely that $\chi=1$  except in the case of obligate specialists who always interact whenever they co-occur and always co-occur.
 When $\chi<1$ we cannot be sure whether an unobserved interaction did not occur and when it occurred but was not observed.
@@
 Some of these factors can be addressed in mesocosm studies of networks (e.g., environmental conditions can be held stable) or could be included in models along the line of trait-matching models (e.g., phenological matching).
-Expanding sampling to cover a broader spatial or temporal range (e.g., sampling in a variety of microhabitats or during a variety of weather conditions) will also help to reduce process uncertainty if resource constraints permit.
-In the field, however, process uncertainty is likely inevitable as long as local conditions are not constant during sampling.
+Expanding sampling to cover a broader spatial or temporal range (e.g., sampling in a variety of microhabitats or during a variety of weather conditions) will also help to reduce uncertainty if resource constraints permit.
+As long as researchers wish to sample empirical networks subject to changing conditions, however, it is not likely that they will be able to eliminate all uncertainty about whether or not pairs of species will interact during a given sampling period.
 
          % One proposed solution to the problem of process uncertainty is to use repeated sampling of networks.
-For example,~\citet{Weinstein2017-wrong one?} used repeated sampling to estimate the daily probability of detecting an interaction and thereby model detection and process uncertainty.[[This apparently confused R3]] While conceptually attractive, this approach is unsuitable for interactions occurring over longer time scales (e.g., associations between hosts and parasitoids with a single generation per year), or very rare interactions which might not occur on any of the sampling days.
-Moreover, the faster accumulation of species than interactions means that repeated sampling will tend to introduce more unobserved interactions than observed interactions unless the number of samples is very high~\citep{Poisot2012}.
+For example,~\citet{Weinstein2017-wrong one?} used repeated sampling to estimate the daily probability of detecting an interaction and thereby attempted to separate detection and process uncertainty.[[This apparently confused R3]] While conceptually attractive, this approach is unsuitable for interactions occurring over longer time scales (e.g., associations between hosts and parasitoids with a single generation per year), which would require multi-year sampling efforts, or very rare interactions which would require extremely high sampling effort to detect.
+Moreover, the faster accumulation of species than interactions means that repeated sampling will tend to introduce more unobserved interactions than observed interactions unless the number of samples is high enough to ensure that all species present have been observed~\citep{Poisot2012,Jordano2016}.
+
+          \textbf{Forbidden links}
+
+            Both of the above sources of uncertainty (i.e., whether species would be able to interact given their traits and whether they are able to interact at a particular place and time) are addressed in the concept of "forbidden links"~\citep{Jordano2016}.
+In this framework, all links which are prevented by spatio-temporal uncoupling~\citep{Jordano1987}, physiological constraints~\citep{Jordano1987,More2012}, etc.
+are considered "structural zeros" that cannot be observed~\citep{Jordano2016}.
+We conceptually distinguish between physiological constraints and spatio-temporal uncoupling to allow for cases in which a species is introduced to a new habitat, expands its range, or shifts phenology.
+In such cases, links which are forbidden due to physiological constraints remain forbidden but links previously forbidden due to spatio-temporal mismatch could potentially occur.
 
@@
           Lastly, measurement errors are a pervasive source of uncertainty in the observation of ecological processes.
-Even if an interaction is feasible and occurs during sampling ($L = 1$ and $X = 1$), we may still fail to detect it.
+Even if an interaction is feasible and occurs during sampling ($L = 1$ and $X = 1$), we may still fail to detect it~\citep{Jordano2016,Weinstein2017}.
 We may define the probability of detecting of an interaction, $D$, given the interaction is feasible and occurs, as a stochastic process with the associated probability $P(D|X=1,L=1)=\delta$.
 Detection failure could happen for many reasons (see~\citet{Wirta2014} for examples and partial solutions to them).
-Some sources of detection error can be minimised with appropriate sampling effort ($\delta$ will approach one with increasing number of samples), but other sources are often difficult to reduce (e.g.
+Some sources of detection error can be minimised with appropriate sampling effort (e.g., combining plant-focused and animal-focused sampling when assembling pollination networks~\citet{Jordano2016}), but other sources are often difficult to reduce (e.g.
 the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification as in~\citealt{Wirta2014,Frost2016}).
@@
 
-          To sum up, the absence of an interaction on a given day could therefore be because it was not feasible [$P(L) = 0$], was feasible but did not occur because of local conditions during sampling ($P(X|L=1) = 0$], or was feasible and occurred during sampling but could not be observed [$P(D|X=1,L=1)=0$].
-Note that some exteral factors can affect both process and detection uncertainty.
-For example, rare species are less likely to interact at a given site due to neutral processes (process uncertainty)~\citep{}.
-Interactions involving rare species are also less likely to be detected (detection uncertainty), unless more sampling effort is focused on rare than common species~\citep{}.
+      To sum up, the absence of an interaction on a given day could  be because it was not feasible [$P(L) = 0$], was feasible but did not occur because of local conditions during sampling ($P(X|L=1) = 0$], or was feasible and occurred during sampling but could not be observed [$P(D|X=1,L=1)=0$].
+Note that some exteral factors can affect more than one level of uncertainty.
+For example, rare species are less likely to interact at a given site due to neutral processes~\citep{}.
+Interactions involving rare species are also less likely to be detected, unless more sampling effort is focused on rare than common species~\citep{Jordano2016}.
+Thus, abundance affects both the probability of an interaction occurring at a particular site \emph{and} our ability to observe the interaction.
 Similarly, bad weather can make interactions such as pollination less likely by reducing pollinator activity~\citep{}.
-For those pollinators which do venture forth in poor conditions, bad weather might also reduce visibility and therefore increase detection uncertainty.
+For those pollinators which do venture forth in poor conditions, bad weather might also  increase detection uncertainty through reduced visibility or if pollinators make shorter trips.
+The "forbidden links" of~\citet{Jordano2016} can also occur due to process or interaction uncertainty in our framework.
 
@@
         An observed interaction indicates that an interaction was feasible, occurred during sampling, and was detectable ($L = 1$, $X = 1$, and $D = 1$).
-An unobserved interaction could be due to any of the three sources of uncertainty ($D$, $X$, and/or $L = 0$).
+An unobserved interaction could be due to any of the three sources of uncertainty ($D$, $X$, and/or $L = 0$) and it is not usually possible to identify the source in empirical data.
 Only the case where $L = 0$ is an interaction that never occurs --the usual interpretation of a $0$ value in an interaction matrix.
@@
 where the interaction occurred at the location but was not observed, and $X = 0 \cup L =1$, i.e., where the interaction is feasible but did not occur at the local site (Fig.~\ref{conceptual_fig}).
-        This is not possible, however, using empirical data.
 An empirical ecologist will instead measure the marginal probability $P(L) = k/n$, where $k$ is the number of observed interactions and $n$ the number of observed co-occurrences.
@@
 For both molecular and rearing techniques, certain types of interactions may go unnoticed due to technical challenges~\citep{Wirta2014}.
-This can bias the set of recorded interactions towards those that are easier to observe.
+This can bias the set of recorded interactions towards those that are easier to observe~\citep{Jordano2016}.
 
@@
 Intensive sampling is, therefore, an important step towards reducing uncertainty in ecological networks but is unlikely to be enough in most cases.
+        Indeed, despite substantial improvements in recent decades, most available interaction networks are still undersampled and, moreover, are only subsets of larger communities~\citep{Jordano2016}.
         To supplement repeated sampling efforts and reduce uncertainty around unobserved interactions, we suggest researchers use prior knowledge of the same or similar systems.
@@
 
-        If traits governing interactions are known (e.g., body size in food webs~\citep{Gravel2013} or corolla depth in pollination networks~\citep{Graham,Weinstein}), then trait-based models may be used as a prior.
+        If traits governing interactions are known (e.g., body size in food webs~\citep{Gravel2013} or corolla depth in pollination networks~\citep{Weinstein2017,Graham}), then trait-based models may be used as a prior.
 Such models address interaction uncertainty directly (i.e., they estimate whether a pair of species \emph{can} interact, regardless of whether they are likely to encounter each other).
@@
 This type of very detailed prior is therefore most appropriate in very well-understood systems where a great deal of expert knowledge can be applied.
+
+        An informed prior could be based on one or a few traits, as those described above, or it could incorporate a great deal of information about co-occurrence and encounter probabilities, forbidden links, etc.~\citep{Jordano2016}.
+Importantly, the complexity of a prior model depends both on the information available and on the question of interest.
+If researchers wish to test for an effect of body mass ratios on interaction probabilities, for example, they should not include body mass in their prior.
+Including a trait in a prior means assuming that trait has an effect on which interactions we detect and it is therefore inappropriate to test for such an effect in the same study.
+
+        The relevant traits and degree of trait-matching between interaction partners is likely to vary between systems~\citep{Gravel2013,Weinstein2017}.
+We therefore urge caution when using a model developed for one system as the prior for another.
 
@@
 
-  Real interaction networks vary over several dimensions~\citep{Kitching1987,Olesen2011a,Pires2011a,Baiser2012,Fodrie2015,Novak2015}, leading to pervasive under-estimation of interactions in published networks.
+  Real interaction networks vary over several dimensions~\citep{Kitching1987,Olesen2011a,Pires2011a,Baiser2012,Fodrie2015,Novak2015}, leading to pervasive under-estimation of interactions in published networks~\citep{Jordano2016}.
 Even in the most extensive data set that we could find, there was very little empirical data for each species pair.
@@
 Increasing sampling is therefore likely to add more zeros than ones to an interaction network.
+
+  Detectability estimated at 23.3\% in~\citet{Weinstein2017}
 
@@
   Based on the framework described above, we can now offer some recommendations for improved descriptions of ecological interactions.
+Observing all interactions in a network is likely impossible~\citep{Jordano2016}, but researchers can take steps to address the uncertainty this implies.
 First, sample sizes should be as large as possible in order to reduce detection uncertainty.
 Second, researchers should acknowledge the varying levels of confidence surrounding interactions between species pairs.
-In the absence of strong prior information a very high level of sampling (i.e., 30-50 observations in our example) is needed \emph{for each species pair}.
-This is not likely to be possible for most studies.
-including the $n$ and $k$ values for each interaction will clearly indicate which unobserved interactions are most likely to be observed with further sampling and which estimates are more reliable.
+Including the $n$ and $k$ values for each interaction will clearly indicate which unobserved interactions are most likely to be observed with further sampling and which estimates are more reliable.
 Where there are strong prior expectations about pairs of species that will not interact, these should be explicitly stated so that readers know which zeros in an interaction matrix are based on observed data and which are based primarily upon expert knowledge.
@@
 The development and decreasing price of novel methods such as DNA barcoding and remote sensing can help field researchers to do more with less, but it remains to be seen whether these improvements will be enough to fully-describe large study systems.
-\\
+In the absence of new break-through sampling techniques, logistical limitations mean that allocating sampling effort is a zero-sum game.
+That is, allocating more sampling to reduce one source of uncertainty will remove sampling effort that could reduce another source of uncertainty.\\
 \textbf{2)} High sampling effort with a constant methodology will reliably describe some interactions but not others.

### 2018-11-26 manuscript/CI_interactions.tex
added all the refs I've come up with

@@
     Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007,Jordano2016}).
-An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to correctly document interactions than species~\citep{Guimera2009,Poisot2012,Bartomeus2013,Jordano2016,Giron2018,Graham2018}.
+An assessment of the accumulation of inter0actions with increasing sampling effort suggests that it is even more challenging to correctly document interactions than species~\citep{Guimera2009,Poisot2012,Bartomeus2013,Jordano2016,Giron2018,Graham2018}.
 As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Bartomeeus2013,Poisot2016}.
 Efforts in this vein usually take the form of creating model food webs that approximate observed empirical networks~\citep{Allesina2008,Guimera2009,Williams2010,Rohr2016}.
-These models may be based on species traits and/or abundances~\citep{Rohr2016,Weinstein2017,Graham2018} or on simple abstract rules~\citep{Allesina2008,Guimera2009,Williams2010}.
-Such networks provide an important ''reality check'' by allowing us to compare the observed network to what would be expected under a particular set of assumptions~\citep{Bartomeus2013,Weinstein??}.
-They allow us to estimate the numbers of interactions which have not been observed~\citep{Jordano2016,Weinstein2017} and predict which unobserved interactions are most likely~\citep{Guimera2009,Bartomeus2013}.
+These models may be based on species traits and/or abundances~\citep{Rohr2016,Weinstein2017,Weinstein2017a,Graham2018} or on simple abstract rules~\citep{Allesina2008,Guimera2009,Williams2010}.
+Such models provide an important ''reality check'' by allowing us to test hypotheses about the factors structuring ecological networks~\citep{Bartomeus2013,Weinstein2017.Weinstein2017a,Graham2018}.
+They can also allow us to estimate the numbers of interactions which have not been observed~\citep{Jordano2016,Weinstein2017a} and predict which unobserved interactions are most likely~\citep{Guimera2009,Bartomeus2013}.
 
-    [[Trying to give a more precise summary of our goal here.]]
-    While predictive networks acknowledge the variability of interaction networks, they do not quantify the different degrees of uncertainty about different interactions.
-In fact, many assume that all interactions which actually occur have been observed and that there are no false positives~\citep{Bartomeus2016,others?}.
-This amounts of assuming that, while the strengths or frequencies of interactions may vary, we can be certain about the structure of the binary presence or absence of interactions.
-Other models assume that the probability of interaction is constant during the sampling period~\citep{Bartomeus2013}.
-Here we show that both assumptions are unlikely due to the many layers of uncertainty affecting the observation of interactions~\citep{Jordano2016}.
-Increased or improved sampling could reduce many of these sources uncertainty, but we suspect that most research groups limit sampling due to time or budget constraints.
-Given that increased sampling is not likely to be a viable solution to the problem of uncertainty about unobserved interactions (see Box 1), we offer a Bayesian framework to capture the uncertainty surrounding interactions which were not observed.
-This framework can be applied to any network type and does not require strong assumptions or pre-existing data about the study system, but can include such information if it is available.
+    [[These two paragraphs try to frame our study more clearly. Any help to shorten them?]]
+    To date, models incorporating uncertainty have either been very general (e.g.,~\citet{Guimera2009,Gravel2013}) or very system-specific (e.g.,~\citet{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}).
+The general models may not include any system-specific information, while the system-specific models may not be applicable outside of their system of origin.
+Here we propose a simple Bayesian framework that can include broad general trends in network structure or highly specific expert knowledge, depending on the situation.
+This framework is designed to make the assumptions used when building networks more explicit and to quantify our uncertainty around each interaction in a network.
+Importantly, the simplicity of the framework means it should be easily applicable to any network type or study system.
+
+    First, we provide a brief description of the nested levels of uncertainty affecting ecological network construction.
+In the context of this uncertainty, which can be reduced but usually not eliminated by high-quality sampling (\citealp[see Box 1]{Bartomes2013}), we present our Bayesian framework for combining observed data with a prior expectation of network structure.
+We conclude with a worked example applying this framework to an intensively-sampled willow-galler network.
+We find that even the highest-quality empirical network we could find had substantial uncertainty about whether many pairs of species interact, demonstrating the need to include information about this uncertainty in published networks.
+We also show that this interaction-level uncertainty leads to uncertainty about estimates of network structure, with important implications for comparisons across networks.
 
@@
 
-          First, and most fundamentally, some interactions are feasible if a pair of species should co-occur while others are not.
+          First, and most fundamentally, some interactions are feasible if a pair of species should co-occur while others are not~\citep{Poisot2015}.
 Assuming that the feasibility of interactions depends on the traits of species involved, we can define the probability of an interaction $L$ given some description of trait-matching $\mathbf{T}$ as $P(L|\mathbf{T}) = \lambda$~\citep{Gravel2013,others}.
@@
           In most cases, however, it is not known what traits might prohibit an interaction~\citep{Dormann2017}.
-Pollinators may visit plants outside of those predicted based on "pollination syndromes"~\citep{Weinstein2017} and herbivores may consume animal prey when it becomes accessible~\citep{}.
+Pollinators may visit plants outside of those predicted based on "pollination syndromes"~\citep{Weinstein2017a} and herbivores may consume animal prey when it becomes accessible~\citep{}.
 These examples show that we often cannot say that an interaction absolutely does not occur.
@@
 
-          Assuming that an interaction is feasible (i.e., $L=1$;), an interaction may still not occur at a particular place or time~\citep{Graham2018}.
-This could be because the two species do not co-occur or, if they did occur, because constraints such as inclement weather or low abundance prevented the interaction~\citep{Jordano2016,Graham2018} or because a more preferred interaction partnre was available~\citep{Weinstein2017}.
+          Assuming that an interaction is feasible (i.e., $L=1$;), an interaction may still not occur at a particular place or time~\citep{Poisot2015,Graham2018}.
+This could be because the two species do not co-occur or, if they did occur, because constraints such as inclement weather or low abundance prevented the interaction~\citep{Jordano2016,Graham2018}, a more preferred interaction partner was available~\citep{Weinstein2017a}, or substantial individual variation in traits meant that local individuals could not interact even if the species in general can~\citep{Gravel2013,Poisot2015}.
 For example, a rare galler may not parasitize a rare plant because they do not encounter each other.
@@
 
+          Some models attempt to eliminate the sources of variation above by sampling intensively over a short time, during which probabilities of interaction are assumed to be constant~\citep{Bartomeus2013,Weinstein2017,Weinstein2017a}.
+Any remaining variation in the interactions observed is therefore assumed to be due to detection uncertainty.
+This assumption may be accurate for some systems where the environment is relatively constant, there is little intraspecific variation in traits or preferences, etc.
+In most systems, and for any effort to compile a metaweb that will apply over broader spatial and temporal scales, probabilities of interaction are likely to vary during sampling.
+
          % One proposed solution to the problem of process uncertainty is to use repeated sampling of networks.
@@
 are considered "structural zeros" that cannot be observed~\citep{Jordano2016}.
-We conceptually distinguish between physiological constraints and spatio-temporal uncoupling to allow for cases in which a species is introduced to a new habitat, expands its range, or shifts phenology.
+We conceptually distinguish between physiological constraints and spatio-temporal uncoupling to allow for cases in which a species is introduced to a new habitat, expands its range, or shifts phenology~\citep{Gravel2013}.
 In such cases, links which are forbidden due to physiological constraints remain forbidden but links previously forbidden due to spatio-temporal mismatch could potentially occur.
@@
 For both molecular and rearing techniques, certain types of interactions may go unnoticed due to technical challenges~\citep{Wirta2014}.
-This can bias the set of recorded interactions towards those that are easier to observe~\citep{Jordano2016}.
+This can bias the set of recorded interactions towards those that are easier to observe~\citep{Carstensen2014,Jordano2016}.
 
@@
         If we are interested only in interactions which occur in the focal system under current environmental conditions, we might use a prior which includes probabilities of co-occurrence.
-That is, we could limit the set of potential interactions to pairs of species which currently co-occur~\citep{Gravel2013}, condition probabilities of interaction on probabilities of co-occurrence based on abundance~\citep{}, etc.
-Note that such models lump together interaction uncertainty and process uncertainty and are only concerned with measuring detection uncertainty.
+That is, we could limit the set of potential interactions to pairs of species which currently co-occur, condition probabilities of interaction on probabilities of co-occurrence based on abundance or habitat use, etc.~\citep{Gravel2013,Weinstein2017} Note that such models lump together interaction uncertainty and process uncertainty and are only concerned with measuring detection uncertainty.
 Whether or not this is appropriate will depend upon the question of interest.
 
-        If traits governing interactions are known (e.g., body size in food webs~\citep{Gravel2013} or corolla depth in pollination networks~\citep{Weinstein2017,Graham}), then trait-based models may be used as a prior.
+        If traits governing interactions are known (e.g., body size in food webs~\citep{Gravel2013} or corolla depth in pollination networks~\citep{Weinstein2017a,Graham}), then trait-based models may be used as a prior.
 Such models address interaction uncertainty directly (i.e., they estimate whether a pair of species \emph{can} interact, regardless of whether they are likely to encounter each other).
@@
 Such a model would reduce the uncertainty about unobserved interactions, but at the cost of adding more assumptions about the study system.
-This type of very detailed prior is therefore most appropriate in very well-understood systems where a great deal of expert knowledge can be applied.
+This type of very detailed prior is therefore most appropriate in very well-understood systems where a great deal of expert knowledge can be applied, or in systems which are believed to follow general rules of, for example, allometric scaling~\citep{Gravel2013}.
+Where there is less system-specific prior knowledge, we can use prior models based on general trends in allometric scaling~\citep{Riede2011,Gravel2013}.
 
@@
 
-        The relevant traits and degree of trait-matching between interaction partners is likely to vary between systems~\citep{Gravel2013,Weinstein2017}.
+        The relevant traits and degree of trait-matching between interaction partners is likely to vary between systems~\citep{Gravel2013,Weinstein2017a}.
 We therefore urge caution when using a model developed for one system as the prior for another.
@@
 We analysed both the \emph{Salix}-galler and galler-natural enemy components of the network but, for brevity, present only the latter here (see~\emph{Appendix S5} for \emph{Salix}-galler results).
+
+      Unlike~\citet{Bartomeus2013,Weinstein2017,Weinstein2017a}, our model can include interactions for species which were observed infrequently (or not at all) during sampling.
 
@@
 
+  % Poisot2015 - also found that NODF was higher in the empirical data than in sims.
+
 \section*{Discussion}
@@
 Most pairs of species were not observed co-occurring even once, less than 10\% of species pairs were observed interacting, and no pairs were observed to co-occur frequently enough to conclude that their probability of interacting was below 0.01.
-This suggests that limited sampling is a major source of uncertainty in empirical networks.
+This suggests that limited sampling is a major source of uncertainty in empirical networks, in agreement with~\citet{Jordano2016,Weinstein2017a,Weinstein2017}.
 This dataset also illustrates the problem of process uncertainty - pairs of species which were observed interacting did not interact in all of the samples in which they co-occurred.
@@
 
-  Detectability estimated at 23.3\% in~\citet{Weinstein2017}
+  Detectability estimated at 23.3\% in~\citet{Weinstein2017a}
 
@@
 This approach is particularly useful when considering interactions involving species entering new ranges due to climate change or introductions.
-Understanding these species' interactions is important for a variety of conservation questions, and a Bayesian approach using a trait-matching model or data from species' current ranges could help us to anticipate how species will integrate into new communities.
+Understanding these species' interactions is important for a variety of conservation questions~\citep{Bartomeus2013,Gravel2013}, and a Bayesian approach using a trait-matching model or data from species' current ranges could help us to anticipate how species will integrate into new communities.
 

### 2018-11-27 manuscript/reply_to_reviewers.tex
getting close to the end, except R2

@@
 
+Changes: reducing discussion of different sources of uncertainty, increasing description of priors, added a bunch of refs, trying to frame our study more clearly.
+
+Still to do: framing, expand discussion of network metrics from sampled vs.
+predicted vs.
+expert knowledge networks...
+(ours reflect about 50\% of links observed, doesn't seem super out of line).
+Make clearer that we are modelling L but could also model X|L with independent $n$ and $k$ data within a single site.
+Maybe in the section introducing the model or introducing the case study?
+
+Ask for help: how would we expand this to interaction frequencies? Still with the Bernoulli?
 % -----------------------------------------------------------------------------
@@
 I see the makings of a really nice paper here, and I’m confident the authors will be able to achieve this text revision.
+			\medskip
+			At the same time, the paper is clear and very readable. I wholly support the method and I think it is something critical that needs to be adopted by the community. \\
+			Having read the paper several times, I think that the authors are trying to cast their net too widely, even starting from the title.
+From that perspective, they don’t meet the expectation of new insight.
+However!!
+I was extremely interested in the brief discussion on using prior knowledge, especially the delicacy of trying to transfer information among networks (L248).
+My recommendation is to drastically reduce the grandiose attempt at a “quantitative framework for networks” (L1 – L246) and really zoom in on the contribution of transferring information among networks through informed priors.	Again L278, this is very well covered in concept by recent papers in MEE that include the authors of this work, as well as several by Weinstein, Bartomeus and others.
 			\end{refquote}
@@
 
-	2. Suggestion to add more literature [[in progress]]
+			We thank the Reviewer for their compliments and accept their suggestion that we are somewhat overexcited about our approach.
+We have refined the introduction to be more specific about the problem we are attempting to solve.
+We have also expanded our treatment of prior selection and hope that our paper now reads as achieving its goal.
+
+	2. Suggestion to add more literature [[done]]
 
@@
 		\textbf{R:} We thank the Reviewer for the literature suggestions and now include them in our introduction and/or discussion.
-We emphasize the board applicability of our appraoch across network types and where species traits affecting interaction probability may not be known.
-[[Make sure this comes through]] We hope that the contribution our manuscript makes is now clearer.
+We emphasize the board applicability of our approach across network types and systems with varying degrees of prior knowledge.
+We also emphasize that our approach is not restricted to species observed X times (as many predictive models are) and can include species not yet observed at a site (e.g., potential invaders).
+We hope that the contribution our manuscript makes is now clearer.
 
@@
 We hope that the revisions make our stance on repeated sampling clearer and that there are no longer apparent contradictions.
-
-	7. Final comment on framing the study [[I think done?]]
-
-		\begin{refquote}
-		At the same time, the paper is clear and very readable. I wholly support the method and I think it is something critical that needs to be adopted by the community. \\
-		Having read the paper several times, I think that the authors are trying to cast their net too widely, even starting from the title.
-From that perspective, they don’t meet the expectation of new insight.
-However!!
-I was extremely interested in the brief discussion on using prior knowledge, especially the delicacy of trying to transfer information among networks (L248).
-My recommendation is to drastically reduce the grandiose attempt at a “quantitative framework for networks” (L1 – L246) and really zoom in on the contribution of transferring information among networks through informed priors.	Again L278, this is very well covered in concept by recent papers in MEE that include the authors of this work, as well as several by Weinstein, Bartomeus and others.
-		\end{refquote}
-
-		\textbf{R:} We thank the Reviewer for their compliments and accept their suggestion that we are somewhat overexcited about our approach.
-We have refined the introduction to be more specific about the problem we are attempting to solve.
-We have also expanded our treatment of prior selection and hope that our paper now reads as achieving its goal.
 
@@
 		I hope this review is helpful.
+
+		More generally, the introduction does not really do justice to what has been done already – even the authors own work.
+The problem in my view is that the community using better statistics – of which the authors are very important members – has not managed to communicate to most people studying networks and better methods are simply not being adopted.
+The current paper is a very nice attempt to show the broader community that the Bayesian approach is not so complex and has many advantages.
+I think this is a very important message and is what makes this paper an important contribution.
+Further, the approach to parse out different types of uncertainty and suggestions for how to come-up with informative priors – is very useful.
+The theory/method is well developed overall and provides an example – which is great.
+
 		\end{refquote}
@@
 
-	1. Add more references to the literature [[in progress]]
+	1. Add more references to the literature [[done]]
 
@@
 We have taken particular care to add references to Graham/Weinsten papers as two of the reviewers suggested work by these authors.
-We hope that we now adequately acknowledge previous work.
+We hope that the introduction now presents a more thorough sample of previous work.
 
@@
 
-		\begin{quotation}
+		\begin{refquote}
 		Line 30.  There are several conceptual and empirical attempts to consider detection probability – why aren’t these cited (work by Bartomeus comes to mind).\\
+		\end{refquote}
 
+			\textbf{R:} We have added a citation to Bartomeus as requested.
+
+		\begin{refquote}
 			Line 36.  I certainly see value in the approach and the general ideas of these authors in particular but they should acknowledge the work that has been done by themselves and others!\\
+		\end{refquote}
 
+		\textbf{R:} We have rephrased the end of this paragraph to mention previous predictive models dealing with uncertainty in interaction matrices.
+
+		\begin{refquote}
 		Line 89.
 In Weinstein and Graham (Ecology Letters) the processes modeled were trait matching (which you place in interaction uncertainty) and abundance (which is perhaps your process uncertainty??).
-I find myself quite confused based on how you describe things in this MS (See text above) and how you cite the literature.\\
+I find myself quite confused based on how you describe things in this MS (See text above) and how you cite the literature.
+		\end{refquote}
 
+		\textbf{R:} We have revised this section and now no longer refer to the specifics of Weinstein and Graham at all.
+Instead, we discuss repeated sampling in a box dedicated to the question of whether sampling is useful (of course it is) and whether it can completely solve problems of uncertainty in ecological networks (almost certinaly not).
+We hope that this is less confusing.
+
+		\begin{refquote}
 		Line 148.
@@
 but the other work should be considered.
-More generally, the introduction does not really do justice to what has been done already – even the authors own work.
-The problem in my view is that the community using better statistics – of which the authors are very important members – has not managed to communicate to most people studying networks and better methods are simply not being adopted.
-The current paper is a very nice attempt to show the broader community that the Bayesian approach is not so complex and has many advantages.
-I think this is a very important message and is what makes this paper an important contribution.
-Further, the approach to parse out different types of uncertainty and suggestions for how to come-up with informative priors – is very useful.
-The theory/method is well developed overall and provides an example – which is great.\\
+		\end{refquote}
+
+		\textbf{R:} We had not seen the Graham and Weinstein paper when we first submitted our manuscript, but now cite it in the introduction.
+We have also revised this section in hopes of making the uniqueness of our framework (its simplicity and adaptability) clear.
+
+		\begin{refquote}
 		Line 288.
@@
 Isn’t this the same as drawing a probability of interaction from a distribution where the distribution of each interaction is an output of the Bayesian method?\\
+		\end{refquote}
+
+		\textbf{R:} Yes, that is exactly the idea.
+We are also sure that this is a common approach and therefore hadn't cited it (in the same way one would not be likely to cite the prior users of common statistical tests).
+We have added a citation to~\citet{Vazquez2005,Guimera2009} as two examples and hope that this is sufficient.
+
+		\begin{refquote}
 		Line 352 – 358.  Citations are needed in this section as this has been suggested before.
@@
 
-		\textbf{R:}
+		\textbf{R:} Most of these lines refer specifically to our results, making it somewhat difficult to add citations.
+We have added citations where possible and rephrased this section to make it clearer when we are referring to work done in the present manuscript.
 
-	2. Confusing terminology [[not done]]
+	2. Confusing terminology [[done]]
 
@@
 
-		\textbf{R:} [[interaction and process uncertainty...]] We respond to the Reviewer's comments about sampling below.
+		\textbf{R:} We have revised this section of the introduction to both avoid introducing rigid terminology and make it clear that our model is not concerned with partitioning different sources of variation (indeed, we state that in many cases this is not possible using empirical data).
+Hopefully this will discourage readers from getting bogged down in trying to isolate which external factors cause which types of uncertainty (there is almost certainly overlap - e.g., bad weather could both reduce the probability that species will be active and interact and the probability that an interaction is observed if visibility is poor).
+We have also added a section (lines XX-XX) referring to "forbidden links" which address aspects of whether species can interact (which we had previously called interaction uncertainty) and whether they do interact at a particular site (previously process uncertainty).
+We hope that this addition clarifies the agreement of our manuscript with previous works listing sources of uncertainty.
 
-	3. Introduction of the case study seems off-topic and illogical. [[not done - R1 also points out that this is a weak point]]
+			\begin{quotation}
+
+        \textbf{Forbidden links}
+
+            Both of the above sources of uncertainty (i.e., whether species would be able to interact given their traits and whether they are able to interact at a particular place and time) are addressed in the concept of "forbidden links"~\citep{Jordano2016}.
+In this framework, all links which are prevented by spatio-temporal uncoupling~\citep{Jordano1987}, physiological constraints~\citep{Jordano1987,More2012}, etc.
+are considered "structural zeros" that cannot be observed~\citep{Jordano2016}.
+We conceptually distinguish between physiological constraints and spatio-temporal uncoupling to allow for cases in which a species is introduced to a new habitat, expands its range, or shifts phenology~\citep{Gravel2013}.
+In such cases, links which are forbidden due to physiological constraints remain forbidden but links previously forbidden due to spatio-temporal mismatch could potentially occur.
+
+      \end{quotation}
+
+	3. Introduction of the case study seems off-topic and illogical. [[done]]
 
@@
 		3.      The set up (introduction) to the case study is quite odd and somehow seems off topic – or at least not logical based on what the reader has read up to that point.
-		\end{refquote}
-
-		\textbf{R:}
-
-		\begin{refquote}
+		\medskip
 		Line 240.
@@
 Is the goal to show the gaps in sampling or to apply the model described thus far to consider the 3 different types of uncertainty outlined?
-At this point the reader is confused about the goal… \\
+At this point the reader is confused about the goal…
+		\medskip
 		Line 249.  The statement about training data is redundant with what is stated above – adjust writing.
@@
 
-		\textbf{R:}
+		\textbf{R:} We have expanded our introduction of the case study (lines XX-XX) to make it clear that we are using the highest-quality empirical network we can find as even such networks have uncertainty about unobserved interactions.
+This relates back to our point that urging increased sampling effort is not likely to solve problems of uncertainty as long as sampling is limited in number of methodologies, biased towards abundant or easy-to-identify species, restricted to particular spatial sites and/or environmental conditions (if the network is intended to be more general), or all of the above.
+We repeat this point in the discussion to ensure that the case study is relevant.
+We have also clarified our statement that strict Bayes does not allow empirical priors, but that they are an option for researchers that are more concerned about matching their prior to their study system than with strict formalism (lines XX-XX).
+As Reviewer 1 points out, this is somewhat controversial and we feel it is important to note the potential objection.
+
+		\begin{quotation}
+
+ 			To illustrate the process of constructing a Bayesian network to quantify uncertainty about interactions, we use the comprehensively-sampled system of willows (\emph{Salix}), herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}.
+This dataset consists of a single community type sampled across Europe over 29 years and at 374 unique locations.
+The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (see \emph{Appendix S4} for details).
+      The high spatiotemporal resolution of this dataset make it ideal for illustrating the difficulties in completely sampling a network; even with such an unusually high sampling effort, we anticipate that there will be many pairs of species which were rarely or never observed together.
+To show the gaps in sampling, we compared the frequencies of observed co-occurrences and interactions.
+We then calculated an empirical prior and computed the posterior distribution of the probability of observing each as-yet-unobserved interaction in the future.
+      \medskip
+			While a strict Bayesian framework requires a prior distribution that does not rely on any information from the study at hand, such data are not always available.
+In that case, researchers must choose between using a less-informative prior (e.g., one based on distributions of links across a large set of networks) or an empirical prior based on some "training data" from the study.
+		\end{quotation}
 
@@
 We chose to be more charitable than the Reviewer and assume that those compiling empirical networks are sampling as much as possible given the constraints of their system and available resources.
-Infite sampling would, of course, be the best option but it is unlikely that researchers will be able to perpetually increase sampling.
+Infinite sampling would, of course, be the best option but it is unlikely that researchers will be able to perpetually increase sampling.
 
@@
 
-	7. Why not always model probabilities of co-occurrance? [[done]]
+	7. Why not always model probabilities of co-occurrence? [[done]]
 
@@
 
-	10. Unsure about the point of filtering networks [[not done]]
+	10. Unsure about the point of filtering networks [[done]]
 
@@
 
-		\textbf{R:}
+		\textbf{R:} The filtering was intended to show how uncertainty likely warps our current understanding of network properties like connectance.
+If we do not observe 20-50\% of the interactions in a network, then many network properties in the published literature will be inaccurate.
+Even worse, networks compiled under different levels of uncertainty (e.g., species with more or less variable traits, or studies with multiple sampling methods or only one) or with different sampling efforts will have network structure metrics that are inaccurate to different degrees.
+Filtering networks in the way that we do could give an idea of how many networks are missing, but we do not think it is necessary to evaluate uncertainty (we believe that examining the posterior distributions directly is a better approach there).
+We have rephrased these lines (XX-XX) to emphasize that the filtered networks are intended to demonstrate the consequences of uncertainty more than anything else.
+
+		\begin{quotation}
+			Measures of network structure which are based on empirical networks that are missing interactions may differ substantially from the values that would be obtained if detection certainty and variation in interactions over space and time could be removed.
+To demonstrate this, we created a suite of filtered networks for each posterior network.
+		\end{quotation}
 
@@
 
-	3. Demand for praise of weighted metrics [[not done]]
+	3. Comment on weighted metrics [[done]]
 
@@
 
-		\textbf{R:} This is slightly confusing.
-How do weighted metrics account for sampling biases, exactly?
-Especially if species abundances are not assessed independently from interactions, it seems like weighted metrics would be more succeptable to sampling bias than unweighted metrics (as the weights will also be affected by differences in detectability).
-[[Is this acutally useful?]]
+		\textbf{R:} We do not see how weighted metrics (which we infer mean metrics including interaction strength/frequencies based on the Reviewer's comment below) account for sampling biases.
+It seems to us that measures of interaction strength should be \emph{more} susceptible to sampling biases, not less, as abundant species are both more likely to have their interactions recorded and more likely to have these interactions recorded as strong/frequent.
+We have rephrased the introduction so that the original line 36 no longer appears.
+If the Reviewer strongly feels that weighted metrics somehow do sampling biases, we must ask for clarification as to why.
+We are willing to add a note as requested, but only if we are convinced that weighted metrics are indeed useful in this regard.
 
@@
 
-		\textbf{R:} Unfortunately, the use of binary networks is not as rare as the Reviewer thinks, particularly in food webs where it is often difficult to quantify interaction strengths or frequencies in the field.
-We absolutely agree that weighted networks are much more valuable when they are available but did not wish to exclude those without such data.
+		\textbf{R:} As stated above, we do not agree that weighted networks reduce sampling biases.
+Moreover, we disagree that it is rare to use binary networks as most food webs (for example) are still binary.
+It takes an even greater sampling effort to quantify interaction strengths than the presence and absence of links, so for species-rich systems in particular there simply are not many high-quality weighted networks published.
+If the Reviewer is only concerned about weighted interactions, we congratulate them on their tractable study system.
+Nevertheless, we do not wish to exclude the many researchers who are not so fortunate.
+		\smallskip
+		To model frequencies of interactions, ...
 			 [[Do we want to add a bit of non-binary stuff or just make it clearer that we are talking about feasibility and that probabilities of occurrance could be layered on later?]]
@@
 
-	6. Process uncertainty poorly defined, many quibbles about sampling [[done?]]
+	6. Process uncertainty poorly defined. [[done]]
 
@@
 
-		\textbf{R:} It seems our descriptions of interaction uncertainty and process uncertainty were both unclear, as the Reviewer has badly mixed them up.
-We have expanded the paragraph introducing the different levels of uncertainty to include plain-language questions addressed by each level of uncertainty; hopefully this will help to avoid confusion at the outset.
+		\textbf{R:} As our manuscript is not concerned with partitioning sources of uncertainty, we felt it was unproductive to get bogged down in a debate over the precise definitions of process vs.
+interaction uncertainty and which external influences might contribute to which sources (there is enough overlap that simple statements such as "bad weather increases process uncertainty" are, at best, incomplete).
+To remove this problem, we have rephrased the introduction and discussion to refer to the questions of whether two species \emph{can} interact under ideal conditions and whether they \emph{do} interact at a given site and time.
+We hope that this reframing, and the addition of clear statements that our framework is not intended to separate different sources of uncertainty, will remove the Reviewer's confusion.
+		\smallskip
+		Our mention of habitat as a factor affecting the probability of species interacting at a site was not intended to refer to species using different habitats, but rather the possibility that habitat type might affect interaction probabilities.
+For example, a more open patch of forest might have different interaction probabilities than a denser patch even if the same set of species use both patches.
+Of course the Reviewer is correct that habitat also affects which species are present at a site.
+We include co-occurrence in process uncertainty since co-occurrence does not tell us much about whether an interaction is feasible under ideal conditions (which would certainly include co-occurrence).
+This speaks to our point above that external factors (habitat, weather, etc.) can affect multiple levels of uncertainty at once.
+In fact, habitat also likely affects detection uncertainty since it is often harder to observe interactions in dense vegetation.
+So, in short, separating sources of uncertainty based on the external factors which contribute to them is not a particularly useful endeavour.
 
-			\begin{quotation}
-
-				As a conceptual guide to the factors affecting this process, we describe three nested levels of uncertainty: interaction uncertainty, process uncertainty, and detection uncertainty (Fig.~\ref{conceptual_fig}).
-These levels roughly address the questions: "Could species $i$ and $j$ interact?", "Do they interact at this site/time?" and "Do we observe the interaction?".
-
-			\end{quotation}
-
-		We have also added a paragraph to explain the interaction uncertainty explicitly \emph{does not} depend on co-occurrence; only on species traits.
-The Reviewer is not correct that habitat belongs in interaction uncertainty as species which do not currently share a habitat might still interact if one is introduced into the other's habitat (for example).
-We now state this explicitly.
-
-			\begin{quotation}
-
-				Note that interaction uncertainty does not depend upon whether species $i$ and $j$ actually co-occur.
-Ecologists are often interested in predicting which species are likely to interact following an introduction~\citep{} or range shift~\citep{}.
-In such cases, models based on trait matching can give some information about $\lambda$ while past co-occurance will, of course, not yield much insight.
-
-			\end{quotation}
-
-		Process uncertainty covers factors which prevent an interaction which \emph{can occur} from actually occurring at particular places/times.
-This includes factors which mean that two potentially interactive species do not co-occur (e.g., habitat requirements) as well as factors which reduce interaction probability between co-occurring species (weather, abundances, etc.).
-We have rephrased the first line of this section to make this explicit.
-
-			\begin{quotation}
-
-				Assuming that an interaction is feasible (i.e., $L=1$; species traits do not prohibit an interaction if they should co-occur), an interaction still not occur at a particular place or time.
-
-			\end{quotation}
-
-		Weather likely affects both process uncertainty and detection uncertainty.
-For pollination, pollinators are much less likely to interact in the rain (process uncertainty) and the lower visibility may mean that some interactions which do occur are missed (detection uncertainty).
-We have added a paragraph in the section describing detection uncertainty to make it clear that some external factors can affect multiple types of uncertainty.
-
-			\begin{quotation}
-
-				Note that some exteral factors can affect both process and detection uncertainty.
-For example, rare species are less likely to interact at a given site due to neutral processes (process uncertainty)~\citep{}.
-Interactions involving rare species are also less likely to be detected (detection uncertainty), unless more sampling effort is focused on rare than common species~\citep{}.
-Similarly, bad weather can make interactions such as pollination less likely by reducing pollinator activity~\citep{}.
-For those pollinators which do venture forth in poor conditions, bad weather might also reduce visibility and therefore increase detection uncertainty.
-
-			\end{quotation}
-
-		The Reviewer is correct that increasing sampling effort to include more interaction-promoting weather, sites, etc.
-will reduce process uncertainty.
-It would also be possible to gerrymander the spatial scale of sampling such that non-interacting species do not co-occur, but we would not advocate selecting a study site to avoid particular species.
-The appropriate spatial and temporal scale of sampling is an important question, but it is not the question we are addressing here.
-Instead, we have added a line to include the Reviewer's point that expanded sampling can help to address process uncertainty and left it at that.
-
-			\begin{quotation}
-
-			Expanding sampling to cover a broader spatial or temporal range (e.g., sampling in a variety of microhabitats or during a variety of weather conditions) will also help to reduce process uncertainty if resource constraints permit.
-
-		\end{quotation}
-
-	7. Point about temporal scales of interaction [[done?]]
+	7. Point about temporal scales of interaction [[done]]
 
@@
 The timescale of an interaction (and the evidence it leaves) does affect detection uncertainty, so we have added a note in that section.
-Long-term interactions may fail to be detected, however, and we now add an example to make it clear that detection uncertainty applies to even long-term interacitons such as gall-forming.
+Long-term interactions may fail to be detected, however, and we now add an example to make it clear that detection uncertainty applies to even long-term interactions such as gall-forming (indeed, our results suggest that uncertainty in gall-forming is quite high).
 
@@
 
-		\textbf{R:}
+		\textbf{R:} In the case study, we are modelling L (the probability that an interaction is feasible).
+We do not have quantitative data within sites in our dataset, so we cannot isolate the probability of detecting an interaction at a site from the probability that the interaction occurs.
+This is also the probability we were most interested in.
+We do note, however, that one could also model X|L using the same framework if there were independent counts of co-occurrences and interactions within a single site.
 
@@
 
-	16. Filtering seems arbitrary [[not done]]
+	16. Filtering seems arbitrary [[done]]
 
@@
 
-		\textbf{R:} The filtering threshold were arbitrary and intended solely to demonstrate how decreasing detection probability might shape the network actually collected in the field.
-We had believed that our example network was extremely well-sampled and therefore clustered filtering thesholds closer to p(detection)=1; as it appears that even this very intesively sampled network did not detect many interactions we have changed to a broader and more even set of filtering thresholds.
-We have also revised this section to make it clear what is being filtered [[to do]].\\
-		Unfortunately, we do cannot compare our filtered networks to many published networks as detection probabilities are not often estimated or reported.
-We do note, however, that Bascompte (2013) also reports quite low proportions of detected interactions ([[exact #]]).
-This suggests that the low detection probabilities we infer are not unique to our study.
-We have added a note comparing our results with Bascompte's [[to do]] and an explicit call for future researchers to report estimates of their detection probabilities [[to do]].
+		\textbf{R:} We have rephrased lines XX-XX to make it clearer that the filtered networks are intended to demonstrate how network structure changes as uncertainty increases (and we miss more interactions).
+As stated, we filtered networks created using the posterior distributions.
+There are therefore no sites or samples in question here.
+We are simply retaining a random 90\%-10\% of the interactions (or removing a random 10\%-90\%; these are equivalent) of the interactions in the "true" (posterior) network.
+We hope that this rephrasing is clearer.
+
+			\begin{quotation}
+				Measures of network structure which are based on empirical networks that are missing interactions may differ substantially from the values that would be obtained if detection certainty and variation in interactions over space and time could be removed.
+To demonstrate this, we created a suite of filtered networks for each posterior network.
+Taking a posterior network as the "true" network, we randomly sampled 90\%, 80\%, 70\%, 60\%, 50\%, 40\%, 30\%, 20\%, and 10\% of the interactions to create a new "filtered" network.
+			\end{quotation}
+
+		Note that our model is not concerned with partitioning different sources of variation; the filtering levels we present therefore represent uncertainty from all sources.
+As such, comparing them directly to "typical sampling effort" would be an apples-to-oranges comparison.
+We do note that~\citet{Weinstein2017a} found a detectability of 23.3\% for interactions despite high sampling effort,~\citet{Jordano2016} found that about half of unobserved interactions did not qualify as "forbidden links", and~\citet{Bartomeus2013} found that 59\% of interactions were detected.
+We therefore do not think that the range of filtering levels we applied were particularly unreasonable (although we note that none of the above studies refer to plant-galler networks).
+That said, the Reviewer is correct that the values we chose were absolutely arbitrary.
+To make this clear, we now filter in 10\% increments from 90\% to 10\% to illustrate a broader range of uncertainty.
 
@@
 
-		\textbf{R:}
+		\textbf{R:} [[This is the network metrics bit - need to expand in discussion.]]
 

### 2018-11-27 manuscript/CI_interactions.tex
getting close to the end, except R2

@@
 Even assuming constant co-occurrence within a given study system, changing abundances can affect interactions if species which would otherwise interact become too rare to detect each other~\citep{Tylianakis2010,Jordano2016}.
-Moreover, interactions vary over space~\citep{Kitching1987,Baiser2012,Emer2018}, time~\citep{Kitching1987,Olesen2011a,Lopez2017}, between individuals~\citep{Pires2011a,Fodrie2015,Novak2015}, throughout life cycles~\citep{Preston2014,Clegg2018}, and with environmental conditions~\citep{Poisot2015}.
+Moreover, interactions vary over space~\citep{Kitching1987,Baiser2012,Emer2018}, time~\citep{Kitching1987,Olesen2011a,Lopez2017}, between individuals~\citep{Pires2011a,Wells2013,Fodrie2015,Novak2015}, throughout life cycles~\citep{Preston2014,Clegg2018}, and with environmental conditions~\citep{Poisot2015}.
 
     Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007,Jordano2016}).
-An assessment of the accumulation of inter0actions with increasing sampling effort suggests that it is even more challenging to correctly document interactions than species~\citep{Guimera2009,Poisot2012,Bartomeus2013,Jordano2016,Giron2018,Graham2018}.
+An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to correctly document interactions than species~\citep{Guimera2009,Poisot2012,Bartomeus2013,Jordano2016,Giron2018,Graham2018}.
 As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Bartomeeus2013,Poisot2016}.
@@
     To date, models incorporating uncertainty have either been very general (e.g.,~\citet{Guimera2009,Gravel2013}) or very system-specific (e.g.,~\citet{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}).
-The general models may not include any system-specific information, while the system-specific models may not be applicable outside of their system of origin.
-Here we propose a simple Bayesian framework that can include broad general trends in network structure or highly specific expert knowledge, depending on the situation.
+Either style of model might be a poor fit for a particular study system.
+Moreover, some of the system-specific models described above cannot accommodate species observed only once~\citep{Bartomeus2013,Weinstein2017}.
+To provide another option for empiricists wishing to address the uncertainty in their networks, we propose a simple Bayesian framework that can easily be adapted to include whatever appropriate prior knowledge is available.
 This framework is designed to make the assumptions used when building networks more explicit and to quantify our uncertainty around each interaction in a network.
-Importantly, the simplicity of the framework means it should be easily applicable to any network type or study system.
 
@@
 We find that even the highest-quality empirical network we could find had substantial uncertainty about whether many pairs of species interact, demonstrating the need to include information about this uncertainty in published networks.
-We also show that this interaction-level uncertainty leads to uncertainty about estimates of network structure, with important implications for comparisons across networks.
+We also show that this interaction-level uncertainty leads to uncertainty about estimates of network structure, with important implications for comparisons across networks; especially those compiled with different sampling intensity~\citep{Weinstein2017}.
 
@@
           First, and most fundamentally, some interactions are feasible if a pair of species should co-occur while others are not~\citep{Poisot2015}.
-Assuming that the feasibility of interactions depends on the traits of species involved, we can define the probability of an interaction $L$ given some description of trait-matching $\mathbf{T}$ as $P(L|\mathbf{T}) = \lambda$~\citep{Gravel2013,others}.
+Assuming that the feasibility of interactions depends on the traits of species involved, we can define the probability of an interaction $L$ given some description of trait-matching $\mathbf{T}$ as $P(L|\mathbf{T}) = \lambda$~\citep{Bartomeus2013,Gravel2013,Weinstein2017}.
           In some cases the traits prohibiting an interaction are known, and there will be little uncertainty about $\lambda$.
@@
 Instead, an unobserved interaction may be a rare phenomenon with $\lambda>0$ and the associated zero in an interaction matrix might be false.
-This uncertainty is partly addressed by trait-matching models in which species with better-matched traits are more likely to interact~\citep{Bartomeus2016,Jordano2016}.
+This uncertainty is partly addressed by trait-matching models in which species with better-matched traits are more likely to interact~\citep{Bartomeus2016,Jordano2016,Weinstein2017}.
 As these models improve and include better information about the influence of traits on interactions, the uncertainty will be reduced~\citep{Jordano2016} and $\lambda$ should either tend to 0 or to 1.
@@
           Assuming that an interaction is feasible (i.e., $L=1$;), an interaction may still not occur at a particular place or time~\citep{Poisot2015,Graham2018}.
-This could be because the two species do not co-occur or, if they did occur, because constraints such as inclement weather or low abundance prevented the interaction~\citep{Jordano2016,Graham2018}, a more preferred interaction partner was available~\citep{Weinstein2017a}, or substantial individual variation in traits meant that local individuals could not interact even if the species in general can~\citep{Gravel2013,Poisot2015}.
+This could be because constraints such as inclement weather or low abundance prevented the interaction~\citep{Jordano2016,Graham2018}, a more preferred interaction partner was available~\citep{Weinstein2017a}, or substantial individual variation in traits meant that local individuals could not interact even if the species in general can~\citep{Gravel2013,Wells2013,Poisot2015}.
 For example, a rare galler may not parasitize a rare plant because they do not encounter each other.
+In metawebs describing an interaction network found at several study sites, an interaction may also fail to occur because two species do not co-occur at a particular site even if they co-occur and interact elsewhere~\citep{}.
 We can define the local realisation of an interaction, $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L=1)=\chi$.
@@
 Some types of interactions will have higher detection uncertainty than others (e.g., pollination or predation often take place very quickly while parasitism can last for months or years).
-Even long-term interactions, however, can be missed, especially if species are difficult to identify or if not all individuals of a species share the interaction.
+Even long-term interactions, however, can be missed, especially if species are difficult to identify or if not all individuals of a species share the interaction~\citep{Wells2013}.
 Parasites, for example, are often concentrated in only a few individuals~\citep{Lagrue2017}.
 If these infected individuals do not happen to be included in a sample, their interactions will be missed.
+Detection probabilities likely vary widely between species, and potentially individuals within species, due to different abundances and behaviours~\citep{Wells2013,Weinstein2017}.
 
@@
 For those pollinators which do venture forth in poor conditions, bad weather might also  increase detection uncertainty through reduced visibility or if pollinators make shorter trips.
-The "forbidden links" of~\citet{Jordano2016} can also occur due to process or interaction uncertainty in our framework.
 
-    \subsection*{Estimating detection and process uncertainty}
+    \subsection*{Estimating uncertainty}
 
@@
         If we are interested only in interactions which occur in the focal system under current environmental conditions, we might use a prior which includes probabilities of co-occurrence.
-That is, we could limit the set of potential interactions to pairs of species which currently co-occur, condition probabilities of interaction on probabilities of co-occurrence based on abundance or habitat use, etc.~\citep{Gravel2013,Weinstein2017} Note that such models lump together interaction uncertainty and process uncertainty and are only concerned with measuring detection uncertainty.
+That is, we could limit the set of potential interactions to pairs of species which currently co-occur, condition probabilities of interaction on probabilities of co-occurrence based on abundance or microhabitat use, etc.~\citep{Gravel2013,Weinstein2017} Note that such models lump together the questions of whether species can interact and whether they interact at a particular site and are only concerned with measuring detection uncertainty.
 Whether or not this is appropriate will depend upon the question of interest.
 
-        If traits governing interactions are known (e.g., body size in food webs~\citep{Gravel2013} or corolla depth in pollination networks~\citep{Weinstein2017a,Graham}), then trait-based models may be used as a prior.
-Such models address interaction uncertainty directly (i.e., they estimate whether a pair of species \emph{can} interact, regardless of whether they are likely to encounter each other).
-To address both interaction and process uncertainty, a researcher might combine trait-based and co-occurrence models into a single prior.
+        If traits governing interactions are known (e.g., body size in food webs~\citep{Gravel2013} or corolla depth in pollination networks~\citep{Weinstein2017a}), then trait-based models may be used as a prior.
+Such models estimate whether a pair of species \emph{can} interact, regardless of whether they are likely to encounter each other (although encounter probabilities and abundances can also be included, as in~\citet{Graham2018}).
+To address both multiple sources of uncertainty, a researcher might combine trait-based and co-occurrence models into a single prior.
 Such a model would reduce the uncertainty about unobserved interactions, but at the cost of adding more assumptions about the study system.
@@
     [[Make the point of this clearer]]
-      To illustrate the process of constructing a Bayesian network, we use the comprehensively-sampled system of willows (\emph{Salix}), herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}.
+      To illustrate the process of constructing a Bayesian network to quantify uncertainty about interactions, we use the comprehensively-sampled system of willows (\emph{Salix}), herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}.
 This dataset consists of a single community type sampled across Europe over 29 years and at 374 unique locations.
 The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (see \emph{Appendix S4} for details).
+      The high spatiotemporal resolution of this dataset make it ideal for illustrating the difficulties in completely sampling a network; even with such an unusually high sampling effort, we anticipate that there will be many pairs of species which were rarely or never observed together.
+To show the gaps in sampling, we compared the frequencies of observed co-occurrences and interactions.
+We then calculated an empirical prior and computed the posterior distribution of the probability of observing each as-yet-unobserved interaction in the future.
+[[Needs a final line.]]
 
-      The high spatiotemporal resolution and unusually high sampling effort of this dataset make it well suited for illustrating the difficulties in completely sampling a network.
-To show the gaps in sampling, we compared the frequencies of observed co-occurrences and interactions.
       We analysed both the \emph{Salix}-galler and galler-natural enemy components of the network but, for brevity, present only the latter here (see~\emph{Appendix S5} for \emph{Salix}-galler results).
@@
     \subsubsection*{Computing the prior and posterior distributions}
-
+      [[Remove the network I used for the prior from the rest of the analyses.]]
         To treat each interaction as a Bayesian probability, we will combine the observed data with a distribution based on prior information.
-A strict Bayesian framework requires a prior distribution that does not rely on any information from the study at hand.
-If such data are not available, one might instead use the first sub-network collected as ``training data" to guide future sampling.
-To simulate this situation, we created priors using a single sub-network from the middle of the geographical distribution of the~\citet{Kopelke2017} dataset.
+While a strict Bayesian framework requires a prior distribution that does not rely on any information from the study at hand, such data are not always available.
+In that case, researchers must choose between using a less-informative prior (e.g., one based on distributions of links across a large set of networks) or an empirical prior based on some "training data" from the study.
+Here, we opted for the latter and created priors using a single sub-network from the middle of the geographical distribution of the~\citet{Kopelke2017} dataset.
 To demonstrate how the use of data from a different system can affect the prior distribution and conclusions based on it, we repeated our analyses using priors derived from a much smaller \emph{Salix}-galler-natural enemy system based around genotypes of a single \emph{Salix} species~\citep[Data available from the Dryad Digital Repository: https://doi.org/10.5061/dryad.g7805]{Barbour2016}\nocite{Barbour2016Dryad}.
@@
 
+      [[Need to make it clear why we're doing this.]]
+
       Researchers usually use interaction matrices as a tool to calculate measures of network structure.
@@
 Any uncertainty in the values of $\lambda$ could bias both the mean and variance of network metrics, giving misleading results (simulated in \emph{Appendix S1}).
-One way to avoid this situation is to calculate the properties of a suite of simulated networks.
+One way to avoid this situation is to calculate the properties of a suite of simulated networks~\citep{Vazquez2005,Guimera209}.
 
@@
 After obtaining these posterior networks, we calculated the connectance of each web, as well as the mean number of links per galler and per natural enemy, and the nestedness (NODF) of the network.
-To demonstrate how these network metrics will be affected by detection uncertainty, we then created a suite of filtered networks for each posterior network.
-Networks were filtered by randomly sampling 99\%, 95\%, 90\%, 80\%, 70\%, 60\%, and 50\% of the interactions included in each posterior network.
-This gradient is akin to a gradient of sampling effort.
-For each level of detection accuracy, we created 100 randomly-sampled networks per posterior-probability network (giving 100 posterior networks and 1000 detection-filtered networks).
-We calculated the same network properties as described above for all posterior and detection-filtered networks.
+
+      Measures of network structure which are based on empirical networks that are missing interactions may differ substantially from the values that would be obtained if detection certainty and variation in interactions over space and time could be removed.
+To demonstrate this, we created a suite of filtered networks for each posterior network.
+Taking a posterior network as the "true" network, we randomly sampled 90\%, 80\%, 70\%, 60\%, 50\%, 40\%, 30\%, 20\%, and 10\% of the interactions to create a new "filtered" network.
+This gradient is akin to a gradient of uncertainty in the network (e.g., due to varying sampling effort or intraspecific trait variability).
+For each level of uncertainty, we created 100 randomly-sampled networks per posterior-probability network (giving 100 posterior networks and 1000 filtered networks).
+We calculated the same network properties as described above for all posterior and filtered networks.
 
@@
 This suggests that limited sampling is a major source of uncertainty in empirical networks, in agreement with~\citet{Jordano2016,Weinstein2017a,Weinstein2017}.
-This dataset also illustrates the problem of process uncertainty - pairs of species which were observed interacting did not interact in all of the samples in which they co-occurred.
+This dataset also illustrates the problem of pairs of species which were observed interacting did not interact in all of the samples in which they co-occurred.
 Increasing sampling is therefore likely to add more zeros than ones to an interaction network.
@@
 
+  [[rephrase to make these more clearly about OUR results]]
   Using prior knowledge to build a Bayesian distribution for each interaction probability allows us to set appropriate bounds on interaction probabilities for species which were rarely or never observed co-occurring.
@@
 The structure of the well-sampled network used in our case study is most similar to the structure of simulated networks including only 50\% of the interactions suggested by the posterior distribution of interaction probabilities.
-If our descriptions of empirical systems are missing up to half of the feasible interactions, then it is vital to acknowledge this inherent uncertainty before comparing structures across systems or relating structure to stability.
+If our descriptions of empirical systems are missing up to half of the feasible interactions, then it is vital to acknowledge this inherent uncertainty before comparing structures across systems or relating structure to stability~\citep{other studies pointing out poor detectability}.[[Add citations?]]
+  ~\citep{Jordano2016,Weinstein2017a}[[for poor detectanility - 50\% to 23\%]]
+  ~\citep{Bartomeus2013}[[had 59\% of interactions detected]]
 
@@
     \caption{Mean connectance, links per galler, nestedness (NODF), and links per natural enemy for networks assembled using posterior distributions based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017} occupied a narrow range.
-To obtain distributions of network properties, we created 100 ``posterior-sampling" networks and then, for each of these, created 100 ``detection-filter" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network.
+To obtain distributions of network properties, we created 100 ``posterior-sampling" networks and then, for each of these, created 100 ``filtered" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network.
 This simulates imperfect detection of interactions in the field.
-Each point represents the mean (+/- SD) network property (e.g., connectance) obtained from a set of 100 detection-filter networks.
-The detection-filter networks cover a broader range of network properties than the posterior-sampling networks but the value of each property decreases as the strength of the detection filter increases.
+Each point represents the mean (+/- SD) network property (e.g., connectance) obtained from a set of 100 filtered networks.
+The filtered networks cover a broader range of network properties than the posterior-sampling networks but the value of each property decreases as the strength of the detection filter increases.
 Values in the original web are indicated by dashed lines.}

### 2018-11-28 manuscript/reply_to_reviewers.tex
reply

@@
 
-	10. Explain Bayesian approach more simply [[done?]]
+	10. Explain Bayesian approach more simply [[done]]
 
@@
 
-		\textbf{R:} This comment conflicts with Reviewer 1's request that we remove much of our early description of the Bayesian framework on the grounds that it is easy to Google.
-As one way to address both comments, we have revised the manuscript to more clearly position our analysis of the willow-galler network as a worked example.
-We hope that the Reviewer will find it easier to understand our framework by following along with an example than would be the case if we expanded our abstract discussion.
+		\textbf{R:} We have expanded our description of different types of priors and when researchers might prefer one over another.
+Following a comment from Reviewer 1 we have removed much of the mathematical background for the Bayesian approach, but this material is still present in the supplemental material.
+We hope that this simplifies the approach adequately.
 
@@
 
-	15. Line 291: does assuming probability of 1 for observed interactions introduce bias? [[not done]]
+	15. Line 291: does assuming probability of 1 for observed interactions introduce bias? [[done]]
 
@@
 
-		\textbf{R:}
+		\textbf{R:} As we are concerned with the metaweb (the set of feasible interactions) rather than the interactions which occurr at a given site on a given day, we do not think that assuming a probability of 1 for observed interactions introduces bias in our study.
+We have added a justification of setting the probability of observed interactions to 1 in \emph{Appendix S2}.
+Note that each posterior web is a prediction of the true metaweb and not a local realization of some interactions drawn from the feasible set.
+These local webs are more akin to our "filtered webs" in which observed interactions are not guaranteed to appear.
+We have also added a line (lines XX-XX) to make this clear.
+		\medskip
+		This is an interesting point, however, as systems with a large risk of false positives (e.g., pollination networks which assume all flower visitors provide pollination service) would be biased by assuming all observed interactions are truly feasible.
+Assuming that all interactions which are known to be feasible actually occur at each site would also introduce bias - I suspect that this is what the Reviewer may be thinking of.
+As described above, our study cannot isolate $\chi$ (the probability that a feasible interaction occurs at a particular site), so this is not a relevant question for the present work.
+Future studies with much, much more detailed data may be able to shed light on this.
+
+		\begin{quotation}
+			we created a suite of 100 webs by randomly sampling from each posterior distribution. Each of these webs is a prediction of the structure of the metaweb.
+		\end{quotation}
 

### 2018-11-28 manuscript/CI_interactions.tex
reply

@@
 To show the gaps in sampling, we compared the frequencies of observed co-occurrences and interactions.
-We then calculated an empirical prior and computed the posterior distribution of the probability of observing each as-yet-unobserved interaction in the future.
-[[Needs a final line.]]
-
+We then calculated an empirical prior and computed the posterior distribution of the probability of an as-yet-unobserved interaction being feasible ($\lambda$).
       We analysed both the \emph{Salix}-galler and galler-natural enemy components of the network but, for brevity, present only the latter here (see~\emph{Appendix S5} for \emph{Salix}-galler results).
@@
       Using the prior distributions and procedures described above, we calculated posterior probability distributions for species pairs that were not observed interacting.
-Using these posterior distributions and assuming probabilities of 1 for pairs of species that were observed interacting, we created a suite of 100 webs by randomly sampling from each posterior distribution.
+Using these posterior distributions and assuming probabilities of 1 for pairs of species that were observed interacting (see \emph{Appendix S2} for a justification), we created a suite of 100 webs by randomly sampling from each posterior distribution.
 After obtaining these posterior networks, we calculated the connectance of each web, as well as the mean number of links per galler and per natural enemy, and the nestedness (NODF) of the network.

### 2018-11-28 manuscript/supplemental.tex
more revisions
reply

@@
 The posterior distribution of $\lambda$ therefore follows the beta distribution with new parameters $\alpha'= \alpha+k$ and $\beta'=\beta+n-k$.
+
+    For interactions which were observed in at least one site ($k$\textgreater$0$), we can set the poseterior probability to 1 as long as the risk of a false positive is low.
+That is, when constructing a metaweb we can assume that an interaction observed at least once is truly feasible.
+The case study presented in the main text refers to a plant-galler network compiled by rearing galling insects obtained from galls; in each case, the plant-galler interaction definitely occurred and we are confident in the identification of both species involved (see \emph{Appendix S4} for details).
+Where the risk of false positives is higher (e.g., plant-pollinator networks where an observed flower visitor may not actually provide a pollination service), it may not be appropriate to assume $\lambda=$ wherever $k$\textgreater$0$.
+In such cases, we can model the posterior probabilities of observed interactions just as we do those that were not observed.
+
+  \subsection*{Properties of the beta distribution}
+
+    %   It is common to perform analyses that require calculating higher-order network properties in interaction networks.
+The fact that the posterior distribution of $\lambda$ follows a beta distribution makes it straightforward to compute moments and other properties needed for these analyses.
+
+    %   The \textbf{average} of $\lambda$ is: 
+    %       \begin{equation}
+    %         \bar{\lambda} = \frac{\alpha+k}{\alpha+\beta+n} ,
+    %         \label{mean}
+    %       \end{equation}
+
+    %     and its \textbf{variance} is:  
+    %       \begin{equation}
+    %         Var(\lambda|k) = \frac{(\alpha + k)(\beta + n - k)}{(\alpha + \beta + n)^{2}(\alpha + \beta + n +1)}
+    %         \label{variance}
+    %       \end{equation}
+
+    %     The \textbf{mode} of the distribution is:
+    %       \begin{equation}
+    %         \hat{\lambda} = \frac{\alpha + k - 1}{\alpha + \beta + n - 2} .
+    %         \label{mode}
+    %       \end{equation}
 

### 2018-11-28 manuscript/reply_to_reviewers.tex
most of reply done, now to look at structure

@@
 
-Ask for help: how would we expand this to interaction frequencies? Still with the Bernoulli?
+Ask for help: how would we expand this to interaction frequencies? Still with the Bernoulli? Worthwhile to add a demo of Jensen's inequality?
 % -----------------------------------------------------------------------------
@@
 
-	5. Novelty of the study not clear in current framing [[not done? Done? Clearer?]]
+	5. Novelty of the study not clear in current framing [[done]]
 
@@
 
-	5. The one valuable section is poorly-integrated with the rest of the paper. [[not done]]
+	5. Description of causes of uncertainty poorly integrated with the case study [[done]]
 
@@
 For instance in the example of the gall-formers, there was not formal discussion about the different sources of uncertainty.
-[[So we need to state more clearly that we cannot distinguish these after the fact.]]
 		\end{refquote}
 
-		\textbf{R:}
+		\textbf{R:} As we state in the section \textbf{Estimating uncertainty}, we usually cannot distinguish different sources of uncertainty in empirical data.
+Those studies which attempt to do so (e.g.,~\citet{Graham2018}) remove process uncertainty by assuming constant interaction probabilities during a short, intense sampling period and also assume that we know the true set of feasible interactions.
+This may be the case for Graham and Weinstein's relatively small and well-studied system but is not likely to be true for systems containing hundreds of species, systems containing recently-arrived species, systems just beginning to be studied, etc.
+		\smallskip
+		To make this more clear, we have rephrased this section and added a line (lines XX-XX) stating that we usually cannot determine the cause of all the zeros in an interaction matrix (we can identify obviously unfeasible interactions, but likely cannot say whether a zero for a rare species is because we did not observe enough individuals, there were not enough individuals to perform a particular interaction, or because the interaction is acutally unfeasible).
+We hope that this revision makes it clearer that the description of different sources of uncertainty is a conceptual guide only.
+
+		\begin{quotation}
+			An observed link definitely occurred, but there are multiple reasons why a given link may not be observed \emph{whether or not the interaction truly occurred}.
+Moreover, given an unobserved interaction in an empirical dataset, we often cannot determine why the interaction did not occur \emph{post hoc}.
+The detection of any interaction is a stochastic process subject to many levels of uncertainty.
+As a conceptual guide to the factors affecting this process, we describe three nested levels of uncertainty that roughly address the questions: "Could species $i$ and $j$ interact?", "Do they interact?" and "Do we observe the interaction?" (Fig.~\ref{conceptual_fig}).
+		\end{quotation}
 
@@
 
-	8. Confusion about goal of modelling [[not done]]
+	8. Confusion about goal of modelling [[done]]
 
@@
 We do note, however, that one could also model X|L using the same framework if there were independent counts of co-occurrences and interactions within a single site.
+We now state throughout the manuscript that we are interested in compiling the metaweb, the set of interaction which can feasibly occur.
+In particular, this is now specified in the introduction.
+We hope that our goal is now crystal clear.
 
-	9. ?? [[not done]]
+		\begin{quotation}
+			To supplement repeated sampling efforts and reduce uncertainty around unobserved interactions, we suggest researchers use prior knowledge of the same or similar systems.
+Here, we outline a Bayesian approach to combining repeated sampling and prior knowledge in order to assemble a metaweb.
+We then demonstrate this approach using an intensively and repeatedly sampled empirical dataset.
+Finally, we show how a probabilistic understanding of a metaweb allows us to establish confidence intervals around measures of network structure.
+			\end{quotation}
+
+	9. Misunderstanding of how biased sampling does not solve problems of uncertainty [[done]]
 
@@
 
-		\textbf{R:}
+		\textbf{R:} We do not believe that biased sampling is a completely different issue as the tendency for some interactions to be sampled more easily than others clearly contributes to varying levels of detection uncertainty.
+Increasing sampling effort will not do much good if we repeatedly sample the same common interactions and very rarely identify any new interactions.
+We now address questions about whether or not sampling more will remove uncertainty in a dedicated box.
+We still mention the fact that increased sampling will not reduce uncertainty evenly across interactions as this is an important point to consider when designing sampling protocols and when analysing empirical data.
+We also point out that combining sampling types is a partial solution to this problem; if different sampling methods have different biases, they may partially cancel each other out.
+We believe that this addresses the question as much as possible given our focus on analysing collected data rather than collecting new data.
 
@@
 
-	11. Integrate L155ff with previous section [[not done]]
+	11. Integrate L155ff with previous section [[done]]
 
@@
 
-		\textbf{R:}
+		\textbf{R:} We have removed much of the preferatory text explaining which quantity we are most interested in ($\lambda$) and now more explicitly state our goals at the end of the introduction.
+We hope that the transition to the methods is now less work for a reader.
 
-	12. Ideas presented in L209, L262, L310 are important but explained too briefly [[not done]]
+	12. Ideas presented in L209, L262, L310 are important but explained too briefly [[done]]
 
@@
 
-		\textbf{R:}
+		\textbf{R:} We are not quite sure what the Reviewer is asking here.
+$\alpha$ and $\beta$ truly are quite simple (as simple as the mean and standard deviation of a normal distribution) so there is not much more to say about them in themselves.
+We have expanded our discussion of different types of priors and how they may be obtained, and we hope that this clarifies matters for the Reviewer.
+We also note that a simple worked example, with accompanying R code, is provided in \emph{Appendix S3} so that readers can see exactly how to obtain $\alpha$ and $\beta$.
+In case the point of confusion is the idea that $\alpha$ and $\beta$ can be specified or derived depending on the type of prior desired, we have added a line (lines XX-XX) spelling this out.
 
-	13. Reframe line 241 in terms of solutions rather than difficulties [[not done]]
+		\begin{quotation}
+			Parameters $\alpha$ and $\beta$ determine the shape of the prior distribution of $\lambda$, which follows a beta distribution.
+These are called hyper parameters and may be chosen to obtain an intentionally uninformative prior or derived using prior information to create an informed or empirical prior.
+			\end{quotation}
+
+	13. Reframe line 241 in terms of solutions rather than difficulties [[done]]
 
@@
 
-		\textbf{R:}
+		\textbf{R:} We appreciate the Reviewer's desire for optimism, but we also selected a high-quality dataset specifically in order to demonstrate that empirically sampling all of the feasible interactions in a system is very unlikely.
+A lower-quality dataset would work just as well with our framework but would not highlight these difficulties so well.
+We have therefore kept this line as-is but have added another line (XX-XX) to show how the Bayesian framework provides a partial solution to the problems inherent in even high-quality empirical data.
 
-	14. Line 283 seems to be a very important point and should be explained more clearly [[not done]]
+		\begin{quotation}
+		 The high spatiotemporal resolution of this dataset make it ideal for illustrating the difficulties in completely sampling a network; even with such an unusually high sampling effort, we anticipate that there will be many pairs of species which were rarely or never observed together.
+Using the Bayesian framework above, we can identify which potential interactions are more and less uncertain, allowing us to better predict the true structure of the metaweb.
+		 \end{quotation}
 
-		\textbf{R:}
+	14. Line 283 seems to be a very important point and should be explained more clearly [[done]]
+
+		\textbf{R:} Due to space constraints, we cannot provide an extensive description of Jensen's inequality here.
+As it is quite easy to look up the inequality by name, we are confident that interested readers can find a description to whatever level of detail suits their interest.
+		[[We could potentially add a demo in a new Appendix. Is this worthwhile?]]
 

### 2018-11-28 manuscript/CI_interactions.tex
most of reply done, now to look at structure

@@
 An observed link definitely occurred, but there are multiple reasons why a given link may not be observed \emph{whether or not the interaction truly occurred}.
-In terms of the ones and zeros in a binary interaction matrix, we know that the ones are true but we cannot be sure that the zeros reflect interactions which actually do not occur.
-The detection of any interaction is a stochastic process.
+Moreover, given an unobserved interaction in an empirical dataset, we often cannot determine why the interaction did not occur \emph{post hoc}.
+The detection of any interaction is a stochastic process subject to many levels of uncertainty.
 As a conceptual guide to the factors affecting this process, we describe three nested levels of uncertainty that roughly address the questions: "Could species $i$ and $j$ interact?", "Do they interact?" and "Do we observe the interaction?" (Fig.~\ref{conceptual_fig}).
@@
 
+        [[move to box
         The obvious rule of thumb to reduce uncertainty is ``sample more".
@@
 This can bias the set of recorded interactions towards those that are easier to observe~\citep{Carstensen2014,Jordano2016}.
+[[Suggest combining approaches for better results - Jordano2016?]] ]]
 
@@
         To supplement repeated sampling efforts and reduce uncertainty around unobserved interactions, we suggest researchers use prior knowledge of the same or similar systems.
-Here, we outline a Bayesian approach to combining repeated sampling and prior knowledge in probabilistic networks.
-We then demonstrate how to construct such a probabilistic network using an intensively and repeatedly sampled empirical dataset.
-Finally, we show how a probabilistic understanding of a network allows us to establish confidence intervals around measures of network structure.
+Here, we outline a Bayesian approach to combining repeated sampling and prior knowledge in order to assemble a metaweb.
+We then demonstrate this approach using an intensively and repeatedly sampled empirical dataset.
+Finally, we show how a probabilistic understanding of a metaweb allows us to establish confidence intervals around measures of network structure.
 
@@
       Parameters $\alpha$ and $\beta$ determine the shape of the prior distribution of $\lambda$, which follows a beta distribution.
-These are called hyper parameters.
+These are called hyper parameters and may be chosen to obtain an intentionally uninformative prior or derived using prior information to create an informed or empirical prior.
 The prior may be chosen to be uninformative, if no external information is available, or may draw on information such as distributions of connectance across webs, degree distributions, or trait-matching functions (see \emph{Appendix S3} for details and a simple quantitative example).
@@
 We therefore urge caution when using a model developed for one system as the prior for another.
+        See \emph{Appendix S3} for a simple quantitative example using degree distributions to obtain $\alpha$ and $\beta$.
 
@@
       The high spatiotemporal resolution of this dataset make it ideal for illustrating the difficulties in completely sampling a network; even with such an unusually high sampling effort, we anticipate that there will be many pairs of species which were rarely or never observed together.
+Using the Bayesian framework above, we can identify which potential interactions are more and less uncertain, allowing us to better predict the true structure of the metaweb.
 To show the gaps in sampling, we compared the frequencies of observed co-occurrences and interactions.
@@
 Using these posterior distributions and assuming probabilities of 1 for pairs of species that were observed interacting (see \emph{Appendix S2} for a justification), we created a suite of 100 webs by randomly sampling from each posterior distribution.
+Each of these webs is a prediction of the structure of the metaweb.
 After obtaining these posterior networks, we calculated the connectance of each web, as well as the mean number of links per galler and per natural enemy, and the nestedness (NODF) of the network.

### 2018-11-28 manuscript/CI_interactions.tex
reply

@@
 
+      The choice of prior distribution will reflect the goal of a study, the amount of prior knowledge available, and the strength of researchers' belief in that prior knowledge.
+Note that there is no 'correct' prior as long as we do not know the true distribution of interaction probabilities~\citep{Spiegelhalter2000}.
+The goal is to select a reasonable prior that reflects our assumptions about the true distribution, and then adjust this prior with observed data as it becomes available.
+When in doubt, it is also possible to model interaction probabilities using a variety of priors and then compare results~\citep{Spiegelhalter2000}.
+
       Parameters $\alpha$ and $\beta$ determine the shape of the prior distribution of $\lambda$, which follows a beta distribution.
-These are called hyper parameters and may be chosen to obtain an intentionally uninformative prior or derived using prior information to create an informed or empirical prior.
+These are called hyperparameters and may be chosen to obtain an intentionally uninformative prior or derived using prior information to create an informed or empirical prior.
 The prior may be chosen to be uninformative, if no external information is available, or may draw on information such as distributions of connectance across webs, degree distributions, or trait-matching functions (see \emph{Appendix S3} for details and a simple quantitative example).
@@
 The sum of $\alpha$ and $\beta$ is roughly equivalent to the weight of the prior, so Jeffreys prior has equal weight to a single observation.
-An uninformative prior is most appropriate when considering a novel system or a system where the only prior knowledge available directly relates to the question we wish to analyse.
+An uninformative prior is most appropriate when considering a novel system where we have no strong prior knowledge about the distribution of interactiom probabilities, where it is very important to limit the number of subjective assumptions~\citep{Berger2006}, or where we wish to account for the possibility that $\alpha$ and $\beta$ may vary~\citep{Leyland2005}.
 
       \textbf{Informed priors}
+
+        AKA "reference Bayes"~\citep{Spiegelhalter2000}
+
+        We already give a few detailed cases in Appendix 3...
 
@@
 
-      \textbf{Empirical priors} [[using data from the data in question]][[contentious]][[should these be drawn from hyperpriors or fixed for each interaction]]
+      \textbf{Empirical priors}
+
+        As well as calculating uninformative priors or informed priors (by specifying $\alpha$ and $\beta$ or deriving them from data outside the study system), it is possible to estimate $\alpha$ and $\beta$ directly from the data being analysed.
+This is known as Empirical Bayes~\citep{Casella1985}.
+In empirical Bayes, we fit a beta distribution to interaction probabilities observed in the empirical data (or some portion thereof, where a pilot study has been performed) or calculated using some property of the empirical data (in the case study below, we use species' degree distributions).
+Empirical Bayes is used in medical testing~\citep{Copas1972,Spiegelhalter2000} and disease modelling~\citep{Leyland2005,Brooks2015}, and is easily applicable to ecological systems.
+It is most useful where researchers do not wish to use an uninformative prior but data from a sufficiently similar system are not available (as in our case study).
+
+        Despite its practicality, empirical Bayes has been criticized for being overly subjective~\citep{Berger2006} and because estimating hyperparameters from data serves as an approximation of some true hyperparameters which remain unknown~\citep{}.
+
+      [[using data from the data in question]][[contentious]][[should these be drawn from hyperpriors or fixed for each interaction]]
 
@@
 \section*{Discussion}
+
+  A benefit of Bayesian estimation is that it allows us to make our assumptions more explicit (e.g., assuming that funding source for a medical trial may affect the reported outcome~\citep{Spiegelhalter2000}).
 

### 2018-11-29 manuscript/CI_interactions.tex
reframing going well

--- 2018-11-28 manuscript/CI_interactions.tex
@@
     [[These two paragraphs try to frame our study more clearly. Any help to shorten them?]]
-    To date, models incorporating uncertainty have either been very general (e.g.,~\citet{Guimera2009,Gravel2013}) or very system-specific (e.g.,~\citet{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}).
-Either style of model might be a poor fit for a particular study system.
+    To date, models incorporating uncertainty have either been very general (e.g.,~\citet{Guimera2009,Gravel2013}) or very system-specific (e.g.,~\citet{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}); in either case one of these models may be a poor fit for a particular study system.
 Moreover, some of the system-specific models described above cannot accommodate species observed only once~\citep{Bartomeus2013,Weinstein2017}.
-To provide another option for empiricists wishing to address the uncertainty in their networks, we propose a simple Bayesian framework that can easily be adapted to include whatever appropriate prior knowledge is available.
-This framework is designed to make the assumptions used when building networks more explicit and to quantify our uncertainty around each interaction in a network.
+As rare species are likely to be observed less frequently~\citep{Bluthgen2010} and may be of particular interest (e.g., when modelling species loss), there is a need for a more widely-applicable framework that includes such rare species.
 
+    Here we introduce a simple Bayesian framework that can easily be adapted to different systems.
 First, we provide a brief description of the nested levels of uncertainty affecting ecological network construction.
-In the context of this uncertainty, which can be reduced but usually not eliminated by high-quality sampling (\citealp[see Box 1]{Bartomes2013}), we present our Bayesian framework for combining observed data with a prior expectation of network structure.
+In the context of this uncertainty, which can be reduced but not eliminated by high-quality sampling (\citealp[see Box 1]{Bartomes2013}), we present our Bayesian framework for combining observed data with a prior expectation of network structure.
 We conclude with a worked example applying this framework to an intensively-sampled willow-galler network.
@@
 Presences and absences are not, however, equally certain.
-An observed link definitely occurred, but there are multiple reasons why a given link may not be observed \emph{whether or not the interaction truly occurred}.
+An observed link definitely occurred (assuming we can correctly identify the species involved), but there are multiple reasons why a given link may not be observed \emph{whether or not the interaction truly occurred}.
 Moreover, given an unobserved interaction in an empirical dataset, we often cannot determine why the interaction did not occur \emph{post hoc}.
 The detection of any interaction is a stochastic process subject to many levels of uncertainty.
-As a conceptual guide to the factors affecting this process, we describe three nested levels of uncertainty that roughly address the questions: "Could species $i$ and $j$ interact?", "Do they interact?" and "Do we observe the interaction?" (Fig.~\ref{conceptual_fig}).
+As a conceptual guide to the factors affecting this process, we describe three nested levels of uncertainty that roughly address the questions: "Could species $i$ and $j$ interact?", "Did they interact?" and "Did we observe the interaction?" (Fig.~\ref{conceptual_fig}).
 
-        \subsubsection*{Could the species interact under ideal conditions?}
+        \subsubsection*{Could the species interact?}
 
@@
           In most cases, however, it is not known what traits might prohibit an interaction~\citep{Dormann2017}.
-Pollinators may visit plants outside of those predicted based on "pollination syndromes"~\citep{Weinstein2017a} and herbivores may consume animal prey when it becomes accessible~\citep{}.
-These examples show that we often cannot say that an interaction absolutely does not occur.
-Instead, an unobserved interaction may be a rare phenomenon with $\lambda>0$ and the associated zero in an interaction matrix might be false.
+Pollinators may visit plants outside of those predicted based on "pollination syndromes"~\citep{Weinstein2017a} and herbivores may consume animal prey when it becomes accessible~\citep{Furness1988,Pietz2000}.
+These examples illustrate the danger in assuming that seemingly unlikely interactions cannot occur.
+
+          An unobserved interaction may be a rare phenomenon with $\lambda>0$ and the associated zero in an interaction matrix might be false.
 This uncertainty is partly addressed by trait-matching models in which species with better-matched traits are more likely to interact~\citep{Bartomeus2016,Jordano2016,Weinstein2017}.
@@
 For example, a rare galler may not parasitize a rare plant because they do not encounter each other.
-In metawebs describing an interaction network found at several study sites, an interaction may also fail to occur because two species do not co-occur at a particular site even if they co-occur and interact elsewhere~\citep{}.
+In metawebs describing a community found at several sites, an interaction may also fail to occur because two species do not co-occur at a particular site even if they do co-occur and interact elsewhere~\citep{Graham2018}.
 We can define the local realisation of an interaction, $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L=1)=\chi$.
 It is unlikely that $\chi=1$  except in the case of obligate specialists who always interact whenever they co-occur and always co-occur.
-When $\chi<1$ we cannot be sure whether an unobserved interaction did not occur and when it occurred but was not observed.
+When $\chi<1$ we cannot be sure whether an unobserved interaction cannot occur or whether it simply did not occur at a particular site.
 
-          This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology  on the topic.
-Phenological matching~\citep{MillerRushing2010,Gezon2016}, species preferences~\citep{Pires2011,Novak2015,Coux2016}, and fear effects~\citep{Luttbeg2005,Wirsing2008} are just some of the factors contributing to variation in the frequency of interactions between a given pair of species.
-Some of these factors can be addressed in mesocosm studies of networks (e.g., environmental conditions can be held stable) or could be included in models along the line of trait-matching models (e.g., phenological matching).
-Expanding sampling to cover a broader spatial or temporal range (e.g., sampling in a variety of microhabitats or during a variety of weather conditions) will also help to reduce uncertainty if resource constraints permit.
-As long as researchers wish to sample empirical networks subject to changing conditions, however, it is not likely that they will be able to eliminate all uncertainty about whether or not pairs of species will interact during a given sampling period.
-
-          Some models attempt to eliminate the sources of variation above by sampling intensively over a short time, during which probabilities of interaction are assumed to be constant~\citep{Bartomeus2013,Weinstein2017,Weinstein2017a}.
-Any remaining variation in the interactions observed is therefore assumed to be due to detection uncertainty.
-This assumption may be accurate for some systems where the environment is relatively constant, there is little intraspecific variation in traits or preferences, etc.
-In most systems, and for any effort to compile a metaweb that will apply over broader spatial and temporal scales, probabilities of interaction are likely to vary during sampling.
+          Some of the uncertainty about $\chi$ could be addressed by drawing on the rich literature about interaction contingencies found in community ecology.
+Phenological matching~\citep{MillerRushing2010,Gezon2016}, species preferences~\citep{Pires2011,Novak2015,Coux2016}, and fear effects~\citep{Luttbeg2005,Wirsing2008} all affect the probability of an interaction occurring at a particular site and time, and could be included in models similar to trait-matching models.
+Alternatively, interaction probabilities could be tested in mesocosm studies with constant conditions.
+Some studies attempt to reduce uncertainty by sampling intensively over a short period of time and restricting the scale of interest to interactions occurring at the sampling site and time (conflating $\chi$ and $\lambda$)~\citep{Bartomeus2013,Weinstein2017,Weinstein2017a}.
+This approach may be suitable for some research questions, but is not appropriate if we wish to assemble the full set of interactions which occur in a community (beyond the specific site and time of sampling).
+In contrast, expanding sampling to cover a broader spatial or temporal range (e.g., sampling in a variety of microhabitats or during a variety of weather conditions) will help to reduce uncertainty about $\chi$ by including a broader range of parameters affecting interaction probability.
+It is unlikely, however, that resources will permit researchers to sample in the full range of sites and conditions covered by a community, and some uncertainty about $\chi$ will remain.
 
@@
 
-            Both of the above sources of uncertainty (i.e., whether species would be able to interact given their traits and whether they are able to interact at a particular place and time) are addressed in the concept of "forbidden links"~\citep{Jordano2016}.
+            Both whether species can interact and whether they do interact at a particular place and time have been discussed in the context of "forbidden links"~\citep{Jordano2016}.
 In this framework, all links which are prevented by spatio-temporal uncoupling~\citep{Jordano1987}, physiological constraints~\citep{Jordano1987,More2012}, etc.
@@
 
-        \subsubsection*{Detection uncertainty}
+        \subsubsection*{Did we observe all interactions that occurred?}
 
@@
 Detection failure could happen for many reasons (see~\citet{Wirta2014} for examples and partial solutions to them).
-Some sources of detection error can be minimised with appropriate sampling effort (e.g., combining plant-focused and animal-focused sampling when assembling pollination networks~\citet{Jordano2016}), but other sources are often difficult to reduce (e.g.
-the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification as in~\citealt{Wirta2014,Frost2016}).
-Some types of interactions will have higher detection uncertainty than others (e.g., pollination or predation often take place very quickly while parasitism can last for months or years).
-Even long-term interactions, however, can be missed, especially if species are difficult to identify or if not all individuals of a species share the interaction~\citep{Wells2013}.
+Some sources of detection error can be minimised with appropriate sampling effort (e.g., combining plant-focused and animal-focused sampling when assembling pollination networks~\citet{Jordano2016}), but other sources are often difficult to reduce.
+For example, cryptic species might require molecular analysis for appropriate taxonomic identification~\citep{Wirta2014,Frost2016} or it may not be possible to sample some species due to conservation concerns~\citep{Lagrue2015}.
+
+          Some types of interactions will have higher detection uncertainty than others.
+Pollination, for example, occurs briefly and does not leave long-lasting evidence, while parasitism can be a lifelong association between species.
+Even long-term interactions can be missed, however, especially if species are difficult to identify or if not all individuals of a species share the interaction~\citep{Wells2013,Cirtwill2016}.
 Parasites, for example, are often concentrated in only a few individuals~\citep{Lagrue2017}.
 If these infected individuals do not happen to be included in a sample, their interactions will be missed.
-Detection probabilities likely vary widely between species, and potentially individuals within species, due to different abundances and behaviours~\citep{Wells2013,Weinstein2017}.
+Detection probabilities also vary widely between species, and potentially individuals within species, due to different abundances and behaviours~\citep{Wells2013,Weinstein2017}.
+
+    \subsection*{Can't we just sample more?}
 
@@
 Note that some exteral factors can affect more than one level of uncertainty.
-For example, rare species are less likely to interact at a given site due to neutral processes~\citep{}.
-Interactions involving rare species are also less likely to be detected, unless more sampling effort is focused on rare than common species~\citep{Jordano2016}.
+For example, rare species are less likely to interact at a given site due to neutral processes~\citep{Jordano2016,Graham2018}.
+Interactions involving rare species are also less likely to be detected, unless more sampling effort is focused on rare than common species~\citep{Bartomeus2013,Jordano2016}.
 Thus, abundance affects both the probability of an interaction occurring at a particular site \emph{and} our ability to observe the interaction.
-Similarly, bad weather can make interactions such as pollination less likely by reducing pollinator activity~\citep{}.
-For those pollinators which do venture forth in poor conditions, bad weather might also  increase detection uncertainty through reduced visibility or if pollinators make shorter trips.
 
-    \subsection*{Estimating uncertainty}
-
-        An observed interaction indicates that an interaction was feasible, occurred during sampling, and was detectable ($L = 1$, $X = 1$, and $D = 1$).
-An unobserved interaction could be due to any of the three sources of uncertainty ($D$, $X$, and/or $L = 0$) and it is not usually possible to identify the source in empirical data.
-Only the case where $L = 0$ is an interaction that never occurs --the usual interpretation of a $0$ value in an interaction matrix.
-It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e.
-where the interaction occurred at the location but was not observed, and $X = 0 \cup L =1$, i.e., where the interaction is feasible but did not occur at the local site (Fig.~\ref{conceptual_fig}).
+        When considering a metaweb, we wish to separate the unobserved interactions where $L = 0$ (i.e., unfeasible interactions) from interactions which could occur but did not at a particular sampling site or which occurred but were not detected (Fig.~\ref{conceptual_fig}).
+Unfortunately, this is not possible for most interactions (except those where we know an interaction is truly not feasible).
 An empirical ecologist will instead measure the marginal probability $P(L) = k/n$, where $k$ is the number of observed interactions and $n$ the number of observed co-occurrences.
@@
 
-        [[move to box
         The obvious rule of thumb to reduce uncertainty is ``sample more".
-Increasing sample sizes will reduce uncertainty about the upper bound of the interaction probability and will also increase the probability of detecting unlikely or cryptic interactions (e.g., interactions where $L$=1 but process or detection uncertainty is high).
+Where resources permit, increasing sample sizes will reduce uncertainty about the upper bound of the interaction probability and will also increase the probability of detecting unlikely or cryptic interactions (e.g., interactions where $L$=1 but process or detection uncertainty is high).
 Despite these benefits, we note that there are limits to the utility of increased sampling.
-Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig.~\ref{histograms}C).
-Thus, the more we sample, the more zeros will appear in our interaction matrix.
+Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig.~\ref{histograms}C), thereby adding more zeros with high uncertainty (which would require more sampling to reduce, and so on).
 
@@
 This can bias the set of recorded interactions towards those that are easier to observe~\citep{Carstensen2014,Jordano2016}.
-[[Suggest combining approaches for better results - Jordano2016?]] ]]
+Combining multiple sampling types can reduce this type of bias~\citep{Wirta2014,Jordano2016}.
+Nevertheless, despite substantial improvements in recent decades, most available interaction networks are still undersampled and, moreover, are only subsets of larger communities~\citep{Bartomeus2013,Jordano2016}.
 
-        Most importantly, if two species are never observed co-occurring during several days of sampling then repeated sampling reveals nothing about their probability of interacting should they ever co-occur.
-Intensive sampling is, therefore, an important step towards reducing uncertainty in ecological networks but is unlikely to be enough in most cases.
-        Indeed, despite substantial improvements in recent decades, most available interaction networks are still undersampled and, moreover, are only subsets of larger communities~\citep{Jordano2016}.
-        To supplement repeated sampling efforts and reduce uncertainty around unobserved interactions, we suggest researchers use prior knowledge of the same or similar systems.
-Here, we outline a Bayesian approach to combining repeated sampling and prior knowledge in order to assemble a metaweb.
-We then demonstrate this approach using an intensively and repeatedly sampled empirical dataset.
-Finally, we show how a probabilistic understanding of a metaweb allows us to establish confidence intervals around measures of network structure.
+        In short, high-quality sampling is an essential component of ecological network construction and increasing sampling (length of time, number of sites, number of distinct methods, etc.) can reduce some of the uncertainty about unobserved interactions.
+We believe, however, that empirical researchers generally sample to the maximum extent possible given constraints of time, resources, and study sites.
+This practical constraint means that reducing one source of uncertainty is likely to increase another source (e.g., sampling intensively at a single site may reduce detection uncertainty but will increase uncertainty due to variation between sites).
+The number of observed co-occurrences needed to believe that an unobserved interaction cannot occur is very high (about 35; Fig.~\ref{upper_limits}), and most datasets will not include this level of sampling for all pairs of species~\citep{Bartomeus2013}.
+For pairs of species with fewer observations, we can reduce uncertainty by combining the observed data available with prior knowledge about the system.
+This is straightforward to do using a Bayesian approach, as detailed below.
 
@@
 
-    We can create a simple Bayesian approach to modelling the probability of observing an interaction ($\lambda$) by combining a maximum likelihood estimate (MLE) of $\lambda$ with a prior distribution (described in the next section) and a normalising function.
+    The basis of a Bayesian approach to modelling the probability that an interaction occurs ($\lambda$) is combining the maximum likelihood estimate (MLE) of $\lambda$ with a prior distribution (described in the next section) and a normalising function.
 The MLE of $\lambda$ can be modelled as a Bernoulli trial based on the number of observed interactions $k$ and observed co-occurrances $n$: $\lambda = \frac{k}{n}$.
@@
 
-    Combining this prior distribution with the MLE of $\lambda$ derived from observed data, we obtain a posterior distribution that also follows a beta distribution with new parameters $\alpha'= \alpha+k$ and $\beta'=\beta+n-k$ (see~\emph{Appendix S2} for details).
-The weight of the prior on the posterior distribution can be understood from these parameter definitions: the difference between the posterior and the prior will increase with $k$ and $n-k$.
+    The shape parameters, or hyperparameters, may be set to particular values or derived from some data (see below).
+Combining the prior distribution with the MLE of $\lambda$ derived from observed data, we obtain a posterior distribution that also follows a beta distribution with new parameters $\alpha'= \alpha+k$ and $\beta'=\beta+n-k$ (see~\emph{Appendix S2} for details).
+The influence of the prior on the posterior distribution can be understood from these parameter definitions: the difference between the posterior and the prior will increase with $k$ and $n-k$.
 In other words, the distribution of $\lambda$ for better-sampled pairs of species will rely less on the information used to build the prior distribution and depend more on the observed data and uncertainty about the probability of the pair interacting will decrease (Fig.~\ref{Salix_pdfs_cdfs}).
@@
 
-    \subsubsection*{Choosing a prior distribution}  [[expand]]
-      [[expand]]
+    \subsubsection*{Choosing a prior distribution}
 
-      Parameters $\alpha$ and $\beta$ determine the shape of the prior distribution of $\lambda$, which follows a beta distribution.
-These are called hyper parameters and may be chosen to obtain an intentionally uninformative prior or derived using prior information to create an informed or empirical prior.
-The prior may be chosen to be uninformative, if no external information is available, or may draw on information such as distributions of connectance across webs, degree distributions, or trait-matching functions (see \emph{Appendix S3} for details and a simple quantitative example).
+      The choice of prior distribution will reflect the goal of a study, the amount of prior knowledge available, and the strength of researchers' belief in that prior knowledge.
+Note that there is no 'correct' prior as long as we do not know the true distribution of interaction probabilities~\citep{Spiegelhalter2000}.
+The goal is to select a reasonable prior that reflects our assumptions about the true distribution, and then adjust this prior with observed data as it becomes available.
+When in doubt, it is also possible to model interaction probabilities using a variety of priors and then compare results~\citep{Spiegelhalter2000}.
+Some researchers may be reluctant to adopt a Bayesian approach because of its perceived subjectivity (i.e., the metaweb we obtain will depend upon the assumptions used when developing a prior).
+We argue that one of the advantages of the Bayesian approach is that it makes some of the subjectivity inherent in network construction explicit.
+Researchers compiling empirical networks face many decisions about where to set community boundaries~\citep{}, the set of species to include in the focal community~\citep{}, what type of sampling is most appropriate~\citep{Wirta2014}, etc.
+All of these choices will affect the compiled network and most do not have clear answers, making all empirical networks (and all theoretical networks, which likewise depend upon the assumptions used in building the network) to some extent subjective.
+In addition, researchers distinguishing "forbidden links" inherently rely on prior knowledge to identify these links~\citep{Jordano2016}.
+Stating that an interaction is "forbidden" is, in effect, applying a very strong prior to reduce/eliminate uncertainty about the non-observation of that interaction.
+Given this reality, we feel it is better to make the assumptions used to build a network as explicit as possible so that these assumptions can be questioned, compared between studies, and tested.
 
-      It is important to ensure that an informative prior accurately reflects the focal  system.
-For example, if the system is a large network containing many plant species and insects from different families, it is inappropriate to use a prior distribution drawn from a small network describing interactions between different genotypes of a single plant species and a set of closely-related insects.
+      \textbf{Uninformative priors}
+
+        If researchers wish to reflect uncertainty in their data without applying any particular assumptions/prior knowledge or account for the possibility that the distribution of probabilities of interaction may vary, they can select $\alpha$ and $\beta$ to produce an intentionally uninformative prior~\citep{Leyland2005,Berger2006}.
+This prior can then be given a low weight, such that any observed data will outweigh the prior distribution.
+For pairs of species with little or no observed data, an uninformative prior will leave large variance about $\lambda$ and reflect our lack of knowledge about the pair.
+Since we model $\lambda$ as a Bernoulli trial, the appropriate uninformative prior is Jeffreys prior: a beta distribution with $\alpha$=$\beta$=0.5.
+The sum of $\alpha$ and $\beta$ is roughly equivalent to the weight of the prior, so Jeffreys prior has equal weight to a single observation.
+
+      \textbf{Informative priors}
+
+        In most cases, we have at least some prior knowledge about a system which we can use to reduce uncertainty about interactions.
+One common example is the well-justified assumption that plants will not consume animals in a food web; excluding carnivorous plants it is not contentious to say that we have little to no uncertainty about unobserved links describing plants feeding on animals.
+Similarly, if we observe two species which are normally obligate mutualists co-occurring but not interacting, we would be very doubtful that a zero reflecting this interaction was true (i.e., high uncertainty about this zero).
+It is straightforward to extend the intuition behind these special cases to the full set of species in a network using trait-based models, as long as the traits likely to affect interaction probabilities are known (e.g.,~\citet{Riede2011,Gravel2013,Bartomeus2016,Weinstein2017}).
+Models for interaction probabilities could also include information on abundances, phenological matching, co-occurrence etc.
+as available~\citep{Jordano2016,Weinstein2017a,Graham2018}.
+This approach allows us to tailor the level of uncertainty surrounding each interaction based on the species involved but involves many assumptions about which parameters affect interaction probabilities and the strength and shapes of these relationships.
+There is, therefore, a risk of over-fitting with complicated trait-based models.
+Also note that researchers wishing to test whether a particular trait influences interaction probabilities should either exclude that trait from their prior or model the network using priors which include and exclude the trait of interest (as in~\citet{Weinstein2017,Weinstein2017a}).
+
+        Alternatively, it is possible to develop a prior based on the properties of a set of published networks (i.e., "reference Bayes"~\citet{Spiegelhalter2000}).
+While this type of prior does not allow for the prior distribution to vary between species pairs, it relies on fewer assumptions about the forces structuring interaction probabilities.
+Instead, we assume only that the focal network will have similar structural properties to those of published networks.
+For example, connectance ($C=L/S^2$, where $L$ is the number of interactions and $S$ is the number of species) is available for many networks.
+The distribution of these connectances can be used to predict the distribution of interaction probabilities in a new network.
+If we know the mean $\overline{C}$ and variance $\sigma_C^2$ of a distribution of connectances, then the hyperparameters are:
+
+        \begin{equation}
+        \alpha = \overline{C}(\frac{\overline{C}(1-\overline{C})}{\sigma_C^2}-1) ,
+        \end{equation}
+
+        \begin{equation}
+        \beta = (1-\overline{C})(\frac{\overline{C}(1-\overline{C})}{\sigma_C^2}-1) .
+        \end{equation}
+
+        Note that, in this case, the prior distribution will be the same for all interaction probabilities.
+It is also possible to use other interaction probabilities.
+For example, species' degrees (numbers of interaction partners) in a similar network or networks could be normalised (divided by the number of potential interaction partners) and interpreted as an interaction probabilities (i.e., "empirical Bayes"~\citep{Spiegelhalter2000}).
+The distribution of these interaction probabilities can be used to inform a prior distribution as show in \emph{Appendix S3}.
+When using network summary statistics or degree distributions, it is important to consider whether the available information reflects what we truly believe about the network.
+Given the likelihood that most published networks are undersampled~\citep{Jordano2016}, it may be wise to include only the highest-quality networks available in a prior.
+Likewise, only the degree distribution for a similar system is likely to be a reasonable prior for a focal system.
+For example, if the system is a large network containing many plant species and insects from different families it is inappropriate to use a prior distribution drawn from a small network describing interactions between different genotypes of a single plant species and a set of closely-related insects (see \emph{Appendix S6} for a demonstration).
 The similarity of traits across genotypes within a species means that an insect which interacts with one genotype is likely to interact with many others.
@@
 
-      The choice of prior will depend on the information available and the question of interest.
-In general, it is best to use a prior taken from a similar system as emphasised above.
-If such data are not available, a prior based on many networks with a similar level of resolution could be useful, as could a prior based on a preliminary round of sampling (analogous to ``training data").
-If there is no suitable informative prior, it is best to use an explicitly uninformative prior.
-While an uninformative prior will not greatly reduce variance about $\lambda$, it does clearly state our lack of prior knowledge and will not bias our conclusions.
-Similarly, if detailed information is available but refers to the question at hand, it is best to use a less informative prior so as not to force a particular result.
-For example, if researchers are interested in testing whether body-size ratios affect probabilities of interaction they should not use a prior which predicts interactions based on body sizes.
-
-      \textbf{Uninformative priors}
-
-        An uninformative prior is chosen so as not to bias the posterior distribution in any particular direction.
-That is, all of the information will come from the observed data.
-For pairs of species with little or no observed data, an uninformative prior will leave large variance about $\lambda$ and reflect our lack of knowledge about the pair.
-Since we model $\lambda$ as a Bernoulli trial, the appropriate uninformative prior is Jeffreys prios: a beta distribution with $\alpha$=$\beta$=0.5.
-The sum of $\alpha$ and $\beta$ is roughly equivalent to the weight of the prior, so Jeffreys prior has equal weight to a single observation.
-An uninformative prior is most appropriate when considering a novel system or a system where the only prior knowledge available directly relates to the question we wish to analyse.
-
-      \textbf{Informed priors}
-
-        In most cases, researchers will be able to draw upon prior knowledge for at least some interactions.
-One very simple example is the assumption that, in a food web, plants will not consume any prey.
-There is very little uncertainty around the lack of a observed predation of any plant upon any animal in the system, regardless of how often the plant and animal are observed together.
-
-        [[addressing different types of uncertainty]]
-        [[drawing upon system-specific or broader knowledge]]
-
-        If we are interested only in interactions which occur in the focal system under current environmental conditions, we might use a prior which includes probabilities of co-occurrence.
-That is, we could limit the set of potential interactions to pairs of species which currently co-occur, condition probabilities of interaction on probabilities of co-occurrence based on abundance or microhabitat use, etc.~\citep{Gravel2013,Weinstein2017} Note that such models lump together the questions of whether species can interact and whether they interact at a particular site and are only concerned with measuring detection uncertainty.
-Whether or not this is appropriate will depend upon the question of interest.
-
-        If traits governing interactions are known (e.g., body size in food webs~\citep{Gravel2013} or corolla depth in pollination networks~\citep{Weinstein2017a}), then trait-based models may be used as a prior.
-Such models estimate whether a pair of species \emph{can} interact, regardless of whether they are likely to encounter each other (although encounter probabilities and abundances can also be included, as in~\citet{Graham2018}).
-To address both multiple sources of uncertainty, a researcher might combine trait-based and co-occurrence models into a single prior.
-Such a model would reduce the uncertainty about unobserved interactions, but at the cost of adding more assumptions about the study system.
-This type of very detailed prior is therefore most appropriate in very well-understood systems where a great deal of expert knowledge can be applied, or in systems which are believed to follow general rules of, for example, allometric scaling~\citep{Gravel2013}.
-Where there is less system-specific prior knowledge, we can use prior models based on general trends in allometric scaling~\citep{Riede2011,Gravel2013}.
-
-        An informed prior could be based on one or a few traits, as those described above, or it could incorporate a great deal of information about co-occurrence and encounter probabilities, forbidden links, etc.~\citep{Jordano2016}.
-Importantly, the complexity of a prior model depends both on the information available and on the question of interest.
-If researchers wish to test for an effect of body mass ratios on interaction probabilities, for example, they should not include body mass in their prior.
-Including a trait in a prior means assuming that trait has an effect on which interactions we detect and it is therefore inappropriate to test for such an effect in the same study.
-
-        The relevant traits and degree of trait-matching between interaction partners is likely to vary between systems~\citep{Gravel2013,Weinstein2017a}.
-We therefore urge caution when using a model developed for one system as the prior for another.
-        See \emph{Appendix S3} for a simple quantitative example using degree distributions to obtain $\alpha$ and $\beta$.
-
-      \textbf{Empirical priors} [[using data from the data in question]][[contentious]][[should these be drawn from hyperpriors or fixed for each interaction]]
+        If a similar dataset is not available, it is also possible to use data from the study at hand to develop a prior (i.e., "approximate Bayes"~\citet{Gelmanblog})~\citep{Casella1985,Spiegelhalter2000}.
+This approach is used in medical testing~\citep{Copas1972,Spiegelhalter2000} and disease modelling~\citep{Leyland2005,Brooks2015} using information from pilot studies and can easily be applied to ecological systems.
+Returning to the example of degree distributions, this approach allows us to use information from abundant and easily-sampled species to predict interaction probabilities for species which were observed only rarely.
+Despite its practicality, empirical Bayes has been criticized for being overly subjective~\citep{Berger2006} and because estimating hyperparameters from data serves as an approximation of some true hyperparameters which remain unknown~\citep{Gelmanblog}.
+We therefore encourage researchers to carefully consider whether external data or an appropriate trait model is available before opting for a prior based on some of their own data.
+Nevertheless, there are likely to be many situations where approximate Bayes provides the best way to describe the uncertainty in the dataset.
+We illustrate this approach in the following empirical example.
 
@@
 
+  A benefit of Bayesian estimation is that it allows us to make our assumptions more explicit (e.g., assuming that funding source for a medical trial may affect the reported outcome~\citep{Spiegelhalter2000}).
+
   Real interaction networks vary over several dimensions~\citep{Kitching1987,Olesen2011a,Pires2011a,Baiser2012,Fodrie2015,Novak2015}, leading to pervasive under-estimation of interactions in published networks~\citep{Jordano2016}.
@@
 
-\captionsetup{singlelinecheck=false, font={stretch=2}}
-
-\section*{Boxes}
-
-\begin{figure}[h!]
-\caption{\textbf{Why isn't sampling the solution?}
-While sufficient sampling is a vital part of any scientific study, we do not think that an exhortation to "sample more" is the appropriate solution to analysing uncertain interactions.
-There are four main reasons for this: \\
-\textbf{1)} First, and most importantly, we assume that the majority of researchers are aware that insufficient sampling leads to shoddy data and are sampling as intensively and extensively as their time and budget allow.
-The development and decreasing price of novel methods such as DNA barcoding and remote sensing can help field researchers to do more with less, but it remains to be seen whether these improvements will be enough to fully-describe large study systems.
-In the absence of new break-through sampling techniques, logistical limitations mean that allocating sampling effort is a zero-sum game.
-That is, allocating more sampling to reduce one source of uncertainty will remove sampling effort that could reduce another source of uncertainty.\\
-\textbf{2)} High sampling effort with a constant methodology will reliably describe some interactions but not others.
-For example, many insect species are difficult to distinguish except by molecular methods.
-Non-descructive sampling (e.g., by observing insect flower-visitors) will not allow researchers to separate these cryptic species~\citep{}.
-Increasing the number of person-hours spent in the field will not change this situation, although of course it will allow more accurate estimations of interaction probabilities for species which \emph{can} be distinguished.
-Adding another type of sampling (e.g., molecular methods) would reduce the set of interactions which cannot be detected/distinguished, but it will also increase the time, resources, and expertise required to complete the study.
-\\
-\textbf{3)} High sampling effort in a narrow spatiotemporal window will reliably describe some interactions but not others.
-Species abundances vary between sites and over time, and some interactions may not occur if one or both partners is rare.
-In addition, some interactions only occur in brief temporal windows (e.g., flowers of Arctic plants may only open for a few days~\citep{}) or when mediated by other species (e.g., consumption of some shellfish by fish only occurs when the shellfish are heavily parasitised and cannot burrow~\citep{}).
-Expanding sampling to cover broader ranges of space and time will expand the set of interactions that are observed, but again will increase the time and resources needed.
-\\
-\textbf{4)}{} Observations of rare species add disproportionately more "zeros" than ones to an interaction matrix.
-Rare species may appear to be specialists purely because of their rarity~\citep{}.
-If increasing sampling effort adds many rare species to a network, but each species is observed only one or a few times, it is likely that only a fraction of the rare species' interactions will be included.
-Note that we should not avoid sampling rare species!
-It is better to identify species about which we know little as targets for future study than to ignore these species.
-Nevertheless, sampling which is sufficiently high to identify most species at a site but not most interactions for rare species will underestimate the number of interactions and skew the distribution of interactions to rare species.
-Targeted sampling of rare species would reduce this problem, but again either increase the cost of a study or take away resources from sampling more abundant species.
-\\
-Increased or targeted sampling could improve (and, given enough resources, perhaps solve) any one of the above problems.
-As each places demands on the same limited resource pool, however, it is extremely unlikely that researchers will be able to sample their way out of uncertainty about interactions.
-To illustrate the scale of sampling needed, we can consider the observation of an interaction as a Bernoulli trial.
-The number of successes ($k$ observed interaction) over ($n$ observed co-occurrances) trials will follow a binomial distribution (see~\emph{Appendix S2} for a full description of the mathematical framework).
-In this framework, the maximum likelihood estimate (MLE) for $\lambda$ is:
-
-        \begin{equation}
-          \lambda_{MLE} = \frac{k}{n}  .
-          \label{theta_MLE}
-        \end{equation}
-
-    Note that $\lambda$ is not a point estimate but rather a random variable with an unknown distribution.
-This means that if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact.
-Rather, $k = 0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless some chance that the two species \emph{could} interact.
-In the situation where $k>0$, in contrast, we are sure that the interaction is feasible.
-$k$ may not equal $n$ if local constraints or detection errors prevent the interaction from being observed in each sample, but we nevertheless know that the interaction does occur.
-
-    Importantly, we can estimate the variance of $\lambda$ as well as the MLE; available methods include the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]).
-Examining the changing variance about $\lambda$ with increasing sample size (Fig.~\ref{upper_limits}), we see that tens of observations are required to establish that two co-occurring species do not interact.
-Most datasets lack such extensive sampling for some species pairs, especially rare species which may be of particular conservation interest~\citep{Bartomeus2013}.
-The main advantage of the Bayesian approach we suggest here is that it can reduce uncertainty about interactions involving species with limited numbers of observations.}
-\label{Box1}
-\end{figure}
+% \captionsetup{singlelinecheck=false, font={stretch=2}}
 
@@
     \begin{center}
-    % \includegraphics*[height=.5\textheight]{figures/conceptual_fig.eps}
+    \includegraphics*[height=.5\textheight]{figures/conceptual_fig.eps}
     % \includegraphics*[height=.5\textheight]{Figure_1.eps}
@@
       \begin{center}
-      % \includegraphics*[height=.6\textheight]{figures/GP_histogram.eps}
+      \includegraphics*[height=.6\textheight]{figures/GP_histogram.eps}
       % \includegraphics*[height=.6\textheight]{Figure_2.eps}
@@
     \caption{Imperfect detection of interactions increases the number of samples required to be confident that an interaction never occurs.
-Assume that two species cannot interact (i.e., $\lambda=0$) and that the number of observed interactions follows a binomial distribution.
+Assume that two species cannot interact (i.e., $\lambda=0$) and that the number of observed interactions follows a binomial distribution depending upon the number of observed interactions $k$ and observed co-occurrances $n$.
+The maximum likelihood estimate (MLE) for $\lambda$ is $\lambda_{MLE}=\frac{k}{n}$.
+Note that $\lambda$ is not a point estimate but rather a random variable with an unknown distribution.
+This means that if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact.
+Rather, $k = 0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless some chance that the two species \emph{could} interact.\\
+    Importantly, we can estimate the variance of $\lambda$ as well as the MLE; available methods include the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]).
     Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true credible interval for the interaction probability $\lambda$ for a pair of species that has been observed co-occurring $n$ times but never interacting ($k = 0$).
 The upper limit of the credible interval only reaches 0.1 (dashed, red line) with 35 observations.
-Thus, adding more observations is useful in controlling uncertainty, but the number of observations added must be very high.
-}
+Thus, adding more observations is useful in controlling uncertainty, but the number of observations added must be very high \emph{unless} we have some other reason to believe that an interaction cannot occur.}
     \label{upper_limits}
     \begin{center}
-    % \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
+    \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
     % \includegraphics*[width=.8\textwidth]{Figure_3.eps}
@@
     \begin{center}
-    % \includegraphics*[width=.8\textwidth]{figures/GP_pdfs_increasing_N_Zillis.eps}
+    \includegraphics*[width=.8\textwidth]{figures/GP_pdfs_increasing_N_Zillis.eps}
     % \includegraphics*[width=.8\textwidth]{Figure_4.eps}
@@
     \begin{center}
-    % \includegraphics[width=.8\textwidth]{figures/GP_posterior_properties_Zillis.eps}
+    \includegraphics[width=.8\textwidth]{figures/GP_posterior_properties_Zillis.eps}
     % \includegraphics[width=.8\textwidth]{Figure_5.eps}

### 2018-11-29 manuscript/supplemental.tex
reframing going well

@@
 Priors may be selected to be uninformative, so as not to bias the posterior distribution in any particular direction, or may be informative and based on some prior knowledge about the system.
-
-    \subsection*{Uninformative prior}
-
-        In the absence of any external information, an uninformative prior is the most conservative hypothesis for the distribution of $\lambda$.
-The beta distribution is in this case a uniform distribution, specified with hyper parameters $\alpha=1$ and $\beta=1$.
-
-    \subsection*{Distribution of connectance}
-
-        The ecological network literature boasts a collection of networks for which connectance has been calculated and for which we can thus define the connectance distribution.
-Connectance is measured as $C = L/S^2$, where $L$ is the number of interactions and $S$ is the number of species.
-It measures the filling of an interaction matrix and thereby expresses the average probability that any two species interact with each other.
-If we know only the mean $\overline{C}$ and the variance $\sigma_C^2$ of the distribution of $C$, then the beta parameters could be computed as follows using the method of moments:
-
-        \begin{equation}
-        \alpha = \overline{C}(\frac{\overline{C}(1-\overline{C})}{\sigma_C^2}-1) ,
-        \end{equation}
-
-        \begin{equation}
-        \beta = (1-\overline{C})(\frac{\overline{C}(1-\overline{C})}{\sigma_C^2}-1) .
-        \end{equation}
-
-    \subsection*{Degree distribution or interaction probabilities}
-
+Here we demonstrate how to calculate a prior distribution using a known set of degrees.
 The degree of a node in a network is defined as its number of connections to other nodes.
@@
 For distributions of either degrees or interaction probabilities, the procedure for the estimation of the hyper parameters follows the same approach as described above for connectance except that each measurement is at the individual interaction level instead of the network level.
-
-    \subsection*{Trait-matching function}
-
-        As a fourth and final approach, it may be possible to obtain the prior distribution of $\lambda$ using the outcome of a trait-matching model, provided such a model has been parameterised using external data and relevant traits are available.
-In such a case, the prior distribution would follow the function $P(\lambda|\mathbf{T})=f(\mathbf{T})$ based on a set of traits for both species $\mathbf{T}$.
-There are several techniques available to perform this inference of interaction probability, some of which are Bayesian, and we refer interested readers to~\citet{Bartomeus2016} and~\citet{Weinstein2017} for recent reviews about this topic.
-Note that in this case the prior might not be beta-distributed and numerical methods might be required to compute the posterior distribution.
-
-        Trait-matching functions reduce uncertainty around the feasibility of interactions.
-Interactions between species with extremely mis-matched traits are very unlikely, and we can therefore be more confident that an unobserved interaction does not occur.
-This approach could be extended to models including environmental or phenological constraints, allowing researchers to reduce process uncertainty as well.
-Such models are, however, likely to be large and therefore may pose a risk of over-fitting.
 

### 2018-11-29 manuscript/CI_interactions.tex
main text fine, adding more levels of filtering

@@
 
-    [[These two paragraphs try to frame our study more clearly. Any help to shorten them?]]
+    [[These two paragraphs try to frame our study more clearly]]
     To date, models incorporating uncertainty have either been very general (e.g.,~\citet{Guimera2009,Gravel2013}) or very system-specific (e.g.,~\citet{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}); in either case one of these models may be a poor fit for a particular study system.
@@
 In the context of this uncertainty, which can be reduced but not eliminated by high-quality sampling (\citealp[see Box 1]{Bartomes2013}), we present our Bayesian framework for combining observed data with a prior expectation of network structure.
-We conclude with a worked example applying this framework to an intensively-sampled willow-galler network.
+We conclude with a worked example applying this framework to an intensively-sampled host-parasitoid network.
 We find that even the highest-quality empirical network we could find had substantial uncertainty about whether many pairs of species interact, demonstrating the need to include information about this uncertainty in published networks.
@@
 We argue that one of the advantages of the Bayesian approach is that it makes some of the subjectivity inherent in network construction explicit.
-Researchers compiling empirical networks face many decisions about where to set community boundaries~\citep{}, the set of species to include in the focal community~\citep{}, what type of sampling is most appropriate~\citep{Wirta2014}, etc.
+Researchers compiling empirical networks face many decisions about where to set community boundaries, the set of species to include in the focal community~\citep{Jordano2016}, what type of sampling is most appropriate~\citep{Wirta2014}, etc.
 All of these choices will affect the compiled network and most do not have clear answers, making all empirical networks (and all theoretical networks, which likewise depend upon the assumptions used in building the network) to some extent subjective.
@@
   \subsection*{An empirical example}
-    [[Make the point of this clearer]]
+
       To illustrate the process of constructing a Bayesian network to quantify uncertainty about interactions, we use the comprehensively-sampled system of willows (\emph{Salix}), herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}.
@@
 
-      Unlike~\citet{Bartomeus2013,Weinstein2017,Weinstein2017a}, our model can include interactions for species which were observed infrequently (or not at all) during sampling.
+    \subsubsection*{Computing the prior and posterior distributions}
 
-    \subsubsection*{Computing the prior and posterior distributions}
-      [[Remove the network I used for the prior from the rest of the analyses.]]
         To treat each interaction as a Bayesian probability, we will combine the observed data with a distribution based on prior information.
@@
 
-      [[Need to make it clear why we're doing this.]]
-
-      Researchers usually use interaction matrices as a tool to calculate measures of network structure.
+      Researchers are often interested in measures of network structure rather than the network itself.
 Computing most network metrics is straightforward when the different $\lambda$ of the adjacency matrix are known and assumed not to vary~\citep{Poisot2016}.
@@
 By Jensen's inequality~\citep{Jensen1906}, this means that the average of a network metric (a function of stochastic interactions) is not the same as the network metric calculated based on the average interaction probability.
-Any uncertainty in the values of $\lambda$ could bias both the mean and variance of network metrics, giving misleading results (simulated in \emph{Appendix S1}).
+Thus, any uncertainty in the values of $\lambda$ could bias both the mean and variance of network metrics, giving misleading results (simulated in \emph{Appendix S1}).
 One way to avoid this situation is to calculate the properties of a suite of simulated networks~\citep{Vazquez2005,Guimera209}.
@@
 After obtaining these posterior networks, we calculated the connectance of each web, as well as the mean number of links per galler and per natural enemy, and the nestedness (NODF) of the network.
+This gives us an estimate for each property reflecting our uncertainty about $\lambda$.
 
@@
 
-  We obtained prior parameters of $\alpha$=0.700, $\beta$=8.49.
-Where $n = 0$, these parameters gave a posterior distribution with $\bar\lambda$=0.076, var($\lambda$)=0.008.
-When $n = 374$, we obtained a posterior distribution with $\bar\lambda_{ij}$=1.83 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=4.76.
+  We obtained prior parameters of $\alpha$=0.700, $\beta$=8.49, giving a beta distribution strongly skewed towards 0.
+Where $n=0$, these parameters gave a posterior distribution with $\bar\lambda$=0.076, var($\lambda$)=0.008.
+When $n=374$, we obtained a posterior distribution with $\bar\lambda_{ij}$=1.83 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=4.76$\times10^6$.
 This distributions is very close to 0 with small variance about $\lambda$; if species $i$ and $j$ co-occurred 374 times without interacting, they are extremely unlikely to do so at other sites or times.
@@
 This suggests that limited sampling is a major source of uncertainty in empirical networks, in agreement with~\citet{Jordano2016,Weinstein2017a,Weinstein2017}.
-This dataset also illustrates the problem of pairs of species which were observed interacting did not interact in all of the samples in which they co-occurred.
-Increasing sampling is therefore likely to add more zeros than ones to an interaction network.
 
@@
 
-  [[rephrase to make these more clearly about OUR results]]
-  Using prior knowledge to build a Bayesian distribution for each interaction probability allows us to set appropriate bounds on interaction probabilities for species which were rarely or never observed co-occurring.
-In such cases, an informative prior distribution gives us more reasonable estimates of interaction probabilities than assuming that $p$=0 for unobserved interactions.
-This approach is particularly useful when considering interactions involving species entering new ranges due to climate change or introductions.
+  Although 374 sampling sites were not enough to obtain sufficient observations of all species pairs, we were able to reduce uncertainty about many potential interactions using a simple Bayesian framework.
+This framework allowed us to set appropriate confidence intervals about the probability of an unobserved interaction occurring, based on the distribution of interactions in one sample site.
+This gives us more reasonable estimates of interaction probabilities than assuming that no unobserved interactions actually occur.
+Such an approach is particularly useful when considering interactions involving species entering new ranges due to climate change or introductions.
 Understanding these species' interactions is important for a variety of conservation questions~\citep{Bartomeus2013,Gravel2013}, and a Bayesian approach using a trait-matching model or data from species' current ranges could help us to anticipate how species will integrate into new communities.
@@
 The structure of the well-sampled network used in our case study is most similar to the structure of simulated networks including only 50\% of the interactions suggested by the posterior distribution of interaction probabilities.
-If our descriptions of empirical systems are missing up to half of the feasible interactions, then it is vital to acknowledge this inherent uncertainty before comparing structures across systems or relating structure to stability~\citep{other studies pointing out poor detectability}.[[Add citations?]]
-  ~\citep{Jordano2016,Weinstein2017a}[[for poor detectanility - 50\% to 23\%]]
-  ~\citep{Bartomeus2013}[[had 59\% of interactions detected]]
+This poor detection rate is similar to that reported in other studies~\citep{Bartomeus2013,Jordano2016,Weinstein2017a}.
+If our descriptions of empirical systems are generally missing so many feasible interactions, then it is vital to acknowledge this inherent uncertainty before comparing structures across systems or relating structure to stability.
 
@@
 Second, researchers should acknowledge the varying levels of confidence surrounding interactions between species pairs.
-Including the $n$ and $k$ values for each interaction will clearly indicate which unobserved interactions are most likely to be observed with further sampling and which estimates are more reliable.
+Including the $n$ and $k$ values for each interaction will clearly indicate which unobserved interactions are most likely to be observed with further sampling and which estimates are more reliable, as well as indicating potential sampling biases.
 Where there are strong prior expectations about pairs of species that will not interact, these should be explicitly stated so that readers know which zeros in an interaction matrix are based on observed data and which are based primarily upon expert knowledge.
@@
 The upper limit of the credible interval only reaches 0.1 (dashed, red line) with 35 observations.
-Thus, adding more observations is useful in controlling uncertainty, but the number of observations added must be very high \emph{unless} we have some other reason to believe that an interaction cannot occur.}
+Thus, adding more observations is useful in controlling uncertainty, but the number of observations added must be very high unless we have some other reason to believe that an interaction cannot occur (i.e., a strong prior).}
     \label{upper_limits}

### 2018-11-29 code/Zillis_prior/calculate_NODF.R

@@ -13,7 +13,8 @@ site="Zillis"
     propdir<-"../../data/Zillis_webs/gp_detection_filter/"
     }
     print(webtype)
-    props<-c(0.5,0.6,0.7,0.8,0.9,0.95,0.99)
+    props<-c(0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9)
+    # props<-c(0.5,0.6,0.7,0.8,0.9,0.95,0.99)
     nesttable<-matrix(nrow=700,ncol=5)
     colnames(nesttable)<-c("Web","Proportion","Obs_NODF","Sample_mean","Sample_SD")
     k<-1      

### 2018-11-29 code/Zillis_prior/calculate_Ziller_simweb_properties.py

@@ -97,14 +97,15 @@ def main():
     for nettype in ['SG','GP']:
       print site, nettype
       # Starting with C
-      summary_dict={'C':{0.5:{},0.6:{},0.7:{},0.8:{},0.9:{},0.95:{},0.99:{}},
-      'LS':{0.5:{},0.6:{},0.7:{},0.8:{},0.9:{},0.95:{},0.99:{}},
-      'LP':{0.5:{},0.6:{},0.7:{},0.8:{},0.9:{},0.95:{},0.99:{}}  }
+      summary_dict={'C':{0.4:{},0.3:{},0.2:{},0.1:{},0.5:{},0.6:{},0.7:{},0.8:{},0.9:{},0.95:{},0.99:{}},
+      'LS':{0.4:{},0.3:{},0.2:{},0.1:{},0.5:{},0.6:{},0.7:{},0.8:{},0.9:{},0.95:{},0.99:{}},
+      'LP':{0.4:{},0.3:{},0.2:{},0.1:{},0.5:{},0.6:{},0.7:{},0.8:{},0.9:{},0.95:{},0.99:{}}  }
 
       for post_number in range(1,101):
         gallers,salixes,links=web_reader(webdir,0,post_number,0,nettype,site)
         obsC,obsLS,obsLP=calculate_original_properties(gallers,salixes,links)
-        for proportion in [0.5,0.6,0.7,0.8,0.9,0.95,0.99]:
+        for proportion in [0.9,0.8,0.7,0.6,0.5,0.4,0.3,0.2,0.1]:
+        # for proportion in [0.5,0.6,0.7,0.8,0.9,0.95,0.99]:
         # for proportion in [0.9,0.95,0.99]:
           filtered_C=[]
           filtered_LS=[]

### 2018-11-29 code/Zillis_prior/create_Zillis_posterior_webs.py

@@ -117,7 +117,8 @@ def main():
       random_ints=posterior_sampling(pdict) # Calculate a set of random trails for each int
       write_posterior_webs(random_ints,postdir,site) # Create a set of random posterior webs
 
-      for proportion in [0.5,0.6,0.7,0.8,0.9,0.95,0.99]:
+      # for proportion in [0.5,0.6,0.7,0.8,0.9,0.95,0.99]:
+      for proportion in [0.9,0.8,0.7,0.6,0.5,0.4,0.2,0.3,0.2,0.1]:
         print nettype, proportion
         # proportion=0.8 # Eventually I probably want to do this for different proportions of links detected
         filter_posterior_webs(postdir,proportion,altdir,site)

### 2018-11-29 manuscript/reply_to_reviewers.tex
reply ready for co-authors

@@
 
-Changes: reducing discussion of different sources of uncertainty, increasing description of priors, added a bunch of refs, trying to frame our study more clearly.
+% Changes: reducing discussion of different sources of uncertainty, increasing description of priors, added a bunch of refs, trying to frame our study more clearly.
+Changed filtering to reflect all uncertainty, not just detection (more accurate, hopefully less confusing).
+No box needed, just "Why sample" section.
 
-Still to do: framing, expand discussion of network metrics from sampled vs.
-predicted vs.
-expert knowledge networks...
-(ours reflect about 50\% of links observed, doesn't seem super out of line).
-Make clearer that we are modelling L but could also model X|L with independent $n$ and $k$ data within a single site.
-Maybe in the section introducing the model or introducing the case study?
-
-Ask for help: how would we expand this to interaction frequencies? Still with the Bernoulli? Worthwhile to add a demo of Jensen's inequality?
+% Ask for help: how would we expand this to interaction frequencies? Still with the Bernoulli? Worthwhile to add a demo of Jensen's inequality?
+% To do: expand discussion of our results as much as possible given space constraints.
 % -----------------------------------------------------------------------------
@@
 We emphasize that we are not introducing a software package (although we do provide simple code to aid those who are new to the field), nor are we introducing an entirely new framework (as the other Reviewers point out, many components of our approach have been touched on by previous work).
-The novelty and impact of our work lies in connecting a Bayesian statistical approach to the problem of limited and uneven sampling (driven by difference in species abundances, detectabilities, constrained time and budgets, etc.) and, we hope, in making this method more accessable to those without extensive statistical or modelling experience.
+The novelty and impact of our work lies in connecting a Bayesian statistical approach to the problem of limited and uneven sampling (driven by difference in species abundances, detectabilities, constrained time and budgets, etc.) and, we hope, in making this method more accessible to those without extensive statistical or modelling experience.
 Because of the difference between Reviewer 2 and the other Reviewers, we have opted to prioritise the majority view and focused first on comments by Reviewers 1, 3, and 4.
-We hope that, in the course of these revisions, we have at least partially adressed Reviewer 2's concertns as well.
+We hope that, in the course of these revisions, we have at least partially addressed Reviewer 2's concerns as well.
+	\smallskip
+	We have taken Reviewer 1's suggestion that we expand upon the different types of priors available and reasons for choosing one over the other.
+We also now offer a brief discussion about concerns over the subjectivity of prior selection.
+We argue that a great deal of subjectivity is baked into the compilation of empirical networks and that a Bayesian approach can be seen as making this subjectivity explicit.
+We hope that this will encourage empiricists to explicitly use their system-specific knowledge to create reasonable priors, as likely already occurs subconsciously (as in the designation of "forbidden links").
+We hope that our revision more clearly frames the importance of uncertainty in ecological networks and positions a simple Bayesian approach as a partial solution (together with high-quality sampling, of course).
+	\smallskip
+	We have also added many references to prior work. While the present study is not intended to be a full review of the literature, we certainly do not wish to downplay other workers in the area.
+	\smallskip
+	Finally, several of the Reviewers appeared to believe that we were advocating for reduced sampling effort.
+That is emphatically not the case (we find the idea absurd), and we have revised the manuscript to be clearer about the fact that increased sampling effort can reduce some sources of uncertainty.
+We hope that it is now clear that the Bayesian framework we promote is a complement to high sampling effort.
+
+	Once again, we thank the Associate Editor and Reviewers for their comments and hope that our revised manuscript will satisfy their concerns.
 
@@
 % ----------------------------------------------------------------------
-{\Large \bf Reply to Reviewer \#1}
+{\Large \bf Reply to Reviewer \#1} [[done]]
 % ---------------------------------------
 
-	1. Suggestion to refocus on prior selection [[not done]]
+	1. Suggestion to refocus on prior selection [[done]]
 
@@
 
-		\textbf{R:} We thank the Reviewer for the suggestion to expand our discussion of prior selection, particularly with regard to approxmimate/empirical bayes.
-[[Expand refs to this]] We now walk through flat, informed, and empirical priors as suggested (lines XX-XX) and refer to the controversy surrounding empirical priors in our discussion (lines XX-XX).\\
+		\textbf{R:} We thank the Reviewer for the suggestion to expand our discussion of prior selection, particularly with regard to approxmimate/empirical Bayes.
+Although we are somewhat space-limited, we have expanded our description of different priors available and why a researcher might choose one over another (lines XX-XX).
+We also touch upon the controversy over using empirical priors (lines XX-XX) although we were unable to find many references addressing this in detail.
+If the Reviewer has particular works in mind, we would be more than happy to include them.
+We hope that this expanded description will be a better guide for empiricists who may not be familiar with Bayesian statistics.
+		\medskip
 		We also appreciate the Reviewer's comments on our introduction.
@@
 We have, however, taken care to introduce our analysis as a worked example (lines XX-XX) and hope that this helps to reduce the conflict between the introduction and our data.
-[[Add something else about different priors?
-Add different priors to our analyses?]]
-			[[Definitely should expand this, but do we want to really focus on those?]][[not quite done]]
-
+		\medskip
 		We thank the Reviewer for their compliments and accept their suggestion that we are somewhat overexcited about our approach.
@@
 
-		\textbf{R:} We thank the Reviewer for their compliments to our introduction and for the recommendation of Jordano 2016.
-We have incorporated this reference as suggested.
+		\textbf{R:} We thank the Reviewer for their compliments to our introduction and for the literature recommendations.
+We have incorporated these reference as suggested.
 Following comments from other reviewers, we have refined and slightly restructured our introduction in the hope of more clearly establishing the goal of our manuscript ('narrowing our net').
 We hope that this revised introduction will also meet with the Reviewer's approval.
-[[done]]
 
@@
 
-		\textbf{R:} The section on the MLE estimate was designed to illustrate the large sample sizes needed in the absence of a Bayesian framework.
-Upon reflection, we see have moved this demonstration to a box dealing specifically with sampling.
-We now begin with the Bayesian beta distribution as suggested.
-[[I think done?]]
+		\textbf{R:} The MLE estimate is part of the Bayesian framework as it dictates the shape of the distribution we use.
+We now introduce the MLE formally within this context (lines XX-XX) and take care to be explicit when using it to explore the sample size needed in the absence of prior knowledge later (lines XX-XX).
+
+		Lines XX-XX:
+
+		\begin{quotation}
+			The basis of a Bayesian approach to modelling the probability that an interaction occurs ($\lambda$) is combining the maximum likelihood estimate (MLE) of $\lambda$ with a prior distribution (described in the next section) and a normalising function.
+The MLE of $\lambda$ can be modelled as a Bernoulli trial based on the number of observed interactions $k$ and observed co-occurrances $n$: $\lambda = \frac{k}{n}$.
+The most appropriate prior distribution for a probability such as $\lambda$ is the beta distribution:
+		\end{quotation}
+
+		Lines XX-XX:
+
+		\begin{quotation}
+			The number of observed co-occurrences needed to believe that an unobserved interaction cannot occur is very high (about 35; Fig.~\ref{upper_limits}), and most datasets will not include this level of sampling for all pairs of species~\citep{Bartomeus2013}.
+		\end{quotation}
 
@@
 
-		\textbf{R:} We have now address questions relating to sampling in a dedicated box.
-We hope that the revisions make our stance on repeated sampling clearer and that there are no longer apparent contradictions.
+		\textbf{R:} We now address questions of sampling in the subsection \textbf{Why can't we sample more?}.
+We hope that this revision makes it clear that sampling should be as high-quality as possible but that sampling is unlikely to completely remove uncertainty.
 
@@
 % ---------------------------------------------------------------------
-{\Large \bf Reply to Referee \#2}
+{\Large \bf Reply to Referee \#2} [[not started]]
 % ---------------------------------------
@@
 		\textbf{R:} We have revised this section and now no longer refer to the specifics of Weinstein and Graham at all.
-Instead, we discuss repeated sampling in a box dedicated to the question of whether sampling is useful (of course it is) and whether it can completely solve problems of uncertainty in ecological networks (almost certinaly not).
+Instead, we discuss repeated sampling in a section dedicated to the question of whether sampling is useful (of course it is) and whether it can completely solve problems of uncertainty in ecological networks (almost certinaly not).
 We hope that this is less confusing.
@@
       The high spatiotemporal resolution of this dataset make it ideal for illustrating the difficulties in completely sampling a network; even with such an unusually high sampling effort, we anticipate that there will be many pairs of species which were rarely or never observed together.
+Using the Bayesian framework above, we can identify which potential interactions are more and less uncertain, allowing us to better predict the true structure of the metaweb.
 To show the gaps in sampling, we compared the frequencies of observed co-occurrences and interactions.
-We then calculated an empirical prior and computed the posterior distribution of the probability of observing each as-yet-unobserved interaction in the future.
-      \medskip
-			While a strict Bayesian framework requires a prior distribution that does not rely on any information from the study at hand, such data are not always available.
-In that case, researchers must choose between using a less-informative prior (e.g., one based on distributions of links across a large set of networks) or an empirical prior based on some "training data" from the study.
+We then calculated an empirical prior and computed the posterior distribution of the probability of an as-yet-unobserved interaction being feasible ($\lambda$).
+      We analysed both the \emph{Salix}-galler and galler-natural enemy components of the network but, for brevity, present only the latter here (see~\emph{Appendix S5} for \emph{Salix}-galler results).
+
 		\end{quotation}
 
-	4. Misunderstanding of our point about sampling effort [[maybe done? in progress]]
+	4. Misunderstanding of our point about sampling effort [[done]]
 
@@
 Rather, we assumed that field researchers already sample to the maximum extent possible given their time and resource constraints and so a call to "sample more" would not be helpful.
-We now address this assumption explicitly in a box dedicated to the potential for sampling effort to reduce uncertainty about interactions.
+We now address this assumption explicitly in a section dedicated to the potential for sampling effort to reduce uncertainty about interactions (\textbf{Why can't we sample more?}.
 Below, we address the Reviewer's sampling-related comments one by one.
@@
 
+		\textbf{R:} We are pleased that this point was clear and have made sure to include it in our revision.
+
 		\begin{refquote}
@@
 
+		\textbf{R:} We are specifically speaking about interactions which were never observed.
+As interaction networks tend to be sparse, there will always be many of these.
+If interaction frequencies were higher among species that co-occurred, then we would have fewer unobserved interactions but the sample sizes needed to be confident that an unobserved interaction does not occur would not change (perhaps our threshold for deciding to believe a zero might, which is why we provide sample sizes for several thresholds).
+The Reviewer has hit the nail on the head with the idea that it is extremely hard to get enough data to be sure about every interaction.
+This is why prior knowledge can be so useful!
+
 		\begin{refquote}
@@
 		\end{refquote}
+
+		\textbf{R:} We had written our first draft with the assumption that empirical ecologists are well aware that large sample sizes are important and that they should sample as much as possible.
+Given that, repeating the call to sample more seemed more likely to come across as patronizing than helpful.
+We did not anticipate that anyone would read the omission of such a call a statement that anyone should sample \emph{less}.
+In our revised manuscript, we collect our discussion of sampling into a dedicated section.
+We hope that this will make it clearer that sampling is very important but cannot completely eliminate uncertainty (except perhaps in some very species-poor and unusually static systems, but these are certainly rare).
+As to adding more zeros than ones specifically, this is only "bad" in the sense that it gives us more high-uncertainty cells in the interaction matrix.
+We take the view that it is better to have "known unknowns" than "unknown unknowns" and it is certainly better to know about more of the species in a community than fewer, but finding a single individual of a rare species will not reduce uncertainty in the web.
+We have added a line (XX-XX) specifically to address this.
+
+		\begin{quotation}
+			we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig.~\ref{histograms}C).
+While this improves our understanding of the set of species present in the community, it introduces yet more uncertainty into the interaction matrix.
+Note that it is better to identify the set of potential interactions than to miss a species, so sampling effort should not be reduced in order to exclude rare species.
+		\end{quotation}
 
@@
 
-	1. Paper is poorly structured [[not done]]
+	1. Paper is poorly structured [[done?]]
 
@@
 
-		\textbf{R:}
+		\textbf{R:} We have revised the manuscript with an eye to clarifying the flow between sections.
+We hope that it is now clear that our proposed framework is designed to use Bayesian theory to complement empirical networks and empiricists' detailed knowledge of their systems.
 
@@
 
-	4. Demand for extension to weighted networks [[not done]]
+	4. Demand for extension to weighted networks [[not done - do we want to do this?]]
 
@@
 Increasing sampling effort will not do much good if we repeatedly sample the same common interactions and very rarely identify any new interactions.
-We now address questions about whether or not sampling more will remove uncertainty in a dedicated box.
+We now address questions about whether or not sampling more will remove uncertainty in a dedicated section (\textbf{Why can't we just sample more?}).
 We still mention the fact that increased sampling will not reduce uncertainty evenly across interactions as this is an important point to consider when designing sampling protocols and when analysing empirical data.
@@
 
-	17. Expand discussion of results on line 321 [[not done]]
+	17. Expand discussion of results on line 321 [[not done - will take this after we see about space]]
 

### 2018-11-29 manuscript/CI_interactions.tex
reply ready for co-authors

@@
 Despite these benefits, we note that there are limits to the utility of increased sampling.
-Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig.~\ref{histograms}C), thereby adding more zeros with high uncertainty (which would require more sampling to reduce, and so on).
+Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig.~\ref{histograms}C).
+While this improves our understanding of the set of species present in the community, it introduces yet more uncertainty into the interaction matrix.
+Note that it is better to identify the set of potential interactions than to miss a species, so sampling effort should not be reduced in order to exclude rare species.
 

### 2018-11-29 manuscript/reply_to_reviewers.tex
most of the summary statistics calculated for new posteriors

@@
 
-	5/ results&discussion too short: the reader is surprised to read 27 lines of raw results only… Given the amount of new methodology that is proposed, one can expect a complete description of its pros and cons.
+	5/ results\&discussion too short: the reader is surprised to read 27 lines of raw results only… Given the amount of new methodology that is proposed, one can expect a complete description of its pros and cons.
 Obvisouly, a simulation study (see above) would enrich the results part.
@@
 The authors chose upper case letters L,T ,X,D for single entities whereas the mathematician is used to expect matrices or constants in upper case.
-Traditionaly, given species i and j, we would consider interaction L_ij, feasibility X_ij, detectionability D_ij...
+Traditionaly, given species i and j, we would consider interaction $L_ij$, feasibility $X_ij$, detectionability $D_ij$...
 	Still, what is T?? not defined, never reused: is it a characteristics on i, on j, on both?
@@
 	Moreover, L is reused later but is the number of interactions (l.100 supp.mat)…
-	What is “N” in Figure 4? is it “n”? What is n_ij and k_ij l.266? Never defined, never reused.
-	In the beginning of the paper, \lambda is a probability (l.62) but it becomes a random variable (l.164): it would be more consistent to introduce before the notion of hyperparameters  (l.209-213) and to explain we consider that \lambda is drawn into its distribution.
+	What is “N” in Figure 4? is it “n”? What is $n_ij$ and $k_ij$ l.266? Never defined, never reused.
+	In the beginning of the paper, $\lambda$ is a probability (l.62) but it becomes a random variable (l.164): it would be more consistent to introduce before the notion of hyperparameters  (l.209-213) and to explain we consider that $\lambda$ is drawn into its distribution.
 

### 2018-12-11 code/create_posterior_webs.py
want to ignore randomised webs with the bad prior

@@ -153,7 +153,8 @@ def main():
     random_ints=posterior_sampling(pdict) # Calculate a set of random trails for each int
     write_posterior_webs(random_ints,postdir) # Create a set of random posterior webs
 
-    for proportion in [0.5,0.6,0.7,0.8,0.9,0.95,0.99]:
+
+    for proportion in [0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9]:
       print nettype, proportion
     # proportion=0.8 # Eventually I probably want to do this for different proportions of links detected
       filter_posterior_webs(postdir,proportion,altdir)

### 2018-12-11 code/figure_generation/Zillis_posterior_plots.py

@@ -1,261 +1,0 @@
-import sys
-import math
-import random
-from decimal import *
-import numpy as np
-
-#Pygrace libraries
-from PyGrace.grace import Grace
-from PyGrace.colors import RandomColorScheme, MarkovChainColorScheme, ColorBrewerScheme
-from PyGrace.dataset import SYMBOLS
-from PyGrace.Extensions.panel import NetworkPanel,Panel,MultiPanelGrace
-from PyGrace.drawing_objects import DrawText, DrawLine, DrawBox
-from PyGrace.axis import LINEAR_SCALE, LOGARITHMIC_SCALE
-from PyGrace.Extensions.network import Network
-
-from PyGrace.Extensions.distribution import CDFGraph, PDFGraph
-from PyGrace.Extensions.latex_string import LatexString, CONVERT
-from PyGrace.Extensions.colorbar import SolidRectangle, ColorBar
-from PyGrace.Styles.el import ElGraph, ElLinColorBar, ElLogColorBar
-
-colors=ColorBrewerScheme('Blues')  # The blue is very beautiful but maybe harder to see.
-colors.add_color(130,20,20,'red')
-# colors.add_color(120,120,120,'grey')
-
-obsvals={'SG':{'C':0.028,'LS':2.71,'LG':1.47,'NODF':0.5600535},
-'GP':{'C':0.078,'LS':9.99,'LG':7.45,'NODF':6.853653}}
-
-def read_summary_file(filename):
-  whiskers={0.5:[],0.6:[],0.7:[],0.8:[],0.9:[],0.95:[],0.99:[]}
-  obs={0.5:[],0.6:[],0.7:[],0.8:[],0.9:[],0.95:[],0.99:[]}
-  pointdict={}
-  f=open(filename,'r')
-  for line in f:
-    if line.split()[0]!='Web':
-      proportion=float(line.split()[1]) # Proportion of links observed
-      obs_C=float(line.split()[2]) # C in the full posterior web
-      sample_mean=float(line.split()[3]) # Mean C in the detection filter webs
-      sample_SD=float(line.split()[4])
-      sample_SE=sample_SD/10 # SD/sqrt(100 filter webs)
-      # CI is +- 1.96SE
-      if proportion not in pointdict:
-        pointdict[proportion]=[(obs_C,sample_mean,sample_SD)]
-      else:
-        pointdict[proportion].append((obs_C,sample_mean,sample_SD))
[…]

### 2018-12-11 code/figure_generation/heatmap.py

@@ -1,153 +1,0 @@
-
-# This example demonstrates how to use a color plot.
-#
-# One important feature of color plots is that drawing objects in
-# XMGrace are plotted above the frame of a graph.  As a result, we use
-# the Grace.clone_graph method to copy the frame of the graph and make
-# things look pretty.
-#
-# Another important feature of color plots is that specifying a
-# particular world coordinate can automatically place drawing objects
-# outside of the domain of the graph.
-# Graph.remove_extraworld_drawing_objects fixes this problem by
-# removing all of the drawing objects that appear in the world
-# coordinates and are out of bounds.
-#
-# It also demonstrates how to use a PyGrace.Style to format figures in
-# a customized format
-
-#import math
-#from PyGrace.Extensions.panel import Panel,MultiPanelGrace
-
-## To run use:
-# python heatmap.py ../../data/Salix_example/cooccur_interact_galler_salix galler salix
-
-import random
-import sys
-import os
-
-from PyGrace.grace import Grace as Plot
-from PyGrace.Extensions.colorbar import SolidRectangle, ColorBar
-from PyGrace.colors import ColorBrewerScheme
-from PyGrace.axis import LINEAR_SCALE, LOGARITHMIC_SCALE
-from PyGrace.drawing_objects import DrawBox, DrawText, DrawLine
-
-from PyGrace.Styles.el import ElGraph, ElLogColorBar, ElLinColorBar
-
-
-#------------------------------------------------------------------------------
-# make a nice figure
-#------------------------------------------------------------------------------
-# get the data (as specified in the command line)
-readfile = sys.argv[1]
-filename = readfile+'.csv'
-troph1 = sys.argv[2]
-tr1id = troph1+'_ID'
-troph2 = sys.argv[3]
-tr2id = troph2+'_ID'
-infile = open(filename)
-header=infile.readline().strip().split(',')
-
-
-# read in the data into something we can manipulate easily
-data = []
-for line in infile:
-	sline = line.strip().split(',')
-	pt = dict(zip(header,[i for i in sline]))
-	data.append(pt)
-infile.close()
-# print data[0:7]
-
-ndata = {}
[…]

### 2018-12-11 code/figure_generation/observation_interaction_histogram.py

@@ -1,189 +1,0 @@
-# # ######### R code to generate data files:
-# galldata=read.csv('../../data/Salix_example/cooccur_interact_galler_salix.csv',header=TRUE,row.names=1)
-# n_pairs=nrow(galldata)
-# unobserved=length(which(galldata$cooccur==0))
-# observed=galldata[which(galldata$cooccur>0),]
-# observed$int_freq=observed$interact/observed$cooccur
-# obs_ints=length(which(observed$interact>0))
-
-# observation_histdata=as.data.frame(tapply(observed$cooccur,observed$cooccur,length))
-# interaction_histdata=as.data.frame(tapply(observed$interact,observed$interact,length))
-# colnames(observation_histdata)=c("cooccurances")
-# colnames(interaction_histdata)=c("interactions")
-
-# write.table(observation_histdata,file='../../data/Salix_example/Salix_Galler/nonzero_cooccurances.tsv',sep='\t')
-# write.table(interaction_histdata,file='../../data/Salix_example/Salix_Galler/observed_interactions.tsv',sep='\t')
-
-# pardata=read.csv('../../data/Salix_example/cooccur_interact_galler_parasit.csv',header=TRUE,row.names=1)
-# n_pairs=nrow(pardata)
-# unobserved=length(which(pardata$cooccur==0))
-# observed=pardata[which(pardata$cooccur>0),]
-# observed$int_freq=observed$interact/observed$cooccur
-# obs_ints=length(which(observed$interact>0))
-
-# observation_histdata=as.data.frame(tapply(observed$cooccur,observed$cooccur,length))
-# interaction_histdata=as.data.frame(tapply(observed$interact,observed$interact,length))
-# colnames(observation_histdata)=c("cooccurances")
-# colnames(interaction_histdata)=c("interactions")
-
-# write.table(observation_histdata,file='../../data/Salix_example/Galler_Parasitoid/nonzero_cooccurances.tsv',sep='\t')
-# write.table(interaction_histdata,file='../../data/Salix_example/Galler_Parasitoid/observed_interactions.tsv',sep='\t')
-
-import sys
-import math
-import random
-from decimal import *
-import numpy as np
-
-#Pygrace libraries
-from PyGrace.grace import Grace
[…]

### 2018-12-11 code/figure_generation/pdf_and_cdf_combined.py

@@ -1,246 +1,0 @@
-# ###### R code to generate data files:
-# Getting distributions:
-# xdata=matrix(ncol=1001,nrow=12)
-# ydata=matrix(ncol=1001,nrow=12)
-# MLEs=matrix(ncol=4,nrow=12)
-# ns=as.vector(c(0,5,10,15,20,25,50,100,150,200,300,374))
-# for(i in 1:length(ns)){
-#   n=ns[i]
-#   print(n)
-#   dist=calculate_distribution(calculate_parameters(sg_int_probs,n,0))
-#   x=seq(-5,5,length=1000)*sqrt(dist[[2]])+dist[[1]]
-#   hx=dnorm(x,dist[[1]],sqrt(dist[[2]]))
-#   xdata[i,]=c(n,x)
-#   ydata[i,]=c(n,hx)
-
-#   MLE=calculate_mean_MLE(sg_int_probs,n,0)
-#   interval=credible_interval(calculate_parameters(sg_int_probs,n,0),0.025,0.975)
-#   MLEs[i,]=c(n,MLE,interval)
-
-# }
-
-# # Data are along rows for pythonic convenience
-# colnames(xdata)=c("N",seq(1,1000))
-# colnames(ydata)=c("N",seq(1,1000))
-# colnames(MLEs)=c("N","MLE","lower","upper")
-
-# write.table(xdata,file='../../data/Salix_example/Zillis/Salix_Galler/distfigure_xvals.tsv',sep='\t')
-# write.table(ydata,file='../../data/Salix_example/Zillis/Salix_Galler/distfigure_yvals.tsv',sep='\t')
-# write.table(MLEs,file='../../data/Salix_example/Zillis/Salix_Galler/distfigure_MLEs.tsv',sep='\t')
-
-# xdata=matrix(ncol=1001,nrow=12)
-# ydata=matrix(ncol=1001,nrow=12)
-# MLEs=matrix(ncol=4,nrow=12)
-# ns=as.vector(c(0,5,10,15,20,25,50,100,150,200,300,374))
-# for(i in 1:length(ns)){
-#   n=ns[i]
-#   dist=calculate_distribution(calculate_parameters(gp_int_probs,n,0))
-#   x=seq(-5,5,length=1000)*sqrt(dist[[2]])+dist[[1]]
-#   hx=dnorm(x,dist[[1]],sqrt(dist[[2]]))
-#   xdata[i,]=c(n,x)
[…]

### 2018-12-11 code/figure_generation/pdfs_and_N.py

@@ -1,239 +1,0 @@
-# ###### R code to generate data files:
-# Getting distributions:
-# xdata=matrix(ncol=1001,nrow=12)
-# ydata=matrix(ncol=1001,nrow=12)
-# MLEs=matrix(ncol=4,nrow=12)
-# ns=as.vector(c(0,5,10,15,20,25,50,100,150,200,300,374))
-# for(i in 1:length(ns)){
-#   n=ns[i]
-#   print(n)
-#   dist=calculate_distribution(calculate_parameters(sg_int_probs,n,0))
-#   x=seq(-5,5,length=1000)*sqrt(dist[[2]])+dist[[1]]
-#   hx=dnorm(x,dist[[1]],sqrt(dist[[2]]))
-#   xdata[i,]=c(n,x)
-#   ydata[i,]=c(n,hx)
-
-#   MLE=calculate_mean_MLE(sg_int_probs,n,0)
-#   interval=credible_interval(calculate_parameters(sg_int_probs,n,0),0.025,0.975)
-#   MLEs[i,]=c(n,MLE,interval)
-
-# }
-
-# # Data are along rows for pythonic convenience
-# colnames(xdata)=c("N",seq(1,1000))
-# colnames(ydata)=c("N",seq(1,1000))
-# colnames(MLEs)=c("N","MLE","lower","upper")
-
-# write.table(xdata,file='../../data/Salix_example/Zillis/Salix_Galler/distfigure_xvals.tsv',sep='\t')
-# write.table(ydata,file='../../data/Salix_example/Zillis/Salix_Galler/distfigure_yvals.tsv',sep='\t')
-# write.table(MLEs,file='../../data/Salix_example/Zillis/Salix_Galler/distfigure_MLEs.tsv',sep='\t')
-
-# xdata=matrix(ncol=1001,nrow=12)
-# ydata=matrix(ncol=1001,nrow=12)
-# MLEs=matrix(ncol=4,nrow=12)
-# ns=as.vector(c(0,5,10,15,20,25,50,100,150,200,300,374))
-# for(i in 1:length(ns)){
-#   n=ns[i]
-#   dist=calculate_distribution(calculate_parameters(gp_int_probs,n,0))
-#   x=seq(-5,5,length=1000)*sqrt(dist[[2]])+dist[[1]]
-#   hx=dnorm(x,dist[[1]],sqrt(dist[[2]]))
-#   xdata[i,]=c(n,x)
[…]

### 2018-12-11 code/figure_generation/posterior_property_dotplot.py

@@ -1,229 +1,0 @@
-import sys
-import math
-import random
-from decimal import *
-import numpy as np
-
-#Pygrace libraries
-from PyGrace.grace import Grace
-from PyGrace.colors import RandomColorScheme, MarkovChainColorScheme, ColorBrewerScheme
-from PyGrace.dataset import SYMBOLS
-from PyGrace.Extensions.panel import NetworkPanel,Panel,MultiPanelGrace
-from PyGrace.drawing_objects import DrawText, DrawLine, DrawBox
-from PyGrace.axis import LINEAR_SCALE, LOGARITHMIC_SCALE
-from PyGrace.Extensions.network import Network
-
-from PyGrace.Extensions.distribution import CDFGraph, PDFGraph
-from PyGrace.Extensions.latex_string import LatexString, CONVERT
-from PyGrace.Extensions.colorbar import SolidRectangle, ColorBar
-from PyGrace.Styles.el import ElGraph, ElLinColorBar, ElLogColorBar
-
-colors=ColorBrewerScheme('Blues')  # The blue is very beautiful but maybe harder to see.
-colors.add_color(130,20,20,'red')
-# colors.add_color(120,120,120,'grey')
-
-obsvals={'SG':{'C':0.028,'LS':2.71,'LG':1.47,'NODF':0.5600535},
-'GP':{'C':0.078,'LS':9.99,'LG':7.45,'NODF':6.853653}}
-
-
-def read_summary_file(filename):
-  whiskers={0.5:[],0.6:[],0.7:[],0.8:[],0.9:[],0.95:[],0.99:[]}
-  obs={0.5:[],0.6:[],0.7:[],0.8:[],0.9:[],0.95:[],0.99:[]}
-  pointdict={}
-  f=open(filename,'r')
-  for line in f:
-    if line.split()[0]!='Web':
-      proportion=float(line.split()[1]) # Proportion of links observed
-      obs_C=float(line.split()[2]) # C in the full posterior web
-      sample_mean=float(line.split()[3]) # Mean C in the detection filter webs
-      sample_SD=float(line.split()[4])
-      sample_SE=sample_SD/10 # SD/sqrt(100 filter webs)
-      # CI is +- 1.96SE
-      if proportion not in pointdict:
-        pointdict[proportion]=[(obs_C,sample_mean,sample_SD)]
-      else:
-        pointdict[proportion].append((obs_C,sample_mean,sample_SD))
[…]

### 2018-12-11 code/figure_generation/posterior_property_plot.py

@@ -1,173 +1,0 @@
-import sys
-import math
-import random
-from decimal import *
-import numpy as np
-
-#Pygrace libraries
-from PyGrace.grace import Grace
-from PyGrace.colors import RandomColorScheme, MarkovChainColorScheme, ColorBrewerScheme
-from PyGrace.dataset import SYMBOLS
-from PyGrace.Extensions.panel import NetworkPanel,Panel,MultiPanelGrace
-from PyGrace.drawing_objects import DrawText, DrawLine, DrawBox
-from PyGrace.axis import LINEAR_SCALE, LOGARITHMIC_SCALE
-from PyGrace.Extensions.network import Network
-
-from PyGrace.Extensions.distribution import CDFGraph, PDFGraph
-from PyGrace.Extensions.latex_string import LatexString, CONVERT
-from PyGrace.Extensions.colorbar import SolidRectangle, ColorBar
-from PyGrace.Styles.el import ElGraph, ElLinColorBar, ElLogColorBar
-
-colors=ColorBrewerScheme('Blues')  # The blue is very beautiful but maybe harder to see.
-colors.add_color(130,20,20,'red')
-# colors.add_color(120,120,120,'grey')
-
-def read_summary_file(filename):
-  pointdict={}
-  f=open(filename,'r')
-  for line in f:
-    if line.split()[0]!='Web':
-      proportion=float(line.split()[1]) # Proportion of links observed
-      obs_C=float(line.split()[2]) # C in the full posterior web
-      sample_mean=float(line.split()[3]) # Mean C in the detection filter webs
-      sample_SD=float(line.split()[4])
-      sample_SE=sample_SD/10 # SD/sqrt(100 filter webs)
-      # CI is +- 1.96SE
-      if proportion not in pointdict:
-        pointdict[proportion]=[(obs_C,sample_mean,sample_SD)]
-      else:
-        pointdict[proportion].append((obs_C,sample_mean,sample_SD))
-  f.close()
-  return pointdict
-
-def format_graph(graph,prop,nettype):
-  graph.yaxis.bar.linewidth=1
-  graph.xaxis.bar.linewidth=1
-  graph.frame.linewidth=1
-
-  if prop=='C':
-    if nettype=='SG':
-      graph.world.xmin=0.52
-      graph.world.ymin=0.20
-      graph.world.xmax=0.575
[…]

### 2018-12-11 code/figure_generation/samples_for_thresholds.py

@@ -1,272 +1,0 @@
-# ######## R code to generate data files:
-# % Getting cdfs:
-# pars=calculate_parameters(sg_int_probs,0,0)
-# n=seq(0,2000,1)
-
-# CDFs=matrix(nrow=3,ncol=2002)
-# colnames(CDFs)=c("Threshold",n)
-# r=1
-# for(threshold in c(0.1,0.05,0.01)){
-#     cdf=pbeta(threshold,shape1=pars[[1]],shape2=pars[[2]]+n)
-#     CDFs[r,1]=threshold
-#     CDFs[r,2:2002]=cdf
-#     print(r)
-#     r=r+1
-# }
-
-
-# samples=matrix(nrow=9,ncol=3)
-# colnames(samples)=c("Threshold","Confidence","Samples")
-# r=1
-# for(threshold in c(0.1,0.05,0.01)){
-#   for(confidence in c(0.9,0.95,0.975)){
-#     n_obs=samples_for_threshold(threshold,confidence,pars)
-#     samples[r,1]=threshold
-#     samples[r,2]=confidence
-#     samples[r,3]=n_obs
-#     print(r)
-#     r=r+1
-#   }
-# }
-
-# write.table(samples,file='../../data/Salix_example/Zillis/Salix_Galler/samples_for_threshold.tsv',sep='\t')
-# write.table(CDFs,file='../../data/Salix_example/Zillis/Salix_Galler/samplefigure.tsv',sep='\t')
-# # write.table(samples,file='../data/Salix_example/Salix_Galler/samples_for_threshold.tsv',sep='\t')
-# # write.table(CDFs,file='../data/Salix_example/Salix_Galler/samplefigure.tsv',sep='\t')
-
-
-# # Galler-parasitoid stuff
-# ######### R code to generate data files:
-# # % Getting cdfs:
-# gp_pars=calculate_parameters(gp_int_probs,0,0)
-# n=seq(0,500,1)
-
-# gp_CDFs=matrix(nrow=3,ncol=502)
-# colnames(gp_CDFs)=c("Threshold",n)
-# r=1
-# for(threshold in c(0.1,0.05,0.01)){
-#     cdf=pbeta(threshold,shape1=gp_pars[[1]],shape2=gp_pars[[2]]+n)
-#     gp_CDFs[r,1]=threshold
-#     gp_CDFs[r,2:502]=cdf
-#     print(r)
-#     r=r+1
-#   }
-
-
-
[…]

### 2018-12-11 code/figure_generation/simulation_summary_fig.py

@@ -1,140 +1,0 @@
-import sys
-import math
-import random
-from decimal import *
-import numpy as np
-
-#Pygrace libraries
-from PyGrace.grace import Grace
-from PyGrace.colors import RandomColorScheme, MarkovChainColorScheme, ColorBrewerScheme
-from PyGrace.dataset import SYMBOLS
-from PyGrace.Extensions.panel import NetworkPanel,Panel,MultiPanelGrace
-from PyGrace.drawing_objects import DrawText, DrawLine, DrawBox
-from PyGrace.axis import LINEAR_SCALE, LOGARITHMIC_SCALE
-from PyGrace.Extensions.network import Network
-
-from PyGrace.Extensions.distribution import CDFGraph, PDFGraph
-from PyGrace.Extensions.latex_string import LatexString, CONVERT
-from PyGrace.Extensions.colorbar import SolidRectangle, ColorBar
-from PyGrace.Styles.el import ElGraph, ElLinColorBar, ElLogColorBar
-
-colors=ColorBrewerScheme('RdYlBu')  # The blue is very beautiful but maybe harder to see.
-colors.add_color(130,20,20,'red')
-# colors.add_color(120,120,120,'grey')
-
-def read_property_lists(propfile):
-  prop_dict={"N_plants":[],"N_gallers":[],"C":[],"L_per_plant":[],"L_per_galler":[],"NODF":[]}
-  f=open(propfile,'r')
-  for line in f:
-    if line.split()[0] not in ['"N_plants"','"L_per_plant"']:
-      if len(line.split())==7:
-        prop_dict["N_plants"].append(float(line.split()[1]))
-        prop_dict["N_gallers"].append(float(line.split()[2]))
-        prop_dict["C"].append((float(line.split()[3])))
-      else:
-        prop_dict["N_plants"].append(50)
-        prop_dict["N_gallers"].append(50)
-        prop_dict["C"].append(0.1)
-      prop_dict["L_per_plant"].append(float(line.split()[-3]))
-      prop_dict["L_per_galler"].append(float(line.split()[-2]))
-      prop_dict["NODF"].append(float(line.split()[-1]))
-
-  mean_dict={}
-  for prop in prop_dict:
-    mean_dict[prop]=(np.mean(prop_dict[prop]),np.std(prop_dict[prop]))
-
-
-  return mean_dict
-
-def configure_yaxes(prop,graph):
[…]

### 2018-12-11 code/figure_generation/upper_CI_after_DG.py

@@ -1,84 +1,0 @@
-# Data generated by manuscript/figure_binomial.R
-
-import sys
-import math
-import random
-from decimal import *
-import numpy as np
-
-#Pygrace libraries
-from PyGrace.grace import Grace
-from PyGrace.colors import RandomColorScheme, MarkovChainColorScheme, ColorBrewerScheme
-from PyGrace.dataset import SYMBOLS
-from PyGrace.Extensions.panel import NetworkPanel,Panel,MultiPanelGrace
-from PyGrace.drawing_objects import DrawText, DrawLine, DrawBox
-from PyGrace.axis import LINEAR_SCALE, LOGARITHMIC_SCALE
-from PyGrace.Extensions.network import Network
-
-from PyGrace.Extensions.distribution import CDFGraph, PDFGraph
-from PyGrace.Extensions.latex_string import LatexString, CONVERT
-from PyGrace.Extensions.colorbar import SolidRectangle, ColorBar
-from PyGrace.Styles.el import ElGraph, ElLinColorBar, ElLogColorBar
-
-colors=ColorBrewerScheme('Spectral')  # The blue is very beautiful but maybe harder to see.
-# colors.add_color(120,120,120,'grey')
-
-def read_Rfiles(filename):
-  dataset=[]
-
-  f=open(filename,'r')
-  for line in f:
-    if line.split()[0]!='"method"':
-      n=int(line.split()[3])
-      upper=float(line.split()[-1])
-      dataset.append((n,upper))
-  f.close()
-  return dataset
-
-def format_graph(graph):
-  graph.yaxis.bar.linewidth=1
-  graph.xaxis.bar.linewidth=1
-  graph.frame.linewidth=1
-  graph.world.xmin=0
-  graph.world.xmax=40
-  graph.world.ymin=-0
-  graph.world.ymax=1
-
-  graph.yaxis.tick.configure(major=.20,onoff='on',minor_ticks=1,major_size=.5,minor_size=.3,place='normal',major_linewidth=1,minor_linewidth=1)
-  graph.yaxis.ticklabel.configure(char_size=.75,format='decimal',prec=1)
-
-  graph.xaxis.tick.configure(major=10,onoff='on',minor_ticks=1,major_size=.5,place='normal',minor_size=.3,major_linewidth=1,minor_linewidth=1)
-  graph.xaxis.ticklabel.configure(char_size=.75,format='decimal',prec=0)
-
[…]

### 2018-12-11 code/Zillis_prior/calculate_NODF.R
updated the SI summary properties fig

@@ -15,7 +15,7 @@ site="Zillis"
     print(webtype)
     props<-c(0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9)
     # props<-c(0.5,0.6,0.7,0.8,0.9,0.95,0.99)
-    nesttable<-matrix(nrow=700,ncol=5)
+    nesttable<-matrix(nrow=900,ncol=5)
     colnames(nesttable)<-c("Web","Proportion","Obs_NODF","Sample_mean","Sample_SD")
     k<-1      
     for(i in 1:100){
@@ -27,7 +27,7 @@ site="Zillis"
       web<-as_adjacency_matrix(G,type="both",names=TRUE,sparse=FALSE)
       NODF<-nestednodf(web,order=TRUE,weighted=FALSE,wbinary=FALSE)$statistic["NODF"]
       # Extract relevant filter webs
-      for(j in 1:7){
+      for(j in 1:length(props)){
         filterwebs<-as.character(list.files(path=paste0(propdir,props[j],sep=''),full.names=TRUE,pattern=paste0('P',i,'_',site,'_',sep='')))
         templist<-matrix(nrow=100,ncol=1)
         # Calculate mean and SD for NODFs

### 2018-12-11 code/calculate_NODF.R

@@ -1,7 +1,7 @@
 library(vegan)
 library(igraph)
 
-for(webtype in c("SG","GP")){
+for(webtype in c("GP","SG")){
   if(webtype=="SG"){
   path<-"../data/randomised_webs/posterior/"
   propdir<-"../data/randomised_webs/detection_filter/"
@@ -10,8 +10,9 @@ for(webtype in c("SG","GP")){
   propdir<-"../data/randomised_webs/gp_detection_filter/"
   }
   print(webtype)
-  props<-c(0.5,0.6,0.7,0.8,0.9,0.95,0.99)
-  nesttable<-matrix(nrow=700,ncol=5)
+  props<-c(0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9)
+  # props<-c(0.8,0.9)
+  nesttable<-matrix(nrow=900,ncol=5)
   colnames(nesttable)<-c("Web","Proportion","Obs_NODF","Sample_mean","Sample_SD")
   k<-1      
   for(i in 1:100){
@@ -23,7 +24,7 @@ for(webtype in c("SG","GP")){
     web<-as_adjacency_matrix(G,type="both",names=TRUE,sparse=FALSE)
     NODF<-nestednodf(web,order=TRUE,weighted=FALSE,wbinary=FALSE)$statistic["NODF"]
     # Extract relevant filter webs
-    for(j in 1:7){
+    for(j in 1:length(props)){
       filterwebs<-as.character(list.files(path=paste0(propdir,props[j],sep=''),full.names=TRUE,pattern=paste0('P',i,'_',sep='')))
       templist<-matrix(nrow=100,ncol=1)
       # Calculate mean and SD for NODFs

### 2018-12-11 code/calculate_sim_network_properties.py

@@ -95,14 +95,14 @@ def main():
 
   for nettype in ['SG','GP']:
     # Starting with C
-    summary_dict={'C':{0.5:{},0.6:{},0.7:{},0.8:{},0.9:{},0.95:{},0.99:{}},
-    'LS':{0.5:{},0.6:{},0.7:{},0.8:{},0.9:{},0.95:{},0.99:{}},
-    'LP':{0.5:{},0.6:{},0.7:{},0.8:{},0.9:{},0.95:{},0.99:{}}  }
+    summary_dict={'C':{0.1:{},0.2:{},0.3:{},0.4:{},0.5:{},0.6:{},0.7:{},0.8:{},0.9:{}},
+    'LS':{0.1:{},0.2:{},0.3:{},0.4:{},0.5:{},0.6:{},0.7:{},0.8:{},0.9:{}},
+    'LP':{0.1:{},0.2:{},0.3:{},0.4:{},0.5:{},0.6:{},0.7:{},0.8:{},0.9:{}}  }
 
     for post_number in range(1,101):
       gallers,salixes,links=web_reader(webdir,0,post_number,0,nettype)
       obsC,obsLS,obsLP=calculate_original_properties(gallers,salixes,links)
-      for proportion in [0.5,0.6,0.7,0.8,0.9,0.95,0.99]:
+      for proportion in [0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9]:
       # for proportion in [0.9,0.95,0.99]:
         filtered_C=[]
         filtered_LS=[]

### 2018-12-12 code/figure_generation/heatmap.py
updated figures

@@ -1,0 +1,153 @@
+
+# This example demonstrates how to use a color plot.
+#
+# One important feature of color plots is that drawing objects in
+# XMGrace are plotted above the frame of a graph.  As a result, we use
+# the Grace.clone_graph method to copy the frame of the graph and make
+# things look pretty.
+#
+# Another important feature of color plots is that specifying a
+# particular world coordinate can automatically place drawing objects
+# outside of the domain of the graph.
+# Graph.remove_extraworld_drawing_objects fixes this problem by
+# removing all of the drawing objects that appear in the world
+# coordinates and are out of bounds.
+#
+# It also demonstrates how to use a PyGrace.Style to format figures in
+# a customized format
+
+#import math
+#from PyGrace.Extensions.panel import Panel,MultiPanelGrace
+
+## To run use:
+# python heatmap.py ../../data/Salix_example/cooccur_interact_galler_salix galler salix
+
+import random
+import sys
+import os
+
+from PyGrace.grace import Grace as Plot
+from PyGrace.Extensions.colorbar import SolidRectangle, ColorBar
+from PyGrace.colors import ColorBrewerScheme
+from PyGrace.axis import LINEAR_SCALE, LOGARITHMIC_SCALE
+from PyGrace.drawing_objects import DrawBox, DrawText, DrawLine
+
+from PyGrace.Styles.el import ElGraph, ElLogColorBar, ElLinColorBar
+
+
+#------------------------------------------------------------------------------
+# make a nice figure
+#------------------------------------------------------------------------------
+# get the data (as specified in the command line)
+readfile = sys.argv[1]
+filename = readfile+'.csv'
+troph1 = sys.argv[2]
+tr1id = troph1+'_ID'
+troph2 = sys.argv[3]
+tr2id = troph2+'_ID'
+infile = open(filename)
+header=infile.readline().strip().split(',')
+
+
+# read in the data into something we can manipulate easily
+data = []
+for line in infile:
+	sline = line.strip().split(',')
+	pt = dict(zip(header,[i for i in sline]))
+	data.append(pt)
+infile.close()
+# print data[0:7]
+
+ndata = {}
[…]

### 2018-12-12 code/figure_generation/observation_interaction_histogram.py

@@ -1,0 +1,189 @@
+# # ######### R code to generate data files:
+# galldata=read.csv('../../data/Salix_example/cooccur_interact_galler_salix.csv',header=TRUE,row.names=1)
+# n_pairs=nrow(galldata)
+# unobserved=length(which(galldata$cooccur==0))
+# observed=galldata[which(galldata$cooccur>0),]
+# observed$int_freq=observed$interact/observed$cooccur
+# obs_ints=length(which(observed$interact>0))
+
+# observation_histdata=as.data.frame(tapply(observed$cooccur,observed$cooccur,length))
+# interaction_histdata=as.data.frame(tapply(observed$interact,observed$interact,length))
+# colnames(observation_histdata)=c("cooccurances")
+# colnames(interaction_histdata)=c("interactions")
+
+# write.table(observation_histdata,file='../../data/Salix_example/Salix_Galler/nonzero_cooccurances.tsv',sep='\t')
+# write.table(interaction_histdata,file='../../data/Salix_example/Salix_Galler/observed_interactions.tsv',sep='\t')
+
+# pardata=read.csv('../../data/Salix_example/cooccur_interact_galler_parasit.csv',header=TRUE,row.names=1)
+# n_pairs=nrow(pardata)
+# unobserved=length(which(pardata$cooccur==0))
+# observed=pardata[which(pardata$cooccur>0),]
+# observed$int_freq=observed$interact/observed$cooccur
+# obs_ints=length(which(observed$interact>0))
+
+# observation_histdata=as.data.frame(tapply(observed$cooccur,observed$cooccur,length))
+# interaction_histdata=as.data.frame(tapply(observed$interact,observed$interact,length))
+# colnames(observation_histdata)=c("cooccurances")
+# colnames(interaction_histdata)=c("interactions")
+
+# write.table(observation_histdata,file='../../data/Salix_example/Galler_Parasitoid/nonzero_cooccurances.tsv',sep='\t')
+# write.table(interaction_histdata,file='../../data/Salix_example/Galler_Parasitoid/observed_interactions.tsv',sep='\t')
+
+import sys
+import math
+import random
+from decimal import *
+import numpy as np
+
+#Pygrace libraries
+from PyGrace.grace import Grace
[…]

### 2018-12-12 code/figure_generation/pdf_and_cdf_combined.py

@@ -1,0 +1,246 @@
+# ###### R code to generate data files:
+# Getting distributions:
+# xdata=matrix(ncol=1001,nrow=12)
+# ydata=matrix(ncol=1001,nrow=12)
+# MLEs=matrix(ncol=4,nrow=12)
+# ns=as.vector(c(0,5,10,15,20,25,50,100,150,200,300,374))
+# for(i in 1:length(ns)){
+#   n=ns[i]
+#   print(n)
+#   dist=calculate_distribution(calculate_parameters(sg_int_probs,n,0))
+#   x=seq(-5,5,length=1000)*sqrt(dist[[2]])+dist[[1]]
+#   hx=dnorm(x,dist[[1]],sqrt(dist[[2]]))
+#   xdata[i,]=c(n,x)
+#   ydata[i,]=c(n,hx)
+
+#   MLE=calculate_mean_MLE(sg_int_probs,n,0)
+#   interval=credible_interval(calculate_parameters(sg_int_probs,n,0),0.025,0.975)
+#   MLEs[i,]=c(n,MLE,interval)
+
+# }
+
+# # Data are along rows for pythonic convenience
+# colnames(xdata)=c("N",seq(1,1000))
+# colnames(ydata)=c("N",seq(1,1000))
+# colnames(MLEs)=c("N","MLE","lower","upper")
+
+# write.table(xdata,file='../../data/Salix_example/Zillis/Salix_Galler/distfigure_xvals.tsv',sep='\t')
+# write.table(ydata,file='../../data/Salix_example/Zillis/Salix_Galler/distfigure_yvals.tsv',sep='\t')
+# write.table(MLEs,file='../../data/Salix_example/Zillis/Salix_Galler/distfigure_MLEs.tsv',sep='\t')
+
+# xdata=matrix(ncol=1001,nrow=12)
+# ydata=matrix(ncol=1001,nrow=12)
+# MLEs=matrix(ncol=4,nrow=12)
+# ns=as.vector(c(0,5,10,15,20,25,50,100,150,200,300,374))
+# for(i in 1:length(ns)){
+#   n=ns[i]
+#   dist=calculate_distribution(calculate_parameters(gp_int_probs,n,0))
+#   x=seq(-5,5,length=1000)*sqrt(dist[[2]])+dist[[1]]
+#   hx=dnorm(x,dist[[1]],sqrt(dist[[2]]))
+#   xdata[i,]=c(n,x)
[…]

### 2018-12-12 code/figure_generation/pdfs_and_N.py

@@ -1,0 +1,239 @@
+# ###### R code to generate data files:
+# Getting distributions:
+# xdata=matrix(ncol=1001,nrow=12)
+# ydata=matrix(ncol=1001,nrow=12)
+# MLEs=matrix(ncol=4,nrow=12)
+# ns=as.vector(c(0,5,10,15,20,25,50,100,150,200,300,374))
+# for(i in 1:length(ns)){
+#   n=ns[i]
+#   print(n)
+#   dist=calculate_distribution(calculate_parameters(sg_int_probs,n,0))
+#   x=seq(-5,5,length=1000)*sqrt(dist[[2]])+dist[[1]]
+#   hx=dnorm(x,dist[[1]],sqrt(dist[[2]]))
+#   xdata[i,]=c(n,x)
+#   ydata[i,]=c(n,hx)
+
+#   MLE=calculate_mean_MLE(sg_int_probs,n,0)
+#   interval=credible_interval(calculate_parameters(sg_int_probs,n,0),0.025,0.975)
+#   MLEs[i,]=c(n,MLE,interval)
+
+# }
+
+# # Data are along rows for pythonic convenience
+# colnames(xdata)=c("N",seq(1,1000))
+# colnames(ydata)=c("N",seq(1,1000))
+# colnames(MLEs)=c("N","MLE","lower","upper")
+
+# write.table(xdata,file='../../data/Salix_example/Zillis/Salix_Galler/distfigure_xvals.tsv',sep='\t')
+# write.table(ydata,file='../../data/Salix_example/Zillis/Salix_Galler/distfigure_yvals.tsv',sep='\t')
+# write.table(MLEs,file='../../data/Salix_example/Zillis/Salix_Galler/distfigure_MLEs.tsv',sep='\t')
+
+# xdata=matrix(ncol=1001,nrow=12)
+# ydata=matrix(ncol=1001,nrow=12)
+# MLEs=matrix(ncol=4,nrow=12)
+# ns=as.vector(c(0,5,10,15,20,25,50,100,150,200,300,374))
+# for(i in 1:length(ns)){
+#   n=ns[i]
+#   dist=calculate_distribution(calculate_parameters(gp_int_probs,n,0))
+#   x=seq(-5,5,length=1000)*sqrt(dist[[2]])+dist[[1]]
+#   hx=dnorm(x,dist[[1]],sqrt(dist[[2]]))
+#   xdata[i,]=c(n,x)
[…]

### 2018-12-12 code/figure_generation/samples_for_thresholds.py

@@ -1,0 +1,272 @@
+# ######## R code to generate data files:
+# % Getting cdfs:
+# pars=calculate_parameters(sg_int_probs,0,0)
+# n=seq(0,2000,1)
+
+# CDFs=matrix(nrow=3,ncol=2002)
+# colnames(CDFs)=c("Threshold",n)
+# r=1
+# for(threshold in c(0.1,0.05,0.01)){
+#     cdf=pbeta(threshold,shape1=pars[[1]],shape2=pars[[2]]+n)
+#     CDFs[r,1]=threshold
+#     CDFs[r,2:2002]=cdf
+#     print(r)
+#     r=r+1
+# }
+
+
+# samples=matrix(nrow=9,ncol=3)
+# colnames(samples)=c("Threshold","Confidence","Samples")
+# r=1
+# for(threshold in c(0.1,0.05,0.01)){
+#   for(confidence in c(0.9,0.95,0.975)){
+#     n_obs=samples_for_threshold(threshold,confidence,pars)
+#     samples[r,1]=threshold
+#     samples[r,2]=confidence
+#     samples[r,3]=n_obs
+#     print(r)
+#     r=r+1
+#   }
+# }
+
+# write.table(samples,file='../../data/Salix_example/Zillis/Salix_Galler/samples_for_threshold.tsv',sep='\t')
+# write.table(CDFs,file='../../data/Salix_example/Zillis/Salix_Galler/samplefigure.tsv',sep='\t')
+# # write.table(samples,file='../data/Salix_example/Salix_Galler/samples_for_threshold.tsv',sep='\t')
+# # write.table(CDFs,file='../data/Salix_example/Salix_Galler/samplefigure.tsv',sep='\t')
+
+
+# # Galler-parasitoid stuff
+# ######### R code to generate data files:
+# # % Getting cdfs:
+# gp_pars=calculate_parameters(gp_int_probs,0,0)
+# n=seq(0,500,1)
+
+# gp_CDFs=matrix(nrow=3,ncol=502)
+# colnames(gp_CDFs)=c("Threshold",n)
+# r=1
+# for(threshold in c(0.1,0.05,0.01)){
+#     cdf=pbeta(threshold,shape1=gp_pars[[1]],shape2=gp_pars[[2]]+n)
+#     gp_CDFs[r,1]=threshold
+#     gp_CDFs[r,2:502]=cdf
+#     print(r)
+#     r=r+1
+#   }
+
+
+
[…]

### 2018-12-12 code/figure_generation/simulation_summary_fig.py

@@ -1,0 +1,140 @@
+import sys
+import math
+import random
+from decimal import *
+import numpy as np
+
+#Pygrace libraries
+from PyGrace.grace import Grace
+from PyGrace.colors import RandomColorScheme, MarkovChainColorScheme, ColorBrewerScheme
+from PyGrace.dataset import SYMBOLS
+from PyGrace.Extensions.panel import NetworkPanel,Panel,MultiPanelGrace
+from PyGrace.drawing_objects import DrawText, DrawLine, DrawBox
+from PyGrace.axis import LINEAR_SCALE, LOGARITHMIC_SCALE
+from PyGrace.Extensions.network import Network
+
+from PyGrace.Extensions.distribution import CDFGraph, PDFGraph
+from PyGrace.Extensions.latex_string import LatexString, CONVERT
+from PyGrace.Extensions.colorbar import SolidRectangle, ColorBar
+from PyGrace.Styles.el import ElGraph, ElLinColorBar, ElLogColorBar
+
+colors=ColorBrewerScheme('RdYlBu')  # The blue is very beautiful but maybe harder to see.
+colors.add_color(130,20,20,'red')
+# colors.add_color(120,120,120,'grey')
+
+def read_property_lists(propfile):
+  prop_dict={"N_plants":[],"N_gallers":[],"C":[],"L_per_plant":[],"L_per_galler":[],"NODF":[]}
+  f=open(propfile,'r')
+  for line in f:
+    if line.split()[0] not in ['"N_plants"','"L_per_plant"']:
+      if len(line.split())==7:
+        prop_dict["N_plants"].append(float(line.split()[1]))
+        prop_dict["N_gallers"].append(float(line.split()[2]))
+        prop_dict["C"].append((float(line.split()[3])))
+      else:
+        prop_dict["N_plants"].append(50)
+        prop_dict["N_gallers"].append(50)
+        prop_dict["C"].append(0.1)
+      prop_dict["L_per_plant"].append(float(line.split()[-3]))
+      prop_dict["L_per_galler"].append(float(line.split()[-2]))
+      prop_dict["NODF"].append(float(line.split()[-1]))
+
+  mean_dict={}
+  for prop in prop_dict:
+    mean_dict[prop]=(np.mean(prop_dict[prop]),np.std(prop_dict[prop]))
+
+
+  return mean_dict
+
+def configure_yaxes(prop,graph):
[…]

### 2018-12-12 code/figure_generation/upper_CI_after_DG.py

@@ -1,0 +1,84 @@
+# Data generated by manuscript/figure_binomial.R
+
+import sys
+import math
+import random
+from decimal import *
+import numpy as np
+
+#Pygrace libraries
+from PyGrace.grace import Grace
+from PyGrace.colors import RandomColorScheme, MarkovChainColorScheme, ColorBrewerScheme
+from PyGrace.dataset import SYMBOLS
+from PyGrace.Extensions.panel import NetworkPanel,Panel,MultiPanelGrace
+from PyGrace.drawing_objects import DrawText, DrawLine, DrawBox
+from PyGrace.axis import LINEAR_SCALE, LOGARITHMIC_SCALE
+from PyGrace.Extensions.network import Network
+
+from PyGrace.Extensions.distribution import CDFGraph, PDFGraph
+from PyGrace.Extensions.latex_string import LatexString, CONVERT
+from PyGrace.Extensions.colorbar import SolidRectangle, ColorBar
+from PyGrace.Styles.el import ElGraph, ElLinColorBar, ElLogColorBar
+
+colors=ColorBrewerScheme('Spectral')  # The blue is very beautiful but maybe harder to see.
+# colors.add_color(120,120,120,'grey')
+
+def read_Rfiles(filename):
+  dataset=[]
+
+  f=open(filename,'r')
+  for line in f:
+    if line.split()[0]!='"method"':
+      n=int(line.split()[3])
+      upper=float(line.split()[-1])
+      dataset.append((n,upper))
+  f.close()
+  return dataset
+
+def format_graph(graph):
+  graph.yaxis.bar.linewidth=1
+  graph.xaxis.bar.linewidth=1
+  graph.frame.linewidth=1
+  graph.world.xmin=0
+  graph.world.xmax=40
+  graph.world.ymin=-0
+  graph.world.ymax=1
+
+  graph.yaxis.tick.configure(major=.20,onoff='on',minor_ticks=1,major_size=.5,minor_size=.3,place='normal',major_linewidth=1,minor_linewidth=1)
+  graph.yaxis.ticklabel.configure(char_size=.75,format='decimal',prec=1)
+
+  graph.xaxis.tick.configure(major=10,onoff='on',minor_ticks=1,major_size=.5,place='normal',minor_size=.3,major_linewidth=1,minor_linewidth=1)
+  graph.xaxis.ticklabel.configure(char_size=.75,format='decimal',prec=0)
+
[…]

### 2019-01-10 manuscript/reply_to_reviewers.tex
Tomas comments to reply letter

@@
 	\textbf{R:} We appreciate the thoughtful feedback by the four referees.
-We take particular note of the comments regarding the structure and grounding of our introduction and have worked to address this.
-Reviewer 2's comments take a different view of the purpose and scope of the manuscript than the other reviewers; we respect their ideas but feel that some are beyond the scope of the present manuscript.
+We take particular note of the comments regarding the structure and grounding of our introduction and have worked to address them.
+
+	Reviewer 2 takes a different view of the purpose and scope of the manuscript from that of the other reviewers.
+We respect his/her ideas but feel that some are beyond the scope of the present manuscript.
 In particular, we do not feel that a full simulation study is necessary given the simplicity of our framework.
 We emphasize that we are not introducing a software package (although we do provide simple code to aid those who are new to the field), nor are we introducing an entirely new framework (as the other Reviewers point out, many components of our approach have been touched on by previous work).
-The novelty and impact of our work lies in connecting a Bayesian statistical approach to the problem of limited and uneven sampling (driven by difference in species abundances, detectabilities, constrained time and budgets, etc.) and, we hope, in making this method more accessible to those without extensive statistical or modelling experience.
+Thus, the novelty and impact of our work explicitly lies in connecting a Bayesian statistical approach to the problem of limited and uneven sampling of networks (driven by difference in species abundances, detectabilities, constrained time and budgets, etc.) and, we hope, in making this method more accessible to those without extensive statistical or modelling experience.
+Please note that Reviewer 3 identified this need explicitly.
+	% Tomas has a line break here, I'm not sure.
 	Because of the difference between Reviewer 2 and the other Reviewers, we have opted to prioritise the majority view and focused first on comments by Reviewers 1, 3, and 4.
-We hope that, in the course of these revisions, we have at least partially addressed Reviewer 2's concerns as well.
-	\smallskip
-	We have taken Reviewer 1's suggestion that we expand upon the different types of priors available and reasons for choosing one over the other.
+However, we hope and trust that, in the course of these revisions, we have at least partially addressed Reviewer 2's concerns as well.
+
+	As a key point of departure for our revision, we have taken Reviewer 1's suggestion that we expand upon the different types of priors available and reasons for choosing one over the other.
 We also now offer a brief discussion about concerns over the subjectivity of prior selection.
@@
 We hope that this will encourage empiricists to explicitly use their system-specific knowledge to create reasonable priors, as likely already occurs subconsciously (as in the designation of "forbidden links").
-We hope that our revision more clearly frames the importance of uncertainty in ecological networks and positions a simple Bayesian approach as a partial solution (together with high-quality sampling, of course).
-	\smallskip
+
+	Overall, we hope that our revision more clearly frames the importance of uncertainty in ecological networks and positions a simple Bayesian approach as a partial solution (together with high-quality sampling, of course).
 	We have also added many references to prior work. While the present study is not intended to be a full review of the literature, we certainly do not wish to downplay other workers in the area.
-	\smallskip
 	Finally, several of the Reviewers appeared to believe that we were advocating for reduced sampling effort.
@@
 % ----------------------------------------------------------------------
-{\Large \bf Reply to Reviewer \#1} [[done]]
+{\Large \bf Reply to Reviewer \#1}
 % ---------------------------------------

### 2019-01-11 manuscript/reply_to_reviewers.tex
integrating Tomas' comments to reply

@@
 % ---------------------------------------
+Preamble.
 
-	1. Suggestion to refocus on prior selection [[done]]
+	1. Suggestion to refocus on prior selection
 
@@
 I see the makings of a really nice paper here, and I’m confident the authors will be able to achieve this text revision.
-			\medskip
+
 			At the same time, the paper is clear and very readable. I wholly support the method and I think it is something critical that needs to be adopted by the community. \\
@@
 
-		\textbf{R:} We thank the Reviewer for the suggestion to expand our discussion of prior selection, particularly with regard to approxmimate/empirical Bayes.
-Although we are somewhat space-limited, we have expanded our description of different priors available and why a researcher might choose one over another (lines XX-XX).
-We also touch upon the controversy over using empirical priors (lines XX-XX) although we were unable to find many references addressing this in detail.
-If the Reviewer has particular works in mind, we would be more than happy to include them.
+		\textbf{R:} We thank the Reviewer for his/her positive evaluation, and have done our utmost to reframe and tighten the introduction and framing of the paper.
+In doing so, we have happily adopted the suggestion to expand our discussion of prior selection, particularly with regard to approximate/empirical Bayes.
+Although we are somewhat space-limited, we have expanded our description of the different priors available and why a researcher might choose one over another (section beginning with line 245).
+We also touch upon the controversy over using empirical priors (lines 340-345) although we were unable to find many references addressing this in detail.
 We hope that this expanded description will be a better guide for empiricists who may not be familiar with Bayesian statistics.
-		\medskip
-		We also appreciate the Reviewer's comments on our introduction.
-We feel that understanding the problem of uncertain detection of interactions is important motivation for a reader not already familiar with Bayesian procedures to wade through a larger discussion on priors.
-Therefore we have revised and, hopefully, streamlined our discussion but do not jump straight in to priors.
-We have, however, taken care to introduce our analysis as a worked example (lines XX-XX) and hope that this helps to reduce the conflict between the introduction and our data.
-		\medskip
-		We thank the Reviewer for their compliments and accept their suggestion that we are somewhat overexcited about our approach.
-We have refined the introduction to be more specific about the problem we are attempting to solve.
+
+		In implementing the Reviewer's comments on our introduction, we believe that most readers who are less familiar with Bayesian procedures will need a quick outline of the problem of uncertain detection of interactions in order to be motivated to dive into the larger discussion of priors.
+We stress that our intended target audience is empirical ecologists working on network description who likely have a different skillset than that of the Reviewer.
+We also note that Reviewer 2 found that \emph{``The introduction is particularly pleasant to read and the problem is well stated"}, praise which we would hate to loose.
+Therefore we have revised and streamlined our introduction but still refrain from jumping straight into prior selection.
+We have, however, taken care to introduce our analysis as a worked example (lines 347) and hope that this helps to reduce the conflict between the introduction and our data.
+
+		Overall, we thank the Reviewer for their compliments and accept their suggestion that we are somewhat overexcited about our approach.
+Thus, we have refined the introduction to be more specific about the problem we are attempting to solve.
 We have also expanded our treatment of prior selection and hope that our paper now reads as achieving its goal.
 
-	2. Suggestion to add more literature [[done]]
+	2. Suggestion to add more literature
 
@@
 		\textbf{R:} We thank the Reviewer for their compliments to our introduction and for the literature recommendations.
-We have incorporated these reference as suggested.
-Following comments from other reviewers, we have refined and slightly restructured our introduction in the hope of more clearly establishing the goal of our manuscript ('narrowing our net').
+We have incorporated these references as suggested (including Jordano, 2016 in the sampling section).
+Following comments from other reviewers, we have refined and slightly restructured our introduction in the hope of more clearly establishing the goal of our manuscript.
 We hope that this revised introduction will also meet with the Reviewer's approval.
 
-	3. Suggestion to de-emphasize MLE estimate and get straight to Bayes [[done]]
+	3. Suggestion to de-emphasize MLE estimate and get straight to Bayes
 
@@
 
-		\textbf{R:} The MLE estimate is part of the Bayesian framework as it dictates the shape of the distribution we use.
-We now introduce the MLE formally within this context (lines XX-XX) and take care to be explicit when using it to explore the sample size needed in the absence of prior knowledge later (lines XX-XX).
+		\textbf{R:} The MLE estimate is part of the Bayesian framework as it dictates the shape of the distribution that we use.
+We now introduce the MLE formally within this context (lines 229-231) and take care to be explicit when using it to explore the sample size needed in the absence of prior knowledge later (caption of Figure 3).
 
-		Lines XX-XX:
+		Lines 229-231:
 
@@
 
-		Lines XX-XX:
+		Caption of figure 3:
 
 		\begin{quotation}
-			The number of observed co-occurrences needed to believe that an unobserved interaction cannot occur is very high (about 35; Fig.~\ref{upper_limits}), and most datasets will not include this level of sampling for all pairs of species~\citep{Bartomeus2013}.
+			The number of observed co-occurrences needed to believe that an unobserved interaction cannot occur is very high (about 35; Fig.
+3), and most datasets will not include this level of sampling for all pairs of species~\citep{Bartomeus2013}.
 		\end{quotation}
 
-	4. Suggestion to remove moments of the beta distribution [[done]]
+	4. Suggestion to remove moments of the beta distribution
 
@@
 
-	5. Novelty of the study not clear in current framing [[done]]
+	5. Novelty of the study not clear in current framing
 
@@
 
-	6. Potential contradiction [[done]]
+	6. Potential contradiction
 
@@
 
+\clearpage
+
 % ----------------------------------------------------------------------
 % ---------------------------------------------------------------------
-{\Large \bf Reply to Referee \#2} [[not started]]
+{\Large \bf Reply to Reviewer \#2} [[not started]]
 % ---------------------------------------
 
-	I do not know what to do with this.
+	The Reviewer stated that our manuscript ``tackles a very interesting problem, quantifying the uncertainity of interactions" which he/she rates as ``one of the hottest topics in the field".
+He/she also points out that ``the introduction is particularly pleasant to read" and that we framed the problem well.
+The Reviewer also pointed out a number of weaknesses to the manuscript that we respond to one-by-one.
+In general, we feel that the Reviewer's comments reflect a high degree of statistical expertise; expertise that we do not expect to be shared by the bulk of our intended audience (empirical ecologists assembing new ecological networks).
+We have therefore prioritised comments by this and the other Reviewers that seemed most likely to improve the manuscript for readers who are relatively new to Bayesian analysis over concerns most relevant to a highly knowledgeable reader.
+We hope that our revised manuscript makes this target audience clearer, and that we have addressed the Reviewer's key concerns with our revision.
+
+	1. Lack of references [done]
 
 		\begin{refquote}
-	The paper by A.Cirtwill and colleagues tackles a very interesting problem, quantifying the uncertainity of interactions, using three levels of nested uncertainity.
-The authors proposed a bayesian framework to obtain estimate of the parameters of the model and show the results of their approach on a recent dataset.
-The question of disentangling the true presence/absence of an interaction given a series of observations (replicates) is of primary interest and, seen in this light, the paper is tackling one of the hottest topics in the field.
 
-	The introduction is particularly pleasant to read and the problematic is well stated. However, the paper has also a number of weaknesses that I enumerate in the following :
-
-	1/ lack of references: the fundamental question about predicting interactions given some incertainity has been and is debated in many papers (see the seminal paper by Roger Guimerà and Marta Sales-Pardo, PNAS, 2009).
+			The fundamental question about predicting interactions given some incertainity has been and is debated in many papers (see the seminal paper by Roger Guimer\`{a} and Marta Sales-Pardo, PNAS, 2009).
 Even if the proposed framework is probably not stated in its exact terms in the literature, bridges between existing approaches (beyond Ecology) and the one in the paper would be very welcomed.
@@
 
+		\end{refquote}
+
+		\textbf{R:} This comment echoes the impression of Reviewers 1 (above) and 3 (below) that we do not give adequate attention to previous work.
+As stated above, we have now added many further pointers to previous work, and also been much more explicit regarding whom we try to reach with what message in the current paper.
+
+	2. Non-independence of interactions not accounted for [written, not done]
+
+		\begin{refquote}
 			2/ network oversight: the approach considers that the interactions are independent, which is not the case in real data.
@@
 Despite of this drawback, the proposed method is interesting but at least the authors should add some discussion on the limits of dealing with independent interactions,
+		\end{refquote}
+
+		\textbf{R:} We agree wholeheartedly that ecological interactions are often not independent.
+Indeed, we refer several times to the effect of species' abundances on their probabilities of interacting.
+This effect alone will introduce non-independence in interaction probabilities, as all interactions involving a common species will be more likely than they would be if that species was rare.
+That said, we also agree that we do not explicitly discuss the non-independence of interactions.
+In part, this is by design.
+We explicitly want to keep our mathematical framework quite simple so that it is easily applicable to a wide variety of situations (including those where the nature of non-independence among interactions is not known).
+Nevertheless, to encourage readers to consider non-independence when designing their priors we are happy to take the Reviewer's suggestion and index our variables by ij and add a line noting that the assumption of independent interactions may not hold.
 
@@
 		\begin{quotation}
-			we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig.~\ref{histograms}C).
+			we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig.
+2C).
 While this improves our understanding of the set of species present in the community, it introduces yet more uncertainty into the interaction matrix.
@@
 The detection of any interaction is a stochastic process subject to many levels of uncertainty.
-As a conceptual guide to the factors affecting this process, we describe three nested levels of uncertainty that roughly address the questions: "Could species $i$ and $j$ interact?", "Do they interact?" and "Do we observe the interaction?" (Fig.~\ref{conceptual_fig}).
+As a conceptual guide to the factors affecting this process, we describe three nested levels of uncertainty that roughly address the questions: "Could species $i$ and $j$ interact?", "Do they interact?" and "Do we observe the interaction?" (Fig.
+1).
 		\end{quotation}
@@
 
+    \bibliographystyle{ecol_let} 
+    \bibliography{manual_abbrev} % Abbreviate journal titles.
+
 \end{document}

### 2019-01-11 manuscript/CI_interactions.tex
integrating Tomas' comments to reply

@@
 An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to correctly document interactions than species~\citep{Guimera2009,Poisot2012,Bartomeus2013,Jordano2016,Giron2018,Graham2018}.
-As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Bartomeeus2013,Poisot2016}.
+As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Bartomeus2013,Poisot2016}.
 Efforts in this vein usually take the form of creating model food webs that approximate observed empirical networks~\citep{Allesina2008,Guimera2009,Williams2010,Rohr2016}.
 These models may be based on species traits and/or abundances~\citep{Rohr2016,Weinstein2017,Weinstein2017a,Graham2018} or on simple abstract rules~\citep{Allesina2008,Guimera2009,Williams2010}.
-Such models provide an important ''reality check'' by allowing us to test hypotheses about the factors structuring ecological networks~\citep{Bartomeus2013,Weinstein2017.Weinstein2017a,Graham2018}.
+Such models provide an important ''reality check'' by allowing us to test hypotheses about the factors structuring ecological networks~\citep{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}.
 They can also allow us to estimate the numbers of interactions which have not been observed~\citep{Jordano2016,Weinstein2017a} and predict which unobserved interactions are most likely~\citep{Guimera2009,Bartomeus2013}.
@@
 Moreover, some of the system-specific models described above cannot accommodate species observed only once~\citep{Bartomeus2013,Weinstein2017}.
-As rare species are likely to be observed less frequently~\citep{Bluthgen2010} and may be of particular interest (e.g., when modelling species loss), there is a need for a more widely-applicable framework that includes such rare species.
+As rare species are likely to be observed less frequently~\citep{Bluthgen2006} and may be of particular interest (e.g., when modelling species loss), there is a need for a more widely-applicable framework that includes such rare species.
 
@@
 First, we provide a brief description of the nested levels of uncertainty affecting ecological network construction.
-In the context of this uncertainty, which can be reduced but not eliminated by high-quality sampling (\citealp[see Box 1]{Bartomes2013}), we present our Bayesian framework for combining observed data with a prior expectation of network structure.
+In the context of this uncertainty, which can be reduced but not eliminated by high-quality sampling (\citealp[see Box 1]{Bartomeus2013}), we present our Bayesian framework for combining observed data with a prior expectation of network structure.
 We conclude with a worked example applying this framework to an intensively-sampled host-parasitoid network.
@@
             Both whether species can interact and whether they do interact at a particular place and time have been discussed in the context of "forbidden links"~\citep{Jordano2016}.
-In this framework, all links which are prevented by spatio-temporal uncoupling~\citep{Jordano1987}, physiological constraints~\citep{Jordano1987,More2012}, etc.
-are considered "structural zeros" that cannot be observed~\citep{Jordano2016}.
+In this framework, all links which are prevented by spatio-temporal uncoupling, physiological constraints, etc.
+are considered "structural zeros" that cannot be observed~\citep{Jordano1987,Jordano2016}.
 We conceptually distinguish between physiological constraints and spatio-temporal uncoupling to allow for cases in which a species is introduced to a new habitat, expands its range, or shifts phenology~\citep{Gravel2013}.
@@
 Even long-term interactions can be missed, however, especially if species are difficult to identify or if not all individuals of a species share the interaction~\citep{Wells2013,Cirtwill2016}.
-Parasites, for example, are often concentrated in only a few individuals~\citep{Lagrue2017}.
+Parasites, for example, are often concentrated in only a few individuals~\citep{Lagrue2015}.
 If these infected individuals do not happen to be included in a sample, their interactions will be missed.
@@
 Returning to the example of degree distributions, this approach allows us to use information from abundant and easily-sampled species to predict interaction probabilities for species which were observed only rarely.
-Despite its practicality, empirical Bayes has been criticized for being overly subjective~\citep{Berger2006} and because estimating hyperparameters from data serves as an approximation of some true hyperparameters which remain unknown~\citep{Gelmanblog}.
+Despite its practicality, approximate Bayes has been criticized for being overly subjective~\citep{Berger2006} and because estimating hyperparameters from data serves as an approximation of some true hyperparameters which remain unknown~\citep{Gelmanblog}.
 We therefore encourage researchers to carefully consider whether external data or an appropriate trait model is available before opting for a prior based on some of their own data.
@@
 Thus, any uncertainty in the values of $\lambda$ could bias both the mean and variance of network metrics, giving misleading results (simulated in \emph{Appendix S1}).
-One way to avoid this situation is to calculate the properties of a suite of simulated networks~\citep{Vazquez2005,Guimera209}.
+One way to avoid this situation is to calculate the properties of a suite of simulated networks~\citep{Vazquez2005,Guimera2009}.
 
@@
     Importantly, we can estimate the variance of $\lambda$ as well as the MLE; available methods include the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]).
+The distribution of the MLE for $\lambda$ thus obtained is a key part of the Bayesian distribution for $\lambda$.
     Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true credible interval for the interaction probability $\lambda$ for a pair of species that has been observed co-occurring $n$ times but never interacting ($k = 0$).

### 2019-01-11 code/figure_generation/pdfs_and_N.py
changed N to nij on fig 4

@@ -144,12 +144,14 @@ def format_graph(graph,nettype):
     graph.legend.configure(box_linestyle=0,fill=0,fill_pattern=0,char_size=.75,
       loc=(0.08,35),loctype='world',size=2)
     # graph.add_drawing_object(DrawText,text="N",x=0.665,y=35.5,char_size=.75,just=2,loctype='world')
-    graph.add_drawing_object(DrawText,text="N",x=0.085,y=35.5,char_size=.75,just=2,loctype='world')
+    graph.add_drawing_object(DrawText,text=\
+      LatexString('n\sij'),x=0.085,y=35.5,char_size=.75,just=2,loctype='world')
   elif nettype=='GP':
     graph.legend.configure(box_linestyle=0,fill=0,fill_pattern=0,char_size=.75,
       loc=(0.25,35),loctype='world',size=2)
     # graph.add_drawing_object(DrawText,text="N",x=0.665,y=35.5,char_size=.75,just=2,loctype='world')
-    graph.add_drawing_object(DrawText,text="N",x=0.265,y=35.5,char_size=.75,just=2,loctype='world')
+    graph.add_drawing_object(DrawText,text=\
+      LatexString('n\sij'),x=0.265,y=35.5,char_size=.75,just=2,loctype='world')
   graph.panel_label.configure(placement='iur',char_size=.75,dx=.02,dy=.02)
 
 

### 2019-01-11 manuscript/reply_to_reviewers.tex
almost finished addressing R2

@@
 
-	2. Non-independence of interactions not accounted for [written, not done]
+	2. Non-independence of interactions not accounted for [done]
 
@@
 		\textbf{R:} We agree wholeheartedly that ecological interactions are often not independent.
-Indeed, we refer several times to the effect of species' abundances on their probabilities of interacting.
-This effect alone will introduce non-independence in interaction probabilities, as all interactions involving a common species will be more likely than they would be if that species was rare.
-That said, we also agree that we do not explicitly discuss the non-independence of interactions.
-In part, this is by design.
-We explicitly want to keep our mathematical framework quite simple so that it is easily applicable to a wide variety of situations (including those where the nature of non-independence among interactions is not known).
-Nevertheless, to encourage readers to consider non-independence when designing their priors we are happy to take the Reviewer's suggestion and index our variables by ij and add a line noting that the assumption of independent interactions may not hold.
-
-	3/ identifiability: the reader would appreciate that the authors discuss and prove the identifiability of the model.
+Indeed, some of the priors we discuss (e.g., those incorporating species' abundances or trait-matching) will introduce covariance between interactions.
+The Reviewer is correct that we did not initially mention this non-independence explicitly.
+Our aim is to keep our mathematical framework simple so that it is easy for those not familiar with Bayesian analysis to adopt.
+Nevertheless, non-independence of interactions is an important consideration.
+We are therefore happy to index all variables referring to interactions by ij and we have added an explicit statement (lines XX-XX) that some priors treat interactions independently while others will introduce covariance (e.g., by species).
+
+		Lines XX-XX:
+
+		\begin{quotation}
+		    The shape parameters, or hyperparameters, may be set to particular values or derived from some data (see below).
+Note that the hyperparameters may be set to the same values for all interactions, allowed to vary independently for all interactions, or may incorporate non-independence betwween interactions (e.g., when the shape of the prior distribution depends upon species' abundances or traits).
+		\end{quotation}
+
+	3. Question about identifiability of the model [done]
+
+		\begin{refquote}
+
+			the reader would appreciate that the authors discuss and prove the identifiability of the model.
 Indeed, the three levels of uncertainity are nested but one could wonder whether different parameters at the three levels can fit the same data with the same quality (i.e.
@@
 
-	4/ absence of simulations: the authors proposed an original approach based on a bayesian framework.
+		\end{refquote}
+
+		\textbf{R:} We believe that this comment stems from a lack of clarity about the goal of our model.
+It is not designed to separate the three levels of uncertainty or introduce parameters at particular levels.
+The only inputs are a prior distribution, which could refer to any level of uncertainty applicable to the study at hand, and post-hoc counts of interactions and co-occurrences.
+Using only the observed data, it is impossible to separate the three levels of uncertainty and our model does not aim to do so (as stated in lines XX-XX and lines XX-XX).
+We therefore do not believe that an in-depth discussion of identifiability would add much value to the manuscript and, in the interest of space, have decided not to include one.
+
+		Lines XX-XX:
+
+		\begin{quotation}
+			When considering a metaweb, we wish to separate the unobserved interactions where $L_{ij} = 0$ (i.e., unfeasible interactions) from interactions which could occur but did not at a particular sampling site or which occurred but were not detected (Fig.~\ref{conceptual_fig}).
+Unfortunately, this is not possible for most interactions (except those where we know an interaction is truly not feasible).
+That is, we generally do not know \emph{why} an interaction was not observed, only that it was not.
+An empirical ecologist will instead measure the marginal probability $P(L_{ij}) = k_{ij}/n_{ij}$, where $k_{ij}$ is the number of observed interactions between species $i$ and $j$ and $n_{ij}$ the number of observed co-occurrences.
+Given this information, the question becomes: how can we reduce the uncertainty around our estimated interaction probability?
+		\end{quotation}
+
+		Lines XX-XX:
+
+		\begin{quotation}
+			Note that these Bayesian models of $\lambda_{ij}$ are designed to quantify (and reduce) the total uncertainty about $\lambda_{ij}$.
+They do not address any of the nested sources of uncertainty in particular except through the choice of prior.
+		\end{quotation}
+
+	4. Request for a simulation study [done; thanks Tomas]
+
+		\begin{refquote}
+			the authors proposed an original approach based on a bayesian framework.
 Beyond the identifiability question (see above), the reader can question the power of the method.
@@
 An so on… Only a well-conducted simulation study can answer these questions.
-
+		\end{refquote}
+
+		\textbf{R:} We agree with the Reviewer that a full simulation study, based on recreating the sources of uncertainty in a data set generated from known processes, is an excellent way to demonstrate the power of a novel method.
+The novelty and impact of our work, however, is not in the method itself (several other Reviewers rightly point out that similar approaches have occasionally been used before) but in connecting a Bayesian statistical approach to the problem of limited and uneven sampling of networks and, we hope, in making this method more accessible to those without extensive statistical or modelling experience.
+In other words, what we try to achieve here is to alert empirical ecologists constructing and analyzing networks to the uncertainties built into their work.
+We then try to provide them with simple tools for grasping the extent and consequences of typical patterns.
+Please note that other Reviewers (as expressed by Reviewer 3 in particular) find this a highly worthwhile objective.
+
+		What Reviewer 2 proposes would be more suitable for an entirely novel method and is substantially beyond the scope of the present study.
+There is indubitably a place for simulation studies in order to find the most powerful method once a variety of tools are in common use, especially for researchers aiming to convince modellers that their tool is more powerful.
+Our manuscript, however, is not aimed at those already comfortable with Bayesian approaches but rather at those who may be aware of the problems of uneven uncertainty but not aware of any way to include this information in their analyses.
+We are confident that even a very simple model which incorporates the differences in sampling across interactions (as ours does) is more powerful than a model which ignores this information completely, and we therefore do not intend to conduct a full-scale simulation study.
+We accept that this means that those already using more intricate Bayesian methods are unlikely to switch to our simpler version; it was never our intention that they should do so.
+
+	5. Request for an extended results and discussion section [no actual response, just words]
+
+		\begin{refquote}
 			5/ results\&discussion too short: the reader is surprised to read 27 lines of raw results only… Given the amount of new methodology that is proposed, one can expect a complete description of its pros and cons.
@@
 Forgetting about the length of these parts, it is still difficult to catch the key messages from the text, and it is not obvious to relate discussion and the obtained results (for instance,from l.343 to l.351).
-
+		\end{refquote}
+
+		\textbf{R:} We very much appreciate the Reviewer's point that the results and discussion do not clearly illustrate the point of the manuscript.
+Although we have not conducted a simulation study (see above), we have extensively revised these sections in order to highlight the main thread through the manuscript.
+Due to space limitations, we were unable to greatly expand either section (we prioritise the introduciton and methods, which lay out the problem of uncertainty in networks and how it can be partially addressed), but we hope that the results now more clearly demonstrate how a Bayesian approach can address the uncertainty inherent in sampling.
+
+	6. Suggestions to improve notation [done? unless anyone else can figure out the last part...]
+
+	\begin{refquote}
 		6/ lack of rigorous notations: it is possible to understand the approach with the present notations but some improvements can help the reader because there are a series of inconsistencies.
@@
 Traditionaly, given species i and j, we would consider interaction $L_ij$, feasibility $X_ij$, detectionability $D_ij$...
-	Still, what is T?? not defined, never reused: is it a characteristics on i, on j, on both?
-	How can be D<1 on l.169? D=0 or 1 since it says if an interaction is detectable or not...
-	Moreover, L is reused later but is the number of interactions (l.100 supp.mat)…
-	What is “N” in Figure 4? is it “n”? What is $n_ij$ and $k_ij$ l.266? Never defined, never reused.
+\\
+		Still, what is T?? not defined, never reused: is it a characteristics on i, on j, on both? \\
+		How can be D<1 on l.169? D=0 or 1 since it says if an interaction is detectable or not... \\
+		Moreover, L is reused later but is the number of interactions (l.100 supp.mat)… \\
+		What is “N” in Figure 4? is it “n”? What is $n_ij$ and $k_ij$ l.266? Never defined, never reused. \\
 		In the beginning of the paper, $\lambda$ is a probability (l.62) but it becomes a random variable (l.164): it would be more consistent to introduce before the notion of hyperparameters  (l.209-213) and to explain we consider that $\lambda$ is drawn into its distribution.
-
-	\end{refquote}
+	\end{refquote}
+
+	\textbf{R:} 
+		\begin{itemize}
+			\item As described above, we have now indexed $L$, $T$, $X$, $D$, etc. by $ij$. 
+			\item $T$ describes trait matching, so it is a characterisation on $i$ and $j$ together. 
+			\item $D$ can be \textless1 because some interactions are detectable but with a lower probability due to limitations in sampling techniques, sampling time, etc.
+With infinite monitoring time and capacity, all $D_{ij}$ would indeed be 0 or 1, but given real-world constraints that lead to otherwise-detectable interactions being missed, we feel it makes sense to discuss $0<D_{ij}<1$.
+For instance, consider a predator feeding upon two prey.
+If one of the prey (A) has many hard parts and is digested slowly, while the other has no hard parts and is digested quickly (B), the interaction involving prey A will be more detectable than the interaction involving prey B.
+The interaction with prey B is does not have D=0, because the interaction might be observed directly or through examination of gut contents very soon after B was consumed, but we cannot say that D=1 because we are quite likely not to detect this interaction in any given sample.
+			\item Using L to mean the number of interactions is incredibly common in the food-web literature, especially when defining connectance (as in the instance the Reviewer points out - now included in the main text).
+That said, we appreciate that this useage may confuse mathematicians.
+We therefore now define the number of interactions as N and hope that this is less puzzling.
+			\item Yes, the N on figure 4 should have been $n_{ij}$. This has been corrected. As discussed above, $n$ and $k$ are now always indexed by $ij$. 
+			\item We do not catch what the Reviewer is aiming at here.
+We hope that our revised introduction and methods have addressed this point; if not, we request that the Reviewer kindly provide some more detail so that we can address his/her concern.
 

### 2019-01-11 manuscript/CI_interactions.tex
almost finished addressing R2

@@
           First, and most fundamentally, some interactions are feasible if a pair of species should co-occur while others are not~\citep{Poisot2015}.
-Assuming that the feasibility of interactions depends on the traits of species involved, we can define the probability of an interaction $L$ given some description of trait-matching $\mathbf{T}$ as $P(L|\mathbf{T}) = \lambda$~\citep{Bartomeus2013,Gravel2013,Weinstein2017}.
-          In some cases the traits prohibiting an interaction are known, and there will be little uncertainty about $\lambda$.
+Assuming that the feasibility of interactions depends on the traits of species involved, we can define the probability of an interaction $L_{ij}$ between species $i$ and $j$, given some description of trait-matching $\mathbf{T_{ij}}$, as $P(L_{ij}|\mathbf{T_{ij}}) = \lambda_{ij}$~\citep{Bartomeus2013,Gravel2013,Weinstein2017}.
+          In some cases the traits prohibiting an interaction are known, and there will be little uncertainty about $\lambda_{ij}$.
           In most cases, however, it is not known what traits might prohibit an interaction~\citep{Dormann2017}.
@@
 This uncertainty is partly addressed by trait-matching models in which species with better-matched traits are more likely to interact~\citep{Bartomeus2016,Jordano2016,Weinstein2017}.
-As these models improve and include better information about the influence of traits on interactions, the uncertainty will be reduced~\citep{Jordano2016} and $\lambda$ should either tend to 0 or to 1.
+As these models improve and include better information about the influence of traits on interactions, the uncertainty will be reduced~\citep{Jordano2016} and $\lambda_{ij}$ should either tend to 0 or to 1.
 Nevertheless, every model is imperfect and lacks information that could be used to define constraints on at least some interactions~\citep{Dormann2017}.
@@
 
-          Assuming that an interaction is feasible (i.e., $L=1$;), an interaction may still not occur at a particular place or time~\citep{Poisot2015,Graham2018}.
+          Assuming that an interaction is feasible (i.e., $L_{ij} = 1$;), an interaction may still not occur at a particular place or time~\citep{Poisot2015,Graham2018}.
 This could be because constraints such as inclement weather or low abundance prevented the interaction~\citep{Jordano2016,Graham2018}, a more preferred interaction partner was available~\citep{Weinstein2017a}, or substantial individual variation in traits meant that local individuals could not interact even if the species in general can~\citep{Gravel2013,Wells2013,Poisot2015}.
@@
 In metawebs describing a community found at several sites, an interaction may also fail to occur because two species do not co-occur at a particular site even if they do co-occur and interact elsewhere~\citep{Graham2018}.
-We can define the local realisation of an interaction, $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L=1)=\chi$.
-It is unlikely that $\chi=1$  except in the case of obligate specialists who always interact whenever they co-occur and always co-occur.
-When $\chi<1$ we cannot be sure whether an unobserved interaction cannot occur or whether it simply did not occur at a particular site.
+We can define the local realisation of an interaction, $X_{ij}$, given that the interaction is feasible, as a stochastic process with associated probability $P(X_{ij}|L_{ij} = 1) = \chi_{ij}$.
+It is unlikely that $\chi_{ij} = 1$  except in the case of obligate specialists who always interact whenever they co-occur and always co-occur.
+When $\chi_{ij} < 1$ we cannot be sure whether an unobserved interaction cannot occur or whether it simply did not occur at a particular site.
 
-          Some of the uncertainty about $\chi$ could be addressed by drawing on the rich literature about interaction contingencies found in community ecology.
+          Some of the uncertainty about $\chi_{ij}$$ could be addressed by drawing on the rich literature about interaction contingencies found in community ecology.
 Phenological matching~\citep{MillerRushing2010,Gezon2016}, species preferences~\citep{Pires2011,Novak2015,Coux2016}, and fear effects~\citep{Luttbeg2005,Wirsing2008} all affect the probability of an interaction occurring at a particular site and time, and could be included in models similar to trait-matching models.
 Alternatively, interaction probabilities could be tested in mesocosm studies with constant conditions.
-Some studies attempt to reduce uncertainty by sampling intensively over a short period of time and restricting the scale of interest to interactions occurring at the sampling site and time (conflating $\chi$ and $\lambda$)~\citep{Bartomeus2013,Weinstein2017,Weinstein2017a}.
+Some studies attempt to reduce uncertainty by sampling intensively over a short period of time and restricting the scale of interest to interactions occurring at the sampling site and time (conflating $\chi_{ij}$ and $\lambda_{ij}$)~\citep{Bartomeus2013,Weinstein2017,Weinstein2017a}.
 This approach may be suitable for some research questions, but is not appropriate if we wish to assemble the full set of interactions which occur in a community (beyond the specific site and time of sampling).
-In contrast, expanding sampling to cover a broader spatial or temporal range (e.g., sampling in a variety of microhabitats or during a variety of weather conditions) will help to reduce uncertainty about $\chi$ by including a broader range of parameters affecting interaction probability.
-It is unlikely, however, that resources will permit researchers to sample in the full range of sites and conditions covered by a community, and some uncertainty about $\chi$ will remain.
+In contrast, expanding sampling to cover a broader spatial or temporal range (e.g., sampling in a variety of microhabitats or during a variety of weather conditions) will help to reduce uncertainty about $\chi_{ij}$ by including a broader range of parameters affecting interaction probability.
+It is unlikely, however, that resources will permit researchers to sample in the full range of sites and conditions covered by a community, and some uncertainty about $\chi_{ij}$ will remain.
 
@@
 
-            Both whether species can interact and whether they do interact at a particular place and time have been discussed in the context of "forbidden links"~\citep{Jordano2016}.
+            Both whether species can interact and whether they do interact at a particular place and time have been discussed in the context of ``forbidden links"~\citep{Jordano2016}.
 In this framework, all links which are prevented by spatio-temporal uncoupling, physiological constraints, etc.
@@
           Lastly, measurement errors are a pervasive source of uncertainty in the observation of ecological processes.
-Even if an interaction is feasible and occurs during sampling ($L = 1$ and $X = 1$), we may still fail to detect it~\citep{Jordano2016,Weinstein2017}.
-We may define the probability of detecting of an interaction, $D$, given the interaction is feasible and occurs, as a stochastic process with the associated probability $P(D|X=1,L=1)=\delta$.
+Even if an interaction is feasible and occurs during sampling ($L_{ij} = 1$ and $X_{ij} = 1$), we may still fail to detect it~\citep{Jordano2016,Weinstein2017}.
+We may define the probability of detecting of an interaction, $D_{ij}$, given the interaction is feasible and occurs, as a stochastic process with the associated probability $P(D_{ij}|X_{ij} = 1,L_{ij} = 1)=\delta_{ij}$.
 Detection failure could happen for many reasons (see~\citet{Wirta2014} for examples and partial solutions to them).
@@
 
-        To sum up, the absence of an interaction on a given day could  be because it was not feasible [$P(L) = 0$], was feasible but did not occur because of local conditions during sampling ($P(X|L=1) = 0$], or was feasible and occurred during sampling but could not be observed [$P(D|X=1,L=1)=0$].
+        To sum up, the absence of an interaction on a given day could  be because it was not feasible [$P(L_{ij}) = 0$], was feasible but did not occur because of local conditions during sampling ($P(X_{ij}|L_{ij} = 1) = 0$], or was feasible and occurred during sampling but could not be observed [$P(D_{ij}|X_{ij} = 1,L_{ij} = 1) = 0$].
 Note that some exteral factors can affect more than one level of uncertainty.
@@
 
-        When considering a metaweb, we wish to separate the unobserved interactions where $L = 0$ (i.e., unfeasible interactions) from interactions which could occur but did not at a particular sampling site or which occurred but were not detected (Fig.~\ref{conceptual_fig}).
+        When considering a metaweb, we wish to separate the unobserved interactions where $L_{ij} = 0$ (i.e., unfeasible interactions) from interactions which could occur but did not at a particular sampling site or which occurred but were not detected (Fig.~\ref{conceptual_fig}).
 Unfortunately, this is not possible for most interactions (except those where we know an interaction is truly not feasible).
-An empirical ecologist will instead measure the marginal probability $P(L) = k/n$, where $k$ is the number of observed interactions and $n$ the number of observed co-occurrences.
+That is, we generally do not know \emph{why} an interaction was not observed, only that it was not.
+An empirical ecologist will instead measure the marginal probability $P(L_{ij}) = k_{ij}/n_{ij}$, where $k_{ij}$ is the number of observed interactions between species $i$ and $j$ and $n_{ij}$ the number of observed co-occurrences.
 Given this information, the question becomes: how can we reduce the uncertainty around our estimated interaction probability?
@@
         The obvious rule of thumb to reduce uncertainty is ``sample more".
-Where resources permit, increasing sample sizes will reduce uncertainty about the upper bound of the interaction probability and will also increase the probability of detecting unlikely or cryptic interactions (e.g., interactions where $L$=1 but process or detection uncertainty is high).
+Where resources permit, increasing sample sizes will reduce uncertainty about the upper bound of the interaction probability and will also increase the probability of detecting unlikely or cryptic interactions (e.g., interactions where $L_{ij} = 1$ but process or detection uncertainty is high).
 Despite these benefits, we note that there are limits to the utility of increased sampling.
@@
         An added complication is that increased sampling will not reduce uncertainty evenly across interactions.
-To record an interaction between A and B, we need to identify both partners correctly (a non-trivial problem in many food webs; e.g.~\citealp{Kaartinen2011,Roslin2016}).
+To record an interaction between species $i$ and $j$, we need to identify both partners correctly (a non-trivial problem in many food webs; e.g.~\citealp{Kaartinen2011,Roslin2016}).
 For both molecular and rearing techniques, certain types of interactions may go unnoticed due to technical challenges~\citep{Wirta2014}.
@@
     % Assume that a pair of species has been observed co-occurring $n$ times and interacting in $k = 0$ cases.
-We want to know the probability $\lambda$ that the species would be observed interacting if not constrained by local conditions, imperfect detection, etc.
+We want to know the probability $\lambda_{ij}$ that the species would be observed interacting if not constrained by local conditions, imperfect detection, etc.
 We can consider the occurrence of an interaction as a Bernoulli trail where the number of successes ($k$) over $n$ trials will follow a binomial distribution (see~\emph{Appendix S2} for a full description of the mathematical framework).
-In this framework, the maximum likelihood estimate (MLE) for $\lambda$ is:
+In this framework, the maximum likelihood estimate (MLE) for $\lambda_{ij}$ is:
 
@@
 
-    % Note that $\lambda$ is not a point estimate but rather a random variable with an unknown distribution.
+    % Note that $\lambda_{ij}$ is not a point estimate but rather a random variable with an unknown distribution.
 This means that if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact.
@@
 In the situation where $k>0$, in contrast, we are sure that the interaction is feasible ($L = 1$).
-If $n>k>0$, the interaction is feasible but there may be local constraints ($X = 0$) or detection errors ($D<1$) causing the interaction not to be observed in some samples.
+If $n>k>0$, the interaction is feasible but there may be local constraints ($X_{ij} = 0$) or detection errors ($D<1$) causing the interaction not to be observed in some samples.
 
-    % To properly interpret $\lambda$, we need to estimate the variance as well as the MLE.
-The variance of a Bernoulli experiment is $n\lambda$(1-$\lambda$) and, importantly, describes the variability of the number of successes $k$ for $n$ trials rather than the variance associated with the estimation of $\lambda$.
-It is, however, straightforward to compute the confidence interval for the MLE of $\lambda$ using any of several methods, including the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]).
+    % To properly interpret $\lambda_{ij}$, we need to estimate the variance as well as the MLE.
+The variance of a Bernoulli experiment is $n\lambda$(1-$\lambda_{ij}$) and, importantly, describes the variability of the number of successes $k$ for $n$ trials rather than the variance associated with the estimation of $\lambda_{ij}$.
+It is, however, straightforward to compute the confidence interval for the MLE of $\lambda_{ij}$ using any of several methods, including the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]).
 
-    % All of the above methods for estimating the variance of $\lambda$ include the number of samples $n$.
-This means that where the number of samples $n$ is very low (e.g., for rare species), there will be considerable uncertainty around our estimate of $\lambda$.
-In Fig.~\ref{upper_limits}, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda$ (for true $\lambda = 0$) varies with sample size.
+    % All of the above methods for estimating the variance of $\lambda_{ij}$ include the number of samples $n$.
+This means that where the number of samples $n$ is very low (e.g., for rare species), there will be considerable uncertainty around our estimate of $\lambda_{ij}$.
+In Fig.~\ref{upper_limits}, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda_{ij}$ (for true $\lambda = 0$) varies with sample size.
 At a small sample size, the 95\% confidence interval is nearly (0, 1).
@@
 
-    The basis of a Bayesian approach to modelling the probability that an interaction occurs ($\lambda$) is combining the maximum likelihood estimate (MLE) of $\lambda$ with a prior distribution (described in the next section) and a normalising function.
-The MLE of $\lambda$ can be modelled as a Bernoulli trial based on the number of observed interactions $k$ and observed co-occurrances $n$: $\lambda = \frac{k}{n}$.
-The most appropriate prior distribution for a probability such as $\lambda$ is the beta distribution:
+    The basis of a Bayesian approach to modelling the probability that an interaction between species $i$ and $j$ occurs ($\lambda_{ij}$) is combining the maximum likelihood estimate (MLE) of $\lambda_{ij}$ with a prior distribution (described in the next section) and a normalising function.
+The MLE of $\lambda_{ij}$ can be modelled as a Bernoulli trial based on the number of observed interactions $k_ij$ and observed co-occurrances $n_{ij}$: $\lambda_{ij} = \frac{k_{ij}}{n_{ij}}$.
+The most appropriate prior distribution for a probability such as $\lambda_{ij}$ is the beta distribution:
 
     \begin{equation}
-          \lambda \sim Beta(\alpha,\beta) , \label{prior}
+          \lambda_{ij} \sim Beta(\alpha_{ij},\beta_{ij}) , \label{prior}
         \end{equation}
 
-        \noindent which has two shape parameters, $\alpha$ and $\beta$.
+        \noindent which has two shape parameters, $\alpha_{ij}$ and $\beta_{ij}$.
 
     The shape parameters, or hyperparameters, may be set to particular values or derived from some data (see below).
-Combining the prior distribution with the MLE of $\lambda$ derived from observed data, we obtain a posterior distribution that also follows a beta distribution with new parameters $\alpha'= \alpha+k$ and $\beta'=\beta+n-k$ (see~\emph{Appendix S2} for details).
-The influence of the prior on the posterior distribution can be understood from these parameter definitions: the difference between the posterior and the prior will increase with $k$ and $n-k$.
-In other words, the distribution of $\lambda$ for better-sampled pairs of species will rely less on the information used to build the prior distribution and depend more on the observed data and uncertainty about the probability of the pair interacting will decrease (Fig.~\ref{Salix_pdfs_cdfs}).
+Note that the hyperparameters may be set to the same values for all interactions, allowed to vary independently for all interactions, or may incorporate non-independence betwween interactions (e.g., when the shape of the prior distribution depends upon species' abundances or traits).
+    Combining the prior distribution with the MLE of $\lambda_{ij}$ derived from observed data, we obtain a posterior distribution that also follows a beta distribution with new parameters $\alpha_{ij}'= \alpha_{ij}+k$ and $\beta_{ij}'=\beta_{ij}+n-k$ (see~\emph{Appendix S2} for details).
+The influence of the prior on the posterior distribution can be understood from these parameter definitions: the difference between the posterior and the prior will increase with $k_{ij}$ and $n_{ij}-k_{ij}$.
+In other words, the distribution of $\lambda_{ij}$ for better-sampled pairs of species will rely less on the information used to build the prior distribution and depend more on the observed data and uncertainty about the probability of the pair interacting will decrease (Fig.~\ref{Salix_pdfs_cdfs}).
+Note that these Bayesian models of $\lambda_{ij}$ are designed to quantify (and reduce) the total uncertainty about $\lambda_{ij}$.
+They do not address any of the nested sources of uncertainty in particular except through the choice of prior.
 
@@
     %   It is common to perform analyses that require calculating higher-order network properties in interaction networks.
-The fact that the posterior distribution of $\lambda$ follows a beta distribution makes it straightforward to compute moments and other properties needed for these analyses.
+The fact that the posterior distribution of $\lambda_{ij}$ follows a beta distribution makes it straightforward to compute moments and other properties needed for these analyses.
 
-    %   The \textbf{average} of $\lambda$ is: 
+    %   The \textbf{average} of $\lambda_{ij}$ is: 
     %       \begin{equation}
-    %         \bar{\lambda} = \frac{\alpha+k}{\alpha+\beta+n} ,
+    %         \bar{\lambda} = \frac{\alpha_{ij}+k}{\alpha_{ij}+\beta_{ij}+n} ,
     %         \label{mean}
@@
     %       \begin{equation}
-    %         Var(\lambda|k) = \frac{(\alpha + k)(\beta + n - k)}{(\alpha + \beta + n)^{2}(\alpha + \beta + n +1)}
+    %         Var(\lambda|k) = \frac{(\alpha_{ij} + k)(\beta_{ij} + n - k)}{(\alpha_{ij} + \beta_{ij} + n)^{2}(\alpha_{ij} + \beta_{ij} + n +1)}
     %         \label{variance}
@@
     %       \begin{equation}
-    %         \hat{\lambda} = \frac{\alpha + k - 1}{\alpha + \beta + n - 2} .
+    %         \hat{\lambda} = \frac{\alpha_{ij} + k - 1}{\alpha_{ij} + \beta_{ij} + n - 2} .
     %         \label{mode}
@@
 All of these choices will affect the compiled network and most do not have clear answers, making all empirical networks (and all theoretical networks, which likewise depend upon the assumptions used in building the network) to some extent subjective.
-In addition, researchers distinguishing "forbidden links" inherently rely on prior knowledge to identify these links~\citep{Jordano2016}.
-Stating that an interaction is "forbidden" is, in effect, applying a very strong prior to reduce/eliminate uncertainty about the non-observation of that interaction.
+In addition, researchers distinguishing ``forbidden links" inherently rely on prior knowledge to identify these links~\citep{Jordano2016}.
+Stating that an interaction is ``forbidden" is, in effect, applying a very strong prior to reduce/eliminate uncertainty about the non-observation of that interaction.
 Given this reality, we feel it is better to make the assumptions used to build a network as explicit as possible so that these assumptions can be questioned, compared between studies, and tested.
@@
 
-        If researchers wish to reflect uncertainty in their data without applying any particular assumptions/prior knowledge or account for the possibility that the distribution of probabilities of interaction may vary, they can select $\alpha$ and $\beta$ to produce an intentionally uninformative prior~\citep{Leyland2005,Berger2006}.
+        If researchers wish to reflect uncertainty in their data without applying any particular assumptions/prior knowledge or account for the possibility that the distribution of probabilities of interaction may vary, they can select $\alpha_{ij}$ and $\beta_{ij}$ to produce an intentionally uninformative prior~\citep{Leyland2005,Berger2006}.
 This prior can then be given a low weight, such that any observed data will outweigh the prior distribution.
-For pairs of species with little or no observed data, an uninformative prior will leave large variance about $\lambda$ and reflect our lack of knowledge about the pair.
-Since we model $\lambda$ as a Bernoulli trial, the appropriate uninformative prior is Jeffreys prior: a beta distribution with $\alpha$=$\beta$=0.5.
-The sum of $\alpha$ and $\beta$ is roughly equivalent to the weight of the prior, so Jeffreys prior has equal weight to a single observation.
+For pairs of species with little or no observed data, an uninformative prior will leave large variance about $\lambda_{ij}$ and reflect our lack of knowledge about the pair.
+Since we model $\lambda_{ij}$ as a Bernoulli trial, the appropriate uninformative prior is Jeffreys prior: a beta distribution with $\alpha_{ij}$=$\beta_{ij}$=0.5.
+The sum of $\alpha_{ij}$ and $\beta_{ij}$ is roughly equivalent to the weight of the prior, so Jeffreys prior has equal weight to a single observation.
 
@@
 Instead, we assume only that the focal network will have similar structural properties to those of published networks.
-For example, connectance ($C=L/S^2$, where $L$ is the number of interactions and $S$ is the number of species) is available for many networks.
+For example, connectance ($C=N/S^2$, where $N$ is the number of interactions and $S$ is the number of species) is available for many networks.
 The distribution of these connectances can be used to predict the distribution of interaction probabilities in a new network.
@@
         \begin{equation}
-        \alpha = \overline{C}(\frac{\overline{C}(1-\overline{C})}{\sigma_C^2}-1) ,
+        \alpha_{ij} = \overline{C}(\frac{\overline{C}(1-\overline{C})}{\sigma_C^2}-1) ,
         \end{equation}
@@
         \begin{equation}
-        \beta = (1-\overline{C})(\frac{\overline{C}(1-\overline{C})}{\sigma_C^2}-1) .
+        \beta_{ij} = (1-\overline{C})(\frac{\overline{C}(1-\overline{C})}{\sigma_C^2}-1) .
         \end{equation}
@@
 To show the gaps in sampling, we compared the frequencies of observed co-occurrences and interactions.
-We then calculated an empirical prior and computed the posterior distribution of the probability of an as-yet-unobserved interaction being feasible ($\lambda$).
+We then calculated an empirical prior and computed the posterior distribution of the probability of an as-yet-unobserved interaction being feasible ($\lambda_{ij}$).
       We analysed both the \emph{Salix}-galler and galler-natural enemy components of the network but, for brevity, present only the latter here (see~\emph{Appendix S5} for \emph{Salix}-galler results).
@@
         To obtain priors based on a single sub-network --Zillis in Graub\"{u}nchen, Switzerland-- we estimated frequencies of interactions based on the normalised degree of each species in each network component (see \emph{Appendix S7} for details and code).
-Using these prior parameters, we then estimated the posterior distributions of interaction probabilities $\lambda$.
+Using these prior parameters, we then estimated the posterior distributions of interaction probabilities $\lambda_{ij}$.
 For species without observed interactions ($n = 0$), the posterior distribution is identical to the prior distribution.
@@
 If we consider only pairs of species which were observed co-occurring but not interacting, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs.
-This gives $\alpha'$=$\alpha$ and $\beta'$=$\beta + n_{ij}$.
+This gives $\alpha_{ij}'$=$\alpha_{ij}$ and $\beta_{ij}'$=$\beta_{ij} + n_{ij}$.
 We calculated posterior distributions and 95\% credible intervals (see function ``credible\_interval";~\emph{Appendix S8}) for species with $n$ ranging between 0 and 374, the total number of sites in our dataset.
@@
 The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact.
-We calculated the number of samples required to reach 95\% confidence that $\lambda$ was below thresholds of 0.1, 0.05, and 0.01 as examples (see function ``samples\_for\_threshold";~\emph{Appendix S8}).
+We calculated the number of samples required to reach 95\% confidence that $\lambda_{ij}$ was below thresholds of 0.1, 0.05, and 0.01 as examples (see function ``samples\_for\_threshold";~\emph{Appendix S8}).
 
@@
       Researchers are often interested in measures of network structure rather than the network itself.
-Computing most network metrics is straightforward when the different $\lambda$ of the adjacency matrix are known and assumed not to vary~\citep{Poisot2016}.
-Incorporating variance in $\lambda$ into these calculations, however, is not so easy.
+Computing most network metrics is straightforward when the different $\lambda_{ij}$ of the adjacency matrix are known and assumed not to vary~\citep{Poisot2016}.
+Incorporating variance in $\lambda_{ij}$ into these calculations, however, is not so easy.
 Computation of these metrics involves non-linear functions.
 By Jensen's inequality~\citep{Jensen1906}, this means that the average of a network metric (a function of stochastic interactions) is not the same as the network metric calculated based on the average interaction probability.
-Thus, any uncertainty in the values of $\lambda$ could bias both the mean and variance of network metrics, giving misleading results (simulated in \emph{Appendix S1}).
+Thus, any uncertainty in the values of $\lambda_{ij}$ could bias both the mean and variance of network metrics, giving misleading results (simulated in \emph{Appendix S1}).
 One way to avoid this situation is to calculate the properties of a suite of simulated networks~\citep{Vazquez2005,Guimera2009}.
@@
 After obtaining these posterior networks, we calculated the connectance of each web, as well as the mean number of links per galler and per natural enemy, and the nestedness (NODF) of the network.
-This gives us an estimate for each property reflecting our uncertainty about $\lambda$.
+This gives us an estimate for each property reflecting our uncertainty about $\lambda_{ij}$.
 
@@
 
-  We obtained prior parameters of $\alpha$=0.700, $\beta$=8.49, giving a beta distribution strongly skewed towards 0.
-Where $n=0$, these parameters gave a posterior distribution with $\bar\lambda$=0.076, var($\lambda$)=0.008.
+  We obtained prior parameters of $\alpha_{ij}$=0.700, $\beta_{ij}$=8.49, giving a beta distribution strongly skewed towards 0.
+Where $n=0$, these parameters gave a posterior distribution with $\bar\lambda$=0.076, var($\lambda_{ij}$)=0.008.
 When $n=374$, we obtained a posterior distribution with $\bar\lambda_{ij}$=1.83 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=4.76$\times10^6$.
-This distributions is very close to 0 with small variance about $\lambda$; if species $i$ and $j$ co-occurred 374 times without interacting, they are extremely unlikely to do so at other sites or times.
+This distributions is very close to 0 with small variance about $\lambda_{ij}$; if species $i$ and $j$ co-occurred 374 times without interacting, they are extremely unlikely to do so at other sites or times.
 
@@
 Assume that two species cannot interact (i.e., $\lambda=0$) and that the number of observed interactions follows a binomial distribution depending upon the number of observed interactions $k$ and observed co-occurrances $n$.
-The maximum likelihood estimate (MLE) for $\lambda$ is $\lambda_{MLE}=\frac{k}{n}$.
-Note that $\lambda$ is not a point estimate but rather a random variable with an unknown distribution.
+The maximum likelihood estimate (MLE) for $\lambda_{ij}$ is $\lambda_{MLE}=\frac{k}{n}$.
+Note that $\lambda_{ij}$ is not a point estimate but rather a random variable with an unknown distribution.
 This means that if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact.
 Rather, $k = 0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless some chance that the two species \emph{could} interact.\\
-    Importantly, we can estimate the variance of $\lambda$ as well as the MLE; available methods include the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]).
-The distribution of the MLE for $\lambda$ thus obtained is a key part of the Bayesian distribution for $\lambda$.
-    Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true credible interval for the interaction probability $\lambda$ for a pair of species that has been observed co-occurring $n$ times but never interacting ($k = 0$).
+    Importantly, we can estimate the variance of $\lambda_{ij}$ as well as the MLE; available methods include the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]).
+The distribution of the MLE for $\lambda_{ij}$ thus obtained is a key part of the Bayesian distribution for $\lambda_{ij}$.
+    Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true credible interval for the interaction probability $\lambda_{ij}$ for a pair of species that has been observed co-occurring $n$ times but never interacting ($k = 0$).
 The upper limit of the credible interval only reaches 0.1 (dashed, red line) with 35 observations.
@@
   \begin{figure}[h!]
-    \caption{Using prior distributions based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017}, we calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting ($k = 0$).
-    Posterior distributions (curves) and 95\% credible intervals (lines at top of panel) for $\lambda$ narrow and approach zero as the number of observed co-occurrences ($n$) increases.
+    \caption{Using prior distributions based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017}, we calculate posterior distributions for the probability of interaction ($\lambda_{ij}$) between two species that have not yet been observed interacting ($k_{ij} = 0$).
+    Posterior distributions (curves) and 95\% credible intervals (lines at top of panel) for $\lambda_{ij}$ narrow and approach zero as the number of observed co-occurrences ($n_{ij}$) increases.
 Diamonds indicate the maximum likelihood estimator for the mean probability of interaction.
@@
 The number of samples required to obtain a 95\% credible interval below each threshold increases rapidly.
-It takes just over 20 observed co-occurrences to be 95\% confident that $\lambda<0.10$, approximately 50 co-occurrences to be 95\% confident that $\lambda<0.05$, and over 100 co-occurrences to be 95\% confident that $\lambda<0.01$.}
+It takes just over 20 observed co-occurrences to be 95\% confident that $\lambda_{ij}<0.10$, approximately 50 co-occurrences to be 95\% confident that $\lambda_{ij}<0.05$, and over 100 co-occurrences to be 95\% confident that $\lambda_{ij}<0.01$.}
     \label{Salix_pdfs_cdfs}

### 2019-01-14 manuscript/reply_to_reviewers.tex
working on reply

@@
 % ---------------------------------------------------------------------
-{\Large \bf Reply to Reviewer \#2} [[not started]]
+{\Large \bf Reply to Reviewer \#2} [[done?]]
 % ---------------------------------------
@@
 		\begin{quotation}
-			When considering a metaweb, we wish to separate the unobserved interactions where $L_{ij} = 0$ (i.e., unfeasible interactions) from interactions which could occur but did not at a particular sampling site or which occurred but were not detected (Fig.~\ref{conceptual_fig}).
+			When considering a metaweb, we wish to separate the unobserved interactions where $L_{ij} = 0$ (i.e., unfeasible interactions) from interactions which could occur but did not at a particular sampling site or which occurred but were not detected (Fig.
+1).
 Unfortunately, this is not possible for most interactions (except those where we know an interaction is truly not feasible).
@@
 We hope that our revised introduction and methods have addressed this point; if not, we request that the Reviewer kindly provide some more detail so that we can address his/her concern.
-
-	Minor points:
-
-	-l.62: define formally T
+			\end{itemize}
+
+	7. l.62: define formally T [done]
+
+		\textbf{R}: We now define $T_{ij}$ as ``some function describing trait-matching between species $i$ and $j$ $\mathbf{T_{ij}}$".
+This definition is intentionally open-ended as we foresee that $T_{ij}$ could be binary (traits are compatible or not) or continuous with a wide array of distributions.
+
+	8. Clarify the point of analysing the data using an alternative prior [done]
+
+		\begin{refquote}	
 			-l.244: this is weird to mention that the analysis has been done on another dataset but that the results will not be discussed… What is the interest for the reader?
+		\end{refquote}
+
+		\textbf{R}: We have removed the reference to the analysis and now explain more thoroughly how the choice of an unsuitable prior can result in unrealistic posterior distributions, as this is the interest for the reader.
+
+	9. No ``moral network" [not sure about this one.]
+
+		\begin{refquote}
 			-l.149: since the authors consider the interactions are independent, there is morally no network in the approach (except the result)
-	-l.252: not clear. Why this choice?
-	-l.259: not clear
+		\end{refquote}
+
+		\textbf{R}: We do not agree with this assessment.
+We do not explicitly consider the interactions to be independent, although we also do not explicitly define a dependence structure (we did not have data on species abundances or preferences that would allow us to do this).
+Even had we specifically stated that interactions are considered independent, this would not be unique among network analyses (see e.g., ...).
+To us, non-independence of interactions is not necessary when considering a network.
+All that is essential is the endeavour to better understand a community of interacting species, which our study does aim to do.
+
+	10. l.252: not clear. Why this choice? [done]
+
+		\textbf{R:} We have expanded the description of the reasoning behind our choice of prior and hope that the following is clearer:
+
+		Lines 369-373:
+
+		\begin{quotation}
+			researchers must choose between using a less-informative prior (e.g., one based on distributions of links across a large set of networks) or an empirical prior based on some ”training data” from the study.
+Here, we opted for the latter and created priors using a single sub-network from the middle of the geographical distribution of the Kopelke et al.
+(2017) dataset.
+		\end{quotation}
+
+	11. l.259: not clear [done]
+
+		\textbf{R:} We have expanded our explanation of how mis-matched priors can give unrealistic results. We hope that the following is clearer:
+
+		Lines 373-379:
+
+		\begin{quotation}
+			To demonstrate how the use of data from a different system can affect the prior distribution and conclusions based on it, we repeated our analyses using priors derived from a much smaller Salix-galler-natural enemy system based around genotypes of a single Salix species (Barbour et al., 2016, Data available from the Dryad Digital Repository: https://doi.org/10.5061/dryad.g7805).
+This smaller system was much more densely-connected than that described in Kopelke et al.
+(2017) and provided unreasonable distributions for interaction probabilities (Appendix S6 ).
+		\end{quotation}
+
+	12. Why connectance and nestedness? [done?]
+
+		\begin{refquote}
 			-l.278: the authors investigate the consequence of uncertainity on network metrics.
@@
 (we guess the answers but we could expect the authors develop these points).
-	l.291: explain better the simulation procedure
-	l.306: given the shape of the distribution (exponential), the mean is not an appropriate indicator.
-	l.327: what does it mean? How is it possible?
+		\end{refquote}
+
+		\textbf{R:} We chose connectance and nestedness (together with degree distributions) as simple examples of commonly-assessed network properties that would be familiar to most readers working with ecological networks.
+Obviously these are not the only parameters of interest, but we do not have space to provide an exhaustive analysis of how uncertainty in the computation of network metrics affects different network properties.
+Our aim was simply to show that including uncertainty in interactions (and accounting for the possibility that many interactions are not observed) can dramatically change our perception of network metrics.
+A full discussion of how and why these values differ is better suited to either an exhaustive simulation study or an experimental study where different sources of uncertainty can be controlled to some degree.
+We now state that these four properties were chosen as illustrative examples (lines 425-428).
+
+		\begin{quotation}
+			After obtaining these posterior networks, we calculated, as examples of commonly-used network properties, the connectance of each web, as well as the mean number of links per galler and per natural enemy, and the nestedness (NODF) of the network.
+		\end{quotation}
+
+	13. l.291: explain better the simulation procedure [done]
+
+		\textbf{R:} In the interest of space, we have added an extended description of the sampling procedure in \emph{Appendix S2}.
+
+		Lines 420-425:
+
+		\begin{quotation}
+			Using the prior distributions and procedures described above, we calculated posterior probability distributions for species pairs that were not observed interacting.
+Using these posterior distributions and assuming probabilities of 1 for pairs of species that were observed interacting (see Appendix S2 for a justification), we created a suite of 100 webs by randomly sampling from each posterior distribution.
+Each of these webs is a prediction of the structure of the metaweb.
+		\end{quotation}
+
+	14. l.306: given the shape of the distribution (exponential), the mean is not an appropriate indicator. [done]
+
+		\textbf{R:} The mean may not be the best indicator with which to describe the shape of the distribution, but we hope that the Reviewer will agree that it gets the point across (co-occurrences are rare; the specific values are not of great importance).
+Nevertheless, we now include both mean and median in order to better reflect the exponential distribution of the data.
+
+		Lines XX-XX:
+
+		\begin{quotation}
+			the total number of co-occurrences was generally low (mean=3.87, median=2; Fig.
+2A).
+The bulk (92.24\%) of these co-occurring species pairs were never observed interacting.
+Of those pairs that did interact, the incidence of interaction was also low (mean=4.04, median=2; Fig.
+2B) and was lower than the number of observed co-occurrences (Fig.
+2C).
+		\end{quotation}
+
+	15. What does higher nestedness in the observed networks mean? How is it possible? [done]
+
+		\textbf{R:} Nestedness being higher in the observed networks simply means that the additional interactions predicted by our model tend not to be between generalists and specialists and, as such, do not contribute strongly to nestedness.
+This is actually somewhat intuitive - ``specialists" in the observed data are exactly those species for which we are most likely to be missing interactions, and interactions between specialists and the most likely to be predicted to occur but not have been observed.
+Due to the tight word limit, we do not have space to discuss this extensively in the manuscript but have added brief interpretations in the results.
+
+		Lines XX-XX:
+
+		\begin{quotation}
+			Nestedness was higher in the observed network (NODF=6.85) than in the posterior webs (6.31 $\leq NODF \leq$ 6.82; Fig.
+5C), indicating that the posterior webs include many more interactions between specialists than the observed network.
+In addition, the stronger the detection filter, the farther apart were the nestedness of the observed and posterior webs.
+This suggests that the interactions included in the observed network are not a random subset of those included in the posterior webs.
+		\end{quotation}
+
+\clearpage
 
@@
             Both of the above sources of uncertainty (i.e., whether species would be able to interact given their traits and whether they are able to interact at a particular place and time) are addressed in the concept of "forbidden links"~\citep{Jordano2016}.
-In this framework, all links which are prevented by spatio-temporal uncoupling~\citep{Jordano1987}, physiological constraints~\citep{Jordano1987,More2012}, etc.
+In this framework, all links which are prevented by spatio-temporal uncoupling~\citep{Jordano1987}, physiological constraints~\citep{Jordano1987}, etc.
 are considered "structural zeros" that cannot be observed~\citep{Jordano2016}.
@@
 In many cases, the assumptions involved in excluding interactions are less clear-cut and different researchers may disagree about which species are "bound to interact" (or not to interact).
-The concept of pollination syndromes is one example - many flower visitors are less rigidly specialized on particular flower types than initially thought~\citep{}.
+The concept of pollination syndromes is one example - many flower visitors are less rigidly specialized on particular flower types than initially thought~\citep{Ollerton2009}.
 To address such "forbidden links", we now suggest that researchers explicitly state both the uncertainty about data-based zeros and the assumptions by which they create structural zeros.
@@
 
-\newpage
+\clearpage
 
@@
 Even long-term interactions, however, can be missed, especially if species are difficult to identify or if not all individuals of a species share the interaction.
-Parasites, for example, are often concentrated in only a few individuals~\citep{Lagrue2017}.
+Parasites, for example, are often concentrated in only a few individuals~\citep{Lagrue2015}.
 If these infected individuals do not happen to be included in a sample, their interactoins will be missed.

### 2019-01-14 manuscript/CI_interactions.tex
working on reply

@@
           First, and most fundamentally, some interactions are feasible if a pair of species should co-occur while others are not~\citep{Poisot2015}.
-Assuming that the feasibility of interactions depends on the traits of species involved, we can define the probability of an interaction $L_{ij}$ between species $i$ and $j$, given some description of trait-matching $\mathbf{T_{ij}}$, as $P(L_{ij}|\mathbf{T_{ij}}) = \lambda_{ij}$~\citep{Bartomeus2013,Gravel2013,Weinstein2017}.
+Assuming that the feasibility of interactions depends on the traits of species involved, we can define the probability of an interaction $L_{ij}$ between species $i$ and $j$, given some function describing trait-matching between species $i$ and $j$ $\mathbf{T_{ij}}$, as $P(L_{ij}|\mathbf{T_{ij}}) = \lambda_{ij}$~\citep{Bartomeus2013,Gravel2013,Weinstein2017}.
           In some cases the traits prohibiting an interaction are known, and there will be little uncertainty about $\lambda_{ij}$.
@@
 
-          Some of the uncertainty about $\chi_{ij}$$ could be addressed by drawing on the rich literature about interaction contingencies found in community ecology.
+          Some of the uncertainty about $\chi_{ij}$ could be addressed by drawing on the rich literature about interaction contingencies found in community ecology.
 Phenological matching~\citep{MillerRushing2010,Gezon2016}, species preferences~\citep{Pires2011,Novak2015,Coux2016}, and fear effects~\citep{Luttbeg2005,Wirsing2008} all affect the probability of an interaction occurring at a particular site and time, and could be included in models similar to trait-matching models.
@@
 Each of these webs is a prediction of the structure of the metaweb.
-After obtaining these posterior networks, we calculated the connectance of each web, as well as the mean number of links per galler and per natural enemy, and the nestedness (NODF) of the network.
+After obtaining these posterior networks, we calculated, as examples of commonly-used network properties, the connectance of each web, as well as the mean number of links per galler and per natural enemy, and the nestedness (NODF) of the network.
 This gives us an estimate for each property reflecting our uncertainty about $\lambda_{ij}$.
@@
 
-  In the \emph{Salix}-based food webs sampled by~\citet{Kopelke2017}, most pairs of gallers and natural enemies (9,794/12,096) never co-occurred and, for species that did occur together, the total number of co-occurrences was generally low (mean=3.87; Fig.~\ref{histograms}A).
+  In the \emph{Salix}-based food webs sampled by~\citet{Kopelke2017}, most pairs of gallers and natural enemies (9,794/12,096) never co-occurred and, for species that did occur together, the total number of co-occurrences was generally low (mean=3.87, median=2; Fig.~\ref{histograms}A).
 The bulk (92.24\%) of these co-occurring species pairs were never observed interacting.
-Of those pairs that did interact, the incidence of interaction was also low (mean=4.04; Fig.~\ref{histograms}B) and was lower than the number of observed co-occurrences (Fig.~\ref{histograms}C).
+Of those pairs that did interact, the incidence of interaction was also low (mean=4.04, median=2; Fig.~\ref{histograms}B) and was lower than the number of observed co-occurrences (Fig.~\ref{histograms}C).
 
@@
 When the detection probability was relatively low (i.e., 50\%), however, the properties of randomised networks became similar to those in the observed webs (Fig.~\ref{posterior_webs}A,B,D).
-Nestedness was higher in the observed network (NODF=6.85) than in the posterior webs (6.31 $\leq NODF \leq$ 6.82; Fig.~\ref{posterior_webs}C); in this case, the stronger the detection filter, the farther apart were the observed and posterior webs.
+Nestedness was higher in the observed network (NODF=6.85) than in the posterior webs (6.31 $\leq NODF \leq$ 6.82; Fig.~\ref{posterior_webs}C), indicating that the posterior webs include many more interactions between specialists than the observed network.
+In addition, the stronger the detection filter, the farther apart were the nestedness of the observed and posterior webs.
+This suggests that the interactions included in the observed network are not a random subset of those included in the posterior webs.
 In general, the observed network is most similar to simulated networks where only half of the plausible links are detected.

### 2019-01-14 manuscript/submission_MEE_2018.tex
working on reply

--- 2019-01-11 manuscript/CI_interactions.tex
@@
 \section*{Abstract}
-  [[was fine? Maybe lightly edit to make clear we're not doing a review]]
+
   \begin{enumerate}
@@
 
-    Representing an ecological community as a network allows ecologists to address both community composition and the interactions between species~\citep{Roslin2016}.
-Identifying these interactions is a crucial step towards understanding (and predicting) the effects that species have on each other and the response of the community as a whole to external perturbations~\citep{Bartomeus2016,Giron2018}.
-Importantly, information is conveyed both by the presence and \emph{absence} of links between species.
-Presences and absences are not, however, equally certain.
-An observed link definitely occurred, but there are multiple reasons why a given link may not be observed~\citep{Jordano2016}.
-
-    First and foremost, ecological communities are known to be stochastic~\citep{Gotelli2000}.
-Community composition and abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}, leading to variation in encounter probabilites and hence in interactions~\citep{Vazquez2005,Poisot2015,Graham2018}.
-Species must co-occur in order to be observed interacting, so any variation in co-occurrence will create variation in the set of observed interactions~\citep{Gravel2013,Graham2018}.
-Even assuming constant co-occurrence within a given study system, changing abundances can affect interactions if species which would otherwise interact become too rare to detect each other~\citep{Tylianakis2010,Jordano2016}.
-Moreover, interactions vary over space~\citep{Kitching1987,Baiser2012,Emer2018}, time~\citep{Kitching1987,Olesen2011a,Lopez2017}, between individuals~\citep{Pires2011a,Wells2013,Fodrie2015,Novak2015}, throughout life cycles~\citep{Preston2014,Clegg2018}, and with environmental conditions~\citep{Poisot2015}.
-
-    Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007,Jordano2016}).
-An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to correctly document interactions than species~\citep{Guimera2009,Poisot2012,Bartomeus2013,Jordano2016,Giron2018,Graham2018}.
-As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Bartomeus2013,Poisot2016}.
-Efforts in this vein usually take the form of creating model food webs that approximate observed empirical networks~\citep{Allesina2008,Guimera2009,Williams2010,Rohr2016}.
-These models may be based on species traits and/or abundances~\citep{Rohr2016,Weinstein2017,Weinstein2017a,Graham2018} or on simple abstract rules~\citep{Allesina2008,Guimera2009,Williams2010}.
-Such models provide an important ''reality check'' by allowing us to test hypotheses about the factors structuring ecological networks~\citep{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}.
-They can also allow us to estimate the numbers of interactions which have not been observed~\citep{Jordano2016,Weinstein2017a} and predict which unobserved interactions are most likely~\citep{Guimera2009,Bartomeus2013}.
-
-    [[These two paragraphs try to frame our study more clearly]]
-    To date, models incorporating uncertainty have either been very general (e.g.,~\citet{Guimera2009,Gravel2013}) or very system-specific (e.g.,~\citet{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}); in either case one of these models may be a poor fit for a particular study system.
-Moreover, some of the system-specific models described above cannot accommodate species observed only once~\citep{Bartomeus2013,Weinstein2017}.
-As rare species are likely to be observed less frequently~\citep{Bluthgen2006} and may be of particular interest (e.g., when modelling species loss), there is a need for a more widely-applicable framework that includes such rare species.
-
-    Here we introduce a simple Bayesian framework that can easily be adapted to different systems.
-First, we provide a brief description of the nested levels of uncertainty affecting ecological network construction.
-In the context of this uncertainty, which can be reduced but not eliminated by high-quality sampling (\citealp[see Box 1]{Bartomeus2013}), we present our Bayesian framework for combining observed data with a prior expectation of network structure.
-We conclude with a worked example applying this framework to an intensively-sampled host-parasitoid network.
-We find that even the highest-quality empirical network we could find had substantial uncertainty about whether many pairs of species interact, demonstrating the need to include information about this uncertainty in published networks.
-We also show that this interaction-level uncertainty leads to uncertainty about estimates of network structure, with important implications for comparisons across networks; especially those compiled with different sampling intensity~\citep{Weinstein2017}.
-
-    % Development of molecular sampling methods such as DNA barcoding hold great potential for uncovering interactions missed by other sampling methods (such as visit surveys)~\citep{Giron2018}, but these novel methods are also somewhat error-prone at present~\citep{}.
-
-    % Accounting for differences in feasible (binary) interactions across life stages changes network structure~\citep{Clegg2018}.
-
-    % Representing an ecological community as a network summarises both species composition and interactions between species.
+    Representing an ecological community as a network summarises both species composition and interactions between species.
 A tabulation of the nodes (species) and their relative abundances forms the basis for traditional metrics of community composition such as alpha diversity.
 A network framework combines this tabulation of nodes with a list of interactions (links between nodes) so that networks provide additional, higher-order information on community structure.
-Despite this additional information, empirical descriptions of ecological networks are still often limited by a lack of data or tools to adequately incorporate variation in interactions into networks.
+Despite this additional information, empirical descriptions of ecological networks are usually limited to static representations of the communities they describe.
 That is, whether the network is assembled based on aggregated data, a single intensive ``snapshot" sample, or expert knowledge, interactions are assumed to occur deterministically wherever and whenever the community is observed~\citep{Olesen2011a}.
 
-    % The assumption of static communities contrasts with the known stochasticity of ecological communities~\citep{Gotelli2000}.
+    The assumption of static communities contrasts with the known stochasticity of ecological communities~\citep{Gotelli2000}.
 Community composition and abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}.
@@
 Interactions can be lost if the interaction partners remain present but are separated in time or are too rare to detect each other~\citep{Tylianakis2010}.
-Interactions can also fail to occur because of environmental contingencies~\citep{Poisot2015} or individual preferences~\citep{Fodrie2015}.
+Interactions can also fail to occur because of environmental contingencies~\citep{Poisot2015}, or because of individual preferences~\citep{Fodrie2015}.
 
-    % Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007}).
-An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to document interactions than species~\citep{Poisot2012,Bartomeus,others}.
+    Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007}).
+An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to document interactions than species~\citep{Poisot2012}.
 As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Poisot2016}.
@@
 
-    % Despite these efforts, we currently lack the quantitative methodology to deal with uncertainty generated by spatiotemporal variation in ecological interactions and by limited sampling.
-[[cite previous attempts]] Even in well-sampled networks, uneven sampling across species can lead to the inference that some species do not interact because they co-occur rarely or have not yet been observed together - even if they do interact when they do co-occur (see Fig.~\ref{histograms}).
+    Despite these efforts, we currently lack the quantitative methodology to deal with uncertainty generated by spatiotemporal variation in ecological interactions and by limited sampling.
+Even in well-sampled networks, uneven sampling across species can lead to the inference that some species do not interact because they co-occur rarely or have not yet been observed together - even if they do interact when they do co-occur (see Fig.~\ref{histograms}).
 Nearly all network studies will thus neglect some interactions, necessitating an approach that acknowledges this uncertainty.
 
-    % In this study, we formalise the description of interactions between species as probabilities and develop analytical tools to capture the uncertainty in the estimation of these interactions.
+    In this study, we formalise the description of interactions between species as probabilities and develop analytical tools to capture the uncertainty in the estimation of these interactions.
 We focus on binary interactions as a first step, but the framework could be expanded to deal with interaction frequencies or strengths.
@@
 Presences and absences are not, however, equally certain.
-An observed link definitely occurred (assuming we can correctly identify the species involved), but there are multiple reasons why a given link may not be observed \emph{whether or not the interaction truly occurred}.
-Moreover, given an unobserved interaction in an empirical dataset, we often cannot determine why the interaction did not occur \emph{post hoc}.
-The detection of any interaction is a stochastic process subject to many levels of uncertainty.
-As a conceptual guide to the factors affecting this process, we describe three nested levels of uncertainty that roughly address the questions: "Could species $i$ and $j$ interact?", "Did they interact?" and "Did we observe the interaction?" (Fig.~\ref{conceptual_fig}).
+An observed link definitely occurred, but there are multiple reasons why a given link may not be observed \emph{whether or not the interaction truly occurred}.
+The detection of any interaction is a stochastic process.
+We define three nested levels of uncertainty contributing to this stochasticity: interaction uncertainty, process uncertainty, and detection uncertainty (Fig.~\ref{conceptual_fig}).
 
-        \subsubsection*{Could the species interact?}
+        \subsubsection*{Interaction uncertainty}
 
-          First, and most fundamentally, some interactions are feasible if a pair of species should co-occur while others are not~\citep{Poisot2015}.
-Assuming that the feasibility of interactions depends on the traits of species involved, we can define the probability of an interaction $L$ given some description of trait-matching $\mathbf{T}$ as $P(L|\mathbf{T}) = \lambda$~\citep{Bartomeus2013,Gravel2013,Weinstein2017}.
-          In some cases the traits prohibiting an interaction are known, and there will be little uncertainty about $\lambda$.
-          In most cases, however, it is not known what traits might prohibit an interaction~\citep{Dormann2017}.
-Pollinators may visit plants outside of those predicted based on "pollination syndromes"~\citep{Weinstein2017a} and herbivores may consume animal prey when it becomes accessible~\citep{Furness1988,Pietz2000}.
-These examples illustrate the danger in assuming that seemingly unlikely interactions cannot occur.
+          First, and most fundamentally, a pair of species may or may not have the appropriate characteristics (or traits) to interact.
+We define the probability of an interaction $L$ given characteristics $\mathbf{T}$ as $P(L | \mathbf{T})=\lambda$.
+Some species pairs, such as a salmon and a saguaro cactus, have incompatible traits and would never interact even if they should co-occur.
+In such cases, $\lambda = 0$ and there is no uncertainty.
 
-          An unobserved interaction may be a rare phenomenon with $\lambda>0$ and the associated zero in an interaction matrix might be false.
-This uncertainty is partly addressed by trait-matching models in which species with better-matched traits are more likely to interact~\citep{Bartomeus2016,Jordano2016,Weinstein2017}.
-As these models improve and include better information about the influence of traits on interactions, the uncertainty will be reduced~\citep{Jordano2016} and $\lambda$ should either tend to 0 or to 1.
-Nevertheless, every model is imperfect and lacks information that could be used to define constraints on at least some interactions~\citep{Dormann2017}.
-Until these gaps are filled, some uncertainty will remain about whether some species pairs could interact.
+          Most species pairs, however, do not have traits that absolutely prevent an interaction.
+This means that it is generally unclear whether an unobserved interaction is impossible or simply a rare phenomenon with $\lambda>0$.
+This uncertainty is partly addressed by trait-matching models in which species with better-matched traits are more likely to interact~\citep{Bartomeus2016}.
+As these models improve and include better information about the influence of traits on interactions, the uncertainty will be reduced and $\lambda$ should either tend to 0 or to 1.
+Nevertheless, every model is imperfect and lacks information that could be used to define constraints on interactions~\citep{Dormann2017}.
+Some interaction uncertainty is therefore inevitable.
 
-        \subsubsection*{Did the species interact during sampling?}
+        \subsubsection*{Process uncertainty}
 
-          Assuming that an interaction is feasible (i.e., $L=1$;), an interaction may still not occur at a particular place or time~\citep{Poisot2015,Graham2018}.
-This could be because constraints such as inclement weather or low abundance prevented the interaction~\citep{Jordano2016,Graham2018}, a more preferred interaction partner was available~\citep{Weinstein2017a}, or substantial individual variation in traits meant that local individuals could not interact even if the species in general can~\citep{Gravel2013,Wells2013,Poisot2015}.
-For example, a rare galler may not parasitize a rare plant because they do not encounter each other.
-In metawebs describing a community found at several sites, an interaction may also fail to occur because two species do not co-occur at a particular site even if they do co-occur and interact elsewhere~\citep{Graham2018}.
-We can define the local realisation of an interaction, $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L=1)=\chi$.
-It is unlikely that $\chi=1$  except in the case of obligate specialists who always interact whenever they co-occur and always co-occur.
-When $\chi<1$ we cannot be sure whether an unobserved interaction cannot occur or whether it simply did not occur at a particular site.
+         Even a feasible interaction, i.e.
+$L=1$, still may not occur at a given location or moment in time because of local constraints such as inclement weather or unsuitable habitat.
+We define the local realisation of an interaction, $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L=1)=\chi$.
+This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology  on the topic.
+Phenological matching~\citep{MillerRushing2010,Gezon2016}, species preferences~\citep{Pires2011,Novak2015,Coux2016}, and fear effects~\citep{Luttbeg2005,Wirsing2008} are just some of the factors contributing to variation in the frequency of interactions between a given pair of species.
+Some of these factors can be addressed in mesocosm studies of networks (e.g., environmental conditions can be held stable) or could be included in models along the line of trait-matching models (e.g., phenological matching).
+In the field, however, process uncertainty is likely inevitable.
 
-          Some of the uncertainty about $\chi$ could be addressed by drawing on the rich literature about interaction contingencies found in community ecology.
-Phenological matching~\citep{MillerRushing2010,Gezon2016}, species preferences~\citep{Pires2011,Novak2015,Coux2016}, and fear effects~\citep{Luttbeg2005,Wirsing2008} all affect the probability of an interaction occurring at a particular site and time, and could be included in models similar to trait-matching models.
-Alternatively, interaction probabilities could be tested in mesocosm studies with constant conditions.
-Some studies attempt to reduce uncertainty by sampling intensively over a short period of time and restricting the scale of interest to interactions occurring at the sampling site and time (conflating $\chi$ and $\lambda$)~\citep{Bartomeus2013,Weinstein2017,Weinstein2017a}.
-This approach may be suitable for some research questions, but is not appropriate if we wish to assemble the full set of interactions which occur in a community (beyond the specific site and time of sampling).
-In contrast, expanding sampling to cover a broader spatial or temporal range (e.g., sampling in a variety of microhabitats or during a variety of weather conditions) will help to reduce uncertainty about $\chi$ by including a broader range of parameters affecting interaction probability.
-It is unlikely, however, that resources will permit researchers to sample in the full range of sites and conditions covered by a community, and some uncertainty about $\chi$ will remain.
+         One proposed solution to the problem of process uncertainty is to use repeated sampling of networks.
+For example,~\citet{Weinstein2017} used repeated sampling to estimate the daily probability of detecting an interaction and thereby model detection and process uncertainty.
+While conceptually attractive, this approach is unsuitable for interactions occurring over longer time scales (e.g., associations between hosts and parasitoids with a single generation per year), or very rare interactions which might not occur on any of the sampling days.
+Moreover, the faster accumulation of species than interactions means that repeated sampling will tend to introduce more unobserved interactions than observed interactions unless the number of samples is very high~\citep{Poisot2012}.
 
-         % One proposed solution to the problem of process uncertainty is to use repeated sampling of networks.
-For example,~\citet{Weinstein2017-wrong one?} used repeated sampling to estimate the daily probability of detecting an interaction and thereby attempted to separate detection and process uncertainty.[[This apparently confused R3]] While conceptually attractive, this approach is unsuitable for interactions occurring over longer time scales (e.g., associations between hosts and parasitoids with a single generation per year), which would require multi-year sampling efforts, or very rare interactions which would require extremely high sampling effort to detect.
-Moreover, the faster accumulation of species than interactions means that repeated sampling will tend to introduce more unobserved interactions than observed interactions unless the number of samples is high enough to ensure that all species present have been observed~\citep{Poisot2012,Jordano2016}.
-
-          \textbf{Forbidden links}
-
-            Both whether species can interact and whether they do interact at a particular place and time have been discussed in the context of "forbidden links"~\citep{Jordano2016}.
-In this framework, all links which are prevented by spatio-temporal uncoupling, physiological constraints, etc.
-are considered "structural zeros" that cannot be observed~\citep{Jordano1987,Jordano2016}.
-We conceptually distinguish between physiological constraints and spatio-temporal uncoupling to allow for cases in which a species is introduced to a new habitat, expands its range, or shifts phenology~\citep{Gravel2013}.
-In such cases, links which are forbidden due to physiological constraints remain forbidden but links previously forbidden due to spatio-temporal mismatch could potentially occur.
-
-        \subsubsection*{Did we observe all interactions that occurred?}
+        \subsubsection*{Detection uncertainty}
 
           Lastly, measurement errors are a pervasive source of uncertainty in the observation of ecological processes.
-Even if an interaction is feasible and occurs during sampling ($L = 1$ and $X = 1$), we may still fail to detect it~\citep{Jordano2016,Weinstein2017}.
+Even if an interaction is feasible and occurs during sampling ($L = 1$ and $X = 1$), we may still fail to detect it.
 We may define the probability of detecting of an interaction, $D$, given the interaction is feasible and occurs, as a stochastic process with the associated probability $P(D|X=1,L=1)=\delta$.
 Detection failure could happen for many reasons (see~\citet{Wirta2014} for examples and partial solutions to them).
-Some sources of detection error can be minimised with appropriate sampling effort (e.g., combining plant-focused and animal-focused sampling when assembling pollination networks~\citet{Jordano2016}), but other sources are often difficult to reduce.
-For example, cryptic species might require molecular analysis for appropriate taxonomic identification~\citep{Wirta2014,Frost2016} or it may not be possible to sample some species due to conservation concerns~\citep{Lagrue2015}.
+Some sources of detection error can be minimised with appropriate sampling effort ($\delta$ will approach one with increasing number of samples), but other sources are often difficult to reduce (e.g.
+the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification as in~\citealt{Wirta2014,Frost2016}).
+The absence of an interaction on a given day could therefore be because it was not feasible [$P(L) = 0$], was feasible but did not occur because of local conditions during sampling ($P(X|L=1) = 0$], or was feasible and occurred during sampling but could not be observed [$P(D|X=1,L=1)=0$].
+Because we cannot separate these possibilities, repeated sampling fails to satisfactorily address the uncertainty inherent in empirical networks.
 
-          Some types of interactions will have higher detection uncertainty than others.
-Pollination, for example, occurs briefly and does not leave long-lasting evidence, while parasitism can be a lifelong association between species.
-Even long-term interactions can be missed, however, especially if species are difficult to identify or if not all individuals of a species share the interaction~\citep{Wells2013,Cirtwill2016}.
-Parasites, for example, are often concentrated in only a few individuals~\citep{Lagrue2015}.
-If these infected individuals do not happen to be included in a sample, their interactions will be missed.
-Detection probabilities also vary widely between species, and potentially individuals within species, due to different abundances and behaviours~\citep{Wells2013,Weinstein2017}.
+    \subsection*{Estimating detection and process uncertainty}
 
-    \subsection*{Can't we just sample more?}
-
-        To sum up, the absence of an interaction on a given day could  be because it was not feasible [$P(L) = 0$], was feasible but did not occur because of local conditions during sampling ($P(X|L=1) = 0$], or was feasible and occurred during sampling but could not be observed [$P(D|X=1,L=1)=0$].
-Note that some exteral factors can affect more than one level of uncertainty.
-For example, rare species are less likely to interact at a given site due to neutral processes~\citep{Jordano2016,Graham2018}.
-Interactions involving rare species are also less likely to be detected, unless more sampling effort is focused on rare than common species~\citep{Bartomeus2013,Jordano2016}.
-Thus, abundance affects both the probability of an interaction occurring at a particular site \emph{and} our ability to observe the interaction.
-
-        When considering a metaweb, we wish to separate the unobserved interactions where $L = 0$ (i.e., unfeasible interactions) from interactions which could occur but did not at a particular sampling site or which occurred but were not detected (Fig.~\ref{conceptual_fig}).
-Unfortunately, this is not possible for most interactions (except those where we know an interaction is truly not feasible).
+        An observed interaction indicates that an interaction was feasible, occurred during sampling, and was detectable ($L = 1$, $X = 1$, and $D = 1$).
+An unobserved interaction could be due to any of the three sources of uncertainty ($D$, $X$, and/or $L = 0$).
+Only the case where $L = 0$ is an interaction that never occurs --the usual interpretation of a $0$ value in an interaction matrix.
+It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e.
+where the interaction occurred at the location but was not observed, and $X = 0 \cup L =1$, i.e., where the interaction is feasible but did not occur at the local site (Fig.~\ref{conceptual_fig}).
+        This is not possible, however, using empirical data.
 An empirical ecologist will instead measure the marginal probability $P(L) = k/n$, where $k$ is the number of observed interactions and $n$ the number of observed co-occurrences.
@@
         The obvious rule of thumb to reduce uncertainty is ``sample more".
-Where resources permit, increasing sample sizes will reduce uncertainty about the upper bound of the interaction probability and will also increase the probability of detecting unlikely or cryptic interactions (e.g., interactions where $L$=1 but process or detection uncertainty is high).
+Increasing sample sizes will reduce uncertainty about the upper bound of the interaction probability and will also increase the probability of detecting unlikely or cryptic interactions (e.g., interactions where $L$=1 but process or detection uncertainty is high).
 Despite these benefits, we note that there are limits to the utility of increased sampling.
 Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig.~\ref{histograms}C).
-While this improves our understanding of the set of species present in the community, it introduces yet more uncertainty into the interaction matrix.
-Note that it is better to identify the set of potential interactions than to miss a species, so sampling effort should not be reduced in order to exclude rare species.
+Thus, the more we sample, the more zeros will appear in our interaction matrix.
 
@@
 For both molecular and rearing techniques, certain types of interactions may go unnoticed due to technical challenges~\citep{Wirta2014}.
-This can bias the set of recorded interactions towards those that are easier to observe~\citep{Carstensen2014,Jordano2016}.
-Combining multiple sampling types can reduce this type of bias~\citep{Wirta2014,Jordano2016}.
-Nevertheless, despite substantial improvements in recent decades, most available interaction networks are still undersampled and, moreover, are only subsets of larger communities~\citep{Bartomeus2013,Jordano2016}.
+This can bias the set of recorded interactions towards those that are easier to observe.
 
-        In short, high-quality sampling is an essential component of ecological network construction and increasing sampling (length of time, number of sites, number of distinct methods, etc.) can reduce some of the uncertainty about unobserved interactions.
-We believe, however, that empirical researchers generally sample to the maximum extent possible given constraints of time, resources, and study sites.
-This practical constraint means that reducing one source of uncertainty is likely to increase another source (e.g., sampling intensively at a single site may reduce detection uncertainty but will increase uncertainty due to variation between sites).
-The number of observed co-occurrences needed to believe that an unobserved interaction cannot occur is very high (about 35; Fig.~\ref{upper_limits}), and most datasets will not include this level of sampling for all pairs of species~\citep{Bartomeus2013}.
-For pairs of species with fewer observations, we can reduce uncertainty by combining the observed data available with prior knowledge about the system.
-This is straightforward to do using a Bayesian approach, as detailed below.
+        Most importantly, if two species are never observed co-occurring during several days of sampling then repeated sampling reveals nothing about their probability of interacting should they ever co-occur.
+Intensive sampling is, therefore, an important step towards reducing uncertainty in ecological networks but is unlikely to be enough in most cases.
+To supplement repeated sampling efforts and reduce uncertainty around unobserved interactions, we suggest researchers use prior knowledge of the same or similar systems.
+Here, we outline a Bayesian approach to combining repeated sampling and prior knowledge in probabilistic networks.
+We then demonstrate how to construct such a probabilistic network using an intensively and repeatedly sampled empirical dataset.
+Finally, we show how a probabilistic understanding of a network allows us to establish confidence intervals around measures of network structure.
 
@@
 
-    % Maybe we can move much of this to the Box and satisfy reviewer 1
-
-    % We are most interested in how to quantify an interaction probability, and its associated uncertainty, for interactions that have not been observed.
-For interactions which have been observed, methods already exist to quantify the probability of the interaction.
-
-    % Assume that a pair of species has been observed co-occurring $n$ times and interacting in $k = 0$ cases.
+    We are most interested in how to quantify an interaction probability, and its associated uncertainty, for interactions that have not been observed.
+Assume that a pair of species has been observed co-occurring $n$ times and interacting in $k = 0$ cases.
 We want to know the probability $\lambda$ that the species would be observed interacting if not constrained by local conditions, imperfect detection, etc.
@@
 
-    %     \begin{equation}
-    %       \lambda_{MLE} = \frac{k}{n}  .
-    %       \label{theta_MLE}
-    %     \end{equation}
+        \begin{equation}
+          \lambda_{MLE} = \frac{k}{n}  .
+          \label{theta_MLE}
+        \end{equation}
 
-    % Note that $\lambda$ is not a point estimate but rather a random variable with an unknown distribution.
+    Note that $\lambda$ is not a point estimate but rather a random variable with an unknown distribution.
 This means that if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact.
@@
 
-    % To properly interpret $\lambda$, we need to estimate the variance as well as the MLE.
+    To properly interpret $\lambda$, we need to estimate the variance as well as the MLE.
 The variance of a Bernoulli experiment is $n\lambda$(1-$\lambda$) and, importantly, describes the variability of the number of successes $k$ for $n$ trials rather than the variance associated with the estimation of $\lambda$.
@@
 
-    % All of the above methods for estimating the variance of $\lambda$ include the number of samples $n$.
+    All of the above methods for estimating the variance of $\lambda$ include the number of samples $n$.
 This means that where the number of samples $n$ is very low (e.g., for rare species), there will be considerable uncertainty around our estimate of $\lambda$.
@@
 
-    The basis of a Bayesian approach to modelling the probability that an interaction occurs ($\lambda$) is combining the maximum likelihood estimate (MLE) of $\lambda$ with a prior distribution (described in the next section) and a normalising function.
-The MLE of $\lambda$ can be modelled as a Bernoulli trial based on the number of observed interactions $k$ and observed co-occurrances $n$: $\lambda = \frac{k}{n}$.
-The most appropriate prior distribution for a probability such as $\lambda$ is the beta distribution:
+    The Bayesian approach combines the MLE of $\lambda$ described above with a prior distribution and a normaliser to give a posterior distribution.
+Since $\lambda$ is a probability and bounded between 0 and 1, the most appropriate prior distribution is the beta:
 
@@
 
-    The shape parameters, or hyperparameters, may be set to particular values or derived from some data (see below).
-Combining the prior distribution with the MLE of $\lambda$ derived from observed data, we obtain a posterior distribution that also follows a beta distribution with new parameters $\alpha'= \alpha+k$ and $\beta'=\beta+n-k$ (see~\emph{Appendix S2} for details).
-The influence of the prior on the posterior distribution can be understood from these parameter definitions: the difference between the posterior and the prior will increase with $k$ and $n-k$.
-In other words, the distribution of $\lambda$ for better-sampled pairs of species will rely less on the information used to build the prior distribution and depend more on the observed data and uncertainty about the probability of the pair interacting will decrease (Fig.~\ref{Salix_pdfs_cdfs}).
+    Combining the beta-distributed prior with the binomial-distributed MLE of $\lambda$ is straightforward (see~\emph{Appendix S2}).
+By doing so, we obtain a posterior distribution that follows a beta distribution with new parameters $\alpha'= \alpha+k$ and $\beta'=\beta+n-k$.
+The weight of the prior on the posterior distribution can be understood from these parameter definitions: the difference between the posterior and the prior will increase with $k$ and $n-k$.
+In other words, the distribution of $\lambda$ for better-sampled pairs of species will rely less on the information used to build the prior distribution and depend more on the observed data.
+When plotted, we find the shape of the distribution gets narrower with $k$ and $n$ (Fig.~\ref{Salix_pdfs_cdfs}).
 
-    % R1 suggests removing this - could be in the SI I guess?
-    % \subsubsection*{Moments and other properties}
+    \subsubsection*{Moments and other properties}
 
-    %   It is common to perform analyses that require calculating higher-order network properties in interaction networks.
+      It is common to perform analyses that require calculating higher-order network properties in interaction networks.
 The fact that the posterior distribution of $\lambda$ follows a beta distribution makes it straightforward to compute moments and other properties needed for these analyses.
 
-    %   The \textbf{average} of $\lambda$ is: 
-    %       \begin{equation}
-    %         \bar{\lambda} = \frac{\alpha+k}{\alpha+\beta+n} ,
-    %         \label{mean}
-    %       \end{equation}
+      The \textbf{average} of $\lambda$ is: 
+          \begin{equation}
+            \bar{\lambda} = \frac{\alpha+k}{\alpha+\beta+n} ,
+            \label{mean}
+          \end{equation}
 
-    %     and its \textbf{variance} is:  
-    %       \begin{equation}
-    %         Var(\lambda|k) = \frac{(\alpha + k)(\beta + n - k)}{(\alpha + \beta + n)^{2}(\alpha + \beta + n +1)}
-    %         \label{variance}
-    %       \end{equation}
+        and its \textbf{variance} is:  
+          \begin{equation}
+            Var(\lambda|k) = \frac{(\alpha + k)(\beta + n - k)}{(\alpha + \beta + n)^{2}(\alpha + \beta + n +1)}
+            \label{variance}
+          \end{equation}
 
-    %     The \textbf{mode} of the distribution is:
-    %       \begin{equation}
-    %         \hat{\lambda} = \frac{\alpha + k - 1}{\alpha + \beta + n - 2} .
-    %         \label{mode}
-    %       \end{equation}
+        The \textbf{mode} of the distribution is:
+          \begin{equation}
+            \hat{\lambda} = \frac{\alpha + k - 1}{\alpha + \beta + n - 2} .
+            \label{mode}
+          \end{equation}
 
@@
 
-      The choice of prior distribution will reflect the goal of a study, the amount of prior knowledge available, and the strength of researchers' belief in that prior knowledge.
-Note that there is no 'correct' prior as long as we do not know the true distribution of interaction probabilities~\citep{Spiegelhalter2000}.
-The goal is to select a reasonable prior that reflects our assumptions about the true distribution, and then adjust this prior with observed data as it becomes available.
-When in doubt, it is also possible to model interaction probabilities using a variety of priors and then compare results~\citep{Spiegelhalter2000}.
-Some researchers may be reluctant to adopt a Bayesian approach because of its perceived subjectivity (i.e., the metaweb we obtain will depend upon the assumptions used when developing a prior).
-We argue that one of the advantages of the Bayesian approach is that it makes some of the subjectivity inherent in network construction explicit.
-Researchers compiling empirical networks face many decisions about where to set community boundaries, the set of species to include in the focal community~\citep{Jordano2016}, what type of sampling is most appropriate~\citep{Wirta2014}, etc.
-All of these choices will affect the compiled network and most do not have clear answers, making all empirical networks (and all theoretical networks, which likewise depend upon the assumptions used in building the network) to some extent subjective.
-In addition, researchers distinguishing "forbidden links" inherently rely on prior knowledge to identify these links~\citep{Jordano2016}.
-Stating that an interaction is "forbidden" is, in effect, applying a very strong prior to reduce/eliminate uncertainty about the non-observation of that interaction.
-Given this reality, we feel it is better to make the assumptions used to build a network as explicit as possible so that these assumptions can be questioned, compared between studies, and tested.
+      Parameters $\alpha$ and $\beta$ determine the shape of the prior distribution of $\lambda$, which follows a beta distribution.
+These are called hyper parameters.
+The prior may be chosen to be uninformative, if no external information is available, or may draw on information such as distributions of connectance across webs, degree distributions, or trait-matching functions (see \emph{Appendix S3} for details and a simple quantitative example).
 
-      \textbf{Uninformative priors}
-
-        If researchers wish to reflect uncertainty in their data without applying any particular assumptions/prior knowledge or account for the possibility that the distribution of probabilities of interaction may vary, they can select $\alpha$ and $\beta$ to produce an intentionally uninformative prior~\citep{Leyland2005,Berger2006}.
-This prior can then be given a low weight, such that any observed data will outweigh the prior distribution.
-For pairs of species with little or no observed data, an uninformative prior will leave large variance about $\lambda$ and reflect our lack of knowledge about the pair.
-Since we model $\lambda$ as a Bernoulli trial, the appropriate uninformative prior is Jeffreys prior: a beta distribution with $\alpha$=$\beta$=0.5.
-The sum of $\alpha$ and $\beta$ is roughly equivalent to the weight of the prior, so Jeffreys prior has equal weight to a single observation.
-
-      \textbf{Informative priors}
-
-        In most cases, we have at least some prior knowledge about a system which we can use to reduce uncertainty about interactions.
-One common example is the well-justified assumption that plants will not consume animals in a food web; excluding carnivorous plants it is not contentious to say that we have little to no uncertainty about unobserved links describing plants feeding on animals.
-Similarly, if we observe two species which are normally obligate mutualists co-occurring but not interacting, we would be very doubtful that a zero reflecting this interaction was true (i.e., high uncertainty about this zero).
-It is straightforward to extend the intuition behind these special cases to the full set of species in a network using trait-based models, as long as the traits likely to affect interaction probabilities are known (e.g.,~\citet{Riede2011,Gravel2013,Bartomeus2016,Weinstein2017}).
-Models for interaction probabilities could also include information on abundances, phenological matching, co-occurrence etc.
-as available~\citep{Jordano2016,Weinstein2017a,Graham2018}.
-This approach allows us to tailor the level of uncertainty surrounding each interaction based on the species involved but involves many assumptions about which parameters affect interaction probabilities and the strength and shapes of these relationships.
-There is, therefore, a risk of over-fitting with complicated trait-based models.
-Also note that researchers wishing to test whether a particular trait influences interaction probabilities should either exclude that trait from their prior or model the network using priors which include and exclude the trait of interest (as in~\citet{Weinstein2017,Weinstein2017a}).
-
-        Alternatively, it is possible to develop a prior based on the properties of a set of published networks (i.e., "reference Bayes"~\citet{Spiegelhalter2000}).
-While this type of prior does not allow for the prior distribution to vary between species pairs, it relies on fewer assumptions about the forces structuring interaction probabilities.
-Instead, we assume only that the focal network will have similar structural properties to those of published networks.
-For example, connectance ($C=L/S^2$, where $L$ is the number of interactions and $S$ is the number of species) is available for many networks.
-The distribution of these connectances can be used to predict the distribution of interaction probabilities in a new network.
-If we know the mean $\overline{C}$ and variance $\sigma_C^2$ of a distribution of connectances, then the hyperparameters are:
-
-        \begin{equation}
-        \alpha = \overline{C}(\frac{\overline{C}(1-\overline{C})}{\sigma_C^2}-1) ,
-        \end{equation}
-
-        \begin{equation}
-        \beta = (1-\overline{C})(\frac{\overline{C}(1-\overline{C})}{\sigma_C^2}-1) .
-        \end{equation}
-
-        Note that, in this case, the prior distribution will be the same for all interaction probabilities.
-It is also possible to use other interaction probabilities.
-For example, species' degrees (numbers of interaction partners) in a similar network or networks could be normalised (divided by the number of potential interaction partners) and interpreted as an interaction probabilities (i.e., "empirical Bayes"~\citep{Spiegelhalter2000}).
-The distribution of these interaction probabilities can be used to inform a prior distribution as show in \emph{Appendix S3}.
-When using network summary statistics or degree distributions, it is important to consider whether the available information reflects what we truly believe about the network.
-Given the likelihood that most published networks are undersampled~\citep{Jordano2016}, it may be wise to include only the highest-quality networks available in a prior.
-Likewise, only the degree distribution for a similar system is likely to be a reasonable prior for a focal system.
-For example, if the system is a large network containing many plant species and insects from different families it is inappropriate to use a prior distribution drawn from a small network describing interactions between different genotypes of a single plant species and a set of closely-related insects (see \emph{Appendix S6} for a demonstration).
+      It is important to ensure that an informative prior accurately reflects the focal  system.
+For example, if the system is a large network containing many plant species and insects from different families, it is inappropriate to use a prior distribution drawn from a small network describing interactions between different genotypes of a single plant species and a set of closely-related insects.
 The similarity of traits across genotypes within a species means that an insect which interacts with one genotype is likely to interact with many others.
@@
 
-        If a similar dataset is not available, it is also possible to use data from the study at hand to develop a prior (i.e., "approximate Bayes"~\citet{Gelmanblog})~\citep{Casella1985,Spiegelhalter2000}.
-This approach is used in medical testing~\citep{Copas1972,Spiegelhalter2000} and disease modelling~\citep{Leyland2005,Brooks2015} using information from pilot studies and can easily be applied to ecological systems.
-Returning to the example of degree distributions, this approach allows us to use information from abundant and easily-sampled species to predict interaction probabilities for species which were observed only rarely.
-Despite its practicality, approximate Bayes has been criticized for being overly subjective~\citep{Berger2006} and because estimating hyperparameters from data serves as an approximation of some true hyperparameters which remain unknown~\citep{Gelmanblog}.
-We therefore encourage researchers to carefully consider whether external data or an appropriate trait model is available before opting for a prior based on some of their own data.
-Nevertheless, there are likely to be many situations where approximate Bayes provides the best way to describe the uncertainty in the dataset.
-We illustrate this approach in the following empirical example.
+      The choice of prior will depend on the information available.
+In general, it is best to use a prior taken from a similar system as emphasised above.
+If such data are not available, a prior based on many networks with a similar level of resolution could be useful, as could a prior based on a preliminary round of sampling (analogous to ``training data").
+If there is no suitable informative prior, it is best to use an explicitly uninformative prior.
+While an uninformative prior will not greatly reduce variance about $\lambda$, it does clearly state our lack of prior knowledge and will not bias our conclusions.
 
@@
 
-      To illustrate the process of constructing a Bayesian network to quantify uncertainty about interactions, we use the comprehensively-sampled system of willows (\emph{Salix}), herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}.
+      To illustrate the process of constructing a Bayesian network, we use the comprehensively-sampled system of willows (\emph{Salix}), herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}.
 This dataset consists of a single community type sampled across Europe over 29 years and at 374 unique locations.
+The data were collected over 29 years at 374 unique locations across Europe.
 The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (see \emph{Appendix S4} for details).
-      The high spatiotemporal resolution of this dataset make it ideal for illustrating the difficulties in completely sampling a network; even with such an unusually high sampling effort, we anticipate that there will be many pairs of species which were rarely or never observed together.
-Using the Bayesian framework above, we can identify which potential interactions are more and less uncertain, allowing us to better predict the true structure of the metaweb.
+
+      The high spatiotemporal resolution and unusually high sampling effort of this dataset make it well suited for illustrating the difficulties in completely sampling a network.
 To show the gaps in sampling, we compared the frequencies of observed co-occurrences and interactions.
-We then calculated an empirical prior and computed the posterior distribution of the probability of an as-yet-unobserved interaction being feasible ($\lambda$).
 We analysed both the \emph{Salix}-galler and galler-natural enemy components of the network but, for brevity, present only the latter here (see~\emph{Appendix S5} for \emph{Salix}-galler results).
@@
         To treat each interaction as a Bayesian probability, we will combine the observed data with a distribution based on prior information.
-While a strict Bayesian framework requires a prior distribution that does not rely on any information from the study at hand, such data are not always available.
-In that case, researchers must choose between using a less-informative prior (e.g., one based on distributions of links across a large set of networks) or an empirical prior based on some "training data" from the study.
-Here, we opted for the latter and created priors using a single sub-network from the middle of the geographical distribution of the~\citet{Kopelke2017} dataset.
+A strict Bayesian framework requires a prior distribution that does not rely on any information from the study at hand.
+If such data are not available, one might instead use the first sub-network collected as ``training data" to guide future sampling.
+To simulate this situation, we created priors using a single sub-network from the middle of the geographical distribution of the~\citet{Kopelke2017} dataset.
 To demonstrate how the use of data from a different system can affect the prior distribution and conclusions based on it, we repeated our analyses using priors derived from a much smaller \emph{Salix}-galler-natural enemy system based around genotypes of a single \emph{Salix} species~\citep[Data available from the Dryad Digital Repository: https://doi.org/10.5061/dryad.g7805]{Barbour2016}\nocite{Barbour2016Dryad}.
@@
 
-      Researchers are often interested in measures of network structure rather than the network itself.
+      Researchers usually use interaction matrices as a tool to calculate measures of network structure.
 Computing most network metrics is straightforward when the different $\lambda$ of the adjacency matrix are known and assumed not to vary~\citep{Poisot2016}.
@@
 By Jensen's inequality~\citep{Jensen1906}, this means that the average of a network metric (a function of stochastic interactions) is not the same as the network metric calculated based on the average interaction probability.
-Thus, any uncertainty in the values of $\lambda$ could bias both the mean and variance of network metrics, giving misleading results (simulated in \emph{Appendix S1}).
-One way to avoid this situation is to calculate the properties of a suite of simulated networks~\citep{Vazquez2005,Guimera2009}.
+Any uncertainty in the values of $\lambda$ could bias both the mean and variance of network metrics, giving misleading results (simulated in \emph{Appendix S1}).
+One way to avoid this situation is to calculate the properties of a suite of simulated networks.
 
       Using the prior distributions and procedures described above, we calculated posterior probability distributions for species pairs that were not observed interacting.
-Using these posterior distributions and assuming probabilities of 1 for pairs of species that were observed interacting (see \emph{Appendix S2} for a justification), we created a suite of 100 webs by randomly sampling from each posterior distribution.
-Each of these webs is a prediction of the structure of the metaweb.
+Using these posterior distributions and assuming probabilities of 1 for pairs of species that were observed interacting, we created a suite of 100 webs by randomly sampling from each posterior distribution.
 After obtaining these posterior networks, we calculated the connectance of each web, as well as the mean number of links per galler and per natural enemy, and the nestedness (NODF) of the network.
-This gives us an estimate for each property reflecting our uncertainty about $\lambda$.
-
-      Measures of network structure which are based on empirical networks that are missing interactions may differ substantially from the values that would be obtained if detection certainty and variation in interactions over space and time could be removed.
-To demonstrate this, we created a suite of filtered networks for each posterior network.
-Taking a posterior network as the "true" network, we randomly sampled 90\%, 80\%, 70\%, 60\%, 50\%, 40\%, 30\%, 20\%, and 10\% of the interactions to create a new "filtered" network.
-This gradient is akin to a gradient of uncertainty in the network (e.g., due to varying sampling effort or intraspecific trait variability).
-For each level of uncertainty, we created 100 randomly-sampled networks per posterior-probability network (giving 100 posterior networks and 1000 filtered networks).
-We calculated the same network properties as described above for all posterior and filtered networks.
+To demonstrate how these network metrics will be affected by detection uncertainty, we then created a suite of filtered networks for each posterior network.
+Networks were filtered by randomly sampling 99\%, 95\%, 90\%, 80\%, 70\%, 60\%, and 50\% of the interactions included in each posterior network.
+This gradient is akin to a gradient of sampling effort.
+For each level of detection accuracy, we created 100 randomly-sampled networks per posterior-probability network (giving 100 posterior networks and 1000 detection-filtered networks).
+We calculated the same network properties as described above for all posterior and detection-filtered networks.
 
@@
 
-  We obtained prior parameters of $\alpha$=0.700, $\beta$=8.49, giving a beta distribution strongly skewed towards 0.
-Where $n=0$, these parameters gave a posterior distribution with $\bar\lambda$=0.076, var($\lambda$)=0.008.
-When $n=374$, we obtained a posterior distribution with $\bar\lambda_{ij}$=1.83 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=4.76$\times10^6$.
+  We obtained prior parameters of $\alpha$=0.700, $\beta$=8.49.
+Where $n = 0$, these parameters gave a posterior distribution with $\bar\lambda$=0.076, var($\lambda$)=0.008.
+When $n = 374$, we obtained a posterior distribution with $\bar\lambda_{ij}$=1.83 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=4.76.
 This distributions is very close to 0 with small variance about $\lambda$; if species $i$ and $j$ co-occurred 374 times without interacting, they   are extremely unlikely to do so at other sites or times.
@@
 
-  % Poisot2015 - also found that NODF was higher in the empirical data than in sims.
-
 \section*{Discussion}
 
-  A benefit of Bayesian estimation is that it allows us to make our assumptions more explicit (e.g., assuming that funding source for a medical trial may affect the reported outcome~\citep{Spiegelhalter2000}).
-
-  Real interaction networks vary over several dimensions~\citep{Kitching1987,Olesen2011a,Pires2011a,Baiser2012,Fodrie2015,Novak2015}, leading to pervasive under-estimation of interactions in published networks~\citep{Jordano2016}.
+  Real interaction networks vary over several dimensions~\citep{Kitching1987,Olesen2011a,Pires2011a,Baiser2012,Fodrie2015,Novak2015}, leading to pervasive under-estimation of interactions in published networks.
 Even in the most extensive data set that we could find, there was very little empirical data for each species pair.
 Most pairs of species were not observed co-occurring even once, less than 10\% of species pairs were observed interacting, and no pairs were observed to co-occur frequently enough to conclude that their probability of interacting was below 0.01.
-This suggests that limited sampling is a major source of uncertainty in empirical networks, in agreement with~\citet{Jordano2016,Weinstein2017a,Weinstein2017}.
+This suggests that limited sampling is a major source of uncertainty in empirical networks.
+This dataset also illustrates the problem of process uncertainty - pairs of species which were observed interacting did not interact in all of the samples in which they co-occurred.
+Increasing sampling is therefore likely to add more zeros than ones to an interaction network.
 
-  Detectability estimated at 23.3\% in~\citet{Weinstein2017a}
-
-  Although 374 sampling sites were not enough to obtain sufficient observations of all species pairs, we were able to reduce uncertainty about many potential interactions using a simple Bayesian framework.
-This framework allowed us to set appropriate confidence intervals about the probability of an unobserved interaction occurring, based on the distribution of interactions in one sample site.
-This gives us more reasonable estimates of interaction probabilities than assuming that no unobserved interactions actually occur.
-Such an approach is particularly useful when considering interactions involving species entering new ranges due to climate change or introductions.
-Understanding these species' interactions is important for a variety of conservation questions~\citep{Bartomeus2013,Gravel2013}, and a Bayesian approach using a trait-matching model or data from species' current ranges could help us to anticipate how species will integrate into new communities.
+  Using prior knowledge to build a Bayesian distribution for each interaction probability allows us to set appropriate bounds on interaction probabilities for species which were rarely or never observed co-occurring.
+In such cases, an informative prior distribution gives us more reasonable estimates of interaction probabilities than assuming that $p$=0 for unobserved interactions.
+This approach is particularly useful when considering interactions involving species entering new ranges due to climate change or introductions.
+Understanding these species' interactions is important for a variety of conservation questions, and a Bayesian approach using a trait-matching model or data from species' current ranges could help us to anticipate how species will integrate into new communities.
 
@@
 The structure of the well-sampled network used in our case study is most similar to the structure of simulated networks including only 50\% of the interactions suggested by the posterior distribution of interaction probabilities.
-This poor detection rate is similar to that reported in other studies~\citep{Bartomeus2013,Jordano2016,Weinstein2017a}.
-If our descriptions of empirical systems are generally missing so many feasible interactions, then it is vital to acknowledge this inherent uncertainty before comparing structures across systems or relating structure to stability.
+If our descriptions of empirical systems are missing up to half of the feasible interactions, then it is vital to acknowledge this inherent uncertainty before comparing structures across systems or relating structure to stability.
 
   Based on the framework described above, we can now offer some recommendations for improved descriptions of ecological interactions.
-Observing all interactions in a network is likely impossible~\citep{Jordano2016}, but researchers can take steps to address the uncertainty this implies.
 First, sample sizes should be as large as possible in order to reduce detection uncertainty.
-Second, researchers should acknowledge the varying levels of confidence surrounding interactions between species pairs.
-Including the $n$ and $k$ values for each interaction will clearly indicate which unobserved interactions are most likely to be observed with further sampling and which estimates are more reliable, as well as indicating potential sampling biases.
-Where there are strong prior expectations about pairs of species that will not interact, these should be explicitly stated so that readers know which zeros in an interaction matrix are based on observed data and which are based primarily upon expert knowledge.
+Second, where sampling on the order of 30-50 observations per species pair is not possible (i.e., in most cases), researchers should acknowledge the varying levels of confidence surrounding interactions between different species pairs.
+Including the $n$ and $k$ values for each interaction will clearly indicate which unobserved interactions are most likely to be observed with further sampling and which estimates are more reliable.
 Third, the uncertainty around interactions should be incorporated in calculations of network properties.
@@
 
-% \captionsetup{singlelinecheck=false, font={stretch=2}}
+\captionsetup{singlelinecheck=false, font={stretch=2}}
 
@@
     \begin{center}
-    \includegraphics*[height=.5\textheight]{figures/conceptual_fig.eps}
+    % \includegraphics*[height=.5\textheight]{figures/conceptual_fig.eps}
     % \includegraphics*[height=.5\textheight]{Figure_1.eps}
@@
       \begin{center}
-      \includegraphics*[height=.6\textheight]{figures/GP_histogram.eps}
+      % \includegraphics*[height=.6\textheight]{figures/GP_histogram.eps}
       % \includegraphics*[height=.6\textheight]{Figure_2.eps}
@@
     \caption{Imperfect detection of interactions increases the number of samples required to be confident that an interaction never occurs.
-Assume that two species cannot interact (i.e., $\lambda=0$) and that the number of observed interactions follows a binomial distribution depending upon the number of observed interactions $k$ and observed co-occurrances $n$.
-The maximum likelihood estimate (MLE) for $\lambda$ is $\lambda_{MLE}=\frac{k}{n}$.
-Note that $\lambda$ is not a point estimate but rather a random variable with an unknown distribution.
-This means that if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact.
-Rather, $k = 0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless some chance that the two species \emph{could} interact.\\
-    Importantly, we can estimate the variance of $\lambda$ as well as the MLE; available methods include the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]).
-The distribution of the MLE for $\lambda$ thus obtained is a key part of the Bayesian distribution for $\lambda$.
+Assume that two species cannot interact (i.e., $\lambda=0$) and that the number of observed interactions follows a binomial distribution.
 Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true credible interval for the interaction probability $\lambda$ for a pair of species that has been observed co-occurring $n$ times but never interacting ($k = 0$).
 The upper limit of the credible interval only reaches 0.1 (dashed, red line) with 35 observations.
-Thus, adding more observations is useful in controlling uncertainty, but the number of observations added must be very high unless we have some other reason to believe that an interaction cannot occur (i.e., a strong prior).}
+Thus, adding more observations is useful in controlling uncertainty, but the number of observations added must be very high.
+}
     \label{upper_limits}
     \begin{center}
-    \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
+    % \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
     % \includegraphics*[width=.8\textwidth]{Figure_3.eps}
@@
     \begin{center}
-    \includegraphics*[width=.8\textwidth]{figures/GP_pdfs_increasing_N_Zillis.eps}
+    % \includegraphics*[width=.8\textwidth]{figures/GP_pdfs_increasing_N_Zillis.eps}
     % \includegraphics*[width=.8\textwidth]{Figure_4.eps}
@@
     \caption{Mean connectance, links per galler, nestedness (NODF), and links per natural enemy for networks assembled using posterior distributions based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017} occupied a narrow range.
-To obtain distributions of network properties, we created 100 ``posterior-sampling" networks and then, for each of these, created 100 ``filtered" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network.
+To obtain distributions of network properties, we created 100 ``posterior-sampling" networks and then, for each of these, created 100 ``detection-filter" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network.
 This simulates imperfect detection of interactions in the field.
-Each point represents the mean (+/- SD) network property (e.g., connectance) obtained from a set of 100 filtered networks.
-The filtered networks cover a broader range of network properties than the posterior-sampling networks but the value of each property decreases as the strength of the detection filter increases.
+Each point represents the mean (+/- SD) network property (e.g., connectance) obtained from a set of 100 detection-filter networks.
+The detection-filter networks cover a broader range of network properties than the posterior-sampling networks but the value of each property decreases as the strength of the detection filter increases.
 Values in the original web are indicated by dashed lines.}
@@
     \begin{center}
-    \includegraphics[width=.8\textwidth]{figures/GP_posterior_properties_Zillis.eps}
+    % \includegraphics[width=.8\textwidth]{figures/GP_posterior_properties_Zillis.eps}
     % \includegraphics[width=.8\textwidth]{Figure_5.eps}

### 2019-01-14 manuscript/reply_to_reviewers.tex
main text is now within word-count limits

@@
 % ---------------------------------------
-Preamble.
+
+	The Reviewer complimented our manuscript as ``well-written'' and addressing the ``hugely important'' question prior choice in network analyses.
+He/she supports our suggestion that researchers use their system-specific knowledge when embarking upon Bayesian analyses, and has suggested that we restructure the manuscript (especially the introduction) in order to come more directly to the issue of prior choice.
+In the present revision we have taken this advice to heart and streamlined our introduction in order to expand our discussion of prior choice.
+In this revision, we have retained some of the introductory material which the Reviewer notes describes ``ground very well-trod'' in order to ensure that readers entirely new to Bayesian analysis will understand the problem at hand.
+We hope that the introduction now strikes a balance between providing essential background information for Bayesian novices and moving quickly enough for those who do not need such a gentle introduction.
+We thank the Reviewer for their feedback and address each point (prefaced by \textbf{R:}) below.
 
@@
 		\begin{refquote}
-			Below I offer my thoughts on this well-written manuscript.
-Normally I condense my review into a few key points, but I found myself uncharacteristically divided with the paper as presented.
-At first, the introduction covers ground very well-trod by prior works and doesn’t really address its contribution.
-I was mostly frustrated by the rehashing of topics made by many previous papers, include many by the authors themselves.
-But then the paper seems to morph and pick up steam on L248.
-Rather than reaching towards an amorphous and grandiose “quantitative framework”, the authors briefly zoom into a very concise, and hugely important, question of choosing prior distributions for harnessing information among networks.
-This has been completely unexplored and merits attention.
 			In ecology more broadly, priors are treated with timidity, as if we couldn’t dare to leverage past work on our current understanding.
@@
 I applaud the authors for taking on this challenge, and I would like to see an introduction that merits and debates this question in much more detail.
-When should we use prior information?
-How do we go about constructing informed priors for networks?
-When can we use priors from the data in question?
-This is sometimes called approximate bayes (http://andrewgelman.com/2016/03/25/28321/), or empirical bayes, perhaps alluded to in the title, but not fully explained in the introduction.
-Should empirical priors be drawn from hyperpriors or fixed for each interaction?
-Can we combine qualitative information and quantitative information?
-This is all exciting ground that will open up new avenues for networks.
+...
 Walking the reader through flat priors, informed priors and empirical priors is crucial for the importance of analysis to be understood by the reader.
 The use of empirical priors can be quite controversial, and should be atleast touched on in the discussion.
-\\
-			I’ve left my comments below on the introduction, but in my opinion, it should be almost wholly rewritten in favor of a more targeted question constructing networks using priors, which is the key novelty of the work and is mostly hidden by the current introduction.
-I’m not convinced any new analysis needs to be done, which speaks to the conflict between the current introduction and the actual data presented.
-I see the makings of a really nice paper here, and I’m confident the authors will be able to achieve this text revision.
-
-			At the same time, the paper is clear and very readable. I wholly support the method and I think it is something critical that needs to be adopted by the community. \\
-			Having read the paper several times, I think that the authors are trying to cast their net too widely, even starting from the title.
-From that perspective, they don’t meet the expectation of new insight.
-However!!
-I was extremely interested in the brief discussion on using prior knowledge, especially the delicacy of trying to transfer information among networks (L248).
-My recommendation is to drastically reduce the grandiose attempt at a “quantitative framework for networks” (L1 – L246) and really zoom in on the contribution of transferring information among networks through informed priors.	Again L278, this is very well covered in concept by recent papers in MEE that include the authors of this work, as well as several by Weinstein, Bartomeus and others.
 			\end{refquote}
@@
 In doing so, we have happily adopted the suggestion to expand our discussion of prior selection, particularly with regard to approximate/empirical Bayes.
-Although we are somewhat space-limited, we have expanded our description of the different priors available and why a researcher might choose one over another (section beginning with line 245).
-We also touch upon the controversy over using empirical priors (lines 340-345) although we were unable to find many references addressing this in detail.
+Although we are somewhat space-limited, we have expanded our description of the different priors available and why a researcher might choose one over another (section beginning with line 253).
+We also touch upon the controversy over using empirical priors (lines 348-353) although we were unable to find many references addressing this in detail.
 We hope that this expanded description will be a better guide for empiricists who may not be familiar with Bayesian statistics.
@@
 Therefore we have revised and streamlined our introduction but still refrain from jumping straight into prior selection.
-We have, however, taken care to introduce our analysis as a worked example (lines 347) and hope that this helps to reduce the conflict between the introduction and our data.
+We have, however, taken care to introduce our analysis as a worked example (lines 355) and hope that this helps to reduce the conflict between the introduction and our data.
 
@@
 We have incorporated these references as suggested (including Jordano, 2016 in the sampling section).
-Following comments from other reviewers, we have refined and slightly restructured our introduction in the hope of more clearly establishing the goal of our manuscript.
+Following comments from other reviewers, we have refined and restructured our introduction in the hope of more clearly establishing the goal of our manuscript.
 We hope that this revised introduction will also meet with the Reviewer's approval.
@@
     \bibliographystyle{ecol_let} 
-    \bibliography{manual_abbrev} % Abbreviate journal titles.
+    \bibliography{manual} % Abbreviate journal titles.
 

### 2019-01-14 manuscript/CI_interactions.tex
main text is now within word-count limits

@@
 % \item Number of references: 37
-% \item Number of figs, tables, \& text boxes: 6 % Limit is 10
+% \item Number of figs, tables, \& text boxes: 4 % Limit is 10
 % \end{itemize}
@@
 % \item Abstract word count: 290
-% \item Main text word count: 6872 % Limit is 6000-7000 including figs, tables, references. 
+% \item Main text word count: 6871 % Limit is 6000-7000 including figs, tables, references. 
 % \end{itemize}
@@
     Representing an ecological community as a network allows ecologists to address both community composition and the interactions between species~\citep{Roslin2016}.
-Identifying these interactions is a crucial step towards understanding (and predicting) the effects that species have on each other and the response of the community as a whole to external perturbations~\citep{Bartomeus2016,Giron2018}.
+Identifying these interactions is critical to understanding species' effects on each other and predicting the community's response to perturbations~\citep{Bartomeus2016,Giron2018}.
 Importantly, information is conveyed both by the presence and \emph{absence} of links between species.
@@
 
-    First and foremost, ecological communities are known to be stochastic~\citep{Gotelli2000}.
-Community composition and abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}, leading to variation in encounter probabilites and hence in interactions~\citep{Vazquez2005,Poisot2015,Graham2018}.
+    First, ecological communities are stochastic~\citep{Gotelli2000}.
+Community composition and abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}, leading to variation in encounter probabilites and hence interactions~\citep{Vazquez2005,Poisot2015,Graham2018}.
 Species must co-occur in order to be observed interacting, so any variation in co-occurrence will create variation in the set of observed interactions~\citep{Gravel2013,Graham2018}.
 Even assuming constant co-occurrence within a given study system, changing abundances can affect interactions if species which would otherwise interact become too rare to detect each other~\citep{Tylianakis2010,Jordano2016}.
-Moreover, interactions vary over space~\citep{Kitching1987,Baiser2012,Emer2018}, time~\citep{Kitching1987,Olesen2011a,Lopez2017}, between individuals~\citep{Pires2011a,Wells2013,Fodrie2015,Novak2015}, throughout life cycles~\citep{Preston2014,Clegg2018}, and with environmental conditions~\citep{Poisot2015}.
+Moreover, interactions vary over space~\citep{Kitching1987,Baiser2012}, time~\citep{Kitching1987,Olesen2011a,Lopez2017}, between individuals~\citep{Pires2011a,Wells2013,Fodrie2015,Novak2015}, throughout life cycles~\citep{Clegg2018}, and with environmental conditions~\citep{Poisot2015}.
 
-    Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007,Jordano2016}).
+    Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Jordano2016}).
 An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to correctly document interactions than species~\citep{Guimera2009,Poisot2012,Bartomeus2013,Jordano2016,Giron2018,Graham2018}.
@@
 
-    [[These two paragraphs try to frame our study more clearly]]
-    To date, models incorporating uncertainty have either been very general (e.g.,~\citet{Guimera2009,Gravel2013}) or very system-specific (e.g.,~\citet{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}); in either case one of these models may be a poor fit for a particular study system.
+    To date, models incorporating uncertainty have either been very general (e.g.,~\citet{Guimera2009,Gravel2013}) or very system-specific (e.g.,~\citet{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}); in either case such a model may be a poor fit for a particular study system.
 Moreover, some of the system-specific models described above cannot accommodate species observed only once~\citep{Bartomeus2013,Weinstein2017}.
@@
 First, we provide a brief description of the nested levels of uncertainty affecting ecological network construction.
-In the context of this uncertainty, which can be reduced but not eliminated by high-quality sampling (\citealp[see Box 1]{Bartomeus2013}), we present our Bayesian framework for combining observed data with a prior expectation of network structure.
+In the context of this uncertainty, which can be reduced but not eliminated by high-quality sampling~\citep{Bartomeus2013}), we present a Bayesian framework for combining observed data with a prior expectation of network structure.
+This prior expectation can be uninformative, or it may include prior knowledge about the study system.
 We conclude with a worked example applying this framework to an intensively-sampled host-parasitoid network.
 We find that even the highest-quality empirical network we could find had substantial uncertainty about whether many pairs of species interact, demonstrating the need to include information about this uncertainty in published networks.
-We also show that this interaction-level uncertainty leads to uncertainty about estimates of network structure, with important implications for comparisons across networks; especially those compiled with different sampling intensity~\citep{Weinstein2017}.
+    % We also show that this interaction-level uncertainty leads to uncertainty about estimates of network structure, with important implications for comparisons across networks; especially those compiled with different sampling intensity~\citep{Weinstein2017}.
 
@@
 
-      We start from the perspective of a community ecologist faced with the task of describing a previously unknown interaction network.
-This ecologist will be interested in generating a description of the species/nodes present and the links between them~\citep{Roslin2016}.
-Importantly, the information sought is conveyed by both the presence and \emph{absence} of links.
-Presences and absences are not, however, equally certain.
-An observed link definitely occurred (assuming we can correctly identify the species involved), but there are multiple reasons why a given link may not be observed \emph{whether or not the interaction truly occurred}.
+      We start from the perspective of a community ecologist wishing to describe an interaction network.
+This ecologist will be interested in describing the species/nodes present and the links between them~\citep{Roslin2016}.
+While an observed link definitely occurred (assuming correct identification of the species involved), a given link may not be observed for many reasons, \emph{whether or not the interaction truly occurred} (Fig.~\ref{conceptual_fig}).
 Moreover, given an unobserved interaction in an empirical dataset, we often cannot determine why the interaction did not occur \emph{post hoc}.
 The detection of any interaction is a stochastic process subject to many levels of uncertainty.
-As a conceptual guide to the factors affecting this process, we describe three nested levels of uncertainty that roughly address the questions: "Could species $i$ and $j$ interact?", "Did they interact?" and "Did we observe the interaction?" (Fig.~\ref{conceptual_fig}).
+As a conceptual guide, we describe three nested levels of uncertainty that roughly address the questions: ``Could species $i$ and $j$ interact?", ``Did they interact during sampling?", and ``Did we observe the interaction?"
 
@@
 
-          First, and most fundamentally, some interactions are feasible if a pair of species should co-occur while others are not~\citep{Poisot2015}.
-Assuming that the feasibility of interactions depends on the traits of species involved, we can define the probability of an interaction $L_{ij}$ between species $i$ and $j$, given some function describing trait-matching between species $i$ and $j$ $\mathbf{T_{ij}}$, as $P(L_{ij}|\mathbf{T_{ij}}) = \lambda_{ij}$~\citep{Bartomeus2013,Gravel2013,Weinstein2017}.
-          In some cases the traits prohibiting an interaction are known, and there will be little uncertainty about $\lambda_{ij}$.
-          In most cases, however, it is not known what traits might prohibit an interaction~\citep{Dormann2017}.
-Pollinators may visit plants outside of those predicted based on "pollination syndromes"~\citep{Weinstein2017a} and herbivores may consume animal prey when it becomes accessible~\citep{Furness1988,Pietz2000}.
+          Fundamentally, some interactions are feasible while others are not~\citep{Poisot2015}.
+Assuming that the feasibility of interactions depends on the traits of species involved, we can define the probability of an interaction $L_{ij}$ between species $i$ and $j$, given some function describing trait-matching between species $i$ and $j$ $\mathbf{T_{ij}}$, as $P(L_{ij}|\mathbf{T_{ij}})=\lambda_{ij}$~\citep{Bartomeus2013,Gravel2013,Weinstein2017}.
+          In some cases the traits prohibiting an interaction are known and there will be little uncertainty about $\lambda_{ij}$.
+          In most cases, however, it is not known what traits might prohibit an interaction~\citep{Dormann2017} and uncertainty about $\lambda_{ij}$ will be high. 
+          %Pollinators may visit plants outside of those predicted based on "pollination syndromes"~\citep{Weinstein2017a} and herbivores may consume animal prey when it becomes accessible~\citep{Furness1988,Pietz2000}.
 These examples illustrate the danger in assuming that seemingly unlikely interactions cannot occur.
@@
           An unobserved interaction may be a rare phenomenon with $\lambda>0$ and the associated zero in an interaction matrix might be false.
-This uncertainty is partly addressed by trait-matching models in which species with better-matched traits are more likely to interact~\citep{Bartomeus2016,Jordano2016,Weinstein2017}.
-As these models improve and include better information about the influence of traits on interactions, the uncertainty will be reduced~\citep{Jordano2016} and $\lambda_{ij}$ should either tend to 0 or to 1.
-Nevertheless, every model is imperfect and lacks information that could be used to define constraints on at least some interactions~\citep{Dormann2017}.
-Until these gaps are filled, some uncertainty will remain about whether some species pairs could interact.
+This uncertainty is partly addressed by trait-matching models~\citep{Bartomeus2016,Jordano2016,Weinstein2017}.
+As these models improve and include better information about the influence of traits on interactions, uncertainty will be reduced~\citep{Jordano2016} and $\lambda_{ij}$ should either tend to 0 or to 1.
+Nevertheless, every model is imperfect and lacks information that could be used to define constraints on at least some interactions~\citep{Dormann2017}, leaving some uncertainty about whether some species pairs could interact.
 
@@
 
-          Assuming that an interaction is feasible (i.e., $L_{ij} = 1$;), an interaction may still not occur at a particular place or time~\citep{Poisot2015,Graham2018}.
-This could be because constraints such as inclement weather or low abundance prevented the interaction~\citep{Jordano2016,Graham2018}, a more preferred interaction partner was available~\citep{Weinstein2017a}, or substantial individual variation in traits meant that local individuals could not interact even if the species in general can~\citep{Gravel2013,Wells2013,Poisot2015}.
+          Assuming that an interaction is feasible (i.e., $L_{ij}=1$;), an interaction may still not occur at a particular place or time~\citep{Poisot2015,Graham2018}.
+This could be because constraints such as inclement weather or low abundance prevented the interaction~\citep{Jordano2016,Graham2018}, a preferred interaction partner was available~\citep{Weinstein2017a}, or individual variation in traits meant that local individuals could not interact even if the species in general can~\citep{Gravel2013,Wells2013,Poisot2015}.
 For example, a rare galler may not parasitize a rare plant because they do not encounter each other.
 In metawebs describing a community found at several sites, an interaction may also fail to occur because two species do not co-occur at a particular site even if they do co-occur and interact elsewhere~\citep{Graham2018}.
-We can define the local realisation of an interaction, $X_{ij}$, given that the interaction is feasible, as a stochastic process with associated probability $P(X_{ij}|L_{ij} = 1) = \chi_{ij}$.
-It is unlikely that $\chi_{ij} = 1$  except in the case of obligate specialists who always interact whenever they co-occur and always co-occur.
-When $\chi_{ij} < 1$ we cannot be sure whether an unobserved interaction cannot occur or whether it simply did not occur at a particular site.
+We can define the local realisation of an interaction, $X_{ij}$, given that the interaction is feasible, as a stochastic process with associated probability $P(X_{ij}|L_{ij}=1)=\chi_{ij}$.
+It is unlikely that $\chi_{ij}=1$  except in the case of obligate specialists who always interact whenever they co-occur and always co-occur.
+When $\chi_{ij}<1$ we cannot be sure whether an unobserved interaction cannot occur or whether it simply did not occur at a particular site.
 
-          Some of the uncertainty about $\chi_{ij}$ could be addressed by drawing on the rich literature about interaction contingencies found in community ecology.
-Phenological matching~\citep{MillerRushing2010,Gezon2016}, species preferences~\citep{Pires2011,Novak2015,Coux2016}, and fear effects~\citep{Luttbeg2005,Wirsing2008} all affect the probability of an interaction occurring at a particular site and time, and could be included in models similar to trait-matching models.
+          Some of the uncertainty about $\chi_{ij}$ could be addressed by drawing on the rich literature about interaction contingencies.
+Phenological matching~\citep{MillerRushing2010}, species preferences~\citep{Pires2011a,Novak2015}, and fear effects~\citep{Luttbeg2005} all affect the probability of an interaction and could be included in models similar to trait-matching models.
 Alternatively, interaction probabilities could be tested in mesocosm studies with constant conditions.
@@
 In contrast, expanding sampling to cover a broader spatial or temporal range (e.g., sampling in a variety of microhabitats or during a variety of weather conditions) will help to reduce uncertainty about $\chi_{ij}$ by including a broader range of parameters affecting interaction probability.
-It is unlikely, however, that resources will permit researchers to sample in the full range of sites and conditions covered by a community, and some uncertainty about $\chi_{ij}$ will remain.
+It is unlikely, however, that resources will permit researchers to sample extensively in the full range of sites and conditions covered by a community, and some uncertainty about $\chi_{ij}$ will remain.
 
@@
 
-        \subsubsection*{Did we observe all interactions that occurred?}
+        \subsubsection*{Did we observe the interaction?}
 
-          Lastly, measurement errors are a pervasive source of uncertainty in the observation of ecological processes.
-Even if an interaction is feasible and occurs during sampling ($L_{ij} = 1$ and $X_{ij} = 1$), we may still fail to detect it~\citep{Jordano2016,Weinstein2017}.
-We may define the probability of detecting of an interaction, $D_{ij}$, given the interaction is feasible and occurs, as a stochastic process with the associated probability $P(D_{ij}|X_{ij} = 1,L_{ij} = 1)=\delta_{ij}$.
-Detection failure could happen for many reasons (see~\citet{Wirta2014} for examples and partial solutions to them).
-Some sources of detection error can be minimised with appropriate sampling effort (e.g., combining plant-focused and animal-focused sampling when assembling pollination networks~\citet{Jordano2016}), but other sources are often difficult to reduce.
+          Lastly, measurement errors are a pervasive source of uncertainty about ecological processes.
+Even if an interaction is feasible and occurs during sampling ($L_{ij}=1$, $X_{ij}=1$), it may still go undetected~\citep{Jordano2016,Weinstein2017}.
+We can define the probability of detecting of an interaction, $D_{ij}$, given the interaction is feasible and occurs, as a stochastic process with  probability $P(D_{ij}|X_{ij}=1,L_{ij}=1)=\delta_{ij}$.
+Detection failure could happen for many reasons (see~\citet{Wirta2014}).
+Some sources of detection error can be minimised with appropriate sampling (e.g., combining plant-focused and animal-focused sampling when assembling pollination networks~\citet{Jordano2016}), but other sources are difficult to reduce.
 For example, cryptic species might require molecular analysis for appropriate taxonomic identification~\citep{Wirta2014,Frost2016} or it may not be possible to sample some species due to conservation concerns~\citep{Lagrue2015}.
+The probability of detecting an interaction will also depend on the duration of the interaction and its evidence, the species involved, and the individuals sampled~\citep{Wells2013,Lagrue2015,Cirtwill2016,Weinstein2017}.
 
-          Some types of interactions will have higher detection uncertainty than others.
-Pollination, for example, occurs briefly and does not leave long-lasting evidence, while parasitism can be a lifelong association between species.
-Even long-term interactions can be missed, however, especially if species are difficult to identify or if not all individuals of a species share the interaction~\citep{Wells2013,Cirtwill2016}.
-Parasites, for example, are often concentrated in only a few individuals~\citep{Lagrue2015}.
-If these infected individuals do not happen to be included in a sample, their interactions will be missed.
-Detection probabilities also vary widely between species, and potentially individuals within species, due to different abundances and behaviours~\citep{Wells2013,Weinstein2017}.
+    % \subsection*{Can't we just sample more?}
 
-    \subsection*{Can't we just sample more?}
-
-        To sum up, the absence of an interaction on a given day could  be because it was not feasible [$P(L_{ij}) = 0$], was feasible but did not occur because of local conditions during sampling ($P(X_{ij}|L_{ij} = 1) = 0$], or was feasible and occurred during sampling but could not be observed [$P(D_{ij}|X_{ij} = 1,L_{ij} = 1) = 0$].
+    To sum up, the absence of an interaction on a given day could be because it was not feasible [$P(L_{ij})=0$], was feasible but did not occur because of local conditions during sampling ($P(X_{ij}|L_{ij}=1)=0$], or was feasible and occurred during sampling but could not be observed [$P(D_{ij}|X_{ij}=1,L_{ij}=1)=0$].
 Note that some exteral factors can affect more than one level of uncertainty.
@@
 
-        When considering a metaweb, we wish to separate the unobserved interactions where $L_{ij} = 0$ (i.e., unfeasible interactions) from interactions which could occur but did not at a particular sampling site or which occurred but were not detected (Fig.~\ref{conceptual_fig}).
+    When considering a metaweb, we wish to separate the unobserved interactions where $L_{ij}=0$ (i.e., unfeasible interactions) from interactions which could occur but did not at a particular sampling site or which occurred but were not detected (Fig.~\ref{conceptual_fig}).
 Unfortunately, this is not possible for most interactions (except those where we know an interaction is truly not feasible).
 That is, we generally do not know \emph{why} an interaction was not observed, only that it was not.
-An empirical ecologist will instead measure the marginal probability $P(L_{ij}) = k_{ij}/n_{ij}$, where $k_{ij}$ is the number of observed interactions between species $i$ and $j$ and $n_{ij}$ the number of observed co-occurrences.
+An empirical ecologist will instead measure the marginal probability $P(L_{ij})=k_{ij}/n_{ij}$, where $k_{ij}$ is the number of observed interactions between species $i$ and $j$ and $n_{ij}$ the number of observed co-occurrences.
 Given this information, the question becomes: how can we reduce the uncertainty around our estimated interaction probability?
@@
     The obvious rule of thumb to reduce uncertainty is ``sample more".
-Where resources permit, increasing sample sizes will reduce uncertainty about the upper bound of the interaction probability and will also increase the probability of detecting unlikely or cryptic interactions (e.g., interactions where $L_{ij} = 1$ but process or detection uncertainty is high).
-Despite these benefits, we note that there are limits to the utility of increased sampling.
-Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig.~\ref{histograms}C).
-While this improves our understanding of the set of species present in the community, it introduces yet more uncertainty into the interaction matrix.
-Note that it is better to identify the set of potential interactions than to miss a species, so sampling effort should not be reduced in order to exclude rare species.
-
-        An added complication is that increased sampling will not reduce uncertainty evenly across interactions.
-To record an interaction between species $i$ and $j$, we need to identify both partners correctly (a non-trivial problem in many food webs; e.g.~\citealp{Kaartinen2011,Roslin2016}).
-For both molecular and rearing techniques, certain types of interactions may go unnoticed due to technical challenges~\citep{Wirta2014}.
-This can bias the set of recorded interactions towards those that are easier to observe~\citep{Carstensen2014,Jordano2016}.
-Combining multiple sampling types can reduce this type of bias~\citep{Wirta2014,Jordano2016}.
-Nevertheless, despite substantial improvements in recent decades, most available interaction networks are still undersampled and, moreover, are only subsets of larger communities~\citep{Bartomeus2013,Jordano2016}.
-
-        In short, high-quality sampling is an essential component of ecological network construction and increasing sampling (length of time, number of sites, number of distinct methods, etc.) can reduce some of the uncertainty about unobserved interactions.
-We believe, however, that empirical researchers generally sample to the maximum extent possible given constraints of time, resources, and study sites.
-This practical constraint means that reducing one source of uncertainty is likely to increase another source (e.g., sampling intensively at a single site may reduce detection uncertainty but will increase uncertainty due to variation between sites).
-The number of observed co-occurrences needed to believe that an unobserved interaction cannot occur is very high (about 35; Fig.~\ref{upper_limits}), and most datasets will not include this level of sampling for all pairs of species~\citep{Bartomeus2013}.
-For pairs of species with fewer observations, we can reduce uncertainty by combining the observed data available with prior knowledge about the system.
+Where resources permit, increasing sample sizes will reduce uncertainty about the upper bound of the interaction probability and will also increase the probability of detecting unlikely or cryptic interactions (e.g., interactions where $L_{ij}=1$ but process or detection uncertainty is high).
+High-quality sampling is undoubtedly a crucial part of constructing an empirical network, but there are limits to the utility of increased sampling (see \emph{Appendix S2}).
+To compliment high-quality sampling, we can reduce uncertainty by combining the observed data available with prior knowledge about the system.
 This is straightforward to do using a Bayesian approach, as detailed below.
@@
 
-    % Assume that a pair of species has been observed co-occurring $n$ times and interacting in $k = 0$ cases.
+    % Assume that a pair of species has been observed co-occurring $n$ times and interacting in $k=0$ cases.
 We want to know the probability $\lambda_{ij}$ that the species would be observed interacting if not constrained by local conditions, imperfect detection, etc.
@@
     %     \begin{equation}
-    %       \lambda_{MLE} = \frac{k}{n}  .
+    %       \lambda_{MLE}=\frac{k}{n}  .
     %       \label{theta_MLE}
@@
     % Note that $\lambda_{ij}$ is not a point estimate but rather a random variable with an unknown distribution.
-This means that if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact.
-Rather, $k = 0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless some chance that the two species \emph{could} interact.
-In the situation where $k>0$, in contrast, we are sure that the interaction is feasible ($L = 1$).
-If $n>k>0$, the interaction is feasible but there may be local constraints ($X_{ij} = 0$) or detection errors ($D<1$) causing the interaction not to be observed in some samples.
+This means that if $k=0$ in a given sample, this does not necessarily imply that the two species will never interact.
+Rather, $k=0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless some chance that the two species \emph{could} interact.
+In the situation where $k>0$, in contrast, we are sure that the interaction is feasible ($L=1$).
+If $n>k>0$, the interaction is feasible but there may be local constraints ($X_{ij}=0$) or detection errors ($D<1$) causing the interaction not to be observed in some samples.
 
@@
 This means that where the number of samples $n$ is very low (e.g., for rare species), there will be considerable uncertainty around our estimate of $\lambda_{ij}$.
-In Fig.~\ref{upper_limits}, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda_{ij}$ (for true $\lambda = 0$) varies with sample size.
+In Fig.~\ref{upper_limits}, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda_{ij}$ (for true $\lambda=0$) varies with sample size.
 At a small sample size, the 95\% confidence interval is nearly (0, 1).
@@
     The basis of a Bayesian approach to modelling the probability that an interaction between species $i$ and $j$ occurs ($\lambda_{ij}$) is combining the maximum likelihood estimate (MLE) of $\lambda_{ij}$ with a prior distribution (described in the next section) and a normalising function.
-The MLE of $\lambda_{ij}$ can be modelled as a Bernoulli trial based on the number of observed interactions $k_ij$ and observed co-occurrances $n_{ij}$: $\lambda_{ij} = \frac{k_{ij}}{n_{ij}}$.
-The most appropriate prior distribution for a probability such as $\lambda_{ij}$ is the beta distribution:
+The MLE of $\lambda_{ij}$ can be modelled as a Bernoulli trial based on the number of observed interactions $k_ij$ and observed co-occurrances $n_{ij}$: $\lambda_{ij}=\frac{k_{ij}}{n_{ij}}$.
+The most appropriate prior distribution for $\lambda_{ij}$ is the beta distribution:
 
@@
 Note that the hyperparameters may be set to the same values for all interactions, allowed to vary independently for all interactions, or may incorporate non-independence betwween interactions (e.g., when the shape of the prior distribution depends upon species' abundances or traits).
-    Combining the prior distribution with the MLE of $\lambda_{ij}$ derived from observed data, we obtain a posterior distribution that also follows a beta distribution with new parameters $\alpha_{ij}'= \alpha_{ij}+k$ and $\beta_{ij}'=\beta_{ij}+n-k$ (see~\emph{Appendix S2} for details).
-The influence of the prior on the posterior distribution can be understood from these parameter definitions: the difference between the posterior and the prior will increase with $k_{ij}$ and $n_{ij}-k_{ij}$.
-In other words, the distribution of $\lambda_{ij}$ for better-sampled pairs of species will rely less on the information used to build the prior distribution and depend more on the observed data and uncertainty about the probability of the pair interacting will decrease (Fig.~\ref{Salix_pdfs_cdfs}).
-Note that these Bayesian models of $\lambda_{ij}$ are designed to quantify (and reduce) the total uncertainty about $\lambda_{ij}$.
-They do not address any of the nested sources of uncertainty in particular except through the choice of prior.
+    Combining the prior distribution with the MLE of $\lambda_{ij}$ derived from observed data, we obtain a posterior distribution that also follows a beta distribution with new hyperparameters $\alpha_{ij}'=\alpha_{ij}+k$ and $\beta_{ij}'=\beta_{ij}+n-k$ (\emph{Appendix S3}).
+The influence of the prior on the posterior distribution can be understood from these definitions: the difference between the posterior and the prior will increase with $k_{ij}$ and $n_{ij}-k_{ij}$.
+In other words, the distribution of $\lambda_{ij}$ for better-sampled pairs of species will rely less on the information used to build the prior distribution and more on the observed data.
+As $n_{ij}$ increases, the total uncertainty about $\lambda_{ij}$ will decrease (Fig.~\ref{Salix_pdfs_cdfs}).
+Note that these Bayesian models of $\lambda_{ij}$ do not distinguish between different sources of uncertainty except through the choice of prior.
 
@@
     %       \begin{equation}
-    %         \bar{\lambda} = \frac{\alpha_{ij}+k}{\alpha_{ij}+\beta_{ij}+n} ,
+    %         \bar{\lambda}=\frac{\alpha_{ij}+k}{\alpha_{ij}+\beta_{ij}+n} ,
     %         \label{mean}
@@
     %       \begin{equation}
-    %         Var(\lambda|k) = \frac{(\alpha_{ij} + k)(\beta_{ij} + n - k)}{(\alpha_{ij} + \beta_{ij} + n)^{2}(\alpha_{ij} + \beta_{ij} + n +1)}
+    %         Var(\lambda|k)=\frac{(\alpha_{ij} + k)(\beta_{ij} + n - k)}{(\alpha_{ij} + \beta_{ij} + n)^{2}(\alpha_{ij} + \beta_{ij} + n +1)}
     %         \label{variance}
@@
     %       \begin{equation}
-    %         \hat{\lambda} = \frac{\alpha_{ij} + k - 1}{\alpha_{ij} + \beta_{ij} + n - 2} .
+    %         \hat{\lambda}=\frac{\alpha_{ij} + k - 1}{\alpha_{ij} + \beta_{ij} + n - 2} .
     %         \label{mode}
@@
 
-      The choice of prior distribution will reflect the goal of a study, the amount of prior knowledge available, and the strength of researchers' belief in that prior knowledge.
-Note that there is no 'correct' prior as long as we do not know the true distribution of interaction probabilities~\citep{Spiegelhalter2000}.
+      The choice of prior distribution reflects a study's goal, the amount of prior knowledge available, and the strength of researchers' belief in that knowledge.
+Note that there is no 'correct' prior as long as the true distribution of interaction probabilities is unknown~\citep{Spiegelhalter2000}.
 The goal is to select a reasonable prior that reflects our assumptions about the true distribution, and then adjust this prior with observed data as it becomes available.
 When in doubt, it is also possible to model interaction probabilities using a variety of priors and then compare results~\citep{Spiegelhalter2000}.
-Some researchers may be reluctant to adopt a Bayesian approach because of its perceived subjectivity (i.e., the metaweb we obtain will depend upon the assumptions used when developing a prior).
-We argue that one of the advantages of the Bayesian approach is that it makes some of the subjectivity inherent in network construction explicit.
+Some researchers may be reluctant to adopt a Bayesian approach because of its perceived subjectivity (i.e., a metaweb simulated using a Bayesian distribution will depend upon the assumptions inherent in the prior).
+We argue that one of the advantages of the Bayesian approach is that it makes this subjectivity explicit~\citep{Spiegelhalter2000}.
 Researchers compiling empirical networks face many decisions about where to set community boundaries, the set of species to include in the focal community~\citep{Jordano2016}, what type of sampling is most appropriate~\citep{Wirta2014}, etc.
-All of these choices will affect the compiled network and most do not have clear answers, making all empirical networks (and all theoretical networks, which likewise depend upon the assumptions used in building the network) to some extent subjective.
+All of these choices will affect the compiled network and most do not have clear answers, making all empirical networks (and all theoretical networks, which likewise depend upon the assumptions used in building the network) somewhat subjective.
 In addition, researchers distinguishing ``forbidden links" inherently rely on prior knowledge to identify these links~\citep{Jordano2016}.
 Stating that an interaction is ``forbidden" is, in effect, applying a very strong prior to reduce/eliminate uncertainty about the non-observation of that interaction.
-Given this reality, we feel it is better to make the assumptions used to build a network as explicit as possible so that these assumptions can be questioned, compared between studies, and tested.
+Given the reality of subjective network construction, we feel it is better to make the assumptions used to build a network as explicit as possible so that these assumptions can be questioned, compared between studies, tested, and perhaps validated.
 
@@
 
-        If researchers wish to reflect uncertainty in their data without applying any particular assumptions/prior knowledge or account for the possibility that the distribution of probabilities of interaction may vary, they can select $\alpha_{ij}$ and $\beta_{ij}$ to produce an intentionally uninformative prior~\citep{Leyland2005,Berger2006}.
-This prior can then be given a low weight, such that any observed data will outweigh the prior distribution.
+        If researchers wish to capture uncertainty in their data without applying any assumptions or prior knowledge, they can select $\alpha_{ij}$ and $\beta_{ij}$ to produce an intentionally uninformative prior~\citep{Leyland2005,Berger2006}.
+This prior can be given a low weight, such that any observed data will outweigh the prior distribution.
 For pairs of species with little or no observed data, an uninformative prior will leave large variance about $\lambda_{ij}$ and reflect our lack of knowledge about the pair.
-Since we model $\lambda_{ij}$ as a Bernoulli trial, the appropriate uninformative prior is Jeffreys prior: a beta distribution with $\alpha_{ij}$=$\beta_{ij}$=0.5.
-The sum of $\alpha_{ij}$ and $\beta_{ij}$ is roughly equivalent to the weight of the prior, so Jeffreys prior has equal weight to a single observation.
+Since we model $\lambda_{ij}$ as a Bernoulli trial, the appropriate uninformative prior is the Jeffreys prior: a beta distribution with $\alpha_{ij}$=$\beta_{ij}$=0.5.
+The sum of $\alpha_{ij}$ and $\beta_{ij}$ is roughly equivalent to the weight of the prior, so the Jeffreys prior has equal weight to a single observation.
 
@@
 
-        In most cases, we have at least some prior knowledge about a system which we can use to reduce uncertainty about interactions.
-One common example is the well-justified assumption that plants will not consume animals in a food web; excluding carnivorous plants it is not contentious to say that we have little to no uncertainty about unobserved links describing plants feeding on animals.
-Similarly, if we observe two species which are normally obligate mutualists co-occurring but not interacting, we would be very doubtful that a zero reflecting this interaction was true (i.e., high uncertainty about this zero).
-It is straightforward to extend the intuition behind these special cases to the full set of species in a network using trait-based models, as long as the traits likely to affect interaction probabilities are known (e.g.,~\citet{Riede2011,Gravel2013,Bartomeus2016,Weinstein2017}).
-Models for interaction probabilities could also include information on abundances, phenological matching, co-occurrence etc.
+        In most cases, we have some prior knowledge which we can use to inform uncertainty about interactions.
+One common example is the well-justified assumption that plants will not consume animals in a food web; excluding carnivorous plants it is not contentious to say that we are certain that unobserved links indicating plants feeding on animals truldy do not occur.
+Similarly, if we observed two species which are normally obligate mutualists co-occurring but not interacting, we would be very doubtful that a zero reflecting this interaction was true (i.e., high uncertainty about this zero).
+It is straightforward to extend the intuition behind these special cases to the full set of species in a network using trait-based models if the traits likely to affect interaction probabilities are known (e.g.,~\citet{Gravel2013,Bartomeus2016,Weinstein2017}).
+Informative models could also include information on abundances, phenological matching, co-occurrence, etc.
 as available~\citep{Jordano2016,Weinstein2017a,Graham2018}.
-This approach allows us to tailor the level of uncertainty surrounding each interaction based on the species involved but involves many assumptions about which parameters affect interaction probabilities and the strength and shapes of these relationships.
+Using an informative prior like these tailors the level of uncertainty surrounding each interaction, but involves many assumptions.
 There is, therefore, a risk of over-fitting with complicated trait-based models.
@@
 
-        Alternatively, it is possible to develop a prior based on the properties of a set of published networks (i.e., "reference Bayes"~\citet{Spiegelhalter2000}).
-While this type of prior does not allow for the prior distribution to vary between species pairs, it relies on fewer assumptions about the forces structuring interaction probabilities.
-Instead, we assume only that the focal network will have similar structural properties to those of published networks.
+        Alternatively, once can develop a prior based on the properties of a set of published networks (i.e., ``empirical" or ``reference Bayes"~\citet{Spiegelhalter2000}).
+While this type of prior does not allow for the prior distribution to vary between species pairs, it relies on only one assumption: that the focal network will have similar structural properties to those of published networks.
 For example, connectance ($C=N/S^2$, where $N$ is the number of interactions and $S$ is the number of species) is available for many networks.
@@
         \begin{equation}
-        \alpha_{ij} = \overline{C}(\frac{\overline{C}(1-\overline{C})}{\sigma_C^2}-1) ,
+        \alpha_{ij}=\overline{C}(\frac{\overline{C}(1-\overline{C})}{\sigma_C^2}-1) ,
         \end{equation}
@@
         \begin{equation}
-        \beta_{ij} = (1-\overline{C})(\frac{\overline{C}(1-\overline{C})}{\sigma_C^2}-1) .
+        \beta_{ij}=(1-\overline{C})(\frac{\overline{C}(1-\overline{C})}{\sigma_C^2}-1) .
         \end{equation}
@@
         Note that, in this case, the prior distribution will be the same for all interaction probabilities.
-It is also possible to use other interaction probabilities.
-For example, species' degrees (numbers of interaction partners) in a similar network or networks could be normalised (divided by the number of potential interaction partners) and interpreted as an interaction probabilities (i.e., "empirical Bayes"~\citep{Spiegelhalter2000}).
-The distribution of these interaction probabilities can be used to inform a prior distribution as show in \emph{Appendix S3}.
+It is also possible to interpret other network properties (e.g., species degrees) in a similar network(s) as interaction probabilities and use these to create a prior (see \emph{Appendix S4} for a worked example).
 When using network summary statistics or degree distributions, it is important to consider whether the available information reflects what we truly believe about the network.
@@
 Likewise, only the degree distribution for a similar system is likely to be a reasonable prior for a focal system.
-For example, if the system is a large network containing many plant species and insects from different families it is inappropriate to use a prior distribution drawn from a small network describing interactions between different genotypes of a single plant species and a set of closely-related insects (see \emph{Appendix S6} for a demonstration).
-The similarity of traits across genotypes within a species means that an insect which interacts with one genotype is likely to interact with many others.
-Trait differences between species mean that a species-species network will likely contain fewer interactions than a genotype-species network.
+For example, if the focal system is large and contains a diverse array of species, it would be inappropriate to use a prior distribution drawn from a small network describing closely-related taxa (see \emph{Appendix S7} for a demonstration).
 Similarly, highly-aggregated networks containing nodes which represent whole classes or families are likely to have very different structures than networks where most nodes represent single species as aggregated nodes are likely to have more interaction partners than single species.
 
-        If a similar dataset is not available, it is also possible to use data from the study at hand to develop a prior (i.e., "approximate Bayes"~\citet{Gelmanblog})~\citep{Casella1985,Spiegelhalter2000}.
-This approach is used in medical testing~\citep{Copas1972,Spiegelhalter2000} and disease modelling~\citep{Leyland2005,Brooks2015} using information from pilot studies and can easily be applied to ecological systems.
-Returning to the example of degree distributions, this approach allows us to use information from abundant and easily-sampled species to predict interaction probabilities for species which were observed only rarely.
+        If a similar dataset is not available, it is also possible to use data from the study at hand to develop a prior (i.e., "approximate Bayes"~\citet{Gelmanblog})~\citep{Spiegelhalter2000}.
+This approach is used in medical testing~\citep{Spiegelhalter2000} and disease modelling~\citep{Leyland2005} using information from pilot studies and can easily be applied to ecological systems.
+Returning to the example of degree distributions, approximate Bayes allows us to use information from abundant and easily-sampled species to predict interaction probabilities for species which were observed only rarely.
 Despite its practicality, approximate Bayes has been criticized for being overly subjective~\citep{Berger2006} and because estimating hyperparameters from data serves as an approximation of some true hyperparameters which remain unknown~\citep{Gelmanblog}.
@@
 Nevertheless, there are likely to be many situations where approximate Bayes provides the best way to describe the uncertainty in the dataset.
-We illustrate this approach in the following empirical example.
+We therefore illustrate this approach in the following empirical example.
 
@@
 This dataset consists of a single community type sampled across Europe over 29 years and at 374 unique locations.
-The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (see \emph{Appendix S4} for details).
-      The high spatiotemporal resolution of this dataset make it ideal for illustrating the difficulties in completely sampling a network; even with such an unusually high sampling effort, we anticipate that there will be many pairs of species which were rarely or never observed together.
+The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (see \emph{Appendix S5} for details).
+      The high spatiotemporal resolution of this dataset make it ideal for illustrating the difficulties in completely sampling a network; even with such an unusually high sampling effort, there were many pairs of species which were rarely or never observed together and about which we therefore have high uncertainty about interaction probabilities (Fig.~\ref{histograms}).
 Using the Bayesian framework above, we can identify which potential interactions are more and less uncertain, allowing us to better predict the true structure of the metaweb.
-To show the gaps in sampling, we compared the frequencies of observed co-occurrences and interactions.
-We then calculated an empirical prior and computed the posterior distribution of the probability of an as-yet-unobserved interaction being feasible ($\lambda_{ij}$).
-      We analysed both the \emph{Salix}-galler and galler-natural enemy components of the network but, for brevity, present only the latter here (see~\emph{Appendix S5} for \emph{Salix}-galler results).
+      % To show the gaps in sampling, we compared the frequencies of observed co-occurrences and interactions. 
+      We calculated an empirical prior and computed the posterior distribution of the probability of an as-yet-unobserved interaction being feasible ($\lambda_{ij}$).
+We analysed both the \emph{Salix}-galler and galler-natural enemy components of the network but, for brevity, present only the latter here (see~\emph{Appendix S6} for \emph{Salix}-galler results).
 
@@
         To treat each interaction as a Bayesian probability, we will combine the observed data with a distribution based on prior information.
-While a strict Bayesian framework requires a prior distribution that does not rely on any information from the study at hand, such data are not always available.
-In that case, researchers must choose between using a less-informative prior (e.g., one based on distributions of links across a large set of networks) or an empirical prior based on some "training data" from the study.
-Here, we opted for the latter and created priors using a single sub-network from the middle of the geographical distribution of the~\citet{Kopelke2017} dataset.
-To demonstrate how the use of data from a different system can affect the prior distribution and conclusions based on it, we repeated our analyses using priors derived from a much smaller \emph{Salix}-galler-natural enemy system based around genotypes of a single \emph{Salix} species~\citep[Data available from the Dryad Digital Repository: https://doi.org/10.5061/dryad.g7805]{Barbour2016}\nocite{Barbour2016Dryad}.
-This smaller system was much more densely-connected than that described in~\citet{Kopelke2017} and provided unreasonable distributions for interaction probabilities (\emph{Appendix S6}).
+As we lack a trait-based model or similar published network, we will use data from a single sub-network from the middle of the geographical distribution of the~\citet{Kopelke2017} dataset to inform our prior distribution.
+This simulates an empirical Bayes model using a pilot site to inform the prior distribution.
+A site in the middle of the geographic distribution was chosed in order to minimize bias due to the potential for a northern or southern site to exclude species with restricted ranges.
+To demonstrate how the use of data from a different system can affect the prior distribution and conclusions based on it, we repeated our analyses using priors derived from a much smaller system, which provided unreasonable distributions for interaction probabilites (\emph{Appendix S7}).
 
-        To obtain priors based on a single sub-network --Zillis in Graub\"{u}nchen, Switzerland-- we estimated frequencies of interactions based on the normalised degree of each species in each network component (see \emph{Appendix S7} for details and code).
+        To obtain priors based on a single sub-network --Zillis in Graub\"{u}nchen, Switzerland-- we estimated frequencies of interactions based on the normalised degree of each species in each network component (see \emph{Appendix S8} for details and code).
 Using these prior parameters, we then estimated the posterior distributions of interaction probabilities $\lambda_{ij}$.
-For species without observed interactions ($n = 0$), the posterior distribution is identical to the prior distribution.
+For species without observed interactions ($n=0$), the posterior distribution is identical to the prior distribution.
 For species where $n>0$, we can update the prior distribution with data.
@@
 This gives $\alpha_{ij}'$=$\alpha_{ij}$ and $\beta_{ij}'$=$\beta_{ij} + n_{ij}$.
-We calculated posterior distributions and 95\% credible intervals (see function ``credible\_interval";~\emph{Appendix S8}) for species with $n$ ranging between 0 and 374, the total number of sites in our dataset.
+We calculated posterior distributions and 95\% credible intervals (see function ``credible\_interval";~\emph{Appendix S9}) for species with $n$ ranging between 0 and 374, the total number of sites in our dataset.
 
@@
 The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact.
-We calculated the number of samples required to reach 95\% confidence that $\lambda_{ij}$ was below thresholds of 0.1, 0.05, and 0.01 as examples (see function ``samples\_for\_threshold";~\emph{Appendix S8}).
+We calculated the number of samples required to reach 95\% confidence that $\lambda_{ij}$ was below thresholds of 0.1, 0.05, and 0.01 as examples (see function ``samples\_for\_threshold";~\emph{Appendix S9}).
+Finally, we may be interested in measures of network structure rather than the network itself.
+We can use the posterior distributions of interactions to generate a suite of plausible ``true'' networks that would be obtained if sampling uncertainty could be eliminated and use these networks to estimate many network properties (see \emph{Appendix S10} for a worked example).
 
-    \subsubsection*{Scaling up to network metrics}
+    % \subsubsection*{Scaling up to network metrics}
 
-      Researchers are often interested in measures of network structure rather than the network itself.
+    %   Researchers are often interested in measures of network structure rather than the network itself.
 Computing most network metrics is straightforward when the different $\lambda_{ij}$ of the adjacency matrix are known and assumed not to vary~\citep{Poisot2016}.
@@
 
-      Using the prior distributions and procedures described above, we calculated posterior probability distributions for species pairs that were not observed interacting.
+    %   Using the prior distributions and procedures described above, we calculated posterior probability distributions for species pairs that were not observed interacting.
 Using these posterior distributions and assuming probabilities of 1 for pairs of species that were observed interacting (see \emph{Appendix S2} for a justification), we created a suite of 100 webs by randomly sampling from each posterior distribution.
@@
 
-      Measures of network structure which are based on empirical networks that are missing interactions may differ substantially from the values that would be obtained if detection certainty and variation in interactions over space and time could be removed.
+    %   Measures of network structure which are based on empirical networks that are missing interactions may differ substantially from the values that would be obtained if detection certainty and variation in interactions over space and time could be removed.
 To demonstrate this, we created a suite of filtered networks for each posterior network.
@@
   For most pairs of species $i$ and $j$, $n_{ij}$ was much less than 374 and our posterior mean and variance therefore retain more of the influence of the prior.
-We can see this in the increasing means and variances as we decrease $n_{ij}$ (Fig.~\ref{Salix_pdfs_cdfs};~\emph{Appendix S9}).
+We can see this in the increasing means and variances as we decrease $n_{ij}$ (Fig.~\ref{Salix_pdfs_cdfs};~\emph{Appendix S11}).
 To be 95\% confident that the probability of interaction is below 0.1, 0.05, or 0.01 would require 15, 39, and 229 observed co-occurrences, respectively.
@@
 
-  Scaling up to network structure, we found that the connectance and mean links per galler and natural enemy were much lower in the observed web (C=0.078, $L_{galler}$=9.99, and $L_{natural enemy}$=7.45, respectively) than in the posterior webs (0.186 $\leq$ C $\leq$ 0.198, 13.4 $\leq L_{galler} \leq$ 14.6, and 23.4 $\leq L_{natural enemy} \leq$ 25.0).
+  % Scaling up to network structure, we found that the connectance and mean links per galler and natural enemy were much lower in the observed web (C=0.078, $L_{galler}$=9.99, and $L_{natural enemy}$=7.45, respectively) than in the posterior webs (0.186 $\leq$ C $\leq$ 0.198, 13.4 $\leq L_{galler} \leq$ 14.6, and 23.4 $\leq L_{natural enemy} \leq$ 25.0).
 When the detection probability was relatively low (i.e., 50\%), however, the properties of randomised networks became similar to those in the observed webs (Fig.~\ref{posterior_webs}A,B,D).
@@
 
-  A benefit of Bayesian estimation is that it allows us to make our assumptions more explicit (e.g., assuming that funding source for a medical trial may affect the reported outcome~\citep{Spiegelhalter2000}).
-
   Real interaction networks vary over several dimensions~\citep{Kitching1987,Olesen2011a,Pires2011a,Baiser2012,Fodrie2015,Novak2015}, leading to pervasive under-estimation of interactions in published networks~\citep{Jordano2016}.
@@
 
-  Detectability estimated at 23.3\% in~\citet{Weinstein2017a}
-
   Although 374 sampling sites were not enough to obtain sufficient observations of all species pairs, we were able to reduce uncertainty about many potential interactions using a simple Bayesian framework.
-This framework allowed us to set appropriate confidence intervals about the probability of an unobserved interaction occurring, based on the distribution of interactions in one sample site.
+This framework allowed us to set confidence intervals about the probability of an unobserved interaction occurring, based on the distribution of interactions in one sample site.
 This gives us more reasonable estimates of interaction probabilities than assuming that no unobserved interactions actually occur.
@@
 
-  Our results also demonstrate how incomplete detection of interactions scales up to affect network structure.
+  % Our results also demonstrate how incomplete detection of interactions scales up to affect network structure.
 The structure of the well-sampled network used in our case study is most similar to the structure of simulated networks including only 50\% of the interactions suggested by the posterior distribution of interaction probabilities.
@@
 
-  Based on the framework described above, we can now offer some recommendations for improved descriptions of ecological interactions.
-Observing all interactions in a network is likely impossible~\citep{Jordano2016}, but researchers can take steps to address the uncertainty this implies.
-First, sample sizes should be as large as possible in order to reduce detection uncertainty.
+  We conclude with some recommendations for improved descriptions of ecological interactions.
+While researchers are not likely to observe all interactions in a network~\citep{Jordano2016}, they can take steps to address the uncertainty this implies.
+First, sample sizes should be as large as possible.
 Second, researchers should acknowledge the varying levels of confidence surrounding interactions between species pairs.
@@
 Re-sampling networks based on a probabilistic understanding of networks is straightforward and gives distributions for network properties rather than point estimates.
-This not only acknowledges the fact that interactions vary over time and space but will also facilitate comparisons between networks by adding confidence intervals to estimates of network properties.
+This not only acknowledges the fact that interactions vary over time and space but will also facilitate comparisons between networks by adding confidence intervals to estimates of network properties (see \emph{Appendix S9} for a worked example).
 This will allow us to say whether networks have different structures \emph{and} whether those differences are greater than we would expect given the inherent variability of interactions.
@@
   \begin{figure}[h!]
-    \caption{Three nested levels of uncertainty mean that an observed interaction matrix is unlikely to capture all of the interactions that can really occur at a site.
-Interaction uncertainty means that some interactions that truly occur (black squares in True matrix) are less likely than others (grey squares; lighter grey is less likely) based on species traits.
+    \caption{Nested levels of uncertainty mean that an observed interaction matrix is unlikely to capture all of the interactions that occur at a site.
+Some interactions that truly occur (black squares in True matrix) are less likely than others (grey squares; lighter grey is less likely) based on species traits.
 For example, lions are less likely to predate upon elephants than zebras.
 If our trait model is incomplete (e.g., if we neglect group hunting in lions), we might assume that elephants are too large to ever be prey for lions and assign this interaction a probability of 0.\\
-    \indent Process uncertainty describes the fact that interactions occur with different probabilities in any given sample.
+    \indent Interactions occur with different probabilities in any given sample.
 We show six example networks representing interactions observed over two days at three sites.
 Interactions which occur during fewer sampling days are less likely to be observed.\\
-    \indent Detection uncertainty reflects the fact that not all interactions are equally detectable. For example, interactions involving cryptic species are less likely to be seen.\\
+    \indent Not all interactions are equally detectable. For example, interactions involving cryptic species are less likely to be observed.\\
     \indent After applying these three layers of uncertainty, some interactions which truly occur are very unlikely to be observed.
-The observed matrix (lower right) is a subsample of the true matrix, with the probability of observing each interaction depending on the interaction, process, and detection uncertainty associated with it.
+The observed matrix (lower right) is a subsample of the true matrix, with the probability of observing each interaction is affected by multiple layers of uncertainty.
 Note that some low-probability interactions (e.g., lion predation on zebra) are included while others (e.g., lion predation on elephants) are not.
@@
 
-  \begin{figure}[h!]
-    \caption{Imperfect detection of interactions increases the number of samples required to be confident that an interaction never occurs.
+  % \begin{figure}[h!]
+  %   \caption{Imperfect detection of interactions increases the number of samples required to be confident that an interaction never occurs.
 Assume that two species cannot interact (i.e., $\lambda=0$) and that the number of observed interactions follows a binomial distribution depending upon the number of observed interactions $k$ and observed co-occurrances $n$.
@@
 Note that $\lambda_{ij}$ is not a point estimate but rather a random variable with an unknown distribution.
-This means that if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact.
-Rather, $k = 0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless some chance that the two species \emph{could} interact.\\
-    Importantly, we can estimate the variance of $\lambda_{ij}$ as well as the MLE; available methods include the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]).
+This means that if $k=0$ in a given sample, this does not necessarily imply that the two species will never interact.
+Rather, $k=0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless some chance that the two species \emph{could} interact.\\
+  %   Importantly, we can estimate the variance of $\lambda_{ij}$ as well as the MLE; available methods include the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]).
 The distribution of the MLE for $\lambda_{ij}$ thus obtained is a key part of the Bayesian distribution for $\lambda_{ij}$.
-    Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true credible interval for the interaction probability $\lambda_{ij}$ for a pair of species that has been observed co-occurring $n$ times but never interacting ($k = 0$).
+  %   Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true credible interval for the interaction probability $\lambda_{ij}$ for a pair of species that has been observed co-occurring $n$ times but never interacting ($k=0$).
 The upper limit of the credible interval only reaches 0.1 (dashed, red line) with 35 observations.
 Thus, adding more observations is useful in controlling uncertainty, but the number of observations added must be very high unless we have some other reason to believe that an interaction cannot occur (i.e., a strong prior).}
-    \label{upper_limits}
-    \begin{center}
-    \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
-    % \includegraphics*[width=.8\textwidth]{Figure_3.eps}
-    \end{center}
-    \end{figure}
+  %   \label{upper_limits}
+  %   \begin{center}
+    % \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
+  %   % \includegraphics*[width=.8\textwidth]{Figure_3.eps}
+  %   \end{center}
+  %   \end{figure}
 
   \begin{figure}[h!]
-    \caption{Using prior distributions based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017}, we calculate posterior distributions for the probability of interaction ($\lambda_{ij}$) between two species that have not yet been observed interacting ($k_{ij} = 0$).
+    \caption{Posterior distributions for the probability of interaction ($\lambda_{ij}$) for two species that have not been observed interacting ($k_{ij}=0$) based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017}.
 Posterior distributions (curves) and 95\% credible intervals (lines at top of panel) for $\lambda_{ij}$ narrow and approach zero as the number of observed co-occurrences ($n_{ij}$) increases.
@@
 
-  \begin{figure}[h!]
-    \caption{Mean connectance, links per galler, nestedness (NODF), and links per natural enemy for networks assembled using posterior distributions based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017} occupied a narrow range.
+  % \begin{figure}[h!]
+  %   \caption{Mean connectance, links per galler, nestedness (NODF), and links per natural enemy for networks assembled using posterior distributions based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017} occupied a narrow range.
 To obtain distributions of network properties, we created 100 ``posterior-sampling" networks and then, for each of these, created 100 ``filtered" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network.
@@
 Values in the original web are indicated by dashed lines.}
-    \label{posterior_webs}    
-    \begin{center}
-    \includegraphics[width=.8\textwidth]{figures/GP_posterior_properties_Zillis.eps}
-    % \includegraphics[width=.8\textwidth]{Figure_5.eps}
-    \end{center}
-    \end{figure}
+  %   \label{posterior_webs}    
+  %   \begin{center}
+  %   % \includegraphics[width=.8\textwidth]{figures/GP_posterior_properties_Zillis.eps}
+  %   % \includegraphics[width=.8\textwidth]{Figure_5.eps}
+  %   \end{center}
+  %   \end{figure}
 
@@
     \bibliographystyle{ecol_let} 
-    \bibliography{manual_abbrev} % Abbreviate journal titles.
+    \bibliography{manual} % Do not abbreviate journal titles, papers with >3 authors should be et. al.
 

### 2019-01-14 manuscript/supplemental.tex
updated the SI summary properties fig
main text is now within word-count limits

@@
 
-\section*{Appendix S2: Mathematical framework}
+\section*{Appendix S2: Can we reduce uncertainty by sampling more?}
+
+        The absence of an interaction on a given day could be because it was not feasible [$P(L_{ij}) = 0$], was feasible but did not occur because of local conditions during sampling ($P(X_{ij}|L_{ij} = 1) = 0$], or was feasible and occurred during sampling but could not be observed [$P(D_{ij}|X_{ij} = 1,L_{ij} = 1) = 0$].
+Note that some exteral factors can affect more than one level of uncertainty.
+For example, rare species are less likely to interact at a given site due to neutral processes~\citep{Jordano2016,Graham2018}.
+Interactions involving rare species are also less likely to be detected, unless more sampling effort is focused on rare than common species~\citep{Bartomeus2013,Jordano2016}.
+Thus, abundance affects both the probability of an interaction occurring at a particular site \emph{and} our ability to observe the interaction.
+
+        When considering a metaweb, we wish to separate the unobserved interactions where $L_{ij} = 0$ (i.e., unfeasible interactions) from interactions which could occur but did not at a particular sampling site or which occurred but were not detected (Fig.~\ref{conceptual_fig}).
+Unfortunately, this is not possible for most interactions (except those where we know an interaction is truly not feasible).
+That is, we generally do not know \emph{why} an interaction was not observed, only that it was not.
+An empirical ecologist will instead measure the marginal probability $P(L_{ij}) = k_{ij}/n_{ij}$, where $k_{ij}$ is the number of observed interactions between species $i$ and $j$ and $n_{ij}$ the number of observed co-occurrences.
+Given this information, the question becomes: how can we reduce the uncertainty around our estimated interaction probability?
+
+        The obvious rule of thumb to reduce uncertainty is ``sample more".
+Where resources permit, increasing sample sizes will reduce uncertainty about the upper bound of the interaction probability and will also increase the probability of detecting unlikely or cryptic interactions (e.g., interactions where $L_{ij} = 1$ but process or detection uncertainty is high).
+Despite these benefits, we note that there are limits to the utility of increased sampling.
+Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig.~\ref{histograms}C).
+While this improves our understanding of the set of species present in the community, it introduces yet more uncertainty into the interaction matrix.
+Note that it is better to identify the set of potential interactions than to miss a species, so sampling effort should not be reduced in order to exclude rare species.
+
+        An added complication is that increased sampling will not reduce uncertainty evenly across interactions.
+To record an interaction between species $i$ and $j$, we need to identify both partners correctly (a non-trivial problem in many food webs; e.g.~\citealp{Kaartinen2011,Roslin2016}).
+For both molecular and rearing techniques, certain types of interactions may go unnoticed due to technical challenges~\citep{Wirta2014}.
+This can bias the set of recorded interactions towards those that are easier to observe~\citep{Carstensen2014,Jordano2016}.
+Combining multiple sampling types can reduce this type of bias~\citep{Wirta2014,Jordano2016}.
+Nevertheless, despite substantial improvements in recent decades, most available interaction networks are still undersampled and, moreover, are only subsets of larger communities~\citep{Bartomeus2013,Jordano2016}.
+
+        In short, high-quality sampling is an essential component of ecological network construction and increasing sampling (length of time, number of sites, number of distinct methods, etc.) can reduce some of the uncertainty about unobserved interactions.
+We believe, however, that empirical researchers generally sample to the maximum extent possible given constraints of time, resources, and study sites.
+This practical constraint means that reducing one source of uncertainty is likely to increase another source (e.g., sampling intensively at a single site may reduce detection uncertainty but will increase uncertainty due to variation between sites).
+The number of observed co-occurrences needed to believe that an unobserved interaction cannot occur is very high (about 35; Fig.~\ref{upper_limits}), and most datasets will not include this level of sampling for all pairs of species~\citep{Bartomeus2013}.
+For pairs of species with fewer observations, we can reduce uncertainty by combining the observed data available with prior knowledge about the system.
+This is straightforward to do using a Bayesian approach, as detailed in the main text.
+
+        \begin{figure}[h!]
+          \caption{Imperfect detection of interactions increases the number of samples required to be confident that an interaction never occurs.
+Assume that two species cannot interact (i.e., $\lambda=0$) and that the number of observed interactions follows a binomial distribution depending upon the number of observed interactions $k$ and observed co-occurrances $n$.
+The maximum likelihood estimate (MLE) for $\lambda_{ij}$ is $\lambda_{MLE}=\frac{k}{n}$.
+Note that $\lambda_{ij}$ is not a point estimate but rather a random variable with an unknown distribution.
+This means that if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact.
+Rather, $k = 0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless some chance that the two species \emph{could} interact.\\
+          Importantly, we can estimate the variance of $\lambda_{ij}$ as well as the MLE; available methods include the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]).
+The distribution of the MLE for $\lambda_{ij}$ thus obtained is a key part of the Bayesian distribution for $\lambda_{ij}$.
+          Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true credible interval for the interaction probability $\lambda_{ij}$ for a pair of species that has been observed co-occurring $n$ times but never interacting ($k = 0$).
+The upper limit of the credible interval only reaches 0.1 (dashed, red line) with 35 observations.
+Thus, adding more observations is useful in controlling uncertainty, but the number of observations added must be very high unless we have some other reason to believe that an interaction cannot occur (i.e., a strong prior).}
+          \label{upper_limits}
+          \begin{center}
+          % \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
+          % \includegraphics*[width=.8\textwidth]{Figure_3.eps}
+          \end{center}
+          \end{figure}
+
+\clearpage
+
+\section*{Appendix S3: Mathematical framework}
 
@@
 
-\section*{Appendix S3: Calculating uninformative and informative priors}
+\section*{Appendix S4: Calculating uninformative and informative priors}
 
@@
 
-\section*{Appendix S4: Details of \emph{Salix} data collection}
+\section*{Appendix S5: Details of \emph{Salix} data collection}
 
@@
 
-\section*{Appendix S5: Results for \emph{Salix}-galler component}
+\section*{Appendix S6: Results for \emph{Salix}-galler component}
 
@@
           \begin{center}
-          \includegraphics*[height=.7\textheight]{figures/SG_histogram.eps}
+          \includegraphics*[height=.65\textheight]{figures/SG_histogram.eps}
           \end{center}
@@
 
-\section*{Appendix S6: Analyses using alternative prior}
+\section*{Appendix S7: Analyses using alternative prior}
 
@@
 
-\section*{Appendix S7: Obtaining prior interaction probabilities}
+\section*{Appendix S8: Obtaining prior interaction probabilities}
 
@@
 
-\section*{Appendix S8: R code for calculating posterior distributions and confidence intervals}
+\section*{Appendix S9: R code for calculating posterior distributions and confidence intervals}
 
@@
 
-\section*{Appendix S9: Calculating the credible interval around a probability estimate}
+\section*{Appendix S10: Calculating network properties using posterior distributions}
+
+  Once we have calculated posterior distributions for the probability of each interaction, we can simulate networks that might be observed if we could sample sufficiently to elminate some of the uncertainty in empirical networks.
+Using these posterior networks, it is straightforward to obtain a plausible distribution for network properties of the predicted ``true'' community.
+Note that these network properties may differ substantially from those of the observed network.
+Here we demonstrate this process with the galler-parasitoid component of the network described in ~\citet{Kopelke2017}.
+
+  \subsection*{Methods}
+
+        \subsubsection*{Scaling up to network metrics}
+
+      Researchers are often interested in measures of network structure rather than the network itself.
+Computing most network metrics is straightforward when the different $\lambda_{ij}$ of the adjacency matrix are known and assumed not to vary~\citep{Poisot2016}.
+Incorporating variance in $\lambda_{ij}$ into these calculations, however, is not so easy.
+Computation of these metrics involves non-linear functions.
+By Jensen's inequality~\citep{Jensen1906}, this means that the average of a network metric (a function of stochastic interactions) is not the same as the network metric calculated based on the average interaction probability.
+Thus, any uncertainty in the values of $\lambda_{ij}$ could bias both the mean and variance of network metrics, giving misleading results (simulated in \emph{Appendix S1}).
+One way to avoid this situation is to calculate the properties of a suite of simulated networks~\citep{Vazquez2005,Guimera2009}.
+
+      Using the prior distributions and procedures described above, we calculated posterior probability distributions for species pairs that were not observed interacting.
+Using these posterior distributions and assuming probabilities of 1 for pairs of species that were observed interacting (see \emph{Appendix S2} for a justification), we created a suite of 100 webs by randomly sampling from each posterior distribution.
+Each of these webs is a prediction of the structure of the metaweb.
+After obtaining these posterior networks, we calculated, as examples of commonly-used network properties, the connectance of each web, as well as the mean number of links per galler and per natural enemy, and the nestedness (NODF) of the network.
+This gives us an estimate for each property reflecting our uncertainty about $\lambda_{ij}$.
+
+      Measures of network structure which are based on empirical networks that are missing interactions may differ substantially from the values that would be obtained if detection certainty and variation in interactions over space and time could be removed.
+To demonstrate this, we created a suite of filtered networks for each posterior network.
+Taking a posterior network as the "true" network, we randomly sampled 90\%, 80\%, 70\%, 60\%, 50\%, 40\%, 30\%, 20\%, and 10\% of the interactions to create a new "filtered" network.
+This gradient is akin to a gradient of uncertainty in the network (e.g., due to varying sampling effort or intraspecific trait variability).
+For each level of uncertainty, we created 100 randomly-sampled networks per posterior-probability network (giving 100 posterior networks and 1000 filtered networks).
+We calculated the same network properties as described above for all posterior and filtered networks.
+
+  \subsection*{Results}
+
+      Scaling up to network structure, we found that the connectance and mean links per galler and natural enemy were much lower in the observed web (C=0.078, $L_{galler}$=9.99, and $L_{natural enemy}$=7.45, respectively) than in the posterior webs (0.186 $\leq$ C $\leq$ 0.198, 13.4 $\leq L_{galler} \leq$ 14.6, and 23.4 $\leq L_{natural enemy} \leq$ 25.0).
+When the detection probability was relatively low (i.e., 50\%), however, the properties of randomised networks became similar to those in the observed webs (Fig.~\ref{posterior_webs}A,B,D).
+Nestedness was higher in the observed network (NODF=6.85) than in the posterior webs (6.31 $\leq NODF \leq$ 6.82; Fig.~\ref{posterior_webs}C), indicating that the posterior webs include many more interactions between specialists than the observed network.
+In addition, the stronger the detection filter, the farther apart were the nestedness of the observed and posterior webs.
+This suggests that the interactions included in the observed network are not a random subset of those included in the posterior webs.
+In general, the observed network is most similar to simulated networks where only half of the plausible links are detected.
+
+  \begin{figure}[h!]
+    \caption{Mean connectance, links per galler, nestedness (NODF), and links per natural enemy for networks assembled using posterior distributions based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017} occupied a narrow range.
+To obtain distributions of network properties, we created 100 ``posterior-sampling" networks and then, for each of these, created 100 ``filtered" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network.
+This simulates imperfect detection of interactions in the field.
+Each point represents the mean (+/- SD) network property (e.g., connectance) obtained from a set of 100 filtered networks.
+The filtered networks cover a broader range of network properties than the posterior-sampling networks but the value of each property decreases as the strength of the detection filter increases.
+Values in the original web are indicated by dashed lines.}
+    \label{posterior_webs}    
+    \begin{center}
+    % \includegraphics[width=.8\textwidth]{figures/GP_posterior_properties_Zillis.eps}
+    % \includegraphics[width=.8\textwidth]{Figure_5.eps}
+    \end{center}
+    \end{figure}
+
+  \bibliographystyle{ecol_let} 
+  \bibliography{manual}
+
+\clearpage
+
+\section*{Appendix S11: Calculating the credible interval around a probability estimate}
 
@@
     \bibliographystyle{ecol_let} 
-  \bibliography{manual_abbrev}
+    \bibliography{manual_abbrev} % Abbreviate journal titles.
 

### 2019-01-15 manuscript/reply_to_reviewers.tex
finished incorporating Tomas comments to reply. Dom next.

@@
 % ---------------------------------------------------------------------
-{\Large \bf Reply to Reviewer \#2} [[done?]]
+{\Large \bf Reply to Reviewer \#2} 
 % ---------------------------------------
@@
 
-	\begin{refquote}
-		Comments to the Corresponding Author
-		Overall, I think this is a very good paper and makes an important contribution.
-I think there are three main ways it can be improved: 1.
-The simplest – do a better job of acknowledging what else has been done in the field – much of which has actually been done by the authors and their collaborators.
-...
-2.
-Provide more clarity in descriptions making sure to consider how terms and ideas have been used previously.
-...
-3.
-The set up (introduction) to the case study is quite odd and somehow seems off topic – or at least not logical based on what the reader has read up to that point.
-		I hope this review is helpful.
-
-		More generally, the introduction does not really do justice to what has been done already – even the authors own work.
-The problem in my view is that the community using better statistics – of which the authors are very important members – has not managed to communicate to most people studying networks and better methods are simply not being adopted.
-The current paper is a very nice attempt to show the broader community that the Bayesian approach is not so complex and has many advantages.
-I think this is a very important message and is what makes this paper an important contribution.
-Further, the approach to parse out different types of uncertainty and suggestions for how to come-up with informative priors – is very useful.
-The theory/method is well developed overall and provides an example – which is great.
-
-		\end{refquote}
-
-		\textbf{R:} We than the Reviewer for their literature suggestions and for demonstrating that our desire not to criticise hard-working empiricists could be misinterpreted as suggesting reduced sampling effort.
-We had not realised that anyone would consider such a possibility and have revised our manuscript to make it clearer that our approach is a complement to extensive sampling, not an excuse for poor sampling.
+	The Reviewer commented that our paper is, overall, very good and ``makes an important contribution" as ``a very nice attempt to show the broader community that the Bayesian approach is not so complex and has many advantages".
+We are glad that the Reviewer agrees about the importance of this message and appreciate his/her suggestions to improve the manuscript.
+We have taken care to add references and clarify the introduction, as well as to state explicitly that we are emphaticallly not suggesting that anyone sample with lower effort/intensity than they otherwise would.
+We considered the benefits of high-quality sampling to be so self-evident that it did not occur to us that our manuscript could be read as suggesting that extensive sampling is not worthwhile.
+We thank the Reviewer for pointing out the potential for confusion over this point and hope that it is now clear that Bayesian analyses are a complement to, not a replacement for, high-quality sampling.
+Below we adress each of the Reviewer's suggestions in detail.
 
@@
 
-		\textbf{R:} We had not intended to write a review paper and did not wish to over-cite ourselves, but we take the Reviewer's point and have expanded our references to the literature.
+		\textbf{R:} We thank the Reviewer for stressing the need to further acknowledge previous work in the field.
+As this was also emphasized by other reviewers, we have taken this carefully \emph{ad notam} and expanded our references to earlier work as much as possible given length restrictions.
 We have taken particular care to add references to Graham/Weinsten papers as two of the reviewers suggested work by these authors.
@@
 
-		\textbf{R:} We have softened this statement to say that empirical networks are "often limited" and hope that this rephrasing will not offend those who are working to include variation in their descriptions.
+		\textbf{R:} We agree with the Reviewer regarding our intended meaning, and have modified this accordingly:
 
@@
 
-			\textbf{R:} We have added a citation to Bartomeus as requested.
+			\textbf{R:} We agree, and have added a citation to Bartomeus as requested.
+In terms of why we will have omitted references to other similar papers and to some less conceptual and empirical attempts, we must stress that we are not striving for a comprehensive review but rather trying to reach a particular audience with a particular message, for which we find MEE the ideal forum.
+The length and formatting constraints of an MEE article mean that, for the sake of brevity and clarity, we cannot cite all previous work concerning detection probability.
 
@@
 		\textbf{R:} We have rephrased the end of this paragraph to mention previous predictive models dealing with uncertainty in interaction matrices.
+As said, we have done our best to improve our coverage of previous work, within the limits offered by the current format.
 
@@
 
-	2. Confusing terminology [[done]]
+	2. Clarify confusing terminology [[done]]
 
@@
 
-		\textbf{R:} We believe that the Reviewer has badly misunderstood the point of our comments on sampling effort.
+		\textbf{R:} We believe that the Reviewer has  misunderstood the point of our comments on sampling effort.
 Several of their comments suggest that we are advocating for reducing sampling effort.
@@
 Rather, we assumed that field researchers already sample to the maximum extent possible given their time and resource constraints and so a call to "sample more" would not be helpful.
-We now address this assumption explicitly in a section dedicated to the potential for sampling effort to reduce uncertainty about interactions (\textbf{Why can't we sample more?}.
+We now address this assumption explicitly in an appendix (Appendix S2)  dedicated to the potential for sampling effort to reduce uncertainty about interactions.
 Below, we address the Reviewer's sampling-related comments one by one.
@@
 
-		\textbf{R:} I do not know how the Reviewer assumes that we are against repeat sampling when this is, in fact, one of the core parts of our approach.
+		\textbf{R:} Here it seems that we have expressed ourselves poorly.
+Of course we are not against repeat sampling.
+This is, in fact, one of the core parts of our approach.
 Our point here is that some species (e.g., cryptic or difficult-to-identify species) and interactions (e.g., brief visits of pollinators to plants) are difficult to detect and may be missed even with multiple sampling.
@@
 For species which are frequently detected, we absolutely learn about the detection probability of their interactions with repeated sampling.
+We have tried to clarify our intended meaning throughout the revised text.
 
@@
 
-		\textbf{R:} We agree that it is dangerous to suggest that anyone sample less, that is why we have not done so.
+		\textbf{R:} We agree that it is dangerous to suggest that anyone sample less, and again we regret the confusion caused by our previous draft.
 We argue only that the amount of sampling required to be confident that co-occurring species do not interact is large -- likely beyond what is feasible for speciose systems given the limited resources available to many researchers.
 Sampling across most network studies is almost certainly not sufficient, but data which would allow readers to judge this (i.e., number of times each species is observed, independent of numbers of observed interactions) is not generally provided.
-We chose to be more charitable than the Reviewer and assume that those compiling empirical networks are sampling as much as possible given the constraints of their system and available resources.
+Overall, we assume that those compiling empirical networks are sampling as much as possible given the constraints of their system and available resources.
 Infinite sampling would, of course, be the best option but it is unlikely that researchers will be able to perpetually increase sampling.
@@
 
-		\textbf{R:} We had written our first draft with the assumption that empirical ecologists are well aware that large sample sizes are important and that they should sample as much as possible.
-Given that, repeating the call to sample more seemed more likely to come across as patronizing than helpful.
-We did not anticipate that anyone would read the omission of such a call a statement that anyone should sample \emph{less}.
-In our revised manuscript, we collect our discussion of sampling into a dedicated section.
-We hope that this will make it clearer that sampling is very important but cannot completely eliminate uncertainty (except perhaps in some very species-poor and unusually static systems, but these are certainly rare).
+		\textbf{R:} In our revised manuscript, we have collected our discussion of sampling into a dedicated appendix and added several explicit statements that high-quality sampling can reduce some sources of uncertainty.
+We hope that it is now clear that sampling is very important but cannot completely eliminate uncertainty (except perhaps in some very species-poor and unusually static systems, but these are certainly rare).
 As to adding more zeros than ones specifically, this is only "bad" in the sense that it gives us more high-uncertainty cells in the interaction matrix.
@@
 
-		\textbf{R:} Of course modelling the probability of co-occurrence is an option for many systems (e.g., aquatic food webs where ranges of fish species are fairly well-known, as in~\citet{Gravel2013}).
+		\textbf{R:} Modelling the probability of co-occurrence is an option for many systems (e.g., aquatic food webs where ranges of fish species are fairly well-known, as in~\citet{Gravel2013}).
 In some systems, however, the factors affecting probabilities of co-occurrence may not be known.
@@
 		The fact remains that a lack of observed interactions between species which do not co-occur tells us nothing about whether these species \emph{could} interact if they should begin to co-occur (e.g., following a range shift).
-Following the Revewier's suggestion, we have revised our manuscript to clarify our technology.
+Following the Reviewer's suggestion, we have revised our manuscript to clarify our technology.
 In particular, we have taken care to specify which level of uncertainty we are addressing at different points in the manuscript.
@@
 		\textbf{R:} Following suggestions by this Reviewer and another, we have substantially expanded our discussion of different options for priors (including the trait-based and co-occurrence models the Reviewer points out).
-It seems fairly obvious that discovering that trait-matching is important in a model framework which relies of trait-matching as a starting assumption does not mean very much...
-but we also recognize that researchers unfamiliar with Bayesian approaches might prioritize reducing uncertainty and therefore include all available information even when it conflicts with the study question.
-We have therefore added an explicit statement that researchers wishing to test the influence of a particular trait (for example) should \emph{not} include that trait in their prior (lines XX-XX).
+We have also added an explicit statement that researchers wishing to test the influence of a particular trait (for example) should \emph{not} include that trait in their prior (lines XX-XX).
 We hope that this statement, and the expanded discussion of different types of priors more generally, allay the Reviewer's concerns.
@@
 Although the ideal sampling effort \emph{can} be calculated using the framework we put forward (as we demonstrate), the real point is to quantify how uncertain we are that an interaction we do not observe really does not occur.
-Given this, we do not think that recommending uncertainty be explicitly stated undermines our point at all.
-		\smallskip
+Given this, we do not think that recommending uncertainty be explicitly stated undermines our point.
+
 		The Reviewer's suggestion that we might need fewer samples for species that are "specialized or bound to interact for some other reason" reflects a very strong prior.
@@
 
-	\begin{refquote}
-		Comments to the Corresponding Author
-		I have been surprised how little that sampling effects have been formally considered in the analysis of networks, so I welcome this contribution that provides a theoretical framework.
-Overall, I felt that this contribution was really helpful, and that it provides both a theoretical framework and a practical example.
-
-		Overall, I fear that this review is rather meandering, but I think that reflects some of the challenges I have with the paper.
-Currently I do not think the paper would be used by empirical network ecologists because they either would not understand its relevance or would not be able to apply it practically.
-This would be a great shame.
-I hope that the comments are clear enough to allow the authors to improve the paper – the paper has the potential to be important and very useful.
-		\end{refquote}
-
-		\textbf{R:} As we did not intend to write a review, we understand the Reviewer's complaint.
-This shows that we did not clearly establish the purpose of our manuscript, and we hope that our revision corrects this.
-In particular, we hope that we have established the relevance of our method and offered enough of an explanation that empiricists will be able to apply it.
+	[[Still need to incorporate Tomas comments]]
+	[[Still need to spellcheck]]
+
+	The Reviewer has ``been surprised how little that sampling effects have been formally considered in the analysis of networks" and therefore feels that our manuscript makes an important contribution.
+Nevertheless, the Reviewer has concerns that the manuscript might not reach empirical ecologists ``because they either would not understand its relevance or would not be able to apply it practically".
+We agree with the Reviewer that this would be a great shame, and appreciate their suggestions to improve the manuscript.
+With this revision, we hope that we have established the relevance of our method and offered enough of an explanation that empiricists will be able to apply it.
 Our goal is to increase access to a statistical technique which we see as complementary to high-quality field work, and we believe that the Reviewer's comments will help us to achieve this.
@@
 
-		\textbf{R:} We have cited addition literature as recommended by Reviewer 1, including a paper by Jordano.
+		\textbf{R:} All of the Reviewers were unhappy with our treatment of the literature, and we have now done our best to improve on this, bearing in mind the strict word limit of MEE and the fact that it was never our goal to conduct a comprehensive review.
+We have cited additional literature as recommended by Reviewer 1, including a paper by Jordano.
 If the Reviewer has any suggestions of specific papers that they feel are missing, we would be happy to consider them as well.
@@
 It seems to us that measures of interaction strength should be \emph{more} susceptible to sampling biases, not less, as abundant species are both more likely to have their interactions recorded and more likely to have these interactions recorded as strong/frequent.
-We have rephrased the introduction so that the original line 36 no longer appears.
-If the Reviewer strongly feels that weighted metrics somehow do sampling biases, we must ask for clarification as to why.
-We are willing to add a note as requested, but only if we are convinced that weighted metrics are indeed useful in this regard.
-
-	4. Demand for extension to weighted networks [[not done - do we want to do this?]]
+Of course weighted metrics have many other strengths, but these are not germane to the topic at hand.
+We have rephrased the introduction so that the original line 36 no longer appears, and hope that this will remove the Reviewer's objection.
+
+	4. Request for extension to weighted networks [[not done - do we want to do this?]]
 
@@
 It takes an even greater sampling effort to quantify interaction strengths than the presence and absence of links, so for species-rich systems in particular there simply are not many high-quality weighted networks published.
-If the Reviewer is only concerned about weighted interactions, we congratulate them on their tractable study system.
-Nevertheless, we do not wish to exclude the many researchers who are not so fortunate.
-		\smallskip
-		To model frequencies of interactions, ...
-			 [[Do we want to add a bit of non-binary stuff or just make it clearer that we are talking about feasibility and that probabilities of occurrance could be layered on later?]]
+Moreover, as the Reviewer mentioned, empirical ecologists may already struggle to apply a Bayesian framework using qualitative data.
+We therefore opted not to extend our framework in this manuscript and leave this as an area for future work.
 
@@
 This may be the case for Graham and Weinstein's relatively small and well-studied system but is not likely to be true for systems containing hundreds of species, systems containing recently-arrived species, systems just beginning to be studied, etc.
-		\smallskip
-		To make this more clear, we have rephrased this section and added a line (lines XX-XX) stating that we usually cannot determine the cause of all the zeros in an interaction matrix (we can identify obviously unfeasible interactions, but likely cannot say whether a zero for a rare species is because we did not observe enough individuals, there were not enough individuals to perform a particular interaction, or because the interaction is acutally unfeasible).
+
+		To make this clearer, we have rephrased this section and added a line (lines XX-XX) stating that we usually cannot determine the cause of all the zeros in an interaction matrix (we can identify obviously unfeasible interactions, but likely cannot say whether a zero for a rare species is because we did not observe enough individuals, there were not enough individuals to perform a particular interaction, or because the interaction is acutally unfeasible).
 We hope that this revision makes it clearer that the description of different sources of uncertainty is a conceptual guide only.
@@
 We hope that this reframing, and the addition of clear statements that our framework is not intended to separate different sources of uncertainty, will remove the Reviewer's confusion.
-		\smallskip
+
 		Our mention of habitat as a factor affecting the probability of species interacting at a site was not intended to refer to species using different habitats, but rather the possibility that habitat type might affect interaction probabilities.
 For example, a more open patch of forest might have different interaction probabilities than a denser patch even if the same set of species use both patches.
-Of course the Reviewer is correct that habitat also affects which species are present at a site.
+The Reviewer is clearly correct that habitat also affects which species are present at a site.
 We include co-occurrence in process uncertainty since co-occurrence does not tell us much about whether an interaction is feasible under ideal conditions (which would certainly include co-occurrence).
@@
 
-		\textbf{R:} Long-term interactions may be easier to detect, but we do not see how this affects process uncertainty.
+		\textbf{R:} Long-term interactions may be easier to detect, but this does not necessarily translate into reduced process uncertainty.
 Spatial variation in interaction probabilities will affect all interaction types, as does variation in abundances between years, so we cannot conceive of any interactions that are exempt from this issue.
@@
 
-		\textbf{R:} We have removed much of the preferatory text explaining which quantity we are most interested in ($\lambda$) and now more explicitly state our goals at the end of the introduction.
+		\textbf{R:} We have removed much of the introductory text explaining which quantity we are most interested in ($\lambda$) and now more explicitly state our goals at the end of the introduction.
 We hope that the transition to the methods is now less work for a reader.
@@
 
-		\textbf{R:} Due to space constraints, we cannot provide an extensive description of Jensen's inequality here.
-As it is quite easy to look up the inequality by name, we are confident that interested readers can find a description to whatever level of detail suits their interest.
-		[[We could potentially add a demo in a new Appendix. Is this worthwhile?]]
+		\textbf{R:} Due to space constraints, we have refrained from adding an extensive description of Jensen's inequality here, but are confident that readers can find a fuller description in the online literature if they choose.
 
@@
 We have also added a line (lines XX-XX) to make this clear.
-		\medskip
+
 		This is an interesting point, however, as systems with a large risk of false positives (e.g., pollination networks which assume all flower visitors provide pollination service) would be biased by assuming all observed interactions are truly feasible.
@@
 
-	17. Expand discussion of results on line 321 [[not done - will take this after we see about space]]
+	17. Expand discussion of results on line 321 [[no space - had to remove network metrics.]]
 
@@
 
-		\textbf{R:} [[This is the network metrics bit - need to expand in discussion.]]
+		\textbf{R:} Ultimately, length restrictions meant that we were obliged to remove our discussion of network metrics to an appendix.
+After adding the additional material requested by Reviewers in the methods, there simply was not space to discuss the network-level metrics in the main manuscript.
+We agree with the Reviewer that this is an extremely important question, but feel that it is essential to provide a clear and useable explanation of the basic Bayesian framework in the present manuscript.
+We hope to return to the question of how network metrics are impacted by sampling issues in more detail in future work.
 

### 2019-01-15 manuscript/reply_to_reviewers.tex
spellchecked UK

@@
 In particular, we do not feel that a full simulation study is necessary given the simplicity of our framework.
-We emphasize that we are not introducing a software package (although we do provide simple code to aid those who are new to the field), nor are we introducing an entirely new framework (as the other Reviewers point out, many components of our approach have been touched on by previous work).
+We emphasise that we are not introducing a software package (although we do provide simple code to aid those who are new to the field), nor are we introducing an entirely new framework (as the other Reviewers point out, many components of our approach have been touched on by previous work).
 Thus, the novelty and impact of our work explicitly lies in connecting a Bayesian statistical approach to the problem of limited and uneven sampling of networks (driven by difference in species abundances, detectabilities, constrained time and budgets, etc.) and, we hope, in making this method more accessible to those without extensive statistical or modelling experience.
@@
 Walking the reader through flat priors, informed priors and empirical priors is crucial for the importance of analysis to be understood by the reader.
-The use of empirical priors can be quite controversial, and should be atleast touched on in the discussion.
+The use of empirical priors can be quite controversial, and should be at least touched on in the discussion.
 			\end{refquote}
@@
 
-	3. Suggestion to de-emphasize MLE estimate and get straight to Bayes
+	3. Suggestion to de-emphasise MLE estimate and get straight to Bayes
 
@@
 			The basis of a Bayesian approach to modelling the probability that an interaction occurs ($\lambda$) is combining the maximum likelihood estimate (MLE) of $\lambda$ with a prior distribution (described in the next section) and a normalising function.
-The MLE of $\lambda$ can be modelled as a Bernoulli trial based on the number of observed interactions $k$ and observed co-occurrances $n$: $\lambda = \frac{k}{n}$.
+The MLE of $\lambda$ can be modelled as a Bernoulli trial based on the number of observed interactions $k$ and observed co-occurrences $n$: $\lambda = \frac{k}{n}$.
 The most appropriate prior distribution for a probability such as $\lambda$ is the beta distribution:
@@
 This is very googleable, and almost too thorough.
-I think the space is better utilized aligning the ecological challenge and the quantitative method.
+I think the space is better utilised aligning the ecological challenge and the quantitative method.
 		\end{refquote}
@@
 		\textbf{R:} We thank the Reviewer for the literature suggestions and now include them in our introduction and/or discussion.
-We emphasize the board applicability of our approach across network types and systems with varying degrees of prior knowledge.
-We also emphasize that our approach is not restricted to species observed X times (as many predictive models are) and can include species not yet observed at a site (e.g., potential invaders).
+We emphasise the board applicability of our approach across network types and systems with varying degrees of prior knowledge.
+We also emphasise that our approach is not restricted to species observed X times (as many predictive models are) and can include species not yet observed at a site (e.g., potential invaders).
 We hope that the contribution our manuscript makes is now clearer.
@@
 
-	The Reviewer stated that our manuscript ``tackles a very interesting problem, quantifying the uncertainity of interactions" which he/she rates as ``one of the hottest topics in the field".
+	The Reviewer stated that our manuscript ``tackles a very interesting problem, quantifying the uncertainty of interactions" which he/she rates as ``one of the hottest topics in the field".
 He/she also points out that ``the introduction is particularly pleasant to read" and that we framed the problem well.
 The Reviewer also pointed out a number of weaknesses to the manuscript that we respond to one-by-one.
-In general, we feel that the Reviewer's comments reflect a high degree of statistical expertise; expertise that we do not expect to be shared by the bulk of our intended audience (empirical ecologists assembing new ecological networks).
+In general, we feel that the Reviewer's comments reflect a high degree of statistical expertise; expertise that we do not expect to be shared by the bulk of our intended audience (empirical ecologists assembling new ecological networks).
 We have therefore prioritised comments by this and the other Reviewers that seemed most likely to improve the manuscript for readers who are relatively new to Bayesian analysis over concerns most relevant to a highly knowledgeable reader.
@@
 
-			The fundamental question about predicting interactions given some incertainity has been and is debated in many papers (see the seminal paper by Roger Guimer\`{a} and Marta Sales-Pardo, PNAS, 2009).
+			The fundamental question about predicting interactions given some uncertainty has been and is debated in many papers (see the seminal paper by Roger Guimer\`{a} and Marta Sales-Pardo, PNAS, 2009).
 Even if the proposed framework is probably not stated in its exact terms in the literature, bridges between existing approaches (beyond Ecology) and the one in the paper would be very welcomed.
@@
 		    The shape parameters, or hyperparameters, may be set to particular values or derived from some data (see below).
-Note that the hyperparameters may be set to the same values for all interactions, allowed to vary independently for all interactions, or may incorporate non-independence betwween interactions (e.g., when the shape of the prior distribution depends upon species' abundances or traits).
+Note that the hyperparameters may be set to the same values for all interactions, allowed to vary independently for all interactions, or may incorporate non-independence between interactions (e.g., when the shape of the prior distribution depends upon species' abundances or traits).
 		\end{quotation}
@@
 			the reader would appreciate that the authors discuss and prove the identifiability of the model.
-Indeed, the three levels of uncertainity are nested but one could wonder whether different parameters at the three levels can fit the same data with the same quality (i.e.
+Indeed, the three levels of uncertainty are nested but one could wonder whether different parameters at the three levels can fit the same data with the same quality (i.e.
 no identifiability).
@@
 		\begin{refquote}
-			the authors proposed an original approach based on a bayesian framework.
+			the authors proposed an original approach based on a Bayesian framework.
 Beyond the identifiability question (see above), the reader can question the power of the method.
 Usually, a methodological proposal comes with a complete simulation study that is supposed to show  the proposed model is adapted/suitable to the question and efficient to solve it.
-In the paper in its present form, the authors assume that the reader will be convinced by the results obtained on a single real dataset… In my opinion, the reader can’t be fairly convinced: how powerfull is the method?
+In the paper in its present form, the authors assume that the reader will be convinced by the results obtained on a single real dataset… In my opinion, the reader can’t be fairly convinced: how powerful is the method?
 what can we say about the priors?
@@
 The novelty and impact of our work, however, is not in the method itself (several other Reviewers rightly point out that similar approaches have occasionally been used before) but in connecting a Bayesian statistical approach to the problem of limited and uneven sampling of networks and, we hope, in making this method more accessible to those without extensive statistical or modelling experience.
-In other words, what we try to achieve here is to alert empirical ecologists constructing and analyzing networks to the uncertainties built into their work.
+In other words, what we try to achieve here is to alert empirical ecologists constructing and analysing networks to the uncertainties built into their work.
 We then try to provide them with simple tools for grasping the extent and consequences of typical patterns.
@@
 			5/ results\&discussion too short: the reader is surprised to read 27 lines of raw results only… Given the amount of new methodology that is proposed, one can expect a complete description of its pros and cons.
-Obvisouly, a simulation study (see above) would enrich the results part.
+Obviously, a simulation study (see above) would enrich the results part.
 Forgetting about the length of these parts, it is still difficult to catch the key messages from the text, and it is not obvious to relate discussion and the obtained results (for instance,from l.343 to l.351).
@@
 Although we have not conducted a simulation study (see above), we have extensively revised these sections in order to highlight the main thread through the manuscript.
-Due to space limitations, we were unable to greatly expand either section (we prioritise the introduciton and methods, which lay out the problem of uncertainty in networks and how it can be partially addressed), but we hope that the results now more clearly demonstrate how a Bayesian approach can address the uncertainty inherent in sampling.
+Due to space limitations, we were unable to greatly expand either section (we prioritise the introduction and methods, which lay out the problem of uncertainty in networks and how it can be partially addressed), but we hope that the results now more clearly demonstrate how a Bayesian approach can address the uncertainty inherent in sampling.
 
@@
 The authors chose upper case letters L,T ,X,D for single entities whereas the mathematician is used to expect matrices or constants in upper case.
-Traditionaly, given species i and j, we would consider interaction $L_ij$, feasibility $X_ij$, detectionability $D_ij$...
+Traditionally, given species i and j, we would consider interaction $L_ij$, feasibility $X_ij$, detection ability $D_ij$...
 \\
@@
 		\begin{refquote}
-			-l.278: the authors investigate the consequence of uncertainity on network metrics.
+			-l.278: the authors investigate the consequence of uncertainty on network metrics.
 This question is of peculiar interest, but here it is restricted to the connectance and nestedness.
@@
 Why not others?
-What is the impact of integrating incertainity into the metrics computation?
+What is the impact of integrating uncertainty into the metrics computation?
 (we guess the answers but we could expect the authors develop these points).
@@
 We are glad that the Reviewer agrees about the importance of this message and appreciate his/her suggestions to improve the manuscript.
-We have taken care to add references and clarify the introduction, as well as to state explicitly that we are emphaticallly not suggesting that anyone sample with lower effort/intensity than they otherwise would.
+We have taken care to add references and clarify the introduction, as well as to state explicitly that we are emphatically not suggesting that anyone sample with lower effort/intensity than they otherwise would.
 We considered the benefits of high-quality sampling to be so self-evident that it did not occur to us that our manuscript could be read as suggesting that extensive sampling is not worthwhile.
 We thank the Reviewer for pointing out the potential for confusion over this point and hope that it is now clear that Bayesian analyses are a complement to, not a replacement for, high-quality sampling.
-Below we adress each of the Reviewer's suggestions in detail.
+Below we address each of the Reviewer's suggestions in detail.
 
@@
 The simplest – do a better job of acknowledging what else has been done in the field – much of which has actually been done by the authors and their collaborators.
-Given that they know there work I won’t point that out (but they are under-siting this literature a bit) but they could consider Graham and Weinstein on-line early 2018 (I realize that this was just out when the author’s submitted but it has some very similar messages) and the empirical example of Weinstein and Graham in Ecology letters 2017.
+Given that they know there work I won’t point that out (but they are under-siting this literature a bit) but they could consider Graham and Weinstein on-line early 2018 (I realise that this was just out when the author’s submitted but it has some very similar messages) and the empirical example of Weinstein and Graham in Ecology letters 2017.
 I don’t think this would in any way diminish the importance of the current paper because I think the challenge in network ecology is to get people to use better quantitative methods.
@@
 		\textbf{R:} We thank the Reviewer for stressing the need to further acknowledge previous work in the field.
-As this was also emphasized by other reviewers, we have taken this carefully \emph{ad notam} and expanded our references to earlier work as much as possible given length restrictions.
+As this was also emphasised by other reviewers, we have taken this carefully \emph{ad notam} and expanded our references to earlier work as much as possible given length restrictions.
 We have taken particular care to add references to Graham/Weinsten papers as two of the reviewers suggested work by these authors.
@@
 		Line 7.
-It is certainly true that most networks are snapshots in time but there is a growing realization – including some nice examples (including those by the authors) that address this issue.
+It is certainly true that most networks are snapshots in time but there is a growing realisation – including some nice examples (including those by the authors) that address this issue.
 Maybe what you want to say is that we know that networks should not be considered static but we lack the tools – or ability to collect data – or whatever you think is the cause – to correct this situation.
@@
 		Line 89.
-In Weinstein and Graham (Ecology Letters) the processes modeled were trait matching (which you place in interaction uncertainty) and abundance (which is perhaps your process uncertainty??).
+In Weinstein and Graham (Ecology Letters) the processes modelled were trait matching (which you place in interaction uncertainty) and abundance (which is perhaps your process uncertainty??).
 I find myself quite confused based on how you describe things in this MS (See text above) and how you cite the literature.
@@
 		\textbf{R:} We have revised this section and now no longer refer to the specifics of Weinstein and Graham at all.
-Instead, we discuss repeated sampling in a section dedicated to the question of whether sampling is useful (of course it is) and whether it can completely solve problems of uncertainty in ecological networks (almost certinaly not).
+Instead, we discuss repeated sampling in a section dedicated to the question of whether sampling is useful (of course it is) and whether it can completely solve problems of uncertainty in ecological networks (almost certainly not).
 We hope that this is less confusing.
@@
 		Line 107.
-There is a lot of literature in wildlife ecology emphasizing the importance of repeat sampling for estimating detection probability.
+There is a lot of literature in wildlife ecology emphasising the importance of repeat sampling for estimating detection probability.
 Is this just wrong?
@@
 We therefore cannot suggest modelling co-occurrence as a panacea.
-Instead, we now emphasize that co-occurrence probabilities are one thing that could be included in a prior (lines XX-XX - section Informative priors).
+Instead, we now emphasise that co-occurrence probabilities are one thing that could be included in a prior (lines XX-XX - section Informative priors).
 		\smallskip
@@
 I think one of the reason non-Bayesians’ are not comfortable with the approach is that if you put in prior information on something like trait matching and test for trait matching and then discover trait matching is important – what does it mean?
-Maybe this is too obvious (I realize there are tons of papers on how to choose priors) but I wonder if it is worth explaining (would a box or something be worthwhile?
+Maybe this is too obvious (I realise there are tons of papers on how to choose priors) but I wonder if it is worth explaining (would a box or something be worthwhile?
 I leave it up to the authors/editor)?
@@
 Filtering networks in the way that we do could give an idea of how many networks are missing, but we do not think it is necessary to evaluate uncertainty (we believe that examining the posterior distributions directly is a better approach there).
-We have rephrased these lines (XX-XX) to emphasize that the filtered networks are intended to demonstrate the consequences of uncertainty more than anything else.
+We have rephrased these lines (XX-XX) to emphasise that the filtered networks are intended to demonstrate the consequences of uncertainty more than anything else.
 
@@
 
-	11. Skepticism about sampling requirements to be sure interactions do not occur [[done]]
+	11. Scepticism about sampling requirements to be sure interactions do not occur [[done]]
 
@@
 This statement is based on this study – are all systems like the gall system?
-If species are specialized or bound to interact for some other reason (i.e., co-occurring when there are few other resources) wouldn’t you need to observe fewer individuals?
+If species are specialised or bound to interact for some other reason (i.e., co-occurring when there are few other resources) wouldn’t you need to observe fewer individuals?
 The point of the method is that you can estimate how many individuals are needed….
@@
 
-		The Reviewer's suggestion that we might need fewer samples for species that are "specialized or bound to interact for some other reason" reflects a very strong prior.
+		The Reviewer's suggestion that we might need fewer samples for species that are "specialised or bound to interact for some other reason" reflects a very strong prior.
 In this case, yes we would need fewer samples for the species concerned.
@@
 In many cases, the assumptions involved in excluding interactions are less clear-cut and different researchers may disagree about which species are "bound to interact" (or not to interact).
-The concept of pollination syndromes is one example - many flower visitors are less rigidly specialized on particular flower types than initially thought~\citep{Ollerton2009}.
+The concept of pollination syndromes is one example - many flower visitors are less rigidly specialised on particular flower types than initially thought~\citep{Ollerton2009}.
 To address such "forbidden links", we now suggest that researchers explicitly state both the uncertainty about data-based zeros and the assumptions by which they create structural zeros.
@@
 
-		To make this clearer, we have rephrased this section and added a line (lines XX-XX) stating that we usually cannot determine the cause of all the zeros in an interaction matrix (we can identify obviously unfeasible interactions, but likely cannot say whether a zero for a rare species is because we did not observe enough individuals, there were not enough individuals to perform a particular interaction, or because the interaction is acutally unfeasible).
+		To make this clearer, we have rephrased this section and added a line (lines XX-XX) stating that we usually cannot determine the cause of all the zeros in an interaction matrix (we can identify obviously unfeasible interactions, but likely cannot say whether a zero for a rare species is because we did not observe enough individuals, there were not enough individuals to perform a particular interaction, or because the interaction is actually unfeasible).
 We hope that this revision makes it clearer that the description of different sources of uncertainty is a conceptual guide only.
@@
 Parasites, for example, are often concentrated in only a few individuals~\citep{Lagrue2015}.
-If these infected individuals do not happen to be included in a sample, their interactoins will be missed.
+If these infected individuals do not happen to be included in a sample, their interactions will be missed.
 
@@
 
-		\textbf{R:} As we are concerned with the metaweb (the set of feasible interactions) rather than the interactions which occurr at a given site on a given day, we do not think that assuming a probability of 1 for observed interactions introduces bias in our study.
+		\textbf{R:} As we are concerned with the metaweb (the set of feasible interactions) rather than the interactions which occur at a given site on a given day, we do not think that assuming a probability of 1 for observed interactions introduces bias in our study.
 We have added a justification of setting the probability of observed interactions to 1 in \emph{Appendix S2}.
-Note that each posterior web is a prediction of the true metaweb and not a local realization of some interactions drawn from the feasible set.
+Note that each posterior web is a prediction of the true metaweb and not a local realisation of some interactions drawn from the feasible set.
 These local webs are more akin to our "filtered webs" in which observed interactions are not guaranteed to appear.

### 2019-01-15 manuscript/CI_interactions.tex
spellcheck UK english

@@
     First, ecological communities are stochastic~\citep{Gotelli2000}.
-Community composition and abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}, leading to variation in encounter probabilites and hence interactions~\citep{Vazquez2005,Poisot2015,Graham2018}.
+Community composition and abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}, leading to variation in encounter probabilities and hence interactions~\citep{Vazquez2005,Poisot2015,Graham2018}.
 Species must co-occur in order to be observed interacting, so any variation in co-occurrence will create variation in the set of observed interactions~\citep{Gravel2013,Graham2018}.
@@
     To sum up, the absence of an interaction on a given day could be because it was not feasible [$P(L_{ij})=0$], was feasible but did not occur because of local conditions during sampling ($P(X_{ij}|L_{ij}=1)=0$], or was feasible and occurred during sampling but could not be observed [$P(D_{ij}|X_{ij}=1,L_{ij}=1)=0$].
-Note that some exteral factors can affect more than one level of uncertainty.
+Note that some external factors can affect more than one level of uncertainty.
 For example, rare species are less likely to interact at a given site due to neutral processes~\citep{Jordano2016,Graham2018}.
@@
     The basis of a Bayesian approach to modelling the probability that an interaction between species $i$ and $j$ occurs ($\lambda_{ij}$) is combining the maximum likelihood estimate (MLE) of $\lambda_{ij}$ with a prior distribution (described in the next section) and a normalising function.
-The MLE of $\lambda_{ij}$ can be modelled as a Bernoulli trial based on the number of observed interactions $k_ij$ and observed co-occurrances $n_{ij}$: $\lambda_{ij}=\frac{k_{ij}}{n_{ij}}$.
+The MLE of $\lambda_{ij}$ can be modelled as a Bernoulli trial based on the number of observed interactions $k_ij$ and observed co-occurrences $n_{ij}$: $\lambda_{ij}=\frac{k_{ij}}{n_{ij}}$.
 The most appropriate prior distribution for $\lambda_{ij}$ is the beta distribution:
@@
     The shape parameters, or hyperparameters, may be set to particular values or derived from some data (see below).
-Note that the hyperparameters may be set to the same values for all interactions, allowed to vary independently for all interactions, or may incorporate non-independence betwween interactions (e.g., when the shape of the prior distribution depends upon species' abundances or traits).
+Note that the hyperparameters may be set to the same values for all interactions, allowed to vary independently for all interactions, or may incorporate non-independence between interactions (e.g., when the shape of the prior distribution depends upon species' abundances or traits).
     Combining the prior distribution with the MLE of $\lambda_{ij}$ derived from observed data, we obtain a posterior distribution that also follows a beta distribution with new hyperparameters $\alpha_{ij}'=\alpha_{ij}+k$ and $\beta_{ij}'=\beta_{ij}+n-k$ (\emph{Appendix S3}).
@@
         In most cases, we have some prior knowledge which we can use to inform uncertainty about interactions.
-One common example is the well-justified assumption that plants will not consume animals in a food web; excluding carnivorous plants it is not contentious to say that we are certain that unobserved links indicating plants feeding on animals truldy do not occur.
+One common example is the well-justified assumption that plants will not consume animals in a food web; excluding carnivorous plants it is not contentious to say that we are certain that unobserved links indicating plants feeding on animals truly do not occur.
 Similarly, if we observed two species which are normally obligate mutualists co-occurring but not interacting, we would be very doubtful that a zero reflecting this interaction was true (i.e., high uncertainty about this zero).
@@
 Returning to the example of degree distributions, approximate Bayes allows us to use information from abundant and easily-sampled species to predict interaction probabilities for species which were observed only rarely.
-Despite its practicality, approximate Bayes has been criticized for being overly subjective~\citep{Berger2006} and because estimating hyperparameters from data serves as an approximation of some true hyperparameters which remain unknown~\citep{Gelmanblog}.
+Despite its practicality, approximate Bayes has been criticised for being overly subjective~\citep{Berger2006} and because estimating hyperparameters from data serves as an approximation of some true hyperparameters which remain unknown~\citep{Gelmanblog}.
 We therefore encourage researchers to carefully consider whether external data or an appropriate trait model is available before opting for a prior based on some of their own data.
@@
 This simulates an empirical Bayes model using a pilot site to inform the prior distribution.
-A site in the middle of the geographic distribution was chosed in order to minimize bias due to the potential for a northern or southern site to exclude species with restricted ranges.
-To demonstrate how the use of data from a different system can affect the prior distribution and conclusions based on it, we repeated our analyses using priors derived from a much smaller system, which provided unreasonable distributions for interaction probabilites (\emph{Appendix S7}).
+A site in the middle of the geographic distribution was chosen in order to minimise bias due to the potential for a northern or southern site to exclude species with restricted ranges.
+To demonstrate how the use of data from a different system can affect the prior distribution and conclusions based on it, we repeated our analyses using priors derived from a much smaller system, which provided unreasonable distributions for interaction probabilities (\emph{Appendix S7}).
 

### 2019-01-16 manuscript/reply_to_reviewers.tex
added Dom comments to reply

@@
 Changed filtering to reflect all uncertainty, not just detection (more accurate, hopefully less confusing).
-No box needed, just "Why sample" section.
+No box needed, just ``Why sample'' section.
 
@@
 We argue that a great deal of subjectivity is baked into the compilation of empirical networks and that a Bayesian approach can be seen as making this subjectivity explicit.
-We hope that this will encourage empiricists to explicitly use their system-specific knowledge to create reasonable priors, as likely already occurs subconsciously (as in the designation of "forbidden links").
+We hope that this will encourage empiricists to explicitly use their system-specific knowledge to create reasonable priors, as likely already occurs subconsciously (as in the designation of ``forbidden links``).
 
@@
 	Finally, several of the Reviewers appeared to believe that we were advocating for reduced sampling effort.
-That is emphatically not the case (we find the idea absurd), and we have revised the manuscript to be clearer about the fact that increased sampling effort can reduce some sources of uncertainty.
-We hope that it is now clear that the Bayesian framework we promote is a complement to high sampling effort.
+That is emphatically not the case (we had not anticipated that anyone would seriously consider sampling less than they otherwise would when using our framework), and we have revised the manuscript to be clearer about the fact that increased sampling effort can reduce some sources of uncertainty and that high-quality sampling should form the basis of any empirical network.
+We hope that it is now clear that the Bayesian framework we promote is a complement to excellent field work, not a replacement for it.
 
@@
 In the present revision we have taken this advice to heart and streamlined our introduction in order to expand our discussion of prior choice.
-In this revision, we have retained some of the introductory material which the Reviewer notes describes ``ground very well-trod'' in order to ensure that readers entirely new to Bayesian analysis will understand the problem at hand.
+In this revision, we have retained some of the introductory material, which the Reviewer notes describes ``ground very well-trod'', in order to ensure that readers entirely new to Bayesian analysis will understand the problem at hand.
 We hope that the introduction now strikes a balance between providing essential background information for Bayesian novices and moving quickly enough for those who do not need such a gentle introduction.
@@
 		\begin{refquote}
-			In ecology more broadly, priors are treated with timidity, as if we couldn’t dare to leverage past work on our current understanding.
+			In ecology more broadly, priors are treated with timidity, as if we couldn't dare to leverage past work on our current understanding.
 Personally, I have always felt limited by this standard.
@@
 In doing so, we have happily adopted the suggestion to expand our discussion of prior selection, particularly with regard to approximate/empirical Bayes.
-Although we are somewhat space-limited, we have expanded our description of the different priors available and why a researcher might choose one over another (section beginning with line 253).
-We also touch upon the controversy over using empirical priors (lines 348-353) although we were unable to find many references addressing this in detail.
+Although we are somewhat space-limited, we have expanded our description of the different priors available and why a researcher might choose one over another (section beginning with line 200).
+We also touch upon the controversy over using empirical priors (lines 283-289) although we were unable to find many references addressing this in detail.
 We hope that this expanded description will be a better guide for empiricists who may not be familiar with Bayesian statistics.
@@
 We stress that our intended target audience is empirical ecologists working on network description who likely have a different skillset than that of the Reviewer.
-We also note that Reviewer 2 found that \emph{``The introduction is particularly pleasant to read and the problem is well stated"}, praise which we would hate to loose.
+We also note that Reviewer 2 found that \emph{``The introduction is particularly pleasant to read and the problem is well stated``}, praise which we would hate to lose.
 Therefore we have revised and streamlined our introduction but still refrain from jumping straight into prior selection.
-We have, however, taken care to introduce our analysis as a worked example (lines 355) and hope that this helps to reduce the conflict between the introduction and our data.
+We have, however, taken care to introduce our analysis as a worked example (lines 200-201) and hope that this helps to reduce the conflict between the introduction and our data.
 
@@
 		\begin{refquote}
-		It’s a bit confusing to lead the reader towards a Bayesian analysis, and then immediately start with the MLE estimate. Why is this needed at all? (L162-186). Just start at 187?
+		It's a bit confusing to lead the reader towards a Bayesian analysis, and then immediately start with the MLE estimate. Why is this needed at all? (L162-186). Just start at 187?
 		\end{refquote}
@@
 		\textbf{R:} The MLE estimate is part of the Bayesian framework as it dictates the shape of the distribution that we use.
-We now introduce the MLE formally within this context (lines 229-231) and take care to be explicit when using it to explore the sample size needed in the absence of prior knowledge later (caption of Figure 3).
-
-		Lines 229-231:
-
-		\begin{quotation}
-			The basis of a Bayesian approach to modelling the probability that an interaction occurs ($\lambda$) is combining the maximum likelihood estimate (MLE) of $\lambda$ with a prior distribution (described in the next section) and a normalising function.
-The MLE of $\lambda$ can be modelled as a Bernoulli trial based on the number of observed interactions $k$ and observed co-occurrences $n$: $\lambda = \frac{k}{n}$.
-The most appropriate prior distribution for a probability such as $\lambda$ is the beta distribution:
-		\end{quotation}
-
-		Caption of figure 3:
+Moreover, it helps to formalise our argument that most networks are undersampled, justifying the Bayesian approach and the use of priors to reduce/set bounds around the resulting uncertainty.
+We therefore feel that it is important to keep some discussion of the MLE estimate in the manuscript.
+We now introduce the MLE formally within this context (lines 179-184) and take care to be explicit when using it to explore the sample size needed in the absence of prior knowledge later (caption of Figure S2, \emph{Appendix S2}}).
+
+		Lines 179-184:
+
+		\begin{quotation}
+			The basis of a Bayesian approach to modelling the probability that an interaction between species $i$ and $j$ occurs ($\lambda_{ij}$) is combining the maximum likelihood estimate (MLE) of $\lambda_{ij}$ with a prior distribution (described in the next section) and a normalising function.
+The MLE of $\lambda_{ij}$ can be modelled as a Bernoulli trial based on the number of observed interactions $k_ij$ and observed co-occurrences $n_{ij}$: $\lambda_{ij}=\frac{k_{ij}}{n_{ij}}$.
+The most appropriate prior distribution for $\lambda_{ij}$ is the beta distribution:
+		\end{quotation}
+
+		Caption of Figure S2:
 
@@
 		\textbf{R:} While we feel that a short introduction to the beta distribution is important to bring researchers new to Bayesian statistics up to speed (and give them some keywords to Google), we accept the Reviewer's suggestion to reduce the amount of space given to the beta.
-We have therefore moved the description of basic properties to Appendix S2.
+We have therefore moved the description of basic properties to Appendix S3.
 The remaining paragraph introducing the beta distribution now leads directly into the section describing prior selection.
@@
 		\begin{refquote}
-		I’m wrestling with the novelty of the work as presented and whether it reaches the standard for publication at MEE.
+		I'm wrestling with the novelty of the work as presented and whether it reaches the standard for publication at MEE.
 Certainly, much of this logic is laid out in other works.
 The authors are well aware of this and have made significant contributions to this topic in the last few years.
-In particular, the authors should try to be much more explicit about the contribution they hope to offer that hasn’t been covered.
+In particular, the authors should try to be much more explicit about the contribution they hope to offer that hasn't been covered.
 ...
@@
 We also emphasise that our approach is not restricted to species observed X times (as many predictive models are) and can include species not yet observed at a site (e.g., potential invaders).
+Finally, we note that there is a need to synthesise the literature on sampling issues and formalise the sources of uncertainty affecting the estimation of pairwise interactions.
+There are, as the Reviewer notes, already a number of publications addressing probabilistic interactions, but none of them adequately characterise uncertainty about interactions.
 We hope that the contribution our manuscript makes is now clearer.
@@
 
-		\textbf{R:} We now address questions of sampling in the subsection \textbf{Why can't we sample more?}.
+		\textbf{R:} We now address questions of sampling in the paragraph beginning with line 168 and in Appendix S2.
 We hope that this revision makes it clear that sampling should be as high-quality as possible but that sampling is unlikely to completely remove uncertainty.
@@
 doi:10.1111/2041-210X.12103
-		% Wells, K., & O’Hara, R.
+		% Wells, K., & O'Hara, R.
 B.
@@
 
-	The Reviewer stated that our manuscript ``tackles a very interesting problem, quantifying the uncertainty of interactions" which he/she rates as ``one of the hottest topics in the field".
-He/she also points out that ``the introduction is particularly pleasant to read" and that we framed the problem well.
+	The Reviewer stated that our manuscript ``tackles a very interesting problem, quantifying the uncertainty of interactions'' which he/she rates as ``one of the hottest topics in the field``.
+He/she also points out that ``the introduction is particularly pleasant to read'' and that we framed the problem well.
 The Reviewer also pointed out a number of weaknesses to the manuscript that we respond to one-by-one.
@@
 We hope that our revised manuscript makes this target audience clearer, and that we have addressed the Reviewer's key concerns with our revision.
-
-	1. Lack of references [done]
+Below, we respond to each of the Reviewer's comments (preceded by \textbf{R:}) in turn.
+
+	1. Lack of references
 
@@
 As stated above, we have now added many further pointers to previous work, and also been much more explicit regarding whom we try to reach with what message in the current paper.
-
-	2. Non-independence of interactions not accounted for [done]
+We have also included references from medical and epidemiological research as examples of the use of Bayesian methods beyond ecology.
+
+	2. Non-independence of interactions not accounted for
 
@@
 			2/ network oversight: the approach considers that the interactions are independent, which is not the case in real data.
-Indeed, the paper is supposed to be “network-oriented“ but the methodology deals with independent interactions (e.g.
+Indeed, the paper is supposed to be ``network-oriented'' but the methodology deals with independent interactions (e.g.
 the variables L,T,X and D introduced lines 62,77,101 are for instance not indexed by ij which could have suggested that the interactions were seen as a whole).
@@
 Nevertheless, non-independence of interactions is an important consideration.
-We are therefore happy to index all variables referring to interactions by ij and we have added an explicit statement (lines XX-XX) that some priors treat interactions independently while others will introduce covariance (e.g., by species).
-
-		Lines XX-XX:
+We are therefore happy to index all variables referring to interactions by ij and we have added explicit statements (lines 186-190 and 248-255) that some priors treat interactions independently while others will introduce covariance (e.g., by species).
+
+		Lines 186-190:
 
@@
 
-	3. Question about identifiability of the model [done]
+		Lines 248-255:
+
+		\begin{quotation}
+			Multiple sources of information can be combined into a single model (e.g., the the $K$ nearest neighbour (KNN) algorithm, which identifies likely interaction partners based on similarity to known partners~\citep{DesjardinsProulx}).
+This would result in a highly informative prior that would, moreover, account for some of the non-independence in interaction probabilities.
+
+	        Using an informative prior like these tailors the level of uncertainty surrounding each interaction and may account for non-independence of interactions (as in abundance-based or KNN models).
+	    \end{quotation}
+
+	3. Question about identifiability of the model
 
@@
 The only inputs are a prior distribution, which could refer to any level of uncertainty applicable to the study at hand, and post-hoc counts of interactions and co-occurrences.
-Using only the observed data, it is impossible to separate the three levels of uncertainty and our model does not aim to do so (as stated in lines XX-XX and lines XX-XX).
+Using only the observed data, it is impossible to separate the three levels of uncertainty and our model does not aim to do so (as stated in lines 159-167 and lines 199-201).
 We therefore do not believe that an in-depth discussion of identifiability would add much value to the manuscript and, in the interest of space, have decided not to include one.
-
-		Lines XX-XX:
-
-		\begin{quotation}
-			When considering a metaweb, we wish to separate the unobserved interactions where $L_{ij} = 0$ (i.e., unfeasible interactions) from interactions which could occur but did not at a particular sampling site or which occurred but were not detected (Fig.
-1).
+Instead, we refer interested readers to~\citet{Weinstein2017} which does attempt to separate sources of uncertainty.
+
+		Lines 159-167:
+
+		\begin{quotation}
+			When considering a metaweb, we wish to separate the unobserved interactions where $L_{ij}=0$ (i.e., unfeasible interactions) from interactions which could occur but did not at a particular sampling site or which occurred but were not detected (Fig.~\ref{conceptual_fig}).
 Unfortunately, this is not possible for most interactions (except those where we know an interaction is truly not feasible).
 That is, we generally do not know \emph{why} an interaction was not observed, only that it was not.
-An empirical ecologist will instead measure the marginal probability $P(L_{ij}) = k_{ij}/n_{ij}$, where $k_{ij}$ is the number of observed interactions between species $i$ and $j$ and $n_{ij}$ the number of observed co-occurrences.
+An empirical ecologist will instead measure the marginal probability $P(L_{ij})=k_{ij}/n_{ij}$, where $k_{ij}$ is the number of observed interactions between species $i$ and $j$ and $n_{ij}$ the number of observed co-occurrences.
 Given this information, the question becomes: how can we reduce the uncertainty around our estimated interaction probability?
@@
 
-		Lines XX-XX:
-
-		\begin{quotation}
-			Note that these Bayesian models of $\lambda_{ij}$ are designed to quantify (and reduce) the total uncertainty about $\lambda_{ij}$.
-They do not address any of the nested sources of uncertainty in particular except through the choice of prior.
-		\end{quotation}
-
-	4. Request for a simulation study [done; thanks Tomas]
+		Lines 199-201:
+
+		\begin{quotation}
+			 Note that these models of $\lambda_{ij}$ do not distinguish between sources of uncertainty except through the choice of prior.
+For a model which attempts to separate sources of uncertainty, see~\citet{Weinstein2017}.
+		\end{quotation}
+
+	4. Request for a simulation study
 
@@
 Usually, a methodological proposal comes with a complete simulation study that is supposed to show  the proposed model is adapted/suitable to the question and efficient to solve it.
-In the paper in its present form, the authors assume that the reader will be convinced by the results obtained on a single real dataset… In my opinion, the reader can’t be fairly convinced: how powerful is the method?
+In the paper in its present form, the authors assume that the reader will be convinced by the results obtained on a single real dataset...
+In my opinion, the reader can't be fairly convinced: how powerful is the method?
 what can we say about the priors?
 how much data (n, k) is necessary to expect good results?
-An so on… Only a well-conducted simulation study can answer these questions.
-		\end{refquote}
-
-		\textbf{R:} We agree with the Reviewer that a full simulation study, based on recreating the sources of uncertainty in a data set generated from known processes, is an excellent way to demonstrate the power of a novel method.
+An so on...
+Only a well-conducted simulation study can answer these questions.
+		\end{refquote}
+
+		\textbf{R:} We agree with the Reviewer that a full simulation study, based on recreating the sources of uncertainty in a data set generated from known processes, is a good way to demonstrate the power of a novel method.
 The novelty and impact of our work, however, is not in the method itself (several other Reviewers rightly point out that similar approaches have occasionally been used before) but in connecting a Bayesian statistical approach to the problem of limited and uneven sampling of networks and, we hope, in making this method more accessible to those without extensive statistical or modelling experience.
@@
 
-	5. Request for an extended results and discussion section [no actual response, just words]
-
-		\begin{refquote}
-			5/ results\&discussion too short: the reader is surprised to read 27 lines of raw results only… Given the amount of new methodology that is proposed, one can expect a complete description of its pros and cons.
+		We must also point out that some of the Reviewer's questions (e.g., how much data is necessary to expect good results) have already been answered analytically.
+Without an informative prior, we need approximately 35 observed co-occurrences with no observed interaction to be 95\% confident that the interaction does not occur.
+We also provide simple R code that will allow interested readers to analytically explore the response of confidence intervals, etc.
+to different amounts of data and different strengths of priors.
+While a simulation study could help to develop intuitions about changing field conditions, these analytical responses are exact and more general.
+
+	5. Request for an extended results and discussion section
+
+		\begin{refquote}
+			5/ results\&discussion too short: the reader is surprised to read 27 lines of raw results only...
+Given the amount of new methodology that is proposed, one can expect a complete description of its pros and cons.
 Obviously, a simulation study (see above) would enrich the results part.
@@
 
-	6. Suggestions to improve notation [done? unless anyone else can figure out the last part...]
+	6. Suggestions to improve notation
 
@@
 			How can be D<1 on l.169? D=0 or 1 since it says if an interaction is detectable or not... \\
-			Moreover, L is reused later but is the number of interactions (l.100 supp.mat)… \\
-			What is “N” in Figure 4? is it “n”? What is $n_ij$ and $k_ij$ l.266? Never defined, never reused. \\
+			Moreover, L is reused later but is the number of interactions (l.100 supp.mat)... \\
+			What is ``N'' in Figure 4? is it ``n''? What is $n_ij$ and $k_ij$ l.266? Never defined, never reused. \\
 			In the beginning of the paper, $\lambda$ is a probability (l.62) but it becomes a random variable (l.164): it would be more consistent to introduce before the notion of hyperparameters  (l.209-213) and to explain we consider that $\lambda$ is drawn into its distribution.
@@
 
-	7. l.62: define formally T [done]
-
-		\textbf{R}: We now define $T_{ij}$ as ``some function describing trait-matching between species $i$ and $j$ $\mathbf{T_{ij}}$".
+	7. l.62: define formally T
+
+		\textbf{R}: We now define $T_{ij}$ as ``some function describing trait-matching $\mathbf{T_{ij}}$``.
 This definition is intentionally open-ended as we foresee that $T_{ij}$ could be binary (traits are compatible or not) or continuous with a wide array of distributions.
 
-	8. Clarify the point of analysing the data using an alternative prior [done]
-
-		\begin{refquote}	
-			-l.244: this is weird to mention that the analysis has been done on another dataset but that the results will not be discussed… What is the interest for the reader?
+	8. Clarify the point of analysing the data using an alternative prior
+
+		\begin{refquote}	
+			-l.244: this is weird to mention that the analysis has been done on another dataset but that the results will not be discussed... What is the interest for the reader?
 		\end{refquote}
@@
 
-	9. No ``moral network" [not sure about this one.]
+	9. No ``moral network''
 
@@
 
-		\textbf{R}: We do not agree with this assessment.
-We do not explicitly consider the interactions to be independent, although we also do not explicitly define a dependence structure (we did not have data on species abundances or preferences that would allow us to do this).
-Even had we specifically stated that interactions are considered independent, this would not be unique among network analyses (see e.g., ...).
+		\textbf{R:} While we do implicitly consider interactions independent, we disagree that there is no network in the approach.
+The structure of the network is used to design our prior distribution for interaction probabilities, and we show how an understanding of uncertainty at the level of species pairs is essential to understand uncertainty about network-level properties (Appendix S10).
+Note that even had we specifically stated that interactions are considered independent, this would not be unique among network analyses (see e.g., ...).
 To us, non-independence of interactions is not necessary when considering a network.
@@
 
-	10. l.252: not clear. Why this choice? [done]
+	10. l.252: not clear. Why this choice?
 
@@
 
-		Lines 369-373:
-
-		\begin{quotation}
-			researchers must choose between using a less-informative prior (e.g., one based on distributions of links across a large set of networks) or an empirical prior based on some ”training data” from the study.
-Here, we opted for the latter and created priors using a single sub-network from the middle of the geographical distribution of the Kopelke et al.
-(2017) dataset.
-		\end{quotation}
-
-	11. l.259: not clear [done]
+		Lines 320-324:
+
+		\begin{quotation}
+			As we lack a trait-based model or similar published network, we will use data from a single sub-network from the middle of the geographical distribution of the~\citet{Kopelke2017} dataset to inform our prior distribution.
+This simulates an empirical Bayes model using a pilot site to inform the prior distribution.
+A site in the middle of the geographic distribution was chosen in order to minimise bias towards species at any geographic extreme.
+		\end{quotation}
+
+	11. l.259: not clear
 
@@
 
-		Lines 373-379:
-
-		\begin{quotation}
-			To demonstrate how the use of data from a different system can affect the prior distribution and conclusions based on it, we repeated our analyses using priors derived from a much smaller Salix-galler-natural enemy system based around genotypes of a single Salix species (Barbour et al., 2016, Data available from the Dryad Digital Repository: https://doi.org/10.5061/dryad.g7805).
-This smaller system was much more densely-connected than that described in Kopelke et al.
-(2017) and provided unreasonable distributions for interaction probabilities (Appendix S6 ).
-		\end{quotation}
-
-	12. Why connectance and nestedness? [done?]
+		Lines 324-326:
+
+		\begin{quotation}
+			To demonstrate how a poor choice of prior can give unreasonable posterior distributions, we repeated our analyses using priors derived from a much smaller system (\emph{Appendix S7}).
+		\end{quotation}
+
+	12. Why connectance and nestedness?
 
@@
 
-	13. l.291: explain better the simulation procedure [done]
+	13. l.291: explain better the simulation procedure
 
@@
 		\textbf{R:} Nestedness being higher in the observed networks simply means that the additional interactions predicted by our model tend not to be between generalists and specialists and, as such, do not contribute strongly to nestedness.
-This is actually somewhat intuitive - ``specialists" in the observed data are exactly those species for which we are most likely to be missing interactions, and interactions between specialists and the most likely to be predicted to occur but not have been observed.
+This is actually somewhat intuitive - ``specialists'' in the observed data are exactly those species for which we are most likely to be missing interactions, and interactions between specialists and the most likely to be predicted to occur but not have been observed.
 Due to the tight word limit, we do not have space to discuss this extensively in the manuscript but have added brief interpretations in the results.
@@
 
-	The Reviewer commented that our paper is, overall, very good and ``makes an important contribution" as ``a very nice attempt to show the broader community that the Bayesian approach is not so complex and has many advantages".
+	The Reviewer commented that our paper is, overall, very good and ``makes an important contribution'' as ``a very nice attempt to show the broader community that the Bayesian approach is not so complex and has many advantages``.
 We are glad that the Reviewer agrees about the importance of this message and appreciate his/her suggestions to improve the manuscript.
@@
 We thank the Reviewer for pointing out the potential for confusion over this point and hope that it is now clear that Bayesian analyses are a complement to, not a replacement for, high-quality sampling.
-Below we address each of the Reviewer's suggestions in detail.
-
-	1. Add more references to the literature [[done]]
+Below we address each of the Reviewer's suggestions (response preceded with \textbf{R:}) in detail.
+
+	1. Add more references to the literature
 
@@
 The simplest – do a better job of acknowledging what else has been done in the field – much of which has actually been done by the authors and their collaborators.
-Given that they know there work I won’t point that out (but they are under-siting this literature a bit) but they could consider Graham and Weinstein on-line early 2018 (I realise that this was just out when the author’s submitted but it has some very similar messages) and the empirical example of Weinstein and Graham in Ecology letters 2017.
-I don’t think this would in any way diminish the importance of the current paper because I think the challenge in network ecology is to get people to use better quantitative methods.
+Given that they know there work I won't point that out (but they are under-siting this literature a bit) but they could consider Graham and Weinstein on-line early 2018 (I realise that this was just out when the author's submitted but it has some very similar messages) and the empirical example of Weinstein and Graham in Ecology letters 2017.
+I don't think this would in any way diminish the importance of the current paper because I think the challenge in network ecology is to get people to use better quantitative methods.
 		\end{refquote}
@@
 We have taken particular care to add references to Graham/Weinsten papers as two of the reviewers suggested work by these authors.
-We hope that the introduction now presents a more thorough sample of previous work.
+We hope that the introduction now presents a more thorough sample of previous work, remembering that our manuscript is not intended to be a comprehensive review.
 
@@
 
-		\textbf{R:} We agree with the Reviewer regarding our intended meaning, and have modified this accordingly:
-
-			\begin{quotation}
-				Despite this additional information, empirical descriptions of ecological networks are still often limited by a lack of data or tools to adequately incorporate variation in interactions into networks.
-			\end{quotation}
-
-		\begin{refquote}
-		Line 30.  There are several conceptual and empirical attempts to consider detection probability – why aren’t these cited (work by Bartomeus comes to mind).\\
+		\textbf{R:} When revising the manusript we removed line 7 and no longer refer to networks as snapshots.
+
+		\begin{refquote}
+		Line 30.  There are several conceptual and empirical attempts to consider detection probability – why aren't these cited (work by Bartomeus comes to mind).\\
 		\end{refquote}
@@
 		\textbf{R:} We have revised this section and now no longer refer to the specifics of Weinstein and Graham at all.
-Instead, we discuss repeated sampling in a section dedicated to the question of whether sampling is useful (of course it is) and whether it can completely solve problems of uncertainty in ecological networks (almost certainly not).
+Instead, we discuss repeated sampling in an appendix dedicated to the question of whether sampling is useful (of course it is) and whether it can completely solve problems of uncertainty in ecological networks (almost certainly not).
 We hope that this is less confusing.
@@
 Please note that a paper with a very similar aim was recently published (Graham and Weinstein).
-This does not to diminish the value of this study in any way, as multiple perspectives on quantitative solutions in network ecology are urgently needed…..
+This does not to diminish the value of this study in any way, as multiple perspectives on quantitative solutions in network ecology are urgently needed.....
 but the other work should be considered.
@@
 We have also revised this section in hopes of making the uniqueness of our framework (its simplicity and adaptability) clear.
+% Dom and Tomas have a paper that also addresses this, but I'm not quite sure which one (you're both too productive!)
 
@@
 I am pretty sure this idea is in the literature several times and should be cited.
-Isn’t this the same as drawing a probability of interaction from a distribution where the distribution of each interaction is an output of the Bayesian method?\\
+Isn't this the same as drawing a probability of interaction from a distribution where the distribution of each interaction is an output of the Bayesian method?
 		\end{refquote}
@@
 
-	2. Clarify confusing terminology [[done]]
+	2. Clarify confusing terminology
 
@@
 Two things come to mind – the use of terms and distinction between interaction and process uncertainty; and the somewhat contradictory sounding statements about if sampling more is actually good.
-		\medskip
+
 		Line 86.
@@
 Should this be stated?
-You might also consider a different word that process as “observation models” and “process models” are commonly used terms in Bayesian stats and in this case “process” often considers what you call “interaction”.
+You might also consider a different word that process as ``observation models'' and ``process models'' are commonly used terms in Bayesian stats and in this case ``process'' often considers what you call ``interaction''.
 There are some interesting to attempts to model co-evolution that consider similar ideas (i.e., a barrier to interaction and then trait-matching; but maybe outside of the scope of this MS).
@@
 Hopefully this will discourage readers from getting bogged down in trying to isolate which external factors cause which types of uncertainty (there is almost certainly overlap - e.g., bad weather could both reduce the probability that species will be active and interact and the probability that an interaction is observed if visibility is poor).
-We have also added a section (lines XX-XX) referring to "forbidden links" which address aspects of whether species can interact (which we had previously called interaction uncertainty) and whether they do interact at a particular site (previously process uncertainty).
+We have also added a section (beginning line 117) referring to ``forbidden links'' which addresses overlap between the questions of whether species can interact (which we had previously called interaction uncertainty) and whether they do interact at a particular site (previously process uncertainty).
 We hope that this addition clarifies the agreement of our manuscript with previous works listing sources of uncertainty.
@@
 			\begin{quotation}
-
         \textbf{Forbidden links}
 
-            Both of the above sources of uncertainty (i.e., whether species would be able to interact given their traits and whether they are able to interact at a particular place and time) are addressed in the concept of "forbidden links"~\citep{Jordano2016}.
-In this framework, all links which are prevented by spatio-temporal uncoupling~\citep{Jordano1987}, physiological constraints~\citep{Jordano1987}, etc.
-are considered "structural zeros" that cannot be observed~\citep{Jordano2016}.
+            Both whether species can ever interact and whether they interact at a particular place and time have been discussed in the context of ``forbidden links``~\citep{Jordano2016}.
+In this framework, all links which are prevented by spatio-temporal uncoupling, physiological constraints, etc.
+are considered ``structural zeros'' that cannot be observed~\citep{Jordano1987,Jordano2016}.
 We conceptually distinguish between physiological constraints and spatio-temporal uncoupling to allow for cases in which a species is introduced to a new habitat, expands its range, or shifts phenology~\citep{Gravel2013}.
-In such cases, links which are forbidden due to physiological constraints remain forbidden but links previously forbidden due to spatio-temporal mismatch could potentially occur.
-
-      \end{quotation}
-
-	3. Introduction of the case study seems off-topic and illogical. [[done]]
+In such cases, links which are impossible due to physiological constraints remain forbidden but links previously ``forbidden'' by spatio-temporal mismatch could potentially occur.
+      \end{quotation}
+
+	3. Introduction of the case study seems off-topic and illogical.
 
@@
 Is the goal to show the gaps in sampling or to apply the model described thus far to consider the 3 different types of uncertainty outlined?
-At this point the reader is confused about the goal…
+At this point the reader is confused about the goal...
 		\medskip
@@
 
-		\textbf{R:} We have expanded our introduction of the case study (lines XX-XX) to make it clear that we are using the highest-quality empirical network we can find as even such networks have uncertainty about unobserved interactions.
-This relates back to our point that urging increased sampling effort is not likely to solve problems of uncertainty as long as sampling is limited in number of methodologies, biased towards abundant or easy-to-identify species, restricted to particular spatial sites and/or environmental conditions (if the network is intended to be more general), or all of the above.
+		\textbf{R:} We have expanded our introduction of the case study (beginning line 295) to make it clear that we are using the highest-quality empirical network we can find as even such networks have uncertainty about unobserved interactions.
+This relates back to our point that urging increased sampling effort is not likely to solve problems of uncertainty as long as sampling is limited in the number of methodologies that can be applied, biased towards abundant or easy-to-identify species, restricted to particular spatial sites and/or environmental conditions (if the network is intended to be more general), or all of the above.
+Given budgetary constraints, it is extremely likely that empirical ecologists cannot sample as intensively and extensively as they would like and therefore some uncertainty is likely to remain.
 We repeat this point in the discussion to ensure that the case study is relevant.
-We have also clarified our statement that strict Bayes does not allow empirical priors, but that they are an option for researchers that are more concerned about matching their prior to their study system than with strict formalism (lines XX-XX).
+We have also clarified our statement that a strict application of Bayesian statistics does not allow empirical priors, but that they are an option for researchers that are more concerned about matching their prior to their study system than with strict formalism (lines 296-293).
 As Reviewer 1 points out, this is somewhat controversial and we feel it is important to note the potential objection.
@@
 		\begin{quotation}
+		  \subsection*{An empirical example}
 
@@
 This dataset consists of a single community type sampled across Europe over 29 years and at 374 unique locations.
-The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (see \emph{Appendix S4} for details).
-      The high spatiotemporal resolution of this dataset make it ideal for illustrating the difficulties in completely sampling a network; even with such an unusually high sampling effort, we anticipate that there will be many pairs of species which were rarely or never observed together.
+The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (see \emph{Appendix S5} for details).
+		      The high spatiotemporal resolution of this dataset make it ideal for illustrating the difficulties in completely sampling a network; even with such an unusually high sampling effort, there were many pairs of species which were rarely or never observed together and about which we therefore have high uncertainty about interaction probabilities (Fig.~\ref{histograms}).
 Using the Bayesian framework above, we can identify which potential interactions are more and less uncertain, allowing us to better predict the true structure of the metaweb.
-To show the gaps in sampling, we compared the frequencies of observed co-occurrences and interactions.
-We then calculated an empirical prior and computed the posterior distribution of the probability of an as-yet-unobserved interaction being feasible ($\lambda$).
-      We analysed both the \emph{Salix}-galler and galler-natural enemy components of the network but, for brevity, present only the latter here (see~\emph{Appendix S5} for \emph{Salix}-galler results).
-
-		\end{quotation}
-
-	4. Misunderstanding of our point about sampling effort [[done]]
+		      % To show the gaps in sampling, we compared the frequencies of observed co-occurrences and interactions. 
+		      We calculated an empirical prior and computed the posterior distribution of the probability of an as-yet-unobserved interaction being feasible ($\lambda_{ij}$).
+We analysed both the \emph{Salix}-galler and galler-natural enemy components of the network but, for brevity, present only the latter here (see~\emph{Appendix S6} for \emph{Salix}-galler results).
+		\end{quotation}
+
+	4. Misunderstanding of our point about sampling effort
 
 		\textbf{R:} We believe that the Reviewer has  misunderstood the point of our comments on sampling effort.
-Several of their comments suggest that we are advocating for reducing sampling effort.
+Several of their comments suggest that they believe that we are advocating for reducing sampling effort.
 This is emphatically not the case.
-Rather, we assumed that field researchers already sample to the maximum extent possible given their time and resource constraints and so a call to "sample more" would not be helpful.
-We now address this assumption explicitly in an appendix (Appendix S2)  dedicated to the potential for sampling effort to reduce uncertainty about interactions.
+Rather, we assumed that field researchers already sample to the maximum extent possible given their time and resource constraints and so a call to ``sample more'' would not be helpful.
+Increased sampling can reduce some sources of uncertainty, but is unlikely to remove all uncertainty and so is not a complete solution.
+We now address this explicitly in an appendix (Appendix S2)  dedicated to the potential for sampling effort to reduce uncertainty about interactions.
 Below, we address the Reviewer's sampling-related comments one by one.
@@
 It can, however, reveal knowledge gaps (as when a rare species is detected, revealing our ignorance of its interactions).
-This is not an argument against multiple sampling but a statement that increased sampling is likely to lead to the addition of more "false zeros" as species about which we know little are added to the network.
+This is not an argument against multiple sampling but a statement that increased sampling is likely to lead to the addition of more ``false zeros'' as species about which we know little are added to the network.
 
@@
 		Line 338 to 342.
-Throughout I am confused if the authors suggest more sampling is good or bad…  At the end of the paragraph it seems it isn’t so great to sample more because you end up with these annoying “0” values…??????
+Throughout I am confused if the authors suggest more sampling is good or bad...
+At the end of the paragraph it seems it isn't so great to sample more because you end up with these annoying ``0'' values...??????
 		\end{refquote}
@@
 We hope that it is now clear that sampling is very important but cannot completely eliminate uncertainty (except perhaps in some very species-poor and unusually static systems, but these are certainly rare).
-As to adding more zeros than ones specifically, this is only "bad" in the sense that it gives us more high-uncertainty cells in the interaction matrix.
-We take the view that it is better to have "known unknowns" than "unknown unknowns" and it is certainly better to know about more of the species in a community than fewer, but finding a single individual of a rare species will not reduce uncertainty in the web.
-We have added a line (XX-XX) specifically to address this.
+As to adding more zeros than ones specifically, this is only ``bad'' in the sense that it gives us more high-uncertainty cells in the interaction matrix.
+We take the view that it is better to have ``known unknowns'' than ``unknown unknowns'' and it is certainly better to know about more of the species in a community than fewer, but finding a single individual of a rare species will not reduce uncertainty in the web.
+We have added a line in \emph{Appendix S2} specifically to address this.
 
@@
 
-	5. Eliminate redundant "because" on line 23 [[done]]
+	5. Eliminate redundant ``because'' on line 23
 
@@
 
-	6. Reduce repetition of inevitable uncertainty [[done]]
+	6. Reduce repetition of inevitable uncertainty
 
@@
 		Line 73, 87.
-Maybe the idea that some uncertainty is “inevitable” should not be repeated in multiple sections.
-Either find a different way of saying it – or state it in your introductory paragraph and then don’t keep repeating.
-		\end{refquote}
-
-		\textbf{R:} We have rephrased the paragraph about detection uncertainty. The last line now reads:
-
-			\begin{quotation}
-
-				Until these gaps are filled, some interaction uncertainty will remain.
-
-			\end{quotation}
-
-	7. Why not always model probabilities of co-occurrence? [[done]]
-
-		\begin{refquote}
-		Line 142.  But shouldn’t you model the probability of two species co-occurring?  The authors have a paper doing this…. Is that not a good idea?
+Maybe the idea that some uncertainty is ``inevitable'' should not be repeated in multiple sections.
+Either find a different way of saying it – or state it in your introductory paragraph and then don't keep repeating.
+		\end{refquote}
+
+		\textbf{R:} We have rephrased the manuscript and the word ``inevitable'' no longer appears. We hope that the current phrasing is less repetitive.
+
+	7. Why not always model probabilities of co-occurrence?
+
+		\begin{refquote}
+		Line 142.  But shouldn't you model the probability of two species co-occurring?  The authors have a paper doing this.... Is that not a good idea?
 		\end{refquote}
@@
 		\textbf{R:} Modelling the probability of co-occurrence is an option for many systems (e.g., aquatic food webs where ranges of fish species are fairly well-known, as in~\citet{Gravel2013}).
+It may also be possible to separate the probability of observing an interaction at a particular location into a metaweb component (the focus of the current manuscript) and a co-occurrence probability as in~\citep{Gravel2018}.
+This addresses the question of interaction probabilities at specific locations, however, in contrast to our focus on metaweb interaction probabilities.
+
 		In some systems, however, the factors affecting probabilities of co-occurrence may not be known.
 We therefore cannot suggest modelling co-occurrence as a panacea.
-Instead, we now emphasise that co-occurrence probabilities are one thing that could be included in a prior (lines XX-XX - section Informative priors).
-		\smallskip
+Instead, we now emphasise that co-occurrence probabilities are one thing that could be included in a prior (section beginning line 231).
+[[Add a ref to Gravel 2018?]]
+
 		The fact remains that a lack of observed interactions between species which do not co-occur tells us nothing about whether these species \emph{could} interact if they should begin to co-occur (e.g., following a range shift).
-Following the Reviewer's suggestion, we have revised our manuscript to clarify our technology.
+Following the Reviewer's suggestion, we have revised our manuscript to clarify our terminology.
 In particular, we have taken care to specify which level of uncertainty we are addressing at different points in the manuscript.
@@
 
-	8. Issue of testing hypotheses based on inputs into models [[done]]
+	8. Issue of testing hypotheses based on inputs into models
 
@@
 		Line 121.
-I think one of the reason non-Bayesians’ are not comfortable with the approach is that if you put in prior information on something like trait matching and test for trait matching and then discover trait matching is important – what does it mean?
+I think one of the reason non-Bayesians' are not comfortable with the approach is that if you put in prior information on something like trait matching and test for trait matching and then discover trait matching is important – what does it mean?
 Maybe this is too obvious (I realise there are tons of papers on how to choose priors) but I wonder if it is worth explaining (would a box or something be worthwhile?
@@
 		\textbf{R:} Following suggestions by this Reviewer and another, we have substantially expanded our discussion of different options for priors (including the trait-based and co-occurrence models the Reviewer points out).
-We have also added an explicit statement that researchers wishing to test the influence of a particular trait (for example) should \emph{not} include that trait in their prior (lines XX-XX).
+We have also added an explicit statement that researchers wishing to test the influence of a particular trait (for example) should \emph{not} include that trait in their prior (lines 252-255).
 We hope that this statement, and the expanded discussion of different types of priors more generally, allay the Reviewer's concerns.
@@
 		\begin{quotation}
-			Similarly, if detailed information is available but refers to the question at hand, it is best to use a less informative prior so as not to force a particular result.
-For example, if researchers are interested in testing whether body-size ratios affect probabilities of interaction they should not use a prior which predicts interactions based on body sizes.
-		\end{quotation}
-
-	9. Redundancy in line 235 [[done]]
+			Also note that researchers wishing to test whether a particular trait influences interaction probabilities should either exclude that trait from their prior or model the network using priors which include and exclude the trait of interest (as in~\citet{Weinstein2017,Weinstein2017a}).
+		\end{quotation}
+
+	9. Redundancy in line 235
 
@@
 
-	10. Unsure about the point of filtering networks [[done]]
+	10. Unsure about the point of filtering networks
 
@@
 If we do not observe 20-50\% of the interactions in a network, then many network properties in the published literature will be inaccurate.
-Even worse, networks compiled under different levels of uncertainty (e.g., species with more or less variable traits, or studies with multiple sampling methods or only one) or with different sampling efforts will have network structure metrics that are inaccurate to different degrees.
+Even worse, networks compiled under different levels of uncertainty (e.g., species with more or less variable traits, or studies with multiple sampling methods versus only one) or with different sampling efforts will have network structure metrics that are inaccurate to different degrees.
 Filtering networks in the way that we do could give an idea of how many networks are missing, but we do not think it is necessary to evaluate uncertainty (we believe that examining the posterior distributions directly is a better approach there).
-We have rephrased these lines (XX-XX) to emphasise that the filtered networks are intended to demonstrate the consequences of uncertainty more than anything else.
+Due to length restrictions, we have moved this anslysis to an appendix (\emph{Appendix S10}) and haverephrased these lines to emphasise that the filtered networks are intended to demonstrate the consequences of uncertainty more than anything else.
 
@@
 
-	11. Scepticism about sampling requirements to be sure interactions do not occur [[done]]
+	11. Scepticism about sampling requirements to be sure interactions do not occur
 
@@
 This statement is based on this study – are all systems like the gall system?
-If species are specialised or bound to interact for some other reason (i.e., co-occurring when there are few other resources) wouldn’t you need to observe fewer individuals?
-The point of the method is that you can estimate how many individuals are needed….
+If species are specialised or bound to interact for some other reason (i.e., co-occurring when there are few other resources) wouldn't you need to observe fewer individuals?
+The point of the method is that you can estimate how many individuals are needed....
 This is great!
 But given that this can be estimated from any given system why give a value from one system and state that is what is required?
-It defeats the point of the very nice method proposed…??
+It defeats the point of the very nice method proposed...??
 		\end{refquote}
@@
 
-		The Reviewer's suggestion that we might need fewer samples for species that are "specialised or bound to interact for some other reason" reflects a very strong prior.
+		The Reviewer's suggestion that we might need fewer samples for species that are ``specialised or bound to interact for some other reason'' reflects a very strong prior.
 In this case, yes we would need fewer samples for the species concerned.
@@
 For example, in most food webs it is assumed that basal resources will never consume prey even if a given resource and a given animal are never observed co-occurring and it is generally accepted that there is very low uncertainty about these zeros.
-In many cases, the assumptions involved in excluding interactions are less clear-cut and different researchers may disagree about which species are "bound to interact" (or not to interact).
+In many cases, the assumptions involved in excluding interactions are less clear-cut and different researchers may disagree about which species are ``bound to interact'' (or not to interact).
 The concept of pollination syndromes is one example - many flower visitors are less rigidly specialised on particular flower types than initially thought~\citep{Ollerton2009}.
-To address such "forbidden links", we now suggest that researchers explicitly state both the uncertainty about data-based zeros and the assumptions by which they create structural zeros.
+To address such ``forbidden links``, we now suggest that researchers explicitly state both the uncertainty about data-based zeros and the assumptions by which they create structural zeros.
 This will allow future researchers to evaluate the uncertainty about all interactions in a network as the state of expert knowledge changes.
@@
 
-		\begin{quotation}
-
-			Second, researchers should acknowledge the varying levels of confidence surrounding interactions between species pairs.
-In the absence of strong prior information a very high level of sampling (i.e., 30-50 observations in our example) is needed \emph{for each species pair}.
-This is not likely to be possible for most studies.
-including the $n$ and $k$ values for each interaction will clearly indicate which unobserved interactions are most likely to be observed with further sampling and which estimates are more reliable.
-Where there are strong prior expectations about pairs of species that will not interact, these should be explicitly stated so that readers know which zeros in an interaction matrix are based on observed data and which are based primarily upon expert knowledge.
-
-		\end{quotation}
+		Finally, we emphasize that the estimate of 30-50 samples does not refer to the \emph{Salix}-galler-natural enemy test system but to a much more general interpretation of the problem.
+Without a prior distribution and with \emph{no prior information}, as long as we assume that interaction probabilities follow a beta distribution it will take 30-50 observations of two species co-occurring to be 95-99\% confident that the species do not interact.
+Sampling requirements will be much less if an interaction was observed (note that in the empirical example we assume an interaction was feasible if it was observed even once).
 
@@
 
-	[[Still need to incorporate Tomas comments]]
-	[[Still need to spellcheck]]
-
-	The Reviewer has ``been surprised how little that sampling effects have been formally considered in the analysis of networks" and therefore feels that our manuscript makes an important contribution.
-Nevertheless, the Reviewer has concerns that the manuscript might not reach empirical ecologists ``because they either would not understand its relevance or would not be able to apply it practically".
+	The Reviewer has ``been surprised how little that sampling effects have been formally considered in the analysis of networks'' and therefore feels that our manuscript makes an important contribution.
+Nevertheless, the Reviewer has concerns that the manuscript might not reach empirical ecologists ``because they either would not understand its relevance or would not be able to apply it practically``.
 We agree with the Reviewer that this would be a great shame, and appreciate their suggestions to improve the manuscript.
@@
 Our goal is to increase access to a statistical technique which we see as complementary to high-quality field work, and we believe that the Reviewer's comments will help us to achieve this.
-
-	1. Paper is poorly structured [[done?]]
+We respond (preceded by \textbf{R:}) to each of the Reviewer's comments in detail below.
+
+	1. Paper is poorly structured
 
@@
 
-	2. Add more citations [[done]]
+	2. Add more citations
 
@@
 
-	3. Comment on weighted metrics [[done]]
+	3. Comment on weighted metrics
 
@@
 
-	4. Request for extension to weighted networks [[not done - do we want to do this?]]
+		Applying our framework to quantitative networks is beyond the scope of the current study due to length restrictions.
+It is, however, an interesting question worthy of future consideration.
+With quantitative interactions, the problem of true and false zeros disappears.
+However, there will now be a great deal of uncertainty about the observed interactions as we must now estimate variability in interaction frequencies.
+There is a significant trade-off here, and whether quantitative or qualitative networks are better-suited to acknowledging uncertainty in species interactions remains a very open question.
+
+	4. Request for extension to weighted networks
 
@@
 
-	5. Description of causes of uncertainty poorly integrated with the case study [[done]]
+	5. Description of causes of uncertainty poorly integrated with the case study
 
@@
 
-		To make this clearer, we have rephrased this section and added a line (lines XX-XX) stating that we usually cannot determine the cause of all the zeros in an interaction matrix (we can identify obviously unfeasible interactions, but likely cannot say whether a zero for a rare species is because we did not observe enough individuals, there were not enough individuals to perform a particular interaction, or because the interaction is actually unfeasible).
+		To make this clearer, we have rephrased this section and added a line (lines 61-68) stating that we usually cannot determine the cause of all the zeros in an interaction matrix (we can identify obviously unfeasible interactions, but likely cannot say whether a zero for a rare species is because we did not observe enough individuals, there were not enough individuals to perform a particular interaction, or because the interaction is actually unfeasible).
 We hope that this revision makes it clearer that the description of different sources of uncertainty is a conceptual guide only.
@@
 		\begin{quotation}
-			An observed link definitely occurred, but there are multiple reasons why a given link may not be observed \emph{whether or not the interaction truly occurred}.
-Moreover, given an unobserved interaction in an empirical dataset, we often cannot determine why the interaction did not occur \emph{post hoc}.
+			While an observed link definitely occurred (assuming correct identification of the species involved), a given link may not be observed for many reasons, \emph{whether or not it truly occurred} (Fig.~\ref{conceptual_fig}).
+Moreover, given an unobserved interaction in an empirical dataset, we often cannot determine why the interaction was not observed \emph{post hoc}.
 The detection of any interaction is a stochastic process subject to many levels of uncertainty.
-As a conceptual guide to the factors affecting this process, we describe three nested levels of uncertainty that roughly address the questions: "Could species $i$ and $j$ interact?", "Do they interact?" and "Do we observe the interaction?" (Fig.
-1).
-		\end{quotation}
-
-	6. Process uncertainty poorly defined. [[done]]
-
-		\begin{refquote}
-		L76ff ‘Process uncertainty’ is not defined.
-The simplistic example of interaction uncertainty (fish eating a cactus) does not help the reader understand the detail of what is meant by ‘interaction uncertainty’.
-The two examples of ‘local constraints’ (weather and habitat) are operating on completely different temporal scales (note – it is defined differently in L109).
+As a conceptual guide, we describe three nested levels of uncertainty that roughly address the questions: ``Could species $i$ and $j$ interact?", ``Did they interact during sampling?", and ``Did we observe the interaction?"
+		\end{quotation}
+
+		For the Reviewer's interest, some of the authors in the present manuscript investigated environmental variables and co-occurrence as potential sources of variance and found that most of the variability was driven by co-occurrence.
+This is analogous to the effect of abundance, but at a larger scale (where many abundances are locally 0).
+These analyses are described in [[Add ref!!!]]
+
+	6. Process uncertainty poorly defined.
+
+		\begin{refquote}
+		L76ff `Process uncertainty' is not defined.
+The simplistic example of interaction uncertainty (fish eating a cactus) does not help the reader understand the detail of what is meant by `interaction uncertainty'.
+The two examples of `local constraints' (weather and habitat) are operating on completely different temporal scales (note – it is defined differently in L109).
 I would regard the issue of weather as much closer to detection uncertainty (e.g.
-for a pollinator, it would be likely to be interacting if the weather was better), whereas the issue of habitat is closer to the authors’ ‘interaction uncertainty’ (the species don’t interact because they are not, or never, co-occurring in a habitat).
+for a pollinator, it would be likely to be interacting if the weather was better), whereas the issue of habitat is closer to the authors' `interaction uncertainty' (the species don't interact because they are not, or never, co-occurring in a habitat).
 Also if the species occur in different habitats then with an appropriate spatial scale of sampling then they do not co-occur – so the issue seems redundant.
 [[I suspect that the authors are thinking of a meta- or master network in much of their study, but this is not clear (or I have misunderstood and it needs to be explained better), i.e.
-the predicted presence of an interaction is not the presence of an interaction at the local site (taking detection and process uncertainty into account) but the ability to assess ‘interaction uncertainty’.]][[This is a bit separate from their issue]]
+the predicted presence of an interaction is not the presence of an interaction at the local site (taking detection and process uncertainty into account) but the ability to assess `interaction uncertainty'.]][[This is a bit separate from their issue]]
 		\end{refquote}
@@
 		\textbf{R:} As our manuscript is not concerned with partitioning sources of uncertainty, we felt it was unproductive to get bogged down in a debate over the precise definitions of process vs.
-interaction uncertainty and which external influences might contribute to which sources (there is enough overlap that simple statements such as "bad weather increases process uncertainty" are, at best, incomplete).
+interaction uncertainty and which external influences might contribute to which sources (there is enough overlap that simple statements such as ``bad weather increases process uncertainty'' are, at best, incomplete).
 To remove this problem, we have rephrased the introduction and discussion to refer to the questions of whether two species \emph{can} interact under ideal conditions and whether they \emph{do} interact at a given site and time.
@@
 The Reviewer is clearly correct that habitat also affects which species are present at a site.
-We include co-occurrence in process uncertainty since co-occurrence does not tell us much about whether an interaction is feasible under ideal conditions (which would certainly include co-occurrence).
+We included co-occurrence in process uncertainty since co-occurrence does not tell us much about whether an interaction is feasible under ideal conditions (which would certainly include co-occurrence).
 This speaks to our point above that external factors (habitat, weather, etc.) can affect multiple levels of uncertainty at once.
 In fact, habitat also likely affects detection uncertainty since it is often harder to observe interactions in dense vegetation.
-So, in short, separating sources of uncertainty based on the external factors which contribute to them is not a particularly useful endeavour.
+So, in short, separating sources of uncertainty based on the external factors which contribute to them is not a particularly useful endeavour and we have revised the manuscript to steer readers away from it.
 
@@
 Spatial variation in interaction probabilities will affect all interaction types, as does variation in abundances between years, so we cannot conceive of any interactions that are exempt from this issue.
-The timescale of an interaction (and the evidence it leaves) does affect detection uncertainty, so we have added a note in that section.
-Long-term interactions may fail to be detected, however, and we now add an example to make it clear that detection uncertainty applies to even long-term interactions such as gall-forming (indeed, our results suggest that uncertainty in gall-forming is quite high).
-
-			\begin{quotation}
-
-				Some types of interactions will have higher detection uncertainty than others (e.g., pollination or predation often take place very quickly while parasitism can last for months or years).
-Even long-term interactions, however, can be missed, especially if species are difficult to identify or if not all individuals of a species share the interaction.
-Parasites, for example, are often concentrated in only a few individuals~\citep{Lagrue2015}.
-If these infected individuals do not happen to be included in a sample, their interactions will be missed.
-
-			\end{quotation}
-
-	8. Confusion about goal of modelling [[done]]
+The timescale of an interaction (and the evidence it leaves) does affect detection uncertainty, so we have added a note in that section (lines 137-140).
+Long-term interactions may still fail to be detected, however, and we now add an example to make it clear that detection uncertainty applies to even long-term interactions such as gall-forming (indeed, our results suggest that uncertainty in gall-forming is quite high).
+
+		Perhaps more important is the effect of sampling interval.
+As sampling time increases toward infinity, interaction probabilities should converge to 0 or 1 with no uncertainty.
+As we discuss, however, sampling times are limited by resources, the trade-off between sampling a single site intensively versus many sites, etc.
+Any interaction could therefore occur outside of the sampling window and hence be missed.
+
+		Lines 137-140:
+
+		\begin{quotation}
+			The probability of detecting an interaction will also depend on the duration of the interaction and its evidence, the species involved, and the individuals sampled~\citep{Wells2013,Lagrue2015,Cirtwill2016,Weinstein2017}.
+		\end{quotation}
+
+	8. Confusion about goal of modelling
 
@@
 		I was struggling to really understand what the authors were really trying to model (partly because of the lack of a link between the theoretical and empirical parts of the paper).
-Are the authors trying to estimate L (the probability that an interaction is feasible or not – I would describe this as a ‘master’ or meta- network), or is it that they are trying to estimate X|L (the probability that the interaction locally occurs)?
+Are the authors trying to estimate L (the probability that an interaction is feasible or not – I would describe this as a `master' or meta- network), or is it that they are trying to estimate X|L (the probability that the interaction locally occurs)?
 I would be interested in both, but the second aspect seemed to be ignored in the gall-former example.
@@
 We do note, however, that one could also model X|L using the same framework if there were independent counts of co-occurrences and interactions within a single site.
+[[Add ref to the 2018 paper that does this]] does just this.
 We now state throughout the manuscript that we are interested in compiling the metaweb, the set of interaction which can feasibly occur.
-In particular, this is now specified in the introduction.
 We hope that our goal is now crystal clear.
 
-		\begin{quotation}
-			To supplement repeated sampling efforts and reduce uncertainty around unobserved interactions, we suggest researchers use prior knowledge of the same or similar systems.
-Here, we outline a Bayesian approach to combining repeated sampling and prior knowledge in order to assemble a metaweb.
-We then demonstrate this approach using an intensively and repeatedly sampled empirical dataset.
-Finally, we show how a probabilistic understanding of a metaweb allows us to establish confidence intervals around measures of network structure.
-			\end{quotation}
-
-	9. Misunderstanding of how biased sampling does not solve problems of uncertainty [[done]]
+	9. Misunderstanding of how biased sampling does not solve problems of uncertainty
 
@@
 Increasing sampling effort will not do much good if we repeatedly sample the same common interactions and very rarely identify any new interactions.
-We now address questions about whether or not sampling more will remove uncertainty in a dedicated section (\textbf{Why can't we just sample more?}).
+We now address questions about whether or not sampling more will remove uncertainty in a dedicated appendix (\emph{Appendix S2}).
 We still mention the fact that increased sampling will not reduce uncertainty evenly across interactions as this is an important point to consider when designing sampling protocols and when analysing empirical data.
@@
 
-	10. Explain Bayesian approach more simply [[done]]
+	10. Explain Bayesian approach more simply
 
@@
 
-	11. Integrate L155ff with previous section [[done]]
+	11. Integrate L155ff with previous section
 
@@
 
-	12. Ideas presented in L209, L262, L310 are important but explained too briefly [[done]]
+	12. Ideas presented in L209, L262, L310 are important but explained too briefly
 
@@
 We have expanded our discussion of different types of priors and how they may be obtained, and we hope that this clarifies matters for the Reviewer.
-We also note that a simple worked example, with accompanying R code, is provided in \emph{Appendix S3} so that readers can see exactly how to obtain $\alpha$ and $\beta$.
-In case the point of confusion is the idea that $\alpha$ and $\beta$ can be specified or derived depending on the type of prior desired, we have added a line (lines XX-XX) spelling this out.
-
-		\begin{quotation}
-			Parameters $\alpha$ and $\beta$ determine the shape of the prior distribution of $\lambda$, which follows a beta distribution.
-These are called hyper parameters and may be chosen to obtain an intentionally uninformative prior or derived using prior information to create an informed or empirical prior.
-			\end{quotation}
-
-	13. Reframe line 241 in terms of solutions rather than difficulties [[done]]
-
-		\begin{refquote}
-		L241 I wonder if you could phrase this more positively as ‘solutions’ rather than just ‘difficulties’?
+We also note that a simple worked example, with accompanying R code, is provided in \emph{Appendix S4} so that readers can see exactly how to obtain $\alpha$ and $\beta$.
+In case the point of confusion is the idea that $\alpha$ and $\beta$ can be specified or derived depending on the type of prior desired, we have added a line (lines 181-185) spelling this out.
+
+		\begin{quotation}
+			The shape parameters, or hyperparameters, may be set to particular values or derived from some data (see below).
+They may be set to the same values for all interactions, allowed to vary independently for all interactions, or incorporate non-independence between interactions (e.g., when the shape of the prior distribution depends upon species' abundances or traits).
+			\end{quotation}
+
+	13. Reframe line 241 in terms of solutions rather than difficulties
+
+		\begin{refquote}
+		L241 I wonder if you could phrase this more positively as `solutions' rather than just `difficulties'?
 		\end{refquote}
@@
 A lower-quality dataset would work just as well with our framework but would not highlight these difficulties so well.
-We have therefore kept this line as-is but have added another line (XX-XX) to show how the Bayesian framework provides a partial solution to the problems inherent in even high-quality empirical data.
-
-		\begin{quotation}
-		 The high spatiotemporal resolution of this dataset make it ideal for illustrating the difficulties in completely sampling a network; even with such an unusually high sampling effort, we anticipate that there will be many pairs of species which were rarely or never observed together.
+We have therefore kept this line as-is but have expanded the paragraph (301-307) to show how the Bayesian framework provides a partial solution to the problems inherent in even high-quality empirical data.
+
+		\begin{quotation}
+		 The high spatiotemporal resolution of this dataset makes it ideal for illustrating the difficulties in completely sampling a network; even with such an unusually high sampling effort, there were many pairs of species which were rarely or never observed together and about which we therefore have high uncertainty about interaction probabilities (Fig.
+2).
 Using the Bayesian framework above, we can identify which potential interactions are more and less uncertain, allowing us to better predict the true structure of the metaweb.
@@
 
-	14. Line 283 seems to be a very important point and should be explained more clearly [[done]]
+	14. Line 283 seems to be a very important point and should be explained more clearly
 
@@
 		L291 I have wondered about this – does assuming a probability of 1 for observed interactions create a bias?
-The observed interactions are a stochastic set of the possible interactions, so by treating observed interactions as 1 and other (equally likely?) unobserved interactions as <1 will surely bias the network metrics.
-I’m not sure of the solution and would welcome thoughts on this in the paper.
+The observed interactions are a stochastic set of the possible interactions, so by treating observed interactions as 1 and other (equally likely?) unobserved interactions as \textless1 will surely bias the network metrics.
+I'm not sure of the solution and would welcome thoughts on this in the paper.
 		\end{refquote}
@@
 		\textbf{R:} As we are concerned with the metaweb (the set of feasible interactions) rather than the interactions which occur at a given site on a given day, we do not think that assuming a probability of 1 for observed interactions introduces bias in our study.
-We have added a justification of setting the probability of observed interactions to 1 in \emph{Appendix S2}.
+We have added a justification of setting the probability of observed interactions to 1 in \emph{Appendix S3}.
 Note that each posterior web is a prediction of the true metaweb and not a local realisation of some interactions drawn from the feasible set.
-These local webs are more akin to our "filtered webs" in which observed interactions are not guaranteed to appear.
-We have also added a line (lines XX-XX) to make this clear.
-
-		This is an interesting point, however, as systems with a large risk of false positives (e.g., pollination networks which assume all flower visitors provide pollination service) would be biased by assuming all observed interactions are truly feasible.
+These local webs are more akin to our ``filtered webs'' in which observed interactions are not guaranteed to appear.
+
+		One interesting point is whether systems with a large risk of false positives (e.g., pollination networks which assume all flower visitors provide pollination service) would be biased by assuming all observed interactions are truly feasible.
 Assuming that all interactions which are known to be feasible actually occur at each site would also introduce bias - I suspect that this is what the Reviewer may be thinking of.
@@
 
-		\begin{quotation}
-			we created a suite of 100 webs by randomly sampling from each posterior distribution. Each of these webs is a prediction of the structure of the metaweb.
-		\end{quotation}
-
-	16. Filtering seems arbitrary [[done]]
+		We suspect, however, that the Reviewer may be thinking of weighted networks where interaction frequencies of feasible (occurring somewhere in the metaweb) interactions vary.
+In this case, the probability of an interaction will almost never be 1 as an interaction which occurred 10 times in 10 observed co-occurrences might not occur at an 11th observation.
+As discussed above, this is an interesting avenue for future extensions but beyond the scope of the present manuscript.
+
+	16. Filtering seems arbitrary
 
@@
 
-		\textbf{R:} We have rephrased lines XX-XX to make it clearer that the filtered networks are intended to demonstrate how network structure changes as uncertainty increases (and we miss more interactions).
+		\textbf{R:} We have rephrased our description (in \emph{Appendix S10}) to make it clearer that the filtered networks are intended to demonstrate how network structure changes as uncertainty increases (and we miss more interactions).
 As stated, we filtered networks created using the posterior distributions.
 There are therefore no sites or samples in question here.
-We are simply retaining a random 90\%-10\% of the interactions (or removing a random 10\%-90\%; these are equivalent) of the interactions in the "true" (posterior) network.
+We are simply retaining a random 90\%-10\% of the interactions (or removing a random 10\%-90\%; these are equivalent) of the interactions in the ``true'' (posterior) network.
 We hope that this rephrasing is clearer.
@@
 To demonstrate this, we created a suite of filtered networks for each posterior network.
-Taking a posterior network as the "true" network, we randomly sampled 90\%, 80\%, 70\%, 60\%, 50\%, 40\%, 30\%, 20\%, and 10\% of the interactions to create a new "filtered" network.
+Taking a posterior network as the ``true'' network, we randomly sampled 90\%, 80\%, 70\%, 60\%, 50\%, 40\%, 30\%, 20\%, and 10\% of the interactions to create a new ``filtered'' network.
 			\end{quotation}
@@
 		Note that our model is not concerned with partitioning different sources of variation; the filtering levels we present therefore represent uncertainty from all sources.
-As such, comparing them directly to "typical sampling effort" would be an apples-to-oranges comparison.
-We do note that~\citet{Weinstein2017a} found a detectability of 23.3\% for interactions despite high sampling effort,~\citet{Jordano2016} found that about half of unobserved interactions did not qualify as "forbidden links", and~\citet{Bartomeus2013} found that 59\% of interactions were detected.
+As such, comparing them directly to ``typical sampling effort'' would be an apples-to-oranges comparison.
+We do note that~\citet{Weinstein2017a} found a detectability of 23.3\% for interactions despite high sampling effort,~\citet{Jordano2016} found that about half of unobserved interactions did not qualify as ``forbidden links``, and~\citet{Bartomeus2013} found that 59\% of interactions were detected.
 We therefore do not think that the range of filtering levels we applied were particularly unreasonable (although we note that none of the above studies refer to plant-galler networks).
@@
 
-	17. Expand discussion of results on line 321 [[no space - had to remove network metrics.]]
+	17. Expand discussion of results on line 321
 
@@
 
-		\textbf{R:} Ultimately, length restrictions meant that we were obliged to remove our discussion of network metrics to an appendix.
+		\textbf{R:} Ultimately, length restrictions meant that we were obliged to remove our discussion of network metrics to an appendix (\emph{Appendix S10}).
 After adding the additional material requested by Reviewers in the methods, there simply was not space to discuss the network-level metrics in the main manuscript.

### 2019-01-16 manuscript/CI_interactions.tex
added Dom comments to reply

@@
 % \item Abstract word count: 290
-% \item Main text word count: 6871 % Limit is 6000-7000 including figs, tables, references. 
+% \item Main text word count: 6973 % Limit is 6000-7000 including figs, tables, references. Would be good to include Dom2018 if I can trim a bit more.
 % \end{itemize}
@@
 This uncertainty can, however, be constrained with informative priors.
-This uncertainty scaled up to summary measures of network structure such as connectance or nestedness.
-By using a comprehensively sampled network as a test case, we find that even with informative priors we are likely to miss many interactions that may occur rarely or under different local conditions.
-    \item Overall, we demonstrate the utility of our approach, given the importance of acknowledging the uncertainty inherent in network studies, and the utility of treating interactions as probabilities in pinpointing areas where more study is needed.
+This uncertainty scaled up to summary measures of network structure such as connectance and nestedness.
+Even with informative priors, we are likely to miss many interactions that may occur rarely or under different local conditions.
+    \item Overall, we demonstrate the importance of acknowledging the uncertainty inherent in network studies, and the utility of treating interactions as probabilities in pinpointing areas where more study is needed.
 Most importantly, we stress that networks are best thought of as systems constructed from random variables, the stochastic nature of which must be acknowledged for an accurate representation.
@@
 
-\linenumbers
+% \linenumbers
 \clearpage
@@
 
-    Representing an ecological community as a network allows ecologists to address both community composition and the interactions between species~\citep{Roslin2016}.
-Identifying these interactions is critical to understanding species' effects on each other and predicting the community's response to perturbations~\citep{Bartomeus2016,Giron2018}.
-Importantly, information is conveyed both by the presence and \emph{absence} of links between species.
+    Representing an ecological community as a network addresses both community composition and interspecific interactions~\citep{Roslin2016}.
+Identifying these interactions is critical to understanding species' effects on each other and predicting community responses to perturbations~\citep{Bartomeus2016,Giron2018}.
+Importantly, information is conveyed both by the presence and \emph{absence} of interactions.
 Presences and absences are not, however, equally certain.
@@
 Species must co-occur in order to be observed interacting, so any variation in co-occurrence will create variation in the set of observed interactions~\citep{Gravel2013,Graham2018}.
-Even assuming constant co-occurrence within a given study system, changing abundances can affect interactions if species which would otherwise interact become too rare to detect each other~\citep{Tylianakis2010,Jordano2016}.
-Moreover, interactions vary over space~\citep{Kitching1987,Baiser2012}, time~\citep{Kitching1987,Olesen2011a,Lopez2017}, between individuals~\citep{Pires2011a,Wells2013,Fodrie2015,Novak2015}, throughout life cycles~\citep{Clegg2018}, and with environmental conditions~\citep{Poisot2015}.
+Even assuming constant co-occurrence within a system, changing abundances can affect interactions if species which would otherwise interact become too rare to detect each other~\citep{Tylianakis2010,Jordano2016}.
+Moreover, interactions vary over space~\citep{Kitching1987,Baiser2012}, time~\citep{Olesen2011a,Lopez2017}, between individuals~\citep{Pires2011a,Wells2013,Fodrie2015,Novak2015}, throughout life cycles~\citep{Clegg2018}, and with environmental conditions~\citep{Poisot2015}.
 
-    Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Jordano2016}).
-An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to correctly document interactions than species~\citep{Guimera2009,Poisot2012,Bartomeus2013,Jordano2016,Giron2018,Graham2018}.
+    Beyond ``true" variation in network structure, several researchers note effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Jordano2016}).
+Assessments of the accumulation of interactions with increasing sampling effort suggest that it is more challenging to correctly document interactions than species~\citep{Guimera2009,Poisot2012,Bartomeus2013,Jordano2016,Giron2018,Graham2018}.
 As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Bartomeus2013,Poisot2016}.
-Efforts in this vein usually take the form of creating model food webs that approximate observed empirical networks~\citep{Allesina2008,Guimera2009,Williams2010,Rohr2016}.
+Such efforts usually take the form of creating model networks that approximate observed empirical networks~\citep{Allesina2008,Guimera2009,Williams2010,Rohr2016}.
 These models may be based on species traits and/or abundances~\citep{Rohr2016,Weinstein2017,Weinstein2017a,Graham2018} or on simple abstract rules~\citep{Allesina2008,Guimera2009,Williams2010}.
-Such models provide an important ''reality check'' by allowing us to test hypotheses about the factors structuring ecological networks~\citep{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}.
-They can also allow us to estimate the numbers of interactions which have not been observed~\citep{Jordano2016,Weinstein2017a} and predict which unobserved interactions are most likely~\citep{Guimera2009,Bartomeus2013}.
+Model networks provide an important ''reality check'' by allowing hypothesis testing about factors structuring ecological networks~\citep{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}.
+They can also allow estimation of the numbers unobserved of interactions~\citep{Jordano2016,Weinstein2017a} and predict which unobserved interactions are most likely~\citep{Guimera2009,Bartomeus2013}.
 
     To date, models incorporating uncertainty have either been very general (e.g.,~\citet{Guimera2009,Gravel2013}) or very system-specific (e.g.,~\citet{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}); in either case such a model may be a poor fit for a particular study system.
-Moreover, some of the system-specific models described above cannot accommodate species observed only once~\citep{Bartomeus2013,Weinstein2017}.
-As rare species are likely to be observed less frequently~\citep{Bluthgen2006} and may be of particular interest (e.g., when modelling species loss), there is a need for a more widely-applicable framework that includes such rare species.
+Moreover, some of the models described above cannot accommodate species observed only once~\citep{Bartomeus2013,Weinstein2017}.
+As rare species are likely to be observed less frequently~\citep{Bluthgen2006} and may be of particular interest (e.g., when modelling species loss), there is a need for a more widely-applicable framework that includes rarely-observed species.
 
-    Here we introduce a simple Bayesian framework that can easily be adapted to different systems.
-First, we provide a brief description of the nested levels of uncertainty affecting ecological network construction.
-In the context of this uncertainty, which can be reduced but not eliminated by high-quality sampling~\citep{Bartomeus2013}), we present a Bayesian framework for combining observed data with a prior expectation of network structure.
-This prior expectation can be uninformative, or it may include prior knowledge about the study system.
+    Here we introduce a simple, adaptable Bayesian framework.
+First, we briefly describe the nested levels of uncertainty affecting ecological network construction.
+In the context of this uncertainty, which can be reduced but not eliminated by high-quality sampling~\citep{Bartomeus2013}), we present a Bayesian framework which combines observed data with a prior expectation of network structure.
 We conclude with a worked example applying this framework to an intensively-sampled host-parasitoid network.
-We find that even the highest-quality empirical network we could find had substantial uncertainty about whether many pairs of species interact, demonstrating the need to include information about this uncertainty in published networks.
+We find that even the highest-quality empirical network data we could find had substantial uncertainty about whether many pairs of species interact, demonstrating the need to include information about this uncertainty in published networks.
     % We also show that this interaction-level uncertainty leads to uncertainty about estimates of network structure, with important implications for comparisons across networks; especially those compiled with different sampling intensity~\citep{Weinstein2017}.
@@
 
-    \subsection*{Why do some interactions \emph{not} occur?}
+    \subsection*{Why are some interactions not observed?}
 
-      We start from the perspective of a community ecologist wishing to describe an interaction network.
+      We start from the perspective of a community ecologist describing an interaction network.
 This ecologist will be interested in describing the species/nodes present and the links between them~\citep{Roslin2016}.
-While an observed link definitely occurred (assuming correct identification of the species involved), a given link may not be observed for many reasons, \emph{whether or not the interaction truly occurred} (Fig.~\ref{conceptual_fig}).
-Moreover, given an unobserved interaction in an empirical dataset, we often cannot determine why the interaction did not occur \emph{post hoc}.
+While an observed link definitely occurred (assuming correct identification of the species involved), a given link may not be observed for many reasons, \emph{whether or not it truly occurred} (Fig.~\ref{conceptual_fig}).
+Moreover, given an unobserved interaction in an empirical dataset, we often cannot determine why the interaction was not observed \emph{post hoc}.
 The detection of any interaction is a stochastic process subject to many levels of uncertainty.
@@
           Fundamentally, some interactions are feasible while others are not~\citep{Poisot2015}.
-Assuming that the feasibility of interactions depends on the traits of species involved, we can define the probability of an interaction $L_{ij}$ between species $i$ and $j$, given some function describing trait-matching between species $i$ and $j$ $\mathbf{T_{ij}}$, as $P(L_{ij}|\mathbf{T_{ij}})=\lambda_{ij}$~\citep{Bartomeus2013,Gravel2013,Weinstein2017}.
+An unobserved interaction may have $\lambda_{ij}>0$, and the associated zero in an interaction matrix might be false.
+This uncertainty is partly addressed by trait-matching models~\citep{Bartomeus2016,Jordano2016,Weinstein2017}.
+Assuming that the feasibility of interactions depends on the traits of species involved, we can define the probability of an interaction $L_{ij}$ between species $i$ and $j$, given some function describing trait matching $\mathbf{T_{ij}}$, as $P(L_{ij}|\mathbf{T_{ij}})=\lambda_{ij}$~\citep{Bartomeus2013,Gravel2013,Weinstein2017}.
 In some cases the traits prohibiting an interaction are known and there will be little uncertainty about $\lambda_{ij}$.
-          In most cases, however, it is not known what traits might prohibit an interaction~\citep{Dormann2017} and uncertainty about $\lambda_{ij}$ will be high. 
+Generally, however, the traits that might prohibit an interaction are unknown~\citep{Dormann2017} and uncertainty about $\lambda_{ij}$ will be high.
           %Pollinators may visit plants outside of those predicted based on "pollination syndromes"~\citep{Weinstein2017a} and herbivores may consume animal prey when it becomes accessible~\citep{Furness1988,Pietz2000}.
 These examples illustrate the danger in assuming that seemingly unlikely interactions cannot occur.
-
-          An unobserved interaction may be a rare phenomenon with $\lambda>0$ and the associated zero in an interaction matrix might be false.
-This uncertainty is partly addressed by trait-matching models~\citep{Bartomeus2016,Jordano2016,Weinstein2017}.
-As these models improve and include better information about the influence of traits on interactions, uncertainty will be reduced~\citep{Jordano2016} and $\lambda_{ij}$ should either tend to 0 or to 1.
-Nevertheless, every model is imperfect and lacks information that could be used to define constraints on at least some interactions~\citep{Dormann2017}, leaving some uncertainty about whether some species pairs could interact.
+          As trait-matching models improve, uncertainty will be reduced~\citep{Jordano2016} and $\lambda_{ij}$ should either tend to 0 or to 1.
+Nevertheless, every model is imperfect and lacks information that could be used to define constraints on at least some interactions~\citep{Dormann2017}.
+This leaves some uncertainty about whether some species pairs could interact.
 
@@
 
-          Assuming that an interaction is feasible (i.e., $L_{ij}=1$;), an interaction may still not occur at a particular place or time~\citep{Poisot2015,Graham2018}.
+          Assuming that an interaction is feasible (i.e., $L_{ij}=1$;), it may still not occur at a particular place and time~\citep{Poisot2015,Graham2018}.
 This could be because constraints such as inclement weather or low abundance prevented the interaction~\citep{Jordano2016,Graham2018}, a preferred interaction partner was available~\citep{Weinstein2017a}, or individual variation in traits meant that local individuals could not interact even if the species in general can~\citep{Gravel2013,Wells2013,Poisot2015}.
 For example, a rare galler may not parasitize a rare plant because they do not encounter each other.
-In metawebs describing a community found at several sites, an interaction may also fail to occur because two species do not co-occur at a particular site even if they do co-occur and interact elsewhere~\citep{Graham2018}.
+In metawebs, an interaction may also not occur because two species do not co-occur at a particular site even if they do co-occur and interact elsewhere~\citep{Graham2018}.
 We can define the local realisation of an interaction, $X_{ij}$, given that the interaction is feasible, as a stochastic process with associated probability $P(X_{ij}|L_{ij}=1)=\chi_{ij}$.
 It is unlikely that $\chi_{ij}=1$  except in the case of obligate specialists who always interact whenever they co-occur and always co-occur.
-When $\chi_{ij}<1$ we cannot be sure whether an unobserved interaction cannot occur or whether it simply did not occur at a particular site.
+When $\chi_{ij}<1$, we cannot be sure whether an unobserved interaction cannot occur or whether it simply did not occur at a particular site.
 
@@
 Phenological matching~\citep{MillerRushing2010}, species preferences~\citep{Pires2011a,Novak2015}, and fear effects~\citep{Luttbeg2005} all affect the probability of an interaction and could be included in models similar to trait-matching models.
-Alternatively, interaction probabilities could be tested in mesocosm studies with constant conditions.
 Some studies attempt to reduce uncertainty by sampling intensively over a short period of time and restricting the scale of interest to interactions occurring at the sampling site and time (conflating $\chi_{ij}$ and $\lambda_{ij}$)~\citep{Bartomeus2013,Weinstein2017,Weinstein2017a}.
@@
 
-            Both whether species can interact and whether they do interact at a particular place and time have been discussed in the context of ``forbidden links"~\citep{Jordano2016}.
+            Both whether species can ever interact and whether they interact at a particular place and time have been discussed in the context of ``forbidden links"~\citep{Jordano2016}.
 In this framework, all links which are prevented by spatio-temporal uncoupling, physiological constraints, etc.
@@
 We conceptually distinguish between physiological constraints and spatio-temporal uncoupling to allow for cases in which a species is introduced to a new habitat, expands its range, or shifts phenology~\citep{Gravel2013}.
-In such cases, links which are forbidden due to physiological constraints remain forbidden but links previously forbidden due to spatio-temporal mismatch could potentially occur.
+In such cases, links which are impossible due to physiological constraints remain forbidden but links previously ``forbidden" by spatio-temporal mismatch could potentially occur.
 
@@
           Lastly, measurement errors are a pervasive source of uncertainty about ecological processes.
-Even if an interaction is feasible and occurs during sampling ($L_{ij}=1$, $X_{ij}=1$), it may still go undetected~\citep{Jordano2016,Weinstein2017}.
+Even an interaction which is feasible and occurs during sampling ($L_{ij}=1$, $X_{ij}=1$), may still go undetected~\citep{Jordano2016,Weinstein2017}.
 We can define the probability of detecting of an interaction, $D_{ij}$, given the interaction is feasible and occurs, as a stochastic process with  probability $P(D_{ij}|X_{ij}=1,L_{ij}=1)=\delta_{ij}$.
 Detection failure could happen for many reasons (see~\citet{Wirta2014}).
-Some sources of detection error can be minimised with appropriate sampling (e.g., combining plant-focused and animal-focused sampling when assembling pollination networks~\citet{Jordano2016}), but other sources are difficult to reduce.
-For example, cryptic species might require molecular analysis for appropriate taxonomic identification~\citep{Wirta2014,Frost2016} or it may not be possible to sample some species due to conservation concerns~\citep{Lagrue2015}.
+Some sources of detection error can be minimised with appropriate sampling (e.g., combining multiple sampling methods~\citet{Wirta2014,Frost2016,Jordano2016}), but other sources are difficult to reduce.
+For example, it may not be possible to sample some species due to conservation concerns~\citep{Lagrue2015}.
 The probability of detecting an interaction will also depend on the duration of the interaction and its evidence, the species involved, and the individuals sampled~\citep{Wells2013,Lagrue2015,Cirtwill2016,Weinstein2017}.
+With improved sampling, $D_{ij}$ should tend towards 1 but, importantly $D_{ij}$ will vary between interactions and it is likely that $D_{ij}<1$ within a sample.
+For example, when detecting interactions based on gut contents interactions with slowly-digested prey with hard parts will be more detectable than interactions with quickly-digested, soft prey.
 
@@
 
-    To sum up, the absence of an interaction on a given day could be because it was not feasible [$P(L_{ij})=0$], was feasible but did not occur because of local conditions during sampling ($P(X_{ij}|L_{ij}=1)=0$], or was feasible and occurred during sampling but could not be observed [$P(D_{ij}|X_{ij}=1,L_{ij}=1)=0$].
+    To sum up, the absence of an interaction could be because it was not feasible [$P(L_{ij})=0$], was feasible but did not occur during sampling ($P(X_{ij}|L_{ij}=1)=0$], or was feasible and occurred during sampling but could not be observed [$P(D_{ij}|X_{ij}=1,L_{ij}=1)=0$].
 Note that some external factors can affect more than one level of uncertainty.
@@
     When considering a metaweb, we wish to separate the unobserved interactions where $L_{ij}=0$ (i.e., unfeasible interactions) from interactions which could occur but did not at a particular sampling site or which occurred but were not detected (Fig.~\ref{conceptual_fig}).
-Unfortunately, this is not possible for most interactions (except those where we know an interaction is truly not feasible).
+Unfortunately, this is impossible for most interactions (unless we know an interaction is truly not feasible).
 That is, we generally do not know \emph{why} an interaction was not observed, only that it was not.
@@
     The obvious rule of thumb to reduce uncertainty is ``sample more".
-Where resources permit, increasing sample sizes will reduce uncertainty about the upper bound of the interaction probability and will also increase the probability of detecting unlikely or cryptic interactions (e.g., interactions where $L_{ij}=1$ but process or detection uncertainty is high).
-High-quality sampling is undoubtedly a crucial part of constructing an empirical network, but there are limits to the utility of increased sampling (see \emph{Appendix S2}).
-To compliment high-quality sampling, we can reduce uncertainty by combining the observed data available with prior knowledge about the system.
+Where resources permit, increasing sample sizes will reduce uncertainty about the upper bound of the interaction probability and will also increase the probability of detecting unlikely or cryptic interactions (e.g., interactions where $L_{ij}=1$ but $\chi_{ij}$ or $\delta_{ij}$ is low).
+In some systems, targetted sampling of particular species pairs could reduce especially high uncertainties about $\lambda_{ij}$, but this will not be possible everywhere (e.g., in host-parasitoid systems).
+High-quality sampling a crucial part of constructing an empirical network, but there are limits to the utility of increased sampling (see \emph{Appendix S2, Fig.
+S2}).
+To compliment high-quality sampling, we can reduce uncertainty by combining observed data with prior knowledge about the system.
 This is straightforward to do using a Bayesian approach, as detailed below.
@@
     The shape parameters, or hyperparameters, may be set to particular values or derived from some data (see below).
-Note that the hyperparameters may be set to the same values for all interactions, allowed to vary independently for all interactions, or may incorporate non-independence between interactions (e.g., when the shape of the prior distribution depends upon species' abundances or traits).
+They may be set to the same values for all interactions, allowed to vary independently for all interactions, or incorporate non-independence between interactions (e.g., when the shape of the prior distribution depends upon species' abundances or traits).
+For example, a prior could account for the tendency for abundant species to interact more frequently with all possible partners than rare species.
+
     Combining the prior distribution with the MLE of $\lambda_{ij}$ derived from observed data, we obtain a posterior distribution that also follows a beta distribution with new hyperparameters $\alpha_{ij}'=\alpha_{ij}+k$ and $\beta_{ij}'=\beta_{ij}+n-k$ (\emph{Appendix S3}).
-The influence of the prior on the posterior distribution can be understood from these definitions: the difference between the posterior and the prior will increase with $k_{ij}$ and $n_{ij}-k_{ij}$.
+These definitions illustrate the influence of the prior on the posterior distribution: the difference between the posterior and the prior will increase with $k_{ij}$ and $n_{ij}-k_{ij}$.
 In other words, the distribution of $\lambda_{ij}$ for better-sampled pairs of species will rely less on the information used to build the prior distribution and more on the observed data.
 As $n_{ij}$ increases, the total uncertainty about $\lambda_{ij}$ will decrease (Fig.~\ref{Salix_pdfs_cdfs}).
-Note that these Bayesian models of $\lambda_{ij}$ do not distinguish between different sources of uncertainty except through the choice of prior.
+Note that these models of $\lambda_{ij}$ do not distinguish between sources of uncertainty except through the choice of prior.
+For a model which attempts to separate sources of uncertainty, see~\citet{Weinstein2017}.
 
@@
 
-      The choice of prior distribution reflects a study's goal, the amount of prior knowledge available, and the strength of researchers' belief in that knowledge.
+      The choice of prior reflects a study's goal, the amount of prior knowledge available, and the strength of researchers' belief in that knowledge.
 Note that there is no 'correct' prior as long as the true distribution of interaction probabilities is unknown~\citep{Spiegelhalter2000}.
-The goal is to select a reasonable prior that reflects our assumptions about the true distribution, and then adjust this prior with observed data as it becomes available.
-When in doubt, it is also possible to model interaction probabilities using a variety of priors and then compare results~\citep{Spiegelhalter2000}.
-Some researchers may be reluctant to adopt a Bayesian approach because of its perceived subjectivity (i.e., a metaweb simulated using a Bayesian distribution will depend upon the assumptions inherent in the prior).
+The goal is to select a reasonable prior that reflects our assumptions about the true distribution and then adjust this prior with observed data as it becomes available.
+When in doubt, it is also possible to model interaction probabilities using a variety of priors and compare results~\citep{Spiegelhalter2000}.
+
+      Some researchers are reluctant to adopt a Bayesian approach because of its perceived subjectivity (i.e., a metaweb simulated using a Bayesian distribution will depend upon the assumptions inherent in the prior).
 We argue that one of the advantages of the Bayesian approach is that it makes this subjectivity explicit~\citep{Spiegelhalter2000}.
 Researchers compiling empirical networks face many decisions about where to set community boundaries, the set of species to include in the focal community~\citep{Jordano2016}, what type of sampling is most appropriate~\citep{Wirta2014}, etc.
-All of these choices will affect the compiled network and most do not have clear answers, making all empirical networks (and all theoretical networks, which likewise depend upon the assumptions used in building the network) somewhat subjective.
+These choices all affect the compiled network and most do not have clear answers, making all empirical networks (and all theoretical networks, which likewise depend upon the assumptions used in building the network) somewhat subjective.
 In addition, researchers distinguishing ``forbidden links" inherently rely on prior knowledge to identify these links~\citep{Jordano2016}.
@@
 as available~\citep{Jordano2016,Weinstein2017a,Graham2018}.
-Using an informative prior like these tailors the level of uncertainty surrounding each interaction, but involves many assumptions.
-There is, therefore, a risk of over-fitting with complicated trait-based models.
+Multiple sources of information can be combined into a single model (e.g., the the $K$ nearest neighbour (KNN) algorithm, which identifies likely interaction partners based on similarity to known partners~\citep{DesjardinsProulx2017}).
+This would result in a highly informative prior that would, moreover, account for some of the non-independence in interaction probabilities.
+
+        Using an informative prior like these tailors the level of uncertainty surrounding each interaction and may account for non-independence of interactions (as in abundance-based or KNN models).
+Despite these benefits, informative priors often involve many assumptions and carry a risk of over-fitting.
 Also note that researchers wishing to test whether a particular trait influences interaction probabilities should either exclude that trait from their prior or model the network using priors which include and exclude the trait of interest (as in~\citet{Weinstein2017,Weinstein2017a}).
@@
         Alternatively, once can develop a prior based on the properties of a set of published networks (i.e., ``empirical" or ``reference Bayes"~\citet{Spiegelhalter2000}).
-While this type of prior does not allow for the prior distribution to vary between species pairs, it relies on only one assumption: that the focal network will have similar structural properties to those of published networks.
+While this type of prior does not allow for the prior distribution to vary, it relies on only one assumption: that the focal network will have similar structural properties to those of published networks.
 For example, connectance ($C=N/S^2$, where $N$ is the number of interactions and $S$ is the number of species) is available for many networks.
@@
 The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (see \emph{Appendix S5} for details).
-      The high spatiotemporal resolution of this dataset make it ideal for illustrating the difficulties in completely sampling a network; even with such an unusually high sampling effort, there were many pairs of species which were rarely or never observed together and about which we therefore have high uncertainty about interaction probabilities (Fig.~\ref{histograms}).
+      The high spatiotemporal resolution of this dataset makes it ideal for illustrating the difficulties in completely sampling a network; even with such an unusually high sampling effort, there were many pairs of species which were rarely or never observed together and about which we therefore have high uncertainty about interaction probabilities (Fig.~\ref{histograms}).
 Using the Bayesian framework above, we can identify which potential interactions are more and less uncertain, allowing us to better predict the true structure of the metaweb.
@@
 This simulates an empirical Bayes model using a pilot site to inform the prior distribution.
-A site in the middle of the geographic distribution was chosen in order to minimise bias due to the potential for a northern or southern site to exclude species with restricted ranges.
-To demonstrate how the use of data from a different system can affect the prior distribution and conclusions based on it, we repeated our analyses using priors derived from a much smaller system, which provided unreasonable distributions for interaction probabilities (\emph{Appendix S7}).
+A site in the middle of the geographic distribution was chosen in order to minimise bias towards species at any geographic extreme.
+To demonstrate how a poor choice of prior can give unreasonable posterior distributions, we repeated our analyses using priors derived from a much smaller system (\emph{Appendix S7}).
 
-        To obtain priors based on a single sub-network --Zillis in Graub\"{u}nchen, Switzerland-- we estimated frequencies of interactions based on the normalised degree of each species in each network component (see \emph{Appendix S8} for details and code).
+        To obtain priors, we estimated interaction frequencies based on the normalised degree of each species (see \emph{Appendix S8} for details and code).
 Using these prior parameters, we then estimated the posterior distributions of interaction probabilities $\lambda_{ij}$.
@@
 First, sample sizes should be as large as possible.
-Second, researchers should acknowledge the varying levels of confidence surrounding interactions between species pairs.
+Second, researchers should acknowledge the varying levels of confidence surrounding interspecific interactions.
 Including the $n$ and $k$ values for each interaction will clearly indicate which unobserved interactions are most likely to be observed with further sampling and which estimates are more reliable, as well as indicating potential sampling biases.
@@
 
-  The authors thank Daniel Cartensen for fruitful discussion of the ideas in this manuscript and K\'{e}vin Cazalles for providing feedback.
-The authors appreciate support from the Swedish Research Council (VR) for grant \#2016-06872 (to TR) and from Formas for grant \#942-2015-1262 (to AE).
+  Thanks to Daniel Cartensen for fruitful discussion and K\'{e}vin Cazelles for providing feedback.
+The manuscript was supported by from the Swedish Research Council (VR; grant \#2016-06872 to TR) and Formas (grant \#942-2015-1262 to AE).
 

### 2019-01-16 manuscript/supplemental.tex
added Dom comments to reply

@@
 
-        When considering a metaweb, we wish to separate the unobserved interactions where $L_{ij} = 0$ (i.e., unfeasible interactions) from interactions which could occur but did not at a particular sampling site or which occurred but were not detected (Fig.~\ref{conceptual_fig}).
+        When considering a metaweb, we wish to separate the unobserved interactions where $L_{ij} = 0$ (i.e., unfeasible interactions) from interactions which could occur but did not at a particular sampling site or which occurred but were not detected (Fig.
+1, main text).
 Unfortunately, this is not possible for most interactions (except those where we know an interaction is truly not feasible).
@@
 Despite these benefits, we note that there are limits to the utility of increased sampling.
-Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig.~\ref{histograms}C).
+Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig.
+2C, main text).
 While this improves our understanding of the set of species present in the community, it introduces yet more uncertainty into the interaction matrix.
@@
 
-      We find, perhaps not surprisingly, that the posterior webs for the Salix-galler network all had much higher connectance than the original, observed web (C=0.028 for the observed web and 0.528 $\leq$ C $\leq$ 0.568 for the posterior webs; Fig.~\ref{posterior_webs}A).
-Likewise, the number of links per \emph{Salix} and galler species in the observed web ($L_{\emph{Salix}}$=2.71 and $L_{galler}$=1.47, respectively) were much lower than those predicted in the posterior webs (27.4 $\leq L_{\emph{Salix}} \leq$ 29.5 and 50.6 $\leq L_{galler} \leq $54.5, respectively; Fig.~\ref{posterior_webs}C,E), even when filtering with a detection probability of only 50\%.
-Nestedness was also much higher in the posterior networks (14.2 $\leq NODF \leq$ 15.4; Fig.~\ref{posterior_webs}G) than in the observed network (NODF=0.560).
+      We find, perhaps not surprisingly, that the posterior webs for the Salix-galler network all had much higher connectance than the original, observed web (C=0.028 for the observed web and 0.528 $\leq$ C $\leq$ 0.568 for the posterior webs; Fig.~\ref{posterior_webs_Barbour}A).
+Likewise, the number of links per \emph{Salix} and galler species in the observed web ($L_{\emph{Salix}}$=2.71 and $L_{galler}$=1.47, respectively) were much lower than those predicted in the posterior webs (27.4 $\leq L_{\emph{Salix}} \leq$ 29.5 and 50.6 $\leq L_{galler} \leq $54.5, respectively; Fig.~\ref{posterior_webs_Barbour}C,E), even when filtering with a detection probability of only 50\%.
+Nestedness was also much higher in the posterior networks (14.2 $\leq NODF \leq$ 15.4; Fig.~\ref{posterior_webs_Barbour}G) than in the observed network (NODF=0.560).
 There are two possible explanations for these discrepancies: either the data of~\citet{Barbour2016} is simply too different from that of~\citet{Kopelke2017} to offer an appropriate prior for our dataset, or the true detection probability for links between \emph{Salix} and galler species is much less than 50\%.
@@
       Considering the galler-natural enemy networks, the connectance, mean links per galler, and mean links per natural enemy were also much lower in the observed web (C=0.078, $L_{galler}$=9.99, and $L_{natural enemy}$=7.45, respectively) than in the posterior webs (0.183 $\leq$ C $\leq$ 0.196, 17.5 $\leq L_{galler} \leq$ 18.9, and 23.0 $\leq L_{natural enemy} \leq$ 24.8).
-When the detection probability was relatively low (i.e., 50\%), however, the properties of randomised networks became similar to those in the observed webs (Fig.~\ref{posterior_webs}B,D,F).
-Nestedness was higher in the observed network (NODF=6.85) than in the posterior networks (6.30 $\leq NODF \leq$ 6.74; Fig.~\ref{posterior_webs}H), but network structure was much more similar in the observed and posterior galler-natural enemy networks than in the \emph{Salix}-galler networks.
+When the detection probability was relatively low (i.e., 50\%), however, the properties of randomised networks became similar to those in the observed webs (Fig.~\ref{posterior_webs_Barbour}B,D,F).
+Nestedness was higher in the observed network (NODF=6.85) than in the posterior networks (6.30 $\leq NODF \leq$ 6.74; Fig.~\ref{posterior_webs_Barbour}H), but network structure was much more similar in the observed and posterior galler-natural enemy networks than in the \emph{Salix}-galler networks.
 The~\citet{Barbour2016} network likely provides a better prior here than for the \emph{Salix}-galler networks, as both networks included different galler and natural enemy species.
@@
 The value of each property decreases with the proportion of links included in the detection-filter networks.}
-      \label{posterior_webs}    
+      \label{posterior_webs_Barbour}    
       \begin{center}
-      \includegraphics[width=.65\textwidth]{Figures/Salix_Galler_posterior_properties.eps}
+      \includegraphics[width=.65\textwidth]{figures/Salix_Galler_posterior_properties.eps}
       \end{center}
@@
 Using these posterior networks, it is straightforward to obtain a plausible distribution for network properties of the predicted ``true'' community.
+This extends earlier work establishing probabilistic forms of network properties (e.g.,~\citet{Poisot2015}) by allowing us to calculate higher moments of network properties rather than only the mean.
 Note that these network properties may differ substantially from those of the observed network.
@@
     \end{figure}
-
-  \bibliographystyle{ecol_let} 
-  \bibliography{manual}
 
@@
 \bibliographystyle{ecol_let} 
-    \bibliography{manual_abbrev} % Abbreviate journal titles.
+\bibliography{manual}
 

### 2019-01-16 manuscript/reply_to_reviewers.tex
finished addressing Dom comments to reply

@@
 		\begin{quotation}
-			When considering a metaweb, we wish to separate the unobserved interactions where $L_{ij}=0$ (i.e., unfeasible interactions) from interactions which could occur but did not at a particular sampling site or which occurred but were not detected (Fig.~\ref{conceptual_fig}).
+			When considering a metaweb, we wish to separate the unobserved interactions where $L_{ij}=0$ (i.e., unfeasible interactions) from interactions which could occur but did not at a particular sampling site or which occurred but were not detected (Fig.
+1).
 Unfortunately, this is not possible for most interactions (except those where we know an interaction is truly not feasible).
@@
 
-		\textbf{R:} When revising the manusript we removed line 7 and no longer refer to networks as snapshots.
+		\textbf{R:} When revising the manuscript we removed line 7 and no longer refer to networks as snapshots.
 
@@
 The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (see \emph{Appendix S5} for details).
-		      The high spatiotemporal resolution of this dataset make it ideal for illustrating the difficulties in completely sampling a network; even with such an unusually high sampling effort, there were many pairs of species which were rarely or never observed together and about which we therefore have high uncertainty about interaction probabilities (Fig.~\ref{histograms}).
+		      The high spatiotemporal resolution of this dataset make it ideal for illustrating the difficulties in completely sampling a network; even with such an unusually high sampling effort, there were many pairs of species which were rarely or never observed together and about which we therefore have high uncertainty about interaction probabilities (Fig.
+2).
 Using the Bayesian framework above, we can identify which potential interactions are more and less uncertain, allowing us to better predict the true structure of the metaweb.
@@
 		\textbf{R:} Modelling the probability of co-occurrence is an option for many systems (e.g., aquatic food webs where ranges of fish species are fairly well-known, as in~\citet{Gravel2013}).
-It may also be possible to separate the probability of observing an interaction at a particular location into a metaweb component (the focus of the current manuscript) and a co-occurrence probability as in~\citep{Gravel2018}.
+It may also be possible to separate the probability of observing an interaction at a particular location into a metaweb component (the focus of the current manuscript) and a co-occurrence probability, as in~\citep{Gravel2018}.
 This addresses the question of interaction probabilities at specific locations, however, in contrast to our focus on metaweb interaction probabilities.
@@
 Instead, we now emphasise that co-occurrence probabilities are one thing that could be included in a prior (section beginning line 231).
-[[Add a ref to Gravel 2018?]]
 
@@
 Filtering networks in the way that we do could give an idea of how many networks are missing, but we do not think it is necessary to evaluate uncertainty (we believe that examining the posterior distributions directly is a better approach there).
-Due to length restrictions, we have moved this anslysis to an appendix (\emph{Appendix S10}) and haverephrased these lines to emphasise that the filtered networks are intended to demonstrate the consequences of uncertainty more than anything else.
+Due to length restrictions, we have moved this analysis to an appendix (\emph{Appendix S10}) and have rephrased these lines to emphasise that the filtered networks are intended to demonstrate the consequences of uncertainty more than anything else.
 
@@
 
-		Finally, we emphasize that the estimate of 30-50 samples does not refer to the \emph{Salix}-galler-natural enemy test system but to a much more general interpretation of the problem.
+		Finally, we emphasise that the estimate of 30-50 samples does not refer to the \emph{Salix}-galler-natural enemy test system but to a much more general interpretation of the problem.
 Without a prior distribution and with \emph{no prior information}, as long as we assume that interaction probabilities follow a beta distribution it will take 30-50 observations of two species co-occurring to be 95-99\% confident that the species do not interact.
@@
 This may be the case for Graham and Weinstein's relatively small and well-studied system but is not likely to be true for systems containing hundreds of species, systems containing recently-arrived species, systems just beginning to be studied, etc.
+A more generally-applicable approach is to test explicitly whether species always interact when co-occurring, whether interaction probability depends on the probability of co-occurrence, and whether both co-occurrence and interaction probabilities depend upon environmental conditions, as in~\citet{Gravel2018}.
+Note, however, that this study refers to the probability of an interaction occurring in a local realisation of a food web while we are concerned with metawebs in the present study.
 
@@
 		\begin{quotation}
-			While an observed link definitely occurred (assuming correct identification of the species involved), a given link may not be observed for many reasons, \emph{whether or not it truly occurred} (Fig.~\ref{conceptual_fig}).
+			While an observed link definitely occurred (assuming correct identification of the species involved), a given link may not be observed for many reasons, \emph{whether or not it truly occurred} (Fig.
+1).
 Moreover, given an unobserved interaction in an empirical dataset, we often cannot determine why the interaction was not observed \emph{post hoc}.
@@
 		\end{quotation}
-
-		For the Reviewer's interest, some of the authors in the present manuscript investigated environmental variables and co-occurrence as potential sources of variance and found that most of the variability was driven by co-occurrence.
-This is analogous to the effect of abundance, but at a larger scale (where many abundances are locally 0).
-These analyses are described in [[Add ref!!!]]
 
@@
 Also if the species occur in different habitats then with an appropriate spatial scale of sampling then they do not co-occur – so the issue seems redundant.
-[[I suspect that the authors are thinking of a meta- or master network in much of their study, but this is not clear (or I have misunderstood and it needs to be explained better), i.e.
-the predicted presence of an interaction is not the presence of an interaction at the local site (taking detection and process uncertainty into account) but the ability to assess `interaction uncertainty'.]][[This is a bit separate from their issue]]
+I suspect that the authors are thinking of a meta- or master network in much of their study, but this is not clear (or I have misunderstood and it needs to be explained better), i.e.
+the predicted presence of an interaction is not the presence of an interaction at the local site (taking detection and process uncertainty into account) but the ability to assess `interaction uncertainty'.
 		\end{refquote}
@@
 
-	7. Point about temporal scales of interaction [[done]]
+	7. Point about temporal scales of interaction
 
@@
 We do note, however, that one could also model X|L using the same framework if there were independent counts of co-occurrences and interactions within a single site.
-[[Add ref to the 2018 paper that does this]] does just this.
+\citet{Gravel2018} does just this.
 We now state throughout the manuscript that we are interested in compiling the metaweb, the set of interaction which can feasibly occur.
@@
 
-	15. Line 291: does assuming probability of 1 for observed interactions introduce bias? [[done]]
+	15. Line 291: does assuming probability of 1 for observed interactions introduce bias?
 

### 2019-01-16 manuscript/CI_interactions.tex
integrated Dom's first-half comments to main text, need to reduce word count again

@@
 Community composition and abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}, leading to variation in encounter probabilities and hence interactions~\citep{Vazquez2005,Poisot2015,Graham2018}.
-Species must co-occur in order to be observed interacting, so any variation in co-occurrence will create variation in the set of observed interactions~\citep{Gravel2013,Graham2018}.
+Species must co-occur in order to be observed interacting, so any variation in co-occurrence will create variation in the set of observed interactions~\citep{Gravel2018,Graham2018}.
 Even assuming constant co-occurrence within a system, changing abundances can affect interactions if species which would otherwise interact become too rare to detect each other~\citep{Tylianakis2010,Jordano2016}.
@@
 
-    To date, models incorporating uncertainty have either been very general (e.g.,~\citet{Guimera2009,Gravel2013}) or very system-specific (e.g.,~\citet{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}); in either case such a model may be a poor fit for a particular study system.
+    To date, models incorporating uncertainty have either been very general (e.g.,~\citet{Guimera2009,Gravel2018}) or very system-specific (e.g.,~\citet{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}); in either case such a model may be a poor fit for a particular study system.
 Moreover, some of the models described above cannot accommodate species observed only once~\citep{Bartomeus2013,Weinstein2017}.
@@
 First, we briefly describe the nested levels of uncertainty affecting ecological network construction.
-In the context of this uncertainty, which can be reduced but not eliminated by high-quality sampling~\citep{Bartomeus2013}), we present a Bayesian framework which combines observed data with a prior expectation of network structure.
+Understanding this nesting is an important step towards formalising our interpretation of the different drivers of uncertainty about interactions.
+Importantly, we distinguish between the possibility that an interaction is unfeasible (cannot occur) and the possibility that, given an interaction is feasible, it may not occur during a particular sampling event.
+
+    In the context of this uncertainty, which can be reduced but not eliminated by high-quality sampling~\citep{Bartomeus2013}), we present a Bayesian framework which combines observed data with a prior expectation of interaction probabilities.
 We conclude with a worked example applying this framework to an intensively-sampled host-parasitoid network.
-We find that even the highest-quality empirical network data we could find had substantial uncertainty about whether many pairs of species interact, demonstrating the need to include information about this uncertainty in published networks.
-    % We also show that this interaction-level uncertainty leads to uncertainty about estimates of network structure, with important implications for comparisons across networks; especially those compiled with different sampling intensity~\citep{Weinstein2017}.
+We find that even the highest-quality empirical network data we could find has substantial uncertainty about whether many pairs of species interact, demonstrating the need to include information about this uncertainty in published networks.
+    % We also show that this interaction-level uncertainty leads to uncertainty about estimates of network structure, with important implications for comparisons across networks; especially those compiled with different sampling intensity~\citep{Pelissier2017,Tylianakis2017,Weinstein2017}.
 
@@
 This uncertainty is partly addressed by trait-matching models~\citep{Bartomeus2016,Jordano2016,Weinstein2017}.
-Assuming that the feasibility of interactions depends on the traits of species involved, we can define the probability of an interaction $L_{ij}$ between species $i$ and $j$, given some function describing trait matching $\mathbf{T_{ij}}$, as $P(L_{ij}|\mathbf{T_{ij}})=\lambda_{ij}$~\citep{Bartomeus2013,Gravel2013,Weinstein2017}.
+Assuming that the feasibility of interactions depends on the traits of species involved, we can define the probability of an interaction $L_{ij}$ between species $i$ and $j$ given some function describing trait matching $\mathbf{T_{ij}}$ as $P(L_{ij}|\mathbf{T_{ij}})=\lambda_{ij}$~\citep{Bartomeus2013,Gravel2013,Weinstein2017}.
 In some cases the traits prohibiting an interaction are known and there will be little uncertainty about $\lambda_{ij}$.
 Generally, however, the traits that might prohibit an interaction are unknown~\citep{Dormann2017} and uncertainty about $\lambda_{ij}$ will be high.
-          %Pollinators may visit plants outside of those predicted based on "pollination syndromes"~\citep{Weinstein2017a} and herbivores may consume animal prey when it becomes accessible~\citep{Furness1988,Pietz2000}.
+          %Pollinators may visit plants outside of those predicted based on ``pollination syndromes"~\citep{Weinstein2017a} and herbivores may consume animal prey when it becomes accessible~\citep{Furness1988,Pietz2000}.
 These examples illustrate the danger in assuming that seemingly unlikely interactions cannot occur.
@@
 In this framework, all links which are prevented by spatio-temporal uncoupling, physiological constraints, etc.
-are considered "structural zeros" that cannot be observed~\citep{Jordano1987,Jordano2016}.
+are considered ``structural zeros" that cannot be observed~\citep{Jordano1987,Jordano2016}.
 We conceptually distinguish between physiological constraints and spatio-temporal uncoupling to allow for cases in which a species is introduced to a new habitat, expands its range, or shifts phenology~\citep{Gravel2013}.
 In such cases, links which are impossible due to physiological constraints remain forbidden but links previously ``forbidden" by spatio-temporal mismatch could potentially occur.
+When considering local realisations of a metaweb, it is possible to distinguish between interactions forbidden by traits and those forbidden by lack of co-occurrence~\citep{Gravel2018}.
+In the present study, we are concerned with identifying the metaweb-- the set of interactions which are feasible assuming species co-occur.
 
@@
 We can define the probability of detecting of an interaction, $D_{ij}$, given the interaction is feasible and occurs, as a stochastic process with  probability $P(D_{ij}|X_{ij}=1,L_{ij}=1)=\delta_{ij}$.
+Note that $D_{ij}$ is a stochastic variable taking the variable 1 if observed and 0 otherwise, while $P(D_{ij})$ is the probability that $D_{ij}=1$.
 Detection failure could happen for many reasons (see~\citet{Wirta2014}).
@@
     To sum up, the absence of an interaction could be because it was not feasible [$P(L_{ij})=0$], was feasible but did not occur during sampling ($P(X_{ij}|L_{ij}=1)=0$], or was feasible and occurred during sampling but could not be observed [$P(D_{ij}|X_{ij}=1,L_{ij}=1)=0$].
-Note that some external factors can affect more than one level of uncertainty.
-For example, rare species are less likely to interact at a given site due to neutral processes~\citep{Jordano2016,Graham2018}.
-Interactions involving rare species are also less likely to be detected, unless more sampling effort is focused on rare than common species~\citep{Bartomeus2013,Jordano2016}.
-Thus, abundance affects both the probability of an interaction occurring at a particular site \emph{and} our ability to observe the interaction.
+Researchers might be interested in whether an un-recorded interaction is feasible (i.e., reducing uncertainty about $\lambda_{ij}$) or whether or not a feasible interaction occurred locally (i.e., reducing uncertainty about $\chi_{ij}$).
+Here we consider the former, while noting that uncertainty about both $\chi_{ij}$ and $\delta_{ij}$ contribute to uncertainty about $\lambda_{ij}$.
+Future sampling should aim to characterise all three probabilities, but for now it is often difficult to distinguish between them.
+One reason for this is the ability of external factors such as abundance to affect multiple levels of uncertainty.
+Rare species are less likely to interact at a given site due to neutral processes~\citep{Jordano2016,Graham2018} and interactions involving rare species are less likely to be detected~\citep{Bartomeus2013,Jordano2016}.
+Thus, abundance affects both $P(X_{ij})$ and $P(D_{ij})$.
 
     When considering a metaweb, we wish to separate the unobserved interactions where $L_{ij}=0$ (i.e., unfeasible interactions) from interactions which could occur but did not at a particular sampling site or which occurred but were not detected (Fig.~\ref{conceptual_fig}).
-Unfortunately, this is impossible for most interactions (unless we know an interaction is truly not feasible).
-That is, we generally do not know \emph{why} an interaction was not observed, only that it was not.
-An empirical ecologist will instead measure the marginal probability $P(L_{ij})=k_{ij}/n_{ij}$, where $k_{ij}$ is the number of observed interactions between species $i$ and $j$ and $n_{ij}$ the number of observed co-occurrences.
+Unfortunately, unlike studies focused on local realisations of a network (e.g.,~\citet{Graham2018,Gravel2018}), in a metaweb we generally do not know \emph{why} an interaction was not observed.
+An empirical ecologist will measure the marginal probability $P(L_{ij})=k_{ij}/n_{ij}$, where $k_{ij}$ is the number of observed interactions between species $i$ and $j$ and $n_{ij}$ the number of observed co-occurrences.
 Given this information, the question becomes: how can we reduce the uncertainty around our estimated interaction probability?
@@
     The basis of a Bayesian approach to modelling the probability that an interaction between species $i$ and $j$ occurs ($\lambda_{ij}$) is combining the maximum likelihood estimate (MLE) of $\lambda_{ij}$ with a prior distribution (described in the next section) and a normalising function.
-The MLE of $\lambda_{ij}$ can be modelled as a Bernoulli trial based on the number of observed interactions $k_ij$ and observed co-occurrences $n_{ij}$: $\lambda_{ij}=\frac{k_{ij}}{n_{ij}}$.
+The MLE of $\lambda_{ij}$ can be computed from the number of observed interactions $k_ij$ and observed co-occurrences $n_{ij}$: $\lambda_{ij}=\frac{k_{ij}}{n_{ij}}$.
 The most appropriate prior distribution for $\lambda_{ij}$ is the beta distribution:
@@
 
-    Combining the prior distribution with the MLE of $\lambda_{ij}$ derived from observed data, we obtain a posterior distribution that also follows a beta distribution with new hyperparameters $\alpha_{ij}'=\alpha_{ij}+k$ and $\beta_{ij}'=\beta_{ij}+n-k$ (\emph{Appendix S3}).
+    Combining the prior distribution with the MLE of $\lambda_{ij}$ derived from observed data, we obtain a posterior distribution of $\lambda_{ij}$ that also follows a beta distribution with new hyperparameters $\alpha_{ij}'=\alpha_{ij}+k$ and $\beta_{ij}'=\beta_{ij}+n-k$ (\emph{Appendix S3}).
 These definitions illustrate the influence of the prior on the posterior distribution: the difference between the posterior and the prior will increase with $k_{ij}$ and $n_{ij}-k_{ij}$.
@@
 As $n_{ij}$ increases, the total uncertainty about $\lambda_{ij}$ will decrease (Fig.~\ref{Salix_pdfs_cdfs}).
-Note that these models of $\lambda_{ij}$ do not distinguish between sources of uncertainty except through the choice of prior.
-For a model which attempts to separate sources of uncertainty, see~\citet{Weinstein2017}.
+Note that these models of $\lambda_{ij}$ are designed to i) quantify and ii) reduce the total uncertainty about $\lambda_{ij}$.
+They do not distinguish between sources of uncertainty except through the choice of prior.
 
@@
 Note that there is no 'correct' prior as long as the true distribution of interaction probabilities is unknown~\citep{Spiegelhalter2000}.
-The goal is to select a reasonable prior that reflects our assumptions about the true distribution and then adjust this prior with observed data as it becomes available.
+The goal is to select a reasonable prior that reflects our assumptions about the true distribution and then adjust it with observed data as it becomes available.
 When in doubt, it is also possible to model interaction probabilities using a variety of priors and compare results~\citep{Spiegelhalter2000}.
@@
 Stating that an interaction is ``forbidden" is, in effect, applying a very strong prior to reduce/eliminate uncertainty about the non-observation of that interaction.
+This is especially true when researchers assume that any species not observed co-occurring could not ever interact.
 Given the reality of subjective network construction, we feel it is better to make the assumptions used to build a network as explicit as possible so that these assumptions can be questioned, compared between studies, tested, and perhaps validated.
@@
 Since we model $\lambda_{ij}$ as a Bernoulli trial, the appropriate uninformative prior is the Jeffreys prior: a beta distribution with $\alpha_{ij}$=$\beta_{ij}$=0.5.
+Note that this prior assumes that interaction probabilities are uniformly distributed between 0 and 1, giving an estimated connectance of 0.5; this is likely unrealistic for most networks.
 The sum of $\alpha_{ij}$ and $\beta_{ij}$ is roughly equivalent to the weight of the prior, so the Jeffreys prior has equal weight to a single observation.
@@
 Informative models could also include information on abundances, phenological matching, co-occurrence, etc.
-as available~\citep{Jordano2016,Weinstein2017a,Graham2018}.
+as available~\citep{Jordano2016,Weinstein2017a,Graham2018,Gravel2018}.
 Multiple sources of information can be combined into a single model (e.g., the the $K$ nearest neighbour (KNN) algorithm, which identifies likely interaction partners based on similarity to known partners~\citep{DesjardinsProulx2017}).
@@
 It is also possible to interpret other network properties (e.g., species degrees) in a similar network(s) as interaction probabilities and use these to create a prior (see \emph{Appendix S4} for a worked example).
-When using network summary statistics or degree distributions, it is important to consider whether the available information reflects what we truly believe about the network.
+When using network summary statistics or degree distributions, it is important to consider whether the available information reflects what we believe about the network.
 Given the likelihood that most published networks are undersampled~\citep{Jordano2016}, it may be wise to include only the highest-quality networks available in a prior.
@@
 
-        If a similar dataset is not available, it is also possible to use data from the study at hand to develop a prior (i.e., "approximate Bayes"~\citet{Gelmanblog})~\citep{Spiegelhalter2000}.
+        If a similar dataset is not available, it is also possible to use data from the study at hand to develop a prior (i.e., ``approximate Bayes"~\citet{Gelmanblog})~\citep{Spiegelhalter2000}.
 This approach is used in medical testing~\citep{Spiegelhalter2000} and disease modelling~\citep{Leyland2005} using information from pilot studies and can easily be applied to ecological systems.
@@
 
-        Rather than calculating credible intervals for a posterior distribution after collecting data, we may wish to know how many data points are necessary to obtain a given level of confidence that two co-occurring species do not interact.
+        Rather than calculating credible intervals for a posterior distribution after collecting data, we may wish to know how many observations are necessary to be confident that two co-occurring species do not interact (note that the beta distribution can never equal 0 or 1).
 The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact.
@@
 To demonstrate this, we created a suite of filtered networks for each posterior network.
-Taking a posterior network as the "true" network, we randomly sampled 90\%, 80\%, 70\%, 60\%, 50\%, 40\%, 30\%, 20\%, and 10\% of the interactions to create a new "filtered" network.
+Taking a posterior network as the ``true" network, we randomly sampled 90\%, 80\%, 70\%, 60\%, 50\%, 40\%, 30\%, 20\%, and 10\% of the interactions to create a new ``filtered" network.
 This gradient is akin to a gradient of uncertainty in the network (e.g., due to varying sampling effort or intraspecific trait variability).
@@
   %   \caption{Imperfect detection of interactions increases the number of samples required to be confident that an interaction never occurs.
-Assume that two species cannot interact (i.e., $\lambda=0$) and that the number of observed interactions follows a binomial distribution depending upon the number of observed interactions $k$ and observed co-occurrances $n$.
+Assume that two species cannot interact (i.e., $\lambda=0$) and that the number of observed interactions follows a binomial distribution depending upon the number of observed interactions $k$ and observed co-occurrences $n$.
 The maximum likelihood estimate (MLE) for $\lambda_{ij}$ is $\lambda_{MLE}=\frac{k}{n}$.

### 2019-01-16 manuscript/supplemental.tex
a few Dom comments that refer to newly-SI material

@@
 Despite these benefits, we note that there are limits to the utility of increased sampling.
-Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig.
+Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present~\citep{Gravel2018}), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig.
 2C, main text).
-While this improves our understanding of the set of species present in the community, it introduces yet more uncertainty into the interaction matrix.
+While this improves our understanding of the set of species present in the community, it introduces yet more uncertainty into the matrix of feasible interactions.
 Note that it is better to identify the set of potential interactions than to miss a species, so sampling effort should not be reduced in order to exclude rare species.

### 2019-01-17 manuscript/reply_to_reviewers.tex
SI ready

@@
 We argue that a great deal of subjectivity is baked into the compilation of empirical networks and that a Bayesian approach can be seen as making this subjectivity explicit.
-We hope that this will encourage empiricists to explicitly use their system-specific knowledge to create reasonable priors, as likely already occurs subconsciously (as in the designation of ``forbidden links``).
+We hope that this will encourage empiricists to explicitly use their system-specific knowledge to create reasonable priors, as likely already occurs subconsciously (as in the designation of ``forbidden links'').
 
@@
 In doing so, we have happily adopted the suggestion to expand our discussion of prior selection, particularly with regard to approximate/empirical Bayes.
-Although we are somewhat space-limited, we have expanded our description of the different priors available and why a researcher might choose one over another (section beginning with line 200).
-We also touch upon the controversy over using empirical priors (lines 283-289) although we were unable to find many references addressing this in detail.
+Although we are somewhat space-limited, we have expanded our description of the different priors available and why a researcher might choose one over another (section beginning with line 201).
+We also touch upon the controversy over using empirical priors (lines 293-298) although we were unable to find many references addressing this in detail.
 We hope that this expanded description will be a better guide for empiricists who may not be familiar with Bayesian statistics.
@@
 Therefore we have revised and streamlined our introduction but still refrain from jumping straight into prior selection.
-We have, however, taken care to introduce our analysis as a worked example (lines 200-201) and hope that this helps to reduce the conflict between the introduction and our data.
+We have, however, taken care to introduce our analysis as a worked example (lines 300-301) and hope that this helps to reduce the conflict between the introduction and our data.
 
@@
 We therefore feel that it is important to keep some discussion of the MLE estimate in the manuscript.
-We now introduce the MLE formally within this context (lines 179-184) and take care to be explicit when using it to explore the sample size needed in the absence of prior knowledge later (caption of Figure S2, \emph{Appendix S2}}).
-
-		Lines 179-184:
+We now introduce the MLE formally within this context (lines 178-184) and take care to be explicit when using it to explore the sample size needed in the absence of prior knowledge later (caption of Figure S2, \emph{Appendix S2}}).
+
+		Lines 178-184:
 
@@
 			The basis of a Bayesian approach to modelling the probability that an interaction between species $i$ and $j$ occurs ($\lambda_{ij}$) is combining the maximum likelihood estimate (MLE) of $\lambda_{ij}$ with a prior distribution (described in the next section) and a normalising function.
-The MLE of $\lambda_{ij}$ can be modelled as a Bernoulli trial based on the number of observed interactions $k_ij$ and observed co-occurrences $n_{ij}$: $\lambda_{ij}=\frac{k_{ij}}{n_{ij}}$.
-The most appropriate prior distribution for $\lambda_{ij}$ is the beta distribution:
+The MLE of $\lambda_{ij}$ can be computed from the number of observed interactions $k_ij$ and observed co-occurrences $n_{ij}$: $\lambda_{ij}=\frac{k_{ij}}{n_{ij}}$.
+The most appropriate prior distribution for $\lambda_{ij}$ is the beta distribution ...
 		\end{quotation}
@@
 			The number of observed co-occurrences needed to believe that an unobserved interaction cannot occur is very high (about 35; Fig.
-3), and most datasets will not include this level of sampling for all pairs of species~\citep{Bartomeus2013}.
+S2), and most datasets will not include this level of sampling for all pairs of species~\citep{Bartomeus2013}.
 		\end{quotation}
@@
 
-		\textbf{R:} We now address questions of sampling in the paragraph beginning with line 168 and in Appendix S2.
+		\textbf{R:} We now address questions of sampling in the paragraph beginning with line 166 and in Appendix S2.
 We hope that this revision makes it clear that sampling should be as high-quality as possible but that sampling is unlikely to completely remove uncertainty.
@@
 Nevertheless, non-independence of interactions is an important consideration.
-We are therefore happy to index all variables referring to interactions by ij and we have added explicit statements (lines 186-190 and 248-255) that some priors treat interactions independently while others will introduce covariance (e.g., by species).
-
-		Lines 186-190:
-
-		\begin{quotation}
-		    The shape parameters, or hyperparameters, may be set to particular values or derived from some data (see below).
-Note that the hyperparameters may be set to the same values for all interactions, allowed to vary independently for all interactions, or may incorporate non-independence between interactions (e.g., when the shape of the prior distribution depends upon species' abundances or traits).
-		\end{quotation}
-
-		Lines 248-255:
-
-		\begin{quotation}
-			Multiple sources of information can be combined into a single model (e.g., the the $K$ nearest neighbour (KNN) algorithm, which identifies likely interaction partners based on similarity to known partners~\citep{DesjardinsProulx}).
+We are therefore happy to index all variables referring to interactions by ij and we have added explicit statements (lines 185-188 and 251-259) that some priors treat interactions independently while others will introduce covariance (e.g., by species).
+
+		Lines 185-188:
+
+		\begin{quotation}
+		    The shape parameters, or hyperparameters, may be set to particular values or derived from data (see below).
+They may be the same for all interactions, allowed to vary independently across interactions, or incorporate non-independence between interactions (e.g., when the shape of the prior distribution depends upon species' abundances or traits).
+		\end{quotation}
+
+		Lines 251-259:
+
+		\begin{quotation}
+			Multiple sources of information can be combined into a single model (e.g., the the $K$ nearest neighbour (KNN) algorithm, which identifies likely interaction partners based on similarity to known partners~\citep{DesjardinsProulx2017}).
 This would result in a highly informative prior that would, moreover, account for some of the non-independence in interaction probabilities.
@@
 The only inputs are a prior distribution, which could refer to any level of uncertainty applicable to the study at hand, and post-hoc counts of interactions and co-occurrences.
-Using only the observed data, it is impossible to separate the three levels of uncertainty and our model does not aim to do so (as stated in lines 159-167 and lines 199-201).
+Using only the observed data, it is impossible to separate the three levels of uncertainty and our model does not aim to do so (as stated in lines 159-165 and lines 198-200).
 We therefore do not believe that an in-depth discussion of identifiability would add much value to the manuscript and, in the interest of space, have decided not to include one.
@@
 
-		Lines 159-167:
-
-		\begin{quotation}
-			When considering a metaweb, we wish to separate the unobserved interactions where $L_{ij}=0$ (i.e., unfeasible interactions) from interactions which could occur but did not at a particular sampling site or which occurred but were not detected (Fig.
+		Lines 159-165:
+
+		\begin{quotation}
+			When considering a metaweb, we wish to separate the unobserved interactions where $L_{ij}=0$ (i.e., unfeasible interactions) from interactions which were feasible but did not occur during sampling or  were not detected (Fig.
 1).
-Unfortunately, this is not possible for most interactions (except those where we know an interaction is truly not feasible).
-That is, we generally do not know \emph{why} an interaction was not observed, only that it was not.
-An empirical ecologist will instead measure the marginal probability $P(L_{ij})=k_{ij}/n_{ij}$, where $k_{ij}$ is the number of observed interactions between species $i$ and $j$ and $n_{ij}$ the number of observed co-occurrences.
-Given this information, the question becomes: how can we reduce the uncertainty around our estimated interaction probability?
-		\end{quotation}
-
-		Lines 199-201:
-
-		\begin{quotation}
-			 Note that these models of $\lambda_{ij}$ do not distinguish between sources of uncertainty except through the choice of prior.
-For a model which attempts to separate sources of uncertainty, see~\citet{Weinstein2017}.
+An empirical ecologist will measure the marginal probability $P(L_{ij})=k_{ij}/n_{ij}$, where $k_{ij}$ is the number of observed interactions between species $i$ and $j$ and $n_{ij}$ the number of observed co-occurrences.
+Given this information, how can we reduce the uncertainty around our estimated interaction probability?
+		\end{quotation}
+
+		Lines 198-200:
+
+		\begin{quotation}
+			 Note that these models of $\lambda_{ij}$ are designed to i) quantify and ii) reduce the total uncertainty about $\lambda_{ij}$.
+They do not distinguish between sources of uncertainty except through the choice of prior.
 		\end{quotation}
@@
 
-		Lines 320-324:
+		Lines 321-326:
 
@@
 
-		Lines 324-326:
+		Lines 326-328:
 
@@
 A full discussion of how and why these values differ is better suited to either an exhaustive simulation study or an experimental study where different sources of uncertainty can be controlled to some degree.
-We now state that these four properties were chosen as illustrative examples (lines 425-428).
+We now state that these four properties were chosen as illustrative examples (Appendix S10).
 
@@
 		\textbf{R:} In the interest of space, we have added an extended description of the sampling procedure in \emph{Appendix S2}.
-
-		Lines 420-425:
 
@@
 
-	14. l.306: given the shape of the distribution (exponential), the mean is not an appropriate indicator. [done]
+	14. l.306: given the shape of the distribution (exponential), the mean is not an appropriate indicator.
 
@@
 
-		Lines XX-XX:
+		Lines 354-357:
 
@@
 
-	15. What does higher nestedness in the observed networks mean? How is it possible? [done]
+	15. What does higher nestedness in the observed networks mean? How is it possible?
 
@@
 
-		Lines XX-XX:
+		Appendix S10:
 
@@
 Hopefully this will discourage readers from getting bogged down in trying to isolate which external factors cause which types of uncertainty (there is almost certainly overlap - e.g., bad weather could both reduce the probability that species will be active and interact and the probability that an interaction is observed if visibility is poor).
-We have also added a section (beginning line 117) referring to ``forbidden links'' which addresses overlap between the questions of whether species can interact (which we had previously called interaction uncertainty) and whether they do interact at a particular site (previously process uncertainty).
+We have also added a section (beginning line 119) referring to ``forbidden links'' which addresses overlap between the questions of whether species can interact (which we had previously called interaction uncertainty) and whether they do interact at a particular site (previously process uncertainty).
 We hope that this addition clarifies the agreement of our manuscript with previous works listing sources of uncertainty.
@@
 
-            Both whether species can ever interact and whether they interact at a particular place and time have been discussed in the context of ``forbidden links``~\citep{Jordano2016}.
+            Both whether species can ever interact and Both whether species can ever interact and whether they interact at a particular place and time have been discussed in the context of ``forbidden links"~\citep{Jordano2016}.
 In this framework, all links which are prevented by spatio-temporal uncoupling, physiological constraints, etc.
-are considered ``structural zeros'' that cannot be observed~\citep{Jordano1987,Jordano2016}.
+are considered ``structural zeros" that cannot be observed~\citep{Jordano1987,Jordano2016}.
 We conceptually distinguish between physiological constraints and spatio-temporal uncoupling to allow for cases in which a species is introduced to a new habitat, expands its range, or shifts phenology~\citep{Gravel2013}.
-In such cases, links which are impossible due to physiological constraints remain forbidden but links previously ``forbidden'' by spatio-temporal mismatch could potentially occur.
+In such cases, links which are impossible due to physiological constraints remain forbidden but links previously ``forbidden" by spatio-temporal mismatch could potentially occur.
       \end{quotation}
@@
 
-		\textbf{R:} We have expanded our introduction of the case study (beginning line 295) to make it clear that we are using the highest-quality empirical network we can find as even such networks have uncertainty about unobserved interactions.
+		\textbf{R:} We have expanded our introduction of the case study (beginning line 302) to make it clear that we are using the highest-quality empirical network we can find as even such networks have uncertainty about unobserved interactions.
 This relates back to our point that urging increased sampling effort is not likely to solve problems of uncertainty as long as sampling is limited in the number of methodologies that can be applied, biased towards abundant or easy-to-identify species, restricted to particular spatial sites and/or environmental conditions (if the network is intended to be more general), or all of the above.
@@
 We repeat this point in the discussion to ensure that the case study is relevant.
-We have also clarified our statement that a strict application of Bayesian statistics does not allow empirical priors, but that they are an option for researchers that are more concerned about matching their prior to their study system than with strict formalism (lines 296-293).
+We have also clarified our statement that a strict application of Bayesian statistics does not allow empirical priors, but that they are an option for researchers that are more concerned about matching their prior to their study system than with strict formalism (lines 293-296).
 As Reviewer 1 points out, this is somewhat controversial and we feel it is important to note the potential objection.
@@
 This dataset consists of a single community type sampled across Europe over 29 years and at 374 unique locations.
-The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (see \emph{Appendix S5} for details).
-		      The high spatiotemporal resolution of this dataset make it ideal for illustrating the difficulties in completely sampling a network; even with such an unusually high sampling effort, there were many pairs of species which were rarely or never observed together and about which we therefore have high uncertainty about interaction probabilities (Fig.
-2).
+The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (\emph{Appendix S5}).
+		      The high spatiotemporal resolution of this dataset makes it ideal for illustrating the difficulties in completely sampling a network; even with such an unusually high sampling effort, there were many pairs of species which were rarely or never observed together and about which we therefore have high uncertainty about interaction probabilities (Fig.~\ref{histograms}).
 Using the Bayesian framework above, we can identify which potential interactions are more and less uncertain, allowing us to better predict the true structure of the metaweb.
@@
 We therefore cannot suggest modelling co-occurrence as a panacea.
-Instead, we now emphasise that co-occurrence probabilities are one thing that could be included in a prior (section beginning line 231).
+Instead, we now emphasise that co-occurrence probabilities are one thing that could be included in a prior (section beginning line 238).
 
@@
 		\textbf{R:} Following suggestions by this Reviewer and another, we have substantially expanded our discussion of different options for priors (including the trait-based and co-occurrence models the Reviewer points out).
-We have also added an explicit statement that researchers wishing to test the influence of a particular trait (for example) should \emph{not} include that trait in their prior (lines 252-255).
+We have also added an explicit statement that researchers wishing to test the influence of a particular trait (for example) should \emph{not} include that trait in their prior (lines 260-263).
 We hope that this statement, and the expanded discussion of different types of priors more generally, allay the Reviewer's concerns.
@@
 This will allow future researchers to evaluate the uncertainty about all interactions in a network as the state of expert knowledge changes.
-We hope that this expanded recommendation (lines XX-XX) is clearer.
+We hope that this expanded recommendation (lines 399-402) is clearer.
 
@@
 
-		To make this clearer, we have rephrased this section and added a line (lines 61-68) stating that we usually cannot determine the cause of all the zeros in an interaction matrix (we can identify obviously unfeasible interactions, but likely cannot say whether a zero for a rare species is because we did not observe enough individuals, there were not enough individuals to perform a particular interaction, or because the interaction is actually unfeasible).
+		To make this clearer, we have rephrased this section and added a line (lines 65-72) stating that we usually cannot determine the cause of all the zeros in an interaction matrix (we can identify obviously unfeasible interactions, but likely cannot say whether a zero for a rare species is because we did not observe enough individuals, there were not enough individuals to perform a particular interaction, or because the interaction is actually unfeasible).
 We hope that this revision makes it clearer that the description of different sources of uncertainty is a conceptual guide only.
@@
 		\begin{quotation}
-			While an observed link definitely occurred (assuming correct identification of the species involved), a given link may not be observed for many reasons, \emph{whether or not it truly occurred} (Fig.
+			While an observed link definitely occurred (assuming species are correctly identified), a link may not be observed for many reasons, \emph{whether or not it truly occurred} (Fig.
 1).
@@
 Spatial variation in interaction probabilities will affect all interaction types, as does variation in abundances between years, so we cannot conceive of any interactions that are exempt from this issue.
-The timescale of an interaction (and the evidence it leaves) does affect detection uncertainty, so we have added a note in that section (lines 137-140).
+The timescale of an interaction (and the evidence it leaves) does affect detection uncertainty, so we have added a note in that section (lines 143-1246).
 Long-term interactions may still fail to be detected, however, and we now add an example to make it clear that detection uncertainty applies to even long-term interactions such as gall-forming (indeed, our results suggest that uncertainty in gall-forming is quite high).
@@
 
-		Lines 137-140:
-
-		\begin{quotation}
-			The probability of detecting an interaction will also depend on the duration of the interaction and its evidence, the species involved, and the individuals sampled~\citep{Wells2013,Lagrue2015,Cirtwill2016,Weinstein2017}.
+		Lines 143-146:
+
+		\begin{quotation}
+			The probability of detecting an interaction also depends on the duration of the interaction and its evidence, the species involved, and the individuals sampled~\citep{Wells2013,Lagrue2015,Cirtwill2016,Weinstein2017}.
 		\end{quotation}
@@
 We also note that a simple worked example, with accompanying R code, is provided in \emph{Appendix S4} so that readers can see exactly how to obtain $\alpha$ and $\beta$.
-In case the point of confusion is the idea that $\alpha$ and $\beta$ can be specified or derived depending on the type of prior desired, we have added a line (lines 181-185) spelling this out.
-
-		\begin{quotation}
-			The shape parameters, or hyperparameters, may be set to particular values or derived from some data (see below).
-They may be set to the same values for all interactions, allowed to vary independently for all interactions, or incorporate non-independence between interactions (e.g., when the shape of the prior distribution depends upon species' abundances or traits).
+In case the point of confusion is the idea that $\alpha$ and $\beta$ can be specified or derived depending on the type of prior desired, we have added a line (lines 185-188) spelling this out.
+
+		\begin{quotation}
+			The shape parameters, or hyperparameters, may be set to particular values or derived from data (see below).
+They may be the same for all interactions, allowed to vary independently across interactions, or incorporate non-independence between interactions (e.g., when the shape of the prior distribution depends upon species' abundances or traits).
 			\end{quotation}
@@
 
-		\textbf{R:} We appreciate the Reviewer's desire for optimism, but we also selected a high-quality dataset specifically in order to demonstrate that empirically sampling all of the feasible interactions in a system is very unlikely.
-A lower-quality dataset would work just as well with our framework but would not highlight these difficulties so well.
-We have therefore kept this line as-is but have expanded the paragraph (301-307) to show how the Bayesian framework provides a partial solution to the problems inherent in even high-quality empirical data.
-
-		\begin{quotation}
-		 The high spatiotemporal resolution of this dataset makes it ideal for illustrating the difficulties in completely sampling a network; even with such an unusually high sampling effort, there were many pairs of species which were rarely or never observed together and about which we therefore have high uncertainty about interaction probabilities (Fig.
-2).
-Using the Bayesian framework above, we can identify which potential interactions are more and less uncertain, allowing us to better predict the true structure of the metaweb.
-		 \end{quotation}
+		\textbf{R:} We appreciate the Reviewer's desire for optimism and have tried to reframe the manuscript in order to present Bayesian approaches as a partial solution to problems of uncertainty.
 

### 2019-01-17 manuscript/CI_interactions.tex
SI ready

@@
 % \item Abstract word count: 290
-% \item Main text word count: 6973 % Limit is 6000-7000 including figs, tables, references. Would be good to include Dom2018 if I can trim a bit more.
+% \item Main text word count: 6995, excluding abstract % Limit is 6000-7000 including figs, tables, references. 
 % \end{itemize}
@@
       We start from the perspective of a community ecologist describing an interaction network.
-This ecologist will be interested in describing the species/nodes present and the links between them~\citep{Roslin2016}.
-While an observed link definitely occurred (assuming correct identification of the species involved), a given link may not be observed for many reasons, \emph{whether or not it truly occurred} (Fig.~\ref{conceptual_fig}).
+This ecologist will want to describe the species present and the links between them~\citep{Roslin2016}.
+While an observed link definitely occurred (assuming species are correctly identified), a link may not be observed for many reasons, \emph{whether or not it truly occurred} (Fig.~\ref{conceptual_fig}).
 Moreover, given an unobserved interaction in an empirical dataset, we often cannot determine why the interaction was not observed \emph{post hoc}.
@@
           Fundamentally, some interactions are feasible while others are not~\citep{Poisot2015}.
-An unobserved interaction may have $\lambda_{ij}>0$, and the associated zero in an interaction matrix might be false.
-This uncertainty is partly addressed by trait-matching models~\citep{Bartomeus2016,Jordano2016,Weinstein2017}.
 Assuming that the feasibility of interactions depends on the traits of species involved, we can define the probability of an interaction $L_{ij}$ between species $i$ and $j$ given some function describing trait matching $\mathbf{T_{ij}}$ as $P(L_{ij}|\mathbf{T_{ij}})=\lambda_{ij}$~\citep{Bartomeus2013,Gravel2013,Weinstein2017}.
@@
 Generally, however, the traits that might prohibit an interaction are unknown~\citep{Dormann2017} and uncertainty about $\lambda_{ij}$ will be high.
-          %Pollinators may visit plants outside of those predicted based on ``pollination syndromes"~\citep{Weinstein2017a} and herbivores may consume animal prey when it becomes accessible~\citep{Furness1988,Pietz2000}.
-These examples illustrate the danger in assuming that seemingly unlikely interactions cannot occur.
-          As trait-matching models improve, uncertainty will be reduced~\citep{Jordano2016} and $\lambda_{ij}$ should either tend to 0 or to 1.
+          An unobserved interaction may have $\lambda_{ij}>0$, and the associated zero in an interaction matrix might be false.
+Using a trait-matching model can reduce uncertainty about $\lambda_{ij}$~\citep{Jordano2016}.
+As these models improve, $\lambda_{ij}$ should either tend to 0 or to 1.
 Nevertheless, every model is imperfect and lacks information that could be used to define constraints on at least some interactions~\citep{Dormann2017}.
@@
 
-          Assuming that an interaction is feasible (i.e., $L_{ij}=1$;), it may still not occur at a particular place and time~\citep{Poisot2015,Graham2018}.
+          A feasible interaction (i.e., $L_{ij}=1$;), still may not occur at a particular place and time~\citep{Poisot2015,Graham2018}.
 This could be because constraints such as inclement weather or low abundance prevented the interaction~\citep{Jordano2016,Graham2018}, a preferred interaction partner was available~\citep{Weinstein2017a}, or individual variation in traits meant that local individuals could not interact even if the species in general can~\citep{Gravel2013,Wells2013,Poisot2015}.
 For example, a rare galler may not parasitize a rare plant because they do not encounter each other.
-In metawebs, an interaction may also not occur because two species do not co-occur at a particular site even if they do co-occur and interact elsewhere~\citep{Graham2018}.
+In metawebs, an interaction may not occur locally because two species do not co-occur at a particular site even if they do co-occur and interact elsewhere~\citep{Graham2018}.
 We can define the local realisation of an interaction, $X_{ij}$, given that the interaction is feasible, as a stochastic process with associated probability $P(X_{ij}|L_{ij}=1)=\chi_{ij}$.
@@
 Some studies attempt to reduce uncertainty by sampling intensively over a short period of time and restricting the scale of interest to interactions occurring at the sampling site and time (conflating $\chi_{ij}$ and $\lambda_{ij}$)~\citep{Bartomeus2013,Weinstein2017,Weinstein2017a}.
-This approach may be suitable for some research questions, but is not appropriate if we wish to assemble the full set of interactions which occur in a community (beyond the specific site and time of sampling).
-In contrast, expanding sampling to cover a broader spatial or temporal range (e.g., sampling in a variety of microhabitats or during a variety of weather conditions) will help to reduce uncertainty about $\chi_{ij}$ by including a broader range of parameters affecting interaction probability.
+This approach does reduce local-scale uncertainty but is not appropriate if we wish to assemble the full set of interactions which occur in a community (beyond the specific site and time of sampling).
+In contrast, expanding sampling to cover a broader spatial or temporal range (e.g., sampling in a variety of micro-habitats or during a variety of weather conditions) will help to reduce uncertainty about $\chi_{ij}$ by including a broader range of parameters affecting interaction probability.
 It is unlikely, however, that resources will permit researchers to sample extensively in the full range of sites and conditions covered by a community, and some uncertainty about $\chi_{ij}$ will remain.
@@
 In such cases, links which are impossible due to physiological constraints remain forbidden but links previously ``forbidden" by spatio-temporal mismatch could potentially occur.
-When considering local realisations of a metaweb, it is possible to distinguish between interactions forbidden by traits and those forbidden by lack of co-occurrence~\citep{Gravel2018}.
-In the present study, we are concerned with identifying the metaweb-- the set of interactions which are feasible assuming species co-occur.
+When considering local realisations of a metaweb, one can distinguish between interactions forbidden by traits and those forbidden by lack of co-occurrence~\citep{Gravel2018}.
+This is not possible, however, when trying to identify the metaweb.
 
@@
           Lastly, measurement errors are a pervasive source of uncertainty about ecological processes.
-Even an interaction which is feasible and occurs during sampling ($L_{ij}=1$, $X_{ij}=1$), may still go undetected~\citep{Jordano2016,Weinstein2017}.
+Even a feasible interaction which occurs during sampling ($L_{ij}=1$, $X_{ij}=1$) may still go undetected~\citep{Jordano2016,Weinstein2017}.
 We can define the probability of detecting of an interaction, $D_{ij}$, given the interaction is feasible and occurs, as a stochastic process with  probability $P(D_{ij}|X_{ij}=1,L_{ij}=1)=\delta_{ij}$.
-Note that $D_{ij}$ is a stochastic variable taking the variable 1 if observed and 0 otherwise, while $P(D_{ij})$ is the probability that $D_{ij}=1$.
-Detection failure could happen for many reasons (see~\citet{Wirta2014}).
-Some sources of detection error can be minimised with appropriate sampling (e.g., combining multiple sampling methods~\citet{Wirta2014,Frost2016,Jordano2016}), but other sources are difficult to reduce.
-For example, it may not be possible to sample some species due to conservation concerns~\citep{Lagrue2015}.
-The probability of detecting an interaction will also depend on the duration of the interaction and its evidence, the species involved, and the individuals sampled~\citep{Wells2013,Lagrue2015,Cirtwill2016,Weinstein2017}.
-With improved sampling, $D_{ij}$ should tend towards 1 but, importantly $D_{ij}$ will vary between interactions and it is likely that $D_{ij}<1$ within a sample.
-For example, when detecting interactions based on gut contents interactions with slowly-digested prey with hard parts will be more detectable than interactions with quickly-digested, soft prey.
+Note that $D_{ij}$ is a stochastic variable where $D_{ij}=1$ if the interaction observed and $D_{ij}=0$ otherwise, while $P(D_{ij})$ is a continuous probability.
+Detection failure could happen for many reasons~\citep{Wirta2014}.
+Some sources of detection failure can be minimised (e.g., by combining multiple sampling methods~\citet{Wirta2014,Jordano2016}), but other sources are difficult to reduce.
+For example, it may not be possible to sample some species directly due to conservation concerns~\citep{Lagrue2015}.
+The probability of detecting an interaction also depends on the duration of the interaction and its evidence, the species involved, and the individuals sampled~\citep{Wells2013,Lagrue2015,Cirtwill2016,Weinstein2017}.
+As sampling improves $D_{ij}$ should tend towards 1 but, importantly, $D_{ij}$ will vary between interactions it is very likely that some $D_{ij}<1$.
+For example, when analysing gut contents interactions involving prey with hard parts will be more detectable than interactions with quickly-digested, soft prey.
 
@@
 
-    To sum up, the absence of an interaction could be because it was not feasible [$P(L_{ij})=0$], was feasible but did not occur during sampling ($P(X_{ij}|L_{ij}=1)=0$], or was feasible and occurred during sampling but could not be observed [$P(D_{ij}|X_{ij}=1,L_{ij}=1)=0$].
-Researchers might be interested in whether an un-recorded interaction is feasible (i.e., reducing uncertainty about $\lambda_{ij}$) or whether or not a feasible interaction occurred locally (i.e., reducing uncertainty about $\chi_{ij}$).
-Here we consider the former, while noting that uncertainty about both $\chi_{ij}$ and $\delta_{ij}$ contribute to uncertainty about $\lambda_{ij}$.
-Future sampling should aim to characterise all three probabilities, but for now it is often difficult to distinguish between them.
-One reason for this is the ability of external factors such as abundance to affect multiple levels of uncertainty.
+    In summary, an unobserved could be unfeasible [$P(L_{ij})=0$], be feasible but not occur during sampling ($P(X_{ij}|L_{ij}=1)=0$], or be feasible and occur during sampling but not be observed [$P(D_{ij}|X_{ij}=1,L_{ij}=1)=0$].
+Researchers might be interested in identifying feasible interactions (i.e., reducing uncertainty about $\lambda_{ij}$) or identifying feasible interactions that occurred locally (i.e., reducing uncertainty about $\chi_{ij}$).
+Here we consider the former problem while noting that uncertainty about both $\chi_{ij}$ and $\delta_{ij}$ contribute to uncertainty about $\lambda_{ij}$.
+Future sampling should aim to characterise all three probabilities, as is possible in some studies focused on local realisations of a metaweb (e.g.,~\citet{Graham2018,Gravel2018}), but for now it is often difficult to distinguish between them.
+    %One reason for this is the effect of factors such as abundance  on multiple levels of uncertainty.
 Rare species are less likely to interact at a given site due to neutral processes~\citep{Jordano2016,Graham2018} and interactions involving rare species are less likely to be detected~\citep{Bartomeus2013,Jordano2016}.
@@
 
-    When considering a metaweb, we wish to separate the unobserved interactions where $L_{ij}=0$ (i.e., unfeasible interactions) from interactions which could occur but did not at a particular sampling site or which occurred but were not detected (Fig.~\ref{conceptual_fig}).
-Unfortunately, unlike studies focused on local realisations of a network (e.g.,~\citet{Graham2018,Gravel2018}), in a metaweb we generally do not know \emph{why} an interaction was not observed.
+    When considering a metaweb, we wish to separate the unobserved interactions where $L_{ij}=0$ (i.e., unfeasible interactions) from interactions which were feasible but did not occur during sampling or  were not detected (Fig.~\ref{conceptual_fig}).
 An empirical ecologist will measure the marginal probability $P(L_{ij})=k_{ij}/n_{ij}$, where $k_{ij}$ is the number of observed interactions between species $i$ and $j$ and $n_{ij}$ the number of observed co-occurrences.
-Given this information, the question becomes: how can we reduce the uncertainty around our estimated interaction probability?
+Given this information, how can we reduce the uncertainty around our estimated interaction probability?
 
-    The obvious rule of thumb to reduce uncertainty is ``sample more".
-Where resources permit, increasing sample sizes will reduce uncertainty about the upper bound of the interaction probability and will also increase the probability of detecting unlikely or cryptic interactions (e.g., interactions where $L_{ij}=1$ but $\chi_{ij}$ or $\delta_{ij}$ is low).
-In some systems, targetted sampling of particular species pairs could reduce especially high uncertainties about $\lambda_{ij}$, but this will not be possible everywhere (e.g., in host-parasitoid systems).
-High-quality sampling a crucial part of constructing an empirical network, but there are limits to the utility of increased sampling (see \emph{Appendix S2, Fig.
+    One obvious way to reduce uncertainty is to increase sampling.
+High sample sizes will reduce uncertainty about the upper bound of $\lambda_{ij}$ and increase the probability of detecting unlikely or cryptic interactions (where $L_{ij}=1$ but $\chi_{ij}$ or $\delta_{ij}$ is low).
+In some systems, targeted sampling of particular species pairs could reduce especially high uncertainties about $\lambda_{ij}$, but this will not be possible everywhere (e.g., in host-parasitoid systems where parasitoid identities are unknown during sample collection).
+High-quality sampling is crucial in studies of empirical networks, but there are limits to the ability of sampling to reduce uncertainty (\emph{Appendix S2, Fig.
 S2}).
-To compliment high-quality sampling, we can reduce uncertainty by combining observed data with prior knowledge about the system.
-This is straightforward to do using a Bayesian approach, as detailed below.
+As a complement to improved sampling, we can also reduce uncertainty by leveraging prior knowledge about the system using a Bayesian approach, as detailed below.
 
@@
 
-    The shape parameters, or hyperparameters, may be set to particular values or derived from some data (see below).
-They may be set to the same values for all interactions, allowed to vary independently for all interactions, or incorporate non-independence between interactions (e.g., when the shape of the prior distribution depends upon species' abundances or traits).
+    The shape parameters, or hyperparameters, may be set to particular values or derived from data (see below).
+They may be the same for all interactions, allowed to vary independently across interactions, or incorporate non-independence between interactions (e.g., when the shape of the prior distribution depends upon species' abundances or traits).
 For example, a prior could account for the tendency for abundant species to interact more frequently with all possible partners than rare species.
@@
 These definitions illustrate the influence of the prior on the posterior distribution: the difference between the posterior and the prior will increase with $k_{ij}$ and $n_{ij}-k_{ij}$.
-In other words, the distribution of $\lambda_{ij}$ for better-sampled pairs of species will rely less on the information used to build the prior distribution and more on the observed data.
-As $n_{ij}$ increases, the total uncertainty about $\lambda_{ij}$ will decrease (Fig.~\ref{Salix_pdfs_cdfs}).
+The distribution of $\lambda_{ij}$ for better-sampled pairs of species relies less on the information used to build the prior distribution and more on the observed data.
+As $n_{ij}$ increases, the total uncertainty about $\lambda_{ij}$ decreases (Fig.~\ref{Salix_pdfs_cdfs}).
 Note that these models of $\lambda_{ij}$ are designed to i) quantify and ii) reduce the total uncertainty about $\lambda_{ij}$.
@@
 
-      The choice of prior reflects a study's goal, the amount of prior knowledge available, and the strength of researchers' belief in that knowledge.
+      The prior used reflects a study's goal, the amount of prior knowledge available, and the strength of researchers' belief in that knowledge.
 Note that there is no 'correct' prior as long as the true distribution of interaction probabilities is unknown~\citep{Spiegelhalter2000}.
-The goal is to select a reasonable prior that reflects our assumptions about the true distribution and then adjust it with observed data as it becomes available.
+The goal is to select a prior that reflects reasonable assumptions about the true distribution and then adjust it with observed data as it becomes available.
 When in doubt, it is also possible to model interaction probabilities using a variety of priors and compare results~\citep{Spiegelhalter2000}.
 
-      Some researchers are reluctant to adopt a Bayesian approach because of its perceived subjectivity (i.e., a metaweb simulated using a Bayesian distribution will depend upon the assumptions inherent in the prior).
+      Some researchers are reluctant to adopt Bayesian approaches because of their perceived subjectivity (i.e., a metaweb simulated using a Bayesian distribution will depend upon the assumptions inherent in the prior).
 We argue that one of the advantages of the Bayesian approach is that it makes this subjectivity explicit~\citep{Spiegelhalter2000}.
-Researchers compiling empirical networks face many decisions about where to set community boundaries, the set of species to include in the focal community~\citep{Jordano2016}, what type of sampling is most appropriate~\citep{Wirta2014}, etc.
-These choices all affect the compiled network and most do not have clear answers, making all empirical networks (and all theoretical networks, which likewise depend upon the assumptions used in building the network) somewhat subjective.
-In addition, researchers distinguishing ``forbidden links" inherently rely on prior knowledge to identify these links~\citep{Jordano2016}.
+Researchers compiling empirical networks face many decisions about defining community boundaries, the set of species to include in the focal community~\citep{Jordano2016}, the most appropriate type of sampling~\citep{Wirta2014}, etc.
+These choices all affect the network obtained and most do not have clear answers, making all empirical networks (and all theoretical networks, which likewise depend upon the assumptions used to build the network) somewhat subjective.
+In addition, researchers identifying ``forbidden links" inherently rely on prior knowledge to identify these links~\citep{Jordano2016}.
 Stating that an interaction is ``forbidden" is, in effect, applying a very strong prior to reduce/eliminate uncertainty about the non-observation of that interaction.
@@
         Note that, in this case, the prior distribution will be the same for all interaction probabilities.
-It is also possible to interpret other network properties (e.g., species degrees) in a similar network(s) as interaction probabilities and use these to create a prior (see \emph{Appendix S4} for a worked example).
+It is also possible to interpret other network properties (e.g., species degrees) in a similar network(s) as interaction probabilities and use these to create a prior (worked example in \emph{Appendix S4}).
 When using network summary statistics or degree distributions, it is important to consider whether the available information reflects what we believe about the network.
@@
 Likewise, only the degree distribution for a similar system is likely to be a reasonable prior for a focal system.
-For example, if the focal system is large and contains a diverse array of species, it would be inappropriate to use a prior distribution drawn from a small network describing closely-related taxa (see \emph{Appendix S7} for a demonstration).
+For example, if the focal system is large and contains a diverse array of species, it would be inappropriate to use a prior distribution drawn from a small network describing closely-related taxa (demonstrated in \emph{Appendix S7}).
 Similarly, highly-aggregated networks containing nodes which represent whole classes or families are likely to have very different structures than networks where most nodes represent single species as aggregated nodes are likely to have more interaction partners than single species.
@@
 This dataset consists of a single community type sampled across Europe over 29 years and at 374 unique locations.
-The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (see \emph{Appendix S5} for details).
+The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (\emph{Appendix S5}).
       The high spatiotemporal resolution of this dataset makes it ideal for illustrating the difficulties in completely sampling a network; even with such an unusually high sampling effort, there were many pairs of species which were rarely or never observed together and about which we therefore have high uncertainty about interaction probabilities (Fig.~\ref{histograms}).
@@
 This gives $\alpha_{ij}'$=$\alpha_{ij}$ and $\beta_{ij}'$=$\beta_{ij} + n_{ij}$.
-We calculated posterior distributions and 95\% credible intervals (see function ``credible\_interval";~\emph{Appendix S9}) for species with $n$ ranging between 0 and 374, the total number of sites in our dataset.
+We calculated posterior distributions and 95\% credible intervals (function ``credible\_interval";~\emph{Appendix S9}) for species with $n$ ranging between 0 and 374, the total number of sites in our dataset.
 
@@
 The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact.
-We calculated the number of samples required to reach 95\% confidence that $\lambda_{ij}$ was below thresholds of 0.1, 0.05, and 0.01 as examples (see function ``samples\_for\_threshold";~\emph{Appendix S9}).
+We calculated the number of samples required to reach 95\% confidence that $\lambda_{ij}$ was below thresholds of 0.1, 0.05, and 0.01 as examples (function ``samples\_for\_threshold";~\emph{Appendix S9}).
 Finally, we may be interested in measures of network structure rather than the network itself.
-We can use the posterior distributions of interactions to generate a suite of plausible ``true'' networks that would be obtained if sampling uncertainty could be eliminated and use these networks to estimate many network properties (see \emph{Appendix S10} for a worked example).
+We can use the posterior distributions of interactions to generate a suite of plausible ``true'' networks that would be obtained if sampling uncertainty could be eliminated and use these networks to estimate many network properties (worked example in \emph{Appendix S10}).
 
@@
 Re-sampling networks based on a probabilistic understanding of networks is straightforward and gives distributions for network properties rather than point estimates.
-This not only acknowledges the fact that interactions vary over time and space but will also facilitate comparisons between networks by adding confidence intervals to estimates of network properties (see \emph{Appendix S9} for a worked example).
+This not only acknowledges the fact that interactions vary over time and space but will also facilitate comparisons between networks by adding confidence intervals to estimates of network properties (worked example in \emph{Appendix S9}).
 This will allow us to say whether networks have different structures \emph{and} whether those differences are greater than we would expect given the inherent variability of interactions.
@@
   \begin{figure}[h!]
-    \caption{Nested levels of uncertainty mean that an observed interaction matrix is unlikely to capture all of the interactions that occur at a site.
-Some interactions that truly occur (black squares in True matrix) are less likely than others (grey squares; lighter grey is less likely) based on species traits.
+    \caption{Nested levels of uncertainty mean that an observed interaction matrix is unlikely to capture all of the interactions that truly occur.
+Some feasible interactions (black squares in True matrix) are less likely than others (grey squares; lighter grey is less likely) based on species traits.
 For example, lions are less likely to predate upon elephants than zebras.
-If our trait model is incomplete (e.g., if we neglect group hunting in lions), we might assume that elephants are too large to ever be prey for lions and assign this interaction a probability of 0.\\
+If our trait model is incomplete (e.g., if we neglect group hunting in lions), we might assume that elephants are too large to be prey for lions and assign this interaction a probability of 0.\\
     \indent Interactions occur with different probabilities in any given sample.
@@
     \indent Not all interactions are equally detectable. For example, interactions involving cryptic species are less likely to be observed.\\
-    \indent After applying these three layers of uncertainty, some interactions which truly occur are very unlikely to be observed.
-The observed matrix (lower right) is a subsample of the true matrix, with the probability of observing each interaction is affected by multiple layers of uncertainty.
+    \indent After combining these layers of uncertainty, some interactions which truly occur are very unlikely to be observed.
+The observed matrix (bottom) is a subsample of the true matrix where the probability of observing each interaction depends upon multiple layers of uncertainty.
 Note that some low-probability interactions (e.g., lion predation on zebra) are included while others (e.g., lion predation on elephants) are not.
 For an illustration of the way in which these levels of uncertainty combine in simulated data, and the effects of uncertainty on network structure, see \emph{Appendix S1}.
-Attributions for PhyloPic silhouette images are given in \emph{Appendix S1-A}.}
+Attributions for images are given in \emph{Appendix S1-A}.}
     \label{conceptual_fig}
@@
   \begin{figure}[h!]
-      \caption{Despite the replication in our empirical dataset, most galler-natural enemy pairs were never observed co-occurring and those that did co-occur rarely interacted.
-\textbf{A)} Here we show a histogram of the number of pairs of species observed co-occurring at least once.
+      \caption{Despite the replication in our empirical dataset, most galler-natural enemy pairs were never observed co-occurring and those that co-occurred rarely interacted.
+\textbf{A)} Histogram of the number of pairs of species observed co-occurring at least once.
 9794 galler-enemy pairs were never observed co-occurring (not shown).
-      \textbf{B)} Here we show a histogram of the number of observed interactions within pairs of co-occurring species. Species which co-occurred but never interacted are included. 
-      \textbf{C)} Here we show, for each species pair, the number of observed interactions plotted against the number of observed co-occurrences.
-The red, dashed line indicates a 1:1 relationship between interactions and co-occurrences.}
+      \textbf{B)} Histogram of the number of observed interactions between co-occurring species. Species which co-occurred but never interacted are included. 
+      \textbf{C)} For each species pair, the number of observed interactions plotted against the number of observed co-occurrences. The red, dashed line indicates a 1:1 relationship.}
       \label{histograms}
@@
   \begin{figure}[h!]
-    \caption{Posterior distributions for the probability of interaction ($\lambda_{ij}$) for two species that have not been observed interacting ($k_{ij}=0$) based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017}.
+    \caption{Posterior distributions for the interaction probability ($\lambda_{ij}$) for two species that have not been observed interacting ($k_{ij}=0$), based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017}.
 Posterior distributions (curves) and 95\% credible intervals (lines at top of panel) for $\lambda_{ij}$ narrow and approach zero as the number of observed co-occurrences ($n_{ij}$) increases.
@@
 The number of samples required to obtain a 95\% credible interval below each threshold increases rapidly.
-It takes just over 20 observed co-occurrences to be 95\% confident that $\lambda_{ij}<0.10$, approximately 50 co-occurrences to be 95\% confident that $\lambda_{ij}<0.05$, and over 100 co-occurrences to be 95\% confident that $\lambda_{ij}<0.01$.}
+It takes just over 20 observed co-occurrences to be 95\% confident that $\lambda_{ij}<0.10$ but over 100 co-occurrences to be 95\% confident that $\lambda_{ij}<0.01$.}
     \label{Salix_pdfs_cdfs}

### 2019-01-17 manuscript/supplemental.tex
SI ready

@@
   \begin{figure}
-  \label{sim_props}
   \caption{We created 100 random networks containing 50 consumers and 50 resources, with a connectance of 0.1.
@@
 For each network, we show the mean (+/- SD) connectance, links per consumer, nestedness (NODF), and links per resource.}
+  \label{sim_props}
   \begin{center}
@@
 
-  \begin{table}
+  \begin{table}[h!]
   \caption{Attributions for silhouette images taken from PhyloPic.org and used in Figure 1 (\emph{main text}).
@@
           \begin{center}
-          % \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
+          \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
           % \includegraphics*[width=.8\textwidth]{Figure_3.eps}
@@
 
-    %   It is common to perform analyses that require calculating higher-order network properties in interaction networks.
+      It is common to perform analyses that require calculating higher-order network properties in interaction networks.
 The fact that the posterior distribution of $\lambda$ follows a beta distribution makes it straightforward to compute moments and other properties needed for these analyses.
 
-    %   The \textbf{average} of $\lambda$ is: 
-    %       \begin{equation}
-    %         \bar{\lambda} = \frac{\alpha+k}{\alpha+\beta+n} ,
-    %         \label{mean}
-    %       \end{equation}
+      The \textbf{average} of $\lambda$ is: 
+          \begin{equation}
+            \bar{\lambda} = \frac{\alpha+k}{\alpha+\beta+n} ,
+            \label{mean}
+          \end{equation}
 
-    %     and its \textbf{variance} is:  
-    %       \begin{equation}
-    %         Var(\lambda|k) = \frac{(\alpha + k)(\beta + n - k)}{(\alpha + \beta + n)^{2}(\alpha + \beta + n +1)}
-    %         \label{variance}
-    %       \end{equation}
+        and its \textbf{variance} is:  
+          \begin{equation}
+            Var(\lambda|k) = \frac{(\alpha + k)(\beta + n - k)}{(\alpha + \beta + n)^{2}(\alpha + \beta + n +1)}
+            \label{variance}
+          \end{equation}
 
-    %     The \textbf{mode} of the distribution is:
-    %       \begin{equation}
-    %         \hat{\lambda} = \frac{\alpha + k - 1}{\alpha + \beta + n - 2} .
-    %         \label{mode}
-    %       \end{equation}
+        The \textbf{mode} of the distribution is:
+          \begin{equation}
+            \hat{\lambda} = \frac{\alpha + k - 1}{\alpha + \beta + n - 2} .
+            \label{mode}
+          \end{equation}
 
@@
 \clearpage
+\newpage
 
@@
       \medskip
-      \begin{table}
+      \begin{table}[h!]
         \label{credints}

### 2019-01-17 manuscript/CI_interactions.tex
main text ready for co-authors

@@
 For example, lions are less likely to predate upon elephants than zebras.
-If our trait model is incomplete (e.g., if we neglect group hunting in lions), we might assume that elephants are too large to be prey for lions and assign this interaction a probability of 0.\\
+If our trait model is incomplete (e.g., if we neglect group hunting in lions), we might assume that elephants are too large to be lion prey and assign this interaction a probability of 0.\\
     \indent Interactions occur with different probabilities in any given sample.
@@
     \begin{center}
-    \includegraphics*[height=.5\textheight]{figures/conceptual_fig.eps}
+    \includegraphics*[height=.45\textheight]{figures/conceptual_fig.eps}
     % \includegraphics*[height=.5\textheight]{Figure_1.eps}

### 2019-01-17 manuscript/reply_to_reviewers.tex
reply now ready for co-authors

@@
 We therefore feel that it is important to keep some discussion of the MLE estimate in the manuscript.
-We now introduce the MLE formally within this context (lines 178-184) and take care to be explicit when using it to explore the sample size needed in the absence of prior knowledge later (caption of Figure S2, \emph{Appendix S2}}).
+We now introduce the MLE formally within this context (lines 178-184) and take care to be explicit when using it to explore the sample size needed in the absence of prior knowledge later (caption of Figure S2, \emph{Appendix S2}).
 
@@
 		\begin{quotation}
-		  \subsection*{An empirical example}
+		  \textbf{An empirical example}
 

### 2019-01-21 manuscript/reply_to_reviewers.tex
Some minor fixes to the manuscript

@@
 		\textbf{R:} We thank the Reviewer for the literature suggestions and now include them in our introduction and/or discussion.
-We emphasise the board applicability of our approach across network types and systems with varying degrees of prior knowledge.
+We emphasise the broad applicability of our approach across network types and systems with varying degrees of prior knowledge.
 We also emphasise that our approach is not restricted to species observed X times (as many predictive models are) and can include species not yet observed at a site (e.g., potential invaders).
@@
 		\textbf{R:} Nestedness being higher in the observed networks simply means that the additional interactions predicted by our model tend not to be between generalists and specialists and, as such, do not contribute strongly to nestedness.
-This is actually somewhat intuitive - ``specialists'' in the observed data are exactly those species for which we are most likely to be missing interactions, and interactions between specialists and the most likely to be predicted to occur but not have been observed.
+This is actually somewhat intuitive - ``specialists'' in the observed data are exactly those species for which we are most likely to be missing interactions, and interactions between specialists are the most likely to be predicted to occur but not have been observed.
 Due to the tight word limit, we do not have space to discuss this extensively in the manuscript but have added brief interpretations in the results.
@@
 Even worse, networks compiled under different levels of uncertainty (e.g., species with more or less variable traits, or studies with multiple sampling methods versus only one) or with different sampling efforts will have network structure metrics that are inaccurate to different degrees.
-Filtering networks in the way that we do could give an idea of how many networks are missing, but we do not think it is necessary to evaluate uncertainty (we believe that examining the posterior distributions directly is a better approach there).
+Filtering networks in the way that we do could give an idea of how many interactions are missing, but we do not think it is necessary to evaluate uncertainty (we believe that examining the posterior distributions directly is a better approach there).
 Due to length restrictions, we have moved this analysis to an appendix (\emph{Appendix S10}) and have rephrased these lines to emphasise that the filtered networks are intended to demonstrate the consequences of uncertainty more than anything else.
@@
 \citet{Gravel2018} does just this.
-We now state throughout the manuscript that we are interested in compiling the metaweb, the set of interaction which can feasibly occur.
+We now state throughout the manuscript that we are interested in compiling the metaweb, the set of interactions which can feasibly occur.
 We hope that our goal is now crystal clear.

### 2019-01-21 manuscript/CI_interactions.tex
Some minor fixes to the manuscript

@@
     The basis of a Bayesian approach to modelling the probability that an interaction between species $i$ and $j$ occurs ($\lambda_{ij}$) is combining the maximum likelihood estimate (MLE) of $\lambda_{ij}$ with a prior distribution (described in the next section) and a normalising function.
-The MLE of $\lambda_{ij}$ can be computed from the number of observed interactions $k_ij$ and observed co-occurrences $n_{ij}$: $\lambda_{ij}=\frac{k_{ij}}{n_{ij}}$.
+The MLE of $\lambda_{ij}$ can be computed from the number of observed interactions $k_{ij}$ and observed co-occurrences $n_{ij}$: $\lambda_{ij}=\frac{k_{ij}}{n_{ij}}$.
 The most appropriate prior distribution for $\lambda_{ij}$ is the beta distribution:
@@
   We obtained prior parameters of $\alpha_{ij}$=0.700, $\beta_{ij}$=8.49, giving a beta distribution strongly skewed towards 0.
-Where $n=0$, these parameters gave a posterior distribution with $\bar\lambda$=0.076, var($\lambda_{ij}$)=0.008.
+Where $n=0$, these parameters gave a posterior distribution with $\bar\lambda_{ij}$=0.076, var($\lambda_{ij}$)=0.008.
 When $n=374$, we obtained a posterior distribution with $\bar\lambda_{ij}$=1.83 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=4.76$\times10^6$.
-This distributions is very close to 0 with small variance about $\lambda_{ij}$; if species $i$ and $j$ co-occurred 374 times without interacting, they are extremely unlikely to do so at other sites or times.
+This distribution is very close to 0 with small variance about $\lambda_{ij}$; if species $i$ and $j$ co-occurred 374 times without interacting, they are extremely unlikely to do so at other sites or times.
 

### 2019-01-22 manuscript/CI_interactions.tex
added Tomas changes

--- 2019-01-17 manuscript/CI_interactions.tex
@@
 Detection failure could happen for many reasons~\citep{Wirta2014}.
-Some sources of detection failure can be minimised (e.g., by combining multiple sampling methods~\citet{Wirta2014,Jordano2016}), but other sources are difficult to reduce.
+Some sources of detection failure can be minimised (e.g., by combining multiple sampling methods~\citep{Wirta2014,Jordano2016}), but other sources are difficult to reduce.
 For example, it may not be possible to sample some species directly due to conservation concerns~\citep{Lagrue2015}.
 The probability of detecting an interaction also depends on the duration of the interaction and its evidence, the species involved, and the individuals sampled~\citep{Wells2013,Lagrue2015,Cirtwill2016,Weinstein2017}.
-As sampling improves $D_{ij}$ should tend towards 1 but, importantly, $D_{ij}$ will vary between interactions it is very likely that some $D_{ij}<1$.
-For example, when analysing gut contents interactions involving prey with hard parts will be more detectable than interactions with quickly-digested, soft prey.
+As sampling improves $D_{ij}$ should tend towards 1 but, importantly, $D_{ij}$ will vary between interactions and it is very likely that some $D_{ij}<1$.
+For example, when analysing gut contents interactions involving prey with hard parts will be more detectable than interactions with quickly-digested, soft prey~\citep{Alberdi2018}.
 
@@
 
-    In summary, an unobserved could be unfeasible [$P(L_{ij})=0$], be feasible but not occur during sampling ($P(X_{ij}|L_{ij}=1)=0$], or be feasible and occur during sampling but not be observed [$P(D_{ij}|X_{ij}=1,L_{ij}=1)=0$].
+    In summary, an unobserved interaction could be unfeasible [$P(L_{ij})=0$], be feasible but not occur during sampling ($P(X_{ij}|L_{ij}=1)=0$], or be feasible and occur during sampling but not be observed [$P(D_{ij}|X_{ij}=1,L_{ij}=1)=0$].
 Researchers might be interested in identifying feasible interactions (i.e., reducing uncertainty about $\lambda_{ij}$) or identifying feasible interactions that occurred locally (i.e., reducing uncertainty about $\chi_{ij}$).
@@
 
-\section*{Materials and methods}
+\section*{Approach}
 
@@
 For example, if the focal system is large and contains a diverse array of species, it would be inappropriate to use a prior distribution drawn from a small network describing closely-related taxa (demonstrated in \emph{Appendix S7}).
-Similarly, highly-aggregated networks containing nodes which represent whole classes or families are likely to have very different structures than networks where most nodes represent single species as aggregated nodes are likely to have more interaction partners than single species.
+Similarly, data from a network where nodes are resolved to different taxonomic levels than the focal network are likely to have quite different properties and would not be an appropriate prior.
 
@@
 
-  \subsection*{An empirical example}
+  \section*{An empirical example}
 
@@
 
-\section*{Results}
+\subsection*{Empirical results}
 
@@
   \begin{figure}[h!]
-      \caption{Despite the replication in our empirical dataset, most galler-natural enemy pairs were never observed co-occurring and those that co-occurred rarely interacted.
+      \caption{Despite the high replication in our empirical dataset, most galler-natural enemy pairs were never observed co-occurring and those that co-occurred rarely interacted.
 \textbf{A)} Histogram of the number of pairs of species observed co-occurring at least once.

### 2019-01-22 manuscript/supplemental.tex
added Tomas and Kate comments to SI

@@
 
-  To demonstrate the effects of nested interaction, process, and detection uncertainty on network structure, we can observe how the structure of randomly-generated networks changes as we add layers of uncertainty.
+  To demonstrate the effects of nested interaction, process, and detection uncertainty on network structure (see Fig.
+1, main text), we can observe how the structure of randomly-generated networks changes as we add layers of uncertainty.
 We began by constructing 100 ``true" networks with 50 consumer species, 50 resource species, and a connectance of 0.1.
@@
   Taking each ``true" network as a starting point, we then applied process uncertainty.
-The probability $p$ of the occurrence of each interaction on a given sampling day was assigned a random probability drawn from the uniform distribution.
+The probability $p_{ij}$ of the occurrence of each interaction on a given sampling day was assigned a random probability drawn from the uniform distribution.
 As the probability that an interaction will occur during sampling also depends on the probability of the two species co-occurring, we also assigned a random number of sampling days on which each species co-occurred.
-The number of co-occurrences, $n$, was drawn from a uniform distribution and could be any integer between 0 and 30 (our simulated number of sampling days), inclusive.
-The number of occurrences, $k$, of each interaction was then drawn from a binomial distribution based on $n$ and $p$.
+The number of co-occurrences, $n_{ij}$, was drawn from a uniform distribution and could be any integer between 0 and 30 (our simulated number of sampling days), inclusive.
+The number of occurrences, $k_{ij}$, of each interaction was then drawn from a binomial distribution based on $n_{ij}$ and $p_{ij}$.
 If the number of occurrences during sampling was greater than 0 and the interaction occurred in the true network, we included the interaction in the ``process-filtered" network.
@@
   Next, we applied a layer of detection uncertainty to create ``detection-filtered" networks.
-As with the process-filtered networks, we randomly selected the number of times each species co-occurred, $n$, from a uniform distribution.
+As with the process-filtered networks, we randomly selected the number of times each species co-occurred, $n_{ij}$, from a uniform distribution.
 We also randomly selected the probability, $p$, of detecting each interaction.
@@
 A single observed network drawn from these detection-filtered webs might well have a higher nestedness than the ``true" network.
-This simulation demonstrates the fact that process and detection uncertainty mean that we are very unlikely to observe all of the interactions that can truly occur in a system, as well as the sometimes unpredictable effects this uncertainty can have on higher-order structures such as nestedness.
+This simulation demonstrates the fact that process and detection uncertainty mean that we are very unlikely to observe all of the interactions that can truly occur in a system.
+It also highlights the sometimes unpredictable effects that this uncertainty can have on higher-order structures such as nestedness.
 
@@
 
-        The absence of an interaction on a given day could be because it was not feasible [$P(L_{ij}) = 0$], was feasible but did not occur because of local conditions during sampling ($P(X_{ij}|L_{ij} = 1) = 0$], or was feasible and occurred during sampling but could not be observed [$P(D_{ij}|X_{ij} = 1,L_{ij} = 1) = 0$].
-Note that some exteral factors can affect more than one level of uncertainty.
+        The absence of an interaction on a given day could be because it was not feasible [$P(L_{ij}) = 0$], was feasible but did not occur because of local conditions during sampling [($P(X_{ij}|L_{ij} = 1) = 0$], or was feasible and occurred during sampling but could not be observed [$P(D_{ij}|X_{ij} = 1,L_{ij} = 1) = 0$].
+Note that some external factors can affect more than one level of uncertainty.
 For example, rare species are less likely to interact at a given site due to neutral processes~\citep{Jordano2016,Graham2018}.
@@
           \caption{Imperfect detection of interactions increases the number of samples required to be confident that an interaction never occurs.
-Assume that two species cannot interact (i.e., $\lambda=0$) and that the number of observed interactions follows a binomial distribution depending upon the number of observed interactions $k$ and observed co-occurrances $n$.
-The maximum likelihood estimate (MLE) for $\lambda_{ij}$ is $\lambda_{MLE}=\frac{k}{n}$.
+Assume that two species $i$ and $j$ cannot interact (i.e., $\lambda_{ij}=0$) and that the number of observed interactions follows a binomial distribution depending upon the number of observed interactions $k_{ij}$ and observed co-occurrances $n_{ij}$.
+The maximum likelihood estimate (MLE) for $\lambda_{ij}$ is $\lambda_{ij,MLE}=\frac{k_{ij}}{n_{ij}}$.
 Note that $\lambda_{ij}$ is not a point estimate but rather a random variable with an unknown distribution.
-This means that if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact.
-Rather, $k = 0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless some chance that the two species \emph{could} interact.\\
+This means that if $k_{ij}=0$ in a given sample, this does not necessarily imply that the two species will never interact.
+Rather, $k_{ij}=0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless some chance that the two species \emph{could} interact.\\
           Importantly, we can estimate the variance of $\lambda_{ij}$ as well as the MLE; available methods include the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]).
 The distribution of the MLE for $\lambda_{ij}$ thus obtained is a key part of the Bayesian distribution for $\lambda_{ij}$.
-          Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true credible interval for the interaction probability $\lambda_{ij}$ for a pair of species that has been observed co-occurring $n$ times but never interacting ($k = 0$).
+          Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true credible interval for the interaction probability $\lambda_{ij}$ for a pair of species that has been observed co-occurring $n_{ij}$ times but never interacting ($k_{ij}=0$).
 The upper limit of the credible interval only reaches 0.1 (dashed, red line) with 35 observations.
@@
     We start by considering how to naively quantify an interaction probability and its associated uncertainty \emph{for an interaction that has not yet been observed}.
-Consider the case where a pair of species have been observed co-occurring $n$ times, of which they have been observed to interact in $k = 0$ cases.
+Consider the case where a pair of species have been observed co-occurring $n_{ij}$ times, of which they have been observed to interact in $k_{ij}= 0$ cases.
 To evaluate the uncertainty of this interaction, consider the occurrence of an interaction as a Bernoulli trial.
-In this framework, the number of successes $k$ over $n$ trials will follow a binomial distribution:
+In this framework, the number of successes $k_{ij}$ over $n_{ij}$ trials will follow a binomial distribution:
 
@@
 
-    \noindent The parameter $\lambda$, the probability of observing an interaction over an infinite time interval and area, is the quantity we want to estimate from empirical data. 
-    The maximal likelihood estimate (MLE) of $\lambda$ is straightforward to find given $k$ and $n$:
+    \noindent The parameter $\lambda_{ij}$, the probability of observing an interaction over an infinite time interval and area, is the quantity we want to estimate from empirical data. 
+    The maximal likelihood estimate (MLE) of $\lambda_{ij}$ is straightforward to find given $k_{ij}$ and $n_{ij}$:
 
@@
 
-    Here we adopt a Bayesian approach to estimate the posterior distribution of the parameter $\lambda$ :
+    Here we adopt a Bayesian approach to estimate the posterior distribution of the parameter $\lambda_{ij}$ :
 
@@
     According to the above description, the likelihood is simply the binomial distribution (Eq.~\ref{likelihood}).
-Since $\lambda$ is a probability, it is bounded between 0 and 1 and the most appropriate prior distribution is the beta:
+Since $\lambda_{ij}$ is a probability, it is bounded between 0 and 1 and the most appropriate prior distribution is the beta:
 
@@
 This allows us to analytically compute the posterior distribution of a binomial model with a beta prior distribution.
-We can re-write the posterior distribution of $\lambda$ as:
+We can re-write the posterior distribution of $\lambda_{ij}$ as:
 
@@
     \noindent where the function $B$ is the beta function.
-The posterior distribution of $\lambda$ therefore follows the beta distribution with new parameters $\alpha'= \alpha+k$ and $\beta'=\beta+n-k$.
+The posterior distribution of $\lambda_{ij}$ therefore follows the beta distribution with new parameters $\alpha'= \alpha+k$ and $\beta'=\beta+n-k$.
 
-    For interactions which were observed in at least one site ($k$\textgreater$0$), we can set the poseterior probability to 1 as long as the risk of a false positive is low.
+    For interactions which were observed in at least one site ($k_{ij}$\textgreater$0$), we can set the poseterior probability to 1 as long as the risk of a false positive is low.
 That is, when constructing a metaweb we can assume that an interaction observed at least once is truly feasible.
 The case study presented in the main text refers to a plant-galler network compiled by rearing galling insects obtained from galls; in each case, the plant-galler interaction definitely occurred and we are confident in the identification of both species involved (see \emph{Appendix S4} for details).
-Where the risk of false positives is higher (e.g., plant-pollinator networks where an observed flower visitor may not actually provide a pollination service), it may not be appropriate to assume $\lambda=$ wherever $k$\textgreater$0$.
+Where the risk of false positives is higher (e.g., plant-pollinator networks where an observed flower visitor may not actually provide a pollination service), it may not be appropriate to assume $\lambda_{ij}=0$ wherever $k_{ij}$\textgreater$0$.
 In such cases, we can model the posterior probabilities of observed interactions just as we do those that were not observed.
@@
       It is common to perform analyses that require calculating higher-order network properties in interaction networks.
-The fact that the posterior distribution of $\lambda$ follows a beta distribution makes it straightforward to compute moments and other properties needed for these analyses.
+The fact that the posterior distribution of $\lambda_{ij}$ follows a beta distribution makes it straightforward to compute moments and other properties needed for these analyses.
 
-      The \textbf{average} of $\lambda$ is: 
+      The \textbf{average} of $\lambda_{ij}$ is: 
           \begin{equation}
@@
       The Bayesian framework can be illustrated with a simple quantitative example.
-Suppose we have $n = 10$ observations of co-occurrence between species $i$ and species $j$ in a given time interval and area, and $k = 3$ observations of interactions.
-The maximum likelihood estimate of the interaction probability is simply $\lambda_{MLE} = 3/10 = 0.3$.
+Suppose we have $n_{ij}=10$ observations of co-occurrence between species $i$ and species $j$ in a given time interval and area, and $k_{ij}=3$ observations of interactions.
+The maximum likelihood estimate of the interaction probability is simply $\lambda_{ij,MLE} = 3/10 = 0.3$.
 
@@
 
-        The mean of these interaction probabilities is 0.176, approximately two-thirds the $\lambda_{MLE}$ obtained from the observed data.
-We can use the distribution of these interaction probabilities as our prior distribution and estimate the uncertainty surrounding our $\lambda_{MLE}$.
+        The mean of these interaction probabilities is 0.176, approximately two-thirds the $\lambda_{ij,MLE}$ obtained from the observed data.
+We can use the distribution of these interaction probabilities as our prior distribution and estimate the uncertainty surrounding our $\lambda_{ij,MLE}$.
 With some simple R code (function ``calculate\_parameters", \emph{Appendix S7}), we obtain prior parameters $\alpha$=0.998 and $\beta$=4.63.
-Using these priors in equations~\ref{mean} and~\ref{variance} above (or in the R function ``calculate\_distribution" in \emph{Appendix S7}), we find a prior $\bar\lambda$=0.177 and var($\lambda$)=0.026.
-Adding the observed data ($n=10$, $k=3$) and using the same code, we obtain posterior parameters $\alpha'$=4.00 and $\beta'$=11.6 and a posterior $\bar\lambda$=0.256 and var($\lambda$)=0.012.
+Using these priors in equations~\ref{mean} and~\ref{variance} above (or in the R function ``calculate\_distribution" in \emph{Appendix S7}), we find a prior $\bar\lambda_{ij}$=0.177 and var($\lambda_{ij}$)=0.026.
+Adding the observed data ($n_{ij}=10$, $k_{ij}=3$) and using the same code, we obtain posterior parameters $\alpha'$=4.00 and $\beta'$=11.6 and a posterior $\bar\lambda_{ij}$=0.256 and var($\lambda_{ij}$)=0.012.
 Comparing the posterior distribution to the prior, we see that the posterior is closer to the observed data and that the additional data about interactions between species $i$ and $j$ has reduced the variance.
@@
 This is also quite straightforward in R (see function ``credible\_interval" in \emph{Appendix S7}).
-In this case, a 95\% credible interval for $\bar\lambda$ is (0.080, 0.491).
+In this case, a 95\% credible interval for $\bar\lambda_{ij}$ is (0.080, 0.491).
 
-        Now, consider the case where the two species have never been observed interacting across $n$ trials, i-e.
-$k=0$.
+        Now, consider the case where the two species have never been observed interacting across $n_{ij}$ trials, i-e.
+$k_{ij}=0$.
 The question is then ``what is the probability that these two species do not interact''?
-Since it is not possible to prove that the two species could never interact (strictly speaking, in a Bayesian approach $\lambda=0$ is impossible), we must fix a threshold below which we consider that there is no interaction ($\lambda \sim 0$).
-We call this threshold probability $\lambda*$.
-We then use the cumulative distribution function to estimate $P(\lambda<\lambda*|L=0,n)$ for different $n$.
-The function ``samples\_for\_threshold" in \emph{Appendix S7} calculates distribution function for $\lambda*$ with an increasing number of trials.
-This yields a surprising result: it requires \textgreater24 observations of no interactions to be 95\% sure that the interaction probability is smaller than $\lambda*$=0.1 (recall Fig.~\ref{upper_limits}, Box 2).
-Note the special case where there is no observation of the two species co-occurring, $n = 0$.
+Since it is not possible to prove that the two species could never interact (strictly speaking, in a Bayesian approach $\lambda_{ij}=0$ is impossible), we must fix a threshold below which we consider that there is no interaction ($\lambda_{ij}\sim0$).
+We call this threshold probability $\lambda_{ij}*$.
+We then use the cumulative distribution function to estimate $P(\lambda_{ij}<\lambda_{ij}*|L=0,n)$ for different $n_{ij}$.
+The function ``samples\_for\_threshold" in \emph{Appendix S7} calculates distribution function for $\lambda_{ij}*$ with an increasing number of trials.
+This yields a surprising result: it requires \textgreater24 observations of no interactions to be 95\% sure that the interaction probability is smaller than $\lambda_{ij}*$=0.1 (recall Fig.~\ref{upper_limits}, Box 2).
+Note the special case where there is no observation of the two species co-occurring, $n_{ij}= 0$.
 In this situation, the posterior distribution converges to the prior distribution since the data include no information on the probability with which species might interact should they co-occur.
@@
 
-      As with the galler-natural enemy component (presented in the main text), we estimated frequencies of \emph{Salix}-galler interactions based on the normalised degree of each species (\emph{Appendix S6}).
+      As with the galler-natural enemy component (presented in the main text), we estimated frequencies of \emph{Salix}-galler interactions based on the normalised degree of each species.
 We obtained prior parameters of $\alpha$=8.72, $\beta$=305 for the \emph{Salix}-galler component.
@@
 
-      For species where $n=0$ (3,986/4,992 \emph{Salix}-galler pairs in our dataset), estimates for the mean and variance of $\lambda_{ij}$ can be calculated directly from the prior distribution (\emph{Appendix S6}).
-For the \emph{Salix}-galler network, these parameters were: $\bar\lambda$=0.028, var($\lambda$)=8.60$\times$10$^{-5}$; note that this mean is much lower than that obtained using a prior based on~\citet[Data available from the Dryad Digital Repository: https://doi.org/10.5061/dryad.g7805]{Barbour2016}.
+      For species where $n_{ij}=0$ (3,986/4,992 \emph{Salix}-galler pairs in our dataset), estimates for the mean and variance of $\lambda_{ij}$ can be calculated directly from the prior distribution.
+For the \emph{Salix}-galler network, these parameters were: $\bar\lambda_{ij}$=0.028, var($\lambda_{ij}$)=8.60$\times$10$^{-5}$; note that this mean is much lower than that obtained using a prior based on~\citet[Data available from the Dryad Digital Repository: https://doi.org/10.5061/dryad.g7805]{Barbour2016}.
 Note that, despite the intensive sampling in the~\ref{Kopelke2017} dataset, most \emph{Salix}-galler pairs were never observed co-occurring (3,986/4,992; Fig.~\ref{histograms}).
@@
 
-      For species with $n>0$, the posterior distribution will depend on the values of $n$ and $k$.
-Here we are interested only in cases where $k = 0$.
+      For species with $n_{ij}>0$, the posterior distribution will depend on the values of $n_{ij}$ and $k_{ij}$.
+Here we are interested only in cases where $k_{ij}=0$.
 This gives $\alpha'$=$\alpha$ and $\beta'$=$\beta + n_{ij}$.
 For a pair of species which co-occurred at all 374 sites and was never observed to interact, the distribution for the \emph{Salix}-galler network would become $\bar\lambda_{ij}$=1.27 $\times$ 10$^{-2}$, var($\lambda_{ij}$)=1.82 $\times$ 10$^{-5}$.
-As $n$ decreases, the distribution widens and moves away from the origin (Fig.~\ref{Salix_pdfs}).
-The 95\% credible interval for hypothetical \emph{Salix}-galler pairs widened from (0.006, 0.022) if the pair co-occurred at all sites to (0.013, 0.049) if they co-occurred at none (Table~\ref{credints}).
+As $n_{ij}$ decreases, the distribution widens and moves away from the origin (Fig.~\ref{Salix_pdfs}).
+The 95\% credible interval for hypothetical \emph{Salix}-galler pairs widened from (0.006, 0.022) if the pair co-occurred at all sites to (0.013, 0.049) if they co-occurred at none (Table~\ref{credints}, \empH{Appendix S11}).
 
       \begin{figure}[h!]
-        \caption{Using prior distributions based on the \emph{Salix}-galler network sampled at a single site in~\citet{Kopelke2017}, we can calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting.
-Here we show posterior distributions for $\lambda$ ranging from the prior distribution ($n=0$ observed co-occurrence) to the distribution obtained when the pair of species has been observed co-occurring 100 times.
+        \caption{Using prior distributions based on the \emph{Salix}-galler network sampled at a single site in~\citet{Kopelke2017}, we can calculate posterior distributions for the probability of interaction ($\lambda_{ij}$) between two species $i$ and $j$ that have not yet been observed interacting.
+Here we show posterior distributions for $\lambda_{ij}$ ranging from the prior distribution ($n_{ij}=0$ observed co-occurrence) to the distribution obtained when the pair of species has been observed co-occurring 100 times.
 The distribution narrows and approaches zero as the sample size increases.
@@
 We then calculated prior distributions using these parameters.
-For the \emph{Salix}-galler network, the prior distribution was: $\bar\lambda$=0.570, var($\lambda$)=0.056.
-The prior distribution for the galler-natural enemy network was: $\bar\lambda$=0.124, var($\lambda$)=0.010.
+For the \emph{Salix}-galler network, the prior distribution was: $\bar\lambda_{ij}$=0.570, var($\lambda_{ij}$)=0.056.
+The prior distribution for the galler-natural enemy network was: $\bar\lambda_{ij}$=0.124, var($\lambda_{ij}$)=0.010.
 As with the results in the main text, we can update this prior distribution using observed co-occurrences.
@@
       \begin{figure}[h!]
-        \caption{Using prior distribution based on the \emph{Salix}-galler and galler-natural enemy networks in~\citet{Barbour2016}, we can calculate posterior distributions for the probability of interaction ($\lambda$) between two species that have not yet been observed interacting.
-Here we show posterior distributions for each $\lambda$ in each network ranging from the prior distribution ($n=0$ observed co-occurrence) to the distribution obtained when the pair of species has been observed co-occurring 100 times.
+        \caption{Using prior distribution based on the \emph{Salix}-galler and galler-natural enemy networks in~\citet{Barbour2016}, we can calculate posterior distributions for the probability of interaction ($\lambda_{ij}$) between two species that have not yet been observed interacting.
+Here we show posterior distributions for each $\lambda_{ij}$ in each network ranging from the prior distribution ($n_{ij}=0$ observed co-occurrence) to the distribution obtained when the pair of species has been observed co-occurring 100 times.
 The distribution narrows and approaches zero as the sample size increases.
@@
 In the galler-natural enemy network, the credible interval for a pair of species with no observed co-occurrences was 0.364.
-All pairs of species therefore have $\lambda$\textless0.5.}
+All pairs of species therefore have $\lambda_{ij}$\textless0.5.}
         \label{Salix_cdfs}
@@
   Priordata is the list of interaction frequencies from the prior 
-  data, $n$ is the number of sites with observed co-occurrence of 
-  species $i$ and $j$, and $k$ is the number of sites with an 
+  data, $n_{ij}$ is the number of sites with observed co-occurrence of 
+  species $i$ and $j$, and $k_{ij}$ is the number of sites with an 
   observed interaction $ij$. When calculating the prior 
-  distribution, both $n$ and $k$ are 0. In the main text we assume 100\%
+  distribution, both $n_{ij}$ and $k_{ij}$ are 0. In the main text we assume 100\%
   confidence in observed interactions and therefore consider only 
-  cases where $k$=0. Only $n$ varies between species pairs.
+  cases where $k_{ij}=0$. Only $n_{ij}$ varies between species pairs.
 
@@
 
-  Here we describe the derivation of the Clopper-Pearson credible interval for the estimated probability of interaction $\lambda$ of a pair of species observed co-occurring $n$ times and interacting $k$ times.
-As we are most interested in the probability of interaction between species pairs that have never been observed co-occurring, we consider only the case where $k=0$ over a variety of $n$.
+  Here we describe the derivation of the Clopper-Pearson credible interval for the estimated probability of interaction $\lambda_{ij}$ of a pair of species observed co-occurring $n_{ij}$ times and interacting $k_{ij}$ times.
+As we are most interested in the probability of interaction between species pairs that have never been observed co-occurring, we consider only the case where $k_{ij}=0$ over a variety of $n_{ij}$.
 This is straightforward to do in R (see the function ``credible\_interval" in \emph{Appendix S7}).
@@
 These parameters can then be used to calculate a credible interval using the R~\citep{R} function qbeta.
-In the table below, we present the 95\% credible intervals for \emph{Salix}-galler and galler-natural enemy pairs with different numbers of observed co-occurrences ($n$) and no observed interactions ($k=0$), calculated using prior information derived from the Zillis sub-network~\citep{Kopelke2017}.
+In the table below, we present the 95\% credible intervals for \emph{Salix}-galler and galler-natural enemy pairs with different numbers of observed co-occurrences ($n_{ij}$) and no observed interactions ($k_{ij}=0$), calculated using prior information derived from the Zillis sub-network~\citep{Kopelke2017}.
 
@@
       \begin{table}[h!]
+        \caption{Here we give the lower and upper bounds of 95\% credible intervals for the probability of interaction $\lambda_{ij}$ between \emph{Salix}-galler or galler-natural enemy pairs that have been observed co-occurring $n_{ij}$ times but have never been observed interacting.}
         \label{credints}
-        \caption{Here we give the lower and upper bounds of 95\% credible intervals for the probability of interaction $\lambda$ between \emph{Salix}-galler or galler-natural enemy pairs that have been observed co-occurring $n$ times but have never been observed interacting.}
         \begin{tabular}{l  c c  c c }
-        \multirow{2}{*}{$n$} & \multicolumn{2}{c}{\emph{Salix}-galler} & \multicolumn{2}{c}{galler-natural enemy}\\
+        \multirow{2}{*}{$n_{ij}$} & \multicolumn{2}{c}{\emph{Salix}-galler} & \multicolumn{2}{c}{galler-natural enemy}\\
          & Lower bound & Upper bound & Lower bound & Upper bound \\

### 2019-01-22 manuscript/reply_to_reviewers.tex
all comments from Tomas, Kate, Anna integrated and back under word count

@@
 Thus, the novelty and impact of our work explicitly lies in connecting a Bayesian statistical approach to the problem of limited and uneven sampling of networks (driven by difference in species abundances, detectabilities, constrained time and budgets, etc.) and, we hope, in making this method more accessible to those without extensive statistical or modelling experience.
-Please note that Reviewer 3 identified this need explicitly.
+Moreover, we believe that introducing a more coherent framework for thinking about uncertainty and bringing some order to the myriad different causes behind it are also valuable contributions (with the proviso that our ``levels" of uncertainty are a conceptual guide rather than a rigorously-tested breakdown).
+Please note that Reviewer 3 identified the need for a coherent, general approach to uncertainty explicitly, and several of the reviewers appreciated our partial formalisation.
 	% Tomas has a line break here, I'm not sure.
@@
 There are, as the Reviewer notes, already a number of publications addressing probabilistic interactions, but none of them adequately characterise uncertainty about interactions.
-We hope that the contribution our manuscript makes is now clearer.
+We hope that the contribution made by our manuscript is now clearer.
 
@@
 
-		We must also point out that some of the Reviewer's questions (e.g., how much data is necessary to expect good results) have already been answered analytically.
+		We must also point out that some of the Reviewer's questions (e.g., how much data is necessary to expect good results) are answered analytically in our manuscript.
 Without an informative prior, we need approximately 35 observed co-occurrences with no observed interaction to be 95\% confident that the interaction does not occur.
@@
 				\item As described above, we have now indexed $L$, $T$, $X$, $D$, etc. by $ij$. 
-				\item $T$ describes trait matching, so it is a characterisation on $i$ and $j$ together. 
+				\item $T$ describes trait matching, so it is a characterisation of $i$ and $j$ together. 
 				\item $D$ can be \textless1 because some interactions are detectable but with a lower probability due to limitations in sampling techniques, sampling time, etc.
@@
 The interaction with prey B is does not have D=0, because the interaction might be observed directly or through examination of gut contents very soon after B was consumed, but we cannot say that D=1 because we are quite likely not to detect this interaction in any given sample.
-				\item Using L to mean the number of interactions is incredibly common in the food-web literature, especially when defining connectance (as in the instance the Reviewer points out - now included in the main text).
+				\item Using L to mean the number of interactions is common in the food-web literature, especially when defining connectance (as in the instance the Reviewer points out - now included in the main text).
 That said, we appreciate that this useage may confuse mathematicians.
@@
 % ----------------------------------------------------------------------
-{\Large \bf Reply to Referee \#3}
+{\Large \bf Reply to Reviewer \#3}
 % ---------------------------------------
@@
 We are also sure that this is a common approach and therefore hadn't cited it (in the same way one would not be likely to cite the prior users of common statistical tests).
-We have added a citation to~\citet{Vazquez2005,Guimera2009} as two examples and hope that this is sufficient.
+We have now added a citation to~\citet{Vazquez2005,Guimera2009} as two examples and hope that this is sufficient.
 
@@
 
-            Both whether species can ever interact and Both whether species can ever interact and whether they interact at a particular place and time have been discussed in the context of ``forbidden links"~\citep{Jordano2016}.
+            Both whether species can ever interact and whether they interact at a particular place and time have been discussed in the context of ``forbidden links"~\citep{Jordano2016}.
 In this framework, all links which are prevented by spatio-temporal uncoupling, physiological constraints, etc.
@@
 
-		\textbf{R:} We have expanded our introduction of the case study (beginning line 302) to make it clear that we are using the highest-quality empirical network we can find as even such networks have uncertainty about unobserved interactions.
+		\textbf{R:} We have now expanded our introduction of the case study (beginning line 302) to make it clear that we are using the highest-quality empirical network we can find as even such networks have uncertainty about unobserved interactions.
 This relates back to our point that urging increased sampling effort is not likely to solve problems of uncertainty as long as sampling is limited in the number of methodologies that can be applied, biased towards abundant or easy-to-identify species, restricted to particular spatial sites and/or environmental conditions (if the network is intended to be more general), or all of the above.
@@
 
-		\textbf{R:} The point of our method is not actually to quantify the amount of sampling needed.
+		\textbf{R:} 
+		We emphasise that the estimate of 30-50 samples does not refer to the \emph{Salix}-galler-natural enemy test system but to a much more general interpretation of the problem.
+Without a prior distribution and with \emph{no prior information}, as long as we assume that interaction probabilities follow a beta distribution it will take 30-50 observations of two species co-occurring to be 95-99\% confident that the species do not interact.
+Sampling requirements will be much less if an interaction was observed (note that in the empirical example we assume an interaction was feasible if it was observed even once).
+
+		The point of our method is not actually to quantify the amount of sampling needed.
 Although the ideal sampling effort \emph{can} be calculated using the framework we put forward (as we demonstrate), the real point is to quantify how uncertain we are that an interaction we do not observe really does not occur.
@@
 
-		Finally, we emphasise that the estimate of 30-50 samples does not refer to the \emph{Salix}-galler-natural enemy test system but to a much more general interpretation of the problem.
-Without a prior distribution and with \emph{no prior information}, as long as we assume that interaction probabilities follow a beta distribution it will take 30-50 observations of two species co-occurring to be 95-99\% confident that the species do not interact.
-Sampling requirements will be much less if an interaction was observed (note that in the empirical example we assume an interaction was feasible if it was observed even once).
-
 \clearpage
@@
 % ----------------------------------------------------------------------
-{\Large \bf Reply to Referee \#4}
+{\Large \bf Reply to Reviewer \#4}
 % ---------------------------------------
@@
 
-		To make this clearer, we have rephrased this section and added a line (lines 65-72) stating that we usually cannot determine the cause of all the zeros in an interaction matrix (we can identify obviously unfeasible interactions, but likely cannot say whether a zero for a rare species is because we did not observe enough individuals, there were not enough individuals to perform a particular interaction, or because the interaction is actually unfeasible).
+		To make this clearer, we have rephrased this section and added a line (lines 65-72) stating that we usually cannot determine the cause of all the zeros in an interaction matrix (we can identify obviously unfeasible interactions, but likely cannot say whether a zero for a rare species is because we did not observe enough individuals, there were not enough individuals to engage in a particular interaction, or because the interaction is actually unfeasible).
 We hope that this revision makes it clearer that the description of different sources of uncertainty is a conceptual guide only.
@@
 		\textbf{R:} As our manuscript is not concerned with partitioning sources of uncertainty, we felt it was unproductive to get bogged down in a debate over the precise definitions of process vs.
-interaction uncertainty and which external influences might contribute to which sources (there is enough overlap that simple statements such as ``bad weather increases process uncertainty'' are, at best, incomplete).
+interaction uncertainty and which external influences might contribute to which sources (there is enough overlap that simple statements such as ``bad weather increases process uncertainty'' are, at best, incomplete); see above under response to Reviewer 3 for more details.
 To remove this problem, we have rephrased the introduction and discussion to refer to the questions of whether two species \emph{can} interact under ideal conditions and whether they \emph{do} interact at a given site and time.
@@
 As sampling time increases toward infinity, interaction probabilities should converge to 0 or 1 with no uncertainty.
-As we discuss, however, sampling times are limited by resources, the trade-off between sampling a single site intensively versus many sites, etc.
+As we discuss, however, sampling times are limited by resources, by the trade-off between sampling a single site intensively versus many sites, etc.
 Any interaction could therefore occur outside of the sampling window and hence be missed.

### 2019-01-22 manuscript/CI_interactions.tex
all comments from Tomas, Kate, Anna integrated and back under word count

@@
 % \item Abstract word count: 290
-% \item Main text word count: 6995, excluding abstract % Limit is 6000-7000 including figs, tables, references. 
+% \item Main text word count: 6993, excluding abstract % Limit is 6000-7000 including figs, tables, references. 
 % \end{itemize}
@@
 
-        In most cases, we have some prior knowledge which we can use to inform uncertainty about interactions.
-One common example is the well-justified assumption that plants will not consume animals in a food web; excluding carnivorous plants it is not contentious to say that we are certain that unobserved links indicating plants feeding on animals truly do not occur.
+        We often have some prior knowledge which can inform uncertainty about interactions.
+One common example is the well-justified assumption that plants never consume animals in a food web; excluding carnivorous plants it is not contentious to say that we are certain that unobserved links indicating plants feeding on animals truly do not occur.
 Similarly, if we observed two species which are normally obligate mutualists co-occurring but not interacting, we would be very doubtful that a zero reflecting this interaction was true (i.e., high uncertainty about this zero).
@@
 
-        Using an informative prior like these tailors the level of uncertainty surrounding each interaction and may account for non-independence of interactions (as in abundance-based or KNN models).
+        Using an informative prior tailors the level of uncertainty surrounding each interaction and may account for non-independence of interactions (as in abundance-based or KNN models).
 Despite these benefits, informative priors often involve many assumptions and carry a risk of over-fitting.
@@
 
-        Alternatively, once can develop a prior based on the properties of a set of published networks (i.e., ``empirical" or ``reference Bayes"~\citet{Spiegelhalter2000}).
-While this type of prior does not allow for the prior distribution to vary, it relies on only one assumption: that the focal network will have similar structural properties to those of published networks.
+        Alternatively, one can develop a prior based on the properties of a set of published networks (i.e., ``empirical" or ``reference Bayes"~\citet{Spiegelhalter2000}).
+This type of prior entails only one assumption: that the focal network has similar structural properties to those of published networks.
 For example, connectance ($C=N/S^2$, where $N$ is the number of interactions and $S$ is the number of species) is available for many networks.
-The distribution of these connectances can be used to predict the distribution of interaction probabilities in a new network.
+The distribution of published connectances can be used to predict the distribution of interaction probabilities in a new network.
 If we know the mean $\overline{C}$ and variance $\sigma_C^2$ of a distribution of connectances, then the hyperparameters are:
@@
 
-        Note that, in this case, the prior distribution will be the same for all interaction probabilities.
+        Note that here the prior distribution will be the same for all interaction probabilities.
 It is also possible to interpret other network properties (e.g., species degrees) in a similar network(s) as interaction probabilities and use these to create a prior (worked example in \emph{Appendix S4}).
@@
 Finally, we may be interested in measures of network structure rather than the network itself.
-We can use the posterior distributions of interactions to generate a suite of plausible ``true'' networks that would be obtained if sampling uncertainty could be eliminated and use these networks to estimate many network properties (worked example in \emph{Appendix S10}).
+We can use posterior distributions of interactions to generate plausible ``true'' networks that would be obtained if sampling uncertainty could be eliminated and use these networks to estimate many network properties (worked example in \emph{Appendix S10}).
 
@@
   Although 374 sampling sites were not enough to obtain sufficient observations of all species pairs, we were able to reduce uncertainty about many potential interactions using a simple Bayesian framework.
-This framework allowed us to set confidence intervals about the probability of an unobserved interaction occurring, based on the distribution of interactions in one sample site.
+This framework allowed us to set confidence intervals about the probability of an unobserved interaction occurring based on the distribution of interactions in one ``pilot'' site.
 This gives us more reasonable estimates of interaction probabilities than assuming that no unobserved interactions actually occur.
-Such an approach is particularly useful when considering interactions involving species entering new ranges due to climate change or introductions.
+Such approaches are particularly useful when considering interactions involving species entering new ranges due to climate change or introductions.
 Understanding these species' interactions is important for a variety of conservation questions~\citep{Bartomeus2013,Gravel2013}, and a Bayesian approach using a trait-matching model or data from species' current ranges could help us to anticipate how species will integrate into new communities.
@@
 
-  We conclude with some recommendations for improved descriptions of ecological interactions.
+  We conclude with some recommendations for improving descriptions of interactions.
 While researchers are not likely to observe all interactions in a network~\citep{Jordano2016}, they can take steps to address the uncertainty this implies.

### 2019-01-22 manuscript/supplemental.tex
fixed one compilation error

@@
 As $n_{ij}$ decreases, the distribution widens and moves away from the origin (Fig.~\ref{Salix_pdfs}).
-The 95\% credible interval for hypothetical \emph{Salix}-galler pairs widened from (0.006, 0.022) if the pair co-occurred at all sites to (0.013, 0.049) if they co-occurred at none (Table~\ref{credints}, \empH{Appendix S11}).
+The 95\% credible interval for hypothetical \emph{Salix}-galler pairs widened from (0.006, 0.022) if the pair co-occurred at all sites to (0.013, 0.049) if they co-occurred at none (Table~\ref{credints}, \emph{Appendix S11}).
 

### 2019-01-24 manuscript/reply_to_reviewers.tex
all ready to resubmit after Dom's ok

@@
 			The basis of a Bayesian approach to modelling the probability that an interaction between species $i$ and $j$ occurs ($\lambda_{ij}$) is combining the maximum likelihood estimate (MLE) of $\lambda_{ij}$ with a prior distribution (described in the next section) and a normalising function.
-The MLE of $\lambda_{ij}$ can be computed from the number of observed interactions $k_ij$ and observed co-occurrences $n_{ij}$: $\lambda_{ij}=\frac{k_{ij}}{n_{ij}}$.
-The most appropriate prior distribution for $\lambda_{ij}$ is the beta distribution ...
+The MLE of $\lambda_{ij}$ can be computed from the number of observed interactions $k_{ij}$ and observed co-occurrences $n_{ij}$: $\lambda_{ij}=\frac{k_{ij}}{n_{ij}}$.
+The most appropriate prior distribution for $\lambda_{ij}$ is the beta distribution: ...
 		\end{quotation}
@@
 
-	        Using an informative prior like these tailors the level of uncertainty surrounding each interaction and may account for non-independence of interactions (as in abundance-based or KNN models).
+	        Using an informative prior tailors the level of uncertainty surrounding each interaction and may account for non-independence of interactions (as in abundance-based or KNN models).
 	    \end{quotation}
@@
 		\begin{quotation}
-			When considering a metaweb, we wish to separate the unobserved interactions where $L_{ij}=0$ (i.e., unfeasible interactions) from interactions which were feasible but did not occur during sampling or  were not detected (Fig.
+			When considering a metaweb, we wish to separate unobserved interactions where $L_{ij}=0$ (unfeasible interactions) from interactions which were feasible but did not occur during sampling or were not detected (Fig.
 1).
@@
 		\begin{quotation}
-			As we lack a trait-based model or similar published network, we will use data from a single sub-network from the middle of the geographical distribution of the~\citet{Kopelke2017} dataset to inform our prior distribution.
+			As we lack a trait-based model or similar published network, we use data from a single sub-network from the middle of the geographical distribution of the~\citet{Kopelke2017} dataset to inform our prior distribution.
 This simulates an empirical Bayes model using a pilot site to inform the prior distribution.
-A site in the middle of the geographic distribution was chosen in order to minimise bias towards species at any geographic extreme.
+A site in the middle of the geographic distribution was selected in order to minimise bias towards species at any geographic extreme.
 		\end{quotation}
@@
 		\begin{quotation}
-		  \textbf{An empirical example}
+		  \textbf{Empirical example}
 
@@
 The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (\emph{Appendix S5}).
-		      The high spatiotemporal resolution of this dataset makes it ideal for illustrating the difficulties in completely sampling a network; even with such an unusually high sampling effort, there were many pairs of species which were rarely or never observed together and about which we therefore have high uncertainty about interaction probabilities (Fig.~\ref{histograms}).
+		      The high spatiotemporal resolution of this dataset makes it ideal for illustrating the difficulties in completely sampling a network; even with such an unusually high sampling effort, there were many pairs of species which were rarely or never observed together and about which we therefore have high uncertainty about interaction probabilities (Fig.
+2).
 Using the Bayesian framework above, we can identify which potential interactions are more and less uncertain, allowing us to better predict the true structure of the metaweb.

### 2019-01-24 manuscript/CI_interactions.tex
turned line numbers back on
all ready to resubmit after Dom's ok

@@
 
-\author{Alyssa R. Cirtwill$^{1\dagger}$, \&  Anna Ekl\"{o}f$^{1}$, Tomas Roslin$^{2}$, Kate Wootton$^{2}$, Dominique Gravel$^{3}$}
+\author{Alyssa R. Cirtwill$^{1,2\dagger}$, \&  Anna Ekl\"{o}f$^{1}$, Tomas Roslin$^{3}$, Kate Wootton$^{3}$, Dominique Gravel$^{4}$}
 \date{
@@
 \medskip
-\small$^2$ Department of Ecology\\ 
+\small$^2$ Current address: Department of Ecology,\\
+Environment, and Plant Sciences (DEEP)\\
+Stockholm University\\
+Stockholm, Sweden\\
+\medskip
+\small$^3$ Department of Ecology\\ 
 P.O. Box 7044\\ 
@@
 \medskip
-\small$^3$ D\'{e}partement de biologie\\ 
+\small$^4$ D\'{e}partement de biologie\\ 
 Universit\'{e} de Sherbrooke\\ 
@@
 % \item Abstract word count: 290
-% \item Main text word count: 6993, excluding abstract % Limit is 6000-7000 including figs, tables, references. 
+% \item Main text word count: 6997, excluding abstract % Limit is 6000-7000 including figs, tables, references. 
 % \end{itemize}
@@
           An unobserved interaction may have $\lambda_{ij}>0$, and the associated zero in an interaction matrix might be false.
-Using a trait-matching model can reduce uncertainty about $\lambda_{ij}$~\citep{Jordano2016}.
+Trait-matching models can reduce uncertainty about $\lambda_{ij}$~\citep{Jordano2016}.
 As these models improve, $\lambda_{ij}$ should either tend to 0 or to 1.
@@
 
-    When considering a metaweb, we wish to separate the unobserved interactions where $L_{ij}=0$ (i.e., unfeasible interactions) from interactions which were feasible but did not occur during sampling or  were not detected (Fig.~\ref{conceptual_fig}).
+    When considering a metaweb, we wish to separate unobserved interactions where $L_{ij}=0$ (unfeasible interactions) from interactions which were feasible but did not occur during sampling or were not detected (Fig.~\ref{conceptual_fig}).
 An empirical ecologist will measure the marginal probability $P(L_{ij})=k_{ij}/n_{ij}$, where $k_{ij}$ is the number of observed interactions between species $i$ and $j$ and $n_{ij}$ the number of observed co-occurrences.
@@
 High sample sizes will reduce uncertainty about the upper bound of $\lambda_{ij}$ and increase the probability of detecting unlikely or cryptic interactions (where $L_{ij}=1$ but $\chi_{ij}$ or $\delta_{ij}$ is low).
-In some systems, targeted sampling of particular species pairs could reduce especially high uncertainties about $\lambda_{ij}$, but this will not be possible everywhere (e.g., in host-parasitoid systems where parasitoid identities are unknown during sample collection).
+In some systems, targeted sampling could also reduce especially high uncertainties about $\lambda_{ij}$, but this will not be possible everywhere (e.g., in host-parasitoid systems where parasitoid identities are unknown during sampling).
 High-quality sampling is crucial in studies of empirical networks, but there are limits to the ability of sampling to reduce uncertainty (\emph{Appendix S2, Fig.
@@
 
-        Alternatively, one can develop a prior based on the properties of a set of published networks (i.e., ``empirical" or ``reference Bayes"~\citet{Spiegelhalter2000}).
+        Alternatively, one can develop a prior based on the properties of a set of published networks (``empirical" or ``reference Bayes"~\citet{Spiegelhalter2000}).
 This type of prior entails only one assumption: that the focal network has similar structural properties to those of published networks.
@@
 
-  \section*{An empirical example}
+  \section*{Empirical example}
 
@@
 
-        To treat each interaction as a Bayesian probability, we will combine the observed data with a distribution based on prior information.
-As we lack a trait-based model or similar published network, we will use data from a single sub-network from the middle of the geographical distribution of the~\citet{Kopelke2017} dataset to inform our prior distribution.
+        To treat each interaction as a Bayesian probability, we combine observed data with a distribution based on prior information.
+As we lack a trait-based model or similar published network, we use data from a single sub-network from the middle of the geographical distribution of the~\citet{Kopelke2017} dataset to inform our prior distribution.
 This simulates an empirical Bayes model using a pilot site to inform the prior distribution.
-A site in the middle of the geographic distribution was chosen in order to minimise bias towards species at any geographic extreme.
+A site in the middle of the geographic distribution was selected in order to minimise bias towards species at any geographic extreme.
 To demonstrate how a poor choice of prior can give unreasonable posterior distributions, we repeated our analyses using priors derived from a much smaller system (\emph{Appendix S7}).
 
-        To obtain priors, we estimated interaction frequencies based on the normalised degree of each species (see \emph{Appendix S8} for details and code).
+        To obtain priors, we estimated interaction frequencies based on the normalised degree of each species (details and code in \emph{Appendix S8}).
 Using these prior parameters, we then estimated the posterior distributions of interaction probabilities $\lambda_{ij}$.
@@
 If we consider only pairs of species which were observed co-occurring but not interacting, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs.
-This gives $\alpha_{ij}'$=$\alpha_{ij}$ and $\beta_{ij}'$=$\beta_{ij} + n_{ij}$.
+This gives $\alpha_{ij}'$=$\alpha_{ij}$ and $\beta_{ij}'$=$\beta_{ij}+n_{ij}$.
 We calculated posterior distributions and 95\% credible intervals (function ``credible\_interval";~\emph{Appendix S9}) for species with $n$ ranging between 0 and 374, the total number of sites in our dataset.
 
-        Rather than calculating credible intervals for a posterior distribution after collecting data, we may wish to know how many observations are necessary to be confident that two co-occurring species do not interact (note that the beta distribution can never equal 0 or 1).
-The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact.
+        Rather than credible intervals for a posterior distribution after collecting data, we be interested in the number of observations necessary to be confident that two co-occurring species do not interact (note that the beta distribution can never equal 0 or 1).
+The number of samples needed will depend on our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact.
 We calculated the number of samples required to reach 95\% confidence that $\lambda_{ij}$ was below thresholds of 0.1, 0.05, and 0.01 as examples (function ``samples\_for\_threshold";~\emph{Appendix S9}).
-Finally, we may be interested in measures of network structure rather than the network itself.
+Finally, we may be interested in measures of network structure.
 We can use posterior distributions of interactions to generate plausible ``true'' networks that would be obtained if sampling uncertainty could be eliminated and use these networks to estimate many network properties (worked example in \emph{Appendix S10}).
@@
     \begin{center}
-    \includegraphics*[height=.45\textheight]{figures/conceptual_fig.eps}
+    % \includegraphics*[height=.45\textheight]{figures/conceptual_fig.eps}
     % \includegraphics*[height=.5\textheight]{Figure_1.eps}

### 2019-01-24 manuscript/coverletter_revision.tex
all ready to resubmit after Dom's ok

--- 2018-07-02 manuscript/coverletter.tex
@@
 % \usepackage[britdate]{canterbury-letter}
-\usepackage[britdate]{LiU-letter}
+\usepackage[britdate]{SU-letter}
 \usepackage{times}
@@
 \position{Postdoctoral fellow}
-\department{Department of Physics, Chemistry, and Biology (IFM)}
-\location{581 83 Link\"{o}ping, Sweden}
-\cityzip{581 83 Link\"{o}ping, Sweden}
+\department{Department of Ecology, Environment, and Plant Sciences (DEEP)}
+\location{Stockholm University}
+\cityzip{Stockholm, Sweden}
 \telephone{}
@@
 
-    My co-authors and I are pleased to submit the attached manuscript \emph{A quantitative framework for investigating the reliability of empirical network construction} for consideration as a research article in \textbf{Methods in Ecology and Evolution}.
-This manuscript is aimed squarely at the audiencce of \textbf{Methods in Ecology and Evolution}: ecologists in need of new tools for addressing topical questions in ecology and for recognizing key limitations and caveats in their research.
-Thus, the goals of this manuscript are to demonstrate the extreme difficulty of observing all interactions that occur within a community and, given this difficulty, to provide a way forward: a framework for combining prior knowledge about the system with observed data in order to gauge the probability of interactions which were not observed.
-We close by offering concrete recommendations that will facilitate researchers' efforts to acknowledge and set bounds on the uncertainty inherent in ecological data.
+    My co-authors and I are pleased to resubmit our manuscript 
+    MEE-18-07-452:  \emph{A quantitative framework for investigating the reliability of empirical network construction} for consideration as a research article in \textbf{Methods in Ecology and Evolution}.
+Dr.
+Aaron Ellison, Senior Editor, noted that the Associate Editor and four reviewers ``\emph{recognise a kernel of important work in this manuscript}" but that a significant shift in emphasis was necessary for this kernel to shine through.
+We believe that this revision has addressed the Associate Editor's and Reviewers' concerns and that our manuscript is clearer and more polished as a result.
+We thank them for their careful feedback.
 
-    % We argue that, because of multiple levels of uncertainty surrounding interactions between species, the set of observed interactions will almost certainly be a subset of the interactions that can occur in a community.
-Interactions may not be observed because a species is rare and does not encounter its partner during sampling, because environmental constraints prohibit the interaction during sampling, because one or both species is difficult to observe in the field, or because the interaction truly does not occur.
-We emphasise that some of these sources of uncertainty can be reduced with increased sampling but that, because it is easier to observe species than interactions between species, increased sampling will tend to add more unobserved than observed interactions to a matrix.
-We illustrate the problem using an extensively-sampled, spatially-replicated \emph{Salix}-galler-natural enemy system (Kopelke \emph{et al.}, 2017.
-\textbf{Ecology} 98: 1730).
+    Note that we uploaded an earlier version of this manuscript to biorXiv \\(doi: \emph{https://doi.org/10.1101/332536}).
+We have uploaded a copy of this version as CI\_preprint.pdf.
+The present version has been substantially re-organised and contains additional material not included in the pre-print.
 
-    % In many cases, it will not be feasible to sample all species pairs intensively enough (tens of observations per pair) to be confident that the pair does not interact.
-Given the time and resource constraints that often restrict fieldwork, we suggest that researchers supplement observed data with prior information about the system.
-Thus, they can set bounds on the probability of interaction between species that were not observed interacting.
-We demonstrate this simple Bayesian framework, including the selection of a prior distribution, and use it to predict the likely set of feasible interactions in our example \emph{Salix} system.
-Based on this framework, we close with a set of recommendations for both empiricists and theoreticians that should improve our ability to deal with the uncertainty inherent in ecological networks and compare networks across systems.
-
-    As our central approach to this topic, we use a simple Bayesian framework.
-We are aware that there are several studies already using various forms of Bayesian networks to treat interactions as probabilities.
-These efforts are, however, generally confined to fairly theoretical work.
-We believe that empirical ecologists will find Bayesian interaction probabilities to be a useful tool when planning field sampling and when describing and analysing their focal communities.
-Our goal with this manuscript is, therefore, to introduce a Bayesian line of thought in as approachable and broadly-applicable terms as possible.
-To that end, we provide simple R code that illustrates each step of our approach.
-
-    We hope that the general nature of uncertainty around interactions, as well as the broadly-applicable solution we offer, will be of interest to the readership of \textbf{Methods in Ecology and Evolution}.
+    We appreciate the opportunity to resubmit our manuscript and thank you for your continued consideration.
+We remain confident that our manuscript will be of broad interest to the readers of \textbf{Methods in Ecology and Evolution} because of the general nature of uncertainty around interactions and the broadly-applicable solution we offer.
 We are confident that our worked example and easy-to-use scripts will provide a useful template for empiricists and theoreticians alike.

### 2019-02-18 manuscript/CI_interactions.tex
starting reply 2

@@
         Alternatively, one can develop a prior based on the properties of a set of published networks (``empirical" or ``reference Bayes"~\citet{Spiegelhalter2000}).
-This type of prior entails only one assumption: that the focal network has similar structural properties to those of published networks.
+This type of prior entails only one assumption: that the focal network has similar structural properties to those of some published networks.
 For example, connectance ($C=N/S^2$, where $N$ is the number of interactions and $S$ is the number of species) is available for many networks.
-The distribution of published connectances can be used to predict the distribution of interaction probabilities in a new network.
+The distribution of published connectances can be used to predict the distribution of interaction probabilities in a new network that is similar to those used to construct the prior (same type of interaction, similar taxonomic resolution, habitat, etc.).
 If we know the mean $\overline{C}$ and variance $\sigma_C^2$ of a distribution of connectances, then the hyperparameters are:
@@
 Similarly, data from a network where nodes are resolved to different taxonomic levels than the focal network are likely to have quite different properties and would not be an appropriate prior.
+
+        Note that if the focal network is substantially different from published networks, empirical Bayes will not give reasonable expectations about interaction probabilities in the focal network.
+[[Seems like R1 is demanding we add some more about how empirical Bayes is crap ...
+maybe we can say it'd give a reasonable expectation for the number of interactions but maybe not the right ones?]]
 
@@
 Such approaches are particularly useful when considering interactions involving species entering new ranges due to climate change or introductions.
-Understanding these species' interactions is important for a variety of conservation questions~\citep{Bartomeus2013,Gravel2013}, and a Bayesian approach using a trait-matching model or data from species' current ranges could help us to anticipate how species will integrate into new communities.
+Our framework could, for example, be used to predict the probability of interaction between a galler and parasitoid at a new site on the frontier of their ranges.
+If the species have not been observed co-occurring at other sites, we would expect them to interact with a probability of approximately 0.1 rather than assuming that they will not interact because they have not been observed interacting elsewhere (Fig.~\ref{Salix_pdfs_cdfs}).
+Understanding species' interactions in novel or changing communities is important for a variety of conservation questions~\citep{Bartomeus2013,Gravel2013}, and a Bayesian approach using a trait-matching model or data from species' current ranges could help us to anticipate how species will integrate into new communities.
 
@@
     \begin{center}
-    % \includegraphics*[height=.45\textheight]{figures/conceptual_fig.eps}
+    \includegraphics*[height=.45\textheight]{figures/conceptual_fig.eps}
     % \includegraphics*[height=.5\textheight]{Figure_1.eps}

### 2019-02-19 code/figure_generation/pdf_comparison_priors.py
made a figure to see the effect of different prior

@@ -1,0 +1,263 @@
+# ###### R code to generate data files:
+# Getting distributions:
+# xdata=matrix(ncol=1001,nrow=12)
+# ydata=matrix(ncol=1001,nrow=12)
+# MLEs=matrix(ncol=4,nrow=12)
+# ns=as.vector(c(0,5,10,15,20,25,50,100,150,200,300,374))
+# for(i in 1:length(ns)){
+#   n=ns[i]
+#   print(n)
+#   dist=calculate_distribution(calculate_parameters(sg_int_probs,n,0))
+#   x=seq(-5,5,length=1000)*sqrt(dist[[2]])+dist[[1]]
+#   hx=dnorm(x,dist[[1]],sqrt(dist[[2]]))
+#   xdata[i,]=c(n,x)
+#   ydata[i,]=c(n,hx)
+
+#   MLE=calculate_mean_MLE(sg_int_probs,n,0)
+#   interval=credible_interval(calculate_parameters(sg_int_probs,n,0),0.025,0.975)
+#   MLEs[i,]=c(n,MLE,interval)
+
+# }
+
+# # Data are along rows for pythonic convenience
+# colnames(xdata)=c("N",seq(1,1000))
+# colnames(ydata)=c("N",seq(1,1000))
+# colnames(MLEs)=c("N","MLE","lower","upper")
+
+# write.table(xdata,file='../../data/Salix_example/Zillis/Salix_Galler/distfigure_xvals.tsv',sep='\t')
+# write.table(ydata,file='../../data/Salix_example/Zillis/Salix_Galler/distfigure_yvals.tsv',sep='\t')
+# write.table(MLEs,file='../../data/Salix_example/Zillis/Salix_Galler/distfigure_MLEs.tsv',sep='\t')
+
+# xdata=matrix(ncol=1001,nrow=12)
+# ydata=matrix(ncol=1001,nrow=12)
+# MLEs=matrix(ncol=4,nrow=12)
+# ns=as.vector(c(0,5,10,15,20,25,50,100,150,200,300,374))
+# for(i in 1:length(ns)){
+#   n=ns[i]
+#   dist=calculate_distribution(calculate_parameters(gp_int_probs,n,0))
+#   x=seq(-5,5,length=1000)*sqrt(dist[[2]])+dist[[1]]
+#   hx=dnorm(x,dist[[1]],sqrt(dist[[2]]))
+#   xdata[i,]=c(n,x)
[…]

### 2019-02-19 manuscript/reply_to_reviewers_2.tex

\documentclass[12pt]{letter}

\usepackage[britdate]{LiU-letter}
\usepackage{times}
\usepackage{letterbib}
\usepackage{geometry}
\usepackage[round]{natbib}
\usepackage{graphicx}
\geometry{a4paper}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage[running]{lineno}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage[margin=10pt,font=small,labelfont=bf]{caption}

%\usepackage{natbib}
% \bibpunct[; ]{(}{)}{;}{a}{,}{;}

\newenvironment{refquote}{\bigskip \begin{it}}{\end{it}\smallskip}

\newenvironment{figure}{}

\begin{document}

\newpage

\setcounter{page}{1}

% Changes: reducing discussion of different sources of uncertainty, increasing description of priors, added a bunch of refs, trying to frame our study more clearly. Changed filtering to reflect all uncertainty, not just detection (more accurate, hopefully less confusing). No box needed, just ``Why sample'' section.

% Ask for help: how would we expand this to interaction frequencies? Still with the Bernoulli? Worthwhile to add a demo of Jensen's inequality?
% To do: expand discussion of our results as much as possible given space constraints.
% -----------------------------------------------------------------------------
% -----------------------------------------------------------------------------
{\Large \bf Reply to Associate Editor}
% ---------------------------------------

	\begin{refquote}

		Thank you for the extensive and detailed reply to the comments of the referees. Your revised manuscript was sent back to one of the referees who reviewed the original version. As you will see, he is very positive about the revised version and has now signed his review. The only outstanding issue is the addition of some discussion about how to detect potential problems with the priors. I agree with this suggestion as one of the most common criticisms of Bayesian methods is precisely the use of priors.

	\end{refquote}

	\textbf{R:} We appreciate the additional comments from the Referee, and agree that prior detection can be quite a challenge. We are therefore quite happy to add to our discussion about how to detect potential problems. Note, however, that after making the additions requested by the previous round of reviews our manuscript was very close to the standard word limit for \textbf{Methods in Ecology and Evolution}. To meaningfully expand our discussion of how to detect problems with priors we must therefore ask for more space. We have kept our addition to the discussion as succinct as possible, and the revised manuscript is now approximately XXXX words. We hope that this will be an acceptable length for publication in \textbf{Methods in Ecology and Evolution}.

	Thanks again to the Associate Editor and Reviewer for their comments. We believe that the manuscript has been much improved by their feedback.

\newpage

% ----------------------------------------------------------------------
% ----------------------------------------------------------------------
{\Large \bf Reply to Reviewer \#1 (Ben Weinstein)}
% ---------------------------------------

	\begin{refquote}

		I am reviewer 1 from the first submission.

		The text is remarkably improved. It is focused and clear. The authors do a good job of identifying the contribution of their work. I appreciate the authors willingness to rewrite much of the paper based on the suggestions of the reviewers.

		I think the authors miss one key discomfort with empirical bayes. It seems vaguely anti-ecology, because it assumes that we can L289 : “use information from abundant and easily-sampled species to predict interaction probabilities for species which were observed only rarely.”  A common goal in network ecology is to describe interaction frequencies by using niche-based proxies (phylogeny, traits, etc). If it was a simply a matter that most networks had the same degree distribution, then predicting networks would be much easier than it is. In fact, we are really bad at predicting pairwise interactions (see Olito and Fox), even when we get the emergent structure of the network correct. Yet empirical bayes assumes a kind of commonality among all networks to help narrow the posteriors. I think the authors need to speak to this concern.

		Sincerely,

		Ben Weinstein

	\end{refquote}

	We thank the Reviewer for his further feedback and address each point (prefaced by \textbf{R:}) below.

	1. Re-emphasize Figure 3.

		\begin{refquote}

			Figure 3 is fun and deserves a bit more central place in the discussion.

		\end{refquote}

		\textbf{R:} We thank the Reviewer for his complement to Figure 3. Although we wish to keep any additions as brief as possible, we are happy to add a short reference to Figure 3 in the discussion as part of an example of how to use our simple Bayesian framework when thinking about insects moving into new communities (e.g., as climate changes). We hope that this puts the figure in a more central place, as intended. We also now compare this reasonable posterior pdf with an un-reasonable one generated by a poor choice of prior, which should further highlight this figure.

		Lines XX-XX:

		\begin{quotation}

			Such approaches are particularly useful when considering interactions involving species entering new ranges due to climate change or introductions. Our framework could, for example, be used to predict the probability of interaction between a galler and parasitoid at a new site on the frontier of their ranges. If the species have not been observed co-occurring at other sites, we would expect them to interact with a probability of approximately 0.1 rather than assuming that they will not interact because they have not been observed interacting elsewhere (Fig.~\ref{Salix_pdfs_cdfs}). Understanding species' interactions in novel or changing communities is important for a variety of conservation questions~\citep{Bartomeus2013,Gravel2013}, and a Bayesian approach using a trait-matching model or data from species' current ranges could help us to anticipate how species will integrate into new communities.

		\end{quotation}

	2.

	3. Include material from \emph{Appendix 7} in the main text

		\begin{refquote}

			My final lingering concern is that something like appendix 7 seems important and should be included in the text? Was this done because of space limitations? I think the authors can appeal to the editor that the paper merits the extra space. As a compromise there could to be atleast a paragraph on what can go wrong and what that looks like. I think a figure would be useful here. If the informed/empirical priors are too narrow, the data will not really move the posterior. The authors certainly acknowledge it in various places, but it needs to be clearer to the reader.

		\end{refquote}

		\textbf{R:} This material was indeed placed in an appendix because of space constraints. We have added a figure showing results with the other prior and a paragraph summarizing \emph{Appendix 7}. As we do not wish to be too demanding with regard to extra space (and our manuscript was essentially at the standard length limit after the last revision), we hope that these smaller additions will be enough to emphasize the potential for spurious results after poor prior choices.

	3. Reduce citations by Graham and Weinstein

		\begin{refquote}

			To be perfectly honest, I feel more than a bit uncomfortable with the amount that Graham and Weinstein are cited in the introduction. I count 18 times. It would be more than sufficient to cite the work in the appropriate places and move on. I understand that the reviewers asked for a broader sense of the literature, but I think the authors have gone a bit overboard. I don’t know how often a reviewer asks the authors to cite himself less, but I assure you the reason that the paper is improved is not because I am cited nearly twenty times.

		\end{refquote}

\clearpage

    \bibliographystyle{ecol_let} 
    \bibliography{manual} % Abbreviate journal titles.

\end{document}

### 2019-02-19 manuscript/reply_to_reviewers_2.tex
removed some Weinstein and Graham refs

@@
 
-		I think the authors miss one key discomfort with empirical bayes.
-It seems vaguely anti-ecology, because it assumes that we can L289 : “use information from abundant and easily-sampled species to predict interaction probabilities for species which were observed only rarely.”  A common goal in network ecology is to describe interaction frequencies by using niche-based proxies (phylogeny, traits, etc).
-If it was a simply a matter that most networks had the same degree distribution, then predicting networks would be much easier than it is.
-In fact, we are really bad at predicting pairwise interactions (see Olito and Fox), even when we get the emergent structure of the network correct.
-Yet empirical bayes assumes a kind of commonality among all networks to help narrow the posteriors.
-I think the authors need to speak to this concern.
-
 		Sincerely,
@@
 
-	1. Re-emphasize Figure 3.
+	1. Re-emphasize Figure 3. [[done]]
 
@@
 We hope that this puts the figure in a more central place, as intended.
-We also now compare this reasonable posterior pdf with an un-reasonable one generated by a poor choice of prior, which should further highlight this figure.
+We also now include a similar figure demonstrating the effect of a change in prior on the posterior pdf's obtained for the \emph{Salix}-galler networks and hope that this also helps to emphasize these results.
 
@@
 
-	3. Include material from \emph{Appendix 7} in the main text
+		\begin{refquote}
+
+			I think the authors miss one key discomfort with empirical bayes.
+It seems vaguely anti-ecology, because it assumes that we can L289 : “use information from abundant and easily-sampled species to predict interaction probabilities for species which were observed only rarely.”  A common goal in network ecology is to describe interaction frequencies by using niche-based proxies (phylogeny, traits, etc).
+If it was a simply a matter that most networks had the same degree distribution, then predicting networks would be much easier than it is.
+In fact, we are really bad at predicting pairwise interactions (see Olito and Fox), even when we get the emergent structure of the network correct.
+Yet empirical bayes assumes a kind of commonality among all networks to help narrow the posteriors.
+I think the authors need to speak to this concern.
+
+		\end{refquote}
+
+		\textbf{R:} We agree that pairwise interactions are often difficult to predict and that different networks can have quite different degree distributions (or whichever other network property you like).
+We disagree, however, that empirical Bayes assumes commonality among all networks.
+Rather, we argue that given some \emph{a priori} similarity among networks (e.g., similar taxa, similar habitats, similar interaction types, similar numbers of species, etc.), we can use that similarity to set bounds on our expectations about pairwise interactions.
+Including clearly dissimilar networks in the set of networks used to create an empirical Bayesian prior would not be reasonable.
+We do point out some of the potential for false results due to the use of very different networks for the prior and posterior in our paragraph on degree distribution, and have added a few more references to the pitfalls of empirical Bayes.
+
+		We would also like to add that we began our discussion of informed priors with trait-based models because these models are likely to give the best results in terms of which specific interactions are most likely.
+We introduce empirical Bayes for those situations where researchers do not have a strong idea of the "niche-based proxies" structuring interactions in a given site.
+In such a situation, we still maintain that using information available from well-sampled species or other networks is likely to be better than nothing.
+For example, we know that empirical networks in general tend to be rather sparse and the well-sampled species in a community probably do not interact will all possible partners, so it is not reasonable to assume that every unobserved interaction truly occurs (leaving a completely connected network) except in extremely unusual circumstances.
+Granted, this is quite an extreme example, but it illustrates the point.
+
+		The Reviewer is quite correct that an empirical Bayes framework does not tell us which interactions are most likely to truly occur (assuming equal observations of co-occurrences).
+While there are many studies which aim to identify the exact set of interactions which occur, there are also others that are more concerned with the structure of the network as a whole.
+In such cases, and absent the information necessary to build a more specific model, we feel that empirical Bayes can still be a useful tool.
+We hope that our additions to this section will now instill an appropriate level of caution in readers without making it seem as though empirical Bayes is completely useless.
+After all, we do have some faith in our empirical Bayes example.
+
+		Lines XX-XX:
+
+		\begin{quotation}
+
+		\end{quotation}
+
+	3. Include material from \emph{Appendix 7} in the main text [[done]]
 
@@
 		\textbf{R:} This material was indeed placed in an appendix because of space constraints.
-We have added a figure showing results with the other prior and a paragraph summarizing \emph{Appendix 7}.
+We have added a figure showing the posterior distributions obtained from both priors and a paragraph summarizing \emph{Appendix 7}.
 As we do not wish to be too demanding with regard to extra space (and our manuscript was essentially at the standard length limit after the last revision), we hope that these smaller additions will be enough to emphasize the potential for spurious results after poor prior choices.
+Also note that the results for the galler-parasitoid community were somewhat similar.
+In order to more clearly demonstrate the potentially large effects of prior choice, we therefore showcase the results from \emph{Salix}-galler networks in this paragraph.
 
-	3. Reduce citations by Graham and Weinstein
+		Lines XX-XX:
+
+		\begin{quotation}
+
+		  Note that, as in all Bayesian analyses, our results do depend on the prior chosen.
+To demonstrate this, we repeated our analyses using a prior derived from a study of gallers found on several genotypes of \emph{Salix hookeriana} and the parasites which emerged from them (\citealp{Barbour2016,Barbour2016Dryad}; \emph{Appendix S7}).
+Although the study system is similar to that in~\citet{Kopelke2017}, the network is quite different due to using different genotypes of a single \emph{Salix} species rather than several \emph{Salix} species as the basis for sampling.
+While this had a relatively small effect on our expectations for the galler-parasitoid community (\emph{Appendix S7}), the prior based on \citep{Barbour2016} resulted in very high probabilities of interaction between \emph{Salix} and galler pairs that were not observed interacting (Fig.~\ref{prior_comparison}).
+No amount of additional sampling would allow us to conclude that a given \emph{Salix}-galler pair did not interact with a threshold interaction probability of 0.01.
+This is reasonable for the situation described in~\citet{Barbour2016}, as it is very likely that gallers which can interact with one \emph{S.
+hookeriana} genotype can interact with most others, but is not reasonable for the more diverse community in~\citet{Kopelke2017}.
+This demonstrates the importance of conducting a "sanity check" on the posterior distribution obtained from any given prior.
+
+		\end{quotation}
+
+	3. Reduce citations by Graham and Weinstein [[done]]
 
@@
 
+		\textbf{R:} We have removed several of the citations to Graham and Weinstein/Weinstein and Graham, and thank the Reviewer for the opportunity to reduce our word count slightly.
+We had added particularly many citations of these papers because a couple of the Reviewers mentioned Graham and Weinstein as references that we had missed, and so we hope that the reduced number of references in the present revision still does justice to your work.
+
 \clearpage

### 2019-02-19 manuscript/CI_interactions.tex
removed some Weinstein and Graham refs

@@
     First, ecological communities are stochastic~\citep{Gotelli2000}.
-Community composition and abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}, leading to variation in encounter probabilities and hence interactions~\citep{Vazquez2005,Poisot2015,Graham2018}.
+Community composition and abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}, leading to variation in encounter probabilities and hence interactions~\citep{Vazquez2005,Poisot2015}.
 Species must co-occur in order to be observed interacting, so any variation in co-occurrence will create variation in the set of observed interactions~\citep{Gravel2018,Graham2018}.
@@
     Beyond ``true" variation in network structure, several researchers note effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Jordano2016}).
-Assessments of the accumulation of interactions with increasing sampling effort suggest that it is more challenging to correctly document interactions than species~\citep{Guimera2009,Poisot2012,Bartomeus2013,Jordano2016,Giron2018,Graham2018}.
+Assessments of the accumulation of interactions with increasing sampling effort suggest that it is more challenging to correctly document interactions than species~\citep{Guimera2009,Poisot2012,Bartomeus2013,Jordano2016,Giron2018}.
 As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Bartomeus2013,Poisot2016}.
 Such efforts usually take the form of creating model networks that approximate observed empirical networks~\citep{Allesina2008,Guimera2009,Williams2010,Rohr2016}.
-These models may be based on species traits and/or abundances~\citep{Rohr2016,Weinstein2017,Weinstein2017a,Graham2018} or on simple abstract rules~\citep{Allesina2008,Guimera2009,Williams2010}.
-Model networks provide an important ''reality check'' by allowing hypothesis testing about factors structuring ecological networks~\citep{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}.
+These models may be based on species traits and/or abundances~\citep{Rohr2016,Weinstein2017a,Graham2018} or on simple abstract rules~\citep{Allesina2008,Guimera2009,Williams2010}.
+Model networks provide an important ''reality check'' by allowing hypothesis testing about factors structuring ecological networks~\citep{Bartomeus2013,Graham2018}.
 They can also allow estimation of the numbers unobserved of interactions~\citep{Jordano2016,Weinstein2017a} and predict which unobserved interactions are most likely~\citep{Guimera2009,Bartomeus2013}.
 
-    To date, models incorporating uncertainty have either been very general (e.g.,~\citet{Guimera2009,Gravel2018}) or very system-specific (e.g.,~\citet{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}); in either case such a model may be a poor fit for a particular study system.
+    To date, models incorporating uncertainty have either been very general (e.g.,~\citet{Guimera2009,Gravel2018}) or very system-specific (e.g.,~\citet{Bartomeus2013,Graham2018}); in either case such a model may be a poor fit for a particular study system.
 Moreover, some of the models described above cannot accommodate species observed only once~\citep{Bartomeus2013,Weinstein2017}.
@@
 We find that even the highest-quality empirical network data we could find has substantial uncertainty about whether many pairs of species interact, demonstrating the need to include information about this uncertainty in published networks.
-    % We also show that this interaction-level uncertainty leads to uncertainty about estimates of network structure, with important implications for comparisons across networks; especially those compiled with different sampling intensity~\citep{Pelissier2017,Tylianakis2017,Weinstein2017}.
-
-    % Development of molecular sampling methods such as DNA barcoding hold great potential for uncovering interactions missed by other sampling methods (such as visit surveys)~\citep{Giron2018}, but these novel methods are also somewhat error-prone at present~\citep{}.
-
-    % Accounting for differences in feasible (binary) interactions across life stages changes network structure~\citep{Clegg2018}.
-
-    % Representing an ecological community as a network summarises both species composition and interactions between species.
-A tabulation of the nodes (species) and their relative abundances forms the basis for traditional metrics of community composition such as alpha diversity.
-A network framework combines this tabulation of nodes with a list of interactions (links between nodes) so that networks provide additional, higher-order information on community structure.
-Despite this additional information, empirical descriptions of ecological networks are still often limited by a lack of data or tools to adequately incorporate variation in interactions into networks.
-That is, whether the network is assembled based on aggregated data, a single intensive ``snapshot" sample, or expert knowledge, interactions are assumed to occur deterministically wherever and whenever the community is observed~\citep{Olesen2011a}.
-
-    % The assumption of static communities contrasts with the known stochasticity of ecological communities~\citep{Gotelli2000}.
-Community composition and abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}.
-Moreover, interactions vary over space~\citep{Kitching1987,Baiser2012}, time~\citep{Kitching1987,Olesen2011a}, and between individuals~\citep{Pires2011a,Fodrie2015,Novak2015}.
-Worse, variability in community composition and interactions may not be closely related.
-The removal of a species from a site will obviously also remove its interactions but, conversely, the co-occurrence of potentially interacting species does not guarantee that the species will interact at a given place and time.
-Interactions can be lost if the interaction partners remain present but are separated in time or are too rare to detect each other~\citep{Tylianakis2010}.
-Interactions can also fail to occur because of environmental contingencies~\citep{Poisot2015} or individual preferences~\citep{Fodrie2015}.
-
-    % Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007}).
-An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to document interactions than species~\citep{Poisot2012,Bartomeus,others}.
-As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Poisot2016}.
-Early work in this vein includes food-web models using likelihood-based approaches~\citep{Allesina2008} or Gaussian~\citep{Williams2010} or binomial~\citep{Rohr2016} probability functions for each possible interaction.
-These models may include information about species' traits~\citep{Rohr2016} or attempt to reproduce empirical network structures using a set of simple rules~\citep{Allesina2008,Williams2010}.
-
-    % Despite these efforts, we currently lack the quantitative methodology to deal with uncertainty generated by spatiotemporal variation in ecological interactions and by limited sampling.
-[[cite previous attempts]] Even in well-sampled networks, uneven sampling across species can lead to the inference that some species do not interact because they co-occur rarely or have not yet been observed together - even if they do interact when they do co-occur (see Fig.~\ref{histograms}).
-Nearly all network studies will thus neglect some interactions, necessitating an approach that acknowledges this uncertainty.
-
-    % In this study, we formalise the description of interactions between species as probabilities and develop analytical tools to capture the uncertainty in the estimation of these interactions.
-We focus on binary interactions as a first step, but the framework could be expanded to deal with interaction frequencies or strengths.
-To define the problem, we first identify different contributions to the uncertainty of an interaction and discuss the implications of each source of uncertainty for the properties of ecological networks.
 
@@
 
-          A feasible interaction (i.e., $L_{ij}=1$;), still may not occur at a particular place and time~\citep{Poisot2015,Graham2018}.
-This could be because constraints such as inclement weather or low abundance prevented the interaction~\citep{Jordano2016,Graham2018}, a preferred interaction partner was available~\citep{Weinstein2017a}, or individual variation in traits meant that local individuals could not interact even if the species in general can~\citep{Gravel2013,Wells2013,Poisot2015}.
+          A feasible interaction (i.e., $L_{ij}=1$;), still may not occur at a particular place and time~\citep{Poisot2015}.
+This could be because constraints such as inclement weather or low abundance prevented the interaction~\citep{Jordano2016}, a preferred interaction partner was available~\citep{Weinstein2017a}, or individual variation in traits meant that local individuals could not interact even if the species in general can~\citep{Gravel2013,Wells2013,Poisot2015}.
 For example, a rare galler may not parasitize a rare plant because they do not encounter each other.
@@
 Phenological matching~\citep{MillerRushing2010}, species preferences~\citep{Pires2011a,Novak2015}, and fear effects~\citep{Luttbeg2005} all affect the probability of an interaction and could be included in models similar to trait-matching models.
-Some studies attempt to reduce uncertainty by sampling intensively over a short period of time and restricting the scale of interest to interactions occurring at the sampling site and time (conflating $\chi_{ij}$ and $\lambda_{ij}$)~\citep{Bartomeus2013,Weinstein2017,Weinstein2017a}.
+Some studies attempt to reduce uncertainty by sampling intensively over a short period of time and restricting the scale of interest to interactions occurring at the sampling site and time (conflating $\chi_{ij}$ and $\lambda_{ij}$)~\citep{Bartomeus2013,Weinstein2017a}.
 This approach does reduce local-scale uncertainty but is not appropriate if we wish to assemble the full set of interactions which occur in a community (beyond the specific site and time of sampling).
@@
 Informative models could also include information on abundances, phenological matching, co-occurrence, etc.
-as available~\citep{Jordano2016,Weinstein2017a,Graham2018,Gravel2018}.
+as available~\citep{Jordano2016,Weinstein2017a,s,Gravel2018}.
 Multiple sources of information can be combined into a single model (e.g., the the $K$ nearest neighbour (KNN) algorithm, which identifies likely interaction partners based on similarity to known partners~\citep{DesjardinsProulx2017}).
@@
 Despite these benefits, informative priors often involve many assumptions and carry a risk of over-fitting.
-Also note that researchers wishing to test whether a particular trait influences interaction probabilities should either exclude that trait from their prior or model the network using priors which include and exclude the trait of interest (as in~\citet{Weinstein2017,Weinstein2017a}).
+Also note that researchers wishing to test whether a particular trait influences interaction probabilities should either exclude that trait from their prior or model the network using priors which include and exclude the trait of interest (as in~\citet{Weinstein2017a}).
 
@@
 Most pairs of species were not observed co-occurring even once, less than 10\% of species pairs were observed interacting, and no pairs were observed to co-occur frequently enough to conclude that their probability of interacting was below 0.01.
-This suggests that limited sampling is a major source of uncertainty in empirical networks, in agreement with~\citet{Jordano2016,Weinstein2017a,Weinstein2017}.
+This suggests that limited sampling is a major source of uncertainty in empirical networks, in agreement with~\citet{Jordano2016,Weinstein2017a}.
 
@@
 Understanding species' interactions in novel or changing communities is important for a variety of conservation questions~\citep{Bartomeus2013,Gravel2013}, and a Bayesian approach using a trait-matching model or data from species' current ranges could help us to anticipate how species will integrate into new communities.
+
+  Note that, as in all Bayesian analyses, our results do depend on the prior chosen.
+To demonstrate this, we repeated our analyses using a prior derived from a study of gallers found on several genotypes of \emph{Salix hookeriana} and the parasites which emerged from them (\citealp{Barbour2016,Barbour2016Dryad}; \emph{Appendix S7}).
+Although the study system is similar to that in~\citet{Kopelke2017}, the network is quite different due to using different genotypes of a single \emph{Salix} species rather than several \emph{Salix} species as the basis for sampling.
+While this had a relatively small effect on our expectations for the galler-parasitoid community (\emph{Appendix S7}), the prior based on \citep{Barbour2016} resulted in very high probabilities of interaction between \emph{Salix} and galler pairs that were not observed interacting (Fig.~\ref{prior_comparison}).
+No amount of additional sampling would allow us to conclude that a given \emph{Salix}-galler pair did not interact with a threshold interaction probability of 0.01.
+This is reasonable for the situation described in~\citet{Barbour2016}, as it is very likely that gallers which can interact with one \emph{S.
+hookeriana} genotype can interact with most others, but is not reasonable for the more diverse community in~\citet{Kopelke2017}.
+This demonstrates the importance of conducting a "sanity check" on the posterior distribution obtained from any given prior.
 
@@
 
+  \begin{figure}[h!]
+    \caption{Posterior distributions for the interaction probability ($\lambda_{ij}$) for two species that have not been observed interacting ($k_{ij}=0$), A) based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017} and B) based on a network describing interactions between gallers and several genotypes of \emph{Salix hookeriana} from~\citet{Barbour2016}.
+Posterior distributions (curves) and 95\% credible intervals (lines at top of panel) for $\lambda_{ij}$ narrow and approach zero as the number of observed co-occurrences ($n_{ij}$) increases.
+Diamonds indicate the maximum likelihood estimator for the mean probability of interaction.
+    Dashed lines indicate threshold probabilities of 0.01, 0.05, and 0.1. Note that the prior obtained from~\citet{Barbour2016} constrains the MLE  of $\lambda_{ij}$ above 0.01.}
+    \label{prior_comparison}
+    \begin{center}
+    \includegraphics*[width=.8\textwidth]{figures/SG_pdfs_prior_comparison.eps}
+    % \includegraphics*[width=.8\textwidth]{Figure_4.eps}
+    \end{center}
+    \end{figure}
+
   % \begin{figure}[h!]

### 2019-02-21 manuscript/reply_to_reviewers_2.tex
revision 2 ready to send out

@@
 
-	2.
+	2. Emphasize the drawbacks of empirical Bayes
 
@@
 
-		\textbf{R:} We agree that pairwise interactions are often difficult to predict and that different networks can have quite different degree distributions (or whichever other network property you like).
-We disagree, however, that empirical Bayes assumes commonality among all networks.
-Rather, we argue that given some \emph{a priori} similarity among networks (e.g., similar taxa, similar habitats, similar interaction types, similar numbers of species, etc.), we can use that similarity to set bounds on our expectations about pairwise interactions.
-Including clearly dissimilar networks in the set of networks used to create an empirical Bayesian prior would not be reasonable.
-We do point out some of the potential for false results due to the use of very different networks for the prior and posterior in our paragraph on degree distribution, and have added a few more references to the pitfalls of empirical Bayes.
+		\textbf{R:} We do not share the Reviewer's highly negative view of empirical Bayes.
+Perhaps this is a matter of perspective: the Reviewer's work seems to focus on a system where a great deal of information about the traits structuring interactions is known and trait values are available for almost all species.
+In such a system it is absolutely best to use a trait-based model to predict interactions.
+This is why we began our section on informative priors with trait-based models and only introduce empirical and approximate Bayes as solutions where trait information/models are lacking or where over-fitting is a strong concern.
+Most of the authors of this manuscript are more used to such relatively information-poor systems.
+In these cases, we agree that empirical Bayes is not perfect but argue that it is much better than nothing (or an uninformative prior, as long as a somewhat similar network is available).
 
-		We would also like to add that we began our discussion of informed priors with trait-based models because these models are likely to give the best results in terms of which specific interactions are most likely.
-We introduce empirical Bayes for those situations where researchers do not have a strong idea of the "niche-based proxies" structuring interactions in a given site.
-In such a situation, we still maintain that using information available from well-sampled species or other networks is likely to be better than nothing.
-For example, we know that empirical networks in general tend to be rather sparse and the well-sampled species in a community probably do not interact will all possible partners, so it is not reasonable to assume that every unobserved interaction truly occurs (leaving a completely connected network) except in extremely unusual circumstances.
-Granted, this is quite an extreme example, but it illustrates the point.
+		The Jeffreys prior gives a maximum likelihood estimate of 0.5 for the probability of an interaction between two species which have never been observed together.
+Based on our understanding of ecological systems, this seems highly unlikely.
+Certainly species differ in many ways, but they also do have some similarities, such as limited foraging time and somewhat consistent morphologies.
+Because of behavioural, morphological, or temporal limits to the number of partners with which a given species can interact, most ecological networks are sparse and most well-sampled species interact with only a small subset of their potential partners (extreme generalists in highly nested mutualistic networks being a notable exception).
+We can therefore reasonably expect that a species entering a new habitat, for example, will interact with far fewer than half of the available partners.
+If we do not know which traits strongly affect interactions involving the focal species, or if those traits are not known for all of the species in the network, we cannot use a trait-based model to predict interaction frequencies.
+This leaves empirical and approximate Bayes as the only viable options unless we are willing to revert to the assumption that unobserved interactions never occur.
+Certainly empirical Bayes is not perfect, but we are strongly confident that it is still gives more reasonable expectations than ignoring the ecological networks literature.
 
-		The Reviewer is quite correct that an empirical Bayes framework does not tell us which interactions are most likely to truly occur (assuming equal observations of co-occurrences).
-While there are many studies which aim to identify the exact set of interactions which occur, there are also others that are more concerned with the structure of the network as a whole.
-In such cases, and absent the information necessary to build a more specific model, we feel that empirical Bayes can still be a useful tool.
-We hope that our additions to this section will now instill an appropriate level of caution in readers without making it seem as though empirical Bayes is completely useless.
-After all, we do have some faith in our empirical Bayes example.
+		Moreover, while we agree that empirical Bayes does not take differences in niche proxies into account, this may not be crucial in all studies.
+Researchers are often more interested in the overall structure of the network or in some emergent property such as stability than in the relationships between niche proxies and interaction frequencies.
+In such cases, the number of additional interactions we expect to be observed with further sampling is likely more important than the exact identity of those interactions, and an empirical Bayes approach is reasonable if a good trait-based model and trait information or not available.
 
-		Lines XX-XX:
+		Finally, we must disagree with the Reviewer's contention that ``empirical Bayes assumes a kind of commonality among all networks".
+This is not so; empirical Bayes only assumes some commonality between the focal network and those used to construct the prior.
+We have revised the text to emphasize the need to use similar networks to construct an empicial Bayes prior and note that \emph{Appendix S7} demonstrates the pitfalls of basing an empirical Bayes prior on a network with little commonality with the focal system.
+
+		We believe that including an expanded reference to \emph{Appendix S7} as suggested below will help to address some of these concerns by demonstrating that empirical Bayes should \emph{not} be based on networks which have major differences from the focal system as this will lead to unreasonable predictions (in our case, although the taxa and interaction types involved were similar, the taxonomic resolution in the \citet{Barbour2016} and \citet{Kopelke2017} were very different).
+To reinforce this point and make the role of empirical Bayes as a solution in the absence of trait-based models and/or trait information, we have made several minor revisions to the section introducing informative priors.
+We hope that these changes will be sufficient to illustrate the drawbacks to empirical Bayes without being overly discouraging for those who lack the necessary information to construct more detailed informative priors.
 
 		\begin{quotation}
+
+			Alternatively, if information on the traits affecting interaction probabilities is lacking, one can develop a prior based on the properties of a set of published networks (``empirical" or ``reference Bayes"~\citet{Spiegelhalter2000}).
+This type of prior does not vary between species pairs but entails only one assumption: that the focal network has similar structural properties to those of some published networks.
+
+		\end{quotation}
+
+		In lines XX-XX we explicitly state that the networks used to build an empirical Bayes prior should be similar to the focal system:
+
+		\begin{quotation}
+
+			The distribution of published connectances can be used to predict the distribution of interaction probabilities in a new network that is similar to those used to construct the prior (same type of interaction, similar taxonomic resolution, habitat, etc.).
+
+		\end{quotation}
+
+		In lines XX-XX we reiterate the fact that an empirical Bayes prior does not vary between pairs of species and that the networks used to build the prior should be similar to the focal network:
+
+		\begin{quotation}
+
+		Note that here the prior distribution will be the same for all interaction probabilities.
+It is also possible to interpret other network properties (e.g., species degrees) in a similar network(s) as interaction probabilities and use these to create a prior (worked example in \emph{Appendix S4}).
 

### 2019-02-21 manuscript/reply_to_reviewers_2.tex
updated text, reply

@@
 To meaningfully expand our discussion of how to detect problems with priors we must therefore ask for more space.
-We have kept our addition to the discussion as succinct as possible, and the revised manuscript is now approximately XXXX words.
-We hope that this will be an acceptable length for publication in \textbf{Methods in Ecology and Evolution}.
+We have kept our addition to the discussion as succinct as possible, and the revised manuscript is now approximately 7433 words.
+We hope that this additional length is justified by our efforts to address the Reviewer's remaining concerns.
 
@@
 
-	1. Re-emphasize Figure 3. [[done]]
+	1. Re-emphasize Figure 3.
 
@@
 
-		Lines XX-XX:
+		Lines 379-389:
 
@@
 Our framework could, for example, be used to predict the probability of interaction between a galler and parasitoid at a new site on the frontier of their ranges.
-If the species have not been observed co-occurring at other sites, we would expect them to interact with a probability of approximately 0.1 rather than assuming that they will not interact because they have not been observed interacting elsewhere (Fig.~\ref{Salix_pdfs_cdfs}).
+If the species have not been observed co-occurring at other sites, we would expect them to interact with a probability of approximately 0.1 rather than assuming that they will not interact because they have not been observed interacting elsewhere (Fig.
+3).
 Understanding species' interactions in novel or changing communities is important for a variety of conservation questions~\citep{Bartomeus2013,Gravel2013}, and a Bayesian approach using a trait-matching model or data from species' current ranges could help us to anticipate how species will integrate into new communities.
@@
 
+		In lines 258-262 we state that empirical Bayes is an option if information about traits is lacking but that an empirical Bayes prior does not vary between species pairs:
+
 		\begin{quotation}
@@
 
-		In lines XX-XX we explicitly state that the networks used to build an empirical Bayes prior should be similar to the focal system:
+		In lines 264-266 we explicitly state that the networks used to build an empirical Bayes prior should be similar to the focal system:
 
@@
 
-		In lines XX-XX we reiterate the fact that an empirical Bayes prior does not vary between pairs of species and that the networks used to build the prior should be similar to the focal network:
+		In lines 269-272 we reiterate the fact that an empirical Bayes prior does not vary between pairs of species and that the networks used to build the prior should be similar to the focal network.
+We also acknowledge the possibility that published data are derived from under-sampled data and therefore will underestimate interaction probabilities
 
@@
 
-	3. Include material from \emph{Appendix 7} in the main text [[done]]
+		Finally, please note that we do discuss caveats to the empirical Bayes approach in lines 272-281, including the possibility that priors based on substantailly different systems will be misleading (with reference to \emph{Appendix S7}) and that published data may reflect under-sampled data:
+
+		\begin{quotation}
+
+			When using network summary statistics or degree distributions, it is important to consider whether the available information reflects what we believe about the network.
+Given the likelihood that most published networks are undersampled~\citep{Jordano2016}, it may be wise to include only the highest-quality networks available in a prior.
+Likewise, only the degree distribution for a similar system is likely to be a reasonable prior for a focal system.
+For example, if the focal system is large and contains a diverse array of species, it would be inappropriate to use a prior distribution drawn from a small network describing closely-related taxa (demonstrated in \emph{Appendix S7}).
+Similarly, data from a network where nodes are resolved to different taxonomic levels than the focal network are likely to have quite different properties and would not be an appropriate prior.
+
+		\end{quotation}
+
+	3. Include material from \emph{Appendix 7} in the main text
 
@@
 
-		Lines XX-XX:
+		Lines 390-405:
 
@@
 Although the study system is similar to that in~\citet{Kopelke2017}, the network is quite different due to using different genotypes of a single \emph{Salix} species rather than several \emph{Salix} species as the basis for sampling.
-While this had a relatively small effect on our expectations for the galler-parasitoid community (\emph{Appendix S7}), the prior based on \citep{Barbour2016} resulted in very high probabilities of interaction between \emph{Salix} and galler pairs that were not observed interacting (Fig.~\ref{prior_comparison}).
+While this had a relatively small effect on our expectations for the galler-parasitoid community (\emph{Appendix S7}), the prior based on \citep{Barbour2016} resulted in very high probabilities of interaction between \emph{Salix} and galler pairs that were not observed interacting (Fig.
+4).
 No amount of additional sampling would allow us to conclude that a given \emph{Salix}-galler pair did not interact with a threshold interaction probability of 0.01.
@@
 
-	3. Reduce citations by Graham and Weinstein [[done]]
+	3. Reduce citations by Graham and Weinstein
 

### 2019-02-21 manuscript/CI_interactions.tex
updated text, reply

@@
 Informative models could also include information on abundances, phenological matching, co-occurrence, etc.
-as available~\citep{Jordano2016,Weinstein2017a,s,Gravel2018}.
+as available~\citep{Jordano2016,Weinstein2017a,Gravel2018}.
 Multiple sources of information can be combined into a single model (e.g., the the $K$ nearest neighbour (KNN) algorithm, which identifies likely interaction partners based on similarity to known partners~\citep{DesjardinsProulx2017}).
@@
 
-        Alternatively, one can develop a prior based on the properties of a set of published networks (``empirical" or ``reference Bayes"~\citet{Spiegelhalter2000}).
-This type of prior entails only one assumption: that the focal network has similar structural properties to those of some published networks.
+        Alternatively, if information on the traits affecting interaction probabilities is lacking, one can develop a prior based on the properties of a set of published networks (``empirical" or ``reference Bayes"~\citet{Spiegelhalter2000}).
+This type of prior does not vary between species pairs but entails only one assumption: that the focal network has similar structural properties to those of some published networks.
 For example, connectance ($C=N/S^2$, where $N$ is the number of interactions and $S$ is the number of species) is available for many networks.
@@
 Similarly, data from a network where nodes are resolved to different taxonomic levels than the focal network are likely to have quite different properties and would not be an appropriate prior.
-
-        Note that if the focal network is substantially different from published networks, empirical Bayes will not give reasonable expectations about interaction probabilities in the focal network.
-[[Seems like R1 is demanding we add some more about how empirical Bayes is crap ...
-maybe we can say it'd give a reasonable expectation for the number of interactions but maybe not the right ones?]]
 
@@
 
-\captionsetup{singlelinecheck=false, font={stretch=2}}
+% \captionsetup{singlelinecheck=false, font={stretch=2}}
 

### 2019-02-21 manuscript/reply_to_reviewers_2.tex
small changes in response to reviewers

@@
 
-		\textbf{R:} We do not share the Reviewer's highly negative view of empirical Bayes.
-Perhaps this is a matter of perspective: the Reviewer's work seems to focus on a system where a great deal of information about the traits structuring interactions is known and trait values are available for almost all species.
-In such a system it is absolutely best to use a trait-based model to predict interactions.
+		\textbf{R:} We do not share the Reviewer's negative view of empirical Bayes.
+Perhaps this is a matter of perspective: in a system where a great deal of information about the traits structuring interactions is known and trait values are available for most species, it is absolutely best to use a trait-based model to predict interactions.
 This is why we began our section on informative priors with trait-based models and only introduce empirical and approximate Bayes as solutions where trait information/models are lacking or where over-fitting is a strong concern.
@@
 
-		Finally, we must disagree with the Reviewer's contention that ``empirical Bayes assumes a kind of commonality among all networks".
+		Finally, we disagree with the Reviewer's contention that ``empirical Bayes assumes a kind of commonality among all networks".
 This is not so; empirical Bayes only assumes some commonality between the focal network and those used to construct the prior.
-We have revised the text to emphasize the need to use similar networks to construct an empicial Bayes prior and note that \emph{Appendix S7} demonstrates the pitfalls of basing an empirical Bayes prior on a network with little commonality with the focal system.
+We have revised the text to emphasize the need to use similar networks to construct an empirical Bayes prior and note that \emph{Appendix S7} demonstrates the pitfalls of basing an empirical Bayes prior on a network with little commonality with the focal system.
 
@@
 
-		Finally, please note that we do discuss caveats to the empirical Bayes approach in lines 272-281, including the possibility that priors based on substantailly different systems will be misleading (with reference to \emph{Appendix S7}) and that published data may reflect under-sampled data:
+		Finally, we discuss caveats to the empirical Bayes approach in lines 272-281, including the possibility that priors based on substantially different systems will be misleading (with reference to \emph{Appendix S7}) and that published data may reflect under-sampled data:
 

### 2019-03-04 manuscript/reply_to_reviewers_2.tex
removed comments
agree with Annas comments, spellchecked

@@
 
-% Changes: reducing discussion of different sources of uncertainty, increasing description of priors, added a bunch of refs, trying to frame our study more clearly.
-Changed filtering to reflect all uncertainty, not just detection (more accurate, hopefully less confusing).
-No box needed, just ``Why sample'' section.
-
-% Ask for help: how would we expand this to interaction frequencies? Still with the Bernoulli? Worthwhile to add a demo of Jensen's inequality?
-% To do: expand discussion of our results as much as possible given space constraints.
 % -----------------------------------------------------------------------------
@@
 
-	1. Re-emphasize Figure 3.
+	1. Re-emphasise Figure 3.
 
@@
 We hope that this puts the figure in a more central place, as intended.
-We also now include a similar figure demonstrating the effect of a change in prior on the posterior pdf's obtained for the \emph{Salix}-galler networks and hope that this also helps to emphasize these results.
+We also now include a similar figure demonstrating the effect of a change in prior on the posterior pdf's obtained for the \emph{Salix}-galler networks and hope that this also helps to emphasise these results.
 
@@
 
-	2. Emphasize the drawbacks of empirical Bayes
+	2. Emphasise the drawbacks of empirical Bayes
 
@@
 
-			I think the authors miss one key discomfort with empirical bayes.
+			I think the authors miss one key discomfort with empirical Bayes.
 It seems vaguely anti-ecology, because it assumes that we can L289 : “use information from abundant and easily-sampled species to predict interaction probabilities for species which were observed only rarely.”  A common goal in network ecology is to describe interaction frequencies by using niche-based proxies (phylogeny, traits, etc).
@@
 In fact, we are really bad at predicting pairwise interactions (see Olito and Fox), even when we get the emergent structure of the network correct.
-Yet empirical bayes assumes a kind of commonality among all networks to help narrow the posteriors.
+Yet empirical Bayes assumes a kind of commonality among all networks to help narrow the posteriors.
 I think the authors need to speak to this concern.
@@
 This is not so; empirical Bayes only assumes some commonality between the focal network and those used to construct the prior.
-We have revised the text to emphasize the need to use similar networks to construct an empirical Bayes prior and note that \emph{Appendix S7} demonstrates the pitfalls of basing an empirical Bayes prior on a network with little commonality with the focal system.
+We have revised the text to emphasise the need to use similar networks to construct an empirical Bayes prior and note that \emph{Appendix S7} demonstrates the pitfalls of basing an empirical Bayes prior on a network with little commonality with the focal system.
 
@@
 I think the authors can appeal to the editor that the paper merits the extra space.
-As a compromise there could to be atleast a paragraph on what can go wrong and what that looks like.
+As a compromise there could to be at least a paragraph on what can go wrong and what that looks like.
 I think a figure would be useful here.
@@
 		\textbf{R:} This material was indeed placed in an appendix because of space constraints.
-We have added a figure showing the posterior distributions obtained from both priors and a paragraph summarizing \emph{Appendix 7}.
-As we do not wish to be too demanding with regard to extra space (and our manuscript was essentially at the standard length limit after the last revision), we hope that these smaller additions will be enough to emphasize the potential for spurious results after poor prior choices.
+We have added a figure showing the posterior distributions obtained from both priors and a paragraph summarising \emph{Appendix 7}.
+As we do not wish to be too demanding with regard to extra space (and our manuscript was essentially at the standard length limit after the last revision), we hope that these smaller additions will be enough to emphasise the potential for spurious results after poor prior choices.
 Also note that the results for the galler-parasitoid community were somewhat similar.

### 2019-03-04 manuscript/reply_to_reviewers_2.tex
added Tomas comments to reply, caught a mis-formatted quote in main text

@@
 
-	\textbf{R:} We appreciate the additional comments from the Referee, and agree that prior detection can be quite a challenge.
+	\textbf{R:} We appreciate the additional comments from the Referee, and agree that the definition of adequate priors can be quite a challenge.
 We are therefore quite happy to add to our discussion about how to detect potential problems.
 Note, however, that after making the additions requested by the previous round of reviews our manuscript was very close to the standard word limit for \textbf{Methods in Ecology and Evolution}.
-To meaningfully expand our discussion of how to detect problems with priors we must therefore ask for more space.
+To meaningfully expand our discussion of how to detect problems with priors we must therefore ask for more space-- a solution also explicitly recommended by the Reviewer.
 We have kept our addition to the discussion as succinct as possible, and the revised manuscript is now approximately 7433 words.
@@
 
-	We thank the Reviewer for his further feedback and address each point (prefaced by \textbf{R:}) below.
+	We thank the Reviewer for his previous and further feedback and address each point (prefaced by \textbf{R:}) below.
 
@@
 
-		\textbf{R:} We do not share the Reviewer's negative view of empirical Bayes.
-Perhaps this is a matter of perspective: in a system where a great deal of information about the traits structuring interactions is known and trait values are available for most species, it is absolutely best to use a trait-based model to predict interactions.
+		\textbf{R:} We appreciate but do not fully share the Reviewer's negative view of empirical Bayes.
+Perhaps this is a matter of perspective: in a system where a great deal of information about the traits structuring interactions is known and trait values are available for most species, trait-based models are indeed often a good way to predict interactions (although far from fool-proof, as the Reviewer points out).
 This is why we began our section on informative priors with trait-based models and only introduce empirical and approximate Bayes as solutions where trait information/models are lacking or where over-fitting is a strong concern.
 Most of the authors of this manuscript are more used to such relatively information-poor systems.
-In these cases, we agree that empirical Bayes is not perfect but argue that it is much better than nothing (or an uninformative prior, as long as a somewhat similar network is available).
+In these cases, we agree that empirical Bayes is not perfect, but argue that it is much better than nothing (or an uninformative prior, as long as a somewhat similar network is available).
 
+		[[Currently one vote for removing this paragraph and one vote for keeping it and strengthening the point]]
 		The Jeffreys prior gives a maximum likelihood estimate of 0.5 for the probability of an interaction between two species which have never been observed together.
@@
 If we do not know which traits strongly affect interactions involving the focal species, or if those traits are not known for all of the species in the network, we cannot use a trait-based model to predict interaction frequencies.
-This leaves empirical and approximate Bayes as the only viable options unless we are willing to revert to the assumption that unobserved interactions never occur.
-Certainly empirical Bayes is not perfect, but we are strongly confident that it is still gives more reasonable expectations than ignoring the ecological networks literature.
+This leaves empirical and approximate Bayes as the only viable options, unless we are willing to revert to the assumption that unobserved interactions never occur.
+Certainly empirical Bayes is not perfect, but we are confident that it is still gives more reasonable expectations than ignoring the ecological networks literature.
 
@@
 Researchers are often more interested in the overall structure of the network or in some emergent property such as stability than in the relationships between niche proxies and interaction frequencies.
-In such cases, the number of additional interactions we expect to be observed with further sampling is likely more important than the exact identity of those interactions, and an empirical Bayes approach is reasonable if a good trait-based model and trait information or not available.
+In such cases, the number of additional interactions that we expect to be observed with further sampling is likely more important than the exact identity of those interactions, and an empirical Bayes approach is reasonable if a good trait-based model and trait information or not available.
 
@@
 We have revised the text to emphasise the need to use similar networks to construct an empirical Bayes prior and note that \emph{Appendix S7} demonstrates the pitfalls of basing an empirical Bayes prior on a network with little commonality with the focal system.
+[[The importance of using prior information from similar networks is a small but very important point that refers back to the core of our argument: if informatiom about a focal system is limited, then closing our eyes to what is known about similar networks and assuming \emph{a priori} that an unobserved interaction in any system is either equally (and rather highly) likely or equally impossible seems more than ``vaguely anti-ecology".
+After all, ecology advances by building upon previous insights and not by ignoring them in an effort to be ``conservative".
+It is essential to realise that ``uninformative" priors can lead to very biased results, just as poorly-chosen informative priors can.
+]][[This last portion strengthens the point in paragraph 2 but may be too much.]]
 
@@
 hookeriana} genotype can interact with most others, but is not reasonable for the more diverse community in~\citet{Kopelke2017}.
-This demonstrates the importance of conducting a "sanity check" on the posterior distribution obtained from any given prior.
+This demonstrates the importance of conducting a ``sanity check" on the posterior distribution obtained from any given prior.
 

### 2019-03-04 manuscript/CI_interactions.tex
removed comments
added Tomas comments to reply, caught a mis-formatted quote in main text

@@
 
-  % \begin{figure}[h!]
-    %   \caption{Imperfect detection of interactions increases the number of samples required to be confident that an interaction never occurs.
-Assume that two species cannot interact (i.e., $\lambda=0$) and that the number of observed interactions follows a binomial distribution depending upon the number of observed interactions $k$ and observed co-occurrences $n$.
-The maximum likelihood estimate (MLE) for $\lambda_{ij}$ is $\lambda_{MLE}=\frac{k}{n}$.
-Note that $\lambda_{ij}$ is not a point estimate but rather a random variable with an unknown distribution.
-This means that if $k=0$ in a given sample, this does not necessarily imply that the two species will never interact.
-Rather, $k=0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless some chance that the two species \emph{could} interact.\\
-    %   Importantly, we can estimate the variance of $\lambda_{ij}$ as well as the MLE; available methods include the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]).
-The distribution of the MLE for $\lambda_{ij}$ thus obtained is a key part of the Bayesian distribution for $\lambda_{ij}$.
-    %   Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true credible interval for the interaction probability $\lambda_{ij}$ for a pair of species that has been observed co-occurring $n$ times but never interacting ($k=0$).
-The upper limit of the credible interval only reaches 0.1 (dashed, red line) with 35 observations.
-Thus, adding more observations is useful in controlling uncertainty, but the number of observations added must be very high unless we have some other reason to believe that an interaction cannot occur (i.e., a strong prior).}
-    %   \label{upper_limits}
-    %   \begin{center}
-      % \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
-    %   % \includegraphics*[width=.8\textwidth]{Figure_3.eps}
-    %   \end{center}
-    %   \end{figure}
-
   \begin{figure}[h!]
@@
     \includegraphics*[width=.8\textwidth]{figures/GP_pdfs_increasing_N_Zillis.eps}
-    % \includegraphics*[width=.8\textwidth]{Figure_4.eps}
+    % \includegraphics*[width=.8\textwidth]{Figure_3.eps}
     \end{center}
@@
 Diamonds indicate the maximum likelihood estimator for the mean probability of interaction.
-    Dashed lines indicate threshold probabilities of 0.01, 0.05, and 0.1. Note that the prior obtained from~\citet{Barbour2016} constrains the MLE  of $\lambda_{ij}$ above 0.01.}
+    Dashed lines indicate threshold probabilities of 0.01, 0.05, and 0.1.
+Note that both priors constrain the MLE of $\lambda_{ij}$ above 0.1 and that the posterior probability distributions become similar for very high $n$.}
     \label{prior_comparison}
@@
 
-  % \begin{figure}[h!]
-  %   \caption{Mean connectance, links per galler, nestedness (NODF), and links per natural enemy for networks assembled using posterior distributions based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017} occupied a narrow range.
-To obtain distributions of network properties, we created 100 ``posterior-sampling" networks and then, for each of these, created 100 ``filtered" networks by randomly sampling 50\%-99\% of the interactions included in the posterior-sampling network.
-This simulates imperfect detection of interactions in the field.
-Each point represents the mean (+/- SD) network property (e.g., connectance) obtained from a set of 100 filtered networks.
-The filtered networks cover a broader range of network properties than the posterior-sampling networks but the value of each property decreases as the strength of the detection filter increases.
-Values in the original web are indicated by dashed lines.}
-  %   \label{posterior_webs}    
-  %   \begin{center}
-  %   % \includegraphics[width=.8\textwidth]{figures/GP_posterior_properties_Zillis.eps}
-  %   % \includegraphics[width=.8\textwidth]{Figure_5.eps}
-  %   \end{center}
-  %   \end{figure}
-
 \clearpage

### 2019-03-05 manuscript/reply_to_reviewers_2.tex
resubmitted second round March 5

@@
 
-		[[Currently one vote for removing this paragraph and one vote for keeping it and strengthening the point]]
-		The Jeffreys prior gives a maximum likelihood estimate of 0.5 for the probability of an interaction between two species which have never been observed together.
+		% [[Currently one vote for removing this paragraph and one vote for keeping it and strengthening the point]]
+		An uninformative prior like the Jeffreys prior gives a maximum likelihood estimate of 0.5 for the probability of an interaction between two species which have never been observed together.
 Based on our understanding of ecological systems, this seems highly unlikely.
@@
 This leaves empirical and approximate Bayes as the only viable options, unless we are willing to revert to the assumption that unobserved interactions never occur.
-Certainly empirical Bayes is not perfect, but we are confident that it is still gives more reasonable expectations than ignoring the ecological networks literature.
+Certainly empirical Bayes is not perfect, but we are confident that it is still gives more reasonable expectations than ignoring the ecological networks literature completely.
 
@@
 Researchers are often more interested in the overall structure of the network or in some emergent property such as stability than in the relationships between niche proxies and interaction frequencies.
-In such cases, the number of additional interactions that we expect to be observed with further sampling is likely more important than the exact identity of those interactions, and an empirical Bayes approach is reasonable if a good trait-based model and trait information or not available.
+In such cases, the number of additional interactions that we expect to be observed with further sampling can be more important than the exact identity of those interactions, and an empirical Bayes approach is reasonable if a good trait-based model and trait information or not available.
 
 		Finally, we disagree with the Reviewer's contention that ``empirical Bayes assumes a kind of commonality among all networks".
-This is not so; empirical Bayes only assumes some commonality between the focal network and those used to construct the prior.
+This is not so; empirical Bayes only assumes some commonality between the focal network and \emph{those used to construct the prior}.
+Empirical Bayes does not imply anything about networks not referred to in the prior.
 We have revised the text to emphasise the need to use similar networks to construct an empirical Bayes prior and note that \emph{Appendix S7} demonstrates the pitfalls of basing an empirical Bayes prior on a network with little commonality with the focal system.
-[[The importance of using prior information from similar networks is a small but very important point that refers back to the core of our argument: if informatiom about a focal system is limited, then closing our eyes to what is known about similar networks and assuming \emph{a priori} that an unobserved interaction in any system is either equally (and rather highly) likely or equally impossible seems more than ``vaguely anti-ecology".
-After all, ecology advances by building upon previous insights and not by ignoring them in an effort to be ``conservative".
-It is essential to realise that ``uninformative" priors can lead to very biased results, just as poorly-chosen informative priors can.
-]][[This last portion strengthens the point in paragraph 2 but may be too much.]]
 
-		We believe that including an expanded reference to \emph{Appendix S7} as suggested below will help to address some of these concerns by demonstrating that empirical Bayes should \emph{not} be based on networks which have major differences from the focal system as this will lead to unreasonable predictions (in our case, although the taxa and interaction types involved were similar, the taxonomic resolution in the \citet{Barbour2016} and \citet{Kopelke2017} were very different).
+		We believe that including an expanded reference to \emph{Appendix S7} as suggested below will help to address some of these concerns by demonstrating that empirical Bayes should \emph{not} be based on networks which have major differences from the focal system as this will lead to unreasonable predictions (in our case, although the taxa and interaction types involved were similar, the taxonomic resolutions in \citet{Barbour2016} and \citet{Kopelke2017} were very different).
 To reinforce this point and make the role of empirical Bayes as a solution in the absence of trait-based models and/or trait information, we have made several minor revisions to the section introducing informative priors.

### 2019-03-05 manuscript/coverletter_revision_2.tex
resubmitted second round March 5

--- 2019-01-24 manuscript/coverletter_revision.tex
@@
 
-    My co-authors and I are pleased to resubmit our manuscript 
-    MEE-18-07-452:  \emph{A quantitative framework for investigating the reliability of empirical network construction} for consideration as a research article in \textbf{Methods in Ecology and Evolution}.
+    My co-authors and I are pleased to resubmit a second revision of our manuscript  MEE-18-07-452:  \emph{A quantitative framework for investigating the reliability of empirical network construction} for consideration as a research article in \textbf{Methods in Ecology and Evolution}.
 Dr.
-Aaron Ellison, Senior Editor, noted that the Associate Editor and four reviewers ``\emph{recognise a kernel of important work in this manuscript}" but that a significant shift in emphasis was necessary for this kernel to shine through.
-We believe that this revision has addressed the Associate Editor's and Reviewers' concerns and that our manuscript is clearer and more polished as a result.
-We thank them for their careful feedback.
+Aaron Ellison, Senior Editor, noted that the reviewer who provided additional feedback was very positive about our revision but requested more discussion about prior choice.
+We have expanded our discussion to emphasise the need for careful prior selection and now refer to a demonstration of problems that can result from a poorly-chosen prior.
+We believe that these additions, although slightly exceeding the normal length restrictions of \textbf{Methods in Ecology and Evolution}, have improved the manuscript enough to justify the extra length.
+We thank the Editor for his encouragement and the Reviewer for his further thoughtful feedback.
 
@@
 
-    We appreciate the opportunity to resubmit our manuscript and thank you for your continued consideration.
-We remain confident that our manuscript will be of broad interest to the readers of \textbf{Methods in Ecology and Evolution} because of the general nature of uncertainty around interactions and the broadly-applicable solution we offer.
-We are confident that our worked example and easy-to-use scripts will provide a useful template for empiricists and theoreticians alike.
+    We appreciate the opportunity to resubmit a further revision of our manuscript and thank you for your continued consideration.
+We remain confident that our manuscript will be of broad interest to the readers of \textbf{Methods in Ecology and Evolution}.
 We hope that you agree and eagerly await your reply.

### 2019-03-13 manuscript/CI_interactions.tex
commented out figures for manuscriptcentral
resubmitted second round March 5
working through SI

@@
 
-All data used in this study have been independently published and are accessible following the references provided in text.
+Data from~\citet{Kopelke2017} used in this manuscript is available from \emph{https://doi.org/10.1002/ecy.1832}.
+Data from~\citet{Barbour2016} used in this manuscript is available from \emph{https://doi.org/10.5061/dryad.g7805}.
+All code used in this manuscript is available in the online supporting information.
 
@@
     \begin{center}
-    \includegraphics*[width=.8\textwidth]{figures/GP_pdfs_increasing_N_Zillis.eps}
+    % \includegraphics*[width=.8\textwidth]{figures/GP_pdfs_increasing_N_Zillis.eps}
     % \includegraphics*[width=.8\textwidth]{Figure_3.eps}
@@
     \begin{center}
-    \includegraphics*[width=.8\textwidth]{figures/SG_pdfs_prior_comparison.eps}
+    % \includegraphics*[width=.8\textwidth]{figures/SG_pdfs_prior_comparison.eps}
     % \includegraphics*[width=.8\textwidth]{Figure_4.eps}

### 2019-03-13 manuscript/supplemental.tex
working through SI

@@
 
-\author{Alyssa R. Cirtwill$^{1\dagger}$, \&  Anna Ekl\"{o}f$^{1}$, Tomas Roslin$^{2}$, Kate Wootton$^{2}$, Dominique Gravel$^{3}$}
+\author{Alyssa R. Cirtwill$^{1,2\dagger}$, \&  Anna Ekl\"{o}f$^{1}$, Tomas Roslin$^{3}$, Kate Wootton$^{3}$, Dominique Gravel$^{4}$}
 \date{\small$^1$Department of Physics, Chemistry\\ 
@@
 Link\"{o}ping, Sweden\\
-\medskip $^2$ Department of Ecology\\ P.O. Box 7044, Swedish University of Agricultural Sciences \\ SE-750 07 Uppsala, Sweden \\
-\medskip$^3$ D\'{e}partement de biologie\\ 
+\medskip $^2$
+Current address: Department of Ecology,\\
+Environment, and Plant Sciences (DEEP)\\
+Stockholm University\\
+Stockholm, Sweden\\
+\medskip $^3$ Department of Ecology\\ P.O. Box 7044, Swedish University of Agricultural Sciences \\ SE-750 07 Uppsala, Sweden \\
+\medskip$^4$ D\'{e}partement de biologie\\ 
 Universit\'{e} de Sherbrooke\\ 
@@
 
-\linenumbers
+% \linenumbers
 
@@
 We ensured that each network had at least one link per consumer and per resource.
-For each network, we calculated the mean number of links per consumer, mean number of links per resource, and nestedness (NODF) as described in the main text.
+For each network, we calculated the mean number of links per consumer, mean number of links per resource, and nestedness (NODF).
 For simplicity, we assume that there is no interaction uncertainty in this system (i.e., all interactions are either 100\% feasible or 100\% unfeasible based on species' traits).
@@
   With each additional layer of uncertainty, the number of consumers and resources included in the web decreased (mean 49.8 of each species type in detection-filter webs and mean 48.6 of each type in process-filtered webs).
-The connectance and number of links per consumer and per resource decreased significantly at each level (Fig.~\ref{sim_props}A,B,D; $p$\textless0.001 in all cases based on one-tailed Student's t tests).
+The connectance and number of links per consumer and per resource decreased significantly at each level (Fig.~\ref{sim_props}A, B, D; $p$\textless0.001 in all cases based on one-tailed Student's t tests).
 The effects of uncertainty on nestedness were less predictable, particularly in the detection-filtered webs where variability was much higher than in other web types.
@@
 Despite these benefits, we note that there are limits to the utility of increased sampling.
-Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present~\citep{Gravel2018}), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig.
+Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present [\citealp{Gravel2018}]), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig.
 2C, main text).
@@
         \noindent\emph{
-          degree=c(14, 4, 2, 3, 17, 6, 2, 15, 1, 1)
-            }.
+          degree=c(14, 4, 2, 3, 17, 6, 2, 15, 1, 1)}.
           \vspace{12pt}
@@
         \noindent\emph{
-           int\_probs = c(0.358, 0.110, 0.055, 0.082, 0.468, 0.165, 0.055, 0.412, 0.028, 0.028) }.
+           int\_probs = c(0.358, 0.110, 0.055, 0.082, 0.468, 0.165, 0.055, 0.412, 0.028, 0.028)}.
           \vspace{12pt}
 
-        The mean of these interaction probabilities is 0.176, approximately two-thirds the $\lambda_{ij,MLE}$ obtained from the observed data.
+        The mean of these interaction probabilities is 0.176, approximately two-thirds of the $\lambda_{ij,MLE}$ obtained from the observed data.
 We can use the distribution of these interaction probabilities as our prior distribution and estimate the uncertainty surrounding our $\lambda_{ij,MLE}$.
@@
       the Arctic. Since the dataset includes repeated visits to a number of sites, the data set 
-      contains 641 site-visits. Here we take the more conservative approach and pool visits to the same site for a sample size of 374 sub-networks.
+      contains 641 site visits. Here we take the more conservative approach and pool visits to the same site for a sample size of 374 sub-networks.
 
@@
       nodes. Interactions were determined by dissecting and rearing gall 
-      inhabitants from 165,424 galls. Some sites were visited repeatedly, for a 
-      total of 641 site-visits. We consider these to be repeated samples and 
-      take the 374 unique sites as our sample size.
+      inhabitants from 165,424 galls.
 
@@
 For the \emph{Salix}-galler network, these parameters were: $\bar\lambda_{ij}$=0.028, var($\lambda_{ij}$)=8.60$\times$10$^{-5}$; note that this mean is much lower than that obtained using a prior based on~\citet[Data available from the Dryad Digital Repository: https://doi.org/10.5061/dryad.g7805]{Barbour2016}.
-Note that, despite the intensive sampling in the~\ref{Kopelke2017} dataset, most \emph{Salix}-galler pairs were never observed co-occurring (3,986/4,992; Fig.~\ref{histograms}).
+This low mean corresponds to the fact that, despite the intensive sampling in the~\citet{Kopelke2017} dataset, most \emph{Salix}-galler pairs were never observed co-occurring (3,986/4,992; Fig.~\ref{histograms}).
 

### 2019-03-13 manuscript/supplemental.tex
updated supporting info

@@
 
-        In our dataset, the entire 95\% credible interval for the probability of an interaction between a \emph{Salix}-galler pair was (0.013, 0.049).
+        In our dataset, the 95\% credible interval for the probability of an interaction between a \emph{Salix}-galler pair was (0.013, 0.049).
 We may therefore be 95\% confident that the interaction probability for \emph{Salix} and galler species that have not been observed co-occurring is below 0.05.
@@
       \begin{figure}[h!]
-        \caption{Using prior distribution based on the \emph{Salix}-galler and galler-natural enemy networks in~\citet{Barbour2016}, we can calculate posterior distributions for the probability of interaction ($\lambda_{ij}$) between two species that have not yet been observed interacting.
+        \caption{Using prior distributions based on the \emph{Salix}-galler and galler-natural enemy networks in~\citet{Barbour2016}, we can calculate posterior distributions for the probability of interaction ($\lambda_{ij}$) between two species that have not yet been observed interacting.
 Here we show posterior distributions for each $\lambda_{ij}$ in each network ranging from the prior distribution ($n_{ij}=0$ observed co-occurrence) to the distribution obtained when the pair of species has been observed co-occurring 100 times.
@@
 Likewise, the maximum likelihood estimator for the mean probability of interaction (diamonds at top of each panel) approaches zero and the 95\% credible interval (lines at top of each panel) narrows as sample size increases.
-\textbf{A)} The posterior distributions for the \emph{Salix}-galler component are always wider and farther from zero than those for \textbf{B)} the galler-natural enemy component.
-This is likely because the prior distribution for the galler-natural enemy component of the network was both narrower and had a mean closer to that in the~\citet{Kopelke2017} data than did the \emph{Salix}-galler component.}
+\textbf{A)} The posterior distributions for the \emph{Salix}-galler and \textbf{B)} the galler-natural enemy component are substantially wider than those obtained using the~\citet{Kopelke2017} data to inform the prior.
+This is likely because the mean probabilities of interaction in the~\citet{Barbour2016} data were substantially higher than those in the present study.}
         \label{Salix_pdfs}
@@
 Note that the number of samples required to reach any given threshold is larger for \textbf{A)} the \emph{Salix}-galler network than for \textbf{B)} the galler-natural enemy network.
-In the galler-natural enemy network, the credible interval for a pair of species with no observed co-occurrences was 0.364.
+In the galler-natural enemy network, the maximum likelihood estimate for $\lambda_{ij}$ for a pair of species with no observed co-occurrences was 0.364.
 All pairs of species therefore have $\lambda_{ij}$\textless0.5.}
@@
       Considering the galler-natural enemy networks, the connectance, mean links per galler, and mean links per natural enemy were also much lower in the observed web (C=0.078, $L_{galler}$=9.99, and $L_{natural enemy}$=7.45, respectively) than in the posterior webs (0.183 $\leq$ C $\leq$ 0.196, 17.5 $\leq L_{galler} \leq$ 18.9, and 23.0 $\leq L_{natural enemy} \leq$ 24.8).
-When the detection probability was relatively low (i.e., 50\%), however, the properties of randomised networks became similar to those in the observed webs (Fig.~\ref{posterior_webs_Barbour}B,D,F).
+When the detection probability was relatively low (i.e., 50\%), however, the properties of randomised networks became similar to those in the observed webs (Fig.~\ref{posterior_webs_Barbour}B, D, F).
 Nestedness was higher in the observed network (NODF=6.85) than in the posterior networks (6.30 $\leq NODF \leq$ 6.74; Fig.~\ref{posterior_webs_Barbour}H), but network structure was much more similar in the observed and posterior galler-natural enemy networks than in the \emph{Salix}-galler networks.

### 2019-03-14 manuscript/CI_interactions.tex
added a dumb repo for redundant code access

@@
 Data from~\citet{Barbour2016} used in this manuscript is available from \emph{https://doi.org/10.5061/dryad.g7805}.
-All code used in this manuscript is available in the online supporting information.
+All code used in this manuscript is available in the online supporting information or can be accessed via \emph{github.com/cirtwill/Constructing-quantitative-interaction-networks} or https://doi.org/10.5281/zenodo.2593695.
 

### 2019-03-26 manuscript/CI_interactions_accepted.tex
added disclaimers

--- 2019-03-14 manuscript/CI_interactions.tex
@@
 
-\vspace{-.4in}
+\vspace{-.2in}
+
+This is the peer reviewed version of the following article:~\citet{Cirtwill2019}, which has been published in final form at \textbf{Methods in Ecology and Evolution} (DOI: 10.1111/2041-210X.13180).
+This article may be used for non-commercial purposes in accordance with Wiley Terms and Conditions for Use of Self-Archived Versions.
 
@@
 
-\begin{spacing}{2.0}
+\begin{spacing}{1.0}
 
@@
 
-\linenumbers
+\end{spacing}{1.0}
+\begin{spacing}{1.5}
+
+% \linenumbers
 \clearpage
@@
 
-Data from~\citet{Kopelke2017} used in this manuscript is available from \emph{https://doi.org/10.1002/ecy.1832}.
+Data from~\citet{Kopelke2017} used in this manuscript is available from the Data Paper \emph{https://doi.org/10.1002/ecy.1832}.
 Data from~\citet{Barbour2016} used in this manuscript is available from \emph{https://doi.org/10.5061/dryad.g7805}.
@@
     % \includegraphics*[height=.45\textheight]{figures/conceptual_fig.eps}
-    % \includegraphics*[height=.5\textheight]{Figure_1.eps}
+    \includegraphics*[height=.5\textheight]{Figure_1.eps}
     \end{center}
@@
       % \includegraphics*[height=.6\textheight]{figures/GP_histogram.eps}
-      % \includegraphics*[height=.6\textheight]{Figure_2.eps}
+      \includegraphics*[height=.6\textheight]{Figure_2.eps}
       \end{center}
@@
     % \includegraphics*[width=.8\textwidth]{figures/GP_pdfs_increasing_N_Zillis.eps}
-    % \includegraphics*[width=.8\textwidth]{Figure_3.eps}
+    \includegraphics*[width=.8\textwidth]{Figure_3.eps}
     \end{center}
@@
     % \includegraphics*[width=.8\textwidth]{figures/SG_pdfs_prior_comparison.eps}
-    % \includegraphics*[width=.8\textwidth]{Figure_4.eps}
+    \includegraphics*[width=.8\textwidth]{Figure_4.eps}
     \end{center}

### 2019-03-26 manuscript/CI_preprint.tex
added disclaimers

@@
 
-\vspace{-.4in}
+\vspace{-.2in}
+
+This is the pre-peer reviewed version.
+This article has been published in final form at \textbf{Methods in Ecology and Evolution} (DOI: 10.1111/2041-210X.13180).
+This article may be used for non-commercial purposes in accordance with Wiley Terms and Conditions for Use of Self-Archived Versions.
+Text of the peer-reviewed accepted version will be uploaded March 26, 2020.
 
